### 2016-08-12 ms_pre_post.Rmd
Initial commit of the manuscript, empty

---
title: "Evolution of precopulatory and postcopulatory inbreeding behaviour"
author: "A. Bradley Duthie et al."
date: "May 27, 2016"
output:
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
  pdf_document:
    fig_caption: yes
  html_document: default
linestretch: 1
---

******************************

```{r, echo=FALSE}
figscale <- 1.0; # Change the scale of a figure
```

Abstract
===================================================

Introduction
===================================================

******************************-

Model
===================================================

******************************

Results
------------------------------------------------

******************************

Discussion
===================================================

Acknowledgements
----------------------------------------------

This work was funded by a European Research Council Starting Grant to JMR.

**************************

References
----------------------------------------------

### 2016-08-15 initial_analysis.R
Initial commit of R script for making 3D plots analysing initial data

@@ -1,0 +1,235 @@
+#==========================================================================
+
+rm(list=ls()); 
+                                                                     
+setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
+
+evo  <- read.table(file="evo.txt", header=FALSE);
+ela  <- evo[evo[,6]==4999,];
+write.table(x=ela, file="ela.txt", col.names=FALSE, row.names=FALSE);
+
+#==========================================================================
+
+
+rm(list=ls()); 
+library(scatterplot3d);
+setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
+
+ela <- read.table(file="ela.txt", header=FALSE);
+
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX Three dimensional scatter plot  XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# First, let's look at the results for Beta = 0 (no inbreeding depression)
+# Note, we're using past modelling to assume that inbreeding preference is
+# favoured in the absence of inbreeding depression.
+# For now, we also have an arbitrary threshold of 1 for indicating selection
+# for or against a trait -- might find a less arbitrary way to do this,
+# but given the type of modelling, I don't think it's unreasonable.
+# -----------  BETA = 0  -------------------------------------------------#
+setEPS();
+cairo_ps("EC_Beta_0.eps",family="Arial",height=7,width=7);
+elaB0 <- ela[ela[,2]==0,]; # Now we have juat the Beta = 0 results in ela
+resB0 <- rep(0,dim(elaB0)[1]); # This vector will find one of four results
+for(i in 1:dim(elaB0)[1]){ # Doing this as a loop just to show the logic
+   if(elaB0[i,7] >= 1 & elaB0[i,9] >= 1){
+       resB0[i] <- "red"; # Pre and post-copulatory evolved
+   }
+   if(elaB0[i,7] >= 1 & elaB0[i,9] < 1){
[…]

### 2016-08-15 code/Inbreed.c
Initial add of all code

@@ -1,0 +1,708 @@
+/***********************************************************************************/
+/* Program: Inbreed.c
+   By: Brad Duthie                                             
+   Description: IBM to simulate inbreeding tolerance/avoidance
+   Compile: gcc Inbreed.c -ansi -Wall -pedantic    */
+/***********************************************************************************/
+
+#include <time.h>
+#include <math.h>
+#include <stdio.h>
+#include <stdlib.h>
+#include <unistd.h>
+#include "array.h"
+#include "randnormINT.h"
+#include "randnorm.h"
+#include "landscape.h"
+#include "arraysort2D.h"
+#include "vectorrank.h"
+#include "Rbuild.h"
+#include "mateselect.h"
+#include "babies.h"
+#include "parents.h"
+#include "mortality.h"
+#include "retain.h"
+#include "deadbottom.h"
+#include "sumstats.h"
+#include "inbrdep.h"
+#include "SampleNoReplace.h"
+
+#define CORES 1 /* For running in parallel, set cores > 1 */
+#define length(x) (sizeof (x) / sizeof *(x))
+
+void Inbreed(int mc, int M, int Imm, int Clu, double *RES, double Beta1, int rep,
+    int Active, int Neutral, int load, double alpha, int gen, int muSt, double mu, 
+    int Kind, int xlen, int prP, double ImmSD, int wpe, int poe, int epe, 
+    double poadj, double epadj, double wpadj, double Scost, double Pcost, 
+    double Ecost, int conSt, int snap, int PostSel, int msel, int EpRestr, 
+    int WpRestr, int condk, int PreSel, int wpVsep, int PreserC){
+
+    /* =========================================================================*/
+    /* =========================================================================*/
+    /* DEFINE VARIABLES TO BE USED: */
+    /* =========================================================================*/
+    /* =========================================================================*/
+
+    int i, j, k, l, h, g; 
+    int Ind, suc, Liv, OLiv, cols, prevOff, removed, pid, pidadd, pidcmb;
+    int Nloci;         /* The number of loci in simulated genome */
+    int TotAlleles;    /* Keep track of total alleles in sim */
+    int StInds;        /* The initial number of females and males */
+    int *O;            /* Keeps track of offspring per nest in a generation */
+    int loadstart;     /* where inbreeding load loci start on table */
+    int Neutstart;     /* Where do the neutral's start on the table */
+    int *shuffImm;     /* Shuffle vector for immigrants */
+
[…]

### 2016-08-15 code/Inbreed.h

@@ -1,0 +1,28 @@
+#include <time.h>
+#include <math.h>
+#include <stdio.h>
+#include <stdlib.h>
+#include <unistd.h>
+#include "array.h"
+#include "randnormINT.h"
+#include "randnorm.h"
+#include "landscape.h"
+#include "arraysort2D.h"
+#include "vectorrank.h"
+#include "Rbuild.h"
+#include "mateselect.h"
+#include "babies.h"
+#include "parents.h"
+#include "mortality.h"
+#include "retain.h"
+#include "deadbottom.h"
+
+#define CORES 2
+#define length(x) (sizeof (x) / sizeof *(x))
+
+void Inbreed(int mc, int M, int Imm, int Clu, double *RES, double Beta1, int rep,
+    int Active, int Neutral, int load, double alpha, int gen, int muSt, double mu, 
+    int Kind, int xlen, int prP, double ImmSD, int wpe, int poe, int epe, 
+    double poadj, double epadj, double wpadj, double Scost, double Pcost, 
+    double Ecost, int conSt, int snap, int PostSel, int msel, int EpRestr, 
+    int WpRestr, int condk, int PreSel, int wpVsep, int PreserC);

### 2016-08-15 code/PolyIn.c

@@ -1,0 +1,115 @@
+/***********************************************************************************/
+/* Program: PolyIn.c
+   By: Brad Duthie                                             
+   Description: Calls Inbreed.c multiple times to simulate different inbreeding
+        scenarios.
+   Compile: To compile with makefile, type `make' within directory, then hit ENTER
+   Run:     To run, type `./PolyIn' on command line, then hit ENTER   */
+/***********************************************************************************/
+#include <time.h>
+#include <math.h>
+#include <stdio.h>
+#include <stdlib.h>
+#include <unistd.h>
+#include "Inbreed.h"
+#include "array.h"
+
+int main(void){
+
+    int    mc, M, Imm, Clu, rep, i, j, xlen, Pedi, prP, conSt, snap, msel, condk;
+    int    Active, Neutral, load, gen, muSt, Kind, EpRestr, WpRestr, PreSel, PostSel;
+    int    PreserC, wpVsep;
+    double Beta1, alpha, mu, *RES, ImmSD, poadj, epadj, wpadj, Scost, Pcost, Ecost;
+    double poe, wpe, epe;
+
+    /* =========== VARIABLES BETWEEN THE Xs BELOW ADJUST MODEL PARAMETERS ================*/
+    /*  XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX   */
+    /* ===================================================================================*/
+    /* Model parameter values                                                             */
+    /* ===================================================================================*/
+    mc      = 100;    /* Number of females a male can mate with (as a social mate)        */
+    M       = 0;      /* Maximum age (0 = non-overlapping gen; do not make >0 [ped error])*/
+    Imm     = 5;      /* Number of immigrants per generation                              */
+    Clu     = 8;      /* Clutch size for each female                                      */
+    alpha   = 1.0;    /* Strength of inbreeding avoidance/preference                      */
+    Beta1   = 0.0000; /* Selection coefficient on deleterious recessives                  */
+    Scost   = 0.0000; /* Cost of having tendancy to non-randomly select social mates      */
+    Pcost   = 0.0000; /* Cost of having tendancy to engage in polyandry                   */
+    Ecost   = 0.0000; /* Cost of having tendancy to non-randomly select extra-pair mates  */
+    gen     = 5000;   /* Number of generations per replicate (default 5000)               */
[…]

### 2016-08-15 code/PolyIn.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+# SGE SUBMISSION SCRIPT 
+# This is an embarrassingly parallel simulation
+# Submit to 1 core -- should print to one output file
+# I estimate that this program will take less than 24 hrs to run
+#
+#$ -V -cwd -l h_rt=24:00:00 -o out.$JOB_ID
+./PolyIn

### 2016-08-15 code/Rbuild.c

@@ -1,0 +1,130 @@
+/***********************************************************************************/
+/* Program: Rbuild.c
+   By: Brad Duthie                                             
+   Description: Uses kinship matrix from previous generation(s) to build new kinships.
+   This is called Rbuild.c, but it really is calculating kinships, not relatedness
+
+   Compile: gcc Rbuild.c -ansi -Wall -pedantic    */
+/***********************************************************************************/
+
+#include <stdio.h>
+#include <math.h>
+#include "array.h"
+
+void Rbuild(double **ID, double **Rmat, double **Rmof, int Liv, int OLiv){
+
+    int i, j; 
+    int MomP, DadP, Om, Od;
+    double rMmuP, rDmuP, rval, w, x, y, z;
+
+    /* =====================================================================*/
+    /* Below finds the correct kinship value between all individuals except */
+    /* immigrants and their children                     */
+    /* =====================================================================*/
+    for(i=0; i<Liv; i++){
+        /* Find Mom position -- -1 if immigrant */
+        if(ID[i][5] < 0){
+            MomP = -1;
+        }else{
+            MomP = 0; /* printf("\t\t\t%f\n",Rmat[0][0]); */
+            while(ID[i][5]!=Rmat[MomP][0]){
+                MomP++;
+            }
+        }
+        /* Find Dad position -- -1 if immigrant */
+        if(ID[i][6] < 0){
+            DadP = -1; 
+        }else{
+            DadP = 0; /* Below finds the matrix position of Dad */
+            while(ID[i][6]!=Rmat[DadP][0]){
+                DadP++;
+            }
+        } 
+
+        if(MomP < 0 || DadP < 0){
+            Rmof[i][i+1] = 1; 
+        }else{
+            Rmof[i][i+1] = 1 + Rmat[MomP][DadP+1]; 
+        }
+
+        for(j=0; j<i; j++){ /* Looking for R for each offspring... */
+            /* Find r between i Mom and j Mom (x) and Dad (y) */
+            /* Establish who the parents are =======================*/
+            if(ID[j][5] < 0){
+                Om = -1;
+            }else{
+                Om = 0; /* Other mom's position */
+                while(ID[j][5]!=Rmat[Om][0]){
+                    Om++;
+                } /* Keeps looking up until hits Mom's Rmat pos */
+            }
+            if(ID[j][6] < 0){
+                Od = -1;
+            }else{
[…]

### 2016-08-15 code/Rbuild.h

@@ -1,0 +1,4 @@
+#include <stdio.h>
+#include <math.h>
+
+void Rbuild(double **ID, double **Rmat, double **Rmof, int Liv, int OLiv);

### 2016-08-15 code/SampleNoReplace.c

@@ -1,0 +1,42 @@
+/***************************************************************/
+/* Program: randunif.c
+   By: Brad Duthie                                             
+   Description: Will sample size "samp" from Vec without replace
+   Compile: gcc randpois.c -ansi -Wall -pedantic    */
+/***************************************************************/
+
+#include "randunif.h" /* Need random unform numbers */
+#include "array.h" /* Array used to handle vectors */
+
+void SampleWithoutReplacement(int Pop, int samp, int *Vec){
+
+    int n = samp;
+    int N = Pop;
+
+    int t = 0; /* total input records dealt with */
+    int m = 0; /* number of items selected so far */    
+    double u;
+
+    while (m < n){
+        u = randunif();
+        if ((N - t)*u >= n - m ){
+            t++;
+        }else{
+           Vec[m] = t;
+           t++; 
+           m++;
+        }
+    }
+}
+
+void shufflesamp(int *Vec, int samp){
+    int i, j, temp;
+    for (i = samp-1; i > 0; i--){
+        j      = floor(randunif()*(i+1));
+        temp   = Vec[i];
+        Vec[i] = Vec[j];
+        Vec[j] = temp;
+    }
+}
+
+

### 2016-08-15 code/SampleNoReplace.h

@@ -1,0 +1,6 @@
+#include "randunif.h"
+#include "array.h"
+
+void SampleWithoutReplacement(int Pop, int samp, int *Vec);
+
+void shufflesamp(int *Vec, int samp);

### 2016-08-15 code/babies.c

@@ -1,0 +1,25 @@
+/***********************************************************************************/
+/* Program: babies.c
+   By: Brad Duthie                                             
+   Description: Uses the tables ID and Roff to make new offspring.
+   Compile: gcc babies.c -ansi -Wall -pedantic    */
+/***********************************************************************************/
+
+#include <stdio.h>
+#include <math.h>
+#include "array.h"
+
+int babies(double **ID, int Clu, int i){
+
+    int Off;
+
+    Off  = 0;
+
+    if(ID[i][8]<0){    /* If female did not find a mate  */
+        Off = 0;       /* She produces no offspring      */
+    }else{             /* If she did find a mate         */
+        Off = Clu;     /* She produces Clu offspring     */
+    }
+
+    return Off;
+}

### 2016-08-15 code/babies.h

@@ -1,0 +1,5 @@
+#include <stdio.h>
+#include <math.h>
+#include "array.h"
+
+int babies(double **ID, int Clu, int i);

### 2016-08-15 code/inbrdep.c

@@ -1,0 +1,98 @@
+/***********************************************************************************/
+/* Program: inbrdep.c 
+   By: Brad Duthie  
+   
+   Description: Two functions to transfer offspring information and check survival 
+   Compile: gcc inbrdep.c -ansi -Wall -pedantic    */
+/***********************************************************************************/
+
+#include <stdio.h>
+#include <math.h>
+#include "array.h"
+#include "randunif.h"
+
+/* This function transfers information from OFF to REGR, as needed */
+void RegrTr(double **REGR, double **OFF, int prevOff){
+
+    int i;
+
+    for(i=0; i<prevOff; i++){
+        REGR[i][0] = OFF[i][0]; /* Get individual number */
+        REGR[i][1] = OFF[i][7]; /* This will store an individual f coefficient */
+        REGR[i][2] = 0; /* Empty now, use for something later? */
+        REGR[i][3] = OFF[i][1];
+        REGR[i][4] = 1; /* Start assuming complete survival probability, adj later */
+        REGR[i][5] = 0; /* Assume dead unless proved otherwise by becoming an adult */
+        REGR[i][6] = OFF[i][2]; /* This was the juvenile probability of survival */
+        REGR[i][7] = 0; /* An individual's offspring production will go here */
+    }
+}
+
+/* This function checks to see if individuals from original OFF ultimately survived */
+void inbrdep(double **ID, double **REGR, int prevOff, int Liv, int M){
+
+    int i, j;
+
+    for(i=0; i<Liv; i++){
+        if(ID[i][4] > -1 && ID[i][4] <= M){ /* If i is alive */
+            for(j=0; j<prevOff; j++){ /* Go through REGR and find it, j */
+                if(ID[i][0] == REGR[j][0]){
+                    REGR[j][5] = 1; /* Add a one to indicate survival */
+                    break; /* No need to keep through this loop */
+                }
+            }
+        }
+    }
+}
+
+
+/* Prints kinship relative to an indivual to a kinship file (use with pedigree) */
+void printMeanKinship(double **Rmof, double **ID, int Liv,
+    int Active, int Neutral, int Neutstart, int load, int loadstart, int pid,
+    double Beta1, double Pcost, int WpRestr, int EpRestr){
+
+    int    j, k, i;
+    double a, b, c;
[…]

### 2016-08-15 code/inbrdep.h

@@ -1,0 +1,12 @@
+#include <stdio.h>
+#include <math.h>
+#include "array.h"
+
+
+void RegrTr(double **REGR, double **OFF, int prevOff);
+
+void inbrdep(double **ID, double **REGR, int prevOff, int Liv, int M);
+
+void printMeanKinship(double **Rmof, double **ID, int Liv,
+    int Active, int Neutral, int Neutstart, int load, int loadstart, int pid,
+    double Beta1, double Pcost, int WpRestr, int EpRestr);

### 2016-08-15 code/mateselect.c

@@ -1,0 +1,184 @@
+/***********************************************************************************/
+/* Program: mateselect.c
+   By: Brad Duthie                                             
+   Description: Allows the dominant sex to select a mate based on a set of criteria.
+   Compile: gcc mateselect.c -ansi -Wall -pedantic    */
+/***********************************************************************************/
+
+#include <stdio.h>
+#include <math.h>
+#include "array.h"
+#include "randunif.h"
+
+void mateselect(double **ID, double **Rmat, int Liv, int Nloci, int M, int mc,
+    int Active, double alpha, int Kind, int wpe, double wpadj, int WpRestr){
+    /* Note that ID should be sorted now, females at array top */    
+    /* Note that females should be sorted by quality at top of ID */
+
+    int i, j, k, h, ch, s, no, ccc, PrCount, g;
+    double r, new, *PrM, *PrT, PrS, PrR, PrC;
+
+    /* ===========================================================*/
+    /* Determine where female and male sex row begins in ID array */
+    /* ===========================================================*/        
+    k = 0; /*Below counts the number of females */
+    for(i=0; i<Liv; i++){
+        if(ID[i][1]==0 && ID[i][4] > -1 && ID[i][4] <= M && ID[i][2] > -1){
+            k++; 
+        }else{
+            break;
+        }
+    } /* So the females that can breed end at k */
+
+    s = 0; /* Below gets the starting point for males */
+    for(i=0; i<Liv; i++){
+        if(ID[i][1]==0){
+            s++;
+        }else{
+            break;
+        }
+    } /* So the males start at s */
+
+    /* =======================================================================*/
+    /* Each female individual assesses and chooses one or more mates          */
+    /* =======================================================================*/
+
+    MAKE_1ARRAY(PrM,Liv); /* Vector for the probability of selecting an individual */
+    MAKE_1ARRAY(PrT,Liv); /* Cumulative probability vector used for sampling */
+
+    for(i=0; i<k; i++){ /* For each female, starting with best */
+        for(j=0; j<Liv; j++){ /* For each other individual in the population */
+            PrM[j] = 0; /* Just start everything off with zero */
+            PrT[j] = 0; /* The cumulative vector elements are zeros too */
+        }
+        ch  = -1; /* Initially, the individual has not made a mate choice(s) */
+        no  = 0;  /* Used to break out of loop later if no more mates available */
[…]

### 2016-08-15 code/mateselect.h

@@ -1,0 +1,6 @@
+#include <stdio.h>
+#include <math.h>
+#include "array.h"
+
+void mateselect(double **ID, double **Rmat, int Liv, int Nloci, int M, int mc,
+    int Active, double alpha, int Kind, int wpe, double wpadj, int WpRestr);

### 2016-08-15 code/mortality.c

@@ -1,0 +1,39 @@
+/***********************************************************************************/
+/* Program: mortality.c
+   By: Brad Duthie                                             
+   Description: Kills off individuals from both the ID and OFF matrices
+   Compile: gcc mortality.c -ansi -Wall -pedantic    */
+/***********************************************************************************/
+
+#include <stdio.h>
+#include <math.h>
+#include "array.h"
+#include "randunif.h"
+
+void mortality(double **ID, double **OFF, int Liv, int l, int M, double Beta1){
+
+    int i;
+    double survival;
+
+    /* First kill the older generation individuals in Liv */
+    for(i=0; i<Liv; i++){ /* If individuals are too old (over M -- usually zero), die */
+        if(ID[i][4]>=(M+1)){ /* They now have no location and -1 age */
+            ID[i][2] = -1;
+            ID[i][3] = -1;
+            ID[i][4] = -1; 
+        }
+        if(ID[i][2] < 0){    /* And, for added measure, ensure they stay dead below */
+            ID[i][4] = -1;
+        }
+    }    
+
+    for(i=0; i<l; i++){ /* Next figure out if anyone dies in the new generation, OFF */
+        survival   = exp(-1 * Beta1 * OFF[i][7]);
+        OFF[i][2]  = survival; /* Put in column 2 for now (est. inbr. dep in sumstat)*/
+        if(randunif()>survival){ /* Check to see if the individual dies */
+            OFF[i][4] = -1;  /* If so, then add the -1 in column 4 */
+        }
+    } /* All juveniles should now have either survived, or died as juveniles */
+}
+
+

### 2016-08-15 code/mortality.h

@@ -1,0 +1,6 @@
+#include <stdio.h>
+#include <math.h>
+#include "array.h"
+#include "randunif.h"
+
+void mortality(double **ID, double **OFF, int Liv, int l, int M, double Beta1);

### 2016-08-15 code/parents.c

@@ -1,0 +1,418 @@
+/***********************************************************************************/
+/* Program: parents.c
+   By: Brad Duthie                                             
+   Description: Determines which offspring came from which parents, and properties.
+   Compile: gcc babies.c -ansi -Wall -pedantic    */
+/***********************************************************************************/
+
+#include <stdio.h>
+#include <math.h>
+#include "array.h"
+#include "randunif.h"
+#include "randpois.h"
+#include "randnorm.h"
+
+void parents(double **ID, double **OFF, double **Rmof, int *O, int Nloci, int Ind, 
+    int k, int l, int Clu, int Liv, int gener, double Beta1, double alpha,
+    double *RES, int rep, int loadstart, int load, int Active, int prP, int Neutstart,
+    int Neutral, int Kind, int M, int poe, int epe, double poadj, double epadj, 
+    double mu, double mumu, double musd, int conSt, int PostSel, int pid, int msel,
+    int lastgen, int EpRestr, double Pcost, int condk, int PreSel, int wpVsep){
+
+    int i, j, g, h, m, s, MomP, DadP, extra, nmale, ch, PrCount, ccc, socmat;
+    int *MALES, rejectm;
+    double pscore, nscore, mscore, gPy, r, PrS, PrR, PrC, new, a, prsoc;
+    double *PrM, *PrT, *Mse;
+    FILE *Pedigree, *Mates;
+
+    char matechar[20];  /* To print to the mate file */
+
+
+    /*===========================================================================*/
+    /* Social male in mating pool, need to select others?  ======================*/
+    /*===========================================================================*/
+    h     = 0;
+    extra = 0; /* Check to see if we need to find a new extra pair mate for nest */
+    MAKE_1ARRAY(MALES,2); /* Just so to not free something that doesn't exist */
+    MAKE_1ARRAY(Mse,2); /* Same as above, will only use if PostCsel > 0 */
+    for(i=0; i<l; i++){
+        if(i==O[h]){   /* If offspring # hits count of off nest*/    
+            h++;       /* Move to the next nest */
+            extra = 0; /* Need to find a new extra pair mate */
+        }
+        /* -- If new extra-pair males need to be selected -- who are they? */
+        if(extra == 0){ /* If a new males not yet selected as an epm */
+            gPy = 0.0;  /* Start out with a zero value for polyandry-like */ 
+            if(poe == 1){ /* no change (gPy = 0) if poe=0 */
[…]

### 2016-08-15 code/parents.h

@@ -1,0 +1,13 @@
+#include <stdio.h>
+#include <math.h>
+#include "array.h"
+#include "randunif.h"
+#include "randpois.h"
+#include "randnorm.h"
+
+void parents(double **ID, double **OFF, double **Rmof, int *O, int Nloci, int Ind, 
+    int k, int l, int Clu, int Liv, int gener, double Beta1, double alpha,
+    double *RES, int rep, int loadstart, int load, int Active, int prP, int Neutstart,
+    int Neutral, int Kind, int M, int poe, int epe, double poadj, double epadj,
+    double mu, double mumu, double musd, int conSt, int PostSel, int pid, int msel,
+    int lastgen, int EpRestr, double Pcost, int condk, int PreSel, int wpVsep);

### 2016-08-15 code/randpois.c

@@ -1,0 +1,24 @@
+/***************************************************************/
+/* Program: randpois.c
+   By: Brad Duthie                                             
+   Description: Will produce a Poisson distributed random number
+   Compile: gcc randpois.c -ansi -Wall -pedantic    */
+/***************************************************************/
+
+
+#include "randunif.h" /* Need randunif header file */
+
+int randpois(double lambda){
+    double L, u, p;
+    int k;
+
+    p = 1;
+    k = 0;
+    L = exp(-1*lambda);
+    do{
+        k++;
+        u = randunif();
+        p = p * u;
+    }while(p > L);
+    return k-1;
+}

### 2016-08-15 code/sumstats.c

@@ -1,0 +1,127 @@
+/***********************************************************************************/
+/* Program: sumstats.c
+   By: Brad Duthie                                             
+   Description: Returns summary stats for the inbreed program.
+   Compile: gcc mortality.c -ansi -Wall -pedantic    */
+/***********************************************************************************/
+
+#include <stdio.h>
+#include <math.h>
+#include "array.h"
+
+void sumstats(double *RES, double **OFF, int M, int Nloci, int loadstart, int load, 
+    int Neutstart, int Neutral, int Active, int l, int Imm, int xlen,
+    double **REGR, int generation, int prevOff){
+
+    int i, j;    
+    double g, k, h, d, x, y, Ex, Ey, Exy, sumx, SSx, SSy, *ActTr, *NeuTr;
+
+    MAKE_1ARRAY(ActTr, l);
+    MAKE_1ARRAY(NeuTr, l);
+    /* ==========================================================*/
+    /* Calculate mean allele values     =========================*/
+    /* ==========================================================*/        
+    g    = 0;
+    h    = 0;
+    d    = 0;
+    k    = 0;
+    for(i=0; i<l; i++){
+        if(OFF[i][4] >= 0 && OFF[i][4] <= M){
+            x = 0;
+            y = 0;
+            for(j=0; j<Active; j++){
+                x += OFF[i][((4*j)+10)];
+                x += OFF[i][((4*j)+11)];
+            }
+            g += x;
+            ActTr[i] = x;
+            for(j=0; j<Neutral; j++){
+                y += OFF[i][((4*j)+Neutstart)];
+                y += OFF[i][((4*j)+Neutstart+1)];
+            }
+            h += y;
+            NeuTr[i] = y;
+            for(j=0; j<load; j++){
+                d += OFF[i][((4*j)+loadstart)];
+                d += OFF[i][((4*j)+loadstart+1)];
+            }
+            k += 2;
+        }
+    }
+
+    RES[0] = g / (Active * k);  /* Inbreeding allele frequency */
+    RES[1] = h / (Neutral * k); /* Polyandry allele frequency */
+    RES[2] = d / (load * k);    /* Neutral allele frequency */
+
[…]

### 2016-08-15 code/sumstats.h

@@ -1,0 +1,7 @@
+#include <stdio.h>
+#include <math.h>
+#include "array.h"
+
+void sumstats(double *RES, double **OFF, int M, int Nloci, int loadstart, int load, 
+    int Neutstart, int Neutral, int Active, int l, int Imm, int xlen,
+    double **REGR, int generation, int prevOff);

### 2016-08-15 code/Inbreed.c
Include a new command 'zallele', which, if set to a value of 1, initialises each zero generation individual's allele value randomly selecting from the distribution N(0,ImmSD). If it is anything else, all allele values will be initialised at zero

@@ -35,7 +35,7 @@ void Inbreed(int mc, int M, int Imm, int Clu, double *RES, double Beta1, int rep
     int Kind, int xlen, int prP, double ImmSD, int wpe, int poe, int epe, 
     double poadj, double epadj, double wpadj, double Scost, double Pcost, 
     double Ecost, int conSt, int snap, int PostSel, int msel, int EpRestr, 
-    int WpRestr, int condk, int PreSel, int wpVsep, int PreserC){
+    int WpRestr, int condk, int PreSel, int wpVsep, int PreserC, int zallele){
 
     /* =========================================================================*/
     /* =========================================================================*/
@@ -132,7 +132,7 @@ void Inbreed(int mc, int M, int Imm, int Clu, double *RES, double Beta1, int rep
     for(i=0; i<TotAlleles; i++){
         GenArch[i][0] = l; /* Row zero is denotes the locus */
         GenArch[i][1] = a; /* Row one denotes the allele */
-        GenArch[i][2] = randnorm(0,1); /* Row two denotes some allele value */ 
+        GenArch[i][2] = randnorm(0,ImmSD); /* Row two denotes some allele value */ 
         if((alleles[l]-1)==a){ /*Need -1 bc count one less than label (a) */ 
             l++;
             a = 0;
@@ -164,26 +164,53 @@ void Inbreed(int mc, int M, int Imm, int Clu, double *RES, double Beta1, int rep
         ID[i][7] = 0;                      /* Coefficient of inbreeding (F) */
         ID[i][8] = -1;                     /* Mate selection (-1 no mate yet) */
         ID[i][9] = 0;                      /* Within (0) or extra-pair (1) ? */
-        for(j=0; j<Nloci; j++){ /* This loop builds starting individual genomes */
-            /* Note below, all 0 alleles are made at the start */
-            a1[0] = floor(randunif()*(alleles[j]-1));
-            a1[1] = floor(randunif()*(alleles[j]-1));
-            ID[i][((4*j)+10)] = a1[0]; /* Adds first allele at locus */
-            ID[i][((4*j)+11)] = a1[1]; /* Adds second allele at locus */
-            suc = 0; /* Triggers break below when allele values are added */
-            for(k=0; k<TotAlleles; k++){ /*Adds norm distr. vals */
-                if(j==GenArch[k][0] && a1[0]==GenArch[k][1]){
-                    ID[i][((4*j)+12)] = GenArch[k][2];
[…]

### 2016-08-15 code/Inbreed.h

@@ -25,4 +25,4 @@ void Inbreed(int mc, int M, int Imm, int Clu, double *RES, double Beta1, int rep
     int Kind, int xlen, int prP, double ImmSD, int wpe, int poe, int epe, 
     double poadj, double epadj, double wpadj, double Scost, double Pcost, 
     double Ecost, int conSt, int snap, int PostSel, int msel, int EpRestr, 
-    int WpRestr, int condk, int PreSel, int wpVsep, int PreserC);
+    int WpRestr, int condk, int PreSel, int wpVsep, int PreserC, int zallele);

### 2016-08-15 code/PolyIn.c

@@ -18,7 +18,7 @@ int main(void){
 
     int    mc, M, Imm, Clu, rep, i, j, xlen, Pedi, prP, conSt, snap, msel, condk;
     int    Active, Neutral, load, gen, muSt, Kind, EpRestr, WpRestr, PreSel, PostSel;
-    int    PreserC, wpVsep;
+    int    PreserC, wpVsep, zallele;
     double Beta1, alpha, mu, *RES, ImmSD, poadj, epadj, wpadj, Scost, Pcost, Ecost;
     double poe, wpe, epe;
 
@@ -50,6 +50,7 @@ int main(void){
     PreSel  = 1;      /* Allow pre-copulatory mate selection for EPMs (0: no, 1:yes)      */
     PostSel = 1;      /* Allow post-copulatory mate selection for EPMs (0: no, 1: yes)    */
     PreserC = 0;      /* Preserve among-individual trait correlations in immigrants       */
+    zallele = 1;      /* Initial alleles at 0 (0) or randomly drawn from N(0,ImmSD) (1)   */
     /* ===================================================================================*/
     /* Genome attributes of individuals                                                   */
     /* ===================================================================================*/
@@ -66,7 +67,7 @@ int main(void){
     /* ===================================================================================*/
     /* Simulation details                                                                 */
     /* ===================================================================================*/
-    rep        = 40;    /* Simulations run                                                */
+    rep        = 4;     /* Simulations run                                                */
     Pedi       = 0;     /* Print last rep's pedigree? (0:no, 1:yes) WARNING: 200Mb file   */
     snap       = 1;     /* Last 2 gens pedigree for all reps printed? (0:no, 1:yes)       */
     msel       = 1;     /* Last 2 gens print mate selection of females? (0:no, 1:yes)     */
@@ -79,12 +80,10 @@ int main(void){
     i    = 0; /* Loops through different replicate simulations */
     prP  = 0; /* Indicator for actually printing the pedigree */
 
-    /* 
     Scost = randunif()*0.05;
     Pcost = randunif()*0.05;
     Ecost = randunif()*0.05;
-    */
-
+    
     while(i < rep){
         if(i == rep-1 && Pedi == 1){ /* If it's the last rep, and should print pedigree */
[…]

### 2016-08-16 initial_analysis.R
Add plots of trait dynamics over time for replicate simulations in which no costs are included. Also add 3D plots of pre and post-copulatory selection for simulations with random trait starting conditions, and add 3D plots showing costs in which polyandry versus monandry evolves

@@ -4,9 +4,9 @@ rm(list=ls());
                                                                      
 setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
 
-evo  <- read.table(file="evo.txt", header=FALSE);
+evo  <- read.table(file="evo_zallele_0.txt", header=FALSE);
 ela  <- evo[evo[,6]==4999,];
-write.table(x=ela, file="ela.txt", col.names=FALSE, row.names=FALSE);
+write.table(x=ela, file="ela_zallele_0.txt", col.names=FALSE, row.names=FALSE);
 
 #==========================================================================
 
@@ -15,7 +15,7 @@ rm(list=ls());
 library(scatterplot3d);
 setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
 
-ela <- read.table(file="ela.txt", header=FALSE);
+ela <- read.table(file="ela_zallele_0.txt", header=FALSE);
 
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX Three dimensional scatter plot  XXX XXX XXX XXX XXX XXX XXX #
@@ -156,9 +156,540 @@ dev.off();
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 
+evo  <- read.table(file="evo_zallele_1.txt", header=FALSE);
+ela  <- evo[evo[,6]==4999,];
+write.table(x=ela, file="ela_zallele_1.txt", col.names=FALSE, row.names=FALSE);
 
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
-# XXX XXX XXX  Large distribution and correlation plots  XXX XXX XXX XXX  #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# Now will do the same thing for random initial conditions
+
+rm(list=ls()); 
+library(scatterplot3d);
+setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
+
[…]

### 2016-08-16 initial_analysis.R
Fixed extension to no cost EPS figures

@@ -311,7 +311,7 @@ setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
 evo_nc <- read.table(file="evo_no_cost.txt", header=FALSE);
 # -----------  BETA = 0  -------------------------------------------------#
 setEPS(); # postscript below for final publication?
-cairo_ps("evo_no_cost_B0",family="Arial",height=7,width=7);
+cairo_ps("evo_no_cost_B0.eps",family="Arial",height=7,width=7);
 evo <- evo_nc[evo_nc[,2]==0,];
 mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
 mPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=mean);
@@ -350,7 +350,7 @@ dev.off();
 
 # -----------  BETA = 1  -------------------------------------------------#
 setEPS(); # postscript below for final publication?
-cairo_ps("evo_no_cost_B1",family="Arial",height=7,width=7);
+cairo_ps("evo_no_cost_B1.eps",family="Arial",height=7,width=7);
 evo <- evo_nc[evo_nc[,2]==1,];
 mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
 mPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=mean);
@@ -389,7 +389,7 @@ dev.off();
 
 # -----------  BETA = 2  -------------------------------------------------#
 setEPS(); # postscript below for final publication?
-cairo_ps("evo_no_cost_B2",family="Arial",height=7,width=7);
+cairo_ps("evo_no_cost_B2.eps",family="Arial",height=7,width=7);
 evo <- evo_nc[evo_nc[,2]==2,];
 mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
 mPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=mean);
@@ -428,7 +428,7 @@ dev.off();
 
 # -----------  BETA = 3  -------------------------------------------------#
 setEPS(); # postscript below for final publication?
-cairo_ps("evo_no_cost_B3",family="Arial",height=7,width=7);
+cairo_ps("evo_no_cost_B3.eps",family="Arial",height=7,width=7);
 evo <- evo_nc[evo_nc[,2]==3,];
[…]

### 2016-08-16 Initial_Results/PDFs/Figures.tex
Initial commit of TEX file to show figures

\documentclass[12pt]{article}
\usepackage[top=1.25in, bottom=1in, left=1.25in, right=1in]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{lineno}
\usepackage{datetime}
\setkomafont{\rmfamily\bfseries\boldmath}
\usepackage{wrapfig,floatrow}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{mathabx}
\usepackage{color}
\usepackage{wasysym}
\usepackage{lipsum}
\floatstyle{plain}
\restylefloat{figure}

\newcommand*{\TitleFont}{
      \usefont{\encodingdefault}{\rmdefault}{r}{n}
      \fontsize{16}{20}
      \selectfont}

\usepackage{fancyheadings}
\pagestyle{fancyplain}
\fancyhf{} 
\renewcommand{\headrulewidth}{0pt} 
\fancyfoot[RO]{\thepage}

\makeatletter
\renewcommand\section{\@startsection{section}{1}{0in}{-0.5\baselineskip}{0.1\baselineskip}{\normalfont\large\bfseries}}
\makeatother

\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{-0.25in}{-0.5\baselineskip}{0.1\baselineskip}{\normalfont\normalsize\bfseries\textit}}
\makeatother

\makeatletter
\renewcommand\subsubsection{\@startsection{subsubsection}{1}{-0.25in}{-0.5\baselineskip}{0.1\baselineskip}{\normalfont\normalsize\textit}}
\makeatother

\title{Figures for pre and postcopulatory inbreeding behaviour}
\author{A. Bradley Duthie\textsuperscript{1,*}, Other Authors\textsuperscript{1}}

\date{}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}

\begin{document}
\maketitle

\begin{center}
\vspace{5 mm}

\noindent 1. Institute of Biological and Environmental Sciences, School of Biological Sciences, Zoology Building, Tillydrone Avenue, University of Aberdeen, Aberdeen AB24 2TZ, United Kingdom \textsuperscript{*} E-mail: aduthie@abdn.ac.uk \\ 
\newline
\end{center}

\vspace{15 mm}

\noindent\textbf{The following figures present results for some initial modelling of evolving traits underlying 1) pre-copulatory inbreeding preference or avoidance, 2) tendency for engaging in polyandry, and 3) post-copulatory inbreeding preference or avoidance (note that post-copulatory inbreeding preference or avoidance is contingent upon focal females being polyandrous. Evolutionary outcomes in Figures 1-16 show evolutionary consequences -- specifically with respect to the mean values of alleles underlying traits -- for inbreeding behaviour and polyandry after 5000 generations. Figures 17-20 show changing mean allele values over generations. Positive allele values underly either inbreeding preference or positive tendency to engage in polyandry, and negative allele values underly either inbreeding avoidance or monandry.}

%\linenumbers
%\modulolinenumbers[2]
%\doublespacing

% -----------------------------------------------------------------------------------

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{EC_Beta_0.pdf}
\end{center}
\caption{Four evolutionary outcomes given three randomised costs. \textbf{Initial trait values are set to zero.}}
\end{figure}

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{PO_Beta_0.pdf}
\end{center}
\caption{Evolution of polyandry versus monandry given three randomised costs. \textbf{Initial trait values are set to zero.}}
\end{figure}

\clearpage

% -----------------------------------------------------------------------------------

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{EC_Beta_1.pdf}
\end{center}
\caption{Four evolutionary outcomes given three randomised costs. \textbf{Initial trait values are set to zero.}}
\end{figure}

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{PO_Beta_1.pdf}
\end{center}
\caption{Evolution of polyandry versus monandry given three randomised costs. \textbf{Initial trait values are set to zero.}}
\end{figure}

\clearpage

% -----------------------------------------------------------------------------------

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{EC_Beta_2.pdf}
\end{center}
\caption{Four evolutionary outcomes given three randomised costs. \textbf{Initial trait values are set to zero.}}
\end{figure}

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{PO_Beta_2.pdf}
\end{center}
\caption{Evolution of polyandry versus monandry given three randomised costs. \textbf{Initial trait values are set to zero.}}
\end{figure}

\clearpage

% -----------------------------------------------------------------------------------

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{EC_Beta_3.pdf}
\end{center}
\caption{Four evolutionary outcomes given three randomised costs. \textbf{Initial trait values are set to zero.}}
\end{figure}

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{PO_Beta_3.pdf}
\end{center}
\caption{Evolution of polyandry versus monandry given three randomised costs. \textbf{Initial trait values are set to zero.}}
\end{figure}

\clearpage

% -----------------------------------------------------------------------------------

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{EC_Beta_0_z1.pdf}
\end{center}
\caption{Four evolutionary outcomes given three randomised costs. \textbf{Initial trait values are randomised $\mathcal{N}\left(0,1\right)$.}}
\end{figure}

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{PO_Beta_0_z1.pdf}
\end{center}
\caption{Evolution of polyandry versus monandry given three randomised costs. \textbf{Initial trait values are randomised $\mathcal{N}\left(0,1\right)$.}}
\end{figure}

\clearpage

% -----------------------------------------------------------------------------------

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{EC_Beta_1_z1.pdf}
\end{center}
\caption{Four evolutionary outcomes given three randomised costs. \textbf{Initial trait values are randomised $\mathcal{N}\left(0,1\right)$.}}
\end{figure}

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{PO_Beta_1_z1.pdf}
\end{center}
\caption{Evolution of polyandry versus monandry given three randomised costs. \textbf{Initial trait values are randomised $\mathcal{N}\left(0,1\right)$.}}
\end{figure}

\clearpage

% -----------------------------------------------------------------------------------

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{EC_Beta_2_z1.pdf}
\end{center}
\caption{Four evolutionary outcomes given three randomised costs. \textbf{Initial trait values are randomised $\mathcal{N}\left(0,1\right)$.}}
\end{figure}

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{PO_Beta_2_z1.pdf}
\end{center}
\caption{Evolution of polyandry versus monandry given three randomised costs. \textbf{Initial trait values are randomised $\mathcal{N}\left(0,1\right)$.}}
\end{figure}

\clearpage

% -----------------------------------------------------------------------------------

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{EC_Beta_3_z1.pdf}
\end{center}
\caption{Four evolutionary outcomes given three randomised costs. \textbf{Initial trait values are randomised $\mathcal{N}\left(0,1\right)$.}}
\end{figure}

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{PO_Beta_3_z1.pdf}
\end{center}
\caption{Evolution of polyandry versus monandry given three randomised costs. \textbf{Initial trait values are randomised $\mathcal{N}\left(0,1\right)$.}}
\end{figure}

\clearpage

% -----------------------------------------------------------------------------------

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{evo_no_cost_B0.pdf}
\end{center}
\caption{Evolution of mean trait values over time. \textbf{Initial trait values are set to zero.}}
\end{figure}

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{evo_no_cost_B1.pdf}
\end{center}
\caption{Evolution of mean trait values over time. \textbf{Initial trait values are set to zero.}}
\end{figure}

\clearpage

% -----------------------------------------------------------------------------------

\begin{figure}
\begin{center}		
\includegraphics[scale=0.5]{evo_no_cost_B2.pdf}
\end{center}
\caption{Evolution of mean trait values over time. \textbf{Initial trait values are set to zero.}}
\end{figure}

\begin{figure}
\begin{center}				
\includegraphics[scale=0.5]{evo_no_cost_B3.pdf}
\end{center}
\caption{Evolution of mean trait values over time. \textbf{Initial trait values are set to zero.}}
\end{figure}

\clearpage

% -----------------------------------------------------------------------------------

\end{document}

### 2016-08-17 initial_analysis.R
Add no cost simulations with random initial trait conditions

@@ -467,6 +467,171 @@ dev.off();
 
 
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX  Plots over time -- no cost rand initial traits XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+
+rm(list=ls()); 
+setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
+
+evo_nc <- read.table(file="evo_no_cost_z1.txt", header=FALSE);
+# -----------  BETA = 0  -------------------------------------------------#
+setEPS(); # postscript below for final publication?
+cairo_ps("evo_no_cost_B0_z1.eps",family="Arial",height=7,width=7);
+evo <- evo_nc[evo_nc[,2]==0,];
+mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
+mPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=mean);
+mEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=mean);
+sWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=sd);
+sPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=sd);
+sEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=sd);
+xxx <- tapply(X=evo[,6],INDEX=evo[,6],FUN=mean);
+len <- dim(evo)[1];
+par(mar=c(5,5,1,1));
+plot(x=xxx,y=mWP,type="l",lwd=2,ylim=c(-9,4),col="blue",
+     xlab="Generation",ylab="Allele value",cex.lab=2,cex.axis=1.5);
+points(x=xxx,y=mPO,type="l",lwd=2,col="red");
+points(x=xxx,y=mEP,type="l",lwd=2,col="black");
+abline(h=0,lwd=0.8,lty="dotted");
+uWP <- mWP + sWP / sqrt(sum(evo[,6]==4999));
+lWP <- mWP - sWP / sqrt(sum(evo[,6]==4999));
+uPO <- mPO + sPO / sqrt(sum(evo[,6]==4999));
+lPO <- mPO - sPO / sqrt(sum(evo[,6]==4999));
+uEP <- mEP + sEP / sqrt(sum(evo[,6]==4999));
[…]

### 2016-08-19 initial_analysis.R
Add code for foor plots showing how three mean allele values change over generations when all possible combinations of 0 and 0.02 costs are applied to trait values

@@ -1,3 +1,1181 @@
+
+rm(list=ls()); 
+library(scatterplot3d);
+setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
+
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX Multi-panel figure of traits over genreations   XXX XXX XXX #
+# XXX XXX XXX with fixed polyandry costs, random other costs  XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+
+evo_cc_02 <- read.table(file="evo_cost_combs02.txt", header=FALSE);
+
+# ------------------------------------------------------------------------#
+# -----------  BETA = 0  -------------------------------------------------#
+# ------------------------------------------------------------------------#
+beta_val <- 0;
+setEPS(); # postscript below for final publication?
+cairo_ps("evo_combs02_B0.eps",family="Arial",height=8,width=5.5);
+par(mfrow=c(4,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
+# ------------------------------------------------------------------------#
+evB <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
+evo <- evB[evB[,2]==beta_val,];
+mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
+mPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=mean);
+mEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=mean);
+sWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=sd);
+sPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=sd);
+sEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=sd);
+xxx <- tapply(X=evo[,6],INDEX=evo[,6],FUN=mean);
+len <- dim(evo)[1];
[…]

### 2016-08-22 initial_analysis.R
Add some more structure to the 3 by 4 plot across three polyandry costs and four beta values

@@ -1185,12 +1185,27 @@ setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
 
 # Random inbreeding traits with a fixed pcost of zero
 evo_rand_pc_00 <- read.table(file="evo_rand_pc_00.txt", header=FALSE);
-ela_rand_pc_00 <- evo_rand_pc_00[evo[,6]==4999,];
+ela_rand_pc_00 <- evo_rand_pc_00[evo_rand_pc_00[,6]==4999,];
 write.table(x=ela_rand_pc_00, file="ela_rand_pc_00.txt", col.names=FALSE, row.names=FALSE);
 
-# -----------  BETA = 0  -------------------------------------------------#
-ela_rand_pc_00 <- read.table(file="ela_rand_pc_00.txt", header=FALSE);
+evo_rand_pc_01 <- read.table(file="evo_rand_pc_01.txt", header=FALSE);
+ela_rand_pc_01 <- evo_rand_pc_01[evo_rand_pc_01[,6]==4999,];
+write.table(x=ela_rand_pc_01, file="ela_rand_pc_01.txt", col.names=FALSE, row.names=FALSE);
 
+# ------------------------------------------------------------------------#
+# ------------------------------------------------------------------------#
+# ------------------------------------------------------------------------#
+
+ela_rand_pc_00 <- read.table(file="ela_rand_pc_00.txt", header=FALSE);
+ela_rand_pc_01 <- read.table(file="ela_rand_pc_01.txt", header=FALSE);
+
+par(mfrow=c(4,3), mar=c(0.5,0.5,0.5,0.5), oma=c(5,5,1,1));
+
+# ------------------------------------------------------------------------#
+# -----------  BETA = 0  -------------------------------------------------#
+# ------------------------------------------------------------------------#
+
+# -----------  P-cost = 0 ---------------
 elaB0 <- ela_rand_pc_00[ela_rand_pc_00[,2]==0,];
 resB0 <- rep(x=0, times=dim(elaB0)[1]);
 for(i in 1:dim(elaB0)[1]){ # Doing this as a loop just to show the logic
@@ -1216,12 +1231,48 @@ for(i in 1:dim(elaB0)[1]){ # Doing this as a loop just to show the logic
    }
 }
[…]

### 2016-08-23 initial_analysis.R
Complete figure showing fixed polyandry costs and random inbreeding strategy costs

@@ -1192,14 +1192,21 @@ evo_rand_pc_01 <- read.table(file="evo_rand_pc_01.txt", header=FALSE);
 ela_rand_pc_01 <- evo_rand_pc_01[evo_rand_pc_01[,6]==4999,];
 write.table(x=ela_rand_pc_01, file="ela_rand_pc_01.txt", col.names=FALSE, row.names=FALSE);
 
+evo_rand_pc_02 <- read.table(file="evo_rand_pc_02.txt", header=FALSE);
+ela_rand_pc_02 <- evo_rand_pc_02[evo_rand_pc_02[,6]==4999,];
+write.table(x=ela_rand_pc_02, file="ela_rand_pc_02.txt", col.names=FALSE, row.names=FALSE);
+
 # ------------------------------------------------------------------------#
 # ------------------------------------------------------------------------#
 # ------------------------------------------------------------------------#
+
+setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
 
 ela_rand_pc_00 <- read.table(file="ela_rand_pc_00.txt", header=FALSE);
 ela_rand_pc_01 <- read.table(file="ela_rand_pc_01.txt", header=FALSE);
+ela_rand_pc_02 <- read.table(file="ela_rand_pc_02.txt", header=FALSE);
 
-par(mfrow=c(4,3), mar=c(0.5,0.5,0.5,0.5), oma=c(5,5,1,1));
+par(mfrow=c(4,3), mar=c(0.5,0.5,0.5,0.5), oma=c(5,5,3,3));
 
 # ------------------------------------------------------------------------#
 # -----------  BETA = 0  -------------------------------------------------#
@@ -1232,7 +1239,11 @@ for(i in 1:dim(elaB0)[1]){ # Doing this as a loop just to show the logic
 }
 plot(x=elaB0[,3], y=elaB0[,5], cex=1.9, lwd=2, col=polB0, pch=21, bg=resB0,
      xlab="", xaxt="n", cex.lab=1.5, cex.axis = 1.5, 
-     ylab="Cost of post-cop inbreeding preference");
+     ylab="Cost of post-cop inbreeding preference", yaxt="n");
+axis(side=2, cex.axis=1.75, at=c(0, 0.01, 0.02, 0.03, 0.04, 0.05));#, 
[…]

### 2016-08-23 initial_analysis.R
Change notation to proper subscripts as to be used in text for showing trait evolution over generations

@@ -1616,9 +1616,9 @@ mtext(text=expression(paste(beta==1)),side=4,outer=TRUE,at=0.625, cex=1.75, line
 mtext(text=expression(paste(beta==2)),side=4,outer=TRUE,at=0.375, cex=1.75, line=1.25);
 mtext(text=expression(paste(beta==3)),side=4,outer=TRUE,at=0.125, cex=1.75, line=1.25);
 
-mtext(text=expression(paste("Cost of mating strategy (",c[M],")")),side=1,outer=TRUE,at=0.5, cex=1.75, line = 3.25);
+mtext(text=expression(paste("Cost of inbreeding mating strategy (",c[M],")")),side=1,outer=TRUE,at=0.5, cex=1.75, line = 3.25);
 
-mtext(text=expression(paste("Cost of fertilisation strategy (",c[F],")")), side=2, outer=TRUE, at=0.5, cex=1.75, line = 2.25);
+mtext(text=expression(paste("Cost of inbreeding fertilisation strategy (",c[F],")")), side=2, outer=TRUE, at=0.5, cex=1.75, line = 2.25);
 
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #

### 2016-08-24 ms_pre_post.Rmd
Write first paragraph of methods

@@
 author: "A. Bradley Duthie et al."
-date: "May 27, 2016"
+date: "August 24, 2016"
 output:
+  html_document: default
+  pdf_document:
+    fig_caption: yes
   word_document:
@@
     - evolution.csl
-  pdf_document:
-    fig_caption: yes
-  html_document: default
 linestretch: 1
+bibliography: ms_pre_post.bib
 ---
@@
 
-******************************-
+******************************
 
@@
 ===================================================
+
+```{r,echo=FALSE}
+#**First paragraph** A general overview of what the model is doing, which will look a lot like Duthie and Reid (AmNat) and Duthie et al.
+(Evolution).
+Mention somewhere in here that all individuals have 30 diploid loci, ten with alleles affecting polyandry, ten with alleles affecting pre-copulatory inbreeding strategy, and ten with alleles affecting post-copulatory inbreeding strategy.
+Also note that the traits affected by each of these loci can each potentially come with some cost ($c_P$, $c_M$, and $c_F$).
+Note that we are not assuming any constraints on accessibility to males, so all males are available at all times.
+```
+
+We track interactions among discrete individuals in a small focal population that persists over multiple generations.
+Individuals within this population are either female or male, and are potentially related if they share a common ancestory.
+We record the coefficient of kinship ($k$), defined as the probability that a randomly selected homologous allele from each individual is identical-by-descent, between all pairs of individuals in each generation using the population pedigree [see @Boyce1983; @Duthie].
+At the start of each generation, each female pays up to three independent costs of (1) tendency to engage in polyandry ($c_{P}$), (2) mating strategy with respect to inbreeding ($c_{M}$), and (3) fertilisation strategy ($c_{F}$) with respect to inbreeding.
+The number of males that a focal female mates with ($N_{males}$) is determined by the effects of 20 alleles ($P_{a}$) across 10 diploid loci that combine additively to determine a her genotype ($P_{g}$), and ultimately the phenotype for her tendency to engage in polandry ($P_{p}$).
+A focal female's choice of mate(s) is affected by 20 alleles ($M_{a}$) across 10 diploid loci that combine additively to affect her genotype ($M_{g}$) and phenotype ($M_{p}$) for pre-copulatory inbreeding avoidance or preference, and $k$ between the focal female and her potential mates.
+Similarly, after mating has occurred, fertilisation of a focal female's $n$ total offspring is affected by 20 alleles ($F_{a}$) across 10 diploid loci that combine additively to affect the genotype ($F_{g}$) and phenotype ($F_{p}$) of the degree to which fertilisation success is affected by $k$.
+After fertilisation, the vialbility of a focal female's $n$ offspring is decreased by inbreeding depression ($\beta$); surviving offspring become adults.
+After inbreeding depression in offspring, $\rho$ adult male immigrants arrive in the population, then density effects reduce the entire population down to female ($K_{f}$) and male ($K_{m}$) carrying capacity.
+Over generations, we record mean values of alleles underlying polyandry, mating strategy, and fertilisation strategy.
 

### 2016-08-24 ms_pre_post.Rmd
Add cost section to the Model

@@
 A focal female's choice of mate(s) is affected by 20 alleles ($M_{a}$) across 10 diploid loci that combine additively to affect her genotype ($M_{g}$) and phenotype ($M_{p}$) for pre-copulatory inbreeding avoidance or preference, and $k$ between the focal female and her potential mates.
-Similarly, after mating has occurred, fertilisation of a focal female's $n$ total offspring is affected by 20 alleles ($F_{a}$) across 10 diploid loci that combine additively to affect the genotype ($F_{g}$) and phenotype ($F_{p}$) of the degree to which fertilisation success is affected by $k$.
+Similarly, after mating has occurred, post-copulatory fertilisation of a focal female's $n$ total offspring is affected by 20 alleles ($F_{a}$) across 10 diploid loci that combine additively to affect the genotype ($F_{g}$) and phenotype ($F_{p}$) of the degree to which fertilisation success is affected by $k$.
 After fertilisation, the vialbility of a focal female's $n$ offspring is decreased by inbreeding depression ($\beta$); surviving offspring become adults.
@@
 
+Costs
+----------------------------------------------
+
+Values of phenotypic traits for tendency to engage in polyandry ($P_{p}$), mating ($M_{p}$), and fertilistation ($F_{p}$) each have costs, which independently increase the probability of a focal female's reproductive failure.
+These costs are all expressed prior to mating.
+In the case of tendency to engage in polyandry and inbreeding mating strategy, costs of $P_{p}$ ($c_{P}$) and $M_{p}$ ($c_{M}$) are interpreted biologically as costs associated with mate searching.
+In the case of inbreeding fertilisation strategy, the cost of $F_{g}$ is interpreted as an energetic cost associated with the physiological or biochemical mechanisms that need to be developed to bias fertilsation for inbreeding avoidance or inbreeding preference.
+Each cost independently increases the risk of female pre-mating mortality and, because generations are non-overlapping, total reproductive failure as a linear function of its associated trait.
+The probability that a focal female dies before mating due to the cost of polyandry is therefore $P_{p} \times c_{P}$.
+Similarly, the probability of pre-mating female mortality due to the cost of mating strategy and fertilisation strategy is $|M_{p}| \times c_{M}$ and $|F_{p}| \times c_{F}$, repectively, where $|M_{p}|$ is the absolute value of $M_{p}$ and $|F_{p}|$ is the absolute value of $F_{p}$.
+Absolute values are used for applying costs to inbreeding strategies because both negative and positive $M_{p}$ and $F_{p}$ bias breeding interactions with respect to kinship, while only positive values of $P_{p}$ affect a female's tendency for polyandry; zero and negative $P_{p}$ values always translate to monandrous phenotypes (see below).
+
+Polyandry
+----------------------------------------------
+
 ******************************
@@
 Results
-------------------------------------------------
+===================================================
 

### 2016-08-24 ms_pre_post.Rmd
Add Polyandry section to the Model

@@
 
-```{r,echo=FALSE}
-#**First paragraph** A general overview of what the model is doing, which will look a lot like Duthie and Reid (AmNat) and Duthie et al.
-(Evolution).
-Mention somewhere in here that all individuals have 30 diploid loci, ten with alleles affecting polyandry, ten with alleles affecting pre-copulatory inbreeding strategy, and ten with alleles affecting post-copulatory inbreeding strategy.
-Also note that the traits affected by each of these loci can each potentially come with some cost ($c_P$, $c_M$, and $c_F$).
-Note that we are not assuming any constraints on accessibility to males, so all males are available at all times.
-```
-
 We track interactions among discrete individuals in a small focal population that persists over multiple generations.
 Individuals within this population are either female or male, and are potentially related if they share a common ancestory.
-We record the coefficient of kinship ($k$), defined as the probability that a randomly selected homologous allele from each individual is identical-by-descent, between all pairs of individuals in each generation using the population pedigree [see @Boyce1983; @Duthie].
+We record the coefficient of kinship ($k$), defined as the probability that a randomly selected homologous allele from each individual is identical-by-descent [@Lynch1998], between all pairs of individuals in each generation using the population pedigree [see @Boyce1983; @Duthie].
 At the start of each generation, each female pays up to three independent costs of (1) tendency to engage in polyandry ($c_{P}$), (2) mating strategy with respect to inbreeding ($c_{M}$), and (3) fertilisation strategy ($c_{F}$) with respect to inbreeding.
@@
 
+Each female chooses a number of males to mate with ($N_{males}$) based on her genetically determined tendency to engage in polyandry ($P_{p}$).
+The exact value of $N_{males}$ is calculated by sampling from a random poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
+This random sampling procedure causes some stochastic variation in the number of realised mates a that female chooses, with a mean $N_{males}$ of $P_{p}+1$.
+A one is added to $P_{p}$ to ensure that all females choose at least one mate, as low values of $P_{p}$ might return $Poisson(P_{p})$ values of zero.
+
+The value of $P_{p}$ is affected by the summed values of her 20 $P_{a}$ alleles.
+Inheritence of all alleles models a diploid genetic architecture in which 10 $P_{a}$ alleles are randomly sampled from each parent with no physical linkage.
+Values of $P_{a}$ can take any real number [continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014].
+The tendency for polyandry genotype $P_{g}$ is defined by the sum of all of a focal female's 20 $P_{a}$ values, which might be negative or positive.
+However, the tendency for polyandry phenotype $P_{p}$ is restricted to zero or positive values because the number of males that a female chooses to mate with cannot be negative.
+Hence, negative values of $P_{g}$ are translated to $P_{p}$ values of zero such that $P_{p} = 0$ when $P_{g} < 0$, but when $P_{g} \geq 0$, then $P_{p} = P_{g}$ (i.e., the phenotype value of polyandry equals the genotype value of polyandry if and only if the genotype value is greater than or equal to zero, else the phenotype value of polyandry always equals zero).
+The resulting $P_{p}$ is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998], in which polyandry is expressed discretely at the threshold value of $P_{g} > 0$, but is determined by the consequence of continuous genetic variation arising from the effects of $P_{a}$ alleles that each contribute additively to a female's tendency toward polyandry.
+Negative genotypic values of $P_{g}$ therefore all have the same phenotype, resulting in consistently monandrous females.
+In contrast, positive values of $P_{g}$ and therefore $P_{p}$ can lead to different degrees of realised polyandry in the form of discrete numbers of mates ($N_{males}$).
+
+Mating
+----------------------------------------------
+
 ******************************

### 2016-08-24 ms_pre_post.Rmd
Add Mating section to the Model

@@
 output:
-  html_document: default
   pdf_document:
     fig_caption: yes
+  html_document: default
   word_document:
@@
 
+Each male within the population is a potential mate for any female to choose.
+We therefore assume that there are no opportunity costs associated with male mating such that mating with one female would reduce a male's ability to mate with and sire the offspring of any other female [e.g., @Waser1986].
+While all males are therefore available as potential mates, we assume that a female mates with her total allotment of $N_{males}$ without replacement, meaning that $N_{males}$ models the total number of distinct males that a female chooses to mate with rather than the number of times that she mates.
+In the unlikely event that a female's $N_{males}$ exceeds the total number of males in the population, then she mates with all of the males in the populaton.
+More likely, $N_{males}$ will be a small subset of the available males in the population [@Duthie], so a focal female will be able to preferentially mate with males that are close kin (high $k$), distant kin (low $k$), or non-kin ($k=0$) through the expression of her mating phenotype ($M_{p}$).
+Like polyandry allele values, mating strategy allele values ($M_{a}$) can take any real number.
+However, unlike polyandry, the sum of all of a female's 20 $M_{a}$ alleles equals both her mating strategy genotype ($M_{g}$) and her mating strategy phenotype ($M_{p}$).
+Negative or positive values of $M_{p}$ cause a female to avoid or prefer mating with kin, respectively.
+Values of $M_{p}=0$ causes females to mate randomly with respect to kinship.
+
+The probability that a focal female $i$ mates with a male $j$ with which she shares some kinship $k_{ij}$ is calculated by first assigning each male a perceived quality $Q_{ij}$.
+This quality depends upon whether the female has a strategy of avoiding mating with kin ($M_{p}<0$) or preferring mating with kin ($M_{p}>0$; if $M_{p}=0$, all males are assigned a quality of 1, $Q_{ij}=1$).
+If a focal female avoids mating with kin, then $Q_{ij} = (-M_{p} \times k_{ij} + 1)^{-1}$, meaning that the perceived quality of a male decreases lineary with increasingly positive values of $k_{ij}$ and increasingly negative values of $M_{p}$.
+If a focal female prefers mating with kin, then $Q_{ij} = M_{p} \times k_{ij} + 1$, meaning that the perceived quality of a male increases with increasingly positive values of $k_{ij}$ and $M_{p}$.
+After a focal female assigns all males a perceived quality, the sum of all male perceived qualities is calculated, then each male quality is divided by this sum.
+This transformation results in each male having a relative perceived quality $q_{ij}$, which is constrained to values between zero and one.
+The value of $q_{ij}$ then defines the probability that a female chooses the male as a mate; female choice is therefore stochastic, meaning that females do not always choose the male of the highest $q_{ij}$.
+For polyandrous females that choose more than one male mate, mates are chosen iteratively such that $Q_{ij}$ and $q_{ij}$ are re-calculated for each additional mate choice, and with $Q_{ij}$ and therefore $q_{ij}$ values of already chosen males set to zero to ensure mate sampling without replacement.
+
 ******************************

### 2016-08-24 ms_pre_post.Rmd
Add first two sentences of Fertilisation section to the Model

@@
 
-The probability that a focal female $i$ mates with a male $j$ with which she shares some kinship $k_{ij}$ is calculated by first assigning each male a perceived quality $Q_{ij}$.
-This quality depends upon whether the female has a strategy of avoiding mating with kin ($M_{p}<0$) or preferring mating with kin ($M_{p}>0$; if $M_{p}=0$, all males are assigned a quality of 1, $Q_{ij}=1$).
-If a focal female avoids mating with kin, then $Q_{ij} = (-M_{p} \times k_{ij} + 1)^{-1}$, meaning that the perceived quality of a male decreases lineary with increasingly positive values of $k_{ij}$ and increasingly negative values of $M_{p}$.
-If a focal female prefers mating with kin, then $Q_{ij} = M_{p} \times k_{ij} + 1$, meaning that the perceived quality of a male increases with increasingly positive values of $k_{ij}$ and $M_{p}$.
+The probability that a focal female $i$ mates with a male $j$ with which she shares some kinship $k_{ij}$ is calculated by first assigning each male a perceived mate quality $Q^{m}_{ij}$.
+This quality depends upon whether the female has a strategy of avoiding mating with kin ($M_{p}<0$) or preferring mating with kin ($M_{p}>0$; if $M_{p}=0$, all males are assigned a quality of 1, $Q^{m}_{ij}=1$).
+If a focal female avoids mating with kin, then $Q^{m}_{ij} = (-M_{p} \times k_{ij} + 1)^{-1}$, meaning that the perceived quality of a male decreases lineary with increasingly positive values of $k_{ij}$ and increasingly negative values of $M_{p}$.
+If a focal female prefers mating with kin, then $Q^{m}_{ij} = M_{p} \times k_{ij} + 1$, meaning that the perceived quality of a male increases with increasingly positive values of $k_{ij}$ and $M_{p}$.
 After a focal female assigns all males a perceived quality, the sum of all male perceived qualities is calculated, then each male quality is divided by this sum.
-This transformation results in each male having a relative perceived quality $q_{ij}$, which is constrained to values between zero and one.
-The value of $q_{ij}$ then defines the probability that a female chooses the male as a mate; female choice is therefore stochastic, meaning that females do not always choose the male of the highest $q_{ij}$.
-For polyandrous females that choose more than one male mate, mates are chosen iteratively such that $Q_{ij}$ and $q_{ij}$ are re-calculated for each additional mate choice, and with $Q_{ij}$ and therefore $q_{ij}$ values of already chosen males set to zero to ensure mate sampling without replacement.
+This transformation results in each male having a relative perceived mate quality $q^{m}_{ij}$, which is constrained to values between zero and one.
+The value of $q^{m}_{ij}$ then defines the probability that a female chooses the male as a mate; female choice is therefore stochastic, meaning that females do not always choose the male of the highest $q^{m}_{ij}$.
+For polyandrous females that choose more than one male mate, mates are chosen iteratively such that $Q^{m}_{ij}$ and $q^{m}_{ij}$ are re-calculated for each additional mate choice, and with $Q^{m}_{ij}$ and therefore $q^{m}_{ij}$ values of already chosen males set to zero to ensure mate sampling without replacement.
+
+Fertilisation
+----------------------------------------------
+
+The fertilisation of a female's $n$ offspring occurs after mating, with each of her $n$ offspring being assigned a sire independently and with replacement from the $N_{males}$ with which the female mated.
+The probability that a male mate successfully sires an offspring is affected by a female's kinship with the potential sire ($k_{ij}$) and her inbreeding fertilisation strategy ($F_{p}$).
 

### 2016-08-25 ms_pre_post.Rmd
Add Fertilisation section to the Model

@@
 output:
+  html_document: default
   pdf_document:
     fig_caption: yes
-  html_document: default
   word_document:
@@
 In the unlikely event that a female's $N_{males}$ exceeds the total number of males in the population, then she mates with all of the males in the populaton.
-More likely, $N_{males}$ will be a small subset of the available males in the population [@Duthie], so a focal female will be able to preferentially mate with males that are close kin (high $k$), distant kin (low $k$), or non-kin ($k=0$) through the expression of her mating phenotype ($M_{p}$).
+Most often, $N_{males}$ will be a small subset of the available males in the population [@Duthie], so a focal female will be able to preferentially mate with males that are close kin (high $k$), distant kin (low $k$), or non-kin ($k=0$) through the expression of her mating phenotype ($M_{p}$).
 Like polyandry allele values, mating strategy allele values ($M_{a}$) can take any real number.
@@
 The probability that a male mate successfully sires an offspring is affected by a female's kinship with the potential sire ($k_{ij}$) and her inbreeding fertilisation strategy ($F_{p}$).
+As with polyandry and inbreeding mating strategy phenotypes, a female's inbreeding fertilisation strategy phenotype is determined by the summed effects of 20 inbreeding fertilisation strategy alleles ($F_{a}$), which can take any real number.
+The sum of all of a female's $F_{a}$ alleles determine her inbreeding fertilisation strategy genotype ($F_{g}$), which is identical to her inbreeding strategy phenotype ($F_{p}$).
+As with mating strategy phenotype ($M_{p}$), negative or positive values of $F_{p}$ correspond to inbreeding avoidance or preference respectively, and $F_{p}=0$ causes random fertilisation with respect to kinship.
+
+The probability that an offspring of a focal female $i$ is fertilised by one of $i$'s mates $j$ is calculated by first assigning a perceived fertilisation quality to each $j$, $Q^{f}_{ij}$.
+Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if a focal female has a fertilisation strategy of avoiding inbreeding ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$.
+If instead a focal female has a fertilisation strategy of preferring inbreeding ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$.
+The perceived qualities of every male that a focal female has mated with are summed, then a relative quality ($q^{f}_{ij}$) is calculated for each male by dividing each individual male mate's $Q^{f}_{ij}$ by this sum.
+As with relative perceived mate quality values ($q^{m}_{ij}$), this results in values of perceived fertilisation quality $q^{f}_{ij}$ between zero and one.
+These $q^{f}_{ij}$ values define the probability that the offspring of a focal female $i$ is fertilised by the male $j$.
+Females produce $n$ offspring, meaning that $q^{f}_{ij}$ values are sampled $n$ times for each female to determine the realised distribution of sires.
+
+Inbreeding depression
+----------------------------------------------
 

### 2016-08-25 ms_pre_post.Rmd
Add Inbreeding depression section to the Model

@@
 
+The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a function of the kinship coefficient between $i$ and the sire of her offspring $j$ ($k_{ij}$), and a log-linear slope of inbreeding depression $\beta$,
+\begin{equation}
+\Psi_{off} = e^{-\beta k_{ij}}
+\end{equation}
+The slope $\beta$ models the number of haploid lethal equivalents that exist in the gametes of $i$ and $j$, and which might combine to become homozygous in offspring and reduce viability.
+Equation 1 assumes that each deleterious recessive allele affects offspring viability independently, meaning that every deleterious recessive allele added will have a multiplicative affect on decreasing viability [@Morton1956; Mills1994], causing the log-linear relationship between parent kinship and inbreeding depression.
+We assume that inbreeding depression always decreases offspring viability, $\beta \geq 0$ (i.e., no outbreeding depression).
+Therefore, because $k_{ij}$ is constrained to values between zero and one, the product of $-\beta$ and $k_{ij}$ must be a value less than or equal to zero, $-\beta \times \k_{ij} leq 0$.
+Values of $\Psi_{off}$ must therefore be between zero and one.
+We can therefore define $\Psi_{off}$ as the probability that an offspring is viable, and sample its realised viability using a Bernoulli trial.
+
+Immigration
+----------------------------------------------
+
 ******************************

### 2016-08-25 ms_pre_post.Rmd
Add Immigration section to the Model

--- 2016-08-25 ms_pre_post.Rmd
@@
 
+The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a function of the kinship coefficient between $i$ and the sire of her offspring $j$ ($k_{ij}$), and a log-linear slope of inbreeding depression $\beta$,
+\begin{equation}
+\Psi_{\textrm{off}} = e^{-\beta k_{ij}}
+\end{equation}
+The slope $\beta$ models the number of haploid lethal equivalents that exist in the gametes of $i$ and $j$, and which might combine to become homozygous in offspring and reduce viability.
+Equation 1 assumes that each deleterious recessive allele affects offspring viability independently, meaning that every deleterious recessive allele added will have a multiplicative affect on decreasing viability [@Morton1956; @Mills1994], causing the log-linear relationship between parent kinship and inbreeding depression.
+We assume that inbreeding depression always decreases offspring viability, $\beta \geq 0$ (i.e., no outbreeding depression).
+Therefore, because $k_{ij}$ is constrained to values between zero and one, the product of $-\beta$ and $k_{ij}$ must be a value less than or equal to zero, $-\beta \times k_{ij} \leq 0$.
+Values of $\Psi_{\textrm{off}}$ must therefore be between zero and one.
+We can therefore define $\Psi_{\textrm{off}}$ as the probability that an offspring is viable, and sample its realised viability using a Bernoulli trial.
+
+Immigration
+----------------------------------------------
+
+After offspring viability is realised, $\rho$ adult immigrants are added to the focal population.
+The coefficient of kinship between an immigrant and all other individuals (including native individuals and other immigrants) always equals zero ($k_{ij}=0$).
+Because kinship coefficient values are calculated directly from the pedigree of the focal population, the addition of immigrants thereby introduces non-kin into the population at a consistent rate and prevents the mean kinship coefficient of the population from asymptoting to a value of 1 over generations.
+If the focal population was instead closed ($\rho=0$), then all alleles would quickly be expected to become identical-by-descent among descendants of the ancestral population.
+To avoid having immigrants affect the evolution of tendency for polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilisation strategy ($F_{p}$), immigrants are always male and can therefore be chosen based on their kinship values of zero but not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$.
+To further avoid having immigrants affect evolutionary dynamics, allele values underlying tendency for polyandry ($P_{a}$), inbreeding mating strategy ($M_{a}$), and inbreeding fertilisation strategy ($F_{a}$) are randomly sampled from normal distributions with means and standard deviations of $P_{a}$, $M_{a}$, and $F_{a}$ values equal to the means and standard deviations of those in the focal population at the time of immigration.
+Overall, this model of immigration effectively assumes that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$.
+
+Density regulation
+----------------------------------------------
+
 ******************************

### 2016-08-25 ms_pre_post.Rmd
Add Density regulation section, Model analysis section, and a mutation section (inserted earlier) into the Model

@@
   html_document: default
-  word_document:
-    fig_caption: yes
-    pandoc_args:
-    - --csl
-    - evolution.csl
+  word_document: null
 linestretch: 1
@@
 These costs are all expressed prior to mating.
-In the case of tendency to engage in polyandry and inbreeding mating strategy, costs of $P_{p}$ ($c_{P}$) and $M_{p}$ ($c_{M}$) are interpreted biologically as costs associated with mate searching.
-In the case of inbreeding fertilisation strategy, the cost of $F_{g}$ is interpreted as an energetic cost associated with the physiological or biochemical mechanisms that need to be developed to bias fertilsation for inbreeding avoidance or inbreeding preference.
+In the case of tendency to engage in polyandry and inbreeding mating strategy, costs of $P_{p}$ ($c_{P}$) and $M_{p}$ ($c_{M}$) are interpreted biologically as costs associated with mate searching or courtship [e.g., @Rowe1988; @Rowe1994; @Ronkainen1994; @Koga1998; @Lasley-Rasher2012].
+In the case of inbreeding fertilisation strategy, the cost of $F_{p}$ ($c_{F}$) is interpreted as an energetic cost associated with the physiological or biochemical mechanisms that need to be developed to bias fertilsation for inbreeding avoidance or inbreeding preference [e.g., @Gasparini2011].
 Each cost independently increases the risk of female pre-mating mortality and, because generations are non-overlapping, total reproductive failure as a linear function of its associated trait.
@@
 
+Mutation
+----------------------------------------------
+
+Alleles of a focal female's offspring mutate with a probability of $\mu=0.001$, with mutation being an independent event across loci.
+In general, loss of function mutations might be expected to be more frequent than mutations that increase the functionality of adaptations that rely on complex physiologies or behaviours.
+If tendency for polyandry, inbreeding mating strategies, or inbreeding fertilisation strategies rely on such complex physiologies or behaviours, then we might expect the direction of mutation to be biased (e.g., towards monandry or random mating).
+However, because we are interested specifically in how selection affects reproductive strategy given varying costs and inbreeding depression, we model mutation as unbiased so that selection can be isolated and inferred clearly from mean allele values.
+
+Hence, when a mutation occurs at a loci, a new value is sampled from a random normal distribution with a mean of zero, $\mathcal{N}(0, \mu_{SD})$.
+This new value is then added to the original value of the allele that mutates [@Kimura1965; @Lande1976; @Bocedi2014; @Duthie].
+The standard deviation of the mutation effect size ($\mu_{SD}$) is set to $\sqrt{1/20}$, which scales the variance of mutation effect size to the total number of alleles affecting $P_{p}$, $M_{p}$, and $F_{p}$ phenotypes [see @Kimura1965; @Lande1976; @Bocedi2014].
+
 Inbreeding depression
@@
 
-The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a function of the kinship coefficient between $i$ and the sire of her offspring $j$ ($k_{ij}$), and a log-linear slope of inbreeding depression $\beta$,
+The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a function of the kinship coefficient between $i$ and the sire of her offspring $j$ ($k_{ij}$), and a log-linear slope of inbreeding depression $\beta$.
+We model selection as having an absolute effect on offspring viability (i.e., hard selection), rather than a relative effect on viability (i.e., soft selection), so that the effect of $\beta$ is consistent over generations and across different parameter combinations.
+Natural selection on tendency for polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilisation strategy ($F_{p}$) can therefore be compared with respect to log-linear inbreeding depression slopes across generations and parameter combinations.
+If offspring viability was instead relative such that the least inbred offspring had a high viability regardless of the absolute value of $k_{ij}$, then the effect of kinship coefficients and inbreeding depression slopes on offspring viability would depend on the population-wide distribution of $k_{ij}$ between females and males, making model inference more difficult.
+Therefore, we define offspring viability as,
 \begin{equation}
@@
 
+To avoid indefinite population growth over generations, we introduce a separate carrying capacity on the total number of females ($K_{f}$) and males ($K_{m}$) in the focal population following immigration [@Guillaume2009; @Duthie].
+If at the end of a generation the number of females or males exceeds their respective carrying capacities, then each sex is reduced back to its $K_{f}$ or $K_{m}$ by randomly removing females and males until each sex is at its carrying capacity.
+Removal of females and males can be interpreted as dispersal outside the focal population, mortality, or as some combination of dispersal and mortality.
+The remaining females and males within the population form the next generation of adults.
+
+Model analysis
+----------------------------------------------
+
+To analyse our model, we track mean values of alleles underlying tendency for polyandry ($P_{a}$), inbreeding mating strategy ($M_{a}$), and inbreeding fertilisation strategy ($F_{a}$) in a focal population.
+We present evolutionary dynamics of these mean allele values across a range of costs and inbreeding depression slopes using two types of simulations.
+First, we consider eight possible cost parameter combinations in which costs of tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$) equal either $0$ or $0.02$ [@Duthie observed $0.02$ to be strong cost of tendency for polyandry].
+Second, we fix $c_{P}$ to values of $0$, $0.01$, or $0.02$, then randomly select $c_{M}$ and $c_{F}$ values between $0-0.05$ for simulation initial starting conditions.
+The objective of the first type of simulation is to test how mean allele values change over generations in response to different combinations of costs and inbreeding depression slopes.
+The objective the second type of simulation is to predict selection for tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy, across a wider range of parameter combinations, and to therefore test under what conditions each is predicted to evolve given different combinations of costs and inbreeding depression slopes.
+
+In the first type of simulation, we record dynamics of mean values of $P_{a}$, $M_{a}$, $F_{a}$ over generations for every possible combination in which the cost associated with each of the three phenotypes ($c_{P}$, $c_{M}$, and $c_{F}$) is either $0$ or $0.02$, and for four slopes of inbreeding depression on offspring viability $\beta = {0, 1, 2, 3}$.
+Each possible cost combination is replicated ten times, and grand mean values and standard deviation of means is calculated in each generation across replicate simulations.
+These analyses allowed us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on inbreeding fertilisation strategy might be weak if polyandry is rare).
+
+In the second type of simulation, we record and present mean values of $P_{a}$, $M_{a}$, $F_{a}$ only from the terminal generation of simulations, and for random costs of inbreeding mating strategy $c_{M} \in [0, 0.05]$ and inbreeding fertilisation strategy $c_{F} \in [0, 0.05]$, but fixed costs of tendency for polyandry $c_{P} = {0, 0.01, 0.02}$.
+We consider four values of $\beta = {0, 1, 2, 3}$, and we simulate 100 replicates for all combinations of $c_{P}$ and $\beta$.
+For different values of $\beta$ given the same $c_{P}$ value, we use the same randomly selected values of $c_{M}$ and $c_{F}$ to better infer how terminal mean allele values are affected by different magnitudes of inbreeding depression.
+We do not use the same randomly selected values of $c_{M}$ and $c_{F}$ across different values of $c_{P}$ because $c_{P}$ values were fixed *a priori* only to facilitate model inference.
+The objective of randomising costs was to sample from a broad range of parameter space, and this range is increased by selecting different $c_{M}$ and $c_{F}$ values for each $c_{P}$.
+
+For each replicate simulation with a unique set of costs, we classify the evolutionary outcome of inbreeding stragies in the simulation in one of four ways: (1) Weak selection for inbreding mating strategy and inbreeding fertilisation strategy, (2) weak selection for inbreeding mating strategy and strong selection for inbreeding fertilisation strategy, (3) strong selection for inbreeding mating strategy and weak selection for inbreeding fertilisation strategy, and (4) strong selection for inbreeding mating strategy and inbreeding fertilisation strategy.
+We additionally classify the evolutionary outcome of tendency for polyandry in the simulation as either weak selection for polyandry or strong selection for polyandry.
+@Duthie showed that selection for inbreeding preference (positive values of $M_{a}$) is predicted when inbreeding depression on offspring viability is $\beta=0$, but selection for inbreeding avoidance (negative values of $M_{a}$) is predicted when $\beta \geq 1$.
+When referring to strong selection for inbreeding mating strategy and inbreeding fertilisation strategy, we therefore refer specifically to inbreeding preference when $\beta=0$ and inbreeding avoidance when $\beta \geq 1$.
+Strong selection is inferred when mean allele values exceed $1$ (when $\beta = 0$) or are less than $-1$ (when $\beta \geq 1$), otherwise selection is inferred to be weak.
+Exploratory simulations suggest that cutoff values of $1$ and $-1$ are conservative for inferring when selection is strong, and other cutoff values do not change the general pattern of evolutionary outcomes (1-4) across cost parameter values.
+
+For all replicates in both the first and second simulation types, we set the maximum number of generations to 5000, which exploratory simulations and previous modelling [@Duthie] showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
+For all replicates, we set the number of immigrants per generation to $\rho=5$, which produced a range of kin and non-kin in each generation such that females could express inbreeding strategies.
+Females always produced $n=8$ offspring, which was sufficient to keep populations consistently near carrying capacities and avoid population extinction.
+Carrying capacities for females ($K_{f}$) and males ($K_{m}$) were both set to 100 because previous modelling has shown that populations of this size are small enough that mating encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but populations are also not so small that selection is typically overwhelmed by genetic drift (Duthie and Reid *in press*).
+
 ******************************

### 2016-08-29 initial_analysis.R
Add long 10km gen sims plot, but panel A is still bad

@@ -1,3 +1,1234 @@
+rm(list=ls()); 
+library(scatterplot3d);
+setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
+
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX Multi-panel figure of traits over genreations   XXX XXX XXX #
+# XXX XXX XXX with fixed polyandry costs, random other costs  XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+
+gens      <- 9999;
+
+# ------------------------------------------------------------------------#
+# -----------  BETA = 0  -------------------------------------------------#
+# ------------------------------------------------------------------------#
+beta_val <- 0;
+setEPS(); # postscript below for final publication?
+cairo_ps("evo_combs02_B0.eps",family="Arial",height=8,width=5.5);
+par(mfrow=c(4,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
+# ------------------------------------------------------------------------#
+evo_cc_02 <- read.table(file="res_c02s/evo_M02_P00_F00.txt", header=FALSE);
+evB <- evo_cc_02[evo_cc_02[,3]==0.02 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
+evo <- evB[evB[,2]==beta_val,];
+mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
+mPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=mean);
+mEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=mean);
+sWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=sd);
+sPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=sd);
+sEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=sd);
[…]

### 2016-08-29 initial_analysis.R
Add multipanel figure of correlations across 10000 generations

@@ -1,10 +1,1100 @@
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# READ THESE PROGRAMS IN FOR SHOWING END CORRELATIONS LATER               #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+#http://musicroamer.com/blog/2011/01/16/r-tips-and-tricks-modified-pairs-plot/
+panel.cor.scale <- function(x, y, digits=2, prefix="", cex.cor){
+	usr <- par("usr"); on.exit(par(usr))
+	par(usr = c(0, 1, 0, 1))
+	r = (cor(x, y,use="pairwise"))
+	txt <- format(c(r, 0.123456789), digits=digits)[1]
+	txt <- paste(prefix, txt, sep="")
+	if(missing(cex.cor)) cex <- 0.8/strwidth(txt)
+	text(0.5, 0.5, txt, cex = cex * abs(r))
+}
+
+panel.cor <- function(x, y, digits=2, prefix="", cex.cor){
+	usr <- par("usr"); on.exit(par(usr))
+	par(usr = c(0, 1, 0, 1))
+	r = (cor(x, y,use="pairwise"))
+	txt <- format(c(r, 0.123456789), digits=digits)[1]
+	txt <- paste(prefix, txt, sep="")
+	if(missing(cex.cor)) cex <- 0.8/strwidth(txt)
+	text(0.5, 0.5, txt, cex = cex )
+}
+
+panel.hist <- function(x, ...){
+	usr <- par("usr"); on.exit(par(usr))
+	par(usr = c(usr[1:2], 0, 1.5) )
+	h <- hist(x, plot = FALSE)
[…]

### 2016-08-29 initial_analysis.R
Fix simulations with no costs (all panels)

@@ -134,8 +134,8 @@ setEPS(); # postscript below for final publication?
 cairo_ps("evo_corrs02_B0.eps",family="Arial",height=8,width=5.5);
 par(mfrow=c(4,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
 # ------------------------------------------------------------------------#
-evo_cc_02 <- read.table(file="res_c02s/evo_M02_P00_F00.txt", header=FALSE);
-evB <- evo_cc_02[evo_cc_02[,3]==0.02 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
+evo_cc_02 <- read.table(file="res_c02s/evo_M00_P00_F00.txt", header=FALSE);
+evB <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
 evo <- evB[evB[,2]==beta_val,]; 
 c_WP_PO <- rep(x=0, times=gens);
 c_WP_EP <- rep(x=0, times=gens);
@@ -160,8 +160,6 @@ text(x=0, y=-0.6, label=expression(paste(c[M]==0.02)),cex=1.25, pos=4);
 text(x=0, y=-0.775, label=expression(paste(c[P]==0.00)),cex=1.25, pos=4);
 text(x=0, y=-0.95, label=expression(paste(c[F]==0.00)),cex=1.25, pos=4);
 text(x=-200, y=0.88, label="A", cex=2, pos=4);
-points(y=c(-8,4),x=c(0,10000),type="l",lwd=5); # XXX TODO XXX REMOVE THIS #
-points(y=c(4,-8),x=c(0,10000),type="l",lwd=5); # XXX TODO XXX REMOVE THIS #
 rm(evo_cc_02);
 # ------------------------------------------------------------------------#
 evo_cc_02 <- read.table(file="res_c02s/evo_M02_P00_F00.txt", header=FALSE);
@@ -373,8 +371,8 @@ setEPS(); # postscript below for final publication?
 cairo_ps("evo_corrs02_B1.eps",family="Arial",height=8,width=5.5);
 par(mfrow=c(4,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
 # ------------------------------------------------------------------------#
[…]

### 2016-08-30 initial_analysis.R
Add end correlations figure between M_a and F_a allele values

@@ -77,37 +77,914 @@ setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
 
 gens      <- 9999;
 
-evo_cc_02 <- read.table(file="res_c02s/evo_M02_P00_F00.txt", header=FALSE);
+
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX CORRELATIONS BETWEEN M[a] and F[a]  XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # ------------------------------------------------------------------------#
 # -----------  BETA = 0  -------------------------------------------------#
 # ------------------------------------------------------------------------#
 beta_val <- 0;
 setEPS(); # postscript below for final publication?
-cairo_ps("evo_corrs02_B0.eps",family="Arial",height=8,width=5.5);
+cairo_ps("end_cor_WP_EP_B0.eps",family="Arial",height=10,width=8);
 par(mfrow=c(4,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
+# ------------------------------------------------------------------------#
+evo_cc_02 <- read.table(file="res_c02s/evo_M00_P00_F00.txt", header=FALSE);
+evB <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
+evo <- evB[evB[,2]==beta_val & evB[,6]==gens,]; 
+WP  <- evo[,7];
+PO  <- evo[,8];
+EP  <- evo[,9];
+plot(x=WP,y=EP,lwd=2,ylim=c(-20,20),xlim=c(-25,10),col="black",xaxt="n",yaxt="n",
+     xlab="",ylab="",cex.lab=2,cex.axis=1.5, lty="solid");
+mod <- lm(EP~WP);
+a   <- mod$coefficients[1];
+b   <- mod$coefficients[2];
+xxx <- seq(from=min(WP),to=max(WP), by=0.01);
+yyy <- a + xxx * b;
+points(x=xxx,y=yyy,type="l",lwd=3);
[…]

### 2016-08-30 scratch.R

@@ -1,0 +1,896 @@
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX CORRELATIONS BETWEEN M[a] and F[a]  XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# ------------------------------------------------------------------------#
+# -----------  BETA = 0  -------------------------------------------------#
+# ------------------------------------------------------------------------#
+beta_val <- 0;
+setEPS(); # postscript below for final publication?
+cairo_ps("end_cor_WP_PO_B0.eps",family="Arial",height=10,width=8);
+par(mfrow=c(4,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
+# ------------------------------------------------------------------------#
+evo_cc_02 <- read.table(file="res_c02s/evo_M00_P00_F00.txt", header=FALSE);
+evB <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
+evo <- evB[evB[,2]==beta_val & evB[,6]==gens,]; 
+WP  <- evo[,7];
+PO  <- evo[,8];
+EP  <- evo[,9];
+plot(x=WP,y=PO,lwd=2,ylim=c(-20,20),xlim=c(-25,10),col="black",xaxt="n",yaxt="n",
+     xlab="",ylab="",cex.lab=2,cex.axis=1.5, lty="solid");
+mod <- lm(PO~WP);
+a   <- mod$coefficients[1];
+b   <- mod$coefficients[2];
+xxx <- seq(from=min(WP),to=max(WP), by=0.01);
+yyy <- a + xxx * b;
+points(x=xxx,y=yyy,type="l",lwd=3);
+abline(h=0,lwd=0.8,lty="dotted");
+axis(side=2,at=c(-10,0,10,20), cex.axis=1.5);
+#axis(side=1,at=c(-10,0,10,20), cex.axis=1.5);
+text(x=-25, y=-14, label=expression(paste(c[M]==0.00)),cex=1.25, pos=4);
+text(x=-25, y=-17, label=expression(paste(c[P]==0.00)),cex=1.25, pos=4);
[…]

### 2016-08-30 initial_analysis.R
Add all end correlation plots

@@ -974,9 +974,1799 @@ mtext(expression(paste("End mean inbreeding fertilisation strategy allele value 
 	outer=TRUE,side=2,line=2.5,cex=1.2);
 dev.off();
 
+
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
-# XXX XXX XXX CORRELATIONS BETWEEN M[a] and F[a]  XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX CORRELATIONS BETWEEN M[a] and P[a]  XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# ------------------------------------------------------------------------#
+# -----------  BETA = 0  -------------------------------------------------#
+# ------------------------------------------------------------------------#
+beta_val <- 0;
+setEPS(); # postscript below for final publication?
+cairo_ps("end_cor_WP_PO_B0.eps",family="Arial",height=10,width=8);
+par(mfrow=c(4,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
+# ------------------------------------------------------------------------#
+evo_cc_02 <- read.table(file="res_c02s/evo_M00_P00_F00.txt", header=FALSE);
+evB <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
+evo <- evB[evB[,2]==beta_val & evB[,6]==gens,]; 
+WP  <- evo[,7];
+PO  <- evo[,8];
+EP  <- evo[,9];
+plot(x=WP,y=PO,lwd=2,ylim=c(-20,20),xlim=c(-25,10),col="black",xaxt="n",yaxt="n",
+     xlab="",ylab="",cex.lab=2,cex.axis=1.5, lty="solid");
+mod <- lm(PO~WP);
+a   <- mod$coefficients[1];
+b   <- mod$coefficients[2];
+xxx <- seq(from=min(WP),to=max(WP), by=0.01);
+yyy <- a + xxx * b;
+points(x=xxx,y=yyy,type="l",lwd=3);
+abline(h=0,lwd=0.8,lty="dotted");
[…]

### 2016-08-30 scratch.R

@@ -1,5 +1,6 @@
+
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
-# XXX XXX XXX CORRELATIONS BETWEEN M[a] and F[a]  XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX CORRELATIONS BETWEEN M[a] and P[a]  XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # ------------------------------------------------------------------------#
 # -----------  BETA = 0  -------------------------------------------------#
@@ -30,7 +31,7 @@ text(x=-25, y=-14, label=expression(paste(c[M]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=-17, label=expression(paste(c[P]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=-20, label=expression(paste(c[F]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=18, label="A", cex=2, pos=4);
-rho1 <- as.character(round(cor(WP,EP),digits=3));
+rho1 <- as.character(round(cor(WP,PO),digits=3));
 text(x=-1, y=18, label=expression(paste("r = ")), cex=1.6, pos=4);
 text(x=2, y=18, label=rho1, cex=1.6, pos=4);
 rm(evo_cc_02);
@@ -56,7 +57,7 @@ text(x=-25, y=-14, label=expression(paste(c[M]==0.02)),cex=1.25, pos=4);
 text(x=-25, y=-17, label=expression(paste(c[P]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=-20, label=expression(paste(c[F]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=18, label="B", cex=2, pos=4);
-rho1 <- as.character(round(cor(WP,EP),digits=3));
+rho1 <- as.character(round(cor(WP,PO),digits=3));
 text(x=-1, y=18, label=expression(paste("r = ")), cex=1.6, pos=4);
 text(x=2, y=18, label=rho1, cex=1.6, pos=4);
 rm(evo_cc_02);
@@ -82,7 +83,7 @@ text(x=-25, y=-14, label=expression(paste(c[M]==0.00)),cex=1.25, pos=4);
[…]

### 2016-08-30 initial_analysis.R
Fix end correlation figures

@@ -1007,7 +1007,7 @@ text(x=-25, y=-14, label=expression(paste(c[M]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=-17, label=expression(paste(c[P]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=-20, label=expression(paste(c[F]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=18, label="A", cex=2, pos=4);
-rho1 <- as.character(round(cor(WP,PO),digits=3));
+rho1 <- as.character(round(cor(PO,WP),digits=3));
 text(x=-1, y=18, label=expression(paste("r = ")), cex=1.6, pos=4);
 text(x=2, y=18, label=rho1, cex=1.6, pos=4);
 rm(evo_cc_02);
@@ -1033,7 +1033,7 @@ text(x=-25, y=-14, label=expression(paste(c[M]==0.02)),cex=1.25, pos=4);
 text(x=-25, y=-17, label=expression(paste(c[P]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=-20, label=expression(paste(c[F]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=18, label="B", cex=2, pos=4);
-rho1 <- as.character(round(cor(WP,PO),digits=3));
+rho1 <- as.character(round(cor(PO,WP),digits=3));
 text(x=-1, y=18, label=expression(paste("r = ")), cex=1.6, pos=4);
 text(x=2, y=18, label=rho1, cex=1.6, pos=4);
 rm(evo_cc_02);
@@ -1059,7 +1059,7 @@ text(x=-25, y=-14, label=expression(paste(c[M]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=-17, label=expression(paste(c[P]==0.02)),cex=1.25, pos=4);
 text(x=-25, y=-20, label=expression(paste(c[F]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=18, label="C", cex=2, pos=4);
-rho1 <- as.character(round(cor(WP,PO),digits=3));
+rho1 <- as.character(round(cor(PO,WP),digits=3));
 text(x=-1, y=18, label=expression(paste("r = ")), cex=1.6, pos=4);
 text(x=2, y=18, label=rho1, cex=1.6, pos=4);
 rm(evo_cc_02);
[…]

### 2016-08-30 scratch.R

@@ -1,13 +1,12 @@
-
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
-# XXX XXX XXX CORRELATIONS BETWEEN M[a] and P[a]  XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX CORRELATIONS BETWEEN F[a] and P[a]  XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # ------------------------------------------------------------------------#
 # -----------  BETA = 0  -------------------------------------------------#
 # ------------------------------------------------------------------------#
 beta_val <- 0;
 setEPS(); # postscript below for final publication?
-cairo_ps("end_cor_WP_PO_B0.eps",family="Arial",height=10,width=8);
+cairo_ps("end_cor_PO_EP_B0.eps",family="Arial",height=10,width=8);
 par(mfrow=c(4,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
 # ------------------------------------------------------------------------#
 evo_cc_02 <- read.table(file="res_c02s/evo_M00_P00_F00.txt", header=FALSE);
@@ -16,12 +15,12 @@ evo <- evB[evB[,2]==beta_val & evB[,6]==gens,];
 WP  <- evo[,7];
 PO  <- evo[,8];
 EP  <- evo[,9];
-plot(x=WP,y=PO,lwd=2,ylim=c(-20,20),xlim=c(-25,10),col="black",xaxt="n",yaxt="n",
+plot(x=PO,y=EP,lwd=2,ylim=c(-20,20),xlim=c(-25,10),col="black",xaxt="n",yaxt="n",
      xlab="",ylab="",cex.lab=2,cex.axis=1.5, lty="solid");
-mod <- lm(PO~WP);
+mod <- lm(EP~PO);
 a   <- mod$coefficients[1];
 b   <- mod$coefficients[2];
-xxx <- seq(from=min(WP),to=max(WP), by=0.01);
+xxx <- seq(from=min(PO),to=max(PO), by=0.01);
 yyy <- a + xxx * b;
[…]

### 2016-08-30 initial_analysis.R
Fix correlations text on the plots showing end correlations between M[a] and P[a]

@@ -975,6 +975,8 @@ mtext(expression(paste("End mean inbreeding fertilisation strategy allele value 
 dev.off();
 
 
+
+
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX CORRELATIONS BETWEEN M[a] and P[a]  XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
@@ -1904,7 +1906,7 @@ text(x=-25, y=-14, label=expression(paste(c[M]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=-17, label=expression(paste(c[P]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=-20, label=expression(paste(c[F]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=18, label="A", cex=2, pos=4);
-rho1 <- as.character(round(cor(WP,EP),digits=3));
+rho1 <- as.character(round(cor(PO,WP),digits=3));
 text(x=-1, y=18, label=expression(paste("r = ")), cex=1.6, pos=4);
 text(x=2, y=18, label=rho1, cex=1.6, pos=4);
 rm(evo_cc_02);
@@ -1930,7 +1932,7 @@ text(x=-25, y=-14, label=expression(paste(c[M]==0.02)),cex=1.25, pos=4);
 text(x=-25, y=-17, label=expression(paste(c[P]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=-20, label=expression(paste(c[F]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=18, label="B", cex=2, pos=4);
-rho1 <- as.character(round(cor(WP,EP),digits=3));
+rho1 <- as.character(round(cor(PO,WP),digits=3));
 text(x=-1, y=18, label=expression(paste("r = ")), cex=1.6, pos=4);
 text(x=2, y=18, label=rho1, cex=1.6, pos=4);
 rm(evo_cc_02);
@@ -1956,7 +1958,7 @@ text(x=-25, y=-14, label=expression(paste(c[M]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=-17, label=expression(paste(c[P]==0.02)),cex=1.25, pos=4);
[…]

### 2016-08-30 scratch.R

@@ -1,12 +1,12 @@
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
-# XXX XXX XXX CORRELATIONS BETWEEN F[a] and P[a]  XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX CORRELATIONS BETWEEN M[a] and P[a]  XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # ------------------------------------------------------------------------#
 # -----------  BETA = 0  -------------------------------------------------#
 # ------------------------------------------------------------------------#
 beta_val <- 0;
 setEPS(); # postscript below for final publication?
-cairo_ps("end_cor_PO_EP_B0.eps",family="Arial",height=10,width=8);
+cairo_ps("end_cor_WP_PO_B0.eps",family="Arial",height=10,width=8);
 par(mfrow=c(4,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
 # ------------------------------------------------------------------------#
 evo_cc_02 <- read.table(file="res_c02s/evo_M00_P00_F00.txt", header=FALSE);
@@ -15,12 +15,12 @@ evo <- evB[evB[,2]==beta_val & evB[,6]==gens,];
 WP  <- evo[,7];
 PO  <- evo[,8];
 EP  <- evo[,9];
-plot(x=PO,y=EP,lwd=2,ylim=c(-20,20),xlim=c(-25,10),col="black",xaxt="n",yaxt="n",
+plot(x=WP,y=PO,lwd=2,ylim=c(-20,20),xlim=c(-25,10),col="black",xaxt="n",yaxt="n",
      xlab="",ylab="",cex.lab=2,cex.axis=1.5, lty="solid");
-mod <- lm(EP~PO);
+mod <- lm(PO~WP);
 a   <- mod$coefficients[1];
 b   <- mod$coefficients[2];
-xxx <- seq(from=min(PO),to=max(PO), by=0.01);
+xxx <- seq(from=min(WP),to=max(WP), by=0.01);
 yyy <- a + xxx * b;
[…]

### 2016-08-31 ms_pre_post.Rmd
End paragraph of introduction

@@
 ===================================================
+
+Here we apply a model of female and male reproductive interactions and associated inbreeding depression in offspring viability to quantify evolution of three separate traits including female tendency for polyandry, female pre-copulatory inbreeding strategy (mating strategy), and female post-copulatory inbreeding strategy (fertilisation strategy).
+We use *in silico* experiments to test the hypotheses that evolution of post-copulatory inbreeding avoidance facilitates evolution of polyandry, and that evolution of pre-copulatory versus post-copulatory inbreeding avoidance can be predicted by the relative costs of each, and the relative cost of polyandry.
+We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across reproductive systems with different relative costs and different magnitudes of inbreeding depression in offspring viability.
 

### 2016-08-31 ms_pre_post.Rmd
Revise end paragraph of introduction

@@
 Here we apply a model of female and male reproductive interactions and associated inbreeding depression in offspring viability to quantify evolution of three separate traits including female tendency for polyandry, female pre-copulatory inbreeding strategy (mating strategy), and female post-copulatory inbreeding strategy (fertilisation strategy).
-We use *in silico* experiments to test the hypotheses that evolution of post-copulatory inbreeding avoidance facilitates evolution of polyandry, and that evolution of pre-copulatory versus post-copulatory inbreeding avoidance can be predicted by the relative costs of each, and the relative cost of polyandry.
+We use *in silico* experiments to test the hypotheses that, given inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance facilitates evolution of polyandry, and that pre-copulatory but not post-copulatory inbreeding avoidance will evolve when pre-copulatory inbreeding avoidance is less costly than the combined cost of post-copulatory inbreeding avoidance and polyandry, while post-copulatory but not pre-copulatory inbreeding avoidance will evolve when pre-copulatory inbreeding avoidance is more costly than the combined costs of post-copulatory inbreeding avoidance and polyandry.
 We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across reproductive systems with different relative costs and different magnitudes of inbreeding depression in offspring viability.

### 2016-08-31 ms_pre_post.Rmd
Revise Model analysis. Outline introductory paragraphs

--- 2016-08-31 ms_pre_post.Rmd
@@
 
+<!--- TODO: GENERAL PARAGRAPH INTRODUCING THE SCOPE AND KEY QUESTION --->
+
+<!--- TODO: PARAGRAGH ON EVOLUTION OF POLYANDRY --->
+
+<!--- TODO: PARAGRAGH ON EVOLUTION OF PRE-COPULATORY INBREEDING AVOIDANCE --->
+
+<!--- TODO: PARAGRAGH ON EVOLUTION OF POST-COPULATORY INBREEDING AVOIDANCE --->
+
+<!--- TODO: PARAGRAGH ON IDEA THAT POSTCOP SELECTION COULD DRIVE SELECTION FOR POLYANDRY --->
+
+<!--- TODO: PARAGRAGH ON IDEA THAT RELATIVE COSTS WILL DETERMINE PRE VS POST --->
+
+<!--- TODO: PARAGRAGH ON COSTS OF POLYANDRY, MATING, AND FERTILISATION STRATEGIES --->
+
 Here we apply a model of female and male reproductive interactions and associated inbreeding depression in offspring viability to quantify evolution of three separate traits including female tendency for polyandry, female pre-copulatory inbreeding strategy (mating strategy), and female post-copulatory inbreeding strategy (fertilisation strategy).
-We use *in silico* experiments to test the hypotheses that evolution of post-copulatory inbreeding avoidance facilitates evolution of polyandry, and that evolution of pre-copulatory versus post-copulatory inbreeding avoidance can be predicted by the relative costs of each, and the relative cost of polyandry.
+We use *in silico* experiments to test the hypotheses that, given inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance causes selection for evolution of polyandry, and that pre-copulatory but not post-copulatory inbreeding avoidance will evolve when pre-copulatory inbreeding avoidance is less costly than the combined cost of post-copulatory inbreeding avoidance and polyandry, while post-copulatory but not pre-copulatory inbreeding avoidance will evolve when pre-copulatory inbreeding avoidance is more costly than the combined costs of post-copulatory inbreeding avoidance and polyandry.
 We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across reproductive systems with different relative costs and different magnitudes of inbreeding depression in offspring viability.
@@
 To analyse our model, we track mean values of alleles underlying tendency for polyandry ($P_{a}$), inbreeding mating strategy ($M_{a}$), and inbreeding fertilisation strategy ($F_{a}$) in a focal population.
-We present evolutionary dynamics of these mean allele values across a range of costs and inbreeding depression slopes using two types of simulations.
-First, we consider eight possible cost parameter combinations in which costs of tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$) equal either $0$ or $0.02$ [@Duthie observed $0.02$ to be strong cost of tendency for polyandry].
-Second, we fix $c_{P}$ to values of $0$, $0.01$, or $0.02$, then randomly select $c_{M}$ and $c_{F}$ values between $0-0.05$ for simulation initial starting conditions.
-The objective of the first type of simulation is to test how mean allele values change over generations in response to different combinations of costs and inbreeding depression slopes.
-The objective the second type of simulation is to predict selection for tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy, across a wider range of parameter combinations, and to therefore test under what conditions each is predicted to evolve given different combinations of costs and inbreeding depression slopes.
-
-In the first type of simulation, we record dynamics of mean values of $P_{a}$, $M_{a}$, $F_{a}$ over generations for every possible combination in which the cost associated with each of the three phenotypes ($c_{P}$, $c_{M}$, and $c_{F}$) is either $0$ or $0.02$, and for four slopes of inbreeding depression on offspring viability $\beta = {0, 1, 2, 3}$.
-Each possible cost combination is replicated ten times, and grand mean values and standard deviation of means is calculated in each generation across replicate simulations.
+We present evolutionary dynamics of these mean allele values across different combinations of inbreeding depression slopes and costs to test our two focal hypotheses.
+The combinations of costs and inbreeding depression slopes that we consider include all eight possible permutations of values of costs of tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$) equal to either $0$ or $0.02$ [@Duthie observed $0.02$ to be strong cost of tendency for polyandry], and for values of $\beta = \{1, 3\}$ ($16$ total combinations).
+In all of these simulations, we record mean values of $P_{a}$, $M_{a}$, $F_{a}$ in each generation.
+Each of the 16 possible cost combinations is replicated $40$ times, and grand mean values and standard deviation of means is calculated in each generation across replicate simulations.
 These analyses allowed us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on inbreeding fertilisation strategy might be weak if polyandry is rare).
 
-In the second type of simulation, we record and present mean values of $P_{a}$, $M_{a}$, $F_{a}$ only from the terminal generation of simulations, and for random costs of inbreeding mating strategy $c_{M} \in [0, 0.05]$ and inbreeding fertilisation strategy $c_{F} \in [0, 0.05]$, but fixed costs of tendency for polyandry $c_{P} = {0, 0.01, 0.02}$.
-We consider four values of $\beta = {0, 1, 2, 3}$, and we simulate 100 replicates for all combinations of $c_{P}$ and $\beta$.
-For different values of $\beta$ given the same $c_{P}$ value, we use the same randomly selected values of $c_{M}$ and $c_{F}$ to better infer how terminal mean allele values are affected by different magnitudes of inbreeding depression.
-We do not use the same randomly selected values of $c_{M}$ and $c_{F}$ across different values of $c_{P}$ because $c_{P}$ values were fixed *a priori* only to facilitate model inference.
-The objective of randomising costs was to sample from a broad range of parameter space, and this range is increased by selecting different $c_{M}$ and $c_{F}$ values for each $c_{P}$.
+To test our hypothesis that selection for evolution of polyandry is driven by female's ability to bias fertilisation toward inbreeding avoidance through post-copulatory mechanisms, we compare simulations in which all three phenotypes including tendency for polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilisation strategy ($F_{p}$) evolve, with an identical set of simulations in which $F_{p}$ cannot evolve.
+In simulations without evolving $F_{p}$, we therefore include all 16 combinations of $c_{P}=\{0,0.02\}$, $c_{M}=\{0,0.02\}$, $c_{F}=\{0,0.02\}$, and $\beta = \{1,3\}$ replicated 40 times each.
+To stop $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes resulting from $F_{a}$ cause random fertilisation with respect to kinship.
+Hence, while mutation and drift can still occur for $F_{a}$ alleles, these alleles have no phenotypic effect and polyandry cannot cause polyandrous females to benefit through an increased ability to bias fertilisation toward inbreeding avoidance.
+By comparing evolution of mean $P_{p}$ values over generations when $F_{p}$ also evolves versus when $F_{p}=0$ (random fertilisation), we test whether or not evolution of inbreeding fertilisation strategy increases selection for evolution of polyandry.
 
-For each replicate simulation with a unique set of costs, we classify the evolutionary outcome of inbreeding stragies in the simulation in one of four ways: (1) Weak selection for inbreding mating strategy and inbreeding fertilisation strategy, (2) weak selection for inbreeding mating strategy and strong selection for inbreeding fertilisation strategy, (3) strong selection for inbreeding mating strategy and weak selection for inbreeding fertilisation strategy, and (4) strong selection for inbreeding mating strategy and inbreeding fertilisation strategy.
-We additionally classify the evolutionary outcome of tendency for polyandry in the simulation as either weak selection for polyandry or strong selection for polyandry.
-@Duthie showed that selection for inbreeding preference (positive values of $M_{a}$) is predicted when inbreeding depression on offspring viability is $\beta=0$, but selection for inbreeding avoidance (negative values of $M_{a}$) is predicted when $\beta \geq 1$.
-When referring to strong selection for inbreeding mating strategy and inbreeding fertilisation strategy, we therefore refer specifically to inbreeding preference when $\beta=0$ and inbreeding avoidance when $\beta \geq 1$.
-Strong selection is inferred when mean allele values exceed $1$ (when $\beta = 0$) or are less than $-1$ (when $\beta \geq 1$), otherwise selection is inferred to be weak.
-Exploratory simulations suggest that cutoff values of $1$ and $-1$ are conservative for inferring when selection is strong, and other cutoff values do not change the general pattern of evolutionary outcomes (1-4) across cost parameter values.
+To test hypotheses regarding evolution under different relative costs of phenotypes, we consider all combinations of costs and inbreeding depression parameter values using only simulations in which all three traits evolve.
+To test our hypothesis that inbreeding mating strategy will evolve toward inbreeding avoidance ($M_{p}<0$) when mating costs are low relative to the costs of tendency for polyandry and inbreeding fertilisation strategy, but that selection for inbreeding fertilisation strategy will then be negligible ($F_{p} \approx 0$), we quantify evolution of $M_{p}$ and $F_{p}$ over generations in simulations where $c_{M}=0$ but $c_{P}$, $c_{F}$, or both equals $0.02$.
+We compare evolution in these three cost parameter value combinations with simulations in which all costs equal either $0$ or $0.02$.
+If our hypothesis is supported, then $M_{p}$ but not $F_{p}$ will evolve to more negative values when $c_{M}$ is relatively low than when all cost values are uniform.
 
-For all replicates in both the first and second simulation types, we set the maximum number of generations to 5000, which exploratory simulations and previous modelling [@Duthie] showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
+To test the complementary hypothesis that inbreeding fertilisation strategy will evolve toward inbreeding avoidance ($F_{p}<0$) given low costs of polyandry and inbreeding fertilisation strategy relative to the cost of inbreeding mating strategy, but that selection on inbreeding mating strategy will be negligible ($M_{p} \approx 0$), we qualtify evolution of $M_{p}$ and $F_{p}$ over generations when $c_{F}=0$, $c_{P}=0$, and $c_{M}=0.02$.
+We compare evolution for this combination of cost parameter values with simulations in which all costs equal either $0$ or $0.02$.
+If our hypothesis is supported, then $F_{p}$ but not $M_{p}$ will evolve to more negative values when $c_{F}$ is relative low than when all cost values are uniform.
+
+For all replicates, we set the maximum number of generations to 10000, which exploratory simulations and previous modelling [@Duthie] showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
 For all replicates, we set the number of immigrants per generation to $\rho=5$, which produced a range of kin and non-kin in each generation such that females could express inbreeding strategies.

### 2016-08-31 initial_analysis.R
Add mean allele value over generation phenotypes for knock-out simulations

@@ -975,8 +975,6 @@ mtext(expression(paste("End mean inbreeding fertilisation strategy allele value 
 dev.off();
 
 
-
-
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX CORRELATIONS BETWEEN M[a] and P[a]  XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
@@ -1160,7 +1158,7 @@ yyy <- a + xxx * b;
 points(x=xxx,y=yyy,type="l",lwd=3);
 abline(h=0,lwd=0.8,lty="dotted");
 axis(side=2,at=c(-10,0,10,20), cex.axis=1.5);
-axis(side=1,at=c(-10,0,10,20), cex.axis=1.5);
+axis(side=1,at=c(-20,-10,0,10), cex.axis=1.5);
 text(x=-25, y=-14, label=expression(paste(c[M]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=-17, label=expression(paste(c[P]==0.02)),cex=1.25, pos=4);
 text(x=-25, y=-20, label=expression(paste(c[F]==0.02)),cex=1.25, pos=4);
@@ -1384,7 +1382,7 @@ yyy <- a + xxx * b;
 points(x=xxx,y=yyy,type="l",lwd=3);
 abline(h=0,lwd=0.8,lty="dotted");
 axis(side=2,at=c(-10,0,10,20), cex.axis=1.5);
-axis(side=1,at=c(-10,0,10), cex.axis=1.5);
+axis(side=1,at=c(-20,-10,0,10), cex.axis=1.5);
 text(x=-25, y=-14, label=expression(paste(c[M]==0.00)),cex=1.25, pos=4);
 text(x=-25, y=-17, label=expression(paste(c[P]==0.02)),cex=1.25, pos=4);
 text(x=-25, y=-20, label=expression(paste(c[F]==0.02)),cex=1.25, pos=4);
@@ -1607,7 +1605,7 @@ yyy <- a + xxx * b;
 points(x=xxx,y=yyy,type="l",lwd=3);
 abline(h=0,lwd=0.8,lty="dotted");
 axis(side=2,at=c(-10,0,10,20), cex.axis=1.5);
[…]

### 2016-08-31 ms_pre_post.Rmd
Clarify that there is no cost of phenotype in the knockout model in the 'Model analysis'

@@
 To stop $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes resulting from $F_{a}$ cause random fertilisation with respect to kinship.
-Hence, while mutation and drift can still occur for $F_{a}$ alleles, these alleles have no phenotypic effect and polyandry cannot cause polyandrous females to benefit through an increased ability to bias fertilisation toward inbreeding avoidance.
+Hence, while mutation and drift can still occur for $F_{a}$ alleles, these alleles have no phenotypic effect and polyandry cannot cause polyandrous females to benefit through an increased ability to bias fertilisation toward inbreeding avoidance (under such conditions, there can also never be a cost of $F_{p}$, meaning that $c_{F}=0$).
 By comparing evolution of mean $P_{p}$ values over generations when $F_{p}$ also evolves versus when $F_{p}=0$ (random fertilisation), we test whether or not evolution of inbreeding fertilisation strategy increases selection for evolution of polyandry.

### 2016-09-01 ms_pre_post.Rmd
First sentence of introduction

@@
 <!--- TODO: GENERAL PARAGRAPH INTRODUCING THE SCOPE AND KEY QUESTION --->
-
-<!--- TODO: PARAGRAGH ON EVOLUTION OF POLYANDRY --->
+Reproductive decisions expressed among interacting individuals directly affect individual fitnesses and the viabilities and genotypes of resulting offspring, and thereby profoundly affect evolutionary dynamics through the differential inheritence of alleles over generations [@Pizzari2012; @Wright2013; @Wild2014; @Liao2015; @Reid2016].
 
@@
 <!--- TODO: PARAGRAGH ON EVOLUTION OF POST-COPULATORY INBREEDING AVOIDANCE --->
+
+<!--- TODO: PARAGRAGH ON EVOLUTION OF POLYANDRY --->
 
@@
 
+<!--- TODO: OVERVIEW OF THE POINT OF THE MODELLING --->
 Here we apply a model of female and male reproductive interactions and associated inbreeding depression in offspring viability to quantify evolution of three separate traits including female tendency for polyandry, female pre-copulatory inbreeding strategy (mating strategy), and female post-copulatory inbreeding strategy (fertilisation strategy).

### 2016-09-01 ms_pre_post.Rmd
Most of first paragraph of Introduction

@@
 Reproductive decisions expressed among interacting individuals directly affect individual fitnesses and the viabilities and genotypes of resulting offspring, and thereby profoundly affect evolutionary dynamics through the differential inheritence of alleles over generations [@Pizzari2012; @Wright2013; @Wild2014; @Liao2015; @Reid2016].
+For example, the number of mates that an individual has is a fundamental reproductive decision that can directly and indirectly affect an individual's fitness, and potentially alter the distribution of genotypes and patterns of inheritence within focal populations [e.g., @Cornell2007; @Diaz2010; @Okada2015; @Roberts2015a].
+The number of mates that an individual chooses, and its expression of mate choice with respect to the potential mates available, might be affected by a mate's genetic quality or complementarity [@Parker2006; @Mays2008].
+
+However, --- something something something patterns of outcomes between mate quality and number fundamentally complex ---.
+
+<!--- TODO: PARAGRAGH ON EVOLUTION OF POLYANDRY --->
 
@@
 <!--- TODO: PARAGRAGH ON EVOLUTION OF POST-COPULATORY INBREEDING AVOIDANCE --->
-
-<!--- TODO: PARAGRAGH ON EVOLUTION OF POLYANDRY --->
 

### 2016-09-02 ms_pre_post.Rmd
Finish first introductory paragraph

--- 2016-09-01 ms_pre_post.Rmd
@@
 <!--- TODO: GENERAL PARAGRAPH INTRODUCING THE SCOPE AND KEY QUESTION --->
-Reproductive decisions expressed among interacting individuals directly affect individual fitnesses and the viabilities and genotypes of resulting offspring, and thereby profoundly affect evolutionary dynamics through the differential inheritence of alleles over generations [@Pizzari2012; @Wright2013; @Wild2014; @Liao2015; @Reid2016].
+Reproductive decisions expressed among interacting individuals directly affect individual fitnesses and the genotypes and viabilities of resulting offspring, and thereby profoundly affect evolutionary dynamics through the differential inheritence of alleles over generations [@Pizzari2012; @Wright2013; @Wild2014; @Liao2015; @Reid2016].
+For example, the frequency at which a focal female mates is a reproductive decision that can directly and indirectly affect her fitness, and potentially alter the distribution of genotypes and patterns of inheritence within a population [e.g., @Cornell2007; @Diaz2010; @Okada2015; @Roberts2015a; @Worthington2016].
+Her mating frequency and expression of mate choice might be affected by the genetic quality or complementarity of available potential mates [@Parker1983 @Parker2006], such as when focal females mate multiply (i.e., polyandry) to avoid inbreeding [e.g., @Mays2008; @Brouwer2011; @Kingma2013; @Duthie].
+Mate choice might therefore be realised by evolution of multiple, potentially interdependent, behavioural and physiological phenotypes affecting mating frequency and pre-copulatory and post-copulatory inbreeding avoidance.
+However, no general modelling framework predicts the conditions under which polyandry, pre-copulatory inbreeding avoidance, and post-copulatory inbreeding avoidance jointly evolve, meaning that there are no formal hypotheses for predicting which of these reproductive decisions should arise across different biological systems.
 
-<!--- TODO: PARAGRAGH ON EVOLUTION OF PRE-COPULATORY INBREEDING AVOIDANCE --->
-
-<!--- TODO: PARAGRAGH ON EVOLUTION OF POST-COPULATORY INBREEDING AVOIDANCE --->
+<!--- TODO: PARAGRAGH ON INBREEDING, PRE-COP, AND POST-COP AVOIDANCE --->
 

### 2016-09-02 ms_pre_post.Rmd
Three introductory paragraphs, one sentence on polyandry paragrpah of introduction

--- 2016-09-01 ms_pre_post.Rmd
@@
   word_document: null
+header-includes:
+- \usepackage{natbib}
+- \usepackage{lineno}
+- \linenumbers
+- \bibliographystyle{amnatnat}
 linestretch: 1
@@
 <!--- TODO: GENERAL PARAGRAPH INTRODUCING THE SCOPE AND KEY QUESTION --->
-Reproductive decisions expressed among interacting individuals directly affect individual fitnesses and the viabilities and genotypes of resulting offspring, and thereby profoundly affect evolutionary dynamics through the differential inheritence of alleles over generations [@Pizzari2012; @Wright2013; @Wild2014; @Liao2015; @Reid2016].
+Reproductive decisions expressed among interacting individuals directly affect individual fitnesses and the genotypes and viabilities of resulting offspring, and thereby profoundly affect evolutionary dynamics through the differential inheritence of alleles over generations [@Pizzari2012; @Wright2013; @Wild2014; @Liao2015; @Reid2016].
+For example, how often a focal female mates is a reproductive decision that can directly and indirectly affect her fitness, and potentially alter the distribution of genotypes and patterns of inheritence within a population [e.g., @Cornell2007; @Diaz2010; @Okada2015; @Roberts2015a; @Worthington2016].
+Her mating frequency and expression of mate choice might be affected by the genetic quality or complementarity of available potential mates, and mate choice might occur before or after copulation [@Parker1983; @Parker2006; @Kuijper2012].
+Female mate choice might therefore be realised by evolution of multiple, potentially interdependent, behavioural and physiological phenotypes operating in tandem.
+However, no general modelling framework predicts the conditions under which polyandry, pre-copulatory mate choice, and post-copulatory mate choice evolve together, meaning that there are no formal hypotheses for predicting the relevance of these reproductive decisions across different biological systems.
 
-<!--- TODO: PARAGRAGH ON EVOLUTION OF PRE-COPULATORY INBREEDING AVOIDANCE --->
+<!--- TODO: PARAGRAGH ON INBREEDING, PRE-COP, AND POST-COP AVOIDANCE --->
+Inbreeding, defined as breeding between relatives, directly affects inheritence of identical-by-descent alleles and the viability of inbred offspring, meaning that the decision to prefer, avoid, or tolerate (i.e., mate randomly with respect to relatedness) is predicted to have profound effects on individual fitness [@Parker2006; @Kokko2006; @Szulkin2012; @Duthie2015a].
+Viability of inbred offspring typically decreases with increasing relatedness between parents [termed 'inbreeding depression'; @Keller2002; @Charlesworth2009].
+If inbreeding depression is sufficiently weak, selection for female inbreeding preference is predicted because inbreeding increases the reproductive success of a focal female's male relative, thereby increasing the number of identical-by-descent copies present in her offspring [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
+However, if inbreeding depression is moderate to strong, selection for female inbreeding avoidance is predicted [@Duthie].
+Female inbreeding strategy can be enacted before or after copulation occurs [e.g., @Tuni2013; @Firman2015; @Daniel2015; @Fischer2015].
+However, models of inbreeding do not consider pre-copulatory inbreeding strategy (hereafter 'inbreeding mating strategy') and post-copulatory inbreeding strategy (hereafter 'inbreeding fertilisation strategy') jointly, meaning that it is unclear when selection for either or both strategies is predicted in empirical systems.
 
-<!--- TODO: PARAGRAGH ON EVOLUTION OF POST-COPULATORY INBREEDING AVOIDANCE --->
+<!--- such as when focal females mate multiply (i.e., polyandry) to avoid inbreeding  [e.g., @Mays2008; @Brouwer2011; @Kingma2013; @Duthie] --->
 
 <!--- TODO: PARAGRAGH ON EVOLUTION OF POLYANDRY --->
+Critically, evolution of post-copulatory inbreeding avoidance is precluded if females only mate with one male, meaning that evolution of polyandry is intrinsically tied to female inbreeding fertilisation strategy.
 

### 2016-09-05 ms_pre_post.Rmd
Add introductory paragraph on the evolution of polyandry

@@
 For example, how often a focal female mates is a reproductive decision that can directly and indirectly affect her fitness, and potentially alter the distribution of genotypes and patterns of inheritence within a population [e.g., @Cornell2007; @Diaz2010; @Okada2015; @Roberts2015a; @Worthington2016].
-Her mating frequency and expression of mate choice might be affected by the genetic quality or complementarity of available potential mates, and mate choice might occur before or after copulation [@Parker1983; @Parker2006; @Kuijper2012].
-Female mate choice might therefore be realised by evolution of multiple, potentially interdependent, behavioural and physiological phenotypes operating in tandem.
-However, no general modelling framework predicts the conditions under which polyandry, pre-copulatory mate choice, and post-copulatory mate choice evolve together, meaning that there are no formal hypotheses for predicting the relevance of these reproductive decisions across different biological systems.
+Her mating frequency and expression of mate choice might be affected by the genetic quality or complementarity of available potential mates, and her choosiness might additionally be expressed through post-copulatory mechanisms [@Parker1983; @Parker2006; @Kuijper2012].
+Female choice might therefore be realised by evolution of multiple, potentially interdependent, behavioural and physiological phenotypes operating in tandem.
+However, no general modelling framework predicts the conditions under which polyandry, pre-copulatory choice, and post-copulatory choice evolve together, meaning that there are no formal hypotheses for predicting the relevance of these reproductive decisions across different biological systems.
 
 <!--- TODO: PARAGRAGH ON INBREEDING, PRE-COP, AND POST-COP AVOIDANCE --->
-Inbreeding, defined as breeding between relatives, directly affects inheritence of identical-by-descent alleles and the viability of inbred offspring, meaning that the decision to prefer, avoid, or tolerate (i.e., mate randomly with respect to relatedness) is predicted to have profound effects on individual fitness [@Parker2006; @Kokko2006; @Szulkin2012; @Duthie2015a].
+Inbreeding, defined as breeding between relatives, directly affects inheritence of identical-by-descent alleles and the viability of inbred offspring, meaning that the decision to prefer, avoid, or tolerate (i.e., mate randomly with respect to relatedness) inbreeding is predicted to have profound effects on individual fitness [@Parker2006; @Kokko2006; @Szulkin2012; @Duthie2015a].
 Viability of inbred offspring typically decreases with increasing relatedness between parents [termed 'inbreeding depression'; @Keller2002; @Charlesworth2009].
@@
 Critically, evolution of post-copulatory inbreeding avoidance is precluded if females only mate with one male, meaning that evolution of polyandry is intrinsically tied to female inbreeding fertilisation strategy.
-
-<!--- TODO: PARAGRAGH ON IDEA THAT POSTCOP SELECTION COULD DRIVE SELECTION FOR POLYANDRY --->
+Although polyandry is commonplace in wild populations, the regularity with which it is observed in the wild remains theoretically puzzling because engaging in polyandry does not necessarily increase the number of offspring that a female produces, meaning that the fitness benefits associated with polyandry are not always clear [@Parker2013; Taylor2014].
+It has been hypothesised that females can acheive a net fitness benefit if polyandry provides them with additional opportunities to adjust their inbreeding through copulations with additional males [e.g., @Tregenza2002; @Akcay2007; @Lehtonen2015].
+@Duthie showed that selection for polyandry to facilitate inbreeding avoidance is sometimes predicted, but only under highly constrained conditions in which very few males are available during a female's initial mate choice but many males are available during a female's additional mate choice(s), or when expression of polyandry is conditionally expressed based on the degree of inbreeding in a female's initially chosen mate.
+However, @Duthie assumed that polyandrous females had no control over the assignment of paternity to their offspring.
+If after engaging in polyandry, females could bias paternity toward non-relatives, then selection for polyandry to avoid inbreeding might be more widely predicted.
+However, no models quantify the degree to which expression of biased paternity resulting from evolving inbreeding fertilisation strategy can feedback to drive evolution of polyandry in populations of potentially inbreeding females and males with biologically realistic distributions of relatedness.
 

### 2016-09-05 ms_pre_post.Rmd
Add introductory paragraph on interaction between different types of inbreeding strategy

@@
   html_document: default
-  word_document: null
+  word_document:
+    fig_caption: yes
+    pandoc_args:
+    - --csl
+    - evolution.csl
 header-includes:
@@
 linestretch: 1
+csl: evolution.csl
 bibliography: ms_pre_post.bib
@@
 Critically, evolution of post-copulatory inbreeding avoidance is precluded if females only mate with one male, meaning that evolution of polyandry is intrinsically tied to female inbreeding fertilisation strategy.
-Although polyandry is commonplace in wild populations, the regularity with which it is observed in the wild remains theoretically puzzling because engaging in polyandry does not necessarily increase the number of offspring that a female produces, meaning that the fitness benefits associated with polyandry are not always clear [@Parker2013; Taylor2014].
+Although polyandry is commonplace in wild populations, the regularity with which it is observed in the wild remains theoretically puzzling because engaging in polyandry does not necessarily increase the number of offspring that a female produces, meaning that the fitness benefits associated with polyandry are not always clear [@Parker2013; @Taylor2014].
 It has been hypothesised that females can acheive a net fitness benefit if polyandry provides them with additional opportunities to adjust their inbreeding through copulations with additional males [e.g., @Tregenza2002; @Akcay2007; @Lehtonen2015].
@@
 However, @Duthie assumed that polyandrous females had no control over the assignment of paternity to their offspring.
-If after engaging in polyandry, females could bias paternity toward non-relatives, then selection for polyandry to avoid inbreeding might be more widely predicted.
+If after engaging in polyandry, females could bias paternity toward non-relatives, then selection for polyandry to avoid inbreeding might be more widely predicted [@Zeh1997].
 However, no models quantify the degree to which expression of biased paternity resulting from evolving inbreeding fertilisation strategy can feedback to drive evolution of polyandry in populations of potentially inbreeding females and males with biologically realistic distributions of relatedness.
@@
 <!--- TODO: PARAGRAGH ON IDEA THAT RELATIVE COSTS WILL DETERMINE PRE VS POST --->
+Evolution of inbreeding fertilisation stratey might increase selection for polyandry, but evolutionary feedbacks between inbreeding fertilisation strategy and polyandry might also be contingent upon evolution of inbreeding mating strategy, thereby leading to complex evolutionary dynamics between inbreeding strategies and polyandry.
+For example, if females can acheive their desired degree of inbreeding through mate choice alone, then subsequent polyandry and inbreeding fertilisation strategy might be superfluous for increasing female fitness.
+Alternatively, if females are often unsuccessful at realising their inbreeding mating strategy due to factors such as sexual conflict over mating and resulting male coercion [e.g., @Parker2006], limited kin recognition amongst potential mates [e.g., @Penn2010], or simply the inherent stochasticity associated with mate encounters or expression of mate choice based on inbreeding [e.g., @Kokko2006; @Duthie], then selection on inbreeding fertilisation strategy might occur to reinforce inbreeding mating strategy.
+In empirical systems where inbreeding depression is severe and inbreeding avoidance is therefore beneficial, expression of inbreeding mating strategy and inbreeding fertilisation strategy have been observed across diverse taxa [e.g., @Gasparini2011; @Tuni2013; @Firman2015; @Fischer2015; @Daniel2015].
+However, no models predict *a priori* which of these inbreeding strategies should be observed when inbreeding depression is sufficiently severe to make inbreeding avoidance adaptive.
 
@@
 
+<!--- The initial evolution of inbreeding fertilisation strategy might be further facilitated if the phenotypic expression of polyandry is caused by continuous genetic variation underlying a female's tendency for engaging in polyandry, as is expected for complex polygenic traits underlying behaviour under the fundamental assumptions of quantitative genetics [@Evans2008].
+Under quantitative genetic assumptions, polyandry can therefore be conceptualised as a 'threshold trait', meaning that multiple mating is only realised above some threshold genetic value [@Lynch1998].
+Expression of  --->
+
 Acknowledgements

### 2016-09-05 ms_pre_post.Rmd
Start introductory cost paragraph, and separate polyandry and inbreeding mating strategy costs in the Model

@@
 
-<!--- TODO: PARAGRAGH ON IDEA THAT RELATIVE COSTS WILL DETERMINE PRE VS POST --->
+<!--- TODO: PARAGRAGH ON IDEA OF PRE VS POST COPULATORY INBREEDING STRATEGY --->
 Evolution of inbreeding fertilisation stratey might increase selection for polyandry, but evolutionary feedbacks between inbreeding fertilisation strategy and polyandry might also be contingent upon evolution of inbreeding mating strategy, thereby leading to complex evolutionary dynamics between inbreeding strategies and polyandry.
@@
 <!--- TODO: PARAGRAGH ON COSTS OF POLYANDRY, MATING, AND FERTILISATION STRATEGIES --->
+Evolution of polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy will ultimately be determined by the, potentially interacting, fitness benefits and costs of each phenotype.
+Given severe inbreeding depression, phenotypes will increase a focal female's fitness by causing her to avoid breeding with close relatives.
+However, evolution of phenotypes will also be directly affected by negative selection (i.e., costs) associated with the tendency to engage in polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
+
+<!--- Mate searching: Lehmann2013, Kokko2006, Jamieson2009.
+Kin discrimination: Waser1986.
+Increased predation risk associated with mate search: Rowe1988, Ronkainen1994, Koga1998.
+Increased risk associated with expression of mate choice (e.g., avoiding male coercion): Rowe1994.
+Risk of not mating due to choosiness: Kokko2013
 
@@
 Here we apply a model of female and male reproductive interactions and associated inbreeding depression in offspring viability to quantify evolution of three separate traits including female tendency for polyandry, female pre-copulatory inbreeding strategy (mating strategy), and female post-copulatory inbreeding strategy (fertilisation strategy).
-We use *in silico* experiments to test the hypotheses that, given inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance causes selection for evolution of polyandry, and that pre-copulatory but not post-copulatory inbreeding avoidance will evolve when pre-copulatory inbreeding avoidance is less costly than the combined cost of post-copulatory inbreeding avoidance and polyandry, while post-copulatory but not pre-copulatory inbreeding avoidance will evolve when pre-copulatory inbreeding avoidance is more costly than the combined costs of post-copulatory inbreeding avoidance and polyandry.
+We use individual-based modelling and *in silico* experiments to test the hypotheses that, given inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance causes selection for evolution of polyandry, and that pre-copulatory but not post-copulatory inbreeding avoidance will evolve when pre-copulatory inbreeding avoidance is less costly than the combined cost of post-copulatory inbreeding avoidance and polyandry, while post-copulatory but not pre-copulatory inbreeding avoidance will evolve when pre-copulatory inbreeding avoidance is more costly than the combined costs of post-copulatory inbreeding avoidance and polyandry.
 We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across reproductive systems with different relative costs and different magnitudes of inbreeding depression in offspring viability.
@@
 
+<!--- Change mating cost to an increased risk of mating failure ---> 
 Values of phenotypic traits for tendency to engage in polyandry ($P_{p}$), mating ($M_{p}$), and fertilistation ($F_{p}$) each have costs, which independently increase the probability of a focal female's reproductive failure.
 These costs are all expressed prior to mating.
-In the case of tendency to engage in polyandry and inbreeding mating strategy, costs of $P_{p}$ ($c_{P}$) and $M_{p}$ ($c_{M}$) are interpreted biologically as costs associated with mate searching or courtship [e.g., @Rowe1988; @Rowe1994; @Ronkainen1994; @Koga1998; @Lasley-Rasher2012].
-In the case of inbreeding fertilisation strategy, the cost of $F_{p}$ ($c_{F}$) is interpreted as an energetic cost associated with the physiological or biochemical mechanisms that need to be developed to bias fertilsation for inbreeding avoidance or inbreeding preference [e.g., @Gasparini2011].
+In the case of tendency to engage in polyandry, the cost of $P_{p}$ ($c_{P}$) is interpreted biologically as a cost associated with mate searching or courtship [e.g., @Rowe1988; @Rowe1994; @Ronkainen1994; @Koga1998; @Lasley-Rasher2012].
+For inbreeding mating strategy, the cost of $M_{p}$ ($c_{M}$) is interpreted biologically as a cost associated with risk of mating failure due to females being overly choosy [e.g., @Kokko2013], and for inbreeding fertilisation strategy, the cost of $F_{p}$ ($c_{F}$) is interpreted as an energetic cost associated with the physiological or biochemical mechanisms that need to be developed to bias fertilsation for inbreeding avoidance or inbreeding preference [e.g., @Gasparini2011].
 Each cost independently increases the risk of female pre-mating mortality and, because generations are non-overlapping, total reproductive failure as a linear function of its associated trait.

### 2016-09-06 initial_analysis.R
Add new figures showing knockout scenarios (2 \times 2 instead of 4 \times 2

@@ -7041,9 +7041,951 @@ mtext(expression(paste("Mean allele value")),
 dev.off();
 #==========================================================================
 
+
+
+
+
+
+
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX SAME THING BELOW, BUT FOR THE KNOCK-OUT OF MATING TRAITS    XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+
+rm(list=ls()); 
+library(scatterplot3d);
+setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
+
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX Multi-panel figure of traits over generations   XXX XXX XXX #
+# XXX XXX XXX combinations of costs = {0, 0.02}               XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+
+gens      <- 9999;
+
+# ------------------------------------------------------------------------#
+# -----------  BETA = 1  -------------------------------------------------#
+# ------------------------------------------------------------------------#
+beta_val <- 1;
+setEPS(); # postscript below for final publication?
[…]

### 2016-09-06 initial_analysis.R
Fix new 2 by 2 figures -- correct axes and add relevant lines

@@ -7680,7 +7680,7 @@ plot(x=xxx,y=mWP,type="l",lwd=2,ylim=c(-9,4),col="blue",xaxt="n",
      xlab="",ylab="Allele value",cex.lab=2,cex.axis=1.5,yaxt="n");
 axis(side=2,at=c(-8,-4,0,4), cex.axis=1.5);
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
-#points(x=xxx,y=mEP,type="l",lwd=2,col="black");
+points(x=xxx,y=rep(x=0,times=length(xxx)),type="l",lwd=2,col="black");
 abline(h=0,lwd=0.8,lty="dotted");
 uWP <- mWP + sWP / sqrt(sum(evo[,6]==gens));
 lWP <- mWP - sWP / sqrt(sum(evo[,6]==gens));
@@ -7714,7 +7714,7 @@ len <- dim(evo)[1];
 plot(x=xxx,y=mWP,type="l",lwd=2,ylim=c(-9,4),col="blue",xaxt="n",yaxt="n",
      xlab="",ylab="",cex.lab=2,cex.axis=1.5);
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
-#points(x=xxx,y=mEP,type="l",lwd=2,col="black");
+points(x=xxx,y=rep(x=0,times=length(xxx)),type="l",lwd=2,col="black");
 uWP <- mWP + sWP / sqrt(sum(evo[,6]==gens));
 lWP <- mWP - sWP / sqrt(sum(evo[,6]==gens));
 uPO <- mPO + sPO / sqrt(sum(evo[,6]==gens));
@@ -7750,7 +7750,7 @@ plot(x=xxx,y=mWP,type="l",lwd=2,ylim=c(-9,4),col="blue",xaxt="n",
 axis(side=2,at=c(-8,-4,0,4), cex.axis=1.5);
 axis(side=1,at=c(0,2000,4000,6000,8000), cex.axis=1.5);
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
-#points(x=xxx,y=mEP,type="l",lwd=2,col="black");
+points(x=xxx,y=rep(x=0,times=length(xxx)),type="l",lwd=2,col="black");
 abline(h=0,lwd=0.8,lty="dotted");
 uWP <- mWP + sWP / sqrt(sum(evo[,6]==gens));
 lWP <- mWP - sWP / sqrt(sum(evo[,6]==gens));
[…]

### 2016-09-06 initial_analysis.R
Add key figures in front

@@ -1,3 +1,648 @@
+
+rm(list=ls()); 
+
+setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
+gens      <- 9999;
+# ------------------------------------------------------------------------#
+# -----------  BETA = 3  -------------------------------------------------#
+# ------------------------------------------------------------------------#
+beta_val <- 3;
+setEPS(); # postscript below for final publication?
+cairo_ps("figures/evo_combs02_B3.eps",family="Arial",height=8,width=5.5);
+par(mfrow=c(4,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
+# ------------------------------------------------------------------------#
+evo_cc_02 <- read.table(file="res_c02s/evo_M00_P00_F00.txt", header=FALSE);
+evB <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
+evo <- evB[evB[,2]==beta_val,];
+mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
+mPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=mean);
+mEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=mean);
+sWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=sd);
+sPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=sd);
+sEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=sd);
+xxx <- tapply(X=evo[,6],INDEX=evo[,6],FUN=mean);
+len <- dim(evo)[1];
+plot(x=xxx,y=mWP,type="l",lwd=2,ylim=c(-9,4),col="blue",xaxt="n",
+     xlab="",ylab="Allele value",cex.lab=2,cex.axis=1.5,yaxt="n");
+axis(side=2,at=c(-8,-4,0,4), cex.axis=1.5);
+points(x=xxx,y=mPO,type="l",lwd=2,col="red");
+points(x=xxx,y=mEP,type="l",lwd=2,col="black");
[…]

### 2016-09-06 ms_pre_post.Rmd
Fix to only \beta = 3 in the manuscript, and tweaks to the main figures up front

@@
 We present evolutionary dynamics of these mean allele values across different combinations of inbreeding depression slopes and costs to test our two focal hypotheses.
-The combinations of costs and inbreeding depression slopes that we consider include all eight possible permutations of values of costs of tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$) equal to either $0$ or $0.02$ [@Duthie observed $0.02$ to be strong cost of tendency for polyandry], and for values of $\beta = \{1, 3\}$ ($16$ total combinations).
+The combinations of costs and inbreeding depression slopes that we consider include all eight possible permutations of values of costs of tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$) equal to either $0$ or $0.02$ [@Duthie observed $0.02$ to be strong cost of tendency for polyandry], and for values of $\beta = 3$ ($8$ total combinations).
 In all of these simulations, we record mean values of $P_{a}$, $M_{a}$, $F_{a}$ in each generation.
@@
 To test our hypothesis that selection for evolution of polyandry is driven by female's ability to bias fertilisation toward inbreeding avoidance through post-copulatory mechanisms, we compare simulations in which all three phenotypes including tendency for polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilisation strategy ($F_{p}$) evolve, with an identical set of simulations in which $F_{p}$ cannot evolve.
-In simulations without evolving $F_{p}$, we therefore include all 16 combinations of $c_{P}=\{0,0.02\}$, $c_{M}=\{0,0.02\}$, $c_{F}=\{0,0.02\}$, and $\beta = \{1,3\}$ replicated 40 times each.
+In simulations without evolving $F_{p}$, we therefore include all 16 combinations of $c_{P}=\{0,0.02\}$, $c_{M}=\{0,0.02\}$, $c_{F}=\{0,0.02\}$, and $\beta = 3$ replicated 40 times each.
 To stop $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes resulting from $F_{a}$ cause random fertilisation with respect to kinship.

### 2016-09-06 initial_analysis.R

@@ -339,8 +339,8 @@ polygon(y=c(lWP,rev(uWP)),x=c(1:(gens+1),(gens+1):1),border=NA,col="lightblue");
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 #points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 points(x=xxx,y=mWP,type="l",lwd=2,col="blue");
-text(x=0, y=-6.0, label=expression(paste(c[M]==0.00)),cex=1, pos=4);
-text(x=0, y=-7.25, label=expression(paste(c[P]==0.00)),cex=1, pos=4);
+text(x=0, y=-7.15, label=expression(paste(c[M]==0.00)),cex=1, pos=4);
+text(x=0, y=-8.50, label=expression(paste(c[P]==0.00)),cex=1, pos=4);
 #text(x=0, y=-8.5, label=expression(paste(c[F]==0.00)),cex=1, pos=4);
 points(x=xxx,y=rep(x=0,times=length(xxx)),type="l",lwd=2,col="black");
 text(x=-100, y=3.0, label="A", cex=2, pos=4);
@@ -374,8 +374,8 @@ points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 polygon(y=c(lWP,rev(uWP)),x=c(1:(gens+1),(gens+1):1),border=NA,col="lightblue");
 points(x=xxx,y=mWP,type="l",lwd=2,col="blue");
 abline(h=0,lwd=0.8,lty="dotted");
-text(x=0, y=-6.0, label=expression(paste(c[M]==0.02)),cex=1, pos=4);
-text(x=0, y=-7.25, label=expression(paste(c[P]==0.00)),cex=1, pos=4);
+text(x=0, y=-7.15, label=expression(paste(c[M]==0.02)),cex=1, pos=4);
+text(x=0, y=-8.50, label=expression(paste(c[P]==0.00)),cex=1, pos=4);
 #text(x=0, y=-8.5, label=expression(paste(c[F]==0.00)),cex=1, pos=4);
 points(x=xxx,y=rep(x=0,times=length(xxx)),type="l",lwd=2,col="black");
 text(x=-100, y=3.0, label="B", cex=2, pos=4);
@@ -413,8 +413,8 @@ points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 points(x=xxx,y=mWP,type="l",lwd=2,col="blue");
[…]

### 2016-09-06 ms_pre_post.Rmd
Add second to last paragraph of introductionand associated references

@@
 For example, how often a focal female mates is a reproductive decision that can directly and indirectly affect her fitness, and potentially alter the distribution of genotypes and patterns of inheritence within a population [e.g., @Cornell2007; @Diaz2010; @Okada2015; @Roberts2015a; @Worthington2016].
-Her mating frequency and expression of mate choice might be affected by the genetic quality or complementarity of available potential mates, and her choosiness might additionally be expressed through post-copulatory mechanisms [@Parker1983; @Parker2006; @Kuijper2012].
+Her mating frequency and expression of mate choice might be affected by the genetic quality or complementarity of available potential mates, and her choosiness might additionally be expressed after mating has taken place through post-copulatory mechanisms [@Parker1983; @Parker2006; @Kuijper2012].
 Female choice might therefore be realised by evolution of multiple, potentially interdependent, behavioural and physiological phenotypes operating in tandem.
@@
 If inbreeding depression is sufficiently weak, selection for female inbreeding preference is predicted because inbreeding increases the reproductive success of a focal female's male relative, thereby increasing the number of identical-by-descent copies present in her offspring [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
-However, if inbreeding depression is moderate to strong, selection for female inbreeding avoidance is predicted [@Duthie].
+However, if inbreeding depression is moderate to strong, selection for female inbreeding avoidance is predicted [@Duthie; Duthie and Reid *in press*].
 Female inbreeding strategy can be enacted before or after copulation occurs [e.g., @Tuni2013; @Firman2015; @Daniel2015; @Fischer2015].
@@
 <!--- TODO: PARAGRAGH ON EVOLUTION OF POLYANDRY --->
-Critically, evolution of post-copulatory inbreeding avoidance is precluded if females only mate with one male, meaning that evolution of polyandry is intrinsically tied to female inbreeding fertilisation strategy.
+Critically, evolution of post-copulatory inbreeding strategy is precluded if females only mate with one male, meaning that evolution of polyandry is intrinsically tied to female inbreeding fertilisation strategy.
 Although polyandry is commonplace in wild populations, the regularity with which it is observed in the wild remains theoretically puzzling because engaging in polyandry does not necessarily increase the number of offspring that a female produces, meaning that the fitness benefits associated with polyandry are not always clear [@Parker2013; @Taylor2014].
@@
 Risk of not mating due to choosiness: Kokko2013
+
+<!--- TODO: PARAGRAGH ON ORDER OF INTERACTIONS --->
+Selection for inbreeding mating strategy versus inbreeding fertilisation strategy and associated polyandry might depend evolutionary constraints, or on existing phentypes in the population.
+For example, if phenotypes biasing fertilisation to avoid inbreeding are precluded by evolutionary constraints [@Bradshaw1991; @Futuyma2010], then inbreeding avoidance might only be possible before copulation occurs, perhaps strengthening selection for inbreeding mating strategy and weakening selection for polyandry.
+Alternatively, evolution of female inbreeding mating strategy might be precluded due to severely limited kin recognition or the inability to resist male coercion given sexual conflict [Arnqvist2005a; Parker2006; @Penn2010].
+In such conditions, females might only be able to express choice through inbreeding fertilisation strategy, perhaps strengthening selection for inbreeding avoidance through polyandry and post-copulatory mechanisms.
+Selection for inbreeding mating or fertilisation strategy might also be weak or negligible if the strategy is redundant due to the presence of an already established adaptive inbreeding strategy (e.g., if females already successfully avoid inbreeding during mate encounters, then they might be unable to increase their fitness further by biasing fertilisation after mating has occurred).
+It is therefore necessary to consider evolution of inbreeding mating strategy and inbreeding fertilisation strategy when each evolves in a population where its complementary inbreeding strategy is evolutionarily constrained or already fixed as an adaptation.
 
@@
 In the case of tendency to engage in polyandry, the cost of $P_{p}$ ($c_{P}$) is interpreted biologically as a cost associated with mate searching or courtship [e.g., @Rowe1988; @Rowe1994; @Ronkainen1994; @Koga1998; @Lasley-Rasher2012].
-For inbreeding mating strategy, the cost of $M_{p}$ ($c_{M}$) is interpreted biologically as a cost associated with risk of mating failure due to females being overly choosy [e.g., @Kokko2013], and for inbreeding fertilisation strategy, the cost of $F_{p}$ ($c_{F}$) is interpreted as an energetic cost associated with the physiological or biochemical mechanisms that need to be developed to bias fertilsation for inbreeding avoidance or inbreeding preference [e.g., @Gasparini2011].
+For inbreeding mating strategy, the cost of $M_{p}$ ($c_{M}$) is interpreted biologically as a cost associated with risk of mating failure due to females being overly choosy [e.g., @Kokko2013], and for inbreeding fertilisation strategy, the cost of $F_{p}$ ($c_{F}$) is interpreted as an energetic cost associated with the physiological or biochemical mechanisms that need to be developed to bias fertilisation for inbreeding avoidance or inbreeding preference [e.g., @Gasparini2011].
 Each cost independently increases the risk of female pre-mating mortality and, because generations are non-overlapping, total reproductive failure as a linear function of its associated trait.
@@
 To test our hypothesis that selection for evolution of polyandry is driven by female's ability to bias fertilisation toward inbreeding avoidance through post-copulatory mechanisms, we compare simulations in which all three phenotypes including tendency for polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilisation strategy ($F_{p}$) evolve, with an identical set of simulations in which $F_{p}$ cannot evolve.
-In simulations without evolving $F_{p}$, we therefore include all 16 combinations of $c_{P}=\{0,0.02\}$, $c_{M}=\{0,0.02\}$, $c_{F}=\{0,0.02\}$, and $\beta = 3$ replicated 40 times each.
+In simulations without evolving $F_{p}$, we therefore include all 8 combinations of $c_{P}=\{0,0.02\}$, $c_{M}=\{0,0.02\}$, $c_{F}=\{0,0.02\}$, and $\beta = 3$ replicated 40 times each.
 To stop $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes resulting from $F_{a}$ cause random fertilisation with respect to kinship.

### 2016-09-06 ms_pre_post.Rmd
Finish Introduction draft

@@
 If inbreeding depression is sufficiently weak, selection for female inbreeding preference is predicted because inbreeding increases the reproductive success of a focal female's male relative, thereby increasing the number of identical-by-descent copies present in her offspring [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
-However, if inbreeding depression is moderate to strong, selection for female inbreeding avoidance is predicted [@Duthie; Duthie and Reid *in press*].
+However, if inbreeding depression is moderate to strong, selection for female inbreeding avoidance is predicted [Duthie and Reid *in press*; @Duthie].
 Female inbreeding strategy can be enacted before or after copulation occurs [e.g., @Tuni2013; @Firman2015; @Daniel2015; @Fischer2015].
@@
 Evolution of polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy will ultimately be determined by the, potentially interacting, fitness benefits and costs of each phenotype.
-Given severe inbreeding depression, phenotypes will increase a focal female's fitness by causing her to avoid breeding with close relatives.
+Given severe inbreeding depression, phenotypes will increase a focal female's fitness if they cause her to avoid breeding with close relatives.
 However, evolution of phenotypes will also be directly affected by negative selection (i.e., costs) associated with the tendency to engage in polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
+For example, females with a tendency to engage in polyandry might pay a cost associated with searching or making themselves available to mates, thereby increasing their own risk of predation [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
+Females that are particularly choosy in mating interactions (e.g., especially reluctant to mate with relatives) might pay a cost of increased risk of mating failure, or harm caused by sexual conflict [@Rowe1994; @Kokko2013].
+Females that are choosy after mating has occurred might pay an energetic cost associated with physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
+Overall, to predict evolution of polyandry and inbreeding strategies, it is therefore necessary to model costs associated with polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
 
@@
 <!--- TODO: PARAGRAGH ON ORDER OF INTERACTIONS --->
-Selection for inbreeding mating strategy versus inbreeding fertilisation strategy and associated polyandry might depend evolutionary constraints, or on existing phentypes in the population.
+Selection for inbreeding mating strategy versus inbreeding fertilisation strategy and associated polyandry might also depend evolutionary constraints, or on existing phentypes in the population.
 For example, if phenotypes biasing fertilisation to avoid inbreeding are precluded by evolutionary constraints [@Bradshaw1991; @Futuyma2010], then inbreeding avoidance might only be possible before copulation occurs, perhaps strengthening selection for inbreeding mating strategy and weakening selection for polyandry.
-Alternatively, evolution of female inbreeding mating strategy might be precluded due to severely limited kin recognition or the inability to resist male coercion given sexual conflict [Arnqvist2005a; Parker2006; @Penn2010].
+Alternatively, evolution of female inbreeding mating strategy might be precluded due to severely limited kin recognition or the inability to resist male coercion given sexual conflict [@Arnqvist2005a; @Parker2006; @Penn2010].
 In such conditions, females might only be able to express choice through inbreeding fertilisation strategy, perhaps strengthening selection for inbreeding avoidance through polyandry and post-copulatory mechanisms.

### 2016-09-06 ms_pre_post.Rmd
Revise Model analysis to add new 'hypotheses'

@@
 
-<!--- TODO: PARAGRAGH ON EVOLUTION OF POLYANDRY --->
+<!--- TODO: PARAGRAGH ON EVOLUTION OF POLYANDRY (H1) --->
 Critically, evolution of post-copulatory inbreeding strategy is precluded if females only mate with one male, meaning that evolution of polyandry is intrinsically tied to female inbreeding fertilisation strategy.
@@
 <!--- TODO: PARAGRAGH ON ORDER OF INTERACTIONS --->
-Selection for inbreeding mating strategy versus inbreeding fertilisation strategy and associated polyandry might also depend evolutionary constraints, or on existing phentypes in the population.
+Selection for inbreeding mating strategy versus inbreeding fertilisation strategy and associated polyandry might also depend evolutionary constraints, or on existing phenotypes in the population.
 For example, if phenotypes biasing fertilisation to avoid inbreeding are precluded by evolutionary constraints [@Bradshaw1991; @Futuyma2010], then inbreeding avoidance might only be possible before copulation occurs, perhaps strengthening selection for inbreeding mating strategy and weakening selection for polyandry.
@@
 Here we apply a model of female and male reproductive interactions and associated inbreeding depression in offspring viability to quantify evolution of three separate traits including female tendency for polyandry, female pre-copulatory inbreeding strategy (mating strategy), and female post-copulatory inbreeding strategy (fertilisation strategy).
-We use individual-based modelling and *in silico* experiments to test the hypotheses that, given inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance causes selection for evolution of polyandry, and that pre-copulatory but not post-copulatory inbreeding avoidance will evolve when pre-copulatory inbreeding avoidance is less costly than the combined cost of post-copulatory inbreeding avoidance and polyandry, while post-copulatory but not pre-copulatory inbreeding avoidance will evolve when pre-copulatory inbreeding avoidance is more costly than the combined costs of post-copulatory inbreeding avoidance and polyandry.
+We use individual-based modelling and *in silico* experiments to test the hypotheses that, given inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance causes selection for evolution of polyandry.
+Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that that pre-copulatory but not post-copulatory inbreeding avoidance will evolve when pre-copulatory inbreeding avoidance is less costly than the combined cost of post-copulatory inbreeding avoidance and polyandry, while post-copulatory but not pre-copulatory inbreeding avoidance will evolve when pre-copulatory inbreeding avoidance is more costly than the combined costs of post-copulatory inbreeding avoidance and polyandry.
+Finally, we test the hypothesis that constraints on evolution of one inbreeding strategy (e.g., inbreeding mating strategy) will increase the strength of selection on evolution of a complementary inbreeding strategy (e.g., inbreeding fertilisation strategy), and that evolution of one inbreeding strategy will be precluded if it is introduced into a population that is already fixed for a complementary inbreeding strategy that is adaptive.
 We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across reproductive systems with different relative costs and different magnitudes of inbreeding depression in offspring viability.
@@
 To analyse our model, we track mean values of alleles underlying tendency for polyandry ($P_{a}$), inbreeding mating strategy ($M_{a}$), and inbreeding fertilisation strategy ($F_{a}$) in a focal population.
-We present evolutionary dynamics of these mean allele values across different combinations of inbreeding depression slopes and costs to test our two focal hypotheses.
+We present evolutionary dynamics of these mean allele values across different combinations of inbreeding depression slopes and costs to test our four focal hypotheses (see below).
 The combinations of costs and inbreeding depression slopes that we consider include all eight possible permutations of values of costs of tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$) equal to either $0$ or $0.02$ [@Duthie observed $0.02$ to be strong cost of tendency for polyandry], and for values of $\beta = 3$ ($8$ total combinations).
 In all of these simulations, we record mean values of $P_{a}$, $M_{a}$, $F_{a}$ in each generation.
-Each of the 16 possible cost combinations is replicated $40$ times, and grand mean values and standard deviation of means is calculated in each generation across replicate simulations.
+Each of the $8$ possible cost combinations is replicated $40$ times, and grand mean values and standard deviation of means is calculated in each generation across replicate simulations.
 These analyses allowed us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on inbreeding fertilisation strategy might be weak if polyandry is rare).
@@
 To test hypotheses regarding evolution under different relative costs of phenotypes, we consider all combinations of costs and inbreeding depression parameter values using only simulations in which all three traits evolve.
-To test our hypothesis that inbreeding mating strategy will evolve toward inbreeding avoidance ($M_{p}<0$) when mating costs are low relative to the costs of tendency for polyandry and inbreeding fertilisation strategy, but that selection for inbreeding fertilisation strategy will then be negligible ($F_{p} \approx 0$), we quantify evolution of $M_{p}$ and $F_{p}$ over generations in simulations where $c_{M}=0$ but $c_{P}$, $c_{F}$, or both equals $0.02$.
+To test our hypothesis that inbreeding mating strategy will evolve toward inbreeding avoidance ($M_{p}<0$) when mating costs are low relative to the costs of tendency for polyandry and inbreeding fertilisation strategy, but that selection for inbreeding fertilisation strategy will then be negligible ($F_{p} \approx 0$), we quantify evolution of $M_{p}$ and $F_{p}$ over generations in simulations where $c_{M}=0$ but $c_{P}$, $c_{F}$, or both equals $0.02$ and $\beta=3$.
 We compare evolution in these three cost parameter value combinations with simulations in which all costs equal either $0$ or $0.02$.
 If our hypothesis is supported, then $M_{p}$ but not $F_{p}$ will evolve to more negative values when $c_{M}$ is relatively low than when all cost values are uniform.
+To test the hypothesis that inbreeding fertilisation strategy will evolve toward inbreeding avoidance ($F_{p}<0$) given low costs of polyandry and inbreeding fertilisation strategy relative to the cost of inbreeding mating strategy, but that selection on inbreeding mating strategy will be negligible ($M_{p} \approx 0$), we qualtify evolution of $M_{p}$ and $F_{p}$ over generations when $c_{F}=0$, $c_{P}=0$, and $c_{M}=0.02$ and $\beta=3$.
+We compare evolution for this combination of cost parameter values with simulations in which all costs equal either $0$ or $0.02$.
+If our hypothesis is supported, then $F_{p}$ but not $M_{p}$ will evolve to more negative values when $c_{F}$ is relatively low than when all cost values are uniform.
 
-To test the complementary hypothesis that inbreeding fertilisation strategy will evolve toward inbreeding avoidance ($F_{p}<0$) given low costs of polyandry and inbreeding fertilisation strategy relative to the cost of inbreeding mating strategy, but that selection on inbreeding mating strategy will be negligible ($M_{p} \approx 0$), we qualtify evolution of $M_{p}$ and $F_{p}$ over generations when $c_{F}=0$, $c_{P}=0$, and $c_{M}=0.02$.
-We compare evolution for this combination of cost parameter values with simulations in which all costs equal either $0$ or $0.02$.
-If our hypothesis is supported, then $F_{p}$ but not $M_{p}$ will evolve to more negative values when $c_{F}$ is relative low than when all cost values are uniform.
+To test the hypothesis that constraints on evolution of one inbreeding strategy will increase the strength of selection on a complementary strategy, we fixed inbreeding strategy phenotypes to values of zero, thereby causing either random mating ($M_{p}=0$) or the random fertilisation of offspring ($F_{p}=0$) according to a fair raffle among mates with respect to kinship.
+We then compare evolution of the non-fixed trait to its evolution in simulations where all traits are allowed to evolve.
+In all simulations testing this hypothesis, we used strong inbreeding depression ($\beta=3$) and included $40$ replicates for each set of parameter values.
+
+To test the hypothesis that the existence of an adaptive inbreeding strategy will decrease the strength of selection on, and thereby preclude the invasion of, a complementary strategy, we first used exploratory simulations to determine evolution of inbreeding mating strategy, and inbreeding fertilisation strategy and associated polyandry, in isolation.
+To test whether or not inbreeding mating avoidance was predicted to evolve when adaptive polyandry to avoid inbreeding was already established, we initiated inbreeding mating strategy allele values at zero ($M_{a}=0$), but fixed inbreeding fertilisation strategy allele values at $F_{a}=-5$ and polyandry allele values at $P_{a}=1$.
+Similarly, to test whether or not inbreeding fertilisation strategy evolved to avoid inbreeding, we initiated inbreeding fertilisation strategy allele values and polyandry allele values at zero ($F_{a}=0$; $P_{a}=0$), but fixed inbreeding mating strategy allele values at $M_{a}=-5$.
+For all simulations testing this hypothesis, we used strong inbreeding depression ($\beta=3$) and included $40$ replicates for each set of parameter values
 

### 2016-09-07 initial_analysis.R
Add two panel figure showing evolving mate choice with fixed post-copulatory inbreeding avoidance

@@ -617,6 +617,81 @@ mtext(expression(paste("Mean allele value")),
 dev.off();
 #==========================================================================
 
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+
+
+rm(list=ls()); 
+
+setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
+gens      <- 9999;
+
+# ------------------------------------------------------------------------#
+beta_val <- 3;
+setEPS(); # postscript below for final publication?
+cairo_ps("figures/evo_combs02_B3_ko_FP-5.eps",family="Arial",height=6,width=4);
+par(mfrow=c(2,1),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
+# ------------------------------------------------------------------------#
+evo_cc_02 <- read.table(file="p_f_ko_5/evo_PF_ko_5.txt", header=FALSE);
+evB <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0,];
+evo <- evB[evB[,2]==beta_val,];
+mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
+sWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=sd);
+xxx <- tapply(X=evo[,6],INDEX=evo[,6],FUN=mean);
+len <- dim(evo)[1];
+plot(x=xxx,y=mWP,type="l",lwd=2,ylim=c(-9,4),col="blue",xaxt="n",
+     xlab="",ylab="Allele value",cex.lab=2,cex.axis=1.5,yaxt="n");
+axis(side=2,at=c(-8,-4,0,4), cex.axis=1.5);
+uWP <- mWP + sWP / sqrt(sum(evo[,6]==gens));
+lWP <- mWP - sWP / sqrt(sum(evo[,6]==gens));
+polygon(y=c(lWP,rev(uWP)),x=c(1:(gens+1),(gens+1):1),border=NA,col="lightblue");
[…]

### 2016-09-07 ms_pre_post.Rmd
Minor revisions to the Introduction

@@
 Reproductive decisions expressed among interacting individuals directly affect individual fitnesses and the genotypes and viabilities of resulting offspring, and thereby profoundly affect evolutionary dynamics through the differential inheritence of alleles over generations [@Pizzari2012; @Wright2013; @Wild2014; @Liao2015; @Reid2016].
-For example, how often a focal female mates is a reproductive decision that can directly and indirectly affect her fitness, and potentially alter the distribution of genotypes and patterns of inheritence within a population [e.g., @Cornell2007; @Diaz2010; @Okada2015; @Roberts2015a; @Worthington2016].
+For example, how frequently a focal female mates is a reproductive decision that can directly and indirectly affect her fitness, and potentially alter the distribution of genotypes and patterns of inheritence within a population [e.g., @Cornell2007; @Diaz2010; @Okada2015; @Roberts2015a; @Worthington2016].
 Her mating frequency and expression of mate choice might be affected by the genetic quality or complementarity of available potential mates, and her choosiness might additionally be expressed after mating has taken place through post-copulatory mechanisms [@Parker1983; @Parker2006; @Kuijper2012].
 Female choice might therefore be realised by evolution of multiple, potentially interdependent, behavioural and physiological phenotypes operating in tandem.
-However, no general modelling framework predicts the conditions under which polyandry, pre-copulatory choice, and post-copulatory choice evolve together, meaning that there are no formal hypotheses for predicting the relevance of these reproductive decisions across different biological systems.
+However, no general modelling framework predicts the conditions under which female mating frequency, pre-copulatory choice, and post-copulatory choice evolve together, meaning that there are no formal hypotheses for predicting the relevance of these reproductive decisions across different biological systems.
 
@@
 Viability of inbred offspring typically decreases with increasing relatedness between parents [termed 'inbreeding depression'; @Keller2002; @Charlesworth2009].
-If inbreeding depression is sufficiently weak, selection for female inbreeding preference is predicted because inbreeding increases the reproductive success of a focal female's male relative, thereby increasing the number of identical-by-descent copies present in her offspring [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
+If inbreeding depression is sufficiently weak, selection for female inbreeding preference is predicted because inbreeding increases the reproductive success of a focal female's male relative, thereby increasing the number of identical-by-descent allele copies present in her offspring [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
 However, if inbreeding depression is moderate to strong, selection for female inbreeding avoidance is predicted [Duthie and Reid *in press*; @Duthie].
@@
 <!--- TODO: PARAGRAGH ON EVOLUTION OF POLYANDRY (H1) --->
-Critically, evolution of post-copulatory inbreeding strategy is precluded if females only mate with one male, meaning that evolution of polyandry is intrinsically tied to female inbreeding fertilisation strategy.
+Critically, evolution of inbreeding fertilisation strategy is precluded if females only mate with one male, meaning that evolution of polyandry (defined as female multiple mating within a single reproductive bout) is intrinsically tied to female inbreeding fertilisation strategy.
 Although polyandry is commonplace in wild populations, the regularity with which it is observed in the wild remains theoretically puzzling because engaging in polyandry does not necessarily increase the number of offspring that a female produces, meaning that the fitness benefits associated with polyandry are not always clear [@Parker2013; @Taylor2014].
 It has been hypothesised that females can acheive a net fitness benefit if polyandry provides them with additional opportunities to adjust their inbreeding through copulations with additional males [e.g., @Tregenza2002; @Akcay2007; @Lehtonen2015].
-@Duthie showed that selection for polyandry to facilitate inbreeding avoidance is sometimes predicted, but only under highly constrained conditions in which very few males are available during a female's initial mate choice but many males are available during a female's additional mate choice(s), or when expression of polyandry is conditionally expressed based on the degree of inbreeding in a female's initially chosen mate.
+@Duthie showed that selection for polyandry to facilitate inbreeding avoidance is sometimes predicted, but only under highly constrained conditions in which very few males are available during a female's initial mate choice but many males are available during a female's additional mate choice(s), or when polyandry is conditionally expressed based on the degree to which a focal female engaged in inbreeding given her initially chosen mate.
 However, @Duthie assumed that polyandrous females had no control over the assignment of paternity to their offspring.
@@
 <!--- TODO: PARAGRAGH ON IDEA OF PRE VS POST COPULATORY INBREEDING STRATEGY --->
-Evolution of inbreeding fertilisation stratey might increase selection for polyandry, but evolutionary feedbacks between inbreeding fertilisation strategy and polyandry might also be contingent upon evolution of inbreeding mating strategy, thereby leading to complex evolutionary dynamics between inbreeding strategies and polyandry.
+Evolution of inbreeding fertilisation strategy might increase selection for polyandry, but evolutionary feedbacks between inbreeding fertilisation strategy and polyandry might also be contingent upon evolution of inbreeding mating strategy, thereby leading to complex evolutionary dynamics between inbreeding strategies and polyandry.
 For example, if females can acheive their desired degree of inbreeding through mate choice alone, then subsequent polyandry and inbreeding fertilisation strategy might be superfluous for increasing female fitness.
@@
 Evolution of polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy will ultimately be determined by the, potentially interacting, fitness benefits and costs of each phenotype.
-Given severe inbreeding depression, phenotypes will increase a focal female's fitness if they cause her to avoid breeding with close relatives.
+Given severe inbreeding depression, phenotypes will increase a focal female's fitness if they cause her to avoid breeding with close relatives [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
 However, evolution of phenotypes will also be directly affected by negative selection (i.e., costs) associated with the tendency to engage in polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
@@
 <!--- TODO: OVERVIEW OF THE POINT OF THE MODELLING --->
-Here we apply a model of female and male reproductive interactions and associated inbreeding depression in offspring viability to quantify evolution of three separate traits including female tendency for polyandry, female pre-copulatory inbreeding strategy (mating strategy), and female post-copulatory inbreeding strategy (fertilisation strategy).
-We use individual-based modelling and *in silico* experiments to test the hypotheses that, given inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance causes selection for evolution of polyandry.
-Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that that pre-copulatory but not post-copulatory inbreeding avoidance will evolve when pre-copulatory inbreeding avoidance is less costly than the combined cost of post-copulatory inbreeding avoidance and polyandry, while post-copulatory but not pre-copulatory inbreeding avoidance will evolve when pre-copulatory inbreeding avoidance is more costly than the combined costs of post-copulatory inbreeding avoidance and polyandry.
+Here we apply a model of female and male reproductive interactions and associated inbreeding depression in offspring viability to quantify evolution of three separate phenotypes including female tendency for polyandry, female pre-copulatory inbreeding strategy (mating strategy), and female post-copulatory inbreeding strategy (fertilisation strategy).
+We use individual-based modelling and *in silico* experiments to test the hypothesis that, given severe inbreeding depression in offspring viability, evolution of inbreeding avoidance through fertilisation bias causes selection for evolution of polyandry.
+Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that that inbreeding avoidance through mate choice but not fertilisation bias will evolve when inbreeding mating strategy is less costly than the combined cost of inbreeding fertilisation strategy and tendency for polyandry polyandry, while inbreeding avoidance through fertilisation bias but not mate choice will evolve when inbreeding mating strategy is more costly than the combined costs of inbreeding fertilisation strategy and tendency for polyandry.
 Finally, we test the hypothesis that constraints on evolution of one inbreeding strategy (e.g., inbreeding mating strategy) will increase the strength of selection on evolution of a complementary inbreeding strategy (e.g., inbreeding fertilisation strategy), and that evolution of one inbreeding strategy will be precluded if it is introduced into a population that is already fixed for a complementary inbreeding strategy that is adaptive.

### 2016-09-07 ms_pre_post.Rmd
Revise Model section to fix errors and incorporate new changes to the model analysis structure

@@
 output:
-  pdf_document:
-    fig_caption: yes
-  html_document: default
   word_document:
@@
     - evolution.csl
+  pdf_document:
+    fig_caption: yes
+  html_document: default
 header-includes:
@@
 We track interactions among discrete individuals in a small focal population that persists over multiple generations.
-Individuals within this population are either female or male, and are potentially related if they share a common ancestory.
+Individuals within this population are either female or male, and can be related to each other if they share a common ancestor.
 We record the coefficient of kinship ($k$), defined as the probability that a randomly selected homologous allele from each individual is identical-by-descent [@Lynch1998], between all pairs of individuals in each generation using the population pedigree [see @Boyce1983; @Duthie].
-At the start of each generation, each female pays up to three independent costs of (1) tendency to engage in polyandry ($c_{P}$), (2) mating strategy with respect to inbreeding ($c_{M}$), and (3) fertilisation strategy ($c_{F}$) with respect to inbreeding.
-The number of males that a focal female mates with ($N_{males}$) is determined by the effects of 20 alleles ($P_{a}$) across 10 diploid loci that combine additively to determine a her genotype ($P_{g}$), and ultimately the phenotype for her tendency to engage in polandry ($P_{p}$).
-A focal female's choice of mate(s) is affected by 20 alleles ($M_{a}$) across 10 diploid loci that combine additively to affect her genotype ($M_{g}$) and phenotype ($M_{p}$) for pre-copulatory inbreeding avoidance or preference, and $k$ between the focal female and her potential mates.
-Similarly, after mating has occurred, post-copulatory fertilisation of a focal female's $n$ total offspring is affected by 20 alleles ($F_{a}$) across 10 diploid loci that combine additively to affect the genotype ($F_{g}$) and phenotype ($F_{p}$) of the degree to which fertilisation success is affected by $k$.
-After fertilisation, the vialbility of a focal female's $n$ offspring is decreased by inbreeding depression ($\beta$); surviving offspring become adults.
+At the start of each generation, each female pays up to three independent costs of (1) tendency to engage in polyandry ($c_{P}$), (2) mating strategy with respect to inbreeding ($c_{M}$), and (3) fertilisation strategy with respect to inbreeding ($c_{F}$).
+The number of males that a focal female mates with ($N_{males}$) is determined by the effects of 20 alleles ($P_{a}$) across 10 diploid loci that combine additively to determine her genotype ($P_{g}$), and ultimately her phenotype for tendency to engage in polandry ($P_{p}$).
+A focal female's choice of mate(s) is affected by 20 alleles ($M_{a}$) across 10 diploid loci that combine additively to affect her genotype ($M_{g}$) and phenotype ($M_{p}$) for pre-copulatory inbreeding avoidance or preference, and kinship between the focal female and her potential mates.
+Similarly, after mating has occurred, post-copulatory fertilisation of a focal female's $n$ total offspring is affected by 20 alleles ($F_{a}$) across 10 diploid loci that combine additively to affect the genotype ($F_{g}$) and phenotype ($F_{p}$) of the degree to which fertilisation success is affected by kinship.
+After fertilisation, the viability of a focal female's $n$ offspring is decreased by inbreeding depression ($\beta$), and surviving offspring become adults.
 After inbreeding depression in offspring, $\rho$ adult male immigrants arrive in the population, then density effects reduce the entire population down to female ($K_{f}$) and male ($K_{m}$) carrying capacity.
-Over generations, we record mean values of alleles underlying polyandry, mating strategy, and fertilisation strategy.
+Over generations, we record mean values of alleles underlying polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
 
@@
 <!--- Change mating cost to an increased risk of mating failure ---> 
-Values of phenotypic traits for tendency to engage in polyandry ($P_{p}$), mating ($M_{p}$), and fertilistation ($F_{p}$) each have costs, which independently increase the probability of a focal female's reproductive failure.
+Values of phenotypic traits for tendency to engage in polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilistation strategy ($F_{p}$) each have costs, which independently increase the probability of a focal female's reproductive failure.
 These costs are all expressed prior to mating.
@@
 The probability that a focal female dies before mating due to the cost of polyandry is therefore $P_{p} \times c_{P}$.
-Similarly, the probability of pre-mating female mortality due to the cost of mating strategy and fertilisation strategy is $|M_{p}| \times c_{M}$ and $|F_{p}| \times c_{F}$, repectively, where $|M_{p}|$ is the absolute value of $M_{p}$ and $|F_{p}|$ is the absolute value of $F_{p}$.
+Similarly, the probability of pre-mating female mortality due to the cost of inbreeding mating strategy and inbreeding fertilisation strategy is $|M_{p}| \times c_{M}$ and $|F_{p}| \times c_{F}$, repectively, where $|M_{p}|$ is the absolute value of $M_{p}$ and $|F_{p}|$ is the absolute value of $F_{p}$.
 Absolute values are used for applying costs to inbreeding strategies because both negative and positive $M_{p}$ and $F_{p}$ bias breeding interactions with respect to kinship, while only positive values of $P_{p}$ affect a female's tendency for polyandry; zero and negative $P_{p}$ values always translate to monandrous phenotypes (see below).
@@
 Each female chooses a number of males to mate with ($N_{males}$) based on her genetically determined tendency to engage in polyandry ($P_{p}$).
-The exact value of $N_{males}$ is calculated by sampling from a random poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
+The exact value of $N_{males}$ is calculated by randomly sampling from a poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
 This random sampling procedure causes some stochastic variation in the number of realised mates a that female chooses, with a mean $N_{males}$ of $P_{p}+1$.
-A one is added to $P_{p}$ to ensure that all females choose at least one mate, as low values of $P_{p}$ might return $Poisson(P_{p})$ values of zero.
+A value of one is added to $P_{p}$ to ensure that all females choose at least one mate, as low values of $P_{p}$ might return $Poisson(P_{p})$ values of zero.
 
@@
 In the unlikely event that a female's $N_{males}$ exceeds the total number of males in the population, then she mates with all of the males in the populaton.
-Most often, $N_{males}$ will be a small subset of the available males in the population [@Duthie], so a focal female will be able to preferentially mate with males that are close kin (high $k$), distant kin (low $k$), or non-kin ($k=0$) through the expression of her mating phenotype ($M_{p}$).
-Like polyandry allele values, mating strategy allele values ($M_{a}$) can take any real number.
-However, unlike polyandry, the sum of all of a female's 20 $M_{a}$ alleles equals both her mating strategy genotype ($M_{g}$) and her mating strategy phenotype ($M_{p}$).
+Most often, $N_{males}$ will be a small subset of the available males in the population [@Duthie], so a focal female will be able to preferentially mate with males that are close kin (high $k$), distant kin (low $k$), or non-kin ($k=0$) through the expression of her inbreeding mating strategy phenotype ($M_{p}$).
+Like polyandry allele values, inbreeding mating strategy allele values ($M_{a}$) can take any real number.
+However, unlike polyandry, the sum of all of a female's 20 $M_{a}$ alleles equals both her inbreeding mating strategy genotype ($M_{g}$) and her inbreeding mating strategy phenotype ($M_{p}$).
 Negative or positive values of $M_{p}$ cause a female to avoid or prefer mating with kin, respectively.
@@
 This quality depends upon whether the female has a strategy of avoiding mating with kin ($M_{p}<0$) or preferring mating with kin ($M_{p}>0$; if $M_{p}=0$, all males are assigned a quality of 1, $Q^{m}_{ij}=1$).
-If a focal female avoids mating with kin, then $Q^{m}_{ij} = (-M_{p} \times k_{ij} + 1)^{-1}$, meaning that the perceived quality of a male decreases lineary with increasingly positive values of $k_{ij}$ and increasingly negative values of $M_{p}$.
+If a focal female avoids mating with kin, then $Q^{m}_{ij} = (-M_{p} \times k_{ij} + 1)^{-1}$, meaning that the perceived quality of a male decreases linearly with increasingly positive values of $k_{ij}$ and increasingly negative values of $M_{p}$.
 If a focal female prefers mating with kin, then $Q^{m}_{ij} = M_{p} \times k_{ij} + 1$, meaning that the perceived quality of a male increases with increasingly positive values of $k_{ij}$ and $M_{p}$.
@@
 These $q^{f}_{ij}$ values define the probability that the offspring of a focal female $i$ is fertilised by the male $j$.
-Females produce $n$ offspring, meaning that $q^{f}_{ij}$ values are sampled $n$ times for each female to determine the realised distribution of sires.
+Females produce $n$ offspring, meaning that $q^{f}_{ij}$ values are sampled $n$ times independently and with replacement for each female to determine the realised distribution of sires.
 
@@
 
-Alleles of a focal female's offspring mutate with a probability of $\mu=0.001$, with mutation being an independent event across loci.
+Alleles of a focal female's offspring mutate with a probability of $\mu=0.001$, with mutation being an independent event the does or does not occur for each locus.
 In general, loss of function mutations might be expected to be more frequent than mutations that increase the functionality of adaptations that rely on complex physiologies or behaviours.
@@
 
-Hence, when a mutation occurs at a loci, a new value is sampled from a random normal distribution with a mean of zero, $\mathcal{N}(0, \mu_{SD})$.
+Hence, when a mutation occurs at a locus, a new value is sampled from a random normal distribution with a mean of zero and a standard devation of mutation effect size $\mu_{SD}$, $\mathcal{N}(0, \mu_{SD})$.
 This new value is then added to the original value of the allele that mutates [@Kimura1965; @Lande1976; @Bocedi2014; @Duthie].
@@
 The slope $\beta$ models the number of haploid lethal equivalents that exist in the gametes of $i$ and $j$, and which might combine to become homozygous in offspring and reduce viability.
-Equation 1 assumes that each deleterious recessive allele affects offspring viability independently, meaning that every deleterious recessive allele added will have a multiplicative affect on decreasing viability [@Morton1956; @Mills1994], causing the log-linear relationship between parent kinship and inbreeding depression.
+Equation 1 assumes that each deleterious recessive allele affects offspring viability independently, meaning that every deleterious recessive allele added will have a multiplicative affect on decreasing total viability [@Morton1956; @Mills1994], causing the log-linear relationship between parent kinship and inbreeding depression.
 We assume that inbreeding depression always decreases offspring viability, $\beta \geq 0$ (i.e., no outbreeding depression).
 Therefore, because $k_{ij}$ is constrained to values between zero and one, the product of $-\beta$ and $k_{ij}$ must be a value less than or equal to zero, $-\beta \times k_{ij} \leq 0$.
-Values of $\Psi_{\textrm{off}}$ must therefore be between zero and one.
+Values of $\Psi_{\textrm{off}}$ must therefore be between zero (if $-\beta \times k_{ij}$ is very negative) and one (if $-\beta \times k_{ij} = 0$).
 We can therefore define $\Psi_{\textrm{off}}$ as the probability that an offspring is viable, and sample its realised viability using a Bernoulli trial.
@@
 
-To avoid indefinite population growth over generations, we introduce a separate carrying capacity on the total number of females ($K_{f}$) and males ($K_{m}$) in the focal population following immigration [@Guillaume2009; @Duthie].
+To avoid having unrestricted population growth over generations, we introduce a separate carrying capacity on the total number of females ($K_{f}$) and males ($K_{m}$) in the focal population following immigration [@Guillaume2009; @Duthie].
 If at the end of a generation the number of females or males exceeds their respective carrying capacities, then each sex is reduced back to its $K_{f}$ or $K_{m}$ by randomly removing females and males until each sex is at its carrying capacity.
@@
 To analyse our model, we track mean values of alleles underlying tendency for polyandry ($P_{a}$), inbreeding mating strategy ($M_{a}$), and inbreeding fertilisation strategy ($F_{a}$) in a focal population.
-We present evolutionary dynamics of these mean allele values across different combinations of inbreeding depression slopes and costs to test our four focal hypotheses (see below).
-The combinations of costs and inbreeding depression slopes that we consider include all eight possible permutations of values of costs of tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$) equal to either $0$ or $0.02$ [@Duthie observed $0.02$ to be strong cost of tendency for polyandry], and for values of $\beta = 3$ ($8$ total combinations).
-In all of these simulations, we record mean values of $P_{a}$, $M_{a}$, $F_{a}$ in each generation.
-Each of the $8$ possible cost combinations is replicated $40$ times, and grand mean values and standard deviation of means is calculated in each generation across replicate simulations.
+We present evolutionary dynamics of these mean allele values across different parameter combinations test our four focal hypotheses (see below).
+We simulate up to eight possible permutations of values of costs of tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$) equal to either $0$ or $0.02$ [@Duthie observed $0.02$ to be a strong cost of tendency for polyandry] for values of $\beta = 3$ ($8$ total combinations).
+In all simulations, we record mean values of $P_{a}$, $M_{a}$, $F_{a}$ in each generation.
+Each of combination of parameter values simulated is replicated $40$ times, and grand mean values and standard deviation of means is calculated in each generation across replicate simulations.
 These analyses allowed us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on inbreeding fertilisation strategy might be weak if polyandry is rare).
+For all replicates, we set the maximum number of generations to 10000, which exploratory simulations and previous modelling [@Duthie] showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
+For all replicates, we also set the number of immigrants per generation to $\rho=5$, which produced a range of kin and non-kin in each generation such that females could express inbreeding strategies.
+Females always produced $n=8$ offspring, which was sufficient to keep populations consistently near carrying capacities and avoid population extinction.
+Carrying capacities for females ($K_{f}$) and males ($K_{m}$) were both set to 100 because previous modelling has shown that populations of this size are small enough that mating encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but populations are also not so small that selection is typically overwhelmed by genetic drift (Duthie and Reid *in press*).
 
 To test our hypothesis that selection for evolution of polyandry is driven by female's ability to bias fertilisation toward inbreeding avoidance through post-copulatory mechanisms, we compare simulations in which all three phenotypes including tendency for polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilisation strategy ($F_{p}$) evolve, with an identical set of simulations in which $F_{p}$ cannot evolve.
-In simulations without evolving $F_{p}$, we therefore include all 8 combinations of $c_{P}=\{0,0.02\}$, $c_{M}=\{0,0.02\}$, $c_{F}=\{0,0.02\}$, and $\beta = 3$ replicated 40 times each.
-To stop $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes resulting from $F_{a}$ cause random fertilisation with respect to kinship.
+In simulations without evolving $F_{p}$, we therefore include all $4$ combinations of $c_{P}=\{0,0.02\}$ and $c_{M}=\{0,0.02\}$.
+To stop $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes resulting from $F_{a}$ cause random fertilisation with respect to kinship (i.e, $F_{p}=0$).
 Hence, while mutation and drift can still occur for $F_{a}$ alleles, these alleles have no phenotypic effect and polyandry cannot cause polyandrous females to benefit through an increased ability to bias fertilisation toward inbreeding avoidance (under such conditions, there can also never be a cost of $F_{p}$, meaning that $c_{F}=0$).
@@
 
-To test hypotheses regarding evolution under different relative costs of phenotypes, we consider all combinations of costs and inbreeding depression parameter values using only simulations in which all three traits evolve.
-To test our hypothesis that inbreeding mating strategy will evolve toward inbreeding avoidance ($M_{p}<0$) when mating costs are low relative to the costs of tendency for polyandry and inbreeding fertilisation strategy, but that selection for inbreeding fertilisation strategy will then be negligible ($F_{p} \approx 0$), we quantify evolution of $M_{p}$ and $F_{p}$ over generations in simulations where $c_{M}=0$ but $c_{P}$, $c_{F}$, or both equals $0.02$ and $\beta=3$.
+To test hypotheses regarding evolution under different relative costs of phenotypes, we consider all combinations of costs using simulations in which all three traits evolve and $\beta=3$.
+To test our hypothesis that inbreeding mating strategy will evolve toward inbreeding avoidance ($M_{p}<0$) when mating costs are low relative to the costs of tendency for polyandry and inbreeding fertilisation strategy, but that selection for inbreeding fertilisation strategy will then be negligible ($F_{p} \approx 0$), we quantify evolution of $M_{p}$ and $F_{p}$ over generations in simulations where $c_{M}=0$ but $c_{P}$, $c_{F}$, or both equals $0.02$.
 We compare evolution in these three cost parameter value combinations with simulations in which all costs equal either $0$ or $0.02$.
 If our hypothesis is supported, then $M_{p}$ but not $F_{p}$ will evolve to more negative values when $c_{M}$ is relatively low than when all cost values are uniform.
-To test the hypothesis that inbreeding fertilisation strategy will evolve toward inbreeding avoidance ($F_{p}<0$) given low costs of polyandry and inbreeding fertilisation strategy relative to the cost of inbreeding mating strategy, but that selection on inbreeding mating strategy will be negligible ($M_{p} \approx 0$), we qualtify evolution of $M_{p}$ and $F_{p}$ over generations when $c_{F}=0$, $c_{P}=0$, and $c_{M}=0.02$ and $\beta=3$.
+To test the hypothesis that inbreeding fertilisation strategy will evolve toward inbreeding avoidance ($F_{p}<0$) given low costs of polyandry and inbreeding fertilisation strategy relative to the cost of inbreeding mating strategy, but that selection on inbreeding mating strategy will be negligible ($M_{p} \approx 0$), we quantify evolution of $M_{p}$ and $F_{p}$ over generations when $c_{F}=0$, $c_{P}=0$, and $c_{M}=0.02$ .
 We compare evolution for this combination of cost parameter values with simulations in which all costs equal either $0$ or $0.02$.
@@
 We then compare evolution of the non-fixed trait to its evolution in simulations where all traits are allowed to evolve.
-In all simulations testing this hypothesis, we used strong inbreeding depression ($\beta=3$) and included $40$ replicates for each set of parameter values.
 
 To test the hypothesis that the existence of an adaptive inbreeding strategy will decrease the strength of selection on, and thereby preclude the invasion of, a complementary strategy, we first used exploratory simulations to determine evolution of inbreeding mating strategy, and inbreeding fertilisation strategy and associated polyandry, in isolation.
-To test whether or not inbreeding mating avoidance was predicted to evolve when adaptive polyandry to avoid inbreeding was already established, we initiated inbreeding mating strategy allele values at zero ($M_{a}=0$), but fixed inbreeding fertilisation strategy allele values at $F_{a}=-5$ and polyandry allele values at $P_{a}=1$.
+To test whether or not inbreeding mating avoidance was predicted to evolve when adaptive polyandry to avoid inbreeding was already established, we initiated inbreeding mating strategy allele values at zero ($M_{a}=0$), but fixed inbreeding fertilisation strategy allele values at $F_{a}=-5$ and polyandry allele values at $P_{a}=1$ (i.e., $F_{p}$ and $P_{p}$ did not evolve).
 Similarly, to test whether or not inbreeding fertilisation strategy evolved to avoid inbreeding, we initiated inbreeding fertilisation strategy allele values and polyandry allele values at zero ($F_{a}=0$; $P_{a}=0$), but fixed inbreeding mating strategy allele values at $M_{a}=-5$.
-For all simulations testing this hypothesis, we used strong inbreeding depression ($\beta=3$) and included $40$ replicates for each set of parameter values
-
-For all replicates, we set the maximum number of generations to 10000, which exploratory simulations and previous modelling [@Duthie] showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
-For all replicates, we set the number of immigrants per generation to $\rho=5$, which produced a range of kin and non-kin in each generation such that females could express inbreeding strategies.
-Females always produced $n=8$ offspring, which was sufficient to keep populations consistently near carrying capacities and avoid population extinction.
-Carrying capacities for females ($K_{f}$) and males ($K_{m}$) were both set to 100 because previous modelling has shown that populations of this size are small enough that mating encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but populations are also not so small that selection is typically overwhelmed by genetic drift (Duthie and Reid *in press*).
 
@@
 ===================================================
+
+Selection for polyandry is driven by inbreeding fertilisation strategy
+----------------------------------------------
+
+Figure 1 will show a spread of all the results (evo combs02 B3.eps), and be contrasted with the four panel Figure 2 showing results when $F_{p}$ is knocked out (evo combs02 B3 ko F.eps).
+
+Selection given relative costs of polyandry and inbreeding strategies
+----------------------------------------------
+
+Figure 1 will further address hypotheses comparing across different costs.
+
+Selection given constraints on evolution
+----------------------------------------------
+
+Figure 3 will show constraints on $M_{p}$ affecting $F_{p}$, while Figure 2 will be used again to show constraints on $F_{p}$ affecting $M_{p}$.
+
+Selection given a pre-existing adaptive inbreeding strategy
+----------------------------------------------
+
+Figure 4 will show evolution of $M_{p}$ given pre-existing post-copulatory inbreeding avoidance, and Figure 5 will show evolution of $P_{p}$ and $F_{p}$ given pre-existing pre-copulatory inbreeding avoidance.
+
+<!--- Get in there that the replicate simulations don't show evidence of alternative states -- one thing happens or does not, though there is some correlation among traits in replicates --->
 

### 2016-09-07 ms_pre_post.Rmd
Add start of table

@@
 output:
+  pdf_document:
+    fig_caption: yes
+  html_document: default
   word_document:
@@
     - evolution.csl
-  pdf_document:
-    fig_caption: yes
-  html_document: default
 header-includes:
@@
 
+Table 1
+----------------------------------------------
+
+|-----|---------------------------------------|-------------|---------------|--------------
+| **A** | **Trait**                           | **Allele**  | **Genotype**  | **Phenotype**
+|       | Tendency for polyandry              | $P_{a}$     | $P_{g}$       | $P_{p}$
+|       | Inbreeding mating strategy          | $M_{a}$     | $M_{g}$       | $M_{p}$
+|       | Inbreeding fertilisation strategy   | $F_{a}$     | $F_{g}$       | $F_{p}$
+|       |                                     |             |               |
+| **B** | **Description**                     | **Parameter**  | | **Defaut value(s)**
+
 References

### 2016-09-08 initial_analysis.R
Add figure in which mating strategy is fixed at random

@@ -682,11 +682,158 @@ dev.off();
 #==========================================================================
 
 
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 
 
-
-
-
+beta_val <- 3;
+setEPS(); # postscript below for final publication?
+cairo_ps("figures/evo_combs02_B3_ko_M-0.eps",family="Arial",height=6,width=5.5);
+par(mfrow=c(2,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
+evo_cc_02 <- read.table(file="m_ko_0/evo_M_ko_0.txt", header=FALSE);
+# ------------------------------------------------------------------------#
+evB <- evo_cc_02[evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
+evo <- evB[evB[,2]==beta_val,];
+mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
+mPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=mean);
+mEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=mean);
+sWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=sd);
+sPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=sd);
+sEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=sd);
+xxx <- tapply(X=evo[,6],INDEX=evo[,6],FUN=mean);
+len <- dim(evo)[1];
+plot(x=xxx,y=mPO,type="l",lwd=2,ylim=c(-9,4),col="red",xaxt="n",
+     xlab="",ylab="Allele value",cex.lab=2,cex.axis=1.5,yaxt="n");
+axis(side=2,at=c(-8,-4,0,4), cex.axis=1.5);
+#points(x=xxx,y=mPO,type="l",lwd=2,col="red");
+points(x=xxx,y=mEP,type="l",lwd=2,col="black");
+abline(h=0,lwd=0.8,lty="dotted");
[…]

### 2016-09-08 ms_pre_post.Rmd
Add Figure positions into the manuscript

@@
 
-We track interactions among discrete individuals in a small focal population that persists over multiple generations.
+We track interactions among discrete individuals in a small focal population that persists over multiple generations (Key individual traits, parameter values, and variables are described in Table 1).
 Individuals within this population are either female or male, and can be related to each other if they share a common ancestor.
@@
 | **B** | **Description**                     | **Parameter**  | | **Defaut value(s)**
+|       | Cost of tendency for polyandry                 | $c_{P}$        | | $0$, $0.02$
+|       | Cost of inbreeding mating strategy             | $c_{M}$        | | $0$, $0.02$
+|       | Cost of inbreeding fertilisation strategy      | $c_{F}$        | | $0$, $0.02$
+|       | Focal female's number of offspring             | $n$            | | $8$
+|       | Log-linear slope of inbreeding depression      | $\beta$        | | $3$
+|       | Adult male immigrants per generation           | $\rho$         | | $5$
+|       | Female carrying capacity                       | $K_{f}$        | | $100$
+|       | Male carrying capacity                         | $K_{m}$        | | $100$
+|       | Mutation rate of alleles                       | $\mu$          | | $0.001$
+|       | Standard deviation of mutation effect size     | $\mu_{SD}$     | | $\sqrt{1/20}$
+|       |                                                |                | |
+| **C** | **Description**                                                   | | | **Variable**
+|       | Coefficient of kinship                                            | | | $k$
+|       | Focal female's number of mates                                    | | | $N_{males}$
+|       | Female $i$'s perceived absolute mate quality of male $j$          | | | $Q^{m}_{ij}$
+|       | Female $i$'s perceived relative mate quality of male $j$          | | | $q^{m}_{ij}$
+|       | Female $i$'s perceived absolute fertilisation quality of male $j$ | | | $Q^{f}_{ij}$
+|       | Female $i$'s perceived relative fertilisation quality of male $j$ | | | $q^{f}_{ij}$
+|       | Viability of a focal female's offspring                           | | | $\Psi_{off}$
+
+![Full caption to go here](Initial_Results/figures/evo_combs02_B3.png)
+
+![Full caption to go here](Initial_Results/figures/evo_combs02_B3_ko_F.png)
 

### 2016-09-08 ms_pre_post.Rmd
Add one section of the results

--- 2016-09-07 ms_pre_post.Rmd
@@
 
-Figure 1 will show a spread of all the results (evo combs02 B3.eps), and be contrasted with the four panel Figure 2 showing results when $F_{p}$ is knocked out (evo combs02 B3 ko F.eps).
+<!--- Figure 1 will show a spread of all the results (evo combs02 B3.eps), and be contrasted with the four panel Figure 2 showing results when $F_{p}$ is knocked out (evo combs02 B3 ko F.eps). --->
+
+We first test our hypothesis that females' ability to bias fertilisation with respect to kinship causes selection for polyandry by comparing simulations in which tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy can all evolve to simulations in which inbreeding fertilisation strategy is fixed to random mating with respect to kinship, as present in Figures 1 and 2, respectively.
+Figure 1 shows changes in mean allele values of tendency for polyandry ($P_{a}$; red lines and shading), inbreeding mating strategy ($M_{a}$; blue lines and shading), and inbreeding fertilisation strategy ($F_{a}$; black lines and shading) over 10000 generations as calculated across all individuals within a focal population over 40 replicate simulations with identical starting conditions.
+Solid lines represent the grand mean of replicate mean allele values, and shading around lines shows standard deviations around the mean.
+Panels A-H show all possible cost combinations for tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$).
+Figure 2 shows an equivalent figure with changes in allele values of tendency for polyandry (red lines and shading) and inbreeding mating strategy (blue lines and shading) only.
+However, in Figure 2, a horizontal black line where mean allele value of inbreeding fertilisation strategy equals zero shows that these allele values have been fixed.
+Figure 2 has only four panels because costs of inbreeding fertilisation strategy is irrelevant when inbreeding fertilisation strategy alleles have no effect and mating is random (i.e., $F_{p}=0$).
+
+Comparison of Figures 1 and 2 shows that evolution of inbreeding fertilisation strategy facilitates evolution of polyandry, particularly when costs of tendency for polyandry and inbreeding fertilisation strategy are zero.
+For example, in Figure 2A, tendency for polyandry allele values consistently become negative over generations ($P_{a}<0$; decreasing red line), causing populations to be monandrous.
+Females in these populations avoid mating with kin ($M_{a}<0$; decreasing blue line), and because these females sample mates with replacement, males that remain after their initial mate choice are more likely to be relatives, causing selection for monandry because females are most likely to succeed in avoiding inbreeding in their initial mate choice [see also @Duthie].
+However, Figure 1A shows that when a focal female can also bias the probability that a particular mate sires her offspring, inbreeding fertilisation strategy evolves to inbreeding avoidance ($F_{a}<0$; decreasing black line).
+Consequently, the ability to bias fertilisation to avoid inbreeding causes polyandry to become adaptive, and positive values of tendency for polyandry alleles increase in frequency ($P_{a}>0$; increasing red line of Figure 1A).
+Although non-zero costs decrease net selection for both tendency for polyandry and inbreeding fertilisation strategy (see below), across all combinations of costs, tendency for polyandry allele values are more positive when inbreeding fertilisation strategy can also evolve.
+Evolution of post-copulatory inbreeding avoidance therefore greatly facilitates evolution of polyandry.
 
@@
 
-Figure 1 will further address hypotheses comparing across different costs.
+Figure 1 shows changes in mean allele values of tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy across all eight possible combinations of costs.
+We can therefore use Figure 1 to test the hypothesis that inbreeding mating strategy will evolve to inbreeding avoidance ($M_{a}<0$) when mating costs are low ($c_{M}=0$) relative to the costs of tendency for polyandry and inbreeding fertilisation strategy by comparing different cost combinations to the null model in which all costs equal zero (Figure 1A).
+In Figure 1A, when no phenotypes are costly, inbreeding mating strategy and inbreeding fertilisation strategy evolve to inbreeding avoidance ($M_{a}<0$ and $F_{a}<0$), and females evolve to be polyandrous ($P_{a}>0$).
 
@@
 | **B** | **Description**                     | **Parameter**  | | **Defaut value(s)**
+|       | Cost of tendency for polyandry                 | $c_{P}$        | | $0$, $0.02$
+|       | Cost of inbreeding mating strategy             | $c_{M}$        | | $0$, $0.02$
+|       | Cost of inbreeding fertilisation strategy      | $c_{F}$        | | $0$, $0.02$
+|       | Focal female's number of offspring             | $n$            | | $8$
+|       | Log-linear slope of inbreeding depression      | $\beta$        | | $3$
+|       | Adult male immigrants per generation           | $\rho$         | | $5$
+|       | Female carrying capacity                       | $K_{f}$        | | $100$
+|       | Male carrying capacity                         | $K_{m}$        | | $100$
+|       | Mutation rate of alleles                       | $\mu$          | | $0.001$
+|       | Standard deviation of mutation effect size     | $\mu_{SD}$     | | $\sqrt{1/20}$
+|       |                                                |                | |
+| **C** | **Description**                                                   | | **Variable** |
+|       | Coefficient of kinship                                            | | $k$          |
+|       | Focal female's number of mates                                    | | $N_{males}$  |
+|       | Female $i$'s perceived absolute mate quality of male $j$          | | $Q^{m}_{ij}$ |
+|       | Female $i$'s perceived relative mate quality of male $j$          | | $q^{m}_{ij}$ |
+|       | Female $i$'s perceived absolute fertilisation quality of male $j$ | | $Q^{f}_{ij}$ |
+|       | Female $i$'s perceived relative fertilisation quality of male $j$ | | $q^{f}_{ij}$ |
+|       | Viability of a focal female's offspring                           | | $\Psi_{off}$ |
+
+\vspace{100 mm}
+
+![Full caption to go here](Initial_Results/figures/evo_combs02_B3.png)
+
+![Full caption to go here](Initial_Results/figures/evo_combs02_B3_ko_F.png)
+
+![Full caption to go here](Initial_Results/figures/evo_combs02_B3_ko_M-0.png)
+
+![Full caption to go here](Initial_Results/figures/evo_combs02_B3_ko_M-5.png)
+
+![Full caption to go here](Initial_Results/figures/evo_combs02_B3_ko_FP-5.png)
 

### 2016-09-08 ms_pre_post.Rmd
Add second section of the results

@@
 Figure 1 shows changes in mean allele values of tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy across all eight possible combinations of costs.
-We can therefore use Figure 1 to test the hypothesis that inbreeding mating strategy will evolve to inbreeding avoidance ($M_{a}<0$) when mating costs are low ($c_{M}=0$) relative to the costs of tendency for polyandry and inbreeding fertilisation strategy by comparing different cost combinations to the null model in which all costs equal zero (Figure 1A).
 In Figure 1A, when no phenotypes are costly, inbreeding mating strategy and inbreeding fertilisation strategy evolve to inbreeding avoidance ($M_{a}<0$ and $F_{a}<0$), and females evolve to be polyandrous ($P_{a}>0$).
+Costs of phenotypes have a direct effect on evolution, causing inbreeding mating strategy and inbreeding fertilisation strategy phenotypes to evolve to values closer to zero (because realisation of inbreeding strategy costs increases with phenotype absolute values) and tendency for polyandry phenotypes to evolve to values that are more negative (because realisation of polyandry costs increases with positive phenotype values).
+
+We can use Figure 1 to test the hypothesis that inbreeding mating strategy will evolve to inbreeding avoidance ($M_{a}<0$), but inbreeding fertilisation strategy will be negligible ($F_{a} \approx 0$) when mating costs are low ($c_{M}=0$) relative to the costs of tendency for polyandry and inbreeding fertilisation strategy ($c_{P}=0.02$ or $c_{F}=0.02$) by comparing different cost combinations to the null model in which all costs equal zero (Figure 1A).
+Figures 1A,C,D,G show that inbreeding avoidance evolves at a comparable rate whenever $c_{M}=0$.
+However, inbreeding fertilisation strategy is never negligible; $F_{a}$ values are still negative over generations even when costs of inbreeding mating strategy is weak and costs of tendency for polyandry and inbreeding fertilisation strategy are strong.
+
+We can also use Figure 1 to test the hypothesis that inbreeding fertilisation strategy will evolve to inbreeding avoidance ($F_{a}<0$), but inbreeding mating strategy will be negligible ($M_{a} \approx 0$) when tendency for polyandry and inbreeding fertilisation strategy costs are low ($c_{P}=0$ and $c_{F}=0$) relative to the cost of inbreeding mating strategy ($c_{M}=0.02$).
+Figure 1B shows that inbreeding avoidance through fertilisation bias evolves ($F_{a}<0$) under these conditions, but evolution of inbreeding mating strategy is not negligible; $M_{a}$ values are consistently negative across all combinations of costs.
+
+<!--- Interestingly, a high cost of only tendency for polyandry (Figure 1C) or only inbreeding fertilisation strategy (Figure 1D) shows how these phenotypes are evolutionarily tied such that a cost of one phenotype can feed back to affect evolution of the other phenotype.
+For example, Figure 1C shows simulations in which inbreeding fertilisation strategy is not costly, causing $F_{a}$ values to become more negative (stronger inbreeding avoidance) than when both inbreeding fertilisation strategy and tendency for polyandry are costly (Figure 1G).
+However, $F_{a}$ values are not as negative as they would be if neither tendency for polyandry or inbreeding fertilisations trategy were costly (Figure 1A) because expression of fertilisation bias was hindered by costs of polyandry and an associated reduction in evolved mating frequency.
+Similarly, Figure 1D shows simulations in which only inbreeding fertilisation strategy was costly, causing less strong inbreeding avoidance through fertilisation bias.
+Consequently, tendency for polyandry values were lower than when inbreeding fertilisation strategy was not costly (Figure 1A) because polyandry was less beneficial when it did not result in strong inbreeding avoidance through fertilisation bias.
+--->
 

### 2016-09-09 ms_pre_post.Rmd
Add third section of the Results

@@
 
-Figure 3 will show constraints on $M_{p}$ affecting $F_{p}$, while Figure 2 will be used again to show constraints on $F_{p}$ affecting $M_{p}$.
+Figure 3 shows evolution of tendency for polyandry and inbreeding fertilisation strategy when inbreeding mating strategy is fixed so that females must mate randomly (blue line at $M_{a}=0$).
+For all cost combinations of tendency for polyandry and inbreeding fertilisation strategy (Figure 3 panels A-D), we observed selection for positive values of tendency for polyandry alleles and negative values of inbreeding fertilisation strategy alleles, which we interpret as strong evidence for evolution of polyandry and associated inbreeding avoidance through fertiisation bias.
+This pattern of evolution contrasts with that observed when inbreeding mating strategy was not fixed, indicating that constraints on evolution of inbreeding mating strategy increased the strength for evolution of polyandry and inbreeding avoidance through fertilisation bias.
+For example, in Figures 1C,D,G,H, tendency for polyandry allele values are typically less than zero, reflecting evolution of monandry, and inbreeding fertilisation strategy allele values were not as negative as they were in simulations with fixed random mating (Figure 3).
+In general, when females were unable to avoid mating with relatives given severe inbreeding depression ($\beta=3$), selection for evolution of polyandry and post-copulatory inbreeding avoidance was strengthened.
+
+Figure 2, which we previously contrasted with Figure 1 to test whether or not evolution of inbreeding fertilisation strategy faciitates selection for polyandry, shows evolution of tendency for polyandry and inbreeding mating strategy when inbreeding fertilisation strategy is fixed such that the sire of a focal female's offspring is randomly assigned from her mates according to a fair raffle.
+In all cost combinations of Figure 2 (panels A-D), tendency for polyandry allele values decreased over generations, reflecting evolution of monandry.
+However, values of inbreeding mating strategy alleles did not greatly differ over generations when inbreeding fertilisation strategy was fixed, meaning that the effect of fixed inbreeding fertilisation strategy on increasing selection for inbreeding avoidance through mate choice was weak or nelgigible.
+A weak effect is discernable in the contrast between Figure 2B and Figure 1B, in which the grand mean inbreeding mating strategy allele value is $-0.627$ when inbreeding fertilisation strategy is not fixed (Figure 1B) versus $-1.036$ when it is fixed (Figure 2B) in generation 10000.
+Therefore, when females were unable to bias fertilisatin to avoid inbreeding given severe inbreeding depression ($\beta=3$), selection for evolution of pre-copulatory inbreeding avoidance was not greatly strengthened.
+
+<!--- Figure 3 will show constraints on $M_{p}$ affecting $F_{p}$, while Figure 2 will be used again to show constraints on $F_{p}$ affecting $M_{p}$. --->
 

### 2016-09-09 ms_pre_post.Rmd
Add last Results section, and switch to a new first paragraph of results explaining figures

@@
 
+We present our results by showing mean allele value changes over generations.
+All Figures 1-5 show changes in mean allele values of tendency for polyandry ($P_{a}$; red lines and shading), inbreeding mating strategy ($M_{a}$; blue lines and shading), and inbreeding fertilisation strategy ($F_{a}$; black lines and shading) over 10000 generations as calculated across all individuals within a focal population over 40 replicate simulations with identical starting conditions.
+Solid lines represent the grand mean of replicate mean allele values, and shading around lines shows standard deviations around the mean.
+Panels within figures show different cost combinations for tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$).
+Figures have fewer than eight panels if some costs are not relevant because allele values are fixed, and fixed allele values are shown as horizontal lines where line height is set to the value of alleles at fixation.
+Supporting Information S1 presents correlations of mean allele values across replicate simulations, which were generally weak; we found no evidence suggesting strong evolutionary divergence among replicates with identical starting conditions (e.g., as might be the case if populations stochastically evolved toward inbreeding avoidance through mate choice or fertilisation, but not both), meaning that inspecting grand means of replicate allele values accurately reflects expected evolutionary dynamics over generations.
+
+<!--- Figure 2 shows an equivalent figure with changes in allele values of tendency for polyandry (red lines and shading) and inbreeding mating strategy (blue lines and shading) only.
+However, in Figure 2, a horizontal black line where mean allele value of inbreeding fertilisation strategy equals zero shows that these allele values have been fixed.
+Figure 2 has only four panels because costs of inbreeding fertilisation strategy is irrelevant when inbreeding fertilisation strategy alleles have no effect and mating is random (i.e., $F_{p}=0$).
+--->
+
 Selection for polyandry is driven by inbreeding fertilisation strategy
@@
 We first test our hypothesis that females' ability to bias fertilisation with respect to kinship causes selection for polyandry by comparing simulations in which tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy can all evolve to simulations in which inbreeding fertilisation strategy is fixed to random mating with respect to kinship, as present in Figures 1 and 2, respectively.
-Figure 1 shows changes in mean allele values of tendency for polyandry ($P_{a}$; red lines and shading), inbreeding mating strategy ($M_{a}$; blue lines and shading), and inbreeding fertilisation strategy ($F_{a}$; black lines and shading) over 10000 generations as calculated across all individuals within a focal population over 40 replicate simulations with identical starting conditions.
-Solid lines represent the grand mean of replicate mean allele values, and shading around lines shows standard deviations around the mean.
-Panels A-H show all possible cost combinations for tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$).
-Figure 2 shows an equivalent figure with changes in allele values of tendency for polyandry (red lines and shading) and inbreeding mating strategy (blue lines and shading) only.
-However, in Figure 2, a horizontal black line where mean allele value of inbreeding fertilisation strategy equals zero shows that these allele values have been fixed.
-Figure 2 has only four panels because costs of inbreeding fertilisation strategy is irrelevant when inbreeding fertilisation strategy alleles have no effect and mating is random (i.e., $F_{p}=0$).
 
@@
 
-Figure 4 will show evolution of $M_{p}$ given pre-existing post-copulatory inbreeding avoidance, and Figure 5 will show evolution of $P_{p}$ and $F_{p}$ given pre-existing pre-copulatory inbreeding avoidance.
+Figure 4 shows change in inbreeding mating strategy allele values over generations when tendency for polyandry and inbreeding fertilisation strategy alleles were fixed for adaptive values of inbreeding avoidance $P_{a}=1$ and $F_{a}=-5$.
+Despite that females in these simulations could already avoid inbreeding after mating occurred, inbreeding mating strategy evolved towards inbreeding avoidance given costs of $c_{M}=0$ (Figure 4A) and $c_{M}=0.02$ (Figure 4B).
+We therefore did not find evidence that the existence of adaptive inbreeding avoidance through fertilisation bias in any way precluded the evolution of adaptive inbreeding avoidance through mate choice.
+
+Figure 5 shows change in tendency for polyandry and inbreeding fertilisation strategy allele values over generations when inbreeding mating strategy alleles were fixed for adaptive inbreeding avoidance $M_{a}=-5$.
+Existence of adaptive inbreeding avoidance through mate choice precluded evolution of polyandry for all combinations of costs (Figure 5), meaning that evolution of adpative polyandry to avoid inbreeding through inbreeding fertilisation strategy was never predicted in populations where females were already avoiding inbreeding through mate choice.
+Further, while inbreeding fertilisation strategy evolved toward inbreeding avoidance ($F_{a}<0$) in the absence of costs (Figure 5A,B), allele values of inbreeding fertilisation strategy were not as negative as when adaptive inbreeding avoidance through mate choice was not fixed at the outset (Figures 1A,B,C,D).
+We therefore found strong evidence that the existence of adaptive inbreeding avoidance through pre-copulatory mate choice precluded evolution of adaptive inbreeding avoidance through post-copulatory inbreeding avoidance through fertilisation bias.
+
+<!--- Figure 4 will show evolution of $M_{p}$ given pre-existing post-copulatory inbreeding avoidance, and Figure 5 will show evolution of $P_{p}$ and $F_{p}$ given pre-existing pre-copulatory inbreeding avoidance.
+--->
 
@@
 
-|-----|---------------------------------------|-------------|---------------|--------------
+|-------|-------------------------------------|-------------|---------------|--------------
 | **A** | **Trait**                           | **Allele**  | **Genotype**  | **Phenotype**
@@
 
+![Full caption to go here](Initial_Results/figures/evo_combs02_B3_ko_FP-5.png)
+
 ![Full caption to go here](Initial_Results/figures/evo_combs02_B3_ko_M-5.png)
-
-![Full caption to go here](Initial_Results/figures/evo_combs02_B3_ko_FP-5.png)
 

### 2016-09-09 ms_pre_post.Rmd
Add table and figure legends

@@
 We present our results by showing mean allele value changes over generations.
-All Figures 1-5 show changes in mean allele values of tendency for polyandry ($P_{a}$; red lines and shading), inbreeding mating strategy ($M_{a}$; blue lines and shading), and inbreeding fertilisation strategy ($F_{a}$; black lines and shading) over 10000 generations as calculated across all individuals within a focal population over 40 replicate simulations with identical starting conditions.
+Figures 1-5 show changes in mean allele values of tendency for polyandry ($P_{a}$; red lines and shading), inbreeding mating strategy ($M_{a}$; blue lines and shading), and inbreeding fertilisation strategy ($F_{a}$; black lines and shading) over 10000 generations as calculated across all individuals within a focal population over 40 replicate simulations with identical starting conditions.
 Solid lines represent the grand mean of replicate mean allele values, and shading around lines shows standard deviations around the mean.
@@
 We first test our hypothesis that females' ability to bias fertilisation with respect to kinship causes selection for polyandry by comparing simulations in which tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy can all evolve to simulations in which inbreeding fertilisation strategy is fixed to random mating with respect to kinship, as present in Figures 1 and 2, respectively.
-
 Comparison of Figures 1 and 2 shows that evolution of inbreeding fertilisation strategy facilitates evolution of polyandry, particularly when costs of tendency for polyandry and inbreeding fertilisation strategy are zero.
@@
 
+Individual traits (A), model parameter values (B), and model variables (C) for an individual based model of the evolution of polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
+
 |-------|-------------------------------------|-------------|---------------|--------------
@@
 
-![Full caption to go here](Initial_Results/figures/evo_combs02_B3.png)
+![Mean allele values underlying tendency for polyandry (red lines and shading), inbreeding mating strategy (i.e., pre-copulatory choice; blue lines and shading), and inbreeding fertilisation strategy (i.e., post-copulatory choice; black lines and shading), as calculated across all individuals within a population over 10000 generations given strong inbreeding depression.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard deviations of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Panels A-H show simulations for different combinations of costs for tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
+Dotted horizontal black lines in panels show values of zero on the y-axis.](Initial_Results/figures/evo_combs02_B3.png)
 
-![Full caption to go here](Initial_Results/figures/evo_combs02_B3_ko_F.png)
+![Mean allele values underlying tendency for polyandry (red lines and shading) and inbreeding mating strategy (i.e., pre-copulatory choice; blue lines and shading), as calculated across all individuals within a population over 10000 generations given strong inbreeding depression when allele values underlying inbreeding fertilisation strategy (i.e., post-copulatory choice) are fixed for random fertilisation among mates (black horizontal lines where y-axes equal zero).
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard deviations of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Panels A-D show simulations for different combinations of costs for tendency for polyandry and inbreeding mating strategy.](Initial_Results/figures/evo_combs02_B3_ko_F.png)
 
-![Full caption to go here](Initial_Results/figures/evo_combs02_B3_ko_M-0.png)
+![Mean allele values underlying tendency for polyandry (red lines and shading) and inbreeding fertilisation strategy (i.e., post-copulatory choice; black lines and shading), as calculated across all individuals within a population over 10000 generations given strong inbreeding depression when allele values underlying inbreeding mating strategy (i.e., pre-copulatory choice) are fixed for random mating (blue horizontal lines where y-axes equal zero).
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard deviations of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Panels A-D show simulations for different combinations of costs for tendency for polyandry and inbreeding mating strategy.](Initial_Results/figures/evo_combs02_B3_ko_M-0.png)
 
-![Full caption to go here](Initial_Results/figures/evo_combs02_B3_ko_FP-5.png)
+![Mean allele values underlying inbreeding mating strategy (i.e., pre-copulatory choice; blue lines and shading), as calculated across all individuals within a population over 10000 generations given strong inbreeding depression and the pre-existence of polyandry to avoid inbreeding (tendency for polyandry allele values equal 1, as indicated by horizontal red lines; inbreeding fertilisation strategy values equal -5, as indicated by horizontal black lines).
+Solid blue lines represent grand means over 40 replicate populations, and blue shading around solid lines shows standard deviations of mean inbreeding mating strategy allele values around grand means.
+Negative mean allele values reflect a strategy of inbreeding avoidance, and positive values reflect a strategy of inbreeding preference.
+Panels A and B show replicate simulations in which inbreeding mating strategy is not costly and has a cost of 0.02, respectively.
+Dotted horizontal black lines in panels show values of zero on the y-axis.](Initial_Results/figures/evo_combs02_B3_ko_FP-5.png)
 
-![Full caption to go here](Initial_Results/figures/evo_combs02_B3_ko_M-5.png)
+![Mean allele values underlying tendency for polyandry (red lines and shading) and inbreeding fertilisation strategy (i.e., post-copulatory choice; black lines and shading), as calculated across all individuals within a population over 10000 generations given strong inbreeding depression and the pre-existence of inbreeding avoidance in mate choice (inbreeding mating strategy values equal -5, as indicated by horizontal blue lines).
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard deviations of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Panels A-D show simulations for different combinations of costs for tendency for polyandry and inbreeding mating strategy.
+Dotted horizontal black lines in panels show values of zero on they-axis.
+](Initial_Results/figures/evo_combs02_B3_ko_M-5.png)
 

### 2016-09-09 ms_pre_post.Rmd
Minor edits up to Results

@@
 We use individual-based modelling and *in silico* experiments to test the hypothesis that, given severe inbreeding depression in offspring viability, evolution of inbreeding avoidance through fertilisation bias causes selection for evolution of polyandry.
-Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that that inbreeding avoidance through mate choice but not fertilisation bias will evolve when inbreeding mating strategy is less costly than the combined cost of inbreeding fertilisation strategy and tendency for polyandry polyandry, while inbreeding avoidance through fertilisation bias but not mate choice will evolve when inbreeding mating strategy is more costly than the combined costs of inbreeding fertilisation strategy and tendency for polyandry.
+Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that that inbreeding avoidance through mate choice but not fertilisation bias will evolve when inbreeding mating strategy is less costly than the combined cost of inbreeding fertilisation strategy and tendency for polyandry, while inbreeding avoidance through fertilisation bias but not mate choice will evolve when inbreeding mating strategy is more costly than the combined costs of inbreeding fertilisation strategy and tendency for polyandry.
 Finally, we test the hypothesis that constraints on evolution of one inbreeding strategy (e.g., inbreeding mating strategy) will increase the strength of selection on evolution of a complementary inbreeding strategy (e.g., inbreeding fertilisation strategy), and that evolution of one inbreeding strategy will be precluded if it is introduced into a population that is already fixed for a complementary inbreeding strategy that is adaptive.
-We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across reproductive systems with different relative costs and different magnitudes of inbreeding depression in offspring viability.
+We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across reproductive systems with different relative costs and strong inbreeding depression in offspring viability.
 
@@
 
-We track interactions among discrete individuals in a small focal population that persists over multiple generations (Key individual traits, parameter values, and variables are described in Table 1).
+We track interactions among discrete individuals in a small focal population that persists over multiple generations (key individual traits, parameter values, and variables are described in Table 1).
 Individuals within this population are either female or male, and can be related to each other if they share a common ancestor.
@@
 The resulting $P_{p}$ is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998], in which polyandry is expressed discretely at the threshold value of $P_{g} > 0$, but is determined by the consequence of continuous genetic variation arising from the effects of $P_{a}$ alleles that each contribute additively to a female's tendency toward polyandry.
-Negative genotypic values of $P_{g}$ therefore all have the same phenotype, resulting in consistently monandrous females.
+Negative genotype values of $P_{g}$ therefore all have the same phenotype, resulting in consistently monandrous females.
 In contrast, positive values of $P_{g}$ and therefore $P_{p}$ can lead to different degrees of realised polyandry in the form of discrete numbers of mates ($N_{males}$).
@@
 Negative or positive values of $M_{p}$ cause a female to avoid or prefer mating with kin, respectively.
-Values of $M_{p}=0$ causes females to mate randomly with respect to kinship.
+Values of $M_{p}=0$ cause females to mate randomly with respect to kinship.
 
@@
 If the focal population was instead closed ($\rho=0$), then all alleles would quickly be expected to become identical-by-descent among descendants of the ancestral population.
-To avoid having immigrants affect the evolution of tendency for polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilisation strategy ($F_{p}$), immigrants are always male and can therefore be chosen based on their kinship values of zero but not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$.
+To avoid having immigrants affect evolution of tendency for polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilisation strategy ($F_{p}$), immigrants are always male and can therefore be chosen based on their kinship values of zero but not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$.
 To further avoid having immigrants affect evolutionary dynamics, allele values underlying tendency for polyandry ($P_{a}$), inbreeding mating strategy ($M_{a}$), and inbreeding fertilisation strategy ($F_{a}$) are randomly sampled from normal distributions with means and standard deviations of $P_{a}$, $M_{a}$, and $F_{a}$ values equal to the means and standard deviations of those in the focal population at the time of immigration.
@@
 In all simulations, we record mean values of $P_{a}$, $M_{a}$, $F_{a}$ in each generation.
-Each of combination of parameter values simulated is replicated $40$ times, and grand mean values and standard deviation of means is calculated in each generation across replicate simulations.
+Each combination of parameter values simulated is replicated $40$ times, and grand mean values and standard deviation of means is calculated in each generation across replicate simulations.
 These analyses allowed us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on inbreeding fertilisation strategy might be weak if polyandry is rare).
@@
 Females always produced $n=8$ offspring, which was sufficient to keep populations consistently near carrying capacities and avoid population extinction.
-Carrying capacities for females ($K_{f}$) and males ($K_{m}$) were both set to 100 because previous modelling has shown that populations of this size are small enough that mating encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but populations are also not so small that selection is typically overwhelmed by genetic drift (Duthie and Reid *in press*).
+Carrying capacities for females ($K_{f}$) and males ($K_{m}$) were both set to 100 because previous modelling has shown that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but populations are also not so small that selection is typically overwhelmed by genetic drift (Duthie and Reid *in press*).
 
@@
 
-We first test our hypothesis that females' ability to bias fertilisation with respect to kinship causes selection for polyandry by comparing simulations in which tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy can all evolve to simulations in which inbreeding fertilisation strategy is fixed to random mating with respect to kinship, as present in Figures 1 and 2, respectively.
+We first test our hypothesis that females' ability to bias fertilisation with respect to kinship causes selection for polyandry by comparing simulations in which tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy can all evolve to simulations in which inbreeding fertilisation strategy is fixed to random mating with respect to kinship, as presented in Figures 1 and 2, respectively.
 Comparison of Figures 1 and 2 shows that evolution of inbreeding fertilisation strategy facilitates evolution of polyandry, particularly when costs of tendency for polyandry and inbreeding fertilisation strategy are zero.
@@
 
-\vspace{100 mm}
-
 ![Mean allele values underlying tendency for polyandry (red lines and shading), inbreeding mating strategy (i.e., pre-copulatory choice; blue lines and shading), and inbreeding fertilisation strategy (i.e., post-copulatory choice; black lines and shading), as calculated across all individuals within a population over 10000 generations given strong inbreeding depression.
@@
 
+\vspace{60 mm}
+
 References

### 2016-09-12 ms_pre_post.Rmd
Tweak Model section

@@
 After fertilisation, the viability of a focal female's $n$ offspring is decreased by inbreeding depression ($\beta$), and surviving offspring become adults.
-After inbreeding depression in offspring, $\rho$ adult male immigrants arrive in the population, then density effects reduce the entire population down to female ($K_{f}$) and male ($K_{m}$) carrying capacity.
-Over generations, we record mean values of alleles underlying polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
+After inbreeding depression in offspring viability, $\rho$ adult male immigrants arrive in the population, then density effects reduce the entire population down to separate female ($K_{f}$) and male ($K_{m}$) carrying capacities Over generations, we record mean values of alleles underlying polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
 
@@
 
-Each female chooses a number of males to mate with ($N_{males}$) based on her genetically determined tendency to engage in polyandry ($P_{p}$).
+After costs are paid, each remaining female chooses a number of males to mate with ($N_{males}$) based on her genetically determined tendency to engage in polyandry ($P_{p}$).
 The exact value of $N_{males}$ is calculated by randomly sampling from a poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
 This random sampling procedure causes some stochastic variation in the number of realised mates a that female chooses, with a mean $N_{males}$ of $P_{p}+1$.
-A value of one is added to $P_{p}$ to ensure that all females choose at least one mate, as low values of $P_{p}$ might return $Poisson(P_{p})$ values of zero.
+A value of one is added to $P_{p}$ to ensure that all females that have not paid a cost choose at least one mate, as low values of $P_{p}$ might return $Poisson(P_{p})$ values of zero.
 
-The value of $P_{p}$ is affected by the summed values of her 20 $P_{a}$ alleles.
+The value of $P_{p}$ is affected by the summed values of a focal female's 20 $P_{a}$ alleles.
 Inheritence of all alleles models a diploid genetic architecture in which 10 $P_{a}$ alleles are randomly sampled from each parent with no physical linkage.
 Values of $P_{a}$ can take any real number [continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014].
-The tendency for polyandry genotype $P_{g}$ is defined by the sum of all of a focal female's 20 $P_{a}$ values, which might be negative or positive.
+The tendency for polyandry genotype $P_{g}$ is therefore defined by the sum of all of a focal female's 20 $P_{a}$ values, which might be negative or positive.
 However, the tendency for polyandry phenotype $P_{p}$ is restricted to zero or positive values because the number of males that a female chooses to mate with cannot be negative.
@@
 
-Alleles of a focal female's offspring mutate with a probability of $\mu=0.001$, with mutation being an independent event the does or does not occur for each locus.
+Alleles of a focal female's offspring mutate with a probability of $\mu=0.001$, with mutation being an independent event that does or does not occur for each locus.
 In general, loss of function mutations might be expected to be more frequent than mutations that increase the functionality of adaptations that rely on complex physiologies or behaviours.
@@
 
-The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a function of the kinship coefficient between $i$ and the sire of her offspring $j$ ($k_{ij}$), and a log-linear slope of inbreeding depression $\beta$.
+The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a function of the coefficient of kinship between $i$ and the sire of her offspring $j$ ($k_{ij}$), and a log-linear slope of inbreeding depression $\beta$.
 We model selection as having an absolute effect on offspring viability (i.e., hard selection), rather than a relative effect on viability (i.e., soft selection), so that the effect of $\beta$ is consistent over generations and across different parameter combinations.
-Natural selection on tendency for polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilisation strategy ($F_{p}$) can therefore be compared with respect to log-linear inbreeding depression slopes across generations and parameter combinations.
+Natural selection on tendency for polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilisation strategy ($F_{p}$) can therefore be compared across generations and parameter combinations.
 If offspring viability was instead relative such that the least inbred offspring had a high viability regardless of the absolute value of $k_{ij}$, then the effect of kinship coefficients and inbreeding depression slopes on offspring viability would depend on the population-wide distribution of $k_{ij}$ between females and males, making model inference more difficult.
@@
 \end{equation}
-The slope $\beta$ models the number of haploid lethal equivalents that exist in the gametes of $i$ and $j$, and which might combine to become homozygous in offspring and reduce viability.
+The slope $\beta$ models the number of haploid lethal equivalents that exist as deleterious recessive alleles in the gametes of $i$ and $j$, and which might combine to become homozygous in offspring and reduce viability.
 Equation 1 assumes that each deleterious recessive allele affects offspring viability independently, meaning that every deleterious recessive allele added will have a multiplicative affect on decreasing total viability [@Morton1956; @Mills1994], causing the log-linear relationship between parent kinship and inbreeding depression.
-We assume that inbreeding depression always decreases offspring viability, $\beta \geq 0$ (i.e., no outbreeding depression).
+We assume that inbreeding depression always decreases offspring viability, $\beta > 0$ (i.e., no outbreeding depression).
 Therefore, because $k_{ij}$ is constrained to values between zero and one, the product of $-\beta$ and $k_{ij}$ must be a value less than or equal to zero, $-\beta \times k_{ij} \leq 0$.
@@
 To analyse our model, we track mean values of alleles underlying tendency for polyandry ($P_{a}$), inbreeding mating strategy ($M_{a}$), and inbreeding fertilisation strategy ($F_{a}$) in a focal population.
-We present evolutionary dynamics of these mean allele values across different parameter combinations test our four focal hypotheses (see below).
+We present evolutionary dynamics of these mean allele values across different parameter combinations to test our four focal hypotheses (see below).
 We simulate up to eight possible permutations of values of costs of tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$) equal to either $0$ or $0.02$ [@Duthie observed $0.02$ to be a strong cost of tendency for polyandry] for values of $\beta = 3$ ($8$ total combinations).
@@
 Each combination of parameter values simulated is replicated $40$ times, and grand mean values and standard deviation of means is calculated in each generation across replicate simulations.
-These analyses allowed us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on inbreeding fertilisation strategy might be weak if polyandry is rare).
+These analyses allow us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on inbreeding fertilisation strategy might be weak if polyandry is rare).
 For all replicates, we set the maximum number of generations to 10000, which exploratory simulations and previous modelling [@Duthie] showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
-For all replicates, we also set the number of immigrants per generation to $\rho=5$, which produced a range of kin and non-kin in each generation such that females could express inbreeding strategies.
+For all replicates, we also set the number of immigrants per generation to $\rho=5$, which produced a range of kin and non-kin in each generation allowing females could express inbreeding strategies.
 Females always produced $n=8$ offspring, which was sufficient to keep populations consistently near carrying capacities and avoid population extinction.
@@
 
-To test our hypothesis that selection for evolution of polyandry is driven by female's ability to bias fertilisation toward inbreeding avoidance through post-copulatory mechanisms, we compare simulations in which all three phenotypes including tendency for polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilisation strategy ($F_{p}$) evolve, with an identical set of simulations in which $F_{p}$ cannot evolve.
-In simulations without evolving $F_{p}$, we therefore include all $4$ combinations of $c_{P}=\{0,0.02\}$ and $c_{M}=\{0,0.02\}$.
+To test our hypothesis that selection for evolution of polyandry is driven by a female's ability to bias fertilisation toward inbreeding avoidance through post-copulatory mechanisms, we compare simulations in which all three phenotypes including tendency for polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilisation strategy ($F_{p}$) evolve, with an identical set of simulations in which $F_{p}$ cannot evolve.
+In simulations without evolving $F_{p}$, we therefore include all $4$ combinations of $c_{P}=\{0,0.02\}$ and $c_{M}=\{0,0.02\}$ (but not $c{F}$).
 To stop $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes resulting from $F_{a}$ cause random fertilisation with respect to kinship (i.e, $F_{p}=0$).
@@
 
-To test hypotheses regarding evolution under different relative costs of phenotypes, we consider all combinations of costs using simulations in which all three traits evolve and $\beta=3$.
-To test our hypothesis that inbreeding mating strategy will evolve toward inbreeding avoidance ($M_{p}<0$) when mating costs are low relative to the costs of tendency for polyandry and inbreeding fertilisation strategy, but that selection for inbreeding fertilisation strategy will then be negligible ($F_{p} \approx 0$), we quantify evolution of $M_{p}$ and $F_{p}$ over generations in simulations where $c_{M}=0$ but $c_{P}$, $c_{F}$, or both equals $0.02$.
+To test hypotheses regarding evolution under different relative costs of phenotypes, we consider all combinations of costs using simulations in which all three traits evolve.
+To test the hypothesis that inbreeding mating strategy will evolve toward inbreeding avoidance ($M_{p}<0$) when mating costs are low relative to the costs of tendency for polyandry and inbreeding fertilisation strategy, but that selection for inbreeding fertilisation strategy will then be negligible ($F_{p} \approx 0$), we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where $c_{M}=0$ but $c_{P}$, $c_{F}$, or both equals $0.02$.
 We compare evolution in these three cost parameter value combinations with simulations in which all costs equal either $0$ or $0.02$.
@@
 We compare evolution for this combination of cost parameter values with simulations in which all costs equal either $0$ or $0.02$.
-If our hypothesis is supported, then $F_{p}$ but not $M_{p}$ will evolve to more negative values when $c_{F}$ is relatively low than when all cost values are uniform.
+If our hypothesis is supported, then $F_{a}$ but not $M_{a}$ allele values will become more negative over generations when $c_{F}$ is relatively low than when all cost values are uniform.
 

### 2016-09-12 ms_pre_post.Rmd
Tweak Results section

@@
 This transformation results in each male having a relative perceived mate quality $q^{m}_{ij}$, which is constrained to values between zero and one.
-The value of $q^{m}_{ij}$ then defines the probability that a female chooses the male as a mate; female choice is therefore stochastic, meaning that females do not always choose the male of the highest $q^{m}_{ij}$.
+The value of $q^{m}_{ij}$ then defines the probability that a focal female chooses the male as a mate; female choice is therefore stochastic, meaning that females do not always choose the male of the highest $q^{m}_{ij}$ (e.g., given $M_{p}$ values of $-2$, $-4$, $-6$, and $-8$, an outbred focal female is $1.5$, $2$, $2.5$, and $3$ times more likely to mate with a non-relative than a full-sibling $k_{ij}=0.25$, respectively).
 For polyandrous females that choose more than one male mate, mates are chosen iteratively such that $Q^{m}_{ij}$ and $q^{m}_{ij}$ are re-calculated for each additional mate choice, and with $Q^{m}_{ij}$ and therefore $q^{m}_{ij}$ values of already chosen males set to zero to ensure mate sampling without replacement.
@@
 We present our results by showing mean allele value changes over generations.
-Figures 1-5 show changes in mean allele values of tendency for polyandry ($P_{a}$; red lines and shading), inbreeding mating strategy ($M_{a}$; blue lines and shading), and inbreeding fertilisation strategy ($F_{a}$; black lines and shading) over 10000 generations as calculated across all individuals within a focal population over 40 replicate simulations with identical starting conditions.
-Solid lines represent the grand mean of replicate mean allele values, and shading around lines shows standard deviations around the mean.
+Figures 1-5 show mean allele values of tendency for polyandry ($P_{a}$; red lines and shading), inbreeding mating strategy ($M_{a}$; blue lines and shading), and inbreeding fertilisation strategy ($F_{a}$; black lines and shading) over 10000 generations as calculated across all individuals (female and male) within a focal population over 40 replicate simulations with identical starting conditions.
+Solid lines represent the grand mean of replicate mean allele values, and shading around lines shows standard deviations of mean allele values around the grand mean.
 Panels within figures show different cost combinations for tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$).
-Figures have fewer than eight panels if some costs are not relevant because allele values are fixed, and fixed allele values are shown as horizontal lines where line height is set to the value of alleles at fixation.
+Figures have fewer than eight panels if some costs are not relevant because allele values are fixed, and fixed allele values are shown as horizontal lines where line height is set to the fixed allele value.
 Supporting Information S1 presents correlations of mean allele values across replicate simulations, which were generally weak; we found no evidence suggesting strong evolutionary divergence among replicates with identical starting conditions (e.g., as might be the case if populations stochastically evolved toward inbreeding avoidance through mate choice or fertilisation, but not both), meaning that inspecting grand means of replicate allele values accurately reflects expected evolutionary dynamics over generations.
@@
 
-We first test our hypothesis that females' ability to bias fertilisation with respect to kinship causes selection for polyandry by comparing simulations in which tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy can all evolve to simulations in which inbreeding fertilisation strategy is fixed to random mating with respect to kinship, as presented in Figures 1 and 2, respectively.
+We first test our hypothesis that a focal female's ability to bias fertilisation with respect to kinship causes selection for polyandry by comparing simulations in which tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy can all evolve to simulations in which inbreeding fertilisation strategy is fixed to random mating with respect to kinship, as presented in Figures 1 and 2, respectively.
 Comparison of Figures 1 and 2 shows that evolution of inbreeding fertilisation strategy facilitates evolution of polyandry, particularly when costs of tendency for polyandry and inbreeding fertilisation strategy are zero.
@@
 For all cost combinations of tendency for polyandry and inbreeding fertilisation strategy (Figure 3 panels A-D), we observed selection for positive values of tendency for polyandry alleles and negative values of inbreeding fertilisation strategy alleles, which we interpret as strong evidence for evolution of polyandry and associated inbreeding avoidance through fertiisation bias.
-This pattern of evolution contrasts with that observed when inbreeding mating strategy was not fixed, indicating that constraints on evolution of inbreeding mating strategy increased the strength for evolution of polyandry and inbreeding avoidance through fertilisation bias.
+This pattern of evolution contrasts with that observed when inbreeding mating strategy was not fixed, indicating that constraints on evolution of inbreeding mating strategy increased the strength of selection for evolution of polyandry and inbreeding avoidance through fertilisation bias.
 For example, in Figures 1C,D,G,H, tendency for polyandry allele values are typically less than zero, reflecting evolution of monandry, and inbreeding fertilisation strategy allele values were not as negative as they were in simulations with fixed random mating (Figure 3).
@@
 
-Figure 2, which we previously contrasted with Figure 1 to test whether or not evolution of inbreeding fertilisation strategy faciitates selection for polyandry, shows evolution of tendency for polyandry and inbreeding mating strategy when inbreeding fertilisation strategy is fixed such that the sire of a focal female's offspring is randomly assigned from her mates according to a fair raffle.
+Figure 2, which we previously contrasted with Figure 1 to test whether or not evolution of inbreeding fertilisation strategy facilitates selection for polyandry, shows evolution of tendency for polyandry and inbreeding mating strategy when inbreeding fertilisation strategy is fixed such that the sire of a focal female's offspring is randomly assigned from her mates according to a fair raffle.
 In all cost combinations of Figure 2 (panels A-D), tendency for polyandry allele values decreased over generations, reflecting evolution of monandry.
@@
 A weak effect is discernable in the contrast between Figure 2B and Figure 1B, in which the grand mean inbreeding mating strategy allele value is $-0.627$ when inbreeding fertilisation strategy is not fixed (Figure 1B) versus $-1.036$ when it is fixed (Figure 2B) in generation 10000.
-Therefore, when females were unable to bias fertilisatin to avoid inbreeding given severe inbreeding depression ($\beta=3$), selection for evolution of pre-copulatory inbreeding avoidance was not greatly strengthened.
+Values of $-0.627$ versus $-1.036$ correspond to an outbred focal female being $1.157$ versus $1.260$ times more likely to choose a non-relative than a full sibling as a mate, respectively.
+Therefore, when females were unable to bias fertilisation to avoid inbreeding given severe inbreeding depression ($\beta=3$), selection for evolution of pre-copulatory inbreeding avoidance was not greatly strengthened.
 

### 2016-09-13 ms_pre_post.Rmd
Add some empirical studies to evolution of polyandry to avoid inbreeding

@@
 
+Inbred offspring are typically less viable than outbred offspring, and when such inbreeding depression is strong, it is predicted to cause selection for inbreeding avoidance [Duthie and Reid *in press*; @Parker1979; @Parker2006; @Pusey1996; @Kokko2006].
+In animals, inbreeding avoidance can be realised through both pre-copulatory and post-copulatory mechanisms [e.g., @Tuni2013; @Firman2015; @Daniel2015; @Fischer2015].
+However, the conditions under which inbreeding avoidance is predicted to evolve via pre-copulatory, post-copulatory, or both pre- and post-copulatory mechanisms has not been modelled.
+There is therefore no framework for predicting what mechanisms of inbreeding avoidance are most likely to evolve in empirical populations where risk of fitness loss caused by inbreeding is high.
+Importantly, evolution of post-copulatory mechanisms of inbreeding avoidance requires females to mate multiply, meaning that post-copulatory inbreeding avoidance cannot occur unless polyandry has evolved in a population.
+Accordingly, we modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency to engage in polyandry, inbreeding mating strategy (pre-copulatory), and inbreeding fertilisation strategy (post-copulatory).
+Using *in silico* experiments, we tested four specific hypothesis to predict evolution of tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy given diverse costs and evolutionary constraints.
+We found that (1) selection for polyandry was greatly strengthened given concurrent evolution of inbreeding fertilisation strategy, (2) selection was strong for low cost, and weak but not negligible for high cost, mechanisms of inbreeding avoidance, (3) constraints on evolution of pre-copulatory inbreeding avoidance greatly strengthened selection for post-copulatory inbreeding avoidance, but not vice versa, and (4) pre-existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of post-copulatory inbreeding avoidance, but not vice versa.
+Our results therefore provide a novel framework for approaching empirical studies of inbreeding avoidance, predicting evolution of polyandry and inbreeding avoidance through pre- and post-copulatory mechanisms.
+
+<!--- (1) selection for polyandry is strengthened given adaptive inbreeding avoidance through fertilisation bias, (2) selection for pre- versus post-copulatory inbreeding avoidance will be strong for the least costly, and negligible for the most costly, mechanism of inbreeding avoidance, (3) selection for pre- or post-copulatory inbreeding avoidance will be strengthened if evolutionary constraints preclude inbreeding avoidance in the complementary mechanism, and (4) selection for pre- versus post-copulatory inbreeding avoidance will be weakened if a complementary adaptive mechanism of inbreeding avoidance is already fixed in a population.--->
+
+Evolution of polyandry to avoid inbreeding
+----------------------------------------------
+
+The opportunity to adjust inbreeding has been widely considered as a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
+Recently, @Duthie found the conditions under which selection for polyandry to avoid inbreeding is predicted to be highly restrictive, requiring strong constraints on the availability of initial compared to additional mates, or the conditional expression of polyandry such that females only engaged in polyandry when their initial choice of mate was of low quality.
+However, @Duthie assumed that fertilisation of offspring was unbiased with respect to mate kinship, meaning that females could not express choice after mating had occurred.
+In contrast, we found that when females could express choice after mating through biased fertilisation, selection for polyandry was greatly strengthened (Figure 1A), especially when constraints restricted evolution of inbreeding avoidance through mate choice (Figure 3).
+The proposition that polyandry might facilitate female choice among males of varying compatability is not new [e.g., @Zeh1997], but the existence of selection for post-copulatory inbreeding avoidance causing feedback to select for polyandry has not been formally modelled.
+Our model therefore has widespread implications for empirical studies of evolution of polyandry.
+
+We predict evolution of polyandry in populations where inbreeding depression is severe and evolution of inbreeding avoidance through post-copulatory mechanisms is not constrained.
+Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa [e.g.
+@Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015].
+For example, @Pizzari2004 find that the number of sperm arriving to eggs is lower for full siblings of female red jungefowl (*Gallus gallus*) than it is for non-relatives, even after controlling for effects of order of oviposition and social familiarity.
+Similarly, Firman and Simmons [-@Firman2008; -@Firman2015] have shown evidence of post-copulatory inbreeding avoidance in house mice, finding fertilisation to be biased toward unrelated males independent of the order in which mating occurs [@Firman2008] most likely due to post-copulatory mechanisms expressed through the secretion of gametic proteins originating in female's eggs [@Firman2015].
+Interestingly, female house mice have also been shown to express pre-copulatory inbreeding avoidance  [@Potts1991; @Roberts2003].
+Our results suggest that post-copulatory inbreeding avoidance is unlikely to evolve when females can already avoid inbreeding through pre-copulatory mechanisms (Figure 5), meaning that evolution of post-copulatory inbreeding avoidance could reasonably be hypothesised to have preceded evolution of pre-copulatory inbreeding avoidance in mice.
+<!--- start talking abou these now --->
+
+<!--- Olsson1996; Pizzari2004; Firman2008; Bretman2009; Gasparini2011; Tuni2013; Firman2015 --->
+
 <!--- The initial evolution of inbreeding fertilisation strategy might be further facilitated if the phenotypic expression of polyandry is caused by continuous genetic variation underlying a female's tendency for engaging in polyandry, as is expected for complex polygenic traits underlying behaviour under the fundamental assumptions of quantitative genetics [@Evans2008].
@@
 
-\vspace{60 mm}
+\vspace{150 mm}
 

### 2016-09-13 ms_pre_post.Rmd
Finish section on Evolution of polyandry to avoid inbreeding

@@
 For example, @Pizzari2004 find that the number of sperm arriving to eggs is lower for full siblings of female red jungefowl (*Gallus gallus*) than it is for non-relatives, even after controlling for effects of order of oviposition and social familiarity.
-Similarly, Firman and Simmons [-@Firman2008; -@Firman2015] have shown evidence of post-copulatory inbreeding avoidance in house mice, finding fertilisation to be biased toward unrelated males independent of the order in which mating occurs [@Firman2008] most likely due to post-copulatory mechanisms expressed through the secretion of gametic proteins originating in female's eggs [@Firman2015].
+Similarly, Firman and Simmons [-@Firman2008; -@Firman2015] have shown evidence of post-copulatory inbreeding avoidance in house mice, finding fertilisation to be biased toward unrelated males independent of the order in which mating occurs [@Firman2008], perhaps due to post-copulatory mechanisms expressed through the secretion of gametic proteins originating in female's eggs [@Firman2015].
 Interestingly, female house mice have also been shown to express pre-copulatory inbreeding avoidance  [@Potts1991; @Roberts2003].
 Our results suggest that post-copulatory inbreeding avoidance is unlikely to evolve when females can already avoid inbreeding through pre-copulatory mechanisms (Figure 5), meaning that evolution of post-copulatory inbreeding avoidance could reasonably be hypothesised to have preceded evolution of pre-copulatory inbreeding avoidance in mice.
+
+Specific mechanisms of post-copulatory inbreeding avoidance are difficult to identify, but recent experimental studies have shown how females can successfully bias fetilisation after mating has occurred in both vertebrates [e.g., @Gasparini2011] and invertebrates [e.g., @Tuni2013].
+For example, @Gasparini2011 artificially inseminated female guppies (*Poecilia reticulata*) with equal quantities of sperm from full-siblings and unrelated males, finding that fertilisation success was higher in non-relatives because the velocity of full siblings' sperm was reduced by females' ovarian fluids.
+Biased fertilisation toward non-relatives might also be accomplished through selective storage of sperm.
+For example, in black field crickets (*Teleogryllus commodus*), females attempt to remove the spermataphores of unwanted male mates after copulation, while male mates guard females to prevent spermatophore removal [@Bussiere2006].
+Even if females are unable to remove spermatophores of unwanted mates, @Tuni2013 found evidence that female *T.
+commodus* are capable of controlling which males' sperm is transferred to their spermatheca, most likely through physical control of the spermathical duct, and reduce sperm storage when being guarded by a related male.
+Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for polyandry, especially if pre-copulatoyr inbreeding avoidance is costly (Figure 1) or constrained (Figure 3).
+
+Costs of polyandry and inbreeding avoidance
+----------------------------------------------
+
+Constraints on polyandry and inbreeding avoidance
+----------------------------------------------
+
 <!--- start talking abou these now --->

### 2016-09-14 ms_pre_post.Rmd
Some progress on Discussion: Costs of polyandry and inbreeding avoidance

@@
 
+Our results show that direct negative selection on phenotypes that increase female promiscuity or choosiness with respect to kinship decrease the strength of selection for tendency for polyandry and inbreeding avoidance (Figure 1).
+Importantly, the cost of tendency for polyandry only decreased female fitness given tendency for polyandry phenotype values greater than zero ($P_{p}>0$), but the threshold nature of the tendency for polyandry phenotype only resulted in selection against positive tendency for polyandry allele values ($P_{a}$) when the sum over a focal female's $20$ $P_{a}$ alleles was greater than zero because summations less than zero all resulted in equivalent monandrous phenotypes ($P_{p}=0$).
+Hence, even when tendency for polyandry was costly, selection for more negative $P_{a}$ values weakened as the frequency of negative $P_{a}$ values increased and monandry was assured [@Duthie].
+This property of threshold traits
+
+<!--- Costs of polyandry including threshold trait -> polyandry affected by cost of inbreeding fertilisation strategy -> Polyandry indirectly affected by cost of inbreeding mating strategy through selection on post-copulatory inbreeding avoidance.
+Cost of inbreeding strategies mostly independent of one another and cost of polyandry.
+--->
+
+<!--- For example, females with a tendency to engage in polyandry might pay a cost associated with searching or making themselves available to mates, thereby increasing their own risk of predation [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
+Females that are particularly choosy in mating interactions (e.g., especially reluctant to mate with relatives) might pay a cost of increased risk of mating failure, or harm caused by sexual conflict [@Rowe1994; @Kokko2013].
+Females that are choosy after mating has occurred might pay an energetic cost associated with physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b] --->
+
 Constraints on polyandry and inbreeding avoidance

### 2016-09-14 ms_pre_post.Rmd
Add two paragraphs on Discussion: Costs of polyandry and inbreeding avoidance

@@
 Importantly, the cost of tendency for polyandry only decreased female fitness given tendency for polyandry phenotype values greater than zero ($P_{p}>0$), but the threshold nature of the tendency for polyandry phenotype only resulted in selection against positive tendency for polyandry allele values ($P_{a}$) when the sum over a focal female's $20$ $P_{a}$ alleles was greater than zero because summations less than zero all resulted in equivalent monandrous phenotypes ($P_{p}=0$).
-Hence, even when tendency for polyandry was costly, selection for more negative $P_{a}$ values weakened as the frequency of negative $P_{a}$ values increased and monandry was assured [@Duthie].
-This property of threshold traits
+Hence, even when tendency for polyandry was costly, selection for more negative $P_{a}$ values weakened as the frequency of negative $P_{a}$ values increased because each individual $P_{a}$ then became less influential in causing females to be monandrous [@Duthie].
+This general property of threshold traits causes maladaptive phenotypes to frequently reappear within populations due to the mutation and recombination of continuous genetic values underlying discrete phenotypes [@Roff1996; @Roff1998].
+Assuming that there is continuous genetic variation underlying threshold polyandry, polyandrous phenotypes are therefore sometimes predicted even when costly [@Duthie], potentially creating the possibility for selection on inbreeding fertilisation strategy when polyandry is expressed.
+This is most evident in Figure 1C, where mean allele values for polyandry are negative (red line), but strong post-copulatory inbreeding avoidance is still predicted (grey line).
+Consequently, costly polyandry does not necessarily preclude evolution of adaptive post-copulatory inbreeding avoidance in populations.
+
+A low relative cost for one inbreeding strategy (e.g., pre-copulatory inbreeding avoidance) did not preclude a more costly complementary inbreeding strategy from persisting in a focal population (Figure 1), meaning that evolution of both pre- and post-copulatory inbreeding avoidance might be expected in populations despite cost asymmetry.
+However, existence of costs strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies.
+Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging [@Pomiankowski1987; @Kokko2003; @Reid2015].
+@Pomiankowski1987 categorised four types of costs that are relevant to mate choice, which we suggest are also relevant costs for polyandry, and include costs of elevated risks associated with (1) predation or (2) disease transmission, and costs incurred through loss of time (3) or depletion of energy (4).
+In our model, we interpreted a cost of tendency for polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of inbreeding mating strategy as a lost of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of inbreeding fertilisation strategy as depletion of energy [e.g., @Tuni2013].
+While these costs are biologically realistic, different costs will be relevant for different populations and be realised in different ways.
+For example, increased risk of disease transmission has been observed for highly polyandrous females [@Roberts2015a], but such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry (as we model).
+Future models will therefore need to carefully consider the magnitudes and realisation of direct costs to accurately predict evolution of inbreeding strategies in populations.
+
+Another type of cost relevant for polyandry and inbreeding strategy is risk of male harm as a consequence of sexual conflict [e.g., @Arnqvist2005a; @Parker2006]. <!--- Male harm --->
 

### 2016-09-14 ms_pre_post.Rmd
Finish off draft of Discussion: Costs of polyandry and inbreeding avoidance

@@
 
-Another type of cost relevant for polyandry and inbreeding strategy is risk of male harm as a consequence of sexual conflict [e.g., @Arnqvist2005a; @Parker2006]. <!--- Male harm --->
+Another type of cost relevant for polyandry and inbreeding strategy is risk of male harm caused by sexual conflict [e.g., @Arnqvist2005a; @Parker2006].
+We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should benefit from a higher tolerance of inbreeding than females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
+Females that express the choice to avoid inbreeding when mating might therefore pay a cost of harm caused by coercion expressed by related males.
+This cost might itself evolve over time as male harm coevolves with female resistance [@Ronn2007; @Perry2011; @Wang2015a], and costs might vary with interactions among male non-relatives and relatives because effects of kin selection are predicted to reduce harm caused by related male suitors [@Rankin2011a].
+To predict evolution of polyandry and inbreeding strategy in populations characterised by active males and sexual conflict, consideration of male inbreeding strategy and coevolution between male harm and female resistance might therefore need to be considered explicitly.
 

### 2016-09-14 ms_pre_post.Rmd
Clean comments, add subtitle

@@
 ---
-title: "Evolution of precopulatory and postcopulatory inbreeding behaviour"
+title: "Evolution of pre-copulatory and post-copulatory inbreeding behaviour: a computational approach"
 author: "A. Bradley Duthie et al."
@@
 
-```{r, echo=FALSE}
-figscale <- 1.0; # Change the scale of a figure
-```
-
 Abstract
@@
 
-<!--- TODO: GENERAL PARAGRAPH INTRODUCING THE SCOPE AND KEY QUESTION --->
 Reproductive decisions expressed among interacting individuals directly affect individual fitnesses and the genotypes and viabilities of resulting offspring, and thereby profoundly affect evolutionary dynamics through the differential inheritence of alleles over generations [@Pizzari2012; @Wright2013; @Wild2014; @Liao2015; @Reid2016].
@@
 
-<!--- TODO: PARAGRAGH ON INBREEDING, PRE-COP, AND POST-COP AVOIDANCE --->
 Inbreeding, defined as breeding between relatives, directly affects inheritence of identical-by-descent alleles and the viability of inbred offspring, meaning that the decision to prefer, avoid, or tolerate (i.e., mate randomly with respect to relatedness) inbreeding is predicted to have profound effects on individual fitness [@Parker2006; @Kokko2006; @Szulkin2012; @Duthie2015a].
@@
 
-<!--- such as when focal females mate multiply (i.e., polyandry) to avoid inbreeding  [e.g., @Mays2008; @Brouwer2011; @Kingma2013; @Duthie] --->
-
-<!--- TODO: PARAGRAGH ON EVOLUTION OF POLYANDRY (H1) --->
 Critically, evolution of inbreeding fertilisation strategy is precluded if females only mate with one male, meaning that evolution of polyandry (defined as female multiple mating within a single reproductive bout) is intrinsically tied to female inbreeding fertilisation strategy.
@@
 
-<!--- TODO: PARAGRAGH ON IDEA OF PRE VS POST COPULATORY INBREEDING STRATEGY --->
 Evolution of inbreeding fertilisation strategy might increase selection for polyandry, but evolutionary feedbacks between inbreeding fertilisation strategy and polyandry might also be contingent upon evolution of inbreeding mating strategy, thereby leading to complex evolutionary dynamics between inbreeding strategies and polyandry.
@@
 
-<!--- TODO: PARAGRAGH ON COSTS OF POLYANDRY, MATING, AND FERTILISATION STRATEGIES --->
 Evolution of polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy will ultimately be determined by the, potentially interacting, fitness benefits and costs of each phenotype.
@@
 
-<!--- Mate searching: Lehmann2013, Kokko2006, Jamieson2009.
-Kin discrimination: Waser1986.
-Increased predation risk associated with mate search: Rowe1988, Ronkainen1994, Koga1998.
-Increased risk associated with expression of mate choice (e.g., avoiding male coercion): Rowe1994.
-Risk of not mating due to choosiness: Kokko2013
-
-<!--- TODO: PARAGRAGH ON ORDER OF INTERACTIONS --->
 Selection for inbreeding mating strategy versus inbreeding fertilisation strategy and associated polyandry might also depend evolutionary constraints, or on existing phenotypes in the population.
@@
 It is therefore necessary to consider evolution of inbreeding mating strategy and inbreeding fertilisation strategy when each evolves in a population where its complementary inbreeding strategy is evolutionarily constrained or already fixed as an adaptation.
-
-<!--- TODO: OVERVIEW OF THE POINT OF THE MODELLING --->
 Here we apply a model of female and male reproductive interactions and associated inbreeding depression in offspring viability to quantify evolution of three separate phenotypes including female tendency for polyandry, female pre-copulatory inbreeding strategy (mating strategy), and female post-copulatory inbreeding strategy (fertilisation strategy).
@@
 
-<!--- Change mating cost to an increased risk of mating failure ---> 
 Values of phenotypic traits for tendency to engage in polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilistation strategy ($F_{p}$) each have costs, which independently increase the probability of a focal female's reproductive failure.
@@
 
-<!--- Figure 2 shows an equivalent figure with changes in allele values of tendency for polyandry (red lines and shading) and inbreeding mating strategy (blue lines and shading) only.
-However, in Figure 2, a horizontal black line where mean allele value of inbreeding fertilisation strategy equals zero shows that these allele values have been fixed.
-Figure 2 has only four panels because costs of inbreeding fertilisation strategy is irrelevant when inbreeding fertilisation strategy alleles have no effect and mating is random (i.e., $F_{p}=0$).
---->
-
 Selection for polyandry is driven by inbreeding fertilisation strategy
 ----------------------------------------------
-
-<!--- Figure 1 will show a spread of all the results (evo combs02 B3.eps), and be contrasted with the four panel Figure 2 showing results when $F_{p}$ is knocked out (evo combs02 B3 ko F.eps). --->
 
@@
 
-<!--- Interestingly, a high cost of only tendency for polyandry (Figure 1C) or only inbreeding fertilisation strategy (Figure 1D) shows how these phenotypes are evolutionarily tied such that a cost of one phenotype can feed back to affect evolution of the other phenotype.
-For example, Figure 1C shows simulations in which inbreeding fertilisation strategy is not costly, causing $F_{a}$ values to become more negative (stronger inbreeding avoidance) than when both inbreeding fertilisation strategy and tendency for polyandry are costly (Figure 1G).
-However, $F_{a}$ values are not as negative as they would be if neither tendency for polyandry or inbreeding fertilisations trategy were costly (Figure 1A) because expression of fertilisation bias was hindered by costs of polyandry and an associated reduction in evolved mating frequency.
-Similarly, Figure 1D shows simulations in which only inbreeding fertilisation strategy was costly, causing less strong inbreeding avoidance through fertilisation bias.
-Consequently, tendency for polyandry values were lower than when inbreeding fertilisation strategy was not costly (Figure 1A) because polyandry was less beneficial when it did not result in strong inbreeding avoidance through fertilisation bias.
---->
-
 Selection given constraints on evolution
@@
 
-<!--- Figure 3 will show constraints on $M_{p}$ affecting $F_{p}$, while Figure 2 will be used again to show constraints on $F_{p}$ affecting $M_{p}$. --->
-
 Selection given a pre-existing adaptive inbreeding strategy
@@
 We therefore found strong evidence that the existence of adaptive inbreeding avoidance through pre-copulatory mate choice precluded evolution of adaptive inbreeding avoidance through post-copulatory inbreeding avoidance through fertilisation bias.
-
-<!--- Figure 4 will show evolution of $M_{p}$ given pre-existing post-copulatory inbreeding avoidance, and Figure 5 will show evolution of $P_{p}$ and $F_{p}$ given pre-existing pre-copulatory inbreeding avoidance.
---->
-
-<!--- Get in there that the replicate simulations don't show evidence of alternative states -- one thing happens or does not, though there is some correlation among traits in replicates --->
 
@@
 Our results therefore provide a novel framework for approaching empirical studies of inbreeding avoidance, predicting evolution of polyandry and inbreeding avoidance through pre- and post-copulatory mechanisms.
-
-<!--- (1) selection for polyandry is strengthened given adaptive inbreeding avoidance through fertilisation bias, (2) selection for pre- versus post-copulatory inbreeding avoidance will be strong for the least costly, and negligible for the most costly, mechanism of inbreeding avoidance, (3) selection for pre- or post-copulatory inbreeding avoidance will be strengthened if evolutionary constraints preclude inbreeding avoidance in the complementary mechanism, and (4) selection for pre- versus post-copulatory inbreeding avoidance will be weakened if a complementary adaptive mechanism of inbreeding avoidance is already fixed in a population.--->
 
@@
 To predict evolution of polyandry and inbreeding strategy in populations characterised by active males and sexual conflict, consideration of male inbreeding strategy and coevolution between male harm and female resistance might therefore need to be considered explicitly.
-
-<!--- Costs of polyandry including threshold trait -> polyandry affected by cost of inbreeding fertilisation strategy -> Polyandry indirectly affected by cost of inbreeding mating strategy through selection on post-copulatory inbreeding avoidance.
-Cost of inbreeding strategies mostly independent of one another and cost of polyandry.
---->
-
-<!--- For example, females with a tendency to engage in polyandry might pay a cost associated with searching or making themselves available to mates, thereby increasing their own risk of predation [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
-Females that are particularly choosy in mating interactions (e.g., especially reluctant to mate with relatives) might pay a cost of increased risk of mating failure, or harm caused by sexual conflict [@Rowe1994; @Kokko2013].
-Females that are choosy after mating has occurred might pay an energetic cost associated with physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b] --->
 

### 2016-09-15 ms_pre_post.Rmd
Initial passage on constraints

@@
 
+Our model assumed that allele values underlying tendency for polyandry, pre-copulatory inbreeding avoidance, and post-copulatory inbreeding avoidance were all initialised at zero (causing monandry, and random mating and fertilisation with respect to kinship), and phenotypes evolved simultaneously after initialisation.
+However, these initial conditions are likely to be atypical, as evolution of pre-copulatory and post-copulatory inbreeding avoidance from ancestral random mating and fertilisation is unlikely to occur simultaneously.
+Rather, initial evolution of one inbreeding strategy (e.g., pre-copulatory inbreeding avoidance) is more likely to occur in the absence of its complementary strategy (e.g., post-copulatory inbreeding avoidance) if the complementary strategy is evolutionarily constrained.
+Alternatively, initial evolution of one inbreeding strategy might occur in the context of an already established adaptive strategy for avoiding inbreeding.
+
 <!--- start talking abou these now --->

### 2016-09-15 ms_pre_post.Rmd
Finish first paragraph on constraints, start second one of empirical studies in cabbage beetles.

@@
 Alternatively, initial evolution of one inbreeding strategy might occur in the context of an already established adaptive strategy for avoiding inbreeding.
+We showed that selection for post-copulatory but not pre-copulatory inbreeding avoidance was strengthened if its complementary strategy was fixed for random choice with respect to kinship, and that selection for post-copulatory but not pre-copulatory inbreeding avoidance was precluded if its complementary strategy was fixed for adaptive inbreeding avoidance.
+
+Few studies address evolution of both pre-copulatory and post-copulatory inbreeding strategies, but existing empirical studies support our model predictions.
+For example, @Lui2014 found evidence for pre-copulatory, but not post-copulatory inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*).
+
+<!---  Lui    --->
 

### 2016-09-15 ms_pre_post.Rmd
Some progress with exclusively pre- or post-copulatory inbreeding avoidance references

@@
 
-Few studies address evolution of both pre-copulatory and post-copulatory inbreeding strategies, but existing empirical studies support our model predictions.
-For example, @Lui2014 found evidence for pre-copulatory, but not post-copulatory inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*).
+Multiple studies have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009].
 
-<!---  Lui    --->
+Few studies address evolution of both pre-copulatory and post-copulatory inbreeding strategies, but existing empirical studies are consistent with our model predictions.
+@Liu2014 found evidence for pre-copulatory, but not post-copulatory inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*).
+In our model, post-copulatory
 
-<!--- start talking abou these now --->
+<!--- Note that females might mate multiply because first need to ensure that they get a mate at all.  \cite{Daniel2015} --->
 
-<!--- Olsson1996; Pizzari2004; Firman2008; Bretman2009; Gasparini2011; Tuni2013; Firman2015 --->
-
-<!--- The initial evolution of inbreeding fertilisation strategy might be further facilitated if the phenotypic expression of polyandry is caused by continuous genetic variation underlying a female's tendency for engaging in polyandry, as is expected for complex polygenic traits underlying behaviour under the fundamental assumptions of quantitative genetics [@Evans2008].
-Under quantitative genetic assumptions, polyandry can therefore be conceptualised as a 'threshold trait', meaning that multiple mating is only realised above some threshold genetic value [@Lynch1998].
-Expression of  --->
+<!---  Constraints on pre-cop: Limited kin recognition --->
 

### 2016-09-15 ms_pre_post.Rmd
Fix error about magnitude of inbreeding avoidance -- allele versus phenotype value

@@
 A weak effect is discernable in the contrast between Figure 2B and Figure 1B, in which the grand mean inbreeding mating strategy allele value is $-0.627$ when inbreeding fertilisation strategy is not fixed (Figure 1B) versus $-1.036$ when it is fixed (Figure 2B) in generation 10000.
-Values of $-0.627$ versus $-1.036$ correspond to an outbred focal female being $1.157$ versus $1.260$ times more likely to choose a non-relative than a full sibling as a mate, respectively.
-Therefore, when females were unable to bias fertilisation to avoid inbreeding given severe inbreeding depression ($\beta=3$), selection for evolution of pre-copulatory inbreeding avoidance was not greatly strengthened.
+Because females have 20 alleles with additive effects on inbreeding mating strategy, an average female is therefore expected to have mean inbreeding mating strategy phenotype values of $M_{p} = -0.627 \times 20 = -12.54$ and $M_{p} = -1.036 \times 20 = -20.72$ for not fixed versus fixed inbreeding fertilisation strategy, respectively.
+These values would cause an outbred focal female to be $2.135$ and $4.180$ times more likely to choose a non-relative than a full sibling as a mate given not fixed fersus fixed inbreeding fertilisation strategy, respectively.
+Therefore, when females were unable to bias fertilisation to avoid inbreeding given severe inbreeding depression ($\beta=3$), selection for evolution of pre-copulatory inbreeding avoidance was strengthened.
 
@@
 
-Multiple studies have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009].
+<!--- Note that females might mate multiply because first need to ensure that they get a mate at all.  \cite{Daniel2015} --->
+
+<!---  Constraints on pre-cop: Limited kin recognition --->
+
+<!---  Concluding paragraph below --->
+
+Studies of multiple species have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009].
+Other studies have
 
@@
 
-<!--- Note that females might mate multiply because first need to ensure that they get a mate at all.  \cite{Daniel2015} --->
+However, empirical hypothesis testing typically does not attempt to predict *a priori* whether or not inbreeding avoidance will be enacted before or after copulation, or if both pre-copulatory and post-copulatory inbreeding avoidance will evolve.
+Here we have shown that evolution of inbreeding strategies and associated polyandry are predicted to affected by direct costs, and constraints and adaptations of
 
-<!---  Constraints on pre-cop: Limited kin recognition --->
+<!---     ----------------------------------------------------------------     --->
 

### 2016-09-15 ms_pre_post.Rmd
Add abstract, a bit more Discussion

@@
 ===================================================
+
+Inbreeding avoidance has been observed through pre-copulatory and post-copulatory mechanisms in empirical systems as a consequence of inbreeding depression.
+However, no models compare evolution of pre-copulatory versus post-copulatory inbreeding avoidance jointly, and given biologically relevant costs of, and constraints on, inbreeding strategies.
+Critically, evolution of post-copulatory inbreeding avoidance is restricted to females that mate multiply, potentially leading to complex evolutionary dynamics among inbreeding strategies and polyandry.
+Accordingly, use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address four questions: (1) Will evolution of post-copulatory inbreeding avoidance strengthen selection for polyandry?
+(2) Will selection for one costly inbreeding strategy be negligible given a non-costly complementary strategy?
+(3) Will constraints on evolution of one inbreeding strategy increase selection on an alternative strategy?
+And (4) will selection for one inbreeding strategy be negligible given existence of an already adaptive alternative strategy?
+We show that evolution of polyandry is greatly facilitated by evolution of post-copulatory inbreeding avoidance.
+Costs and constraints on pre-copulatory inbreeding avoidance generally affected evolution of post-copulatory inbreeding avoidance, but not vice versa.
+Our model thereby introduces a novel framework for predicting evolution of both pre-copulatory and post-copulatory inbreeding strategies in empirical systems.
 
@@
 Because females have 20 alleles with additive effects on inbreeding mating strategy, an average female is therefore expected to have mean inbreeding mating strategy phenotype values of $M_{p} = -0.627 \times 20 = -12.54$ and $M_{p} = -1.036 \times 20 = -20.72$ for not fixed versus fixed inbreeding fertilisation strategy, respectively.
-These values would cause an outbred focal female to be $2.135$ and $4.180$ times more likely to choose a non-relative than a full sibling as a mate given not fixed fersus fixed inbreeding fertilisation strategy, respectively.
+These values would cause an outbred focal female to be $2.135$ and $4.180$ times more likely to choose a non-relative than a full sibling as a mate given not fixed versus fixed inbreeding fertilisation strategy, respectively.
 Therefore, when females were unable to bias fertilisation to avoid inbreeding given severe inbreeding depression ($\beta=3$), selection for evolution of pre-copulatory inbreeding avoidance was strengthened.
@@
 We showed that selection for post-copulatory but not pre-copulatory inbreeding avoidance was strengthened if its complementary strategy was fixed for random choice with respect to kinship, and that selection for post-copulatory but not pre-copulatory inbreeding avoidance was precluded if its complementary strategy was fixed for adaptive inbreeding avoidance.
+
+<!--- Also: note, pre-copulatory but not post-copulatory inbreeding avoidance can occur for males --->
 

### 2016-09-16 ms_pre_post.Rmd
Add small changes to Abstract

@@
 ---
-title: "Evolution of pre-copulatory and post-copulatory inbreeding behaviour: a computational approach"
+title: 'Evolution of pre-copulatory and post-copulatory inbreeding behaviour: a computational
+  approach'
 author: "A. Bradley Duthie et al."
@@
 
-Inbreeding avoidance has been observed through pre-copulatory and post-copulatory mechanisms in empirical systems as a consequence of inbreeding depression.
-However, no models compare evolution of pre-copulatory versus post-copulatory inbreeding avoidance jointly, and given biologically relevant costs of, and constraints on, inbreeding strategies.
+Inbreeding avoidance has been widely observed through pre-copulatory and post-copulatory mechanisms as a consequence of inbreeding depression in offspring viability.
+However, no models compare evolution of pre-copulatory and post-copulatory inbreeding avoidance jointly, and given biologically relevant costs of, and constraints on, inbreeding strategies.
 Critically, evolution of post-copulatory inbreeding avoidance is restricted to females that mate multiply, potentially leading to complex evolutionary dynamics among inbreeding strategies and polyandry.

### 2016-09-16 initial_analysis.R
Add plot of 20k generation simulations

@@ -850,6 +850,337 @@ dev.off();
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX  SAME THING BUT FOR TWICE AS MANY GENERAGTIONS FIGURE 1     XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+
+
+
+rm(list=ls()); 
+
+setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
+gens      <- 19999;
+# ------------------------------------------------------------------------#
+# -----------  BETA = 3  -------------------------------------------------#
+# ------------------------------------------------------------------------#
+beta_val <- 3;
+setEPS(); # postscript below for final publication?
[…]

### 2016-09-16 ms_pre_post.Rmd
Correct standard deviation to standard error in reference to plot shading

@@
 In all simulations, we record mean values of $P_{a}$, $M_{a}$, $F_{a}$ in each generation.
-Each combination of parameter values simulated is replicated $40$ times, and grand mean values and standard deviation of means is calculated in each generation across replicate simulations.
+Each combination of parameter values simulated is replicated $40$ times, and grand mean values and standard error of means is calculated in each generation across replicate simulations.
 These analyses allow us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on inbreeding fertilisation strategy might be weak if polyandry is rare).
@@
 Figures 1-5 show mean allele values of tendency for polyandry ($P_{a}$; red lines and shading), inbreeding mating strategy ($M_{a}$; blue lines and shading), and inbreeding fertilisation strategy ($F_{a}$; black lines and shading) over 10000 generations as calculated across all individuals (female and male) within a focal population over 40 replicate simulations with identical starting conditions.
-Solid lines represent the grand mean of replicate mean allele values, and shading around lines shows standard deviations of mean allele values around the grand mean.
+Solid lines represent the grand mean of replicate mean allele values, and shading around lines shows standard errors of mean allele values around the grand mean.
 Panels within figures show different cost combinations for tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$).
@@
 We found that (1) selection for polyandry was greatly strengthened given concurrent evolution of inbreeding fertilisation strategy, (2) selection was strong for low cost, and weak but not negligible for high cost, mechanisms of inbreeding avoidance, (3) constraints on evolution of pre-copulatory inbreeding avoidance greatly strengthened selection for post-copulatory inbreeding avoidance, but not vice versa, and (4) pre-existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of post-copulatory inbreeding avoidance, but not vice versa.
-Our results therefore provide a novel framework for approaching empirical studies of inbreeding avoidance, predicting evolution of polyandry and inbreeding avoidance through pre- and post-copulatory mechanisms.
+More generally, we provide a novel framework for approaching empirical studies of inbreeding avoidance, predicting evolution of polyandry and inbreeding avoidance through pre- and post-copulatory mechanisms.
 
@@
 In contrast, we found that when females could express choice after mating through biased fertilisation, selection for polyandry was greatly strengthened (Figure 1A), especially when constraints restricted evolution of inbreeding avoidance through mate choice (Figure 3).
-The proposition that polyandry might facilitate female choice among males of varying compatability is not new [e.g., @Zeh1997], but the existence of selection for post-copulatory inbreeding avoidance causing feedback to select for polyandry has not been formally modelled.
+The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but the existence of selection for post-copulatory inbreeding avoidance causing feedback to select for polyandry has not been formally modelled.
 Our model therefore has widespread implications for empirical studies of evolution of polyandry.
@@
 @Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015].
-For example, @Pizzari2004 find that the number of sperm arriving to eggs is lower for full siblings of female red jungefowl (*Gallus gallus*) than it is for non-relatives, even after controlling for effects of order of oviposition and social familiarity.
+For example, @Pizzari2004 found that the number of sperm arriving to eggs is lower for full siblings of female red jungefowl (*Gallus gallus*) than it is for non-relatives, even after controlling for effects of order of oviposition and social familiarity.
 Similarly, Firman and Simmons [-@Firman2008; -@Firman2015] have shown evidence of post-copulatory inbreeding avoidance in house mice, finding fertilisation to be biased toward unrelated males independent of the order in which mating occurs [@Firman2008], perhaps due to post-copulatory mechanisms expressed through the secretion of gametic proteins originating in female's eggs [@Firman2015].
@@
 Even if females are unable to remove spermatophores of unwanted mates, @Tuni2013 found evidence that female *T.
-commodus* are capable of controlling which males' sperm is transferred to their spermatheca, most likely through physical control of the spermathical duct, and reduce sperm storage when being guarded by a related male.
-Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for polyandry, especially if pre-copulatoyr inbreeding avoidance is costly (Figure 1) or constrained (Figure 3).
+commodus* are capable of controlling the transfer of sperm to their spermatheca, most likely through physical control of the spermathical duct, and can reduce sperm storage despite being guarded by a related male.
+Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for polyandry, especially if pre-precopulatory inbreeding avoidance is costly (Figure 1) or constrained (Figure 3).
 
@@
 This general property of threshold traits causes maladaptive phenotypes to frequently reappear within populations due to the mutation and recombination of continuous genetic values underlying discrete phenotypes [@Roff1996; @Roff1998].
-Assuming that there is continuous genetic variation underlying threshold polyandry, polyandrous phenotypes are therefore sometimes predicted even when costly [@Duthie], potentially creating the possibility for selection on inbreeding fertilisation strategy when polyandry is expressed.
+Assuming that there is continuous genetic variation underlying threshold polyandry, polyandrous phenotypes are therefore sometimes predicted to persist within populations even when costly [@Duthie], potentially creating the possibility for selection on inbreeding fertilisation strategy when polyandry is expressed.
 This is most evident in Figure 1C, where mean allele values for polyandry are negative (red line), but strong post-copulatory inbreeding avoidance is still predicted (grey line).
@@
 @Pomiankowski1987 categorised four types of costs that are relevant to mate choice, which we suggest are also relevant costs for polyandry, and include costs of elevated risks associated with (1) predation or (2) disease transmission, and costs incurred through loss of time (3) or depletion of energy (4).
-In our model, we interpreted a cost of tendency for polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of inbreeding mating strategy as a lost of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of inbreeding fertilisation strategy as depletion of energy [e.g., @Tuni2013].
+In our model, we interpreted a cost of tendency for polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of inbreeding mating strategy as a lost of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of inbreeding fertilisation strategy as depletion of energy.
 While these costs are biologically realistic, different costs will be relevant for different populations and be realised in different ways.
-For example, increased risk of disease transmission has been observed for highly polyandrous females [@Roberts2015a], but such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry (as we model).
+For example, increased risk of disease transmission has been observed for highly polyandrous females [@Roberts2015a], but such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry.
 Future models will therefore need to carefully consider the magnitudes and realisation of direct costs to accurately predict evolution of inbreeding strategies in populations.
+<!--- add Tuni citation for depletion of energy?
+--->
 
@@
 <!---  Constraints on pre-cop: Limited kin recognition --->
+
+<!--- BARRIERS to having both pre and post-copulatory inbreeding avoidance evolve are few, although -- all else being equal -- post-copulatory avoidance might evolve less often if there is existing mating avoidance.
+--->
 
@@
 ![Mean allele values underlying tendency for polyandry (red lines and shading), inbreeding mating strategy (i.e., pre-copulatory choice; blue lines and shading), and inbreeding fertilisation strategy (i.e., post-copulatory choice; black lines and shading), as calculated across all individuals within a population over 10000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard deviations of allele values around grand means.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
 Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
@@
 ![Mean allele values underlying tendency for polyandry (red lines and shading) and inbreeding mating strategy (i.e., pre-copulatory choice; blue lines and shading), as calculated across all individuals within a population over 10000 generations given strong inbreeding depression when allele values underlying inbreeding fertilisation strategy (i.e., post-copulatory choice) are fixed for random fertilisation among mates (black horizontal lines where y-axes equal zero).
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard deviations of allele values around grand means.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
 Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
@@
 ![Mean allele values underlying tendency for polyandry (red lines and shading) and inbreeding fertilisation strategy (i.e., post-copulatory choice; black lines and shading), as calculated across all individuals within a population over 10000 generations given strong inbreeding depression when allele values underlying inbreeding mating strategy (i.e., pre-copulatory choice) are fixed for random mating (blue horizontal lines where y-axes equal zero).
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard deviations of allele values around grand means.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
 Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
@@
 ![Mean allele values underlying inbreeding mating strategy (i.e., pre-copulatory choice; blue lines and shading), as calculated across all individuals within a population over 10000 generations given strong inbreeding depression and the pre-existence of polyandry to avoid inbreeding (tendency for polyandry allele values equal 1, as indicated by horizontal red lines; inbreeding fertilisation strategy values equal -5, as indicated by horizontal black lines).
-Solid blue lines represent grand means over 40 replicate populations, and blue shading around solid lines shows standard deviations of mean inbreeding mating strategy allele values around grand means.
+Solid blue lines represent grand means over 40 replicate populations, and blue shading around solid lines shows standard errors of mean inbreeding mating strategy allele values around grand means.
 Negative mean allele values reflect a strategy of inbreeding avoidance, and positive values reflect a strategy of inbreeding preference.
@@
 ![Mean allele values underlying tendency for polyandry (red lines and shading) and inbreeding fertilisation strategy (i.e., post-copulatory choice; black lines and shading), as calculated across all individuals within a population over 10000 generations given strong inbreeding depression and the pre-existence of inbreeding avoidance in mate choice (inbreeding mating strategy values equal -5, as indicated by horizontal blue lines).
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard deviations of allele values around grand means.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
 Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.

### 2016-09-16 initial_analysis.R
Tweak some of the text placement in the new 20k Figure

@@ -1165,12 +1165,316 @@ dev.off();
 #==========================================================================
 
 
-
-
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 
+# And now with easier to follow axes, as allele values get higher and lower
+
+rm(list=ls()); 
+
+setwd("~/Dropbox/DuthieManu/pre_post_cop/Initial_Results");
+gens      <- 19999;
+# ------------------------------------------------------------------------#
+# -----------  BETA = 3  -------------------------------------------------#
+# ------------------------------------------------------------------------#
+beta_val <- 3;
+setEPS(); # postscript below for final publication?
+cairo_ps("figures/20K/evo_combs02_B3_2.eps",family="Arial",height=8,width=5.5);
+par(mfrow=c(4,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
+# ------------------------------------------------------------------------#
+evo_cc_02 <- read.table(file="res_c02s_20k/evo_M00_P00_F00_20k.txt", header=FALSE);
+evB <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
+evo <- evB[evB[,2]==beta_val,];
+mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
+mPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=mean);
+mEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=mean);
+sWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=sd);
[…]

### 2016-09-16 ms_pre_post.Rmd
Finish a rough draft for review among colleagues

@@
 - \bibliographystyle{amnatnat}
-linestretch: 1
+linestretch: 2
 csl: evolution.csl
@@
 ---
+
+<!--- Need to do 40k generations to see allele values level off, 40 replicates each:
+
+Figure    1: 100 hours total
+Figures   2: 48  hours total
+Figures   3: 48  hours total
+Figures   4: 48  hours total
+Figures   5: 48  hours total
+
+Nah, these are too much.
+I've decided to increase to 40k generations for the costs only (100 hours total).
+Reasoning for this is that when we look at the fixed traits, we are really interested in whether or not the initial invasion changes, hence fewer generations are better.
+When we start everything at zero and let it evolve, then long-term stuff becomes more important, so 40k are useful.
+
+--->
 
@@
 
+<!--- Some of these conclusions will need to be changed in light of the need for more generations of data: Strategies were concluded to be non-negligible, they they actually become negligible given a sufficient amount of time.
+--->
+
 Figure 1 shows changes in mean allele values of tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy across all eight possible combinations of costs.
@@
 For example, in black field crickets (*Teleogryllus commodus*), females attempt to remove the spermataphores of unwanted male mates after copulation, while male mates guard females to prevent spermatophore removal [@Bussiere2006].
-Even if females are unable to remove spermatophores of unwanted mates, @Tuni2013 found evidence that female *T.
-commodus* are capable of controlling the transfer of sperm to their spermatheca, most likely through physical control of the spermathical duct, and can reduce sperm storage despite being guarded by a related male.
-Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for polyandry, especially if pre-precopulatory inbreeding avoidance is costly (Figure 1) or constrained (Figure 3).
+Even if females are unable to remove spermatophores of unwanted mates, @Tuni2013 found that female *T.
+commodus* are capable of controlling the transfer of sperm to their spermatheca, most likely through physical control of the spermathecal duct, and can reduce sperm storage despite being guarded by a related male.
+Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for polyandry, especially if pre-copulatory inbreeding avoidance is costly (Figure 1) or constrained (Figure 3).
 
@@
 
+Constraints on pre-copulatory and post-copulatory inbreeding avoidance might vary widely in empirical systems.
+Female mate choice might be evolutionarily constrained if females are unable to discriminate among kin and therefore incapable of choosing to avoid inbreeding [Duthie and Reid *in press*; @Penn2010].
+Similarly, females might choose to avoid inbreeding, but be ecologically constrained in their choice by the availability of males if few non-relatives are available [e.g., @Kokko2006a; @Kokko2013], or if females are unable to resist male coercion given sexual conflict [@Arnqvist2005, pp.
+44-91].
+Females might also be unable to discriminate between sperm of relatives versus non-relatives, or be unable to successfully bias fertilisation toward non-relative's sperm.
+Our results suggest that such constraints on one strategy of inbreeding avoidance (pre-copulatory versus post-copulatory) will strengthen selection on a complementary strategy, perhaps making inbreeding avoidance more detectable in empirical systems.
+
 <!--- Also: note, pre-copulatory but not post-copulatory inbreeding avoidance can occur for males --->
@@
 
-Studies of multiple species have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009].
-Other studies have
-
-Few studies address evolution of both pre-copulatory and post-copulatory inbreeding strategies, but existing empirical studies are consistent with our model predictions.
-@Liu2014 found evidence for pre-copulatory, but not post-copulatory inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*).
-In our model, post-copulatory
-
-However, empirical hypothesis testing typically does not attempt to predict *a priori* whether or not inbreeding avoidance will be enacted before or after copulation, or if both pre-copulatory and post-copulatory inbreeding avoidance will evolve.
-Here we have shown that evolution of inbreeding strategies and associated polyandry are predicted to affected by direct costs, and constraints and adaptations of
+Studies of multiple species have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013; @Fischer2015], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009].
+Further, evidence of both pre-copulatory and post-copulatory inbreeding avoidance has been found for a handful of well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015], while @Liu2014 found evidence for pre-copulatory, but not post-copulatory, inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*).
+These empirical studies demonstrate that evolution of all combinations of pre-copulatory and post-copulatory inbreeding avoidance are possible, but no general modelling attempts to predict *a priori* whether or not inbreeding avoidance will be enacted before or after copulation, or if both pre-copulatory and post-copulatory inbreeding avoidance will evolve.
+Here we have shown that evolution of inbreeding strategies and associated polyandry are predicted to be affected by direct costs, and constraints and adaptations of complementary inbreeding strategies.
 
@@
 **************************
+
+\vspace{70 mm}
 
@@
 
-\vspace{150 mm}
+\vspace{180 mm}
 

### 2016-09-19 analysis.R
Initial commit of full analysis. Complete Figure 1 and draft of Figure 2

@@ -1,0 +1,375 @@
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+#  ____                                 _                         #
+# |  _ \ _ __ ___       _ __   ___  ___| |_    ___ ___  _ __      #
+# | |_) | '__/ _ \_____| '_ \ / _ \/ __| __|  / __/ _ \| '_ \     #
+# |  __/| | |  __/_____| |_) | (_) \__ \ |_  | (_| (_) | |_) |    #
+# |_|   |_|  \___|     | .__/ \___/|___/\__|  \___\___/| .__/     #
+#                      |_|                             |_|        #
+#                                                                 #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+
+rm(list=ls()); 
+setwd("~/Dropbox/DuthieManu/pre_post_cop");
+gens      <- 39999;
+beta_val <- 3;
+
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX      PLOT FIGURE 1  XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+setEPS(); # postscript below for final publication?
+cairo_ps("figures/M00_P01_F00.eps",family="Arial",height=6,width=6);
+par(oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
+# ------------------------------------------------------------------------#
+evo_cc_02 <- read.table(file="results/fig1/evo_M00_P01_F00.txt", header=FALSE);
[…]

### 2016-09-19 ms_pre_post.Rmd
Make some minor wording tweeks and correct typos

@@
 It is therefore necessary to consider evolution of inbreeding mating strategy and inbreeding fertilisation strategy when each evolves in a population where its complementary inbreeding strategy is evolutionarily constrained or already fixed as an adaptation.
+
 Here we apply a model of female and male reproductive interactions and associated inbreeding depression in offspring viability to quantify evolution of three separate phenotypes including female tendency for polyandry, female pre-copulatory inbreeding strategy (mating strategy), and female post-copulatory inbreeding strategy (fertilisation strategy).
 We use individual-based modelling and *in silico* experiments to test the hypothesis that, given severe inbreeding depression in offspring viability, evolution of inbreeding avoidance through fertilisation bias causes selection for evolution of polyandry.
-Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that that inbreeding avoidance through mate choice but not fertilisation bias will evolve when inbreeding mating strategy is less costly than the combined cost of inbreeding fertilisation strategy and tendency for polyandry, while inbreeding avoidance through fertilisation bias but not mate choice will evolve when inbreeding mating strategy is more costly than the combined costs of inbreeding fertilisation strategy and tendency for polyandry.
+Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that inbreeding avoidance through mate choice but not fertilisation bias will evolve when inbreeding mating strategy is less costly than the combined cost of inbreeding fertilisation strategy and tendency for polyandry, while inbreeding avoidance through fertilisation bias but not mate choice will evolve when inbreeding mating strategy is more costly than the combined costs of inbreeding fertilisation strategy and tendency for polyandry.
 Finally, we test the hypothesis that constraints on evolution of one inbreeding strategy (e.g., inbreeding mating strategy) will increase the strength of selection on evolution of a complementary inbreeding strategy (e.g., inbreeding fertilisation strategy), and that evolution of one inbreeding strategy will be precluded if it is introduced into a population that is already fixed for a complementary inbreeding strategy that is adaptive.

### 2016-09-19 ms_pre_post.Rmd
Update Results and Discussion for new results that very long term evolution of strategies goes to random mating for the relatively more costly strategy.

@@
 In Figure 1A, when no phenotypes are costly, inbreeding mating strategy and inbreeding fertilisation strategy evolve to inbreeding avoidance ($M_{a}<0$ and $F_{a}<0$), and females evolve to be polyandrous ($P_{a}>0$).
-Costs of phenotypes have a direct effect on evolution, causing inbreeding mating strategy and inbreeding fertilisation strategy phenotypes to evolve to values closer to zero (because realisation of inbreeding strategy costs increases with phenotype absolute values) and tendency for polyandry phenotypes to evolve to values that are more negative (because realisation of polyandry costs increases with positive phenotype values).
+Costs of phenotypes had a direct effect on evolution, causing inbreeding mating strategy and inbreeding fertilisation strategy phenotypes to evolve to values closer to zero (because realisation of inbreeding strategy costs increases with phenotype absolute values) and tendency for polyandry phenotypes to evolve to values that were more negative (because realisation of polyandry costs increases with positive phenotype values).
 
 We can use Figure 1 to test the hypothesis that inbreeding mating strategy will evolve to inbreeding avoidance ($M_{a}<0$), but inbreeding fertilisation strategy will be negligible ($F_{a} \approx 0$) when mating costs are low ($c_{M}=0$) relative to the costs of tendency for polyandry and inbreeding fertilisation strategy ($c_{P}=0.02$ or $c_{F}=0.02$) by comparing different cost combinations to the null model in which all costs equal zero (Figure 1A).
-Figures 1A,C,D,G show that inbreeding avoidance evolves at a comparable rate whenever $c_{M}=0$.
-However, inbreeding fertilisation strategy is never negligible; $F_{a}$ values are still negative over generations even when costs of inbreeding mating strategy is weak and costs of tendency for polyandry and inbreeding fertilisation strategy are strong.
+Figure 1A,C,D,G show that inbreeding avoidance in mating ($M_{a}<0$) evolved consistently whenever $c_{M}=0$.
+When inbreeding fertilisation strategy was costly and inbreeding avoidance strategy was not costly (Figure 1D,G), inbreeding fertilisation strategy initially evolved toward inbreeding avoidance ($F_{a} < 0$), but long-term evolution of inbreeding fertilisation strategy stabilised at random mating ($F_{a} \approx 0$).
+However, when only tendency for polyandry was costly (Figure 1C), both inbreeding mating strategy and inbreeding fertilisation strategy evolved to inbreeding avoidance over generations ($M_{a} < 0$ and $F_{a} < 0$).
 
 We can also use Figure 1 to test the hypothesis that inbreeding fertilisation strategy will evolve to inbreeding avoidance ($F_{a}<0$), but inbreeding mating strategy will be negligible ($M_{a} \approx 0$) when tendency for polyandry and inbreeding fertilisation strategy costs are low ($c_{P}=0$ and $c_{F}=0$) relative to the cost of inbreeding mating strategy ($c_{M}=0.02$).
-Figure 1B shows that inbreeding avoidance through fertilisation bias evolves ($F_{a}<0$) under these conditions, but evolution of inbreeding mating strategy is not negligible; $M_{a}$ values are consistently negative across all combinations of costs.
+Figure 1B shows that inbreeding avoidance through fertilisation bias evolved ($F_{a}<0$) under these conditions.
+While inbreeding mating strategy initially evolved toward inbreeding avoidance ($M_{a} < 0$), long-term evolution of inbreeding mating strategy stabilised at random mating ($M_{a} \approx 0$).
 
@@
 This pattern of evolution contrasts with that observed when inbreeding mating strategy was not fixed, indicating that constraints on evolution of inbreeding mating strategy increased the strength of selection for evolution of polyandry and inbreeding avoidance through fertilisation bias.
-For example, in Figures 1C,D,G,H, tendency for polyandry allele values are typically less than zero, reflecting evolution of monandry, and inbreeding fertilisation strategy allele values were not as negative as they were in simulations with fixed random mating (Figure 3).
+For example, in Figures 1C,D,G,H, tendency for polyandry allele values were typically less than zero, reflecting evolution of monandry, and inbreeding fertilisation strategy allele values were not as negative as they were in simulations with fixed random mating (Figure 3).
 In general, when females were unable to avoid mating with relatives given severe inbreeding depression ($\beta=3$), selection for evolution of polyandry and post-copulatory inbreeding avoidance was strengthened.
@@
 A weak effect is discernable in the contrast between Figure 2B and Figure 1B, in which the grand mean inbreeding mating strategy allele value is $-0.627$ when inbreeding fertilisation strategy is not fixed (Figure 1B) versus $-1.036$ when it is fixed (Figure 2B) in generation 10000.
-Because females have 20 alleles with additive effects on inbreeding mating strategy, an average female is therefore expected to have mean inbreeding mating strategy phenotype values of $M_{p} = -0.627 \times 20 = -12.54$ and $M_{p} = -1.036 \times 20 = -20.72$ for not fixed versus fixed inbreeding fertilisation strategy, respectively.
+Because females have 20 alleles with additive effects on inbreeding mating strategy, an average female was therefore expected to have mean inbreeding mating strategy phenotype values of $M_{p} = -0.627 \times 20 = -12.54$ and $M_{p} = -1.036 \times 20 = -20.72$ for not fixed versus fixed inbreeding fertilisation strategy, respectively.
 These values would cause an outbred focal female to be $2.135$ and $4.180$ times more likely to choose a non-relative than a full sibling as a mate given not fixed versus fixed inbreeding fertilisation strategy, respectively.
@@
 
-A low relative cost for one inbreeding strategy (e.g., pre-copulatory inbreeding avoidance) did not preclude a more costly complementary inbreeding strategy from persisting in a focal population (Figure 1), meaning that evolution of both pre- and post-copulatory inbreeding avoidance might be expected in populations despite cost asymmetry.
-However, existence of costs strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies.
+A low relative cost for one inbreeding strategy (e.g., pre-copulatory inbreeding avoidance) precluded a more costly complementary inbreeding strategy from persisting in a focal population (Figure 1), meaning that long-term persistence of both pre- and post-copulatory inbreeding avoidance might not be expected in populations given cost asymmetry.
+Direct costs therefore strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies.
 Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging [@Pomiankowski1987; @Kokko2003; @Reid2015].

### 2016-09-19 analysis.R
Add Supporting Figure showing polyandry phenotype in last generation

@@ -33,9 +33,9 @@ sPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=sd);
 sEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=sd);
 xxx <- tapply(X=evo[,6],INDEX=evo[,6],FUN=mean);
 len <- dim(evo)[1];
-plot(x=xxx,y=mWP,type="l",lwd=2,ylim=c(-24,4),col="blue",xaxt="n",
+plot(x=xxx,y=mWP,type="l",lwd=2,ylim=c(-24,14),col="blue",xaxt="n",
      xlab="",ylab="",cex.lab=2,cex.axis=1.5,yaxt="n");
-axis(side=2,at=c(-20,-10,0), cex.axis=1.5);
+axis(side=2,at=c(-20,-10,0,10), cex.axis=1.5);
 axis(side=1,at=c(0,10000,20000,30000), cex.axis=1.5);
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 points(x=xxx,y=mEP,type="l",lwd=2,col="black");
@@ -53,8 +53,8 @@ points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 points(x=xxx,y=mWP,type="l",lwd=2,col="blue");
 text(x=0, y=-18.0, label=expression(paste(c[M]==0.00)),cex=1, pos=4);
-text(x=0, y=-20.0, label=expression(paste(c[P]==0.01)),cex=1, pos=4);
-text(x=0, y=-22.0, label=expression(paste(c[F]==0.00)),cex=1, pos=4);
+text(x=0, y=-21.0, label=expression(paste(c[P]==0.01)),cex=1, pos=4);
+text(x=0, y=-24.0, label=expression(paste(c[F]==0.00)),cex=1, pos=4);
 mtext(expression(paste("Generation")),
 	outer=TRUE,side=1,line=3.0,cex=1.5);
 mtext(expression(paste("Mean allele value")),
@@ -84,9 +84,9 @@ sPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=sd);
 sEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=sd);
 xxx <- tapply(X=evo[,6],INDEX=evo[,6],FUN=mean);
 len <- dim(evo)[1];
[…]

### 2016-09-19 initial_analysis.R

@@ -12102,6 +12102,163 @@ dev.off();
 
 
 
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
[…]

### 2016-09-19 initial_analysis.R
Draft of 4 by 4 plot of individual sims and correlations

@@ -12221,15 +12221,105 @@ axis(side=1,at=c(0,10000,20000,30000), cex.axis=1.5);
 
 
 
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 
+gens     <- 39999;
+beta_val <- 3;
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX SUPPORTING INFORMATION FOR P00 M00 F00 SIMULATIONS  XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# ------------------------------------------------------------------------#
+evo_cc_02 <- read.table(file="results/fig2/evo_M00_P00_F00_a.txt", header=FALSE);
[…]

### 2016-09-20 analysis.R
Tweaks to four panel SI figure, add a second for different parameter combinations

@@ -441,5 +441,186 @@ evo_bel_phn <- as.character(round(x=mean(pedbe[,11]),digits=3));
 text(x=mean(pedbe[,11])+0.4,y=2.5,labels=evo_bel_phn,cex=0.8);
 dev.off();
 
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+
+gens     <- 39999;
+beta_val <- 3;
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX SUPPORTING INFORMATION FOR P00 M00 F00 SIMULATIONS  XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# ------------------------------------------------------------------------#
+evo_cc_02 <- read.table(file="results/fig2/evo_M00_P00_F00_a.txt", header=FALSE);
+evB <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
+evo <- evB[evB[,2]==beta_val,]; 
+c_WP_PO <- rep(x=0, times=gens);
+c_WP_EP <- rep(x=0, times=gens);
+c_PO_EP <- rep(x=0, times=gens);
+for(i in 0:gens){ # XXX XXX  NOTE: THIS LOOP TAKES A LONG TIME TO RUN XXX #
+    use          <- evo[evo[,6]==i,];
+    c_WP_PO[i+1] <- cor(use[,7],use[,8]);
+    c_WP_EP[i+1] <- cor(use[,7],use[,9]);
+    c_PO_EP[i+1] <- cor(use[,8],use[,9]);
+    if(i %% 1000 == 0){
+        print(paste("Generation ",i));
+    }
+}
+
+xxx  <- 0:gens;
+sims <- unique(evo_cc_02[,1]);
+# ------------------------------------------------------------------------#
+setEPS(); # postscript below for final publication?
[…]

### 2016-09-20 analysis.R
Add a third parameter combination for supporting information.

@@ -514,11 +514,11 @@ axis(side=1,at=c(0,10000,20000,30000), cex.axis=1.5);
 text(x=-900, y=27.0, label="C", cex=2, pos=4);
 # ----------------------------------------------------------------
 par(lwd=2);
-plot(x=xxx,y=c_WP_PO,type="l",lwd=1,ylim=c(-1,1),col="black",xaxt="n",yaxt="n",
+plot(x=xxx,y=c_WP_PO,type="l",lwd=1,ylim=c(-1,1),col="purple",xaxt="n",yaxt="n",
      xlab="",ylab="",cex.lab=2,cex.axis=1.5, lty="solid");
 axis(side=4,at=c(-1,-0.5,0,0.5,1), cex.axis=1.5);
-points(x=xxx,y=c_WP_EP,type="l",lwd=1,col="green",lty="solid");
-points(x=xxx,y=c_PO_EP,type="l",lwd=1,col="orange",lty="solid");
+points(x=xxx,y=c_WP_EP,type="l",lwd=1,col="royalblue4",lty="solid");
+points(x=xxx,y=c_PO_EP,type="l",lwd=1,col="red4",lty="solid");
 abline(h=0,lwd="0.8",lty="dotted");
 text(x=-300, y=0.88, label="D", cex=2, pos=4);
 axis(side=1,at=c(0,10000,20000,30000), cex.axis=1.5);
@@ -600,11 +600,11 @@ axis(side=1,at=c(0,10000,20000,30000), cex.axis=1.5);
 text(x=-900, y=27.0, label="C", cex=2, pos=4);
 # ----------------------------------------------------------------
 par(lwd=2);
-plot(x=xxx,y=c_WP_PO,type="l",lwd=1,ylim=c(-1,1),col="black",xaxt="n",yaxt="n",
+plot(x=xxx,y=c_WP_PO,type="l",lwd=1,ylim=c(-1,1),col="purple",xaxt="n",yaxt="n",
      xlab="",ylab="",cex.lab=2,cex.axis=1.5, lty="solid");
 axis(side=4,at=c(-1,-0.5,0,0.5,1), cex.axis=1.5);
-points(x=xxx,y=c_WP_EP,type="l",lwd=1,col="green",lty="solid");
-points(x=xxx,y=c_PO_EP,type="l",lwd=1,col="orange",lty="solid");
+points(x=xxx,y=c_WP_EP,type="l",lwd=1,col="royalblue4",lty="solid");
[…]

### 2016-09-20 ms_pre_post.Rmd
Fix Discussion numbering

@@
 Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging [@Pomiankowski1987; @Kokko2003; @Reid2015].
-@Pomiankowski1987 categorised four types of costs that are relevant to mate choice, which we suggest are also relevant costs for polyandry, and include costs of elevated risks associated with (1) predation or (2) disease transmission, and costs incurred through loss of time (3) or depletion of energy (4).
+@Pomiankowski1987 categorised four types of costs that are relevant to mate choice, which we suggest are also relevant costs for polyandry, and include costs of elevated risks associated with (1) predation or (2) disease transmission, and costs incurred through (3) loss of time or (4) depletion of energy.
 In our model, we interpreted a cost of tendency for polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of inbreeding mating strategy as a lost of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of inbreeding fertilisation strategy as depletion of energy.

### 2016-09-20 ms_pre_post.Rmd
Fix Abstract

@@
 - \bibliographystyle{amnatnat}
-linestretch: 2
+linestretch: 1
 csl: evolution.csl
@@
 Critically, evolution of post-copulatory inbreeding avoidance is restricted to females that mate multiply, potentially leading to complex evolutionary dynamics among inbreeding strategies and polyandry.
-Accordingly, use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address four questions: (1) Will evolution of post-copulatory inbreeding avoidance strengthen selection for polyandry?
+Accordingly, we use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address four questions: (1) Will evolution of post-copulatory inbreeding avoidance strengthen selection for polyandry?
 (2) Will selection for one costly inbreeding strategy be negligible given a non-costly complementary strategy?
@@
 We show that evolution of polyandry is greatly facilitated by evolution of post-copulatory inbreeding avoidance.
-Costs and constraints on pre-copulatory inbreeding avoidance generally affected evolution of post-copulatory inbreeding avoidance, but not vice versa.
+Costs and constraints on pre-copulatory inbreeding avoidance generally affected evolution of post-copulatory inbreeding avoidance, and vice versa.
 Our model thereby introduces a novel framework for predicting evolution of both pre-copulatory and post-copulatory inbreeding strategies in empirical systems.
@@
 
-\vspace{70 mm}
+\vspace{80 mm}
 

### 2016-09-21 analysis.R
Open new concatenated files with 40 replicates instead of old files with 20 replicates

@@ -73,7 +73,7 @@ setEPS(); # postscript below for final publication?
 cairo_ps("figures/evo_combs.eps",family="Arial",height=8,width=5.5);
 par(mfrow=c(4,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
 # ------------------------------------------------------------------------#
-evo_cc_02 <- read.table(file="results/fig2/evo_M00_P00_F00_a.txt", header=FALSE);
+evo_cc_02 <- read.table(file="results/fig2/evo_M00_P00_F00.txt", header=FALSE);
 evB <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
 evo <- evB[evB[,2]==beta_val,];
 mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
@@ -108,7 +108,7 @@ text(x=0, y=-24.0, label=expression(paste(c[F]==0.00)),cex=1, pos=4);
 text(x=-300, y=11.0, label="A", cex=2, pos=4);
 rm(evo_cc_02);
 # ------------------------------------------------------------------------#
-evo_cc_02 <- read.table(file="results/fig2/evo_M02_P00_F00_a.txt", header=FALSE);
+evo_cc_02 <- read.table(file="results/fig2/evo_M02_P00_F00.txt", header=FALSE);
 evB <- evo_cc_02[evo_cc_02[,3]==0.02 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
 evo <- evB[evB[,2]==beta_val,]; 
 mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
@@ -142,7 +142,7 @@ text(x=0, y=-24.0, label=expression(paste(c[F]==0.00)),cex=1, pos=4);
 text(x=-300, y=11.0, label="B", cex=2, pos=4);
 rm(evo_cc_02);
 # ------------------------------------------------------------------------#
-evo_cc_02 <- read.table(file="results/fig2/evo_M00_P02_F00_a.txt", header=FALSE);
+evo_cc_02 <- read.table(file="results/fig2/evo_M00_P02_F00.txt", header=FALSE);
[…]

### 2016-09-21 analysis.R
Supporting Information: Open new concatenated files with 40 replicates instead of old files with 20 replicates

@@ -396,7 +396,7 @@ setwd("~/Dropbox/DuthieManu/pre_post_cop");
 gens      <- 39999;
 beta_val  <- 3;
 
-evo_cc_02 <- read.table(file="results/fig2/evo_M00_P02_F00_a.txt", header=FALSE);
+evo_cc_02 <- read.table(file="results/fig2/evo_M00_P02_F00.txt", header=FALSE);
 evgens <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0.02 & evo_cc_02[,5]==0,];
 evlast <- evgens[evgens[,6]==gens,]; 
 above1 <- which(evlast[,8] == min(evlast[(evlast[,8]-1)>0,8]))[1];
@@ -404,7 +404,7 @@ below1 <- which(evlast[,8] == max(evlast[(evlast[,8]-0)<0,8]))[1];
 simabo <- evlast[above1,1];
 simbel <- evlast[below1,1];
 
-ped_cc_02 <- read.table(file="results/fig2/ped_M00_P02_F00_a.txt", header=FALSE);
+ped_cc_02 <- read.table(file="results/fig2/ped_M00_P02_F00.txt", header=FALSE);
 xxx <- 0:gens;
 
 setEPS(); # postscript below for final publication?
@@ -451,7 +451,7 @@ beta_val <- 3;
 # XXX SUPPORTING INFORMATION FOR P00 M00 F00 SIMULATIONS  XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # ------------------------------------------------------------------------#
-evo_cc_02 <- read.table(file="results/fig2/evo_M00_P00_F00_a.txt", header=FALSE);
+evo_cc_02 <- read.table(file="results/fig2/evo_M00_P00_F00.txt", header=FALSE);
 evB <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
 evo <- evB[evB[,2]==beta_val,]; 
 c_WP_PO <- rep(x=0, times=gens);
@@ -540,7 +540,7 @@ dev.off();
 # XXX SUPPORTING INFORMATION FOR P00 M02 F00 SIMULATIONS  XXX XXX XXX XXX #
[…]

### 2016-09-22 ms_pre_post.Rmd
Change title: First of many changes following internal review
Shorten introduction, four paragraphs, third might still need work

@@
 ---
-title: 'Evolution of pre-copulatory and post-copulatory inbreeding behaviour: a computational
-  approach'
+title: 'Evolution of pre-copulatory and post-copulatory inbreeding behaviour'
 author: "A. Bradley Duthie et al."
@@
 
-Reproductive decisions expressed among interacting individuals directly affect individual fitnesses and the genotypes and viabilities of resulting offspring, and thereby profoundly affect evolutionary dynamics through the differential inheritence of alleles over generations [@Pizzari2012; @Wright2013; @Wild2014; @Liao2015; @Reid2016].
+<!--- Reproductive decisions expressed among interacting individuals directly affect individual fitnesses and the genotypes and viabilities of resulting offspring, and thereby profoundly affect evolutionary dynamics through the differential inheritence of alleles over generations [@Pizzari2012; @Wright2013; @Wild2014; @Liao2015; @Reid2016].
 For example, how frequently a focal female mates is a reproductive decision that can directly and indirectly affect her fitness, and potentially alter the distribution of genotypes and patterns of inheritence within a population [e.g., @Cornell2007; @Diaz2010; @Okada2015; @Roberts2015a; @Worthington2016].
@@
 However, no general modelling framework predicts the conditions under which female mating frequency, pre-copulatory choice, and post-copulatory choice evolve together, meaning that there are no formal hypotheses for predicting the relevance of these reproductive decisions across different biological systems.
+--->
 
-Inbreeding, defined as breeding between relatives, directly affects inheritence of identical-by-descent alleles and the viability of inbred offspring, meaning that the decision to prefer, avoid, or tolerate (i.e., mate randomly with respect to relatedness) inbreeding is predicted to have profound effects on individual fitness [@Parker2006; @Kokko2006; @Szulkin2012; @Duthie2015a].
+Polyandry, defined as female multiple mating within a single reproductive bout, is a reproductive strategy that simultaneously allows females to choose multiple mates and creates the opportunity for further cryptic choice enacted through post-copulatory mechanisms.
+One key choice for females is the decision to prefer, avoid, or tolerate breeding with relatives ['inbreeding'; @Szulkin2012].
+Inbreeding often reduces the fitness of inbred offspring [@Charlesworth1999; @Keller2002; @Charlesworth2009], and polyandry has been widely hypothesised to evolve as an adaptation to allow females to reduce their inbreeding and therefore produce higher fitness offspring [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007].
+In a recent model, @Duthie showed that selection for alleles underlying polyandry and pre-copulatory inbreeding avoidance occurred only under highly constrained conditions in which direct costs of polyandry were low, and when very few males were available during a female's initial mate choice but many males were available during a female's additional mate choice(s), or when polyandry was conditionally expressed based on the degree to which a focal female engaged in inbreeding given her initially chosen mate.
+In the absence of these constraints, expression of polyandry was expected to increase inbreeding with each additional mate because remaining males were more likely to be relatives once available non-relatives were chosen.
+However, @Duthie assumed that polyandrous females had no control over the assignment of paternity to their offspring.
+If after engaging in polyandry, females could bias paternity through post-copulatory mechanisms, then selection for polyandry to avoid inbreeding might be more widely predicted when inbreeding depression is severe [@Zeh1997].
+
+<!--- I fear we're starting down a rabbit hole here. ---> 
+Severe inbreeding depression might cause selection for alleles underlying active pre- and post-copulatory inbreeding avoidance and associated polyandry, but if evolution of one strategy renders its complement redundant for avoiding inbreeding, then selection might instead be sustained over generations for only one strategy.
+Empirical studies of multiple species have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013; @Fischer2015], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009].
+Further, evidence of both pre-copulatory and post-copulatory inbreeding avoidance has been found for a handful of well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015], while @Liu2014 found evidence for pre-copulatory, but not post-copulatory, inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*).
+These empirical studies demonstrate that all combinations of adaptive pre-copulatory and post-copulatory inbreeding avoidance are possible, but no conceptual framework exists to predict *a priori* what combinations should be favoured by selection when both pre- and post-copulatory inbreeding avoidance, and polyandry, can evolve.
+Frequencies of alleles underlying active pre- and post-copulatory inbreeding avoidance and polyandry are likely to be affected by direct negative selection on phenotypes (i.e., costs).
+For example, females that are genetically predisposed to polyandry often pay a cost associated with searching or making themselves available to mates, thereby increasing their own risk of predation [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
+Females that express pre-copulatory choice (e.g., reluctance to mate with relatives) might pay a cost of increased risk of mating failure, or harm caused by sexual conflict [@Rowe1994; @Kokko2013].
+Females that express post-copulatory choice might pay an energetic cost associated with physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
+If the relative costs affecting pre- and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly inbreeding strategy might become fixed in the population over generations, while alleles underlying the more costly inbreeding strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
+
+In addition to the relative importance of costs, evolution of pre- or post-copulatory inbreeding avoidance might be precluded if inbreeding avoidance is already acheived through a complementary strategy.
+Initial evolution of pre- and post-copulatory inbreeding avoidance strategies is unlikely to be simultaneous, so to predict evolutionary outcomes, it is necessary to consider evolution when one inbreeding avoidance strategy is initially rare, and the other strategy is common.
+For example, if pre-adaptation or rapid selection resulted in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect that such invading alleles had on decreasing total inbreeding avoidance would be weak or nelgigible.
+
+<!--- It is therefore necessary to consider evolution of inbreeding mating strategy and inbreeding fertilisation strategy when each evolves in a population where its complementary inbreeding strategy is evolutionarily constrained or already fixed as an adaptation.
+--->
+
+<!--- Overall, to predict evolution of polyandry and inbreeding strategies, it is therefore necessary to model costs associated with polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
+--->
+
+<!--- Inbreeding, defined as breeding between relatives, directly affects inheritence of identical-by-descent alleles and the viability of inbred offspring, meaning that the decision to prefer, avoid, or tolerate (i.e., mate randomly with respect to relatedness) inbreeding is predicted to have profound effects on individual fitness [@Parker2006; @Kokko2006; @Szulkin2012; @Duthie2015a].
 Viability of inbred offspring typically decreases with increasing relatedness between parents [termed 'inbreeding depression'; @Keller2002; @Charlesworth2009].
@@
 However, models of inbreeding do not consider pre-copulatory inbreeding strategy (hereafter 'inbreeding mating strategy') and post-copulatory inbreeding strategy (hereafter 'inbreeding fertilisation strategy') jointly, meaning that it is unclear when selection for either or both strategies is predicted in empirical systems.
+--->
 
-Critically, evolution of inbreeding fertilisation strategy is precluded if females only mate with one male, meaning that evolution of polyandry (defined as female multiple mating within a single reproductive bout) is intrinsically tied to female inbreeding fertilisation strategy.
+<!--- Critically, evolution of inbreeding fertilisation strategy is precluded if females only mate with one male, meaning that evolution of polyandry (defined as female multiple mating within a single reproductive bout) is intrinsically tied to female inbreeding fertilisation strategy.
 Although polyandry is commonplace in wild populations, the regularity with which it is observed in the wild remains theoretically puzzling because engaging in polyandry does not necessarily increase the number of offspring that a female produces, meaning that the fitness benefits associated with polyandry are not always clear [@Parker2013; @Taylor2014].
 It has been hypothesised that females can acheive a net fitness benefit if polyandry provides them with additional opportunities to adjust their inbreeding through copulations with additional males [e.g., @Tregenza2002; @Akcay2007; @Lehtonen2015].
-@Duthie showed that selection for polyandry to facilitate inbreeding avoidance is sometimes predicted, but only under highly constrained conditions in which very few males are available during a female's initial mate choice but many males are available during a female's additional mate choice(s), or when polyandry is conditionally expressed based on the degree to which a focal female engaged in inbreeding given her initially chosen mate.
-However, @Duthie assumed that polyandrous females had no control over the assignment of paternity to their offspring.
-If after engaging in polyandry, females could bias paternity toward non-relatives, then selection for polyandry to avoid inbreeding might be more widely predicted [@Zeh1997].
 However, no models quantify the degree to which expression of biased paternity resulting from evolving inbreeding fertilisation strategy can feedback to drive evolution of polyandry in populations of potentially inbreeding females and males with biologically realistic distributions of relatedness.
+--->
 
-Evolution of inbreeding fertilisation strategy might increase selection for polyandry, but evolutionary feedbacks between inbreeding fertilisation strategy and polyandry might also be contingent upon evolution of inbreeding mating strategy, thereby leading to complex evolutionary dynamics between inbreeding strategies and polyandry.
+<!--- Evolution of inbreeding fertilisation strategy might increase selection for polyandry, but evolutionary feedbacks between inbreeding fertilisation strategy and polyandry might also be contingent upon evolution of inbreeding mating strategy, thereby leading to complex evolutionary dynamics between inbreeding strategies and polyandry.
 For example, if females can acheive their desired degree of inbreeding through mate choice alone, then subsequent polyandry and inbreeding fertilisation strategy might be superfluous for increasing female fitness.
@@
 However, no models predict *a priori* which of these inbreeding strategies should be observed when inbreeding depression is sufficiently severe to make inbreeding avoidance adaptive.
+--->
 
-Evolution of polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy will ultimately be determined by the, potentially interacting, fitness benefits and costs of each phenotype.
+<!--- Evolution of polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy will ultimately be determined by the, potentially interacting, fitness benefits and costs of each phenotype.
 Given severe inbreeding depression, phenotypes will increase a focal female's fitness if they cause her to avoid breeding with close relatives [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
-However, evolution of phenotypes will also be directly affected by negative selection (i.e., costs) associated with the tendency to engage in polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
-For example, females with a tendency to engage in polyandry might pay a cost associated with searching or making themselves available to mates, thereby increasing their own risk of predation [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
-Females that are particularly choosy in mating interactions (e.g., especially reluctant to mate with relatives) might pay a cost of increased risk of mating failure, or harm caused by sexual conflict [@Rowe1994; @Kokko2013].
-Females that are choosy after mating has occurred might pay an energetic cost associated with physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
-Overall, to predict evolution of polyandry and inbreeding strategies, it is therefore necessary to model costs associated with polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
+However,  --->
 
-Selection for inbreeding mating strategy versus inbreeding fertilisation strategy and associated polyandry might also depend evolutionary constraints, or on existing phenotypes in the population.
+<!--- Selection for inbreeding mating strategy versus inbreeding fertilisation strategy and associated polyandry might also depend evolutionary constraints, or on existing phenotypes in the population.
 For example, if phenotypes biasing fertilisation to avoid inbreeding are precluded by evolutionary constraints [@Bradshaw1991; @Futuyma2010], then inbreeding avoidance might only be possible before copulation occurs, perhaps strengthening selection for inbreeding mating strategy and weakening selection for polyandry.
@@
 Selection for inbreeding mating or fertilisation strategy might also be weak or negligible if the strategy is redundant due to the presence of an already established adaptive inbreeding strategy (e.g., if females already successfully avoid inbreeding during mate encounters, then they might be unable to increase their fitness further by biasing fertilisation after mating has occurred).
-It is therefore necessary to consider evolution of inbreeding mating strategy and inbreeding fertilisation strategy when each evolves in a population where its complementary inbreeding strategy is evolutionarily constrained or already fixed as an adaptation.
+--->
 
@@
 
-Studies of multiple species have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013; @Fischer2015], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009].
+<!--- Studies of multiple species have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013; @Fischer2015], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009].
 Further, evidence of both pre-copulatory and post-copulatory inbreeding avoidance has been found for a handful of well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015], while @Liu2014 found evidence for pre-copulatory, but not post-copulatory, inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*).
@@
 Here we have shown that evolution of inbreeding strategies and associated polyandry are predicted to be affected by direct costs, and constraints and adaptations of complementary inbreeding strategies.
+--->
 

### 2016-09-22 analysis.R
Fixed cost text on figure, add new figure

@@ -396,7 +396,7 @@ setwd("~/Dropbox/DuthieManu/pre_post_cop");
 gens      <- 39999;
 beta_val  <- 3;
 
-evo_cc_02 <- read.table(file="results/fig2/evo_M00_P02_F00.txt", header=FALSE);
+evo_cc_02 <- read.table(file="results/fig2/evo_M00_P02_F00_b.txt", header=FALSE);
 evgens <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0.02 & evo_cc_02[,5]==0,];
 evlast <- evgens[evgens[,6]==gens,]; 
 above1 <- which(evlast[,8] == min(evlast[(evlast[,8]-1)>0,8]))[1];
@@ -404,7 +404,7 @@ below1 <- which(evlast[,8] == max(evlast[(evlast[,8]-0)<0,8]))[1];
 simabo <- evlast[above1,1];
 simbel <- evlast[below1,1];
 
-ped_cc_02 <- read.table(file="results/fig2/ped_M00_P02_F00.txt", header=FALSE);
+ped_cc_02 <- read.table(file="results/fig2/ped_M00_P02_F00_b.txt", header=FALSE);
 xxx <- 0:gens;
 
 setEPS(); # postscript below for final publication?
@@ -715,7 +715,7 @@ dev.off();
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
-# XXX SUPPORTING INFORMATION FOR P02 M00 F00 SIMULATIONS  XXX XXX XXX XXX #
+# XXX SUPPORTING INFORMATION FOR P00 M00 F02 SIMULATIONS  XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # ------------------------------------------------------------------------#
 evo_cc_02 <- read.table(file="results/fig2/evo_M00_P00_F02.txt", header=FALSE);
@@ -803,5 +803,184 @@ mtext(expression(paste("Mean allele value correlation\t\t\t\t\t\t")),
 dev.off();
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 
[…]

### 2016-09-22 ms_pre_post.Rmd
New abstract and tweaks to Introduction

@@
 Inbreeding avoidance has been widely observed through pre-copulatory and post-copulatory mechanisms as a consequence of inbreeding depression in offspring viability.
-However, no models compare evolution of pre-copulatory and post-copulatory inbreeding avoidance jointly, and given biologically relevant costs of, and constraints on, inbreeding strategies.
+However, no conceptual framework compares evolution of pre-copulatory and post-copulatory inbreeding avoidance jointly, and given biologically relevant costs of inbreeding strategies.
 Critically, evolution of post-copulatory inbreeding avoidance is restricted to females that mate multiply, potentially leading to complex evolutionary dynamics among inbreeding strategies and polyandry.
-Accordingly, we use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address four questions: (1) Will evolution of post-copulatory inbreeding avoidance strengthen selection for polyandry?
-(2) Will selection for one costly inbreeding strategy be negligible given a non-costly complementary strategy?
-(3) Will constraints on evolution of one inbreeding strategy increase selection on an alternative strategy?
-And (4) will selection for one inbreeding strategy be negligible given existence of an already adaptive alternative strategy?
-We show that evolution of polyandry is greatly facilitated by evolution of post-copulatory inbreeding avoidance.
-Costs and constraints on pre-copulatory inbreeding avoidance generally affected evolution of post-copulatory inbreeding avoidance, and vice versa.
+Accordingly, we use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address three questions: Will evolution of post-copulatory inbreeding avoidance strengthen selection for polyandry?
+Will selection for one costly inbreeding strategy be negligible given a non-costly complementary strategy?
+And will selection for one inbreeding strategy be negligible given existence of an already adaptive alternative strategy?
+We show that evolution of polyandry is greatly facilitated by post-copulatory inbreeding avoidance.
+Strong selection for relatively low cost inbreeding avoidance strategies was observed, while selection for functionally redundant high cost strategies decreased over generations.
+Finally, existence of an adaptive inbreeding strategy precluded evolution of post-copulatory, but not pre-copulatory, inbreeding avoidance.
 Our model thereby introduces a novel framework for predicting evolution of both pre-copulatory and post-copulatory inbreeding strategies in empirical systems.
@@
 Empirical studies of multiple species have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013; @Fischer2015], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009].
-Further, evidence of both pre-copulatory and post-copulatory inbreeding avoidance has been found for a handful of well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015], while @Liu2014 found evidence for pre-copulatory, but not post-copulatory, inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*).
+Further, evidence of both pre-copulatory and post-copulatory inbreeding avoidance has been found for a handful of well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015], while @Liu2014 found evidence for pre-copulatory, but not post-copulatory, inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*).
 These empirical studies demonstrate that all combinations of adaptive pre-copulatory and post-copulatory inbreeding avoidance are possible, but no conceptual framework exists to predict *a priori* what combinations should be favoured by selection when both pre- and post-copulatory inbreeding avoidance, and polyandry, can evolve.
@@
 In addition to the relative importance of costs, evolution of pre- or post-copulatory inbreeding avoidance might be precluded if inbreeding avoidance is already acheived through a complementary strategy.
-Initial evolution of pre- and post-copulatory inbreeding avoidance strategies is unlikely to be simultaneous, so to predict evolutionary outcomes, it is necessary to consider evolution when one inbreeding avoidance strategy is initially rare, and the other strategy is common.
-For example, if pre-adaptation or rapid selection resulted in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect that such invading alleles had on decreasing total inbreeding avoidance would be weak or nelgigible.
+Previous models considered the fate of a rare allele underlying inbreeding avoidance in a population initially fixed for random mating [e.g., Duthie and Reid *In press*; @Parker1979; @Parker2006; @Duthie2016].
+Such models thereby isolate the invasion fitness of a single focal strategy, but when multiple strategies affect realised inbreeding, it cannot be assumed that both will invade simultaneously, nor that invasion fitness of one inbreeding strategy will be independent of another.
+For example, if pre-adaptation or rapid selection resulted in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect that such invading alleles had on decreasing total inbreeding avoidance would be weak or negligible.
+To predict evolutionary outcomes, it is therefore necessary to consider evolution when one inbreeding avoidance strategy is initially rare, and the other strategy is common.
+
+<!--- Rubbish: is unlikely to be simultaneous.
+Testing whether or not initially rare alleles underlying inbreeding avoidance can successfully invade a population Even if invasion fitness of alleles underlying inbreeding avoidance are high when mating and fertilisation is random with respect to relatedness, initial invasion of Initial evolution of pre- and post-copulatory inbreeding avoidance strategies is unlikely to be simultaneous, so to predict evolutionary outcomes, it is necessary to consider evolution when one inbreeding avoidance strategy is initially rare, and the other strategy is common.
+For example, if pre-adaptation or rapid selection resulted in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect that such invading alleles had on decreasing total inbreeding avoidance would be weak or negligible.
+--->
 
@@
 Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that inbreeding avoidance through mate choice but not fertilisation bias will evolve when inbreeding mating strategy is less costly than the combined cost of inbreeding fertilisation strategy and tendency for polyandry, while inbreeding avoidance through fertilisation bias but not mate choice will evolve when inbreeding mating strategy is more costly than the combined costs of inbreeding fertilisation strategy and tendency for polyandry.
-Finally, we test the hypothesis that constraints on evolution of one inbreeding strategy (e.g., inbreeding mating strategy) will increase the strength of selection on evolution of a complementary inbreeding strategy (e.g., inbreeding fertilisation strategy), and that evolution of one inbreeding strategy will be precluded if it is introduced into a population that is already fixed for a complementary inbreeding strategy that is adaptive.
+Finally, we test the hypothesis that evolution of one inbreeding strategy will be precluded if it is introduced into a population that is already fixed for a complementary inbreeding strategy that is adaptive.
 We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across reproductive systems with different relative costs and strong inbreeding depression in offspring viability.
+
+<!--- that constraints on evolution of one inbreeding strategy (e.g., inbreeding mating strategy) will increase the strength of selection on evolution of a complementary inbreeding strategy (e.g., inbreeding fertilisation strategy), and that --->
 

### 2016-09-22 ms_pre_post.Rmd
Fix last paragraph of the Introduction

@@
 These empirical studies demonstrate that all combinations of adaptive pre-copulatory and post-copulatory inbreeding avoidance are possible, but no conceptual framework exists to predict *a priori* what combinations should be favoured by selection when both pre- and post-copulatory inbreeding avoidance, and polyandry, can evolve.
+
 Frequencies of alleles underlying active pre- and post-copulatory inbreeding avoidance and polyandry are likely to be affected by direct negative selection on phenotypes (i.e., costs).
@@
 In addition to the relative importance of costs, evolution of pre- or post-copulatory inbreeding avoidance might be precluded if inbreeding avoidance is already acheived through a complementary strategy.
-Previous models considered the fate of a rare allele underlying inbreeding avoidance in a population initially fixed for random mating [e.g., Duthie and Reid *In press*; @Parker1979; @Parker2006; @Duthie2016].
-Such models thereby isolate the invasion fitness of a single focal strategy, but when multiple strategies affect realised inbreeding, it cannot be assumed that both will invade simultaneously, nor that invasion fitness of one inbreeding strategy will be independent of another.
-For example, if pre-adaptation or rapid selection resulted in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect that such invading alleles had on decreasing total inbreeding avoidance would be weak or negligible.
+Previous models considered the fate of a rare allele underlying inbreeding avoidance in a population initially fixed for random mating [e.g., Duthie and Reid *In press*; @Parker1979; @Parker2006; @Duthie].
+Such models thereby isolate the invasion fitness of a single focal strategy, but when multiple distinct strategies affect realised inbreeding, it cannot be assumed that both will invade simultaneously, nor that invasion fitness of one inbreeding strategy will be independent of another.
+For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect that such invading alleles have on decreasing total inbreeding avoidance could be weak or negligible.
 To predict evolutionary outcomes, it is therefore necessary to consider evolution when one inbreeding avoidance strategy is initially rare, and the other strategy is common.
@@
 
-Here we apply a model of female and male reproductive interactions and associated inbreeding depression in offspring viability to quantify evolution of three separate phenotypes including female tendency for polyandry, female pre-copulatory inbreeding strategy (mating strategy), and female post-copulatory inbreeding strategy (fertilisation strategy).
-We use individual-based modelling and *in silico* experiments to test the hypothesis that, given severe inbreeding depression in offspring viability, evolution of inbreeding avoidance through fertilisation bias causes selection for evolution of polyandry.
-Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that inbreeding avoidance through mate choice but not fertilisation bias will evolve when inbreeding mating strategy is less costly than the combined cost of inbreeding fertilisation strategy and tendency for polyandry, while inbreeding avoidance through fertilisation bias but not mate choice will evolve when inbreeding mating strategy is more costly than the combined costs of inbreeding fertilisation strategy and tendency for polyandry.
+<!--- Here we apply a model of female and male reproductive interactions and associated inbreeding depression in offspring viability to quantify evolution of three separate phenotypes including female tendency for polyandry, female pre-copulatory inbreeding strategy (mating strategy), and female post-copulatory inbreeding strategy (fertilisation strategy).
+--->
+
+Here we use individual-based modelling and *in silico* experiments to test the hypothesis that, given severe inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance causes selection for evolution of polyandry.
+Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that selection for pre-copulatory inbreeding avoidance but not post-copulatory inbreeding avoidance will occur when pre-copulatory inbreeding avoidance is less costly than the cost of post-copulatory inbreeding avoidance, while selection for post-copulatory inbreeding avoidance but not pre-copulatory inbreeding avoidance will occur when pre-copulatory inbreeding avoidance is more costly than the cost of post-copulatory inbreeding avoidance.
 Finally, we test the hypothesis that evolution of one inbreeding strategy will be precluded if it is introduced into a population that is already fixed for a complementary inbreeding strategy that is adaptive.

### 2016-09-22 ms_pre_post.Rmd
Edit Model up to model analysis

@@
 After fertilisation, the viability of a focal female's $n$ offspring is decreased by inbreeding depression ($\beta$), and surviving offspring become adults.
-After inbreeding depression in offspring viability, $\rho$ adult male immigrants arrive in the population, then density effects reduce the entire population down to separate female ($K_{f}$) and male ($K_{m}$) carrying capacities Over generations, we record mean values of alleles underlying polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
+After inbreeding depression in offspring viability, $\rho$ adult male immigrants arrive in the population, then density effects reduce the entire population down to separate female ($K_{f}$) and male ($K_{m}$) carrying capacities.
+Over generations, we record mean values of alleles underlying polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
 
@@
 
-Values of phenotypic traits for tendency to engage in polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilistation strategy ($F_{p}$) each have costs, which independently increase the probability of a focal female's reproductive failure.
-These costs are all expressed prior to mating.
-In the case of tendency to engage in polyandry, the cost of $P_{p}$ ($c_{P}$) is interpreted biologically as a cost associated with mate searching or courtship [e.g., @Rowe1988; @Rowe1994; @Ronkainen1994; @Koga1998; @Lasley-Rasher2012].
+<!--- In the case of tendency to engage in polyandry, the cost of $P_{p}$ ($c_{P}$) is interpreted biologically as a cost associated with mate searching or courtship [e.g., @Rowe1988; @Rowe1994; @Ronkainen1994; @Koga1998; @Lasley-Rasher2012].
 For inbreeding mating strategy, the cost of $M_{p}$ ($c_{M}$) is interpreted biologically as a cost associated with risk of mating failure due to females being overly choosy [e.g., @Kokko2013], and for inbreeding fertilisation strategy, the cost of $F_{p}$ ($c_{F}$) is interpreted as an energetic cost associated with the physiological or biochemical mechanisms that need to be developed to bias fertilisation for inbreeding avoidance or inbreeding preference [e.g., @Gasparini2011].
+--->
+
+Values of phenotypic traits for tendency to engage in polyandry ($P_{p}$), pre-copulatory inbreeding strategy (i.e., inbreeding mating strategy, $M_{p}$), and post-copulatory inbreeding strategy (i.e., inbreeding fertilisation strategy, $F_{p}$) each have costs.
 Each cost independently increases the risk of female pre-mating mortality and, because generations are non-overlapping, total reproductive failure as a linear function of its associated trait.
@@
 Hence, negative values of $P_{g}$ are translated to $P_{p}$ values of zero such that $P_{p} = 0$ when $P_{g} < 0$, but when $P_{g} \geq 0$, then $P_{p} = P_{g}$ (i.e., the phenotype value of polyandry equals the genotype value of polyandry if and only if the genotype value is greater than or equal to zero, else the phenotype value of polyandry always equals zero).
-The resulting $P_{p}$ is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998], in which polyandry is expressed discretely at the threshold value of $P_{g} > 0$, but is determined by the consequence of continuous genetic variation arising from the effects of $P_{a}$ alleles that each contribute additively to a female's tendency toward polyandry.
+The resulting $P_{p}$ is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998; @Duthie], in which polyandry is expressed discretely at the threshold value of $P_{g} > 0$, but is determined by the consequence of continuous genetic variation arising from the effects of $P_{a}$ alleles that each contribute additively to a female's tendency toward polyandry.
 Negative genotype values of $P_{g}$ therefore all have the same phenotype, resulting in consistently monandrous females.
@@
 In the unlikely event that a female's $N_{males}$ exceeds the total number of males in the population, then she mates with all of the males in the populaton.
-Most often, $N_{males}$ will be a small subset of the available males in the population [@Duthie], so a focal female will be able to preferentially mate with males that are close kin (high $k$), distant kin (low $k$), or non-kin ($k=0$) through the expression of her inbreeding mating strategy phenotype ($M_{p}$).
-Like polyandry allele values, inbreeding mating strategy allele values ($M_{a}$) can take any real number.
-However, unlike polyandry, the sum of all of a female's 20 $M_{a}$ alleles equals both her inbreeding mating strategy genotype ($M_{g}$) and her inbreeding mating strategy phenotype ($M_{p}$).
+Most often, $N_{males}$ will be a small subset of the available males in the population [@Duthie], so a focal female will be able to preferentially mate with males that are close kin (high $k$), distant kin (low $k$), or non-kin ($k=0$) through the expression of her pre-copulatory inbreeding strategy phenotype ($M_{p}$).
+Like polyandry allele values, pre-copulatory inbreeding strategy allele values ($M_{a}$) can take any real number.
+However, unlike polyandry, the sum of all of a female's 20 $M_{a}$ alleles equals both her pre-copulatory inbreeding strategy genotype ($M_{g}$) and her pre-copulatory inbreeding strategy phenotype ($M_{p}$).
 Negative or positive values of $M_{p}$ cause a female to avoid or prefer mating with kin, respectively.
@@
 The fertilisation of a female's $n$ offspring occurs after mating, with each of her $n$ offspring being assigned a sire independently and with replacement from the $N_{males}$ with which the female mated.
-The probability that a male mate successfully sires an offspring is affected by a female's kinship with the potential sire ($k_{ij}$) and her inbreeding fertilisation strategy ($F_{p}$).
-As with polyandry and inbreeding mating strategy phenotypes, a female's inbreeding fertilisation strategy phenotype is determined by the summed effects of 20 inbreeding fertilisation strategy alleles ($F_{a}$), which can take any real number.
-The sum of all of a female's $F_{a}$ alleles determine her inbreeding fertilisation strategy genotype ($F_{g}$), which is identical to her inbreeding strategy phenotype ($F_{p}$).
-As with mating strategy phenotype ($M_{p}$), negative or positive values of $F_{p}$ correspond to inbreeding avoidance or preference respectively, and $F_{p}=0$ causes random fertilisation with respect to kinship.
+The probability that a male mate successfully sires an offspring is affected by a female's kinship with the potential sire ($k_{ij}$) and her post-copulatory inbreeding strategy ($F_{p}$).
+As with polyandry and pre-copulatory inbreeding strategy phenotypes, a female's post-copulatory inbreeding strategy phenotype is determined by the summed effects of 20 post-copulatory inbreeding strategy alleles ($F_{a}$), which can take any real number.
+The sum of all of a female's $F_{a}$ alleles determine her post-copulatory inbreeding strategy genotype ($F_{g}$), which is identical to her post-copulatory inbreeding strategy phenotype ($F_{p}$).
+As with pre-copulatory inbreeding strategy phenotype ($M_{p}$), negative or positive values of $F_{p}$ correspond to inbreeding avoidance or preference respectively, and $F_{p}=0$ causes random fertilisation with respect to kinship.
 
 The probability that an offspring of a focal female $i$ is fertilised by one of $i$'s mates $j$ is calculated by first assigning a perceived fertilisation quality to each $j$, $Q^{f}_{ij}$.
-Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if a focal female has a fertilisation strategy of avoiding inbreeding ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$.
-If instead a focal female has a fertilisation strategy of preferring inbreeding ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$.
+Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if a focal female has a post-copulatory strategy of avoiding inbreeding ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$.
+If instead a focal female has a post-copulatory strategy of preferring inbreeding ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$.
 The perceived qualities of every male that a focal female has mated with are summed, then a relative quality ($q^{f}_{ij}$) is calculated for each male by dividing each individual male mate's $Q^{f}_{ij}$ by this sum.
@@
 The coefficient of kinship between an immigrant and all other individuals (including native individuals and other immigrants) always equals zero ($k_{ij}=0$).
-Because kinship coefficient values are calculated directly from the pedigree of the focal population, the addition of immigrants thereby introduces non-kin into the population at a consistent rate and prevents the mean kinship coefficient of the population from asymptoting to a value of 1 over generations.
+Because kinship coefficient values are calculated directly from the pedigree of the focal population, the addition of immigrants thereby introduces non-kin into the population at a constant rate and prevents the mean kinship coefficient of the population from asymptoting to a value of 1 over generations.
 If the focal population was instead closed ($\rho=0$), then all alleles would quickly be expected to become identical-by-descent among descendants of the ancestral population.
@@
 ----------------------------------------------
+
+<!--- ---------------------------------------------------------------------- --->
+<!--- -------------------- LEFT OFF HERE ----------------------------------- --->
+<!--- ---------------------------------------------------------------------- --->
 

### 2016-09-23 ms_pre_post.Rmd
Revise up through Methods

@@
 To analyse our model, we track mean values of alleles underlying tendency for polyandry ($P_{a}$), inbreeding mating strategy ($M_{a}$), and inbreeding fertilisation strategy ($F_{a}$) in a focal population.
-We present evolutionary dynamics of these mean allele values across different parameter combinations to test our four focal hypotheses (see below).
-We simulate up to eight possible permutations of values of costs of tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$) equal to either $0$ or $0.02$ [@Duthie observed $0.02$ to be a strong cost of tendency for polyandry] for values of $\beta = 3$ ($8$ total combinations).
-In all simulations, we record mean values of $P_{a}$, $M_{a}$, $F_{a}$ in each generation.
-Each combination of parameter values simulated is replicated $40$ times, and grand mean values and standard error of means is calculated in each generation across replicate simulations.
-These analyses allow us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on inbreeding fertilisation strategy might be weak if polyandry is rare).
-For all replicates, we set the maximum number of generations to 10000, which exploratory simulations and previous modelling [@Duthie] showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
-For all replicates, we also set the number of immigrants per generation to $\rho=5$, which produced a range of kin and non-kin in each generation allowing females could express inbreeding strategies.
-Females always produced $n=8$ offspring, which was sufficient to keep populations consistently near carrying capacities and avoid population extinction.
-Carrying capacities for females ($K_{f}$) and males ($K_{m}$) were both set to 100 because previous modelling has shown that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but populations are also not so small that selection is typically overwhelmed by genetic drift (Duthie and Reid *in press*).
+We present evolutionary dynamics of these mean allele values across different parameter combinations to test our three focal hypotheses.
 
-To test our hypothesis that selection for evolution of polyandry is driven by a female's ability to bias fertilisation toward inbreeding avoidance through post-copulatory mechanisms, we compare simulations in which all three phenotypes including tendency for polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilisation strategy ($F_{p}$) evolve, with an identical set of simulations in which $F_{p}$ cannot evolve.
-In simulations without evolving $F_{p}$, we therefore include all $4$ combinations of $c_{P}=\{0,0.02\}$ and $c_{M}=\{0,0.02\}$ (but not $c{F}$).
+To test our hypothesis that selection for polyandry is driven by a female's ability to bias fertilisation toward inbreeding avoidance through post-copulatory mechanisms, we compare simulations in which all three phenotypes including tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory strategy ($F_{p}$) evolve, with an identical set of simulations in which $F_{p}$ cannot evolve given $c_{P} = \{0, 0.0025, 0.005}$.
 To stop $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes resulting from $F_{a}$ cause random fertilisation with respect to kinship (i.e, $F_{p}=0$).
-Hence, while mutation and drift can still occur for $F_{a}$ alleles, these alleles have no phenotypic effect and polyandry cannot cause polyandrous females to benefit through an increased ability to bias fertilisation toward inbreeding avoidance (under such conditions, there can also never be a cost of $F_{p}$, meaning that $c_{F}=0$).
-By comparing evolution of mean $P_{p}$ values over generations when $F_{p}$ also evolves versus when $F_{p}=0$ (random fertilisation), we test whether or not evolution of inbreeding fertilisation strategy increases selection for evolution of polyandry.
+Hence, while mutation and drift can still occur for $F_{a}$ alleles, these alleles have no phenotypic effect and polyandry cannot cause polyandrous females to benefit through an increased ability to bias fertilisation toward inbreeding avoidance.
+By comparing evolution of mean $P_{p}$ values over generations when $F_{p}$ also evolves versus when $F_{p}=0$ (random fertilisation), we test whether or not evolution of post-copulatory inbreeding strategy increases selection for polyandry.
 
-To test hypotheses regarding evolution under different relative costs of phenotypes, we consider all combinations of costs using simulations in which all three traits evolve.
+<!--- We simulate up to eight possible permutations of values of costs of tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$) equal to either $0$ or $0.02$ [@Duthie observed $0.02$ to be a strong cost of tendency for polyandry] for values of $\beta = 3$ ($8$ total combinations).
+--->
+
+<!--- In simulations without evolving $F_{p}$, we therefore include all $4$ combinations of $c_{P}=\{0,0.02\}$ and $c_{M}=\{0,0.02\}$ (but not $c{F}$). --->
+
+<!--- TODO: NEED TO DO THESE SIMULATIONS ASAP --->
+To test the hypothesis that selection for a costly strategy of inbreeding avoidance will be negligible given a less costly alternative strategy, we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where the cost of pre-copulatory inbreeding strategy $c_{M}=0$ but the cost of post-copulatory inbreeding strategy $c_{F}=0.02$, and where $c_{F}=0$ but $c_{M}=0.02$.
+We contrast these simulations with evolution of a costly strategy in the absence of evolution of an alternative strategy (e.g., evolution of pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy phenotype is fixed at zero, $F_{p}=0$).
+A contrast between the baseline expectation for how costs affect evolution of a focal inbreeding strategy in the absence of an alternative strategy, and evolution of a focal strategy given that an alternative strategy also evolves, tests whether or not a relatively low cost alternative strategy decreases selection for a focal strategy.
+
+<!--- To test hypotheses regarding evolution under different relative costs of phenotypes, we consider all combinations of costs using simulations in which all three traits evolve.
 To test the hypothesis that inbreeding mating strategy will evolve toward inbreeding avoidance ($M_{p}<0$) when mating costs are low relative to the costs of tendency for polyandry and inbreeding fertilisation strategy, but that selection for inbreeding fertilisation strategy will then be negligible ($F_{p} \approx 0$), we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where $c_{M}=0$ but $c_{P}$, $c_{F}$, or both equals $0.02$.
@@
 If our hypothesis is supported, then $F_{a}$ but not $M_{a}$ allele values will become more negative over generations when $c_{F}$ is relatively low than when all cost values are uniform.
+--->
 
-To test the hypothesis that constraints on evolution of one inbreeding strategy will increase the strength of selection on a complementary strategy, we fixed inbreeding strategy phenotypes to values of zero, thereby causing either random mating ($M_{p}=0$) or the random fertilisation of offspring ($F_{p}=0$) according to a fair raffle among mates with respect to kinship.
+<!--- To test the hypothesis that constraints on evolution of one inbreeding strategy will increase the strength of selection on a complementary strategy, we fixed inbreeding strategy phenotypes to values of zero, thereby causing either random mating ($M_{p}=0$) or the random fertilisation of offspring ($F_{p}=0$) according to a fair raffle among mates with respect to kinship.
 We then compare evolution of the non-fixed trait to its evolution in simulations where all traits are allowed to evolve.
+--->
 
-To test the hypothesis that the existence of an adaptive inbreeding strategy will decrease the strength of selection on, and thereby preclude the invasion of, a complementary strategy, we first used exploratory simulations to determine evolution of inbreeding mating strategy, and inbreeding fertilisation strategy and associated polyandry, in isolation.
-To test whether or not inbreeding mating avoidance was predicted to evolve when adaptive polyandry to avoid inbreeding was already established, we initiated inbreeding mating strategy allele values at zero ($M_{a}=0$), but fixed inbreeding fertilisation strategy allele values at $F_{a}=-5$ and polyandry allele values at $P_{a}=1$ (i.e., $F_{p}$ and $P_{p}$ did not evolve).
-Similarly, to test whether or not inbreeding fertilisation strategy evolved to avoid inbreeding, we initiated inbreeding fertilisation strategy allele values and polyandry allele values at zero ($F_{a}=0$; $P_{a}=0$), but fixed inbreeding mating strategy allele values at $M_{a}=-5$.
+To test the hypothesis that the existence of an adaptive inbreeding strategy will decrease the strength of selection on, and thereby preclude the invasion of, a complementary strategy, we first used exploratory simulations to determine evolution of precopulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation.
+To test whether or not pre-copulatory inbreeding avoidance was predicted to evolve when adaptive polyandry to avoid inbreeding was already established, we initiated pre-copulatory inbreeding strategy allele values at zero ($M_{a}=0$), but fixed post-copulatory inbreeding allele values at $F_{a}=-10$ and polyandry allele values at $P_{a}=1$ (i.e., $F_{p}$ and $P_{p}$ did not evolve).
+Similarly, to test whether or not inbreeding fertilisation strategy evolved to avoid inbreeding, we initiated inbreeding fertilisation strategy allele values and polyandry allele values at zero ($F_{a}=0$; $P_{a}=0$), but fixed inbreeding mating strategy allele values at $M_{a}=-10$.
+
+In all simulations, we record mean values of $P_{a}$, $M_{a}$, $F_{a}$ in each generation.
+Each combination of parameter values simulated is replicated $40$ times, and grand mean values and standard error of means is calculated in each generation across replicate simulations.
+These analyses allow us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on inbreeding fertilisation strategy might be weak if polyandry is rare).
+For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling [@Duthie] showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
+For all replicates, we set $\rho=5$ immigrants, which produced a range of kin and non-kin in each generation allowing females could express inbreeding strategies, and $n=8$ offspring, which was sufficient to keep populations consistently near carrying capacities and avoid population extinction.
+Values of $K_{f}$ and $K_{m}$ were both set to 100 because previous modelling has shown that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but populations are also not so small that selection is typically overwhelmed by genetic drift (Duthie and Reid *in press*).
 

### 2016-09-23 analysis.R
Add next supporting figure

@@ -20,7 +20,47 @@ beta_val <- 3;
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 setEPS(); # postscript below for final publication?
 cairo_ps("figures/M00_P01_F00.eps",family="Arial",height=6,width=6);
-par(oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
+par(mfrow=c(3,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
+# XXX -----> TODO: CHANGE THE BELOW to P00 text.
+# ------------------------------------------------------------------------#
+evo_cc_02 <- read.table(file="results/fig1/evo_M00_P01_F00_ko.txt", header=FALSE);
+evB <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0.01 & evo_cc_02[,5]==0,];
+evo <- evB[evB[,2]==beta_val,];
+mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
+mPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=mean);
+mEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=mean);
+sWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=sd);
+sPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=sd);
+sEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=sd);
+xxx <- tapply(X=evo[,6],INDEX=evo[,6],FUN=mean);
+len <- dim(evo)[1];
+plot(x=xxx,y=mWP,type="l",lwd=2,ylim=c(-24,14),col="blue",xaxt="n",
+     xlab="",ylab="",cex.lab=2,cex.axis=1.5,yaxt="n");
+axis(side=2,at=c(-20,-10,0,10), cex.axis=1.5);
+axis(side=1,at=c(0,10000,20000,30000), cex.axis=1.5);
+points(x=xxx,y=mPO,type="l",lwd=2,col="red");
+points(x=xxx,y=mEP,type="l",lwd=2,col="black");
+abline(h=0,lwd=0.8,lty="dotted");
+uWP <- mWP + sWP / sqrt(sum(evo[,6]==gens));
+lWP <- mWP - sWP / sqrt(sum(evo[,6]==gens));
[…]

### 2016-09-23 code/PolyIn.c
Add 'no' explanation to condk

@@ -44,7 +44,7 @@ int main(void){
     ImmSD   = 1.0;    /* SD around the mean for immigrant allelic values                  */
     conSt   = 0;      /* Constrain WP & EP avoidance/preference to be equal? (0:no, 1:yes)*/
     wpVsep  = 1;      /* 0: wpe is soc, epe is poly mates | 1: wpe is pre, epe is postcop */ 
-    condk   = 0;      /* Will females reject EPMs if none better than soc? (1:yes)        */
+    condk   = 0;      /* Will females reject EPMs if none better than soc? (1:yes, 0:no)  */
     EpRestr = 0;      /* Restrict additional mate acces? (0: no, >0: Restriction number   */
     WpRestr = 0;      /* Restrict mate access for WP mates? (0: no, >0: Restriction #     */
     PreSel  = 1;      /* Allow pre-copulatory mate selection for EPMs (0: no, 1:yes)      */

### 2016-09-23 code/PolyIn.c
Remove randomised costs

@@ -79,10 +79,6 @@ int main(void){
 
     i    = 0; /* Loops through different replicate simulations */
     prP  = 0; /* Indicator for actually printing the pedigree */
-
-    Scost = randunif()*0.05;
-    Pcost = randunif()*0.05;
-    Ecost = randunif()*0.05;
     
     while(i < rep){
         if(i == rep-1 && Pedi == 1){ /* If it's the last rep, and should print pedigree */

### 2016-09-24 analysis.R
Add last individual sim combination (all costs) supporting figure

@@ -1104,6 +1104,7 @@ dev.off();
 evo_cc_02 <- read.table(file="results/fig2/evo_M02_P00_F02.txt", header=FALSE);
 evB <- evo_cc_02[evo_cc_02[,3]==0.02 & evo_cc_02[,4]==0.00 & evo_cc_02[,5]==0.02,];
 evo <- evB[evB[,2]==beta_val,]; 
+evo <- evo[evo[,1]!=289106184,]; # Got 39 out of this one.
 c_WP_PO <- rep(x=0, times=gens);
 c_WP_EP <- rep(x=0, times=gens);
 c_PO_EP <- rep(x=0, times=gens);
@@ -1122,6 +1123,97 @@ sims <- unique(evo_cc_02[,1]);
 # ------------------------------------------------------------------------#
 setEPS(); # postscript below for final publication?
 cairo_ps("figures/SI_M02_P00_E02.eps",family="Arial",height=7,width=7.5);
+par(mfrow=c(2,2),oma=c(5,5,1,4), mar=c(0.5,0.5,0.5,0.5),lwd=1);
+# ----------------------------------------------------------------
+mPo <- tapply(X=evo[,8],INDEX=evo[,6],FUN=mean);
+plot(x=xxx,y=mPo,type="l",lwd=2,ylim=c(-50,30),col="red",xaxt="n",
+     xlab="",ylab="",cex.lab=2,cex.axis=1.5,yaxt="n");
+for(i in sims){
+ iter <- evo[evo[,1]==i,8];
+ points(x=xxx,y=iter,type="l",lwd=0.5,col="thistle");
+}
+points(x=xxx,y=mPo,type="l",lwd=2,col="red");
+abline(h=0,lwd=0.8,lty="dotted");
+axis(side=2,at=c(-40,-20,0,20),cex.axis=1.5);
+text(x=-900, y=27.0, label="A", cex=2, pos=4);
+#text(x=0, y=-35.0, label=expression(paste(c[M]==0.00)),cex=1.2, pos=4);
+#text(x=0, y=-42.0, label=expression(paste(c[P]==0.02)),cex=1.2, pos=4);
+#text(x=0, y=-49.0, label=expression(paste(c[F]==0.00)),cex=1.2, pos=4);
+text(x=0, y=-47.0, label=expression(paste(c[P]==0.00)),cex=1.5, pos=4);
+# ----------------------------------------------------------------
[…]

### 2016-09-26 analysis.R
Add revised Figure 1 showing all costs and knockouts

@@ -19,9 +19,195 @@ beta_val <- 3;
 # XXX XXX      PLOT FIGURE 1  XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 setEPS(); # postscript below for final publication?
-cairo_ps("figures/M00_P01_F00.eps",family="Arial",height=6,width=6);
-par(mfrow=c(3,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
+cairo_ps("figures/M00_P01_F00.eps",family="Arial",height=8,width=5.5);
+par(mfrow=c(4,2),oma=c(5,5,2,1), mar=c(0.5,0.5,0.5,0.5));
 # XXX -----> TODO: CHANGE THE BELOW to P00 text.
+# ------------------------------------------------------------------------#
+evo_cc_02 <- read.table(file="results/fig1/evo_M00_P00_F00_ko.txt", header=FALSE);
+evB <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0.00 & evo_cc_02[,5]==0,];
+evo <- evB[evB[,2]==beta_val,];
+mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
+mPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=mean);
+mEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=mean);
+sWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=sd);
+sPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=sd);
+sEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=sd);
+xxx <- tapply(X=evo[,6],INDEX=evo[,6],FUN=mean);
+len <- dim(evo)[1];
+plot(x=xxx,y=mWP,type="l",lwd=2,ylim=c(-24,14),col="blue",xaxt="n",
+     xlab="",ylab="",cex.lab=2,cex.axis=1.5,yaxt="n");
+axis(side=2,at=c(-20,-10,0,10), cex.axis=1.5);
+points(x=xxx,y=mPO,type="l",lwd=2,col="red");
+#points(x=xxx,y=mEP,type="l",lwd=2,col="black");
[…]

### 2016-09-26 ms_pre_post.Rmd
Revise Model analysis section

@@
 
-To test our hypothesis that selection for polyandry is driven by a female's ability to bias fertilisation toward inbreeding avoidance through post-copulatory mechanisms, we compare simulations in which all three phenotypes including tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory strategy ($F_{p}$) evolve, with an identical set of simulations in which $F_{p}$ cannot evolve given $c_{P} = \{0, 0.0025, 0.005}$.
+To test our hypothesis that selection for polyandry is driven by a female's ability to bias fertilisation toward inbreeding avoidance through post-copulatory mechanisms, we compare simulations in which all three phenotypes including tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory strategy ($F_{p}$) evolve, with an identical set of simulations in which $F_{p}$ cannot evolve given $c_{P} = \{0, 0.0025, 0.005,  0.01\}$.
 To stop $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes resulting from $F_{a}$ cause random fertilisation with respect to kinship (i.e, $F_{p}=0$).
 Hence, while mutation and drift can still occur for $F_{a}$ alleles, these alleles have no phenotypic effect and polyandry cannot cause polyandrous females to benefit through an increased ability to bias fertilisation toward inbreeding avoidance.
-By comparing evolution of mean $P_{p}$ values over generations when $F_{p}$ also evolves versus when $F_{p}=0$ (random fertilisation), we test whether or not evolution of post-copulatory inbreeding strategy increases selection for polyandry.
+By comparing mean $P_{a}$ values over generations when post-copulatory inbreeding avoidance also evolves versus when fertilisation is random, we test whether or not evolution of post-copulatory inbreeding strategy increases selection for polyandry.
 
@@
 
-<!--- TODO: NEED TO DO THESE SIMULATIONS ASAP --->
 To test the hypothesis that selection for a costly strategy of inbreeding avoidance will be negligible given a less costly alternative strategy, we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where the cost of pre-copulatory inbreeding strategy $c_{M}=0$ but the cost of post-copulatory inbreeding strategy $c_{F}=0.02$, and where $c_{F}=0$ but $c_{M}=0.02$.
@@
 To test whether or not pre-copulatory inbreeding avoidance was predicted to evolve when adaptive polyandry to avoid inbreeding was already established, we initiated pre-copulatory inbreeding strategy allele values at zero ($M_{a}=0$), but fixed post-copulatory inbreeding allele values at $F_{a}=-10$ and polyandry allele values at $P_{a}=1$ (i.e., $F_{p}$ and $P_{p}$ did not evolve).
-Similarly, to test whether or not inbreeding fertilisation strategy evolved to avoid inbreeding, we initiated inbreeding fertilisation strategy allele values and polyandry allele values at zero ($F_{a}=0$; $P_{a}=0$), but fixed inbreeding mating strategy allele values at $M_{a}=-10$.
+Similarly, to test whether or not post-copulatory inbreeding strategy evolved to avoid inbreeding, we initiated post-copulatory inbreeding strategy allele values and polyandry allele values at zero ($F_{a}=0$; $P_{a}=0$), but fixed pre-copulatory inbreeding strategy allele values at $M_{a}=-10$.
+For reference, because females have 10 diploid loci, when $M_{a}$ or $F_{a}$ alleles were fixed at $-10$, outbred females were $51$ times less likely to choose a full sibling and $13.5$ times times less likely to choose a first cousin than a non-relative in pre- and post-copulatory choice, respectively.
 

### 2016-09-26 ms_pre_post.Rmd
Revise first results section

@@
 
-<!--- ---------------------------------------------------------------------- --->
-<!--- -------------------- LEFT OFF HERE ----------------------------------- --->
-<!--- ---------------------------------------------------------------------- --->
-
 To analyse our model, we track mean values of alleles underlying tendency for polyandry ($P_{a}$), inbreeding mating strategy ($M_{a}$), and inbreeding fertilisation strategy ($F_{a}$) in a focal population.
@@
 
-We present our results by showing mean allele value changes over generations.
+<!--- We present our results by showing mean allele value changes over generations.
 Figures 1-5 show mean allele values of tendency for polyandry ($P_{a}$; red lines and shading), inbreeding mating strategy ($M_{a}$; blue lines and shading), and inbreeding fertilisation strategy ($F_{a}$; black lines and shading) over 10000 generations as calculated across all individuals (female and male) within a focal population over 40 replicate simulations with identical starting conditions.
@@
 Supporting Information S1 presents correlations of mean allele values across replicate simulations, which were generally weak; we found no evidence suggesting strong evolutionary divergence among replicates with identical starting conditions (e.g., as might be the case if populations stochastically evolved toward inbreeding avoidance through mate choice or fertilisation, but not both), meaning that inspecting grand means of replicate allele values accurately reflects expected evolutionary dynamics over generations.
+--->
 
@@
 
-We first test our hypothesis that a focal female's ability to bias fertilisation with respect to kinship causes selection for polyandry by comparing simulations in which tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy can all evolve to simulations in which inbreeding fertilisation strategy is fixed to random mating with respect to kinship, as presented in Figures 1 and 2, respectively.
-Comparison of Figures 1 and 2 shows that evolution of inbreeding fertilisation strategy facilitates evolution of polyandry, particularly when costs of tendency for polyandry and inbreeding fertilisation strategy are zero.
+We first test our hypothesis that a focal female's ability to express post-copulatory choice with respect to kinship causes selection for polyandry by comparing simulations in which post-copulatory inbreeding strategy is fixed to random mating with respect to kinship to simulations in which tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy can all evolve.
+The left and right columns of Figure 1 show results for fixed versus evolving post-copulatory choice, respectively, across four rows of costs of tendency for polyandry.
+For low costs of tendency for polyandry, $c_{P} < 0.005$, selection caused expected tendency for polyandry allele values ($P_{a}$) to be positive only when post-copulatory inbreeding avoidance evolved (Figure 1A-D), and for all $c_{P}$, $P_{a}$ values were higher when post-copulatory inbreeding avoidance evolved than when it could not evolve.
+When post-copulatory inbreeding avoidance could not evolve, $P_{a}$ values were negative even in the absence of a direct cost ($c_{P}=0$; Figure 1A) because females that expressed polyandry were more likely to increase their inbreeding due to sampling males without replacement [@Duthie].
+Strong post-copulatory inbreeding avoidance consistently evolved in all simulations, even when $P_{a}$ values were not expected to be positive (Figure 1F,H), because of the threshold nature of the polyandry phenotype; Figure 2 shows how phenotypic polyandry was common even when mean polyandry allele values within a populatoin were expected to be negative.
+In all simulations, pre-copulatory inbreeding avoidance also evolved ($M_{a}<0$), meaning that both pre- and post-copulatory inbreeding avoidance was predicted, and evolution of adaptive polyandry occurred given sufficiently low costs of tendency for polyandry.
+
+<!--- Comparison of Figures 1 and 2 shows that evolution of inbreeding fertilisation strategy facilitates evolution of polyandry, particularly when costs of tendency for polyandry and inbreeding fertilisation strategy are zero.
 For example, in Figure 2A, tendency for polyandry allele values consistently become negative over generations ($P_{a}<0$; decreasing red line), causing populations to be monandrous.
@@
 Evolution of post-copulatory inbreeding avoidance therefore greatly facilitates evolution of polyandry.
+--->
 
@@
 --->
+
+<!--- ---------------------------------------------------------------------- --->
+<!--- -------------------- LEFT OFF HERE ----------------------------------- --->
+<!--- ---------------------------------------------------------------------- --->
 
@@
 
-Selection given constraints on evolution
-----------------------------------------------
+<!--- Selection given constraints on evolution --->
+<!--- ---------------------------------------------- --->
 
-Figure 3 shows evolution of tendency for polyandry and inbreeding fertilisation strategy when inbreeding mating strategy is fixed so that females must mate randomly (blue line at $M_{a}=0$).
+<!--- Figure 3 shows evolution of tendency for polyandry and inbreeding fertilisation strategy when inbreeding mating strategy is fixed so that females must mate randomly (blue line at $M_{a}=0$).
 For all cost combinations of tendency for polyandry and inbreeding fertilisation strategy (Figure 3 panels A-D), we observed selection for positive values of tendency for polyandry alleles and negative values of inbreeding fertilisation strategy alleles, which we interpret as strong evidence for evolution of polyandry and associated inbreeding avoidance through fertiisation bias.
@@
 In general, when females were unable to avoid mating with relatives given severe inbreeding depression ($\beta=3$), selection for evolution of polyandry and post-copulatory inbreeding avoidance was strengthened.
+--->
 
-Figure 2, which we previously contrasted with Figure 1 to test whether or not evolution of inbreeding fertilisation strategy facilitates selection for polyandry, shows evolution of tendency for polyandry and inbreeding mating strategy when inbreeding fertilisation strategy is fixed such that the sire of a focal female's offspring is randomly assigned from her mates according to a fair raffle.
+<!--- Figure 2, which we previously contrasted with Figure 1 to test whether or not evolution of inbreeding fertilisation strategy facilitates selection for polyandry, shows evolution of tendency for polyandry and inbreeding mating strategy when inbreeding fertilisation strategy is fixed such that the sire of a focal female's offspring is randomly assigned from her mates according to a fair raffle.
 In all cost combinations of Figure 2 (panels A-D), tendency for polyandry allele values decreased over generations, reflecting evolution of monandry.
@@
 Therefore, when females were unable to bias fertilisation to avoid inbreeding given severe inbreeding depression ($\beta=3$), selection for evolution of pre-copulatory inbreeding avoidance was strengthened.
+--->
 

### 2016-09-26 analysis.R
Add new Figures 1-2

@@ -52,6 +52,7 @@ polygon(y=c(lWP,rev(uWP)),x=c(1:(gens+1),(gens+1):1),border=NA,col="lightblue");
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 #points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 points(x=xxx,y=mWP,type="l",lwd=2,col="blue");
+text(x=0, y=-22.0, label=expression(paste(c[P]==0.01)),cex=1.75, pos=4);
 rm(evo_cc_02);
 # ------------------------------------------------------------------------#
 evo_cc_02 <- read.table(file="results/fig2/evo_M00_P00_F00.txt", header=FALSE);
@@ -114,6 +115,7 @@ polygon(y=c(lWP,rev(uWP)),x=c(1:(gens+1),(gens+1):1),border=NA,col="lightblue");
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 #points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 points(x=xxx,y=mWP,type="l",lwd=2,col="blue");
+text(x=0, y=-22.0, label=expression(paste(c[P]==0.01)),cex=1.75, pos=4);
 rm(evo_cc_02);
 # ------------------------------------------------------------------------#
 evo_cc_02 <- read.table(file="results/fig1/evo_M00_P0025_F00.txt", header=FALSE);
@@ -176,6 +178,7 @@ polygon(y=c(lWP,rev(uWP)),x=c(1:(gens+1),(gens+1):1),border=NA,col="lightblue");
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 #points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 points(x=xxx,y=mWP,type="l",lwd=2,col="blue");
+text(x=0, y=-22.0, label=expression(paste(c[P]==0.01)),cex=1.75, pos=4);
 rm(evo_cc_02);
 # ------------------------------------------------------------------------#
 evo_cc_02 <- read.table(file="results/fig1/evo_M00_P005_F00.txt", header=FALSE);
[…]

### 2016-09-27 analysis.R
Add horizontal lines showing where allele values are fixed

@@ -40,6 +40,7 @@ axis(side=2,at=c(-20,-10,0,10), cex.axis=1.5);
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 #points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 abline(h=0,lwd=0.8,lty="dotted");
+abline(h=0,lwd=3);
 uWP <- mWP + sWP / sqrt(sum(evo[,6]==gens));
 lWP <- mWP - sWP / sqrt(sum(evo[,6]==gens));
 uPO <- mPO + sPO / sqrt(sum(evo[,6]==gens));
@@ -52,7 +53,7 @@ polygon(y=c(lWP,rev(uWP)),x=c(1:(gens+1),(gens+1):1),border=NA,col="lightblue");
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 #points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 points(x=xxx,y=mWP,type="l",lwd=2,col="blue");
-text(x=0, y=-22.0, label=expression(paste(c[P]==0.01)),cex=1.75, pos=4);
+text(x=0, y=-22.0, label=expression(paste(c[P]==0.0)),cex=1.75, pos=4);
 rm(evo_cc_02);
 # ------------------------------------------------------------------------#
 evo_cc_02 <- read.table(file="results/fig2/evo_M00_P00_F00.txt", header=FALSE);
@@ -103,6 +104,7 @@ axis(side=2,at=c(-20,-10,0,10), cex.axis=1.5);
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 #points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 abline(h=0,lwd=0.8,lty="dotted");
+abline(h=0,lwd=3);
 uWP <- mWP + sWP / sqrt(sum(evo[,6]==gens));
 lWP <- mWP - sWP / sqrt(sum(evo[,6]==gens));
 uPO <- mPO + sPO / sqrt(sum(evo[,6]==gens));
@@ -115,7 +117,7 @@ polygon(y=c(lWP,rev(uWP)),x=c(1:(gens+1),(gens+1):1),border=NA,col="lightblue");
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 #points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 points(x=xxx,y=mWP,type="l",lwd=2,col="blue");
[…]

### 2016-09-27 analysis.R
Change text size within figures, insert proper figure 2 earlier in the code

@@ -19,7 +19,7 @@ beta_val <- 3;
 # XXX XXX      PLOT FIGURE 1  XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 setEPS(); # postscript below for final publication?
-cairo_ps("figures/M00_P01_F00.eps",family="Arial",height=8,width=5.5);
+cairo_ps("figures/poly_costs.eps",family="Arial",height=8,width=5.5);
 par(mfrow=c(4,2),oma=c(5,5,2,1), mar=c(0.5,0.5,0.5,0.5));
 # XXX -----> TODO: CHANGE THE BELOW to P00 text.
 # ------------------------------------------------------------------------#
@@ -53,7 +53,7 @@ polygon(y=c(lWP,rev(uWP)),x=c(1:(gens+1),(gens+1):1),border=NA,col="lightblue");
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 #points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 points(x=xxx,y=mWP,type="l",lwd=2,col="blue");
-text(x=0, y=-22.0, label=expression(paste(c[P]==0.0)),cex=1.75, pos=4);
+text(x=0, y=-22.0, label=expression(paste(c[P]==0.0)),cex=1.5, pos=4);
 rm(evo_cc_02);
 # ------------------------------------------------------------------------#
 evo_cc_02 <- read.table(file="results/fig2/evo_M00_P00_F00.txt", header=FALSE);
@@ -84,7 +84,7 @@ polygon(y=c(lWP,rev(uWP)),x=c(1:(gens+1),(gens+1):1),border=NA,col="lightblue");
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 points(x=xxx,y=mWP,type="l",lwd=2,col="blue");
-text(x=0, y=-22.0, label=expression(paste(c[P]==0.00)),cex=1.75, pos=4);
+text(x=0, y=-22.0, label=expression(paste(c[P]==0.00)),cex=1.5, pos=4);
 rm(evo_cc_02);
[…]

### 2016-09-27 analysis.R
Fix some typos on the file paths for figures

@@ -553,7 +553,7 @@ text(x=0, y=-22.0, label=expression(paste(c[M]==0.00)),cex=1.5, pos=4);
 text(x=-300, y=11.0, label="A", cex=2, pos=4);
 rm(evo_cc_02);
 # ------------------------------------------------------------------------#
-evo_cc_02 <- read.table(file="results/fig2/evo_M02_Pf1_Ff-10.txt", header=FALSE);
+evo_cc_02 <- read.table(file="results/fig3_new/evo_M02_Pf1_Ff-10.txt", header=FALSE);
 evB <- evo_cc_02[evo_cc_02[,3]==0.02 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
 evo <- evB[evB[,2]==beta_val,]; 
 mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
@@ -589,7 +589,7 @@ text(x=0, y=-22.0, label=expression(paste(c[M]==0.02)),cex=1.5, pos=4);
 text(x=-300, y=11.0, label="B", cex=2, pos=4);
 rm(evo_cc_02);
 # ------------------------------------------------------------------------#
-evo_cc_02 <- read.table(file="results/fig2/evo_Mf-10_P00_F00.txt", header=FALSE);
+evo_cc_02 <- read.table(file="results/fig3_new/evo_Mf-10_P00_F00.txt", header=FALSE);
 evB <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0.0,];
 evo <- evB[evB[,2]==beta_val,]; 
 mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
@@ -626,7 +626,7 @@ text(x=0, y=-22.0, label=expression(paste(c[F]==0.02)),cex=1.5, pos=4);
 text(x=-300, y=11.0, label="C", cex=2, pos=4);
 rm(evo_cc_02);
 # ------------------------------------------------------------------------#
-evo_cc_02 <- read.table(file="results/fig2/evo_M-10_P00_F02.txt", header=FALSE);
+evo_cc_02 <- read.table(file="results/fig3_new/evo_Mf-10_P00_F02.txt", header=FALSE);
[…]

### 2016-09-27 ms_pre_post.Rmd
Edit Discussion, tweaks to results

@@
 ---
-title: 'Evolution of pre-copulatory and post-copulatory inbreeding behaviour'
+title: "Evolution of pre-copulatory and post-copulatory inbreeding behaviour"
 author: "A. Bradley Duthie et al."
@@
 ---
-
-<!--- Need to do 40k generations to see allele values level off, 40 replicates each:
-
-Figure    1: 100 hours total
-Figures   2: 48  hours total
-Figures   3: 48  hours total
-Figures   4: 48  hours total
-Figures   5: 48  hours total
-
-Nah, these are too much.
-I've decided to increase to 40k generations for the costs only (100 hours total).
-Reasoning for this is that when we look at the fixed traits, we are really interested in whether or not the initial invasion changes, hence fewer generations are better.
-When we start everything at zero and let it evolve, then long-term stuff becomes more important, so 40k are useful.
-
---->
 
@@
 We first test our hypothesis that a focal female's ability to express post-copulatory choice with respect to kinship causes selection for polyandry by comparing simulations in which post-copulatory inbreeding strategy is fixed to random mating with respect to kinship to simulations in which tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy can all evolve.
-The left and right columns of Figure 1 show results for fixed versus evolving post-copulatory choice, respectively, across four rows of costs of tendency for polyandry.
-For low costs of tendency for polyandry, $c_{P} < 0.005$, selection caused expected tendency for polyandry allele values ($P_{a}$) to be positive only when post-copulatory inbreeding avoidance evolved (Figure 1A-D), and for all $c_{P}$, $P_{a}$ values were higher when post-copulatory inbreeding avoidance evolved than when it could not evolve.
+For low costs of tendency for polyandry, $c_{P} < 0.005$, selection caused expected tendency for polyandry allele values ($P_{a}$) to be positive only when post-copulatory inbreeding avoidance evolved (Figure 1A-D), and for all $c_{P}$, $P_{a}$ values were higher when post-copulatory inbreeding avoidance evolved than when it could not evolve (Figure 1).
 When post-copulatory inbreeding avoidance could not evolve, $P_{a}$ values were negative even in the absence of a direct cost ($c_{P}=0$; Figure 1A) because females that expressed polyandry were more likely to increase their inbreeding due to sampling males without replacement [@Duthie].
@@
 
-<!--- ---------------------------------------------------------------------- --->
-<!--- -------------------- LEFT OFF HERE ----------------------------------- --->
-<!--- ---------------------------------------------------------------------- --->
+Our second hypothesis that selection for a costly inbreeding avoidance strategy will be negligible given a less costly alternative was generally supported by our simulations (Figure 3).
+For simulations in which either pre- or post-copulatory inbreeding strategy allele values were fixed for random choice with respect to kinship ($M_{a}=0$ or $F_{a}=0$, respectively), the alternative costly inbreeding strategy evolved to inbreeding avoidance ($F_{a}<0$ or $M_{a}<0$).
+However, when the alternative inbreeding strategy could evolve and was not costly, the focal costly inbreeding strategy evolved toward random choice given increasingly negative allele values of the alternative strategy over generations (Figure 3B,D).
+For example, given fixed $F_{a}=0$, grand mean $M_{a}$ values were $-0.868$ in the last $10000$ generations of evolution (Figure 3A), meaning that an outbred focal female was ca $5.34$ times less likely to choose a full-sibling and ca $2.10$ times less likely to choose a first cousin than a non-relative given a strong cost of pre-copulatory inbreeding avoidance, $c_{M}=0.02$.
+In contrast, grand mean $M_{a}$ allele values were $-0.288$ when post-copulatory inbreeding avoidance evolved.
+More strongly, given fixed $M_{a}=0$, grand mean $F_{a}$ values were $-1.092$ in the last $10000$ generations of evolution (Figure 3C), meaning that an outbred focal female was ca $6.46$ times less likely to choose a full-sibling and ca $2.37$ times less likely to choose a first cousin than a non-relative given a strong cost of pre-copulatory inbreeding avoidance, $c_{F}=0.02$.
+However, grand-mean $F_{a}$ values were $-0.070$ when pre-copulatory inbreeding strategy evolved, and polyandry allele values were negative.
+Overall, selection for a costly inbreeding strategy that was adaptive in isolation was greatly weakened given evolution of a less costly strategy.
 
-Figure 1 shows changes in mean allele values of tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy across all eight possible combinations of costs.
+<!--- Figure 1 shows changes in mean allele values of tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy across all eight possible combinations of costs.
 In Figure 1A, when no phenotypes are costly, inbreeding mating strategy and inbreeding fertilisation strategy evolve to inbreeding avoidance ($M_{a}<0$ and $F_{a}<0$), and females evolve to be polyandrous ($P_{a}>0$).
 Costs of phenotypes had a direct effect on evolution, causing inbreeding mating strategy and inbreeding fertilisation strategy phenotypes to evolve to values closer to zero (because realisation of inbreeding strategy costs increases with phenotype absolute values) and tendency for polyandry phenotypes to evolve to values that were more negative (because realisation of polyandry costs increases with positive phenotype values).
+--->
 
-We can use Figure 1 to test the hypothesis that inbreeding mating strategy will evolve to inbreeding avoidance ($M_{a}<0$), but inbreeding fertilisation strategy will be negligible ($F_{a} \approx 0$) when mating costs are low ($c_{M}=0$) relative to the costs of tendency for polyandry and inbreeding fertilisation strategy ($c_{P}=0.02$ or $c_{F}=0.02$) by comparing different cost combinations to the null model in which all costs equal zero (Figure 1A).
+<!--- We can use Figure 1 to test the hypothesis that inbreeding mating strategy will evolve to inbreeding avoidance ($M_{a}<0$), but inbreeding fertilisation strategy will be negligible ($F_{a} \approx 0$) when mating costs are low ($c_{M}=0$) relative to the costs of tendency for polyandry and inbreeding fertilisation strategy ($c_{P}=0.02$ or $c_{F}=0.02$) by comparing different cost combinations to the null model in which all costs equal zero (Figure 1A).
 Figure 1A,C,D,G show that inbreeding avoidance in mating ($M_{a}<0$) evolved consistently whenever $c_{M}=0$.
@@
 However, when only tendency for polyandry was costly (Figure 1C), both inbreeding mating strategy and inbreeding fertilisation strategy evolved to inbreeding avoidance over generations ($M_{a} < 0$ and $F_{a} < 0$).
+--->
 
-We can also use Figure 1 to test the hypothesis that inbreeding fertilisation strategy will evolve to inbreeding avoidance ($F_{a}<0$), but inbreeding mating strategy will be negligible ($M_{a} \approx 0$) when tendency for polyandry and inbreeding fertilisation strategy costs are low ($c_{P}=0$ and $c_{F}=0$) relative to the cost of inbreeding mating strategy ($c_{M}=0.02$).
+<!--- We can also use Figure 1 to test the hypothesis that inbreeding fertilisation strategy will evolve to inbreeding avoidance ($F_{a}<0$), but inbreeding mating strategy will be negligible ($M_{a} \approx 0$) when tendency for polyandry and inbreeding fertilisation strategy costs are low ($c_{P}=0$ and $c_{F}=0$) relative to the cost of inbreeding mating strategy ($c_{M}=0.02$).
 Figure 1B shows that inbreeding avoidance through fertilisation bias evolved ($F_{a}<0$) under these conditions.
 While inbreeding mating strategy initially evolved toward inbreeding avoidance ($M_{a} < 0$), long-term evolution of inbreeding mating strategy stabilised at random mating ($M_{a} \approx 0$).
+--->
 
@@
 
-Figure 4 shows change in inbreeding mating strategy allele values over generations when tendency for polyandry and inbreeding fertilisation strategy alleles were fixed for adaptive values of inbreeding avoidance $P_{a}=1$ and $F_{a}=-5$.
+Our third hypothesis that invasion of pre- or post-copulatory inbreeding avoidance would be precluded by the existence of an already adaptive complementary strategy was supported for invading post-copulatory, but not pre-copulatory, inbreeding avoidance.
+When pre-copulatory inbreeding strategy was initialised for random mating, but polyandry and post-copulatory inbreeding strategy allele values were fixed for adaptive inbreeding avoidance (Figure 4A,B), negative pre-copulatory inbreeding allele values became increasingly more freqent ($M_{a}<0$), causing inbreeding avoidance in mate choice.
+However, $M_{a}$ values were not as negative after $40000$ generations when post-copulatory inbreeding avoidance and polyandry were fixed as they were when no post-copulatory inbreeding avoidance occurred (e.g., compare Figure 4A with Figure 1A, and Figure 4B with Figure 2A).
+When post-copulatory inbreeding strategy was initialised for random fertilisation, existence of an already adaptive strategy of pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance (Figure 4C,D).
+Mean allele values affecting polyandry consistently decreased over generations regardless of the cost of post-copulatory inbreeding strategy, $c_{F}$.
+Consequently, when $c_{F}=0$, post-copulatory inbreeding strategy allele values had no effect because females were consistently monandrous, resulting in high drift of $F_{a}$ values among replicates (Figure 4C).
+However, when $c_{F}=0.02$, $F_{a}$ values remained near zero to minimise direct costs.
+
+<!--- Figure 4 shows change in inbreeding mating strategy allele values over generations when tendency for polyandry and inbreeding fertilisation strategy alleles were fixed for adaptive values of inbreeding avoidance $P_{a}=1$ and $F_{a}=-5$.
 Despite that females in these simulations could already avoid inbreeding after mating occurred, inbreeding mating strategy evolved towards inbreeding avoidance given costs of $c_{M}=0$ (Figure 4A) and $c_{M}=0.02$ (Figure 4B).
 We therefore did not find evidence that the existence of adaptive inbreeding avoidance through fertilisation bias in any way precluded the evolution of adaptive inbreeding avoidance through mate choice.
+--->
 
-Figure 5 shows change in tendency for polyandry and inbreeding fertilisation strategy allele values over generations when inbreeding mating strategy alleles were fixed for adaptive inbreeding avoidance $M_{a}=-5$.
+<!--- Figure 5 shows change in tendency for polyandry and inbreeding fertilisation strategy allele values over generations when inbreeding mating strategy alleles were fixed for adaptive inbreeding avoidance $M_{a}=-5$.
 Existence of adaptive inbreeding avoidance through mate choice precluded evolution of polyandry for all combinations of costs (Figure 5), meaning that evolution of adpative polyandry to avoid inbreeding through inbreeding fertilisation strategy was never predicted in populations where females were already avoiding inbreeding through mate choice.
@@
 We therefore found strong evidence that the existence of adaptive inbreeding avoidance through pre-copulatory mate choice precluded evolution of adaptive inbreeding avoidance through post-copulatory inbreeding avoidance through fertilisation bias.
+--->
 
@@
 
-Inbred offspring are typically less viable than outbred offspring, and when such inbreeding depression is strong, it is predicted to cause selection for inbreeding avoidance [Duthie and Reid *in press*; @Parker1979; @Parker2006; @Pusey1996; @Kokko2006].
+<!--- ---------------------------------------------------------------------- --->
+<!--- -------------------- LEFT OFF HERE ----------------------------------- --->
+<!--- ---------------------------------------------------------------------- --->
+
+<!--- Inbred offspring are typically less viable than outbred offspring, and when such inbreeding depression is strong, it is predicted to cause selection for inbreeding avoidance [Duthie and Reid *in press*; @Parker1979; @Parker2006; @Pusey1996; @Kokko2006].
 In animals, inbreeding avoidance can be realised through both pre-copulatory and post-copulatory mechanisms [e.g., @Tuni2013; @Firman2015; @Daniel2015; @Fischer2015].
@@
 Importantly, evolution of post-copulatory mechanisms of inbreeding avoidance requires females to mate multiply, meaning that post-copulatory inbreeding avoidance cannot occur unless polyandry has evolved in a population.
-Accordingly, we modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency to engage in polyandry, inbreeding mating strategy (pre-copulatory), and inbreeding fertilisation strategy (post-copulatory).
-Using *in silico* experiments, we tested four specific hypothesis to predict evolution of tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy given diverse costs and evolutionary constraints.
-We found that (1) selection for polyandry was greatly strengthened given concurrent evolution of inbreeding fertilisation strategy, (2) selection was strong for low cost, and weak but not negligible for high cost, mechanisms of inbreeding avoidance, (3) constraints on evolution of pre-copulatory inbreeding avoidance greatly strengthened selection for post-copulatory inbreeding avoidance, but not vice versa, and (4) pre-existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of post-copulatory inbreeding avoidance, but not vice versa.
+Accordingly, --->
+
+We modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency to engage in polyandry, inbreeding mating strategy (pre-copulatory), and inbreeding fertilisation strategy (post-copulatory).
+Using *in silico* experiments, we tested three specific hypothesis to predict evolution of polyandry, and pre- and post-copulatory inbreeding strategy.
+We found that (1) selection for polyandry was greatly strengthened given concurrent evolution of post-copulatory inbreeding avoidance, (2) selection for costly pre- or post-copulatory inbreeding avoidance was negligible given evolution of a less costly strategy of inbreeding avoidance, and (3) pre-existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of post-copulatory inbreeding avoidance, but not vice versa.
 More generally, we provide a novel framework for approaching empirical studies of inbreeding avoidance, predicting evolution of polyandry and inbreeding avoidance through pre- and post-copulatory mechanisms.
 
-Evolution of polyandry to avoid inbreeding
-----------------------------------------------
+<!--- Evolution of polyandry to avoid inbreeding --->
+<!--- ---------------------------------------------- --->
 
 The opportunity to adjust inbreeding has been widely considered as a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
-Recently, @Duthie found the conditions under which selection for polyandry to avoid inbreeding is predicted to be highly restrictive, requiring strong constraints on the availability of initial compared to additional mates, or the conditional expression of polyandry such that females only engaged in polyandry when their initial choice of mate was of low quality.
-However, @Duthie assumed that fertilisation of offspring was unbiased with respect to mate kinship, meaning that females could not express choice after mating had occurred.
-In contrast, we found that when females could express choice after mating through biased fertilisation, selection for polyandry was greatly strengthened (Figure 1A), especially when constraints restricted evolution of inbreeding avoidance through mate choice (Figure 3).
+Recently, @Duthie found the conditions under which selection for polyandry and pre-copulatory inbreeding avoidance is predicted to be highly restrictive, requiring strong constraints on the availability of initial compared to additional mates, or the conditional expression of polyandry such that females only engaged in polyandry when their initial choice of mate was of low quality.
+However, @Duthie assumed that fertilisation of offspring was unbiased with respect to mate kinship, meaning that females could not express post-copulatory choice.
+In contrast, we found that when post-copulatory inbreeding avoidance could evolve, selection for polyandry was greatly strengthened (Figure 1).
 The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but the existence of selection for post-copulatory inbreeding avoidance causing feedback to select for polyandry has not been formally modelled.
@@
 Interestingly, female house mice have also been shown to express pre-copulatory inbreeding avoidance  [@Potts1991; @Roberts2003].
-Our results suggest that post-copulatory inbreeding avoidance is unlikely to evolve when females can already avoid inbreeding through pre-copulatory mechanisms (Figure 5), meaning that evolution of post-copulatory inbreeding avoidance could reasonably be hypothesised to have preceded evolution of pre-copulatory inbreeding avoidance in mice.
+Our results suggest that post-copulatory inbreeding avoidance is unlikely to evolve when females can already avoid inbreeding through pre-copulatory mechanisms (Figure 4), meaning that evolution of post-copulatory inbreeding avoidance could reasonably be hypothesised to have preceded evolution of pre-copulatory inbreeding avoidance in mice.
 
@@
 commodus* are capable of controlling the transfer of sperm to their spermatheca, most likely through physical control of the spermathecal duct, and can reduce sperm storage despite being guarded by a related male.
-Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for polyandry, especially if pre-copulatory inbreeding avoidance is costly (Figure 1) or constrained (Figure 3).
+Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for polyandry, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
 
-Costs of polyandry and inbreeding avoidance
-----------------------------------------------
+<!---Costs of polyandry and inbreeding avoidance --->
+<!--- ---------------------------------------------- --->
 
-Our results show that direct negative selection on phenotypes that increase female promiscuity or choosiness with respect to kinship decrease the strength of selection for tendency for polyandry and inbreeding avoidance (Figure 1).
+<!---- Our results show that direct negative selection on phenotypes that increase female promiscuity or choosiness with respect to kinship decrease the strength of selection for tendency for polyandry and inbreeding avoidance (Figure 1).
 Importantly, the cost of tendency for polyandry only decreased female fitness given tendency for polyandry phenotype values greater than zero ($P_{p}>0$), but the threshold nature of the tendency for polyandry phenotype only resulted in selection against positive tendency for polyandry allele values ($P_{a}$) when the sum over a focal female's $20$ $P_{a}$ alleles was greater than zero because summations less than zero all resulted in equivalent monandrous phenotypes ($P_{p}=0$).
@@
 Consequently, costly polyandry does not necessarily preclude evolution of adaptive post-copulatory inbreeding avoidance in populations.
+--->
 
-A low relative cost for one inbreeding strategy (e.g., pre-copulatory inbreeding avoidance) precluded a more costly complementary inbreeding strategy from persisting in a focal population (Figure 1), meaning that long-term persistence of both pre- and post-copulatory inbreeding avoidance might not be expected in populations given cost asymmetry.
+In our model, a cost free inbreeding strategy precluded a more costly complementary inbreeding strategy from persisting in a focal population (Figure 2), meaning that long-term persistence of both pre- and post-copulatory inbreeding avoidance might not be expected in populations given cost asymmetry.
 Direct costs therefore strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies.
@@
 
-Constraints on polyandry and inbreeding avoidance
-----------------------------------------------
+<!--- Constraints on polyandry and inbreeding avoidance --->
+<!--- ---------------------------------------------- --->
 
@@
 
-Constraints on pre-copulatory and post-copulatory inbreeding avoidance might vary widely in empirical systems.
+<!--- Constraints on pre-copulatory and post-copulatory inbreeding avoidance might vary widely in empirical systems.
 Female mate choice might be evolutionarily constrained if females are unable to discriminate among kin and therefore incapable of choosing to avoid inbreeding [Duthie and Reid *in press*; @Penn2010].
@@
 Our results suggest that such constraints on one strategy of inbreeding avoidance (pre-copulatory versus post-copulatory) will strengthen selection on a complementary strategy, perhaps making inbreeding avoidance more detectable in empirical systems.
+--->
 

### 2016-09-27 ms_pre_post.Rmd
Tweak and add new figures

@@
 Accordingly, we use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address three questions: Will evolution of post-copulatory inbreeding avoidance strengthen selection for polyandry?
-Will selection for one costly inbreeding strategy be negligible given a non-costly complementary strategy?
-And will selection for one inbreeding strategy be negligible given existence of an already adaptive alternative strategy?
-We show that evolution of polyandry is greatly facilitated by post-copulatory inbreeding avoidance.
+Will selection for a costly inbreeding strategy be negligible given a non-costly complementary strategy?
+And will selection for an inbreeding strategy be negligible given existence of an already adaptive alternative strategy?
+We show that selection for polyandry is greatly strengthened by post-copulatory inbreeding avoidance.
 Strong selection for relatively low cost inbreeding avoidance strategies was observed, while selection for functionally redundant high cost strategies decreased over generations.
@@
 
-<!--- It is therefore necessary to consider evolution of inbreeding mating strategy and inbreeding fertilisation strategy when each evolves in a population where its complementary inbreeding strategy is evolutionarily constrained or already fixed as an adaptation.
+<!--- It is therefore necessary to consider evolution of pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy when each evolves in a population where its complementary inbreeding strategy is evolutionarily constrained or already fixed as an adaptation.
 --->
 
-<!--- Overall, to predict evolution of polyandry and inbreeding strategies, it is therefore necessary to model costs associated with polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
+<!--- Overall, to predict evolution of polyandry and inbreeding strategies, it is therefore necessary to model costs associated with polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
 --->
@@
 Female inbreeding strategy can be enacted before or after copulation occurs [e.g., @Tuni2013; @Firman2015; @Daniel2015; @Fischer2015].
-However, models of inbreeding do not consider pre-copulatory inbreeding strategy (hereafter 'inbreeding mating strategy') and post-copulatory inbreeding strategy (hereafter 'inbreeding fertilisation strategy') jointly, meaning that it is unclear when selection for either or both strategies is predicted in empirical systems.
+However, models of inbreeding do not consider pre-copulatory inbreeding strategy (hereafter 'pre-copulatory inbreeding strategy') and post-copulatory inbreeding strategy (hereafter 'post-copulatory inbreeding strategy') jointly, meaning that it is unclear when selection for either or both strategies is predicted in empirical systems.
 --->
 
-<!--- Critically, evolution of inbreeding fertilisation strategy is precluded if females only mate with one male, meaning that evolution of polyandry (defined as female multiple mating within a single reproductive bout) is intrinsically tied to female inbreeding fertilisation strategy.
+<!--- Critically, evolution of post-copulatory inbreeding strategy is precluded if females only mate with one male, meaning that evolution of polyandry (defined as female multiple mating within a single reproductive bout) is intrinsically tied to female post-copulatory inbreeding strategy.
 Although polyandry is commonplace in wild populations, the regularity with which it is observed in the wild remains theoretically puzzling because engaging in polyandry does not necessarily increase the number of offspring that a female produces, meaning that the fitness benefits associated with polyandry are not always clear [@Parker2013; @Taylor2014].
 It has been hypothesised that females can acheive a net fitness benefit if polyandry provides them with additional opportunities to adjust their inbreeding through copulations with additional males [e.g., @Tregenza2002; @Akcay2007; @Lehtonen2015].
-However, no models quantify the degree to which expression of biased paternity resulting from evolving inbreeding fertilisation strategy can feedback to drive evolution of polyandry in populations of potentially inbreeding females and males with biologically realistic distributions of relatedness.
+However, no models quantify the degree to which expression of biased paternity resulting from evolving post-copulatory inbreeding strategy can feedback to drive evolution of polyandry in populations of potentially inbreeding females and males with biologically realistic distributions of relatedness.
 --->
 
-<!--- Evolution of inbreeding fertilisation strategy might increase selection for polyandry, but evolutionary feedbacks between inbreeding fertilisation strategy and polyandry might also be contingent upon evolution of inbreeding mating strategy, thereby leading to complex evolutionary dynamics between inbreeding strategies and polyandry.
-For example, if females can acheive their desired degree of inbreeding through mate choice alone, then subsequent polyandry and inbreeding fertilisation strategy might be superfluous for increasing female fitness.
-Alternatively, if females are often unsuccessful at realising their inbreeding mating strategy due to factors such as sexual conflict over mating and resulting male coercion [e.g., @Parker2006], limited kin recognition amongst potential mates [e.g., @Penn2010], or simply the inherent stochasticity associated with mate encounters or expression of mate choice based on inbreeding [e.g., @Kokko2006; @Duthie], then selection on inbreeding fertilisation strategy might occur to reinforce inbreeding mating strategy.
-In empirical systems where inbreeding depression is severe and inbreeding avoidance is therefore beneficial, expression of inbreeding mating strategy and inbreeding fertilisation strategy have been observed across diverse taxa [e.g., @Gasparini2011; @Tuni2013; @Firman2015; @Fischer2015; @Daniel2015].
+<!--- Evolution of post-copulatory inbreeding strategy might increase selection for polyandry, but evolutionary feedbacks between post-copulatory inbreeding strategy and polyandry might also be contingent upon evolution of pre-copulatory inbreeding strategy, thereby leading to complex evolutionary dynamics between inbreeding strategies and polyandry.
+For example, if females can acheive their desired degree of inbreeding through mate choice alone, then subsequent polyandry and post-copulatory inbreeding strategy might be superfluous for increasing female fitness.
+Alternatively, if females are often unsuccessful at realising their pre-copulatory inbreeding strategy due to factors such as sexual conflict over mating and resulting male coercion [e.g., @Parker2006], limited kin recognition amongst potential mates [e.g., @Penn2010], or simply the inherent stochasticity associated with mate encounters or expression of mate choice based on inbreeding [e.g., @Kokko2006; @Duthie], then selection on post-copulatory inbreeding strategy might occur to reinforce pre-copulatory inbreeding strategy.
+In empirical systems where inbreeding depression is severe and inbreeding avoidance is therefore beneficial, expression of pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy have been observed across diverse taxa [e.g., @Gasparini2011; @Tuni2013; @Firman2015; @Fischer2015; @Daniel2015].
 However, no models predict *a priori* which of these inbreeding strategies should be observed when inbreeding depression is sufficiently severe to make inbreeding avoidance adaptive.
@@
 
-<!--- Evolution of polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy will ultimately be determined by the, potentially interacting, fitness benefits and costs of each phenotype.
+<!--- Evolution of polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy will ultimately be determined by the, potentially interacting, fitness benefits and costs of each phenotype.
 Given severe inbreeding depression, phenotypes will increase a focal female's fitness if they cause her to avoid breeding with close relatives [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
@@
 
-<!--- Selection for inbreeding mating strategy versus inbreeding fertilisation strategy and associated polyandry might also depend evolutionary constraints, or on existing phenotypes in the population.
-For example, if phenotypes biasing fertilisation to avoid inbreeding are precluded by evolutionary constraints [@Bradshaw1991; @Futuyma2010], then inbreeding avoidance might only be possible before copulation occurs, perhaps strengthening selection for inbreeding mating strategy and weakening selection for polyandry.
-Alternatively, evolution of female inbreeding mating strategy might be precluded due to severely limited kin recognition or the inability to resist male coercion given sexual conflict [@Arnqvist2005a; @Parker2006; @Penn2010].
-In such conditions, females might only be able to express choice through inbreeding fertilisation strategy, perhaps strengthening selection for inbreeding avoidance through polyandry and post-copulatory mechanisms.
+<!--- Selection for pre-copulatory inbreeding strategy versus post-copulatory inbreeding strategy and associated polyandry might also depend evolutionary constraints, or on existing phenotypes in the population.
+For example, if phenotypes biasing fertilisation to avoid inbreeding are precluded by evolutionary constraints [@Bradshaw1991; @Futuyma2010], then inbreeding avoidance might only be possible before copulation occurs, perhaps strengthening selection for pre-copulatory inbreeding strategy and weakening selection for polyandry.
+Alternatively, evolution of female pre-copulatory inbreeding strategy might be precluded due to severely limited kin recognition or the inability to resist male coercion given sexual conflict [@Arnqvist2005a; @Parker2006; @Penn2010].
+In such conditions, females might only be able to express choice through post-copulatory inbreeding strategy, perhaps strengthening selection for inbreeding avoidance through polyandry and post-copulatory mechanisms.
 Selection for inbreeding mating or fertilisation strategy might also be weak or negligible if the strategy is redundant due to the presence of an already established adaptive inbreeding strategy (e.g., if females already successfully avoid inbreeding during mate encounters, then they might be unable to increase their fitness further by biasing fertilisation after mating has occurred).
@@
 
-Here we use individual-based modelling and *in silico* experiments to test the hypothesis that, given severe inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance causes selection for evolution of polyandry.
+Here we use individual-based modelling and *in silico* experiments to test the hypothesis that, given severe inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance causes selection for polyandry.
 Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that selection for pre-copulatory inbreeding avoidance but not post-copulatory inbreeding avoidance will occur when pre-copulatory inbreeding avoidance is less costly than the cost of post-copulatory inbreeding avoidance, while selection for post-copulatory inbreeding avoidance but not pre-copulatory inbreeding avoidance will occur when pre-copulatory inbreeding avoidance is more costly than the cost of post-copulatory inbreeding avoidance.
@@
 
-<!--- that constraints on evolution of one inbreeding strategy (e.g., inbreeding mating strategy) will increase the strength of selection on evolution of a complementary inbreeding strategy (e.g., inbreeding fertilisation strategy), and that --->
+<!--- that constraints on evolution of one inbreeding strategy (e.g., pre-copulatory inbreeding strategy) will increase the strength of selection on evolution of a complementary inbreeding strategy (e.g., post-copulatory inbreeding strategy), and that --->
 
@@
 After inbreeding depression in offspring viability, $\rho$ adult male immigrants arrive in the population, then density effects reduce the entire population down to separate female ($K_{f}$) and male ($K_{m}$) carrying capacities.
-Over generations, we record mean values of alleles underlying polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
+Over generations, we record mean values of alleles underlying polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
 
@@
 <!--- In the case of tendency to engage in polyandry, the cost of $P_{p}$ ($c_{P}$) is interpreted biologically as a cost associated with mate searching or courtship [e.g., @Rowe1988; @Rowe1994; @Ronkainen1994; @Koga1998; @Lasley-Rasher2012].
-For inbreeding mating strategy, the cost of $M_{p}$ ($c_{M}$) is interpreted biologically as a cost associated with risk of mating failure due to females being overly choosy [e.g., @Kokko2013], and for inbreeding fertilisation strategy, the cost of $F_{p}$ ($c_{F}$) is interpreted as an energetic cost associated with the physiological or biochemical mechanisms that need to be developed to bias fertilisation for inbreeding avoidance or inbreeding preference [e.g., @Gasparini2011].
+For pre-copulatory inbreeding strategy, the cost of $M_{p}$ ($c_{M}$) is interpreted biologically as a cost associated with risk of mating failure due to females being overly choosy [e.g., @Kokko2013], and for post-copulatory inbreeding strategy, the cost of $F_{p}$ ($c_{F}$) is interpreted as an energetic cost associated with the physiological or biochemical mechanisms that need to be developed to bias fertilisation for inbreeding avoidance or inbreeding preference [e.g., @Gasparini2011].
 --->
@@
 The probability that a focal female dies before mating due to the cost of polyandry is therefore $P_{p} \times c_{P}$.
-Similarly, the probability of pre-mating female mortality due to the cost of inbreeding mating strategy and inbreeding fertilisation strategy is $|M_{p}| \times c_{M}$ and $|F_{p}| \times c_{F}$, repectively, where $|M_{p}|$ is the absolute value of $M_{p}$ and $|F_{p}|$ is the absolute value of $F_{p}$.
+Similarly, the probability of pre-mating female mortality due to the cost of pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy is $|M_{p}| \times c_{M}$ and $|F_{p}| \times c_{F}$, repectively, where $|M_{p}|$ is the absolute value of $M_{p}$ and $|F_{p}|$ is the absolute value of $F_{p}$.
 Absolute values are used for applying costs to inbreeding strategies because both negative and positive $M_{p}$ and $F_{p}$ bias breeding interactions with respect to kinship, while only positive values of $P_{p}$ affect a female's tendency for polyandry; zero and negative $P_{p}$ values always translate to monandrous phenotypes (see below).
@@
 We model selection as having an absolute effect on offspring viability (i.e., hard selection), rather than a relative effect on viability (i.e., soft selection), so that the effect of $\beta$ is consistent over generations and across different parameter combinations.
-Natural selection on tendency for polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilisation strategy ($F_{p}$) can therefore be compared across generations and parameter combinations.
+Natural selection on tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$) can therefore be compared across generations and parameter combinations.
 If offspring viability was instead relative such that the least inbred offspring had a high viability regardless of the absolute value of $k_{ij}$, then the effect of kinship coefficients and inbreeding depression slopes on offspring viability would depend on the population-wide distribution of $k_{ij}$ between females and males, making model inference more difficult.
@@
 If the focal population was instead closed ($\rho=0$), then all alleles would quickly be expected to become identical-by-descent among descendants of the ancestral population.
-To avoid having immigrants affect evolution of tendency for polyandry ($P_{p}$), inbreeding mating strategy ($M_{p}$), and inbreeding fertilisation strategy ($F_{p}$), immigrants are always male and can therefore be chosen based on their kinship values of zero but not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$.
-To further avoid having immigrants affect evolutionary dynamics, allele values underlying tendency for polyandry ($P_{a}$), inbreeding mating strategy ($M_{a}$), and inbreeding fertilisation strategy ($F_{a}$) are randomly sampled from normal distributions with means and standard deviations of $P_{a}$, $M_{a}$, and $F_{a}$ values equal to the means and standard deviations of those in the focal population at the time of immigration.
+To avoid having immigrants affect evolution of tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$), immigrants are always male and can therefore be chosen based on their kinship values of zero but not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$.
+To further avoid having immigrants affect evolutionary dynamics, allele values underlying tendency for polyandry ($P_{a}$), pre-copulatory inbreeding strategy ($M_{a}$), and post-copulatory inbreeding strategy ($F_{a}$) are randomly sampled from normal distributions with means and standard deviations of $P_{a}$, $M_{a}$, and $F_{a}$ values equal to the means and standard deviations of those in the focal population at the time of immigration.
 Overall, this model of immigration effectively assumes that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$.
@@
 
-To analyse our model, we track mean values of alleles underlying tendency for polyandry ($P_{a}$), inbreeding mating strategy ($M_{a}$), and inbreeding fertilisation strategy ($F_{a}$) in a focal population.
+To analyse our model, we track mean values of alleles underlying tendency for polyandry ($P_{a}$), pre-copulatory inbreed strategy ($M_{a}$), and post-copulatory inbreeding strategy ($F_{a}$) in a focal population.
 We present evolutionary dynamics of these mean allele values across different parameter combinations to test our three focal hypotheses.
@@
 To stop $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes resulting from $F_{a}$ cause random fertilisation with respect to kinship (i.e, $F_{p}=0$).
-Hence, while mutation and drift can still occur for $F_{a}$ alleles, these alleles have no phenotypic effect and polyandry cannot cause polyandrous females to benefit through an increased ability to bias fertilisation toward inbreeding avoidance.
+Hence $F_{a}$ alleles have no phenotypic effect and polyandry cannot cause polyandrous females to benefit through an increased ability to bias fertilisation toward inbreeding avoidance.
 By comparing mean $P_{a}$ values over generations when post-copulatory inbreeding avoidance also evolves versus when fertilisation is random, we test whether or not evolution of post-copulatory inbreeding strategy increases selection for polyandry.
 
-<!--- We simulate up to eight possible permutations of values of costs of tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$) equal to either $0$ or $0.02$ [@Duthie observed $0.02$ to be a strong cost of tendency for polyandry] for values of $\beta = 3$ ($8$ total combinations).
+<!--- We simulate up to eight possible permutations of values of costs of tendency for polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) equal to either $0$ or $0.02$ [@Duthie observed $0.02$ to be a strong cost of tendency for polyandry] for values of $\beta = 3$ ($8$ total combinations).
 --->
@@
 <!--- To test hypotheses regarding evolution under different relative costs of phenotypes, we consider all combinations of costs using simulations in which all three traits evolve.
-To test the hypothesis that inbreeding mating strategy will evolve toward inbreeding avoidance ($M_{p}<0$) when mating costs are low relative to the costs of tendency for polyandry and inbreeding fertilisation strategy, but that selection for inbreeding fertilisation strategy will then be negligible ($F_{p} \approx 0$), we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where $c_{M}=0$ but $c_{P}$, $c_{F}$, or both equals $0.02$.
+To test the hypothesis that pre-copulatory inbreeding strategy will evolve toward inbreeding avoidance ($M_{p}<0$) when mating costs are low relative to the costs of tendency for polyandry and post-copulatory inbreeding strategy, but that selection for post-copulatory inbreeding strategy will then be negligible ($F_{p} \approx 0$), we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where $c_{M}=0$ but $c_{P}$, $c_{F}$, or both equals $0.02$.
 We compare evolution in these three cost parameter value combinations with simulations in which all costs equal either $0$ or $0.02$.
 If our hypothesis is supported, then $M_{p}$ but not $F_{p}$ will evolve to more negative values when $c_{M}$ is relatively low than when all cost values are uniform.
-To test the hypothesis that inbreeding fertilisation strategy will evolve toward inbreeding avoidance ($F_{p}<0$) given low costs of polyandry and inbreeding fertilisation strategy relative to the cost of inbreeding mating strategy, but that selection on inbreeding mating strategy will be negligible ($M_{p} \approx 0$), we quantify evolution of $M_{p}$ and $F_{p}$ over generations when $c_{F}=0$, $c_{P}=0$, and $c_{M}=0.02$ .
+To test the hypothesis that post-copulatory inbreeding strategy will evolve toward inbreeding avoidance ($F_{p}<0$) given low costs of polyandry and post-copulatory inbreeding strategy relative to the cost of pre-copulatory inbreeding strategy, but that selection on pre-copulatory inbreeding strategy will be negligible ($M_{p} \approx 0$), we quantify evolution of $M_{p}$ and $F_{p}$ over generations when $c_{F}=0$, $c_{P}=0$, and $c_{M}=0.02$ .
 We compare evolution for this combination of cost parameter values with simulations in which all costs equal either $0$ or $0.02$.
@@
 
-To test the hypothesis that the existence of an adaptive inbreeding strategy will decrease the strength of selection on, and thereby preclude the invasion of, a complementary strategy, we first used exploratory simulations to determine evolution of precopulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation.
+To test the hypothesis that the existence of an adaptive inbreeding strategy will decrease the strength of selection on, and thereby preclude the invasion of, a complementary strategy, we first used exploratory simulations to determine evolution of pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation.
 To test whether or not pre-copulatory inbreeding avoidance was predicted to evolve when adaptive polyandry to avoid inbreeding was already established, we initiated pre-copulatory inbreeding strategy allele values at zero ($M_{a}=0$), but fixed post-copulatory inbreeding allele values at $F_{a}=-10$ and polyandry allele values at $P_{a}=1$ (i.e., $F_{p}$ and $P_{p}$ did not evolve).
@@
 Each combination of parameter values simulated is replicated $40$ times, and grand mean values and standard error of means is calculated in each generation across replicate simulations.
-These analyses allow us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on inbreeding fertilisation strategy might be weak if polyandry is rare).
+These analyses allow us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on post-copulatory inbreeding strategy might be weak if polyandry is rare).
 For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling [@Duthie] showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
@@
 <!--- We present our results by showing mean allele value changes over generations.
-Figures 1-5 show mean allele values of tendency for polyandry ($P_{a}$; red lines and shading), inbreeding mating strategy ($M_{a}$; blue lines and shading), and inbreeding fertilisation strategy ($F_{a}$; black lines and shading) over 10000 generations as calculated across all individuals (female and male) within a focal population over 40 replicate simulations with identical starting conditions.
+Figures 1-5 show mean allele values of tendency for polyandry ($P_{a}$; red lines and shading), pre-copulatory inbreeding strategy ($M_{a}$; blue lines and shading), and post-copulatory inbreeding strategy ($F_{a}$; black lines and shading) over 10000 generations as calculated across all individuals (female and male) within a focal population over 40 replicate simulations with identical starting conditions.
 Solid lines represent the grand mean of replicate mean allele values, and shading around lines shows standard errors of mean allele values around the grand mean.
-Panels within figures show different cost combinations for tendency for polyandry ($c_{P}$), inbreeding mating strategy ($c_{M}$), and inbreeding fertilisation strategy ($c_{F}$).
+Panels within figures show different cost combinations for tendency for polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$).
 Figures have fewer than eight panels if some costs are not relevant because allele values are fixed, and fixed allele values are shown as horizontal lines where line height is set to the fixed allele value.
@@
 
-Selection for polyandry is driven by inbreeding fertilisation strategy
+Selection for polyandry is driven by pre-copulatory inbreeding avoidance
 ----------------------------------------------
@@
 When post-copulatory inbreeding avoidance could not evolve, $P_{a}$ values were negative even in the absence of a direct cost ($c_{P}=0$; Figure 1A) because females that expressed polyandry were more likely to increase their inbreeding due to sampling males without replacement [@Duthie].
-Strong post-copulatory inbreeding avoidance consistently evolved in all simulations, even when $P_{a}$ values were not expected to be positive (Figure 1F,H), because of the threshold nature of the polyandry phenotype; Figure 2 shows how phenotypic polyandry was common even when mean polyandry allele values within a populatoin were expected to be negative.
+Strong post-copulatory inbreeding avoidance consistently evolved in all simulations, even when $P_{a}$ values were expected to be slightly negative (Figure 1F,H), because of the threshold nature of the polyandry phenotype; Figure 2 shows how phenotypic polyandry was common even when mean polyandry allele values within a population were expected to be negative.
 In all simulations, pre-copulatory inbreeding avoidance also evolved ($M_{a}<0$), meaning that both pre- and post-copulatory inbreeding avoidance was predicted, and evolution of adaptive polyandry occurred given sufficiently low costs of tendency for polyandry.
 
-<!--- Comparison of Figures 1 and 2 shows that evolution of inbreeding fertilisation strategy facilitates evolution of polyandry, particularly when costs of tendency for polyandry and inbreeding fertilisation strategy are zero.
+<!--- Comparison of Figures 1 and 2 shows that evolution of post-copulatory inbreeding strategy facilitates evolution of polyandry, particularly when costs of tendency for polyandry and post-copulatory inbreeding strategy are zero.
 For example, in Figure 2A, tendency for polyandry allele values consistently become negative over generations ($P_{a}<0$; decreasing red line), causing populations to be monandrous.
 Females in these populations avoid mating with kin ($M_{a}<0$; decreasing blue line), and because these females sample mates with replacement, males that remain after their initial mate choice are more likely to be relatives, causing selection for monandry because females are most likely to succeed in avoiding inbreeding in their initial mate choice [see also @Duthie].
-However, Figure 1A shows that when a focal female can also bias the probability that a particular mate sires her offspring, inbreeding fertilisation strategy evolves to inbreeding avoidance ($F_{a}<0$; decreasing black line).
+However, Figure 1A shows that when a focal female can also bias the probability that a particular mate sires her offspring, post-copulatory inbreeding strategy evolves to inbreeding avoidance ($F_{a}<0$; decreasing black line).
 Consequently, the ability to bias fertilisation to avoid inbreeding causes polyandry to become adaptive, and positive values of tendency for polyandry alleles increase in frequency ($P_{a}>0$; increasing red line of Figure 1A).
-Although non-zero costs decrease net selection for both tendency for polyandry and inbreeding fertilisation strategy (see below), across all combinations of costs, tendency for polyandry allele values are more positive when inbreeding fertilisation strategy can also evolve.
+Although non-zero costs decrease net selection for both tendency for polyandry and post-copulatory inbreeding strategy (see below), across all combinations of costs, tendency for polyandry allele values are more positive when post-copulatory inbreeding strategy can also evolve.
 Evolution of post-copulatory inbreeding avoidance therefore greatly facilitates evolution of polyandry.
@@
 
-Selection given relative costs of polyandry and inbreeding strategies
+Selection greatly weakened for a relatively more costly inbreeding strategy
 ----------------------------------------------
@@
 However, when the alternative inbreeding strategy could evolve and was not costly, the focal costly inbreeding strategy evolved toward random choice given increasingly negative allele values of the alternative strategy over generations (Figure 3B,D).
-For example, given fixed $F_{a}=0$, grand mean $M_{a}$ values were $-0.868$ in the last $10000$ generations of evolution (Figure 3A), meaning that an outbred focal female was ca $5.34$ times less likely to choose a full-sibling and ca $2.10$ times less likely to choose a first cousin than a non-relative given a strong cost of pre-copulatory inbreeding avoidance, $c_{M}=0.02$.
-In contrast, grand mean $M_{a}$ allele values were $-0.288$ when post-copulatory inbreeding avoidance evolved.
-More strongly, given fixed $M_{a}=0$, grand mean $F_{a}$ values were $-1.092$ in the last $10000$ generations of evolution (Figure 3C), meaning that an outbred focal female was ca $6.46$ times less likely to choose a full-sibling and ca $2.37$ times less likely to choose a first cousin than a non-relative given a strong cost of pre-copulatory inbreeding avoidance, $c_{F}=0.02$.
+For example, given fixed $F_{a}=0$, grand mean $M_{a}$ values were $-0.868$ in the last $10000$ generations (Figure 3A), meaning that an outbred focal female was ca $5.34$ times less likely to choose a full-sibling and ca $2.10$ times less likely to choose a first cousin than a non-relative given a strong cost of pre-copulatory inbreeding avoidance, $c_{M}=0.02$.
+In contrast, grand mean $M_{a}$ allele values were $-0.288$ when post-copulatory inbreeding avoidance also evolved.
+More strongly, given fixed $M_{a}=0$, grand mean $F_{a}$ values were $-1.092$ in the last $10000$ generations (Figure 3C), meaning that an outbred focal female was ca $6.46$ times less likely to choose a full-sibling and ca $2.37$ times less likely to choose a first cousin than a non-relative given a strong cost of pre-copulatory inbreeding avoidance, $c_{F}=0.02$.
 However, grand-mean $F_{a}$ values were $-0.070$ when pre-copulatory inbreeding strategy evolved, and polyandry allele values were negative.
@@
 
-<!--- Figure 1 shows changes in mean allele values of tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy across all eight possible combinations of costs.
-In Figure 1A, when no phenotypes are costly, inbreeding mating strategy and inbreeding fertilisation strategy evolve to inbreeding avoidance ($M_{a}<0$ and $F_{a}<0$), and females evolve to be polyandrous ($P_{a}>0$).
-Costs of phenotypes had a direct effect on evolution, causing inbreeding mating strategy and inbreeding fertilisation strategy phenotypes to evolve to values closer to zero (because realisation of inbreeding strategy costs increases with phenotype absolute values) and tendency for polyandry phenotypes to evolve to values that were more negative (because realisation of polyandry costs increases with positive phenotype values).
+<!--- Figure 1 shows changes in mean allele values of tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy across all eight possible combinations of costs.
+In Figure 1A, when no phenotypes are costly, pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy evolve to inbreeding avoidance ($M_{a}<0$ and $F_{a}<0$), and females evolve to be polyandrous ($P_{a}>0$).
+Costs of phenotypes had a direct effect on evolution, causing pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy phenotypes to evolve to values closer to zero (because realisation of inbreeding strategy costs increases with phenotype absolute values) and tendency for polyandry phenotypes to evolve to values that were more negative (because realisation of polyandry costs increases with positive phenotype values).
 --->
 
-<!--- We can use Figure 1 to test the hypothesis that inbreeding mating strategy will evolve to inbreeding avoidance ($M_{a}<0$), but inbreeding fertilisation strategy will be negligible ($F_{a} \approx 0$) when mating costs are low ($c_{M}=0$) relative to the costs of tendency for polyandry and inbreeding fertilisation strategy ($c_{P}=0.02$ or $c_{F}=0.02$) by comparing different cost combinations to the null model in which all costs equal zero (Figure 1A).
+<!--- We can use Figure 1 to test the hypothesis that pre-copulatory inbreeding strategy will evolve to inbreeding avoidance ($M_{a}<0$), but post-copulatory inbreeding strategy will be negligible ($F_{a} \approx 0$) when mating costs are low ($c_{M}=0$) relative to the costs of tendency for polyandry and post-copulatory inbreeding strategy ($c_{P}=0.02$ or $c_{F}=0.02$) by comparing different cost combinations to the null model in which all costs equal zero (Figure 1A).
 Figure 1A,C,D,G show that inbreeding avoidance in mating ($M_{a}<0$) evolved consistently whenever $c_{M}=0$.
-When inbreeding fertilisation strategy was costly and inbreeding avoidance strategy was not costly (Figure 1D,G), inbreeding fertilisation strategy initially evolved toward inbreeding avoidance ($F_{a} < 0$), but long-term evolution of inbreeding fertilisation strategy stabilised at random mating ($F_{a} \approx 0$).
-However, when only tendency for polyandry was costly (Figure 1C), both inbreeding mating strategy and inbreeding fertilisation strategy evolved to inbreeding avoidance over generations ($M_{a} < 0$ and $F_{a} < 0$).
+When post-copulatory inbreeding strategy was costly and inbreeding avoidance strategy was not costly (Figure 1D,G), post-copulatory inbreeding strategy initially evolved toward inbreeding avoidance ($F_{a} < 0$), but long-term evolution of post-copulatory inbreeding strategy stabilised at random mating ($F_{a} \approx 0$).
+However, when only tendency for polyandry was costly (Figure 1C), both pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy evolved to inbreeding avoidance over generations ($M_{a} < 0$ and $F_{a} < 0$).
 --->
 
-<!--- We can also use Figure 1 to test the hypothesis that inbreeding fertilisation strategy will evolve to inbreeding avoidance ($F_{a}<0$), but inbreeding mating strategy will be negligible ($M_{a} \approx 0$) when tendency for polyandry and inbreeding fertilisation strategy costs are low ($c_{P}=0$ and $c_{F}=0$) relative to the cost of inbreeding mating strategy ($c_{M}=0.02$).
+<!--- We can also use Figure 1 to test the hypothesis that post-copulatory inbreeding strategy will evolve to inbreeding avoidance ($F_{a}<0$), but pre-copulatory inbreeding strategy will be negligible ($M_{a} \approx 0$) when tendency for polyandry and post-copulatory inbreeding strategy costs are low ($c_{P}=0$ and $c_{F}=0$) relative to the cost of pre-copulatory inbreeding strategy ($c_{M}=0.02$).
 Figure 1B shows that inbreeding avoidance through fertilisation bias evolved ($F_{a}<0$) under these conditions.
-While inbreeding mating strategy initially evolved toward inbreeding avoidance ($M_{a} < 0$), long-term evolution of inbreeding mating strategy stabilised at random mating ($M_{a} \approx 0$).
+While pre-copulatory inbreeding strategy initially evolved toward inbreeding avoidance ($M_{a} < 0$), long-term evolution of pre-copulatory inbreeding strategy stabilised at random mating ($M_{a} \approx 0$).
 --->
@@
 
-<!--- Figure 3 shows evolution of tendency for polyandry and inbreeding fertilisation strategy when inbreeding mating strategy is fixed so that females must mate randomly (blue line at $M_{a}=0$).
-For all cost combinations of tendency for polyandry and inbreeding fertilisation strategy (Figure 3 panels A-D), we observed selection for positive values of tendency for polyandry alleles and negative values of inbreeding fertilisation strategy alleles, which we interpret as strong evidence for evolution of polyandry and associated inbreeding avoidance through fertiisation bias.
-This pattern of evolution contrasts with that observed when inbreeding mating strategy was not fixed, indicating that constraints on evolution of inbreeding mating strategy increased the strength of selection for evolution of polyandry and inbreeding avoidance through fertilisation bias.
-For example, in Figures 1C,D,G,H, tendency for polyandry allele values were typically less than zero, reflecting evolution of monandry, and inbreeding fertilisation strategy allele values were not as negative as they were in simulations with fixed random mating (Figure 3).
+<!--- Figure 3 shows evolution of tendency for polyandry and post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed so that females must mate randomly (blue line at $M_{a}=0$).
+For all cost combinations of tendency for polyandry and post-copulatory inbreeding strategy (Figure 3 panels A-D), we observed selection for positive values of tendency for polyandry alleles and negative values of post-copulatory inbreeding strategy alleles, which we interpret as strong evidence for evolution of polyandry and associated inbreeding avoidance through fertiisation bias.
+This pattern of evolution contrasts with that observed when pre-copulatory inbreeding strategy was not fixed, indicating that constraints on evolution of pre-copulatory inbreeding strategy increased the strength of selection for evolution of polyandry and inbreeding avoidance through fertilisation bias.
+For example, in Figures 1C,D,G,H, tendency for polyandry allele values were typically less than zero, reflecting evolution of monandry, and post-copulatory inbreeding strategy allele values were not as negative as they were in simulations with fixed random mating (Figure 3).
 In general, when females were unable to avoid mating with relatives given severe inbreeding depression ($\beta=3$), selection for evolution of polyandry and post-copulatory inbreeding avoidance was strengthened.
@@
 
-<!--- Figure 2, which we previously contrasted with Figure 1 to test whether or not evolution of inbreeding fertilisation strategy facilitates selection for polyandry, shows evolution of tendency for polyandry and inbreeding mating strategy when inbreeding fertilisation strategy is fixed such that the sire of a focal female's offspring is randomly assigned from her mates according to a fair raffle.
+<!--- Figure 2, which we previously contrasted with Figure 1 to test whether or not evolution of post-copulatory inbreeding strategy facilitates selection for polyandry, shows evolution of tendency for polyandry and pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy is fixed such that the sire of a focal female's offspring is randomly assigned from her mates according to a fair raffle.
 In all cost combinations of Figure 2 (panels A-D), tendency for polyandry allele values decreased over generations, reflecting evolution of monandry.
-However, values of inbreeding mating strategy alleles did not greatly differ over generations when inbreeding fertilisation strategy was fixed, meaning that the effect of fixed inbreeding fertilisation strategy on increasing selection for inbreeding avoidance through mate choice was weak or nelgigible.
-A weak effect is discernable in the contrast between Figure 2B and Figure 1B, in which the grand mean inbreeding mating strategy allele value is $-0.627$ when inbreeding fertilisation strategy is not fixed (Figure 1B) versus $-1.036$ when it is fixed (Figure 2B) in generation 10000.
-Because females have 20 alleles with additive effects on inbreeding mating strategy, an average female was therefore expected to have mean inbreeding mating strategy phenotype values of $M_{p} = -0.627 \times 20 = -12.54$ and $M_{p} = -1.036 \times 20 = -20.72$ for not fixed versus fixed inbreeding fertilisation strategy, respectively.
-These values would cause an outbred focal female to be $2.135$ and $4.180$ times more likely to choose a non-relative than a full sibling as a mate given not fixed versus fixed inbreeding fertilisation strategy, respectively.
+However, values of pre-copulatory inbreeding strategy alleles did not greatly differ over generations when post-copulatory inbreeding strategy was fixed, meaning that the effect of fixed post-copulatory inbreeding strategy on increasing selection for inbreeding avoidance through mate choice was weak or nelgigible.
+A weak effect is discernable in the contrast between Figure 2B and Figure 1B, in which the grand mean pre-copulatory inbreeding strategy allele value is $-0.627$ when post-copulatory inbreeding strategy is not fixed (Figure 1B) versus $-1.036$ when it is fixed (Figure 2B) in generation 10000.
+Because females have 20 alleles with additive effects on pre-copulatory inbreeding strategy, an average female was therefore expected to have mean pre-copulatory inbreeding strategy phenotype values of $M_{p} = -0.627 \times 20 = -12.54$ and $M_{p} = -1.036 \times 20 = -20.72$ for not fixed versus fixed post-copulatory inbreeding strategy, respectively.
+These values would cause an outbred focal female to be $2.135$ and $4.180$ times more likely to choose a non-relative than a full sibling as a mate given not fixed versus fixed post-copulatory inbreeding strategy, respectively.
 Therefore, when females were unable to bias fertilisation to avoid inbreeding given severe inbreeding depression ($\beta=3$), selection for evolution of pre-copulatory inbreeding avoidance was strengthened.
@@
 
-Selection given a pre-existing adaptive inbreeding strategy
+Existing adaptation preclude post- but not pre-copulatory inbreeding avoidance
 ----------------------------------------------
@@
 Our third hypothesis that invasion of pre- or post-copulatory inbreeding avoidance would be precluded by the existence of an already adaptive complementary strategy was supported for invading post-copulatory, but not pre-copulatory, inbreeding avoidance.
-When pre-copulatory inbreeding strategy was initialised for random mating, but polyandry and post-copulatory inbreeding strategy allele values were fixed for adaptive inbreeding avoidance (Figure 4A,B), negative pre-copulatory inbreeding allele values became increasingly more freqent ($M_{a}<0$), causing inbreeding avoidance in mate choice.
+When pre-copulatory inbreeding strategy was initialised for random mating, but polyandry and post-copulatory inbreeding strategy allele values were fixed for adaptive inbreeding avoidance (Figure 4A,B), negative pre-copulatory inbreeding allele values became increasingly more frequent ($M_{a}<0$), causing inbreeding avoidance in mate choice.
 However, $M_{a}$ values were not as negative after $40000$ generations when post-copulatory inbreeding avoidance and polyandry were fixed as they were when no post-copulatory inbreeding avoidance occurred (e.g., compare Figure 4A with Figure 1A, and Figure 4B with Figure 2A).
@@
 
-<!--- Figure 4 shows change in inbreeding mating strategy allele values over generations when tendency for polyandry and inbreeding fertilisation strategy alleles were fixed for adaptive values of inbreeding avoidance $P_{a}=1$ and $F_{a}=-5$.
-Despite that females in these simulations could already avoid inbreeding after mating occurred, inbreeding mating strategy evolved towards inbreeding avoidance given costs of $c_{M}=0$ (Figure 4A) and $c_{M}=0.02$ (Figure 4B).
+<!--- Figure 4 shows change in pre-copulatory inbreeding strategy allele values over generations when tendency for polyandry and post-copulatory inbreeding strategy alleles were fixed for adaptive values of inbreeding avoidance $P_{a}=1$ and $F_{a}=-5$.
+Despite that females in these simulations could already avoid inbreeding after mating occurred, pre-copulatory inbreeding strategy evolved towards inbreeding avoidance given costs of $c_{M}=0$ (Figure 4A) and $c_{M}=0.02$ (Figure 4B).
 We therefore did not find evidence that the existence of adaptive inbreeding avoidance through fertilisation bias in any way precluded the evolution of adaptive inbreeding avoidance through mate choice.
@@
 
-<!--- Figure 5 shows change in tendency for polyandry and inbreeding fertilisation strategy allele values over generations when inbreeding mating strategy alleles were fixed for adaptive inbreeding avoidance $M_{a}=-5$.
-Existence of adaptive inbreeding avoidance through mate choice precluded evolution of polyandry for all combinations of costs (Figure 5), meaning that evolution of adpative polyandry to avoid inbreeding through inbreeding fertilisation strategy was never predicted in populations where females were already avoiding inbreeding through mate choice.
-Further, while inbreeding fertilisation strategy evolved toward inbreeding avoidance ($F_{a}<0$) in the absence of costs (Figure 5A,B), allele values of inbreeding fertilisation strategy were not as negative as when adaptive inbreeding avoidance through mate choice was not fixed at the outset (Figures 1A,B,C,D).
+<!--- Figure 5 shows change in tendency for polyandry and post-copulatory inbreeding strategy allele values over generations when pre-copulatory inbreeding strategy alleles were fixed for adaptive inbreeding avoidance $M_{a}=-5$.
+Existence of adaptive inbreeding avoidance through mate choice precluded evolution of polyandry for all combinations of costs (Figure 5), meaning that evolution of adpative polyandry to avoid inbreeding through post-copulatory inbreeding strategy was never predicted in populations where females were already avoiding inbreeding through mate choice.
+Further, while post-copulatory inbreeding strategy evolved toward inbreeding avoidance ($F_{a}<0$) in the absence of costs (Figure 5A,B), allele values of post-copulatory inbreeding strategy were not as negative as when adaptive inbreeding avoidance through mate choice was not fixed at the outset (Figures 1A,B,C,D).
 We therefore found strong evidence that the existence of adaptive inbreeding avoidance through pre-copulatory mate choice precluded evolution of adaptive inbreeding avoidance through post-copulatory inbreeding avoidance through fertilisation bias.
@@
 
-We modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency to engage in polyandry, inbreeding mating strategy (pre-copulatory), and inbreeding fertilisation strategy (post-copulatory).
+We modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency to engage in polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
 Using *in silico* experiments, we tested three specific hypothesis to predict evolution of polyandry, and pre- and post-copulatory inbreeding strategy.
@@
 
-Specific mechanisms of post-copulatory inbreeding avoidance are difficult to identify, but recent experimental studies have shown how females can successfully bias fetilisation after mating has occurred in both vertebrates [e.g., @Gasparini2011] and invertebrates [e.g., @Tuni2013].
+Specific mechanisms of post-copulatory inbreeding avoidance are difficult to identify, but recent experimental studies have shown how females can successfully bias fertilisation after mating has occurred in both vertebrates [e.g., @Gasparini2011] and invertebrates [e.g., @Tuni2013].
 For example, @Gasparini2011 artificially inseminated female guppies (*Poecilia reticulata*) with equal quantities of sperm from full-siblings and unrelated males, finding that fertilisation success was higher in non-relatives because the velocity of full siblings' sperm was reduced by females' ovarian fluids.
@@
 This general property of threshold traits causes maladaptive phenotypes to frequently reappear within populations due to the mutation and recombination of continuous genetic values underlying discrete phenotypes [@Roff1996; @Roff1998].
-Assuming that there is continuous genetic variation underlying threshold polyandry, polyandrous phenotypes are therefore sometimes predicted to persist within populations even when costly [@Duthie], potentially creating the possibility for selection on inbreeding fertilisation strategy when polyandry is expressed.
+Assuming that there is continuous genetic variation underlying threshold polyandry, polyandrous phenotypes are therefore sometimes predicted to persist within populations even when costly [@Duthie], potentially creating the possibility for selection on post-copulatory inbreeding strategy when polyandry is expressed.
 This is most evident in Figure 1C, where mean allele values for polyandry are negative (red line), but strong post-copulatory inbreeding avoidance is still predicted (grey line).
@@
 @Pomiankowski1987 categorised four types of costs that are relevant to mate choice, which we suggest are also relevant costs for polyandry, and include costs of elevated risks associated with (1) predation or (2) disease transmission, and costs incurred through (3) loss of time or (4) depletion of energy.
-In our model, we interpreted a cost of tendency for polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of inbreeding mating strategy as a lost of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of inbreeding fertilisation strategy as depletion of energy.
+In our model, we interpreted a cost of tendency for polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of pre-copulatory inbreeding strategy as a lost of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of post-copulatory inbreeding strategy as depletion of energy.
 While these costs are biologically realistic, different costs will be relevant for different populations and be realised in different ways.
@@
 
-Individual traits (A), model parameter values (B), and model variables (C) for an individual based model of the evolution of polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
+Individual traits (A), model parameter values (B), and model variables (C) for an individual based model of the evolution of polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
 
@@
 |       | Tendency for polyandry              | $P_{a}$     | $P_{g}$       | $P_{p}$
-|       | Inbreeding mating strategy          | $M_{a}$     | $M_{g}$       | $M_{p}$
-|       | Inbreeding fertilisation strategy   | $F_{a}$     | $F_{g}$       | $F_{p}$
+|       | Pre-copulatory inbreeding strategy  | $M_{a}$     | $M_{g}$       | $M_{p}$
+|       | Post-copulatory inbreeding strategy | $F_{a}$     | $F_{g}$       | $F_{p}$
 |       |                                     |             |               |
@@
 |       | Cost of tendency for polyandry                 | $c_{P}$        | | $0$, $0.02$
-|       | Cost of inbreeding mating strategy             | $c_{M}$        | | $0$, $0.02$
-|       | Cost of inbreeding fertilisation strategy      | $c_{F}$        | | $0$, $0.02$
+|       | Cost of pre-copulatory inbreeding strategy     | $c_{M}$        | | $0$, $0.02$
+|       | Cost of post-copulatory inbreeding strategy    | $c_{F}$        | | $0$, $0.02$
 |       | Focal female's number of offspring             | $n$            | | $8$
@@
 
-![Mean allele values underlying tendency for polyandry (red lines and shading), inbreeding mating strategy (i.e., pre-copulatory choice; blue lines and shading), and inbreeding fertilisation strategy (i.e., post-copulatory choice; black lines and shading), as calculated across all individuals within a population over 10000 generations given strong inbreeding depression.
+![Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
 Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
 Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panels A-H show simulations for different combinations of costs for tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
-Dotted horizontal black lines in panels show values of zero on the y-axis.](Initial_Results/figures/evo_combs02_B3.png)
+Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre- and post-copulatory inbreeding avoidance.
+Costs of polyandry increase with rows from top to bottom.
+Dotted horizontal black lines in panels show values of zero on the y-axis.](figures/poly_costs.png)
 
-![Mean allele values underlying tendency for polyandry (red lines and shading) and inbreeding mating strategy (i.e., pre-copulatory choice; blue lines and shading), as calculated across all individuals within a population over 10000 generations given strong inbreeding depression when allele values underlying inbreeding fertilisation strategy (i.e., post-copulatory choice) are fixed for random fertilisation among mates (black horizontal lines where y-axes equal zero).
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panels A-D show simulations for different combinations of costs for tendency for polyandry and inbreeding mating strategy.](Initial_Results/figures/evo_combs02_B3_ko_F.png)
+![](figures/Pp_vals1.png)
 
-![Mean allele values underlying tendency for polyandry (red lines and shading) and inbreeding fertilisation strategy (i.e., post-copulatory choice; black lines and shading), as calculated across all individuals within a population over 10000 generations given strong inbreeding depression when allele values underlying inbreeding mating strategy (i.e., pre-copulatory choice) are fixed for random mating (blue horizontal lines where y-axes equal zero).
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panels A-D show simulations for different combinations of costs for tendency for polyandry and inbreeding mating strategy.](Initial_Results/figures/evo_combs02_B3_ko_M-0.png)
+![](figures/rel_costs.png)
 
-![Mean allele values underlying inbreeding mating strategy (i.e., pre-copulatory choice; blue lines and shading), as calculated across all individuals within a population over 10000 generations given strong inbreeding depression and the pre-existence of polyandry to avoid inbreeding (tendency for polyandry allele values equal 1, as indicated by horizontal red lines; inbreeding fertilisation strategy values equal -5, as indicated by horizontal black lines).
-Solid blue lines represent grand means over 40 replicate populations, and blue shading around solid lines shows standard errors of mean inbreeding mating strategy allele values around grand means.
-Negative mean allele values reflect a strategy of inbreeding avoidance, and positive values reflect a strategy of inbreeding preference.
-Panels A and B show replicate simulations in which inbreeding mating strategy is not costly and has a cost of 0.02, respectively.
-Dotted horizontal black lines in panels show values of zero on the y-axis.](Initial_Results/figures/evo_combs02_B3_ko_FP-5.png)
-
-![Mean allele values underlying tendency for polyandry (red lines and shading) and inbreeding fertilisation strategy (i.e., post-copulatory choice; black lines and shading), as calculated across all individuals within a population over 10000 generations given strong inbreeding depression and the pre-existence of inbreeding avoidance in mate choice (inbreeding mating strategy values equal -5, as indicated by horizontal blue lines).
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panels A-D show simulations for different combinations of costs for tendency for polyandry and inbreeding mating strategy.
-Dotted horizontal black lines in panels show values of zero on they-axis.
-](Initial_Results/figures/evo_combs02_B3_ko_M-5.png)
+![](figures/fixed_adapt.png)
 

### 2016-09-28 ms_pre_post.Rmd
Add figure legends

@@
 
-![](figures/Pp_vals1.png)
+![Relationship between polyandry allele values and phenotypes for an individual-based model in which pre- and post-copulatory inbreeding strategies evolve jointly with polyandry.
+The red line in (A) shows the mean value of alleles underlying polyandry for a single replicate simulation over 40000 generations.
+Positive allele values contribute to polyandry, while negative values contribute to monandry (dotted line shows zero on the y-axis).
+In the last generation, mean allele value was below zero.
+Nevertheless, due to among-individual variation and the threshold nature of the polyandry phenotype, polyandry persists in the population.
+The histogram in (B) shows females' tendency for polyandry phenotypes in the last generation; white and grey shading indicates monandrous and polyandrous females, respectively.
+While the average female was monandrous, several females were polyandrous.](figures/Pp_vals1.png)
 
-![](figures/rel_costs.png)
+![Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Panel (A) shows evolution of costly pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy is fixed for random fertilisation (solid black horizontal line), while (B) instead allows post-copulatory inbreeding strategy to evolve under otherwise identical conditions.
+Similarly, panel (C) shows evolution of costly post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for random mating (solid blue horizontal line), while (D) allows pre-copulatory inbreeding strategy to evolve under otherwise identical conditions.](figures/rel_costs.png)
 
-![](figures/fixed_adapt.png)
+![Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Panel (A) shows evolution of pre-copulatory inbreeding strategy given fixed polyandry (solid red line) and inbreeding avoidance (solid black line), and (B) shows these same conditions given a cost of pre-copulatory inbreeding strategy.
+Similarly, panel (C) shows evolution of polyandry and post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for inbreeding avoidance (solid blue line), while (D) shows these same conditions given a cost of post-copulatory inbreeding strategy.](figures/fixed_adapt.png)
 

### 2016-09-28 ms_pre_post.Rmd
Add minor tweaks before sending to coauthors

@@
 Accordingly, we use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address three questions: Will evolution of post-copulatory inbreeding avoidance strengthen selection for polyandry?
-Will selection for a costly inbreeding strategy be negligible given a non-costly complementary strategy?
+Will selection for a costly inbreeding strategy be negligible given a non-costly alternative strategy?
 And will selection for an inbreeding strategy be negligible given existence of an already adaptive alternative strategy?
@@
 We record the coefficient of kinship ($k$), defined as the probability that a randomly selected homologous allele from each individual is identical-by-descent [@Lynch1998], between all pairs of individuals in each generation using the population pedigree [see @Boyce1983; @Duthie].
-At the start of each generation, each female pays up to three independent costs of (1) tendency to engage in polyandry ($c_{P}$), (2) mating strategy with respect to inbreeding ($c_{M}$), and (3) fertilisation strategy with respect to inbreeding ($c_{F}$).
+At the start of each generation, each female pays up to three independent costs of (1) tendency to engage in polyandry ($c_{P}$), (2) pre-copulatory inbreeding strategy (i.e., cost of mate choice; $c_{M}$), and (3) post-copulatory inbreeding strategy (i.e., cost of fertilisation bias; $c_{F}$).
 The number of males that a focal female mates with ($N_{males}$) is determined by the effects of 20 alleles ($P_{a}$) across 10 diploid loci that combine additively to determine her genotype ($P_{g}$), and ultimately her phenotype for tendency to engage in polandry ($P_{p}$).
@@
 After costs are paid, each remaining female chooses a number of males to mate with ($N_{males}$) based on her genetically determined tendency to engage in polyandry ($P_{p}$).
-The exact value of $N_{males}$ is calculated by randomly sampling from a poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
+The exact value of $N_{males}$ is calculated by randomly sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
 This random sampling procedure causes some stochastic variation in the number of realised mates a that female chooses, with a mean $N_{males}$ of $P_{p}+1$.
@@
 Hence, negative values of $P_{g}$ are translated to $P_{p}$ values of zero such that $P_{p} = 0$ when $P_{g} < 0$, but when $P_{g} \geq 0$, then $P_{p} = P_{g}$ (i.e., the phenotype value of polyandry equals the genotype value of polyandry if and only if the genotype value is greater than or equal to zero, else the phenotype value of polyandry always equals zero).
-The resulting $P_{p}$ is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998; @Duthie], in which polyandry is expressed discretely at the threshold value of $P_{g} > 0$, but is determined by the consequence of continuous genetic variation arising from the effects of $P_{a}$ alleles that each contribute additively to a female's tendency toward polyandry.
+The resulting $P_{p}$ is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998; @Duthie], in which polyandry is expressed discretely at the threshold value of $P_{g} > 0$, but is determined by the consequence of continuous genetic variation arising from the effects of $P_{a}$ alleles that each contribute additively to polyandry.
 Negative genotype values of $P_{g}$ therefore all have the same phenotype, resulting in consistently monandrous females.
@@
 As with polyandry and pre-copulatory inbreeding strategy phenotypes, a female's post-copulatory inbreeding strategy phenotype is determined by the summed effects of 20 post-copulatory inbreeding strategy alleles ($F_{a}$), which can take any real number.
-The sum of all of a female's $F_{a}$ alleles determine her post-copulatory inbreeding strategy genotype ($F_{g}$), which is identical to her post-copulatory inbreeding strategy phenotype ($F_{p}$).
-As with pre-copulatory inbreeding strategy phenotype ($M_{p}$), negative or positive values of $F_{p}$ correspond to inbreeding avoidance or preference respectively, and $F_{p}=0$ causes random fertilisation with respect to kinship.
+The sum of all of a female's $F_{a}$ alleles determines her post-copulatory inbreeding strategy genotype ($F_{g}$), which is identical to her post-copulatory inbreeding strategy phenotype ($F_{p}$).
+As with pre-copulatory inbreeding strategy phenotype ($M_{p}$), negative or positive values of $F_{p}$ correspond to inbreeding avoidance or preference, respectively, and $F_{p}=0$ causes random fertilisation with respect to kinship.
 
@@
 
-We first test our hypothesis that a focal female's ability to express post-copulatory choice with respect to kinship causes selection for polyandry by comparing simulations in which post-copulatory inbreeding strategy is fixed to random mating with respect to kinship to simulations in which tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy can all evolve.
+<!--- We first test our hypothesis that a focal female's ability to express post-copulatory choice with respect to kinship causes selection for polyandry by comparing simulations in which post-copulatory inbreeding strategy is fixed to random mating with respect to kinship to simulations in which tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy can all evolve.
+--->
+
 For low costs of tendency for polyandry, $c_{P} < 0.005$, selection caused expected tendency for polyandry allele values ($P_{a}$) to be positive only when post-copulatory inbreeding avoidance evolved (Figure 1A-D), and for all $c_{P}$, $P_{a}$ values were higher when post-copulatory inbreeding avoidance evolved than when it could not evolve (Figure 1).
@@
 
-Our second hypothesis that selection for a costly inbreeding avoidance strategy will be negligible given a less costly alternative was generally supported by our simulations (Figure 3).
-For simulations in which either pre- or post-copulatory inbreeding strategy allele values were fixed for random choice with respect to kinship ($M_{a}=0$ or $F_{a}=0$, respectively), the alternative costly inbreeding strategy evolved to inbreeding avoidance ($F_{a}<0$ or $M_{a}<0$).
-However, when the alternative inbreeding strategy could evolve and was not costly, the focal costly inbreeding strategy evolved toward random choice given increasingly negative allele values of the alternative strategy over generations (Figure 3B,D).
+<!--- Our second hypothesis that selection for a costly inbreeding avoidance strategy will be negligible given a less costly alternative was generally supported by our simulations (Figure 3).  --->
+
+For simulations in which either pre- or post-copulatory inbreeding strategy allele values were fixed for random choice with respect to kinship ($M_{a}=0$ or $F_{a}=0$, respectively), the alternative costly inbreeding strategy evolved to inbreeding avoidance ($F_{a}<0$ or $M_{a}<0$; Figure 3).
+However, when the alternative inbreeding strategy could evolve and was not costly, the focal costly inbreeding strategy initially evolved towards inbreeding avoidance, but then evolved toward random choice given increasingly negative allele values of the alternative strategy over generations (Figure 3B,D).
 For example, given fixed $F_{a}=0$, grand mean $M_{a}$ values were $-0.868$ in the last $10000$ generations (Figure 3A), meaning that an outbred focal female was ca $5.34$ times less likely to choose a full-sibling and ca $2.10$ times less likely to choose a first cousin than a non-relative given a strong cost of pre-copulatory inbreeding avoidance, $c_{M}=0.02$.
@@
 
-Our third hypothesis that invasion of pre- or post-copulatory inbreeding avoidance would be precluded by the existence of an already adaptive complementary strategy was supported for invading post-copulatory, but not pre-copulatory, inbreeding avoidance.
+<!--- Our third hypothesis that invasion of pre- or post-copulatory inbreeding avoidance would be precluded by the existence of an already adaptive complementary strategy was supported for invading post-copulatory, but not pre-copulatory, inbreeding avoidance.
+--->
+
 When pre-copulatory inbreeding strategy was initialised for random mating, but polyandry and post-copulatory inbreeding strategy allele values were fixed for adaptive inbreeding avoidance (Figure 4A,B), negative pre-copulatory inbreeding allele values became increasingly more frequent ($M_{a}<0$), causing inbreeding avoidance in mate choice.
@@
 Using *in silico* experiments, we tested three specific hypothesis to predict evolution of polyandry, and pre- and post-copulatory inbreeding strategy.
-We found that (1) selection for polyandry was greatly strengthened given concurrent evolution of post-copulatory inbreeding avoidance, (2) selection for costly pre- or post-copulatory inbreeding avoidance was negligible given evolution of a less costly strategy of inbreeding avoidance, and (3) pre-existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of post-copulatory inbreeding avoidance, but not vice versa.
+We found that (1) selection for polyandry was greatly strengthened given concurrent evolution of post-copulatory inbreeding avoidance, (2) selection for costly pre- or post-copulatory inbreeding avoidance was negligible given evolution of a less costly strategy of inbreeding avoidance, and (3) pre-existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance, but not vice versa.
 More generally, we provide a novel framework for approaching empirical studies of inbreeding avoidance, predicting evolution of polyandry and inbreeding avoidance through pre- and post-copulatory mechanisms.

### 2016-09-28 analysis.R
Fix error creating vector of simulation numbers

@@ -40,7 +40,7 @@ axis(side=2,at=c(-20,-10,0,10), cex.axis=1.5);
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 #points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 abline(h=0,lwd=0.8,lty="dotted");
-abline(h=0,lwd=3);
+points(x=1:gens,y=rep(0,length(1:gens)),type="l",lwd=2,col="black");
 uWP <- mWP + sWP / sqrt(sum(evo[,6]==gens));
 lWP <- mWP - sWP / sqrt(sum(evo[,6]==gens));
 uPO <- mPO + sPO / sqrt(sum(evo[,6]==gens));
@@ -53,7 +53,8 @@ polygon(y=c(lWP,rev(uWP)),x=c(1:(gens+1),(gens+1):1),border=NA,col="lightblue");
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 #points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 points(x=xxx,y=mWP,type="l",lwd=2,col="blue");
-text(x=0, y=-22.0, label=expression(paste(c[P]==0.0)),cex=1.5, pos=4);
+text(x=-300, y=-23.0, label=expression(paste(c[P]==0.0)),cex=1.5, pos=4);
+text(x=-300, y=11.0, label="A", cex=2, pos=4);
 rm(evo_cc_02);
 # ------------------------------------------------------------------------#
 evo_cc_02 <- read.table(file="results/fig2/evo_M00_P00_F00.txt", header=FALSE);
@@ -84,7 +85,8 @@ polygon(y=c(lWP,rev(uWP)),x=c(1:(gens+1),(gens+1):1),border=NA,col="lightblue");
 points(x=xxx,y=mPO,type="l",lwd=2,col="red");
 points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 points(x=xxx,y=mWP,type="l",lwd=2,col="blue");
-text(x=0, y=-22.0, label=expression(paste(c[P]==0.00)),cex=1.5, pos=4);
+text(x=-300, y=-23.0, label=expression(paste(c[P]==0.00)),cex=1.5, pos=4);
+text(x=-300, y=11.0, label="B", cex=2, pos=4);
 rm(evo_cc_02);
 # ------------------------------------------------------------------------#
[…]

### 2016-09-29 ms_pre_post.Rmd
Add caveat that invasion of strategy results change for post-copulatory inbreeding avoidance when polyandry is fixed

@@
 However, when $c_{F}=0.02$, $F_{a}$ values remained near zero to minimise direct costs.
+This lack of evolution of post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
+When pre-copulatory inbreeding avoidance and polyandry were both fixed ($F_{a}=-10$ and $P_{a}=1$), post-copulatory inbreeding strategy evolved to similarly negative mean allele values as pre-copulatory inbreeding strategy did in Figure 4A,B (see Supporting Information).
 

### 2016-09-29 analysis.R
Add new supporting figure showing fixed pre-copulatory inbreeding and polyandry

@@ -1002,6 +1002,99 @@ mtext(expression(paste("Mean allele value")),
 dev.off();
 #==========================================================================
 
+
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+
+
+
+setEPS(); # postscript below for final publication?
+cairo_ps("figures/extra_MfPf.eps",family="Arial",height=6,width=8);
+par(mfrow=c(1,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
+# ------------------------------------------------------------------------#
+evo_cc_02 <- read.table(file="results/fig3_new/evo_Mf-10_Pf1_F00.txt", header=FALSE);
+evB <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
+evo <- evB[evB[,2]==beta_val,];
+mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
+mPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=mean);
+mEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=mean);
+sWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=sd);
+sPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=sd);
+sEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=sd);
+xxx <- tapply(X=evo[,6],INDEX=evo[,6],FUN=mean);
+len <- dim(evo)[1];
+plot(x=xxx,y=mWP,type="n",lwd=2,ylim=c(-24,14),col="blue",xaxt="n",
+     xlab="",ylab="Allele value",cex.lab=2,cex.axis=1.5,yaxt="n");
+axis(side=2,at=c(-20,-10,0,10), cex.axis=1.5);
+axis(side=1,at=c(0,10000,20000,30000), cex.axis=1.5);
[…]

### 2016-09-30 Supplement.tex
Initialise supporting information TEX file

\documentclass[12pt]{article}
\usepackage[top=1.25in, bottom=1in, left=1.25in, right=1in]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{lineno}
\usepackage{datetime}
\setkomafont{\rmfamily\bfseries\boldmath}
\usepackage{wrapfig,floatrow}
\usepackage{float}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{fancyhdr}
\usepackage{titling}
\usepackage{bm}
\floatstyle{plain}
\restylefloat{figure}

\newcommand\mydef{\mathrel{\stackrel{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily def}}}{=}}}

\def\wl{\par \vspace{\baselineskip}} %defines \wl as a line skip.

\renewcommand{\thesection}{S1.\arabic{section}}
\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}
\renewcommand{\thepage}{S1-\arabic{page}}

\makeatletter %% With ams
\def\tagform@#1{\maketag@@@{(S1-\ignorespaces#1\unskip\@@italiccorr)}}
\makeatother

\makeatletter
\makeatletter \renewcommand{\fnum@figure}
{\figurename~S1-\thefigure}
\makeatother

\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}

\setcitestyle{round,aysep={},yysep={;}}

\makeatletter
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
\begin{flushleft}
  \fontsize{18}{16}
  \textbf{\@title}
  \vspace{8 mm}
  \fontsize{12}{14}
  \@author
\end{flushleft}\egroup
}
\makeatother

%\newlength{\saveparindent} %Makes ragged right alignment for Evolution
\setlength{\saveparindent}{\parindent} %Does not suppress paragraph indents
%\raggedright
\setlength{\parindent}{\saveparindent}

\renewcommand\refname{LITERATURE CITED}
\newcommand*\mystrut[1]{\vrule width0pt height1pt depth#1\relax}
\newcommand={\mathrel{\stackrel{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily def}}}{=}}}

\newenvironment{phv}{\fontfamily{phv}\selectfont}{\phv}

\title{Evolution of pre-copulatory and post-copulatory inbreeding behaviour \\ \vspace{10 mm} {\sffamily\Large\bfseries Supplemental results showing change in allele values over different parameter combinations, and allele values over generations for single replicates}}

\author{\\ \textbf{A. Bradley Duthie\textsuperscript{1,2} and Jane M. Reid\textsuperscript{1}}\\ \textit{\textsuperscript{1} Institute of Biological and Environmental Sciences, School of Biological Sciences, Zoology Building, Tillydrone Avenue, University of Aberdeen, Aberdeen AB24 2TZ, United Kingdom \\ \hspace{10 mm} \textsuperscript{2} E-mail: aduthie@abdn.ac.uk}}

\date{}

\linenumbers
\doublespacing

\pagestyle{fancy}
\lhead{DUTHIE ET AL}
\rhead{PRE- & POST-COPULATORY (SUPPLEMENT)}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

\makeatletter
\renewcommand\section{\@startsection {section}{1}{\z@}%
                                   {-3.5ex \@plus -1ex \@minus -.2ex}%
                                   {2.3ex \@plus.2ex}%
                                   {\sffamily\Large\itshape}}% from \Large
\renewcommand\subsection{\@startsection{subsection}{2}{\z@}%
                                     {-3.25ex\@plus -1ex \@minus -.2ex}%
                                     {1.5ex \@plus .2ex}%
                                     {\sffamily\Large\bfseries}}% from \large
\renewcommand\subsubsection{\@startsection{subsubsection}{3}{\z@}%
                                     {-3.25ex\@plus -1ex \@minus -.2ex}%
                                     {1.5ex \@plus .2ex}%
                                     {\sffmaily\large\bfseries}}% from \normalsize
\makeatother

\begin{phv}
\thispagestyle{empty} % single page disable page number

\maketitle

\vspace{10 mm}

\noindent \textbf{Here we present supplemental results from an individual-based model in which alleles underlying polyandry (\bm{$P_{a}$}), pre-copulatory inbreeding strategy (\bm{$M_{a}$}) and post-copulatory inbreeding strategy (\bm{$F_{a}$}) affect phenotypic values for .}

\clearpage

\vspace*{5 mm}

{\Large Table of Contents}

\hrulefill

\contentsline {section}{\tocsection {}{}{\small Figure S\ref{allcombs}: All cost combinations}}{S3}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{extra_MfPf}: All cost combinations}}{S4}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P00_E00}: All cost combinations}}{S5}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P00_E00}: All cost combinations}}{S6}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P02_E00}: All cost combinations}}{S7}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P00_E02}: All cost combinations}}{S8}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P02_E00}: All cost combinations}}{S9}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P00_E02}: All cost combinations}}{S10}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P02_E02}: All cost combinations}}{S11}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P02_E02}: All cost combinations}}{S12}

\hrulefill

\end{phv}

\clearpage

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.85]{figures/evo_combs.pdf}
\end{center}
\caption{Some new costs}
\label{allcombs}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.8]{figures/extra_MfPf.pdf}
\end{center}
\caption{A key caveat to the results}
\label{extra_MfPf}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.8]{figures/SI_M00_P00_E00.pdf}
\end{center}
\caption{A key caveat to the results}
\label{SI_M00_P00_E00}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.8]{figures/SI_M02_P00_E00.pdf}
\end{center}
\caption{A key caveat to the results}
\label{SI_M02_P00_E00}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.8]{figures/SI_M00_P02_E00.pdf}
\end{center}
\caption{A key caveat to the results}
\label{SI_M00_P02_E00}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.8]{figures/SI_M00_P00_E02.pdf}
\end{center}
\caption{A key caveat to the results}
\label{SI_M00_P00_E02}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.8]{figures/SI_M02_P02_E00.pdf}
\end{center}
\caption{A key caveat to the results}
\label{SI_M02_P02_E00}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.8]{figures/SI_M02_P00_E02.pdf}
\end{center}
\caption{A key caveat to the results}
\label{SI_M02_P00_E02}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.8]{figures/SI_M00_P02_E02.pdf}
\end{center}
\caption{A key caveat to the results}
\label{SI_M00_P02_E02}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.8]{figures/SI_M02_P02_E02.pdf}
\end{center}
\caption{A key caveat to the results}
\label{SI_M02_P02_E02}
\end{figure}

\end{document}

### 2016-09-30 analysis.R
Fix error of cost in figure text

@@ -1047,7 +1047,7 @@ points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 #points(x=xxx,y=mWP,type="l",lwd=2,col="blue");
 #text(x=0, y=-18.0, label=expression(paste(c[M]==0.00)),cex=1, pos=4);
 #text(x=0, y=-21.0, label=expression(paste(c[P]==0.00)),cex=1, pos=4);
-text(x=0, y=-23.0, label=expression(paste(c[F]==0.00)),cex=1.25, pos=4);
+text(x=0, y=-23.0, label=expression(paste(c[F]==0.00)),cex=1.5, pos=4);
 text(x=-300, y=11.0, label="A", cex=2, pos=4);
 rm(evo_cc_02);
 # ------------------------------------------------------------------------#
@@ -1084,7 +1084,7 @@ points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 abline(h=0,lwd=0.8,lty="dotted");
 #text(x=0, y=-18.0, label=expression(paste(c[M]==0.02)),cex=1, pos=4);
 #text(x=0, y=-21.0, label=expression(paste(c[P]==0.00)),cex=1, pos=4);
-text(x=0, y=-23.0, label=expression(paste(c[F]==0.02)),cex=1, pos=4);
+text(x=0, y=-23.0, label=expression(paste(c[F]==0.02)),cex=1.5, pos=4);
 text(x=-300, y=11.0, label="B", cex=2, pos=4);
 rm(evo_cc_02);
 # ------------------------------------------------------------------------#
@@ -1553,7 +1553,7 @@ text(x=-900, y=27.0, label="A", cex=2, pos=4);
 #text(x=0, y=-35.0, label=expression(paste(c[M]==0.00)),cex=1.2, pos=4);
 #text(x=0, y=-42.0, label=expression(paste(c[P]==0.02)),cex=1.2, pos=4);
 #text(x=0, y=-49.0, label=expression(paste(c[F]==0.00)),cex=1.2, pos=4);
-text(x=0, y=-47.0, label=expression(paste(c[P]==0.00)),cex=1.5, pos=4);
+text(x=0, y=-47.0, label=expression(paste(c[P]==0.02)),cex=1.5, pos=4);
 # ----------------------------------------------------------------
 mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
[…]

### 2016-09-30 Supplement.tex
Add most figure legends

@@
 \lhead{DUTHIE ET AL}
-\rhead{PRE- & POST-COPULATORY (SUPPLEMENT)}
+\rhead{PRE- \& POST-COPULATORY (SUPPLEMENT)}
 \renewcommand{\headrulewidth}{0pt}
@@
 \contentsline {section}{\tocsection {}{}{\small Figure S\ref{allcombs}: All cost combinations}}{S3}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{extra_MfPf}: All cost combinations}}{S4}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P00_E00}: All cost combinations}}{S5}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P00_E00}: All cost combinations}}{S6}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P02_E00}: All cost combinations}}{S7}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P00_E02}: All cost combinations}}{S8}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P02_E00}: All cost combinations}}{S9}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P00_E02}: All cost combinations}}{S10}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P02_E02}: All cost combinations}}{S11}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P02_E02}: All cost combinations}}{S12}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{extra_MfPf}: Dynamic \bm{$F_{a}$}, fixed \bm{$P_{a}=1$} and \bm{$M_{a}=-10$}}}{S4}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P00_E00}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0$}}}{S5}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P00_E00}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0$}}}{S6}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P02_E00}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0$}}}{S7}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P00_E02}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0.02$}}}{S8}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P02_E00}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0$}}}{S9}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P00_E02}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0.02$}}}{S10}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P02_E02}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0.02$}}}{S11}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P02_E02}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0.02$}}}{S12}
 
@@
 \begin{center}				
-\includegraphics[scale=0.85]{figures/evo_combs.pdf}
+\includegraphics[scale=0.82]{figures/evo_combs.pdf}
 \end{center}
-\caption{Some new costs}
+\caption{Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard deviations of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Panels A-H show simulations for different combinations of costs for tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
+Dotted horizontal black lines in panels show values of zero on the y-axis.
+Individual replicates for all cost combinations are shown in Figures S\ref{SI_M00_P00_E00}-S\ref{SI_M02_P02_E02}.
+Dotted horizontal lines show where the y-axis equals zero.}
 \label{allcombs}
@@
 \end{center}
-\caption{A key caveat to the results}
+\caption{Mean allele values underlying post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid black lines represent grand means over 40 replicate populations, and grey shading around solid lines show standard errors of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance, and positive values reflect strategies of inbreeding preference.
+Red and blue horizontal lines reflect fixed polyandry allele values of $P_{a}=1$ and fixed pre-copulatory inbreeding strategy allele values of $M_{a}=-10$, respectively.
+Panels (A) and (B) show simulations given not costly and costly post-copulatory inbreeding strategy, respectively.
+Dotted horizontal lines show where the y-axis equals zero.}
 \label{extra_MfPf}
@@
 \end{center}
-\caption{A key caveat to the results}
+\caption{Mean allele values underlying tendency for polyandry (A; red lines), pre-copulatory inbreeding strategy (B; blue lines), and post-copulatory inbreeding strategy (C; black lines), as calculated across all individuals in 40 replicate simulations with identical starting conditions over 40000 generations and given strong inbreeding depression.
+Thick lines show grand means of replicates, and thin lines show individual replicates.
+Panels A-C thereby show the same information as in Figure S\ref{allcombs}A, but with individual replicates replacing standard error around grand mean values.
+Panel D illustrates among replicate correlations in mean allele values over generations.
+Purple, dark red, and dark blue lines show correlations between $P_{a}$ \& $M_{a}$, $P_{a}$ \& $F_{a}$, and $M_{a}$ \& $F_{a}$, respectively.
+Dotted horizontal lines show where the y-axis equals zero.}
 \label{SI_M00_P00_E00}

### 2016-09-30 Supplement.tex
Finish first draft of Supplement

@@
 
-\noindent \textbf{Here we present supplemental results from an individual-based model in which alleles underlying polyandry (\bm{$P_{a}$}), pre-copulatory inbreeding strategy (\bm{$M_{a}$}) and post-copulatory inbreeding strategy (\bm{$F_{a}$}) affect phenotypic values for .}
+\noindent \textbf{Here we present supplemental results from an individual-based model in which alleles underlying polyandry (\bm{$P_{a}$}), pre-copulatory inbreeding strategy (\bm{$M_{a}$}) and post-copulatory inbreeding strategy (\bm{$F_{a}$}) affect evolving phenotypic values for each trait over 40000 generations.
+The first figure in this supplement shows how \bm{$F_{a}$} alleles change over generations given that \bm{$M_{a}$} alleles are fixed for strong inbreeding avoidance and \bm{$P_{a}$} alleles are fixed for polyandry.
+Remaining figures show all cost combinations of \bm{$0$} and \bm{$0.02$} for polyandry (\bm{$c_{P}$}), pre-copulatory inbreeding strategy (\bm{$c_{M}$}), and post-copulatory inbreeding strategy (\bm{$c_{F}$}), including a summary among \bm{$40$} replicates and dynamics of individual replicates.
+Figures also show correlations of mean allele values among replicates.}
 
@@
 
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{allcombs}: All cost combinations}}{S3}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{extra_MfPf}: Dynamic \bm{$F_{a}$}, fixed \bm{$P_{a}=1$} and \bm{$M_{a}=-10$}}}{S4}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{extra_MfPf}: Dynamic \bm{$F_{a}$}, fixed \bm{$P_{a}=1$} and \bm{$M_{a}=-10$}}}{S3}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{allcombs}: All cost combinations}}{S4}
 \contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P00_E00}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0$}}}{S5}
@@
 \begin{center}				
+\includegraphics[scale=0.8]{figures/extra_MfPf.pdf}
+\end{center}
+\caption{Mean allele values underlying post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid black lines represent grand means over 40 replicate populations, and grey shading around solid lines show standard errors of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance, and positive values reflect strategies of inbreeding preference.
+Red and blue horizontal lines reflect fixed polyandry allele values of $P_{a}=1$ and fixed pre-copulatory inbreeding strategy allele values of $M_{a}=-10$, respectively.
+Panels (A) and (B) show simulations given not costly and costly post-copulatory inbreeding strategy, respectively.
+Dotted horizontal lines show where the y-axis equals zero.}
+\label{extra_MfPf}
+\end{figure}
+
+\clearpage
+\begin{figure}
+\begin{center}				
 \includegraphics[scale=0.82]{figures/evo_combs.pdf}
@@
 \label{allcombs}
-\end{figure}
-
-\clearpage
-\begin{figure}
-\begin{center}				
-\includegraphics[scale=0.8]{figures/extra_MfPf.pdf}
-\end{center}
-\caption{Mean allele values underlying post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid black lines represent grand means over 40 replicate populations, and grey shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance, and positive values reflect strategies of inbreeding preference.
-Red and blue horizontal lines reflect fixed polyandry allele values of $P_{a}=1$ and fixed pre-copulatory inbreeding strategy allele values of $M_{a}=-10$, respectively.
-Panels (A) and (B) show simulations given not costly and costly post-copulatory inbreeding strategy, respectively.
-Dotted horizontal lines show where the y-axis equals zero.}
-\label{extra_MfPf}
 \end{figure}
@@
 \end{center}
-\caption{A key caveat to the results}
+\caption{Mean allele values underlying tendency for polyandry (A; red lines), pre-copulatory inbreeding strategy (B; blue lines), and post-copulatory inbreeding strategy (C; black lines), as calculated across all individuals in 40 replicate simulations with identical starting conditions over 40000 generations and given strong inbreeding depression.
+Thick lines show grand means of replicates, and thin lines show individual replicates.
+Panels A-C thereby show the same information as in Figure S\ref{allcombs}B, but with individual replicates replacing standard error around grand mean values.
+Panel D illustrates among replicate correlations in mean allele values over generations.
+Purple, dark red, and dark blue lines show correlations between $P_{a}$ \& $M_{a}$, $P_{a}$ \& $F_{a}$, and $M_{a}$ \& $F_{a}$, respectively.
+Dotted horizontal lines show where the y-axis equals zero.}
 \label{SI_M02_P00_E00}
@@
 \end{center}
-\caption{A key caveat to the results}
+\caption{Mean allele values underlying tendency for polyandry (A; red lines), pre-copulatory inbreeding strategy (B; blue lines), and post-copulatory inbreeding strategy (C; black lines), as calculated across all individuals in 40 replicate simulations with identical starting conditions over 40000 generations and given strong inbreeding depression.
+Thick lines show grand means of replicates, and thin lines show individual replicates.
+Panels A-C thereby show the same information as in Figure S\ref{allcombs}C, but with individual replicates replacing standard error around grand mean values.
+Panel D illustrates among replicate correlations in mean allele values over generations.
+Purple, dark red, and dark blue lines show correlations between $P_{a}$ \& $M_{a}$, $P_{a}$ \& $F_{a}$, and $M_{a}$ \& $F_{a}$, respectively.
+Dotted horizontal lines show where the y-axis equals zero.}
 \label{SI_M00_P02_E00}
@@
 \end{center}
-\caption{A key caveat to the results}
+\caption{Mean allele values underlying tendency for polyandry (A; red lines), pre-copulatory inbreeding strategy (B; blue lines), and post-copulatory inbreeding strategy (C; black lines), as calculated across all individuals in 40 replicate simulations with identical starting conditions over 40000 generations and given strong inbreeding depression.
+Thick lines show grand means of replicates, and thin lines show individual replicates.
+Panels A-C thereby show the same information as in Figure S\ref{allcombs}D, but with individual replicates replacing standard error around grand mean values.
+Panel D illustrates among replicate correlations in mean allele values over generations.
+Purple, dark red, and dark blue lines show correlations between $P_{a}$ \& $M_{a}$, $P_{a}$ \& $F_{a}$, and $M_{a}$ \& $F_{a}$, respectively.
+Dotted horizontal lines show where the y-axis equals zero.}
 \label{SI_M00_P00_E02}
@@
 \end{center}
-\caption{A key caveat to the results}
+\caption{Mean allele values underlying tendency for polyandry (A; red lines), pre-copulatory inbreeding strategy (B; blue lines), and post-copulatory inbreeding strategy (C; black lines), as calculated across all individuals in 40 replicate simulations with identical starting conditions over 40000 generations and given strong inbreeding depression.
+Thick lines show grand means of replicates, and thin lines show individual replicates.
+Panels A-C thereby show the same information as in Figure S\ref{allcombs}E, but with individual replicates replacing standard error around grand mean values.
+Panel D illustrates among replicate correlations in mean allele values over generations.
+Purple, dark red, and dark blue lines show correlations between $P_{a}$ \& $M_{a}$, $P_{a}$ \& $F_{a}$, and $M_{a}$ \& $F_{a}$, respectively.
+Dotted horizontal lines show where the y-axis equals zero.}
 \label{SI_M02_P02_E00}
@@
 \end{center}
-\caption{A key caveat to the results}
+\caption{Mean allele values underlying tendency for polyandry (A; red lines), pre-copulatory inbreeding strategy (B; blue lines), and post-copulatory inbreeding strategy (C; black lines), as calculated across all individuals in 40 replicate simulations with identical starting conditions over 40000 generations and given strong inbreeding depression.
+Thick lines show grand means of replicates, and thin lines show individual replicates.
+Panels A-C thereby show the same information as in Figure S\ref{allcombs}F, but with individual replicates replacing standard error around grand mean values.
+Panel D illustrates among replicate correlations in mean allele values over generations.
+Purple, dark red, and dark blue lines show correlations between $P_{a}$ \& $M_{a}$, $P_{a}$ \& $F_{a}$, and $M_{a}$ \& $F_{a}$, respectively.
+Dotted horizontal lines show where the y-axis equals zero.}
 \label{SI_M02_P00_E02}
@@
 \end{center}
-\caption{A key caveat to the results}
+\caption{Mean allele values underlying tendency for polyandry (A; red lines), pre-copulatory inbreeding strategy (B; blue lines), and post-copulatory inbreeding strategy (C; black lines), as calculated across all individuals in 40 replicate simulations with identical starting conditions over 40000 generations and given strong inbreeding depression.
+Thick lines show grand means of replicates, and thin lines show individual replicates.
+Panels A-C thereby show the same information as in Figure S\ref{allcombs}G, but with individual replicates replacing standard error around grand mean values.
+Panel D illustrates among replicate correlations in mean allele values over generations.
+Purple, dark red, and dark blue lines show correlations between $P_{a}$ \& $M_{a}$, $P_{a}$ \& $F_{a}$, and $M_{a}$ \& $F_{a}$, respectively.
+Dotted horizontal lines show where the y-axis equals zero.}
 \label{SI_M00_P02_E02}
@@
 \end{center}
-\caption{A key caveat to the results}
+\caption{Mean allele values underlying tendency for polyandry (A; red lines), pre-copulatory inbreeding strategy (B; blue lines), and post-copulatory inbreeding strategy (C; black lines), as calculated across all individuals in 40 replicate simulations with identical starting conditions over 40000 generations and given strong inbreeding depression.
+Thick lines show grand means of replicates, and thin lines show individual replicates.
+Panels A-C thereby show the same information as in Figure S\ref{allcombs}H, but with individual replicates replacing standard error around grand mean values.
+Panel D illustrates among replicate correlations in mean allele values over generations.
+Purple, dark red, and dark blue lines show correlations between $P_{a}$ \& $M_{a}$, $P_{a}$ \& $F_{a}$, and $M_{a}$ \& $F_{a}$, respectively.
+Dotted horizontal lines show where the y-axis equals zero.}
 \label{SI_M02_P02_E02}

### 2016-10-12 Figure_pre_post.R
Initialise new branch for new_draft_1

@@ -39,4 +39,23 @@ text(x=800, y=8.00, labels=paste("Pos_cost = ",cpos), cex=1.25);
 
 
 
+rm(list=ls()); 
+
+setwd("~/Dropbox/DuthieManu/pre_post_cop/presentation");
+
+x  <- seq(from=0, to=1, by=0.0001);
+b0 <- exp(-0 * x);
+b1 <- exp(-1 * x);
+b2 <- exp(-2 * x);
+b3 <- exp(-3 * x);
+setEPS();
+cairo_ps("betas.eps",family="Arial",height=6,width=6);
+par(mar=c(5,5,1,1), lwd=3);
+plot(x=x, y=b0, cex.lab=1.5, cex.axis=1.5, type="l", lwd=3, ylim=c(0,1),
+     ylab=expression(paste("Offspring viability (",Psi[off],")")),
+     xlab=expression(paste("Kinship between parents (",k[ij],")")));
+points(x=x, y=b1, cex.lab=1.5, cex.axis=1.5, type="l", lwd=3)
+points(x=x, y=b2, cex.lab=1.5, cex.axis=1.5, type="l", lwd=3)
+points(x=x, y=b3, cex.lab=1.5, cex.axis=1.5, type="l", lwd=3)
+dev.off();
 

### 2016-10-12 code/Inbreed.c

@@ -711,10 +711,10 @@ void Inbreed(int mc, int M, int Imm, int Clu, double *RES, double Beta1, int rep
         evol = fopen(evolres,"a+");
         fprintf(evol,"%d\t%f\t%f\t%f\t%f\t%d\t%f\t%f\t%f\t%f\t%f\t%f\t%f\t%f\n",pidcmb,Beta1,
             Scost,Pcost,Ecost,i,RES[0],RES[1],RES[2],RES[3],RES[4],RES[5],RES[6],RES[7]);
-        /*
+    
         printf("%d  %d  %f  %f  %f  %f  %f  %f  %f\n",
             rep,i,Scost,Pcost,Ecost,RES[0],RES[1],RES[2],RES[6]);
-        */
+        
         fclose(evol);
 
         /* ==========================================================*/

### 2016-10-12 code/PolyIn.c

@@ -36,7 +36,7 @@ int main(void){
     Scost   = 0.0000; /* Cost of having tendancy to non-randomly select social mates      */
     Pcost   = 0.0000; /* Cost of having tendancy to engage in polyandry                   */
     Ecost   = 0.0000; /* Cost of having tendancy to non-randomly select extra-pair mates  */
-    gen     = 5000;   /* Number of generations per replicate (default 5000)               */
+    gen     = 50;     /* Number of generations per replicate (default 5000)               */
     muSt    = 0;      /* Generation at which mutations may start                          */
     mu      = 0.001;  /* Mutation rate of any given allele                                */
     Kind    = 1;      /* Kin recognition (1 = recognise all; 0 = recognise only siblings) */
@@ -50,7 +50,7 @@ int main(void){
     PreSel  = 1;      /* Allow pre-copulatory mate selection for EPMs (0: no, 1:yes)      */
     PostSel = 1;      /* Allow post-copulatory mate selection for EPMs (0: no, 1: yes)    */
     PreserC = 0;      /* Preserve among-individual trait correlations in immigrants       */
-    zallele = 1;      /* Initial alleles at 0 (0) or randomly drawn from N(0,ImmSD) (1)   */
+    zallele = 0;      /* Initial alleles at 0 (0) or randomly drawn from N(0,ImmSD) (1)   */
     /* ===================================================================================*/
     /* Genome attributes of individuals                                                   */
     /* ===================================================================================*/
@@ -67,7 +67,7 @@ int main(void){
     /* ===================================================================================*/
     /* Simulation details                                                                 */
     /* ===================================================================================*/
-    rep        = 4;     /* Simulations run                                                */
+    rep        = 1;     /* Simulations run                                                */
     Pedi       = 0;     /* Print last rep's pedigree? (0:no, 1:yes) WARNING: 200Mb file   */
     snap       = 1;     /* Last 2 gens pedigree for all reps printed? (0:no, 1:yes)       */
     msel       = 1;     /* Last 2 gens print mate selection of females? (0:no, 1:yes)     */

### 2016-10-12 ms_pre_post.Rmd
Some initial work on the first paragraph revision

@@
 
-<!--- Reproductive decisions expressed among interacting individuals directly affect individual fitnesses and the genotypes and viabilities of resulting offspring, and thereby profoundly affect evolutionary dynamics through the differential inheritence of alleles over generations [@Pizzari2012; @Wright2013; @Wild2014; @Liao2015; @Reid2016].
-For example, how frequently a focal female mates is a reproductive decision that can directly and indirectly affect her fitness, and potentially alter the distribution of genotypes and patterns of inheritence within a population [e.g., @Cornell2007; @Diaz2010; @Okada2015; @Roberts2015a; @Worthington2016].
-Her mating frequency and expression of mate choice might be affected by the genetic quality or complementarity of available potential mates, and her choosiness might additionally be expressed after mating has taken place through post-copulatory mechanisms [@Parker1983; @Parker2006; @Kuijper2012].
-Female choice might therefore be realised by evolution of multiple, potentially interdependent, behavioural and physiological phenotypes operating in tandem.
-However, no general modelling framework predicts the conditions under which female mating frequency, pre-copulatory choice, and post-copulatory choice evolve together, meaning that there are no formal hypotheses for predicting the relevance of these reproductive decisions across different biological systems.
+Inbreeding often reduces the fitness of inbred offspring (termed 'inbreeding depression'), potentially driving evolution of inbreeding avoidance when inbreeding depression is strong [@Parker1979; @Parker2006; @Pusey1996; @Charlesworth1999; @Keller2002; @Charlesworth2009; @Szulkin2012].
+For focal females, inbreeding avoidance might be acheived by avoiding related potential mates (pre-copulatory inbreeding avoidance), or by biasing fertilisation after mating has occurred so that related mates are less likely to sire offspring (post-copulatory inbreeding avoidance).
+Importantly, evolution of post-copulatory inbreeding avoidance requires that females be polyandrous, mating with multiple males during a single reproductive bout to ensure that post-copulatory choice is possible.
+As a reproductive strategy, polyandry thereby simultaneously allows females to choose multiple mates and creates the opportunity for further cryptic choice enacted through post-copulatory mechanisms.
+Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to reduce their inbreeding and therefore produce higher fitness offspring [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007].
+However, it remains unclear  <!--- Just fix this last sentence somehow...
 --->
-
-Polyandry, defined as female multiple mating within a single reproductive bout, is a reproductive strategy that simultaneously allows females to choose multiple mates and creates the opportunity for further cryptic choice enacted through post-copulatory mechanisms.
-One key choice for females is the decision to prefer, avoid, or tolerate breeding with relatives ['inbreeding'; @Szulkin2012].
-Inbreeding often reduces the fitness of inbred offspring [@Charlesworth1999; @Keller2002; @Charlesworth2009], and polyandry has been widely hypothesised to evolve as an adaptation to allow females to reduce their inbreeding and therefore produce higher fitness offspring [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007].
-In a recent model, @Duthie showed that selection for alleles underlying polyandry and pre-copulatory inbreeding avoidance occurred only under highly constrained conditions in which direct costs of polyandry were low, and when very few males were available during a female's initial mate choice but many males were available during a female's additional mate choice(s), or when polyandry was conditionally expressed based on the degree to which a focal female engaged in inbreeding given her initially chosen mate.
-In the absence of these constraints, expression of polyandry was expected to increase inbreeding with each additional mate because remaining males were more likely to be relatives once available non-relatives were chosen.
-However, @Duthie assumed that polyandrous females had no control over the assignment of paternity to their offspring.
-If after engaging in polyandry, females could bias paternity through post-copulatory mechanisms, then selection for polyandry to avoid inbreeding might be more widely predicted when inbreeding depression is severe [@Zeh1997].
 
@@
 
-<!--- Rubbish: is unlikely to be simultaneous.
-Testing whether or not initially rare alleles underlying inbreeding avoidance can successfully invade a population Even if invasion fitness of alleles underlying inbreeding avoidance are high when mating and fertilisation is random with respect to relatedness, initial invasion of Initial evolution of pre- and post-copulatory inbreeding avoidance strategies is unlikely to be simultaneous, so to predict evolutionary outcomes, it is necessary to consider evolution when one inbreeding avoidance strategy is initially rare, and the other strategy is common.
-For example, if pre-adaptation or rapid selection resulted in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect that such invading alleles had on decreasing total inbreeding avoidance would be weak or negligible.
---->
-
-<!--- It is therefore necessary to consider evolution of pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy when each evolves in a population where its complementary inbreeding strategy is evolutionarily constrained or already fixed as an adaptation.
---->
-
-<!--- Overall, to predict evolution of polyandry and inbreeding strategies, it is therefore necessary to model costs associated with polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
---->
-
-<!--- Inbreeding, defined as breeding between relatives, directly affects inheritence of identical-by-descent alleles and the viability of inbred offspring, meaning that the decision to prefer, avoid, or tolerate (i.e., mate randomly with respect to relatedness) inbreeding is predicted to have profound effects on individual fitness [@Parker2006; @Kokko2006; @Szulkin2012; @Duthie2015a].
-Viability of inbred offspring typically decreases with increasing relatedness between parents [termed 'inbreeding depression'; @Keller2002; @Charlesworth2009].
-If inbreeding depression is sufficiently weak, selection for female inbreeding preference is predicted because inbreeding increases the reproductive success of a focal female's male relative, thereby increasing the number of identical-by-descent allele copies present in her offspring [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
-However, if inbreeding depression is moderate to strong, selection for female inbreeding avoidance is predicted [Duthie and Reid *in press*; @Duthie].
-Female inbreeding strategy can be enacted before or after copulation occurs [e.g., @Tuni2013; @Firman2015; @Daniel2015; @Fischer2015].
-However, models of inbreeding do not consider pre-copulatory inbreeding strategy (hereafter 'pre-copulatory inbreeding strategy') and post-copulatory inbreeding strategy (hereafter 'post-copulatory inbreeding strategy') jointly, meaning that it is unclear when selection for either or both strategies is predicted in empirical systems.
---->
-
-<!--- Critically, evolution of post-copulatory inbreeding strategy is precluded if females only mate with one male, meaning that evolution of polyandry (defined as female multiple mating within a single reproductive bout) is intrinsically tied to female post-copulatory inbreeding strategy.
-Although polyandry is commonplace in wild populations, the regularity with which it is observed in the wild remains theoretically puzzling because engaging in polyandry does not necessarily increase the number of offspring that a female produces, meaning that the fitness benefits associated with polyandry are not always clear [@Parker2013; @Taylor2014].
-It has been hypothesised that females can acheive a net fitness benefit if polyandry provides them with additional opportunities to adjust their inbreeding through copulations with additional males [e.g., @Tregenza2002; @Akcay2007; @Lehtonen2015].
-However, no models quantify the degree to which expression of biased paternity resulting from evolving post-copulatory inbreeding strategy can feedback to drive evolution of polyandry in populations of potentially inbreeding females and males with biologically realistic distributions of relatedness.
---->
-
-<!--- Evolution of post-copulatory inbreeding strategy might increase selection for polyandry, but evolutionary feedbacks between post-copulatory inbreeding strategy and polyandry might also be contingent upon evolution of pre-copulatory inbreeding strategy, thereby leading to complex evolutionary dynamics between inbreeding strategies and polyandry.
-For example, if females can acheive their desired degree of inbreeding through mate choice alone, then subsequent polyandry and post-copulatory inbreeding strategy might be superfluous for increasing female fitness.
-Alternatively, if females are often unsuccessful at realising their pre-copulatory inbreeding strategy due to factors such as sexual conflict over mating and resulting male coercion [e.g., @Parker2006], limited kin recognition amongst potential mates [e.g., @Penn2010], or simply the inherent stochasticity associated with mate encounters or expression of mate choice based on inbreeding [e.g., @Kokko2006; @Duthie], then selection on post-copulatory inbreeding strategy might occur to reinforce pre-copulatory inbreeding strategy.
-In empirical systems where inbreeding depression is severe and inbreeding avoidance is therefore beneficial, expression of pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy have been observed across diverse taxa [e.g., @Gasparini2011; @Tuni2013; @Firman2015; @Fischer2015; @Daniel2015].
-However, no models predict *a priori* which of these inbreeding strategies should be observed when inbreeding depression is sufficiently severe to make inbreeding avoidance adaptive.
---->
-
-<!--- Evolution of polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy will ultimately be determined by the, potentially interacting, fitness benefits and costs of each phenotype.
-Given severe inbreeding depression, phenotypes will increase a focal female's fitness if they cause her to avoid breeding with close relatives [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
-However,  --->
-
-<!--- Selection for pre-copulatory inbreeding strategy versus post-copulatory inbreeding strategy and associated polyandry might also depend evolutionary constraints, or on existing phenotypes in the population.
-For example, if phenotypes biasing fertilisation to avoid inbreeding are precluded by evolutionary constraints [@Bradshaw1991; @Futuyma2010], then inbreeding avoidance might only be possible before copulation occurs, perhaps strengthening selection for pre-copulatory inbreeding strategy and weakening selection for polyandry.
-Alternatively, evolution of female pre-copulatory inbreeding strategy might be precluded due to severely limited kin recognition or the inability to resist male coercion given sexual conflict [@Arnqvist2005a; @Parker2006; @Penn2010].
-In such conditions, females might only be able to express choice through post-copulatory inbreeding strategy, perhaps strengthening selection for inbreeding avoidance through polyandry and post-copulatory mechanisms.
-Selection for inbreeding mating or fertilisation strategy might also be weak or negligible if the strategy is redundant due to the presence of an already established adaptive inbreeding strategy (e.g., if females already successfully avoid inbreeding during mate encounters, then they might be unable to increase their fitness further by biasing fertilisation after mating has occurred).
---->
-
-<!--- Here we apply a model of female and male reproductive interactions and associated inbreeding depression in offspring viability to quantify evolution of three separate phenotypes including female tendency for polyandry, female pre-copulatory inbreeding strategy (mating strategy), and female post-copulatory inbreeding strategy (fertilisation strategy).
---->
+<!--- Probably want to clean up the below ---> 
+In a recent model, @Duthie showed that selection for alleles underlying polyandry and pre-copulatory inbreeding avoidance occurred only under highly constrained conditions in which direct costs of polyandry were low, and when very few males were available during a female's initial mate choice but many males were available during a female's additional mate choice(s), or when polyandry was conditionally expressed based on the degree to which a focal female engaged in inbreeding given her initially chosen mate.
+In the absence of these constraints, expression of polyandry was expected to increase inbreeding with each additional mate because remaining males were more likely to be relatives once available non-relatives were chosen.
+However, @Duthie assumed that polyandrous females had no control over the assignment of paternity to their offspring.
+If after engaging in polyandry, females could bias paternity through post-copulatory mechanisms, then selection for polyandry to avoid inbreeding might be more widely predicted when inbreeding depression is severe [@Zeh1997].
 
@@
 We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across reproductive systems with different relative costs and strong inbreeding depression in offspring viability.
-
-<!--- that constraints on evolution of one inbreeding strategy (e.g., pre-copulatory inbreeding strategy) will increase the strength of selection on evolution of a complementary inbreeding strategy (e.g., post-copulatory inbreeding strategy), and that --->
 
@@
 ----------------------------------------------
-
-<!--- In the case of tendency to engage in polyandry, the cost of $P_{p}$ ($c_{P}$) is interpreted biologically as a cost associated with mate searching or courtship [e.g., @Rowe1988; @Rowe1994; @Ronkainen1994; @Koga1998; @Lasley-Rasher2012].
-For pre-copulatory inbreeding strategy, the cost of $M_{p}$ ($c_{M}$) is interpreted biologically as a cost associated with risk of mating failure due to females being overly choosy [e.g., @Kokko2013], and for post-copulatory inbreeding strategy, the cost of $F_{p}$ ($c_{F}$) is interpreted as an energetic cost associated with the physiological or biochemical mechanisms that need to be developed to bias fertilisation for inbreeding avoidance or inbreeding preference [e.g., @Gasparini2011].
---->
 
@@
 
-<!--- We simulate up to eight possible permutations of values of costs of tendency for polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) equal to either $0$ or $0.02$ [@Duthie observed $0.02$ to be a strong cost of tendency for polyandry] for values of $\beta = 3$ ($8$ total combinations).
---->
-
-<!--- In simulations without evolving $F_{p}$, we therefore include all $4$ combinations of $c_{P}=\{0,0.02\}$ and $c_{M}=\{0,0.02\}$ (but not $c{F}$). --->
-
 To test the hypothesis that selection for a costly strategy of inbreeding avoidance will be negligible given a less costly alternative strategy, we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where the cost of pre-copulatory inbreeding strategy $c_{M}=0$ but the cost of post-copulatory inbreeding strategy $c_{F}=0.02$, and where $c_{F}=0$ but $c_{M}=0.02$.
@@
 A contrast between the baseline expectation for how costs affect evolution of a focal inbreeding strategy in the absence of an alternative strategy, and evolution of a focal strategy given that an alternative strategy also evolves, tests whether or not a relatively low cost alternative strategy decreases selection for a focal strategy.
-
-<!--- To test hypotheses regarding evolution under different relative costs of phenotypes, we consider all combinations of costs using simulations in which all three traits evolve.
-To test the hypothesis that pre-copulatory inbreeding strategy will evolve toward inbreeding avoidance ($M_{p}<0$) when mating costs are low relative to the costs of tendency for polyandry and post-copulatory inbreeding strategy, but that selection for post-copulatory inbreeding strategy will then be negligible ($F_{p} \approx 0$), we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where $c_{M}=0$ but $c_{P}$, $c_{F}$, or both equals $0.02$.
-We compare evolution in these three cost parameter value combinations with simulations in which all costs equal either $0$ or $0.02$.
-If our hypothesis is supported, then $M_{p}$ but not $F_{p}$ will evolve to more negative values when $c_{M}$ is relatively low than when all cost values are uniform.
-To test the hypothesis that post-copulatory inbreeding strategy will evolve toward inbreeding avoidance ($F_{p}<0$) given low costs of polyandry and post-copulatory inbreeding strategy relative to the cost of pre-copulatory inbreeding strategy, but that selection on pre-copulatory inbreeding strategy will be negligible ($M_{p} \approx 0$), we quantify evolution of $M_{p}$ and $F_{p}$ over generations when $c_{F}=0$, $c_{P}=0$, and $c_{M}=0.02$ .
-We compare evolution for this combination of cost parameter values with simulations in which all costs equal either $0$ or $0.02$.
-If our hypothesis is supported, then $F_{a}$ but not $M_{a}$ allele values will become more negative over generations when $c_{F}$ is relatively low than when all cost values are uniform.
---->
-
-<!--- To test the hypothesis that constraints on evolution of one inbreeding strategy will increase the strength of selection on a complementary strategy, we fixed inbreeding strategy phenotypes to values of zero, thereby causing either random mating ($M_{p}=0$) or the random fertilisation of offspring ($F_{p}=0$) according to a fair raffle among mates with respect to kinship.
-We then compare evolution of the non-fixed trait to its evolution in simulations where all traits are allowed to evolve.
---->
 
@@
 
-<!--- We present our results by showing mean allele value changes over generations.
-Figures 1-5 show mean allele values of tendency for polyandry ($P_{a}$; red lines and shading), pre-copulatory inbreeding strategy ($M_{a}$; blue lines and shading), and post-copulatory inbreeding strategy ($F_{a}$; black lines and shading) over 10000 generations as calculated across all individuals (female and male) within a focal population over 40 replicate simulations with identical starting conditions.
-Solid lines represent the grand mean of replicate mean allele values, and shading around lines shows standard errors of mean allele values around the grand mean.
-Panels within figures show different cost combinations for tendency for polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$).
-Figures have fewer than eight panels if some costs are not relevant because allele values are fixed, and fixed allele values are shown as horizontal lines where line height is set to the fixed allele value.
-Supporting Information S1 presents correlations of mean allele values across replicate simulations, which were generally weak; we found no evidence suggesting strong evolutionary divergence among replicates with identical starting conditions (e.g., as might be the case if populations stochastically evolved toward inbreeding avoidance through mate choice or fertilisation, but not both), meaning that inspecting grand means of replicate allele values accurately reflects expected evolutionary dynamics over generations.
---->
-
 Selection for polyandry is driven by pre-copulatory inbreeding avoidance
 ----------------------------------------------
-
-<!--- We first test our hypothesis that a focal female's ability to express post-copulatory choice with respect to kinship causes selection for polyandry by comparing simulations in which post-copulatory inbreeding strategy is fixed to random mating with respect to kinship to simulations in which tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy can all evolve.
---->
 
@@
 
-<!--- Comparison of Figures 1 and 2 shows that evolution of post-copulatory inbreeding strategy facilitates evolution of polyandry, particularly when costs of tendency for polyandry and post-copulatory inbreeding strategy are zero.
-For example, in Figure 2A, tendency for polyandry allele values consistently become negative over generations ($P_{a}<0$; decreasing red line), causing populations to be monandrous.
-Females in these populations avoid mating with kin ($M_{a}<0$; decreasing blue line), and because these females sample mates with replacement, males that remain after their initial mate choice are more likely to be relatives, causing selection for monandry because females are most likely to succeed in avoiding inbreeding in their initial mate choice [see also @Duthie].
-However, Figure 1A shows that when a focal female can also bias the probability that a particular mate sires her offspring, post-copulatory inbreeding strategy evolves to inbreeding avoidance ($F_{a}<0$; decreasing black line).
-Consequently, the ability to bias fertilisation to avoid inbreeding causes polyandry to become adaptive, and positive values of tendency for polyandry alleles increase in frequency ($P_{a}>0$; increasing red line of Figure 1A).
-Although non-zero costs decrease net selection for both tendency for polyandry and post-copulatory inbreeding strategy (see below), across all combinations of costs, tendency for polyandry allele values are more positive when post-copulatory inbreeding strategy can also evolve.
-Evolution of post-copulatory inbreeding avoidance therefore greatly facilitates evolution of polyandry.
---->
-
 Selection greatly weakened for a relatively more costly inbreeding strategy
 ----------------------------------------------
-
-<!--- Some of these conclusions will need to be changed in light of the need for more generations of data: Strategies were concluded to be non-negligible, they they actually become negligible given a sufficient amount of time.
---->
-
-<!--- Our second hypothesis that selection for a costly inbreeding avoidance strategy will be negligible given a less costly alternative was generally supported by our simulations (Figure 3).  --->
 
@@
 
-<!--- Figure 1 shows changes in mean allele values of tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy across all eight possible combinations of costs.
-In Figure 1A, when no phenotypes are costly, pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy evolve to inbreeding avoidance ($M_{a}<0$ and $F_{a}<0$), and females evolve to be polyandrous ($P_{a}>0$).
-Costs of phenotypes had a direct effect on evolution, causing pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy phenotypes to evolve to values closer to zero (because realisation of inbreeding strategy costs increases with phenotype absolute values) and tendency for polyandry phenotypes to evolve to values that were more negative (because realisation of polyandry costs increases with positive phenotype values).
---->
-
-<!--- We can use Figure 1 to test the hypothesis that pre-copulatory inbreeding strategy will evolve to inbreeding avoidance ($M_{a}<0$), but post-copulatory inbreeding strategy will be negligible ($F_{a} \approx 0$) when mating costs are low ($c_{M}=0$) relative to the costs of tendency for polyandry and post-copulatory inbreeding strategy ($c_{P}=0.02$ or $c_{F}=0.02$) by comparing different cost combinations to the null model in which all costs equal zero (Figure 1A).
-Figure 1A,C,D,G show that inbreeding avoidance in mating ($M_{a}<0$) evolved consistently whenever $c_{M}=0$.
-When post-copulatory inbreeding strategy was costly and inbreeding avoidance strategy was not costly (Figure 1D,G), post-copulatory inbreeding strategy initially evolved toward inbreeding avoidance ($F_{a} < 0$), but long-term evolution of post-copulatory inbreeding strategy stabilised at random mating ($F_{a} \approx 0$).
-However, when only tendency for polyandry was costly (Figure 1C), both pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy evolved to inbreeding avoidance over generations ($M_{a} < 0$ and $F_{a} < 0$).
---->
-
-<!--- We can also use Figure 1 to test the hypothesis that post-copulatory inbreeding strategy will evolve to inbreeding avoidance ($F_{a}<0$), but pre-copulatory inbreeding strategy will be negligible ($M_{a} \approx 0$) when tendency for polyandry and post-copulatory inbreeding strategy costs are low ($c_{P}=0$ and $c_{F}=0$) relative to the cost of pre-copulatory inbreeding strategy ($c_{M}=0.02$).
-Figure 1B shows that inbreeding avoidance through fertilisation bias evolved ($F_{a}<0$) under these conditions.
-While pre-copulatory inbreeding strategy initially evolved toward inbreeding avoidance ($M_{a} < 0$), long-term evolution of pre-copulatory inbreeding strategy stabilised at random mating ($M_{a} \approx 0$).
---->
-
-<!--- Selection given constraints on evolution --->
-<!--- ---------------------------------------------- --->
-
-<!--- Figure 3 shows evolution of tendency for polyandry and post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed so that females must mate randomly (blue line at $M_{a}=0$).
-For all cost combinations of tendency for polyandry and post-copulatory inbreeding strategy (Figure 3 panels A-D), we observed selection for positive values of tendency for polyandry alleles and negative values of post-copulatory inbreeding strategy alleles, which we interpret as strong evidence for evolution of polyandry and associated inbreeding avoidance through fertiisation bias.
-This pattern of evolution contrasts with that observed when pre-copulatory inbreeding strategy was not fixed, indicating that constraints on evolution of pre-copulatory inbreeding strategy increased the strength of selection for evolution of polyandry and inbreeding avoidance through fertilisation bias.
-For example, in Figures 1C,D,G,H, tendency for polyandry allele values were typically less than zero, reflecting evolution of monandry, and post-copulatory inbreeding strategy allele values were not as negative as they were in simulations with fixed random mating (Figure 3).
-In general, when females were unable to avoid mating with relatives given severe inbreeding depression ($\beta=3$), selection for evolution of polyandry and post-copulatory inbreeding avoidance was strengthened.
---->
-
-<!--- Figure 2, which we previously contrasted with Figure 1 to test whether or not evolution of post-copulatory inbreeding strategy facilitates selection for polyandry, shows evolution of tendency for polyandry and pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy is fixed such that the sire of a focal female's offspring is randomly assigned from her mates according to a fair raffle.
-In all cost combinations of Figure 2 (panels A-D), tendency for polyandry allele values decreased over generations, reflecting evolution of monandry.
-However, values of pre-copulatory inbreeding strategy alleles did not greatly differ over generations when post-copulatory inbreeding strategy was fixed, meaning that the effect of fixed post-copulatory inbreeding strategy on increasing selection for inbreeding avoidance through mate choice was weak or nelgigible.
-A weak effect is discernable in the contrast between Figure 2B and Figure 1B, in which the grand mean pre-copulatory inbreeding strategy allele value is $-0.627$ when post-copulatory inbreeding strategy is not fixed (Figure 1B) versus $-1.036$ when it is fixed (Figure 2B) in generation 10000.
-Because females have 20 alleles with additive effects on pre-copulatory inbreeding strategy, an average female was therefore expected to have mean pre-copulatory inbreeding strategy phenotype values of $M_{p} = -0.627 \times 20 = -12.54$ and $M_{p} = -1.036 \times 20 = -20.72$ for not fixed versus fixed post-copulatory inbreeding strategy, respectively.
-These values would cause an outbred focal female to be $2.135$ and $4.180$ times more likely to choose a non-relative than a full sibling as a mate given not fixed versus fixed post-copulatory inbreeding strategy, respectively.
-Therefore, when females were unable to bias fertilisation to avoid inbreeding given severe inbreeding depression ($\beta=3$), selection for evolution of pre-copulatory inbreeding avoidance was strengthened.
---->
-
 Existing adaptation preclude post- but not pre-copulatory inbreeding avoidance
 ----------------------------------------------
-
-<!--- Our third hypothesis that invasion of pre- or post-copulatory inbreeding avoidance would be precluded by the existence of an already adaptive complementary strategy was supported for invading post-copulatory, but not pre-copulatory, inbreeding avoidance.
---->
 
@@
 
-<!--- Figure 4 shows change in pre-copulatory inbreeding strategy allele values over generations when tendency for polyandry and post-copulatory inbreeding strategy alleles were fixed for adaptive values of inbreeding avoidance $P_{a}=1$ and $F_{a}=-5$.
-Despite that females in these simulations could already avoid inbreeding after mating occurred, pre-copulatory inbreeding strategy evolved towards inbreeding avoidance given costs of $c_{M}=0$ (Figure 4A) and $c_{M}=0.02$ (Figure 4B).
-We therefore did not find evidence that the existence of adaptive inbreeding avoidance through fertilisation bias in any way precluded the evolution of adaptive inbreeding avoidance through mate choice.
---->
-
-<!--- Figure 5 shows change in tendency for polyandry and post-copulatory inbreeding strategy allele values over generations when pre-copulatory inbreeding strategy alleles were fixed for adaptive inbreeding avoidance $M_{a}=-5$.
-Existence of adaptive inbreeding avoidance through mate choice precluded evolution of polyandry for all combinations of costs (Figure 5), meaning that evolution of adpative polyandry to avoid inbreeding through post-copulatory inbreeding strategy was never predicted in populations where females were already avoiding inbreeding through mate choice.
-Further, while post-copulatory inbreeding strategy evolved toward inbreeding avoidance ($F_{a}<0$) in the absence of costs (Figure 5A,B), allele values of post-copulatory inbreeding strategy were not as negative as when adaptive inbreeding avoidance through mate choice was not fixed at the outset (Figures 1A,B,C,D).
-We therefore found strong evidence that the existence of adaptive inbreeding avoidance through pre-copulatory mate choice precluded evolution of adaptive inbreeding avoidance through post-copulatory inbreeding avoidance through fertilisation bias.
---->
-
 ******************************
@@
 
-<!--- ---------------------------------------------------------------------- --->
-<!--- -------------------- LEFT OFF HERE ----------------------------------- --->
-<!--- ---------------------------------------------------------------------- --->
-
-<!--- Inbred offspring are typically less viable than outbred offspring, and when such inbreeding depression is strong, it is predicted to cause selection for inbreeding avoidance [Duthie and Reid *in press*; @Parker1979; @Parker2006; @Pusey1996; @Kokko2006].
-In animals, inbreeding avoidance can be realised through both pre-copulatory and post-copulatory mechanisms [e.g., @Tuni2013; @Firman2015; @Daniel2015; @Fischer2015].
-However, the conditions under which inbreeding avoidance is predicted to evolve via pre-copulatory, post-copulatory, or both pre- and post-copulatory mechanisms has not been modelled.
-There is therefore no framework for predicting what mechanisms of inbreeding avoidance are most likely to evolve in empirical populations where risk of fitness loss caused by inbreeding is high.
-Importantly, evolution of post-copulatory mechanisms of inbreeding avoidance requires females to mate multiply, meaning that post-copulatory inbreeding avoidance cannot occur unless polyandry has evolved in a population.
-Accordingly, --->
-
 We modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency to engage in polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
@@
 More generally, we provide a novel framework for approaching empirical studies of inbreeding avoidance, predicting evolution of polyandry and inbreeding avoidance through pre- and post-copulatory mechanisms.
-
-<!--- Evolution of polyandry to avoid inbreeding --->
-<!--- ---------------------------------------------- --->
 
@@
 
-<!---Costs of polyandry and inbreeding avoidance --->
-<!--- ---------------------------------------------- --->
-
-<!---- Our results show that direct negative selection on phenotypes that increase female promiscuity or choosiness with respect to kinship decrease the strength of selection for tendency for polyandry and inbreeding avoidance (Figure 1).
-Importantly, the cost of tendency for polyandry only decreased female fitness given tendency for polyandry phenotype values greater than zero ($P_{p}>0$), but the threshold nature of the tendency for polyandry phenotype only resulted in selection against positive tendency for polyandry allele values ($P_{a}$) when the sum over a focal female's $20$ $P_{a}$ alleles was greater than zero because summations less than zero all resulted in equivalent monandrous phenotypes ($P_{p}=0$).
-Hence, even when tendency for polyandry was costly, selection for more negative $P_{a}$ values weakened as the frequency of negative $P_{a}$ values increased because each individual $P_{a}$ then became less influential in causing females to be monandrous [@Duthie].
-This general property of threshold traits causes maladaptive phenotypes to frequently reappear within populations due to the mutation and recombination of continuous genetic values underlying discrete phenotypes [@Roff1996; @Roff1998].
-Assuming that there is continuous genetic variation underlying threshold polyandry, polyandrous phenotypes are therefore sometimes predicted to persist within populations even when costly [@Duthie], potentially creating the possibility for selection on post-copulatory inbreeding strategy when polyandry is expressed.
-This is most evident in Figure 1C, where mean allele values for polyandry are negative (red line), but strong post-copulatory inbreeding avoidance is still predicted (grey line).
-Consequently, costly polyandry does not necessarily preclude evolution of adaptive post-copulatory inbreeding avoidance in populations.
---->
-
 In our model, a cost free inbreeding strategy precluded a more costly complementary inbreeding strategy from persisting in a focal population (Figure 2), meaning that long-term persistence of both pre- and post-copulatory inbreeding avoidance might not be expected in populations given cost asymmetry.
@@
 
-<!--- Constraints on polyandry and inbreeding avoidance --->
-<!--- ---------------------------------------------- --->
-
 Our model assumed that allele values underlying tendency for polyandry, pre-copulatory inbreeding avoidance, and post-copulatory inbreeding avoidance were all initialised at zero (causing monandry, and random mating and fertilisation with respect to kinship), and phenotypes evolved simultaneously after initialisation.
@@
 We showed that selection for post-copulatory but not pre-copulatory inbreeding avoidance was strengthened if its complementary strategy was fixed for random choice with respect to kinship, and that selection for post-copulatory but not pre-copulatory inbreeding avoidance was precluded if its complementary strategy was fixed for adaptive inbreeding avoidance.
-
-<!--- Constraints on pre-copulatory and post-copulatory inbreeding avoidance might vary widely in empirical systems.
-Female mate choice might be evolutionarily constrained if females are unable to discriminate among kin and therefore incapable of choosing to avoid inbreeding [Duthie and Reid *in press*; @Penn2010].
-Similarly, females might choose to avoid inbreeding, but be ecologically constrained in their choice by the availability of males if few non-relatives are available [e.g., @Kokko2006a; @Kokko2013], or if females are unable to resist male coercion given sexual conflict [@Arnqvist2005, pp.
-44-91].
-Females might also be unable to discriminate between sperm of relatives versus non-relatives, or be unable to successfully bias fertilisation toward non-relative's sperm.
-Our results suggest that such constraints on one strategy of inbreeding avoidance (pre-copulatory versus post-copulatory) will strengthen selection on a complementary strategy, perhaps making inbreeding avoidance more detectable in empirical systems.
---->
-
-<!--- Also: note, pre-copulatory but not post-copulatory inbreeding avoidance can occur for males --->
-
-<!--- Note that females might mate multiply because first need to ensure that they get a mate at all.  \cite{Daniel2015} --->
-
-<!---  Constraints on pre-cop: Limited kin recognition --->
-
-<!--- BARRIERS to having both pre and post-copulatory inbreeding avoidance evolve are few, although -- all else being equal -- post-copulatory avoidance might evolve less often if there is existing mating avoidance.
---->
-
-<!---  Concluding paragraph below --->
-
-<!--- Studies of multiple species have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013; @Fischer2015], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009].
-Further, evidence of both pre-copulatory and post-copulatory inbreeding avoidance has been found for a handful of well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015], while @Liu2014 found evidence for pre-copulatory, but not post-copulatory, inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*).
-These empirical studies demonstrate that evolution of all combinations of pre-copulatory and post-copulatory inbreeding avoidance are possible, but no general modelling attempts to predict *a priori* whether or not inbreeding avoidance will be enacted before or after copulation, or if both pre-copulatory and post-copulatory inbreeding avoidance will evolve.
-Here we have shown that evolution of inbreeding strategies and associated polyandry are predicted to be affected by direct costs, and constraints and adaptations of complementary inbreeding strategies.
---->
-
-<!---     ----------------------------------------------------------------     --->
 

### 2016-10-13 ms_pre_post.Rmd
Revise first paragraph

@@
 For focal females, inbreeding avoidance might be acheived by avoiding related potential mates (pre-copulatory inbreeding avoidance), or by biasing fertilisation after mating has occurred so that related mates are less likely to sire offspring (post-copulatory inbreeding avoidance).
-Importantly, evolution of post-copulatory inbreeding avoidance requires that females be polyandrous, mating with multiple males during a single reproductive bout to ensure that post-copulatory choice is possible.
+Importantly, evolution of post-copulatory inbreeding avoidance requires that females be polyandrous, mating with multiple males during a single reproductive bout to ensure that post-copulatory choice can be expressed.
 As a reproductive strategy, polyandry thereby simultaneously allows females to choose multiple mates and creates the opportunity for further cryptic choice enacted through post-copulatory mechanisms.
 Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to reduce their inbreeding and therefore produce higher fitness offspring [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007].
-However, it remains unclear  <!--- Just fix this last sentence somehow...
+However, how pre- and post-copulatory strategies of inbreeding avoidance evolve jointly, and how such evolution is predicted to feedback to affect evolution of polyandry, still remains largely unknown.
+While pre-copulatory inbreeding avoidance can facilitate evolution of polyandry under some restrictive conditions [@Duthie], the opportunity for post-copulatory choice might facilitate evolution of polyandry under a much wider range of conditions by allowing females to bias fertilisation toward non-kin.
+<!--- Just fix this last sentence somehow...
 --->

### 2016-10-21 ms_pre_post.Rmd
Edit second introductory paragraph

@@
 Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to reduce their inbreeding and therefore produce higher fitness offspring [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007].
-However, how pre- and post-copulatory strategies of inbreeding avoidance evolve jointly, and how such evolution is predicted to feedback to affect evolution of polyandry, still remains largely unknown.
+However, how pre- and post-copulatory strategies of inbreeding avoidance evolve jointly, and how such evolution is predicted to feed back to affect evolution of polyandry, still remains largely unknown.
 While pre-copulatory inbreeding avoidance can facilitate evolution of polyandry under some restrictive conditions [@Duthie], the opportunity for post-copulatory choice might facilitate evolution of polyandry under a much wider range of conditions by allowing females to bias fertilisation toward non-kin.
-<!--- Just fix this last sentence somehow...
---->
 
-<!--- I fear we're starting down a rabbit hole here. ---> 
 Severe inbreeding depression might cause selection for alleles underlying active pre- and post-copulatory inbreeding avoidance and associated polyandry, but if evolution of one strategy renders its complement redundant for avoiding inbreeding, then selection might instead be sustained over generations for only one strategy.
@@
 Further, evidence of both pre-copulatory and post-copulatory inbreeding avoidance has been found for a handful of well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015], while @Liu2014 found evidence for pre-copulatory, but not post-copulatory, inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*).
+Other studies do not find any evidence for inbreeding avoidance despite strong inbreeding depression, suggesting that evolution of pre- or post-copulatory inbreeding avoidance cannot be presumed [e.g., @Frere2010; @Reid2014; @Reid2015].
 These empirical studies demonstrate that all combinations of adaptive pre-copulatory and post-copulatory inbreeding avoidance are possible, but no conceptual framework exists to predict *a priori* what combinations should be favoured by selection when both pre- and post-copulatory inbreeding avoidance, and polyandry, can evolve.
+
+<!--- Lack of evidence for inbreeding:
+
+      PreCop: @Holand2007 [Strong ID?] @Alho2012 [Strong ID?] @Hansson2006 @Reynolds2014 [Strong ID?] @Olson2012
+
+      PostCop: @Jennions2004
+
+      Neither: @Reid2014 @Reid2015 @Frere2010
+
+--->
+
+<!--- ---------------------------------------------------------------------------- --->
+<!--- -------------------- LEFT OFF HERE ----------------------------------------- --->
+<!--- ---------------------------------------------------------------------------- --->
 

### 2016-10-21 ms_pre_post.Rmd
Finish draft of Introduction

@@
 
-<!--- Lack of evidence for inbreeding:
-
-      PreCop: @Holand2007 [Strong ID?] @Alho2012 [Strong ID?] @Hansson2006 @Reynolds2014 [Strong ID?] @Olson2012
-
-      PostCop: @Jennions2004
-
-      Neither: @Reid2014 @Reid2015 @Frere2010
-
---->
-
-<!--- ---------------------------------------------------------------------------- --->
-<!--- -------------------- LEFT OFF HERE ----------------------------------------- --->
-<!--- ---------------------------------------------------------------------------- --->
-
 Frequencies of alleles underlying active pre- and post-copulatory inbreeding avoidance and polyandry are likely to be affected by direct negative selection on phenotypes (i.e., costs).
-For example, females that are genetically predisposed to polyandry often pay a cost associated with searching or making themselves available to mates, thereby increasing their own risk of predation [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
+For example, polyandrous often pay a cost associated with searching or making themselves available to mates, thereby increasing their own risk of predation [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
 Females that express pre-copulatory choice (e.g., reluctance to mate with relatives) might pay a cost of increased risk of mating failure, or harm caused by sexual conflict [@Rowe1994; @Kokko2013].
@@
 
-In addition to the relative importance of costs, evolution of pre- or post-copulatory inbreeding avoidance might be precluded if inbreeding avoidance is already acheived through a complementary strategy.
+In addition to the relative importance of costs, evolution of pre- or post-copulatory inbreeding avoidance might be precluded if inbreeding avoidance is already acheived through a complementary strategy, thereby reducing net benefits.
 Previous models considered the fate of a rare allele underlying inbreeding avoidance in a population initially fixed for random mating [e.g., Duthie and Reid *In press*; @Parker1979; @Parker2006; @Duthie].
-Such models thereby isolate the invasion fitness of a single focal strategy, but when multiple distinct strategies affect realised inbreeding, it cannot be assumed that both will invade simultaneously, nor that invasion fitness of one inbreeding strategy will be independent of another.
+Such models thereby isolate the invasion fitness of a single focal strategy.
+However, when multiple distinct strategies affect realised inbreeding, it cannot be assumed that both will invade simultaneously, nor that invasion fitness of one inbreeding strategy will be independent of another.
 For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect that such invading alleles have on decreasing total inbreeding avoidance could be weak or negligible.
-To predict evolutionary outcomes, it is therefore necessary to consider evolution when one inbreeding avoidance strategy is initially rare, and the other strategy is common.
 
-<!--- Probably want to clean up the below ---> 
 In a recent model, @Duthie showed that selection for alleles underlying polyandry and pre-copulatory inbreeding avoidance occurred only under highly constrained conditions in which direct costs of polyandry were low, and when very few males were available during a female's initial mate choice but many males were available during a female's additional mate choice(s), or when polyandry was conditionally expressed based on the degree to which a focal female engaged in inbreeding given her initially chosen mate.
@@
 However, @Duthie assumed that polyandrous females had no control over the assignment of paternity to their offspring.
-If after engaging in polyandry, females could bias paternity through post-copulatory mechanisms, then selection for polyandry to avoid inbreeding might be more widely predicted when inbreeding depression is severe [@Zeh1997].
+If after engaging in polyandry, females could bias paternity through post-copulatory mechanisms, then selection for polyandry to avoid inbreeding might be more widely predicted when inbreeding depression is severe [@Zeh1997], potentially feeding back to drive further evolution of pre- and post-copulatory strategies.
 
 Here we use individual-based modelling and *in silico* experiments to test the hypothesis that, given severe inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance causes selection for polyandry.
-Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that selection for pre-copulatory inbreeding avoidance but not post-copulatory inbreeding avoidance will occur when pre-copulatory inbreeding avoidance is less costly than the cost of post-copulatory inbreeding avoidance, while selection for post-copulatory inbreeding avoidance but not pre-copulatory inbreeding avoidance will occur when pre-copulatory inbreeding avoidance is more costly than the cost of post-copulatory inbreeding avoidance.
+Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that selection for only the less costly inbreeding avoidance strategy will be sustained over generations.
 Finally, we test the hypothesis that evolution of one inbreeding strategy will be precluded if it is introduced into a population that is already fixed for a complementary inbreeding strategy that is adaptive.
@@
 ===================================================
+
+<!--- ---------------------------------------------------------------------------- --->
+<!--- -------------------- LEFT OFF HERE ----------------------------------------- --->
+<!--- ---------------------------------------------------------------------------- --->
 

### 2016-10-21 ms_pre_post.Rmd
Full edits for new draft; still need to redo figure 2

@@
 
-<!--- ---------------------------------------------------------------------------- --->
-<!--- -------------------- LEFT OFF HERE ----------------------------------------- --->
-<!--- ---------------------------------------------------------------------------- --->
-
-We track interactions among discrete individuals in a small focal population that persists over multiple generations (key individual traits, parameter values, and variables are described in Table 1).
+We model evolution of polyandry and inbreeding avoidance through pre- and post-copulatory mechanisms by tracking interactions among discrete individuals in a small focal population that persists over multiple generations (key individual traits, parameter values, and variables are described in Table 1).
 Individuals within this population are either female or male, and can be related to each other if they share a common ancestor.
-We record the coefficient of kinship ($k$), defined as the probability that a randomly selected homologous allele from each individual is identical-by-descent [@Lynch1998], between all pairs of individuals in each generation using the population pedigree [see @Boyce1983; @Duthie].
-At the start of each generation, each female pays up to three independent costs of (1) tendency to engage in polyandry ($c_{P}$), (2) pre-copulatory inbreeding strategy (i.e., cost of mate choice; $c_{M}$), and (3) post-copulatory inbreeding strategy (i.e., cost of fertilisation bias; $c_{F}$).
-The number of males that a focal female mates with ($N_{males}$) is determined by the effects of 20 alleles ($P_{a}$) across 10 diploid loci that combine additively to determine her genotype ($P_{g}$), and ultimately her phenotype for tendency to engage in polandry ($P_{p}$).
-A focal female's choice of mate(s) is affected by 20 alleles ($M_{a}$) across 10 diploid loci that combine additively to affect her genotype ($M_{g}$) and phenotype ($M_{p}$) for pre-copulatory inbreeding avoidance or preference, and kinship between the focal female and her potential mates.
-Similarly, after mating has occurred, post-copulatory fertilisation of a focal female's $n$ total offspring is affected by 20 alleles ($F_{a}$) across 10 diploid loci that combine additively to affect the genotype ($F_{g}$) and phenotype ($F_{p}$) of the degree to which fertilisation success is affected by kinship.
-After fertilisation, the viability of a focal female's $n$ offspring is decreased by inbreeding depression ($\beta$), and surviving offspring become adults.
-After inbreeding depression in offspring viability, $\rho$ adult male immigrants arrive in the population, then density effects reduce the entire population down to separate female ($K_{f}$) and male ($K_{m}$) carrying capacities.
+Each individual has 10 diploid loci and therefore 20 alleles underlying each trait: polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$), and post-copulatory inbreeding avoidance ($F_{a}$).
+Alleles combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for each trait.
 Over generations, we record mean values of alleles underlying polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
+One generation proceeds with females paying costs, expressing polyandry, mating, and fertilising offspring; offspring alleles then mutate and offspring express inbreeding depression; finally, immigrants arrive in the populatoin and density regulation limits population growth.
 
@@
 In the unlikely event that a female's $N_{males}$ exceeds the total number of males in the population, then she mates with all of the males in the populaton.
-Most often, $N_{males}$ will be a small subset of the available males in the population [@Duthie], so a focal female will be able to preferentially mate with males that are close kin (high $k$), distant kin (low $k$), or non-kin ($k=0$) through the expression of her pre-copulatory inbreeding strategy phenotype ($M_{p}$).
+Most often, $N_{males}$ will be a small subset of the available males in the population [@Duthie], so the male(s) a focal female chooses will reflect her expression of pre-copulatory inbreeding strategy phenotype ($M_{p}$).
 Like polyandry allele values, pre-copulatory inbreeding strategy allele values ($M_{a}$) can take any real number.
@@
 Alleles of a focal female's offspring mutate with a probability of $\mu=0.001$, with mutation being an independent event that does or does not occur for each locus.
-In general, loss of function mutations might be expected to be more frequent than mutations that increase the functionality of adaptations that rely on complex physiologies or behaviours.
-If tendency for polyandry, inbreeding mating strategies, or inbreeding fertilisation strategies rely on such complex physiologies or behaviours, then we might expect the direction of mutation to be biased (e.g., towards monandry or random mating).
-However, because we are interested specifically in how selection affects reproductive strategy given varying costs and inbreeding depression, we model mutation as unbiased so that selection can be isolated and inferred clearly from mean allele values.
-
-Hence, when a mutation occurs at a locus, a new value is sampled from a random normal distribution with a mean of zero and a standard devation of mutation effect size $\mu_{SD}$, $\mathcal{N}(0, \mu_{SD})$.
+When a mutation occurs at a locus, a new value is sampled from a random normal distribution with a mean of zero and a standard devation of mutation effect size $\mu_{SD}$, $\mathcal{N}(0, \mu_{SD})$.
 This new value is then added to the original value of the allele that mutates [@Kimura1965; @Lande1976; @Bocedi2014; @Duthie].
@@
 
+<!--- ---------------------------------------------------------------------------- --->
+<!--- -------------------- LEFT OFF HERE ----------------------------------------- --->
+<!--- ---------------------------------------------------------------------------- --->
+
 Results
@@
 
-Selection for polyandry is driven by pre-copulatory inbreeding avoidance
+Will evolution of post-copulatory inbreeding avoidance stratengthen selection for polyandry?
 ----------------------------------------------
 
-For low costs of tendency for polyandry, $c_{P} < 0.005$, selection caused expected tendency for polyandry allele values ($P_{a}$) to be positive only when post-copulatory inbreeding avoidance evolved (Figure 1A-D), and for all $c_{P}$, $P_{a}$ values were higher when post-copulatory inbreeding avoidance evolved than when it could not evolve (Figure 1).
+For low costs of polyandry, $c_{P} < 0.005$, selection caused expected polyandry allele values ($P_{a}$) to be positive only when post-copulatory inbreeding avoidance evolved (Figure 1A-D).
+For all $c_{P}$, $P_{a}$ values were higher when post-copulatory inbreeding avoidance evolved than when it could not evolve (Figure 1).
 When post-copulatory inbreeding avoidance could not evolve, $P_{a}$ values were negative even in the absence of a direct cost ($c_{P}=0$; Figure 1A) because females that expressed polyandry were more likely to increase their inbreeding due to sampling males without replacement [@Duthie].
 Strong post-copulatory inbreeding avoidance consistently evolved in all simulations, even when $P_{a}$ values were expected to be slightly negative (Figure 1F,H), because of the threshold nature of the polyandry phenotype; Figure 2 shows how phenotypic polyandry was common even when mean polyandry allele values within a population were expected to be negative.
-In all simulations, pre-copulatory inbreeding avoidance also evolved ($M_{a}<0$), meaning that both pre- and post-copulatory inbreeding avoidance was predicted, and evolution of adaptive polyandry occurred given sufficiently low costs of tendency for polyandry.
+In all simulations, pre-copulatory inbreeding avoidance also evolved ($M_{a}<0$), meaning that both pre- and post-copulatory inbreeding avoidance was predicted, and evolution of adaptive polyandry occurred given sufficiently low costs of polyandry.
 
-Selection greatly weakened for a relatively more costly inbreeding strategy
+Will selection for a costly inbreeding strategy be negligible given a non-costly alternative strategy?
 ----------------------------------------------
@@
 For simulations in which either pre- or post-copulatory inbreeding strategy allele values were fixed for random choice with respect to kinship ($M_{a}=0$ or $F_{a}=0$, respectively), the alternative costly inbreeding strategy evolved to inbreeding avoidance ($F_{a}<0$ or $M_{a}<0$; Figure 3).
-However, when the alternative inbreeding strategy could evolve and was not costly, the focal costly inbreeding strategy initially evolved towards inbreeding avoidance, but then evolved toward random choice given increasingly negative allele values of the alternative strategy over generations (Figure 3B,D).
+However, when the alternative inbreeding strategy could evolve and was not costly, the focal costly inbreeding strategy initially evolved towards inbreeding avoidance, but then evolved toward random choice with respect to kinship given increasingly negative allele values of the alternative strategy over generations (Figure 3B,D).
 For example, given fixed $F_{a}=0$, grand mean $M_{a}$ values were $-0.868$ in the last $10000$ generations (Figure 3A), meaning that an outbred focal female was ca $5.34$ times less likely to choose a full-sibling and ca $2.10$ times less likely to choose a first cousin than a non-relative given a strong cost of pre-copulatory inbreeding avoidance, $c_{M}=0.02$.
@@
 
-Existing adaptation preclude post- but not pre-copulatory inbreeding avoidance
+Will selection for a costly inbreeding strategy be negligible given existence of an already adaptive alternative strategy?
 ----------------------------------------------
@@
 
-We modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency to engage in polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
+We have provided a novel framework for approaching empirical studies of inbreeding avoidance, predicting evolution of polyandry and inbreeding avoidance through pre- and post-copulatory mechanisms.
+Accordingly, we modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency to engage in polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
 Using *in silico* experiments, we tested three specific hypothesis to predict evolution of polyandry, and pre- and post-copulatory inbreeding strategy.
 We found that (1) selection for polyandry was greatly strengthened given concurrent evolution of post-copulatory inbreeding avoidance, (2) selection for costly pre- or post-copulatory inbreeding avoidance was negligible given evolution of a less costly strategy of inbreeding avoidance, and (3) pre-existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance, but not vice versa.
-More generally, we provide a novel framework for approaching empirical studies of inbreeding avoidance, predicting evolution of polyandry and inbreeding avoidance through pre- and post-copulatory mechanisms.
 
@@
 commodus* are capable of controlling the transfer of sperm to their spermatheca, most likely through physical control of the spermathecal duct, and can reduce sperm storage despite being guarded by a related male.
-Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for polyandry, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
+Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for further polyandry, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
 
@@
 @Pomiankowski1987 categorised four types of costs that are relevant to mate choice, which we suggest are also relevant costs for polyandry, and include costs of elevated risks associated with (1) predation or (2) disease transmission, and costs incurred through (3) loss of time or (4) depletion of energy.
-In our model, we interpreted a cost of tendency for polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of pre-copulatory inbreeding strategy as a lost of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of post-copulatory inbreeding strategy as depletion of energy.
+In our model, we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of pre-copulatory inbreeding strategy as a lost of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of post-copulatory inbreeding strategy as depletion of energy.
 While these costs are biologically realistic, different costs will be relevant for different populations and be realised in different ways.
@@
 
-Our model assumed that allele values underlying tendency for polyandry, pre-copulatory inbreeding avoidance, and post-copulatory inbreeding avoidance were all initialised at zero (causing monandry, and random mating and fertilisation with respect to kinship), and phenotypes evolved simultaneously after initialisation.
+Our model assumed that allele values underlying polyandry, pre-copulatory inbreeding avoidance, and post-copulatory inbreeding avoidance were all initialised at zero (causing monandry, and random mating and fertilisation with respect to kinship), and phenotypes evolved simultaneously after initialisation.
 However, these initial conditions are likely to be atypical, as evolution of pre-copulatory and post-copulatory inbreeding avoidance from ancestral random mating and fertilisation is unlikely to occur simultaneously.
@@
 
-\vspace{80 mm}
+\vspace{140 mm}
 

### 2016-10-24 analysis.R
Change two panel figure to four panel figure (Fig. 2)

@@ -305,49 +305,81 @@ dev.off();
 # XXX XXX      PLOT FIGURE 2  XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 
-evo_cc_02 <- read.table(file="results/fig2/evo_M00_P02_F00_b.txt", header=FALSE);
-evgens <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0.02 & evo_cc_02[,5]==0,];
+evo_cc_02 <- read.table(file="results/fig2/evo_M00_P02_F00.txt", header=FALSE);
+evgens <- evo_cc_02[evo_cc_02[,3]==0 & evo_cc_02[,4]==0.02 & evo_cc_02[,5]==0.00,];
 evlast <- evgens[evgens[,6]==gens,]; 
-above1 <- which(evlast[,8] == min(evlast[(evlast[,8]-1)>0,8]))[1];
-below1 <- which(evlast[,8] == max(evlast[(evlast[,8]-0)<0,8]))[1];
+above1 <- which(evlast[,8] == min(evlast[(evlast[,8]-0.25)>0,8]))[1];
+below1 <- which(evlast[,8] == max(evlast[(evlast[,8]+0.35)<0,8]))[1];
 simabo <- evlast[above1,1];
 simbel <- evlast[below1,1];
 
-ped_cc_02 <- read.table(file="results/fig2/ped_M00_P02_F00_b.txt", header=FALSE);
+ped_cc_02 <- read.table(file="results/fig2/ped_M00_P02_F00.txt", header=FALSE);
 xxx <- 0:gens;
 
 setEPS(); # postscript below for final publication?
-cairo_ps("figures/Pp_vals.eps",family="Arial",height=11,width=9);
-par(mfrow=c(2,1),mar=c(5,5,1,3));
+cairo_ps("figures/Pp_vals.eps",family="Arial",height=8,width=10);
+par(mfrow=c(2,2),mar=c(1,5,1,3));
+#---------------------------------------------------------------------------
 evo_bel <- evo_cc_02[evo_cc_02[,1]==simbel,8];
-plot(x=xxx,y=evo_bel,type="l",lwd=2,ylim=c(-4.2,4.2),col="red",xaxt="n",
-     xlab=expression(paste("Generation")),
-     ylab=expression(paste("Mean allele value")),
[…]

### 2016-10-24 ms_pre_post.Rmd
Fix legend of Figure 2 to correspond with new figure. Add a clause in the Results to include new figure idea

@@
 When post-copulatory inbreeding avoidance could not evolve, $P_{a}$ values were negative even in the absence of a direct cost ($c_{P}=0$; Figure 1A) because females that expressed polyandry were more likely to increase their inbreeding due to sampling males without replacement [@Duthie].
-Strong post-copulatory inbreeding avoidance consistently evolved in all simulations, even when $P_{a}$ values were expected to be slightly negative (Figure 1F,H), because of the threshold nature of the polyandry phenotype; Figure 2 shows how phenotypic polyandry was common even when mean polyandry allele values within a population were expected to be negative.
+Strong post-copulatory inbreeding avoidance consistently evolved in all simulations, even when $P_{a}$ values were expected to be slightly negative (Figure 1F,H), because of the threshold nature of the polyandry phenotype; Figure 2 shows how phenotypic polyandry was common even when mean polyandry allele values within a population were expected to be negative, and how monandry occurred even when mean polyandry allele values were expected to be positive.
 In all simulations, pre-copulatory inbreeding avoidance also evolved ($M_{a}<0$), meaning that both pre- and post-copulatory inbreeding avoidance was predicted, and evolution of adaptive polyandry occurred given sufficiently low costs of polyandry.
@@
 ![Relationship between polyandry allele values and phenotypes for an individual-based model in which pre- and post-copulatory inbreeding strategies evolve jointly with polyandry.
-The red line in (A) shows the mean value of alleles underlying polyandry for a single replicate simulation over 40000 generations.
+Two simulations with identical starting conditions (default parameter values with no costs) are shown in panels A,B and C,D.
+Red lines in (A) and (C) show mean value of alleles underlying polyandry for a single replicate simulation over 40000 generations.
 Positive allele values contribute to polyandry, while negative values contribute to monandry (dotted line shows zero on the y-axis).
-In the last generation, mean allele value was below zero.
-Nevertheless, due to among-individual variation and the threshold nature of the polyandry phenotype, polyandry persists in the population.
-The histogram in (B) shows females' tendency for polyandry phenotypes in the last generation; white and grey shading indicates monandrous and polyandrous females, respectively.
-While the average female was monandrous, several females were polyandrous.](figures/Pp_vals1.png)
+In the last generation, mean allele value was below (A) or above (C) zero.
+Nevertheless, due to among-individual variation and the threshold nature of the polyandry phenotype, polyandry persists in the population in (A) and monandry persists in (C).
+The histograms in (B) and (D) show females' tendency for polyandry phenotypes in the last generation; white and grey shading indicates monandrous and polyandrous females, respectively.](figures/Pp_vals.png)
 

### 2016-10-25 analysis.R
Add parenthetical allele on y-axis of Fig 2

@@ -322,7 +322,7 @@ par(mfrow=c(2,2),mar=c(1,5,1,3));
 #---------------------------------------------------------------------------
 evo_bel <- evo_cc_02[evo_cc_02[,1]==simbel,8];
 plot(x=xxx,y=evo_bel,type="l",lwd=2,ylim=c(-6.2,3.2),col="red",xaxt="n",
-     xlab="",ylab=expression(paste("Mean allele value")),
+     xlab="",ylab=expression(paste("Mean allele value (",P[a],")")),
      cex.lab=1.75,cex.axis=1.5,yaxt="n",lty="solid");
 abline(h=0,lty="dotted",lwd=0.8);
 arrows(x0=gens+5000,x1=gens+250,y0=evo_bel[gens],y1=evo_bel[gens],length=0.1,lwd=2);
@@ -354,7 +354,7 @@ par(mar=c(5,5,1,3));
 evo_abo <- evo_cc_02[evo_cc_02[,1]==simabo,8];
 plot(x=xxx,y=evo_abo,type="l",lwd=2,ylim=c(-6.2,3.2),col="red",xaxt="n",
      xlab=expression(paste("Generation")),
-     ylab=expression(paste("Mean allele value")),
+     ylab=expression(paste("Mean allele value (",P[a],")")),
      cex.lab=1.75,cex.axis=1.75,yaxt="n",lty="solid");
 abline(h=0,lty="dotted",lwd=0.8);
 arrows(x0=gens+5000,x1=gens+250,y0=evo_abo[gens],y1=evo_abo[gens],length=0.1,lwd=2);

### 2016-10-25 ms_pre_post.Rmd
Final draft to send off to coauthors

@@
 
-Inbreeding often reduces the fitness of inbred offspring (termed 'inbreeding depression'), potentially driving evolution of inbreeding avoidance when inbreeding depression is strong [@Parker1979; @Parker2006; @Pusey1996; @Charlesworth1999; @Keller2002; @Charlesworth2009; @Szulkin2012].
+Inbreeding typically reduces the fitness of inbred offspring (termed 'inbreeding depression'), potentially driving evolution of inbreeding avoidance when inbreeding depression is strong [@Parker1979; @Parker2006; @Pusey1996; @Charlesworth1999; @Keller2002; @Charlesworth2009; @Szulkin2012].
 For focal females, inbreeding avoidance might be acheived by avoiding related potential mates (pre-copulatory inbreeding avoidance), or by biasing fertilisation after mating has occurred so that related mates are less likely to sire offspring (post-copulatory inbreeding avoidance).
@@
 As a reproductive strategy, polyandry thereby simultaneously allows females to choose multiple mates and creates the opportunity for further cryptic choice enacted through post-copulatory mechanisms.
-Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to reduce their inbreeding and therefore produce higher fitness offspring [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007].
+Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and therefore produce higher fitness offspring [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007].
 However, how pre- and post-copulatory strategies of inbreeding avoidance evolve jointly, and how such evolution is predicted to feed back to affect evolution of polyandry, still remains largely unknown.
@@
 Frequencies of alleles underlying active pre- and post-copulatory inbreeding avoidance and polyandry are likely to be affected by direct negative selection on phenotypes (i.e., costs).
-For example, polyandrous often pay a cost associated with searching or making themselves available to mates, thereby increasing their own risk of predation [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
+For example, polyandrous females often pay a cost associated with searching or making themselves available to mates, thereby increasing their own risk of predation [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
 Females that express pre-copulatory choice (e.g., reluctance to mate with relatives) might pay a cost of increased risk of mating failure, or harm caused by sexual conflict [@Rowe1994; @Kokko2013].
@@
 Individuals within this population are either female or male, and can be related to each other if they share a common ancestor.
-Each individual has 10 diploid loci and therefore 20 alleles underlying each trait: polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$), and post-copulatory inbreeding avoidance ($F_{a}$).
+Each individual has 10 diploid loci and therefore 20 alleles underlying each trait: tendency to engage in polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$ i.e., 'fertilisation' alleles).
 Alleles combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for each trait.
@@
 
-Values of phenotypic traits for tendency to engage in polyandry ($P_{p}$), pre-copulatory inbreeding strategy (i.e., inbreeding mating strategy, $M_{p}$), and post-copulatory inbreeding strategy (i.e., inbreeding fertilisation strategy, $F_{p}$) each have costs.
+Values of phenotypic traits for tendency to engage in polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$) each have costs.
 Each cost independently increases the risk of female pre-mating mortality and, because generations are non-overlapping, total reproductive failure as a linear function of its associated trait.
-The probability that a focal female dies before mating due to the cost of polyandry is therefore $P_{p} \times c_{P}$.
-Similarly, the probability of pre-mating female mortality due to the cost of pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy is $|M_{p}| \times c_{M}$ and $|F_{p}| \times c_{F}$, repectively, where $|M_{p}|$ is the absolute value of $M_{p}$ and $|F_{p}|$ is the absolute value of $F_{p}$.
+The probability that a focal female dies before mating due to the cost of polyandry ($c_{P}$) is therefore $P_{p} \times c_{P}$.
+Similarly, the probability of pre-mating female mortality due to the cost of pre-copulatory inbreeding strategy ($c_{M}$) and post-copulatory inbreeding strategy ($c_{F}$) is $|M_{p}| \times c_{M}$ and $|F_{p}| \times c_{F}$, repectively, where $|M_{p}|$ is the absolute value of $M_{p}$ and $|F_{p}|$ is the absolute value of $F_{p}$.
 Absolute values are used for applying costs to inbreeding strategies because both negative and positive $M_{p}$ and $F_{p}$ bias breeding interactions with respect to kinship, while only positive values of $P_{p}$ affect a female's tendency for polyandry; zero and negative $P_{p}$ values always translate to monandrous phenotypes (see below).
@@
 While all males are therefore available as potential mates, we assume that a female mates with her total allotment of $N_{males}$ without replacement, meaning that $N_{males}$ models the total number of distinct males that a female chooses to mate with rather than the number of times that she mates.
-In the unlikely event that a female's $N_{males}$ exceeds the total number of males in the population, then she mates with all of the males in the populaton.
+In the unlikely event that a female's $N_{males}$ exceeds the total number of males in the population, then she mates with all of the males in the population.
 Most often, $N_{males}$ will be a small subset of the available males in the population [@Duthie], so the male(s) a focal female chooses will reflect her expression of pre-copulatory inbreeding strategy phenotype ($M_{p}$).
@@
 
-The fertilisation of a female's $n$ offspring occurs after mating, with each of her $n$ offspring being assigned a sire independently and with replacement from the $N_{males}$ with which the female mated.
+Fertilisation of a female's $n$ offspring occurs after mating, with each of her $n$ offspring being assigned a sire independently and with replacement from the $N_{males}$ with which the female mated.
 The probability that a male mate successfully sires an offspring is affected by a female's kinship with the potential sire ($k_{ij}$) and her post-copulatory inbreeding strategy ($F_{p}$).
@@
 The coefficient of kinship between an immigrant and all other individuals (including native individuals and other immigrants) always equals zero ($k_{ij}=0$).
-Because kinship coefficient values are calculated directly from the pedigree of the focal population, the addition of immigrants thereby introduces non-kin into the population at a constant rate and prevents the mean kinship coefficient of the population from asymptoting to a value of 1 over generations.
+Because kinship coefficient values are calculated directly from the pedigree of the focal population [not from individuals' genomes; see @Duthie], the addition of immigrants introduces non-kin into the population at a constant rate and prevents the mean kinship coefficient of the population from asymptoting to a value of 1 over generations.
 If the focal population was instead closed ($\rho=0$), then all alleles would quickly be expected to become identical-by-descent among descendants of the ancestral population.
 To avoid having immigrants affect evolution of tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$), immigrants are always male and can therefore be chosen based on their kinship values of zero but not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$.
-To further avoid having immigrants affect evolutionary dynamics, allele values underlying tendency for polyandry ($P_{a}$), pre-copulatory inbreeding strategy ($M_{a}$), and post-copulatory inbreeding strategy ($F_{a}$) are randomly sampled from normal distributions with means and standard deviations of $P_{a}$, $M_{a}$, and $F_{a}$ values equal to the means and standard deviations of those in the focal population at the time of immigration.
+To further avoid having immigrants affect evolutionary dynamics, allele values underlying ($P_{a}$), pre-copulatory inbreeding strategy ($M_{a}$), and post-copulatory inbreeding strategy ($F_{a}$) are randomly sampled from normal distributions with means and standard deviations of $P_{a}$, $M_{a}$, and $F_{a}$ values equal to the means and standard deviations of those in the focal population at the time of immigration.
 Overall, this model of immigration effectively assumes that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$.
@@
 For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling [@Duthie] showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
-For all replicates, we set $\rho=5$ immigrants, which produced a range of kin and non-kin in each generation allowing females could express inbreeding strategies, and $n=8$ offspring, which was sufficient to keep populations consistently near carrying capacities and avoid population extinction.
+For all replicates, we set $\rho=5$ immigrants, which produced a range of kin and non-kin in each generation allowing females could express inbreeding strategies, and $n=8$ offspring, which was sufficient to keep populations consistently at carrying capacities and avoid population extinction.
 Values of $K_{f}$ and $K_{m}$ were both set to 100 because previous modelling has shown that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but populations are also not so small that selection is typically overwhelmed by genetic drift (Duthie and Reid *in press*).
@@
 
-<!--- ---------------------------------------------------------------------------- --->
-<!--- -------------------- LEFT OFF HERE ----------------------------------------- --->
-<!--- ---------------------------------------------------------------------------- --->
-
 Results
@@
 
-Will evolution of post-copulatory inbreeding avoidance stratengthen selection for polyandry?
+Will evolution of post-copulatory inbreeding avoidance strengthen selection for polyandry?
 ----------------------------------------------
@@
 When post-copulatory inbreeding avoidance could not evolve, $P_{a}$ values were negative even in the absence of a direct cost ($c_{P}=0$; Figure 1A) because females that expressed polyandry were more likely to increase their inbreeding due to sampling males without replacement [@Duthie].
-Strong post-copulatory inbreeding avoidance consistently evolved in all simulations, even when $P_{a}$ values were expected to be slightly negative (Figure 1F,H), because of the threshold nature of the polyandry phenotype; Figure 2 shows how phenotypic polyandry was common even when mean polyandry allele values within a population were expected to be negative, and how monandry occurred even when mean polyandry allele values were expected to be positive.
+Strong post-copulatory inbreeding avoidance consistently evolved in all simulations, even when $P_{a}$ values were expected to be slightly negative (Figure 1F,H), because of the threshold nature of the polyandry phenotype.
+Figure 2 shows how phenotypic polyandry was common even when mean polyandry allele values within a population were expected to be negative, and how monandry occurred even when mean polyandry allele values were expected to be positive.
 In all simulations, pre-copulatory inbreeding avoidance also evolved ($M_{a}<0$), meaning that both pre- and post-copulatory inbreeding avoidance was predicted, and evolution of adaptive polyandry occurred given sufficiently low costs of polyandry.
@@
 This lack of evolution of post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
-When pre-copulatory inbreeding avoidance and polyandry were both fixed ($F_{a}=-10$ and $P_{a}=1$), post-copulatory inbreeding strategy evolved to similarly negative mean allele values as pre-copulatory inbreeding strategy did in Figure 4A,B (see Supporting Information).
+When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), post-copulatory inbreeding strategy evolved to similarly negative mean allele values as pre-copulatory inbreeding strategy did in Figure 4A,B (see Supporting Information).
 

### 2016-10-25 pre_post_biorxiv.tex
Initial biorXiv format; still must add three figures accurately

--- 2016-10-25 ms_pre_post.Rmd
@@
----
-title: "Evolution of pre-copulatory and post-copulatory inbreeding behaviour"
-author: "A. Bradley Duthie et al."
-date: "August 24, 2016"
-output:
-  pdf_document:
-    fig_caption: yes
-  html_document: default
-  word_document:
-    fig_caption: yes
-    pandoc_args:
-    - --csl
-    - evolution.csl
-header-includes:
-- \usepackage{natbib}
-- \usepackage{lineno}
-- \linenumbers
-- \bibliographystyle{amnatnat}
-linestretch: 2
-csl: evolution.csl
-bibliography: ms_pre_post.bib
----
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in,marginparwidth=2in]{geometry}
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{setspace}
+\usepackage{natbib}
+\usepackage{rotating}
+\usepackage{multirow}
+\usepackage{datetime}
+\setkomafont{\rmfamily\bfseries\boldmath}
+\usepackage{wrapfig,floatrow}
+\usepackage{float}
+\usepackage[font=small,labelfont=bf]{caption}
+\usepackage{mathabx}
+\usepackage{color}
+\usepackage{wasysym}
+\usepackage{sidecap}
+%\usepackage{caption}
+\usepackage{xargs,caption,changepage,ifthen}
+\usepackage[demo]{graphicx}
 
-******************************
+% use Unicode characters - try changing the option if you run into troubles with special characters (e.g. umlauts)
+\usepackage[utf8]{inputenc}
 
-Abstract
-===================================================
+% clean citations
+%\usepackage{cite}
 
+% hyperref makes references clicky. use \url{www.example.com} or \href{www.example.com}{description} to add a clicky url
+\usepackage{nameref,hyperref}
+\hypersetup{
+     colorlinks   = true,
+     citecolor    = blue,
+     linkcolor    = black
+}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% improves typesetting in LaTeX
+\usepackage{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
+
+% text layout - change as needed
+%\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in 
+\textheight 8.75in
+
+% Remove % for double line spacing
+%\usepackage{setspace} 
+%\doublespacing
+
+% use adjustwidth environment to exceed text width (see examples in text)
+\usepackage{changepage}
+
+% adjust caption style
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,singlelinecheck=off]{caption}
+
+% remove brackets from references
+\makeatletter
+\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
+
+% headrule, footrule and page numbers
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
+\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+
+% use \textcolor{color}{text} for colored text (e.g. highlight to-do areas)
+\usepackage{color}
+
+% define custom colors (this one is for figure captions)
+\definecolor{Gray}{gray}{.25}
+
+% this is required to include graphics
+\usepackage{graphicx}
+
+% use if you want to put caption to the side of the figure - see example in text
+\usepackage{sidecap}
+
+% use for have text wrap around figures
+\usepackage{wrapfig}
+\usepackage[pscoord]{eso-pic}
+\usepackage[fulladjust]{marginnote}
+\reversemarginpar
+
+%----------------------------------------
+%COMMAND FOR DOING SIDE CAPTION.
+%----------------------------------------
+\newcommandx{\mycaptionminipage}[3][3=c,usedefault]{%
+    \begin{minipage}[#3]{#1}%
+        \ifthenelse{\equal{#3}{b}}{\captionsetup{aboveskip=0pt}}{}
+        \ifthenelse{\equal{#3}{t}}{\captionsetup{belowskip=0pt}}{}
+        \vspace{0pt}\centering\captionsetup{width=\textwidth} %Temporarily set caption width
+        #2%
+    \end{minipage}%
+}%
+\newcommandx{\mysidecaption}[4][4=c,usedefault]{%
+    \checkoddpage%
+    \ifoddpage%
+        %CASE ODD PAGES
+        \mycaptionminipage{\dimexpr\linewidth-#1\linewidth-\intextsep\relax}{#3}[#4]%
+        \hfill%
+        \mycaptionminipage{#1\linewidth}{#2}[#4]%
+    \else%
+        %CASE EVEN PAGES
+        \mycaptionminipage{#1\linewidth}{#2}[#4]%
+        \hfill%
+        \mycaptionminipage{\dimexpr\linewidth-#1\linewidth-\intextsep\relax}{#3}[#4]%
+    \fi%
+}%
+
+% document begins here
+\begin{document}
+\vspace*{0.35in}
+
+% title goes here:
+\begin{flushleft}
+{\LARGE
+\textbf\newline{Evolution of pre-copulatory and post-copulatory inbreeding behaviour}
+}
+\newline
+% authors go here:
+\\
+A. Bradley Duthie\textsuperscript{1,*},
+Jane M. Reid\textsuperscript{1},
+\\
+\bigskip
+\bf{1} Institute of Biological and Environmental Sciences, School of Biological Sciences, Zoology Building, Tillydrone Avenue, University of Aberdeen, Aberdeen AB24 2TZ, United Kingdom
+%\\
+%\bf{2} Affiliation B
+\\
+\bigskip
+*  aduthie@abdn.ac.uk, brad.duthie@gmail.com
+
+\end{flushleft}
+
+\section*{Abstract}
+\marginpar{
+\vspace{0.0cm} % adjust vertical position relative to text with \vspace{} - note that you can enter negative numbers to move margin caption up
+\color{Gray} % this gives caption a grey color to set it apart from text body
+\textbf{Key words:} % note that \ref{fig1} refers to the corresponding wrapfigure
+Inbreeding, inbreeding avoidance, inbreeding depression, mate choice, relatedness, reproductive strategy
+}
 Inbreeding avoidance has been widely observed through pre-copulatory and post-copulatory mechanisms as a consequence of inbreeding depression in offspring viability.
@@
 
-Introduction
-===================================================
+\section*{Introduction}
 
-Inbreeding typically reduces the fitness of inbred offspring (termed 'inbreeding depression'), potentially driving evolution of inbreeding avoidance when inbreeding depression is strong [@Parker1979; @Parker2006; @Pusey1996; @Charlesworth1999; @Keller2002; @Charlesworth2009; @Szulkin2012].
+Inbreeding typically reduces the fitness of inbred offspring (termed `inbreeding depression'), potentially driving evolution of inbreeding avoidance when inbreeding depression is strong \cite[][]{Parker1979, Parker2006, Pusey1996, Charlesworth1999, Keller2002, Charlesworth2009, Szulkin2012}.
 For focal females, inbreeding avoidance might be acheived by avoiding related potential mates (pre-copulatory inbreeding avoidance), or by biasing fertilisation after mating has occurred so that related mates are less likely to sire offspring (post-copulatory inbreeding avoidance).
@@
 As a reproductive strategy, polyandry thereby simultaneously allows females to choose multiple mates and creates the opportunity for further cryptic choice enacted through post-copulatory mechanisms.
-Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and therefore produce higher fitness offspring [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007].
+Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and therefore produce higher fitness offspring \cite[][]{Zeh1997, Jennions2000, Tregenza2002, Akcay2007}.
 However, how pre- and post-copulatory strategies of inbreeding avoidance evolve jointly, and how such evolution is predicted to feed back to affect evolution of polyandry, still remains largely unknown.
-While pre-copulatory inbreeding avoidance can facilitate evolution of polyandry under some restrictive conditions [@Duthie], the opportunity for post-copulatory choice might facilitate evolution of polyandry under a much wider range of conditions by allowing females to bias fertilisation toward non-kin.
+While pre-copulatory inbreeding avoidance can facilitate evolution of polyandry under some restrictive conditions \cite[][]{Duthie}, the opportunity for post-copulatory choice might facilitate evolution of polyandry under a much wider range of conditions by allowing females to bias fertilisation toward non-kin.
 
 Severe inbreeding depression might cause selection for alleles underlying active pre- and post-copulatory inbreeding avoidance and associated polyandry, but if evolution of one strategy renders its complement redundant for avoiding inbreeding, then selection might instead be sustained over generations for only one strategy.
-Empirical studies of multiple species have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013; @Fischer2015], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009].
-Further, evidence of both pre-copulatory and post-copulatory inbreeding avoidance has been found for a handful of well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015], while @Liu2014 found evidence for pre-copulatory, but not post-copulatory, inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*).
-Other studies do not find any evidence for inbreeding avoidance despite strong inbreeding depression, suggesting that evolution of pre- or post-copulatory inbreeding avoidance cannot be presumed [e.g., @Frere2010; @Reid2014; @Reid2015].
-These empirical studies demonstrate that all combinations of adaptive pre-copulatory and post-copulatory inbreeding avoidance are possible, but no conceptual framework exists to predict *a priori* what combinations should be favoured by selection when both pre- and post-copulatory inbreeding avoidance, and polyandry, can evolve.
+Empirical studies of multiple species have found evidence for female pre-copulatory inbreeding avoidance \cite[e.g.,][]{Lihoreau2007, Kuriwada2011, Kingma2013, Fischer2015}, and for post-copulatory inbreeding avoidance \cite[e.g.,][]{Simmons2006, Bretman2009}.
+Further, evidence of both pre-copulatory and post-copulatory inbreeding avoidance has been found for a handful of well-studied species, including Trinidadian guppies \cite[\textit{Poecilia reticulata};][]{Gasparini2011, Daniel2015} and house mice \cite[\textit{Mus domesticus};][]{Potts1991, Firman2015}, while \cite{Liu2014} found evidence for pre-copulatory, but not post-copulatory, inbreeding avoidance in an experimental study of cabbage beetles (\textit{Colaphellus bowringi}).
+Other studies do not find any evidence for inbreeding avoidance despite strong inbreeding depression, suggesting that evolution of pre- or post-copulatory inbreeding avoidance cannot be presumed \cite[e.g.,][]{Frere2010, Reid2014, Reid2015}.
+These empirical studies demonstrate that all combinations of adaptive pre-copulatory and post-copulatory inbreeding avoidance are possible, but no conceptual framework exists to predict \textit{a priori} what combinations should be favoured by selection when both pre- and post-copulatory inbreeding avoidance, and polyandry, can evolve.
 
 Frequencies of alleles underlying active pre- and post-copulatory inbreeding avoidance and polyandry are likely to be affected by direct negative selection on phenotypes (i.e., costs).
-For example, polyandrous females often pay a cost associated with searching or making themselves available to mates, thereby increasing their own risk of predation [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
-Females that express pre-copulatory choice (e.g., reluctance to mate with relatives) might pay a cost of increased risk of mating failure, or harm caused by sexual conflict [@Rowe1994; @Kokko2013].
-Females that express post-copulatory choice might pay an energetic cost associated with physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
+For example, polyandrous females often pay a cost associated with searching or making themselves available to mates, thereby increasing their own risk of predation \cite[e.g.,][]{Rowe1988, Ronkainen1994, Koga1998}.
+Females that express pre-copulatory choice (e.g., reluctance to mate with relatives) might pay a cost of increased risk of mating failure, or harm caused by sexual conflict \cite[][]{Rowe1994, Kokko2013}.
+Females that express post-copulatory choice might pay an energetic cost associated with physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation \cite[e.g.,][]{Gasparini2011, Tuni2013, Fitzpatrick2014b}.
 If the relative costs affecting pre- and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly inbreeding strategy might become fixed in the population over generations, while alleles underlying the more costly inbreeding strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
@@
 In addition to the relative importance of costs, evolution of pre- or post-copulatory inbreeding avoidance might be precluded if inbreeding avoidance is already acheived through a complementary strategy, thereby reducing net benefits.
-Previous models considered the fate of a rare allele underlying inbreeding avoidance in a population initially fixed for random mating [e.g., Duthie and Reid *In press*; @Parker1979; @Parker2006; @Duthie].
+Previous models considered the fate of a rare allele underlying inbreeding avoidance in a population initially fixed for random mating \cite[e.g.,][; Duthie and Reid \textit{In press}]{Parker1979, Parker2006, Duthie}.
 Such models thereby isolate the invasion fitness of a single focal strategy.
@@
 
-In a recent model, @Duthie showed that selection for alleles underlying polyandry and pre-copulatory inbreeding avoidance occurred only under highly constrained conditions in which direct costs of polyandry were low, and when very few males were available during a female's initial mate choice but many males were available during a female's additional mate choice(s), or when polyandry was conditionally expressed based on the degree to which a focal female engaged in inbreeding given her initially chosen mate.
+In a recent model, \cite{Duthie} showed that selection for alleles underlying polyandry and pre-copulatory inbreeding avoidance occurred only under highly constrained conditions in which direct costs of polyandry were low, and when very few males were available during a female's initial mate choice but many males were available during a female's additional mate choice(s), or when polyandry was conditionally expressed based on the degree to which a focal female engaged in inbreeding given her initially chosen mate.
 In the absence of these constraints, expression of polyandry was expected to increase inbreeding with each additional mate because remaining males were more likely to be relatives once available non-relatives were chosen.
-However, @Duthie assumed that polyandrous females had no control over the assignment of paternity to their offspring.
-If after engaging in polyandry, females could bias paternity through post-copulatory mechanisms, then selection for polyandry to avoid inbreeding might be more widely predicted when inbreeding depression is severe [@Zeh1997], potentially feeding back to drive further evolution of pre- and post-copulatory strategies.
+However, \cite{Duthie} assumed that polyandrous females had no control over the assignment of paternity to their offspring.
+If after engaging in polyandry, females could bias paternity through post-copulatory mechanisms, then selection for polyandry to avoid inbreeding might be more widely predicted when inbreeding depression is severe \cite[][]{Zeh1997}, potentially feeding back to drive further evolution of pre- and post-copulatory strategies.
 
@@
 
-******************************
+\section*{Model}
 
-Model
-===================================================
+\begin{table}[!ht]
+\begin{adjustwidth}{-1.75in}{0in}
+\centering
+\caption{\color{Gray}Individual traits (A), model parameter values (B), and model variables (C) for an individual based model of the evolution of polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.}
+\begin{tabular}{lllll}
+\hline
+A & Trait & Allele & Genotype & Phenotype &
+\hline
+  & Tendency for polyandry               &   $P_{a}$  &  $P_{g}$  &  $P_{p}$  &
+  & Pre-copulatory inbreeding strategy   &   $M_{a}$  &  $M_{g}$  &  $M_{p}$  &
+  & Post-copulatory inbreeding strategy  &   $F_{a}$  &  $F_{g}$  &  $F_{p}$  &
+  &                                      &            &           &           &
+\hline
+B & Description & Parameter & & Default value(s) &
+\hline
+
+  & Cost of pre-copulatory inbreeding strategy    & $c_{M}$    & & $0$, $0.02$   &
+  & Cost of post-copulatory inbreeding strategy   & $c_{F}$    & & $0$, $0.02$   &
+  & Focal female's number of offspring            & $n$        & & $8$           &
+  & Log-linear slope of inbreeding depression     & $\beta$    & & $3$           &
+  & Adult male immigrants per generation          & $\rho$     & & $5$           & 
+  & Female carrying capacity                      & $K_{f}$    & & $100$         &
+  & Male carrying capacity                        & $K_{m}$    & & $100$         &
+  & Mutation rate of alleles                      & $\mu$      & & $0.001$       &
+  & Standard deviation of mutation effect size    & $\mu_{SD}$ & & $\sqrt{1/20}$ &
+  &                                               &            & &               &
+\hline
+C & Description & & & Variable &
+\hline
+  & Coefficient of kinship                                            & & & $k$              &
+  & Focal female's number of mates                                    & & & $N_{males}$      &
+  & Female $i$'s perceived absolute mate quality of male $j$          & & & $Q^{m}_{ij}$     &
+  & Female $i$'s perceived relative mate quality of male $j$          & & & $q^{m}_{ij}$     &
+  & Female $i$'s perceived absolute fertilisation quality of male $j$ & & & $Q^{f}_{ij}$     &
+  & Female $i$'s perceived relative fertilisation quality of male $j$ & & & $q^{f}_{ij}$     &
+  & Viability of a focal female's offspring                           & & & $\Psi_{off}$     &
+\hline
+\end{tabular}
+\end{adjustwidth}
+\end{table}
 
@@
 Individuals within this population are either female or male, and can be related to each other if they share a common ancestor.
-Each individual has 10 diploid loci and therefore 20 alleles underlying each trait: tendency to engage in polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$ i.e., 'fertilisation' alleles).
+Each individual has 10 diploid loci and therefore 20 alleles underlying each trait: tendency to engage in polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$ i.e., `fertilisation' alleles).
 Alleles combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for each trait.
@@
 
-Costs
-----------------------------------------------
+\subsection*{Costs}
 
@@
 
-Polyandry
-----------------------------------------------
+\subsection*{Polyandry}
 
@@
 Inheritence of all alleles models a diploid genetic architecture in which 10 $P_{a}$ alleles are randomly sampled from each parent with no physical linkage.
-Values of $P_{a}$ can take any real number [continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014].
+Values of $P_{a}$ can take any real number \cite[continuum-of-alleles model;][]{Kimura1965, Lande1976, Reeve2000, Bocedi2014}.
 The tendency for polyandry genotype $P_{g}$ is therefore defined by the sum of all of a focal female's 20 $P_{a}$ values, which might be negative or positive.
@@
 Hence, negative values of $P_{g}$ are translated to $P_{p}$ values of zero such that $P_{p} = 0$ when $P_{g} < 0$, but when $P_{g} \geq 0$, then $P_{p} = P_{g}$ (i.e., the phenotype value of polyandry equals the genotype value of polyandry if and only if the genotype value is greater than or equal to zero, else the phenotype value of polyandry always equals zero).
-The resulting $P_{p}$ is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998; @Duthie], in which polyandry is expressed discretely at the threshold value of $P_{g} > 0$, but is determined by the consequence of continuous genetic variation arising from the effects of $P_{a}$ alleles that each contribute additively to polyandry.
+The resulting $P_{p}$ is therefore modelled as a threshold trait \cite[][]{Lynch1998, Roff1996, Roff1998, Duthie}, in which polyandry is expressed discretely at the threshold value of $P_{g} > 0$, but is determined by the consequence of continuous genetic variation arising from the effects of $P_{a}$ alleles that each contribute additively to polyandry.
 Negative genotype values of $P_{g}$ therefore all have the same phenotype, resulting in consistently monandrous females.
@@
 
-Mating
-----------------------------------------------
+\subsection*{Mating}
 
 Each male within the population is a potential mate for any female to choose.
-We therefore assume that there are no opportunity costs associated with male mating such that mating with one female would reduce a male's ability to mate with and sire the offspring of any other female [e.g., @Waser1986].
+We therefore assume that there are no opportunity costs associated with male mating such that mating with one female would reduce a male's ability to mate with and sire the offspring of any other female \cite[e.g.,][]{Waser1986}.
 While all males are therefore available as potential mates, we assume that a female mates with her total allotment of $N_{males}$ without replacement, meaning that $N_{males}$ models the total number of distinct males that a female chooses to mate with rather than the number of times that she mates.
 In the unlikely event that a female's $N_{males}$ exceeds the total number of males in the population, then she mates with all of the males in the population.
-Most often, $N_{males}$ will be a small subset of the available males in the population [@Duthie], so the male(s) a focal female chooses will reflect her expression of pre-copulatory inbreeding strategy phenotype ($M_{p}$).
+Most often, $N_{males}$ will be a small subset of the available males in the population \cite[][]{Duthie}, so the male(s) a focal female chooses will reflect her expression of pre-copulatory inbreeding strategy phenotype ($M_{p}$).
 Like polyandry allele values, pre-copulatory inbreeding strategy allele values ($M_{a}$) can take any real number.
@@
 
-Fertilisation
-----------------------------------------------
+\subsection*{Fertilisation}
 
@@
 
-Mutation
-----------------------------------------------
+\subsection*{Mutation}
 
@@
 When a mutation occurs at a locus, a new value is sampled from a random normal distribution with a mean of zero and a standard devation of mutation effect size $\mu_{SD}$, $\mathcal{N}(0, \mu_{SD})$.
-This new value is then added to the original value of the allele that mutates [@Kimura1965; @Lande1976; @Bocedi2014; @Duthie].
-The standard deviation of the mutation effect size ($\mu_{SD}$) is set to $\sqrt{1/20}$, which scales the variance of mutation effect size to the total number of alleles affecting $P_{p}$, $M_{p}$, and $F_{p}$ phenotypes [see @Kimura1965; @Lande1976; @Bocedi2014].
+This new value is then added to the original value of the allele that mutates \cite[][]{Kimura1965, Lande1976, Bocedi2014, Duthie}.
+The standard deviation of the mutation effect size ($\mu_{SD}$) is set to $\sqrt{1/20}$, which scales the variance of mutation effect size to the total number of alleles affecting $P_{p}$, $M_{p}$, and $F_{p}$ phenotypes \cite[see][]{Kimura1965, Lande1976, Bocedi2014}.
 
-Inbreeding depression
-----------------------------------------------
+\subsection*{Inbreeding depression}
 
@@
 The slope $\beta$ models the number of haploid lethal equivalents that exist as deleterious recessive alleles in the gametes of $i$ and $j$, and which might combine to become homozygous in offspring and reduce viability.
-Equation 1 assumes that each deleterious recessive allele affects offspring viability independently, meaning that every deleterious recessive allele added will have a multiplicative affect on decreasing total viability [@Morton1956; @Mills1994], causing the log-linear relationship between parent kinship and inbreeding depression.
+Equation 1 assumes that each deleterious recessive allele affects offspring viability independently, meaning that every deleterious recessive allele added will have a multiplicative affect on decreasing total viability \cite[][]{Morton1956, Mills1994}, causing the log-linear relationship between parent kinship and inbreeding depression.
 We assume that inbreeding depression always decreases offspring viability, $\beta > 0$ (i.e., no outbreeding depression).
@@
 
-Immigration
-----------------------------------------------
+\subsection*{Immigration}
 
@@
 The coefficient of kinship between an immigrant and all other individuals (including native individuals and other immigrants) always equals zero ($k_{ij}=0$).
-Because kinship coefficient values are calculated directly from the pedigree of the focal population [not from individuals' genomes; see @Duthie], the addition of immigrants introduces non-kin into the population at a constant rate and prevents the mean kinship coefficient of the population from asymptoting to a value of 1 over generations.
+Because kinship coefficient values are calculated directly from the pedigree of the focal population \cite[not from individuals' genomes; see][]{Duthie}, the addition of immigrants introduces non-kin into the population at a constant rate and prevents the mean kinship coefficient of the population from asymptoting to a value of 1 over generations.
 If the focal population was instead closed ($\rho=0$), then all alleles would quickly be expected to become identical-by-descent among descendants of the ancestral population.
@@
 
-Density regulation
-----------------------------------------------
+\subsection*{Density regulation}
 
-To avoid having unrestricted population growth over generations, we introduce a separate carrying capacity on the total number of females ($K_{f}$) and males ($K_{m}$) in the focal population following immigration [@Guillaume2009; @Duthie].
+To avoid having unrestricted population growth over generations, we introduce a separate carrying capacity on the total number of females ($K_{f}$) and males ($K_{m}$) in the focal population following immigration \cite[][]{Guillaume2009, Duthie}.
 If at the end of a generation the number of females or males exceeds their respective carrying capacities, then each sex is reduced back to its $K_{f}$ or $K_{m}$ by randomly removing females and males until each sex is at its carrying capacity.
@@
 
-Model analysis
-----------------------------------------------
+\subsection*{Model analysis}
 
@@
 
+%\begin{SCfigure}
+%\begin{adjustwidth}{-4.0in}{0in}
+%    \includegraphics{figures/poly_costs.pdf}
+%  \caption{Foo bar}
+%\end{adjustwidth}
+%\end{SCfigure}
+
+ {\color{Gray}
+\begin{adjustwidth}{-2.5in}{0in}
+\mysidecaption{0.65}
+{%
+   \includegraphics[height=18cm]{figures/poly_costs.pdf}%
+}%
+{%
+   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{10 mm} \textbf{Figure 1:} Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre- and post-copulatory inbreeding avoidance.
+Costs of polyandry increase with rows from top to bottom.
+Dotted horizontal black lines in panels show values of zero on the y-axis.\end{justify}{\t}%
+}[t]
+\end{adjustwidth}
+}
+
+% {\color{Gray}
+%\begin{adjustwidth}{-2.5in}{0in}
+%\mysidecaption{0.35}{%
+%   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{10 mm} \textbf{Figure 1:} Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre- and post-copulatory inbreeding avoidance.
+Costs of polyandry increase with rows from top to bottom.
+Dotted horizontal black lines in panels show values of zero on the y-axis.\end{justify}{\t}%
+%}{%
+%   \includegraphics[height=18cm]{figures/poly_costs.pdf}%
+%}[t]%
+%\end{adjustwidth}
+%}
+
+%\begin{adjustwidth}{-2.0in}{0in}
+
+%\end{adjustwidth}
+
+%\begin{figure}
+%\begin{adjustwidth}{-2.0in}{0in}
+%\floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,top},capbesidewidth=4cm}}]{figure}[7cm]
+%{\caption{Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre- and post-copulatory inbreeding avoidance.
+Costs of polyandry increase with rows from top to bottom.
+Dotted horizontal black lines in panels show values of zero on the y-axis.}\label{poly_costs}}
+%{\includegraphics[width=10cm]{figures/poly_costs.pdf}}
+%\end{adjustwidth}
+%\end{figure}
+
+%\begin{figure}
+%\begin{adjustwidth}{-2.0in}{0in}
+%  \begin{minipage}[c]{0.67\textwidth}
+%    \includegraphics[width=\textwidth]{figures/poly_costs.pdf}
+%  \end{minipage}\hfill
+%  \begin{minipage}[c]{0.3\textwidth}
+%    \caption{Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre- and post-copulatory inbreeding avoidance.
+Costs of polyandry increase with rows from top to bottom.
+Dotted horizontal black lines in panels show values of zero on the y-axis.
+%    } 
+%  \label{poly_costs}
+%  \end{minipage}
+%\end{adjustwidth}
+%\end{figure}
+
+%\marginpar{
+%\vspace{1cm} 
+%\color{Gray} 
+%\textbf{Figure \ref{poly_costs}:} 
+%Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre- and post-copulatory inbreeding avoidance.
+Costs of polyandry increase with rows from top to bottom.
+Dotted horizontal black lines in panels show values of zero on the y-axis.
+%}
+%\begin{wrapfigure}[50]{r}{135mm}
+%\includegraphics[width=135mm]{figures/poly_costs.pdf}
+%\captionsetup{labelformat=empty} 
+%\caption{} 
+%\label{poly_costs} 
+%\end{wrapfigure}
+
 In all simulations, we record mean values of $P_{a}$, $M_{a}$, $F_{a}$ in each generation.
@@
 These analyses allow us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on post-copulatory inbreeding strategy might be weak if polyandry is rare).
-For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling [@Duthie] showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
+For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling \cite[][]{Duthie} showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
 For all replicates, we set $\rho=5$ immigrants, which produced a range of kin and non-kin in each generation allowing females could express inbreeding strategies, and $n=8$ offspring, which was sufficient to keep populations consistently at carrying capacities and avoid population extinction.
-Values of $K_{f}$ and $K_{m}$ were both set to 100 because previous modelling has shown that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but populations are also not so small that selection is typically overwhelmed by genetic drift (Duthie and Reid *in press*).
+Values of $K_{f}$ and $K_{m}$ were both set to 100 because previous modelling has shown that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but populations are also not so small that selection is typically overwhelmed by genetic drift (Duthie and Reid \textit{in press}).
 
-******************************
+\section*{Results}
 
-Results
-===================================================
+\subsection*{Will evolution of post-copulatory inbreeding avoidance strengthen selection for polyandry?}
 
-Will evolution of post-copulatory inbreeding avoidance strengthen selection for polyandry?
-----------------------------------------------
-
+%\marginpar{
+%\vspace{1cm} 
+%\color{Gray} 
+%\textbf{Figure \ref{Pp_vals}:} 
+%Relationship between polyandry allele values and phenotypes for an individual-based model in which pre- and post-copulatory inbreeding strategies evolve jointly with polyandry.
+Two simulations with identical starting conditions (default parameter values with no costs) are shown in panels A,B and C,D.
+Red lines in (A) and (C) show mean value of alleles underlying polyandry for a single replicate simulation over 40000 generations.
+Positive allele values contribute to polyandry, while negative values contribute to monandry (dotted line shows zero on the y-axis).
+In the last generation, mean allele value was below (A) or above (C) zero.
+Nevertheless, due to among-individual variation and the threshold nature of the polyandry phenotype, polyandry persists in the population in (A) and monandry persists in (C).
+The histograms in (B) and (D) show females' tendency for polyandry phenotypes in the last generation; white and grey shading indicates monandrous and polyandrous females, respectively.
+%}
+%\begin{wrapfigure}[25]{l}{75mm}
+%\includegraphics[width=75mm]{figures/Pp_vals.pdf}
+%\captionsetup{labelformat=empty} 
+%\caption{} 
+%\label{Pp_vals} % use \ref{fig1} to reference to this figure
+%\end{wrapfigure} % avoid blank space here
 For low costs of polyandry, $c_{P} < 0.005$, selection caused expected polyandry allele values ($P_{a}$) to be positive only when post-copulatory inbreeding avoidance evolved (Figure 1A-D).
 For all $c_{P}$, $P_{a}$ values were higher when post-copulatory inbreeding avoidance evolved than when it could not evolve (Figure 1).
-When post-copulatory inbreeding avoidance could not evolve, $P_{a}$ values were negative even in the absence of a direct cost ($c_{P}=0$; Figure 1A) because females that expressed polyandry were more likely to increase their inbreeding due to sampling males without replacement [@Duthie].
+When post-copulatory inbreeding avoidance could not evolve, $P_{a}$ values were negative even in the absence of a direct cost ($c_{P}=0$; Figure 1A) because females that expressed polyandry were more likely to increase their inbreeding due to sampling males without replacement \cite[][]{Duthie}.
 Strong post-copulatory inbreeding avoidance consistently evolved in all simulations, even when $P_{a}$ values were expected to be slightly negative (Figure 1F,H), because of the threshold nature of the polyandry phenotype.
@@
 
-Will selection for a costly inbreeding strategy be negligible given a non-costly alternative strategy?
-----------------------------------------------
+\subsection*{Will selection for a costly inbreeding strategy be negligible given a non-costly alternative strategy?}
 
+%\marginpar{
+%\vspace{1cm} 
+%\color{Gray} 
+%\textbf{Figure \ref{rel_costs}:} 
+%Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Panel (A) shows evolution of costly pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy is fixed for random fertilisation (solid black horizontal line), while (B) instead allows post-copulatory inbreeding strategy to evolve under otherwise identical conditions.
+Similarly, panel (C) shows evolution of costly post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for random mating (solid blue horizontal line), while (D) allows pre-copulatory inbreeding strategy to evolve under otherwise identical conditions.
+%}
+%\begin{wrapfigure}[25]{l}{75mm}
+%\includegraphics[width=75mm]{figures/rel_costs.pdf}
+%\captionsetup{labelformat=empty} 
+%\caption{} 
+%\label{rel_costs} % use \ref{fig1} to reference to this figure
+%\end{wrapfigure} % avoid blank space here
 For simulations in which either pre- or post-copulatory inbreeding strategy allele values were fixed for random choice with respect to kinship ($M_{a}=0$ or $F_{a}=0$, respectively), the alternative costly inbreeding strategy evolved to inbreeding avoidance ($F_{a}<0$ or $M_{a}<0$; Figure 3).
@@
 
-Will selection for a costly inbreeding strategy be negligible given existence of an already adaptive alternative strategy?
-----------------------------------------------
+\subsection*{Will selection for a costly inbreeding strategy be negligible given existence of an already adaptive alternative strategy?}
 
+%\marginpar{
+%\vspace{1cm} 
+%\color{Gray} 
+%\textbf{Figure \ref{fixed_adapt}:} 
+%Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Panel (A) shows evolution of pre-copulatory inbreeding strategy given fixed polyandry (solid red line) and inbreeding avoidance (solid black line), and (B) shows these same conditions given a cost of pre-copulatory inbreeding strategy.
+Similarly, panel (C) shows evolution of polyandry and post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for inbreeding avoidance (solid blue line), while (D) shows these same conditions given a cost of post-copulatory inbreeding strategy.
+%}
+%\begin{wrapfigure}[25]{l}{75mm}
+%\includegraphics[width=75mm]{figures/fixed_adapt.pdf}
+%\captionsetup{labelformat=empty} 
+%\caption{} 
+%\label{fixed_adapt} % use \ref{fig1} to reference to this figure
+%\end{wrapfigure} % avoid blank space here
 When pre-copulatory inbreeding strategy was initialised for random mating, but polyandry and post-copulatory inbreeding strategy allele values were fixed for adaptive inbreeding avoidance (Figure 4A,B), negative pre-copulatory inbreeding allele values became increasingly more frequent ($M_{a}<0$), causing inbreeding avoidance in mate choice.
@@
 
-******************************
-
-Discussion
-===================================================
+\section*{Discussion}
 
@@
 Accordingly, we modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency to engage in polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
-Using *in silico* experiments, we tested three specific hypothesis to predict evolution of polyandry, and pre- and post-copulatory inbreeding strategy.
+Using \textit{in silico} experiments, we tested three specific hypothesis to predict evolution of polyandry, and pre- and post-copulatory inbreeding strategy.
 We found that (1) selection for polyandry was greatly strengthened given concurrent evolution of post-copulatory inbreeding avoidance, (2) selection for costly pre- or post-copulatory inbreeding avoidance was negligible given evolution of a less costly strategy of inbreeding avoidance, and (3) pre-existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance, but not vice versa.
 
-The opportunity to adjust inbreeding has been widely considered as a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
-Recently, @Duthie found the conditions under which selection for polyandry and pre-copulatory inbreeding avoidance is predicted to be highly restrictive, requiring strong constraints on the availability of initial compared to additional mates, or the conditional expression of polyandry such that females only engaged in polyandry when their initial choice of mate was of low quality.
-However, @Duthie assumed that fertilisation of offspring was unbiased with respect to mate kinship, meaning that females could not express post-copulatory choice.
+The opportunity to adjust inbreeding has been widely considered as a driver of adaptive evolution of polyandry \cite[][]{Tregenza2002, Foerster2003, Akcay2007, Varian-Ramos2012, Kingma2013, Lehtonen2015, Reid2014}.
+Recently, \cite{Duthie} found the conditions under which selection for polyandry and pre-copulatory inbreeding avoidance is predicted to be highly restrictive, requiring strong constraints on the availability of initial compared to additional mates, or the conditional expression of polyandry such that females only engaged in polyandry when their initial choice of mate was of low quality.
+However, \cite{Duthie} assumed that fertilisation of offspring was unbiased with respect to mate kinship, meaning that females could not express post-copulatory choice.
 In contrast, we found that when post-copulatory inbreeding avoidance could evolve, selection for polyandry was greatly strengthened (Figure 1).
-The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but the existence of selection for post-copulatory inbreeding avoidance causing feedback to select for polyandry has not been formally modelled.
+The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new \cite[e.g.,][]{Zeh1997}, but the existence of selection for post-copulatory inbreeding avoidance causing feedback to select for polyandry has not been formally modelled.
 Our model therefore has widespread implications for empirical studies of evolution of polyandry.
@@
 We predict evolution of polyandry in populations where inbreeding depression is severe and evolution of inbreeding avoidance through post-copulatory mechanisms is not constrained.
-Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa [e.g.
-@Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015].
-For example, @Pizzari2004 found that the number of sperm arriving to eggs is lower for full siblings of female red jungefowl (*Gallus gallus*) than it is for non-relatives, even after controlling for effects of order of oviposition and social familiarity.
-Similarly, Firman and Simmons [-@Firman2008; -@Firman2015] have shown evidence of post-copulatory inbreeding avoidance in house mice, finding fertilisation to be biased toward unrelated males independent of the order in which mating occurs [@Firman2008], perhaps due to post-copulatory mechanisms expressed through the secretion of gametic proteins originating in female's eggs [@Firman2015].
-Interestingly, female house mice have also been shown to express pre-copulatory inbreeding avoidance  [@Potts1991; @Roberts2003].
+Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa \textit[e.g.,][]{Pizzari2004, Firman2008, Bretman2009, Gasparini2011, Tuni2013, Firman2015}.
+For example, \cite{Pizzari2004} found that the number of sperm arriving to eggs is lower for full siblings of female red jungefowl (\textit{Gallus gallus}) than it is for non-relatives, even after controlling for effects of order of oviposition and social familiarity.
+Similarly, Firman and Simmons \citeyearpar{Firman2008, Firman2015} have shown evidence of post-copulatory inbreeding avoidance in house mice, finding fertilisation to be biased toward unrelated males independent of the order in which mating occurs \cite[][]{Firman2008}, perhaps due to post-copulatory mechanisms expressed through the secretion of gametic proteins originating in female's eggs \cite[][]{Firman2015}.
+Interestingly, female house mice have also been shown to express pre-copulatory inbreeding avoidance  \cite[][]{Potts1991, Roberts2003}.
 Our results suggest that post-copulatory inbreeding avoidance is unlikely to evolve when females can already avoid inbreeding through pre-copulatory mechanisms (Figure 4), meaning that evolution of post-copulatory inbreeding avoidance could reasonably be hypothesised to have preceded evolution of pre-copulatory inbreeding avoidance in mice.
 
-Specific mechanisms of post-copulatory inbreeding avoidance are difficult to identify, but recent experimental studies have shown how females can successfully bias fertilisation after mating has occurred in both vertebrates [e.g., @Gasparini2011] and invertebrates [e.g., @Tuni2013].
-For example, @Gasparini2011 artificially inseminated female guppies (*Poecilia reticulata*) with equal quantities of sperm from full-siblings and unrelated males, finding that fertilisation success was higher in non-relatives because the velocity of full siblings' sperm was reduced by females' ovarian fluids.
+Specific mechanisms of post-copulatory inbreeding avoidance are difficult to identify, but recent experimental studies have shown how females can successfully bias fertilisation after mating has occurred in both vertebrates \cite[e.g.,][]{Gasparini2011} and invertebrates \cite[e.g.,][]{Tuni2013}.
+For example, \cite{Gasparini2011} artificially inseminated female guppies (\textit{Poecilia reticulata}) with equal quantities of sperm from full-siblings and unrelated males, finding that fertilisation success was higher in non-relatives because the velocity of full siblings' sperm was reduced by females' ovarian fluids.
 Biased fertilisation toward non-relatives might also be accomplished through selective storage of sperm.
-For example, in black field crickets (*Teleogryllus commodus*), females attempt to remove the spermataphores of unwanted male mates after copulation, while male mates guard females to prevent spermatophore removal [@Bussiere2006].
-Even if females are unable to remove spermatophores of unwanted mates, @Tuni2013 found that female *T.
-commodus* are capable of controlling the transfer of sperm to their spermatheca, most likely through physical control of the spermathecal duct, and can reduce sperm storage despite being guarded by a related male.
+For example, in black field crickets (\textit{Teleogryllus commodus}), females attempt to remove the spermataphores of unwanted male mates after copulation, while male mates guard females to prevent spermatophore removal \cite[][]{Bussiere2006}.
+Even if females are unable to remove spermatophores of unwanted mates, \cite{Tuni2013} found that female \textit{T.
+commodus} are capable of controlling the transfer of sperm to their spermatheca, most likely through physical control of the spermathecal duct, and can reduce sperm storage despite being guarded by a related male.
 Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for further polyandry, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
@@
 Direct costs therefore strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies.
-Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging [@Pomiankowski1987; @Kokko2003; @Reid2015].
-@Pomiankowski1987 categorised four types of costs that are relevant to mate choice, which we suggest are also relevant costs for polyandry, and include costs of elevated risks associated with (1) predation or (2) disease transmission, and costs incurred through (3) loss of time or (4) depletion of energy.
-In our model, we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of pre-copulatory inbreeding strategy as a lost of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of post-copulatory inbreeding strategy as depletion of energy.
+Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging \cite[][]{Pomiankowski1987, Kokko2003, Reid2015}.
+\cite{Pomiankowski1987} categorised four types of costs that are relevant to mate choice, which we suggest are also relevant costs for polyandry, and include costs of elevated risks associated with (1) predation or (2) disease transmission, and costs incurred through (3) loss of time or (4) depletion of energy.
+In our model, we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates \cite[e.g.,][]{Rowe1988, Rowe1994}, a cost of pre-copulatory inbreeding strategy as a lost of time \cite[i.e., risk of not finding a mate in time due to choosiness; e.g.,][]{Kokko2013}, and a cost of post-copulatory inbreeding strategy as depletion of energy.
 While these costs are biologically realistic, different costs will be relevant for different populations and be realised in different ways.
-For example, increased risk of disease transmission has been observed for highly polyandrous females [@Roberts2015a], but such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry.
+For example, increased risk of disease transmission has been observed for highly polyandrous females \cite[][]{Roberts2015a}, but such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry.
 Future models will therefore need to carefully consider the magnitudes and realisation of direct costs to accurately predict evolution of inbreeding strategies in populations.
-<!--- add Tuni citation for depletion of energy?
---->
 
-Another type of cost relevant for polyandry and inbreeding strategy is risk of male harm caused by sexual conflict [e.g., @Arnqvist2005a; @Parker2006].
-We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should benefit from a higher tolerance of inbreeding than females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
+Another type of cost relevant for polyandry and inbreeding strategy is risk of male harm caused by sexual conflict \cite[e.g.,][]{Arnqvist2005a, Parker2006}.
+We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should benefit from a higher tolerance of inbreeding than females, leading to sexual conflict over inbreeding \cite[][]{Parker1979, Parker2006, Kokko2006, Duthie2015a}.
 Females that express the choice to avoid inbreeding when mating might therefore pay a cost of harm caused by coercion expressed by related males.
-This cost might itself evolve over time as male harm coevolves with female resistance [@Ronn2007; @Perry2011; @Wang2015a], and costs might vary with interactions among male non-relatives and relatives because effects of kin selection are predicted to reduce harm caused by related male suitors [@Rankin2011a].
+This cost might itself evolve over time as male harm coevolves with female resistance \cite[][]{Ronn2007, Perry2011, Wang2015a}, and costs might vary with interactions among male non-relatives and relatives because effects of kin selection are predicted to reduce harm caused by related male suitors \cite[][]{Rankin2011a}.
 To predict evolution of polyandry and inbreeding strategy in populations characterised by active males and sexual conflict, consideration of male inbreeding strategy and coevolution between male harm and female resistance might therefore need to be considered explicitly.
@@
 
-Acknowledgements
-----------------------------------------------
+\subsection*{Acknowledgments}
 
@@
 
-**************************
+\begin{small}
+\bibliography{ms_pre_post}
+\bibliographystyle{amnatnat}
+\end{small}
 
-\vspace{140 mm}
-
-Table 1
-----------------------------------------------
-
-Individual traits (A), model parameter values (B), and model variables (C) for an individual based model of the evolution of polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
-
-|-------|-------------------------------------|-------------|---------------|--------------
-| **A** | **Trait**                           | **Allele**  | **Genotype**  | **Phenotype**
-|       | Tendency for polyandry              | $P_{a}$     | $P_{g}$       | $P_{p}$
-|       | Pre-copulatory inbreeding strategy  | $M_{a}$     | $M_{g}$       | $M_{p}$
-|       | Post-copulatory inbreeding strategy | $F_{a}$     | $F_{g}$       | $F_{p}$
-|       |                                     |             |               |
-| **B** | **Description**                     | **Parameter**  | | **Defaut value(s)**
-|       | Cost of tendency for polyandry                 | $c_{P}$        | | $0$, $0.02$
-|       | Cost of pre-copulatory inbreeding strategy     | $c_{M}$        | | $0$, $0.02$
-|       | Cost of post-copulatory inbreeding strategy    | $c_{F}$        | | $0$, $0.02$
-|       | Focal female's number of offspring             | $n$            | | $8$
-|       | Log-linear slope of inbreeding depression      | $\beta$        | | $3$
-|       | Adult male immigrants per generation           | $\rho$         | | $5$
-|       | Female carrying capacity                       | $K_{f}$        | | $100$
-|       | Male carrying capacity                         | $K_{m}$        | | $100$
-|       | Mutation rate of alleles                       | $\mu$          | | $0.001$
-|       | Standard deviation of mutation effect size     | $\mu_{SD}$     | | $\sqrt{1/20}$
-|       |                                                |                | |
-| **C** | **Description**                                                   | | **Variable** |
-|       | Coefficient of kinship                                            | | $k$          |
-|       | Focal female's number of mates                                    | | $N_{males}$  |
-|       | Female $i$'s perceived absolute mate quality of male $j$          | | $Q^{m}_{ij}$ |
-|       | Female $i$'s perceived relative mate quality of male $j$          | | $q^{m}_{ij}$ |
-|       | Female $i$'s perceived absolute fertilisation quality of male $j$ | | $Q^{f}_{ij}$ |
-|       | Female $i$'s perceived relative fertilisation quality of male $j$ | | $q^{f}_{ij}$ |
-|       | Viability of a focal female's offspring                           | | $\Psi_{off}$ |
-
-![Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre- and post-copulatory inbreeding avoidance.
-Costs of polyandry increase with rows from top to bottom.
-Dotted horizontal black lines in panels show values of zero on the y-axis.](figures/poly_costs.png)
-
-![Relationship between polyandry allele values and phenotypes for an individual-based model in which pre- and post-copulatory inbreeding strategies evolve jointly with polyandry.
-Two simulations with identical starting conditions (default parameter values with no costs) are shown in panels A,B and C,D.
-Red lines in (A) and (C) show mean value of alleles underlying polyandry for a single replicate simulation over 40000 generations.
-Positive allele values contribute to polyandry, while negative values contribute to monandry (dotted line shows zero on the y-axis).
-In the last generation, mean allele value was below (A) or above (C) zero.
-Nevertheless, due to among-individual variation and the threshold nature of the polyandry phenotype, polyandry persists in the population in (A) and monandry persists in (C).
-The histograms in (B) and (D) show females' tendency for polyandry phenotypes in the last generation; white and grey shading indicates monandrous and polyandrous females, respectively.](figures/Pp_vals.png)
-
-![Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panel (A) shows evolution of costly pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy is fixed for random fertilisation (solid black horizontal line), while (B) instead allows post-copulatory inbreeding strategy to evolve under otherwise identical conditions.
-Similarly, panel (C) shows evolution of costly post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for random mating (solid blue horizontal line), while (D) allows pre-copulatory inbreeding strategy to evolve under otherwise identical conditions.](figures/rel_costs.png)
-
-![Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panel (A) shows evolution of pre-copulatory inbreeding strategy given fixed polyandry (solid red line) and inbreeding avoidance (solid black line), and (B) shows these same conditions given a cost of pre-copulatory inbreeding strategy.
-Similarly, panel (C) shows evolution of polyandry and post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for inbreeding avoidance (solid blue line), while (D) shows these same conditions given a cost of post-copulatory inbreeding strategy.](figures/fixed_adapt.png)
-
-\vspace{180 mm}
-
-References
-----------------------------------------------
+\end{document}

### 2016-10-26 pre_post_biorxiv.tex
Stable biorXiv version with tables and figures paginated

@@
 \begin{table}[!ht]
+\captionsetup{margin={-1.75in,0in}}
 \begin{adjustwidth}{-1.75in}{0in}
-\centering
+%\centering
 \caption{\color{Gray}Individual traits (A), model parameter values (B), and model variables (C) for an individual based model of the evolution of polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.}
@@
 
-%\begin{SCfigure}
-%\begin{adjustwidth}{-4.0in}{0in}
-%    \includegraphics{figures/poly_costs.pdf}
-%  \caption{Foo bar}
-%\end{adjustwidth}
-%\end{SCfigure}
-
  {\color{Gray}
 \begin{adjustwidth}{-2.5in}{0in}
-\mysidecaption{0.65}
+\mysidecaption{0.68}
 {%
@@
 
-% {\color{Gray}
-%\begin{adjustwidth}{-2.5in}{0in}
-%\mysidecaption{0.35}{%
-%   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{10 mm} \textbf{Figure 1:} Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre- and post-copulatory inbreeding avoidance.
-Costs of polyandry increase with rows from top to bottom.
-Dotted horizontal black lines in panels show values of zero on the y-axis.\end{justify}{\t}%
-%}{%
-%   \includegraphics[height=18cm]{figures/poly_costs.pdf}%
-%}[t]%
-%\end{adjustwidth}
-%}
-
-%\begin{adjustwidth}{-2.0in}{0in}
-
-%\end{adjustwidth}
-
-%\begin{figure}
-%\begin{adjustwidth}{-2.0in}{0in}
-%\floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,top},capbesidewidth=4cm}}]{figure}[7cm]
-%{\caption{Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre- and post-copulatory inbreeding avoidance.
-Costs of polyandry increase with rows from top to bottom.
-Dotted horizontal black lines in panels show values of zero on the y-axis.}\label{poly_costs}}
-%{\includegraphics[width=10cm]{figures/poly_costs.pdf}}
-%\end{adjustwidth}
-%\end{figure}
-
-%\begin{figure}
-%\begin{adjustwidth}{-2.0in}{0in}
-%  \begin{minipage}[c]{0.67\textwidth}
-%    \includegraphics[width=\textwidth]{figures/poly_costs.pdf}
-%  \end{minipage}\hfill
-%  \begin{minipage}[c]{0.3\textwidth}
-%    \caption{Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre- and post-copulatory inbreeding avoidance.
-Costs of polyandry increase with rows from top to bottom.
-Dotted horizontal black lines in panels show values of zero on the y-axis.
-%    } 
-%  \label{poly_costs}
-%  \end{minipage}
-%\end{adjustwidth}
-%\end{figure}
-
-%\marginpar{
-%\vspace{1cm} 
-%\color{Gray} 
-%\textbf{Figure \ref{poly_costs}:} 
-%Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre- and post-copulatory inbreeding avoidance.
-Costs of polyandry increase with rows from top to bottom.
-Dotted horizontal black lines in panels show values of zero on the y-axis.
-%}
-%\begin{wrapfigure}[50]{r}{135mm}
-%\includegraphics[width=135mm]{figures/poly_costs.pdf}
-%\captionsetup{labelformat=empty} 
-%\caption{} 
-%\label{poly_costs} 
-%\end{wrapfigure}
-
 In all simulations, we record mean values of $P_{a}$, $M_{a}$, $F_{a}$ in each generation.
@@
 
-%\marginpar{
-%\vspace{1cm} 
-%\color{Gray} 
-%\textbf{Figure \ref{Pp_vals}:} 
-%Relationship between polyandry allele values and phenotypes for an individual-based model in which pre- and post-copulatory inbreeding strategies evolve jointly with polyandry.
-Two simulations with identical starting conditions (default parameter values with no costs) are shown in panels A,B and C,D.
-Red lines in (A) and (C) show mean value of alleles underlying polyandry for a single replicate simulation over 40000 generations.
-Positive allele values contribute to polyandry, while negative values contribute to monandry (dotted line shows zero on the y-axis).
-In the last generation, mean allele value was below (A) or above (C) zero.
-Nevertheless, due to among-individual variation and the threshold nature of the polyandry phenotype, polyandry persists in the population in (A) and monandry persists in (C).
-The histograms in (B) and (D) show females' tendency for polyandry phenotypes in the last generation; white and grey shading indicates monandrous and polyandrous females, respectively.
-%}
-%\begin{wrapfigure}[25]{l}{75mm}
-%\includegraphics[width=75mm]{figures/Pp_vals.pdf}
-%\captionsetup{labelformat=empty} 
-%\caption{} 
-%\label{Pp_vals} % use \ref{fig1} to reference to this figure
-%\end{wrapfigure} % avoid blank space here
 For low costs of polyandry, $c_{P} < 0.005$, selection caused expected polyandry allele values ($P_{a}$) to be positive only when post-copulatory inbreeding avoidance evolved (Figure 1A-D).
@@
 
-%\marginpar{
-%\vspace{1cm} 
-%\color{Gray} 
-%\textbf{Figure \ref{rel_costs}:} 
-%Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panel (A) shows evolution of costly pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy is fixed for random fertilisation (solid black horizontal line), while (B) instead allows post-copulatory inbreeding strategy to evolve under otherwise identical conditions.
-Similarly, panel (C) shows evolution of costly post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for random mating (solid blue horizontal line), while (D) allows pre-copulatory inbreeding strategy to evolve under otherwise identical conditions.
-%}
-%\begin{wrapfigure}[25]{l}{75mm}
-%\includegraphics[width=75mm]{figures/rel_costs.pdf}
-%\captionsetup{labelformat=empty} 
-%\caption{} 
-%\label{rel_costs} % use \ref{fig1} to reference to this figure
-%\end{wrapfigure} % avoid blank space here
 For simulations in which either pre- or post-copulatory inbreeding strategy allele values were fixed for random choice with respect to kinship ($M_{a}=0$ or $F_{a}=0$, respectively), the alternative costly inbreeding strategy evolved to inbreeding avoidance ($F_{a}<0$ or $M_{a}<0$; Figure 3).
@@
 
+{\color{Gray}
+\begin{adjustwidth}{-2.5in}{0in}
+\mysidecaption{0.68}
+{%
+   \includegraphics[height=10.25cm]{figures/Pp_vals.pdf}%
+}%
+{%
+   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 2:} Relationship between polyandry allele values and phenotypes for an individual-based model in which pre- and post-copulatory inbreeding strategies evolve jointly with polyandry.
+Two simulations with identical starting conditions (default parameter values with no costs) are shown in panels A,B and C,D.
+Red lines in (A) and (C) show mean value of alleles underlying polyandry for a single replicate simulation over 40000 generations.
+Positive allele values contribute to polyandry, while negative values contribute to monandry (dotted line shows zero on the y-axis).
+In the last generation, mean allele value was below (A) or above (C) zero.
+Nevertheless, due to among-individual variation and the threshold nature of the polyandry phenotype, polyandry persists in the population in (A) and monandry persists in (C).
+The histograms in (B) and (D) show females' tendency for polyandry phenotypes in the last generation; white and grey shading indicates monandrous and polyandrous females, respectively.\end{justify}{\t}%
+}[t]
+\end{adjustwidth}
+}
+
 \subsection*{Will selection for a costly inbreeding strategy be negligible given existence of an already adaptive alternative strategy?}
 
-%\marginpar{
-%\vspace{1cm} 
-%\color{Gray} 
-%\textbf{Figure \ref{fixed_adapt}:} 
-%Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panel (A) shows evolution of pre-copulatory inbreeding strategy given fixed polyandry (solid red line) and inbreeding avoidance (solid black line), and (B) shows these same conditions given a cost of pre-copulatory inbreeding strategy.
-Similarly, panel (C) shows evolution of polyandry and post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for inbreeding avoidance (solid blue line), while (D) shows these same conditions given a cost of post-copulatory inbreeding strategy.
-%}
-%\begin{wrapfigure}[25]{l}{75mm}
-%\includegraphics[width=75mm]{figures/fixed_adapt.pdf}
-%\captionsetup{labelformat=empty} 
-%\caption{} 
-%\label{fixed_adapt} % use \ref{fig1} to reference to this figure
-%\end{wrapfigure} % avoid blank space here
 When pre-copulatory inbreeding strategy was initialised for random mating, but polyandry and post-copulatory inbreeding strategy allele values were fixed for adaptive inbreeding avoidance (Figure 4A,B), negative pre-copulatory inbreeding allele values became increasingly more frequent ($M_{a}<0$), causing inbreeding avoidance in mate choice.
@@
 
+{\color{Gray}
+\begin{adjustwidth}{-2.5in}{0in}
+\mysidecaption{0.31}
+{%
+   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 3:} Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Panel (A) shows evolution of costly pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy is fixed for random fertilisation (solid black horizontal line), while (B) instead allows post-copulatory inbreeding strategy to evolve under otherwise identical conditions.
+Similarly, panel (C) shows evolution of costly post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for random mating (solid blue horizontal line), while (D) allows pre-copulatory inbreeding strategy to evolve under otherwise identical conditions.\end{justify}{\t}%
+}
+{%
+   \includegraphics[height=14.5cm]{figures/rel_costs.pdf}%
+}%
+[t]
+\end{adjustwidth}
+}
+
 \section*{Discussion}
@@
 We found that (1) selection for polyandry was greatly strengthened given concurrent evolution of post-copulatory inbreeding avoidance, (2) selection for costly pre- or post-copulatory inbreeding avoidance was negligible given evolution of a less costly strategy of inbreeding avoidance, and (3) pre-existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance, but not vice versa.
+
+{\color{Gray}
+\begin{adjustwidth}{-2.5in}{0in}
+\mysidecaption{0.68}
+{%
+   \includegraphics[height=14cm]{figures/rel_costs.pdf}%
+}%
+{%
+   \captionof{figures/fixed_adapt.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Panel (A) shows evolution of pre-copulatory inbreeding strategy given fixed polyandry (solid red line) and inbreeding avoidance (solid black line), and (B) shows these same conditions given a cost of pre-copulatory inbreeding strategy.
+Similarly, panel (C) shows evolution of polyandry and post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for inbreeding avoidance (solid blue line), while (D) shows these same conditions given a cost of post-copulatory inbreeding strategy.\end{justify}{\t}%
+}[t]
+\end{adjustwidth}
+}
 
@@
 We predict evolution of polyandry in populations where inbreeding depression is severe and evolution of inbreeding avoidance through post-copulatory mechanisms is not constrained.
-Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa \textit[e.g.,][]{Pizzari2004, Firman2008, Bretman2009, Gasparini2011, Tuni2013, Firman2015}.
+Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa \cite[e.g.,][]{Pizzari2004, Firman2008, Bretman2009, Gasparini2011, Tuni2013, Firman2015}.
 For example, \cite{Pizzari2004} found that the number of sperm arriving to eggs is lower for full siblings of female red jungefowl (\textit{Gallus gallus}) than it is for non-relatives, even after controlling for effects of order of oviposition and social familiarity.

### 2016-10-26 pre_post_biorxiv.tex
Fix italics

@@
 A. Bradley Duthie\textsuperscript{1,*},
-Jane M. Reid\textsuperscript{1},
+Jane M. Reid\textsuperscript{1}
 \\
@@
 
-Here we use individual-based modelling and *in silico* experiments to test the hypothesis that, given severe inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance causes selection for polyandry.
+Here we use individual-based modelling and \textit{in silico} experiments to test the hypothesis that, given severe inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance causes selection for polyandry.
 Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that selection for only the less costly inbreeding avoidance strategy will be sustained over generations.

### 2016-10-26 pre_post_biorxiv.tex
Minor tweaks to style

@@
 \begin{table}[!ht]
-\captionsetup{margin={-1.75in,0in}}
+\captionsetup{margin={-1.75in,0.1in}}
 \begin{adjustwidth}{-1.75in}{0in}
@@
   & Female $i$'s perceived relative fertilisation quality of male $j$ & & & $q^{f}_{ij}$     &
-  & Viability of a focal female's offspring                           & & & $\Psi_{off}$     &
+  & Viability of a focal female's offspring                           & & & $\Psi_{\textrm{off}}$     &
 \hline

### 2016-10-27 pre_post_biorxiv.tex
Tweak margin inward

@@
 %\centering
-\caption{\color{Gray}Individual traits (A), model parameter values (B), and model variables (C) for an individual based model of the evolution of polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.}
+\caption{\color{Gray}Individual traits (A), model parameter values (B), and model variables (C) for an individual-based model of the evolution of polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.}
 \begin{tabular}{lllll}
@@
  {\color{Gray}
-\begin{adjustwidth}{-2.5in}{0in}
+\begin{adjustwidth}{-2.2in}{0in}
 \mysidecaption{0.68}
@@
 {\color{Gray}
-\begin{adjustwidth}{-2.5in}{0in}
+\begin{adjustwidth}{-2.2in}{0in}
 \mysidecaption{0.68}
@@
 {\color{Gray}
-\begin{adjustwidth}{-2.5in}{0in}
+\begin{adjustwidth}{-2.2in}{0in}
 \mysidecaption{0.31}

### 2016-10-27 ms_pre_post.Rmd
Add new call to DOCX template, nicer?

@@
     - evolution.csl
+    reference_docx: docx_template.docx
+  pdf_document:
+    fig_caption: yes
+  html_document: default
 header-includes:

### 2016-10-31 ms_pre_post.Rmd
Remove unnecessary comment
Last commit before getting to coauthor comments
Edit first paragraph of Introduction

@@
 ---
-title: "Evolution of pre-copulatory and post-copulatory inbreeding behaviour"
+title: "Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry"
 author: "A. Bradley Duthie et al."
@@
 
-Inbreeding typically reduces the fitness of inbred offspring (termed 'inbreeding depression'), potentially driving evolution of inbreeding avoidance when inbreeding depression is strong [@Parker1979; @Parker2006; @Pusey1996; @Charlesworth1999; @Keller2002; @Charlesworth2009; @Szulkin2012].
-For focal females, inbreeding avoidance might be acheived by avoiding related potential mates (pre-copulatory inbreeding avoidance), or by biasing fertilisation after mating has occurred so that related mates are less likely to sire offspring (post-copulatory inbreeding avoidance).
-Importantly, evolution of post-copulatory inbreeding avoidance requires that females be polyandrous, mating with multiple males during a single reproductive bout to ensure that post-copulatory choice can be expressed.
-As a reproductive strategy, polyandry thereby simultaneously allows females to choose multiple mates and creates the opportunity for further cryptic choice enacted through post-copulatory mechanisms.
-Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and therefore produce higher fitness offspring [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007].
-However, how pre- and post-copulatory strategies of inbreeding avoidance evolve jointly, and how such evolution is predicted to feed back to affect evolution of polyandry, still remains largely unknown.
-While pre-copulatory inbreeding avoidance can facilitate evolution of polyandry under some restrictive conditions [@Duthie], the opportunity for post-copulatory choice might facilitate evolution of polyandry under a much wider range of conditions by allowing females to bias fertilisation toward non-kin.
+Inbreeding often greatly reduces the fitness of inbred offspring [termed 'inbreeding depression'; @Charlesworth1999; @Keller2002; @Charlesworth2009].
+Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple forms of mate choice in species with obligate biparental reproduction [@Parker1979; @Parker2006; @Pusey1996; @Szulkin2012].
+From the perspective of a focal breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred, meaning that related males are less likely to sire offspring (i.e., post-copulatory inbreeding avoidance).
+Importantly, evolution of post-copulatory inbreeding avoidance requires that females are polyandrous, defined as mating with multiple males during a single reproductive bout.
+Further, such polyandry could itself evolve because it allows females to mate with additional unrelated males following initial mating with a relative, thereby facilitating pre-copulatory inbreeding avoidance even in the absence of any post-copulatory female choice or otherwise biased fertilisation (e.g., given a 'fair raffle' among sperm provided by feamles' mates).
+As a reproductive strategy, polyandry can thereby simultaneously allow females to mate with less closely related males and creates the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
+Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007].
+However, despite such well-established hypotheses, no modelling investigates conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are likely to evolve, or predicts how such evolution will feed back to affect underlying evolution of polyandry.
+
+<!--- ------------------------------------------------------------------------- --->
+<!--- ------------- LEFT OFF HERE --------------------------------------------- --->
+<!--- ------------------------------------------------------------------------- --->
 
@@
 Future models will therefore need to carefully consider the magnitudes and realisation of direct costs to accurately predict evolution of inbreeding strategies in populations.
-<!--- add Tuni citation for depletion of energy?
---->
 

### 2016-10-31 ms_pre_post.Rmd
Edit second paragraph of Introduction

@@
 
+Meanwhile, empirical studies of diverse species have found evidence for female inbreeding avoidance enacted through pre-copulatory or post-copulatory routes, or both.
+For example, pre-copulatory inbreeding avoidance has been documented in weevils, birds, and butterflies [e.g., @Kuriwada2011; @Kingma2013; @Fischer2015], and post-copulatory inbreeding avoidance has been documented in crickets [e.g., @Simmons2006; @Bretman2009].
+Evidence of both pre-copulatory and post-copulatory inbreeding avoidance has accumulated for some well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015].
+While most studies consider either pre- or post-copulatory inbreeding avoidance in isolation, a small number of studies consider both.
+Accordingly, @Liu2014 found evidence of pre-copulatory, but not post-copulatory, inbreeding avoidance in cabbage beetles (*Colaphellus bowringi*).
+Other studies found no evidence of pre- or post-copulatory inbreeding avoidane despite strong inbreeding depression [e.g., @Reid2014; @Reid2015].
+These empirical studies demonstrate that diverse combinations of pre- and post-copulatory inbreeding avoidance occur in nature.
+However, there is as yet no conceptual framework that predicts *a priori* what combinations should be favoured by selection when both pre- and post-copulatory inbreeding avoidance, and polyandry can evolve.
+Such a framework would allow prediction of the form of mating system evolution across different systems that experience inbreeding depression and allow existing empirical studies to be used to test evolutionary predictions through comparative analyses.
+
+<!--- The terminal sentence is non-sensical.
+It confuses what theory actually is and suggests a post-hoc testing of a model through already existing data -- what does *prediction* even mean in this context !?
+This is bad science.
+--->
+
 <!--- ------------------------------------------------------------------------- --->
@@
 <!--- ------------------------------------------------------------------------- --->
-
-Severe inbreeding depression might cause selection for alleles underlying active pre- and post-copulatory inbreeding avoidance and associated polyandry, but if evolution of one strategy renders its complement redundant for avoiding inbreeding, then selection might instead be sustained over generations for only one strategy.
-Empirical studies of multiple species have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013; @Fischer2015], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009].
-Further, evidence of both pre-copulatory and post-copulatory inbreeding avoidance has been found for a handful of well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015], while @Liu2014 found evidence for pre-copulatory, but not post-copulatory, inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*).
-Other studies do not find any evidence for inbreeding avoidance despite strong inbreeding depression, suggesting that evolution of pre- or post-copulatory inbreeding avoidance cannot be presumed [e.g., @Frere2010; @Reid2014; @Reid2015].
-These empirical studies demonstrate that all combinations of adaptive pre-copulatory and post-copulatory inbreeding avoidance are possible, but no conceptual framework exists to predict *a priori* what combinations should be favoured by selection when both pre- and post-copulatory inbreeding avoidance, and polyandry, can evolve.
 

### 2016-10-31 ms_pre_post.Rmd
Edit third and fourth paragraph of Introduction

@@
 
+A recent genetically-explicit individual-based model showed that selection for alleles underlying polyandry and pre-copulatory inbreeding avoidance, and resulting joint evolution of these reproductive strategies, occurred only under highly constrained conditions [@Duthie].
+Specifically, such evolution occurred when direct costs of polyandry were small, when very fewe males were available for a female's initial mate choice but many were available for additional mate choice(s), or when polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
+In the absence of these conditions, increasing degrees of polyandry tended to increase the overall degree of inbreeding that females experienced, and hence increase inbreeding depression in offspring fitness.
+This occurred because polyandrous females that had evolved to avoid inbreeding had already chosen available unrelated males as their initial mates.
+Their additional mates, chosen from the remaining male population, were therefore increasingly likely to include relatives.
+Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance was consequently restricted.
+
+However, while @Duthie considered simultaneous evolution of polyandry and pre-copulatory inbreeding avoidance, they did not also allow simultaneous evolution of post-copulatory inbreeding avoidance, and assumed that polyandrous females had no post-copulatory control over fertilisation.
+If post-copulatory inbreeding avoidance could also evolve, polyandrous females could further bias paternity towards unrelated males within their set of chosen mates.
+This process might reduce the cost of polyandry stemming from accumulation of related mates, potentially facilitating evolution of polyandry to avoid inbreeding [@Zeh1997], and driving further consequent evolution of pre-copulatory or post-copulatory mate choice strategies.
+Therefore, while pre-copulatory inbreeding avoidance can facilitate evolution of polyandry under some restrictive conditions [@Duthie], the opportunity for post-copulatory choice might facilitate evolution of polyandry under a much wider range of conditions by allowing females to bias fertilisation toward non-kin.
+The long-term evolutionary dynamics of pre- and post-copulatory inbreeding avoidance then become unclear.
+Strong inbreeding depression might drive initial evolution of both pre- and post-copulatory inbreeding avoidance and associated polyandry.
+However, if evolution of polyandry and post-copulatory inbreeding avoidance renders pre-copulatory inbreeding avoidance redundant, or vice versa, then only one strategy might be maintained in the long-term.
+
 <!--- ------------------------------------------------------------------------- --->
@@
 For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect that such invading alleles have on decreasing total inbreeding avoidance could be weak or negligible.
-
-In a recent model, @Duthie showed that selection for alleles underlying polyandry and pre-copulatory inbreeding avoidance occurred only under highly constrained conditions in which direct costs of polyandry were low, and when very few males were available during a female's initial mate choice but many males were available during a female's additional mate choice(s), or when polyandry was conditionally expressed based on the degree to which a focal female engaged in inbreeding given her initially chosen mate.
-In the absence of these constraints, expression of polyandry was expected to increase inbreeding with each additional mate because remaining males were more likely to be relatives once available non-relatives were chosen.
-However, @Duthie assumed that polyandrous females had no control over the assignment of paternity to their offspring.
-If after engaging in polyandry, females could bias paternity through post-copulatory mechanisms, then selection for polyandry to avoid inbreeding might be more widely predicted when inbreeding depression is severe [@Zeh1997], potentially feeding back to drive further evolution of pre- and post-copulatory strategies.
 

### 2016-10-31 ms_pre_post.Rmd
Edit Introduction in line with co-author comments

@@
 
-<!--- ------------------------------------------------------------------------- --->
-<!--- ------------- LEFT OFF HERE --------------------------------------------- --->
-<!--- ------------------------------------------------------------------------- --->
+Previous models implicitly or explicitly considered the fate of a rare allele underlying pre-copulatory inbreeding avoidance in a population initially fixed for random mating [e.g., Duthie and Reid *In press*; @Parker1979; @Parker2006; @Duthie].
+Such models thereby isolate the invasion fitness of this single strategy.
+However, when both pre- and post-copulatory strategies can affect realised inbreeding, it cannot be assumed that both strategies will invade simultaneously, nor that invasion fitness of one strategy will be independent of the other For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect of such invading alleles could be weak or negligible.
 
-Frequencies of alleles underlying active pre- and post-copulatory inbreeding avoidance and polyandry are likely to be affected by direct negative selection on phenotypes (i.e., costs).
-For example, polyandrous females often pay a cost associated with searching or making themselves available to mates, thereby increasing their own risk of predation [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
+Ultimately, the absolute and relative frequencies of alleles underlying pre- and post-copulatory inbreeding avoidance and polyandry are likely to be affected by direct negative selection on resulting phenotypes (i.e., costs) and hence on the net costs versus benefits stemming from inbreeding avoidance.
+Polyandrous females can pay costs of mate searching or mating, for example, because these activities increase predation risk [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
 Females that express pre-copulatory choice (e.g., reluctance to mate with relatives) might pay a cost of increased risk of mating failure, or harm caused by sexual conflict [@Rowe1994; @Kokko2013].
@@
 
-In addition to the relative importance of costs, evolution of pre- or post-copulatory inbreeding avoidance might be precluded if inbreeding avoidance is already acheived through a complementary strategy, thereby reducing net benefits.
-Previous models considered the fate of a rare allele underlying inbreeding avoidance in a population initially fixed for random mating [e.g., Duthie and Reid *In press*; @Parker1979; @Parker2006; @Duthie].
-Such models thereby isolate the invasion fitness of a single focal strategy.
-However, when multiple distinct strategies affect realised inbreeding, it cannot be assumed that both will invade simultaneously, nor that invasion fitness of one inbreeding strategy will be independent of another.
-For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect that such invading alleles have on decreasing total inbreeding avoidance could be weak or negligible.
-
-Here we use individual-based modelling and *in silico* experiments to test the hypothesis that, given severe inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance causes selection for polyandry.
-Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that selection for only the less costly inbreeding avoidance strategy will be sustained over generations.
-Finally, we test the hypothesis that evolution of one inbreeding strategy will be precluded if it is introduced into a population that is already fixed for a complementary inbreeding strategy that is adaptive.
-We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across reproductive systems with different relative costs and strong inbreeding depression in offspring viability.
+Here we use individual-based modelling to set up *in silico* experiments, which test the hypothesis that, given strong inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance facilitates evolution of polyandry.
+Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution such that only the less costly inbreeding avoidance strategy will be expressed in the long term.
+Finally, we test the hypothesis that evolution of one inbreeding avoidance strategy (i.e., pre- or post-copulatory) will be precluded if it is introduced into a population that is already fixed for the other inbreeding avoidance strategy that is adaptive.
+We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across different reproductive systems.
 
@@
 ===================================================
+
+<!--- ------------------------------------------------------------------------- --->
+<!--- ------------- LEFT OFF HERE --------------------------------------------- --->
+<!--- ------------------------------------------------------------------------- --->
 

### 2016-10-31 ms_pre_post.Rmd
Edit model up through costs

@@
 
-<!--- ------------------------------------------------------------------------- --->
-<!--- ------------- LEFT OFF HERE --------------------------------------------- --->
-<!--- ------------------------------------------------------------------------- --->
-
-We model evolution of polyandry and inbreeding avoidance through pre- and post-copulatory mechanisms by tracking interactions among discrete individuals in a small focal population that persists over multiple generations (key individual traits, parameter values, and variables are described in Table 1).
-Individuals within this population are either female or male, and can be related to each other if they share a common ancestor.
-Each individual has 10 diploid loci and therefore 20 alleles underlying each trait: tendency to engage in polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$ i.e., 'fertilisation' alleles).
-Alleles combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for each trait.
-Over generations, we record mean values of alleles underlying polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
-One generation proceeds with females paying costs, expressing polyandry, mating, and fertilising offspring; offspring alleles then mutate and offspring express inbreeding depression; finally, immigrants arrive in the populatoin and density regulation limits population growth.
+We model evolution of polyandry and pre-copulatory and post-copulatory inbreeding avoidance by tracking reproductive interactions among individual females and males in a small focal population.
+Individuals are defined as related if they share a common ancestor within the population pedigree (i.e., non-zero kinship).
+Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of the three reproductive strategy traits: tendency for polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$ i.e., 'fertilisation' alleles).
+Alleles can take any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014] and combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for each trait.
+In overview, each generation proceeds with females paying costs, expressing polyandry, mating, and fertilisation.
+Offspring inherit a randomly sampled allele from each parent at each locas with no physical linkage.
+Alleles can then mutate and offspring express inbreeding depression.
+Immigrants arrive in the population and density regulation limits population growth.
+Key individual traits, parameter values, and variables are described in Table 1.
 
@@
 
-Values of phenotypic traits for tendency to engage in polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$) each have costs.
-Each cost independently increases the risk of female pre-mating mortality and, because generations are non-overlapping, total reproductive failure as a linear function of its associated trait.
-The probability that a focal female dies before mating due to the cost of polyandry ($c_{P}$) is therefore $P_{p} \times c_{P}$.
-Similarly, the probability of pre-mating female mortality due to the cost of pre-copulatory inbreeding strategy ($c_{M}$) and post-copulatory inbreeding strategy ($c_{F}$) is $|M_{p}| \times c_{M}$ and $|F_{p}| \times c_{F}$, repectively, where $|M_{p}|$ is the absolute value of $M_{p}$ and $|F_{p}|$ is the absolute value of $F_{p}$.
-Absolute values are used for applying costs to inbreeding strategies because both negative and positive $M_{p}$ and $F_{p}$ bias breeding interactions with respect to kinship, while only positive values of $P_{p}$ affect a female's tendency for polyandry; zero and negative $P_{p}$ values always translate to monandrous phenotypes (see below).
+Phenotypic values for tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$) each have costs that are assumed to independently increase the probability that a focal female will die before mating.
+The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, repectively.
+Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
+Absolute values are used for applying costs to inbreeding strategies as appropriate because both negative and positive $M_{p}$ and $F_{p}$ values affect the degree of inbreeding.
+In contrast, only positive values of $P_{p}$ cause females to be polyandrous (see below).
+Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases as a linear function with each trait value.
 
@@
 ----------------------------------------------
+
+<!--- ------------------------------------------------------------------------- --->
+<!--- ------------- LEFT OFF HERE --------------------------------------------- --->
+<!--- ------------------------------------------------------------------------- --->
 

### 2016-10-31 ms_pre_post.Rmd
Edit through Model: Polyandry

@@
 
+After costs are paid, each remaining female chooses $N_{males}$ males to mate with, where $N_{males}$ is calculated by sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
+This ensures that all surviving females choose at least one mate, and causes some stochastic variation aroudn the expected mean $N_{males}$ of $P_{p}+1$.
+A female's value of $P_{p}$ depends on the sum of her 20 $P_{a}$ allele values, which might be negative or positive.
+However, because females cannot mate with a negative number of males, $P_{p}$ is constrained to be zero or positive such that $P_{p} = 0$ when $P_{g} < 0$, but $P_{p} = P_{g}$ when $P_{g} \geq 0$.
+Polyandry is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998; @Duthie] that is influenced by continuous genetic variation but only expressed at the threshold value of $P_{g} > 0$.
+Any negative $P_{g}$ value therefore generates phenotypic monandry, while positive $P_{g}$ values can lead to different degrees of realised polyandry (i.e., different numbers of mates, $N_{males}$).
+
+Mating
+----------------------------------------------
+
 <!--- ------------------------------------------------------------------------- --->
@@
 <!--- ------------------------------------------------------------------------- --->
-
-After costs are paid, each remaining female chooses a number of males to mate with ($N_{males}$) based on her genetically determined tendency to engage in polyandry ($P_{p}$).
-The exact value of $N_{males}$ is calculated by randomly sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
-This random sampling procedure causes some stochastic variation in the number of realised mates a that female chooses, with a mean $N_{males}$ of $P_{p}+1$.
-A value of one is added to $P_{p}$ to ensure that all females that have not paid a cost choose at least one mate, as low values of $P_{p}$ might return $Poisson(P_{p})$ values of zero.
-
-The value of $P_{p}$ is affected by the summed values of a focal female's 20 $P_{a}$ alleles.
-Inheritence of all alleles models a diploid genetic architecture in which 10 $P_{a}$ alleles are randomly sampled from each parent with no physical linkage.
-Values of $P_{a}$ can take any real number [continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014].
-The tendency for polyandry genotype $P_{g}$ is therefore defined by the sum of all of a focal female's 20 $P_{a}$ values, which might be negative or positive.
-However, the tendency for polyandry phenotype $P_{p}$ is restricted to zero or positive values because the number of males that a female chooses to mate with cannot be negative.
-Hence, negative values of $P_{g}$ are translated to $P_{p}$ values of zero such that $P_{p} = 0$ when $P_{g} < 0$, but when $P_{g} \geq 0$, then $P_{p} = P_{g}$ (i.e., the phenotype value of polyandry equals the genotype value of polyandry if and only if the genotype value is greater than or equal to zero, else the phenotype value of polyandry always equals zero).
-The resulting $P_{p}$ is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998; @Duthie], in which polyandry is expressed discretely at the threshold value of $P_{g} > 0$, but is determined by the consequence of continuous genetic variation arising from the effects of $P_{a}$ alleles that each contribute additively to polyandry.
-Negative genotype values of $P_{g}$ therefore all have the same phenotype, resulting in consistently monandrous females.
-In contrast, positive values of $P_{g}$ and therefore $P_{p}$ can lead to different degrees of realised polyandry in the form of discrete numbers of mates ($N_{males}$).
-
-Mating
-----------------------------------------------
 

### 2016-10-31 ms_pre_post.Rmd
Edit Model: Mating section

@@
 
+All males in the population are assumed to be available for any female to choose.
+We therefore assume that there is no opportunity cost of male mating such that mating with one female would reduce a male's availability to mate with any other female.
+Individual females mate with their total allotment of $N_{males}$ without replacement, meaning that $N_{males}$ models a female's total number of different mates rather than solely her total number of matings.
+
+Most often, $N_{males}$ will be smaller than the total number of available males [@Duthie].
+Here, each female chooses her $N_{males}$ mates based on her pre-copulatory inbreeding strategy phenotype ($M_{p}$), which equals her pre-copulatory inbreeding strategy genotype ($M_{g}$) defined as the sum of the values of her 20 $M_{a}$ alleles.
+Negative or positive $M_{p}$ values cause a female to avoid or prefer mating with kin, respectively.
+Values of $M_{p}=0$ cause females to mate randomly with respect to kinship.
+
+The probability that a focal female $i$ mates with a male $j$ with which she shares some kinship $k_{ij}$ is calculated by first assigning each male a perceived mate quality $Q^{m}_{ij}$.
+If the female has a strategy of pre-copulatory inbreeding avoidance ($M_{p}<0$), then $Q^{m}_{ij} = (-M_{p} \times k_{ij} + 1)^{-1}$, meaning that $Q^{m}_{ij}$ decreases linearly with increasingly positive values of $k_{ij}$ and increasingly negative values of $M_{p}$.
+If the female has a strategy of pre-copulatory inbreeding preference ($M_{p}>0$), then $Q^{m}_{ij} = M_{p} \times k_{ij} + 1$, meaning that $Q^{m}_{ij}$ increases with increasingly positive $k_{ij}$ and $M_{p}$.
+If $M_{p}=0$, then all males are assigned a quality of 1
+
+After a focal female assigns all males a $Q^{m}_{ij}$ value, each male's value is divided by the sum of all $Q^{m}_{ij}$ values across all males, thereby assigning each male a relative perceived quality $q^{m}_{ij}$, which is constrained to values between zero and one.
+The value of $q^{m}_{ij}$ then defines the probability that a focal female mates with the male; mating is therefore stochastic, and females do not always mate with the male of the highest $q^{m}_{ij}$.
+For polyandrous females that choose multiple mates (i.e., $N_{mates}>1$), mates are chosen iteratively such that $Q^{m}_{ij}$ and $q^{m}_{ij}$ are re-calculated for each additional mate choice, and with $Q^{m}_{ij}$ and therefore $q^{m}_{ij}$ values of already chosen males set to zero to ensure mate sampling without replacement.
+In the unlikely event that a female's $N_{males}$ exceeds the total number of available males, then she simply mates with all males.
+
+Fertilisation
+----------------------------------------------
+
 <!--- ------------------------------------------------------------------------- --->
@@
 <!--- ------------------------------------------------------------------------- --->
-
-Each male within the population is a potential mate for any female to choose.
-We therefore assume that there are no opportunity costs associated with male mating such that mating with one female would reduce a male's ability to mate with and sire the offspring of any other female [e.g., @Waser1986].
-While all males are therefore available as potential mates, we assume that a female mates with her total allotment of $N_{males}$ without replacement, meaning that $N_{males}$ models the total number of distinct males that a female chooses to mate with rather than the number of times that she mates.
-In the unlikely event that a female's $N_{males}$ exceeds the total number of males in the population, then she mates with all of the males in the population.
-Most often, $N_{males}$ will be a small subset of the available males in the population [@Duthie], so the male(s) a focal female chooses will reflect her expression of pre-copulatory inbreeding strategy phenotype ($M_{p}$).
-Like polyandry allele values, pre-copulatory inbreeding strategy allele values ($M_{a}$) can take any real number.
-However, unlike polyandry, the sum of all of a female's 20 $M_{a}$ alleles equals both her pre-copulatory inbreeding strategy genotype ($M_{g}$) and her pre-copulatory inbreeding strategy phenotype ($M_{p}$).
-Negative or positive values of $M_{p}$ cause a female to avoid or prefer mating with kin, respectively.
-Values of $M_{p}=0$ cause females to mate randomly with respect to kinship.
-
-The probability that a focal female $i$ mates with a male $j$ with which she shares some kinship $k_{ij}$ is calculated by first assigning each male a perceived mate quality $Q^{m}_{ij}$.
-This quality depends upon whether the female has a strategy of avoiding mating with kin ($M_{p}<0$) or preferring mating with kin ($M_{p}>0$; if $M_{p}=0$, all males are assigned a quality of 1, $Q^{m}_{ij}=1$).
-If a focal female avoids mating with kin, then $Q^{m}_{ij} = (-M_{p} \times k_{ij} + 1)^{-1}$, meaning that the perceived quality of a male decreases linearly with increasingly positive values of $k_{ij}$ and increasingly negative values of $M_{p}$.
-If a focal female prefers mating with kin, then $Q^{m}_{ij} = M_{p} \times k_{ij} + 1$, meaning that the perceived quality of a male increases with increasingly positive values of $k_{ij}$ and $M_{p}$.
-After a focal female assigns all males a perceived quality, the sum of all male perceived qualities is calculated, then each male quality is divided by this sum.
-This transformation results in each male having a relative perceived mate quality $q^{m}_{ij}$, which is constrained to values between zero and one.
-The value of $q^{m}_{ij}$ then defines the probability that a focal female chooses the male as a mate; female choice is therefore stochastic, meaning that females do not always choose the male of the highest $q^{m}_{ij}$ (e.g., given $M_{p}$ values of $-2$, $-4$, $-6$, and $-8$, an outbred focal female is $1.5$, $2$, $2.5$, and $3$ times more likely to mate with a non-relative than a full-sibling $k_{ij}=0.25$, respectively).
-For polyandrous females that choose more than one male mate, mates are chosen iteratively such that $Q^{m}_{ij}$ and $q^{m}_{ij}$ are re-calculated for each additional mate choice, and with $Q^{m}_{ij}$ and therefore $q^{m}_{ij}$ values of already chosen males set to zero to ensure mate sampling without replacement.
-
-Fertilisation
-----------------------------------------------
 

### 2016-10-31 ms_pre_post.Rmd
Edit Model: Mutation

@@
 
-<!--- ------------------------------------------------------------------------- --->
-<!--- ------------- LEFT OFF HERE --------------------------------------------- --->
-<!--- ------------------------------------------------------------------------- --->
+Following mating, fertilisation occurs such that each of a female's $n$ offspring is independently assigned a sire (with replacement) from the $N_{males}$ with which the female mated.
+Sire identity depends on female's kinship with each potential sire ($k_{ij}$) and her post-copulatory inbreeding strategy phenotype ($F_{p}$), which equals her post-copulatory inbreeding strategy genotype ($F_{g}$), defined as the sum of the values of her 20 $F_{a}$ alleles.
+Negative and positive values of $F_{p}$ correspond to post-copulatory inbreeding avoidance or preference, respectively, and $F_{p}=0$ causes random fertilisation with respect to kinship.
 
-Fertilisation of a female's $n$ offspring occurs after mating, with each of her $n$ offspring being assigned a sire independently and with replacement from the $N_{males}$ with which the female mated.
-The probability that a male mate successfully sires an offspring is affected by a female's kinship with the potential sire ($k_{ij}$) and her post-copulatory inbreeding strategy ($F_{p}$).
-As with polyandry and pre-copulatory inbreeding strategy phenotypes, a female's post-copulatory inbreeding strategy phenotype is determined by the summed effects of 20 post-copulatory inbreeding strategy alleles ($F_{a}$), which can take any real number.
-The sum of all of a female's $F_{a}$ alleles determines her post-copulatory inbreeding strategy genotype ($F_{g}$), which is identical to her post-copulatory inbreeding strategy phenotype ($F_{p}$).
-As with pre-copulatory inbreeding strategy phenotype ($M_{p}$), negative or positive values of $F_{p}$ correspond to inbreeding avoidance or preference, respectively, and $F_{p}=0$ causes random fertilisation with respect to kinship.
-
-The probability that an offspring of a focal female $i$ is fertilised by one of $i$'s mates $j$ is calculated by first assigning a perceived fertilisation quality to each $j$, $Q^{f}_{ij}$.
-Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if a focal female has a post-copulatory strategy of avoiding inbreeding ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$.
-If instead a focal female has a post-copulatory strategy of preferring inbreeding ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$.
-The perceived qualities of every male that a focal female has mated with are summed, then a relative quality ($q^{f}_{ij}$) is calculated for each male by dividing each individual male mate's $Q^{f}_{ij}$ by this sum.
-As with relative perceived mate quality values ($q^{m}_{ij}$), this results in values of perceived fertilisation quality $q^{f}_{ij}$ between zero and one.
-These $q^{f}_{ij}$ values define the probability that the offspring of a focal female $i$ is fertilised by the male $j$.
-Females produce $n$ offspring, meaning that $q^{f}_{ij}$ values are sampled $n$ times independently and with replacement for each female to determine the realised distribution of sires.
+The probability that an offspring of a focal female $i$ is sired by any one of $i$'s mates $j$ is calculated by assigning a perceived fertilisation quality to each $j$, $Q^{f}_{ij}$.
+Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if a focal female has a strategy of post-copulatory inbreeding avoidance ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$.
+If the focal female has strategy of post-copulatory inbreeding preference ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$.
+A relative quality ($q^{f}_{ij}$) is then calculated for each male by dividing his $Q^{f}_{ij}$ by the sum of the $Q^{f}_{ij}$ values across all of a female's mates.
+These $q^{f}_{ij}$ values, which lie between zero and one, define the probability of paternity.
 
@@
 
-Alleles of a focal female's offspring mutate with a probability of $\mu=0.001$, with mutation being an independent event that does or does not occur for each locus.
-When a mutation occurs at a locus, a new value is sampled from a random normal distribution with a mean of zero and a standard devation of mutation effect size $\mu_{SD}$, $\mathcal{N}(0, \mu_{SD})$.
-This new value is then added to the original value of the allele that mutates [@Kimura1965; @Lande1976; @Bocedi2014; @Duthie].
-The standard deviation of the mutation effect size ($\mu_{SD}$) is set to $\sqrt{1/20}$, which scales the variance of mutation effect size to the total number of alleles affecting $P_{p}$, $M_{p}$, and $F_{p}$ phenotypes [see @Kimura1965; @Lande1976; @Bocedi2014].
+Offsprings' alleles mutate with independent probabilities $\mu=0.001$.
+When a mutation occurs, a mutation effect is sampled from a normal distribution with a mean of zero and a standard deviation of $\mu_{SD}$ and added to the original allele value [@Kimura1965; @Lande1976; @Bocedi2014; @Duthie].
+The value of $\mu_{SD}$ is set to $\sqrt{1/20}$, which scales the variance of mutation effect size to the total number of alleles affecting each phenotype.
 

### 2016-11-01 ms_pre_post.Rmd
Edit Model: Inbreeding Depression subsection

@@
 
+The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a log-linear function of her kinship with the sire of her offspring $j$ ($k_{ij}$) and inbreeding depression slope $\beta$,
+\begin{equation}
+\Psi_{\textrm{off}} = e^{-\beta k_{ij}}
+\end{equation}
+Here, $\beta$ models the number of haploid lethal equivalents that exist as deleterious recessive alleles in the gametes of $i$ and $j$, and which might be homozygous in offspring and reduce viability.
+Equation 1 assumes independent allelic effects, generating multiplicative effects on offspring viability [@Morton1956; @Mills1994].
+We model inbreeding depression as having an absolute rather than relative effect on offspring viability )i.e., hard rather than sof selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
+We also assume that inbreeding always decreases offspring viability, $\beta > 0$ (i.e., no outbreeding depression).
+Therefore, because $k_{ij}$ is constrained to values between zero and one, $-\beta \times k_{ij} \leq 0$.
+Values of $\Psi_{\textrm{off}}$ must therefore be between zero (if $-\beta \times k_{ij}$ is very negative) and one (if $-\beta \times k_{ij} = 0$).
+We therefore define $\Psi_{\textrm{off}}$ as the probability that an offspring is viable, and sample its realised viability (versus mortality) using a Bernoulli trial.
+
+Immigration
+----------------------------------------------
+
 <!--- ------------------------------------------------------------------------- --->
@@
 <!--- ------------------------------------------------------------------------- --->
-
-The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a function of the coefficient of kinship between $i$ and the sire of her offspring $j$ ($k_{ij}$), and a log-linear slope of inbreeding depression $\beta$.
-We model selection as having an absolute effect on offspring viability (i.e., hard selection), rather than a relative effect on viability (i.e., soft selection), so that the effect of $\beta$ is consistent over generations and across different parameter combinations.
-Natural selection on tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$) can therefore be compared across generations and parameter combinations.
-If offspring viability was instead relative such that the least inbred offspring had a high viability regardless of the absolute value of $k_{ij}$, then the effect of kinship coefficients and inbreeding depression slopes on offspring viability would depend on the population-wide distribution of $k_{ij}$ between females and males, making model inference more difficult.
-Therefore, we define offspring viability as,
-\begin{equation}
-\Psi_{\textrm{off}} = e^{-\beta k_{ij}}
-\end{equation}
-The slope $\beta$ models the number of haploid lethal equivalents that exist as deleterious recessive alleles in the gametes of $i$ and $j$, and which might combine to become homozygous in offspring and reduce viability.
-Equation 1 assumes that each deleterious recessive allele affects offspring viability independently, meaning that every deleterious recessive allele added will have a multiplicative affect on decreasing total viability [@Morton1956; @Mills1994], causing the log-linear relationship between parent kinship and inbreeding depression.
-We assume that inbreeding depression always decreases offspring viability, $\beta > 0$ (i.e., no outbreeding depression).
-Therefore, because $k_{ij}$ is constrained to values between zero and one, the product of $-\beta$ and $k_{ij}$ must be a value less than or equal to zero, $-\beta \times k_{ij} \leq 0$.
-Values of $\Psi_{\textrm{off}}$ must therefore be between zero (if $-\beta \times k_{ij}$ is very negative) and one (if $-\beta \times k_{ij} = 0$).
-We can therefore define $\Psi_{\textrm{off}}$ as the probability that an offspring is viable, and sample its realised viability using a Bernoulli trial.
-
-Immigration
-----------------------------------------------
 

### 2016-11-01 ms_pre_post.Rmd
Edit Model: Density regulation subsection

@@
 
-<!--- ------------------------------------------------------------------------- --->
-<!--- ------------- LEFT OFF HERE --------------------------------------------- --->
-<!--- ------------------------------------------------------------------------- --->
-
-After offspring viability is realised, $\rho$ adult immigrants are added to the focal population.
-The coefficient of kinship between an immigrant and all other individuals (including native individuals and other immigrants) always equals zero ($k_{ij}=0$).
-Because kinship coefficient values are calculated directly from the pedigree of the focal population [not from individuals' genomes; see @Duthie], the addition of immigrants introduces non-kin into the population at a constant rate and prevents the mean kinship coefficient of the population from asymptoting to a value of 1 over generations.
-If the focal population was instead closed ($\rho=0$), then all alleles would quickly be expected to become identical-by-descent among descendants of the ancestral population.
-To avoid having immigrants affect evolution of tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$), immigrants are always male and can therefore be chosen based on their kinship values of zero but not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$.
-To further avoid having immigrants affect evolutionary dynamics, allele values underlying ($P_{a}$), pre-copulatory inbreeding strategy ($M_{a}$), and post-copulatory inbreeding strategy ($F_{a}$) are randomly sampled from normal distributions with means and standard deviations of $P_{a}$, $M_{a}$, and $F_{a}$ values equal to the means and standard deviations of those in the focal population at the time of immigration.
-Overall, this model of immigration effectively assumes that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$.
+After offspring mortality, $\rho$ adult immigrants are added to the focal population.
+The kinship between an immigrant and all other individuals always equals zero ($k_{ij}=0$).
+Immigration therefore prevents the mean kinship within the population from asymptoting to one over generations.
+To ensure that immigrants do not directly affect genotypic or phenotypic values of tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$), immigrants are always male.
+Consequently, they can be chosen as females' mates based on their kinship values of zero but do not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$.
+Further, immigrants $P_{a}$, $M_{a}$, and $F_{a}$ allele values are randomly sampled from normal distributions with means and standard deviations equal to those in the focal population at the time of immigration.
+We thereby effectively assume that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$.
 
@@
 
-To avoid having unrestricted population growth over generations, we introduce a separate carrying capacity on the total number of females ($K_{f}$) and males ($K_{m}$) in the focal population following immigration [@Guillaume2009; @Duthie].
-If at the end of a generation the number of females or males exceeds their respective carrying capacities, then each sex is reduced back to its $K_{f}$ or $K_{m}$ by randomly removing females and males until each sex is at its carrying capacity.
-Removal of females and males can be interpreted as dispersal outside the focal population, mortality, or as some combination of dispersal and mortality.
-The remaining females and males within the population form the next generation of adults.
+To avoid unrestricted population growth, we set separate carrying capacities for the total numbers of females ($K_{f}$) and males ($K_{m}$) in the focal population following immigration [@Guillaume2009; @Duthie].
+If at the end of a generation the number of females or males exceeds $K_{f}$ or $K_{m}$  respectively, then individuals are randomly removed until each sex is at its carrying capacity.
+Such removal can be interpreted as some combination of dispersal and mortality.
+The remaining females and males form the next generation of potentially breeding adults.
 

### 2016-11-01 ms_pre_post.Rmd
Edit through Model section, update bib to include recent Duthie and Reid AmNat paper

@@
 
-Previous models implicitly or explicitly considered the fate of a rare allele underlying pre-copulatory inbreeding avoidance in a population initially fixed for random mating [e.g., Duthie and Reid *In press*; @Parker1979; @Parker2006; @Duthie].
+Previous models implicitly or explicitly considered the fate of a rare allele underlying pre-copulatory inbreeding avoidance in a population initially fixed for random mating [e.g., @Parker1979; @Parker2006; @Duthie; @Duthie2016a].
 Such models thereby isolate the invasion fitness of this single strategy.
@@
 
-<!--- ------------------------------------------------------------------------- --->
-<!--- ------------- LEFT OFF HERE --------------------------------------------- --->
-<!--- ------------------------------------------------------------------------- --->
+To test the hypothesis that evolution of post-copulatory inbreeding avoidance can facilitate evolution of costly polyandry, we compare simulations in which polyandry and pre-copulatory and post-copulatory inbreeding can all evolve, with otherwise identical simulations in which post-copulatory inbreeding strategy cannot evolve given four different costs of polyandry ($c_{P} = \{0, 0.0025, 0.005,  0.01\}$).
+To prevent $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes cause random fertilisation with respect to kinship.
+Hence $F_{a}$ alleles have no phenotypic effect, meaning that polyandrous females cannot enact post-copulatory inbreeding avoidance.
 
-To analyse our model, we track mean values of alleles underlying tendency for polyandry ($P_{a}$), pre-copulatory inbreed strategy ($M_{a}$), and post-copulatory inbreeding strategy ($F_{a}$) in a focal population.
-We present evolutionary dynamics of these mean allele values across different parameter combinations to test our three focal hypotheses.
+To test the hypothesis that selection for a costly strategy of inbreeding avoidance will be negligible given a less costly alternative strategy, we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where the cost of pre-copulatory inbreeding strategy $c_{M}=0$ but the cost of post-copulatory inbreeding strategy $c_{F}=0.02$, and vice versa.
+We compare these simulations with evolution of a costly strategy in the absence of evolution of an alternative strategy (e.g., evolution of pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy phenotype is fixed at zero, $F_{p}=0$).
 
-To test our hypothesis that selection for polyandry is driven by a female's ability to bias fertilisation toward inbreeding avoidance through post-copulatory mechanisms, we compare simulations in which all three phenotypes including tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory strategy ($F_{p}$) evolve, with an identical set of simulations in which $F_{p}$ cannot evolve given $c_{P} = \{0, 0.0025, 0.005,  0.01\}$.
-To stop $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes resulting from $F_{a}$ cause random fertilisation with respect to kinship (i.e, $F_{p}=0$).
-Hence $F_{a}$ alleles have no phenotypic effect and polyandry cannot cause polyandrous females to benefit through an increased ability to bias fertilisation toward inbreeding avoidance.
-By comparing mean $P_{a}$ values over generations when post-copulatory inbreeding avoidance also evolves versus when fertilisation is random, we test whether or not evolution of post-copulatory inbreeding strategy increases selection for polyandry.
-
-To test the hypothesis that selection for a costly strategy of inbreeding avoidance will be negligible given a less costly alternative strategy, we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where the cost of pre-copulatory inbreeding strategy $c_{M}=0$ but the cost of post-copulatory inbreeding strategy $c_{F}=0.02$, and where $c_{F}=0$ but $c_{M}=0.02$.
-We contrast these simulations with evolution of a costly strategy in the absence of evolution of an alternative strategy (e.g., evolution of pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy phenotype is fixed at zero, $F_{p}=0$).
-A contrast between the baseline expectation for how costs affect evolution of a focal inbreeding strategy in the absence of an alternative strategy, and evolution of a focal strategy given that an alternative strategy also evolves, tests whether or not a relatively low cost alternative strategy decreases selection for a focal strategy.
-
-To test the hypothesis that the existence of an adaptive inbreeding strategy will decrease the strength of selection on, and thereby preclude the invasion of, a complementary strategy, we first used exploratory simulations to determine evolution of pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation.
-To test whether or not pre-copulatory inbreeding avoidance was predicted to evolve when adaptive polyandry to avoid inbreeding was already established, we initiated pre-copulatory inbreeding strategy allele values at zero ($M_{a}=0$), but fixed post-copulatory inbreeding allele values at $F_{a}=-10$ and polyandry allele values at $P_{a}=1$ (i.e., $F_{p}$ and $P_{p}$ did not evolve).
-Similarly, to test whether or not post-copulatory inbreeding strategy evolved to avoid inbreeding, we initiated post-copulatory inbreeding strategy allele values and polyandry allele values at zero ($F_{a}=0$; $P_{a}=0$), but fixed pre-copulatory inbreeding strategy allele values at $M_{a}=-10$.
-For reference, because females have 10 diploid loci, when $M_{a}$ or $F_{a}$ alleles were fixed at $-10$, outbred females were $51$ times less likely to choose a full sibling and $13.5$ times times less likely to choose a first cousin than a non-relative in pre- and post-copulatory choice, respectively.
+To test the hypothesis that the existence of adaptive post-copulatory inbreeding avoidance will preclude the invasion of pre-copulatory inbreeding avoidance, or vice versa, we first used exploratory simulations to determine evolution of pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation.
+To test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance was already established, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., meaning that $F_{p}$ and $P_{p}$ did not evolve).
+Similarly, to test whether post-copulatory inbreeding avoidance evolved when pre-copulatory inbreeding avoidance was already established, we initiated $F_{a}$ and $P_{a}$ allele values at zero but fixed $M_{a}$ allele values at $-10$.
+Consequently, because females have 10 diploid loci, when $M_{a}$ or $F_{a}$ alleles were fixed at $-10$, outbred females were $51$ times less likely to choose a full brother and $13.5$ times times less likely to choose a first cousin than a non-relative in pre-copulatory and post-copulatory choice, respectively.
 
 In all simulations, we record mean values of $P_{a}$, $M_{a}$, $F_{a}$ in each generation.
-Each combination of parameter values simulated is replicated $40$ times, and grand mean values and standard error of means is calculated in each generation across replicate simulations.
+Each combination of parameter values simulated is replicated $40$ times, and grand mean values and standard errors of means are calculated in each generation across replicates.
 These analyses allow us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on post-copulatory inbreeding strategy might be weak if polyandry is rare).
 For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling [@Duthie] showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
-For all replicates, we set $\rho=5$ immigrants, which produced a range of kin and non-kin in each generation allowing females could express inbreeding strategies, and $n=8$ offspring, which was sufficient to keep populations consistently at carrying capacities and avoid population extinction.
-Values of $K_{f}$ and $K_{m}$ were both set to 100 because previous modelling has shown that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but populations are also not so small that selection is typically overwhelmed by genetic drift (Duthie and Reid *in press*).
+For all replicates, we set $\rho=5$ immigrants, which produced a range of kin and non-kin in each generation allowing females to express inbreeding strategies, and $n=8$ offspring, which was sufficient to keep populations consistently at carrying capacities and avoid population extinction.
+Values of $K_{f}$ and $K_{m}$ were both set to 100 because previous modelling has shown that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but populations are also not so small that selection is typically overwhelmed by genetic drift [@Duthie2016a].
 

### 2016-11-01 ms_pre_post.Rmd
Edit Results: First subsection

@@
 
-Will evolution of post-copulatory inbreeding avoidance strengthen selection for polyandry?
+Does evolution of post-copulatory inbreeding avoidance facilitate evolution of costly polyandry?
+----------------------------------------------
+
+When post-copulatory inbreeding avoidance alleles ($F_{a}$) were fixed to zero and could not evolve, $P_{a}$ values were always negative (Figure 1A,C,E,G).
+This shows that there is selection against unconditional polyandry even given zero direct cost ($c_{P}=0$; Figure 1A).
+This is because polyandrous females sampled more males from the available population and were consequently likely to mate with some relatives and hence produce some inbred offspring with low viability [@Duthie2016].
+
+When post-copulatory inbreeding avoidance was allowed to evolve, mean $P_{a}$ values were substantially higher than in comparable simulations where post-copulatory inbreeding avoidance could not evolve (Figure 1B,D,F,H).
+Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry.
+However, $P_{a}$ values were expeted to be positive only given a low cost of polyandry ($c_{P} < 0.005$, Figure 1A,B).
+This implies that, even given strong inbreeding depression in offspring viability, inbreeding avoidance might generally be a weak force driving polyandry evolution.
+
+Strong post-copulatory inbreeding avoidance consistently evolved in all simulations where such such evolution was allowed (Figure 1B,D,F,H), even when $P_{a}$ values were expected to be slightly negative (i.e., when there is selection against polyandry, Figure 1F,H).
+This reflects the threshold nature of phenotypic expression of polygenic polyandry, wherein random sampling of alleles means that polyandry is commonly expressed (i.e., $P_{g}>0$) even when mean $P_{a}$ values are negative (Figure 2).
+This means that there is commonly opportunity for expression of post-copulatory inbreeding avoidance and associated selection that drives evolution of $F_{a}$ allele values.
+
+Strong pre-copulatory inbreeding avoidance also evolved (i.e., $M_{a}<0$) in all simulations, irrespective of $c_{P}$ and irrespective of whether post-copulatory inbreeding avoidance was allowed to evolve (Figure 1).
+
+Will selection for a costly inbreeding strategy be negligible given a non-costly alternative strategy?
 ----------------------------------------------
@@
 <!--- ------------------------------------------------------------------------- --->
-
-For low costs of polyandry, $c_{P} < 0.005$, selection caused expected polyandry allele values ($P_{a}$) to be positive only when post-copulatory inbreeding avoidance evolved (Figure 1A-D).
-For all $c_{P}$, $P_{a}$ values were higher when post-copulatory inbreeding avoidance evolved than when it could not evolve (Figure 1).
-When post-copulatory inbreeding avoidance could not evolve, $P_{a}$ values were negative even in the absence of a direct cost ($c_{P}=0$; Figure 1A) because females that expressed polyandry were more likely to increase their inbreeding due to sampling males without replacement [@Duthie].
-Strong post-copulatory inbreeding avoidance consistently evolved in all simulations, even when $P_{a}$ values were expected to be slightly negative (Figure 1F,H), because of the threshold nature of the polyandry phenotype.
-Figure 2 shows how phenotypic polyandry was common even when mean polyandry allele values within a population were expected to be negative, and how monandry occurred even when mean polyandry allele values were expected to be positive.
-In all simulations, pre-copulatory inbreeding avoidance also evolved ($M_{a}<0$), meaning that both pre- and post-copulatory inbreeding avoidance was predicted, and evolution of adaptive polyandry occurred given sufficiently low costs of polyandry.
-
-Will selection for a costly inbreeding strategy be negligible given a non-costly alternative strategy?
-----------------------------------------------
 

### 2016-11-01 ms_pre_post.Rmd
Edit Results: Second subsection

@@
 Evidence of both pre-copulatory and post-copulatory inbreeding avoidance has accumulated for some well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015].
-While most studies consider either pre- or post-copulatory inbreeding avoidance in isolation, a small number of studies consider both.
+While most studies consider either pre-copulatoryor post-copulatory inbreeding avoidance in isolation, a small number of studies consider both.
 Accordingly, @Liu2014 found evidence of pre-copulatory, but not post-copulatory, inbreeding avoidance in cabbage beetles (*Colaphellus bowringi*).
-Other studies found no evidence of pre- or post-copulatory inbreeding avoidane despite strong inbreeding depression [e.g., @Reid2014; @Reid2015].
-These empirical studies demonstrate that diverse combinations of pre- and post-copulatory inbreeding avoidance occur in nature.
-However, there is as yet no conceptual framework that predicts *a priori* what combinations should be favoured by selection when both pre- and post-copulatory inbreeding avoidance, and polyandry can evolve.
+Other studies found no evidence of pre-copulatoryor post-copulatory inbreeding avoidane despite strong inbreeding depression [e.g., @Reid2014; @Reid2015].
+These empirical studies demonstrate that diverse combinations of pre-copulatoryand post-copulatory inbreeding avoidance occur in nature.
+However, there is as yet no conceptual framework that predicts *a priori* what combinations should be favoured by selection when both pre-copulatoryand post-copulatory inbreeding avoidance, and polyandry can evolve.
 Such a framework would allow prediction of the form of mating system evolution across different systems that experience inbreeding depression and allow existing empirical studies to be used to test evolutionary predictions through comparative analyses.
@@
 Therefore, while pre-copulatory inbreeding avoidance can facilitate evolution of polyandry under some restrictive conditions [@Duthie], the opportunity for post-copulatory choice might facilitate evolution of polyandry under a much wider range of conditions by allowing females to bias fertilisation toward non-kin.
-The long-term evolutionary dynamics of pre- and post-copulatory inbreeding avoidance then become unclear.
-Strong inbreeding depression might drive initial evolution of both pre- and post-copulatory inbreeding avoidance and associated polyandry.
+The long-term evolutionary dynamics of pre-copulatoryand post-copulatory inbreeding avoidance then become unclear.
+Strong inbreeding depression might drive initial evolution of both pre-copulatoryand post-copulatory inbreeding avoidance and associated polyandry.
 However, if evolution of polyandry and post-copulatory inbreeding avoidance renders pre-copulatory inbreeding avoidance redundant, or vice versa, then only one strategy might be maintained in the long-term.
@@
 Such models thereby isolate the invasion fitness of this single strategy.
-However, when both pre- and post-copulatory strategies can affect realised inbreeding, it cannot be assumed that both strategies will invade simultaneously, nor that invasion fitness of one strategy will be independent of the other For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect of such invading alleles could be weak or negligible.
+However, when both pre-copulatoryand post-copulatory strategies can affect realised inbreeding, it cannot be assumed that both strategies will invade simultaneously, nor that invasion fitness of one strategy will be independent of the other For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect of such invading alleles could be weak or negligible.
 
-Ultimately, the absolute and relative frequencies of alleles underlying pre- and post-copulatory inbreeding avoidance and polyandry are likely to be affected by direct negative selection on resulting phenotypes (i.e., costs) and hence on the net costs versus benefits stemming from inbreeding avoidance.
+Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatoryand post-copulatory inbreeding avoidance and polyandry are likely to be affected by direct negative selection on resulting phenotypes (i.e., costs) and hence on the net costs versus benefits stemming from inbreeding avoidance.
 Polyandrous females can pay costs of mate searching or mating, for example, because these activities increase predation risk [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
@@
 Females that express post-copulatory choice might pay an energetic cost associated with physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
-If the relative costs affecting pre- and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly inbreeding strategy might become fixed in the population over generations, while alleles underlying the more costly inbreeding strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
+If the relative costs affecting pre-copulatoryand post-copulatory inbreeding avoidance differ, then alleles underlying the less costly inbreeding strategy might become fixed in the population over generations, while alleles underlying the more costly inbreeding strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
 
@@
 Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution such that only the less costly inbreeding avoidance strategy will be expressed in the long term.
-Finally, we test the hypothesis that evolution of one inbreeding avoidance strategy (i.e., pre- or post-copulatory) will be precluded if it is introduced into a population that is already fixed for the other inbreeding avoidance strategy that is adaptive.
+Finally, we test the hypothesis that evolution of one inbreeding avoidance strategy (i.e., pre-copulatoryor post-copulatory) will be precluded if it is introduced into a population that is already fixed for the other inbreeding avoidance strategy that is adaptive.
 We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across different reproductive systems.
@@
 
+When either pre-copulatory or post-copulatory inbreeding strategy allele values were fixed to zero and could not evolve, the alternative inbreeding strategy evolved to inbreeding avoidance even when costly (Figure 3A,C).
+However, when one inbreeding strategy could evolve and had zero cost, the other strategy initially evolved towards inbreeding avoidance but then back towards random choice across generations following increasing evolution of inbreeding avoidance (i.e., negative allele values) through the former (zero cost) strategy (Figure 3B,D).
+For example, given fixed $F_{a}=0$, grand mean $M_{a}$ value in the last $10000$ generations was $-0.868$ (Figure 3A), meaning that a female was ca $5.34$ times less likely to choose a full-sibling and ca $2.10$ times less likely to mate with a first cousin than a non-relative given a high cost of pre-copulatory inbreeding avoidance, $c_{M}=0.02$.
+However, when $F_{a}$ allele values could also evolve, grand mean $M_{a}$ allele value in the last $10000$ generations was only $-0.288$ (Figure 3B).
+Further, given fixed $M_{a}=0$, grand mean $F_{a}$ value in the last $10000$ generations was $-1.092$ (Figure 3C), meaning that a female was ca $6.46$ times less likely to choose a full-sibling and ca $2.37$ times less likely to choose a first cousin than a non-relative given a high cost of pre-copulatory inbreeding avoidance, $c_{F}=0.02$.
+However, when $M_{a}$ values could also evolve and $P_{a}$ values were negative, grand mean $F_{a}$ value in the last $10000$ generations was only $-0.070$ (Figure 3D).
+Overall, evolution of a costly inbreeding strategy that readily evolved in isolation was greatly impeded by evolution of a less costly strategy.
+
+<!--- Co-author wants to talk about polyandry and stuff: But these figures don’t look very symmetrical – there’s stuff going on in Fig 3 that isn’t really noted in the text – should we do a bit more with this?
+The most obvious difference is that polyandry evolves in B but not D - i.e.
+when pre-cop IA is costly but not when post-cop IA is costly.
+Wouldn’t it be helpful to point this out and explain it?
+NB, presumably polyandry is cost-free in all these simulations?
+Might it be worth re-iterating that too?
+--->
+
+Will selection for a costly inbreeding strategy be negligible given existence of an already adaptive alternative strategy?
+----------------------------------------------
+
 <!--- ------------------------------------------------------------------------- --->
@@
 <!--- ------------------------------------------------------------------------- --->
-
-For simulations in which either pre- or post-copulatory inbreeding strategy allele values were fixed for random choice with respect to kinship ($M_{a}=0$ or $F_{a}=0$, respectively), the alternative costly inbreeding strategy evolved to inbreeding avoidance ($F_{a}<0$ or $M_{a}<0$; Figure 3).
-However, when the alternative inbreeding strategy could evolve and was not costly, the focal costly inbreeding strategy initially evolved towards inbreeding avoidance, but then evolved toward random choice with respect to kinship given increasingly negative allele values of the alternative strategy over generations (Figure 3B,D).
-For example, given fixed $F_{a}=0$, grand mean $M_{a}$ values were $-0.868$ in the last $10000$ generations (Figure 3A), meaning that an outbred focal female was ca $5.34$ times less likely to choose a full-sibling and ca $2.10$ times less likely to choose a first cousin than a non-relative given a strong cost of pre-copulatory inbreeding avoidance, $c_{M}=0.02$.
-In contrast, grand mean $M_{a}$ allele values were $-0.288$ when post-copulatory inbreeding avoidance also evolved.
-More strongly, given fixed $M_{a}=0$, grand mean $F_{a}$ values were $-1.092$ in the last $10000$ generations (Figure 3C), meaning that an outbred focal female was ca $6.46$ times less likely to choose a full-sibling and ca $2.37$ times less likely to choose a first cousin than a non-relative given a strong cost of pre-copulatory inbreeding avoidance, $c_{F}=0.02$.
-However, grand-mean $F_{a}$ values were $-0.070$ when pre-copulatory inbreeding strategy evolved, and polyandry allele values were negative.
-Overall, selection for a costly inbreeding strategy that was adaptive in isolation was greatly weakened given evolution of a less costly strategy.
-
-Will selection for a costly inbreeding strategy be negligible given existence of an already adaptive alternative strategy?
-----------------------------------------------
 
@@
 
-We have provided a novel framework for approaching empirical studies of inbreeding avoidance, predicting evolution of polyandry and inbreeding avoidance through pre- and post-copulatory mechanisms.
+We have provided a novel framework for approaching empirical studies of inbreeding avoidance, predicting evolution of polyandry and inbreeding avoidance through pre-copulatoryand post-copulatory mechanisms.
 Accordingly, we modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency to engage in polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
-Using *in silico* experiments, we tested three specific hypothesis to predict evolution of polyandry, and pre- and post-copulatory inbreeding strategy.
-We found that (1) selection for polyandry was greatly strengthened given concurrent evolution of post-copulatory inbreeding avoidance, (2) selection for costly pre- or post-copulatory inbreeding avoidance was negligible given evolution of a less costly strategy of inbreeding avoidance, and (3) pre-existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance, but not vice versa.
+Using *in silico* experiments, we tested three specific hypothesis to predict evolution of polyandry, and pre-copulatoryand post-copulatory inbreeding strategy.
+We found that (1) selection for polyandry was greatly strengthened given concurrent evolution of post-copulatory inbreeding avoidance, (2) selection for costly pre-copulatoryor post-copulatory inbreeding avoidance was negligible given evolution of a less costly strategy of inbreeding avoidance, and (3) pre-existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance, but not vice versa.
 
@@
 
-In our model, a cost free inbreeding strategy precluded a more costly complementary inbreeding strategy from persisting in a focal population (Figure 2), meaning that long-term persistence of both pre- and post-copulatory inbreeding avoidance might not be expected in populations given cost asymmetry.
+In our model, a cost free inbreeding strategy precluded a more costly complementary inbreeding strategy from persisting in a focal population (Figure 2), meaning that long-term persistence of both pre-copulatoryand post-copulatory inbreeding avoidance might not be expected in populations given cost asymmetry.
 Direct costs therefore strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies.
@@
 Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre- and post-copulatory inbreeding avoidance.
+Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre-copulatoryand post-copulatory inbreeding avoidance.
 Costs of polyandry increase with rows from top to bottom.
@@
 
-![Relationship between polyandry allele values and phenotypes for an individual-based model in which pre- and post-copulatory inbreeding strategies evolve jointly with polyandry.
+![Relationship between polyandry allele values and phenotypes for an individual-based model in which pre-copulatoryand post-copulatory inbreeding strategies evolve jointly with polyandry.
 Two simulations with identical starting conditions (default parameter values with no costs) are shown in panels A,B and C,D.

### 2016-11-01 ms_pre_post.Rmd
Edit up to Discussion

@@
 
-<!--- Co-author wants to talk about polyandry and stuff: But these figures don’t look very symmetrical – there’s stuff going on in Fig 3 that isn’t really noted in the text – should we do a bit more with this?
+<!--- Co-author wants to talk about polyandry and stuff: ''But these figures don’t look very symmetrical – there’s stuff going on in Fig 3 that isn't really noted in the text – should we do a bit more with this?
 The most obvious difference is that polyandry evolves in B but not D - i.e.
@@
 NB, presumably polyandry is cost-free in all these simulations?
-Might it be worth re-iterating that too?
---->
+Might it be worth re-iterating that too?'' --->
 
@@
 
-<!--- ------------------------------------------------------------------------- --->
-<!--- ------------- LEFT OFF HERE --------------------------------------------- --->
-<!--- ------------------------------------------------------------------------- --->
+When polyandry and post-copulatory inbreeding strategy allele values were fixed for adaptive inbreeding avoidance, pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}$ values became increasingly negative; Figure 4A).
+Such evolution still occurred, but to a much smaller degree, when pre-copulatory inbreeding avoidance was costly (Figure 4B).
+However, after $40000$ generations, $M_{a}$ values were less negative when post-copulatory inbreeding avoidance and polyandry were fixed at non-zero values than when they also evolved from initial values of zero (e.g., compare the blue lines in Figures 4A versus Figure 1A).
 
-When pre-copulatory inbreeding strategy was initialised for random mating, but polyandry and post-copulatory inbreeding strategy allele values were fixed for adaptive inbreeding avoidance (Figure 4A,B), negative pre-copulatory inbreeding allele values became increasingly more frequent ($M_{a}<0$), causing inbreeding avoidance in mate choice.
-However, $M_{a}$ values were not as negative after $40000$ generations when post-copulatory inbreeding avoidance and polyandry were fixed as they were when no post-copulatory inbreeding avoidance occurred (e.g., compare Figure 4A with Figure 1A, and Figure 4B with Figure 2A).
-When post-copulatory inbreeding strategy was initialised for random fertilisation, existence of an already adaptive strategy of pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance (Figure 4C,D).
-Mean allele values affecting polyandry consistently decreased over generations regardless of the cost of post-copulatory inbreeding strategy, $c_{F}$.
-Consequently, when $c_{F}=0$, post-copulatory inbreeding strategy allele values had no effect because females were consistently monandrous, resulting in high drift of $F_{a}$ values among replicates (Figure 4C).
+When pre-copulatory inbreeding strategy values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently trend toward negative values (Figure 4C,D).
+Additionally, mean $P_{a}$ allele values consistently decreased over generations regardless of the cost of post-copulatory inbreeding strategy (Figure 4C,D).
+Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values among replicates (illustrated by wide standard errors, Figure 4C).
 However, when $c_{F}=0.02$, $F_{a}$ values remained near zero to minimise direct costs.
 This lack of evolution of post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
-When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), post-copulatory inbreeding strategy evolved to similarly negative mean allele values as pre-copulatory inbreeding strategy did in Figure 4A,B (see Supporting Information).
+When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information).
 

### 2016-11-01 ms_pre_post.Rmd
Once all the way through this draft, but a lot more needs to be done.

@@
 
-<!--- ------------------------------------------------------------------------- --->
-<!--- ------------- LEFT OFF HERE --------------------------------------------- --->
-<!--- ------------------------------------------------------------------------- --->
+<!--- ‘Hypothesis that polyandry and pre- and post-cop IA might co-evolve.
+However no theory tests these hypotheses or predicts circumstances under which different strategies of pre- and/or post-cop IA might arise and hence drive polyandry evolution, impeding rationalization of empirical observations...
+--->
 
-We have provided a novel framework for approaching empirical studies of inbreeding avoidance, predicting evolution of polyandry and inbreeding avoidance through pre-copulatoryand post-copulatory mechanisms.
-Accordingly, we modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency to engage in polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
-Using *in silico* experiments, we tested three specific hypothesis to predict evolution of polyandry, and pre-copulatoryand post-copulatory inbreeding strategy.
+<!--- Theory cannot test hypotheses -- I don't think this is how theory works (or how hypotheses work), and it runs the risk of confusing people, or worse.
+Furthermore, I don't see how what we've done here could help 'rationalise' empirical observations (or if this is even desirable).
+Hence, I'm not really sure I understand the suggested change to the first sentence.
+I've tried to adjust things to make a bit broader, but I think it's very important that we get the science and clear and accurate as possible in the first sentence.
+--->
+
+We have used *in silico* experiments to test three key hypotheses concerning evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
+The modelling that we develop provides a novel framework for approaching empirical studies of inbreeding avoidance, predicting evolution of polyandry and inbreeding avoidance through pre-copulatoryand post-copulatory mechanisms.
+Accordingly, we modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
+
+<!--- Using *in silico* experiments, we tested three specific hypothesis to predict evolution of polyandry, and pre-copulatoryand post-copulatory inbreeding strategy.
 We found that (1) selection for polyandry was greatly strengthened given concurrent evolution of post-copulatory inbreeding avoidance, (2) selection for costly pre-copulatoryor post-copulatory inbreeding avoidance was negligible given evolution of a less costly strategy of inbreeding avoidance, and (3) pre-existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance, but not vice versa.
+--->
 
 The opportunity to adjust inbreeding has been widely considered as a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
-Recently, @Duthie found the conditions under which selection for polyandry and pre-copulatory inbreeding avoidance is predicted to be highly restrictive, requiring strong constraints on the availability of initial compared to additional mates, or the conditional expression of polyandry such that females only engaged in polyandry when their initial choice of mate was of low quality.
+Recently, @Duthie found the conditions under which selection for polyandry and pre-copulatory inbreeding avoidance is predicted to be highly restrictive.
 However, @Duthie assumed that fertilisation of offspring was unbiased with respect to mate kinship, meaning that females could not express post-copulatory choice.
@@
 @Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015].
-For example, @Pizzari2004 found that the number of sperm arriving to eggs is lower for full siblings of female red jungefowl (*Gallus gallus*) than it is for non-relatives, even after controlling for effects of order of oviposition and social familiarity.
-Similarly, Firman and Simmons [-@Firman2008; -@Firman2015] have shown evidence of post-copulatory inbreeding avoidance in house mice, finding fertilisation to be biased toward unrelated males independent of the order in which mating occurs [@Firman2008], perhaps due to post-copulatory mechanisms expressed through the secretion of gametic proteins originating in female's eggs [@Firman2015].
-Interestingly, female house mice have also been shown to express pre-copulatory inbreeding avoidance  [@Potts1991; @Roberts2003].
+For example, the number of sperm arriving to eggs is lower for full siblings of female red jungefowl (*Gallus gallus*) than it is for non-relatives, even after controlling for effects of order of oviposition and social familiarity [@Pizzari2004].
+Similarly, in house mice, fertilisation was biased toward unrelated males independent of mating order, perhaps due to post-copulatory mechanisms expressed through the secretion of gametic proteins originating in eggs [@Firman2008; @Firman2015].
+Interestingly, female house mice also show pre-copulatory inbreeding avoidance  [@Potts1991; @Roberts2003].
 Our results suggest that post-copulatory inbreeding avoidance is unlikely to evolve when females can already avoid inbreeding through pre-copulatory mechanisms (Figure 4), meaning that evolution of post-copulatory inbreeding avoidance could reasonably be hypothesised to have preceded evolution of pre-copulatory inbreeding avoidance in mice.
 
-Specific mechanisms of post-copulatory inbreeding avoidance are difficult to identify, but recent experimental studies have shown how females can successfully bias fertilisation after mating has occurred in both vertebrates [e.g., @Gasparini2011] and invertebrates [e.g., @Tuni2013].
-For example, @Gasparini2011 artificially inseminated female guppies (*Poecilia reticulata*) with equal quantities of sperm from full-siblings and unrelated males, finding that fertilisation success was higher in non-relatives because the velocity of full siblings' sperm was reduced by females' ovarian fluids.
-Biased fertilisation toward non-relatives might also be accomplished through selective storage of sperm.
-For example, in black field crickets (*Teleogryllus commodus*), females attempt to remove the spermataphores of unwanted male mates after copulation, while male mates guard females to prevent spermatophore removal [@Bussiere2006].
-Even if females are unable to remove spermatophores of unwanted mates, @Tuni2013 found that female *T.
-commodus* are capable of controlling the transfer of sperm to their spermatheca, most likely through physical control of the spermathecal duct, and can reduce sperm storage despite being guarded by a related male.
+<!--- ------------------------------------------------------------------------- --->
+<!--- ------------- LEFT OFF HERE --------------------------------------------- --->
+<!--- ------------------------------------------------------------------------- --->
+
+<!--- Similar comment to above - I’m finding the structure of this paragraph a bit backwards.
+Might it be more helpful to give the conclusion drawn from our model and then explain how it fits with existing empirical studies?
+At the moment I read the stuff about the empirical studies without having any idea how it was going to be linked into our results – so then I had to go back and read it again once you’d told me the link at the end.
+I’m still not quite sure I get it, or why we need so much detail on mechanisms?
+Also, I think the writing could be greatly shortened here - could probably say more or less the same thing in half the words.
+I’ve done some editing to illustrate this - but I doubt this’ll be a definitive version because I can’t really see where this para is going.
+-->
+
+Recent studies have shown how females can successfully bias fertilisation after mating has occurred.
+For example, when female guppies (*Poecilia reticulata*) were artificially inseminated with equal quantities of sperm from full-siblings and unrelated males, more eggs were fertilised by unrealted males because the veolcities of full siblings' sperm were reduced by females' ovarian fluids [@Gasparini2011].
+In black field crickets (*Teleogryllus commodus*), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs [@Bussiere2006; @Tuni2013].
 Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for further polyandry, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
 
-In our model, a cost free inbreeding strategy precluded a more costly complementary inbreeding strategy from persisting in a focal population (Figure 2), meaning that long-term persistence of both pre-copulatoryand post-copulatory inbreeding avoidance might not be expected in populations given cost asymmetry.
+<!--- Regarding last sentence: ''OK this is a much better opening to this section – states the key result from our model and then goes on the develop/consider the implications.
+Could you use the same kind of structure for the previous sections?'' --->
+
+In our model, one cost free inbreeding strategy precluded another more costly inbreeding strategy from persisting in a focal population (Figure 2), meaning that long-term persistence of both pre-copulatoryand post-copulatory inbreeding avoidance might not be expected in populations given cost asymmetry.
 Direct costs therefore strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies.
@@
 
-![Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre-copulatoryand post-copulatory inbreeding avoidance.
-Costs of polyandry increase with rows from top to bottom.
-Dotted horizontal black lines in panels show values of zero on the y-axis.](figures/poly_costs.png)
+![Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fiext to zero (i.e., random fertilisation) or (B, D, F, H) allowed to evolve freeely.
+Costs of polyandry (c_p) increase across rows from zero (A and B) to 0.01 (G and H).
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values indicate inbreeding avoidance or tendency for monandry, and positive values indicate inbreeding preference or tendency for polyandry.
+Dotted lines demarcate mean allele values of zero.](figures/poly_costs.png)
 
-![Relationship between polyandry allele values and phenotypes for an individual-based model in which pre-copulatoryand post-copulatory inbreeding strategies evolve jointly with polyandry.
-Two simulations with identical starting conditions (default parameter values with no costs) are shown in panels A,B and C,D.
-Red lines in (A) and (C) show mean value of alleles underlying polyandry for a single replicate simulation over 40000 generations.
-Positive allele values contribute to polyandry, while negative values contribute to monandry (dotted line shows zero on the y-axis).
-In the last generation, mean allele value was below (A) or above (C) zero.
-Nevertheless, due to among-individual variation and the threshold nature of the polyandry phenotype, polyandry persists in the population in (A) and monandry persists in (C).
-The histograms in (B) and (D) show females' tendency for polyandry phenotypes in the last generation; white and grey shading indicates monandrous and polyandrous females, respectively.](figures/Pp_vals.png)
+![Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs.
+Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations.
+Positive and negative allele values contribute to polyandry and monandry, respectively.
+In the final generation, mean allele value was below (A) or above (C) zero (demarcated by the dotted line).
+Nevertheless, due to the threshold nature of expression of the polygenic polyandry phenotype, polyandry and monandry are expressed in both populations.
+Histograms in (B) and (D) show females' tendency for polyandry phenotypes in the final generation; white and grey shading indicates monandrous and polyandrous females, respectively.](figures/Pp_vals.png)
 
-![Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panel (A) shows evolution of costly pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy is fixed for random fertilisation (solid black horizontal line), while (B) instead allows post-copulatory inbreeding strategy to evolve under otherwise identical conditions.
-Similarly, panel (C) shows evolution of costly post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for random mating (solid blue horizontal line), while (D) allows pre-copulatory inbreeding strategy to evolve under otherwise identical conditions.](figures/rel_costs.png)
+![Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy can evolve and pre-copulatory inbreeding strategy is (A) fixed for random mating or (B) can also evolve.
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.](figures/rel_costs.png)
 
-![Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panel (A) shows evolution of pre-copulatory inbreeding strategy given fixed polyandry (solid red line) and inbreeding avoidance (solid black line), and (B) shows these same conditions given a cost of pre-copulatory inbreeding strategy.
-Similarly, panel (C) shows evolution of polyandry and post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for inbreeding avoidance (solid blue line), while (D) shows these same conditions given a cost of post-copulatory inbreeding strategy.](figures/fixed_adapt.png)
+![Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is (A and C) cost-free or (B and D) costly.
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.](figures/fixed_adapt.png)
 

### 2016-11-01 ms_pre_post.Rmd
Minor changes responding to coauthor comments; add more coauthors who will, I hope, agree to be on this paper

@@
 title: "Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry"
-author: "A. Bradley Duthie et al."
+author: "A. Bradley Duthie, Greta Bocedi, Ryan Germain, Matthew E. Wolak, and Jane M. Reid"
 date: "August 24, 2016"
@@
 
-Inbreeding avoidance has been widely observed through pre-copulatory and post-copulatory mechanisms as a consequence of inbreeding depression in offspring viability.
-However, no conceptual framework compares evolution of pre-copulatory and post-copulatory inbreeding avoidance jointly, and given biologically relevant costs of inbreeding strategies.
+Inbreeding avoidance has been widely hypothesised to evolve through pre-copulatory and post-copulatory mechanisms as a consequence of inbreeding depression in offspring viability.
+However, no modelling compares evolution of pre-copulatory and post-copulatory inbreeding avoidance jointly, and given biologically relevant costs of inbreeding strategies.
 Critically, evolution of post-copulatory inbreeding avoidance is restricted to females that mate multiply, potentially leading to complex evolutionary dynamics among inbreeding strategies and polyandry.
-Accordingly, we use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address three questions: Will evolution of post-copulatory inbreeding avoidance strengthen selection for polyandry?
-Will selection for a costly inbreeding strategy be negligible given a non-costly alternative strategy?
-And will selection for an inbreeding strategy be negligible given existence of an already adaptive alternative strategy?
-We show that selection for polyandry is greatly strengthened by post-copulatory inbreeding avoidance.
-Strong selection for relatively low cost inbreeding avoidance strategies was observed, while selection for functionally redundant high cost strategies decreased over generations.
+Accordingly, we use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address three questions: Does evolution of post-copulatory inbreeding avoidance facilitate evolution of costly polyandry?
+Is evolution of one costly inbreeding strategy inhibited by another non-costly alternative strategy?
+And is evolution of one inbreeding strategy precluded by existence of another already adaptive strategy.
+We show that evolution of polyandry is facilitated by post-copulatory inbreeding avoidance.
+Evolution of relatively low cost inbreeding avoidance strategies was observed, while selection for functionally redundant high cost strategies decreased over generations.
 Finally, existence of an adaptive inbreeding strategy precluded evolution of post-copulatory, but not pre-copulatory, inbreeding avoidance.
@@
 
+<!--- What is 'quantitative theory'?
+I don't think that I understand what the implied knowledge gap is here, actually.
+We set up an empirical system to test some interesting hypotheses; I suppose that the knowledge gap is whether or not those specific hypotheses are supported given the parameters we model.
+The hypothesis testing sort of relates to the brief verbal theory that we mention in the introduction, but this manuscript does not address any theoretical knowledge gap using modelling.
+I don't think this is an esoteric issue; we have to make it clear that we know what we're doing and why we're doing it.
+--->
+
 Meanwhile, empirical studies of diverse species have found evidence for female inbreeding avoidance enacted through pre-copulatory or post-copulatory routes, or both.
@@
 These empirical studies demonstrate that diverse combinations of pre-copulatoryand post-copulatory inbreeding avoidance occur in nature.
-However, there is as yet no conceptual framework that predicts *a priori* what combinations should be favoured by selection when both pre-copulatoryand post-copulatory inbreeding avoidance, and polyandry can evolve.
-Such a framework would allow prediction of the form of mating system evolution across different systems that experience inbreeding depression and allow existing empirical studies to be used to test evolutionary predictions through comparative analyses.
+However, there is as yet no modelling framework that predicts *a priori* what combinations should be favoured by selection when both pre-copulatory and post-copulatory inbreeding avoidance, and polyandry can evolve.
+Such a framework would allow prediction of the form of mating system evolution across different systems that experience inbreeding depression and allow existing empirical studies to be compared to model predictions.
 
-<!--- The terminal sentence is non-sensical.
-It confuses what theory actually is and suggests a post-hoc testing of a model through already existing data -- what does *prediction* even mean in this context !?
-This is bad science.
---->
+<!--- I'm sorry, I didn't understand the suggested terminal sentence or the accompanying comment.
+I'm not sure I'm clear on what we're considering a prediction versus what we're considering a test of prediction, or what 'underlying understanding' refers to in the context of the key hypotheses and where the come from.
+''Maybe end on something like this, to emphasise the value of having such a framework (which I think comes both through prediction and through testing predictions and hence underlying understanding?).
+I expect you’ll want to edit though'' --->
 
@@
 
+<!--- I am happy to switch back to using statements as titles instead of questions --->
+
 Does evolution of post-copulatory inbreeding avoidance facilitate evolution of costly polyandry?
@@
 
-Will selection for a costly inbreeding strategy be negligible given a non-costly alternative strategy?
+Is evolution of one costly inbreeding strategy inhibited by another non-costly alternative strategy?
 ----------------------------------------------
@@
 However, when $M_{a}$ values could also evolve and $P_{a}$ values were negative, grand mean $F_{a}$ value in the last $10000$ generations was only $-0.070$ (Figure 3D).
+Evolution of post-copulatory inbreeding avoidance faciliated evolution of polyandry (Figure 3B,C), while monandry evolved in the absence of post-copulatory inbreeding avoidance (Figure 3A,D; polyandry was cost free in all these simulations).
 Overall, evolution of a costly inbreeding strategy that readily evolved in isolation was greatly impeded by evolution of a less costly strategy.
 
-<!--- Co-author wants to talk about polyandry and stuff: ''But these figures don’t look very symmetrical – there’s stuff going on in Fig 3 that isn't really noted in the text – should we do a bit more with this?
-The most obvious difference is that polyandry evolves in B but not D - i.e.
-when pre-cop IA is costly but not when post-cop IA is costly.
-Wouldn’t it be helpful to point this out and explain it?
-NB, presumably polyandry is cost-free in all these simulations?
-Might it be worth re-iterating that too?'' --->
-
-Will selection for a costly inbreeding strategy be negligible given existence of an already adaptive alternative strategy?
+Is evolution of one inbreeding strategy precluded by existence of another already adaptive strategy
 ----------------------------------------------
@@
 Our results suggest that post-copulatory inbreeding avoidance is unlikely to evolve when females can already avoid inbreeding through pre-copulatory mechanisms (Figure 4), meaning that evolution of post-copulatory inbreeding avoidance could reasonably be hypothesised to have preceded evolution of pre-copulatory inbreeding avoidance in mice.
-
-<!--- ------------------------------------------------------------------------- --->
-<!--- ------------- LEFT OFF HERE --------------------------------------------- --->
-<!--- ------------------------------------------------------------------------- --->
 

### 2016-11-01 ms_pre_post.Rmd
Remove some of the empirical/theory language from the manuscript; this really needs to be written as an empirical paper, and hence one result of many across taxa

@@
 Critically, evolution of post-copulatory inbreeding avoidance is restricted to females that mate multiply, potentially leading to complex evolutionary dynamics among inbreeding strategies and polyandry.
-Accordingly, we use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address three questions: Does evolution of post-copulatory inbreeding avoidance facilitate evolution of costly polyandry?
-Is evolution of one costly inbreeding strategy inhibited by another non-costly alternative strategy?
-And is evolution of one inbreeding strategy precluded by existence of another already adaptive strategy.
+Accordingly, we use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address three questions: (1) Does evolution of post-copulatory inbreeding avoidance facilitate evolution of costly polyandry?
+(2) Is evolution of one costly inbreeding strategy inhibited by another non-costly alternative strategy?
+And (3) is evolution of one inbreeding strategy precluded by existence of another already adaptive strategy?
 We show that evolution of polyandry is facilitated by post-copulatory inbreeding avoidance.
@@
 Finally, existence of an adaptive inbreeding strategy precluded evolution of post-copulatory, but not pre-copulatory, inbreeding avoidance.
-Our model thereby introduces a novel framework for predicting evolution of both pre-copulatory and post-copulatory inbreeding strategies in empirical systems.
+Our model thereby introduces a novel framework for predicting evolution of both pre-copulatory and post-copulatory inbreeding strategies in biological systems.
 
@@
 
+<!--- I have removed 'mate' in front of 'choice' and replaced it with 'reproductive decisions' in the second sentence because post-copulatory inbreeding avoidance isn't an expression of mate choice; mating has already happened at this point; females are choosing paternity among the mates that they already chose --->
+
 Inbreeding often greatly reduces the fitness of inbred offspring [termed 'inbreeding depression'; @Charlesworth1999; @Keller2002; @Charlesworth2009].
-Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple forms of mate choice in species with obligate biparental reproduction [@Parker1979; @Parker2006; @Pusey1996; @Szulkin2012].
+Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple reproductive decisions in species with obligate biparental reproduction [@Parker1979; @Parker2006; @Pusey1996; @Szulkin2012].
 From the perspective of a focal breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred, meaning that related males are less likely to sire offspring (i.e., post-copulatory inbreeding avoidance).
@@
 
-Meanwhile, empirical studies of diverse species have found evidence for female inbreeding avoidance enacted through pre-copulatory or post-copulatory routes, or both.
+Meanwhile, evidence for female inbreeding avoidance enacted through pre-copulatory or post-copulatory routes, or both, has been found across diverse taxa.
 For example, pre-copulatory inbreeding avoidance has been documented in weevils, birds, and butterflies [e.g., @Kuriwada2011; @Kingma2013; @Fischer2015], and post-copulatory inbreeding avoidance has been documented in crickets [e.g., @Simmons2006; @Bretman2009].
 Evidence of both pre-copulatory and post-copulatory inbreeding avoidance has accumulated for some well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015].
-While most studies consider either pre-copulatoryor post-copulatory inbreeding avoidance in isolation, a small number of studies consider both.
+While most studies consider either pre-copulatory or post-copulatory inbreeding avoidance in isolation, a small number of studies consider both.
 Accordingly, @Liu2014 found evidence of pre-copulatory, but not post-copulatory, inbreeding avoidance in cabbage beetles (*Colaphellus bowringi*).
-Other studies found no evidence of pre-copulatoryor post-copulatory inbreeding avoidane despite strong inbreeding depression [e.g., @Reid2014; @Reid2015].
-These empirical studies demonstrate that diverse combinations of pre-copulatoryand post-copulatory inbreeding avoidance occur in nature.
-However, there is as yet no modelling framework that predicts *a priori* what combinations should be favoured by selection when both pre-copulatory and post-copulatory inbreeding avoidance, and polyandry can evolve.
-Such a framework would allow prediction of the form of mating system evolution across different systems that experience inbreeding depression and allow existing empirical studies to be compared to model predictions.
+Other studies found no evidence of pre-copulatory or post-copulatory inbreeding avoidance despite strong inbreeding depression [e.g., @Reid2014; @Reid2015].
+These studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature.
+However, there is as yet no modelling framework that predicts *a priori* what combinations should be favoured by selection when both pre-copulatory and post-copulatory inbreeding avoidance, and polyandry, can evolve.
+Such a framework would allow prediction of the form of mating system evolution across different systems that experience inbreeding depression and allow existing studies to be compared to model predictions.
 
@@
 A recent genetically-explicit individual-based model showed that selection for alleles underlying polyandry and pre-copulatory inbreeding avoidance, and resulting joint evolution of these reproductive strategies, occurred only under highly constrained conditions [@Duthie].
-Specifically, such evolution occurred when direct costs of polyandry were small, when very fewe males were available for a female's initial mate choice but many were available for additional mate choice(s), or when polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
+Specifically, such evolution occurred when direct costs of polyandry were small, when very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or when polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
 In the absence of these conditions, increasing degrees of polyandry tended to increase the overall degree of inbreeding that females experienced, and hence increase inbreeding depression in offspring fitness.
@@
 Therefore, while pre-copulatory inbreeding avoidance can facilitate evolution of polyandry under some restrictive conditions [@Duthie], the opportunity for post-copulatory choice might facilitate evolution of polyandry under a much wider range of conditions by allowing females to bias fertilisation toward non-kin.
-The long-term evolutionary dynamics of pre-copulatoryand post-copulatory inbreeding avoidance then become unclear.
-Strong inbreeding depression might drive initial evolution of both pre-copulatoryand post-copulatory inbreeding avoidance and associated polyandry.
+The long-term evolutionary dynamics of pre-copulatory and post-copulatory inbreeding avoidance then become unclear.
+Strong inbreeding depression might drive initial evolution of both pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
 However, if evolution of polyandry and post-copulatory inbreeding avoidance renders pre-copulatory inbreeding avoidance redundant, or vice versa, then only one strategy might be maintained in the long-term.
@@
 Such models thereby isolate the invasion fitness of this single strategy.
-However, when both pre-copulatoryand post-copulatory strategies can affect realised inbreeding, it cannot be assumed that both strategies will invade simultaneously, nor that invasion fitness of one strategy will be independent of the other For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect of such invading alleles could be weak or negligible.
+However, when both pre-copulatory and post-copulatory strategies can affect realised inbreeding, it cannot be assumed that both strategies will invade simultaneously, nor that invasion fitness of one strategy will be independent of the other For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect of such invading alleles could be weak or negligible.
 
-Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatoryand post-copulatory inbreeding avoidance and polyandry are likely to be affected by direct negative selection on resulting phenotypes (i.e., costs) and hence on the net costs versus benefits stemming from inbreeding avoidance.
+Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry are likely to be affected by direct negative selection on resulting phenotypes (i.e., costs) and hence on the net costs versus benefits stemming from inbreeding avoidance.
 Polyandrous females can pay costs of mate searching or mating, for example, because these activities increase predation risk [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
@@
 Females that express post-copulatory choice might pay an energetic cost associated with physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
-If the relative costs affecting pre-copulatoryand post-copulatory inbreeding avoidance differ, then alleles underlying the less costly inbreeding strategy might become fixed in the population over generations, while alleles underlying the more costly inbreeding strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
+If the relative costs affecting pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly inbreeding strategy might become fixed in the population over generations, while alleles underlying the more costly inbreeding strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
 
@@
 Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution such that only the less costly inbreeding avoidance strategy will be expressed in the long term.
-Finally, we test the hypothesis that evolution of one inbreeding avoidance strategy (i.e., pre-copulatoryor post-copulatory) will be precluded if it is introduced into a population that is already fixed for the other inbreeding avoidance strategy that is adaptive.
+Finally, we test the hypothesis that evolution of one inbreeding avoidance strategy (i.e., pre-copulatory or post-copulatory) will be precluded if it is introduced into a population that is already fixed for the other inbreeding avoidance strategy that is adaptive.
 We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across different reproductive systems.
@@
 We have used *in silico* experiments to test three key hypotheses concerning evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
-The modelling that we develop provides a novel framework for approaching empirical studies of inbreeding avoidance, predicting evolution of polyandry and inbreeding avoidance through pre-copulatoryand post-copulatory mechanisms.
+The modelling that we develop provides a novel framework for approaching questions concerning inbreeding avoidance, and for predicting evolution of polyandry and inbreeding avoidance through pre-copulatory and post-copulatory mechanisms.
 Accordingly, we modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
 
-<!--- Using *in silico* experiments, we tested three specific hypothesis to predict evolution of polyandry, and pre-copulatoryand post-copulatory inbreeding strategy.
-We found that (1) selection for polyandry was greatly strengthened given concurrent evolution of post-copulatory inbreeding avoidance, (2) selection for costly pre-copulatoryor post-copulatory inbreeding avoidance was negligible given evolution of a less costly strategy of inbreeding avoidance, and (3) pre-existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance, but not vice versa.
+<!--- Using *in silico* experiments, we tested three specific hypothesis to predict evolution of polyandry, and pre-copulatory and post-copulatory inbreeding strategy.
+We found that (1) selection for polyandry was greatly strengthened given concurrent evolution of post-copulatory inbreeding avoidance, (2) selection for costly pre-copulatory or post-copulatory inbreeding avoidance was negligible given evolution of a less costly strategy of inbreeding avoidance, and (3) pre-existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance, but not vice versa.
 --->
@@
 The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but the existence of selection for post-copulatory inbreeding avoidance causing feedback to select for polyandry has not been formally modelled.
-Our model therefore has widespread implications for empirical studies of evolution of polyandry.
+Our model therefore has widespread implications for understanding evolution of polyandry.
 
@@
 
-In our model, one cost free inbreeding strategy precluded another more costly inbreeding strategy from persisting in a focal population (Figure 2), meaning that long-term persistence of both pre-copulatoryand post-copulatory inbreeding avoidance might not be expected in populations given cost asymmetry.
+In our model, one cost free inbreeding strategy precluded another more costly inbreeding strategy from persisting in a focal population (Figure 2), meaning that long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given cost asymmetry.
 Direct costs therefore strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies.

### 2016-11-02 ms_pre_post.Rmd
Make minor tweaks to the text, especially concerning the framing as an empirical paper, not a theory paper; fix spelling errors in multiple places.

@@
 Finally, existence of an adaptive inbreeding strategy precluded evolution of post-copulatory, but not pre-copulatory, inbreeding avoidance.
-Our model thereby introduces a novel framework for predicting evolution of both pre-copulatory and post-copulatory inbreeding strategies in biological systems.
+Our model thereby introduces a novel framework for understanding evolution of both pre-copulatory and post-copulatory inbreeding strategies in biological systems.
 
@@
 Further, such polyandry could itself evolve because it allows females to mate with additional unrelated males following initial mating with a relative, thereby facilitating pre-copulatory inbreeding avoidance even in the absence of any post-copulatory female choice or otherwise biased fertilisation (e.g., given a 'fair raffle' among sperm provided by feamles' mates).
-As a reproductive strategy, polyandry can thereby simultaneously allow females to mate with less closely related males and creates the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
+As a reproductive strategy, polyandry can thereby simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
 Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007].
@@
 I don't think that I understand what the implied knowledge gap is here, actually.
-We set up an empirical system to test some interesting hypotheses; I suppose that the knowledge gap is whether or not those specific hypotheses are supported given the parameters we model.
+We set up an empirical system to test some interesting hypotheses; I suppose that the knowledge gap is whether or not those specific hypotheses are supported given the parameters we model?
 The hypothesis testing sort of relates to the brief verbal theory that we mention in the introduction, but this manuscript does not address any theoretical knowledge gap using modelling.
 I don't think this is an esoteric issue; we have to make it clear that we know what we're doing and why we're doing it.
+Hence, I think that we need to be clear that we are addressing an empirical knowledge gap derived from verbal theory -- or reframe the key questions.
 --->
@@
 These studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature.
-However, there is as yet no modelling framework that predicts *a priori* what combinations should be favoured by selection when both pre-copulatory and post-copulatory inbreeding avoidance, and polyandry, can evolve.
-Such a framework would allow prediction of the form of mating system evolution across different systems that experience inbreeding depression and allow existing studies to be compared to model predictions.
+However, there is as yet no clear understanding of what combinations should be favoured by selection when both pre-copulatory and post-copulatory inbreeding avoidance, and polyandry, can evolve.
+Empirical hypothesis testing using computer simulation models can address key questions concerning mating system evolution across different systems that experience inbreeding depression, and can allow existing studies to be compared to model outcomes.
 
@@
 Previous models implicitly or explicitly considered the fate of a rare allele underlying pre-copulatory inbreeding avoidance in a population initially fixed for random mating [e.g., @Parker1979; @Parker2006; @Duthie; @Duthie2016a].
-Such models thereby isolate the invasion fitness of this single strategy.
-However, when both pre-copulatory and post-copulatory strategies can affect realised inbreeding, it cannot be assumed that both strategies will invade simultaneously, nor that invasion fitness of one strategy will be independent of the other For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect of such invading alleles could be weak or negligible.
+Such models thereby isolated the invasion fitness of this single strategy.
+However, when both pre-copulatory and post-copulatory strategies can affect realised inbreeding, it cannot be assumed that both strategies will invade simultaneously, nor that invasion fitness of one strategy will be independent of the other.
+For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect of such invading alleles could be weak or negligible.
 
@@
 Finally, we test the hypothesis that evolution of one inbreeding avoidance strategy (i.e., pre-copulatory or post-copulatory) will be precluded if it is introduced into a population that is already fixed for the other inbreeding avoidance strategy that is adaptive.
-We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across different reproductive systems.
+We thereby provide a framework for understanding evolution of pre-copulatory and post-copulatory inbreeding avoidance across different reproductive systems.
 
@@
 In overview, each generation proceeds with females paying costs, expressing polyandry, mating, and fertilisation.
-Offspring inherit a randomly sampled allele from each parent at each locas with no physical linkage.
+Offspring inherit a randomly sampled allele from each parent at each locus with no physical linkage.
 Alleles can then mutate and offspring express inbreeding depression.
@@
 Phenotypic values for tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$) each have costs that are assumed to independently increase the probability that a focal female will die before mating.
-The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, repectively.
-Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
+The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
+Here, $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
 Absolute values are used for applying costs to inbreeding strategies as appropriate because both negative and positive $M_{p}$ and $F_{p}$ values affect the degree of inbreeding.
@@
 After costs are paid, each remaining female chooses $N_{males}$ males to mate with, where $N_{males}$ is calculated by sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
-This ensures that all surviving females choose at least one mate, and causes some stochastic variation aroudn the expected mean $N_{males}$ of $P_{p}+1$.
+This ensures that all surviving females choose at least one mate, and causes some stochastic variation around the expected mean $N_{males}$ of $P_{p}+1$.
 A female's value of $P_{p}$ depends on the sum of her 20 $P_{a}$ allele values, which might be negative or positive.
@@
 Most often, $N_{males}$ will be smaller than the total number of available males [@Duthie].
-Here, each female chooses her $N_{males}$ mates based on her pre-copulatory inbreeding strategy phenotype ($M_{p}$), which equals her pre-copulatory inbreeding strategy genotype ($M_{g}$) defined as the sum of the values of her 20 $M_{a}$ alleles.
+Here, each female chooses her $N_{males}$ mates based on her pre-copulatory inbreeding strategy phenotype ($M_{p}$), which equals her pre-copulatory inbreeding strategy genotype ($M_{g}$), defined as the sum of the values of her 20 $M_{a}$ alleles.
 Negative or positive $M_{p}$ values cause a female to avoid or prefer mating with kin, respectively.
@@
 Equation 1 assumes independent allelic effects, generating multiplicative effects on offspring viability [@Morton1956; @Mills1994].
-We model inbreeding depression as having an absolute rather than relative effect on offspring viability )i.e., hard rather than sof selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
+We model inbreeding depression as having an absolute rather than relative effect on offspring viability ) i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
 We also assume that inbreeding always decreases offspring viability, $\beta > 0$ (i.e., no outbreeding depression).
@@
 Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry.
-However, $P_{a}$ values were expeted to be positive only given a low cost of polyandry ($c_{P} < 0.005$, Figure 1A,B).
+However, $P_{a}$ values were expected to be positive only given a low cost of polyandry ($c_{P} < 0.005$, Figure 1A,B).
 This implies that, even given strong inbreeding depression in offspring viability, inbreeding avoidance might generally be a weak force driving polyandry evolution.
 
-Strong post-copulatory inbreeding avoidance consistently evolved in all simulations where such such evolution was allowed (Figure 1B,D,F,H), even when $P_{a}$ values were expected to be slightly negative (i.e., when there is selection against polyandry, Figure 1F,H).
+Strong post-copulatory inbreeding avoidance consistently evolved in all simulations where such evolution was allowed (Figure 1B,D,F,H), even when $P_{a}$ values were expected to be slightly negative (i.e., when there is selection against polyandry, Figure 1F,H).
 This reflects the threshold nature of phenotypic expression of polygenic polyandry, wherein random sampling of alleles means that polyandry is commonly expressed (i.e., $P_{g}>0$) even when mean $P_{a}$ values are negative (Figure 2).
@@
 However, when $M_{a}$ values could also evolve and $P_{a}$ values were negative, grand mean $F_{a}$ value in the last $10000$ generations was only $-0.070$ (Figure 3D).
-Evolution of post-copulatory inbreeding avoidance faciliated evolution of polyandry (Figure 3B,C), while monandry evolved in the absence of post-copulatory inbreeding avoidance (Figure 3A,D; polyandry was cost free in all these simulations).
+Evolution of post-copulatory inbreeding avoidance facilitated evolution of polyandry (Figure 3B,C), while monandry evolved in the absence of post-copulatory inbreeding avoidance (Figure 3A,D; polyandry was cost free in all these simulations).
 Overall, evolution of a costly inbreeding strategy that readily evolved in isolation was greatly impeded by evolution of a less costly strategy.
@@
 We have used *in silico* experiments to test three key hypotheses concerning evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
-The modelling that we develop provides a novel framework for approaching questions concerning inbreeding avoidance, and for predicting evolution of polyandry and inbreeding avoidance through pre-copulatory and post-copulatory mechanisms.
+The modelling that we develop provides a novel framework for approaching complex questions concerning inbreeding avoidance, and for predicting evolution of polyandry and inbreeding avoidance through pre-copulatory and post-copulatory mechanisms.
 Accordingly, we modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
@@
 
-We predict evolution of polyandry in populations where inbreeding depression is severe and evolution of inbreeding avoidance through post-copulatory mechanisms is not constrained.
-Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa [e.g.
+We observed evolution of polyandry in populations where inbreeding depression was severe and evolution of inbreeding avoidance through post-copulatory mechanisms was not constrained.
+Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions across diverse taxa [e.g.
 @Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015].
@@
 Interestingly, female house mice also show pre-copulatory inbreeding avoidance  [@Potts1991; @Roberts2003].
-Our results suggest that post-copulatory inbreeding avoidance is unlikely to evolve when females can already avoid inbreeding through pre-copulatory mechanisms (Figure 4), meaning that evolution of post-copulatory inbreeding avoidance could reasonably be hypothesised to have preceded evolution of pre-copulatory inbreeding avoidance in mice.
+Our results suggest that post-copulatory inbreeding avoidance is unlikely to evolve when females can already avoid inbreeding through pre-copulatory mechanisms (Figure 4), meaning that evolution of post-copulatory inbreeding avoidance might typically precede evolution of pre-copulatory inbreeding avoidance in mice.
 
@@
 Recent studies have shown how females can successfully bias fertilisation after mating has occurred.
-For example, when female guppies (*Poecilia reticulata*) were artificially inseminated with equal quantities of sperm from full-siblings and unrelated males, more eggs were fertilised by unrealted males because the veolcities of full siblings' sperm were reduced by females' ovarian fluids [@Gasparini2011].
+For example, when female guppies (*Poecilia reticulata*) were artificially inseminated with equal quantities of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full siblings' sperm were reduced by females' ovarian fluids [@Gasparini2011].
 In black field crickets (*Teleogryllus commodus*), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs [@Bussiere2006; @Tuni2013].

### 2016-11-02 ms_pre_post.Rmd
Minor tweaks

@@
 
-<!--- What is 'quantitative theory'?
-I don't think that I understand what the implied knowledge gap is here, actually.
+<!--- I don't think that I understand what the implied knowledge gap is here, actually.
 We set up an empirical system to test some interesting hypotheses; I suppose that the knowledge gap is whether or not those specific hypotheses are supported given the parameters we model?
@@
 
-<!--- ‘Hypothesis that polyandry and pre- and post-cop IA might co-evolve.
+<!--- 'Hypothesis that polyandry and pre- and post-cop IA might co-evolve.
 However no theory tests these hypotheses or predicts circumstances under which different strategies of pre- and/or post-cop IA might arise and hence drive polyandry evolution, impeding rationalization of empirical observations...

### 2016-11-02 ms_pre_post.Rmd
Add some titles to the Discussion, and start to reframe the current last paragraph and prepare for a concluding paragraph

--- 2016-11-01 ms_pre_post.Rmd
@@
 title: "Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry"
-author: "A. Bradley Duthie, Greta Bocedi, Ryan Germain, Matthew E. Wolak, and Jane M. Reid"
+author: "A. Bradley Duthie, Greta Bocedi, Ryan R. Germain, Matthew E. Wolak, and Jane M. Reid"
 date: "August 24, 2016"
@@
 Finally, existence of an adaptive inbreeding strategy precluded evolution of post-copulatory, but not pre-copulatory, inbreeding avoidance.
-Our model thereby introduces a novel framework for predicting evolution of both pre-copulatory and post-copulatory inbreeding strategies in biological systems.
+Our model thereby introduces a novel framework for predicting evolution of both pre-copulatory and post-copulatory inbreeding strategies in empirical systems.
 
@@
 
-Meanwhile, evidence for female inbreeding avoidance enacted through pre-copulatory or post-copulatory routes, or both, has been found across diverse taxa.
+Meanwhile, empirical studies of diverse species have found evidence for female inbreeding avoidance enacted through pre-copulatory or post-copulatory routes, or both.
 For example, pre-copulatory inbreeding avoidance has been documented in weevils, birds, and butterflies [e.g., @Kuriwada2011; @Kingma2013; @Fischer2015], and post-copulatory inbreeding avoidance has been documented in crickets [e.g., @Simmons2006; @Bretman2009].
@@
 Other studies found no evidence of pre-copulatory or post-copulatory inbreeding avoidance despite strong inbreeding depression [e.g., @Reid2014; @Reid2015].
-These studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature.
+These empirical studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature.
 However, there is as yet no modelling framework that predicts *a priori* what combinations should be favoured by selection when both pre-copulatory and post-copulatory inbreeding avoidance, and polyandry, can evolve.
-Such a framework would allow prediction of the form of mating system evolution across different systems that experience inbreeding depression and allow existing studies to be compared to model predictions.
+Such a framework would allow prediction of the form of mating system evolution across different systems that experience inbreeding depression and allow existing empirical studies to be compared to model predictions.
 
@@
 We have used *in silico* experiments to test three key hypotheses concerning evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
-The modelling that we develop provides a novel framework for approaching questions concerning inbreeding avoidance, and for predicting evolution of polyandry and inbreeding avoidance through pre-copulatory and post-copulatory mechanisms.
+The modelling that we develop provides a novel framework for approaching empirical studies of inbreeding avoidance, using simulations to address relevant knowledge gaps in understanding evolution of polyandry and inbreeding avoidance through pre-copulatory and post-copulatory mechanisms.
 Accordingly, we modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
@@
 
+Evolution of polyandry is facilitated by post-copulatory inbreeding avoidance
+-------------------------------------------------------------------
+
 The opportunity to adjust inbreeding has been widely considered as a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
@@
 The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but the existence of selection for post-copulatory inbreeding avoidance causing feedback to select for polyandry has not been formally modelled.
-Our model therefore has widespread implications for understanding evolution of polyandry.
+Our model therefore has widespread implications for empirical studies of evolution of polyandry.
 
@@
 Could you use the same kind of structure for the previous sections?'' --->
+
+Evolution of a costly inbreeding strategy is inhibited by a non-costly alternative strategy
+-------------------------------------------------------------------
 
@@
 For example, increased risk of disease transmission has been observed for highly polyandrous females [@Roberts2015a], but such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry.
-Future models will therefore need to carefully consider the magnitudes and realisation of direct costs to accurately predict evolution of inbreeding strategies in populations.
+Future studies will therefore need to carefully consider the magnitudes and realisation of direct costs to accurately predict evolution of inbreeding strategies in populations.
 
@@
 
-Our model assumed that allele values underlying polyandry, pre-copulatory inbreeding avoidance, and post-copulatory inbreeding avoidance were all initialised at zero (causing monandry, and random mating and fertilisation with respect to kinship), and phenotypes evolved simultaneously after initialisation.
+Evolution of post-copulatory inbreeding avoidance is precluded by existing pre-copulatory inbreeding avoidance, but not vice versa
+-------------------------------------------------------------------
+
+In our model, existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
+However, existence of adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Figure 3A,B).
+In wild populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
+Rather, for example, initial evolution of pre-copulatory inbreeding avoidance is much more likely to evolve in the absence of evolving post-copulatory inbreeding avoidance due to constraints, or in the presence of already evolved post-copulatory inbreeding avoidance.
+When framing hypotheses for existence of post-copulatory inbreeding avoidance and polyandry, it might therefore be necessary to consider whether or not inbreeding avoidance already occurs through pre-copulatory mate choice.
+
+<!--- Our model assumed that allele values underlying polyandry, pre-copulatory inbreeding avoidance, and post-copulatory inbreeding avoidance were all initialised at zero (causing monandry, and random mating and fertilisation with respect to kinship), and phenotypes evolved simultaneously after initialisation.
 However, these initial conditions are likely to be atypical, as evolution of pre-copulatory and post-copulatory inbreeding avoidance from ancestral random mating and fertilisation is unlikely to occur simultaneously.
-Rather, initial evolution of one inbreeding strategy (e.g., pre-copulatory inbreeding avoidance) is more likely to occur in the absence of its complementary strategy (e.g., post-copulatory inbreeding avoidance) if the complementary strategy is evolutionarily constrained.
+Evolution of a single inbreeding strategy (e.g., pre-copulatory inbreeding avoidance) might occur in the absence of its complementary strategy (e.g., post-copulatory inbreeding avoidance) if the complementary strategy is evolutionarily constrained.
 Alternatively, initial evolution of one inbreeding strategy might occur in the context of an already established adaptive strategy for avoiding inbreeding.
 We showed that selection for post-copulatory but not pre-copulatory inbreeding avoidance was strengthened if its complementary strategy was fixed for random choice with respect to kinship, and that selection for post-copulatory but not pre-copulatory inbreeding avoidance was precluded if its complementary strategy was fixed for adaptive inbreeding avoidance.
+--->
 

### 2016-11-02 ms_pre_post.Rmd
New empirical studies in the discussion concerning monandry and inbreeding avoidance; new general prediction at end of discussion

@@
 When framing hypotheses for existence of post-copulatory inbreeding avoidance and polyandry, it might therefore be necessary to consider whether or not inbreeding avoidance already occurs through pre-copulatory mate choice.
+Additionally, the opportunity for post-copulatory inbreeding avoidance will also naturally depend on the degree to which females are polyandrous.
+For species in which pre-copulatory inbreeding avoidance occurs and monandry is common, evolution of post-copulatory inbreeding avoidance is especially unlikely.
+For example, females of the gregarious cockroach *Blatella germanica* (L.) avoid inbreeding and are typically monandrous [@Lihoreau2007]; while occurrence of post-copulatory inbreeding avoidance in *B.
+germanica* has not, to our knowledge, been tested, we predict that such inbreeding avoidance is highly unlikely.
+Similarly, females of the solitary parasitoid wasp *Venturia canescens* are monandrous, and appear to avoid mating with siblings [@Metzger2010; @Metzger2010a].
+We suggest that post-copulatory inbreeding avoidance in *V.
+canescens* would be highly unlikely to evolve.
+
+General predictions
+-------------------------------------------------------------------
+
+Some broad predictions are possible given the verbal theory that we have developed and the populations that we have simulated.
+For example, given that post-copulatory inbreeding avoidance is useless for monandrous females and most effective for polyandrous females, while pre-copulatory inbreeding avoidance is perhaps most effective for monandrous females and less effective for polyandrous females, it would be interesting to test whether or not occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with degree of polyandory.
+To address such a question, more work is needed to identify the degree to which females of different species engage in polyandrous and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
+
+<!--- Some general conclusions addressing 1) what future theory should be developed, and 2) what future empirical studies need to consider.
+For 2, need to be aware of both pre- and post-copulatory inbreeding avoidance, potentially, and that the two are not independent, necessarily; cannot find any general theory for what happens when you have this kind of strategy redundancy -- two ways of getting at the same outcome.
+--->
 

### 2016-11-02 ms_pre_post.Rmd
Clean up the RMD file comments a bit

@@
 
-<!--- What is 'quantitative theory'?
-I don't think that I understand what the implied knowledge gap is here, actually.
-We set up an empirical system to test some interesting hypotheses; I suppose that the knowledge gap is whether or not those specific hypotheses are supported given the parameters we model.
-The hypothesis testing sort of relates to the brief verbal theory that we mention in the introduction, but this manuscript does not address any theoretical knowledge gap using modelling.
-I don't think this is an esoteric issue; we have to make it clear that we know what we're doing and why we're doing it.
---->
-
 Meanwhile, empirical studies of diverse species have found evidence for female inbreeding avoidance enacted through pre-copulatory or post-copulatory routes, or both.
@@
 Such a framework would allow prediction of the form of mating system evolution across different systems that experience inbreeding depression and allow existing empirical studies to be compared to model predictions.
-
-<!--- I'm sorry, I didn't understand the suggested terminal sentence or the accompanying comment.
-I'm not sure I'm clear on what we're considering a prediction versus what we're considering a test of prediction, or what 'underlying understanding' refers to in the context of the key hypotheses and where the come from.
-''Maybe end on something like this, to emphasise the value of having such a framework (which I think comes both through prediction and through testing predictions and hence underlying understanding?).
-I expect you’ll want to edit though'' --->
 
@@
 
-<!--- ‘Hypothesis that polyandry and pre- and post-cop IA might co-evolve.
-However no theory tests these hypotheses or predicts circumstances under which different strategies of pre- and/or post-cop IA might arise and hence drive polyandry evolution, impeding rationalization of empirical observations...
---->
-
-<!--- Theory cannot test hypotheses -- I don't think this is how theory works (or how hypotheses work), and it runs the risk of confusing people, or worse.
-Furthermore, I don't see how what we've done here could help 'rationalise' empirical observations (or if this is even desirable).
-Hence, I'm not really sure I understand the suggested change to the first sentence.
-I've tried to adjust things to make a bit broader, but I think it's very important that we get the science and clear and accurate as possible in the first sentence.
---->
-
 We have used *in silico* experiments to test three key hypotheses concerning evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
@@
 Accordingly, we modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
-
-<!--- Using *in silico* experiments, we tested three specific hypothesis to predict evolution of polyandry, and pre-copulatory and post-copulatory inbreeding strategy.
-We found that (1) selection for polyandry was greatly strengthened given concurrent evolution of post-copulatory inbreeding avoidance, (2) selection for costly pre-copulatory or post-copulatory inbreeding avoidance was negligible given evolution of a less costly strategy of inbreeding avoidance, and (3) pre-existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance, but not vice versa.
---->
 

### 2016-11-02 ms_pre_post.Rmd
A couple more sentences in the last paragraph; fix some spelling

@@
 Similarly, females of the solitary parasitoid wasp *Venturia canescens* are monandrous, and appear to avoid mating with siblings [@Metzger2010; @Metzger2010a].
-We suggest that post-copulatory inbreeding avoidance in *V.
+We hypothesise that post-copulatory inbreeding avoidance in *V.
 canescens* would be highly unlikely to evolve.
@@
 Some broad predictions are possible given the verbal theory that we have developed and the populations that we have simulated.
-For example, given that post-copulatory inbreeding avoidance is useless for monandrous females and most effective for polyandrous females, while pre-copulatory inbreeding avoidance is perhaps most effective for monandrous females and less effective for polyandrous females, it would be interesting to test whether or not occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with degree of polyandory.
-To address such a question, more work is needed to identify the degree to which females of different species engage in polyandrous and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
+For example, given that post-copulatory inbreeding avoidance is useless for monandrous females and most effective for polyandrous females, while pre-copulatory inbreeding avoidance is perhaps most effective for monandrous females and less effective for polyandrous females, it would be interesting to test whether or not occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with degree of polyandry.
+In addition to polyandry making post-copulatory inbreeding avoidance relevant, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself.
+Hence, well-grounded biological hypotheses might be derived for the relationship between female multiple mating and mode of inbreeding avoidance.
+To test such hypotheses, more work is needed to identify the degree to which females of different species engage in polyandrous and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
 

### 2016-11-03 ms_pre_post.Rmd
Minor spelling corrections, completely update biorXiv version from Rmd version

@@
 Importantly, evolution of post-copulatory inbreeding avoidance requires that females are polyandrous, defined as mating with multiple males during a single reproductive bout.
-Further, such polyandry could itself evolve because it allows females to mate with additional unrelated males following initial mating with a relative, thereby facilitating pre-copulatory inbreeding avoidance even in the absence of any post-copulatory female choice or otherwise biased fertilisation (e.g., given a 'fair raffle' among sperm provided by feamles' mates).
+Further, such polyandry could itself evolve because it allows females to mate with additional unrelated males following initial mating with a relative, thereby facilitating pre-copulatory inbreeding avoidance even in the absence of any post-copulatory female choice or otherwise biased fertilisation (e.g., given a 'fair raffle' among sperm provided by females' mates).
 As a reproductive strategy, polyandry can thereby simultaneously allow females to mate with less closely related males and creates the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
@@
 Equation 1 assumes independent allelic effects, generating multiplicative effects on offspring viability [@Morton1956; @Mills1994].
-We model inbreeding depression as having an absolute rather than relative effect on offspring viability )i.e., hard rather than sof selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
+We model inbreeding depression as having an absolute rather than relative effect on offspring viability) i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
 We also assume that inbreeding always decreases offspring viability, $\beta > 0$ (i.e., no outbreeding depression).
@@
 We predict evolution of polyandry in populations where inbreeding depression is severe and evolution of inbreeding avoidance through post-copulatory mechanisms is not constrained.
-Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa [e.g.
-@Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015].
+Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa [e.g., @Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015].
 For example, the number of sperm arriving to eggs is lower for full siblings of female red jungefowl (*Gallus gallus*) than it is for non-relatives, even after controlling for effects of order of oviposition and social familiarity [@Pizzari2004].

### 2016-11-03 pre_post_biorxiv.tex
Fix figure 3 height
Add correct figure 4 (was repeat of fig 3)
Minor spelling corrections, completely update biorXiv version from Rmd version

@@
 A. Bradley Duthie\textsuperscript{1,*},
+Greta Bocedi\textsuperscript{1},
+Ryan R. Germain\textsuperscript{1},
+Matthew E. Wolak\textsuperscript{1},
 Jane M. Reid\textsuperscript{1}
@@
 }
-Inbreeding avoidance has been widely observed through pre-copulatory and post-copulatory mechanisms as a consequence of inbreeding depression in offspring viability.
-However, no conceptual framework compares evolution of pre-copulatory and post-copulatory inbreeding avoidance jointly, and given biologically relevant costs of inbreeding strategies.
+Inbreeding avoidance has been widely hypothesised to evolve through pre-copulatory and post-copulatory mechanisms as a consequence of inbreeding depression in offspring viability.
+However, no modelling compares evolution of pre-copulatory and post-copulatory inbreeding avoidance jointly, and given biologically relevant costs of inbreeding strategies.
 Critically, evolution of post-copulatory inbreeding avoidance is restricted to females that mate multiply, potentially leading to complex evolutionary dynamics among inbreeding strategies and polyandry.
-Accordingly, we use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address three questions: Will evolution of post-copulatory inbreeding avoidance strengthen selection for polyandry?
-Will selection for a costly inbreeding strategy be negligible given a non-costly alternative strategy?
-And will selection for an inbreeding strategy be negligible given existence of an already adaptive alternative strategy?
-We show that selection for polyandry is greatly strengthened by post-copulatory inbreeding avoidance.
-Strong selection for relatively low cost inbreeding avoidance strategies was observed, while selection for functionally redundant high cost strategies decreased over generations.
+Accordingly, we use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address three questions: (1) Does evolution of post-copulatory inbreeding avoidance facilitate evolution of costly polyandry?
+(2) Is evolution of one costly inbreeding strategy inhibited by another non-costly alternative strategy?
+And (3) is evolution of one inbreeding strategy precluded by existence of another already adaptive strategy?
+We show that evolution of polyandry is facilitated by post-copulatory inbreeding avoidance.
+Evolution of relatively low cost inbreeding avoidance strategies was observed, while selection for functionally redundant high cost strategies decreased over generations.
 Finally, existence of an adaptive inbreeding strategy precluded evolution of post-copulatory, but not pre-copulatory, inbreeding avoidance.
@@
 
-Inbreeding typically reduces the fitness of inbred offspring (termed `inbreeding depression'), potentially driving evolution of inbreeding avoidance when inbreeding depression is strong \cite[][]{Parker1979, Parker2006, Pusey1996, Charlesworth1999, Keller2002, Charlesworth2009, Szulkin2012}.
-For focal females, inbreeding avoidance might be acheived by avoiding related potential mates (pre-copulatory inbreeding avoidance), or by biasing fertilisation after mating has occurred so that related mates are less likely to sire offspring (post-copulatory inbreeding avoidance).
-Importantly, evolution of post-copulatory inbreeding avoidance requires that females be polyandrous, mating with multiple males during a single reproductive bout to ensure that post-copulatory choice can be expressed.
-As a reproductive strategy, polyandry thereby simultaneously allows females to choose multiple mates and creates the opportunity for further cryptic choice enacted through post-copulatory mechanisms.
-Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and therefore produce higher fitness offspring \cite[][]{Zeh1997, Jennions2000, Tregenza2002, Akcay2007}.
-However, how pre- and post-copulatory strategies of inbreeding avoidance evolve jointly, and how such evolution is predicted to feed back to affect evolution of polyandry, still remains largely unknown.
-While pre-copulatory inbreeding avoidance can facilitate evolution of polyandry under some restrictive conditions \cite[][]{Duthie}, the opportunity for post-copulatory choice might facilitate evolution of polyandry under a much wider range of conditions by allowing females to bias fertilisation toward non-kin.
+Inbreeding often greatly reduces the fitness of inbred offspring \cite[termed `inbreeding depression';][]{Charlesworth1999, Keller2002, Charlesworth2009}.
+Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple reproductive decisions in species with obligate biparental reproduction \cite[][]{Parker1979, Parker2006, Pusey1996, Szulkin2012}.
+From the perspective of a focal breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred, meaning that related males are less likely to sire offspring (i.e., post-copulatory inbreeding avoidance).
+Importantly, evolution of post-copulatory inbreeding avoidance requires that females are polyandrous, defined as mating with multiple males during a single reproductive bout.
+Further, such polyandry could itself evolve because it allows females to mate with additional unrelated males following initial mating with a relative, thereby facilitating pre-copulatory inbreeding avoidance even in the absence of any post-copulatory female choice or otherwise biased fertilisation (e.g., given a 'fair raffle' among sperm provided by females' mates).
+As a reproductive strategy, polyandry can thereby simultaneously allow females to mate with less closely related males and creates the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
+Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness \cite[][]{Zeh1997, Jennions2000, Tregenza2002, Akcay2007}.
+However, despite such well-established hypotheses, no modelling investigates conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are likely to evolve, or predicts how such evolution will feed back to affect underlying evolution of polyandry.
 
-Severe inbreeding depression might cause selection for alleles underlying active pre- and post-copulatory inbreeding avoidance and associated polyandry, but if evolution of one strategy renders its complement redundant for avoiding inbreeding, then selection might instead be sustained over generations for only one strategy.
-Empirical studies of multiple species have found evidence for female pre-copulatory inbreeding avoidance \cite[e.g.,][]{Lihoreau2007, Kuriwada2011, Kingma2013, Fischer2015}, and for post-copulatory inbreeding avoidance \cite[e.g.,][]{Simmons2006, Bretman2009}.
-Further, evidence of both pre-copulatory and post-copulatory inbreeding avoidance has been found for a handful of well-studied species, including Trinidadian guppies \cite[\textit{Poecilia reticulata};][]{Gasparini2011, Daniel2015} and house mice \cite[\textit{Mus domesticus};][]{Potts1991, Firman2015}, while \cite{Liu2014} found evidence for pre-copulatory, but not post-copulatory, inbreeding avoidance in an experimental study of cabbage beetles (\textit{Colaphellus bowringi}).
-Other studies do not find any evidence for inbreeding avoidance despite strong inbreeding depression, suggesting that evolution of pre- or post-copulatory inbreeding avoidance cannot be presumed \cite[e.g.,][]{Frere2010, Reid2014, Reid2015}.
-These empirical studies demonstrate that all combinations of adaptive pre-copulatory and post-copulatory inbreeding avoidance are possible, but no conceptual framework exists to predict \textit{a priori} what combinations should be favoured by selection when both pre- and post-copulatory inbreeding avoidance, and polyandry, can evolve.
+Meanwhile, empirical studies of diverse species have found evidence for female inbreeding avoidance enacted through pre-copulatory or post-copulatory routes, or both.
+For example, pre-copulatory inbreeding avoidance has been documented in weevils, birds, and butterflies \cite[e.g.,][]{Kuriwada2011, Kingma2013, Fischer2015}, and post-copulatory inbreeding avoidance has been documented in crickets \cite[e.g.,][]{Simmons2006, Bretman2009}.
+Evidence of both pre-copulatory and post-copulatory inbreeding avoidance has accumulated for some well-studied species, including Trinidadian guppies \cite[\textit{Poecilia reticulata};][]{Gasparini2011, Daniel2015} and house mice \cite[\textit{Mus domesticus};][]{Potts1991, Firman2015}.
+While most studies consider either pre-copulatory or post-copulatory inbreeding avoidance in isolation, a small number of studies consider both.
+Accordingly, \cite{Liu2014} found evidence of pre-copulatory, but not post-copulatory, inbreeding avoidance in cabbage beetles (\textit{Colaphellus bowringi}).
+Other studies found no evidence of pre-copulatory or post-copulatory inbreeding avoidance despite strong inbreeding depression \cite[e.g.,][]{Reid2014, Reid2015}.
+These empirical studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature.
+However, there is as yet no modelling framework that predicts \textit{a priori} what combinations should be favoured by selection when both pre-copulatory and post-copulatory inbreeding avoidance, and polyandry, can evolve.
+Such a framework would allow prediction of the form of mating system evolution across different systems that experience inbreeding depression and allow existing empirical studies to be compared to model predictions.
 
-Frequencies of alleles underlying active pre- and post-copulatory inbreeding avoidance and polyandry are likely to be affected by direct negative selection on phenotypes (i.e., costs).
-For example, polyandrous females often pay a cost associated with searching or making themselves available to mates, thereby increasing their own risk of predation \cite[e.g.,][]{Rowe1988, Ronkainen1994, Koga1998}.
+A recent genetically-explicit individual-based model showed that selection for alleles underlying polyandry and pre-copulatory inbreeding avoidance, and resulting joint evolution of these reproductive strategies, occurred only under highly constrained conditions \cite[][]{Duthie}.
+Specifically, such evolution occurred when direct costs of polyandry were small, when very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or when polyandry was conditionally expressed when a focal female was related to her initial mate \cite[][]{Duthie}.
+In the absence of these conditions, increasing degrees of polyandry tended to increase the overall degree of inbreeding that females experienced, and hence increase inbreeding depression in offspring fitness.
+This occurred because polyandrous females that had evolved to avoid inbreeding had already chosen available unrelated males as their initial mates.
+Their additional mates, chosen from the remaining male population, were therefore increasingly likely to include relatives.
+Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance was consequently restricted.
+
+However, while \cite{Duthie} considered simultaneous evolution of polyandry and pre-copulatory inbreeding avoidance, they did not also allow simultaneous evolution of post-copulatory inbreeding avoidance, and assumed that polyandrous females had no post-copulatory control over fertilisation.
+If post-copulatory inbreeding avoidance could also evolve, polyandrous females could further bias paternity towards unrelated males within their set of chosen mates.
+This process might reduce the cost of polyandry stemming from accumulation of related mates, potentially facilitating evolution of polyandry to avoid inbreeding \cite[][]{Zeh1997}, and driving further consequent evolution of pre-copulatory or post-copulatory mate choice strategies.
+Therefore, while pre-copulatory inbreeding avoidance can facilitate evolution of polyandry under some restrictive conditions \cite[][]{Duthie}, the opportunity for post-copulatory choice might facilitate evolution of polyandry under a much wider range of conditions by allowing females to bias fertilisation toward non-kin.
+The long-term evolutionary dynamics of pre-copulatory and post-copulatory inbreeding avoidance then become unclear.
+Strong inbreeding depression might drive initial evolution of both pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
+However, if evolution of polyandry and post-copulatory inbreeding avoidance renders pre-copulatory inbreeding avoidance redundant, or vice versa, then only one strategy might be maintained in the long-term.
+
+Previous models implicitly or explicitly considered the fate of a rare allele underlying pre-copulatory inbreeding avoidance in a population initially fixed for random mating \cite[e.g.,][]{Parker1979, Parker2006, Duthie, Duthie2016a}.
+Such models thereby isolate the invasion fitness of this single strategy.
+However, when both pre-copulatory and post-copulatory strategies can affect realised inbreeding, it cannot be assumed that both strategies will invade simultaneously, nor that invasion fitness of one strategy will be independent of the other For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect of such invading alleles could be weak or negligible.
+
+Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry are likely to be affected by direct negative selection on resulting phenotypes (i.e., costs) and hence on the net costs versus benefits stemming from inbreeding avoidance.
+Polyandrous females can pay costs of mate searching or mating, for example, because these activities increase predation risk \cite[e.g.,][]{Rowe1988, Ronkainen1994, Koga1998}.
 Females that express pre-copulatory choice (e.g., reluctance to mate with relatives) might pay a cost of increased risk of mating failure, or harm caused by sexual conflict \cite[][]{Rowe1994, Kokko2013}.
 Females that express post-copulatory choice might pay an energetic cost associated with physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation \cite[e.g.,][]{Gasparini2011, Tuni2013, Fitzpatrick2014b}.
-If the relative costs affecting pre- and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly inbreeding strategy might become fixed in the population over generations, while alleles underlying the more costly inbreeding strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
+If the relative costs affecting pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly inbreeding strategy might become fixed in the population over generations, while alleles underlying the more costly inbreeding strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
 
-In addition to the relative importance of costs, evolution of pre- or post-copulatory inbreeding avoidance might be precluded if inbreeding avoidance is already acheived through a complementary strategy, thereby reducing net benefits.
-Previous models considered the fate of a rare allele underlying inbreeding avoidance in a population initially fixed for random mating \cite[e.g.,][; Duthie and Reid \textit{In press}]{Parker1979, Parker2006, Duthie}.
-Such models thereby isolate the invasion fitness of a single focal strategy.
-However, when multiple distinct strategies affect realised inbreeding, it cannot be assumed that both will invade simultaneously, nor that invasion fitness of one inbreeding strategy will be independent of another.
-For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect that such invading alleles have on decreasing total inbreeding avoidance could be weak or negligible.
-
-In a recent model, \cite{Duthie} showed that selection for alleles underlying polyandry and pre-copulatory inbreeding avoidance occurred only under highly constrained conditions in which direct costs of polyandry were low, and when very few males were available during a female's initial mate choice but many males were available during a female's additional mate choice(s), or when polyandry was conditionally expressed based on the degree to which a focal female engaged in inbreeding given her initially chosen mate.
-In the absence of these constraints, expression of polyandry was expected to increase inbreeding with each additional mate because remaining males were more likely to be relatives once available non-relatives were chosen.
-However, \cite{Duthie} assumed that polyandrous females had no control over the assignment of paternity to their offspring.
-If after engaging in polyandry, females could bias paternity through post-copulatory mechanisms, then selection for polyandry to avoid inbreeding might be more widely predicted when inbreeding depression is severe \cite[][]{Zeh1997}, potentially feeding back to drive further evolution of pre- and post-copulatory strategies.
-
-Here we use individual-based modelling and \textit{in silico} experiments to test the hypothesis that, given severe inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance causes selection for polyandry.
-Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that selection for only the less costly inbreeding avoidance strategy will be sustained over generations.
-Finally, we test the hypothesis that evolution of one inbreeding strategy will be precluded if it is introduced into a population that is already fixed for a complementary inbreeding strategy that is adaptive.
-We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across reproductive systems with different relative costs and strong inbreeding depression in offspring viability.
+Here we use individual-based modelling to set up \textit{in silico} experiments, which test the hypothesis that, given strong inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance facilitates evolution of polyandry.
+Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution such that only the less costly inbreeding avoidance strategy will be expressed in the long term.
+Finally, we test the hypothesis that evolution of one inbreeding avoidance strategy (i.e., pre-copulatory or post-copulatory) will be precluded if it is introduced into a population that is already fixed for the other inbreeding avoidance strategy that is adaptive.
+We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across different reproductive systems.
 
 \section*{Model}
+
+We model evolution of polyandry and pre-copulatory and post-copulatory inbreeding avoidance by tracking reproductive interactions among individual females and males in a small focal population.
+Individuals are defined as related if they share a common ancestor within the population pedigree (i.e., non-zero kinship).
+Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of the three reproductive strategy traits: tendency for polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., `mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$ i.e., `fertilisation' alleles).
+Alleles can take any real number \cite[i.e., a continuum-of-alleles model;][]{Kimura1965, Lande1976, Reeve2000, Bocedi2014} and combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for each trait.
+In overview, each generation proceeds with females paying costs, expressing polyandry, mating, and fertilisation.
+Offspring inherit a randomly sampled allele from each parent at each locas with no physical linkage.
+Alleles can then mutate and offspring express inbreeding depression.
+Immigrants arrive in the population and density regulation limits population growth.
+Key individual traits, parameter values, and variables are described in Table 1.
+
+\vspace{5 mm}
 
@@
 
-We model evolution of polyandry and inbreeding avoidance through pre- and post-copulatory mechanisms by tracking interactions among discrete individuals in a small focal population that persists over multiple generations (key individual traits, parameter values, and variables are described in Table 1).
-Individuals within this population are either female or male, and can be related to each other if they share a common ancestor.
-Each individual has 10 diploid loci and therefore 20 alleles underlying each trait: tendency to engage in polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$ i.e., `fertilisation' alleles).
-Alleles combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for each trait.
-Over generations, we record mean values of alleles underlying polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
-One generation proceeds with females paying costs, expressing polyandry, mating, and fertilising offspring; offspring alleles then mutate and offspring express inbreeding depression; finally, immigrants arrive in the populatoin and density regulation limits population growth.
-
 \subsection*{Costs}
 
-Values of phenotypic traits for tendency to engage in polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$) each have costs.
-Each cost independently increases the risk of female pre-mating mortality and, because generations are non-overlapping, total reproductive failure as a linear function of its associated trait.
-The probability that a focal female dies before mating due to the cost of polyandry ($c_{P}$) is therefore $P_{p} \times c_{P}$.
-Similarly, the probability of pre-mating female mortality due to the cost of pre-copulatory inbreeding strategy ($c_{M}$) and post-copulatory inbreeding strategy ($c_{F}$) is $|M_{p}| \times c_{M}$ and $|F_{p}| \times c_{F}$, repectively, where $|M_{p}|$ is the absolute value of $M_{p}$ and $|F_{p}|$ is the absolute value of $F_{p}$.
-Absolute values are used for applying costs to inbreeding strategies because both negative and positive $M_{p}$ and $F_{p}$ bias breeding interactions with respect to kinship, while only positive values of $P_{p}$ affect a female's tendency for polyandry; zero and negative $P_{p}$ values always translate to monandrous phenotypes (see below).
+Phenotypic values for tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$) each have costs that are assumed to independently increase the probability that a focal female will die before mating.
+The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, repectively.
+Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
+Absolute values are used for applying costs to inbreeding strategies as appropriate because both negative and positive $M_{p}$ and $F_{p}$ values affect the degree of inbreeding.
+In contrast, only positive values of $P_{p}$ cause females to be polyandrous (see below).
+Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases as a linear function with each trait value.
 
@@
 
-After costs are paid, each remaining female chooses a number of males to mate with ($N_{males}$) based on her genetically determined tendency to engage in polyandry ($P_{p}$).
-The exact value of $N_{males}$ is calculated by randomly sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
-This random sampling procedure causes some stochastic variation in the number of realised mates a that female chooses, with a mean $N_{males}$ of $P_{p}+1$.
-A value of one is added to $P_{p}$ to ensure that all females that have not paid a cost choose at least one mate, as low values of $P_{p}$ might return $Poisson(P_{p})$ values of zero.
-
-The value of $P_{p}$ is affected by the summed values of a focal female's 20 $P_{a}$ alleles.
-Inheritence of all alleles models a diploid genetic architecture in which 10 $P_{a}$ alleles are randomly sampled from each parent with no physical linkage.
-Values of $P_{a}$ can take any real number \cite[continuum-of-alleles model;][]{Kimura1965, Lande1976, Reeve2000, Bocedi2014}.
-The tendency for polyandry genotype $P_{g}$ is therefore defined by the sum of all of a focal female's 20 $P_{a}$ values, which might be negative or positive.
-However, the tendency for polyandry phenotype $P_{p}$ is restricted to zero or positive values because the number of males that a female chooses to mate with cannot be negative.
-Hence, negative values of $P_{g}$ are translated to $P_{p}$ values of zero such that $P_{p} = 0$ when $P_{g} < 0$, but when $P_{g} \geq 0$, then $P_{p} = P_{g}$ (i.e., the phenotype value of polyandry equals the genotype value of polyandry if and only if the genotype value is greater than or equal to zero, else the phenotype value of polyandry always equals zero).
-The resulting $P_{p}$ is therefore modelled as a threshold trait \cite[][]{Lynch1998, Roff1996, Roff1998, Duthie}, in which polyandry is expressed discretely at the threshold value of $P_{g} > 0$, but is determined by the consequence of continuous genetic variation arising from the effects of $P_{a}$ alleles that each contribute additively to polyandry.
-Negative genotype values of $P_{g}$ therefore all have the same phenotype, resulting in consistently monandrous females.
-In contrast, positive values of $P_{g}$ and therefore $P_{p}$ can lead to different degrees of realised polyandry in the form of discrete numbers of mates ($N_{males}$).
+After costs are paid, each remaining female chooses $N_{males}$ males to mate with, where $N_{males}$ is calculated by sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
+This ensures that all surviving females choose at least one mate, and causes some stochastic variation aroudn the expected mean $N_{males}$ of $P_{p}+1$.
+A female's value of $P_{p}$ depends on the sum of her 20 $P_{a}$ allele values, which might be negative or positive.
+However, because females cannot mate with a negative number of males, $P_{p}$ is constrained to be zero or positive such that $P_{p} = 0$ when $P_{g} < 0$, but $P_{p} = P_{g}$ when $P_{g} \geq 0$.
+Polyandry is therefore modelled as a threshold trait \cite[][]{Lynch1998, Roff1996, Roff1998, Duthie} that is influenced by continuous genetic variation but only expressed at the threshold value of $P_{g} > 0$.
+Any negative $P_{g}$ value therefore generates phenotypic monandry, while positive $P_{g}$ values can lead to different degrees of realised polyandry (i.e., different numbers of mates, $N_{males}$).
 
@@
 
-Each male within the population is a potential mate for any female to choose.
-We therefore assume that there are no opportunity costs associated with male mating such that mating with one female would reduce a male's ability to mate with and sire the offspring of any other female \cite[e.g.,][]{Waser1986}.
-While all males are therefore available as potential mates, we assume that a female mates with her total allotment of $N_{males}$ without replacement, meaning that $N_{males}$ models the total number of distinct males that a female chooses to mate with rather than the number of times that she mates.
-In the unlikely event that a female's $N_{males}$ exceeds the total number of males in the population, then she mates with all of the males in the population.
-Most often, $N_{males}$ will be a small subset of the available males in the population \cite[][]{Duthie}, so the male(s) a focal female chooses will reflect her expression of pre-copulatory inbreeding strategy phenotype ($M_{p}$).
-Like polyandry allele values, pre-copulatory inbreeding strategy allele values ($M_{a}$) can take any real number.
-However, unlike polyandry, the sum of all of a female's 20 $M_{a}$ alleles equals both her pre-copulatory inbreeding strategy genotype ($M_{g}$) and her pre-copulatory inbreeding strategy phenotype ($M_{p}$).
-Negative or positive values of $M_{p}$ cause a female to avoid or prefer mating with kin, respectively.
+All males in the population are assumed to be available for any female to choose.
+We therefore assume that there is no opportunity cost of male mating such that mating with one female would reduce a male's availability to mate with any other female.
+Individual females mate with their total allotment of $N_{males}$ without replacement, meaning that $N_{males}$ models a female's total number of different mates rather than solely her total number of matings.
+
+Most often, $N_{males}$ will be smaller than the total number of available males \cite[][]{Duthie}.
+Here, each female chooses her $N_{males}$ mates based on her pre-copulatory inbreeding strategy phenotype ($M_{p}$), which equals her pre-copulatory inbreeding strategy genotype ($M_{g}$) defined as the sum of the values of her 20 $M_{a}$ alleles.
+Negative or positive $M_{p}$ values cause a female to avoid or prefer mating with kin, respectively.
 Values of $M_{p}=0$ cause females to mate randomly with respect to kinship.
@@
 The probability that a focal female $i$ mates with a male $j$ with which she shares some kinship $k_{ij}$ is calculated by first assigning each male a perceived mate quality $Q^{m}_{ij}$.
-This quality depends upon whether the female has a strategy of avoiding mating with kin ($M_{p}<0$) or preferring mating with kin ($M_{p}>0$; if $M_{p}=0$, all males are assigned a quality of 1, $Q^{m}_{ij}=1$).
-If a focal female avoids mating with kin, then $Q^{m}_{ij} = (-M_{p} \times k_{ij} + 1)^{-1}$, meaning that the perceived quality of a male decreases linearly with increasingly positive values of $k_{ij}$ and increasingly negative values of $M_{p}$.
-If a focal female prefers mating with kin, then $Q^{m}_{ij} = M_{p} \times k_{ij} + 1$, meaning that the perceived quality of a male increases with increasingly positive values of $k_{ij}$ and $M_{p}$.
-After a focal female assigns all males a perceived quality, the sum of all male perceived qualities is calculated, then each male quality is divided by this sum.
-This transformation results in each male having a relative perceived mate quality $q^{m}_{ij}$, which is constrained to values between zero and one.
-The value of $q^{m}_{ij}$ then defines the probability that a focal female chooses the male as a mate; female choice is therefore stochastic, meaning that females do not always choose the male of the highest $q^{m}_{ij}$ (e.g., given $M_{p}$ values of $-2$, $-4$, $-6$, and $-8$, an outbred focal female is $1.5$, $2$, $2.5$, and $3$ times more likely to mate with a non-relative than a full-sibling $k_{ij}=0.25$, respectively).
-For polyandrous females that choose more than one male mate, mates are chosen iteratively such that $Q^{m}_{ij}$ and $q^{m}_{ij}$ are re-calculated for each additional mate choice, and with $Q^{m}_{ij}$ and therefore $q^{m}_{ij}$ values of already chosen males set to zero to ensure mate sampling without replacement.
+If the female has a strategy of pre-copulatory inbreeding avoidance ($M_{p}<0$), then $Q^{m}_{ij} = (-M_{p} \times k_{ij} + 1)^{-1}$, meaning that $Q^{m}_{ij}$ decreases linearly with increasingly positive values of $k_{ij}$ and increasingly negative values of $M_{p}$.
+If the female has a strategy of pre-copulatory inbreeding preference ($M_{p}>0$), then $Q^{m}_{ij} = M_{p} \times k_{ij} + 1$, meaning that $Q^{m}_{ij}$ increases with increasingly positive $k_{ij}$ and $M_{p}$.
+If $M_{p}=0$, then all males are assigned a quality of 1
+
+After a focal female assigns all males a $Q^{m}_{ij}$ value, each male's value is divided by the sum of all $Q^{m}_{ij}$ values across all males, thereby assigning each male a relative perceived quality $q^{m}_{ij}$, which is constrained to values between zero and one.
+The value of $q^{m}_{ij}$ then defines the probability that a focal female mates with the male; mating is therefore stochastic, and females do not always mate with the male of the highest $q^{m}_{ij}$.
+For polyandrous females that choose multiple mates (i.e., $N_{mates}>1$), mates are chosen iteratively such that $Q^{m}_{ij}$ and $q^{m}_{ij}$ are re-calculated for each additional mate choice, and with $Q^{m}_{ij}$ and therefore $q^{m}_{ij}$ values of already chosen males set to zero to ensure mate sampling without replacement.
+In the unlikely event that a female's $N_{males}$ exceeds the total number of available males, then she simply mates with all males.
 
@@
 
-Fertilisation of a female's $n$ offspring occurs after mating, with each of her $n$ offspring being assigned a sire independently and with replacement from the $N_{males}$ with which the female mated.
-The probability that a male mate successfully sires an offspring is affected by a female's kinship with the potential sire ($k_{ij}$) and her post-copulatory inbreeding strategy ($F_{p}$).
-As with polyandry and pre-copulatory inbreeding strategy phenotypes, a female's post-copulatory inbreeding strategy phenotype is determined by the summed effects of 20 post-copulatory inbreeding strategy alleles ($F_{a}$), which can take any real number.
-The sum of all of a female's $F_{a}$ alleles determines her post-copulatory inbreeding strategy genotype ($F_{g}$), which is identical to her post-copulatory inbreeding strategy phenotype ($F_{p}$).
-As with pre-copulatory inbreeding strategy phenotype ($M_{p}$), negative or positive values of $F_{p}$ correspond to inbreeding avoidance or preference, respectively, and $F_{p}=0$ causes random fertilisation with respect to kinship.
+Following mating, fertilisation occurs such that each of a female's $n$ offspring is independently assigned a sire (with replacement) from the $N_{males}$ with which the female mated.
+Sire identity depends on female's kinship with each potential sire ($k_{ij}$) and her post-copulatory inbreeding strategy phenotype ($F_{p}$), which equals her post-copulatory inbreeding strategy genotype ($F_{g}$), defined as the sum of the values of her 20 $F_{a}$ alleles.
+Negative and positive values of $F_{p}$ correspond to post-copulatory inbreeding avoidance or preference, respectively, and $F_{p}=0$ causes random fertilisation with respect to kinship.
 
-The probability that an offspring of a focal female $i$ is fertilised by one of $i$'s mates $j$ is calculated by first assigning a perceived fertilisation quality to each $j$, $Q^{f}_{ij}$.
-Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if a focal female has a post-copulatory strategy of avoiding inbreeding ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$.
-If instead a focal female has a post-copulatory strategy of preferring inbreeding ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$.
-The perceived qualities of every male that a focal female has mated with are summed, then a relative quality ($q^{f}_{ij}$) is calculated for each male by dividing each individual male mate's $Q^{f}_{ij}$ by this sum.
-As with relative perceived mate quality values ($q^{m}_{ij}$), this results in values of perceived fertilisation quality $q^{f}_{ij}$ between zero and one.
-These $q^{f}_{ij}$ values define the probability that the offspring of a focal female $i$ is fertilised by the male $j$.
-Females produce $n$ offspring, meaning that $q^{f}_{ij}$ values are sampled $n$ times independently and with replacement for each female to determine the realised distribution of sires.
+The probability that an offspring of a focal female $i$ is sired by any one of $i$'s mates $j$ is calculated by assigning a perceived fertilisation quality to each $j$, $Q^{f}_{ij}$.
+Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if a focal female has a strategy of post-copulatory inbreeding avoidance ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$.
+If the focal female has strategy of post-copulatory inbreeding preference ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$.
+A relative quality ($q^{f}_{ij}$) is then calculated for each male by dividing his $Q^{f}_{ij}$ by the sum of the $Q^{f}_{ij}$ values across all of a female's mates.
+These $q^{f}_{ij}$ values, which lie between zero and one, define the probability of paternity.
 
@@
 
-Alleles of a focal female's offspring mutate with a probability of $\mu=0.001$, with mutation being an independent event that does or does not occur for each locus.
-When a mutation occurs at a locus, a new value is sampled from a random normal distribution with a mean of zero and a standard devation of mutation effect size $\mu_{SD}$, $\mathcal{N}(0, \mu_{SD})$.
-This new value is then added to the original value of the allele that mutates \cite[][]{Kimura1965, Lande1976, Bocedi2014, Duthie}.
-The standard deviation of the mutation effect size ($\mu_{SD}$) is set to $\sqrt{1/20}$, which scales the variance of mutation effect size to the total number of alleles affecting $P_{p}$, $M_{p}$, and $F_{p}$ phenotypes \cite[see][]{Kimura1965, Lande1976, Bocedi2014}.
+Offsprings' alleles mutate with independent probabilities $\mu=0.001$.
+When a mutation occurs, a mutation effect is sampled from a normal distribution with a mean of zero and a standard deviation of $\mu_{SD}$ and added to the original allele value \cite[][]{Kimura1965, Lande1976, Bocedi2014, Duthie}.
+The value of $\mu_{SD}$ is set to $\sqrt{1/20}$, which scales the variance of mutation effect size to the total number of alleles affecting each phenotype.
 
@@
 
-The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a function of the coefficient of kinship between $i$ and the sire of her offspring $j$ ($k_{ij}$), and a log-linear slope of inbreeding depression $\beta$.
-We model selection as having an absolute effect on offspring viability (i.e., hard selection), rather than a relative effect on viability (i.e., soft selection), so that the effect of $\beta$ is consistent over generations and across different parameter combinations.
-Natural selection on tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$) can therefore be compared across generations and parameter combinations.
-If offspring viability was instead relative such that the least inbred offspring had a high viability regardless of the absolute value of $k_{ij}$, then the effect of kinship coefficients and inbreeding depression slopes on offspring viability would depend on the population-wide distribution of $k_{ij}$ between females and males, making model inference more difficult.
-Therefore, we define offspring viability as,
+The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a log-linear function of her kinship with the sire of her offspring $j$ ($k_{ij}$) and inbreeding depression slope $\beta$,
 \begin{equation}
@@
 \end{equation}
-The slope $\beta$ models the number of haploid lethal equivalents that exist as deleterious recessive alleles in the gametes of $i$ and $j$, and which might combine to become homozygous in offspring and reduce viability.
-Equation 1 assumes that each deleterious recessive allele affects offspring viability independently, meaning that every deleterious recessive allele added will have a multiplicative affect on decreasing total viability \cite[][]{Morton1956, Mills1994}, causing the log-linear relationship between parent kinship and inbreeding depression.
-We assume that inbreeding depression always decreases offspring viability, $\beta > 0$ (i.e., no outbreeding depression).
-Therefore, because $k_{ij}$ is constrained to values between zero and one, the product of $-\beta$ and $k_{ij}$ must be a value less than or equal to zero, $-\beta \times k_{ij} \leq 0$.
+Here, $\beta$ models the number of haploid lethal equivalents that exist as deleterious recessive alleles in the gametes of $i$ and $j$, and which might be homozygous in offspring and reduce viability.
+Equation 1 assumes independent allelic effects, generating multiplicative effects on offspring viability \cite[][]{Morton1956, Mills1994}.
+We model inbreeding depression as having an absolute rather than relative effect on offspring viability) i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
+We also assume that inbreeding always decreases offspring viability, $\beta > 0$ (i.e., no outbreeding depression).
+Therefore, because $k_{ij}$ is constrained to values between zero and one, $-\beta \times k_{ij} \leq 0$.
 Values of $\Psi_{\textrm{off}}$ must therefore be between zero (if $-\beta \times k_{ij}$ is very negative) and one (if $-\beta \times k_{ij} = 0$).
-We can therefore define $\Psi_{\textrm{off}}$ as the probability that an offspring is viable, and sample its realised viability using a Bernoulli trial.
+We therefore define $\Psi_{\textrm{off}}$ as the probability that an offspring is viable, and sample its realised viability (versus mortality) using a Bernoulli trial.
 
@@
 
-After offspring viability is realised, $\rho$ adult immigrants are added to the focal population.
-The coefficient of kinship between an immigrant and all other individuals (including native individuals and other immigrants) always equals zero ($k_{ij}=0$).
-Because kinship coefficient values are calculated directly from the pedigree of the focal population \cite[not from individuals' genomes; see][]{Duthie}, the addition of immigrants introduces non-kin into the population at a constant rate and prevents the mean kinship coefficient of the population from asymptoting to a value of 1 over generations.
-If the focal population was instead closed ($\rho=0$), then all alleles would quickly be expected to become identical-by-descent among descendants of the ancestral population.
-To avoid having immigrants affect evolution of tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$), immigrants are always male and can therefore be chosen based on their kinship values of zero but not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$.
-To further avoid having immigrants affect evolutionary dynamics, allele values underlying ($P_{a}$), pre-copulatory inbreeding strategy ($M_{a}$), and post-copulatory inbreeding strategy ($F_{a}$) are randomly sampled from normal distributions with means and standard deviations of $P_{a}$, $M_{a}$, and $F_{a}$ values equal to the means and standard deviations of those in the focal population at the time of immigration.
-Overall, this model of immigration effectively assumes that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$.
+After offspring mortality, $\rho$ adult immigrants are added to the focal population.
+The kinship between an immigrant and all other individuals always equals zero ($k_{ij}=0$).
+Immigration therefore prevents the mean kinship within the population from asymptoting to one over generations.
+To ensure that immigrants do not directly affect genotypic or phenotypic values of tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$), immigrants are always male.
+Consequently, they can be chosen as females' mates based on their kinship values of zero but do not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$.
+Further, immigrants $P_{a}$, $M_{a}$, and $F_{a}$ allele values are randomly sampled from normal distributions with means and standard deviations equal to those in the focal population at the time of immigration.
+We thereby effectively assume that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$.
 
@@
 
-To avoid having unrestricted population growth over generations, we introduce a separate carrying capacity on the total number of females ($K_{f}$) and males ($K_{m}$) in the focal population following immigration \cite[][]{Guillaume2009, Duthie}.
-If at the end of a generation the number of females or males exceeds their respective carrying capacities, then each sex is reduced back to its $K_{f}$ or $K_{m}$ by randomly removing females and males until each sex is at its carrying capacity.
-Removal of females and males can be interpreted as dispersal outside the focal population, mortality, or as some combination of dispersal and mortality.
-The remaining females and males within the population form the next generation of adults.
+To avoid unrestricted population growth, we set separate carrying capacities for the total numbers of females ($K_{f}$) and males ($K_{m}$) in the focal population following immigration \cite[][]{Guillaume2009, Duthie}.
+If at the end of a generation the number of females or males exceeds $K_{f}$ or $K_{m}$  respectively, then individuals are randomly removed until each sex is at its carrying capacity.
+Such removal can be interpreted as some combination of dispersal and mortality.
+The remaining females and males form the next generation of potentially breeding adults.
 
@@
 
-To analyse our model, we track mean values of alleles underlying tendency for polyandry ($P_{a}$), pre-copulatory inbreed strategy ($M_{a}$), and post-copulatory inbreeding strategy ($F_{a}$) in a focal population.
-We present evolutionary dynamics of these mean allele values across different parameter combinations to test our three focal hypotheses.
+To test the hypothesis that evolution of post-copulatory inbreeding avoidance can facilitate evolution of costly polyandry, we compare simulations in which polyandry and pre-copulatory and post-copulatory inbreeding can all evolve, with otherwise identical simulations in which post-copulatory inbreeding strategy cannot evolve given four different costs of polyandry ($c_{P} = \{0, 0.0025, 0.005,  0.01\}$).
+To prevent $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes cause random fertilisation with respect to kinship.
+Hence $F_{a}$ alleles have no phenotypic effect, meaning that polyandrous females cannot enact post-copulatory inbreeding avoidance.
 
-To test our hypothesis that selection for polyandry is driven by a female's ability to bias fertilisation toward inbreeding avoidance through post-copulatory mechanisms, we compare simulations in which all three phenotypes including tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory strategy ($F_{p}$) evolve, with an identical set of simulations in which $F_{p}$ cannot evolve given $c_{P} = \{0, 0.0025, 0.005,  0.01\}$.
-To stop $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes resulting from $F_{a}$ cause random fertilisation with respect to kinship (i.e, $F_{p}=0$).
-Hence $F_{a}$ alleles have no phenotypic effect and polyandry cannot cause polyandrous females to benefit through an increased ability to bias fertilisation toward inbreeding avoidance.
-By comparing mean $P_{a}$ values over generations when post-copulatory inbreeding avoidance also evolves versus when fertilisation is random, we test whether or not evolution of post-copulatory inbreeding strategy increases selection for polyandry.
+To test the hypothesis that selection for a costly strategy of inbreeding avoidance will be negligible given a less costly alternative strategy, we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where the cost of pre-copulatory inbreeding strategy $c_{M}=0$ but the cost of post-copulatory inbreeding strategy $c_{F}=0.02$, and vice versa.
+We compare these simulations with evolution of a costly strategy in the absence of evolution of an alternative strategy (e.g., evolution of pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy phenotype is fixed at zero, $F_{p}=0$).
 
-To test the hypothesis that selection for a costly strategy of inbreeding avoidance will be negligible given a less costly alternative strategy, we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where the cost of pre-copulatory inbreeding strategy $c_{M}=0$ but the cost of post-copulatory inbreeding strategy $c_{F}=0.02$, and where $c_{F}=0$ but $c_{M}=0.02$.
-We contrast these simulations with evolution of a costly strategy in the absence of evolution of an alternative strategy (e.g., evolution of pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy phenotype is fixed at zero, $F_{p}=0$).
-A contrast between the baseline expectation for how costs affect evolution of a focal inbreeding strategy in the absence of an alternative strategy, and evolution of a focal strategy given that an alternative strategy also evolves, tests whether or not a relatively low cost alternative strategy decreases selection for a focal strategy.
+To test the hypothesis that the existence of adaptive post-copulatory inbreeding avoidance will preclude the invasion of pre-copulatory inbreeding avoidance, or vice versa, we first used exploratory simulations to determine evolution of pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation.
+To test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance was already established, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., meaning that $F_{p}$ and $P_{p}$ did not evolve).
+Similarly, to test whether post-copulatory inbreeding avoidance evolved when pre-copulatory inbreeding avoidance was already established, we initiated $F_{a}$ and $P_{a}$ allele values at zero but fixed $M_{a}$ allele values at $-10$.
+Consequently, because females have 10 diploid loci, when $M_{a}$ or $F_{a}$ alleles were fixed at $-10$, outbred females were $51$ times less likely to choose a full brother and $13.5$ times times less likely to choose a first cousin than a non-relative in pre-copulatory and post-copulatory choice, respectively.
 
-To test the hypothesis that the existence of an adaptive inbreeding strategy will decrease the strength of selection on, and thereby preclude the invasion of, a complementary strategy, we first used exploratory simulations to determine evolution of pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation.
-To test whether or not pre-copulatory inbreeding avoidance was predicted to evolve when adaptive polyandry to avoid inbreeding was already established, we initiated pre-copulatory inbreeding strategy allele values at zero ($M_{a}=0$), but fixed post-copulatory inbreeding allele values at $F_{a}=-10$ and polyandry allele values at $P_{a}=1$ (i.e., $F_{p}$ and $P_{p}$ did not evolve).
-Similarly, to test whether or not post-copulatory inbreeding strategy evolved to avoid inbreeding, we initiated post-copulatory inbreeding strategy allele values and polyandry allele values at zero ($F_{a}=0$; $P_{a}=0$), but fixed pre-copulatory inbreeding strategy allele values at $M_{a}=-10$.
-For reference, because females have 10 diploid loci, when $M_{a}$ or $F_{a}$ alleles were fixed at $-10$, outbred females were $51$ times less likely to choose a full sibling and $13.5$ times times less likely to choose a first cousin than a non-relative in pre- and post-copulatory choice, respectively.
+In all simulations, we record mean values of $P_{a}$, $M_{a}$, $F_{a}$ in each generation.
+Each combination of parameter values simulated is replicated $40$ times, and grand mean values and standard errors of means are calculated in each generation across replicates.
+These analyses allow us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on post-copulatory inbreeding strategy might be weak if polyandry is rare).
+For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling \cite[][]{Duthie} showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
+For all replicates, we set $\rho=5$ immigrants, which produced a range of kin and non-kin in each generation allowing females to express inbreeding strategies, and $n=8$ offspring, which was sufficient to keep populations consistently at carrying capacities and avoid population extinction.
+Values of $K_{f}$ and $K_{m}$ were both set to 100 because previous modelling has shown that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but populations are also not so small that selection is typically overwhelmed by genetic drift \cite[][]{Duthie2016a}.
+
+\section*{Results}
+
+\subsection*{Does evolution of post-copulatory inbreeding avoidance facilitate evolution of costly polyandry?}
+
+When post-copulatory inbreeding avoidance alleles ($F_{a}$) were fixed to zero and could not evolve, $P_{a}$ values were always negative (Figure 1A,C,E,G).
+This shows that there is selection against unconditional polyandry even given zero direct cost ($c_{P}=0$; Figure 1A).
+This is because polyandrous females sampled more males from the available population and were consequently likely to mate with some relatives and hence produce some inbred offspring with low viability \cite[][]{Duthie}.
+
+When post-copulatory inbreeding avoidance was allowed to evolve, mean $P_{a}$ values were substantially higher than in comparable simulations where post-copulatory inbreeding avoidance could not evolve (Figure 1B,D,F,H).
+Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry.
+However, $P_{a}$ values were expeted to be positive only given a low cost of polyandry ($c_{P} < 0.005$, Figure 1A,B).
+This implies that, even given strong inbreeding depression in offspring viability, inbreeding avoidance might generally be a weak force driving polyandry evolution.
+
+Strong post-copulatory inbreeding avoidance consistently evolved in all simulations where such such evolution was allowed (Figure 1B,D,F,H), even when $P_{a}$ values were expected to be slightly negative (i.e., when there is selection against polyandry, Figure 1F,H).
+This reflects the threshold nature of phenotypic expression of polygenic polyandry, wherein random sampling of alleles means that polyandry is commonly expressed (i.e., $P_{g}>0$) even when mean $P_{a}$ values are negative (Figure 2).
+This means that there is commonly opportunity for expression of post-copulatory inbreeding avoidance and associated selection that drives evolution of $F_{a}$ allele values.
+
+Strong pre-copulatory inbreeding avoidance also evolved (i.e., $M_{a}<0$) in all simulations, irrespective of $c_{P}$ and irrespective of whether post-copulatory inbreeding avoidance was allowed to evolve (Figure 1).
 
@@
 {%
-   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{10 mm} \textbf{Figure 1:} Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre- and post-copulatory inbreeding avoidance.
-Costs of polyandry increase with rows from top to bottom.
-Dotted horizontal black lines in panels show values of zero on the y-axis.\end{justify}{\t}%
+   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{10 mm} \textbf{Figure 1:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fiext to zero (i.e., random fertilisation) or (B, D, F, H) allowed to evolve freeely.
+Costs of polyandry ($c_{p}$) increase across rows from zero (A and B) to 0.01 (G and H).
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values indicate inbreeding avoidance or tendency for monandry, and positive values indicate inbreeding preference or tendency for polyandry.
+Dotted lines demarcate mean allele values of zero.
+\end{justify}{\t}%
 }[t]
@@
 }
-
-In all simulations, we record mean values of $P_{a}$, $M_{a}$, $F_{a}$ in each generation.
-Each combination of parameter values simulated is replicated $40$ times, and grand mean values and standard error of means is calculated in each generation across replicate simulations.
-These analyses allow us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on post-copulatory inbreeding strategy might be weak if polyandry is rare).
-For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling \cite[][]{Duthie} showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
-For all replicates, we set $\rho=5$ immigrants, which produced a range of kin and non-kin in each generation allowing females could express inbreeding strategies, and $n=8$ offspring, which was sufficient to keep populations consistently at carrying capacities and avoid population extinction.
-Values of $K_{f}$ and $K_{m}$ were both set to 100 because previous modelling has shown that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but populations are also not so small that selection is typically overwhelmed by genetic drift (Duthie and Reid \textit{in press}).
-
-\section*{Results}
-
-\subsection*{Will evolution of post-copulatory inbreeding avoidance strengthen selection for polyandry?}
-
-For low costs of polyandry, $c_{P} < 0.005$, selection caused expected polyandry allele values ($P_{a}$) to be positive only when post-copulatory inbreeding avoidance evolved (Figure 1A-D).
-For all $c_{P}$, $P_{a}$ values were higher when post-copulatory inbreeding avoidance evolved than when it could not evolve (Figure 1).
-When post-copulatory inbreeding avoidance could not evolve, $P_{a}$ values were negative even in the absence of a direct cost ($c_{P}=0$; Figure 1A) because females that expressed polyandry were more likely to increase their inbreeding due to sampling males without replacement \cite[][]{Duthie}.
-Strong post-copulatory inbreeding avoidance consistently evolved in all simulations, even when $P_{a}$ values were expected to be slightly negative (Figure 1F,H), because of the threshold nature of the polyandry phenotype.
-Figure 2 shows how phenotypic polyandry was common even when mean polyandry allele values within a population were expected to be negative, and how monandry occurred even when mean polyandry allele values were expected to be positive.
-In all simulations, pre-copulatory inbreeding avoidance also evolved ($M_{a}<0$), meaning that both pre- and post-copulatory inbreeding avoidance was predicted, and evolution of adaptive polyandry occurred given sufficiently low costs of polyandry.
-
-\subsection*{Will selection for a costly inbreeding strategy be negligible given a non-costly alternative strategy?}
-
-For simulations in which either pre- or post-copulatory inbreeding strategy allele values were fixed for random choice with respect to kinship ($M_{a}=0$ or $F_{a}=0$, respectively), the alternative costly inbreeding strategy evolved to inbreeding avoidance ($F_{a}<0$ or $M_{a}<0$; Figure 3).
-However, when the alternative inbreeding strategy could evolve and was not costly, the focal costly inbreeding strategy initially evolved towards inbreeding avoidance, but then evolved toward random choice with respect to kinship given increasingly negative allele values of the alternative strategy over generations (Figure 3B,D).
-For example, given fixed $F_{a}=0$, grand mean $M_{a}$ values were $-0.868$ in the last $10000$ generations (Figure 3A), meaning that an outbred focal female was ca $5.34$ times less likely to choose a full-sibling and ca $2.10$ times less likely to choose a first cousin than a non-relative given a strong cost of pre-copulatory inbreeding avoidance, $c_{M}=0.02$.
-In contrast, grand mean $M_{a}$ allele values were $-0.288$ when post-copulatory inbreeding avoidance also evolved.
-More strongly, given fixed $M_{a}=0$, grand mean $F_{a}$ values were $-1.092$ in the last $10000$ generations (Figure 3C), meaning that an outbred focal female was ca $6.46$ times less likely to choose a full-sibling and ca $2.37$ times less likely to choose a first cousin than a non-relative given a strong cost of pre-copulatory inbreeding avoidance, $c_{F}=0.02$.
-However, grand-mean $F_{a}$ values were $-0.070$ when pre-copulatory inbreeding strategy evolved, and polyandry allele values were negative.
-Overall, selection for a costly inbreeding strategy that was adaptive in isolation was greatly weakened given evolution of a less costly strategy.
 
@@
 {%
-   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 2:} Relationship between polyandry allele values and phenotypes for an individual-based model in which pre- and post-copulatory inbreeding strategies evolve jointly with polyandry.
-Two simulations with identical starting conditions (default parameter values with no costs) are shown in panels A,B and C,D.
-Red lines in (A) and (C) show mean value of alleles underlying polyandry for a single replicate simulation over 40000 generations.
-Positive allele values contribute to polyandry, while negative values contribute to monandry (dotted line shows zero on the y-axis).
-In the last generation, mean allele value was below (A) or above (C) zero.
-Nevertheless, due to among-individual variation and the threshold nature of the polyandry phenotype, polyandry persists in the population in (A) and monandry persists in (C).
-The histograms in (B) and (D) show females' tendency for polyandry phenotypes in the last generation; white and grey shading indicates monandrous and polyandrous females, respectively.\end{justify}{\t}%
+   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs.
+Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations.
+Positive and negative allele values contribute to polyandry and monandry, respectively.
+In the final generation, mean allele value was below (A) or above (C) zero (demarcated by the dotted line).
+Nevertheless, due to the threshold nature of expression of the polygenic polyandry phenotype, polyandry and monandry are expressed in both populations.
+Histograms in (B) and (D) show females' tendency for polyandry phenotypes in the final generation; white and grey shading indicates monandrous and polyandrous females, respectively.\end{justify}{\t}%
 }[t]
+\end{adjustwidth}
+}
+
+\subsection*{Is evolution of one costly inbreeding strategy inhibited by another non-costly alternative strategy?}
+
+When either pre-copulatory or post-copulatory inbreeding strategy allele values were fixed to zero and could not evolve, the alternative inbreeding strategy evolved to inbreeding avoidance even when costly (Figure 3A,C).
+However, when one inbreeding strategy could evolve and had zero cost, the other strategy initially evolved towards inbreeding avoidance but then back towards random choice across generations following increasing evolution of inbreeding avoidance (i.e., negative allele values) through the former (zero cost) strategy (Figure 3B,D).
+For example, given fixed $F_{a}=0$, grand mean $M_{a}$ value in the last $10000$ generations was $-0.868$ (Figure 3A), meaning that a female was ca $5.34$ times less likely to choose a full-sibling and ca $2.10$ times less likely to mate with a first cousin than a non-relative given a high cost of pre-copulatory inbreeding avoidance, $c_{M}=0.02$.
+However, when $F_{a}$ allele values could also evolve, grand mean $M_{a}$ allele value in the last $10000$ generations was only $-0.288$ (Figure 3B).
+Further, given fixed $M_{a}=0$, grand mean $F_{a}$ value in the last $10000$ generations was $-1.092$ (Figure 3C), meaning that a female was ca $6.46$ times less likely to choose a full-sibling and ca $2.37$ times less likely to choose a first cousin than a non-relative given a high cost of pre-copulatory inbreeding avoidance, $c_{F}=0.02$.
+However, when $M_{a}$ values could also evolve and $P_{a}$ values were negative, grand mean $F_{a}$ value in the last $10000$ generations was only $-0.070$ (Figure 3D).
+Evolution of post-copulatory inbreeding avoidance faciliated evolution of polyandry (Figure 3B,C), while monandry evolved in the absence of post-copulatory inbreeding avoidance (Figure 3A,D; polyandry was cost free in all these simulations).
+Overall, evolution of a costly inbreeding strategy that readily evolved in isolation was greatly impeded by evolution of a less costly strategy.
+
+{\color{Gray}
+\begin{adjustwidth}{-2.2in}{0in}
+\mysidecaption{0.31}
+{%
+   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 3:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy can evolve and pre-copulatory inbreeding strategy is (A) fixed for random mating or (B) can also evolve.
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.\end{justify}{\t}%
+}
+{%
+   \includegraphics[height=14cm]{figures/rel_costs.pdf}%
+}%
+[t]
 \end{adjustwidth}
@@
 
-When pre-copulatory inbreeding strategy was initialised for random mating, but polyandry and post-copulatory inbreeding strategy allele values were fixed for adaptive inbreeding avoidance (Figure 4A,B), negative pre-copulatory inbreeding allele values became increasingly more frequent ($M_{a}<0$), causing inbreeding avoidance in mate choice.
-However, $M_{a}$ values were not as negative after $40000$ generations when post-copulatory inbreeding avoidance and polyandry were fixed as they were when no post-copulatory inbreeding avoidance occurred (e.g., compare Figure 4A with Figure 1A, and Figure 4B with Figure 2A).
-When post-copulatory inbreeding strategy was initialised for random fertilisation, existence of an already adaptive strategy of pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance (Figure 4C,D).
-Mean allele values affecting polyandry consistently decreased over generations regardless of the cost of post-copulatory inbreeding strategy, $c_{F}$.
-Consequently, when $c_{F}=0$, post-copulatory inbreeding strategy allele values had no effect because females were consistently monandrous, resulting in high drift of $F_{a}$ values among replicates (Figure 4C).
+When polyandry and post-copulatory inbreeding strategy allele values were fixed for adaptive inbreeding avoidance, pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}$ values became increasingly negative; Figure 4A).
+Such evolution still occurred, but to a much smaller degree, when pre-copulatory inbreeding avoidance was costly (Figure 4B).
+However, after $40000$ generations, $M_{a}$ values were less negative when post-copulatory inbreeding avoidance and polyandry were fixed at non-zero values than when they also evolved from initial values of zero (e.g., compare the blue lines in Figures 4A versus Figure 1A).
+
+When pre-copulatory inbreeding strategy values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently trend toward negative values (Figure 4C,D).
+Additionally, mean $P_{a}$ allele values consistently decreased over generations regardless of the cost of post-copulatory inbreeding strategy (Figure 4C,D).
+Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values among replicates (illustrated by wide standard errors, Figure 4C).
 However, when $c_{F}=0.02$, $F_{a}$ values remained near zero to minimise direct costs.
 This lack of evolution of post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
-When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), post-copulatory inbreeding strategy evolved to similarly negative mean allele values as pre-copulatory inbreeding strategy did in Figure 4A,B (see Supporting Information).
+When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information).
 
@@
 {%
-   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 3:} Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panel (A) shows evolution of costly pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy is fixed for random fertilisation (solid black horizontal line), while (B) instead allows post-copulatory inbreeding strategy to evolve under otherwise identical conditions.
-Similarly, panel (C) shows evolution of costly post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for random mating (solid blue horizontal line), while (D) allows pre-copulatory inbreeding strategy to evolve under otherwise identical conditions.\end{justify}{\t}%
+   \captionof{figures/fixed_adapt.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is (A and C) cost-free or (B and D) costly.
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.\end{justify}{\t}%
 }
 {%
-   \includegraphics[height=14.5cm]{figures/rel_costs.pdf}%
+   \includegraphics[height=14cm]{figures/fixed_adapt.pdf}%
 }%
@@
 
-We have provided a novel framework for approaching empirical studies of inbreeding avoidance, predicting evolution of polyandry and inbreeding avoidance through pre- and post-copulatory mechanisms.
-Accordingly, we modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency to engage in polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
-Using \textit{in silico} experiments, we tested three specific hypothesis to predict evolution of polyandry, and pre- and post-copulatory inbreeding strategy.
-We found that (1) selection for polyandry was greatly strengthened given concurrent evolution of post-copulatory inbreeding avoidance, (2) selection for costly pre- or post-copulatory inbreeding avoidance was negligible given evolution of a less costly strategy of inbreeding avoidance, and (3) pre-existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance, but not vice versa.
+We have used \textit{in silico} experiments to test three key hypotheses concerning evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
+The modelling that we develop provides a novel framework for approaching empirical studies of inbreeding avoidance, using simulations to address relevant knowledge gaps in understanding evolution of polyandry and inbreeding avoidance through pre-copulatory and post-copulatory mechanisms.
+Accordingly, we modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
 
-{\color{Gray}
-\begin{adjustwidth}{-2.2in}{0in}
-\mysidecaption{0.68}
-{%
-   \includegraphics[height=14cm]{figures/rel_costs.pdf}%
-}%
-{%
-   \captionof{figures/fixed_adapt.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panel (A) shows evolution of pre-copulatory inbreeding strategy given fixed polyandry (solid red line) and inbreeding avoidance (solid black line), and (B) shows these same conditions given a cost of pre-copulatory inbreeding strategy.
-Similarly, panel (C) shows evolution of polyandry and post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for inbreeding avoidance (solid blue line), while (D) shows these same conditions given a cost of post-copulatory inbreeding strategy.\end{justify}{\t}%
-}[t]
-\end{adjustwidth}
-}
+\subsection*{Evolution of polyandry is facilitated by post-copulatory inbreeding avoidance}
 
 The opportunity to adjust inbreeding has been widely considered as a driver of adaptive evolution of polyandry \cite[][]{Tregenza2002, Foerster2003, Akcay2007, Varian-Ramos2012, Kingma2013, Lehtonen2015, Reid2014}.
-Recently, \cite{Duthie} found the conditions under which selection for polyandry and pre-copulatory inbreeding avoidance is predicted to be highly restrictive, requiring strong constraints on the availability of initial compared to additional mates, or the conditional expression of polyandry such that females only engaged in polyandry when their initial choice of mate was of low quality.
+Recently, \cite{Duthie} found the conditions under which selection for polyandry and pre-copulatory inbreeding avoidance is predicted to be highly restrictive.
 However, \cite{Duthie} assumed that fertilisation of offspring was unbiased with respect to mate kinship, meaning that females could not express post-copulatory choice.
@@
 Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa \cite[e.g.,][]{Pizzari2004, Firman2008, Bretman2009, Gasparini2011, Tuni2013, Firman2015}.
-For example, \cite{Pizzari2004} found that the number of sperm arriving to eggs is lower for full siblings of female red jungefowl (\textit{Gallus gallus}) than it is for non-relatives, even after controlling for effects of order of oviposition and social familiarity.
-Similarly, Firman and Simmons \citeyearpar{Firman2008, Firman2015} have shown evidence of post-copulatory inbreeding avoidance in house mice, finding fertilisation to be biased toward unrelated males independent of the order in which mating occurs \cite[][]{Firman2008}, perhaps due to post-copulatory mechanisms expressed through the secretion of gametic proteins originating in female's eggs \cite[][]{Firman2015}.
-Interestingly, female house mice have also been shown to express pre-copulatory inbreeding avoidance  \cite[][]{Potts1991, Roberts2003}.
+For example, the number of sperm arriving to eggs is lower for full siblings of female red jungefowl (\textit{Gallus gallus}) than it is for non-relatives, even after controlling for effects of order of oviposition and social familiarity \cite[][]{Pizzari2004}.
+Similarly, in house mice, fertilisation was biased toward unrelated males independent of mating order, perhaps due to post-copulatory mechanisms expressed through the secretion of gametic proteins originating in eggs \cite[][]{Firman2008, Firman2015}.
+Interestingly, female house mice also show pre-copulatory inbreeding avoidance  \cite[][]{Potts1991, Roberts2003}.
 Our results suggest that post-copulatory inbreeding avoidance is unlikely to evolve when females can already avoid inbreeding through pre-copulatory mechanisms (Figure 4), meaning that evolution of post-copulatory inbreeding avoidance could reasonably be hypothesised to have preceded evolution of pre-copulatory inbreeding avoidance in mice.
 
-Specific mechanisms of post-copulatory inbreeding avoidance are difficult to identify, but recent experimental studies have shown how females can successfully bias fertilisation after mating has occurred in both vertebrates \cite[e.g.,][]{Gasparini2011} and invertebrates \cite[e.g.,][]{Tuni2013}.
-For example, \cite{Gasparini2011} artificially inseminated female guppies (\textit{Poecilia reticulata}) with equal quantities of sperm from full-siblings and unrelated males, finding that fertilisation success was higher in non-relatives because the velocity of full siblings' sperm was reduced by females' ovarian fluids.
-Biased fertilisation toward non-relatives might also be accomplished through selective storage of sperm.
-For example, in black field crickets (\textit{Teleogryllus commodus}), females attempt to remove the spermataphores of unwanted male mates after copulation, while male mates guard females to prevent spermatophore removal \cite[][]{Bussiere2006}.
-Even if females are unable to remove spermatophores of unwanted mates, \cite{Tuni2013} found that female \textit{T.
-commodus} are capable of controlling the transfer of sperm to their spermatheca, most likely through physical control of the spermathecal duct, and can reduce sperm storage despite being guarded by a related male.
+Recent studies have shown how females can successfully bias fertilisation after mating has occurred.
+For example, when female guppies (*Poecilia reticulata*) were artificially inseminated with equal quantities of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full siblings' sperm were reduced by females' ovarian fluids \cite[][]{Gasparini2011}.
+In black field crickets (\textit{Teleogryllus commodus}), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs \cite{Bussiere2006, Tuni2013}.
 Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for further polyandry, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
 
-In our model, a cost free inbreeding strategy precluded a more costly complementary inbreeding strategy from persisting in a focal population (Figure 2), meaning that long-term persistence of both pre- and post-copulatory inbreeding avoidance might not be expected in populations given cost asymmetry.
+\subsection*{Evolution of a costly inbreeding strategy is inhibited by a non-costly alternative strategy}
+
+In our model, one cost free inbreeding strategy precluded another more costly inbreeding strategy from persisting in a focal population (Figure 2), meaning that long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given cost asymmetry.
 Direct costs therefore strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies.
@@
 For example, increased risk of disease transmission has been observed for highly polyandrous females \cite[][]{Roberts2015a}, but such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry.
-Future models will therefore need to carefully consider the magnitudes and realisation of direct costs to accurately predict evolution of inbreeding strategies in populations.
+Future studies will therefore need to carefully consider the magnitudes and realisation of direct costs to accurately predict evolution of inbreeding strategies in populations.
 
@@
 
-Our model assumed that allele values underlying polyandry, pre-copulatory inbreeding avoidance, and post-copulatory inbreeding avoidance were all initialised at zero (causing monandry, and random mating and fertilisation with respect to kinship), and phenotypes evolved simultaneously after initialisation.
-However, these initial conditions are likely to be atypical, as evolution of pre-copulatory and post-copulatory inbreeding avoidance from ancestral random mating and fertilisation is unlikely to occur simultaneously.
-Rather, initial evolution of one inbreeding strategy (e.g., pre-copulatory inbreeding avoidance) is more likely to occur in the absence of its complementary strategy (e.g., post-copulatory inbreeding avoidance) if the complementary strategy is evolutionarily constrained.
-Alternatively, initial evolution of one inbreeding strategy might occur in the context of an already established adaptive strategy for avoiding inbreeding.
-We showed that selection for post-copulatory but not pre-copulatory inbreeding avoidance was strengthened if its complementary strategy was fixed for random choice with respect to kinship, and that selection for post-copulatory but not pre-copulatory inbreeding avoidance was precluded if its complementary strategy was fixed for adaptive inbreeding avoidance.
+\subsection*{Evolution of post-copulatory inbreeding avoidance is precluded by existing pre-copulatory inbreeding avoidance, but not vice versa}
+
+In our model, existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
+However, existence of adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Figure 3A,B).
+In wild populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
+Rather, for example, initial evolution of pre-copulatory inbreeding avoidance is much more likely to evolve in the absence of evolving post-copulatory inbreeding avoidance due to constraints, or in the presence of already evolved post-copulatory inbreeding avoidance.
+When framing hypotheses for existence of post-copulatory inbreeding avoidance and polyandry, it might therefore be necessary to consider whether or not inbreeding avoidance already occurs through pre-copulatory mate choice.
+Additionally, the opportunity for post-copulatory inbreeding avoidance will also naturally depend on the degree to which females are polyandrous.
+For species in which pre-copulatory inbreeding avoidance occurs and monandry is common, evolution of post-copulatory inbreeding avoidance is especially unlikely.
+For example, females of the gregarious cockroach \textit{Blatella germanica} (L.) avoid inbreeding and are typically monandrous \cite[][]{Lihoreau2007}; while occurrence of post-copulatory inbreeding avoidance in \textit{B.
+germanica} has not, to our knowledge, been tested, we predict that such inbreeding avoidance is highly unlikely.
+Similarly, females of the solitary parasitoid wasp \textit{Venturia canescens} are monandrous, and appear to avoid mating with siblings \cite[][]{Metzger2010, Metzger2010a}.
+We hypothesise that post-copulatory inbreeding avoidance in \textit{V.
+canescens} would be highly unlikely to evolve.
+
+\subsection*{General predictions}
+
+Some broad predictions are possible given the verbal theory that we have developed and the populations that we have simulated.
+For example, given that post-copulatory inbreeding avoidance is useless for monandrous females and most effective for polyandrous females, while pre-copulatory inbreeding avoidance is perhaps most effective for monandrous females and less effective for polyandrous females, it would be interesting to test whether or not occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with degree of polyandry.
+In addition to polyandry making post-copulatory inbreeding avoidance relevant, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself.
+Hence, well-grounded biological hypotheses might be derived for the relationship between female multiple mating and mode of inbreeding avoidance.
+To test such hypotheses, more work is needed to identify the degree to which females of different species engage in polyandrous and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
 

### 2016-11-11 pre_post_biorxiv.tex
Fix title

@@
 {\LARGE
-\textbf\newline{Evolution of pre-copulatory and post-copulatory inbreeding behaviour}
+\textbf\newline{Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry}
 }
@@
 \bigskip
-*  aduthie@abdn.ac.uk, brad.duthie@gmail.com
+*  alexander.duthie@stir.ac.uk, brad.duthie@gmail.com
 

### 2016-11-11 ms_pre_post.Rmd
Several tweaks, mostly fix typos

@@
 Further, such polyandry could itself evolve because it allows females to mate with additional unrelated males following initial mating with a relative, thereby facilitating pre-copulatory inbreeding avoidance even in the absence of any post-copulatory female choice or otherwise biased fertilisation (e.g., given a 'fair raffle' among sperm provided by females' mates).
-As a reproductive strategy, polyandry can thereby simultaneously allow females to mate with less closely related males and creates the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
+As a reproductive strategy, polyandry can thereby simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
 Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007].
@@
 
-Meanwhile, empirical studies of diverse species have found evidence for female inbreeding avoidance enacted through pre-copulatory or post-copulatory routes, or both.
+Meanwhile, studies of diverse species have found evidence for female inbreeding avoidance enacted through pre-copulatory or post-copulatory routes, or both.
 For example, pre-copulatory inbreeding avoidance has been documented in weevils, birds, and butterflies [e.g., @Kuriwada2011; @Kingma2013; @Fischer2015], and post-copulatory inbreeding avoidance has been documented in crickets [e.g., @Simmons2006; @Bretman2009].
@@
 Other studies found no evidence of pre-copulatory or post-copulatory inbreeding avoidance despite strong inbreeding depression [e.g., @Reid2014; @Reid2015].
-These empirical studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature.
-However, there is as yet no modelling framework that predicts *a priori* what combinations should be favoured by selection when both pre-copulatory and post-copulatory inbreeding avoidance, and polyandry, can evolve.
+These studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature.
+However, there is as yet no modelling framework that predicts what combinations should be favoured by selection when both pre-copulatory and post-copulatory inbreeding avoidance, and polyandry, can evolve.
 Such a framework would allow prediction of the form of mating system evolution across different systems that experience inbreeding depression and allow existing empirical studies to be compared to model predictions.
+
+Verbal theory
+----------------------------------------------
 
@@
 Such models thereby isolate the invasion fitness of this single strategy.
-However, when both pre-copulatory and post-copulatory strategies can affect realised inbreeding, it cannot be assumed that both strategies will invade simultaneously, nor that invasion fitness of one strategy will be independent of the other For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect of such invading alleles could be weak or negligible.
+However, when both pre-copulatory and post-copulatory strategies can affect realised inbreeding, it cannot be assumed that both strategies will invade simultaneously, nor that invasion fitness of one strategy will be independent of the other.
+For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect of such invading alleles could be weak or negligible.
 
@@
 
-Model
+Methods
 ===================================================
@@
 Individuals are defined as related if they share a common ancestor within the population pedigree (i.e., non-zero kinship).
-Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of the three reproductive strategy traits: tendency for polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$ i.e., 'fertilisation' alleles).
+Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of the three reproductive strategy traits: tendency for polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$, i.e., 'fertilisation' alleles).
 Alleles can take any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014] and combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for each trait.
 In overview, each generation proceeds with females paying costs, expressing polyandry, mating, and fertilisation.
-Offspring inherit a randomly sampled allele from each parent at each locas with no physical linkage.
+Offspring inherit a randomly sampled allele from each parent at each locus with no physical linkage.
 Alleles can then mutate and offspring express inbreeding depression.
@@
 Equation 1 assumes independent allelic effects, generating multiplicative effects on offspring viability [@Morton1956; @Mills1994].
-We model inbreeding depression as having an absolute rather than relative effect on offspring viability) i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
+We model inbreeding depression as having an absolute rather than relative effect on offspring viability (i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
 We also assume that inbreeding always decreases offspring viability, $\beta > 0$ (i.e., no outbreeding depression).
@@
 
-Model analysis
+Simulation and analysis
 ----------------------------------------------
@@
 
-When post-copulatory inbreeding avoidance alleles ($F_{a}$) were fixed to zero and could not evolve, $P_{a}$ values were always negative (Figure 1A,C,E,G).
+When post-copulatory inbreeding avoidance alleles ($F_{a}$) were fixed to zero and $F_{p}$ could not evolve, $P_{a}$ values were always negative (Figure 1A,C,E,G).
 This shows that there is selection against unconditional polyandry even given zero direct cost ($c_{P}=0$; Figure 1A).
@@
 Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry.
-However, $P_{a}$ values were expeted to be positive only given a low cost of polyandry ($c_{P} < 0.005$, Figure 1A,B).
+However, $P_{a}$ values were expected to be positive only given a low cost of polyandry ($c_{P} < 0.005$, Figure 1B,D).
 This implies that, even given strong inbreeding depression in offspring viability, inbreeding avoidance might generally be a weak force driving polyandry evolution.
 
-Strong post-copulatory inbreeding avoidance consistently evolved in all simulations where such such evolution was allowed (Figure 1B,D,F,H), even when $P_{a}$ values were expected to be slightly negative (i.e., when there is selection against polyandry, Figure 1F,H).
+Strong post-copulatory inbreeding avoidance consistently evolved in all simulations where such evolution was allowed (Figure 1B,D,F,H), even when $P_{a}$ values were expected to be slightly negative (i.e., when there is selection against polyandry, Figure 1F,H).
 This reflects the threshold nature of phenotypic expression of polygenic polyandry, wherein random sampling of alleles means that polyandry is commonly expressed (i.e., $P_{g}>0$) even when mean $P_{a}$ values are negative (Figure 2).
@@
 
-When either pre-copulatory or post-copulatory inbreeding strategy allele values were fixed to zero and could not evolve, the alternative inbreeding strategy evolved to inbreeding avoidance even when costly (Figure 3A,C).
+When either pre-copulatory or post-copulatory inbreeding strategy allele values were fixed to zero, the alternative inbreeding strategy evolved to inbreeding avoidance even when costly (Figure 3A,C).
 However, when one inbreeding strategy could evolve and had zero cost, the other strategy initially evolved towards inbreeding avoidance but then back towards random choice across generations following increasing evolution of inbreeding avoidance (i.e., negative allele values) through the former (zero cost) strategy (Figure 3B,D).
@@
 The opportunity to adjust inbreeding has been widely considered as a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
-Recently, @Duthie found the conditions under which selection for polyandry and pre-copulatory inbreeding avoidance is predicted to be highly restrictive.
+Recently, @Duthie found that the conditions under which selection for polyandry and pre-copulatory inbreeding avoidance is predicted are highly restrictive.
 However, @Duthie assumed that fertilisation of offspring was unbiased with respect to mate kinship, meaning that females could not express post-copulatory choice.
@@
 The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but the existence of selection for post-copulatory inbreeding avoidance causing feedback to select for polyandry has not been formally modelled.
-Our model therefore has widespread implications for empirical studies of evolution of polyandry.
+Our model therefore has widespread implications for future studies of evolution of polyandry.
 
@@
 
-In our model, one cost free inbreeding strategy precluded another more costly inbreeding strategy from persisting in a focal population (Figure 2), meaning that long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given cost asymmetry.
+In our model, one cost free inbreeding strategy precluded another more costly inbreeding strategy from persisting in a focal population (Figure 3), meaning that long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given cost asymmetry.
 Direct costs therefore strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies.
@@
 
-![Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fiext to zero (i.e., random fertilisation) or (B, D, F, H) allowed to evolve freeely.
+![Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fixed to zero (i.e., random fertilisation) or (B, D, F, H) allowed to evolve freely.
 Costs of polyandry (c_p) increase across rows from zero (A and B) to 0.01 (G and H).

### 2016-11-11 pre_post_biorxiv.tex
Several tweaks, mostly fix typos

@@
 Importantly, evolution of post-copulatory inbreeding avoidance requires that females are polyandrous, defined as mating with multiple males during a single reproductive bout.
-Further, such polyandry could itself evolve because it allows females to mate with additional unrelated males following initial mating with a relative, thereby facilitating pre-copulatory inbreeding avoidance even in the absence of any post-copulatory female choice or otherwise biased fertilisation (e.g., given a 'fair raffle' among sperm provided by females' mates).
-As a reproductive strategy, polyandry can thereby simultaneously allow females to mate with less closely related males and creates the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
+Further, such polyandry could itself evolve because it allows females to mate with additional unrelated males following initial mating with a relative, thereby facilitating pre-copulatory inbreeding avoidance even in the absence of any post-copulatory female choice or otherwise biased fertilisation (e.g., given a `fair raffle' among sperm provided by females' mates).
+As a reproductive strategy, polyandry can thereby simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
 Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness \cite[][]{Zeh1997, Jennions2000, Tregenza2002, Akcay2007}.
@@
 
-Meanwhile, empirical studies of diverse species have found evidence for female inbreeding avoidance enacted through pre-copulatory or post-copulatory routes, or both.
+Meanwhile, studies of diverse species have found evidence for female inbreeding avoidance enacted through pre-copulatory or post-copulatory routes, or both.
 For example, pre-copulatory inbreeding avoidance has been documented in weevils, birds, and butterflies \cite[e.g.,][]{Kuriwada2011, Kingma2013, Fischer2015}, and post-copulatory inbreeding avoidance has been documented in crickets \cite[e.g.,][]{Simmons2006, Bretman2009}.
@@
 Other studies found no evidence of pre-copulatory or post-copulatory inbreeding avoidance despite strong inbreeding depression \cite[e.g.,][]{Reid2014, Reid2015}.
-These empirical studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature.
-However, there is as yet no modelling framework that predicts \textit{a priori} what combinations should be favoured by selection when both pre-copulatory and post-copulatory inbreeding avoidance, and polyandry, can evolve.
+These studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature.
+However, there is as yet no modelling framework that predicts what combinations should be favoured by selection when both pre-copulatory and post-copulatory inbreeding avoidance, and polyandry, can evolve.
 Such a framework would allow prediction of the form of mating system evolution across different systems that experience inbreeding depression and allow existing empirical studies to be compared to model predictions.
+
+\subsection*{Verbal theory}
 
@@
 
-\section*{Model}
+\section*{Methods}
 
@@
 Individuals are defined as related if they share a common ancestor within the population pedigree (i.e., non-zero kinship).
-Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of the three reproductive strategy traits: tendency for polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., `mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$ i.e., `fertilisation' alleles).
+Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of the three reproductive strategy traits: tendency for polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., `mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$, i.e., `fertilisation' alleles).
 Alleles can take any real number \cite[i.e., a continuum-of-alleles model;][]{Kimura1965, Lande1976, Reeve2000, Bocedi2014} and combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for each trait.
 In overview, each generation proceeds with females paying costs, expressing polyandry, mating, and fertilisation.
-Offspring inherit a randomly sampled allele from each parent at each locas with no physical linkage.
+Offspring inherit a randomly sampled allele from each parent at each locus with no physical linkage.
 Alleles can then mutate and offspring express inbreeding depression.
@@
 Equation 1 assumes independent allelic effects, generating multiplicative effects on offspring viability \cite[][]{Morton1956, Mills1994}.
-We model inbreeding depression as having an absolute rather than relative effect on offspring viability) i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
+We model inbreeding depression as having an absolute rather than relative effect on offspring viability (i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
 We also assume that inbreeding always decreases offspring viability, $\beta > 0$ (i.e., no outbreeding depression).
@@
 
-\subsection*{Model analysis}
+\subsection*{Simulation and analysis}
 
@@
 {%
-   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{10 mm} \textbf{Figure 1:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fiext to zero (i.e., random fertilisation) or (B, D, F, H) allowed to evolve freeely.
+   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{10 mm} \textbf{Figure 1:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fixed to zero (i.e., random fertilisation) or (B, D, F, H) allowed to evolve freely.
 Costs of polyandry ($c_{p}$) increase across rows from zero (A and B) to 0.01 (G and H).
@@
 The opportunity to adjust inbreeding has been widely considered as a driver of adaptive evolution of polyandry \cite[][]{Tregenza2002, Foerster2003, Akcay2007, Varian-Ramos2012, Kingma2013, Lehtonen2015, Reid2014}.
-Recently, \cite{Duthie} found the conditions under which selection for polyandry and pre-copulatory inbreeding avoidance is predicted to be highly restrictive.
+Recently, \cite{Duthie} found that the conditions under which selection for polyandry and pre-copulatory inbreeding avoidance is predicted are highly restrictive.
 However, \cite{Duthie} assumed that fertilisation of offspring was unbiased with respect to mate kinship, meaning that females could not express post-copulatory choice.
@@
 The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new \cite[e.g.,][]{Zeh1997}, but the existence of selection for post-copulatory inbreeding avoidance causing feedback to select for polyandry has not been formally modelled.
-Our model therefore has widespread implications for empirical studies of evolution of polyandry.
+Our model therefore has widespread implications for future studies of evolution of polyandry.
 
@@
 Recent studies have shown how females can successfully bias fertilisation after mating has occurred.
-For example, when female guppies (*Poecilia reticulata*) were artificially inseminated with equal quantities of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full siblings' sperm were reduced by females' ovarian fluids \cite[][]{Gasparini2011}.
-In black field crickets (\textit{Teleogryllus commodus}), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs \cite{Bussiere2006, Tuni2013}.
+For example, when female guppies (\textit{Poecilia reticulata}) were artificially inseminated with equal quantities of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full siblings' sperm were reduced by females' ovarian fluids \cite[][]{Gasparini2011}.
+In black field crickets (\textit{Teleogryllus commodus}), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs \cite[][]{Bussiere2006, Tuni2013}.
 Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for further polyandry, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).

### 2016-11-28 ms_pre_post.Rmd
Add Fisher reference somewhere note

@@
 ---
-title: "Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry"
-author: "A. Bradley Duthie, Greta Bocedi, Ryan R. Germain, Matthew E. Wolak, and Jane M. Reid"
+title: Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated
+  polyandry
+author: A. Bradley Duthie, Greta Bocedi, Ryan R. Germain, Matthew E. Wolak, and Jane
+  M. Reid
 date: "August 24, 2016"
 output:
+  pdf_document:
+    fig_caption: yes
+  html_document: default
   word_document:
@@
     reference_docx: docx_template.docx
-  pdf_document:
-    fig_caption: yes
-  html_document: default
 header-includes:
@@
 ******************************
+
+<!--- Will most likely need to read and cite \cite{Fisher2016} here (Fisher et al. 2016 Behavioural Ecology -- pre- and post-copulatory competition using network theory --->
 

### 2016-12-10 ms_pre_post.Rmd
New revisions following coauthor comments: edit first paragraph of methods

@@
 
-We model evolution of polyandry and pre-copulatory and post-copulatory inbreeding avoidance by tracking reproductive interactions among individual females and males in a small focal population.
+We model evolution of polyandry and pre-copulatory and post-copulatory inbreeding avoidance by tracking the dynamics of alleles underlying reproductive strategies enacted by interacting females and males within a small focal population.
 Individuals are defined as related if they share a common ancestor within the population pedigree (i.e., non-zero kinship).
 Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of the three reproductive strategy traits: tendency for polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$, i.e., 'fertilisation' alleles).
-Alleles can take any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014] and combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for each trait.
+All alleles can take any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014] and combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for each of the three traits whereby an individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
 In overview, each generation proceeds with females paying costs, expressing polyandry, mating, and fertilisation.

### 2016-12-10 ms_pre_post.Rmd
Methods edits up through fertilisation

@@
 Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
-Absolute values are used for applying costs to inbreeding strategies as appropriate because both negative and positive $M_{p}$ and $F_{p}$ values affect the degree of inbreeding.
+Absolute values are used for applying costs to inbreeding strategies because both negative and positive $M_{p}$ and $F_{p}$ values affect the degree of inbreeding.
 In contrast, only positive values of $P_{p}$ cause females to be polyandrous (see below).
-Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases as a linear function with each trait value.
+Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with each trait value.
 
@@
 This ensures that all surviving females choose at least one mate, and causes some stochastic variation around the expected mean $N_{males}$ of $P_{p}+1$.
-A female's value of $P_{p}$ depends on the sum of her 20 $P_{a}$ allele values, which might be negative or positive.
+A female's value of $P_{p}$ depends on the sum of her 20 $P_{a}$ allele values (i.e., $P_{g}$), which might be negative or positive.
 However, because females cannot mate with a negative number of males, $P_{p}$ is constrained to be zero or positive such that $P_{p} = 0$ when $P_{g} < 0$, but $P_{p} = P_{g}$ when $P_{g} \geq 0$.
-Polyandry is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998; @Duthie] that is influenced by continuous genetic variation but only expressed at the threshold value of $P_{g} > 0$.
+Polyandry is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998; @Duthie] that is influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
 Any negative $P_{g}$ value therefore generates phenotypic monandry, while positive $P_{g}$ values can lead to different degrees of realised polyandry (i.e., different numbers of mates, $N_{males}$).
 
-Mating
+Mating and pre-copulatory inbreeding avoidance
 ----------------------------------------------
@@
 Most often, $N_{males}$ will be smaller than the total number of available males [@Duthie].
-Here, each female chooses her $N_{males}$ mates based on her pre-copulatory inbreeding strategy phenotype ($M_{p}$), which equals her pre-copulatory inbreeding strategy genotype ($M_{g}$) defined as the sum of the values of her 20 $M_{a}$ alleles.
-Negative or positive $M_{p}$ values cause a female to avoid or prefer mating with kin, respectively.
-Values of $M_{p}=0$ cause females to mate randomly with respect to kinship.
+Each female then chooses her $N_{males}$ mates based on her pre-copulatory inbreeding avoidance phenotype ($M_{p}$), which equals her genotype ($M_{g}$).
+Negative or positive $M_{p}$ values cause a female to avoid or prefer mating with kin, respectively, whereas $M_{p}=0$ cause females to mate randomly with respect to kinship.
 
-The probability that a focal female $i$ mates with a male $j$ with which she shares some kinship $k_{ij}$ is calculated by first assigning each male a perceived mate quality $Q^{m}_{ij}$.
+To calculate the probability that a focal female $i$ mates with a male $j$ to whom she is related by some kinship $k_{ij}$, each male is first assigned a perceived mate quality $Q^{m}_{ij}$.
 If the female has a strategy of pre-copulatory inbreeding avoidance ($M_{p}<0$), then $Q^{m}_{ij} = (-M_{p} \times k_{ij} + 1)^{-1}$, meaning that $Q^{m}_{ij}$ decreases linearly with increasingly positive values of $k_{ij}$ and increasingly negative values of $M_{p}$.
 If the female has a strategy of pre-copulatory inbreeding preference ($M_{p}>0$), then $Q^{m}_{ij} = M_{p} \times k_{ij} + 1$, meaning that $Q^{m}_{ij}$ increases with increasingly positive $k_{ij}$ and $M_{p}$.
-If $M_{p}=0$, then all males are assigned a quality of 1
+If $M_{p}=0$, then all males are assigned $Q^{m}_{ij}=1$.
 
-After a focal female assigns all males a $Q^{m}_{ij}$ value, each male's value is divided by the sum of all $Q^{m}_{ij}$ values across all males, thereby assigning each male a relative perceived quality $q^{m}_{ij}$, which is constrained to values between zero and one.
-The value of $q^{m}_{ij}$ then defines the probability that a focal female mates with the male; mating is therefore stochastic, and females do not always mate with the male of the highest $q^{m}_{ij}$.
+Each male's value with respect to each focal female is then divided by the sum of all $Q^{m}_{ij}$ values across all males with respect to that female, thereby assigning each male a relative perceived quality $q^{m}_{ij}$, which is constrained to values between zero and one.
+The value of $q^{m}_{ij}$ then defines the probability that a focal female mates with the male.
+Mating is realised by placing each $q^{m}_{ij}$ value into a vector whose elements sum to unity, and a random uniform number is then generated to sample a single male from this vector.
+Mating is therefore stochastic, and females do not always mate with the male of the highest $q^{m}_{ij}$.
 For polyandrous females that choose multiple mates (i.e., $N_{mates}>1$), mates are chosen iteratively such that $Q^{m}_{ij}$ and $q^{m}_{ij}$ are re-calculated for each additional mate choice, and with $Q^{m}_{ij}$ and therefore $q^{m}_{ij}$ values of already chosen males set to zero to ensure mate sampling without replacement.
@@
 
-Fertilisation
+Fertilisation and post-copulatory inbreeding avoidance
 ----------------------------------------------

### 2016-12-10 ms_pre_post.Rmd
Edit methods up through simulation and analysis, which is going to need more careful attention -- note that we're *not* looking at a situation where pre-copulatory inbreeding avoidance facilitates evolution of polyandry, so this can't make it into the methods (and maybe should be clear)

@@
 Following mating, fertilisation occurs such that each of a female's $n$ offspring is independently assigned a sire (with replacement) from the $N_{males}$ with which the female mated.
-Sire identity depends on female's kinship with each potential sire ($k_{ij}$) and her post-copulatory inbreeding strategy phenotype ($F_{p}$), which equals her post-copulatory inbreeding strategy genotype ($F_{g}$), defined as the sum of the values of her 20 $F_{a}$ alleles.
-Negative and positive values of $F_{p}$ correspond to post-copulatory inbreeding avoidance or preference, respectively, and $F_{p}=0$ causes random fertilisation with respect to kinship.
+Sire identity depends on female's kinship with each mate ($k_{ij}$) and her post-copulatory inbreeding strategy phenotype ($F_{p}$), which equals her genotype ($F_{g}$).
+Negative and positive values of $F_{p}$ correspond to post-copulatory inbreeding avoidance or preference, respectively, whereas $F_{p}=0$ causes random fertilisation with respect to kinship.
 
-The probability that an offspring of a focal female $i$ is sired by any one of $i$'s mates $j$ is calculated by assigning a perceived fertilisation quality to each $j$, $Q^{f}_{ij}$.
+The probability that an offspring of a focal female $i$ is sired by any one of $i$'s mates $j$ is calculated by assigning a perceived fertilisation quality to each $j$ with respect to $i$, $Q^{f}_{ij}$.
 Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if a focal female has a strategy of post-copulatory inbreeding avoidance ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$.
@@
 These $q^{f}_{ij}$ values, which lie between zero and one, define the probability of paternity.
+As with mate choice, $q^{f}_{ij}$ values are placed into a vector whose elements sum to unity, and a random uniform number is used to sample paternity.
+Females produce $n$ offspring, so $q^{f}{ij}$ values are sampled $n$ times independently and with replacement for each female to determine the realised distribution of sires.
+<!--- This last sentence has now been added back in, with another explaining it further.
+These things seem to get taken out as extraneous, but then added back in because the methods are not clear when they are removed --->
 
@@
 When a mutation occurs, a mutation effect is sampled from a normal distribution with a mean of zero and a standard deviation of $\mu_{SD}$ and added to the original allele value [@Kimura1965; @Lande1976; @Bocedi2014; @Duthie].
-The value of $\mu_{SD}$ is set to $\sqrt{1/20}$, which scales the variance of mutation effect size to the total number of alleles affecting each phenotype.
+The value of $\mu_{SD}$ is set to $\sqrt{1/20}$.
 
@@
 
-The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a log-linear function of her kinship with the sire of her offspring $j$ ($k_{ij}$) and inbreeding depression slope $\beta$,
+The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a log-linear function of her kinship with the sire $j$ of her offspring ($k_{ij}$) and inbreeding depression slope $\beta$,
 \begin{equation}
@@
 We model inbreeding depression as having an absolute rather than relative effect on offspring viability (i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
-We also assume that inbreeding always decreases offspring viability, $\beta > 0$ (i.e., no outbreeding depression).
-Therefore, because $k_{ij}$ is constrained to values between zero and one, $-\beta \times k_{ij} \leq 0$.
+We also assume that inbreeding always decreases offspring viability (i.e., $\beta > 0$, no outbreeding depression).
+Therefore, because $0 \leq k_{ij} \leq 1$, $-\beta \times k_{ij} \leq 0$.
 Values of $\Psi_{\textrm{off}}$ must therefore be between zero (if $-\beta \times k_{ij}$ is very negative) and one (if $-\beta \times k_{ij} = 0$).
@@
 Immigration therefore prevents the mean kinship within the population from asymptoting to one over generations.
-To ensure that immigrants do not directly affect genotypic or phenotypic values of tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$), immigrants are always male.
-Consequently, they can be chosen as females' mates based on their kinship values of zero but do not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$.
-Further, immigrants $P_{a}$, $M_{a}$, and $F_{a}$ allele values are randomly sampled from normal distributions with means and standard deviations equal to those in the focal population at the time of immigration.
+To ensure that immigrants do not directly affect genotypic or phenotypic values of tendency for polyandry or pre-copulatory or post-copulatory inbreeding avoidance, immigrants are always male.
+Consequently, they can be chosen as females' mates based on their values of $k_{ij}=0$ but do not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$.
+Further, immigrants $P_{a}$, $M_{a}$, and $F_{a}$ allele values are randomly sampled from normal distributions with means and standard deviations equal to those in the focal population at the time of immigration, meaning that they do not directly cause any change in the distribution of allele values.
 We thereby effectively assume that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$.

### 2016-12-15 ms_pre_post.Rmd
Revise abstract

@@
   polyandry
-author: A. Bradley Duthie, Greta Bocedi, Ryan R. Germain, Matthew E. Wolak, and Jane
-  M. Reid
-date: "August 24, 2016"
+author: "A. Bradley Duthie, Ryan R. Germain, and Jane M. Reid"
+date: "December 15, 2016"
 output:
-  pdf_document:
-    fig_caption: yes
-  html_document: default
   word_document:
@@
     reference_docx: docx_template.docx
+  pdf_document:
+    fig_caption: yes
+  html_document: default
 header-includes:
@@
 
-Inbreeding avoidance has been widely hypothesised to evolve through pre-copulatory and post-copulatory mechanisms as a consequence of inbreeding depression in offspring viability.
-However, no modelling compares evolution of pre-copulatory and post-copulatory inbreeding avoidance jointly, and given biologically relevant costs of inbreeding strategies.
-Critically, evolution of post-copulatory inbreeding avoidance is restricted to females that mate multiply, potentially leading to complex evolutionary dynamics among inbreeding strategies and polyandry.
-Accordingly, we use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address three questions: (1) Does evolution of post-copulatory inbreeding avoidance facilitate evolution of costly polyandry?
-(2) Is evolution of one costly inbreeding strategy inhibited by another non-costly alternative strategy?
-And (3) is evolution of one inbreeding strategy precluded by existence of another already adaptive strategy?
-We show that evolution of polyandry is facilitated by post-copulatory inbreeding avoidance.
-Evolution of relatively low cost inbreeding avoidance strategies was observed, while selection for functionally redundant high cost strategies decreased over generations.
-Finally, existence of an adaptive inbreeding strategy precluded evolution of post-copulatory, but not pre-copulatory, inbreeding avoidance.
-Our model thereby introduces a novel framework for predicting evolution of both pre-copulatory and post-copulatory inbreeding strategies in empirical systems.
+Inbreeding avoidance has been widely hypothesised to evolve through pre-copulatory and post-copulatory mechanisms as a consequence of inbreeding depression in offspring viability and female multiple mating (polyandry).
+However, no theoretical framework exists from which to derive hypothese concerning joint evolution of pre-copulatory and post-copulatory inbreeding avoidance.
+Evolution of post-copulatory inbreeding avoidance necessitates polyandry, potentially leading to complex evolutionary dynamics among inbreeding strategies and female mating frequency, each of which might be affected by direct negative costs.
+Hence, we use individual-based modelling to quantify evolution of interacting pre- and post-copulatory inbreeding avoidance and associated polyandry across multiple cost combinations given severe inbreeding depression.
+We find that evolution of post-copulatory inbreeding avoidance increases selection for polyandry, that selection for costly inbreeding strategies was weak or negligible given a non-costly alternative strategy.
+Established pre-copulatory inbreeding avoidance generally precluded evolution of polyandry and therefore inbreeding avoidance, but established post-copulatory inbreeding aviodance did not preclude pre-copulatory inbreeding avoidance from evolving.
+We thereby provide a general framework for understanding evolution of pre- and/or post-copulatory inbreeding avoidance across systems, and conclude that evolution of inbreeding avoidance phenotypes and associated polyandry are predicted to interact and be strongly affected by direct costs.
 

### 2016-12-15 ms_pre_post.Rmd
Edit up to right before the (soon to be former?) 'Verbal Theory' subsection in the introduction

@@
 Evolution of post-copulatory inbreeding avoidance necessitates polyandry, potentially leading to complex evolutionary dynamics among inbreeding strategies and female mating frequency, each of which might be affected by direct negative costs.
-Hence, we use individual-based modelling to quantify evolution of interacting pre- and post-copulatory inbreeding avoidance and associated polyandry across multiple cost combinations given severe inbreeding depression.
+Hence, we use individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry across multiple cost combinations given severe inbreeding depression.
 We find that evolution of post-copulatory inbreeding avoidance increases selection for polyandry, that selection for costly inbreeding strategies was weak or negligible given a non-costly alternative strategy.
 Established pre-copulatory inbreeding avoidance generally precluded evolution of polyandry and therefore inbreeding avoidance, but established post-copulatory inbreeding aviodance did not preclude pre-copulatory inbreeding avoidance from evolving.
-We thereby provide a general framework for understanding evolution of pre- and/or post-copulatory inbreeding avoidance across systems, and conclude that evolution of inbreeding avoidance phenotypes and associated polyandry are predicted to interact and be strongly affected by direct costs.
+We thereby provide a general framework for understanding evolution of pre-copulatory and/or post-copulatory inbreeding avoidance across systems, and conclude that evolution of inbreeding avoidance phenotypes and associated polyandry are predicted to interact and be strongly affected by direct costs.
 
@@
 
-Inbreeding often greatly reduces the fitness of inbred offspring [termed 'inbreeding depression'; @Charlesworth1999; @Keller2002; @Charlesworth2009].
-Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple reproductive decisions in species with obligate biparental reproduction [@Parker1979; @Parker2006; @Pusey1996; @Szulkin2012].
-From the perspective of a focal breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred, meaning that related males are less likely to sire offspring (i.e., post-copulatory inbreeding avoidance).
-Importantly, evolution of post-copulatory inbreeding avoidance requires that females are polyandrous, defined as mating with multiple males during a single reproductive bout.
-Further, such polyandry could itself evolve because it allows females to mate with additional unrelated males following initial mating with a relative, thereby facilitating pre-copulatory inbreeding avoidance even in the absence of any post-copulatory female choice or otherwise biased fertilisation (e.g., given a 'fair raffle' among sperm provided by females' mates).
-As a reproductive strategy, polyandry can thereby simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
-Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007].
-However, despite such well-established hypotheses, no modelling investigates conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are likely to evolve, or predicts how such evolution will feed back to affect underlying evolution of polyandry.
+<!--- Note that there are twice as many butterfly species and about eight times as many weevil species as there are bird species.
+I think that weevils and butterflies can be on at least equal footing with birds in terms of generality --->
 
-Meanwhile, studies of diverse species have found evidence for female inbreeding avoidance enacted through pre-copulatory or post-copulatory routes, or both.
-For example, pre-copulatory inbreeding avoidance has been documented in weevils, birds, and butterflies [e.g., @Kuriwada2011; @Kingma2013; @Fischer2015], and post-copulatory inbreeding avoidance has been documented in crickets [e.g., @Simmons2006; @Bretman2009].
-Evidence of both pre-copulatory and post-copulatory inbreeding avoidance has accumulated for some well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015].
-While most studies consider either pre-copulatory or post-copulatory inbreeding avoidance in isolation, a small number of studies consider both.
-Accordingly, @Liu2014 found evidence of pre-copulatory, but not post-copulatory, inbreeding avoidance in cabbage beetles (*Colaphellus bowringi*).
-Other studies found no evidence of pre-copulatory or post-copulatory inbreeding avoidance despite strong inbreeding depression [e.g., @Reid2014; @Reid2015].
-These studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature.
-However, there is as yet no modelling framework that predicts what combinations should be favoured by selection when both pre-copulatory and post-copulatory inbreeding avoidance, and polyandry, can evolve.
-Such a framework would allow prediction of the form of mating system evolution across different systems that experience inbreeding depression and allow existing empirical studies to be compared to model predictions.
+Inbreeding, defined as reproduction between relatives, often greatly reduces the fitness of resulting inbred offspring [termed 'inbreeding depression'; @Charlesworth1999; @Keller2002; @Charlesworth2009].
+Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple reproductive decisions [@Parker1979; @Parker2006; @Pusey1996; @Szulkin2012].
+From the perspective of a focal breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), and by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
+Evolution of post-copulatory inbreeding avoidance requires that females are polyandrous, defined as mating with multiple males during a single reproductive bout.
+Further, such polyandry could itself evolve because it allows females to mate with additional unrelated males following an initial mating with a relative, thereby facilitating pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation (i.e., given a 'fair raffle' among sperm provided by females' mates).
+Polyandry can thereby simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
+Polyandry, which might not increase female reproductive success and therefore requires explanation [@Parker2013], has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002].
+However, there is surprisingly little theory or modelling that critically examines such widely-invoked hypotheses, and hence examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or how evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
+
+Despite a lack of non-verbal theory and resulting predictions, numerous studies on diverse species have found evidence for female inbreeding avoidance.
+However, only a few such studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
+Among these few studies, pre-copulatory inbreeding avoidance has been documented in weevils, birds, and butterflies [e.g., @Kuriwada2011; @Kingma2013; @Fischer2015], and post-copulatory inbreeding avoidance has been documented in crickets [e.g., @Simmons2006; @Bretman2009].
+An even smaller number of studies comprise sufficient evidence for mechanisms of both pre-copulatory and post-copulatory inbreeding avoidance in two well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015].
+A lack of both pre-copulatory and post-copulatory inbreeding has been found in fruit flies [e.g., @Ala-Honkola2011; @Tan2012], and might be reasonably inferred where no evidence of inbreeding avoidance exists [e.g., @Reid2014; @Reid2015].
+To our knowledge, only @Liu2014 consider both pre-copulatory and post-copulatory inbreeding avoidance jointly, finding evidence of pre-copulatory, but not post-copulatory, inbreeding avoidance in cabbage beetles (*Colaphellus bowringi*).
+Taken together, all of these studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature.
+However, there is as yet no framework that predicts what combinations should be favoured by selection when polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all potentially evolve.
+Consequently, there is no framework that allows the diversity of existing empirical results to be rationalised or interpreted, and no clear hypotheses that could be tested with these studies through comparative analyses or that could be applied to future empirical studies of individual systems.
+
+<!--- LEFT OFF HERE ------------------------------------------------------->
 

### 2016-12-16 ms_pre_post.Rmd
Edit up to second to last paragraph of Introduction

@@
 
+A recent genetically-explicit individual-based model examined the conditions under which polyandry is predicted to evolve slely due to selection stemming from pre-copulatory inbreeding avoidance [@Duthie].
+Evolution of polyandry occurred only under highly restricted conditions, requiring that direct costs were small, that very few males were available for a female's initial mate chioce but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
+Without these conditions, increasing polyandry tended to increase rather than decrease the overall degree of inbreeding that females experienced, and hence reduced offspring fitness.
+This occurred because, once pre-copulatory inbreeding avoidance evolved, polyandrous females had already chosen available unrelated males as their initial mates.
+Their additional mates, chosen from the remaining male population, were therefore increasingly likely to include relatives.
+Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance, and hence the resulting degree of inbreeding avoidance, was consequently restricted [@Duthie].
+
+<!--- This is getting awfully narrow in terms of theory; postcopulatory *might* happen given a fairly specific set of conditions concerning evolution of pre-copulatory inbreeding avoidance and polyandry.
+Are we confident these conditions are general?
+--->
+
+<!--- I'm not suggesting that things need to be changed (probably too late for that), just that, to me, this reads as the theoretical equivalent of a very system-specific question being address, not like a question that has broad implications across different systems --->
+
+However, if post-copulatory inbreeding avoidance could also evolve, polyandrous females could further bias paternity towards unrelated males within their set of chosen mates.
+Post-copulatory inbreeding avoidance might consequently reduce the cost of polyandry stemming from the accumulation of related mates, potentially facilitating evolution of polyandry to avoid inbreeding under broader conditions, and driving further consequent evolution of pre-copulatory or post-copulatory mate choice strategies.
+However, once both pre-copulatory and post-copulatory inbreeding avoidance, and resulting polyandry, can evolve, the long-term dynamics of these reproductive strategies become difficult to conceptualise and predict.
+Strong inbreeding depression might drive initial evolution of both pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
+However, if evolution of polyandry and post-copulatory inbreeding avoidance renders pre-copulatory inbreeding avoidance redundant, or vice versa, then only one inbreeding avoidance strategy might be maintained in the long-term.
+
+The few previous models that considered the evolution of inbreeding avoidance through mate choice (as opposed to dispersal) have implicitly or explicitly considered the fate of a rare allele underlying pre-copulatory inbreeding avoidance in a population initially fixed for random mating [e.g., @Parker1979; @Parker2006; @Duthie; @Duthie2016a].
+Such models are useful for isolating the invasion fitness of this single strategy.
+However, when both pre-copulatory and post-copulatory strategies can affect realised inbreeding, it cannot be assumed that both strategies will simultaneously invade a randomly mating population, nor that the invasion fitness of one strategy will be independent of the existence of invasion fitness of the other strategy.
+For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then new alleles underlying polyandry and post-copulatory inbreeding avoidance might be precluded from invading a population because the phenotypic effect of such alleles on the degree of inbreeding could be negligible.
+Conversely, fixation of alleles underlying polyandry and post-copulatory inbreeding avodiance might eliminate positive selection on alleles underlying pre-copulatory inbreeding avoidance.
+New theory, guided by modelling that evaluates invasion dynamics given appropriate sets of evolutionary constraints, is therefore needed.
+
 <!--- LEFT OFF HERE ------------------------------------------------------->
-
-Verbal theory
-----------------------------------------------
-
-A recent genetically-explicit individual-based model showed that selection for alleles underlying polyandry and pre-copulatory inbreeding avoidance, and resulting joint evolution of these reproductive strategies, occurred only under highly constrained conditions [@Duthie].
-Specifically, such evolution occurred when direct costs of polyandry were small, when very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or when polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
-In the absence of these conditions, increasing degrees of polyandry tended to increase the overall degree of inbreeding that females experienced, and hence increase inbreeding depression in offspring fitness.
-This occurred because polyandrous females that had evolved to avoid inbreeding had already chosen available unrelated males as their initial mates.
-Their additional mates, chosen from the remaining male population, were therefore increasingly likely to include relatives.
-Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance was consequently restricted.
-
-However, while @Duthie considered simultaneous evolution of polyandry and pre-copulatory inbreeding avoidance, they did not also allow simultaneous evolution of post-copulatory inbreeding avoidance, and assumed that polyandrous females had no post-copulatory control over fertilisation.
-If post-copulatory inbreeding avoidance could also evolve, polyandrous females could further bias paternity towards unrelated males within their set of chosen mates.
-This process might reduce the cost of polyandry stemming from accumulation of related mates, potentially facilitating evolution of polyandry to avoid inbreeding [@Zeh1997], and driving further consequent evolution of pre-copulatory or post-copulatory mate choice strategies.
-Therefore, while pre-copulatory inbreeding avoidance can facilitate evolution of polyandry under some restrictive conditions [@Duthie], the opportunity for post-copulatory choice might facilitate evolution of polyandry under a much wider range of conditions by allowing females to bias fertilisation toward non-kin.
-The long-term evolutionary dynamics of pre-copulatory and post-copulatory inbreeding avoidance then become unclear.
-Strong inbreeding depression might drive initial evolution of both pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
-However, if evolution of polyandry and post-copulatory inbreeding avoidance renders pre-copulatory inbreeding avoidance redundant, or vice versa, then only one strategy might be maintained in the long-term.
-
-Previous models implicitly or explicitly considered the fate of a rare allele underlying pre-copulatory inbreeding avoidance in a population initially fixed for random mating [e.g., @Parker1979; @Parker2006; @Duthie; @Duthie2016a].
-Such models thereby isolate the invasion fitness of this single strategy.
-However, when both pre-copulatory and post-copulatory strategies can affect realised inbreeding, it cannot be assumed that both strategies will invade simultaneously, nor that invasion fitness of one strategy will be independent of the other.
-For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect of such invading alleles could be weak or negligible.
 

### 2016-12-16 ms_pre_post.Rmd
Edits up through Introduction made: left off now on last Model section. Switching to questions instead of hypotheses

@@
 
-<!--- LEFT OFF HERE ------------------------------------------------------->
+Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will depend not only on the magnitudes of positive indirect selection steming from reduced inbreeding depression in females' offspring, but also on the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
+Polyandrous females can pay costs of mate searching or mating, for example, because these activities increase predation risk [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
+Females that express pre-copulatory choice and consequent reluctance to mate with relatives might pay costs of increased risk of complete mating failure or harm caused by sexual conflict [@Rowe1994; @Kokko2013].
+Females that express post-copulatory choice might pay energetic costs associated with physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
+If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly inbreeding strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
+However, such trajectories will also depend on the indirect benefits of each strategy, which might also differ and vary in relation to the evolution of the other strategy.
+Dynamic models are consequently required to understand and predict evolutionary outcomes.
 
-Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry are likely to be affected by direct negative selection on resulting phenotypes (i.e., costs) and hence on the net costs versus benefits stemming from inbreeding avoidance.
-Polyandrous females can pay costs of mate searching or mating, for example, because these activities increase predation risk [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
-Females that express pre-copulatory choice (e.g., reluctance to mate with relatives) might pay a cost of increased risk of mating failure, or harm caused by sexual conflict [@Rowe1994; @Kokko2013].
-Females that express post-copulatory choice might pay an energetic cost associated with physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
-If the relative costs affecting pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly inbreeding strategy might become fixed in the population over generations, while alleles underlying the more costly inbreeding strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
+<!--- This last sentence sounds good and strong, but it doesn’t actually follow logically from the rest of the paragraph – how do we know that we can’t predict or understand evolutionary outcomes with non-dynamic models, perhaps one that predicts long-term equilibria?
+This doesn’t seem obvious or well argued if we’re just talking about costs and benefits – what, specifically, can a dynamic model (I assume, a simulation, i.e., a model where things change over time) address that another type of model cannot?
+--->
 
-Here we use individual-based modelling to set up *in silico* experiments, which test the hypothesis that, given strong inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance facilitates evolution of polyandry.
-Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution such that only the less costly inbreeding avoidance strategy will be expressed in the long term.
-Finally, we test the hypothesis that evolution of one inbreeding avoidance strategy (i.e., pre-copulatory or post-copulatory) will be precluded if it is introduced into a population that is already fixed for the other inbreeding avoidance strategy that is adaptive.
-We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across different reproductive systems.
+We address three key questions for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression.
+These questions include: (1) Does evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance facilitate evolution of polyandry that is otherwise severely constrained by increasing relatedness of additional mates?
+(2) How do costs associated with polyandry and pre-copulatory and post-copulatory inbreeding avoidance affect evolutionary outcomes and, in particular, the long-term persistence of reproductive strategies given cost assymetry?
+Finally, (3) how is selection for initially rare pre-copulatory or post-copulatory inbreeding avoidance affected if the other strategy of inbreeding avoidance is already fixed?
+By addressing these questions, we provide a framework for exploring the simultaneous evolution of multiple reproductive strategies through the use of individidual-based modelling, and we derive hypotheses amenable to empirical tests within and across taxa.
 
@@
 ----------------------------------------------
+
+<!--- LEFT OFF HERE ------------------------------------------------------->
 

### 2016-12-16 Supplement.tex
Remove some unnecessary white space
Switch Supporting Information figures 1 and 2

@@
 
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{extra_MfPf}: Dynamic \bm{$F_{a}$}, fixed \bm{$P_{a}=1$} and \bm{$M_{a}=-10$}}}{S3}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{allcombs}: All cost combinations}}{S4}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{allcombs}: All cost combinations}}{S3}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{extra_MfPf}: Dynamic \bm{$F_{a}$}, fixed \bm{$P_{a}=1$} and \bm{$M_{a}=-10$}}}{S4}
 \contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P00_E00}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0$}}}{S5}
@@
 \begin{center}				
-\includegraphics[scale=0.8]{figures/extra_MfPf.pdf}
-\end{center}
-\caption{Mean allele values underlying post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid black lines represent grand means over 40 replicate populations, and grey shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance, and positive values reflect strategies of inbreeding preference.
-Red and blue horizontal lines reflect fixed polyandry allele values of $P_{a}=1$ and fixed pre-copulatory inbreeding strategy allele values of $M_{a}=-10$, respectively.
-Panels (A) and (B) show simulations given not costly and costly post-copulatory inbreeding strategy, respectively.
-Dotted horizontal lines show where the y-axis equals zero.}
-\label{extra_MfPf}
-\end{figure}
-
-\clearpage
-\begin{figure}
-\begin{center}				
 \includegraphics[scale=0.82]{figures/evo_combs.pdf}
@@
 \label{allcombs}
+\end{figure}
+
+\clearpage
+\begin{figure}
+\begin{center}				
+\includegraphics[scale=0.8]{figures/extra_MfPf.pdf}
+\end{center}
+\caption{Mean allele values underlying post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid black lines represent grand means over 40 replicate populations, and grey shading around solid lines show standard errors of allele values around grand means.
+Negative mean allele values reflect strategies of inbreeding avoidance, and positive values reflect strategies of inbreeding preference.
+Red and blue horizontal lines reflect fixed polyandry allele values of $P_{a}=1$ and fixed pre-copulatory inbreeding strategy allele values of $M_{a}=-10$, respectively.
+Panels (A) and (B) show simulations given not costly and costly post-copulatory inbreeding strategy, respectively.
+Dotted horizontal lines show where the y-axis equals zero.}
+\label{extra_MfPf}
 \end{figure}

### 2016-12-16 ms_pre_post.Rmd
Edits up through end of Model

@@
 
-Methods
+Model
 ===================================================
@@
 
-<!--- LEFT OFF HERE ------------------------------------------------------->
+<!--- Note given previous comments: I've reworded because we don't know that pre-copulatory inbreeding avoidance is facilitating evolution of polyandry, not anymore.
+With the addition of post-copulatory strategy, it might be hindering it instead.
+If we wanted the answer to this, we would need to fix different levels of post-copulatory inbreeding avoidance and see if we get the same pattern as in Duthie et al.
+(2016) Evolution.
+We might not see the same result of pre-copulatory inbreeding avoidance facilitating evolution of polyandry.
+--->
 
-To test the hypothesis that evolution of post-copulatory inbreeding avoidance can facilitate evolution of costly polyandry, we compare simulations in which polyandry and pre-copulatory and post-copulatory inbreeding can all evolve, with otherwise identical simulations in which post-copulatory inbreeding strategy cannot evolve given four different costs of polyandry ($c_{P} = \{0, 0.0025, 0.005,  0.01\}$).
-To prevent $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes cause random fertilisation with respect to kinship.
-Hence $F_{a}$ alleles have no phenotypic effect, meaning that polyandrous females cannot enact post-copulatory inbreeding avoidance.
+<!--- The above point is especially problematic here because in the absence of post-copulatory inbreeding avoidance (in the current model) pre-copulatory inbreeding avoidance definitely does not facilitate evolution of costly polyandry -- this only happens under the severe constraints of our previous Evolution paper.
+Hence, it would have been a bit strange to suggest that post-copulatory inbreeding avoidance works `alongside' pre-copulatory inbreeding avoidance when we know that pre-copulatory inbreeding avoidance isn't doing anything.
+--->
 
-To test the hypothesis that selection for a costly strategy of inbreeding avoidance will be negligible given a less costly alternative strategy, we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where the cost of pre-copulatory inbreeding strategy $c_{M}=0$ but the cost of post-copulatory inbreeding strategy $c_{F}=0.02$, and vice versa.
+To address whether or not evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance can facilitate evolution of polyandry, we compare simulations in which polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, with otherwise identical simulations in which post-copulatory inbreeding avoidance cannot evolve given four different costs of polyandry ($c_{P} = \{0, 0.0025, 0.005,  0.01\}$).
+To prevent post-copulatory inbreeding avoidance from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes cause random fertilisation with respect to kinship, so $F_{a}$ alleles have no phenotypic effect.
+
+To address how asymmetric costs associated with pre-copulatory and post-copulatory inbreeding avoidance and polyandry affect the long-term persistence of reproductive strategies, we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where the cost of pre-copulatory inbreeding strategy $c_{M}=0$ but the cost of post-copulatory inbreeding strategy $c_{F}=0.02$, and vice versa.
 We compare these simulations with evolution of a costly strategy in the absence of evolution of an alternative strategy (e.g., evolution of pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy phenotype is fixed at zero, $F_{p}=0$).
+In Supporting Information, we present results for all possible cost combinations of $0$ and $0.02$.
 
-To test the hypothesis that the existence of adaptive post-copulatory inbreeding avoidance will preclude the invasion of pre-copulatory inbreeding avoidance, or vice versa, we first used exploratory simulations to determine evolution of pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation.
-To test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance was already established, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., meaning that $F_{p}$ and $P_{p}$ did not evolve).
-Similarly, to test whether post-copulatory inbreeding avoidance evolved when pre-copulatory inbreeding avoidance was already established, we initiated $F_{a}$ and $P_{a}$ allele values at zero but fixed $M_{a}$ allele values at $-10$.
+To address how selection on an initially rare strategy of pre-copulatory or post-copulatory inbreeding avoidance is affected by the existence of the other strategy of inbreeding avoidance already being fixed, we first used exploratory simulations to quantify evolution of pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation.
+Then, to test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance was already established, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., meaning that $F_{p}$ and $P_{p}$ did not evolve).
+Similarly, to test whether post-copulatory inbreeding avoidance would evolve when pre-copulatory inbreeding avoidance was already established, we initiated $F_{a}$ and $P_{a}$ allele values at zero but fixed $M_{a}$ allele values at $-10$.
 Consequently, because females have 10 diploid loci, when $M_{a}$ or $F_{a}$ alleles were fixed at $-10$, outbred females were $51$ times less likely to choose a full brother and $13.5$ times times less likely to choose a first cousin than a non-relative in pre-copulatory and post-copulatory choice, respectively.
 
-In all simulations, we record mean values of $P_{a}$, $M_{a}$, $F_{a}$ in each generation.
-Each combination of parameter values simulated is replicated $40$ times, and grand mean values and standard errors of means are calculated in each generation across replicates.
-These analyses allow us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on post-copulatory inbreeding strategy might be weak if polyandry is rare).
-For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling [@Duthie] showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
+In all simulations, we recorded mean values of $P_{a}$, $M_{a}$, and $F_{a}$ in each generation, and we present these values over generations to infer selection on phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$).
+Each combination of parameter values simulated was replicated $40$ times, and grand mean values and standard errors of means are calculated in each generation across replicates.
+These analyses allow us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potential evolutionary feedbacks among reproductive strategies (e.g., selection on post-copulatory inbreeding strategy might be weak if polyandry is rare).
+For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling [@Duthie] showed to be sufficient for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
 For all replicates, we set $\rho=5$ immigrants, which produced a range of kin and non-kin in each generation allowing females to express inbreeding strategies, and $n=8$ offspring, which was sufficient to keep populations consistently at carrying capacities and avoid population extinction.
-Values of $K_{f}$ and $K_{m}$ were both set to 100 because previous modelling has shown that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but populations are also not so small that selection is typically overwhelmed by genetic drift [@Duthie2016a].
+Values of $K_{f}$ and $K_{m}$ were both set to 100 because previous modelling showed that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but not so small that selection is typically overwhelmed by genetic drift [@Duthie2016a].
 
 ******************************
+
+<!--- LEFT OFF HERE ------------------------------------------------------->
 

### 2016-12-16 ms_pre_post.Rmd
Edit first subsection of results

@@
 
-<!--- LEFT OFF HERE ------------------------------------------------------->
-
 Results
@@
 
-When post-copulatory inbreeding avoidance alleles ($F_{a}$) were fixed to zero and $F_{p}$ could not evolve, $P_{a}$ values were always negative (Figure 1A,C,E,G).
-This shows that there is selection against unconditional polyandry even given zero direct cost ($c_{P}=0$; Figure 1A).
-This is because polyandrous females sampled more males from the available population and were consequently likely to mate with some relatives and hence produce some inbred offspring with low viability [@Duthie2016].
+When post-copulatory inbreeding avoidance alleles ($F_{a}$) were fixed to zero, meaning that $F_{p}$ could not evolve, $P_{a}$ alleles underlying polyandry always decreased to negative values over generations (Figure 1A,C,E,G).
+This shows that despite strong inbreeding depression in offspring viability, there is selection against unconditional polyandry even given zero direct cost ($c_{P}=0$; Figure 1A).
+This is because values of the $M_{a}$ also evolved to be negative, meaning that females typically avoided inbreeding through their initial mating.
+Polyandrous females that subsequently sampled more males from the available population were consequently more likely to mate with some relatives and hence produce some inbred offspring with low viability [@Duthie].
 
-When post-copulatory inbreeding avoidance was allowed to evolve, mean $P_{a}$ values were substantially higher than in comparable simulations where post-copulatory inbreeding avoidance could not evolve (Figure 1B,D,F,H).
+<!--- Changed several things back here because alleles cannot evolve --->
+
+When post-copulatory inbreeding avoidance was allowed to evolve, mean $P_{a}$ values became substantially higher than in comparable simulations where $F_{a}$ values were fixed to zero and post-copulatory inbreeding avoidance could not evolve (Figure 1B,D,F,H).
 Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry.
@@
 
-Strong post-copulatory inbreeding avoidance consistently evolved in all simulations where such evolution was allowed (Figure 1B,D,F,H), even when $P_{a}$ values were expected to be slightly negative (i.e., when there is selection against polyandry, Figure 1F,H).
+Strong post-copulatory inbreeding avoidance, manifested as very negative $F_{a}$ values, consistently evolved in all simulations where such evolution was allowed (Figure 1B,D,F,H).
+Evolution of post-copulatory inbreeding avoidance occurred even when $P_{a}$ values were expected to be slightly negative, and hence when there was selection against polyandry, (Figure 1F,H).
 This reflects the threshold nature of phenotypic expression of polygenic polyandry, wherein random sampling of alleles means that polyandry is commonly expressed (i.e., $P_{g}>0$) even when mean $P_{a}$ values are negative (Figure 2).
-This means that there is commonly opportunity for expression of post-copulatory inbreeding avoidance and associated selection that drives evolution of $F_{a}$ allele values.
+This means that, even in populations where female reproductive strategy evolves toward monandry, there is still commonly some opportunity for expression of post-copulatory inbreeding avoidance and associated selection that drives evolution of $F_{a}$ allele values.
 
-Strong pre-copulatory inbreeding avoidance also evolved (i.e., $M_{a}<0$) in all simulations, irrespective of $c_{P}$ and irrespective of whether post-copulatory inbreeding avoidance was allowed to evolve (Figure 1).
+Strong pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}<0$) in all simulations, irrespective of $c_{P}$ and irrespective of whether post-copulatory inbreeding avoidance was allowed to evolve or hence whether polyandry evolved (Figure 1).
+This might be expected given strong inbreeding depression in offspring viability, which imposes selection against inbreeding.
+
+<!--- LEFT OFF HERE ------------------------------------------------------->
 

### 2016-12-16 ms_pre_post.Rmd
Add some progress to Discussion; more general stuff moved forward

@@
 
-Is evolution of one costly inbreeding strategy inhibited by another non-costly alternative strategy?
+How do cost asymmetries affect long-term persistence of reproductive strategies?
 ----------------------------------------------
 
-When either pre-copulatory or post-copulatory inbreeding strategy allele values were fixed to zero, the alternative inbreeding strategy evolved to inbreeding avoidance even when costly (Figure 3A,C).
-However, when one inbreeding strategy could evolve and had zero cost, the other strategy initially evolved towards inbreeding avoidance but then back towards random choice across generations following increasing evolution of inbreeding avoidance (i.e., negative allele values) through the former (zero cost) strategy (Figure 3B,D).
-For example, given fixed $F_{a}=0$, grand mean $M_{a}$ value in the last $10000$ generations was $-0.868$ (Figure 3A), meaning that a female was ca $5.34$ times less likely to choose a full-sibling and ca $2.10$ times less likely to mate with a first cousin than a non-relative given a high cost of pre-copulatory inbreeding avoidance, $c_{M}=0.02$.
+When either pre-copulatory ($M_{a}$) or post-copulatory ($F_{a}$) inbreeding avoidance allele values were fixed to zero, the alternative inbreeding strategy evolved to inbreeding avoidance even when costly (Figure 3A,C).
+Females therefore evolved to avoid inbreeding, and thereby avoid the cost of producing inbred offspring, through whichever route was available.
+
+However, when both pre-copulatory and post-copulatory inbreeding avoidance could evolve, their relative evolutionary dynamics depended on their relative costs.
+When one inbreeding strategy had zero cost, the other strategy initially evolved towards inbreeding avoidance (i.e., negative $M_{a}$ or $F_{a}$) but then evolved back towards random mating or fertilisation (i.e., $M_{a}=0$ or $F_{a}=0$) across generations following increasing evolution of inbreeding avoidance through the cost-free strategy (Figure 3B,D).
+<!--- For example, given fixed $F_{a}=0$, grand mean $M_{a}$ value in the last $10000$ generations was $-0.868$ (Figure 3A), meaning that a female was ca $5.34$ times less likely to choose a full-sibling and ca $2.10$ times less likely to mate with a first cousin than a non-relative given a high cost of pre-copulatory inbreeding avoidance, $c_{M}=0.02$.
 However, when $F_{a}$ allele values could also evolve, grand mean $M_{a}$ allele value in the last $10000$ generations was only $-0.288$ (Figure 3B).
@@
 However, when $M_{a}$ values could also evolve and $P_{a}$ values were negative, grand mean $F_{a}$ value in the last $10000$ generations was only $-0.070$ (Figure 3D).
+--->
+
 Evolution of post-copulatory inbreeding avoidance facilitated evolution of polyandry (Figure 3B,C), while monandry evolved in the absence of post-copulatory inbreeding avoidance (Figure 3A,D; polyandry was cost free in all these simulations).
-Overall, evolution of a costly inbreeding strategy that readily evolved in isolation was greatly impeded by evolution of a less costly strategy.
+<!--- Overall, evolution of a costly inbreeding strategy that readily evolved in isolation was greatly impeded by evolution of a less costly strategy.
+--->
 
-Is evolution of one inbreeding strategy precluded by existence of another already adaptive strategy
+How is evolution of one inbreeding strategy affected by the existence of another already adaptive strategy?
 ----------------------------------------------
 
-When polyandry and post-copulatory inbreeding strategy allele values were fixed for adaptive inbreeding avoidance, pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}$ values became increasingly negative; Figure 4A).
+When polyandry alleles ($P_{a}$) were fixed to be positive so that all females were expected to mate multiply and post-copulatory inbreeding allele ($F_{a}$) values were fixed for adaptive inbreeding avoidance, pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}$ values became increasingly negative; Figure 4A).
 Such evolution still occurred, but to a much smaller degree, when pre-copulatory inbreeding avoidance was costly (Figure 4B).
@@
 
-When pre-copulatory inbreeding strategy values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently trend toward negative values (Figure 4C,D).
-Additionally, mean $P_{a}$ allele values consistently decreased over generations regardless of the cost of post-copulatory inbreeding strategy (Figure 4C,D).
+Conversely, when pre-copulatory inbreeding allele ($M_{a}$) values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently become negative over generations (Figure 4C,D).
+However, in this case, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless whether or not post-copulatory inbreeding strategy was costly (Figure 4C,D).
 Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values among replicates (illustrated by wide standard errors, Figure 4C).
@@
 
-We have used *in silico* experiments to test three key hypotheses concerning evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
-The modelling that we develop provides a novel framework for approaching empirical studies of inbreeding avoidance, using simulations to address relevant knowledge gaps in understanding evolution of polyandry and inbreeding avoidance through pre-copulatory and post-copulatory mechanisms.
-Accordingly, we modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
+Evolution of reproductive strategies cannot be presumed to occur in isolation in wild populations, meaning that observed patterns of reproductive strategy within and across taxa are likely to be affected by evolutionary feedbacks and (potentially asymmetric) costs.
+We have addressed key questions regarding the effect of such feedbacks and costs on evolution of pre-copulatory inbreeding avoidance, post-copulatory inbreeding avoidance, and polyandry.
+A critical analysis of our model results in new predictions concerning evolutionary dynamics given the joint evolution of these traits, which may be used to formulate new empirical hypotheses within and across taxa.
+
+For example, our results highlight a simple but theoretically under-developed conclusion concerning the relationship between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding avoidance.
+Post-copulatory inbreeding avoidance is useless for monandrous females, and most effective for highly polyandrous females that can choose amongst multiple mates to ensure that offspring are fertilised favourably.
+In contrast, pre-copulatory inbreeding avoidance is perhaps most effective for monandrous females and less effective for polyandrous females.
+This conclusion is reflected in our simulation results, as selection for post-copulatory inbreeding avoidance was negligible in monandrous populations, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D).
+The effect of monandry on selection for pre-copulatory inbreeding avoidance was weaker, but pre-copulatory inbreeding avoidance was generally stronger when populations where monandrous (e.g., Figure 3A vs 3B; see also Supporting Information p.
+S1-1).
+In addition to polyandry increasing selection for post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).
+It would therefore be interesting to test the hypothesis that, across taxa, occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with degree of polyandry.
+To test this hypothesis, more work is needed to identify the degree to which females of different species engage in polyandrous and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
+
+Another general inference from our model concerns the dynamics of phenotypes with highly overlapping effects with respect to selection, realised through functionally different traits.
+Pre-copulatory inbreeding avoidance, typically expressed through mating behaviour, versus post-copulatory inbreeding avoidance, typically expressed through phenotypes affecting fertilisation, are both driven by the shared selective pressure of inbreeding depression in offspring viability.
+Hence, evolution of each of these strategies might make the other strategy more or less adaptive by modifying its impact on the degree to which a female avoids inbreeding and consequently has offspring that express inbreeding depression.
+
+<!--- Some general conclusions addressing 1) what future theory should be developed, and 2) what future empirical studies need to consider.
+For 2, need to be aware of both pre- and post-copulatory inbreeding avoidance, potentially, and that the two are not independent, necessarily; cannot find any general theory for what happens when you have this kind of strategy redundancy -- two ways of getting at the same outcome.
+--->
 
@@
 The opportunity to adjust inbreeding has been widely considered as a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
-Recently, @Duthie found that the conditions under which selection for polyandry and pre-copulatory inbreeding avoidance is predicted are highly restrictive.
-However, @Duthie assumed that fertilisation of offspring was unbiased with respect to mate kinship, meaning that females could not express post-copulatory choice.
-In contrast, we found that when post-copulatory inbreeding avoidance could evolve, selection for polyandry was greatly strengthened (Figure 1).
-The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but the existence of selection for post-copulatory inbreeding avoidance causing feedback to select for polyandry has not been formally modelled.
-Our model therefore has widespread implications for future studies of evolution of polyandry.
+We found that when post-copulatory inbreeding avoidance could evolve, selection for polyandry was greatly strengthened (Figure 1).
+The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but our model provides support for this verbal hypothesis and therefore has widespread implications for future studies of evolution of polyandry.
 
@@
 canescens* would be highly unlikely to evolve.
-
-General predictions
--------------------------------------------------------------------
-
-Some broad predictions are possible given the verbal theory that we have developed and the populations that we have simulated.
-For example, given that post-copulatory inbreeding avoidance is useless for monandrous females and most effective for polyandrous females, while pre-copulatory inbreeding avoidance is perhaps most effective for monandrous females and less effective for polyandrous females, it would be interesting to test whether or not occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with degree of polyandry.
-In addition to polyandry making post-copulatory inbreeding avoidance relevant, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself.
-Hence, well-grounded biological hypotheses might be derived for the relationship between female multiple mating and mode of inbreeding avoidance.
-To test such hypotheses, more work is needed to identify the degree to which females of different species engage in polyandrous and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
-
-<!--- Some general conclusions addressing 1) what future theory should be developed, and 2) what future empirical studies need to consider.
-For 2, need to be aware of both pre- and post-copulatory inbreeding avoidance, potentially, and that the two are not independent, necessarily; cannot find any general theory for what happens when you have this kind of strategy redundancy -- two ways of getting at the same outcome.
---->
 

### 2016-12-22 ms_pre_post.Rmd
Add three references of note to cite later
Edits to second paragraph of Discussion; progress on 'degeneracy' in the third

@@
 
-For example, our results highlight a simple but theoretically under-developed conclusion concerning the relationship between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding avoidance.
+For example, our results highlight a fundamental but theoretically under-developed conclusion concerning the relationship between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding avoidance.
 Post-copulatory inbreeding avoidance is useless for monandrous females, and most effective for highly polyandrous females that can choose amongst multiple mates to ensure that offspring are fertilised favourably.
-In contrast, pre-copulatory inbreeding avoidance is perhaps most effective for monandrous females and less effective for polyandrous females.
+In contrast, pre-copulatory mechanisms are most salient for monandrous females that have no post-copulatory means for avoiding inbreeding.
 This conclusion is reflected in our simulation results, as selection for post-copulatory inbreeding avoidance was negligible in monandrous populations, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D).
@@
 It would therefore be interesting to test the hypothesis that, across taxa, occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with degree of polyandry.
-To test this hypothesis, more work is needed to identify the degree to which females of different species engage in polyandrous and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
+To test this hypothesis, more work is needed to identify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
 
-Another general inference from our model concerns the dynamics of phenotypes with highly overlapping effects with respect to selection, realised through functionally different traits.
+Another general inference from our model concerns the dynamics of phenotypes with highly overlapping effects with respect to selection, as realised through functionally different traits.
 Pre-copulatory inbreeding avoidance, typically expressed through mating behaviour, versus post-copulatory inbreeding avoidance, typically expressed through phenotypes affecting fertilisation, are both driven by the shared selective pressure of inbreeding depression in offspring viability.
 Hence, evolution of each of these strategies might make the other strategy more or less adaptive by modifying its impact on the degree to which a female avoids inbreeding and consequently has offspring that express inbreeding depression.
+The ability of structurally different phenotypes to perform the same adaptive function is an example of 'degeneracy', a term which defines a more general phenomenon whereby unique elements of a system result in identical outputs [@Edelman2001].
 
@@
 For 2, need to be aware of both pre- and post-copulatory inbreeding avoidance, potentially, and that the two are not independent, necessarily; cannot find any general theory for what happens when you have this kind of strategy redundancy -- two ways of getting at the same outcome.
---->
+See: @Nowak1997, @Edelman2001, @Whitacre2010, @Price2002, @Park2013, Atamas2009, @Whitacre2012, @Whitacre2010a, @Levin2008 --->
 

### 2016-12-22 ms_pre_post.Rmd
Add some new degeneracy citations

@@
 The ability of structurally different phenotypes to perform the same adaptive function is an example of 'degeneracy', a term which defines a more general phenomenon whereby unique elements of a system result in identical outputs [@Edelman2001].
+Effects of degeneracy can be observed across nearly all biological scales [@Edelman2001], including complex systems affecting organismal development [e.g., @Nowak1997], adaptation [@Whitacre2010; @Whitacre2010a], and cognition [@Price2002; @Park2013], as well as population [@Atamas2009] and ecosystem [e.g., @Levin2008] dynamics.
+The relevance of degeneracy with respect to reproductive strategies requires further theoretical development, and might potentally result in new empirical predictions and conceptual synthesis across biological scales.
 

### 2016-12-22 ms_pre_post.Rmd
Complete third Discusion paragraph on degeneracy

@@
 Another general inference from our model concerns the dynamics of phenotypes with highly overlapping effects with respect to selection, as realised through functionally different traits.
-Pre-copulatory inbreeding avoidance, typically expressed through mating behaviour, versus post-copulatory inbreeding avoidance, typically expressed through phenotypes affecting fertilisation, are both driven by the shared selective pressure of inbreeding depression in offspring viability.
-Hence, evolution of each of these strategies might make the other strategy more or less adaptive by modifying its impact on the degree to which a female avoids inbreeding and consequently has offspring that express inbreeding depression.
 The ability of structurally different phenotypes to perform the same adaptive function is an example of 'degeneracy', a term which defines a more general phenomenon whereby unique elements of a system result in identical outputs [@Edelman2001].
 Effects of degeneracy can be observed across nearly all biological scales [@Edelman2001], including complex systems affecting organismal development [e.g., @Nowak1997], adaptation [@Whitacre2010; @Whitacre2010a], and cognition [@Price2002; @Park2013], as well as population [@Atamas2009] and ecosystem [e.g., @Levin2008] dynamics.
-The relevance of degeneracy with respect to reproductive strategies requires further theoretical development, and might potentally result in new empirical predictions and conceptual synthesis across biological scales.
+In the context of reproductive strategy, pre-copulatory inbreeding avoidance, typically expressed through mating behaviour, versus post-copulatory inbreeding avoidance, typically expressed through phenotypes affecting fertilisation, are both driven by the shared selective pressure of inbreeding depression in offspring viability.
+Hence, degeneracy occurred in our model through an overlap in how phenotypes cause adaptive inbreeding avoidance.
+Such degeneracy might increase biological robustness [@Gardner2006; @Whitacre2010a], potentially facilitating realised inbreeding avoidance across environments in which either pre-copulatory or post-copulatory mechanisms alone would be ineffective (e.g., due to sexual conflict affecting mate choice or injury affecting fertilisation).
+However, evolution of each of these strategies might decrease selection on the other strategy by modifying its impact on the degree to which a female avoids inbreeding and consequently has offspring that express inbreeding depression [*sensu* evolution of genetic redundancy; see @Nowak1997].
+The relevance of degeneracy with respect to such reproductive strategies therefore requires further theoretical development, which could result in new empirical predictions and conceptual synthesis across biological scales.
 

### 2016-12-22 ms_pre_post.Rmd
Finish off Discussion (?)

@@
 
-<!--- LEFT OFF HERE ------------------------------------------------------->
-
 How do cost asymmetries affect long-term persistence of reproductive strategies?
@@
 
+Interaction of polyandry and inbreeding avoidance strategies
+-------------------------------------------------------------------
+
+<!--- Get in the idea that costs could interact with benefits of degeneracy in a similar way that mutation rate and gene function interact? -- Nowak --->
+
+Evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but was affected by the joint evolution of polyandry and the existence of asymmetric costs.
+One cost free inbreeding strategy precluded another more costly inbreeding strategy from persisting in a focal population by modifying its effect on inbeding avodance (Figure 3).
+Consequetly, long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given sufficient cost asymmetry.
+Direct costs therefore strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies.
+Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging [@Pomiankowski1987; @Kokko2003; @Reid2015].
+@Pomiankowski1987 categorised four types of costs that are relevant to mate choice, which we suggest are also relevant costs for polyandry, and include costs of elevated risks associated with (1) predation or (2) disease transmission, and costs incurred through (3) loss of time or (4) depletion of energy.
+Another type of cost relevant for polyandry and inbreeding strategy is risk of male harm caused by sexual conflict [e.g., @Arnqvist2005a; @Parker2006].
+We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should benefit from a higher tolerance of inbreeding than females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
+Here we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of pre-copulatory inbreeding strategy as a lost of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of post-copulatory inbreeding strategy as depletion of energy.
+While these costs are biologically realistic, different costs will be relevant for different populations and be realised in different ways.
+For example, increased risk of disease transmission has been observed for highly polyandrous females [@Roberts2015a], but such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry.
+Different types of costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
+Evolution of individual phenotypes therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.
+
+<!--- Persistence of degenerate inbreeding strategies in spite of cost asymmetries can be interpreted as analagous to the persistence of degenerate alleles across multiple loci when genotype fitness and mutation rates vary [@Nowak1997].
+--->
+
+<!--- Another type of cost relevant for polyandry and inbreeding strategy is risk of male harm caused by sexual conflict [e.g., @Arnqvist2005a; @Parker2006].
+We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should benefit from a higher tolerance of inbreeding than females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
+Females that express the choice to avoid inbreeding when mating might therefore pay a cost of harm caused by coercion expressed by related males.
+This cost might itself evolve over time as male harm coevolves with female resistance [@Ronn2007; @Perry2011; @Wang2015a], and costs might vary with interactions among male non-relatives and relatives because effects of kin selection are predicted to reduce harm caused by related male suitors [@Rankin2011a].
+To predict evolution of polyandry and inbreeding strategy in populations characterised by active males and sexual conflict, consideration of male inbreeding strategy and coevolution between male harm and female resistance might therefore need to be considered explicitly.
+--->
+
+In our model, existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
+However, existence of adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Figure 3A,B).
+In wild populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
+Rather, for example, initial evolution of pre-copulatory inbreeding avoidance is much more likely to evolve in the absence of evolving post-copulatory inbreeding avoidance due to constraints, or in the presence of already evolved post-copulatory inbreeding avoidance.
+When framing hypotheses for existence of post-copulatory inbreeding avoidance and polyandry, it might therefore be necessary to consider whether or not inbreeding avoidance already occurs through pre-copulatory mate choice.
+Additionally, the opportunity for post-copulatory inbreeding avoidance will also naturally depend on the degree to which females are polyandrous.
+For species in which pre-copulatory inbreeding avoidance occurs and monandry is common [@Lihoreau2007; @Metzger2010; @Metzger2010a], evolution of post-copulatory inbreeding avoidance is highly unlikely.
+
 <!--- Some general conclusions addressing 1) what future theory should be developed, and 2) what future empirical studies need to consider.
@@
 
-Evolution of polyandry is facilitated by post-copulatory inbreeding avoidance
+<!--- LEFT OFF HERE ------------------------------------------------------->
+
+Evolution of polyandry
 -------------------------------------------------------------------
@@
 Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa [e.g., @Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015].
-For example, the number of sperm arriving to eggs is lower for full siblings of female red jungefowl (*Gallus gallus*) than it is for non-relatives, even after controlling for effects of order of oviposition and social familiarity [@Pizzari2004].
-Similarly, in house mice, fertilisation was biased toward unrelated males independent of mating order, perhaps due to post-copulatory mechanisms expressed through the secretion of gametic proteins originating in eggs [@Firman2008; @Firman2015].
-Interestingly, female house mice also show pre-copulatory inbreeding avoidance  [@Potts1991; @Roberts2003].
-Our results suggest that post-copulatory inbreeding avoidance is unlikely to evolve when females can already avoid inbreeding through pre-copulatory mechanisms (Figure 4), meaning that evolution of post-copulatory inbreeding avoidance could reasonably be hypothesised to have preceded evolution of pre-copulatory inbreeding avoidance in mice.
+Recent studies have shown how females can successfully bias fertilisation after mating has occurred.
+For example, when female guppies (*Poecilia reticulata*) were artificially inseminated with equal quantities of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full siblings' sperm were reduced by females' ovarian fluids [@Gasparini2011].
+In black field crickets (*Teleogryllus commodus*), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs [@Bussiere2006; @Tuni2013].
+Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for further polyandry, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
+
+Conclusion
+-------------------------------------------------------------------
+
+Evolution of reproductive strategies involves multiple potentially interacting and degenerate phenotypes.
+Here we modelled evolution of three reproductive strategies including polyandry, pre-copulatory inbreeding avoidance, and post-copulatory inbreeding avoidance, focusing on three key questions.
+Using individual-based modelling, we found that evolution of post-copulatory inbreeding avoidance facilitated evolution of polyandry, that evolution of a costly inbreeding avoidance strategy was inhibited when the other inbreeding avoidance strategy was cost free, and that evolution of post-copulatory inbreeding avoidance but not pre-copulatory inbreeding avoidance was precluded when the other inbreeding avoidance strategy was fixed for strong inbreeding avoidance.
+We thereby conclude that evolution of inbreeding avoidance strategies and associated polyandry are likely to interact in predictable ways, potentially generating new hypotheses concerning evolution of reproductive strategies within and across taxa.
 
@@
 
-Recent studies have shown how females can successfully bias fertilisation after mating has occurred.
-For example, when female guppies (*Poecilia reticulata*) were artificially inseminated with equal quantities of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full siblings' sperm were reduced by females' ovarian fluids [@Gasparini2011].
-In black field crickets (*Teleogryllus commodus*), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs [@Bussiere2006; @Tuni2013].
-Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for further polyandry, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
-
 <!--- Regarding last sentence: ''OK this is a much better opening to this section – states the key result from our model and then goes on the develop/consider the implications.
 Could you use the same kind of structure for the previous sections?'' --->
-
-Evolution of a costly inbreeding strategy is inhibited by a non-costly alternative strategy
--------------------------------------------------------------------
-
-In our model, one cost free inbreeding strategy precluded another more costly inbreeding strategy from persisting in a focal population (Figure 3), meaning that long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given cost asymmetry.
-Direct costs therefore strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies.
-Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging [@Pomiankowski1987; @Kokko2003; @Reid2015].
-@Pomiankowski1987 categorised four types of costs that are relevant to mate choice, which we suggest are also relevant costs for polyandry, and include costs of elevated risks associated with (1) predation or (2) disease transmission, and costs incurred through (3) loss of time or (4) depletion of energy.
-In our model, we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of pre-copulatory inbreeding strategy as a lost of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of post-copulatory inbreeding strategy as depletion of energy.
-While these costs are biologically realistic, different costs will be relevant for different populations and be realised in different ways.
-For example, increased risk of disease transmission has been observed for highly polyandrous females [@Roberts2015a], but such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry.
-Future studies will therefore need to carefully consider the magnitudes and realisation of direct costs to accurately predict evolution of inbreeding strategies in populations.
-
-Another type of cost relevant for polyandry and inbreeding strategy is risk of male harm caused by sexual conflict [e.g., @Arnqvist2005a; @Parker2006].
-We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should benefit from a higher tolerance of inbreeding than females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
-Females that express the choice to avoid inbreeding when mating might therefore pay a cost of harm caused by coercion expressed by related males.
-This cost might itself evolve over time as male harm coevolves with female resistance [@Ronn2007; @Perry2011; @Wang2015a], and costs might vary with interactions among male non-relatives and relatives because effects of kin selection are predicted to reduce harm caused by related male suitors [@Rankin2011a].
-To predict evolution of polyandry and inbreeding strategy in populations characterised by active males and sexual conflict, consideration of male inbreeding strategy and coevolution between male harm and female resistance might therefore need to be considered explicitly.
-
-Evolution of post-copulatory inbreeding avoidance is precluded by existing pre-copulatory inbreeding avoidance, but not vice versa
--------------------------------------------------------------------
-
-In our model, existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
-However, existence of adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Figure 3A,B).
-In wild populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
-Rather, for example, initial evolution of pre-copulatory inbreeding avoidance is much more likely to evolve in the absence of evolving post-copulatory inbreeding avoidance due to constraints, or in the presence of already evolved post-copulatory inbreeding avoidance.
-When framing hypotheses for existence of post-copulatory inbreeding avoidance and polyandry, it might therefore be necessary to consider whether or not inbreeding avoidance already occurs through pre-copulatory mate choice.
-Additionally, the opportunity for post-copulatory inbreeding avoidance will also naturally depend on the degree to which females are polyandrous.
-For species in which pre-copulatory inbreeding avoidance occurs and monandry is common, evolution of post-copulatory inbreeding avoidance is especially unlikely.
-For example, females of the gregarious cockroach *Blatella germanica* (L.) avoid inbreeding and are typically monandrous [@Lihoreau2007]; while occurrence of post-copulatory inbreeding avoidance in *B.
-germanica* has not, to our knowledge, been tested, we predict that such inbreeding avoidance is highly unlikely.
-Similarly, females of the solitary parasitoid wasp *Venturia canescens* are monandrous, and appear to avoid mating with siblings [@Metzger2010; @Metzger2010a].
-We hypothesise that post-copulatory inbreeding avoidance in *V.
-canescens* would be highly unlikely to evolve.
 

### 2016-12-22 ms_pre_post.Rmd
Some final minor tweaks

@@
 As with mate choice, $q^{f}_{ij}$ values are placed into a vector whose elements sum to unity, and a random uniform number is used to sample paternity.
-Females produce $n$ offspring, so $q^{f}{ij}$ values are sampled $n$ times independently and with replacement for each female to determine the realised distribution of sires.
+Females produce $n$ offspring, so $q^{f}_{ij}$ values are sampled $n$ times independently and with replacement for each female to determine the realised distribution of sires.
 <!--- This last sentence has now been added back in, with another explaining it further.

### 2016-12-31 ms_pre_post.Rmd
Tweak the introduction

@@
 Inbreeding avoidance has been widely hypothesised to evolve through pre-copulatory and post-copulatory mechanisms as a consequence of inbreeding depression in offspring viability and female multiple mating (polyandry).
-However, no theoretical framework exists from which to derive hypothese concerning joint evolution of pre-copulatory and post-copulatory inbreeding avoidance.
+However, no theoretical framework exists from which to derive hypotheses concerning joint evolution of pre-copulatory and post-copulatory inbreeding avoidance.
 Evolution of post-copulatory inbreeding avoidance necessitates polyandry, potentially leading to complex evolutionary dynamics among inbreeding strategies and female mating frequency, each of which might be affected by direct negative costs.
-Hence, we use individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry across multiple cost combinations given severe inbreeding depression.
+We use individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry across multiple cost combinations given severe inbreeding depression.
 We find that evolution of post-copulatory inbreeding avoidance increases selection for polyandry, that selection for costly inbreeding strategies was weak or negligible given a non-costly alternative strategy.
-Established pre-copulatory inbreeding avoidance generally precluded evolution of polyandry and therefore inbreeding avoidance, but established post-copulatory inbreeding aviodance did not preclude pre-copulatory inbreeding avoidance from evolving.
-We thereby provide a general framework for understanding evolution of pre-copulatory and/or post-copulatory inbreeding avoidance across systems, and conclude that evolution of inbreeding avoidance phenotypes and associated polyandry are predicted to interact and be strongly affected by direct costs.
+Established pre-copulatory inbreeding avoidance generally precluded evolution of polyandry and therefore inbreeding avoidance, but established post-copulatory inbreeding avoidance did not preclude pre-copulatory inbreeding avoidance from evolving.
+We thereby provide a general framework for understanding joint evolution of pre-copulatory and/or post-copulatory inbreeding avoidance, and conclude that evolution of inbreeding avoidance phenotypes and associated polyandry are predicted to interact and be strongly affected by direct costs.
 
@@
 Evolution of post-copulatory inbreeding avoidance requires that females are polyandrous, defined as mating with multiple males during a single reproductive bout.
-Further, such polyandry could itself evolve because it allows females to mate with additional unrelated males following an initial mating with a relative, thereby facilitating pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation (i.e., given a 'fair raffle' among sperm provided by females' mates).
+Further, such polyandry might itself be under selection because given inbreeding depression it allows females to mate with additional unrelated males following an initial mating with a relative, thereby facilitating pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation (i.e., given a 'fair raffle' among sperm provided by females' mates).
 Polyandry can thereby simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
@@
 
-Despite a lack of non-verbal theory and resulting predictions, numerous studies on diverse species have found evidence for female inbreeding avoidance.
+Despite a paucity of theory and resulting predictions, numerous empirical studies on diverse species have found evidence for female inbreeding avoidance.
 However, only a few such studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
@@
 Taken together, all of these studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature.
-However, there is as yet no framework that predicts what combinations should be favoured by selection when polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all potentially evolve.
-Consequently, there is no framework that allows the diversity of existing empirical results to be rationalised or interpreted, and no clear hypotheses that could be tested with these studies through comparative analyses or that could be applied to future empirical studies of individual systems.
+However, there is as yet no theory that predicts what combinations should be favoured by selection when polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all potentially evolve.
+Consequently, there is no theory that allows the diversity of existing empirical results to be rationalised or interpreted, and no clear hypotheses that could be tested with these studies through comparative analyses or that could be applied to future empirical studies of individual systems.
 
-A recent genetically-explicit individual-based model examined the conditions under which polyandry is predicted to evolve slely due to selection stemming from pre-copulatory inbreeding avoidance [@Duthie].
-Evolution of polyandry occurred only under highly restricted conditions, requiring that direct costs were small, that very few males were available for a female's initial mate chioce but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
+A recent genetically-explicit individual-based model examined the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance [@Duthie].
+Evolution of polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., 'costs') on polyandry were small, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
 Without these conditions, increasing polyandry tended to increase rather than decrease the overall degree of inbreeding that females experienced, and hence reduced offspring fitness.
@@
 Post-copulatory inbreeding avoidance might consequently reduce the cost of polyandry stemming from the accumulation of related mates, potentially facilitating evolution of polyandry to avoid inbreeding under broader conditions, and driving further consequent evolution of pre-copulatory or post-copulatory mate choice strategies.
-However, once both pre-copulatory and post-copulatory inbreeding avoidance, and resulting polyandry, can evolve, the long-term dynamics of these reproductive strategies become difficult to conceptualise and predict.
+However, once both pre-copulatory and post-copulatory inbreeding avoidance, and resulting polyandry, can all evolve, the long-term dynamics of these reproductive strategies become difficult to conceptualise and predict.
 Strong inbreeding depression might drive initial evolution of both pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
@@
 For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then new alleles underlying polyandry and post-copulatory inbreeding avoidance might be precluded from invading a population because the phenotypic effect of such alleles on the degree of inbreeding could be negligible.
-Conversely, fixation of alleles underlying polyandry and post-copulatory inbreeding avodiance might eliminate positive selection on alleles underlying pre-copulatory inbreeding avoidance.
+Conversely, fixation of alleles underlying polyandry and post-copulatory inbreeding avoidance might eliminate positive selection on alleles underlying pre-copulatory inbreeding avoidance.
 New theory, guided by modelling that evaluates invasion dynamics given appropriate sets of evolutionary constraints, is therefore needed.
 
-Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will depend not only on the magnitudes of positive indirect selection steming from reduced inbreeding depression in females' offspring, but also on the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
+Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will depend not only on the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also on the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
 Polyandrous females can pay costs of mate searching or mating, for example, because these activities increase predation risk [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
@@
 We address three key questions for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression.
-These questions include: (1) Does evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance facilitate evolution of polyandry that is otherwise severely constrained by increasing relatedness of additional mates?
-(2) How do costs associated with polyandry and pre-copulatory and post-copulatory inbreeding avoidance affect evolutionary outcomes and, in particular, the long-term persistence of reproductive strategies given cost assymetry?
+These questions include: (1) Does evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance facilitate evolution of polyandry that is otherwise severely constrained from increasing relatedness of additional mates?
+(2) How do costs associated with polyandry and pre-copulatory and post-copulatory inbreeding avoidance affect evolutionary outcomes and, in particular, the long-term persistence of reproductive strategies given cost asymmetry?
 Finally, (3) how is selection for initially rare pre-copulatory or post-copulatory inbreeding avoidance affected if the other strategy of inbreeding avoidance is already fixed?

### 2016-12-31 ms_pre_post.Rmd
Minor edits to the Model section

@@
 Individuals are defined as related if they share a common ancestor within the population pedigree (i.e., non-zero kinship).
-Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of the three reproductive strategy traits: tendency for polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$, i.e., 'fertilisation' alleles).
+Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of the three reproductive strategy traits (i.e., 30 total diploid loci): tendency for polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$, i.e., 'fertilisation' alleles).
 All alleles can take any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014] and combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for each of the three traits whereby an individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
@@
 Phenotypic values for tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$) each have costs that are assumed to independently increase the probability that a focal female will die before mating.
-The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, repectively.
+The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
 Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
@@
 Consequently, they can be chosen as females' mates based on their values of $k_{ij}=0$ but do not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$.
-Further, immigrants $P_{a}$, $M_{a}$, and $F_{a}$ allele values are randomly sampled from normal distributions with means and standard deviations equal to those in the focal population at the time of immigration, meaning that they do not directly cause any change in the distribution of allele values.
+Further, immigrants' $P_{a}$, $M_{a}$, and $F_{a}$ allele values are randomly sampled from normal distributions with means and standard deviations equal to those in the focal population at the time of immigration, meaning that they do not directly cause any change in the distribution of allele values.
 We thereby effectively assume that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$.
@@
 Each combination of parameter values simulated was replicated $40$ times, and grand mean values and standard errors of means are calculated in each generation across replicates.
-These analyses allow us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potential evolutionary feedbacks among reproductive strategies (e.g., selection on post-copulatory inbreeding strategy might be weak if polyandry is rare).
+These analyses allowed us to infer how allele values changed over generations in response to costs, but also in response to the changing values of other alleles and therefore potential evolutionary feedbacks among reproductive strategies (e.g., selection on post-copulatory inbreeding strategy might be weak if polyandry is rare).
 For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling [@Duthie] showed to be sufficient for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.

### 2017-01-01 ms_pre_post.Rmd
Minor tweaks to Results

@@
 However, when $c_{F}=0.02$, $F_{a}$ values remained near zero to minimise direct costs.
-This lack of evolution of post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
+This lack of selection for post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
 When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information).

### 2017-01-01 ms_pre_post.Rmd
Add bird reference for post-cop avoidance in Intro

@@
 However, only a few such studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
-Among these few studies, pre-copulatory inbreeding avoidance has been documented in weevils, birds, and butterflies [e.g., @Kuriwada2011; @Kingma2013; @Fischer2015], and post-copulatory inbreeding avoidance has been documented in crickets [e.g., @Simmons2006; @Bretman2009].
+Among these few studies, pre-copulatory inbreeding avoidance has been documented in weevils, birds, and butterflies [e.g., @Kuriwada2011; @Kingma2013; @Fischer2015], and post-copulatory inbreeding avoidance has been documented in birds and crickets [e.g., @Pizzari2004; @Simmons2006; @Bretman2009].
 An even smaller number of studies comprise sufficient evidence for mechanisms of both pre-copulatory and post-copulatory inbreeding avoidance in two well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015].
@@
 We have addressed key questions regarding the effect of such feedbacks and costs on evolution of pre-copulatory inbreeding avoidance, post-copulatory inbreeding avoidance, and polyandry.
-A critical analysis of our model results in new predictions concerning evolutionary dynamics given the joint evolution of these traits, which may be used to formulate new empirical hypotheses within and across taxa.
+A critical analysis of our model engenders new predictions concerning evolutionary dynamics given the joint evolution of these traits, which may be used to formulate new empirical hypotheses within and across taxa.
 
-For example, our results highlight a fundamental but theoretically under-developed conclusion concerning the relationship between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding avoidance.
+For example, our results highlight a fundamental but theoretically under-developed relationship between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding avoidance.
 Post-copulatory inbreeding avoidance is useless for monandrous females, and most effective for highly polyandrous females that can choose amongst multiple mates to ensure that offspring are fertilised favourably.
 In contrast, pre-copulatory mechanisms are most salient for monandrous females that have no post-copulatory means for avoiding inbreeding.
-This conclusion is reflected in our simulation results, as selection for post-copulatory inbreeding avoidance was negligible in monandrous populations, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D).
+This theory is borne out in our simulation results, as selection for post-copulatory inbreeding avoidance was negligible in monandrous populations, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D).
 The effect of monandry on selection for pre-copulatory inbreeding avoidance was weaker, but pre-copulatory inbreeding avoidance was generally stronger when populations where monandrous (e.g., Figure 3A vs 3B; see also Supporting Information p.
@@
 
-Another general inference from our model concerns the dynamics of phenotypes with highly overlapping effects with respect to selection, as realised through functionally different traits.
+Another general inference from our simulation results concerns the dynamics of phenotypes with highly overlapping effects with respect to selection, as realised through functionally different traits.
 The ability of structurally different phenotypes to perform the same adaptive function is an example of 'degeneracy', a term which defines a more general phenomenon whereby unique elements of a system result in identical outputs [@Edelman2001].

### 2017-01-01 ms_pre_post.Rmd
Minor tweaks to the Discussion

@@
 Evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but was affected by the joint evolution of polyandry and the existence of asymmetric costs.
-One cost free inbreeding strategy precluded another more costly inbreeding strategy from persisting in a focal population by modifying its effect on inbeding avodance (Figure 3).
-Consequetly, long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given sufficient cost asymmetry.
+One cost free inbreeding strategy precluded another more costly inbreeding strategy from persisting in a focal population by modifying its effect on inbreeding avodance (Figure 3).
+Consequently, long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given sufficient cost asymmetry.
 Direct costs therefore strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies.

### 2017-01-01 ms_pre_post.Rmd
Remove comments; finalise version to send to coauthors

@@
 
-<!--- Will most likely need to read and cite \cite{Fisher2016} here (Fisher et al. 2016 Behavioural Ecology -- pre- and post-copulatory competition using network theory --->
-
 Abstract
@@
 ===================================================
-
-<!--- I have removed 'mate' in front of 'choice' and replaced it with 'reproductive decisions' in the second sentence because post-copulatory inbreeding avoidance isn't an expression of mate choice; mating has already happened at this point; females are choosing paternity among the mates that they already chose --->
-
-<!--- Note that there are twice as many butterfly species and about eight times as many weevil species as there are bird species.
-I think that weevils and butterflies can be on at least equal footing with birds in terms of generality --->
 
@@
 
-<!--- This is getting awfully narrow in terms of theory; postcopulatory *might* happen given a fairly specific set of conditions concerning evolution of pre-copulatory inbreeding avoidance and polyandry.
-Are we confident these conditions are general?
---->
-
-<!--- I'm not suggesting that things need to be changed (probably too late for that), just that, to me, this reads as the theoretical equivalent of a very system-specific question being address, not like a question that has broad implications across different systems --->
-
 However, if post-copulatory inbreeding avoidance could also evolve, polyandrous females could further bias paternity towards unrelated males within their set of chosen mates.
@@
 Dynamic models are consequently required to understand and predict evolutionary outcomes.
-
-<!--- This last sentence sounds good and strong, but it doesn’t actually follow logically from the rest of the paragraph – how do we know that we can’t predict or understand evolutionary outcomes with non-dynamic models, perhaps one that predicts long-term equilibria?
-This doesn’t seem obvious or well argued if we’re just talking about costs and benefits – what, specifically, can a dynamic model (I assume, a simulation, i.e., a model where things change over time) address that another type of model cannot?
---->
 
@@
 Females produce $n$ offspring, so $q^{f}_{ij}$ values are sampled $n$ times independently and with replacement for each female to determine the realised distribution of sires.
-<!--- This last sentence has now been added back in, with another explaining it further.
-These things seem to get taken out as extraneous, but then added back in because the methods are not clear when they are removed --->
 
@@
 
-<!--- Note given previous comments: I've reworded because we don't know that pre-copulatory inbreeding avoidance is facilitating evolution of polyandry, not anymore.
-With the addition of post-copulatory strategy, it might be hindering it instead.
-If we wanted the answer to this, we would need to fix different levels of post-copulatory inbreeding avoidance and see if we get the same pattern as in Duthie et al.
-(2016) Evolution.
-We might not see the same result of pre-copulatory inbreeding avoidance facilitating evolution of polyandry.
---->
-
-<!--- The above point is especially problematic here because in the absence of post-copulatory inbreeding avoidance (in the current model) pre-copulatory inbreeding avoidance definitely does not facilitate evolution of costly polyandry -- this only happens under the severe constraints of our previous Evolution paper.
-Hence, it would have been a bit strange to suggest that post-copulatory inbreeding avoidance works `alongside' pre-copulatory inbreeding avoidance when we know that pre-copulatory inbreeding avoidance isn't doing anything.
---->
-
 To address whether or not evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance can facilitate evolution of polyandry, we compare simulations in which polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, with otherwise identical simulations in which post-copulatory inbreeding avoidance cannot evolve given four different costs of polyandry ($c_{P} = \{0, 0.0025, 0.005,  0.01\}$).
@@
 
-<!--- I am happy to switch back to using statements as titles instead of questions --->
-
 Does evolution of post-copulatory inbreeding avoidance facilitate evolution of costly polyandry?
@@
 Polyandrous females that subsequently sampled more males from the available population were consequently more likely to mate with some relatives and hence produce some inbred offspring with low viability [@Duthie].
-
-<!--- Changed several things back here because alleles cannot evolve --->
 
@@
 When one inbreeding strategy had zero cost, the other strategy initially evolved towards inbreeding avoidance (i.e., negative $M_{a}$ or $F_{a}$) but then evolved back towards random mating or fertilisation (i.e., $M_{a}=0$ or $F_{a}=0$) across generations following increasing evolution of inbreeding avoidance through the cost-free strategy (Figure 3B,D).
-<!--- For example, given fixed $F_{a}=0$, grand mean $M_{a}$ value in the last $10000$ generations was $-0.868$ (Figure 3A), meaning that a female was ca $5.34$ times less likely to choose a full-sibling and ca $2.10$ times less likely to mate with a first cousin than a non-relative given a high cost of pre-copulatory inbreeding avoidance, $c_{M}=0.02$.
-However, when $F_{a}$ allele values could also evolve, grand mean $M_{a}$ allele value in the last $10000$ generations was only $-0.288$ (Figure 3B).
-Further, given fixed $M_{a}=0$, grand mean $F_{a}$ value in the last $10000$ generations was $-1.092$ (Figure 3C), meaning that a female was ca $6.46$ times less likely to choose a full-sibling and ca $2.37$ times less likely to choose a first cousin than a non-relative given a high cost of pre-copulatory inbreeding avoidance, $c_{F}=0.02$.
-However, when $M_{a}$ values could also evolve and $P_{a}$ values were negative, grand mean $F_{a}$ value in the last $10000$ generations was only $-0.070$ (Figure 3D).
---->
 
 Evolution of post-copulatory inbreeding avoidance facilitated evolution of polyandry (Figure 3B,C), while monandry evolved in the absence of post-copulatory inbreeding avoidance (Figure 3A,D; polyandry was cost free in all these simulations).
-<!--- Overall, evolution of a costly inbreeding strategy that readily evolved in isolation was greatly impeded by evolution of a less costly strategy.
---->
 
@@
 
-<!--- Get in the idea that costs could interact with benefits of degeneracy in a similar way that mutation rate and gene function interact? -- Nowak --->
-
 Evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but was affected by the joint evolution of polyandry and the existence of asymmetric costs.
@@
 
-<!--- Persistence of degenerate inbreeding strategies in spite of cost asymmetries can be interpreted as analagous to the persistence of degenerate alleles across multiple loci when genotype fitness and mutation rates vary [@Nowak1997].
---->
-
-<!--- Another type of cost relevant for polyandry and inbreeding strategy is risk of male harm caused by sexual conflict [e.g., @Arnqvist2005a; @Parker2006].
-We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should benefit from a higher tolerance of inbreeding than females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
-Females that express the choice to avoid inbreeding when mating might therefore pay a cost of harm caused by coercion expressed by related males.
-This cost might itself evolve over time as male harm coevolves with female resistance [@Ronn2007; @Perry2011; @Wang2015a], and costs might vary with interactions among male non-relatives and relatives because effects of kin selection are predicted to reduce harm caused by related male suitors [@Rankin2011a].
-To predict evolution of polyandry and inbreeding strategy in populations characterised by active males and sexual conflict, consideration of male inbreeding strategy and coevolution between male harm and female resistance might therefore need to be considered explicitly.
---->
-
 In our model, existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
@@
 For species in which pre-copulatory inbreeding avoidance occurs and monandry is common [@Lihoreau2007; @Metzger2010; @Metzger2010a], evolution of post-copulatory inbreeding avoidance is highly unlikely.
-
-<!--- Some general conclusions addressing 1) what future theory should be developed, and 2) what future empirical studies need to consider.
-For 2, need to be aware of both pre- and post-copulatory inbreeding avoidance, potentially, and that the two are not independent, necessarily; cannot find any general theory for what happens when you have this kind of strategy redundancy -- two ways of getting at the same outcome.
-See: @Nowak1997, @Edelman2001, @Whitacre2010, @Price2002, @Park2013, Atamas2009, @Whitacre2012, @Whitacre2010a, @Levin2008 --->
-
-<!--- LEFT OFF HERE ------------------------------------------------------->
 
@@
 We thereby conclude that evolution of inbreeding avoidance strategies and associated polyandry are likely to interact in predictable ways, potentially generating new hypotheses concerning evolution of reproductive strategies within and across taxa.
-
-<!--- Similar comment to above - I’m finding the structure of this paragraph a bit backwards.
-Might it be more helpful to give the conclusion drawn from our model and then explain how it fits with existing empirical studies?
-At the moment I read the stuff about the empirical studies without having any idea how it was going to be linked into our results – so then I had to go back and read it again once you’d told me the link at the end.
-I’m still not quite sure I get it, or why we need so much detail on mechanisms?
-Also, I think the writing could be greatly shortened here - could probably say more or less the same thing in half the words.
-I’ve done some editing to illustrate this - but I doubt this’ll be a definitive version because I can’t really see where this para is going.
--->
-
-<!--- Regarding last sentence: ''OK this is a much better opening to this section – states the key result from our model and then goes on the develop/consider the implications.
-Could you use the same kind of structure for the previous sections?'' --->
-
-<!--- Our model assumed that allele values underlying polyandry, pre-copulatory inbreeding avoidance, and post-copulatory inbreeding avoidance were all initialised at zero (causing monandry, and random mating and fertilisation with respect to kinship), and phenotypes evolved simultaneously after initialisation.
-However, these initial conditions are likely to be atypical, as evolution of pre-copulatory and post-copulatory inbreeding avoidance from ancestral random mating and fertilisation is unlikely to occur simultaneously.
-Evolution of a single inbreeding strategy (e.g., pre-copulatory inbreeding avoidance) might occur in the absence of its complementary strategy (e.g., post-copulatory inbreeding avoidance) if the complementary strategy is evolutionarily constrained.
-Alternatively, initial evolution of one inbreeding strategy might occur in the context of an already established adaptive strategy for avoiding inbreeding.
-We showed that selection for post-copulatory but not pre-copulatory inbreeding avoidance was strengthened if its complementary strategy was fixed for random choice with respect to kinship, and that selection for post-copulatory but not pre-copulatory inbreeding avoidance was precluded if its complementary strategy was fixed for adaptive inbreeding avoidance.
---->
 

### 2017-01-16 ms_pre_post.Rmd
Add reference on degeneracy in carnivores, in the context of predator-prey interactions and their effect on prey abundance (Suraci et al. 2017 PLoS One)

@@
 The ability of structurally different phenotypes to perform the same adaptive function is an example of 'degeneracy', a term which defines a more general phenomenon whereby unique elements of a system result in identical outputs [@Edelman2001].
-Effects of degeneracy can be observed across nearly all biological scales [@Edelman2001], including complex systems affecting organismal development [e.g., @Nowak1997], adaptation [@Whitacre2010; @Whitacre2010a], and cognition [@Price2002; @Park2013], as well as population [@Atamas2009] and ecosystem [e.g., @Levin2008] dynamics.
+Effects of degeneracy can be observed across nearly all biological scales [@Edelman2001], including complex systems affecting organismal development [e.g., @Nowak1997], adaptation [@Whitacre2010; @Whitacre2010a], and cognition [@Price2002; @Park2013], as well as population [@Atamas2009], community [@Suraci2017], and ecosystem [e.g., @Levin2008] dynamics.
 In the context of reproductive strategy, pre-copulatory inbreeding avoidance, typically expressed through mating behaviour, versus post-copulatory inbreeding avoidance, typically expressed through phenotypes affecting fertilisation, are both driven by the shared selective pressure of inbreeding depression in offspring viability.
@@
 
+|       |                                     |             |               |
 |-------|-------------------------------------|-------------|---------------|--------------

### 2017-02-19 ms_pre_post.Rmd
Revise first paragraph

@@
 Inbreeding, defined as reproduction between relatives, often greatly reduces the fitness of resulting inbred offspring [termed 'inbreeding depression'; @Charlesworth1999; @Keller2002; @Charlesworth2009].
-Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple reproductive decisions [@Parker1979; @Parker2006; @Pusey1996; @Szulkin2012].
-From the perspective of a focal breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), and by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
-Evolution of post-copulatory inbreeding avoidance requires that females are polyandrous, defined as mating with multiple males during a single reproductive bout.
-Further, such polyandry might itself be under selection because given inbreeding depression it allows females to mate with additional unrelated males following an initial mating with a relative, thereby facilitating pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation (i.e., given a 'fair raffle' among sperm provided by females' mates).
-Polyandry can thereby simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
-Polyandry, which might not increase female reproductive success and therefore requires explanation [@Parker2013], has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002].
-However, there is surprisingly little theory or modelling that critically examines such widely-invoked hypotheses, and hence examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or how evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
+Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple interacting reproductive strategies [@Parker1979; @Parker2006; @Pusey1996; @Szulkin2012].
+From the perspective of a focal breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
+Evolution of post-copulatory inbreeding avoidance requires that females express some non-trivial degree of polyandry, defined as mating with multiple males during a single reproductive bout.
+Further, given inbreeding depression, such polyandry might itself be under selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative.
+Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm provided by females' mates (i.e., 'fair raffle').
+Overall, polyandry can therefore simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice, and has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002].
+Resulting indirect selection on polyandry could explain its evolution in cases where multiple mating does not increase female reproductive success, or even where polyandry reduces reproductive success and therefore imposes direct fitness costs to polyandrous females.
+However, despite such widely-invoked hypotheses, there is surprising little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
+
+<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
+
+<!--- Something seems redundant about ''sperm provided by females' mates''. This is probably okay though  --->
+<!--- I think I know what you mean, but is there any reason not to be bolder than 'help explain'?
+Could it not entirely explain most or all of the reason for selection for polyandry in some cases?
+--->
+<!--- I've left out survival, as decreased survival isn't really a cost unless it reduces reproductive success --->
+<!--- Parker and Birkhead (2013) was cited to identify the problem of polyandry, but I've removed it here because they don't really discuss inbreeding, and there wasn't really a good way to cite them here given the edits to the text.
+--->
 

### 2017-02-19 ms_pre_post.Rmd
Revise second paragraph

@@
 
-<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
-
 <!--- Something seems redundant about ''sperm provided by females' mates''. This is probably okay though  --->
@@
 
-Despite a paucity of theory and resulting predictions, numerous empirical studies on diverse species have found evidence for female inbreeding avoidance.
-However, only a few such studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
-Among these few studies, pre-copulatory inbreeding avoidance has been documented in weevils, birds, and butterflies [e.g., @Kuriwada2011; @Kingma2013; @Fischer2015], and post-copulatory inbreeding avoidance has been documented in birds and crickets [e.g., @Pizzari2004; @Simmons2006; @Bretman2009].
-An even smaller number of studies comprise sufficient evidence for mechanisms of both pre-copulatory and post-copulatory inbreeding avoidance in two well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015].
-A lack of both pre-copulatory and post-copulatory inbreeding has been found in fruit flies [e.g., @Ala-Honkola2011; @Tan2012], and might be reasonably inferred where no evidence of inbreeding avoidance exists [e.g., @Reid2014; @Reid2015].
-To our knowledge, only @Liu2014 consider both pre-copulatory and post-copulatory inbreeding avoidance jointly, finding evidence of pre-copulatory, but not post-copulatory, inbreeding avoidance in cabbage beetles (*Colaphellus bowringi*).
-Taken together, all of these studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature.
-However, there is as yet no theory that predicts what combinations should be favoured by selection when polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all potentially evolve.
-Consequently, there is no theory that allows the diversity of existing empirical results to be rationalised or interpreted, and no clear hypotheses that could be tested with these studies through comparative analyses or that could be applied to future empirical studies of individual systems.
+Despite the paucity of theory and resulting predictions, numerous empirical studies on diverse species have tested for, and found evidence of, female inbreeding avoidance in systems where polyandry also occurs.
+However, relatively few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
+Pre-copulatory inbreeding avoidance has been reported in diverse species, spanning sweet potato weevils [*Cylas formicarius*, @Kuriwada2011], purple-crowned fairy-wrens [*Malurus coronatus*, @Kuriwada2011], and a tropical butterfly [*Bicyclus anynana*, @Fischer2015], while post-copulatory inbreeding avoidance has been reported in species including red junglefowl [*Gallus gallus*, @Pizzari2004] and crickets [*Teleogryllus oceanicus*, @Simmons2006; *Gryllus bimaculatus*, @Bretman2009].
+Evidence for both pre-copulatory and post-copulatory inbreeding avoidance is available across different studies of Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015].
+Meanwhile, @Liu2014 found evidence of pre-copulatory but not post-copulatory inbreeding avoidance within a single study of cabbage beetles (*Colaphellus bowringi*).
+However, @Ala-Honkola2011 and @Tan2012 found no evidence for pre-copulatory or post-copulatory inbreeding avoidance in fruit flies (*Drosophila melanogaster*), respectively, and Reid et al.
+[-@Reid2014; -@Reid2015] found no net inbreeding avoidance in song sparrows (*Melospiza melodia*) despite strong inbreeding depression.
+Taken together, these studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature alongside polyandry.
+However, there is as yet no theory that predicts what combinations of pre-copulatory and post-copulatory inbreeding avoidance and polyandry should be favoured by selection when all combinations of phenotypes can evolve.
+Consequently, there is no theory that allows the diversity of existing empirical results regarding pre-copulatory and post-copulatory inbreeding avoidance to be rationalised or interpreted, and no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
+
+<!--- I don't know of any review articles or meta-analyses that look at polyandry to avoid inbreeding. At least, none within the last 10 years. --->
+<!--- I'm not sure I understand the point of ''tractable systems'' for post-copulatory inbreeding avoidance -- why not just 'species', as with pre-copulatory? --->
+<!--- What is the difference between 'rationalised' and 'interpreted'? Do these refer to the same thing, and if so, can we get rid of 'rationalised'? --->
+<!--- I still think that the end of this paragraph misses the point a bit with regard to how theory is supposed to function. --->
+
+<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
 

### 2017-02-22 ms_pre_post.Rmd
Finish edits through the Introduction

@@
 
-<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
-
+Developing theory on evolution of polyandry given inbreeding depression, @Duthie used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance.
 A recent genetically-explicit individual-based model examined the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance [@Duthie].
 Evolution of polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., 'costs') on polyandry were small, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
-Without these conditions, increasing polyandry tended to increase rather than decrease the overall degree of inbreeding that females experienced, and hence reduced offspring fitness.
+Without these conditions, increasing polyandry tended to increase rather than decrease the overall degree of inbreeding that females experienced, and hence reduce offspring fitness.
 This occurred because, once pre-copulatory inbreeding avoidance evolved, polyandrous females had already chosen available unrelated males as their initial mates.
@@
 
-However, if post-copulatory inbreeding avoidance could also evolve, polyandrous females could further bias paternity towards unrelated males within their set of chosen mates.
-Post-copulatory inbreeding avoidance might consequently reduce the cost of polyandry stemming from the accumulation of related mates, potentially facilitating evolution of polyandry to avoid inbreeding under broader conditions, and driving further consequent evolution of pre-copulatory or post-copulatory mate choice strategies.
-However, once both pre-copulatory and post-copulatory inbreeding avoidance, and resulting polyandry, can all evolve, the long-term dynamics of these reproductive strategies become difficult to conceptualise and predict.
+<!--- I don't think 'provide initial theory' is particularly clear (i.e., 'initial' in what respect?), so I've made an edit to the first sentence, though it does seem slightly redundant in both of our cases.
+--->
+
+However, if post-copulatory inbreeding avoidance could also evolve, polyandrous females would also have an opportunity to bias paternity towards unrelated males within their set of chosen mates.
+Evolution of post-copulatory inbreeding avoidance might consequently reduce the cost of polyandry stemming from the accumulation of related mates across multiple matings, potentially facilitating evolution of polyandry to avoid inbreeding under broader conditions, and driving further evolution of pre-copulatory or post-copulatory mate choice strategies.
+However, if polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, the long-term dynamics of these three reproductive strategies become difficult to predict.
 Strong inbreeding depression might drive initial evolution of both pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
-However, if evolution of polyandry and post-copulatory inbreeding avoidance renders pre-copulatory inbreeding avoidance redundant, or vice versa, then only one inbreeding avoidance strategy might be maintained in the long-term.
+However, the co-occurence of pre-copulatory and post-copulatory inbreeding avoidance might engender some degree of `degeneracy', defined as a phenomenon by which different elements of a system result in identical outputs [i.e., @Edelman2001].
+Consequently, if evolution of polyandry and post-copulatory inbreeding avoidance renders pre-copulatory inbreeding avoidance functionally redundant, or vice versa, then only one inbreeding avoidance strategy might be maintained in the long-term.
+
+<!--- the 'polyandry and pre-copulatory and post-copulatory inbreeding avoidance' seems technically off.
+It relies on readers to recognise that 'inbreeding avoidance' only applies to the first two items in the list.
+I suspect this shouldn't be a problem in practice, but I wonder if there's a better way to word this  --->
+
+<!--- Regarding the removal of 'conceptualise', are we suggesting then that prediction is only or most important thing to predict in the long term, and that we can do it with our model?
+I'm not sure if I agree with either.
+--->
+
+<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
 
@@
 Such models are useful for isolating the invasion fitness of this single strategy.
-However, when both pre-copulatory and post-copulatory strategies can affect realised inbreeding, it cannot be assumed that both strategies will simultaneously invade a randomly mating population, nor that the invasion fitness of one strategy will be independent of the existence of invasion fitness of the other strategy.
-For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then new alleles underlying polyandry and post-copulatory inbreeding avoidance might be precluded from invading a population because the phenotypic effect of such alleles on the degree of inbreeding could be negligible.
-Conversely, fixation of alleles underlying polyandry and post-copulatory inbreeding avoidance might eliminate positive selection on alleles underlying pre-copulatory inbreeding avoidance.
-New theory, guided by modelling that evaluates invasion dynamics given appropriate sets of evolutionary constraints, is therefore needed.
+However, when both pre-copulatory and post-copulatory strategies can affect the realised degree of inbreeding, it cannot be assumed that both strategies will simultaneously invade a randomly mating population, nor that the invasion fitness of one strategy will be independent of the pre-existence or invasion fitness of the other strategy.
+For example, if pre-adaptation or a selective sweep results in fixation of alleles underlying pre-copulatory inbreeding avoidance, then new alleles underlying polyandry and post-copulatory inbreeding avoidance might be unlikely to invade a population because the phenotypic effect of such alleles on the overall degree of inbreeding, and resulting indirect selection, could be negligible.
+Conversely, fixation of alleles underlying polyandry and post-copulatory inbreeding avoidance might reduce or eliminate positive selection on alleles underlying pre-copulatory inbreeding avoidance and hence impede adaptive evolution of mate choice.
+New theory, guided by modelling that evaluates invasion dynamics of alleles underlying multiple interacting and potentially functionally redundant (i.e., `degenerate') traits, is therefore needed.
+
+<!--- I'm not entirely sure the 'resulting indirect selection' helps --->
+
+<!--- I've made the suggested hedging changes.
+I originally introduced things boldly with 'preclude' or 'eliminate' by themselves as a way to introduce readers to the idea of the logic in the strongest terms possible, without thinking that readers would try to draw definite conclusions in the introduction or dwell on exceptions.
+Of course, as with anything in biology, the empirical (or even IBM) reality is going to be messier.
+--->
+
+<!--- Along the lines of the above then, I don't think it's always helpful to use 'evolution' as a short-hand for when we mean 'adaptive evolution'.
+For example, elimation of positive selection on alleles might not 'impede evolution' at all (which will still happen as long as there is mutation, drift, etc.), but rather change the direction of evolution.
+--->
+
+<!--- I don't understand why 'the simultaneous' invasion dynamics was being emphasised.
+Isn't the point of invasion analysis to look at one thing at a time and see whether or not the trait can invade (this is what we talk about in this paragraph, at least, and what we do later).
+By constraints, I mean something to the effect of *not having everything start out at zero and evolve simultaneously, which is biologically unrealistic*.--->
+
+<!--- I still don't like this last sentence very much.
+It doesn't really explain *why* new theory is needed, nor why such a specific set of modelling assumptions are required to address the theoretical question.
+I'm not even sure that I see a clear theoretical question in there.
+--->
 
@@
 However, such trajectories will also depend on the indirect benefits of each strategy, which might also differ and vary in relation to the evolution of the other strategy.
-Dynamic models are consequently required to understand and predict evolutionary outcomes.
+Dynamic models that track the frequencies of alleles underlying multiple reproductive strategies that might influence each other's evolution across generations, and that are enacted among relatives that themselves result from reproductive strategies and inbreeding depression expressed in previous generations, are consequently useful to understand and predict evolutionary outcomes.
 
-We address three key questions for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression.
-These questions include: (1) Does evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance facilitate evolution of polyandry that is otherwise severely constrained from increasing relatedness of additional mates?
-(2) How do costs associated with polyandry and pre-copulatory and post-copulatory inbreeding avoidance affect evolutionary outcomes and, in particular, the long-term persistence of reproductive strategies given cost asymmetry?
-Finally, (3) how is selection for initially rare pre-copulatory or post-copulatory inbreeding avoidance affected if the other strategy of inbreeding avoidance is already fixed?
-By addressing these questions, we provide a framework for exploring the simultaneous evolution of multiple reproductive strategies through the use of individidual-based modelling, and we derive hypotheses amenable to empirical tests within and across taxa.
+<!--- Do we really need ''absolute and relative'' frequencies? This just gets me thinking about the distinction and why it might be important, but we don't actually talk about that here. --->
+
+<!--- I think that the addition to the last sentence here is probably an improvement, but it still doesn't quite address my question -- there's not much of an argument for concluding that dynamic models are *required*.
+The implicit argument seems to be something like, ''look, there's a lot of complex stuff that's happening here; we can't figure out how to model how the evolutionary trajectories will play out without a dynamic model, so we're just going to assume that it's not possible''.
+My tendency is to be careful with these kinds of things, and maybe instead emphasise that dynamic models *can be useful* for understanding these kinds of dynamics without suggesting that they are necessary (time will tell if this is true).
+--->
+
+We use individual-based modelling to address three key questions regarding evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression.
+First, does evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance facilitate evolution of polyandry that is otherwise severely constrained from increasing relatedness of additional mates?
+Second, how do costs associated with polyandry and pre-copulatory and post-copulatory inbreeding avoidance affect evolutionary outcomes and, in particular, the long-term persistence of reproductive strategies given cost asymmetry?
+Third, how is selection for initially rare pre-copulatory or post-copulatory inbreeding avoidance affected if the other strategy of inbreeding avoidance is already fixed?
+By addressing these questions, we illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes; we thereby provide a framework for deriving hypotheses amenable to empirical tests within and across taxa.
+
+<!--- the 'outcomes; we' replaces the 'outcomes and' just to avoid making it sound like the second part of the sentence follows just from 'diverse evolutionary outcomes' instead of the whole first part.
+--->
 

### 2017-02-23 ms_pre_post.Rmd
Up to 'Fertilisation and post-copulatory inbreeding avoidance' in Methods

@@
 Strong inbreeding depression might drive initial evolution of both pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
-However, the co-occurence of pre-copulatory and post-copulatory inbreeding avoidance might engender some degree of `degeneracy', defined as a phenomenon by which different elements of a system result in identical outputs [i.e., @Edelman2001].
+However, the co-occurence of pre-copulatory and post-copulatory inbreeding avoidance might engender some degree of 'degeneracy', defined as a phenomenon by which different elements of a system result in identical outputs [i.e., @Edelman2001].
 Consequently, if evolution of polyandry and post-copulatory inbreeding avoidance renders pre-copulatory inbreeding avoidance functionally redundant, or vice versa, then only one inbreeding avoidance strategy might be maintained in the long-term.
@@
 --->
-
-<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
 
@@
 Females that express pre-copulatory choice and consequent reluctance to mate with relatives might pay costs of increased risk of complete mating failure or harm caused by sexual conflict [@Rowe1994; @Kokko2013].
-Females that express post-copulatory choice might pay energetic costs associated with physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
+Females that express post-copulatory choice might pay initial energetic costs associated with developing the physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
 If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly inbreeding strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
@@
 
-We model evolution of polyandry and pre-copulatory and post-copulatory inbreeding avoidance by tracking the dynamics of alleles underlying reproductive strategies enacted by interacting females and males within a small focal population.
-Individuals are defined as related if they share a common ancestor within the population pedigree (i.e., non-zero kinship).
-Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of the three reproductive strategy traits (i.e., 30 total diploid loci): tendency for polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$, i.e., 'fertilisation' alleles).
+We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance, by tracking the dynamics of alleles underlying reproductive strategies enacted by interacting females and males within a small focal population.
+We thereby tracked evolutionary dynamics given internally-consistent patterns of relatedness caused by non-random mating while also allowing mutation, gene flow, drift, and selection to potentially affect evolution.
+Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of the three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$, i.e., 'fertilisation' alleles).
 All alleles can take any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014] and combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for each of the three traits whereby an individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
@@
 Offspring inherit a randomly sampled allele from each parent at each locus with no physical linkage.
-Alleles can then mutate and offspring express inbreeding depression.
+Alleles can then mutate and offspring express inbreeding depression in viability.
 Immigrants arrive in the population and density regulation limits population growth.
+We record the population pedigree and directly calculate the coefficient of kinship ($k$) between all potential mates in each generation (defined as the probability that two homologous alleles will be identical-by-descent), allowing individual strategies of pre-copulatory and post-copulatory inbreeding avoidance to be enacted.
 Key individual traits, parameter values, and variables are described in Table 1.
+
+<!--- Avoided 'used an IBM' to prevent the redundancy of 'used an IBM to model'--->
+
+<!--- I have added a sentence like that suggested, hitting the key evolutionary processes (as all pop-geneticists will recognise these as fundamental, emphasising that we're accounting for all the possible ways evolution can occur).
+It's tempting to remove 'gene-flow', which we only really use to prevent kinships from getting too high, but without it it sounds as if we're leaving something out.
+I don't see why this deals with the concern in the intro though -- the sentence just says what we did; it doesn't really explain why we *needed* to do what we did to address the knowledge gap.
+--->
 
@@
 
-Phenotypic values for tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$) each have costs that are assumed to independently increase the probability that a focal female will die before mating.
+Phenotypic values for tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$) each have costs that are assumed to independently increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
 The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
@@
 Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with each trait value.
+
+<!--- One issue with the 'see Discussion' though is that it's not clear what we're telling readers to see the discussion *about*.
+Were I to read this as reviewer, I would be confused, ''see Discussion?
+What for?
+Because you made an assumption in a model, the biological context of which was already explained in the Introduction?
+(2nd to last paragraph)''.
+I've tried to provide a bit of context in parentheses, but it makes me nervous catering to any (mistaken) readers who might be confused about what assumptions are used for in models.
+I'd rather deal with confused reviewers than write a paper that perpetuates some (increasingly frustrating) misunderstandings of modelling and theory.
+--->
 
@@
 All males in the population are assumed to be available for any female to choose.
-We therefore assume that there is no opportunity cost of male mating such that mating with one female would reduce a male's availability to mate with any other female.
+We therefore assume that there is no opportunity cost of male mating such that mating with one female does not reduce a male's availability to mate with any other female.
 Individual females mate with their total allotment of $N_{males}$ without replacement, meaning that $N_{males}$ models a female's total number of different mates rather than solely her total number of matings.
@@
 The value of $q^{m}_{ij}$ then defines the probability that a focal female mates with the male.
-Mating is realised by placing each $q^{m}_{ij}$ value into a vector whose elements sum to unity, and a random uniform number is then generated to sample a single male from this vector.
+Mating is realised by placing each $q^{m}_{ij}$ value into a vector whose elements sum to unity.
+A new vector of identical size is then created where each element equals the summation of all previous elements in the original vector of $q^{m}_{ij}$ values.
+Because each element in the vector corresponds to a unique male, a random uniform number between zero and one can identify a female's realised mate.
+This realisation is enacted by identifying the element in the vector that is closest to, but not less than, the random uniform number.
 Mating is therefore stochastic, and females do not always mate with the male of the highest $q^{m}_{ij}$.
@@
 In the unlikely event that a female's $N_{males}$ exceeds the total number of available males, then she simply mates with all males.
+
+<!--- Jane, we might want to step back a bit on this one and figure out what exactly it is that is confusing and needs clarifying, as I'm not sure I see what the issue is anymore or, rather, why we're going into so much detail about a very routine procedure in an IBM (or any bit of code, really).
+This kind of sampling procedure was used in both of our previous IBM papers and I don't recall it being an issue.
+I have explained the procedure as carefully as I can, but it's getting to the point now where it's essentially turning the specifics of the C programming language into English (i.e., the methods here are now language dependent -- could be done differently in R or Perl or whatever, essentially just to say that we're sampling an element randomly from a weighted vector (I'm still not sure why we can't go back to just saying it that way; actually, I don't see why we can't just stop after ''the value of q^m_ij then defines the probability that a focal female mates with the male'' -- why does this need further explanation in the text?)).
+--->
+
+<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
 

### 2017-02-23 ms_pre_post.Rmd
A bit more detail to the sampling

@@
 Mating is realised by placing each $q^{m}_{ij}$ value into a vector whose elements sum to unity.
-A new vector of identical size is then created where each element equals the summation of all previous elements in the original vector of $q^{m}_{ij}$ values.
+A new vector of identical size is then created where each element equals the summation of all earlier position elements in the original vector of $q^{m}_{ij}$ values (such that the first element is zero and last is a number $\leq 1$).
 Because each element in the vector corresponds to a unique male, a random uniform number between zero and one can identify a female's realised mate.

### 2017-02-24 ms_pre_post.Rmd
Edits up through the last section of the Results

@@
 
-<!--- Jane, we might want to step back a bit on this one and figure out what exactly it is that is confusing and needs clarifying, as I'm not sure I see what the issue is anymore or, rather, why we're going into so much detail about a very routine procedure in an IBM (or any bit of code, really).
+<!--- We might want to step back a bit on this one and figure out what exactly it is that is confusing and needs clarifying, as I'm not sure I see what the issue is anymore or, rather, why we're going into so much detail about a very routine procedure in an IBM (or any bit of code, really).
 This kind of sampling procedure was used in both of our previous IBM papers and I don't recall it being an issue.
@@
 These $q^{f}_{ij}$ values, which lie between zero and one, define the probability of paternity.
-As with mate choice, $q^{f}_{ij}$ values are placed into a vector whose elements sum to unity, and a random uniform number is used to sample paternity.
+As with mate choice, one vector element representing a single male is samplied as weighted by these probabilities to determine paternity.
 Females produce $n$ offspring, so $q^{f}_{ij}$ values are sampled $n$ times independently and with replacement for each female to determine the realised distribution of sires.
+
+<!--- I've tried another way of explaining that sampling is done from a vector of probabilities in the second to last sentence here --->
 
@@
 We therefore define $\Psi_{\textrm{off}}$ as the probability that an offspring is viable, and sample its realised viability (versus mortality) using a Bernoulli trial.
+
+<!--- See the PDF for the equation. Not sure why it's not showing up in the DOCX. --->
 
@@
 
-To address how asymmetric costs associated with pre-copulatory and post-copulatory inbreeding avoidance and polyandry affect the long-term persistence of reproductive strategies, we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where the cost of pre-copulatory inbreeding strategy $c_{M}=0$ but the cost of post-copulatory inbreeding strategy $c_{F}=0.02$, and vice versa.
+To address how asymmetric costs associated with pre-copulatory and post-copulatory inbreeding avoidance and polyandry affect the long-term persistence of reproductive strategies, we quantify the change in $M_{a}$ and $F_{a}$ over generations in simulations where the cost of pre-copulatory inbreeding strategy $c_{M}=0$ but the cost of post-copulatory inbreeding strategy $c_{F}=0.02$, and vice versa.
 We compare these simulations with evolution of a costly strategy in the absence of evolution of an alternative strategy (e.g., evolution of pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy phenotype is fixed at zero, $F_{p}=0$).
 In Supporting Information, we present results for all possible cost combinations of $0$ and $0.02$.
+Previous modelling using similar genetic architecture suggests that a cost of $0.02$ imposes strong but not overhwleming direct negative selection on polyandry [@Duthie].
 
-To address how selection on an initially rare strategy of pre-copulatory or post-copulatory inbreeding avoidance is affected by the existence of the other strategy of inbreeding avoidance already being fixed, we first used exploratory simulations to quantify evolution of pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation.
-Then, to test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance was already established, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., meaning that $F_{p}$ and $P_{p}$ did not evolve).
-Similarly, to test whether post-copulatory inbreeding avoidance would evolve when pre-copulatory inbreeding avoidance was already established, we initiated $F_{a}$ and $P_{a}$ allele values at zero but fixed $M_{a}$ allele values at $-10$.
+To address how selection on an initially rare strategy of pre-copulatory or post-copulatory inbreeding avoidance is affected by the other strategy of inbreeding avoidance already being fixed, we first used exploratory simulations to quantify evolution of pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation.
+Then, to test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance were fixed, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., meaning that $F_{p}$ and $P_{p}$ did not evolve).
+Similarly, to test whether post-copulatory inbreeding avoidance would evolve when pre-copulatory inbreeding avoidance was already fixed, we initiated $F_{a}$ and $P_{a}$ allele values at zero but fixed $M_{a}$ allele values at $-10$.
 Consequently, because females have 10 diploid loci, when $M_{a}$ or $F_{a}$ alleles were fixed at $-10$, outbred females were $51$ times less likely to choose a full brother and $13.5$ times times less likely to choose a first cousin than a non-relative in pre-copulatory and post-copulatory choice, respectively.
@@
 
-When post-copulatory inbreeding avoidance alleles ($F_{a}$) were fixed to zero, meaning that $F_{p}$ could not evolve, $P_{a}$ alleles underlying polyandry always decreased to negative values over generations (Figure 1A,C,E,G).
+When post-copulatory inbreeding avoidance alleles ($F_{a}$) were fixed to zero, meaning that $F_{p}$ could not evolve, $P_{a}$ alleles underlying polyandry always decreased to negative values over generations (red lines, Figure 1A,C,E,G).
 This shows that despite strong inbreeding depression in offspring viability, there is selection against unconditional polyandry even given zero direct cost ($c_{P}=0$; Figure 1A).
-This is because values of the $M_{a}$ also evolved to be negative, meaning that females typically avoided inbreeding through their initial mating.
+This is because $M_{a}$ values became negative over generations, meaning that females typically avoided inbreeding through their initial mating (blue lines, Figure 1A,C,E,G).
 Polyandrous females that subsequently sampled more males from the available population were consequently more likely to mate with some relatives and hence produce some inbred offspring with low viability [@Duthie].
@@
 Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry.
-However, $P_{a}$ values were expected to be positive only given a low cost of polyandry ($c_{P} < 0.005$, Figure 1B,D).
+However, $P_{a}$ values were expected to become positive only given a low cost of polyandry ($c_{P} < 0.005$, Figure 1B,D versus 1F,H).
 This implies that, even given strong inbreeding depression in offspring viability, inbreeding avoidance might generally be a weak force driving polyandry evolution.
 
-Strong post-copulatory inbreeding avoidance, manifested as very negative $F_{a}$ values, consistently evolved in all simulations where such evolution was allowed (Figure 1B,D,F,H).
+<!--- I've not added the suggested ''to the degree that most females mated multiply'' because it's not actually true unless costs are less than or equal to 0.025.
+Also, do we really need to point out figure 2 here?
+The very next paragraph explains that the degree of polyandry isn't trivial, and I should hope that readers aren't so impatient or put off by Figure 1 that they stop reading entirely!
+--->
+
+Strong post-copulatory inbreeding avoidance, manifested as very negative $F_{a}$ values, consistently evolved in all simulations where such evolution was allowed (black lines, Figure 1B,D,F,H).
 Evolution of post-copulatory inbreeding avoidance occurred even when $P_{a}$ values were expected to be slightly negative, and hence when there was selection against polyandry, (Figure 1F,H).
-This reflects the threshold nature of phenotypic expression of polygenic polyandry, wherein random sampling of alleles means that polyandry is commonly expressed (i.e., $P_{g}>0$) even when mean $P_{a}$ values are negative (Figure 2).
-This means that, even in populations where female reproductive strategy evolves toward monandry, there is still commonly some opportunity for expression of post-copulatory inbreeding avoidance and associated selection that drives evolution of $F_{a}$ allele values.
+This reflects the threshold nature of phenotypic expression of polygenic polyandry, wherein random sampling of alleles means that polyandry is expressed expressed by some females (i.e., $P_{g}>0$) even when mean $P_{a}$ values are negative (Figure 2C,D).
+This means that, even in populations where female reproductive strategy evolves toward monandry, there is still commonly some opportunity for expression of post-copulatory inbreeding avoidance and associated selection that drives evolution of post-copulatory inbreeding avoidance.
+
+<!--- I'm not sure what aspects of Figure 1 you want me to mention in the main text? Are these things that are also in the legend, and if so, do we really need to repeat them? --->
 
@@
 
+<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
+
 How do cost asymmetries affect long-term persistence of reproductive strategies?
@@
 
-When either pre-copulatory ($M_{a}$) or post-copulatory ($F_{a}$) inbreeding avoidance allele values were fixed to zero, the alternative inbreeding strategy evolved to inbreeding avoidance even when costly (Figure 3A,C).
+When post-copulatory inbreeding avoidance allele values ($F_{a}$) were fixed to zero, pre-copulatory inbreeding avoidance evolved even when costly (Figure 3A).
+Likewise, when pre-copulatory inbreeding avoidance allele values ($M_{a}$) were fixed to zero, costly post-copulatory inbreeding avoidance evolved (Figure 3C).
 Females therefore evolved to avoid inbreeding, and thereby avoid the cost of producing inbred offspring, through whichever route was available.
 
+<!--- Last time we were through this, it was suggested that I scrap the former term ''inbreeding strategy'' because we don't deal at all with inbreeding preference.
+I have rewritten these sections in attempt to make the writing clearer.
+TODO: Additionally, I have tweaked the figure legends appropriately.--->
+
 However, when both pre-copulatory and post-copulatory inbreeding avoidance could evolve, their relative evolutionary dynamics depended on their relative costs.
-When one inbreeding strategy had zero cost, the other strategy initially evolved towards inbreeding avoidance (i.e., negative $M_{a}$ or $F_{a}$) but then evolved back towards random mating or fertilisation (i.e., $M_{a}=0$ or $F_{a}=0$) across generations following increasing evolution of inbreeding avoidance through the cost-free strategy (Figure 3B,D).
+When pre-copulatory but not post-copulatory inbreeding avoidance was costly ($c_{M}=0.02$ and $c_{F}=0$), pre-copulatory inbreeding avoidance initially evolved (i.e., negative $M_{a}$) but then evolved back towards random mating (i.e., $M_{a}=0$) following increasing evolution of post-copulatory inbreeding avoidance (Figure 3B).
+Similarly, when post-copulatory but not pre-copulatory inbreeding avoidance was costly ($c_{F}=0.02$ and $c_{M}=0$), post-copulatory inbreeding avoidance intially evolved ($F_{a}=0$) before returning to random fertilisation after ca $20000$ generations (Figure 3D).
 
-Evolution of post-copulatory inbreeding avoidance facilitated evolution of polyandry (Figure 3B,C), while monandry evolved in the absence of post-copulatory inbreeding avoidance (Figure 3A,D; polyandry was cost free in all these simulations).
+Evolution of post-copulatory inbreeding avoidance facilitated evolution of polyandry (Figure 3B,C).
+In the absence of post-copulatory inbreeding avoidance, polyandry did not evolve (Figure 3A,D; polyandry was cost free in all these simulations).
+
+<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
 
@@
 Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.](figures/rel_costs.png)
+Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+In all panels, polyandry is cost free.](figures/rel_costs.png)
 

### 2017-03-04 ms_pre_post.Rmd
Add quantitative statistics to last section of Results

@@
 
-<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
-
 How do cost asymmetries affect long-term persistence of reproductive strategies?
@@
 
-How is evolution of one inbreeding strategy affected by the existence of another already adaptive strategy?
+How do evolution of pre-copulatory and post-copulatory inbreeding avoidance affect one another?
 ----------------------------------------------
@@
 Such evolution still occurred, but to a much smaller degree, when pre-copulatory inbreeding avoidance was costly (Figure 4B).
-However, after $40000$ generations, $M_{a}$ values were less negative when post-copulatory inbreeding avoidance and polyandry were fixed at non-zero values than when they also evolved from initial values of zero (e.g., compare the blue lines in Figures 4A versus Figure 1A).
+However, after $40000$ generations, $M_{a}$ values were less negative when post-copulatory inbreeding avoidance and polyandry were fixed at non-zero values than when they also evolved from initial values of zero ($-15.45$ vs.
+$-17.62$; compare the blue lines in Figures 4A versus Figure 1B).
+
+<!--- Mean pre-cop value is -17.62444  in Figure 1B --->
+<!--- Mean pre-cop value is -15.44786  in Figure 4A --->
+
+<!--- I know I've mentioned this too many times, but I'm really not a fan of this kind of quantitative statistic because it doesn't really mean anything in the context of a model like this.
+At the very least though, I think it's better to put the actual numbers up because ''X% less negative'' just seems very confusing to me.
+--->
 

### 2017-03-04 ms_pre_post.Rmd
Initial edits up through the Discussion

@@
 
-<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
-
 How do evolution of pre-copulatory and post-copulatory inbreeding avoidance affect one another?
@@
 $-17.62$; compare the blue lines in Figures 4A versus Figure 1B).
+This shows that fixation of post-copulatory inbreeding avoidance weakens selection for pre-copulatory inbreeding avoidance.
 
@@
 
+<!--- I added this last sentence for summary, but stopped it a bit earlier than the suggestion because I'm not sure where you were going with it.
+If we know how selection is changed, isn't this the point?
+Evolution more broadly encompasses mutation and drift, but we've not changed either of these so why do we need to say 'weakens selection' and therefore evolution was affected?
+--->
+
 Conversely, when pre-copulatory inbreeding allele ($M_{a}$) values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently become negative over generations (Figure 4C,D).
+Fixation of pre-copulatory inbreeding avoidance therefore prevented evolution of post-copulatory inbreeding avoidance.
 However, in this case, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless whether or not post-copulatory inbreeding strategy was costly (Figure 4C,D).
@@
 ===================================================
+
+<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
 

### 2017-03-04 ms_pre_post.Rmd
Some comments on the first paragraph of the Discussion

@@
 
+<!---  I think these changes have been good ones, and hence that we’re heading along decent lines with the Discussion.
+However I think it could to with a moderately hefty edit to 1) tidy up some overarching points about what we did near the start, 2) perhaps clarify the structure of the Discussion in relation to the three questions that are now very clearly stated at the end of the Intro, and 3) tighten up the writing a bit (I can tell that the Discussion is a few iterations behind the rest of the manuscript in terms of tight and precise writing, but that’s easily fixed once we get the structure sorted).
+--->
+
+<!--- Unusually for me (and sorry if this opening was my suggestion from an earlier draft!), I’m wondering whether it’s a good idea to start this broad, or whether we’d be better to keep a bit more focused to start with, and then bring in the generality after that?
+I’ll make some suggestions, see what you think.
+Writing is NOT intended to be a definitive version, just me getting some ideas down!
+--->
+
+<!--- I do think we need to get this into the start of the Discussion.
+It’s because our current analyses don’t play around with the magnitude of ID, it’s a fixed parameter = strong.
+Think we need to make sure that’s clear in peoples’ minds, otherwise we’ll get people asking about IP etc...
+Hence my suggestion to nail it at the start – which then mirrors the start of the Intro.
+--->
+
+<!--- To me, this sentence isn’t very helpful, doesn’t say what the questions are or what we concluded, or even how we tackled them, so it seems pretty redundant.
+Can we weave into next section along lines suggested?
+--->
+
+<!--- SUGGESTED CHANGE: Strong inbreeding depression in offspring fitness is widely hypothesised to drive evolution of both pre-copulatory and post-copulatory inbreeding avoidance, and hence drive evolution of polyandry [@Zeh1997; @Jennions2000; @Tregenza2002].
+However, evolution of such degenerate (i.e.
+functionally overlapping) mechanisms of inbreeding avoidance cannot be presumed to occur independently, meaning that emerging reproductive strategies are likely to be shaped by relative costs, and might exhibit complex dynamic evolutionary feedbacks across multiple generations.
+--->
+
+<!--- I actually don't understand the motivation behind any of these suggested changes, nor the internal logic of some of these sentences.
+The proposed first sentence of the introduction now shifts from talking generally about all of our results to only referring to the first stated question.
+The proposed second sentence is especially difficult for me -- I'm not sure how to start editing it.
+The second sentence suggests that evolution of degenerate traits can't be assumed to occur independently (but this is trivially true -- almost by definition!
+And it inverts the key logic -- the point is that traits don't have independent effects *potentially leading to degeneracy*).
+The next part of the second sentence suggests it necessarily follows from degeneracy that relative costs will shape reproductive interactions, but why does this have to be the case?
+There needs to be some logical connection between these two claims that just isn't there.
+I can't really figure out how to edit this because I'm really unclear as to what the logical progression of ideas is here.
+Can you clarify what you mean by this?
+--->
+
 Evolution of reproductive strategies cannot be presumed to occur in isolation in wild populations, meaning that observed patterns of reproductive strategy within and across taxa are likely to be affected by evolutionary feedbacks and (potentially asymmetric) costs.

### 2017-03-07 ms_pre_post.Rmd
Most of the Discussion is now edited, though needs to be reviewed. Last section remains

@@
 
-<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
+<!--- ==================================================================== --->
+<!--- BEGIN COMMENTS NOT TO BE TRANSFERRED TO THE WORD DOCUMENT FOR COAUTHORS
+<!--- ==================================================================== --->
+
+<!--- Evolution of reproductive strategies involves multiple potentially interacting and degenerate phenotypes.
+Here we modelled evolution of three reproductive strategies including polyandry, pre-copulatory inbreeding avoidance, and post-copulatory inbreeding avoidance, focusing on three key questions.
+Using individual-based modelling, we found that evolution of post-copulatory inbreeding avoidance facilitated evolution of polyandry, that evolution of a costly inbreeding avoidance strategy was inhibited when the other inbreeding avoidance strategy was cost free, and that evolution of post-copulatory inbreeding avoidance but not pre-copulatory inbreeding avoidance was precluded when the other inbreeding avoidance strategy was fixed for strong inbreeding avoidance.
+We thereby conclude that evolution of inbreeding avoidance strategies and associated polyandry are likely to interact in predictable ways, potentially generating new hypotheses concerning evolution of reproductive strategies within and across taxa.
+--->
 
@@
 
+<!--- Too much/too vague no doubt – but this is a hanger to link back to the bit you flagged up as a worry in the Intro, about whether someone would query why we need ‘dynamic models’ – so here we could flag up the dynamicism again somehow?
+--->
+
 <!--- To me, this sentence isn’t very helpful, doesn’t say what the questions are or what we concluded, or even how we tackled them, so it seems pretty redundant.
@@
 
-<!--- I actually don't understand the motivation behind any of these suggested changes, nor the internal logic of some of these sentences.
-The proposed first sentence of the introduction now shifts from talking generally about all of our results to only referring to the first stated question.
-The proposed second sentence is especially difficult for me -- I'm not sure how to start editing it.
-The second sentence suggests that evolution of degenerate traits can't be assumed to occur independently (but this is trivially true -- almost by definition!
+<!--- I was wondering about reiterating a clearer KG here, but actually I think it’s fine without – see comment attached to end of this suggested paragraph. --->
+
+<!--- One of my main comments about the Discussion at the moment is that the really clear structure of the 3 questions that’s now set up at the end of the Intro and followed through the Methods and Results has completely disappeared here.
+Can we get it back again, a bit?
+Restating the questions here might be overkill, but yet I’m thinking that a short summary version might be helpful – something like this?
+--->
+
+<!--- I didn’t get much from this here, and anyway you pretty much repeat the exact same thing in the ‘conclusions’ section at the end?
+So, if we have to have a conclusions section (for JEB?), then I think it’s best there?
+--->
+
+<!--- This sentence might need tweaking a bit, but I think something like it would be a good strong end to this first para? --->
+
+<!--- So this is where I start to find the structure of the Discussion a bit hard to follow – seem to be addressing the three questions in reverse order.
+This first bit (and the link to fig 4), is really addressing question 3, isn’t it?
+And then we go on to Q2 (fig 3) and then finally Q1 (fig 1).
+This is pretty confusing.
+Would it be possible to turn this section around so that the three questions are dealt with in the ‘right’ order?
+I haven’t tried to implement.
+Or if you want to keep it like this we might need to clarify that structure and (implicitly or explicitly) note why things are reversed?
+--->
+
+<!--- ==================================================================== --->
+<!--- END COMMENTS NOT TO BE TRANSFERRED TO THE WORD DOCUMENT FOR COAUTHORS
+<!--- ==================================================================== --->
+
+Evolution of reproductive strategies cannot be presumed to occur in isolation in wild populations, and is instead likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundance) among phenotypes under selection.
+For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently feed back to drive selection for polyandry [e.g., @Zeh1997; @Jennions2000; @Tregenza2002].
+Evolution of inbreeding avoidance can be driven by selection on both pre-copulatory and post-copulatory mechanisms, so simultaneous evolution of each phenotype is likely to be affected by degeneracy, in addition to any direct costs on phenotypes.
+We used individual-based modelling to explore evolution of pre-copulatory and post-copulatory inbreeding avoidance and polyandry given (1) hard constraints on evolution of post-copulatory inbreeding avoidance, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding avoidance, and (3) evolution of one inbreeding avoidance phenotype given the pre-existence the other.
+We thereby highlight fundamental but theoretically under-developed relationships between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding avoidance.
+
+<!--- I have tried to re-work this first paragraph, but I had a very hard time following the logical flow of ideas given the suggested changes.
+I understand that you want to get all of the components of this manuscript into the front of the Discussion, but I think they need to fit together much more coherently.
+I didn't quite understand the motivation behind the suggested changes.
+For example, the proposed first sentence of the Discussion shifted from talking generally about all of our results to only referring to one of our questions.
+I didn't understand the proposed second sentence at all, which suggested that evolution of degenerate traits can't be assumed to occur independently?
+(But this is trivially true -- almost by definition!
 And it inverts the key logic -- the point is that traits don't have independent effects *potentially leading to degeneracy*).
-The next part of the second sentence suggests it necessarily follows from degeneracy that relative costs will shape reproductive interactions, but why does this have to be the case?
+The next part of the proposed second sentence suggested that it necessarily follows from degeneracy that relative costs will shape reproductive interactions, but why does this have to be the case?
 There needs to be some logical connection between these two claims that just isn't there.
-I can't really figure out how to edit this because I'm really unclear as to what the logical progression of ideas is here.
+I couldn't really figure out how to re-work it because I was really unclear as to what the logical progression of ideas was.
 Can you clarify what you mean by this?
@@
 
-Evolution of reproductive strategies cannot be presumed to occur in isolation in wild populations, meaning that observed patterns of reproductive strategy within and across taxa are likely to be affected by evolutionary feedbacks and (potentially asymmetric) costs.
-We have addressed key questions regarding the effect of such feedbacks and costs on evolution of pre-copulatory inbreeding avoidance, post-copulatory inbreeding avoidance, and polyandry.
-A critical analysis of our model engenders new predictions concerning evolutionary dynamics given the joint evolution of these traits, which may be used to formulate new empirical hypotheses within and across taxa.
+<!--- I think the logic of the first sentence is important here, though it might need some tweaks.
+The point is that phenotypes don't occur in isolation -> multiple phenotypes interact -> two types of interaction are feedbacks and degeneracy.
+Hence, degeneracy is one *type* of way that phenotypes might interact, so I think that the sentence structure needs to reflect this so readers don't get confused (i.e., we can't just skip to 'such degenerate' because it doesn't clearly follow from the previous sentence.
+--->
 
-For example, our results highlight a fundamental but theoretically under-developed relationship between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding avoidance.
-Post-copulatory inbreeding avoidance is useless for monandrous females, and most effective for highly polyandrous females that can choose amongst multiple mates to ensure that offspring are fertilised favourably.
-In contrast, pre-copulatory mechanisms are most salient for monandrous females that have no post-copulatory means for avoiding inbreeding.
-This theory is borne out in our simulation results, as selection for post-copulatory inbreeding avoidance was negligible in monandrous populations, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D).
-The effect of monandry on selection for pre-copulatory inbreeding avoidance was weaker, but pre-copulatory inbreeding avoidance was generally stronger when populations where monandrous (e.g., Figure 3A vs 3B; see also Supporting Information p.
-S1-1).
-In addition to polyandry increasing selection for post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).
-It would therefore be interesting to test the hypothesis that, across taxa, occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with degree of polyandry.
-To test this hypothesis, more work is needed to identify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
+<!--- I don't think just mentioning 'dynamic models' is enough to make a convincing argument that they were necessary to address the knowledge gap.
+If we really wanted to flesh out the idea, we would have to explain *why* we couldn't get the answer we did with non-dynamic models.
+This isn't obvious or trivial!
+--->
 
-Another general inference from our simulation results concerns the dynamics of phenotypes with highly overlapping effects with respect to selection, as realised through functionally different traits.
-The ability of structurally different phenotypes to perform the same adaptive function is an example of 'degeneracy', a term which defines a more general phenomenon whereby unique elements of a system result in identical outputs [@Edelman2001].
-Effects of degeneracy can be observed across nearly all biological scales [@Edelman2001], including complex systems affecting organismal development [e.g., @Nowak1997], adaptation [@Whitacre2010; @Whitacre2010a], and cognition [@Price2002; @Park2013], as well as population [@Atamas2009], community [@Suraci2017], and ecosystem [e.g., @Levin2008] dynamics.
-In the context of reproductive strategy, pre-copulatory inbreeding avoidance, typically expressed through mating behaviour, versus post-copulatory inbreeding avoidance, typically expressed through phenotypes affecting fertilisation, are both driven by the shared selective pressure of inbreeding depression in offspring viability.
-Hence, degeneracy occurred in our model through an overlap in how phenotypes cause adaptive inbreeding avoidance.
-Such degeneracy might increase biological robustness [@Gardner2006; @Whitacre2010a], potentially facilitating realised inbreeding avoidance across environments in which either pre-copulatory or post-copulatory mechanisms alone would be ineffective (e.g., due to sexual conflict affecting mate choice or injury affecting fertilisation).
-However, evolution of each of these strategies might decrease selection on the other strategy by modifying its impact on the degree to which a female avoids inbreeding and consequently has offspring that express inbreeding depression [*sensu* evolution of genetic redundancy; see @Nowak1997].
-The relevance of degeneracy with respect to such reproductive strategies therefore requires further theoretical development, which could result in new empirical predictions and conceptual synthesis across biological scales.
+Evolution of polyandry
+-------------------------------------------------------------------
+
+<!--- I have re-ordered the Discussion to reflect the order of the questions, but this sacrifices something by putting the specifics points ahead of more general questions (i.e., those references to Figure 4 were not related to any of the three questions specifically, but were used to help make a more general point derived from a holistic understanding of the model).
+Hence, I have created a new section for more general points concerning reproductive strategy, also removing the conclusion.
+--->
+
+The opportunity to adjust inbreeding has been widely considered as a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
+We found that when post-copulatory inbreeding avoidance could evolve, selection for polyandry was greatly strengthened (Figure 1).
+The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but our model provides support for this verbal hypothesis and therefore has widespread implications for future studies of evolution of polyandry.
+
+We predict evolution of polyandry in populations where inbreeding depression is severe and inbreeding avoidance through post-copulatory mechanisms can also evolve.
+Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa [e.g., @Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015].
+Recent studies have shown how females can successfully bias fertilisation after mating has occurred.
+For example, when female guppies (*Poecilia reticulata*) were artificially inseminated with equal quantities of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full siblings' sperm were reduced by females' ovarian fluids [@Gasparini2011].
+In black field crickets (*Teleogryllus commodus*), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs [@Bussiere2006; @Tuni2013].
+Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for further polyandry, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
 
@@
 Here we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of pre-copulatory inbreeding strategy as a lost of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of post-copulatory inbreeding strategy as depletion of energy.
-While these costs are biologically realistic, different costs will be relevant for different populations and be realised in different ways.
+While these costs thereby reflect empirical observations in some populations and are therefore biologically realistic, other types of costs have also been observed and could therefore be considered in future models.
 For example, increased risk of disease transmission has been observed for highly polyandrous females [@Roberts2015a], but such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry.
@@
 Evolution of individual phenotypes therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.
+
+<!--- I don't understand the contrast between the two comments, the first of which suggests that the empirical examples of costs cited are not needed here, and the second of which suggests that we need to be more explicit about why we did things the way we did.
+Hence, I have revised to clarify that we made the modelling choices that we did with respect to costs *because they are observed in empirical systems*.
+Of course, the costs that we modelled are not the *only* kinds of 'costs' that are observed in empirical systems (hence the Roberts reference), so other models might want to look into different types of costs.
+I agree that it would not be at all surprising if a reviewer raised a question about how we modelled the costs (or anything else), but this always seems to be true for modelling and I think it kind of misses the big picture about how models like this try to develop theory.
+We can't model *every* kind of cost that we can possibly think of, and we're not modelling a specific system where we might be able to justify some costs being more reasonable than others.
+We also can't (I don't think) logically show with an IBM that the type of cost will be arbitray with respect to the questions of interest (i.e., any cost will do).
+In the end, we have to make reasonable decisions about how to model costs and work from there.
+I think that citing empirical studies shows that our assumptions of cost type are reasonable for some systems (though potentially not others).
+Had we made different assumptions, I suspect we'd get queries from some readers wondering why we didn't do it a different way.
+--->
 
@@
 Additionally, the opportunity for post-copulatory inbreeding avoidance will also naturally depend on the degree to which females are polyandrous.
-For species in which pre-copulatory inbreeding avoidance occurs and monandry is common [@Lihoreau2007; @Metzger2010; @Metzger2010a], evolution of post-copulatory inbreeding avoidance is highly unlikely.
+For species in which pre-copulatory inbreeding avoidance occurs and polyandry is uncommon [@Lihoreau2007; @Metzger2010; @Metzger2010a], evolution of post-copulatory inbreeding avoidance is highly unlikely.
 
-Evolution of polyandry
+<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
+
+General predictions concering inbreeding avoidance and polyandry
 -------------------------------------------------------------------
 
-The opportunity to adjust inbreeding has been widely considered as a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
-We found that when post-copulatory inbreeding avoidance could evolve, selection for polyandry was greatly strengthened (Figure 1).
-The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but our model provides support for this verbal hypothesis and therefore has widespread implications for future studies of evolution of polyandry.
+Post-copulatory inbreeding avoidance is useless for monandrous females, and most effective for highly polyandrous females that can choose amongst multiple mates to ensure that offspring are fertilised favourably.
+In contrast, pre-copulatory mechanisms are most salient for monandrous females that have no post-copulatory means for avoiding inbreeding.
+This theory is borne out in our simulation results, as selection for post-copulatory inbreeding avoidance was negligible in monandrous populations, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D).
+The effect of monandry on selection for pre-copulatory inbreeding avoidance was weaker, but pre-copulatory inbreeding avoidance was generally stronger when populations where monandrous (e.g., Figure 3A vs 3B; see also Supporting Information p.
+S1-1).
+In addition to polyandry increasing selection for post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).
+It would therefore be interesting to test the hypothesis that, across taxa, occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with degree of polyandry.
+To test this hypothesis, more work is needed to identify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
 
-We predict evolution of polyandry in populations where inbreeding depression is severe and evolution of inbreeding avoidance through post-copulatory mechanisms is not constrained.
-Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa [e.g., @Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015].
-Recent studies have shown how females can successfully bias fertilisation after mating has occurred.
-For example, when female guppies (*Poecilia reticulata*) were artificially inseminated with equal quantities of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full siblings' sperm were reduced by females' ovarian fluids [@Gasparini2011].
-In black field crickets (*Teleogryllus commodus*), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs [@Bussiere2006; @Tuni2013].
-Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for further polyandry, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
+<!---  Diluting the idea of degeneracy throughout the manuscript now makes me worry that some readers will miss it entirely.
+If they're not reading carefully, they'll miss (or simply forget) the buried definition in the fourth paragraph of the Introduction.
+Because the concept of degeneracy becomes so important later on, they'll need to back track to remember what it actually means.
+I'm less a fan of 'flagging' things for this reason -- readers don't really *need* to understand degeneracy completely until now, but here they have to go all the way back to the Introduction to get the full scope of its importance.
+--->
 
-Conclusion
--------------------------------------------------------------------
-
-Evolution of reproductive strategies involves multiple potentially interacting and degenerate phenotypes.
-Here we modelled evolution of three reproductive strategies including polyandry, pre-copulatory inbreeding avoidance, and post-copulatory inbreeding avoidance, focusing on three key questions.
-Using individual-based modelling, we found that evolution of post-copulatory inbreeding avoidance facilitated evolution of polyandry, that evolution of a costly inbreeding avoidance strategy was inhibited when the other inbreeding avoidance strategy was cost free, and that evolution of post-copulatory inbreeding avoidance but not pre-copulatory inbreeding avoidance was precluded when the other inbreeding avoidance strategy was fixed for strong inbreeding avoidance.
-We thereby conclude that evolution of inbreeding avoidance strategies and associated polyandry are likely to interact in predictable ways, potentially generating new hypotheses concerning evolution of reproductive strategies within and across taxa.
+Another general inference from our simulation results concerns the dynamics of phenotypes with highly overlapping effects with respect to selection, as realised through functionally different traits.
+The ability of structurally different phenotypes to perform the same adaptive function is an example of 'degeneracy', a term which defines a more general phenomenon whereby unique elements of a system result in identical outputs [@Edelman2001].
+Effects of degeneracy can be observed across nearly all biological scales [@Edelman2001], including complex systems affecting organismal development [e.g., @Nowak1997], adaptation [@Whitacre2010; @Whitacre2010a], and cognition [@Price2002; @Park2013], as well as population [@Atamas2009], community [@Suraci2017], and ecosystem [e.g., @Levin2008] dynamics.
+In the context of reproductive strategy, pre-copulatory inbreeding avoidance, typically expressed through mating behaviour, versus post-copulatory inbreeding avoidance, typically expressed through phenotypes affecting fertilisation, are both driven by the shared selective pressure of inbreeding depression in offspring viability.
+Hence, degeneracy occurred in our model through an overlap in how phenotypes cause adaptive inbreeding avoidance.
+Such degeneracy might increase biological robustness [@Gardner2006; @Whitacre2010a], potentially facilitating realised inbreeding avoidance across environments in which either pre-copulatory or post-copulatory mechanisms alone would be ineffective (e.g., due to sexual conflict affecting mate choice or injury affecting fertilisation).
+However, evolution of each of these strategies might decrease selection on the other strategy by modifying its impact on the degree to which a female avoids inbreeding and consequently has offspring that express inbreeding depression [*sensu* evolution of genetic redundancy; see @Nowak1997].
+The relevance of degeneracy with respect to such reproductive strategies therefore requires further theoretical development, which could result in new empirical predictions and conceptual synthesis across biological scales.
 

### 2017-03-07 ms_pre_post.Rmd
Mid-sentence edit in the last paragraph, but it's time to go home

@@
 
-Another general inference from our simulation results concerns the dynamics of phenotypes with highly overlapping effects with respect to selection, as realised through functionally different traits.
-The ability of structurally different phenotypes to perform the same adaptive function is an example of 'degeneracy', a term which defines a more general phenomenon whereby unique elements of a system result in identical outputs [@Edelman2001].
-Effects of degeneracy can be observed across nearly all biological scales [@Edelman2001], including complex systems affecting organismal development [e.g., @Nowak1997], adaptation [@Whitacre2010; @Whitacre2010a], and cognition [@Price2002; @Park2013], as well as population [@Atamas2009], community [@Suraci2017], and ecosystem [e.g., @Levin2008] dynamics.
-In the context of reproductive strategy, pre-copulatory inbreeding avoidance, typically expressed through mating behaviour, versus post-copulatory inbreeding avoidance, typically expressed through phenotypes affecting fertilisation, are both driven by the shared selective pressure of inbreeding depression in offspring viability.
-Hence, degeneracy occurred in our model through an overlap in how phenotypes cause adaptive inbreeding avoidance.
-Such degeneracy might increase biological robustness [@Gardner2006; @Whitacre2010a], potentially facilitating realised inbreeding avoidance across environments in which either pre-copulatory or post-copulatory mechanisms alone would be ineffective (e.g., due to sexual conflict affecting mate choice or injury affecting fertilisation).
+<!--- By removing the sentence specifying how degeneracy works with respect to inbreeding avoidance, we are asking the readers to recall these specifics from the introduction (or go back and find them again).
+The exact mechanism by which functional overlap occurs is removed from the more vague 'phenotypic reproductive strategies'.
+I'm afraid this will lose some readers who might be a bit tired by the end of the Discussion.--->
+
+Degeneracy occurs at nearly all biological scales [@Edelman2001], including complex systems affecting organismal development [e.g., @Nowak1997], adaptation [@Whitacre2010; @Whitacre2010a], and cognition [@Price2002; @Park2013], as well as population [@Atamas2009], community [@Suraci2017], and ecosystem [e.g., @Levin2008] dynamics.
+In our model, degeneracy occurred through overlaps in how different reproductive strategies caused adaptive inbreeding avoidance.
+In general, degeneracy might increase biological robustness by fine-tuning degenerate phenotypes to different local environments [@Gardner2006; @Whitacre2010a].
+For example, such degeneracy might facilitate inbreeding avoidance via pre-copulatory or post-copulatory mechanisms depending on different selective environments in which either pre-copulatory or post-copulatory mechanisms alone would be ineffective (e.g., due to sexual conflict affecting mate choice or injury affecting fertilisation).
 However, evolution of each of these strategies might decrease selection on the other strategy by modifying its impact on the degree to which a female avoids inbreeding and consequently has offspring that express inbreeding depression [*sensu* evolution of genetic redundancy; see @Nowak1997].

### 2017-03-07 ms_pre_post.Rmd
Further comments, again

@@
 I agree that it would not be at all surprising if a reviewer raised a question about how we modelled the costs (or anything else), but this always seems to be true for modelling and I think it kind of misses the big picture about how models like this try to develop theory.
-We can't model *every* kind of cost that we can possibly think of, and we're not modelling a specific system where we might be able to justify some costs being more reasonable than others.
+We can't model *every* kind of cost that we can possibly think of (nor would we want to), and we're not modelling a specific system where we might be able to justify some costs being more reasonable than others.
 We also can't (I don't think) logically show with an IBM that the type of cost will be arbitray with respect to the questions of interest (i.e., any cost will do).
@@
 Had we made different assumptions, I suspect we'd get queries from some readers wondering why we didn't do it a different way.
+I don't mean to keep belabouring this point, but I think that the point of using a model to develop theory isn't to match your assumptions with empirical reality as closely as possible (if we tried, we'd miss a lot of important stuff!).
+Assumptions need to be clear and useful for addressing the theoretical question(s) of interest -- when I review theory papers, this is the criteria I have in mind, not (necessarily) whether or not the assumptions match how things are in nature (they might deliberately not be, for the better!).
+The only reason I have repeatedly justified the cost assumption is, really, for fear that readers might not entirely understand the nature of model assumptions in theory.
 --->

### 2017-03-07 ms_pre_post.Rmd
Another comment -- maybe shorten later

@@
 
+<!---If we're spending this much time justifying an assumption, then we should be able to explain *why* it's an important assumption *with respect to addressing our questions* (there are hundreds of other assumptions we don't spend time on -- number of loci probably isn't going to affect our take-home message).
+If we can't, and the answer is that 'we don't know if it's important or not', then we're probably not doing theory very well.
+Actually, I don't think the nature of the costs is going to be important because it's not going to affect any key hypotheses that might be derived from our model -- the effect of a direct negative cost has a very clear interpretatation; changing how a cost is paid might quantitatively affect the end *net* cost as a counter-balance to selection, but so will changing the exact values of the costs we do use.
+There's no good reason to believe that the way a cost is paid will affect any of the major conclusions (degeneracy is important, polyandry is more likely to evolve given post-copulatory selection, etc.) except by tweaking the overall net cost countering adaptive benefit of inbreeding avoidance (alternatively, if we *can* think of one, it would be a great opportunity for another theory paper!).
+--->
+
 In our model, existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, evolution of post-copulatory inbreeding avoidance (Figure 3C,D).

### 2017-03-07 ms_pre_post.Rmd
One more point

@@
 I don't mean to keep belabouring this point, but I think that the point of using a model to develop theory isn't to match your assumptions with empirical reality as closely as possible (if we tried, we'd miss a lot of important stuff!).
-Assumptions need to be clear and useful for addressing the theoretical question(s) of interest -- when I review theory papers, this is the criteria I have in mind, not (necessarily) whether or not the assumptions match how things are in nature (they might deliberately not be, for the better!).
-The only reason I have repeatedly justified the cost assumption is, really, for fear that readers might not entirely understand the nature of model assumptions in theory.
+Assumptions need to be clear and useful for addressing the theoretical question(s) of interest -- in other words, the model needs to change *how* people think, not *what* they think.
+When I review theory papers, this is the criteria I have in mind, not (necessarily) whether or not the assumptions match how things are in nature (they might deliberately not be, for the better!).
+The only reason I have repeatedly justified the cost assumption is, really, for fear that readers might not entirely understand the nature of model assumptions in theory, not because I think the specifics of the assumptions that we make actually matter in terms of thinking about the three aspects of reproductive strategy we consider.
 --->

### 2017-03-08 ms_pre_post.Rmd
First pass of revisions is complete

@@
 
-Post-copulatory inbreeding avoidance is useless for monandrous females, and most effective for highly polyandrous females that can choose amongst multiple mates to ensure that offspring are fertilised favourably.
-In contrast, pre-copulatory mechanisms are most salient for monandrous females that have no post-copulatory means for avoiding inbreeding.
-This theory is borne out in our simulation results, as selection for post-copulatory inbreeding avoidance was negligible in monandrous populations, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D).
-The effect of monandry on selection for pre-copulatory inbreeding avoidance was weaker, but pre-copulatory inbreeding avoidance was generally stronger when populations where monandrous (e.g., Figure 3A vs 3B; see also Supporting Information p.
+Post-copulatory inbreeding avoidance is useless for females that are not polyandrous, and most effective for highly polyandrous females that can choose amongst multiple mates to ensure that offspring are fertilised favourably.
+In contrast, pre-copulatory mechanisms are most salient for females that mate only once and therefore have no post-copulatory opportunity to avoiding inbreeding.
+This theory is borne out in our simulation results, as selection for post-copulatory inbreeding avoidance was negligible in populations where polyandry did not evolve, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D).
+Selection for pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information p.
 S1-1).
@@
 In general, degeneracy might increase biological robustness by fine-tuning degenerate phenotypes to different local environments [@Gardner2006; @Whitacre2010a].
-For example, such degeneracy might facilitate inbreeding avoidance via pre-copulatory or post-copulatory mechanisms depending on different selective environments in which either pre-copulatory or post-copulatory mechanisms alone would be ineffective (e.g., due to sexual conflict affecting mate choice or injury affecting fertilisation).
-However, evolution of each of these strategies might decrease selection on the other strategy by modifying its impact on the degree to which a female avoids inbreeding and consequently has offspring that express inbreeding depression [*sensu* evolution of genetic redundancy; see @Nowak1997].
+For example, degeneracy might ensure successful inbreeding avoidance through pre-copulatory or post-copulatory mechanisms where or when avoidance through the other mechanism is ineffective (e.g., due to sexual conflict affecting mate choice or injury affecting fertilisation).
+However, evolution of one inbreeding avoidance mechanism might also weaken selection on the other by modifying the latter's impact on total realised inbreeding avoidance [*sensu* evolution of genetic redundancy; see @Nowak1997].
 The relevance of degeneracy with respect to such reproductive strategies therefore requires further theoretical development, which could result in new empirical predictions and conceptual synthesis across biological scales.
+
+<!--- I don't understand the comment about 'getting at the genetic scales'.  --->
 

### 2017-03-08 ms_pre_post.Rmd
Finish tweaking figure legends

@@
   polyandry
-author: "A. Bradley Duthie, Ryan R. Germain, and Jane M. Reid"
+author: ""
 date: "December 15, 2016"
@@
 Nevertheless, due to the threshold nature of expression of the polygenic polyandry phenotype, polyandry and monandry are expressed in both populations.
-Histograms in (B) and (D) show females' tendency for polyandry phenotypes in the final generation; white and grey shading indicates monandrous and polyandrous females, respectively.](figures/Pp_vals.png)
+Histograms in (B) and (D) show females' tendency for polyandry phenotypes in the final generation; white and grey shading indicates monandrous and polyandrous females, respectively.
+Arrows and numbers indicate mean phenotype values.
+Because each trait includes 10 diploid loci with additive effects, phenotype values are ca 20 times allele values.](figures/Pp_vals.png)
 
-![Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy can evolve and pre-copulatory inbreeding strategy is (A) fixed for random mating or (B) can also evolve.
+![Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding avoidance ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (A) fixed for random mating or (B) can also evolve.
 Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
 In all panels, polyandry is cost free.](figures/rel_costs.png)
 
-![Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is (A and C) cost-free or (B and D) costly.
+![Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is cost-free (A, $c_{M} = 0$; C, $c_{F} = 0$) or costly (B, $c_{M}=0.02$; D, $c_{F}=0.02$).
 Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.

### 2017-03-10 ms_pre_post.Rmd
Edit abstract

@@
   polyandry
-author: ""
+author: ''
 date: "December 15, 2016"
 output:
+  pdf_document:
+    fig_caption: yes
+  html_document: default
   word_document:
@@
 
-Inbreeding avoidance has been widely hypothesised to evolve through pre-copulatory and post-copulatory mechanisms as a consequence of inbreeding depression in offspring viability and female multiple mating (polyandry).
-However, no theoretical framework exists from which to derive hypotheses concerning joint evolution of pre-copulatory and post-copulatory inbreeding avoidance.
-Evolution of post-copulatory inbreeding avoidance necessitates polyandry, potentially leading to complex evolutionary dynamics among inbreeding strategies and female mating frequency, each of which might be affected by direct negative costs.
-We use individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry across multiple cost combinations given severe inbreeding depression.
-We find that evolution of post-copulatory inbreeding avoidance increases selection for polyandry, that selection for costly inbreeding strategies was weak or negligible given a non-costly alternative strategy.
-Established pre-copulatory inbreeding avoidance generally precluded evolution of polyandry and therefore inbreeding avoidance, but established post-copulatory inbreeding avoidance did not preclude pre-copulatory inbreeding avoidance from evolving.
-We thereby provide a general framework for understanding joint evolution of pre-copulatory and/or post-copulatory inbreeding avoidance, and conclude that evolution of inbreeding avoidance phenotypes and associated polyandry are predicted to interact and be strongly affected by direct costs.
+Inbreeding depression is widely hypothesised to drive adaptive evolution of pre-copulatory and post-copulatory mechanisms of inbreeding avoidance, which in turn are hypothesised to affect evolution of polyandry (i.e., female multiple mating).
+However, surprisingly little theory or modelling critically examines selection for pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, given evolutionary constraints and direct costs, or examines how evolution of inbreeding avoidance strategies might feed back to affect evolution of polyandry.
+Selection for post-copulatory but not pre-copulatory inbreeding avoidance requires polyandry, while interaction between pre-copulatory and post-copulatory inbreeding avoidance might cause functional redundancy (i.e., 'degeneracy') potentially generating complex evolutionary dynamics among inbreeding strategies and polyandry.
+We use individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression and different evolutionary constraints and direct costs.
+We find that evolution of post-copulatory inbreeding avoidance causes selection for increased polyandry, and that selection for a costly inbreeding avoidance strategy was weak or negligible given a non-costly alternative strategy.
+Further, fixed pre-copulatory inbreeding avoidance generally precluded evolution of polyandry and therefore post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude pre-copulatory inbreeding avoidance from evolving.
+We thereby provide a general framework for understanding joint evolution of pre-copulatory and/or post-copulatory inbreeding avoidance, and conclude that evolution of inbreeding avoidance phenotypes and associated polyandry are predicted to be strongly affected by evolutionary feedbacks and degeneracy, and by direct costs on phenotypes affecting reproductive strategy.
+
+<!--- The phrasing ''and hence to drive evolution of polyandry'' made it sound a bit like polyandry is believed to be a necessary consequency of inbreeding avoidance, but I don't think this is the case --->
 

### 2017-03-10 ms_pre_post.Rmd
Minor Introduction tweaks

@@
 <!--- I'm not sure I understand the point of ''tractable systems'' for post-copulatory inbreeding avoidance -- why not just 'species', as with pre-copulatory? --->
+<!--- ''However, there is yet no theory ...'' seems a bit off; we don't really use the model to predict what combinations should be favoured by selection or weigh in on the above studies...
+at least, not in a way that is clear to me (if I'm mistaken -- could there be an example of how predictions in one of the above systems follows from our model?).
+--->
 <!--- What is the difference between 'rationalised' and 'interpreted'? Do these refer to the same thing, and if so, can we get rid of 'rationalised'? --->
@@
 Developing theory on evolution of polyandry given inbreeding depression, @Duthie used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance.
-A recent genetically-explicit individual-based model examined the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance [@Duthie].
-Evolution of polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., 'costs') on polyandry were small, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
+Selection for polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., 'costs') on polyandry were small, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
 Without these conditions, increasing polyandry tended to increase rather than decrease the overall degree of inbreeding that females experienced, and hence reduce offspring fitness.
@@
 
+<!--- Evolution of polyandry often occurred, but it was only under highly restrictive conditions that it was *adaptive* (i.e., evolved due to selection --->
 <!--- I don't think 'provide initial theory' is particularly clear (i.e., 'initial' in what respect?), so I've made an edit to the first sentence, though it does seem slightly redundant in both of our cases.
@@
 However, such trajectories will also depend on the indirect benefits of each strategy, which might also differ and vary in relation to the evolution of the other strategy.
-Dynamic models that track the frequencies of alleles underlying multiple reproductive strategies that might influence each other's evolution across generations, and that are enacted among relatives that themselves result from reproductive strategies and inbreeding depression expressed in previous generations, are consequently useful to understand and predict evolutionary outcomes.
+Dynamic models that track the frequencies of alleles underlying multiple reproductive strategies that might influence each others evolution across generations, and that are enacted among relatives that themselves result from reproductive strategies and inbreeding depression expressed in previous generations, are consequently useful to understand and predict evolutionary outcomes.
 
@@
 The implicit argument seems to be something like, ''look, there's a lot of complex stuff that's happening here; we can't figure out how to model how the evolutionary trajectories will play out without a dynamic model, so we're just going to assume that it's not possible''.
-My tendency is to be careful with these kinds of things, and maybe instead emphasise that dynamic models *can be useful* for understanding these kinds of dynamics without suggesting that they are necessary (time will tell if this is true).
+My tendency is to be careful with these kinds of bold claims, and maybe instead emphasise that dynamic models *can be useful* for understanding these kinds of dynamics without suggesting that they are necessary (time will tell if this is true -- I don't want to dissuade someone from giving it a shot -- Corina tarnita, whose work I've often disagreed with, made a good point about this in a recent comment of Physics of Life Reviews).
 --->

### 2017-03-11 ms_pre_post.Rmd
More edits through discussion on second pass

@@
 --->
-<!--- What is the difference between 'rationalised' and 'interpreted'? Do these refer to the same thing, and if so, can we get rid of 'rationalised'? --->
+<!--- What is the difference between 'rationalised' and 'interpreted'?
+Do these refer to the same thing, and if so, can we get rid of 'rationalised'?
+The word 'rationalised' to me suggests guided reasoning instead of honest interpretation.
+--->
 <!--- I still think that the end of this paragraph misses the point a bit with regard to how theory is supposed to function. --->
@@
 I suspect this shouldn't be a problem in practice, but I wonder if there's a better way to word this  --->
-
 <!--- Regarding the removal of 'conceptualise', are we suggesting then that prediction is only or most important thing to predict in the long term, and that we can do it with our model?
@@
 All males in the population are assumed to be available for any female to choose.
-We therefore assume that there is no opportunity cost of male mating such that mating with one female does not reduce a male's availability to mate with any other female.
+We therefore assume that there is no opportunity cost of male mating, so mating with one female does not reduce a male's availability to mate with any other female.
 Individual females mate with their total allotment of $N_{males}$ without replacement, meaning that $N_{males}$ models a female's total number of different mates rather than solely her total number of matings.
@@
 
-Each male's value with respect to each focal female is then divided by the sum of all $Q^{m}_{ij}$ values across all males with respect to that female, thereby assigning each male a relative perceived quality $q^{m}_{ij}$, which is constrained to values between zero and one.
+Each male's value with respect to a focal female is then divided by the sum of all $Q^{m}_{ij}$ values across all males with respect to that female, thereby assigning each male a relative perceived quality $q^{m}_{ij}$, which is constrained to values between zero and one.
 The value of $q^{m}_{ij}$ then defines the probability that a focal female mates with the male.
@@
 These $q^{f}_{ij}$ values, which lie between zero and one, define the probability of paternity.
-As with mate choice, one vector element representing a single male is samplied as weighted by these probabilities to determine paternity.
+As with mate choice, one vector element representing a single male is sampled as weighted by these probabilities to determine paternity.
 Females produce $n$ offspring, so $q^{f}_{ij}$ values are sampled $n$ times independently and with replacement for each female to determine the realised distribution of sires.
@@
 Similarly, when post-copulatory but not pre-copulatory inbreeding avoidance was costly ($c_{F}=0.02$ and $c_{M}=0$), post-copulatory inbreeding avoidance intially evolved ($F_{a}=0$) before returning to random fertilisation after ca $20000$ generations (Figure 3D).
+
+<!--- Something about this 'evolved' and 'evolved back' language just sounds very amateurish -- can't we reframe this in terms of selection? --->
 

### 2017-03-11 ms_pre_post.Rmd
Final edits

@@
 
+<!--- Is this really correct?
+Degeneracy is defined by different processes having the same effect, so I don't think pre- and post-copulatory inbreeding avoidance are *affected by* degeneracy so much as *characterised by*, or *an example of* degeneracy.
+--->
+
 <!--- I think the logic of the first sentence is important here, though it might need some tweaks.
@@
 The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but our model provides support for this verbal hypothesis and therefore has widespread implications for future studies of evolution of polyandry.
+
+<!--- Something doesn't seem quite right here.
+Our model doesn't provide support for the verbal hypothesis in the same way that real data would.
+Perhaps it *clarifies* the verbal hypothesis, *formalises?* --->
 

### 2017-03-11 ms_pre_post.Rmd
Final edits before sending to coauthors

@@
 The implicit argument seems to be something like, ''look, there's a lot of complex stuff that's happening here; we can't figure out how to model how the evolutionary trajectories will play out without a dynamic model, so we're just going to assume that it's not possible''.
-My tendency is to be careful with these kinds of bold claims, and maybe instead emphasise that dynamic models *can be useful* for understanding these kinds of dynamics without suggesting that they are necessary (time will tell if this is true -- I don't want to dissuade someone from giving it a shot -- Corina tarnita, whose work I've often disagreed with, made a good point about this in a recent comment of Physics of Life Reviews).
+My tendency is to be careful with these kinds of bold claims, and maybe instead emphasise that dynamic models *can be useful* for understanding these kinds of dynamics without suggesting that they are necessary (time will tell if this is true -- I don't want to dissuade someone from giving it a shot -- Corina Tarnita, whose work I've often disagreed with, made a good point about this in a recent comment of Physics of Life Reviews).
 --->
@@
 I have rewritten these sections in attempt to make the writing clearer.
-TODO: Additionally, I have tweaked the figure legends appropriately.--->
+TODO: Additionally, I have tweaked the figure legends appropriately.
+--->
 
@@
 For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently feed back to drive selection for polyandry [e.g., @Zeh1997; @Jennions2000; @Tregenza2002].
-Evolution of inbreeding avoidance can be driven by selection on both pre-copulatory and post-copulatory mechanisms, so simultaneous evolution of each phenotype is likely to be affected by degeneracy, in addition to any direct costs on phenotypes.
+Evolution of inbreeding avoidance can be driven by selection on both pre-copulatory and post-copulatory mechanisms, so simultaneous evolution of each phenotype is likely to be defined by degeneracy, in addition to any direct costs on phenotypes.
 We used individual-based modelling to explore evolution of pre-copulatory and post-copulatory inbreeding avoidance and polyandry given (1) hard constraints on evolution of post-copulatory inbreeding avoidance, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding avoidance, and (3) evolution of one inbreeding avoidance phenotype given the pre-existence the other.

### 2017-03-18 ms_pre_post.Rmd
New round -- making clean edits with no comments for now. Change title and abstract

@@
 ---
-title: Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated
-  polyandry
+title: Evolution of pre-copulatory and post-copulatory strategies of inbreeding avoidance and associated polyandry
 author: ''
@@
 However, surprisingly little theory or modelling critically examines selection for pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, given evolutionary constraints and direct costs, or examines how evolution of inbreeding avoidance strategies might feed back to affect evolution of polyandry.
-Selection for post-copulatory but not pre-copulatory inbreeding avoidance requires polyandry, while interaction between pre-copulatory and post-copulatory inbreeding avoidance might cause functional redundancy (i.e., 'degeneracy') potentially generating complex evolutionary dynamics among inbreeding strategies and polyandry.
+Selection for post-copulatory inbreeding avoidance but not for pre-copulatory inbreeding avoidance, requires polyandry, while interactions between pre-copulatory and post-copulatory inbreeding avoidance might cause functional redundancy (i.e., 'degeneracy') potentially generating complex evolutionary dynamics among inbreeding strategies and polyandry.
 We use individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression and different evolutionary constraints and direct costs.
-We find that evolution of post-copulatory inbreeding avoidance causes selection for increased polyandry, and that selection for a costly inbreeding avoidance strategy was weak or negligible given a non-costly alternative strategy.
-Further, fixed pre-copulatory inbreeding avoidance generally precluded evolution of polyandry and therefore post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude pre-copulatory inbreeding avoidance from evolving.
+We find that evolution of post-copulatory inbreeding avoidance causes selection for increased polyandry, and that selection for a costly inbreeding avoidance strategy was weak or negligible given a cost free alternative strategy.
+Further, fixed pre-copulatory inbreeding avoidance generally precluded evolution of polyandry and therefore post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance.
 We thereby provide a general framework for understanding joint evolution of pre-copulatory and/or post-copulatory inbreeding avoidance, and conclude that evolution of inbreeding avoidance phenotypes and associated polyandry are predicted to be strongly affected by evolutionary feedbacks and degeneracy, and by direct costs on phenotypes affecting reproductive strategy.

### 2017-03-18 ms_pre_post.Rmd
Edits up through the Introduction

@@
 
+<!--- 
+General notes about this version:
+
+If we're interested in evolution and not selection (hence the phrasing), then we really need to put more energy into looking at the assumptions underlying genetic variance, and other things having to do with quantitative genetics.
+At the moment, we're just assuming that there is pretty much always enough genetic variance on which selection to act.
+I've assumed we'd be most interested in selection given three reproductive strategy traits, but if we're interested in evolvability of traits, then I think we're ignoring some key things.
+
+--->
+
 Abstract
@@
 
-<!--- The phrasing ''and hence to drive evolution of polyandry'' made it sound a bit like polyandry is believed to be a necessary consequency of inbreeding avoidance, but I don't think this is the case --->
-
 Introduction
@@
 Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm provided by females' mates (i.e., 'fair raffle').
-Overall, polyandry can therefore simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice, and has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002].
-Resulting indirect selection on polyandry could explain its evolution in cases where multiple mating does not increase female reproductive success, or even where polyandry reduces reproductive success and therefore imposes direct fitness costs to polyandrous females.
+Overall, polyandry can therefore simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
+Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002].
+Resulting indirect selection on polyandry could explain its evolution in cases where multiple mating does not increase female reproductive success, or even where polyandry reduces reproductive success and therefore imposes direct fitness costs on polyandrous females.
 However, despite such widely-invoked hypotheses, there is surprising little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
 
-<!--- Something seems redundant about ''sperm provided by females' mates''. This is probably okay though  --->
-<!--- I think I know what you mean, but is there any reason not to be bolder than 'help explain'?
-Could it not entirely explain most or all of the reason for selection for polyandry in some cases?
---->
-<!--- I've left out survival, as decreased survival isn't really a cost unless it reduces reproductive success --->
-<!--- Parker and Birkhead (2013) was cited to identify the problem of polyandry, but I've removed it here because they don't really discuss inbreeding, and there wasn't really a good way to cite them here given the edits to the text.
---->
-
-Despite the paucity of theory and resulting predictions, numerous empirical studies on diverse species have tested for, and found evidence of, female inbreeding avoidance in systems where polyandry also occurs.
+Despite the paucity of theory and resulting predictions, numerous empirical studies on diverse species have tested for, and in some cases found evidence of, female inbreeding avoidance in systems where polyandry also occurs [@Arct2015; but see @Reid2015a].
 However, relatively few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
-Pre-copulatory inbreeding avoidance has been reported in diverse species, spanning sweet potato weevils [*Cylas formicarius*, @Kuriwada2011], purple-crowned fairy-wrens [*Malurus coronatus*, @Kuriwada2011], and a tropical butterfly [*Bicyclus anynana*, @Fischer2015], while post-copulatory inbreeding avoidance has been reported in species including red junglefowl [*Gallus gallus*, @Pizzari2004] and crickets [*Teleogryllus oceanicus*, @Simmons2006; *Gryllus bimaculatus*, @Bretman2009].
+Pre-copulatory inbreeding avoidance has been reported in diverse species, spanning sweet potato weevils [*Cylas formicarius*, @Kuriwada2011], purple-crowned fairy-wrens [*Malurus coronatus*, @Kuriwada2011], and a tropical butterfly [*Bicyclus anynana*, @Fischer2015], while post-copulatory inbreeding avoidance has been reported in red junglefowl [*Gallus gallus*, @Pizzari2004] and crickets [*Teleogryllus oceanicus*, @Simmons2006; *Gryllus bimaculatus*, @Bretman2009].
 Evidence for both pre-copulatory and post-copulatory inbreeding avoidance is available across different studies of Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015].
@@
 However, there is as yet no theory that predicts what combinations of pre-copulatory and post-copulatory inbreeding avoidance and polyandry should be favoured by selection when all combinations of phenotypes can evolve.
-Consequently, there is no theory that allows the diversity of existing empirical results regarding pre-copulatory and post-copulatory inbreeding avoidance to be rationalised or interpreted, and no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
+Consequently, there is no theory that allows the diversity of existing empirical results regarding pre-copulatory and post-copulatory inbreeding avoidance to be interpreted, and no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
 
-<!--- I don't know of any review articles or meta-analyses that look at polyandry to avoid inbreeding. At least, none within the last 10 years. --->
-<!--- I'm not sure I understand the point of ''tractable systems'' for post-copulatory inbreeding avoidance -- why not just 'species', as with pre-copulatory? --->
-<!--- ''However, there is yet no theory ...'' seems a bit off; we don't really use the model to predict what combinations should be favoured by selection or weigh in on the above studies...
-at least, not in a way that is clear to me (if I'm mistaken -- could there be an example of how predictions in one of the above systems follows from our model?).
---->
-<!--- What is the difference between 'rationalised' and 'interpreted'?
-Do these refer to the same thing, and if so, can we get rid of 'rationalised'?
-The word 'rationalised' to me suggests guided reasoning instead of honest interpretation.
---->
-<!--- I still think that the end of this paragraph misses the point a bit with regard to how theory is supposed to function. --->
-
-Developing theory on evolution of polyandry given inbreeding depression, @Duthie used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance.
+To develop theory on evolution of polyandry given inbreeding depression, @Duthie used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance.
 Selection for polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., 'costs') on polyandry were small, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
@@
 Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance, and hence the resulting degree of inbreeding avoidance, was consequently restricted [@Duthie].
-
-<!--- Evolution of polyandry often occurred, but it was only under highly restrictive conditions that it was *adaptive* (i.e., evolved due to selection --->
-<!--- I don't think 'provide initial theory' is particularly clear (i.e., 'initial' in what respect?), so I've made an edit to the first sentence, though it does seem slightly redundant in both of our cases.
---->
 
@@
 
-<!--- the 'polyandry and pre-copulatory and post-copulatory inbreeding avoidance' seems technically off.
-It relies on readers to recognise that 'inbreeding avoidance' only applies to the first two items in the list.
-I suspect this shouldn't be a problem in practice, but I wonder if there's a better way to word this  --->
-<!--- Regarding the removal of 'conceptualise', are we suggesting then that prediction is only or most important thing to predict in the long term, and that we can do it with our model?
-I'm not sure if I agree with either.
---->
-
 The few previous models that considered the evolution of inbreeding avoidance through mate choice (as opposed to dispersal) have implicitly or explicitly considered the fate of a rare allele underlying pre-copulatory inbreeding avoidance in a population initially fixed for random mating [e.g., @Parker1979; @Parker2006; @Duthie; @Duthie2016a].
@@
 
-<!--- I'm not entirely sure the 'resulting indirect selection' helps --->
-
-<!--- I've made the suggested hedging changes.
-I originally introduced things boldly with 'preclude' or 'eliminate' by themselves as a way to introduce readers to the idea of the logic in the strongest terms possible, without thinking that readers would try to draw definite conclusions in the introduction or dwell on exceptions.
-Of course, as with anything in biology, the empirical (or even IBM) reality is going to be messier.
---->
-
-<!--- Along the lines of the above then, I don't think it's always helpful to use 'evolution' as a short-hand for when we mean 'adaptive evolution'.
-For example, elimation of positive selection on alleles might not 'impede evolution' at all (which will still happen as long as there is mutation, drift, etc.), but rather change the direction of evolution.
---->
-
-<!--- I don't understand why 'the simultaneous' invasion dynamics was being emphasised.
-Isn't the point of invasion analysis to look at one thing at a time and see whether or not the trait can invade (this is what we talk about in this paragraph, at least, and what we do later).
-By constraints, I mean something to the effect of *not having everything start out at zero and evolve simultaneously, which is biologically unrealistic*.--->
-
-<!--- I still don't like this last sentence very much.
-It doesn't really explain *why* new theory is needed, nor why such a specific set of modelling assumptions are required to address the theoretical question.
-I'm not even sure that I see a clear theoretical question in there.
---->
-
 Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will depend not only on the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also on the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
@@
 Females that express post-copulatory choice might pay initial energetic costs associated with developing the physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
-If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly inbreeding strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
+If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly inbreeding avoidance strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
 However, such trajectories will also depend on the indirect benefits of each strategy, which might also differ and vary in relation to the evolution of the other strategy.
@@
 
-<!--- Do we really need ''absolute and relative'' frequencies? This just gets me thinking about the distinction and why it might be important, but we don't actually talk about that here. --->
-
-<!--- I think that the addition to the last sentence here is probably an improvement, but it still doesn't quite address my question -- there's not much of an argument for concluding that dynamic models are *required*.
-The implicit argument seems to be something like, ''look, there's a lot of complex stuff that's happening here; we can't figure out how to model how the evolutionary trajectories will play out without a dynamic model, so we're just going to assume that it's not possible''.
-My tendency is to be careful with these kinds of bold claims, and maybe instead emphasise that dynamic models *can be useful* for understanding these kinds of dynamics without suggesting that they are necessary (time will tell if this is true -- I don't want to dissuade someone from giving it a shot -- Corina Tarnita, whose work I've often disagreed with, made a good point about this in a recent comment of Physics of Life Reviews).
---->
-
-We use individual-based modelling to address three key questions regarding evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression.
-First, does evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance facilitate evolution of polyandry that is otherwise severely constrained from increasing relatedness of additional mates?
+We use individual-based modelling to address three key questions regarding evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given opportunity for inbreeding and strong inbreeding depression.
+First, does evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance facilitate evolution of polyandry that is otherwise severely constrained by increasing relatedness of polyandrous females' additional mates?
 Second, how do costs associated with polyandry and pre-copulatory and post-copulatory inbreeding avoidance affect evolutionary outcomes and, in particular, the long-term persistence of reproductive strategies given cost asymmetry?
 Third, how is selection for initially rare pre-copulatory or post-copulatory inbreeding avoidance affected if the other strategy of inbreeding avoidance is already fixed?
-By addressing these questions, we illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes; we thereby provide a framework for deriving hypotheses amenable to empirical tests within and across taxa.
-
-<!--- the 'outcomes; we' replaces the 'outcomes and' just to avoid making it sound like the second part of the sentence follows just from 'diverse evolutionary outcomes' instead of the whole first part.
---->
+By addressing these questions, we illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
+We thereby provide a framework for deriving hypotheses amenable to empirical tests within and across taxa.
 
@@
 
-<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
-
 General predictions concering inbreeding avoidance and polyandry

### 2017-03-18 ms_pre_post.Rmd
Edits up through Methods and first subsection of Results

@@
 I've assumed we'd be most interested in selection given three reproductive strategy traits, but if we're interested in evolvability of traits, then I think we're ignoring some key things.
+
+I think people will have a problem with our approach if it is not clear why our approach is the best one for addressing our key questions.
+I sometimes see researchers using a population, adaptive dynamic, individual-based, etc., not because it is the appropriate model for addressing their question, but because it's the one with which they are most familiar.
+As a result, models can become mathematically intractable (should have used an IBM) or conceptually incoherent (should have simplified in some way).
+We need to be able to make it clear why we are using such a complex individual-based model instead of something else.
+
+My concern with some unusual highlighting of assumptions isn't (of course) that we're going to make some readers less confused.
+My concern is that we're going to make some readers *more* confused.
+Theoretically literate readers might be confused by some of the assumptions we keep coming back to, thinking that we're making a biological point about their relative importance that I don't think we are.
+I don't want to write a paper just that gets through review by playing to people's misconceptions (even if those who hold such misconceptions are the majority) because it rienforces the idea that those misconceptions are justified.
+If we continue to do this, then writing and publishing good theory will get even more difficult in the future.
+Increasingly I fear that I am doing my colleagues who work on theory a disservice by writing papers that placating people's concerns rather than articulating why (some, but of course not all) these concerns are misplaced, and hence setting a bad precedent.
+
+Hence, when we explain why a cost of 0.02 is appropriate, we are giving readers the impression that its value really needed to be justified.
+I would much prefer to explain why this isn't necessarily the case, and what a cost means in the context of exploring theory, so as to avoid reviewers of other papers point to Duthie et al.
+(XXXX) and say, ''they justified their cost, so you should have to as well!''.
+I tend to see the same thing for mutation rates -- the whole point of setting a mutation rate (usually to 0.001, for purely arbitrary reasons) is to introduce a bit of variation and see what happens.
+The exact rate is inconsequential with respect to most theoretical questions that models address (i.e., changing it might changes outcomes a bit, perhaps even qualitatively, but it would not change how peoples *thinking* and *conceptualisation* of biology would be affected by the model).
+If a reader is worried about the exact rate of mutation then they probably aren't actually understanding the point of the model.
 
@@
 
-<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
-
 We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance, by tracking the dynamics of alleles underlying reproductive strategies enacted by interacting females and males within a small focal population.
@@
 
-<!--- Avoided 'used an IBM' to prevent the redundancy of 'used an IBM to model'--->
-
-<!--- I have added a sentence like that suggested, hitting the key evolutionary processes (as all pop-geneticists will recognise these as fundamental, emphasising that we're accounting for all the possible ways evolution can occur).
-It's tempting to remove 'gene-flow', which we only really use to prevent kinships from getting too high, but without it it sounds as if we're leaving something out.
-I don't see why this deals with the concern in the intro though -- the sentence just says what we did; it doesn't really explain why we *needed* to do what we did to address the knowledge gap.
---->
-
 Costs
@@
 
-Phenotypic values for tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$) each have costs that are assumed to independently increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
-The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
+Phenotypic values for tendency for polyandry ($P_{p}$), pre-copulatory inbreeding avoidance strategy ($M_{p}$), and post-copulatory inbreeding avoidance strategy ($F_{p}$) each have costs that are assumed to independently increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
+The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding avoidance strategy ($c_{M}$), and post-copulatory inbreeding avoidance strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
 Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
-Absolute values are used for applying costs to inbreeding strategies because both negative and positive $M_{p}$ and $F_{p}$ values affect the degree of inbreeding.
+Absolute values are used for applying costs to inbreeding avoidance strategies (hereafter simply 'inbreeding strategies') because both negative and positive $M_{p}$ and $F_{p}$ values affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively.
 In contrast, only positive values of $P_{p}$ cause females to be polyandrous (see below).
-Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with each trait value.
-
-<!--- One issue with the 'see Discussion' though is that it's not clear what we're telling readers to see the discussion *about*.
-Were I to read this as reviewer, I would be confused, ''see Discussion?
-What for?
-Because you made an assumption in a model, the biological context of which was already explained in the Introduction?
-(2nd to last paragraph)''.
-I've tried to provide a bit of context in parentheses, but it makes me nervous catering to any (mistaken) readers who might be confused about what assumptions are used for in models.
-I'd rather deal with confused reviewers than write a paper that perpetuates some (increasingly frustrating) misunderstandings of modelling and theory.
---->
+Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
 
@@
 The value of $q^{m}_{ij}$ then defines the probability that a focal female mates with the male.
-Mating is realised by placing each $q^{m}_{ij}$ value into a vector whose elements sum to unity.
-A new vector of identical size is then created where each element equals the summation of all earlier position elements in the original vector of $q^{m}_{ij}$ values (such that the first element is zero and last is a number $\leq 1$).
-Because each element in the vector corresponds to a unique male, a random uniform number between zero and one can identify a female's realised mate.
-This realisation is enacted by identifying the element in the vector that is closest to, but not less than, the random uniform number.
 Mating is therefore stochastic, and females do not always mate with the male of the highest $q^{m}_{ij}$.
@@
 In the unlikely event that a female's $N_{males}$ exceeds the total number of available males, then she simply mates with all males.
-
-<!--- We might want to step back a bit on this one and figure out what exactly it is that is confusing and needs clarifying, as I'm not sure I see what the issue is anymore or, rather, why we're going into so much detail about a very routine procedure in an IBM (or any bit of code, really).
-This kind of sampling procedure was used in both of our previous IBM papers and I don't recall it being an issue.
-I have explained the procedure as carefully as I can, but it's getting to the point now where it's essentially turning the specifics of the C programming language into English (i.e., the methods here are now language dependent -- could be done differently in R or Perl or whatever, essentially just to say that we're sampling an element randomly from a weighted vector (I'm still not sure why we can't go back to just saying it that way; actually, I don't see why we can't just stop after ''the value of q^m_ij then defines the probability that a focal female mates with the male'' -- why does this need further explanation in the text?)).
---->
 
@@
 Females produce $n$ offspring, so $q^{f}_{ij}$ values are sampled $n$ times independently and with replacement for each female to determine the realised distribution of sires.
-
-<!--- I've tried another way of explaining that sampling is done from a vector of probabilities in the second to last sentence here --->
 
@@
 We model inbreeding depression as having an absolute rather than relative effect on offspring viability (i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
-We also assume that inbreeding always decreases offspring viability (i.e., $\beta > 0$, no outbreeding depression).
+We assume that inbreeding always decreases offspring viability (i.e., $\beta > 0$, giving inbreeding depression but no outbreeding depression).
 Therefore, because $0 \leq k_{ij} \leq 1$, $-\beta \times k_{ij} \leq 0$.
@@
 We therefore define $\Psi_{\textrm{off}}$ as the probability that an offspring is viable, and sample its realised viability (versus mortality) using a Bernoulli trial.
-
-<!--- See the PDF for the equation. Not sure why it's not showing up in the DOCX. --->
+Our model therefore considers evolution of strategies of inbreeding avoidance caused by inbreeding depression, not evolution of strategies of inbreeding preference, such as might be expected to arise given weak or zero inbreeding depression [@Parker1979; @Kokko2006; @Duthie2016a], or given outbreeding depression [@Bateson1983; @Greeff2009].
 
@@
 
-To address how asymmetric costs associated with pre-copulatory and post-copulatory inbreeding avoidance and polyandry affect the long-term persistence of reproductive strategies, we quantify the change in $M_{a}$ and $F_{a}$ over generations in simulations where the cost of pre-copulatory inbreeding strategy $c_{M}=0$ but the cost of post-copulatory inbreeding strategy $c_{F}=0.02$, and vice versa.
-We compare these simulations with evolution of a costly strategy in the absence of evolution of an alternative strategy (e.g., evolution of pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy phenotype is fixed at zero, $F_{p}=0$).
+To address how asymmetric costs associated with pre-copulatory and post-copulatory inbreeding avoidance and polyandry affect the long-term persistence of reproductive strategies, we quantify the change in $M_{a}$ and $F_{a}$ over generations in simulations where pre-copulatory inbreeding strategy was cost free ($c_{M}=0$) but post-copulatory inbreeding strategy was moderately costly ($c_{F}=0.02$), and vice versa.
+We compare evolutionary trajectories with those of a costly strategy in the absence of evolution of an alternative strategy (e.g., evolution of pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy phenotype is fixed at zero, $F_{p}=0$).
 In Supporting Information, we present results for all possible cost combinations of $0$ and $0.02$.
-Previous modelling using similar genetic architecture suggests that a cost of $0.02$ imposes strong but not overhwleming direct negative selection on polyandry [@Duthie].
+Previous modelling using similar genetic architecture suggests that a cost of $0.02$ imposes strong but not overwhelming direct negative selection on polyandry [@Duthie].
+This value is therefore appropriate to illustrate the different evolutionary consequences that could result from asymmetrical costs.
 
-To address how selection on an initially rare strategy of pre-copulatory or post-copulatory inbreeding avoidance is affected by the other strategy of inbreeding avoidance already being fixed, we first used exploratory simulations to quantify evolution of pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation.
+To address how selection on an initially rare strategy of pre-copulatory or post-copulatory inbreeding avoidance, and resulting evolution, is affected by the other strategy of inbreeding avoidance already being fixed, we first used exploratory simulations to quantify evolution of pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation.
 Then, to test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance were fixed, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., meaning that $F_{p}$ and $P_{p}$ did not evolve).
@@
 Each combination of parameter values simulated was replicated $40$ times, and grand mean values and standard errors of means are calculated in each generation across replicates.
-These analyses allowed us to infer how allele values changed over generations in response to costs, but also in response to the changing values of other alleles and therefore potential evolutionary feedbacks among reproductive strategies (e.g., selection on post-copulatory inbreeding strategy might be weak if polyandry is rare).
+These analyses allowed us to infer how allele values changed over generations in response to costs, but also in response to the changing values of other alleles and therefore potential evolutionary feedbacks among reproductive strategies.
 For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling [@Duthie] showed to be sufficient for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
@@
 When post-copulatory inbreeding avoidance was allowed to evolve, mean $P_{a}$ values became substantially higher than in comparable simulations where $F_{a}$ values were fixed to zero and post-copulatory inbreeding avoidance could not evolve (Figure 1B,D,F,H).
-Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry.
-However, $P_{a}$ values were expected to become positive only given a low cost of polyandry ($c_{P} < 0.005$, Figure 1B,D versus 1F,H).
-This implies that, even given strong inbreeding depression in offspring viability, inbreeding avoidance might generally be a weak force driving polyandry evolution.
-
-<!--- I've not added the suggested ''to the degree that most females mated multiply'' because it's not actually true unless costs are less than or equal to 0.025.
-Also, do we really need to point out figure 2 here?
-The very next paragraph explains that the degree of polyandry isn't trivial, and I should hope that readers aren't so impatient or put off by Figure 1 that they stop reading entirely!
---->
+Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry to the degree that most females mated multiply given low costs of polyandry ($c_{P} < 0.005$; e.g., Figure 2A,B).
+Hence, given a low cost of polyandry, $P_{a}$ allele values increased from zero and persisted at low positive values (Figure 1B,D).
+In contrast, highers cost of polyandry ($c_{P} \geq 0.005$) resulted in initial increases of $P_{a}$ allele values from zero, but then became slightly negative over generations.
+Trajectories of $P_{a}$ values in individual simulations were typically highly stochastic, but also consistent in long-term direction (Supporting Information pp.
+S5-S12).
+Overall, this implies that, even given strong inbreeding depression in offspring viability, inbreeding avoidance might generally be a weak force driving polyandry evolution.
 
 Strong post-copulatory inbreeding avoidance, manifested as very negative $F_{a}$ values, consistently evolved in all simulations where such evolution was allowed (black lines, Figure 1B,D,F,H).
-Evolution of post-copulatory inbreeding avoidance occurred even when $P_{a}$ values were expected to be slightly negative, and hence when there was selection against polyandry, (Figure 1F,H).
-This reflects the threshold nature of phenotypic expression of polygenic polyandry, wherein random sampling of alleles means that polyandry is expressed expressed by some females (i.e., $P_{g}>0$) even when mean $P_{a}$ values are negative (Figure 2C,D).
+Evolution of post-copulatory inbreeding avoidance occurred even when $P_{a}$ values were expected to be slightly negative, and hence when there was selection against polyandry (Figure 1F,H).
+This reflects the threshold nature of phenotypic expression of polygenic polyandry, wherein random sampling of alleles means that polyandry is expressed by some females (i.e., $P_{g}>0$) even when mean $P_{a}$ values are negative (Figure 2).
 This means that, even in populations where female reproductive strategy evolves toward monandry, there is still commonly some opportunity for expression of post-copulatory inbreeding avoidance and associated selection that drives evolution of post-copulatory inbreeding avoidance.
-
-<!--- I'm not sure what aspects of Figure 1 you want me to mention in the main text? Are these things that are also in the legend, and if so, do we really need to repeat them? --->
 
@@
 ----------------------------------------------
+
+<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
 

### 2017-03-18 ms_pre_post.Rmd
Edits up to Discussion

@@
 If a reader is worried about the exact rate of mutation then they probably aren't actually understanding the point of the model.
+
+Honestly, I also think that some of our wording here is a bit insulting to empirical biologists, many of whom are quite capable of reading, understanding, and applying theory.
 
@@
 
-<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
-
 When post-copulatory inbreeding avoidance allele values ($F_{a}$) were fixed to zero, pre-copulatory inbreeding avoidance evolved even when costly (Figure 3A).
@@
 
-<!--- Last time we were through this, it was suggested that I scrap the former term ''inbreeding strategy'' because we don't deal at all with inbreeding preference.
-I have rewritten these sections in attempt to make the writing clearer.
-TODO: Additionally, I have tweaked the figure legends appropriately.
---->
-
 However, when both pre-copulatory and post-copulatory inbreeding avoidance could evolve, their relative evolutionary dynamics depended on their relative costs.
 When pre-copulatory but not post-copulatory inbreeding avoidance was costly ($c_{M}=0.02$ and $c_{F}=0$), pre-copulatory inbreeding avoidance initially evolved (i.e., negative $M_{a}$) but then evolved back towards random mating (i.e., $M_{a}=0$) following increasing evolution of post-copulatory inbreeding avoidance (Figure 3B).
-Similarly, when post-copulatory but not pre-copulatory inbreeding avoidance was costly ($c_{F}=0.02$ and $c_{M}=0$), post-copulatory inbreeding avoidance intially evolved ($F_{a}=0$) before returning to random fertilisation after ca $20000$ generations (Figure 3D).
+Similarly, when post-copulatory but not pre-copulatory inbreeding avoidance was costly ($c_{F}=0.02$ and $c_{M}=0$), post-copulatory inbreeding avoidance initially evolved ($F_{a}=0$) before evolving back to random fertilisation after ca $20000$ generations (Figure 3D).
 
-<!--- Something about this 'evolved' and 'evolved back' language just sounds very amateurish -- can't we reframe this in terms of selection? --->
-
-Evolution of post-copulatory inbreeding avoidance facilitated evolution of polyandry (Figure 3B,C).
-In the absence of post-copulatory inbreeding avoidance, polyandry did not evolve (Figure 3A,D; polyandry was cost free in all these simulations).
+When pre-copulatory inbreeding avoidance was costly, allowing evolution of cost free post-copulatory inbreeding avoidance greatly facilitated evolution of polyandry (Figure 3A versus 3B).
+However when post-copulatory inbreeding avoidance was costly, allowing evolution of cost free pre-copulatory inbreeding avoidance caused $P_{a}$ alleles to decrease to very negative values, reducing expression of polyandry (Figure 3C versus 3D; polyandry was cost free in all these simulations).
 
@@
 
-<!--- Mean pre-cop value is -17.62444  in Figure 1B --->
-<!--- Mean pre-cop value is -15.44786  in Figure 4A --->
-
-<!--- I know I've mentioned this too many times, but I'm really not a fan of this kind of quantitative statistic because it doesn't really mean anything in the context of a model like this.
-At the very least though, I think it's better to put the actual numbers up because ''X% less negative'' just seems very confusing to me.
---->
-
-<!--- I added this last sentence for summary, but stopped it a bit earlier than the suggestion because I'm not sure where you were going with it.
-If we know how selection is changed, isn't this the point?
-Evolution more broadly encompasses mutation and drift, but we've not changed either of these so why do we need to say 'weakens selection' and therefore evolution was affected?
---->
-
 Conversely, when pre-copulatory inbreeding allele ($M_{a}$) values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently become negative over generations (Figure 4C,D).
 Fixation of pre-copulatory inbreeding avoidance therefore prevented evolution of post-copulatory inbreeding avoidance.
-However, in this case, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless whether or not post-copulatory inbreeding strategy was costly (Figure 4C,D).
+However, in this case, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
 Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values among replicates (illustrated by wide standard errors, Figure 4C).
@@
 
-<!--- ==================================================================== --->
-<!--- BEGIN COMMENTS NOT TO BE TRANSFERRED TO THE WORD DOCUMENT FOR COAUTHORS
-<!--- ==================================================================== --->
+<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
 
-<!--- Evolution of reproductive strategies involves multiple potentially interacting and degenerate phenotypes.
-Here we modelled evolution of three reproductive strategies including polyandry, pre-copulatory inbreeding avoidance, and post-copulatory inbreeding avoidance, focusing on three key questions.
-Using individual-based modelling, we found that evolution of post-copulatory inbreeding avoidance facilitated evolution of polyandry, that evolution of a costly inbreeding avoidance strategy was inhibited when the other inbreeding avoidance strategy was cost free, and that evolution of post-copulatory inbreeding avoidance but not pre-copulatory inbreeding avoidance was precluded when the other inbreeding avoidance strategy was fixed for strong inbreeding avoidance.
-We thereby conclude that evolution of inbreeding avoidance strategies and associated polyandry are likely to interact in predictable ways, potentially generating new hypotheses concerning evolution of reproductive strategies within and across taxa.
---->
-
-<!---  I think these changes have been good ones, and hence that we’re heading along decent lines with the Discussion.
-However I think it could to with a moderately hefty edit to 1) tidy up some overarching points about what we did near the start, 2) perhaps clarify the structure of the Discussion in relation to the three questions that are now very clearly stated at the end of the Intro, and 3) tighten up the writing a bit (I can tell that the Discussion is a few iterations behind the rest of the manuscript in terms of tight and precise writing, but that’s easily fixed once we get the structure sorted).
---->
-
-<!--- Unusually for me (and sorry if this opening was my suggestion from an earlier draft!), I’m wondering whether it’s a good idea to start this broad, or whether we’d be better to keep a bit more focused to start with, and then bring in the generality after that?
-I’ll make some suggestions, see what you think.
-Writing is NOT intended to be a definitive version, just me getting some ideas down!
---->
-
-<!--- I do think we need to get this into the start of the Discussion.
-It’s because our current analyses don’t play around with the magnitude of ID, it’s a fixed parameter = strong.
-Think we need to make sure that’s clear in peoples’ minds, otherwise we’ll get people asking about IP etc...
-Hence my suggestion to nail it at the start – which then mirrors the start of the Intro.
---->
-
-<!--- Too much/too vague no doubt – but this is a hanger to link back to the bit you flagged up as a worry in the Intro, about whether someone would query why we need ‘dynamic models’ – so here we could flag up the dynamicism again somehow?
---->
-
-<!--- To me, this sentence isn’t very helpful, doesn’t say what the questions are or what we concluded, or even how we tackled them, so it seems pretty redundant.
-Can we weave into next section along lines suggested?
---->
-
-<!--- SUGGESTED CHANGE: Strong inbreeding depression in offspring fitness is widely hypothesised to drive evolution of both pre-copulatory and post-copulatory inbreeding avoidance, and hence drive evolution of polyandry [@Zeh1997; @Jennions2000; @Tregenza2002].
-However, evolution of such degenerate (i.e.
-functionally overlapping) mechanisms of inbreeding avoidance cannot be presumed to occur independently, meaning that emerging reproductive strategies are likely to be shaped by relative costs, and might exhibit complex dynamic evolutionary feedbacks across multiple generations.
---->
-
-<!--- I was wondering about reiterating a clearer KG here, but actually I think it’s fine without – see comment attached to end of this suggested paragraph. --->
-
-<!--- One of my main comments about the Discussion at the moment is that the really clear structure of the 3 questions that’s now set up at the end of the Intro and followed through the Methods and Results has completely disappeared here.
-Can we get it back again, a bit?
-Restating the questions here might be overkill, but yet I’m thinking that a short summary version might be helpful – something like this?
---->
-
-<!--- I didn’t get much from this here, and anyway you pretty much repeat the exact same thing in the ‘conclusions’ section at the end?
-So, if we have to have a conclusions section (for JEB?), then I think it’s best there?
---->
-
-<!--- This sentence might need tweaking a bit, but I think something like it would be a good strong end to this first para? --->
-
-<!--- So this is where I start to find the structure of the Discussion a bit hard to follow – seem to be addressing the three questions in reverse order.
-This first bit (and the link to fig 4), is really addressing question 3, isn’t it?
-And then we go on to Q2 (fig 3) and then finally Q1 (fig 1).
-This is pretty confusing.
-Would it be possible to turn this section around so that the three questions are dealt with in the ‘right’ order?
-I haven’t tried to implement.
-Or if you want to keep it like this we might need to clarify that structure and (implicitly or explicitly) note why things are reversed?
---->
-
-<!--- ==================================================================== --->
-<!--- END COMMENTS NOT TO BE TRANSFERRED TO THE WORD DOCUMENT FOR COAUTHORS
-<!--- ==================================================================== --->
-
-Evolution of reproductive strategies cannot be presumed to occur in isolation in wild populations, and is instead likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundance) among phenotypes under selection.
+Evolution of reproductive strategies cannot be presumed to occur in isolation from each other in real-world populations, and is instead likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundance) among phenotypes under selection.
 For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently feed back to drive selection for polyandry [e.g., @Zeh1997; @Jennions2000; @Tregenza2002].
@@
 We thereby highlight fundamental but theoretically under-developed relationships between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding avoidance.
-
-<!--- I have tried to re-work this first paragraph, but I had a very hard time following the logical flow of ideas given the suggested changes.
-I understand that you want to get all of the components of this manuscript into the front of the Discussion, but I think they need to fit together much more coherently.
-I didn't quite understand the motivation behind the suggested changes.
-For example, the proposed first sentence of the Discussion shifted from talking generally about all of our results to only referring to one of our questions.
-I didn't understand the proposed second sentence at all, which suggested that evolution of degenerate traits can't be assumed to occur independently?
-(But this is trivially true -- almost by definition!
-And it inverts the key logic -- the point is that traits don't have independent effects *potentially leading to degeneracy*).
-The next part of the proposed second sentence suggested that it necessarily follows from degeneracy that relative costs will shape reproductive interactions, but why does this have to be the case?
-There needs to be some logical connection between these two claims that just isn't there.
-I couldn't really figure out how to re-work it because I was really unclear as to what the logical progression of ideas was.
-Can you clarify what you mean by this?
---->
-
-<!--- Is this really correct?
-Degeneracy is defined by different processes having the same effect, so I don't think pre- and post-copulatory inbreeding avoidance are *affected by* degeneracy so much as *characterised by*, or *an example of* degeneracy.
---->
-
-<!--- I think the logic of the first sentence is important here, though it might need some tweaks.
-The point is that phenotypes don't occur in isolation -> multiple phenotypes interact -> two types of interaction are feedbacks and degeneracy.
-Hence, degeneracy is one *type* of way that phenotypes might interact, so I think that the sentence structure needs to reflect this so readers don't get confused (i.e., we can't just skip to 'such degenerate' because it doesn't clearly follow from the previous sentence.
---->
-
-<!--- I don't think just mentioning 'dynamic models' is enough to make a convincing argument that they were necessary to address the knowledge gap.
-If we really wanted to flesh out the idea, we would have to explain *why* we couldn't get the answer we did with non-dynamic models.
-This isn't obvious or trivial!
---->
 

### 2017-03-18 ms_pre_post.Rmd
Final edits through the Discussion

@@
 author: ''
-date: "December 15, 2016"
+date: "19 March 2017"
 output:
@@
 
-If we're interested in evolution and not selection (hence the phrasing), then we really need to put more energy into looking at the assumptions underlying genetic variance, and other things having to do with quantitative genetics.
+If we're interested in evolution and not selection (hence the phrasing), and not wanting to assume that the latter strictly implies the former (as of course is sometimes the case in nature), then we really need to put more energy into looking at the assumptions underlying genetic variance, and other things having to do with quantitative genetics.
 At the moment, we're just assuming that there is pretty much always enough genetic variance on which selection to act.
 I've assumed we'd be most interested in selection given three reproductive strategy traits, but if we're interested in evolvability of traits, then I think we're ignoring some key things.
+Hence my previous concerns about the theoretical question really not being entirely clear here.
 
@@
 
-<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->
-
 Evolution of reproductive strategies cannot be presumed to occur in isolation from each other in real-world populations, and is instead likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundance) among phenotypes under selection.
-For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently feed back to drive selection for polyandry [e.g., @Zeh1997; @Jennions2000; @Tregenza2002].
+For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently drive selection for polyandry [e.g., @Zeh1997; @Jennions2000; @Tregenza2002].
 Evolution of inbreeding avoidance can be driven by selection on both pre-copulatory and post-copulatory mechanisms, so simultaneous evolution of each phenotype is likely to be defined by degeneracy, in addition to any direct costs on phenotypes.
@@
 
-<!--- I have re-ordered the Discussion to reflect the order of the questions, but this sacrifices something by putting the specifics points ahead of more general questions (i.e., those references to Figure 4 were not related to any of the three questions specifically, but were used to help make a more general point derived from a holistic understanding of the model).
-Hence, I have created a new section for more general points concerning reproductive strategy, also removing the conclusion.
---->
-
 The opportunity to adjust inbreeding has been widely considered as a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
-We found that when post-copulatory inbreeding avoidance could evolve, selection for polyandry was greatly strengthened (Figure 1).
-The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but our model provides support for this verbal hypothesis and therefore has widespread implications for future studies of evolution of polyandry.
-
-<!--- Something doesn't seem quite right here.
-Our model doesn't provide support for the verbal hypothesis in the same way that real data would.
-Perhaps it *clarifies* the verbal hypothesis, *formalises?* --->
+We found that when post-copulatory inbreeding avoidance could evolve, selection for and resulting evolution of polyandry was greatly strengthened (Figure 1).
+The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but our model clarifies this verbal hypothesis and therefore has widespread implications for future studies of evolution of polyandry.
 
@@
 Evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but was affected by the joint evolution of polyandry and the existence of asymmetric costs.
-One cost free inbreeding strategy precluded another more costly inbreeding strategy from persisting in a focal population by modifying its effect on inbreeding avodance (Figure 3).
+One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population by modifying its effect on inbreeding avoidance (Figure 3).
 Consequently, long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given sufficient cost asymmetry.
 Direct costs therefore strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies.
-Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging [@Pomiankowski1987; @Kokko2003; @Reid2015].
-@Pomiankowski1987 categorised four types of costs that are relevant to mate choice, which we suggest are also relevant costs for polyandry, and include costs of elevated risks associated with (1) predation or (2) disease transmission, and costs incurred through (3) loss of time or (4) depletion of energy.
+Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging [@Pomiankowski1987; @Kokko2003].
+@Pomiankowski1987 categorised four types of costs that are relevant to mate choice, which are also relevant for polyandry, and include costs of elevated risks of predation or disease transmission, and costs incurred through time or energy expenditure.
 Another type of cost relevant for polyandry and inbreeding strategy is risk of male harm caused by sexual conflict [e.g., @Arnqvist2005a; @Parker2006].
@@
 Evolution of individual phenotypes therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.
-
-<!--- I don't understand the contrast between the two comments, the first of which suggests that the empirical examples of costs cited are not needed here, and the second of which suggests that we need to be more explicit about why we did things the way we did.
-Hence, I have revised to clarify that we made the modelling choices that we did with respect to costs *because they are observed in empirical systems*.
-Of course, the costs that we modelled are not the *only* kinds of 'costs' that are observed in empirical systems (hence the Roberts reference), so other models might want to look into different types of costs.
-I agree that it would not be at all surprising if a reviewer raised a question about how we modelled the costs (or anything else), but this always seems to be true for modelling and I think it kind of misses the big picture about how models like this try to develop theory.
-We can't model *every* kind of cost that we can possibly think of (nor would we want to), and we're not modelling a specific system where we might be able to justify some costs being more reasonable than others.
-We also can't (I don't think) logically show with an IBM that the type of cost will be arbitray with respect to the questions of interest (i.e., any cost will do).
-In the end, we have to make reasonable decisions about how to model costs and work from there.
-I think that citing empirical studies shows that our assumptions of cost type are reasonable for some systems (though potentially not others).
-Had we made different assumptions, I suspect we'd get queries from some readers wondering why we didn't do it a different way.
-I don't mean to keep belabouring this point, but I think that the point of using a model to develop theory isn't to match your assumptions with empirical reality as closely as possible (if we tried, we'd miss a lot of important stuff!).
-Assumptions need to be clear and useful for addressing the theoretical question(s) of interest -- in other words, the model needs to change *how* people think, not *what* they think.
-When I review theory papers, this is the criteria I have in mind, not (necessarily) whether or not the assumptions match how things are in nature (they might deliberately not be, for the better!).
-The only reason I have repeatedly justified the cost assumption is, really, for fear that readers might not entirely understand the nature of model assumptions in theory, not because I think the specifics of the assumptions that we make actually matter in terms of thinking about the three aspects of reproductive strategy we consider.
---->
-
-<!---If we're spending this much time justifying an assumption, then we should be able to explain *why* it's an important assumption *with respect to addressing our questions* (there are hundreds of other assumptions we don't spend time on -- number of loci probably isn't going to affect our take-home message).
-If we can't, and the answer is that 'we don't know if it's important or not', then we're probably not doing theory very well.
-Actually, I don't think the nature of the costs is going to be important because it's not going to affect any key hypotheses that might be derived from our model -- the effect of a direct negative cost has a very clear interpretatation; changing how a cost is paid might quantitatively affect the end *net* cost as a counter-balance to selection, but so will changing the exact values of the costs we do use.
-There's no good reason to believe that the way a cost is paid will affect any of the major conclusions (degeneracy is important, polyandry is more likely to evolve given post-copulatory selection, etc.) except by tweaking the overall net cost countering adaptive benefit of inbreeding avoidance (alternatively, if we *can* think of one, it would be a great opportunity for another theory paper!).
---->
 
@@
 
-General predictions concering inbreeding avoidance and polyandry
+General predictions concerning inbreeding avoidance and polyandry
 -------------------------------------------------------------------
 
-Post-copulatory inbreeding avoidance is useless for females that are not polyandrous, and most effective for highly polyandrous females that can choose amongst multiple mates to ensure that offspring are fertilised favourably.
-In contrast, pre-copulatory mechanisms are most salient for females that mate only once and therefore have no post-copulatory opportunity to avoiding inbreeding.
-This theory is borne out in our simulation results, as selection for post-copulatory inbreeding avoidance was negligible in populations where polyandry did not evolve, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D).
-Selection for pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information p.
+Post-copulatory inbreeding avoidance cannot be realised if females are not polyandrous, and is most effective for highly polyandrous females that can choose amongst multiple mates and therefore bias fertilisation accordingly.
+In contrast, pre-copulatory inbreeding avoidance mechanisms are most critical for females that mate only once and therefore have no post-copulatory opportunity to avoiding inbreeding.
+This theory is borne out in our simulation results, as selection for, and consequent evolution of, post-copulatory inbreeding avoidance was negligible in populations where polyandry did not evolve, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D).
+Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information p.
 S1-1).
-In addition to polyandry increasing selection for post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).
+In addition to polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).
 It would therefore be interesting to test the hypothesis that, across taxa, occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with degree of polyandry.
 To test this hypothesis, more work is needed to identify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
-
-<!---  Diluting the idea of degeneracy throughout the manuscript now makes me worry that some readers will miss it entirely.
-If they're not reading carefully, they'll miss (or simply forget) the buried definition in the fourth paragraph of the Introduction.
-Because the concept of degeneracy becomes so important later on, they'll need to back track to remember what it actually means.
-I'm less a fan of 'flagging' things for this reason -- readers don't really *need* to understand degeneracy completely until now, but here they have to go all the way back to the Introduction to get the full scope of its importance.
---->
-
-<!--- By removing the sentence specifying how degeneracy works with respect to inbreeding avoidance, we are asking the readers to recall these specifics from the introduction (or go back and find them again).
-The exact mechanism by which functional overlap occurs is removed from the more vague 'phenotypic reproductive strategies'.
-I'm afraid this will lose some readers who might be a bit tired by the end of the Discussion.--->
 
@@
 The relevance of degeneracy with respect to such reproductive strategies therefore requires further theoretical development, which could result in new empirical predictions and conceptual synthesis across biological scales.
-
-<!--- I don't understand the comment about 'getting at the genetic scales'.  --->
 

### 2017-03-18 ms_pre_post.Rmd
Small change to generalise

@@
 In contrast, highers cost of polyandry ($c_{P} \geq 0.005$) resulted in initial increases of $P_{a}$ allele values from zero, but then became slightly negative over generations.
-Trajectories of $P_{a}$ values in individual simulations were typically highly stochastic, but also consistent in long-term direction (Supporting Information pp.
+Trajectories of allele values in individual simulations were typically highly stochastic, but also consistent in long-term direction (Supporting Information pp.
 S5-S12).

### 2017-03-19 ms_pre_post.Rmd
Add final copies with Bateson reference read in accurately
Minor changes -- obvious tweaks

@@
 ---
-title: Evolution of pre-copulatory and post-copulatory strategies of inbreeding avoidance and associated polyandry
+title: Evolution of pre-copulatory and post-copulatory strategies of inbreeding avoidance
+  and associated polyandry
 author: ''
@@
 However, surprisingly little theory or modelling critically examines selection for pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, given evolutionary constraints and direct costs, or examines how evolution of inbreeding avoidance strategies might feed back to affect evolution of polyandry.
-Selection for post-copulatory inbreeding avoidance but not for pre-copulatory inbreeding avoidance, requires polyandry, while interactions between pre-copulatory and post-copulatory inbreeding avoidance might cause functional redundancy (i.e., 'degeneracy') potentially generating complex evolutionary dynamics among inbreeding strategies and polyandry.
+Selection for post-copulatory inbreeding avoidance, but not for pre-copulatory inbreeding avoidance, requires polyandry, while interactions between pre-copulatory and post-copulatory inbreeding avoidance might cause functional redundancy (i.e., 'degeneracy') potentially generating complex evolutionary dynamics among inbreeding strategies and polyandry.
 We use individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression and different evolutionary constraints and direct costs.
@@
 
-When post-copulatory inbreeding avoidance alleles ($F_{a}$) were fixed to zero, meaning that $F_{p}$ could not evolve, $P_{a}$ alleles underlying polyandry always decreased to negative values over generations (red lines, Figure 1A,C,E,G).
+When post-copulatory inbreeding avoidance alleles ($F_{a}$) had no effect (i.e., $F_{g}$ genotypes were fixed to zero), meaning that $F_{p}$ could not evolve, $P_{a}$ alleles underlying polyandry always decreased to negative values over generations (red lines, Figure 1A,C,E,G).
 This shows that despite strong inbreeding depression in offspring viability, there is selection against unconditional polyandry even given zero direct cost ($c_{P}=0$; Figure 1A).

### 2017-03-19 ms_pre_post.Rmd
More minor changes before sending

@@
 Honestly, I also think that some of our wording here is a bit insulting to empirical biologists, many of whom are quite capable of reading, understanding, and applying theory.
+
+The empirical examples almost make this worse.
+It seems like part of our point in the discussion is that indirection selection on polyandry via post-copulatory inbreeding avoidance is possible, but then we already knew that as a result of the empirical examples.
+Why did we need this model?
+We need to explain what it is that the model adds in terms of interpretation and theoretical understanding.
+Just recreating something already observed in empirical studies isn't particularly helpful.
 
@@
 Hence, given a low cost of polyandry, $P_{a}$ allele values increased from zero and persisted at low positive values (Figure 1B,D).
-In contrast, highers cost of polyandry ($c_{P} \geq 0.005$) resulted in initial increases of $P_{a}$ allele values from zero, but then became slightly negative over generations.
+In contrast, higher costs of polyandry ($c_{P} \geq 0.005$) resulted in initial increases of $P_{a}$ allele values from zero, but then became slightly negative over generations.
 Trajectories of allele values in individual simulations were typically highly stochastic, but also consistent in long-term direction (Supporting Information pp.

### 2017-03-23 ms_pre_post.Rmd
New edits up through Methods

@@
 Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple interacting reproductive strategies [@Parker1979; @Parker2006; @Pusey1996; @Szulkin2012].
+
 From the perspective of a focal breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
@@
 
-Despite the paucity of theory and resulting predictions, numerous empirical studies on diverse species have tested for, and in some cases found evidence of, female inbreeding avoidance in systems where polyandry also occurs [@Arct2015; but see @Reid2015a].
+Despite the paucity of theory and resulting predictions, numerous empirical studies on diverse species have tested for, and in some cases found evidence of, female inbreeding avoidance in systems where polyandry also occurs [@Tregenza2002; @Varian-Ramos2012; @Kingma20134; @Arct2015; but see @Reid2015a].
 However, relatively few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
@@
 To develop theory on evolution of polyandry given inbreeding depression, @Duthie used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance.
-Selection for polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., 'costs') on polyandry were small, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
+Net selection for polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., 'costs') on polyandry was weak, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
 Without these conditions, increasing polyandry tended to increase rather than decrease the overall degree of inbreeding that females experienced, and hence reduce offspring fitness.
@@
 
-We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance, by tracking the dynamics of alleles underlying reproductive strategies enacted by interacting females and males within a small focal population.
-We thereby tracked evolutionary dynamics given internally-consistent patterns of relatedness caused by non-random mating while also allowing mutation, gene flow, drift, and selection to potentially affect evolution.
-Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of the three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$, i.e., 'fertilisation' alleles).
+We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply 'inbreeding strategies' because of the possibility for inbreeding preference to evolve in the model), by tracking the dynamics of alleles underlying reproductive strategies enacted by interacting females and males within a small focal population.
+We thereby track evolutionary dynamics given internally consistent patterns of relatedness caused by non-random mating and allowing for effects of mutation, gene flow, drift, and selection.
+Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of the three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$), pre-copulatory inbreeding strategy ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., 'fertilisation' alleles).
 All alleles can take any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014] and combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for each of the three traits whereby an individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
-In overview, each generation proceeds with females paying costs, expressing polyandry, mating, and fertilisation.
+In overview, each generation proceeds with females paying costs and expressing polyandry, mating, and fertilisation.
 Offspring inherit a randomly sampled allele from each parent at each locus with no physical linkage.
@@
 Immigrants arrive in the population and density regulation limits population growth.
-We record the population pedigree and directly calculate the coefficient of kinship ($k$) between all potential mates in each generation (defined as the probability that two homologous alleles will be identical-by-descent), allowing individual strategies of pre-copulatory and post-copulatory inbreeding avoidance to be enacted.
+We record the population pedigree and directly calculate the coefficient of kinship ($k$) between all potential mates in each generation (defined as the probability that two homologous alleles will be identical-by-descent), allowing individual pre-copulatory and post-copulatory inbreeding strategies to be enacted.
 Key individual traits, parameter values, and variables are described in Table 1.
@@
 
-Phenotypic values for tendency for polyandry ($P_{p}$), pre-copulatory inbreeding avoidance strategy ($M_{p}$), and post-copulatory inbreeding avoidance strategy ($F_{p}$) each have costs that are assumed to independently increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
-The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding avoidance strategy ($c_{M}$), and post-copulatory inbreeding avoidance strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
+Phenotypic values for tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$) each have costs that are assumed to independently increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
+The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
 Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
-Absolute values are used for applying costs to inbreeding avoidance strategies (hereafter simply 'inbreeding strategies') because both negative and positive $M_{p}$ and $F_{p}$ values affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively.
-In contrast, only positive values of $P_{p}$ cause females to be polyandrous (see below).
+Absolute values are used for applying costs to inbreeding avoidance strategies because both negative and positive $M_{p}$ and $F_{p}$ values could potentially arise and affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively (see details of mating and fertilisation strategies below).
+In contrast, only positive values of $P_{p}$ cause females to be polyandrous (see details of polyandry below).
 Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
@@
 
-After costs are paid, each remaining female chooses $N_{males}$ males to mate with, where $N_{males}$ is calculated by sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
+After costs are realised, each remaining female chooses $N_{males}$ males to mate with, where $N_{males}$ is calculated by sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
 This ensures that all surviving females choose at least one mate, and causes some stochastic variation around the expected mean $N_{males}$ of $P_{p}+1$.
@@
 These $q^{f}_{ij}$ values, which lie between zero and one, define the probability of paternity.
-As with mate choice, one vector element representing a single male is sampled as weighted by these probabilities to determine paternity.
 Females produce $n$ offspring, so $q^{f}_{ij}$ values are sampled $n$ times independently and with replacement for each female to determine the realised distribution of sires.
@@
 We therefore define $\Psi_{\textrm{off}}$ as the probability that an offspring is viable, and sample its realised viability (versus mortality) using a Bernoulli trial.
-Our model therefore considers evolution of strategies of inbreeding avoidance caused by inbreeding depression, not evolution of strategies of inbreeding preference, such as might be expected to arise given weak or zero inbreeding depression [@Parker1979; @Kokko2006; @Duthie2016a], or given outbreeding depression [@Bateson1983; @Greeff2009].
+We simulate evolution under conditions where inbreeding avoidance is adaptive due to strong inbreeding depression, and not evolution where inbreeding preference is adaptive due to weak or zero inbreeding depression [@Parker1979; @Kokko2006; @Duthie2016a], or given outbreeding depression [@Bateson1983; @Greeff2009].
+However, as described above, positive $M_{p}$ and $F_{p}$ values resulting in inbreeding preference are permitted to evolve, and could potentially arise due to mutation or drift.
 
@@
 
-Simulation and analysis
+Simulations and analysis
 ----------------------------------------------
@@
 We compare evolutionary trajectories with those of a costly strategy in the absence of evolution of an alternative strategy (e.g., evolution of pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy phenotype is fixed at zero, $F_{p}=0$).
-In Supporting Information, we present results for all possible cost combinations of $0$ and $0.02$.
 Previous modelling using similar genetic architecture suggests that a cost of $0.02$ imposes strong but not overwhelming direct negative selection on polyandry [@Duthie].
@@
 For all replicates, we set $\rho=5$ immigrants, which produced a range of kin and non-kin in each generation allowing females to express inbreeding strategies, and $n=8$ offspring, which was sufficient to keep populations consistently at carrying capacities and avoid population extinction.
-Values of $K_{f}$ and $K_{m}$ were both set to 100 because previous modelling showed that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but not so small that selection is typically overwhelmed by genetic drift [@Duthie2016a].
+Values of $K_{f}$ and $K_{m}$ were both set to 100 because previous modelling showed that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but not so small that selection is typically overwhelmed by drift [@Duthie2016a].
 

### 2017-03-23 ms_pre_post.Rmd
Remaining edits to manuscript

@@
 author: ''
-date: "19 March 2017"
+date: "23 March 2017"
 output:
@@
 
-In all simulations, we recorded mean values of $P_{a}$, $M_{a}$, and $F_{a}$ in each generation, and we present these values over generations to infer selection on phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$).
+In all simulations, we recorded mean values of $P_{a}$, $M_{a}$, and $F_{a}$ in each generation and present these values over generations to infer selection on phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$).
 Each combination of parameter values simulated was replicated $40$ times, and grand mean values and standard errors of means are calculated in each generation across replicates.
@@
 Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry to the degree that most females mated multiply given low costs of polyandry ($c_{P} < 0.005$; e.g., Figure 2A,B).
-Hence, given a low cost of polyandry, $P_{a}$ allele values increased from zero and persisted at low positive values (Figure 1B,D).
-In contrast, higher costs of polyandry ($c_{P} \geq 0.005$) resulted in initial increases of $P_{a}$ allele values from zero, but then became slightly negative over generations.
-Trajectories of allele values in individual simulations were typically highly stochastic, but also consistent in long-term direction (Supporting Information pp.
+Here, $P_{a}$ allele values increased from zero and persisted at low positive values (Figure 1B,D).
+Given higher costs of polyandry ($c_{P} \geq 0.005$), $P_{a}$ allele values still initially increased from zero, but then became slightly negative over generations (Figure 1F,H).
+Trajectories of allele values in individual simulations were typically highly stochastic, but were consistent in their long-term direction (Supporting Information pp.
 S5-S12).
@@
 However when post-copulatory inbreeding avoidance was costly, allowing evolution of cost free pre-copulatory inbreeding avoidance caused $P_{a}$ alleles to decrease to very negative values, reducing expression of polyandry (Figure 3C versus 3D; polyandry was cost free in all these simulations).
+Results for all possible cost combinations of $0$ and $0.02$ are provided in Supporting Information (pp.
+S5-S12).
 
@@
 This lack of selection for post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
-When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information).
+When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information p.
+S4).
 
@@
 
-Evolution of reproductive strategies cannot be presumed to occur in isolation from each other in real-world populations, and is instead likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundance) among phenotypes under selection.
+Evolution of different reproductive strategies cannot be presumed to occur in isolation from each other in real-world populations.
+Rather, such evolution is likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundance) among phenotypes under selection.
 For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently drive selection for polyandry [e.g., @Zeh1997; @Jennions2000; @Tregenza2002].
@@
 
-The opportunity to adjust inbreeding has been widely considered as a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
+The opportunity to adjust inbreeding has been widely suggested to be a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
 We found that when post-copulatory inbreeding avoidance could evolve, selection for and resulting evolution of polyandry was greatly strengthened (Figure 1).
@@
 
-We predict evolution of polyandry in populations where inbreeding depression is severe and inbreeding avoidance through post-copulatory mechanisms can also evolve.
+We predict evolution of polyandry in populations where inbreeding depression is severe and inbreeding avoidance through post-copulatory mechanisms can also evolve, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
 Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa [e.g., @Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015].
@@
 In black field crickets (*Teleogryllus commodus*), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs [@Bussiere2006; @Tuni2013].
-Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for further polyandry, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
 
@@
 Consequently, long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given sufficient cost asymmetry.
-Direct costs therefore strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies.
+Since direct costs strongly affected the evolution of the focal phenotype(s), quantifying costs is necessary for predicting evolution of inbreeding strategies.
 Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging [@Pomiankowski1987; @Kokko2003].
@@
 When framing hypotheses for existence of post-copulatory inbreeding avoidance and polyandry, it might therefore be necessary to consider whether or not inbreeding avoidance already occurs through pre-copulatory mate choice.
-Additionally, the opportunity for post-copulatory inbreeding avoidance will also naturally depend on the degree to which females are polyandrous.
-For species in which pre-copulatory inbreeding avoidance occurs and polyandry is uncommon [@Lihoreau2007; @Metzger2010; @Metzger2010a], evolution of post-copulatory inbreeding avoidance is highly unlikely.
+Additionally, the opportunity for post-copulatory inbreeding avoidance will also depend on the degree to which females are polyandrous.
+For species in which pre-copulatory inbreeding avoidance occurs and polyandry is uncommon [@Lihoreau2007; @Metzger2010; @Metzger2010a], evolution of post-copulatory inbreeding avoidance is highly unlikely even if such a strategy incurs little direct cost.
 
@@
 
+<!--- TEMPORARILY REMOVED FOR DOUBLE-BLIND PEER REVIEW
+
 Acknowledgements
@@
 
-This work was funded by a European Research Council Starting Grant to JMR.
+This work was funded by a European Research Council Starting Grant to JMR. Computer simulations were performed using the Maxwell Computing Cluster at the University of Aberdeen.
+
+--->
 
@@
 
-![Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fixed to zero (i.e., random fertilisation) or (B, D, F, H) allowed to evolve freely.
+![Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fixed to zero (i.e., random fertilisation) or (B, D, F, and H) allowed to evolve freely.
 Costs of polyandry (c_p) increase across rows from zero (A and B) to 0.01 (G and H).
@@
 
-![Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding avoidance ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (A) fixed for random mating or (B) can also evolve.
+![Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding avoidance ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve.
 Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
-Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
+Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.
 In all panels, polyandry is cost free.](figures/rel_costs.png)
@@
 Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.](figures/fixed_adapt.png)
+Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.](figures/fixed_adapt.png)
 

### 2017-03-23 Supplement.tex
Update Supporting Information

@@
 
-\renewcommand{\thesection}{S1.\arabic{section}}
+\renewcommand{\thesection}{S.\arabic{section}}
 \renewcommand{\thesubsection}{\thesection.\arabic{subsection}}
-\renewcommand{\thepage}{S1-\arabic{page}}
+\renewcommand{\thepage}{S\arabic{page}}
 
 \makeatletter %% With ams
-\def\tagform@#1{\maketag@@@{(S1-\ignorespaces#1\unskip\@@italiccorr)}}
+\def\tagform@#1{\maketag@@@{(S\ignorespaces#1\unskip\@@italiccorr)}}
 \makeatother
@@
 \makeatletter \renewcommand{\fnum@figure}
-{\figurename~S1-\thefigure}
+{\figurename~S\thefigure}
 \makeatother
@@
 
-\title{Evolution of pre-copulatory and post-copulatory inbreeding behaviour \\ \vspace{10 mm} {\sffamily\Large\bfseries Supplemental results showing change in allele values over different parameter combinations, and allele values over generations for single replicates}}
+\title{Evolution of pre-copulatory and post-copulatory strategies of inbreeding avoidance
+  and associated polyandry \\ \vspace{10 mm} {\sffamily\Large\bfseries Supplemental results showing change in allele values over different parameter combinations, and allele values over generations for single replicates}}
 
-\author{\\ \textbf{A.
+%\author{\\ \textbf{A.
 Bradley Duthie\textsuperscript{1,2} and Jane M.
@@
 \pagestyle{fancy}
-\lhead{DUTHIE ET AL}
+%\lhead{DUTHIE ET AL}
 \rhead{PRE- \& POST-COPULATORY (SUPPLEMENT)}
@@
 \noindent \textbf{Here we present supplemental results from an individual-based model in which alleles underlying polyandry (\bm{$P_{a}$}), pre-copulatory inbreeding strategy (\bm{$M_{a}$}) and post-copulatory inbreeding strategy (\bm{$F_{a}$}) affect evolving phenotypic values for each trait over 40000 generations.
-The first figure in this supplement shows how \bm{$F_{a}$} alleles change over generations given that \bm{$M_{a}$} alleles are fixed for strong inbreeding avoidance and \bm{$P_{a}$} alleles are fixed for polyandry.
-Remaining figures show all cost combinations of \bm{$0$} and \bm{$0.02$} for polyandry (\bm{$c_{P}$}), pre-copulatory inbreeding strategy (\bm{$c_{M}$}), and post-copulatory inbreeding strategy (\bm{$c_{F}$}), including a summary among \bm{$40$} replicates and dynamics of individual replicates.
-Figures also show correlations of mean allele values among replicates.}
+The first figure in this supplement summarises trajectories of allele values across replicate simulations for all cost combinations of \bm{$0$} and \bm{$0.02$} for polyandry (\bm{$c_{P}$}), pre-copulatory inbreeding strategy (\bm{$c_{M}$}), and post-copulatory inbreeding strategy (\bm{$c_{F}$}).
+The second figure shows how \bm{$F_{a}$} alleles change over generations given that \bm{$M_{a}$} alleles are fixed for strong inbreeding avoidance and \bm{$P_{a}$} alleles are fixed for polyandry.
+Remaining figures show the dynamics of individual replicate simulations for all trait cost combinations of \bm{$0$} and \bm{$0.02$}; these figures also show correlations of mean allele values among replicates.}
 
@@
 \begin{center}				
-\includegraphics[scale=0.82]{figures/evo_combs.pdf}
+\includegraphics[scale=0.82]{figures/evo_combs.png}
 \end{center}
-\caption{Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+\caption{Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (blue lines and shading), and post-copulatory inbreeding strategy (black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
 Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard deviations of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.
-Panels A-H show simulations for different combinations of costs for tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy.
+Negative mean allele values indicate inbreeding avoidance or tendency for monandry, and positive values indicate inbreeding preference or tendency for polyandry.
+Panels A-H show simulations for different combinations of costs for tendency for polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$).
 Dotted horizontal black lines in panels show values of zero on the y-axis.
-Individual replicates for all cost combinations are shown in Figures S\ref{SI_M00_P00_E00}-S\ref{SI_M02_P02_E02}.
-Dotted horizontal lines show where the y-axis equals zero.}
+Individual replicates for all cost combinations are shown in Figures S\ref{SI_M00_P00_E00}-S\ref{SI_M02_P02_E02}.}
 \label{allcombs}
@@
 \begin{center}				
-\includegraphics[scale=0.8]{figures/extra_MfPf.pdf}
+\includegraphics[scale=0.8]{figures/extra_MfPf.png}
 \end{center}
@@
 Solid black lines represent grand means over 40 replicate populations, and grey shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values reflect strategies of inbreeding avoidance, and positive values reflect strategies of inbreeding preference.
-Red and blue horizontal lines reflect fixed polyandry allele values of $P_{a}=1$ and fixed pre-copulatory inbreeding strategy allele values of $M_{a}=-10$, respectively.
+Negative mean allele values indicate strategies of inbreeding avoidance, and positive values indicate strategies of inbreeding preference.
+Red and blue horizontal lines indicate fixed polyandry allele values of $P_{a}=1$ and fixed pre-copulatory inbreeding strategy allele values of $M_{a}=-10$, respectively.
 Panels (A) and (B) show simulations given not costly and costly post-copulatory inbreeding strategy, respectively.
@@
 \begin{center}				
-\includegraphics[scale=0.8]{figures/SI_M00_P00_E00.pdf}
+\includegraphics[scale=0.8]{figures/SI_M00_P00_E00.png}
 \end{center}
@@
 \begin{center}				
-\includegraphics[scale=0.8]{figures/SI_M02_P00_E00.pdf}
+\includegraphics[scale=0.8]{figures/SI_M02_P00_E00.png}
 \end{center}
@@
 \begin{center}				
-\includegraphics[scale=0.8]{figures/SI_M00_P02_E00.pdf}
+\includegraphics[scale=0.8]{figures/SI_M00_P02_E00.png}
 \end{center}
@@
 \begin{center}				
-\includegraphics[scale=0.8]{figures/SI_M00_P00_E02.pdf}
+\includegraphics[scale=0.8]{figures/SI_M00_P00_E02.png}
 \end{center}
@@
 \begin{center}				
-\includegraphics[scale=0.8]{figures/SI_M02_P02_E00.pdf}
+\includegraphics[scale=0.8]{figures/SI_M02_P02_E00.png}
 \end{center}
@@
 \begin{center}				
-\includegraphics[scale=0.8]{figures/SI_M02_P00_E02.pdf}
+\includegraphics[scale=0.8]{figures/SI_M02_P00_E02.png}
 \end{center}
@@
 \begin{center}				
-\includegraphics[scale=0.8]{figures/SI_M00_P02_E02.pdf}
+\includegraphics[scale=0.8]{figures/SI_M00_P02_E02.png}
 \end{center}
@@
 \begin{center}				
-\includegraphics[scale=0.8]{figures/SI_M02_P02_E02.pdf}
+\includegraphics[scale=0.8]{figures/SI_M02_P02_E02.png}
 \end{center}

### 2017-03-23 ms_pre_post.Rmd
Fix reference to supporting information

@@
 
-Despite the paucity of theory and resulting predictions, numerous empirical studies on diverse species have tested for, and in some cases found evidence of, female inbreeding avoidance in systems where polyandry also occurs [@Tregenza2002; @Varian-Ramos2012; @Kingma20134; @Arct2015; but see @Reid2015a].
+Despite the paucity of theory and resulting predictions, numerous empirical studies on diverse species have tested for, and in some cases found evidence of, female inbreeding avoidance in systems where polyandry also occurs [@Tregenza2002; @Varian-Ramos2012; @Kingma2013; @Arct2015; but see @Reid2015a].
 However, relatively few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
@@
 Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information p.
-S1-1).
+S1).
 In addition to polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).

### 2017-04-04 ms_pre_post.Rmd
Add a couple sentences about model assumptions and quantitative prediction limitations

@@
 We thereby highlight fundamental but theoretically under-developed relationships between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding avoidance.
+We present our model and simulation results as a tool for thinking more clearly about reproductive strategies, not for making accurate quantitative predictions in any specific system.
+While the logic of our model can be usefully applied to constructing hypotheses within and across empirical systems, accurate quantitative prediction would require additional detail and the incorporation of empirical data for model parameterisation.
 

### 2017-04-05 ms_pre_post.Rmd
Minor tweaks to Introduction

@@
 Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002].
-Resulting indirect selection on polyandry could explain its evolution in cases where multiple mating does not increase female reproductive success, or even where polyandry reduces reproductive success and therefore imposes direct fitness costs on polyandrous females.
+Resulting indirect selection on polyandry could explain its evolution in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct fitness costs on polyandrous females.
 However, despite such widely-invoked hypotheses, there is surprising little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
@@
 First, does evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance facilitate evolution of polyandry that is otherwise severely constrained by increasing relatedness of polyandrous females' additional mates?
-Second, how do costs associated with polyandry and pre-copulatory and post-copulatory inbreeding avoidance affect evolutionary outcomes and, in particular, the long-term persistence of reproductive strategies given cost asymmetry?
+Second, how do costs associated with polyandry and pre-copulatory and post-copulatory inbreeding avoidance affect evolutionary outcomes and, in particular, the long-term persistence of these reproductive strategies given cost asymmetry?
 Third, how is selection for initially rare pre-copulatory or post-copulatory inbreeding avoidance affected if the other strategy of inbreeding avoidance is already fixed?

### 2017-04-05 ms_pre_post.Rmd
Minor tweaks to Methods

@@
 
-We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply 'inbreeding strategies' because of the possibility for inbreeding preference to evolve in the model), by tracking the dynamics of alleles underlying reproductive strategies enacted by interacting females and males within a small focal population.
+We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply 'inbreeding strategies' because the model did not preclude evolution of inbreeding preference), by tracking the dynamics of alleles underlying reproductive strategies enacted by interacting females and males within a small focal population.
 We thereby track evolutionary dynamics given internally consistent patterns of relatedness caused by non-random mating and allowing for effects of mutation, gene flow, drift, and selection.
-Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of the three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$), pre-copulatory inbreeding strategy ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., 'fertilisation' alleles).
-All alleles can take any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014] and combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for each of the three traits whereby an individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
+Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$, i.e., 'polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., 'fertilisation' alleles).
+All alleles can take the value of any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014] and combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively, whereby an individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
 In overview, each generation proceeds with females paying costs and expressing polyandry, mating, and fertilisation.
@@
 
-Phenotypic values for tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$) each have costs that are assumed to independently increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
+Phenotypic values of $P_{p}$, $M_{p}$, and $F_{p}$ each have costs that are assumed to independently increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
 The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
@@
 
-The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a log-linear function of her kinship with the sire $j$ of her offspring ($k_{ij}$) and inbreeding depression slope $\beta$,
+The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a log-linear function of her kinship with the sire $j$ of the offspring ($k_{ij}$) and inbreeding depression slope $\beta$,
 \begin{equation}
@@
 We therefore define $\Psi_{\textrm{off}}$ as the probability that an offspring is viable, and sample its realised viability (versus mortality) using a Bernoulli trial.
-We simulate evolution under conditions where inbreeding avoidance is adaptive due to strong inbreeding depression, and not evolution where inbreeding preference is adaptive due to weak or zero inbreeding depression [@Parker1979; @Kokko2006; @Duthie2016a], or given outbreeding depression [@Bateson1983; @Greeff2009].
+Given our current objectives, we simulate evolution under conditions where inbreeding avoidance is adaptive due to strong inbreeding depression, and not evolution where inbreeding preference is adaptive due to weak or zero inbreeding depression [@Parker1979; @Kokko2006; @Duthie2016a], or given outbreeding depression [@Bateson1983; @Greeff2009].
 However, as described above, positive $M_{p}$ and $F_{p}$ values resulting in inbreeding preference are permitted to evolve, and could potentially arise due to mutation or drift.
@@
 
-To address how selection on an initially rare strategy of pre-copulatory or post-copulatory inbreeding avoidance, and resulting evolution, is affected by the other strategy of inbreeding avoidance already being fixed, we first used exploratory simulations to quantify evolution of pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation.
-Then, to test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance were fixed, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., meaning that $F_{p}$ and $P_{p}$ did not evolve).
+To address how selection on an initially rare strategy of pre-copulatory or post-copulatory inbreeding avoidance, and resulting evolution, is affected by the other strategy of inbreeding avoidance already being fixed in the population, we first used exploratory simulations to quantify evolution of pre-copulatory inbreeding strategy, and of post-copulatory inbreeding strategy and associated polyandry, in isolation.
+Then, to test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance were fixed, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., meaning that $F_{p}$ and $P_{p}$ were expressed did not evolve further).
 Similarly, to test whether post-copulatory inbreeding avoidance would evolve when pre-copulatory inbreeding avoidance was already fixed, we initiated $F_{a}$ and $P_{a}$ allele values at zero but fixed $M_{a}$ allele values at $-10$.

### 2017-04-05 Supplement.tex
Rearrange figures in the supplemental material

@@
 \noindent \textbf{Here we present supplemental results from an individual-based model in which alleles underlying polyandry (\bm{$P_{a}$}), pre-copulatory inbreeding strategy (\bm{$M_{a}$}) and post-copulatory inbreeding strategy (\bm{$F_{a}$}) affect evolving phenotypic values for each trait over 40000 generations.
-The first figure in this supplement summarises trajectories of allele values across replicate simulations for all cost combinations of \bm{$0$} and \bm{$0.02$} for polyandry (\bm{$c_{P}$}), pre-copulatory inbreeding strategy (\bm{$c_{M}$}), and post-copulatory inbreeding strategy (\bm{$c_{F}$}).
-The second figure shows how \bm{$F_{a}$} alleles change over generations given that \bm{$M_{a}$} alleles are fixed for strong inbreeding avoidance and \bm{$P_{a}$} alleles are fixed for polyandry.
-Remaining figures show the dynamics of individual replicate simulations for all trait cost combinations of \bm{$0$} and \bm{$0.02$}; these figures also show correlations of mean allele values among replicates.}
+Figures S\ref{SI_M00_P00_E00}-S\ref{SI_M02_P02_E02} show the dynamics of individual replicate simulations for all trait cost combinations of \bm{$0$} and \bm{$0.02$}; these figures also show correlations of mean allele values among replicates.
+Figure S\ref{allcombs} summarises trajectories of allele values across replicate simulations for all cost combinations of \bm{$0$} and \bm{$0.02$} for polyandry (\bm{$c_{P}$}), pre-copulatory inbreeding strategy (\bm{$c_{M}$}), and post-copulatory inbreeding strategy (\bm{$c_{F}$}).
+Figure \ref{extra_MfPf} shows how \bm{$F_{a}$} alleles change over generations given that \bm{$M_{a}$} alleles are fixed for strong inbreeding avoidance and \bm{$P_{a}$} alleles are fixed for polyandry.}
 
@@
 
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{allcombs}: All cost combinations}}{S3}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{extra_MfPf}: Dynamic \bm{$F_{a}$}, fixed \bm{$P_{a}=1$} and \bm{$M_{a}=-10$}}}{S4}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P00_E00}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0$}}}{S5}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P00_E00}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0$}}}{S6}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P02_E00}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0$}}}{S7}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P00_E02}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0.02$}}}{S8}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P02_E00}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0$}}}{S9}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P00_E02}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0.02$}}}{S10}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P02_E02}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0.02$}}}{S11}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P02_E02}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0.02$}}}{S12}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P00_E00}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0$}}}{S3}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P00_E00}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0$}}}{S4}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P02_E00}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0$}}}{S5}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P00_E02}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0.02$}}}{S6}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P02_E00}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0$}}}{S7}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P00_E02}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0.02$}}}{S8}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P02_E02}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0.02$}}}{S9}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P02_E02}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0.02$}}}{S10}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{allcombs}: All cost combinations}}{S11}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{extra_MfPf}: Dynamic \bm{$F_{a}$}, fixed \bm{$P_{a}=1$} and \bm{$M_{a}=-10$}}}{S12}
 
@@
 \clearpage
-
-\clearpage
-\begin{figure}
-\begin{center}				
-\includegraphics[scale=0.82]{figures/evo_combs.png}
-\end{center}
-\caption{Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (blue lines and shading), and post-copulatory inbreeding strategy (black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard deviations of allele values around grand means.
-Negative mean allele values indicate inbreeding avoidance or tendency for monandry, and positive values indicate inbreeding preference or tendency for polyandry.
-Panels A-H show simulations for different combinations of costs for tendency for polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$).
-Dotted horizontal black lines in panels show values of zero on the y-axis.
-Individual replicates for all cost combinations are shown in Figures S\ref{SI_M00_P00_E00}-S\ref{SI_M02_P02_E02}.}
-\label{allcombs}
-\end{figure}
-
-\clearpage
-\begin{figure}
-\begin{center}				
-\includegraphics[scale=0.8]{figures/extra_MfPf.png}
-\end{center}
-\caption{Mean allele values underlying post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
-Solid black lines represent grand means over 40 replicate populations, and grey shading around solid lines show standard errors of allele values around grand means.
-Negative mean allele values indicate strategies of inbreeding avoidance, and positive values indicate strategies of inbreeding preference.
-Red and blue horizontal lines indicate fixed polyandry allele values of $P_{a}=1$ and fixed pre-copulatory inbreeding strategy allele values of $M_{a}=-10$, respectively.
-Panels (A) and (B) show simulations given not costly and costly post-copulatory inbreeding strategy, respectively.
-Dotted horizontal lines show where the y-axis equals zero.}
-\label{extra_MfPf}
-\end{figure}
 
@@
 
+\clearpage
+\begin{figure}
+\begin{center}				
+\includegraphics[scale=0.82]{figures/evo_combs.png}
+\end{center}
+\caption{Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (blue lines and shading), and post-copulatory inbreeding strategy (black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard deviations of allele values around grand means.
+Negative mean allele values indicate inbreeding avoidance or tendency for monandry, and positive values indicate inbreeding preference or tendency for polyandry.
+Panels A-H show simulations for different combinations of costs for tendency for polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$).
+Dotted horizontal black lines in panels show values of zero on the y-axis.
+Individual replicates for all cost combinations are shown in Figures S\ref{SI_M00_P00_E00}-S\ref{SI_M02_P02_E02}.}
+\label{allcombs}
+\end{figure}
+
+\clearpage
+\begin{figure}
+\begin{center}				
+\includegraphics[scale=0.8]{figures/extra_MfPf.png}
+\end{center}
+\caption{Mean allele values underlying post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression.
+Solid black lines represent grand means over 40 replicate populations, and grey shading around solid lines show standard errors of allele values around grand means.
+Negative mean allele values indicate strategies of inbreeding avoidance, and positive values indicate strategies of inbreeding preference.
+Red and blue horizontal lines indicate fixed polyandry allele values of $P_{a}=1$ and fixed pre-copulatory inbreeding strategy allele values of $M_{a}=-10$, respectively.
+Panels (A) and (B) show simulations given not costly and costly post-copulatory inbreeding strategy, respectively.
+Dotted horizontal lines show where the y-axis equals zero.}
+\label{extra_MfPf}
+\end{figure}
+
 \end{document}

### 2017-04-05 ms_pre_post.Rmd
Minor tweaks to the Results

@@
 
-When post-copulatory inbreeding avoidance alleles ($F_{a}$) had no effect (i.e., $F_{g}$ genotypes were fixed to zero), meaning that $F_{p}$ could not evolve, $P_{a}$ alleles underlying polyandry always decreased to negative values over generations (red lines, Figure 1A,C,E,G).
+When post-copulatory inbreeding avoidance alleles ($F_{a}$) had no effect (i.e., $F_{g}$ values were fixed to zero), meaning that $F_{p}$ could not evolve, $P_{a}$ alleles underlying polyandry always decreased to negative values over generations (red lines, Figure 1A,C,E,G).
 This shows that despite strong inbreeding depression in offspring viability, there is selection against unconditional polyandry even given zero direct cost ($c_{P}=0$; Figure 1A).
@@
 Given higher costs of polyandry ($c_{P} \geq 0.005$), $P_{a}$ allele values still initially increased from zero, but then became slightly negative over generations (Figure 1F,H).
-Trajectories of allele values in individual simulations were typically highly stochastic, but were consistent in their long-term direction (Supporting Information pp.
-S5-S12).
-Overall, this implies that, even given strong inbreeding depression in offspring viability, inbreeding avoidance might generally be a weak force driving polyandry evolution.
+Trajectories of allele values in individual simulations were typically highly stochastic, but were consistent in their long-term direction (Supporting Information Figures S1-S8).
+Overall, this implies that, even given strong inbreeding depression in offspring viability and simultaneous evolution of pre-copulatory and post-copulatory strategies, inbreeding avoidance might generally be a weak force driving polyandry evolution.
 
@@
 However when post-copulatory inbreeding avoidance was costly, allowing evolution of cost free pre-copulatory inbreeding avoidance caused $P_{a}$ alleles to decrease to very negative values, reducing expression of polyandry (Figure 3C versus 3D; polyandry was cost free in all these simulations).
-Results for all possible cost combinations of $0$ and $0.02$ are provided in Supporting Information (pp.
-S5-S12).
+Results for all possible cost combinations of $0$ and $0.02$ are provided in Supporting Information (Figure S9).
 
@@
 This lack of selection for post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
-When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information p.
-S4).
+When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information Figure S10).
 

### 2017-04-05 ms_pre_post.Rmd
Final tweaks before sending to potential coauthors

@@
 author: ''
-date: "23 March 2017"
+date: "5 April 2017"
 output:
-  pdf_document:
-    fig_caption: yes
-  html_document: default
   word_document:
@@
 Evolution of inbreeding avoidance can be driven by selection on both pre-copulatory and post-copulatory mechanisms, so simultaneous evolution of each phenotype is likely to be defined by degeneracy, in addition to any direct costs on phenotypes.
-We used individual-based modelling to explore evolution of pre-copulatory and post-copulatory inbreeding avoidance and polyandry given (1) hard constraints on evolution of post-copulatory inbreeding avoidance, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding avoidance, and (3) evolution of one inbreeding avoidance phenotype given the pre-existence the other.
-We thereby highlight fundamental but theoretically under-developed relationships between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding avoidance.
-We present our model and simulation results as a tool for thinking more clearly about reproductive strategies, not for making accurate quantitative predictions in any specific system.
+We used individual-based modelling to explore evolution of pre-copulatory and post-copulatory inbreeding strategy and polyandry given (1) hard constraints on evolution of post-copulatory inbreeding strategy, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding strategy, and (3) evolution of one inbreeding strategy phenotype given the pre-existence of the other.
+We thereby highlight fundamental but theoretically under-developed relationships between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding strategy.
+We present our model and simulation results as a tool for thinking more clearly about the dynamics of simultaneously evolving reproductive strategies, not for making accurate quantitative predictions for any specific system.
 While the logic of our model can be usefully applied to constructing hypotheses within and across empirical systems, accurate quantitative prediction would require additional detail and the incorporation of empirical data for model parameterisation.
@@
 @Pomiankowski1987 categorised four types of costs that are relevant to mate choice, which are also relevant for polyandry, and include costs of elevated risks of predation or disease transmission, and costs incurred through time or energy expenditure.
-Another type of cost relevant for polyandry and inbreeding strategy is risk of male harm caused by sexual conflict [e.g., @Arnqvist2005a; @Parker2006].
+Another relevant cost is risk of male harm caused by sexual conflict [e.g., @Arnqvist2005a; @Parker2006].
 We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should benefit from a higher tolerance of inbreeding than females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
-Here we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of pre-copulatory inbreeding strategy as a lost of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of post-copulatory inbreeding strategy as depletion of energy.
-While these costs thereby reflect empirical observations in some populations and are therefore biologically realistic, other types of costs have also been observed and could therefore be considered in future models.
-For example, increased risk of disease transmission has been observed for highly polyandrous females [@Roberts2015a], but such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry.
+Here we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of pre-copulatory inbreeding strategy as a lost of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy.
+While these costs reflect empirical observations in some populations and are therefore biologically realistic, other types of costs have also been observed and could be considered in future models tailored to specific systems.
+For example, increased risk of disease transmission has been observed for highly polyandrous females [@Roberts2015a], and such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry.
 Different types of costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
@@
 In wild populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
-Rather, for example, initial evolution of pre-copulatory inbreeding avoidance is much more likely to evolve in the absence of evolving post-copulatory inbreeding avoidance due to constraints, or in the presence of already evolved post-copulatory inbreeding avoidance.
+Rather, the timing of the invasion of adaptive inbreeding avoidance phenotypes will differ, so the initial evolution of one inbreeding strategy will likely occur in the absence of the other, or where selection for and subsequent evolution of the other strategy has already occurred.
 When framing hypotheses for existence of post-copulatory inbreeding avoidance and polyandry, it might therefore be necessary to consider whether or not inbreeding avoidance already occurs through pre-copulatory mate choice.
@@
 This theory is borne out in our simulation results, as selection for, and consequent evolution of, post-copulatory inbreeding avoidance was negligible in populations where polyandry did not evolve, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D).
-Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information p.
-S1).
+Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information Figure S9).
 In addition to polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).
-It would therefore be interesting to test the hypothesis that, across taxa, occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with degree of polyandry.
-To test this hypothesis, more work is needed to identify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
+It would therefore be interesting to test the hypothesis that, across taxa, occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with the degree of polyandry.
+To test this hypothesis, more work is needed to quantify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
 
@@
 In general, degeneracy might increase biological robustness by fine-tuning degenerate phenotypes to different local environments [@Gardner2006; @Whitacre2010a].
-For example, degeneracy might ensure successful inbreeding avoidance through pre-copulatory or post-copulatory mechanisms where or when avoidance through the other mechanism is ineffective (e.g., due to sexual conflict affecting mate choice or injury affecting fertilisation).
+For example, degeneracy might ensure successful inbreeding avoidance through either pre-copulatory or post-copulatory mechanisms when avoidance through the other mechanism is ineffective (e.g., due to sexual conflict affecting mate choice or injury affecting fertilisation).
 However, evolution of one inbreeding avoidance mechanism might also weaken selection on the other by modifying the latter's impact on total realised inbreeding avoidance [*sensu* evolution of genetic redundancy; see @Nowak1997].
@@
 
-![Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding avoidance ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve.
+![Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve.
 Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.

### 2017-04-06 pre_post_biorxiv.tex
Update the biorXiv through methods -- need to finish from Results onward

@@
 }
-Inbreeding avoidance has been widely hypothesised to evolve through pre-copulatory and post-copulatory mechanisms as a consequence of inbreeding depression in offspring viability.
-However, no modelling compares evolution of pre-copulatory and post-copulatory inbreeding avoidance jointly, and given biologically relevant costs of inbreeding strategies.
-Critically, evolution of post-copulatory inbreeding avoidance is restricted to females that mate multiply, potentially leading to complex evolutionary dynamics among inbreeding strategies and polyandry.
-Accordingly, we use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address three questions: (1) Does evolution of post-copulatory inbreeding avoidance facilitate evolution of costly polyandry?
-(2) Is evolution of one costly inbreeding strategy inhibited by another non-costly alternative strategy?
-And (3) is evolution of one inbreeding strategy precluded by existence of another already adaptive strategy?
-We show that evolution of polyandry is facilitated by post-copulatory inbreeding avoidance.
-Evolution of relatively low cost inbreeding avoidance strategies was observed, while selection for functionally redundant high cost strategies decreased over generations.
-Finally, existence of an adaptive inbreeding strategy precluded evolution of post-copulatory, but not pre-copulatory, inbreeding avoidance.
-Our model thereby introduces a novel framework for predicting evolution of both pre-copulatory and post-copulatory inbreeding strategies in empirical systems.
+Inbreeding depression is widely hypothesised to drive adaptive evolution of pre-copulatory and post-copulatory mechanisms of inbreeding avoidance, which in turn are hypothesised to affect evolution of polyandry (i.e., female multiple mating).
+However, surprisingly little theory or modelling critically examines selection for pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, given evolutionary constraints and direct costs, or examines how evolution of inbreeding avoidance strategies might feed back to affect evolution of polyandry.
+Selection for post-copulatory inbreeding avoidance, but not for pre-copulatory inbreeding avoidance, requires polyandry, while interactions between pre-copulatory and post-copulatory inbreeding avoidance might cause functional redundancy (i.e., 'degeneracy') potentially generating complex evolutionary dynamics among inbreeding strategies and polyandry.
+We use individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression and different evolutionary constraints and direct costs.
+We find that evolution of post-copulatory inbreeding avoidance causes selection for increased polyandry, and that selection for a costly inbreeding avoidance strategy was weak or negligible given a cost free alternative strategy.
+Further, fixed pre-copulatory inbreeding avoidance generally precluded evolution of polyandry and therefore post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance.
+We thereby provide a general framework for understanding joint evolution of pre-copulatory and/or post-copulatory inbreeding avoidance, and conclude that evolution of inbreeding avoidance phenotypes and associated polyandry are predicted to be strongly affected by evolutionary feedbacks and degeneracy, and by direct costs on phenotypes affecting reproductive strategy.
 
@@
 
-Inbreeding often greatly reduces the fitness of inbred offspring \cite[termed `inbreeding depression';][]{Charlesworth1999, Keller2002, Charlesworth2009}.
-Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple reproductive decisions in species with obligate biparental reproduction \cite[][]{Parker1979, Parker2006, Pusey1996, Szulkin2012}.
-From the perspective of a focal breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred, meaning that related males are less likely to sire offspring (i.e., post-copulatory inbreeding avoidance).
-Importantly, evolution of post-copulatory inbreeding avoidance requires that females are polyandrous, defined as mating with multiple males during a single reproductive bout.
-Further, such polyandry could itself evolve because it allows females to mate with additional unrelated males following initial mating with a relative, thereby facilitating pre-copulatory inbreeding avoidance even in the absence of any post-copulatory female choice or otherwise biased fertilisation (e.g., given a `fair raffle' among sperm provided by females' mates).
-As a reproductive strategy, polyandry can thereby simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
-Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness \cite[][]{Zeh1997, Jennions2000, Tregenza2002, Akcay2007}.
-However, despite such well-established hypotheses, no modelling investigates conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are likely to evolve, or predicts how such evolution will feed back to affect underlying evolution of polyandry.
+Inbreeding, defined as reproduction between relatives, often greatly reduces the fitness of resulting inbred offspring \cite[termed `inbreeding depression';][]{Charlesworth1999, Keller2002, Charlesworth2009}.
+Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple interacting reproductive strategies \cite[][]{Parker1979, Parker2006, Pusey1996, Szulkin2012}.
 
-Meanwhile, studies of diverse species have found evidence for female inbreeding avoidance enacted through pre-copulatory or post-copulatory routes, or both.
-For example, pre-copulatory inbreeding avoidance has been documented in weevils, birds, and butterflies \cite[e.g.,][]{Kuriwada2011, Kingma2013, Fischer2015}, and post-copulatory inbreeding avoidance has been documented in crickets \cite[e.g.,][]{Simmons2006, Bretman2009}.
-Evidence of both pre-copulatory and post-copulatory inbreeding avoidance has accumulated for some well-studied species, including Trinidadian guppies \cite[\textit{Poecilia reticulata};][]{Gasparini2011, Daniel2015} and house mice \cite[\textit{Mus domesticus};][]{Potts1991, Firman2015}.
-While most studies consider either pre-copulatory or post-copulatory inbreeding avoidance in isolation, a small number of studies consider both.
-Accordingly, \cite{Liu2014} found evidence of pre-copulatory, but not post-copulatory, inbreeding avoidance in cabbage beetles (\textit{Colaphellus bowringi}).
-Other studies found no evidence of pre-copulatory or post-copulatory inbreeding avoidance despite strong inbreeding depression \cite[e.g.,][]{Reid2014, Reid2015}.
-These studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature.
-However, there is as yet no modelling framework that predicts what combinations should be favoured by selection when both pre-copulatory and post-copulatory inbreeding avoidance, and polyandry, can evolve.
-Such a framework would allow prediction of the form of mating system evolution across different systems that experience inbreeding depression and allow existing empirical studies to be compared to model predictions.
+From the perspective of a focal breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
+Evolution of post-copulatory inbreeding avoidance requires that females express some non-trivial degree of polyandry, defined as mating with multiple males during a single reproductive bout.
+Further, given inbreeding depression, such polyandry might itself be under selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative.
+Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm provided by females' mates (i.e., `fair raffle').
+Overall, polyandry can therefore simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
+Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness \cite[][]{Zeh1997, Jennions2000, Tregenza2002}.
+Resulting indirect selection on polyandry could explain its evolution in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct fitness costs on polyandrous females.
+However, despite such widely-invoked hypotheses, there is surprising little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
 
-\subsection*{Verbal theory}
+Despite the paucity of theory and resulting predictions, numerous empirical studies on diverse species have tested for, and in some cases found evidence of, female inbreeding avoidance in systems where polyandry also occurs \cite[][but see \citealt{Reid2015a}]{Tregenza2002, Varian-Ramos2012, Kingma2013, Arct2015}.
+However, relatively few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
+Pre-copulatory inbreeding avoidance has been reported in diverse species, spanning sweet potato weevils \cite[\textit{Cylas formicarius};][]{Kuriwada2011}, purple-crowned fairy-wrens \cite[\textit{Malurus coronatus};][]{Kuriwada2011}, and a tropical butterfly \cite[\textit{Bicyclus anynana};][]{Fischer2015}, while post-copulatory inbreeding avoidance has been reported in red junglefowl \cite[\textit{Gallus gallus};][]{Pizzari2004} and crickets \cite[\textit{Teleogryllus oceanicus}, \textit{Gryllus bimaculatus};][]{Simmons2006, Bretman2009}.
+Evidence for both pre-copulatory and post-copulatory inbreeding avoidance is available across different studies of Trinidadian guppies \cite[\textit{Poecilia reticulata};][]{Gasparini2011, Daniel2015} and house mice \cite[\textit{Mus domesticus};][]{Potts1991, Firman2015}.
+Meanwhile, \cite{Liu2014} found evidence of pre-copulatory but not post-copulatory inbreeding avoidance within a single study of cabbage beetles (\textit{Colaphellus bowringi}).
+However, \cite{Ala-Honkola2011} and \cite{Tan2012} found no evidence for pre-copulatory or post-copulatory inbreeding avoidance in fruit flies (\textit{Drosophila melanogaster}), respectively, and Reid et al.
+\citeyearpar{Reid2014, Reid2015} found no net inbreeding avoidance in song sparrows (\textit{Melospiza melodia}) despite strong inbreeding depression.
+Taken together, these studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature alongside polyandry.
+However, there is as yet no theory that predicts what combinations of pre-copulatory and post-copulatory inbreeding avoidance and polyandry should be favoured by selection when all combinations of phenotypes can evolve.
+Consequently, there is no theory that allows the diversity of existing empirical results regarding pre-copulatory and post-copulatory inbreeding avoidance to be interpreted, and no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
 
-A recent genetically-explicit individual-based model showed that selection for alleles underlying polyandry and pre-copulatory inbreeding avoidance, and resulting joint evolution of these reproductive strategies, occurred only under highly constrained conditions \cite[][]{Duthie}.
-Specifically, such evolution occurred when direct costs of polyandry were small, when very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or when polyandry was conditionally expressed when a focal female was related to her initial mate \cite[][]{Duthie}.
-In the absence of these conditions, increasing degrees of polyandry tended to increase the overall degree of inbreeding that females experienced, and hence increase inbreeding depression in offspring fitness.
-This occurred because polyandrous females that had evolved to avoid inbreeding had already chosen available unrelated males as their initial mates.
+To develop theory on evolution of polyandry given inbreeding depression, \cite{Duthie} used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance.
+Net selection for polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., `costs') on polyandry was weak, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate \cite[][]{Duthie}.
+Without these conditions, increasing polyandry tended to increase rather than decrease the overall degree of inbreeding that females experienced, and hence reduce offspring fitness.
+This occurred because, once pre-copulatory inbreeding avoidance evolved, polyandrous females had already chosen available unrelated males as their initial mates.
 Their additional mates, chosen from the remaining male population, were therefore increasingly likely to include relatives.
-Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance was consequently restricted.
+Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance, and hence the resulting degree of inbreeding avoidance, was consequently restricted \cite[][]{Duthie}.
 
-However, while \cite{Duthie} considered simultaneous evolution of polyandry and pre-copulatory inbreeding avoidance, they did not also allow simultaneous evolution of post-copulatory inbreeding avoidance, and assumed that polyandrous females had no post-copulatory control over fertilisation.
-If post-copulatory inbreeding avoidance could also evolve, polyandrous females could further bias paternity towards unrelated males within their set of chosen mates.
-This process might reduce the cost of polyandry stemming from accumulation of related mates, potentially facilitating evolution of polyandry to avoid inbreeding \cite[][]{Zeh1997}, and driving further consequent evolution of pre-copulatory or post-copulatory mate choice strategies.
-Therefore, while pre-copulatory inbreeding avoidance can facilitate evolution of polyandry under some restrictive conditions \cite[][]{Duthie}, the opportunity for post-copulatory choice might facilitate evolution of polyandry under a much wider range of conditions by allowing females to bias fertilisation toward non-kin.
-The long-term evolutionary dynamics of pre-copulatory and post-copulatory inbreeding avoidance then become unclear.
+However, if post-copulatory inbreeding avoidance could also evolve, polyandrous females would also have an opportunity to bias paternity towards unrelated males within their set of chosen mates.
+Evolution of post-copulatory inbreeding avoidance might consequently reduce the cost of polyandry stemming from the accumulation of related mates across multiple matings, potentially facilitating evolution of polyandry to avoid inbreeding under broader conditions, and driving further evolution of pre-copulatory or post-copulatory mate choice strategies.
+However, if polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, the long-term dynamics of these three reproductive strategies become difficult to predict.
 Strong inbreeding depression might drive initial evolution of both pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
-However, if evolution of polyandry and post-copulatory inbreeding avoidance renders pre-copulatory inbreeding avoidance redundant, or vice versa, then only one strategy might be maintained in the long-term.
+However, the co-occurence of pre-copulatory and post-copulatory inbreeding avoidance might engender some degree of `degeneracy', defined as a phenomenon by which different elements of a system result in identical outputs \cite[i.e.,][]{Edelman2001}.
+Consequently, if evolution of polyandry and post-copulatory inbreeding avoidance renders pre-copulatory inbreeding avoidance functionally redundant, or vice versa, then only one inbreeding avoidance strategy might be maintained in the long-term.
 
-Previous models implicitly or explicitly considered the fate of a rare allele underlying pre-copulatory inbreeding avoidance in a population initially fixed for random mating \cite[e.g.,][]{Parker1979, Parker2006, Duthie, Duthie2016a}.
-Such models thereby isolate the invasion fitness of this single strategy.
-However, when both pre-copulatory and post-copulatory strategies can affect realised inbreeding, it cannot be assumed that both strategies will invade simultaneously, nor that invasion fitness of one strategy will be independent of the other.
-For example, if pre-adaptation or rapid selection results in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect of such invading alleles could be weak or negligible.
+The few previous models that considered the evolution of inbreeding avoidance through mate choice (as opposed to dispersal) have implicitly or explicitly considered the fate of a rare allele underlying pre-copulatory inbreeding avoidance in a population initially fixed for random mating \cite[e.g.,][]{Parker1979, Parker2006, Duthie, Duthie2016a}.
+Such models are useful for isolating the invasion fitness of this single strategy.
+However, when both pre-copulatory and post-copulatory strategies can affect the realised degree of inbreeding, it cannot be assumed that both strategies will simultaneously invade a randomly mating population, nor that the invasion fitness of one strategy will be independent of the pre-existence or invasion fitness of the other strategy.
+For example, if pre-adaptation or a selective sweep results in fixation of alleles underlying pre-copulatory inbreeding avoidance, then new alleles underlying polyandry and post-copulatory inbreeding avoidance might be unlikely to invade a population because the phenotypic effect of such alleles on the overall degree of inbreeding, and resulting indirect selection, could be negligible.
+Conversely, fixation of alleles underlying polyandry and post-copulatory inbreeding avoidance might reduce or eliminate positive selection on alleles underlying pre-copulatory inbreeding avoidance and hence impede adaptive evolution of mate choice.
+New theory, guided by modelling that evaluates invasion dynamics of alleles underlying multiple interacting and potentially functionally redundant (i.e., `degenerate') traits, is therefore needed.
 
-Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry are likely to be affected by direct negative selection on resulting phenotypes (i.e., costs) and hence on the net costs versus benefits stemming from inbreeding avoidance.
+Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will depend not only on the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also on the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
 Polyandrous females can pay costs of mate searching or mating, for example, because these activities increase predation risk \cite[e.g.,][]{Rowe1988, Ronkainen1994, Koga1998}.
-Females that express pre-copulatory choice (e.g., reluctance to mate with relatives) might pay a cost of increased risk of mating failure, or harm caused by sexual conflict \cite[][]{Rowe1994, Kokko2013}.
-Females that express post-copulatory choice might pay an energetic cost associated with physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation \cite[e.g.,][]{Gasparini2011, Tuni2013, Fitzpatrick2014b}.
-If the relative costs affecting pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly inbreeding strategy might become fixed in the population over generations, while alleles underlying the more costly inbreeding strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
+Females that express pre-copulatory choice and consequent reluctance to mate with relatives might pay costs of increased risk of complete mating failure or harm caused by sexual conflict \cite[][]{Rowe1994, Kokko2013}.
+Females that express post-copulatory choice might pay initial energetic costs associated with developing the physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation \cite[e.g.,][]{Gasparini2011, Tuni2013, Fitzpatrick2014b}.
+If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly inbreeding avoidance strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
+However, such trajectories will also depend on the indirect benefits of each strategy, which might also differ and vary in relation to the evolution of the other strategy.
+Dynamic models that track the frequencies of alleles underlying multiple reproductive strategies that might influence each others evolution across generations, and that are enacted among relatives that themselves result from reproductive strategies and inbreeding depression expressed in previous generations, are consequently useful to understand and predict evolutionary outcomes.
 
-Here we use individual-based modelling to set up \textit{in silico} experiments, which test the hypothesis that, given strong inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance facilitates evolution of polyandry.
-Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution such that only the less costly inbreeding avoidance strategy will be expressed in the long term.
-Finally, we test the hypothesis that evolution of one inbreeding avoidance strategy (i.e., pre-copulatory or post-copulatory) will be precluded if it is introduced into a population that is already fixed for the other inbreeding avoidance strategy that is adaptive.
-We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across different reproductive systems.
+We use individual-based modelling to address three key questions regarding evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given opportunity for inbreeding and strong inbreeding depression.
+First, does evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance facilitate evolution of polyandry that is otherwise severely constrained by increasing relatedness of polyandrous females' additional mates?
+Second, how do costs associated with polyandry and pre-copulatory and post-copulatory inbreeding avoidance affect evolutionary outcomes and, in particular, the long-term persistence of these reproductive strategies given cost asymmetry?
+Third, how is selection for initially rare pre-copulatory or post-copulatory inbreeding avoidance affected if the other strategy of inbreeding avoidance is already fixed?
+By addressing these questions, we illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
+We thereby provide a framework for deriving hypotheses amenable to empirical tests within and across taxa.
 
-\section*{Methods}
+\section*{Model}
 
-We model evolution of polyandry and pre-copulatory and post-copulatory inbreeding avoidance by tracking reproductive interactions among individual females and males in a small focal population.
-Individuals are defined as related if they share a common ancestor within the population pedigree (i.e., non-zero kinship).
-Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of the three reproductive strategy traits: tendency for polyandry ($P_{a}$), pre-copulatory inbreeding avoidance ($M_{a}$, i.e., `mating' alleles), and post-copulatory inbreeding avoidance ($F_{a}$, i.e., `fertilisation' alleles).
-Alleles can take any real number \cite[i.e., a continuum-of-alleles model;][]{Kimura1965, Lande1976, Reeve2000, Bocedi2014} and combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for each trait.
-In overview, each generation proceeds with females paying costs, expressing polyandry, mating, and fertilisation.
+We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply 'inbreeding strategies' because the model did not preclude evolution of inbreeding preference), by tracking the dynamics of alleles underlying reproductive strategies enacted by interacting females and males within a small focal population.
+We thereby track evolutionary dynamics given internally consistent patterns of relatedness caused by non-random mating and allowing for effects of mutation, gene flow, drift, and selection.
+Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$, i.e., `polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., `mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., `fertilisation' alleles).
+All alleles can take the value of any real number \cite[i.e., a continuum-of-alleles model;][]{Kimura1965, Lande1976, Reeve2000, Bocedi2014} and combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively, whereby an individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
+In overview, each generation proceeds with females paying costs and expressing polyandry, mating, and fertilisation.
 Offspring inherit a randomly sampled allele from each parent at each locus with no physical linkage.
-Alleles can then mutate and offspring express inbreeding depression.
+Alleles can then mutate and offspring express inbreeding depression in viability.
 Immigrants arrive in the population and density regulation limits population growth.
+We record the population pedigree and directly calculate the coefficient of kinship ($k$) between all potential mates in each generation (defined as the probability that two homologous alleles will be identical-by-descent), allowing individual pre-copulatory and post-copulatory inbreeding strategies to be enacted.
 Key individual traits, parameter values, and variables are described in Table 1.
+
+\subsection*{Costs}
+
+Phenotypic values of $P_{p}$, $M_{p}$, and $F_{p}$ each have costs that are assumed to independently increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
+The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
+Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
+Absolute values are used for applying costs to inbreeding avoidance strategies because both negative and positive $M_{p}$ and $F_{p}$ values could potentially arise and affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively (see details of mating and fertilisation strategies below).
+In contrast, only positive values of $P_{p}$ cause females to be polyandrous (see details of polyandry below).
+Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
 
@@
 
+  & Cost of tendency for polyandry                & $c_{P}$    & & $0$, $0.02$   &
   & Cost of pre-copulatory inbreeding strategy    & $c_{M}$    & & $0$, $0.02$   &
@@
 
-\subsection*{Costs}
-
-Phenotypic values for tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$) each have costs that are assumed to independently increase the probability that a focal female will die before mating.
-The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, repectively.
-Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
-Absolute values are used for applying costs to inbreeding strategies as appropriate because both negative and positive $M_{p}$ and $F_{p}$ values affect the degree of inbreeding.
-In contrast, only positive values of $P_{p}$ cause females to be polyandrous (see below).
-Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases as a linear function with each trait value.
-
 \subsection*{Polyandry}
 
-After costs are paid, each remaining female chooses $N_{males}$ males to mate with, where $N_{males}$ is calculated by sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
+After costs are realised, each remaining female chooses $N_{males}$ males to mate with, where $N_{males}$ is calculated by sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
 This ensures that all surviving females choose at least one mate, and causes some stochastic variation around the expected mean $N_{males}$ of $P_{p}+1$.
-A female's value of $P_{p}$ depends on the sum of her 20 $P_{a}$ allele values, which might be negative or positive.
+A female's value of $P_{p}$ depends on the sum of her 20 $P_{a}$ allele values (i.e., $P_{g}$), which might be negative or positive.
 However, because females cannot mate with a negative number of males, $P_{p}$ is constrained to be zero or positive such that $P_{p} = 0$ when $P_{g} < 0$, but $P_{p} = P_{g}$ when $P_{g} \geq 0$.
-Polyandry is therefore modelled as a threshold trait \cite[][]{Lynch1998, Roff1996, Roff1998, Duthie} that is influenced by continuous genetic variation but only expressed at the threshold value of $P_{g} > 0$.
+Polyandry is therefore modelled as a threshold trait \cite[][]{Lynch1998, Roff1996, Roff1998, Duthie} that is influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
 Any negative $P_{g}$ value therefore generates phenotypic monandry, while positive $P_{g}$ values can lead to different degrees of realised polyandry (i.e., different numbers of mates, $N_{males}$).
@@
 All males in the population are assumed to be available for any female to choose.
-We therefore assume that there is no opportunity cost of male mating such that mating with one female would reduce a male's availability to mate with any other female.
+We therefore assume that there is no opportunity cost of male mating, so mating with one female does not reduce a male's availability to mate with any other female.
 Individual females mate with their total allotment of $N_{males}$ without replacement, meaning that $N_{males}$ models a female's total number of different mates rather than solely her total number of matings.
@@
 Most often, $N_{males}$ will be smaller than the total number of available males \cite[][]{Duthie}.
-Here, each female chooses her $N_{males}$ mates based on her pre-copulatory inbreeding strategy phenotype ($M_{p}$), which equals her pre-copulatory inbreeding strategy genotype ($M_{g}$) defined as the sum of the values of her 20 $M_{a}$ alleles.
-Negative or positive $M_{p}$ values cause a female to avoid or prefer mating with kin, respectively.
-Values of $M_{p}=0$ cause females to mate randomly with respect to kinship.
+Each female then chooses her $N_{males}$ mates based on her pre-copulatory inbreeding avoidance phenotype ($M_{p}$), which equals her genotype ($M_{g}$).
+Negative or positive $M_{p}$ values cause a female to avoid or prefer mating with kin, respectively, whereas $M_{p}=0$ cause females to mate randomly with respect to kinship.
 
-The probability that a focal female $i$ mates with a male $j$ with which she shares some kinship $k_{ij}$ is calculated by first assigning each male a perceived mate quality $Q^{m}_{ij}$.
+To calculate the probability that a focal female $i$ mates with a male $j$ to whom she is related by some kinship $k_{ij}$, each male is first assigned a perceived mate quality $Q^{m}_{ij}$.
 If the female has a strategy of pre-copulatory inbreeding avoidance ($M_{p}<0$), then $Q^{m}_{ij} = (-M_{p} \times k_{ij} + 1)^{-1}$, meaning that $Q^{m}_{ij}$ decreases linearly with increasingly positive values of $k_{ij}$ and increasingly negative values of $M_{p}$.
 If the female has a strategy of pre-copulatory inbreeding preference ($M_{p}>0$), then $Q^{m}_{ij} = M_{p} \times k_{ij} + 1$, meaning that $Q^{m}_{ij}$ increases with increasingly positive $k_{ij}$ and $M_{p}$.
-If $M_{p}=0$, then all males are assigned a quality of 1
+If $M_{p}=0$, then all males are assigned $Q^{m}_{ij}=1$.
 
-After a focal female assigns all males a $Q^{m}_{ij}$ value, each male's value is divided by the sum of all $Q^{m}_{ij}$ values across all males, thereby assigning each male a relative perceived quality $q^{m}_{ij}$, which is constrained to values between zero and one.
-The value of $q^{m}_{ij}$ then defines the probability that a focal female mates with the male; mating is therefore stochastic, and females do not always mate with the male of the highest $q^{m}_{ij}$.
+Each male's value with respect to a focal female is then divided by the sum of all $Q^{m}_{ij}$ values across all males with respect to that female, thereby assigning each male a relative perceived quality $q^{m}_{ij}$, which is constrained to values between zero and one.
+The value of $q^{m}_{ij}$ then defines the probability that a focal female mates with the male.
+Mating is therefore stochastic, and females do not always mate with the male of the highest $q^{m}_{ij}$.
 For polyandrous females that choose multiple mates (i.e., $N_{mates}>1$), mates are chosen iteratively such that $Q^{m}_{ij}$ and $q^{m}_{ij}$ are re-calculated for each additional mate choice, and with $Q^{m}_{ij}$ and therefore $q^{m}_{ij}$ values of already chosen males set to zero to ensure mate sampling without replacement.
@@
 These $q^{f}_{ij}$ values, which lie between zero and one, define the probability of paternity.
+Females produce $n$ offspring, so $q^{f}_{ij}$ values are sampled $n$ times independently and with replacement for each female to determine the realised distribution of sires.
 
@@
 When a mutation occurs, a mutation effect is sampled from a normal distribution with a mean of zero and a standard deviation of $\mu_{SD}$ and added to the original allele value \cite[][]{Kimura1965, Lande1976, Bocedi2014, Duthie}.
-The value of $\mu_{SD}$ is set to $\sqrt{1/20}$, which scales the variance of mutation effect size to the total number of alleles affecting each phenotype.
+The value of $\mu_{SD}$ is set to $\sqrt{1/20}$.
 
@@
 
-The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a log-linear function of her kinship with the sire of her offspring $j$ ($k_{ij}$) and inbreeding depression slope $\beta$,
+The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a log-linear function of her kinship with the sire $j$ of the offspring ($k_{ij}$) and inbreeding depression slope $\beta$,
 \begin{equation}
@@
 We model inbreeding depression as having an absolute rather than relative effect on offspring viability (i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
-We also assume that inbreeding always decreases offspring viability, $\beta > 0$ (i.e., no outbreeding depression).
-Therefore, because $k_{ij}$ is constrained to values between zero and one, $-\beta \times k_{ij} \leq 0$.
+We assume that inbreeding always decreases offspring viability (i.e., $\beta > 0$, giving inbreeding depression but no outbreeding depression).
+Therefore, because $0 \leq k_{ij} \leq 1$, $-\beta \times k_{ij} \leq 0$.
 Values of $\Psi_{\textrm{off}}$ must therefore be between zero (if $-\beta \times k_{ij}$ is very negative) and one (if $-\beta \times k_{ij} = 0$).
 We therefore define $\Psi_{\textrm{off}}$ as the probability that an offspring is viable, and sample its realised viability (versus mortality) using a Bernoulli trial.
+Given our current objectives, we simulate evolution under conditions where inbreeding avoidance is adaptive due to strong inbreeding depression, and not evolution where inbreeding preference is adaptive due to weak or zero inbreeding depression \cite[][]{Parker1979, Kokko2006, Duthie2016a}, or given outbreeding depression \cite[][]{Bateson1983, Greeff2009}.
+However, as described above, positive $M_{p}$ and $F_{p}$ values resulting in inbreeding preference are permitted to evolve, and could potentially arise due to mutation or drift.
 
@@
 Immigration therefore prevents the mean kinship within the population from asymptoting to one over generations.
-To ensure that immigrants do not directly affect genotypic or phenotypic values of tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$), immigrants are always male.
-Consequently, they can be chosen as females' mates based on their kinship values of zero but do not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$.
-Further, immigrants $P_{a}$, $M_{a}$, and $F_{a}$ allele values are randomly sampled from normal distributions with means and standard deviations equal to those in the focal population at the time of immigration.
+To ensure that immigrants do not directly affect genotypic or phenotypic values of tendency for polyandry or pre-copulatory or post-copulatory inbreeding avoidance, immigrants are always male.
+Consequently, they can be chosen as females' mates based on their values of $k_{ij}=0$ but do not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$.
+Further, immigrants' $P_{a}$, $M_{a}$, and $F_{a}$ allele values are randomly sampled from normal distributions with means and standard deviations equal to those in the focal population at the time of immigration, meaning that they do not directly cause any change in the distribution of allele values.
 We thereby effectively assume that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$.
@@
 
-To test the hypothesis that evolution of post-copulatory inbreeding avoidance can facilitate evolution of costly polyandry, we compare simulations in which polyandry and pre-copulatory and post-copulatory inbreeding can all evolve, with otherwise identical simulations in which post-copulatory inbreeding strategy cannot evolve given four different costs of polyandry ($c_{P} = \{0, 0.0025, 0.005,  0.01\}$).
-To prevent $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes cause random fertilisation with respect to kinship.
-Hence $F_{a}$ alleles have no phenotypic effect, meaning that polyandrous females cannot enact post-copulatory inbreeding avoidance.
+To address whether or not evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance can facilitate evolution of polyandry, we compare simulations in which polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, with otherwise identical simulations in which post-copulatory inbreeding avoidance cannot evolve given four different costs of polyandry ($c_{P} = \{0, 0.0025, 0.005,  0.01\}$).
+To prevent post-copulatory inbreeding avoidance from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes cause random fertilisation with respect to kinship, so $F_{a}$ alleles have no phenotypic effect.
 
-To test the hypothesis that selection for a costly strategy of inbreeding avoidance will be negligible given a less costly alternative strategy, we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where the cost of pre-copulatory inbreeding strategy $c_{M}=0$ but the cost of post-copulatory inbreeding strategy $c_{F}=0.02$, and vice versa.
-We compare these simulations with evolution of a costly strategy in the absence of evolution of an alternative strategy (e.g., evolution of pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy phenotype is fixed at zero, $F_{p}=0$).
+To address how asymmetric costs associated with pre-copulatory and post-copulatory inbreeding avoidance and polyandry affect the long-term persistence of reproductive strategies, we quantify the change in $M_{a}$ and $F_{a}$ over generations in simulations where pre-copulatory inbreeding strategy was cost free ($c_{M}=0$) but post-copulatory inbreeding strategy was moderately costly ($c_{F}=0.02$), and vice versa.
+We compare evolutionary trajectories with those of a costly strategy in the absence of evolution of an alternative strategy (e.g., evolution of pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy phenotype is fixed at zero, $F_{p}=0$).
+Previous modelling using similar genetic architecture suggests that a cost of $0.02$ imposes strong but not overwhelming direct negative selection on polyandry \cite[][]{Duthie}.
+This value is therefore appropriate to illustrate the different evolutionary consequences that could result from asymmetrical costs.
 
-To test the hypothesis that the existence of adaptive post-copulatory inbreeding avoidance will preclude the invasion of pre-copulatory inbreeding avoidance, or vice versa, we first used exploratory simulations to determine evolution of pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation.
-To test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance was already established, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., meaning that $F_{p}$ and $P_{p}$ did not evolve).
-Similarly, to test whether post-copulatory inbreeding avoidance evolved when pre-copulatory inbreeding avoidance was already established, we initiated $F_{a}$ and $P_{a}$ allele values at zero but fixed $M_{a}$ allele values at $-10$.
+To address how selection on an initially rare strategy of pre-copulatory or post-copulatory inbreeding avoidance, and resulting evolution, is affected by the other strategy of inbreeding avoidance already being fixed in the population, we first used exploratory simulations to quantify evolution of pre-copulatory inbreeding strategy, and of post-copulatory inbreeding strategy and associated polyandry, in isolation.
+Then, to test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance were fixed, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., meaning that $F_{p}$ and $P_{p}$ were expressed did not evolve further).
+Similarly, to test whether post-copulatory inbreeding avoidance would evolve when pre-copulatory inbreeding avoidance was already fixed, we initiated $F_{a}$ and $P_{a}$ allele values at zero but fixed $M_{a}$ allele values at $-10$.
 Consequently, because females have 10 diploid loci, when $M_{a}$ or $F_{a}$ alleles were fixed at $-10$, outbred females were $51$ times less likely to choose a full brother and $13.5$ times times less likely to choose a first cousin than a non-relative in pre-copulatory and post-copulatory choice, respectively.
 
-In all simulations, we record mean values of $P_{a}$, $M_{a}$, $F_{a}$ in each generation.
-Each combination of parameter values simulated is replicated $40$ times, and grand mean values and standard errors of means are calculated in each generation across replicates.
-These analyses allow us to infer how allele values change over generations in response to costs, but also in response to the changing values of other alleles and therefore potentially interacting phenotypes (e.g., selection on post-copulatory inbreeding strategy might be weak if polyandry is rare).
-For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling \cite[][]{Duthie} showed to be a sufficient number of generations for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
+In all simulations, we recorded mean values of $P_{a}$, $M_{a}$, and $F_{a}$ in each generation and present these values over generations to infer selection on phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$).
+Each combination of parameter values simulated was replicated $40$ times, and grand mean values and standard errors of means are calculated in each generation across replicates.
+These analyses allowed us to infer how allele values changed over generations in response to costs, but also in response to the changing values of other alleles and therefore potential evolutionary feedbacks among reproductive strategies.
+For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling \cite[][]{Duthie} showed to be sufficient for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
 For all replicates, we set $\rho=5$ immigrants, which produced a range of kin and non-kin in each generation allowing females to express inbreeding strategies, and $n=8$ offspring, which was sufficient to keep populations consistently at carrying capacities and avoid population extinction.
-Values of $K_{f}$ and $K_{m}$ were both set to 100 because previous modelling has shown that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but populations are also not so small that selection is typically overwhelmed by genetic drift \cite[][]{Duthie2016a}.
+Values of $K_{f}$ and $K_{m}$ were both set to 100 because previous modelling showed that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but not so small that selection is typically overwhelmed by drift \cite[][]{Duthie2016a}.
 

### 2017-04-12 pre_post_biorxiv.tex
Tidy up the Results

@@
 
-When post-copulatory inbreeding avoidance alleles ($F_{a}$) were fixed to zero and $F_{p}$ could not evolve, $P_{a}$ values were always negative (Figure 1A,C,E,G).
-This shows that there is selection against unconditional polyandry even given zero direct cost ($c_{P}=0$; Figure 1A).
-This is because polyandrous females sampled more males from the available population and were consequently likely to mate with some relatives and hence produce some inbred offspring with low viability \cite[][]{Duthie}.
+When post-copulatory inbreeding avoidance alleles ($F_{a}$) had no effect (i.e., $F_{g}$ values were fixed to zero), meaning that $F_{p}$ could not evolve, $P_{a}$ alleles underlying polyandry always decreased to negative values over generations (red lines, Figure 1A,C,E,G).
+This shows that despite strong inbreeding depression in offspring viability, there is selection against unconditional polyandry even given zero direct cost ($c_{P}=0$; Figure 1A).
+This is because $M_{a}$ values became negative over generations, meaning that females typically avoided inbreeding through their initial mating (blue lines, Figure 1A,C,E,G).
+Polyandrous females that subsequently sampled more males from the available population were consequently more likely to mate with some relatives and hence produce some inbred offspring with low viability \cite[][]{Duthie}.
 
-When post-copulatory inbreeding avoidance was allowed to evolve, mean $P_{a}$ values were substantially higher than in comparable simulations where post-copulatory inbreeding avoidance could not evolve (Figure 1B,D,F,H).
-Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry.
-However, $P_{a}$ values were expected to be positive only given a low cost of polyandry ($c_{P} < 0.005$, Figure 1B,D).
-This implies that, even given strong inbreeding depression in offspring viability, inbreeding avoidance might generally be a weak force driving polyandry evolution.
+When post-copulatory inbreeding avoidance was allowed to evolve, mean $P_{a}$ values became substantially higher than in comparable simulations where $F_{a}$ values were fixed to zero and post-copulatory inbreeding avoidance could not evolve (Figure 1B,D,F,H).
+Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry to the degree that most females mated multiply given low costs of polyandry ($c_{P} < 0.005$; e.g., Figure 2A,B).
+Here, $P_{a}$ allele values increased from zero and persisted at low positive values (Figure 1B,D).
+Given higher costs of polyandry ($c_{P} \geq 0.005$), $P_{a}$ allele values still initially increased from zero, but then became slightly negative over generations (Figure 1F,H).
+Trajectories of allele values in individual simulations were typically highly stochastic, but were consistent in their long-term direction (Supporting Information Figures S1-S8).
+Overall, this implies that, even given strong inbreeding depression in offspring viability and simultaneous evolution of pre-copulatory and post-copulatory strategies, inbreeding avoidance might generally be a weak force driving polyandry evolution.
 
-Strong post-copulatory inbreeding avoidance consistently evolved in all simulations where such evolution was allowed (Figure 1B,D,F,H), even when $P_{a}$ values were expected to be slightly negative (i.e., when there is selection against polyandry, Figure 1F,H).
-This reflects the threshold nature of phenotypic expression of polygenic polyandry, wherein random sampling of alleles means that polyandry is commonly expressed (i.e., $P_{g}>0$) even when mean $P_{a}$ values are negative (Figure 2).
-This means that there is commonly opportunity for expression of post-copulatory inbreeding avoidance and associated selection that drives evolution of $F_{a}$ allele values.
+Strong post-copulatory inbreeding avoidance, manifested as very negative $F_{a}$ values, consistently evolved in all simulations where such evolution was allowed (black lines, Figure 1B,D,F,H).
+Evolution of post-copulatory inbreeding avoidance occurred even when $P_{a}$ values were expected to be slightly negative, and hence when there was selection against polyandry (Figure 1F,H).
+This reflects the threshold nature of phenotypic expression of polygenic polyandry, wherein random sampling of alleles means that polyandry is expressed by some females (i.e., $P_{g}>0$) even when mean $P_{a}$ values are negative (Figure 2).
+This means that, even in populations where female reproductive strategy evolves toward monandry, there is still commonly some opportunity for expression of post-copulatory inbreeding avoidance and associated selection that drives evolution of post-copulatory inbreeding avoidance.
 
-Strong pre-copulatory inbreeding avoidance also evolved (i.e., $M_{a}<0$) in all simulations, irrespective of $c_{P}$ and irrespective of whether post-copulatory inbreeding avoidance was allowed to evolve (Figure 1).
+Strong pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}<0$) in all simulations, irrespective of $c_{P}$ and irrespective of whether post-copulatory inbreeding avoidance was allowed to evolve or hence whether polyandry evolved (Figure 1).
+This might be expected given strong inbreeding depression in offspring viability, which imposes selection against inbreeding.
 
@@
 {%
-   \includegraphics[height=18cm]{figures/poly_costs.pdf}%
+   \includegraphics[height=18cm]{figures/poly_costs.png}%
 }%
 {%
-   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{10 mm} \textbf{Figure 1:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fixed to zero (i.e., random fertilisation) or (B, D, F, H) allowed to evolve freely.
-Costs of polyandry ($c_{p}$) increase across rows from zero (A and B) to 0.01 (G and H).
+   \captionof{figures/poly_costs.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 1:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fixed to zero (i.e., random fertilisation) or (B, D, F, and H) allowed to evolve freely.
+Costs of polyandry ($c_p$) increase across rows from zero (A and B) to 0.01 (G and H).
 Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
@@
 {%
-   \includegraphics[height=10.25cm]{figures/Pp_vals.pdf}%
+   \includegraphics[height=10.25cm]{figures/Pp_vals.png}%
 }%
 {%
-   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs.
+   \captionof{figures/Pp_vals.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs.
 Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations.
@@
 Nevertheless, due to the threshold nature of expression of the polygenic polyandry phenotype, polyandry and monandry are expressed in both populations.
-Histograms in (B) and (D) show females' tendency for polyandry phenotypes in the final generation; white and grey shading indicates monandrous and polyandrous females, respectively.\end{justify}{\t}%
+Histograms in (B) and (D) show females' tendency for polyandry phenotypes in the final generation; white and grey shading indicates monandrous and polyandrous females, respectively.
+Arrows and numbers indicate mean phenotype values.
+Because each trait includes 10 diploid loci with additive effects, phenotype values are ca 20 times allele values.
+\end{justify}{\t}%
 }[t]
@@
 
-\subsection*{Is evolution of one costly inbreeding strategy inhibited by another non-costly alternative strategy?}
+\subsection*{How do cost asymmetries affect long-term persistence of reproductive strategies?}
 
-When either pre-copulatory or post-copulatory inbreeding strategy allele values were fixed to zero, the alternative inbreeding strategy evolved to inbreeding avoidance even when costly (Figure 3A,C).
-However, when one inbreeding strategy could evolve and had zero cost, the other strategy initially evolved towards inbreeding avoidance but then back towards random choice across generations following increasing evolution of inbreeding avoidance (i.e., negative allele values) through the former (zero cost) strategy (Figure 3B,D).
-For example, given fixed $F_{a}=0$, grand mean $M_{a}$ value in the last $10000$ generations was $-0.868$ (Figure 3A), meaning that a female was ca $5.34$ times less likely to choose a full-sibling and ca $2.10$ times less likely to mate with a first cousin than a non-relative given a high cost of pre-copulatory inbreeding avoidance, $c_{M}=0.02$.
-However, when $F_{a}$ allele values could also evolve, grand mean $M_{a}$ allele value in the last $10000$ generations was only $-0.288$ (Figure 3B).
-Further, given fixed $M_{a}=0$, grand mean $F_{a}$ value in the last $10000$ generations was $-1.092$ (Figure 3C), meaning that a female was ca $6.46$ times less likely to choose a full-sibling and ca $2.37$ times less likely to choose a first cousin than a non-relative given a high cost of pre-copulatory inbreeding avoidance, $c_{F}=0.02$.
-However, when $M_{a}$ values could also evolve and $P_{a}$ values were negative, grand mean $F_{a}$ value in the last $10000$ generations was only $-0.070$ (Figure 3D).
-Evolution of post-copulatory inbreeding avoidance facilitated evolution of polyandry (Figure 3B,C), while monandry evolved in the absence of post-copulatory inbreeding avoidance (Figure 3A,D; polyandry was cost free in all these simulations).
-Overall, evolution of a costly inbreeding strategy that readily evolved in isolation was greatly impeded by evolution of a less costly strategy.
+When post-copulatory inbreeding avoidance allele values ($F_{a}$) were fixed to zero, pre-copulatory inbreeding avoidance evolved even when costly (Figure 3A).
+Likewise, when pre-copulatory inbreeding avoidance allele values ($M_{a}$) were fixed to zero, costly post-copulatory inbreeding avoidance evolved (Figure 3C).
+Females therefore evolved to avoid inbreeding, and thereby avoid the cost of producing inbred offspring, through whichever route was available.
+
+However, when both pre-copulatory and post-copulatory inbreeding avoidance could evolve, their relative evolutionary dynamics depended on their relative costs.
+When pre-copulatory but not post-copulatory inbreeding avoidance was costly ($c_{M}=0.02$ and $c_{F}=0$), pre-copulatory inbreeding avoidance initially evolved (i.e., negative $M_{a}$) but then evolved back towards random mating (i.e., $M_{a}=0$) following increasing evolution of post-copulatory inbreeding avoidance (Figure 3B).
+Similarly, when post-copulatory but not pre-copulatory inbreeding avoidance was costly ($c_{F}=0.02$ and $c_{M}=0$), post-copulatory inbreeding avoidance initially evolved ($F_{a}=0$) before evolving back to random fertilisation after ca $20000$ generations (Figure 3D).
+
+When pre-copulatory inbreeding avoidance was costly, allowing evolution of cost free post-copulatory inbreeding avoidance greatly facilitated evolution of polyandry (Figure 3A versus 3B).
+However when post-copulatory inbreeding avoidance was costly, allowing evolution of cost free pre-copulatory inbreeding avoidance caused $P_{a}$ alleles to decrease to very negative values, reducing expression of polyandry (Figure 3C versus 3D; polyandry was cost free in all these simulations).
+Results for all possible cost combinations of $0$ and $0.02$ are provided in Supporting Information (Figure S9).
 
@@
 {%
-   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 3:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy can evolve and pre-copulatory inbreeding strategy is (A) fixed for random mating or (B) can also evolve.
+   \captionof{figures/rel_costs.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 3:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve.
 Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.\end{justify}{\t}%
+Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.
+In all panels, polyandry is cost free.
+\end{justify}{\t}%
 }
 {%
-   \includegraphics[height=14cm]{figures/rel_costs.pdf}%
+   \includegraphics[height=14cm]{figures/rel_costs.png}%
 }%
@@
 
-\subsection*{Will selection for a costly inbreeding strategy be negligible given existence of an already adaptive alternative strategy?}
+\subsection*{How do evolution of pre-copulatory and post-copulatory inbreeding avoidance affect one another?}
 
-When polyandry and post-copulatory inbreeding strategy allele values were fixed for adaptive inbreeding avoidance, pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}$ values became increasingly negative; Figure 4A).
+When polyandry alleles ($P_{a}$) were fixed to be positive so that all females were expected to mate multiply and post-copulatory inbreeding allele ($F_{a}$) values were fixed for adaptive inbreeding avoidance, pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}$ values became increasingly negative; Figure 4A).
 Such evolution still occurred, but to a much smaller degree, when pre-copulatory inbreeding avoidance was costly (Figure 4B).
-However, after $40000$ generations, $M_{a}$ values were less negative when post-copulatory inbreeding avoidance and polyandry were fixed at non-zero values than when they also evolved from initial values of zero (e.g., compare the blue lines in Figures 4A versus Figure 1A).
+However, after $40000$ generations, $M_{a}$ values were less negative when post-copulatory inbreeding avoidance and polyandry were fixed at non-zero values than when they also evolved from initial values of zero ($-15.45$ vs.
+$-17.62$; compare the blue lines in Figures 4A versus Figure 1B).
+This shows that fixation of post-copulatory inbreeding avoidance weakens selection for pre-copulatory inbreeding avoidance.
 
-When pre-copulatory inbreeding strategy values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently trend toward negative values (Figure 4C,D).
-Additionally, mean $P_{a}$ allele values consistently decreased over generations regardless of the cost of post-copulatory inbreeding strategy (Figure 4C,D).
+Conversely, when pre-copulatory inbreeding allele ($M_{a}$) values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently become negative over generations (Figure 4C,D).
+Fixation of pre-copulatory inbreeding avoidance therefore prevented evolution of post-copulatory inbreeding avoidance.
+However, in this case, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
 Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values among replicates (illustrated by wide standard errors, Figure 4C).
 However, when $c_{F}=0.02$, $F_{a}$ values remained near zero to minimise direct costs.
-This lack of evolution of post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
-When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information).
+This lack of selection for post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
+When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information Figure S10).
 
@@
 {%
-   \captionof{figures/fixed_adapt.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is (A and C) cost-free or (B and D) costly.
+   \captionof{figures/fixed_adapt.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is cost-free (A, $c_{M} = 0$; C, $c_{F} = 0$) or costly (B, $c_{M}=0.02$; D, $c_{F}=0.02$).
 Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
-Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry.\end{justify}{\t}%
+Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.
+\end{justify}{\t}%
 }
 {%
-   \includegraphics[height=14cm]{figures/fixed_adapt.pdf}%
+   \includegraphics[height=14cm]{figures/fixed_adapt.png}%
 }%

### 2017-04-12 pre_post_biorxiv.tex
Typesetting of figures needs to be fixed

@@
 
+{\color{Gray}
+    \begin{adjustwidth}{-2.2in}{0in}
+    \mysidecaption{0.32}
+{ 
+        \begin{justify}
+        \vspace{-0.25 mm}
+        \captionof{figures/poly_costs.pdf}
+        {\bf Figure 1:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fixed to zero (i.e., random fertilisation) or (B, D, F, and H) allowed to evolve freely.
+Costs of polyandry ($c_p$) increase across rows from zero (A and B) to 0.01 (G and H).
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values indicate inbreeding avoidance or tendency for monandry, and positive values indicate inbreeding preference or tendency for polyandry.
+Dotted lines demarcate mean allele values of zero.
+    \end{justify}{\t}
+}[t]
+{
+   \includegraphics[height=18cm]{figures/poly_costs.pdf}%
+}
+    \end{adjustwidth}
+}
+
 Strong post-copulatory inbreeding avoidance, manifested as very negative $F_{a}$ values, consistently evolved in all simulations where such evolution was allowed (black lines, Figure 1B,D,F,H).
@@
 
- {\color{Gray}
-\begin{adjustwidth}{-2.2in}{0in}
-\mysidecaption{0.68}
-{%
-   \includegraphics[height=18cm]{figures/poly_costs.png}%
-}%
-{%
-   \captionof{figures/poly_costs.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 1:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fixed to zero (i.e., random fertilisation) or (B, D, F, and H) allowed to evolve freely.
-Costs of polyandry ($c_p$) increase across rows from zero (A and B) to 0.01 (G and H).
-Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
-Negative mean allele values indicate inbreeding avoidance or tendency for monandry, and positive values indicate inbreeding preference or tendency for polyandry.
-Dotted lines demarcate mean allele values of zero.
-\end{justify}{\t}%
-}[t]
-\end{adjustwidth}
-}
-
-{\color{Gray}
-\begin{adjustwidth}{-2.2in}{0in}
-\mysidecaption{0.68}
-{%
-   \includegraphics[height=10.25cm]{figures/Pp_vals.png}%
-}%
-{%
-   \captionof{figures/Pp_vals.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs.
+%{\color{Gray}
+%\begin{adjustwidth}{-2.2in}{0in}
+%\mysidecaption{0.68}
+%{%
+%   \includegraphics[height=10.25cm]{figures/Pp_vals.png}%
+%}%
+%{%
+%   \captionof{figures/Pp_vals.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs.
 Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations.
@@
 \end{justify}{\t}%
-}[t]
-\end{adjustwidth}
-}
+%}[t]
+%\end{adjustwidth}
+%}
 
@@
 
-{\color{Gray}
-\begin{adjustwidth}{-2.2in}{0in}
-\mysidecaption{0.31}
-{%
-   \captionof{figures/rel_costs.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 3:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve.
+%{\color{Gray}
+%\begin{adjustwidth}{-2.2in}{0in}
+%\mysidecaption{0.31}
+%{%
+%   \captionof{figures/rel_costs.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 3:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve.
 Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
@@
 \end{justify}{\t}%
-}
-{%
-   \includegraphics[height=14cm]{figures/rel_costs.png}%
-}%
-[t]
-\end{adjustwidth}
-}
+%}
+%{%
+%   \includegraphics[height=14cm]{figures/rel_costs.png}%
+%}%
+%[t]
+%\end{adjustwidth}
+%}
 
@@
 
-{\color{Gray}
-\begin{adjustwidth}{-2.2in}{0in}
-\mysidecaption{0.31}
-{%
-   \captionof{figures/fixed_adapt.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is cost-free (A, $c_{M} = 0$; C, $c_{F} = 0$) or costly (B, $c_{M}=0.02$; D, $c_{F}=0.02$).
+%{\color{Gray}
+%\begin{adjustwidth}{-2.2in}{0in}
+%\mysidecaption{0.31}
+%{%
+%   \captionof{figures/fixed_adapt.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is cost-free (A, $c_{M} = 0$; C, $c_{F} = 0$) or costly (B, $c_{M}=0.02$; D, $c_{F}=0.02$).
 Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
@@
 \end{justify}{\t}%
-}
-{%
-   \includegraphics[height=14cm]{figures/fixed_adapt.png}%
-}%
-[t]
-\end{adjustwidth}
-}
+%}
+%{%
+%   \includegraphics[height=14cm]{figures/fixed_adapt.png}%
+%}%
+%[t]
+%\end{adjustwidth}
+%}
 
@@
 
-We have used \textit{in silico} experiments to test three key hypotheses concerning evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
-The modelling that we develop provides a novel framework for approaching empirical studies of inbreeding avoidance, using simulations to address relevant knowledge gaps in understanding evolution of polyandry and inbreeding avoidance through pre-copulatory and post-copulatory mechanisms.
-Accordingly, we modelled evolution of three separate traits affecting polyandry and inbreeding avoidance, including tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
+Evolution of different reproductive strategies cannot be presumed to occur in isolation from each other in real-world populations.
+Rather, such evolution is likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundance) among phenotypes under selection.
+For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently drive selection for polyandry \cite[e.g., ][]{Zeh1997, Jennions2000, Tregenza2002}.
+Evolution of inbreeding avoidance can be driven by selection on both pre-copulatory and post-copulatory mechanisms, so simultaneous evolution of each phenotype is likely to be defined by degeneracy, in addition to any direct costs on phenotypes.
+We used individual-based modelling to explore evolution of pre-copulatory and post-copulatory inbreeding strategy and polyandry given (1) hard constraints on evolution of post-copulatory inbreeding strategy, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding strategy, and (3) evolution of one inbreeding strategy phenotype given the pre-existence of the other.
+We thereby highlight fundamental but theoretically under-developed relationships between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding strategy.
+We present our model and simulation results as a tool for thinking more clearly about the dynamics of simultaneously evolving reproductive strategies, not for making accurate quantitative predictions for any specific system.
+While the logic of our model can be usefully applied to constructing hypotheses within and across empirical systems, accurate quantitative prediction would require additional detail and the incorporation of empirical data for model parameterisation.
 
-\subsection*{Evolution of polyandry is facilitated by post-copulatory inbreeding avoidance}
+\subsection*{Evolution of polyandry}
 
-The opportunity to adjust inbreeding has been widely considered as a driver of adaptive evolution of polyandry \cite[][]{Tregenza2002, Foerster2003, Akcay2007, Varian-Ramos2012, Kingma2013, Lehtonen2015, Reid2014}.
-Recently, \cite{Duthie} found that the conditions under which selection for polyandry and pre-copulatory inbreeding avoidance is predicted are highly restrictive.
-However, \cite{Duthie} assumed that fertilisation of offspring was unbiased with respect to mate kinship, meaning that females could not express post-copulatory choice.
-In contrast, we found that when post-copulatory inbreeding avoidance could evolve, selection for polyandry was greatly strengthened (Figure 1).
-The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new \cite[e.g.,][]{Zeh1997}, but the existence of selection for post-copulatory inbreeding avoidance causing feedback to select for polyandry has not been formally modelled.
-Our model therefore has widespread implications for future studies of evolution of polyandry.
+The opportunity to adjust inbreeding has been widely suggested to be a driver of adaptive evolution of polyandry \cite[][]{Tregenza2002, Foerster2003, Akcay2007, Varian-Ramos2012, Kingma2013, Lehtonen2015, Reid2014}.
+We found that when post-copulatory inbreeding avoidance could evolve, selection for and resulting evolution of polyandry was greatly strengthened (Figure 1).
+The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new \cite[e.g.,][]{Zeh1997}, but our model clarifies this verbal hypothesis and therefore has widespread implications for future studies of evolution of polyandry.
 
-We predict evolution of polyandry in populations where inbreeding depression is severe and evolution of inbreeding avoidance through post-copulatory mechanisms is not constrained.
+We predict evolution of polyandry in populations where inbreeding depression is severe and inbreeding avoidance through post-copulatory mechanisms can also evolve, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
 Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa \cite[e.g.,][]{Pizzari2004, Firman2008, Bretman2009, Gasparini2011, Tuni2013, Firman2015}.
-For example, the number of sperm arriving to eggs is lower for full siblings of female red jungefowl (\textit{Gallus gallus}) than it is for non-relatives, even after controlling for effects of order of oviposition and social familiarity \cite[][]{Pizzari2004}.
-Similarly, in house mice, fertilisation was biased toward unrelated males independent of mating order, perhaps due to post-copulatory mechanisms expressed through the secretion of gametic proteins originating in eggs \cite[][]{Firman2008, Firman2015}.
-Interestingly, female house mice also show pre-copulatory inbreeding avoidance  \cite[][]{Potts1991, Roberts2003}.
-Our results suggest that post-copulatory inbreeding avoidance is unlikely to evolve when females can already avoid inbreeding through pre-copulatory mechanisms (Figure 4), meaning that evolution of post-copulatory inbreeding avoidance could reasonably be hypothesised to have preceded evolution of pre-copulatory inbreeding avoidance in mice.
-
 Recent studies have shown how females can successfully bias fertilisation after mating has occurred.
@@
 In black field crickets (\textit{Teleogryllus commodus}), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs \cite[][]{Bussiere2006, Tuni2013}.
-Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for further polyandry, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
 
-\subsection*{Evolution of a costly inbreeding strategy is inhibited by a non-costly alternative strategy}
+\subsection*{Interaction of polyandry and inbreeding avoidance strategies}
 
-In our model, one cost free inbreeding strategy precluded another more costly inbreeding strategy from persisting in a focal population (Figure 3), meaning that long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given cost asymmetry.
-Direct costs therefore strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies.
-Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging \cite[][]{Pomiankowski1987, Kokko2003, Reid2015}.
-\cite{Pomiankowski1987} categorised four types of costs that are relevant to mate choice, which we suggest are also relevant costs for polyandry, and include costs of elevated risks associated with (1) predation or (2) disease transmission, and costs incurred through (3) loss of time or (4) depletion of energy.
-In our model, we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates \cite[e.g.,][]{Rowe1988, Rowe1994}, a cost of pre-copulatory inbreeding strategy as a lost of time \cite[i.e., risk of not finding a mate in time due to choosiness; e.g.,][]{Kokko2013}, and a cost of post-copulatory inbreeding strategy as depletion of energy.
-While these costs are biologically realistic, different costs will be relevant for different populations and be realised in different ways.
-For example, increased risk of disease transmission has been observed for highly polyandrous females \cite[][]{Roberts2015a}, but such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry.
-Future studies will therefore need to carefully consider the magnitudes and realisation of direct costs to accurately predict evolution of inbreeding strategies in populations.
-
-Another type of cost relevant for polyandry and inbreeding strategy is risk of male harm caused by sexual conflict \cite[e.g.,][]{Arnqvist2005a, Parker2006}.
+Evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but was affected by the joint evolution of polyandry and the existence of asymmetric costs.
+One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population by modifying its effect on inbreeding avoidance (Figure 3).
+Consequently, long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given sufficient cost asymmetry.
+Since direct costs strongly affected the evolution of the focal phenotype(s), quantifying costs is necessary for predicting evolution of inbreeding strategies.
+Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging \cite[][]{Pomiankowski1987, Kokko2003}.
+\cite{Pomiankowski1987} categorised four types of costs that are relevant to mate choice, which are also relevant for polyandry, and include costs of elevated risks of predation or disease transmission, and costs incurred through time or energy expenditure.
+Another relevant cost is risk of male harm caused by sexual conflict \cite[e.g.,][]{Arnqvist2005a, Parker2006}.
 We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should benefit from a higher tolerance of inbreeding than females, leading to sexual conflict over inbreeding \cite[][]{Parker1979, Parker2006, Kokko2006, Duthie2015a}.
-Females that express the choice to avoid inbreeding when mating might therefore pay a cost of harm caused by coercion expressed by related males.
-This cost might itself evolve over time as male harm coevolves with female resistance \cite[][]{Ronn2007, Perry2011, Wang2015a}, and costs might vary with interactions among male non-relatives and relatives because effects of kin selection are predicted to reduce harm caused by related male suitors \cite[][]{Rankin2011a}.
-To predict evolution of polyandry and inbreeding strategy in populations characterised by active males and sexual conflict, consideration of male inbreeding strategy and coevolution between male harm and female resistance might therefore need to be considered explicitly.
-
-\subsection*{Evolution of post-copulatory inbreeding avoidance is precluded by existing pre-copulatory inbreeding avoidance, but not vice versa}
+Here we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates \cite[e.g.,][]{Rowe1988, Rowe1994}, a cost of pre-copulatory inbreeding strategy as a lost of time \cite[i.e., risk of not finding a mate in time due to choosiness; e.g.,][]{Kokko2013}, and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy.
+While these costs reflect empirical observations in some populations and are therefore biologically realistic, other types of costs have also been observed and could be considered in future models tailored to specific systems.
+For example, increased risk of disease transmission has been observed for highly polyandrous females \cite[][]{Roberts2015a}, and such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry.
+Different types of costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
+Evolution of individual phenotypes therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.
 
@@
 In wild populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
-Rather, for example, initial evolution of pre-copulatory inbreeding avoidance is much more likely to evolve in the absence of evolving post-copulatory inbreeding avoidance due to constraints, or in the presence of already evolved post-copulatory inbreeding avoidance.
+Rather, the timing of the invasion of adaptive inbreeding avoidance phenotypes will differ, so the initial evolution of one inbreeding strategy will likely occur in the absence of the other, or where selection for and subsequent evolution of the other strategy has already occurred.
 When framing hypotheses for existence of post-copulatory inbreeding avoidance and polyandry, it might therefore be necessary to consider whether or not inbreeding avoidance already occurs through pre-copulatory mate choice.
-Additionally, the opportunity for post-copulatory inbreeding avoidance will also naturally depend on the degree to which females are polyandrous.
-For species in which pre-copulatory inbreeding avoidance occurs and monandry is common, evolution of post-copulatory inbreeding avoidance is especially unlikely.
-For example, females of the gregarious cockroach \textit{Blatella germanica} (L.) avoid inbreeding and are typically monandrous \cite[][]{Lihoreau2007}; while occurrence of post-copulatory inbreeding avoidance in \textit{B.
-germanica} has not, to our knowledge, been tested, we predict that such inbreeding avoidance is highly unlikely.
-Similarly, females of the solitary parasitoid wasp \textit{Venturia canescens} are monandrous, and appear to avoid mating with siblings \cite[][]{Metzger2010, Metzger2010a}.
-We hypothesise that post-copulatory inbreeding avoidance in \textit{V.
-canescens} would be highly unlikely to evolve.
+Additionally, the opportunity for post-copulatory inbreeding avoidance will also depend on the degree to which females are polyandrous.
+For species in which pre-copulatory inbreeding avoidance occurs and polyandry is uncommon \cite[][]{Lihoreau2007, Metzger2010, Metzger2010a}, evolution of post-copulatory inbreeding avoidance is highly unlikely even if such a strategy incurs little direct cost.
 
-\subsection*{General predictions}
+\subsection*{General predictions concerning inbreeding avoidance and polyandry}
 
-Some broad predictions are possible given the verbal theory that we have developed and the populations that we have simulated.
-For example, given that post-copulatory inbreeding avoidance is useless for monandrous females and most effective for polyandrous females, while pre-copulatory inbreeding avoidance is perhaps most effective for monandrous females and less effective for polyandrous females, it would be interesting to test whether or not occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with degree of polyandry.
-In addition to polyandry making post-copulatory inbreeding avoidance relevant, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself.
-Hence, well-grounded biological hypotheses might be derived for the relationship between female multiple mating and mode of inbreeding avoidance.
-To test such hypotheses, more work is needed to identify the degree to which females of different species engage in polyandrous and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
+Post-copulatory inbreeding avoidance cannot be realised if females are not polyandrous, and is most effective for highly polyandrous females that can choose amongst multiple mates and therefore bias fertilisation accordingly.
+In contrast, pre-copulatory inbreeding avoidance mechanisms are most critical for females that mate only once and therefore have no post-copulatory opportunity to avoiding inbreeding.
+This theory is borne out in our simulation results, as selection for, and consequent evolution of, post-copulatory inbreeding avoidance was negligible in populations where polyandry did not evolve, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D).
+Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information Figure S9).
+In addition to polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).
+It would therefore be interesting to test the hypothesis that, across taxa, occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with the degree of polyandry.
+To test this hypothesis, more work is needed to quantify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
+
+Degeneracy occurs at nearly all biological scales \cite[][]{Edelman2001}, including complex systems affecting organismal development \cite[e.g.,][]{Nowak1997}, adaptation \cite[][]{Whitacre2010, Whitacre2010a}, and cognition \cite[][]{Price2002, Park2013}, as well as population \cite[][]{Atamas2009}, community \cite[][]{Suraci2017}, and ecosystem \cite[e.g.,][]{Levin2008} dynamics.
+In our model, degeneracy occurred through overlaps in how different reproductive strategies caused adaptive inbreeding avoidance.
+In general, degeneracy might increase biological robustness by fine-tuning degenerate phenotypes to different local environments \cite[][]{Gardner2006, Whitacre2010a}.
+For example, degeneracy might ensure successful inbreeding avoidance through either pre-copulatory or post-copulatory mechanisms when avoidance through the other mechanism is ineffective (e.g., due to sexual conflict affecting mate choice or injury affecting fertilisation).
+However, evolution of one inbreeding avoidance mechanism might also weaken selection on the other by modifying the latter's impact on total realised inbreeding avoidance \cite[\textit{sensu} evolution of genetic redundancy; see][]{Nowak1997}.
+The relevance of degeneracy with respect to such reproductive strategies therefore requires further theoretical development, which could result in new empirical predictions and conceptual synthesis across biological scales.
 
@@
 
-This work was funded by a European Research Council Starting Grant to JMR.
+This work was funded by a European Research Council Starting Grant to JMR. Computer simulations were performed using the Maxwell Computing Cluster at the University of Aberdeen.
 

### 2017-04-13 pre_post.tex
Add for-submission TEX file

--- 2017-04-12 pre_post_biorxiv.tex
@@
-\documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in,marginparwidth=2in]{geometry}
+\documentclass[12pt]{article}
+\usepackage[top=1.25in, bottom=1in, left=1.25in, right=1in]{geometry}
 \usepackage{amssymb}
@@
 \usepackage{rotating}
+\usepackage{graphicx}
 \usepackage{multirow}
+\usepackage{lineno}
 \usepackage{datetime}
@@
 \usepackage{float}
+\usepackage{fancyhdr}
 \usepackage[font=small,labelfont=bf]{caption}
@@
 \usepackage{wasysym}
-\usepackage{sidecap}
-%\usepackage{caption}
-\usepackage{xargs,caption,changepage,ifthen}
-\usepackage[demo]{graphicx}
+\usepackage{lipsum}
+\floatstyle{plain}
+\restylefloat{figure}
 
-% use Unicode characters - try changing the option if you run into troubles with special characters (e.g. umlauts)
-\usepackage[utf8]{inputenc}
+\renewbibmacro*{name:andothers}{% Based on name:andothers from biblatex.def
+  \ifboolexpr{
+    test {\ifnumequal{\value{listcount}}{\value{liststop}}}
+    and
+    test \ifmorenames
+  }
+    {\ifnumgreater{\value{liststop}}{1}
+       {\finalandcomma}
+       {}%
+     \andothersdelim\bibstring[\emph]{andothers}}
+    {}}
 
-% clean citations
-%\usepackage{cite}
+\title{Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry}
 
-% hyperref makes references clicky. use \url{www.example.com} or \href{www.example.com}{description} to add a clicky url
-\usepackage{nameref,hyperref}
-\hypersetup{
-     colorlinks   = true,
-     citecolor    = blue,
-     linkcolor    = black
-}
+\date{}
 
-% line numbers
-\usepackage[right]{lineno}
+\begin{document}
+\maketitle
 
-% improves typesetting in LaTeX
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
+\begin{center}
+\vspace{5 mm}
 
-% text layout - change as needed
-%\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in 
-\textheight 8.75in
+%\noindent {\bf A. Bradley Duthie\textsuperscript{1,*}, Aline M. Lee\textsuperscript{1}, and Jane M. Reid\textsuperscript{1}}
 
-% Remove % for double line spacing
-%\usepackage{setspace} 
-%\doublespacing
+\vspace{5 mm}
 
-% use adjustwidth environment to exceed text width (see examples in text)
-\usepackage{changepage}
+%\noindent{\footnotesize \textsuperscript{1} Institute of Biological and Environmental Sciences, School of Biological Sciences, Zoology Building, Tillydrone Avenue, University of Aberdeen, Aberdeen AB24 2TZ, United Kingdom \textsuperscript{*} E-mail: aduthie@abdn.ac.uk}
 
-% adjust caption style
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,singlelinecheck=off]{caption}
+\vspace{15 mm}
 
-% remove brackets from references
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
+\noindent Submitted to the \emph{Journal of Evolutionary Biology}
 
-% headrule, footrule and page numbers
-\usepackage{lastpage,fancyhdr,graphicx}
-\usepackage{epstopdf}
-\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
+\vspace{15 mm}
 
-% use \textcolor{color}{text} for colored text (e.g. highlight to-do areas)
-\usepackage{color}
+\noindent Manuscript elements: Table 1, Figure 1, Figure 2, Figure 3, Figure 4, Supporting Information S1
 
-% define custom colors (this one is for figure captions)
-\definecolor{Gray}{gray}{.25}
+\vspace{15 mm}
 
-% this is required to include graphics
-\usepackage{graphicx}
+\noindent \textbf{Key Words:} Inbreeding, inbreeding avoidance, inbreeding depression, mate choice, relatedness, reproductive strategy
+\newline
 
-% use if you want to put caption to the side of the figure - see example in text
-\usepackage{sidecap}
+\end{center}
 
-% use for have text wrap around figures
-\usepackage{wrapfig}
-\usepackage[pscoord]{eso-pic}
-\usepackage[fulladjust]{marginnote}
-\reversemarginpar
+\linenumbers
+\modulolinenumbers[2]
+\doublespacing
 
-%----------------------------------------
-%COMMAND FOR DOING SIDE CAPTION.
-%----------------------------------------
-\newcommandx{\mycaptionminipage}[3][3=c,usedefault]{%
-    \begin{minipage}[#3]{#1}%
-        \ifthenelse{\equal{#3}{b}}{\captionsetup{aboveskip=0pt}}{}
-        \ifthenelse{\equal{#3}{t}}{\captionsetup{belowskip=0pt}}{}
-        \vspace{0pt}\centering\captionsetup{width=\textwidth} %Temporarily set caption width
-        #2%
-    \end{minipage}%
-}%
-\newcommandx{\mysidecaption}[4][4=c,usedefault]{%
-    \checkoddpage%
-    \ifoddpage%
-        %CASE ODD PAGES
-        \mycaptionminipage{\dimexpr\linewidth-#1\linewidth-\intextsep\relax}{#3}[#4]%
-        \hfill%
-        \mycaptionminipage{#1\linewidth}{#2}[#4]%
-    \else%
-        %CASE EVEN PAGES
-        \mycaptionminipage{#1\linewidth}{#2}[#4]%
-        \hfill%
-        \mycaptionminipage{\dimexpr\linewidth-#1\linewidth-\intextsep\relax}{#3}[#4]%
-    \fi%
-}%
-
-% document begins here
-\begin{document}
-\vspace*{0.35in}
-
-% title goes here:
-\begin{flushleft}
-{\LARGE
-\textbf\newline{Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry}
-}
-\newline
-% authors go here:
-\\
-A. Bradley Duthie\textsuperscript{1,*},
-Greta Bocedi\textsuperscript{1},
-Ryan R. Germain\textsuperscript{1},
-Matthew E. Wolak\textsuperscript{1},
-Jane M. Reid\textsuperscript{1}
-\\
-\bigskip
-\bf{1} Institute of Biological and Environmental Sciences, School of Biological Sciences, Zoology Building, Tillydrone Avenue, University of Aberdeen, Aberdeen AB24 2TZ, United Kingdom
-%\\
-%\bf{2} Affiliation B
-\\
-\bigskip
-*  alexander.duthie@stir.ac.uk, brad.duthie@gmail.com
-
-\end{flushleft}
+\clearpage
 
 \section*{Abstract}
-\marginpar{
-\vspace{0.0cm} % adjust vertical position relative to text with \vspace{} - note that you can enter negative numbers to move margin caption up
-\color{Gray} % this gives caption a grey color to set it apart from text body
-\textbf{Key words:} % note that \ref{fig1} refers to the corresponding wrapfigure
-Inbreeding, inbreeding avoidance, inbreeding depression, mate choice, relatedness, reproductive strategy
-}
+
 Inbreeding depression is widely hypothesised to drive adaptive evolution of pre-copulatory and post-copulatory mechanisms of inbreeding avoidance, which in turn are hypothesised to affect evolution of polyandry (i.e., female multiple mating).
@@
 Meanwhile, \cite{Liu2014} found evidence of pre-copulatory but not post-copulatory inbreeding avoidance within a single study of cabbage beetles (\textit{Colaphellus bowringi}).
-However, \cite{Ala-Honkola2011} and \cite{Tan2012} found no evidence for pre-copulatory or post-copulatory inbreeding avoidance in fruit flies (\textit{Drosophila melanogaster}), respectively, and Reid et al.
-\citeyearpar{Reid2014, Reid2015} found no net inbreeding avoidance in song sparrows (\textit{Melospiza melodia}) despite strong inbreeding depression.
+However, \cite{Ala-Honkola2011} and \cite{Tan2012} found no evidence for pre-copulatory or post-copulatory inbreeding avoidance in fruit flies (\textit{Drosophila melanogaster}), respectively, and Reid \textit{et al.} \citeyearpar{Reid2014, Reid2015} found no net inbreeding avoidance in song sparrows (\textit{Melospiza melodia}) despite strong inbreeding depression.
 Taken together, these studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature alongside polyandry.
@@
 Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
-
-\vspace{5 mm}
-
-\begin{table}[!ht]
-\captionsetup{margin={-1.75in,0.1in}}
-\begin{adjustwidth}{-1.75in}{0in}
-%\centering
-\caption{\color{Gray}Individual traits (A), model parameter values (B), and model variables (C) for an individual-based model of the evolution of polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.}
-\begin{tabular}{lllll}
-\hline
-A & Trait & Allele & Genotype & Phenotype &
-\hline
-  & Tendency for polyandry               &   $P_{a}$  &  $P_{g}$  &  $P_{p}$  &
-  & Pre-copulatory inbreeding strategy   &   $M_{a}$  &  $M_{g}$  &  $M_{p}$  &
-  & Post-copulatory inbreeding strategy  &   $F_{a}$  &  $F_{g}$  &  $F_{p}$  &
-  &                                      &            &           &           &
-\hline
-B & Description & Parameter & & Default value(s) &
-\hline
-
-  & Cost of tendency for polyandry                & $c_{P}$    & & $0$, $0.02$   &
-  & Cost of pre-copulatory inbreeding strategy    & $c_{M}$    & & $0$, $0.02$   &
-  & Cost of post-copulatory inbreeding strategy   & $c_{F}$    & & $0$, $0.02$   &
-  & Focal female's number of offspring            & $n$        & & $8$           &
-  & Log-linear slope of inbreeding depression     & $\beta$    & & $3$           &
-  & Adult male immigrants per generation          & $\rho$     & & $5$           & 
-  & Female carrying capacity                      & $K_{f}$    & & $100$         &
-  & Male carrying capacity                        & $K_{m}$    & & $100$         &
-  & Mutation rate of alleles                      & $\mu$      & & $0.001$       &
-  & Standard deviation of mutation effect size    & $\mu_{SD}$ & & $\sqrt{1/20}$ &
-  &                                               &            & &               &
-\hline
-C & Description & & & Variable &
-\hline
-  & Coefficient of kinship                                            & & & $k$              &
-  & Focal female's number of mates                                    & & & $N_{males}$      &
-  & Female $i$'s perceived absolute mate quality of male $j$          & & & $Q^{m}_{ij}$     &
-  & Female $i$'s perceived relative mate quality of male $j$          & & & $q^{m}_{ij}$     &
-  & Female $i$'s perceived absolute fertilisation quality of male $j$ & & & $Q^{f}_{ij}$     &
-  & Female $i$'s perceived relative fertilisation quality of male $j$ & & & $q^{f}_{ij}$     &
-  & Viability of a focal female's offspring                           & & & $\Psi_{\textrm{off}}$     &
-\hline
-\end{tabular}
-\end{adjustwidth}
-\end{table}
 
@@
 
-To address whether or not evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance can facilitate evolution of polyandry, we compare simulations in which polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, with otherwise identical simulations in which post-copulatory inbreeding avoidance cannot evolve given four different costs of polyandry ($c_{P} = \{0, 0.0025, 0.005,  0.01\}$).
+To address whether or not evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance can facilitate evolution of polyandry, we compare simulations in which polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, with otherwise identical simulations in which post-copulatory inbreeding avoidance cannot evolve given four different costs of polyandry ($c_{P}$ = $\{$0, 0.0025, 0.005,  0.01$\}$).
 To prevent post-copulatory inbreeding avoidance from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes cause random fertilisation with respect to kinship, so $F_{a}$ alleles have no phenotypic effect.
@@
 
-{\color{Gray}
-    \begin{adjustwidth}{-2.2in}{0in}
-    \mysidecaption{0.32}
-{ 
-        \begin{justify}
-        \vspace{-0.25 mm}
-        \captionof{figures/poly_costs.pdf}
-        {\bf Figure 1:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fixed to zero (i.e., random fertilisation) or (B, D, F, and H) allowed to evolve freely.
-Costs of polyandry ($c_p$) increase across rows from zero (A and B) to 0.01 (G and H).
-Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
-Negative mean allele values indicate inbreeding avoidance or tendency for monandry, and positive values indicate inbreeding preference or tendency for polyandry.
-Dotted lines demarcate mean allele values of zero.
-    \end{justify}{\t}
-}[t]
-{
-   \includegraphics[height=18cm]{figures/poly_costs.pdf}%
-}
-    \end{adjustwidth}
-}
-
 Strong post-copulatory inbreeding avoidance, manifested as very negative $F_{a}$ values, consistently evolved in all simulations where such evolution was allowed (black lines, Figure 1B,D,F,H).
@@
 This might be expected given strong inbreeding depression in offspring viability, which imposes selection against inbreeding.
-
-%{\color{Gray}
-%\begin{adjustwidth}{-2.2in}{0in}
-%\mysidecaption{0.68}
-%{%
-%   \includegraphics[height=10.25cm]{figures/Pp_vals.png}%
-%}%
-%{%
-%   \captionof{figures/Pp_vals.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs.
-Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations.
-Positive and negative allele values contribute to polyandry and monandry, respectively.
-In the final generation, mean allele value was below (A) or above (C) zero (demarcated by the dotted line).
-Nevertheless, due to the threshold nature of expression of the polygenic polyandry phenotype, polyandry and monandry are expressed in both populations.
-Histograms in (B) and (D) show females' tendency for polyandry phenotypes in the final generation; white and grey shading indicates monandrous and polyandrous females, respectively.
-Arrows and numbers indicate mean phenotype values.
-Because each trait includes 10 diploid loci with additive effects, phenotype values are ca 20 times allele values.
-\end{justify}{\t}%
-%}[t]
-%\end{adjustwidth}
-%}
 
@@
 Results for all possible cost combinations of $0$ and $0.02$ are provided in Supporting Information (Figure S9).
-
-%{\color{Gray}
-%\begin{adjustwidth}{-2.2in}{0in}
-%\mysidecaption{0.31}
-%{%
-%   \captionof{figures/rel_costs.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 3:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve.
-Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
-Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.
-In all panels, polyandry is cost free.
-\end{justify}{\t}%
-%}
-%{%
-%   \includegraphics[height=14cm]{figures/rel_costs.png}%
-%}%
-%[t]
-%\end{adjustwidth}
-%}
 
@@
 When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information Figure S10).
-
-%{\color{Gray}
-%\begin{adjustwidth}{-2.2in}{0in}
-%\mysidecaption{0.31}
-%{%
-%   \captionof{figures/fixed_adapt.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is cost-free (A, $c_{M} = 0$; C, $c_{F} = 0$) or costly (B, $c_{M}=0.02$; D, $c_{F}=0.02$).
-Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
-Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.
-\end{justify}{\t}%
-%}
-%{%
-%   \includegraphics[height=14cm]{figures/fixed_adapt.png}%
-%}%
-%[t]
-%\end{adjustwidth}
-%}
 
@@
 
-\subsection*{Acknowledgments}
+%\subsection*{Competing interests}
 
-This work was funded by a European Research Council Starting Grant to JMR. Computer simulations were performed using the Maxwell Computing Cluster at the University of Aberdeen.
+%We have no competing interests.
 
-\begin{small}
-\bibliography{ms_pre_post}
-\bibliographystyle{amnatnat}
-\end{small}
+%\subsection*{Acknowledgments}
+
+%This work was funded by a European Research Council Starting Grant to JMR. Computer simulations were performed using the Maxwell Computing Cluster at the University of Aberdeen.
+
+\begin{thebibliography}{73}
+\providecommand{\natexlab}[1]{#1}
+
+\bibitem[{Ak{\c{c}}ay \& Roughgarden(2007)}]{Akcay2007}
+Ak{\c{c}}ay, E. \& Roughgarden, J. 2007.
+\newblock {Extra-pair paternity in birds: Review of the genetic benefits}.
+\newblock \textit{Evol. Ecol. Res.} \textbf{9}:855--868.
+
+\bibitem[{Ala-Honkola \textit{et~al.}(2011)Ala-Honkola, Manier, L{\"{u}}pold, and
+  Pitnick}]{Ala-Honkola2011}
+Ala-Honkola, O., Manier, M.~K., L{\"{u}}pold S. \& Pitnick, S. 2011.
+\newblock {No evidence for postcopulatory inbreeding avoidance in \textit{Drosophila
+  melanogaster}}.
+\newblock \textit{Evolution} \textbf{65}:2699--2705.
+
+\bibitem[{Arct \textit{et~al.}(2015)Arct, Drobniak, \& Cicho}]{Arct2015}
+Arct, A., Drobniak, S.~M. \& Cicho, M. 2015.
+\newblock {Genetic similarity between mates predicts extrapair paternity--a
+  meta-analysis of bird studies}.
+\newblock \textit{Behav. Ecol.} \textbf{26}:959--968.
+
+\bibitem[{Arnqvist \& Rowe(2005)}]{Arnqvist2005a}
+Arnqvist, G. \& Rowe, L. 2005.
+\newblock {\textit{Sexual Conflict}}.
+\newblock Princeton University Press, Princeton, New Jersey.
+
+\bibitem[{Atamas \& Bell(2009)}]{Atamas2009}
+Atamas, S.~P. \& Bell, J. 2009.
+\newblock {Degeneracy-driven self-structuring dynamics in selective
+  repertoires}.
+\newblock \textit{Bull. Math. Biol.} \textbf{71}:1349--1365.
+
+\bibitem[{Bateson(1983)}]{Bateson1983}
+Bateson, P. 1983.
+\newblock {Optimal outbreeding}.
+\newblock Pages 257--277 \emph{in} \textit{Mate Choice}. University Press, Cambridge,
+  Cambridge.
+
+\bibitem[{Bocedi \& Reid(2014)}]{Bocedi2014}
+Bocedi, G. \& Reid, J.~M. 2014.
+\newblock {Evolution of female multiple mating: a quantitative model of the
+  ``sexually-selected sperm'' hypothesis}.
+\newblock \textit{Evolution} \textbf{69}:39--58.
+
+\bibitem[{Bretman \textit{et~al.}(2009)Bretman, Newcombe, \& Tregenza}]{Bretman2009}
+Bretman, A., Newcombe, D. \& Tregenza, T. 2009.
+\newblock {Promiscuous females avoid inbreeding by controlling sperm storage}.
+\newblock \textit{Mol. Ecol.} \textbf{18}:3340--3345.
+
+\bibitem[{Bussi{\'{e}}re \textit{et~al.}(2006)Bussi{\'{e}}re, Hunt, Jennions, \&
+  Brooks}]{Bussiere2006}
+Bussi{\'{e}}re, L.~F., Hunt, J., Jennions, M.~D. \& Brooks, R. 2006.
+\newblock {Sexual conflict and cryptic female choice in the black field
+  cricket, \textit{Teleogryllus commodus}}.
+\newblock \textit{Evolution} \textbf{60}:792--800.
+
+\bibitem[{Charlesworth \& Charlesworth(1999)}]{Charlesworth1999}
+Charlesworth, B. \& Charlesworth, D. 1999.
+\newblock {The genetic basis of inbreeding depression}.
+\newblock \textit{Genet. Res.} \textbf{74}:329--340.
+
+\bibitem[{Charlesworth \& Willis(2009)}]{Charlesworth2009}
+Charlesworth, D. \& Willis, J.~H. 2009.
+\newblock {The genetics of inbreeding depression}.
+\newblock \textit{Nat. Rev. Genet.} \textbf{10}:783--796.
+
+\bibitem[{Daniel \& Rodd(2015)}]{Daniel2015}
+Daniel, M.~J. \& Rodd, F.~H. 2015.
+\newblock {Female guppies can recognize kin but only avoid incest when
+  previously mated}.
+\newblock \textit{Behav. Ecol.} \textbf{27}:55--61.
+
+\bibitem[{Duthie \textit{et~al.}(2016)Duthie, Bocedi, \& Reid}]{Duthie}
+Duthie, A.~B., Bocedi G. \& Reid, J.~M. 2016.
+\newblock {When does female multiple mating evolve to adjust inbreeding?
+  Effects of inbreeding depression, direct costs, mating constraints, and
+  polyandry as a threshold trait}.
+\newblock \textit{Evolution} \textbf{70}:1927--1943.
+
+\bibitem[{Duthie \& Reid(2015)}]{Duthie2015a}
+Duthie, A.~B. \& Reid, J.~M. 2015.
+\newblock {What happens after inbreeding avoidance? Inbreeding by rejected
+  relatives and the inclusive fitness benefit of inbreeding avoidance}.
+\newblock \textit{PLoS One} \textbf{10}:e0125140.
+
+\bibitem[{Duthie \& Reid(2016)}]{Duthie2016a}
+Duthie, A.~B. \& Reid, J.~M. 2016.
+\newblock {Evolution of inbreeding avoidance and inbreeding preference through
+  mate choice among interacting relatives}.
+\newblock \textit{Am. Nat.} \textbf{188}:651--667.
+
+\bibitem[{Edelman \& Gally(2001)}]{Edelman2001}
+Edelman, G.~M. \& Gally, J.~A. 2001.
+\newblock {Degeneracy and complexity in biological systems}.
+\newblock \textit{Proc. Natl. Acad. Sci. USA} \textbf{98}:13763--13768.
+
+\bibitem[{Firman \& Simmons(2008)}]{Firman2008}
+Firman, R.~C. \& Simmons, L.~W. 2008.
+\newblock {Polyandry facilitates postcopulatory inbreeding avoidance in house
+  mice}.
+\newblock \textit{Evolution} \textbf{62}:603--611.
+
+\bibitem[{Firman \& Simmons(2015)}]{Firman2015}
+Firman, R.~C. \& Simmons, L.~W. 2015.
+\newblock {Gametic interactions promote inbreeding avoidance in house mice}.
+\newblock \textit{Ecol. Lett.} \textbf{18}:937--943.
+
+\bibitem[{Fischer \textit{et~al.}(2015)Fischer, Karl, Heuskin, Janowitz, \&
+  D{\"{o}}tterl}]{Fischer2015}
+Fischer, K., Karl, I., Heuskin, S., Janowitz, S. \& D{\"{o}}tterl, S. 2015.
+\newblock {Kin recognition and inbreeding avoidance in a butterfly}.
+\newblock \textit{Ethology} \textbf{121}:977--984.
+
+\bibitem[{Fitzpatrick \& Evans(2014)}]{Fitzpatrick2014b}
+Fitzpatrick, J.~L. \& Evans, J.~P. 2014.
+\newblock {Postcopulatory inbreeding avoidance in guppies}.
+\newblock \textit{J. Evol. Biol.} \textbf{27}:2585--2594.
+
+\bibitem[{Foerster \textit{et~al.}(2003)Foerster, Delhey, Johnsen, Lifjeld, \&
+  Kempenaers}]{Foerster2003}
+Foerster, K., Delhey K., Johnsen, A., Lifjeld, J.~T. \& Kempenaers B. 2003.
+\newblock {Females increase offspring heterozygosity and fitness through
+  extra-pair matings}.
+\newblock \textit{Nature} \textbf{425}:714--717.
+
+\bibitem[{Gardner \& Kalinka(2006)}]{Gardner2006}
+Gardner, A. \& Kalinka, A.~T. 2006.
+\newblock {Recombination and the evolution of mutational robustness}.
+\newblock \textit{J. Theor. Biol.} \textbf{241}:707--715.
+
+\bibitem[{Gasparini \& Pilastro(2011)}]{Gasparini2011}
+Gasparini, C. \& Pilastro, A. 2011.
+\newblock {Cryptic female preference for genetically unrelated males is
+  mediated by ovarian fluid in the guppy.}
+\newblock \textit{Proc. Biol. Sci.} \textbf{278}:2495--2501.
+
+\bibitem[{Greeff \textit{et~al.}(2009)Greeff, Vuuren, Kryger \& Moore}]{Greeff2009}
+Greeff, J.~M., Jansen van Vuuren, G.~J., Kryger, P. \& Moore, J.~C. 2009.
+\newblock {Outbreeding and possibly inbreeding depression in a pollinating fig
+  wasp with a mixed mating system}.
+\newblock \textit{Heredity} \textbf{102}:349--356.
+
+\bibitem[{Guillaume \& Perrin(2009)}]{Guillaume2009}
+Guillaume, F. \& Perrin, N. 2009.
+\newblock {Inbreeding load, bet hedging, and the evolution of sex-biased
+  dispersal.}
+\newblock \textit{Am. Nat.} \textbf{173}:536--541.
+
+\bibitem[{Jennions \& Petrie(2000)}]{Jennions2000}
+Jennions, M.~D. \& Petrie, M. 2000.
+\newblock {Why do females mate multiply? A review of the genetic benefits}.
+\newblock \textit{Biol. Rev. Camb. Philos. Soc.} \textbf{75}:21--64.
+
+\bibitem[{Keller \& Waller(2002)}]{Keller2002}
+Keller, L.~F. \& Waller,  D.~M. 2002.
+\newblock {Inbreeding effects in wild populations}.
+\newblock \textit{Trends Ecol. Evol.} \textbf{17}:19--23.
+
+\bibitem[{Kimura(1965)}]{Kimura1965}
+Kimura, M. 1965.
+\newblock {A stochastic model concerning the maintenance of genetic variability
+  in quantitative characters}.
+\newblock \textit{Proc. Natl. Acad. Sci. USA} \textbf{54}:731--736.
+
+\bibitem[{Kingma \textit{et~al.}(2013)Kingma, Hall, \& Peters}]{Kingma2013}
+Kingma, S.~A., Hall, M.~L. \& Peters A. 2013.
+\newblock {Breeding synchronization facilitates extrapair mating for inbreeding
+  avoidance}.
+\newblock \textit{Behav. Ecol.} \textbf{24}:1390--1397.
+
+\bibitem[{Koga \textit{et~al.}(1998)Koga, Backwell, Jennions \& Christy}]{Koga1998}
+Koga, T., Backwell, P.~R.~Y., Jennions, M.~D. \& Christy J.~H. 1998.
+\newblock {Elevated predation risk changes mating behaviour and courtship in a
+  fiddler crab}.
+\newblock \textit{Proc. Biol. Sci.} \textbf{265}:1385--1390.
+
+\bibitem[{Kokko \textit{et~al.}(2003)Kokko, Brooks, Jennions \& Morley}]{Kokko2003}
+Kokko, H., Brooks R., Jennions M.~D. \& Morley J. 2003.
+\newblock {The evolution of mate choice and mating biases.}
+\newblock \textit{Proc. Biol. Sci.} \textbf{270}:653--664.
+
+\bibitem[{Kokko \& Mappes(2013)}]{Kokko2013}
+Kokko, H. \& Mappes, J. 2013.
+\newblock {Multiple mating by females is a natural outcome of a null model of
+  mate encounters}.
+\newblock \textit{Entomol. Exp. Appl.} \textbf{146}:26--37.
+
+\bibitem[{Kokko \& Ots(2006)}]{Kokko2006}
+Kokko, H., \& Ots, I. 2006.
+\newblock {When not to avoid inbreeding}.
+\newblock \textit{Evolution} \textbf{60}:467--475.
+% ==================================================================================================
+\bibitem[{Kuriwada et~al.(2011)Kuriwada, Kumano, Shiromoto, and
+  Haraguchi}]{Kuriwada2011}
+Kuriwada, T., N.~Kumano, K.~Shiromoto, and D.~Haraguchi. 2011.
+\newblock {Inbreeding avoidance or tolerance? Comparison of mating behavior
+  between mass-reared and wild strains of the sweet potato weevil}.
+\newblock Behavioral Ecology and Sociobiology 65:1483--1489.
+
+\bibitem[{Lande(1976)}]{Lande1976}
+Lande, R. 1976.
+\newblock {The maintenance of genetic variability by mutation in a polygenic
+  character with linked loci}.
+\newblock Genetical Research 36:221--235.
+
+\bibitem[{Lehtonen and Kokko(2015)}]{Lehtonen2015}
+Lehtonen, J., and H.~Kokko. 2015.
+\newblock {Why inclusive fitness can make it adaptive to produce less fit
+  extra-pair offspring}.
+\newblock Proceedings of the Royal Society B 282:20142716.
+
+\bibitem[{Levin and Lubchenco(2008)}]{Levin2008}
+Levin, S.~A., and J.~Lubchenco. 2008.
+\newblock {Resilience, robustness, and marine ecosystem-based management}
+  58:27--32.
+
+\bibitem[{Lihoreau et~al.(2007)Lihoreau, Zimmer, and Rivault}]{Lihoreau2007}
+Lihoreau, M., C.~Zimmer, and C.~Rivault. 2007.
+\newblock {Kin recognition and incest avoidance in a group-living insect}.
+\newblock Behavioral Ecology 18:880--887.
+
+\bibitem[{Liu et~al.(2014)Liu, Tu, He, Chen, and Xue}]{Liu2014}
+Liu, X., X.~Tu, H.~He, C.~Chen, and F.~Xue. 2014.
+\newblock {Evidence for inbreeding depression and pre-copulatory, but not post
+  copulatory inbreeding avoidance in the cabbage beetle Colaphellus bowringi.}
+\newblock PloS one 9:e94389.
+
+\bibitem[{Lynch and Walsh(1998)}]{Lynch1998}
+Lynch, M., and B.~Walsh. 1998.
+\newblock {Genetics and Analysis of Quantitative Traits}.
+\newblock Sinauer, Sunderland.
+
+\bibitem[{Metzger et~al.(2010{\natexlab{\emph{a}}})Metzger, Bernstein,
+  Hoffmeister, and Desouhant}]{Metzger2010}
+Metzger, M., C.~Bernstein, T.~S. Hoffmeister, and E.~Desouhant.
+  2010{\natexlab{\emph{a}}}.
+\newblock {Does kin recognition and sib-mating avoidance limit the risk of
+  genetic incompatibility in a parasitic wasp?}
+\newblock PLoS One 5:1--6.
+
+\bibitem[{Metzger et~al.(2010{\natexlab{\emph{b}}})Metzger, Fischbein, Auguste,
+  Fauvergue, Bernstein, and Desouhant}]{Metzger2010a}
+Metzger, M., D.~Fischbein, A.~Auguste, X.~Fauvergue, C.~Bernstein, and
+  E.~Desouhant. 2010{\natexlab{\emph{b}}}.
+\newblock {Synergy in information use for mate finding: Demonstration in a
+  parasitoid wasp}.
+\newblock Animal Behaviour 79:1307--1315.
+
+\bibitem[{Mills and Smouse(1994)}]{Mills1994}
+Mills, L.~S., and P.~E. Smouse. 1994.
+\newblock {Demographic consequences of inbreeding in remnant populations}.
+\newblock American Naturalist 144:412--431.
+
+\bibitem[{Morton et~al.(1956)Morton, Crow, and Muller}]{Morton1956}
+Morton, N.~E., J.~F. Crow, and H.~J. Muller. 1956.
+\newblock {An estimate of the mutational damage in man from data on
+  consanguineous marriages}.
+\newblock Proceedings of the National Academy of Sciences 42:855--863.
+
+\bibitem[{Nowak et~al.(1997)Nowak, Boerlijst, Cooke, and {Maynard
+  Smith}}]{Nowak1997}
+Nowak, M.~A., M.~C. Boerlijst, J.~Cooke, and J.~{Maynard Smith}. 1997.
+\newblock {Evolution of genetic redundancy}.
+\newblock Nature 388:167--171.
+
+\bibitem[{Park and Friston(2013)}]{Park2013}
+Park, H.~J., and K.~J. Friston. 2013.
+\newblock {Structural and functional brain networks: from connections to
+  cognition.}
+\newblock Science 342:1238411.
+
+\bibitem[{Parker(1979)}]{Parker1979}
+Parker, G.~A. 1979.
+\newblock {Sexual selection and sexual conflict}.
+\newblock Pages 123--166 \emph{in} M.~S. Blum and N.~A. Blum, eds. Sexual
+  selection and reproductive competition in insects. Academic Press, Inc, New
+  York.
+
+\bibitem[{Parker(2006)}]{Parker2006}
+---{}---{}---. 2006.
+\newblock {Sexual conflict over mating and fertilization: an overview}.
+\newblock Philosophical Transactions of the Royal Society B 361:235--259.
+
+\bibitem[{Pizzari et~al.(2004)Pizzari, L{\o}vlie, and Cornwallis}]{Pizzari2004}
+Pizzari, T., H.~L{\o}vlie, and C.~K. Cornwallis. 2004.
+\newblock {Sex-specific, counteracting responses to inbreeding in a bird}.
+\newblock Proceedings of The Royal Society B 271:2115--2121.
+
+\bibitem[{Pomiankowski(1987)}]{Pomiankowski1987}
+Pomiankowski, A. 1987.
+\newblock {The costs of choice in sexual selection}.
+\newblock Journal of Theoretical Biology 128:195--218.
+
+\bibitem[{Potts et~al.(1991)Potts, Manning, and Wakeland}]{Potts1991}
+Potts, W.~K., C.~J. Manning, and E.~K. Wakeland. 1991.
+\newblock {Mating patterns in seminatural populations of mice influenced by MHC
+  genotype}.
+\newblock Nature 352:619--621.
+
+\bibitem[{Price and Friston(2002)}]{Price2002}
+Price, C.~J., and K.~J. Friston. 2002.
+\newblock {Degeneracy and cognitive anatomy}.
+\newblock Trends in Cognitive Sciences 6:416--421.
+
+\bibitem[{Pusey and Wolf(1996)}]{Pusey1996}
+Pusey, A., and M.~Wolf. 1996.
+\newblock {Inbreeding avoidance in animals}.
+\newblock Trends in Ecology {\&} Evolution 5347:298--301.
+
+\bibitem[{Reeve(2000)}]{Reeve2000}
+Reeve, J.~P. 2000.
+\newblock {Predicting long-term response to selection}.
+\newblock Genetical Research 75:83--94.
+
+\bibitem[{Reid(2015)}]{Reid2015a}
+Reid, J.~M. 2015.
+\newblock {What can we really say about relatedness and extrapair paternity: a
+  comment on Arct et al}.
+\newblock Behavioral Ecology 00:1--2.
+
+\bibitem[{Reid et~al.(2015{\natexlab{\emph{a}}})Reid, Arcese, Keller, Germain,
+  Duthie, Losdat, Wolak, and Nietlisbach}]{Reid2014}
+Reid, J.~M., P.~Arcese, L.~F. Keller, R.~R. Germain, A.~B. Duthie, S.~Losdat,
+  M.~E. Wolak, and P.~Nietlisbach. 2015{\natexlab{\emph{a}}}.
+\newblock {Quantifying inbreeding avoidance through extra-pair reproduction}.
+\newblock Evolution 69:59--74.
+
+\bibitem[{Reid et~al.(2015{\natexlab{\emph{b}}})Reid, Duthie, Wolak, and
+  Arcese}]{Reid2015}
+Reid, J.~M., A.~B. Duthie, M.~E. Wolak, and P.~Arcese.
+  2015{\natexlab{\emph{b}}}.
+\newblock {Demographic mechanisms of inbreeding adjustment through extra-pair
+  reproduction}.
+\newblock Journal of Animal Ecology 84:1029--1040.
+
+\bibitem[{Roberts et~al.(2015)Roberts, Evison, Baer, and Hughes}]{Roberts2015a}
+Roberts, K.~E., S.~E.~F. Evison, B.~Baer, and W.~O.~H. Hughes. 2015.
+\newblock {The cost of promiscuity: sexual transmission of Nosema
+  microsporidian parasites in polyandrous honey bees}.
+\newblock Scientific Reports 5:10982.
+
+\bibitem[{Roff(1996)}]{Roff1996}
+Roff, D.~A. 1996.
+\newblock {The evolution of threshold traits in animals}.
+\newblock The Quarterly Review of Biology 71:3--35.
+
+\bibitem[{Roff(1998)}]{Roff1998}
+---{}---{}---. 1998.
+\newblock {Evolution of threshold traits: the balance between directional
+  selection, drift and mutation}.
+\newblock Heredity 80:25--32.
+
+\bibitem[{Ronkainen and Ylonen(1994)}]{Ronkainen1994}
+Ronkainen, H., and H.~Ylonen. 1994.
+\newblock {Behaviour of cyclic bank voles under risk of mustelid predation: Do
+  females avoid copulations?}
+\newblock Oecologia 97:377--381.
+
+\bibitem[{Rowe(1988)}]{Rowe1988}
+Rowe, L. 1988.
+\newblock {Cost of mating for female insects: risk of predation in Photinus
+  collustrans (Coleoptera: Lampyridae)}.
+\newblock American Naturalist 121:139--142.
+
+\bibitem[{Rowe et~al.(1994)Rowe, Arnqvist, Sih, and Krupa}]{Rowe1994}
+Rowe, L., G.~Arnqvist, A.~Sih, and J.~J. Krupa. 1994.
+\newblock {Sexual conflict and the evolutionary ecology of mating patterns:
+  water striders as a model system}.
+\newblock Trends in Ecology {\&} Evolution 9:289--293.
+
+\bibitem[{Simmons et~al.(2006)Simmons, Beveridge, Wedell, and
+  Tregenza}]{Simmons2006}
+Simmons, L.~W., M.~Beveridge, N.~Wedell, and T.~Tregenza. 2006.
+\newblock {Postcopulatory inbreeding avoidance by female crickets only revealed
+  by molecular markers}.
+\newblock Molecular Ecology 15:3817--3824.
+
+\bibitem[{Suraci et~al.(2017)Suraci, Clinchy, and Zanette}]{Suraci2017}
+Suraci, J.~P., M.~Clinchy, and L.~Y. Zanette. 2017.
+\newblock {Do large carnivores and mesocarnivores have redundant impacts on
+  intertidal prey?}
+\newblock PLoS One 12:e0170255.
+
+\bibitem[{Szulkin et~al.(2013)Szulkin, Stopher, Pemberton, and
+  Reid}]{Szulkin2012}
+Szulkin, M., K.~V. Stopher, J.~M. Pemberton, and J.~M. Reid. 2013.
+\newblock {Inbreeding avoidance, tolerance, or preference in animals?}
+\newblock Trends in Ecology {\&} Evolution 28:205--211.
+
+\bibitem[{Tan et~al.(2012)Tan, L{\o}vlie, Pizzari, and Wigby}]{Tan2012}
+Tan, C. K.~W., H.~L{\o}vlie, T.~Pizzari, and S.~Wigby. 2012.
+\newblock {No evidence for precopulatory inbreeding avoidance in Drosophila
+  melanogaster}.
+\newblock Animal Behaviour 83:1433--1441.
+
+\bibitem[{Tregenza and Wedell(2002)}]{Tregenza2002}
+Tregenza, T., and N.~Wedell. 2002.
+\newblock {Polyandrous females avoid costs of inbreeding}.
+\newblock Nature 415:71--73.
+
+\bibitem[{Tuni et~al.(2013)Tuni, Beveridge, and Simmons}]{Tuni2013}
+Tuni, C., M.~Beveridge, and L.~W. Simmons. 2013.
+\newblock {Female crickets assess relatedness during mate guarding and bias
+  storage of sperm towards unrelated males}.
+\newblock Journal of Evolutionary Biology 26:1261--1268.
+
+\bibitem[{Varian-Ramos and Webster(2012)}]{Varian-Ramos2012}
+Varian-Ramos, C.~W., and M.~S. Webster. 2012.
+\newblock {Extrapair copulations reduce inbreeding for female red-backed
+  fairy-wrens, Malurus melanocephalus}.
+\newblock Animal Behaviour 83:857--864.
+
+\bibitem[{Whitacre and Bender(2010)}]{Whitacre2010}
+Whitacre, J., and A.~Bender. 2010.
+\newblock {Degeneracy: A design principle for achieving robustness and
+  evolvability}.
+\newblock Journal of Theoretical Biology 263:143--153.
+
+\bibitem[{Whitacre(2010)}]{Whitacre2010a}
+Whitacre, J.~M. 2010.
+\newblock {Degeneracy: a link between evolvability, robustness and complexity
+  in biological systems}.
+\newblock Theoretical Biology and Medical Modelling 7:6.
+
+\bibitem[{Zeh and Zeh(1997)}]{Zeh1997}
+Zeh, J.~A., and D.~W. Zeh. 1997.
+\newblock {The evolution of polyandry II: post-copulatory defenses against
+  genetic incompatibility}.
+\newblock Proceedings of the Royal Society B 264:69--75.
+
+\end{thebibliography}
+
+\clearpage
+
+\noindent \textbf{Table 1:} Individual traits (A), model parameter values (B), and model variables (C) for an individual-based model of the evolution of polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.
+\\
+
+\noindent \textbf{Figure 1:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fixed to zero (i.e., random fertilisation) or (B, D, F, and H) allowed to evolve freely.
+Costs of polyandry ($c_p$) increase across rows from zero (A and B) to 0.01 (G and H).
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values indicate inbreeding avoidance or tendency for monandry, and positive values indicate inbreeding preference or tendency for polyandry.
+Dotted lines demarcate mean allele values of zero.
+\\
+
+\noindent \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs.
+Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations.
+Positive and negative allele values contribute to polyandry and monandry, respectively.
+In the final generation, mean allele value was below (A) or above (C) zero (demarcated by the dotted line).
+Nevertheless, due to the threshold nature of expression of the polygenic polyandry phenotype, polyandry and monandry are expressed in both populations.
+Histograms in (B) and (D) show females' tendency for polyandry phenotypes in the final generation; white and grey shading indicates monandrous and polyandrous females, respectively.
+Arrows and numbers indicate mean phenotype values.
+Because each trait includes 10 diploid loci with additive effects, phenotype values are ca 20 times allele values.
+\\
+
+\noindent \textbf{Figure 3:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve.
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.
+In all panels, polyandry is cost free.
+\\
+
+\noindent \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is cost-free (A, $c_{M} = 0$; C, $c_{F} = 0$) or costly (B, $c_{M}=0.02$; D, $c_{F}=0.02$).
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.
+
+\clearpage
+\begin{sidewaystable}[!ht]
+\caption{Individual traits (A), model parameter values (B), and model variables (C) for an individual-based model of the evolution of polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.}
+\begin{tabular}{lllll}
+\hline
+A & Trait & Allele & Genotype & Phenotype &
+\hline
+  & Tendency for polyandry               &   $P_{a}$  &  $P_{g}$  &  $P_{p}$  &
+  & Pre-copulatory inbreeding strategy   &   $M_{a}$  &  $M_{g}$  &  $M_{p}$  &
+  & Post-copulatory inbreeding strategy  &   $F_{a}$  &  $F_{g}$  &  $F_{p}$  &
+  &                                      &            &           &           &
+\hline
+B & Description & Parameter & & Default value(s) &
+\hline
+
+  & Cost of tendency for polyandry                & $c_{P}$    & & $0$, $0.02$   &
+  & Cost of pre-copulatory inbreeding strategy    & $c_{M}$    & & $0$, $0.02$   &
+  & Cost of post-copulatory inbreeding strategy   & $c_{F}$    & & $0$, $0.02$   &
+  & Focal female's number of offspring            & $n$        & & $8$           &
+  & Log-linear slope of inbreeding depression     & $\beta$    & & $3$           &
+  & Adult male immigrants per generation          & $\rho$     & & $5$           & 
+  & Female carrying capacity                      & $K_{f}$    & & $100$         &
+  & Male carrying capacity                        & $K_{m}$    & & $100$         &
+  & Mutation rate of alleles                      & $\mu$      & & $0.001$       &
+  & Standard deviation of mutation effect size    & $\mu_{SD}$ & & $\sqrt{1/20}$ &
+  &                                               &            & &               &
+\hline
+C & Description & & & Variable &
+\hline
+  & Coefficient of kinship                                            & & & $k$              &
+  & Focal female's number of mates                                    & & & $N_{males}$      &
+  & Female $i$'s perceived absolute mate quality of male $j$          & & & $Q^{m}_{ij}$     &
+  & Female $i$'s perceived relative mate quality of male $j$          & & & $q^{m}_{ij}$     &
+  & Female $i$'s perceived absolute fertilisation quality of male $j$ & & & $Q^{f}_{ij}$     &
+  & Female $i$'s perceived relative fertilisation quality of male $j$ & & & $q^{f}_{ij}$     &
+  & Viability of a focal female's offspring                           & & & $\Psi_{\textrm{off}}$     &
+\hline
+\end{tabular}
+\end{sidewaystable}
+
+\clearpage
+\begin{figure}
+\begin{center}				
+\includegraphics[scale=0.85]{figures/poly_costs.pdf}
+\end{center}
+\caption{Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fixed to zero (i.e., random fertilisation) or (B, D, F, and H) allowed to evolve freely.
+Costs of polyandry ($c_p$) increase across rows from zero (A and B) to 0.01 (G and H).
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values indicate inbreeding avoidance or tendency for monandry, and positive values indicate inbreeding preference or tendency for polyandry.
+Dotted lines demarcate mean allele values of zero.}
+%\label{Fig1}
+\end{figure}
+
+\clearpage
+\begin{figure}
+\begin{center}				
+\includegraphics[scale=0.60]{figures/Pp_vals.pdf}
+\end{center}
+\caption{Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs.
+Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations.
+Positive and negative allele values contribute to polyandry and monandry, respectively.
+In the final generation, mean allele value was below (A) or above (C) zero (demarcated by the dotted line).
+Nevertheless, due to the threshold nature of expression of the polygenic polyandry phenotype, polyandry and monandry are expressed in both populations.
+Histograms in (B) and (D) show females' tendency for polyandry phenotypes in the final generation; white and grey shading indicates monandrous and polyandrous females, respectively.
+Arrows and numbers indicate mean phenotype values.
+Because each trait includes 10 diploid loci with additive effects, phenotype values are ca 20 times allele values.}
+%\label{Fig2}
+\end{figure}
+
+\clearpage
+\begin{figure}
+\begin{center}				
+\includegraphics[scale=1.00]{figures/rel_costs.pdf}
+\end{center}
+\caption{Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve.
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.
+In all panels, polyandry is cost free.}
+%\label{Fig3}
+\end{figure}
+
+\clearpage
+\begin{figure}
+\begin{center}				
+\includegraphics[scale=1.00]{figures/fixed_adapt.pdf}
+\end{center}
+\caption{Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is cost-free (A, $c_{M} = 0$; C, $c_{F} = 0$) or costly (B, $c_{M}=0.02$; D, $c_{F}=0.02$).
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.}
+%\label{Fig4}
+\end{figure}
 

### 2017-04-14 pre_post.tex
Finish reference formatting

@@
 
-\bibitem[{Kingma \textit{et~al.}(2013)Kingma, Hall, \& Peters}]{Kingma2013}
+\bibitem[{Kingma \textit{et~al.}(2013)Kingma, Hall \& Peters}]{Kingma2013}
 Kingma, S.~A., Hall, M.~L. \& Peters A. 2013.
@@
 % ==================================================================================================
-\bibitem[{Kuriwada et~al.(2011)Kuriwada, Kumano, Shiromoto, and
+\bibitem[{Kuriwada \textit{et~al.}(2011)Kuriwada, Kumano, Shiromoto \&
   Haraguchi}]{Kuriwada2011}
-Kuriwada, T., N.~Kumano, K.~Shiromoto, and D.~Haraguchi. 2011.
+Kuriwada, T., Kumano, N., Shiromoto, K. \& Haraguchi, D. 2011.
 \newblock {Inbreeding avoidance or tolerance? Comparison of mating behavior
   between mass-reared and wild strains of the sweet potato weevil}.
-\newblock Behavioral Ecology and Sociobiology 65:1483--1489.
+\newblock \textit{Behav. Ecol. Sociobiol.} \textbf{65}:1483--1489.
 
@@
   character with linked loci}.
-\newblock Genetical Research 36:221--235.
+\newblock \textit{Genet. Res.} \textbf{36}:221--235.
 
-\bibitem[{Lehtonen and Kokko(2015)}]{Lehtonen2015}
-Lehtonen, J., and H.~Kokko. 2015.
+\bibitem[{Lehtonen \& Kokko(2015)}]{Lehtonen2015}
+Lehtonen, J. \& Kokko, H. 2015.
 \newblock {Why inclusive fitness can make it adaptive to produce less fit
   extra-pair offspring}.
-\newblock Proceedings of the Royal Society B 282:20142716.
+\newblock \textit{Proc. Biol. Sci.} \textbf{282}:20142716.
 
-\bibitem[{Levin and Lubchenco(2008)}]{Levin2008}
-Levin, S.~A., and J.~Lubchenco. 2008.
+\bibitem[{Levin \& Lubchenco(2008)}]{Levin2008}
+Levin, S.~A. \& Lubchenco, J. 2008.
 \newblock {Resilience, robustness, and marine ecosystem-based management}
-  58:27--32.
+\newblock \textit{BioScience} \textbf{58}:27--32.
 
-\bibitem[{Lihoreau et~al.(2007)Lihoreau, Zimmer, and Rivault}]{Lihoreau2007}
-Lihoreau, M., C.~Zimmer, and C.~Rivault. 2007.
+\bibitem[{Lihoreau \textit{et~al.}(2007)Lihoreau, Zimmer \& Rivault}]{Lihoreau2007}
+Lihoreau, M., Zimmer, C. \& Rivault, C. 2007.
 \newblock {Kin recognition and incest avoidance in a group-living insect}.
-\newblock Behavioral Ecology 18:880--887.
+\newblock \textit{Behav. Ecol.} \textbf{18}:880--887.
 
-\bibitem[{Liu et~al.(2014)Liu, Tu, He, Chen, and Xue}]{Liu2014}
-Liu, X., X.~Tu, H.~He, C.~Chen, and F.~Xue. 2014.
+\bibitem[{Liu \textit{et~al.}(2014)Liu, Tu, He, Chen \& Xue}]{Liu2014}
+Liu, X., Tu, X., He, H., Chen, C. \& Xue, F. 2014.
 \newblock {Evidence for inbreeding depression and pre-copulatory, but not post
-  copulatory inbreeding avoidance in the cabbage beetle Colaphellus bowringi.}
-\newblock PloS one 9:e94389.
+  copulatory inbreeding avoidance in the cabbage beetle \textit{Colaphellus bowringi}.}
+\newblock \textit{PloS one} \textbf{9}:e94389.
 
-\bibitem[{Lynch and Walsh(1998)}]{Lynch1998}
-Lynch, M., and B.~Walsh. 1998.
-\newblock {Genetics and Analysis of Quantitative Traits}.
+\bibitem[{Lynch \& Walsh(1998)}]{Lynch1998}
+Lynch, M. \& Walsh, B. 1998.
+\newblock {\textit{Genetics and Analysis of Quantitative Traits}}.
 \newblock Sinauer, Sunderland.
 
-\bibitem[{Metzger et~al.(2010{\natexlab{\emph{a}}})Metzger, Bernstein,
-  Hoffmeister, and Desouhant}]{Metzger2010}
-Metzger, M., C.~Bernstein, T.~S. Hoffmeister, and E.~Desouhant.
+\bibitem[{Metzger \textit{et~al.}(2010{\natexlab{\emph{a}}})Metzger, Bernstein,
+  Hoffmeister \& Desouhant}]{Metzger2010}
+Metzger, M., Bernstein, C., Hoffmeister, T.~S. \& Desouhant, E.
   2010{\natexlab{\emph{a}}}.
@@
   genetic incompatibility in a parasitic wasp?}
-\newblock PLoS One 5:1--6.
+\newblock \textit{PLoS One} \textbf{5}:1--6.
 
-\bibitem[{Metzger et~al.(2010{\natexlab{\emph{b}}})Metzger, Fischbein, Auguste,
-  Fauvergue, Bernstein, and Desouhant}]{Metzger2010a}
-Metzger, M., D.~Fischbein, A.~Auguste, X.~Fauvergue, C.~Bernstein, and
-  E.~Desouhant. 2010{\natexlab{\emph{b}}}.
+\bibitem[{Metzger \textit{et~al.}(2010{\natexlab{\emph{b}}})Metzger, Fischbein, Auguste,
+  Fauvergue, Bernstein \& Desouhant}]{Metzger2010a}
+Metzger, M., Fischbein, D., Auguste, A., Fauvergue, X., Bernstein, C., \&
+  Desouhant, E. 2010{\natexlab{\emph{b}}}.
 \newblock {Synergy in information use for mate finding: Demonstration in a
   parasitoid wasp}.
-\newblock Animal Behaviour 79:1307--1315.
+\newblock \textit{Anim. Behav.} 79:1307--1315.
 
-\bibitem[{Mills and Smouse(1994)}]{Mills1994}
-Mills, L.~S., and P.~E. Smouse. 1994.
+\bibitem[{Mills \& Smouse(1994)}]{Mills1994}
+Mills, L.~S. \& Smouse, P.~E. 1994.
 \newblock {Demographic consequences of inbreeding in remnant populations}.
-\newblock American Naturalist 144:412--431.
+\newblock \textit{Am. Nat.} \textbf{144}:412--431.
 
-\bibitem[{Morton et~al.(1956)Morton, Crow, and Muller}]{Morton1956}
-Morton, N.~E., J.~F. Crow, and H.~J. Muller. 1956.
+\bibitem[{Morton et~al.(1956)Morton, Crow \& Muller}]{Morton1956}
+Morton, N.~E., Crow, J.~F., \& Muller, H.~J. 1956.
 \newblock {An estimate of the mutational damage in man from data on
   consanguineous marriages}.
-\newblock Proceedings of the National Academy of Sciences 42:855--863.
+\newblock \textit{Proc. Natl. Acad. Sci. USA} \textbf{42}:855--863.
 
-\bibitem[{Nowak et~al.(1997)Nowak, Boerlijst, Cooke, and {Maynard
+\bibitem[{Nowak \textit{et~al.}(1997)Nowak, Boerlijst, Cooke, \& {Maynard
   Smith}}]{Nowak1997}
-Nowak, M.~A., M.~C. Boerlijst, J.~Cooke, and J.~{Maynard Smith}. 1997.
+Nowak, M.~A., Boerlijst, M.~C., Cooke, J. \& {Maynard Smith}, J. 1997.
 \newblock {Evolution of genetic redundancy}.
-\newblock Nature 388:167--171.
+\newblock \textit{Nature} \textbf{388}:167--171.
 
-\bibitem[{Park and Friston(2013)}]{Park2013}
-Park, H.~J., and K.~J. Friston. 2013.
+\bibitem[{Park \& Friston(2013)}]{Park2013}
+Park, H.~J. \& Friston, K.~J. 2013.
 \newblock {Structural and functional brain networks: from connections to
   cognition.}
-\newblock Science 342:1238411.
+\newblock \textit{Science} \textbf{342}:1238411.
 
@@
 \newblock {Sexual selection and sexual conflict}.
-\newblock Pages 123--166 \emph{in} M.~S. Blum and N.~A. Blum, eds. Sexual
-  selection and reproductive competition in insects. Academic Press, Inc, New
+\newblock Pages 123--166 \emph{in} M.~S. Blum \& N.~A. Blum, eds. \textit{Sexual
+  selection and reproductive competition in insects}. Academic Press, Inc, New
   York.
@@
 \bibitem[{Parker(2006)}]{Parker2006}
----{}---{}---. 2006.
+Parker, G.~A. 2006.
 \newblock {Sexual conflict over mating and fertilization: an overview}.
-\newblock Philosophical Transactions of the Royal Society B 361:235--259.
+\newblock \textit{Phil. Trans. R. Soc. Lond. B Biol. Sci.} \textbf{361}:235--259.
 
-\bibitem[{Pizzari et~al.(2004)Pizzari, L{\o}vlie, and Cornwallis}]{Pizzari2004}
-Pizzari, T., H.~L{\o}vlie, and C.~K. Cornwallis. 2004.
+\bibitem[{Pizzari \textit{et~al.}(2004)Pizzari, L{\o}vlie, \& Cornwallis}]{Pizzari2004}
+Pizzari, T., L{\o}vlie, H. \& Cornwallis, C.~K. 2004.
 \newblock {Sex-specific, counteracting responses to inbreeding in a bird}.
-\newblock Proceedings of The Royal Society B 271:2115--2121.
+\newblock \textit{Proc. Biol. Sci.} \textbf{271}:2115--2121.
 
@@
 \newblock {The costs of choice in sexual selection}.
-\newblock Journal of Theoretical Biology 128:195--218.
+\newblock \textit{J. Theor. Biol.} \textbf{128}:195--218.
 
-\bibitem[{Potts et~al.(1991)Potts, Manning, and Wakeland}]{Potts1991}
-Potts, W.~K., C.~J. Manning, and E.~K. Wakeland. 1991.
+\bibitem[{Potts \textit{et~al.}(1991)Potts, Manning \& Wakeland}]{Potts1991}
+Potts, W.~K., Manning, C.~J. \& Wakeland, E.~K. 1991.
 \newblock {Mating patterns in seminatural populations of mice influenced by MHC
   genotype}.
-\newblock Nature 352:619--621.
+\newblock \textit{Nature} \textbf{352}:619--621.
 
-\bibitem[{Price and Friston(2002)}]{Price2002}
-Price, C.~J., and K.~J. Friston. 2002.
+\bibitem[{Price \& Friston(2002)}]{Price2002}
+Price, C.~J. \& Friston, K.~J. 2002.
 \newblock {Degeneracy and cognitive anatomy}.
-\newblock Trends in Cognitive Sciences 6:416--421.
+\newblock \textit{Trends Cogn. Sci.} \textbf{6}:416--421.
 
-\bibitem[{Pusey and Wolf(1996)}]{Pusey1996}
-Pusey, A., and M.~Wolf. 1996.
+\bibitem[{Pusey \& Wolf(1996)}]{Pusey1996}
+Pusey, A., \& Wolf, M. 1996.
 \newblock {Inbreeding avoidance in animals}.
-\newblock Trends in Ecology {\&} Evolution 5347:298--301.
+\newblock \textit{Trends Ecol. Evol.} \textbf{5347}:298--301.
 
@@
 \newblock {Predicting long-term response to selection}.
-\newblock Genetical Research 75:83--94.
+\newblock \textit{Genet. Res.} \textbf{75}:83--94.
 
@@
 \newblock {What can we really say about relatedness and extrapair paternity: a
-  comment on Arct et al}.
-\newblock Behavioral Ecology 00:1--2.
+  comment on Arct \textit{et al}}.
+\newblock \textit{Behav. Ecol.} \textbf{26}:969--970.
 
-\bibitem[{Reid et~al.(2015{\natexlab{\emph{a}}})Reid, Arcese, Keller, Germain,
-  Duthie, Losdat, Wolak, and Nietlisbach}]{Reid2014}
-Reid, J.~M., P.~Arcese, L.~F. Keller, R.~R. Germain, A.~B. Duthie, S.~Losdat,
-  M.~E. Wolak, and P.~Nietlisbach. 2015{\natexlab{\emph{a}}}.
+\bibitem[{Reid \textit{et~al.}(2015{\natexlab{\emph{a}}})Reid, Arcese, Keller, Germain,
+  Duthie, Losdat, Wolak \& Nietlisbach}]{Reid2014}
+Reid, J.~M., Arcese, P., Keller, L.~F., Germain, R.~R., Duthie, A.~B., Losdat, S.,
+  Wolak, M.~E. \& Nietlisbach, P. 2015{\natexlab{\emph{a}}}.
 \newblock {Quantifying inbreeding avoidance through extra-pair reproduction}.
-\newblock Evolution 69:59--74.
+\newblock \textit{Evolution} \textbf{69}:59--74.
 
-\bibitem[{Reid et~al.(2015{\natexlab{\emph{b}}})Reid, Duthie, Wolak, and
+\bibitem[{Reid \textit{et~al.}(2015{\natexlab{\emph{b}}})Reid, Duthie, Wolak \&
   Arcese}]{Reid2015}
-Reid, J.~M., A.~B. Duthie, M.~E. Wolak, and P.~Arcese.
+Reid, J.~M., Duthie, A.~B., Wolak, M.~E. \& Arcese, P.
   2015{\natexlab{\emph{b}}}.
@@
   reproduction}.
-\newblock Journal of Animal Ecology 84:1029--1040.
+\newblock \textit{J. Anim. Ecol.} \textbf{84}:1029--1040.
 
-\bibitem[{Roberts et~al.(2015)Roberts, Evison, Baer, and Hughes}]{Roberts2015a}
-Roberts, K.~E., S.~E.~F. Evison, B.~Baer, and W.~O.~H. Hughes. 2015.
-\newblock {The cost of promiscuity: sexual transmission of Nosema
-  microsporidian parasites in polyandrous honey bees}.
-\newblock Scientific Reports 5:10982.
+\bibitem[{Roberts \textit{et~al.}(2015)Roberts, Evison, Baer \& Hughes}]{Roberts2015a}
+Roberts, K.~E., Evison, S.~E.~F., Baer, B. \& Hughes, W.~O.~H. 2015.
+\newblock {The cost of promiscuity: sexual transmission of \textit{Nosema
+  microsporidian} parasites in polyandrous honey bees}.
+\newblock \textit{Sci. Rep.} \textbf{5}:10982.
 
@@
 \newblock {The evolution of threshold traits in animals}.
-\newblock The Quarterly Review of Biology 71:3--35.
+\newblock \textit{Q. Rev. Biol.} \textbf{71}:3--35.
 
 \bibitem[{Roff(1998)}]{Roff1998}
----{}---{}---. 1998.
+Roff, D.~A. 1998.
 \newblock {Evolution of threshold traits: the balance between directional
   selection, drift and mutation}.
-\newblock Heredity 80:25--32.
+\newblock \textit{Heredity} \textbf{80}:25--32.
 
-\bibitem[{Ronkainen and Ylonen(1994)}]{Ronkainen1994}
-Ronkainen, H., and H.~Ylonen. 1994.
+\bibitem[{Ronkainen \& Ylonen(1994)}]{Ronkainen1994}
+Ronkainen, H. \& Ylonen, H. 1994.
 \newblock {Behaviour of cyclic bank voles under risk of mustelid predation: Do
   females avoid copulations?}
-\newblock Oecologia 97:377--381.
+\newblock \textit{Oecologia} \textbf{97}:377--381.
 
@@
 Rowe, L. 1988.
-\newblock {Cost of mating for female insects: risk of predation in Photinus
-  collustrans (Coleoptera: Lampyridae)}.
-\newblock American Naturalist 121:139--142.
+\newblock {Cost of mating for female insects: risk of predation in \textit{Photinus
+  collustrans} (Coleoptera: Lampyridae)}.
+\newblock \textit{Am. Nat.} \textbf{121}:139--142.
 
-\bibitem[{Rowe et~al.(1994)Rowe, Arnqvist, Sih, and Krupa}]{Rowe1994}
-Rowe, L., G.~Arnqvist, A.~Sih, and J.~J. Krupa. 1994.
+\bibitem[{Rowe \textit{et~al.}(1994)Rowe, Arnqvist, Sih \& Krupa}]{Rowe1994}
+Rowe, L., Arnqvist, G., Sih, A. \& Krupa, J.~J. 1994.
 \newblock {Sexual conflict and the evolutionary ecology of mating patterns:
   water striders as a model system}.
-\newblock Trends in Ecology {\&} Evolution 9:289--293.
+\newblock \textit{Trends Ecol. Evol.} \textbf{9}:289--293.
 
-\bibitem[{Simmons et~al.(2006)Simmons, Beveridge, Wedell, and
+\bibitem[{Simmons \textit{et~al.}(2006)Simmons, Beveridge, Wedell \&
   Tregenza}]{Simmons2006}
-Simmons, L.~W., M.~Beveridge, N.~Wedell, and T.~Tregenza. 2006.
+Simmons, L.~W., Beveridge, M., Wedell, N. \& Tregenza, T. 2006.
 \newblock {Postcopulatory inbreeding avoidance by female crickets only revealed
   by molecular markers}.
-\newblock Molecular Ecology 15:3817--3824.
+\newblock \textit{Mol. Ecol.} \textbf{15}:3817--3824.
 
-\bibitem[{Suraci et~al.(2017)Suraci, Clinchy, and Zanette}]{Suraci2017}
-Suraci, J.~P., M.~Clinchy, and L.~Y. Zanette. 2017.
+\bibitem[{Suraci \textit{et~al.}(2017)Suraci, Clinchy \& Zanette}]{Suraci2017}
+Suraci, J.~P., Clinchy, M. \& Zanette, L.~Y. 2017.
 \newblock {Do large carnivores and mesocarnivores have redundant impacts on
   intertidal prey?}
-\newblock PLoS One 12:e0170255.
+\newblock \textit{PLoS One} \textbf{12}:e0170255.
 
-\bibitem[{Szulkin et~al.(2013)Szulkin, Stopher, Pemberton, and
+\bibitem[{Szulkin \textit{et~al.}(2013)Szulkin, Stopher, Pemberton \&
   Reid}]{Szulkin2012}
-Szulkin, M., K.~V. Stopher, J.~M. Pemberton, and J.~M. Reid. 2013.
+Szulkin, M., Stopher, K.~V., Pemberton, J.~M. \& Reid, J.~M. 2013.
 \newblock {Inbreeding avoidance, tolerance, or preference in animals?}
-\newblock Trends in Ecology {\&} Evolution 28:205--211.
+\newblock \textit{Trends Ecol. Evol.} \textbf{28}:205--211.
 
-\bibitem[{Tan et~al.(2012)Tan, L{\o}vlie, Pizzari, and Wigby}]{Tan2012}
-Tan, C. K.~W., H.~L{\o}vlie, T.~Pizzari, and S.~Wigby. 2012.
-\newblock {No evidence for precopulatory inbreeding avoidance in Drosophila
-  melanogaster}.
-\newblock Animal Behaviour 83:1433--1441.
+\bibitem[{Tan \textit{et~al.}(2012)Tan, L{\o}vlie, Pizzari \& Wigby}]{Tan2012}
+Tan, C. K.~W., L{\o}vlie, H., Pizzari, T. \& Wigby, S. 2012.
+\newblock {No evidence for precopulatory inbreeding avoidance in \textit{Drosophila
+  melanogaster}}.
+\newblock \textit{Anim. Behav.} \textbf{83}:1433--1441.
 
-\bibitem[{Tregenza and Wedell(2002)}]{Tregenza2002}
-Tregenza, T., and N.~Wedell. 2002.
+\bibitem[{Tregenza \& Wedell(2002)}]{Tregenza2002}
+Tregenza, T. \& Wedell, N. 2002.
 \newblock {Polyandrous females avoid costs of inbreeding}.
-\newblock Nature 415:71--73.
+\newblock \textit{Nature} \textbf{415}:71--73.
 
-\bibitem[{Tuni et~al.(2013)Tuni, Beveridge, and Simmons}]{Tuni2013}
-Tuni, C., M.~Beveridge, and L.~W. Simmons. 2013.
+\bibitem[{Tuni \textit{et~al.}(2013)Tuni, Beveridge \& Simmons}]{Tuni2013}
+Tuni, C., Beveridge, M. \& Simmons, L.~W. 2013.
 \newblock {Female crickets assess relatedness during mate guarding and bias
   storage of sperm towards unrelated males}.
-\newblock Journal of Evolutionary Biology 26:1261--1268.
+\newblock \textit{J. Evol. Biol.} \textbf{26}:1261--1268.
 
-\bibitem[{Varian-Ramos and Webster(2012)}]{Varian-Ramos2012}
-Varian-Ramos, C.~W., and M.~S. Webster. 2012.
+\bibitem[{Varian-Ramos \& Webster(2012)}]{Varian-Ramos2012}
+Varian-Ramos, C.~W. \& Webster, M.~S. 2012.
 \newblock {Extrapair copulations reduce inbreeding for female red-backed
-  fairy-wrens, Malurus melanocephalus}.
-\newblock Animal Behaviour 83:857--864.
+  fairy-wrens, \textit{Malurus melanocephalus}}.
+\newblock \textit{Anim. Behav.} \textbf{83}:857--864.
 
-\bibitem[{Whitacre and Bender(2010)}]{Whitacre2010}
-Whitacre, J., and A.~Bender. 2010.
+\bibitem[{Whitacre \& Bender(2010)}]{Whitacre2010}
+Whitacre, J. \& Bender, A. 2010.
 \newblock {Degeneracy: A design principle for achieving robustness and
   evolvability}.
-\newblock Journal of Theoretical Biology 263:143--153.
+\newblock \textit{J. Theor Biol.} \textbf{263}:143--153.
 
@@
   in biological systems}.
-\newblock Theoretical Biology and Medical Modelling 7:6.
+\newblock \textit{Theor. Biol. Med. Model.} \textbf{7}:6.
 
-\bibitem[{Zeh and Zeh(1997)}]{Zeh1997}
-Zeh, J.~A., and D.~W. Zeh. 1997.
+\bibitem[{Zeh \& Zeh(1997)}]{Zeh1997}
+Zeh, J.~A. \& Zeh, D.~W. 1997.
 \newblock {The evolution of polyandry II: post-copulatory defenses against
   genetic incompatibility}.
-\newblock Proceedings of the Royal Society B 264:69--75.
+\newblock \textit{Proc. Biol. Sci.} \textbf{264}:69--75.
 

### 2017-04-14 pre_post_biorxiv.tex
Working PDF of submitting and biorXiv versions

@@
 \\
-A. Bradley Duthie\textsuperscript{1,*},
-Greta Bocedi\textsuperscript{1},
-Ryan R. Germain\textsuperscript{1},
-Matthew E. Wolak\textsuperscript{1},
-Jane M. Reid\textsuperscript{1}
+A. Bradley Duthie\textsuperscript{1,*}, [...],
+%Greta Bocedi\textsuperscript{1},
+%Ryan R. Germain\textsuperscript{1},
+%Matthew E. Wolak\textsuperscript{1},
+Jane M. Reid\textsuperscript{2}
 \\
 \bigskip
-\bf{1} Institute of Biological and Environmental Sciences, School of Biological Sciences, Zoology Building, Tillydrone Avenue, University of Aberdeen, Aberdeen AB24 2TZ, United Kingdom
+\begin{small}
+\bf{1.} Biological and Environmental Sciences, University of Stirling, Stirling FK9 4LA, United Kingdom \\
+\bf{2.} Institute of Biological and Environmental Sciences, University of Aberdeen, Aberdeen AB24 2TZ, United Kingdom
+\end{small}
 %\\
@@
     \begin{adjustwidth}{-2.2in}{0in}
-    \mysidecaption{0.32}
+    \mysidecaption{0.275}
 { 
         \begin{justify}
-        \vspace{-0.25 mm}
+        \vspace{-14.25 mm}
         \captionof{figures/poly_costs.pdf}
@@
     \end{justify}{\t}
-}[t]
+}
 {
@@
 
-%{\color{Gray}
-%\begin{adjustwidth}{-2.2in}{0in}
-%\mysidecaption{0.68}
-%{%
-%   \includegraphics[height=10.25cm]{figures/Pp_vals.png}%
-%}%
-%{%
-%   \captionof{figures/Pp_vals.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs.
+{\color{Gray}
+\begin{adjustwidth}{-2.2in}{0in}
+\mysidecaption{0.70}
+{
+   \includegraphics[height=10.25cm]{figures/Pp_vals.pdf}%
+}
+{%
+   \captionof{figures/Pp_vals.png}\begin{justify}\vspace{0.75 mm} \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs.
 Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations.
@@
 \end{justify}{\t}%
-%}[t]
-%\end{adjustwidth}
-%}
+}
+\end{adjustwidth}
+}
 
@@
 
-%{\color{Gray}
-%\begin{adjustwidth}{-2.2in}{0in}
-%\mysidecaption{0.31}
-%{%
-%   \captionof{figures/rel_costs.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 3:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve.
+{\color{Gray}
+\begin{adjustwidth}{-2.2in}{0in}
+\mysidecaption{0.275}
+{%
+   \captionof{figures/rel_costs.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 3:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve.
 Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
@@
 \end{justify}{\t}%
-%}
-%{%
-%   \includegraphics[height=14cm]{figures/rel_costs.png}%
-%}%
-%[t]
-%\end{adjustwidth}
-%}
+}
+{%
+   \includegraphics[height=13.5cm]{figures/rel_costs.pdf}%
+}%
+\end{adjustwidth}
+}
 
@@
 
+{\color{Gray}
+\begin{adjustwidth}{-2.2in}{0in}
+\mysidecaption{0.70}
+{%
+   \includegraphics[height=13.5cm]{figures/fixed_adapt.pdf}%
+}
+{%
+   \captionof{figures/fixed_adapt.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is cost-free (A, $c_{M} = 0$; C, $c_{F} = 0$) or costly (B, $c_{M}=0.02$; D, $c_{F}=0.02$).
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.
+\end{justify}{\t}%
+}
+\end{adjustwidth}
+}
+
 Conversely, when pre-copulatory inbreeding allele ($M_{a}$) values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently become negative over generations (Figure 4C,D).
@@
 
-\begin{small}
-\bibliography{ms_pre_post}
-\bibliographystyle{amnatnat}
-\end{small}
+%\begin{small}
+
+\begin{thebibliography}{73}
+\providecommand{\natexlab}[1]{#1}
+
+\bibitem[{Ak{\c{c}}ay \& Roughgarden(2007)}]{Akcay2007}
+Ak{\c{c}}ay, E. \& Roughgarden, J. 2007.
+\newblock {Extra-pair paternity in birds: Review of the genetic benefits}.
+\newblock \textit{Evol. Ecol. Res.} \textbf{9}:855--868.
+
+\bibitem[{Ala-Honkola \textit{et~al.}(2011)Ala-Honkola, Manier, L{\"{u}}pold, and
+  Pitnick}]{Ala-Honkola2011}
+Ala-Honkola, O., Manier, M.~K., L{\"{u}}pold S. \& Pitnick, S. 2011.
+\newblock {No evidence for postcopulatory inbreeding avoidance in \textit{Drosophila
+  melanogaster}}.
+\newblock \textit{Evolution} \textbf{65}:2699--2705.
+
+\bibitem[{Arct \textit{et~al.}(2015)Arct, Drobniak, \& Cicho}]{Arct2015}
+Arct, A., Drobniak, S.~M. \& Cicho, M. 2015.
+\newblock {Genetic similarity between mates predicts extrapair paternity--a
+  meta-analysis of bird studies}.
+\newblock \textit{Behav. Ecol.} \textbf{26}:959--968.
+
+\bibitem[{Arnqvist \& Rowe(2005)}]{Arnqvist2005a}
+Arnqvist, G. \& Rowe, L. 2005.
+\newblock {\textit{Sexual Conflict}}.
+\newblock Princeton University Press, Princeton, New Jersey.
+
+\bibitem[{Atamas \& Bell(2009)}]{Atamas2009}
+Atamas, S.~P. \& Bell, J. 2009.
+\newblock {Degeneracy-driven self-structuring dynamics in selective
+  repertoires}.
+\newblock \textit{Bull. Math. Biol.} \textbf{71}:1349--1365.
+
+\bibitem[{Bateson(1983)}]{Bateson1983}
+Bateson, P. 1983.
+\newblock {Optimal outbreeding}.
+\newblock Pages 257--277 \emph{in} \textit{Mate Choice}. University Press, Cambridge,
+  Cambridge.
+
+\bibitem[{Bocedi \& Reid(2014)}]{Bocedi2014}
+Bocedi, G. \& Reid, J.~M. 2014.
+\newblock {Evolution of female multiple mating: a quantitative model of the
+  ``sexually-selected sperm'' hypothesis}.
+\newblock \textit{Evolution} \textbf{69}:39--58.
+
+\bibitem[{Bretman \textit{et~al.}(2009)Bretman, Newcombe, \& Tregenza}]{Bretman2009}
+Bretman, A., Newcombe, D. \& Tregenza, T. 2009.
+\newblock {Promiscuous females avoid inbreeding by controlling sperm storage}.
+\newblock \textit{Mol. Ecol.} \textbf{18}:3340--3345.
+
+\bibitem[{Bussi{\'{e}}re \textit{et~al.}(2006)Bussi{\'{e}}re, Hunt, Jennions, \&
+  Brooks}]{Bussiere2006}
+Bussi{\'{e}}re, L.~F., Hunt, J., Jennions, M.~D. \& Brooks, R. 2006.
+\newblock {Sexual conflict and cryptic female choice in the black field
+  cricket, \textit{Teleogryllus commodus}}.
+\newblock \textit{Evolution} \textbf{60}:792--800.
+
+\bibitem[{Charlesworth \& Charlesworth(1999)}]{Charlesworth1999}
+Charlesworth, B. \& Charlesworth, D. 1999.
+\newblock {The genetic basis of inbreeding depression}.
+\newblock \textit{Genet. Res.} \textbf{74}:329--340.
+
+\bibitem[{Charlesworth \& Willis(2009)}]{Charlesworth2009}
+Charlesworth, D. \& Willis, J.~H. 2009.
+\newblock {The genetics of inbreeding depression}.
+\newblock \textit{Nat. Rev. Genet.} \textbf{10}:783--796.
+
+\bibitem[{Daniel \& Rodd(2015)}]{Daniel2015}
+Daniel, M.~J. \& Rodd, F.~H. 2015.
+\newblock {Female guppies can recognize kin but only avoid incest when
+  previously mated}.
+\newblock \textit{Behav. Ecol.} \textbf{27}:55--61.
+
+\bibitem[{Duthie \textit{et~al.}(2016)Duthie, Bocedi, \& Reid}]{Duthie}
+Duthie, A.~B., Bocedi G. \& Reid, J.~M. 2016.
+\newblock {When does female multiple mating evolve to adjust inbreeding?
+  Effects of inbreeding depression, direct costs, mating constraints, and
+  polyandry as a threshold trait}.
+\newblock \textit{Evolution} \textbf{70}:1927--1943.
+
+\bibitem[{Duthie \& Reid(2015)}]{Duthie2015a}
+Duthie, A.~B. \& Reid, J.~M. 2015.
+\newblock {What happens after inbreeding avoidance? Inbreeding by rejected
+  relatives and the inclusive fitness benefit of inbreeding avoidance}.
+\newblock \textit{PLoS One} \textbf{10}:e0125140.
+
+\bibitem[{Duthie \& Reid(2016)}]{Duthie2016a}
+Duthie, A.~B. \& Reid, J.~M. 2016.
+\newblock {Evolution of inbreeding avoidance and inbreeding preference through
+  mate choice among interacting relatives}.
+\newblock \textit{Am. Nat.} \textbf{188}:651--667.
+
+\bibitem[{Edelman \& Gally(2001)}]{Edelman2001}
+Edelman, G.~M. \& Gally, J.~A. 2001.
+\newblock {Degeneracy and complexity in biological systems}.
+\newblock \textit{Proc. Natl. Acad. Sci. USA} \textbf{98}:13763--13768.
+
+\bibitem[{Firman \& Simmons(2008)}]{Firman2008}
+Firman, R.~C. \& Simmons, L.~W. 2008.
+\newblock {Polyandry facilitates postcopulatory inbreeding avoidance in house
+  mice}.
+\newblock \textit{Evolution} \textbf{62}:603--611.
+
+\bibitem[{Firman \& Simmons(2015)}]{Firman2015}
+Firman, R.~C. \& Simmons, L.~W. 2015.
+\newblock {Gametic interactions promote inbreeding avoidance in house mice}.
+\newblock \textit{Ecol. Lett.} \textbf{18}:937--943.
+
+\bibitem[{Fischer \textit{et~al.}(2015)Fischer, Karl, Heuskin, Janowitz, \&
+  D{\"{o}}tterl}]{Fischer2015}
+Fischer, K., Karl, I., Heuskin, S., Janowitz, S. \& D{\"{o}}tterl, S. 2015.
+\newblock {Kin recognition and inbreeding avoidance in a butterfly}.
+\newblock \textit{Ethology} \textbf{121}:977--984.
+
+\bibitem[{Fitzpatrick \& Evans(2014)}]{Fitzpatrick2014b}
+Fitzpatrick, J.~L. \& Evans, J.~P. 2014.
+\newblock {Postcopulatory inbreeding avoidance in guppies}.
+\newblock \textit{J. Evol. Biol.} \textbf{27}:2585--2594.
+
+\bibitem[{Foerster \textit{et~al.}(2003)Foerster, Delhey, Johnsen, Lifjeld, \&
+  Kempenaers}]{Foerster2003}
+Foerster, K., Delhey K., Johnsen, A., Lifjeld, J.~T. \& Kempenaers B. 2003.
+\newblock {Females increase offspring heterozygosity and fitness through
+  extra-pair matings}.
+\newblock \textit{Nature} \textbf{425}:714--717.
+
+\bibitem[{Gardner \& Kalinka(2006)}]{Gardner2006}
+Gardner, A. \& Kalinka, A.~T. 2006.
+\newblock {Recombination and the evolution of mutational robustness}.
+\newblock \textit{J. Theor. Biol.} \textbf{241}:707--715.
+
+\bibitem[{Gasparini \& Pilastro(2011)}]{Gasparini2011}
+Gasparini, C. \& Pilastro, A. 2011.
+\newblock {Cryptic female preference for genetically unrelated males is
+  mediated by ovarian fluid in the guppy.}
+\newblock \textit{Proc. Biol. Sci.} \textbf{278}:2495--2501.
+
+\bibitem[{Greeff \textit{et~al.}(2009)Greeff, Vuuren, Kryger \& Moore}]{Greeff2009}
+Greeff, J.~M., Jansen van Vuuren, G.~J., Kryger, P. \& Moore, J.~C. 2009.
+\newblock {Outbreeding and possibly inbreeding depression in a pollinating fig
+  wasp with a mixed mating system}.
+\newblock \textit{Heredity} \textbf{102}:349--356.
+
+\bibitem[{Guillaume \& Perrin(2009)}]{Guillaume2009}
+Guillaume, F. \& Perrin, N. 2009.
+\newblock {Inbreeding load, bet hedging, and the evolution of sex-biased
+  dispersal.}
+\newblock \textit{Am. Nat.} \textbf{173}:536--541.
+
+\bibitem[{Jennions \& Petrie(2000)}]{Jennions2000}
+Jennions, M.~D. \& Petrie, M. 2000.
+\newblock {Why do females mate multiply? A review of the genetic benefits}.
+\newblock \textit{Biol. Rev. Camb. Philos. Soc.} \textbf{75}:21--64.
+
+\bibitem[{Keller \& Waller(2002)}]{Keller2002}
+Keller, L.~F. \& Waller,  D.~M. 2002.
+\newblock {Inbreeding effects in wild populations}.
+\newblock \textit{Trends Ecol. Evol.} \textbf{17}:19--23.
+
+\bibitem[{Kimura(1965)}]{Kimura1965}
+Kimura, M. 1965.
+\newblock {A stochastic model concerning the maintenance of genetic variability
+  in quantitative characters}.
+\newblock \textit{Proc. Natl. Acad. Sci. USA} \textbf{54}:731--736.
+
+\bibitem[{Kingma \textit{et~al.}(2013)Kingma, Hall \& Peters}]{Kingma2013}
+Kingma, S.~A., Hall, M.~L. \& Peters A. 2013.
+\newblock {Breeding synchronization facilitates extrapair mating for inbreeding
+  avoidance}.
+\newblock \textit{Behav. Ecol.} \textbf{24}:1390--1397.
+
+\bibitem[{Koga \textit{et~al.}(1998)Koga, Backwell, Jennions \& Christy}]{Koga1998}
+Koga, T., Backwell, P.~R.~Y., Jennions, M.~D. \& Christy J.~H. 1998.
+\newblock {Elevated predation risk changes mating behaviour and courtship in a
+  fiddler crab}.
+\newblock \textit{Proc. Biol. Sci.} \textbf{265}:1385--1390.
+
+\bibitem[{Kokko \textit{et~al.}(2003)Kokko, Brooks, Jennions \& Morley}]{Kokko2003}
+Kokko, H., Brooks R., Jennions M.~D. \& Morley J. 2003.
+\newblock {The evolution of mate choice and mating biases.}
+\newblock \textit{Proc. Biol. Sci.} \textbf{270}:653--664.
+
+\bibitem[{Kokko \& Mappes(2013)}]{Kokko2013}
+Kokko, H. \& Mappes, J. 2013.
+\newblock {Multiple mating by females is a natural outcome of a null model of
+  mate encounters}.
+\newblock \textit{Entomol. Exp. Appl.} \textbf{146}:26--37.
+
+\bibitem[{Kokko \& Ots(2006)}]{Kokko2006}
+Kokko, H., \& Ots, I. 2006.
+\newblock {When not to avoid inbreeding}.
+\newblock \textit{Evolution} \textbf{60}:467--475.
+
+\bibitem[{Kuriwada \textit{et~al.}(2011)Kuriwada, Kumano, Shiromoto \&
+  Haraguchi}]{Kuriwada2011}
+Kuriwada, T., Kumano, N., Shiromoto, K. \& Haraguchi, D. 2011.
+\newblock {Inbreeding avoidance or tolerance? Comparison of mating behavior
+  between mass-reared and wild strains of the sweet potato weevil}.
+\newblock \textit{Behav. Ecol. Sociobiol.} \textbf{65}:1483--1489.
+
+\bibitem[{Lande(1976)}]{Lande1976}
+Lande, R. 1976.
+\newblock {The maintenance of genetic variability by mutation in a polygenic
+  character with linked loci}.
+\newblock \textit{Genet. Res.} \textbf{36}:221--235.
+
+\bibitem[{Lehtonen \& Kokko(2015)}]{Lehtonen2015}
+Lehtonen, J. \& Kokko, H. 2015.
+\newblock {Why inclusive fitness can make it adaptive to produce less fit
+  extra-pair offspring}.
+\newblock \textit{Proc. Biol. Sci.} \textbf{282}:20142716.
+
+\bibitem[{Levin \& Lubchenco(2008)}]{Levin2008}
+Levin, S.~A. \& Lubchenco, J. 2008.
+\newblock {Resilience, robustness, and marine ecosystem-based management}
+\newblock \textit{BioScience} \textbf{58}:27--32.
+
+\bibitem[{Lihoreau \textit{et~al.}(2007)Lihoreau, Zimmer \& Rivault}]{Lihoreau2007}
+Lihoreau, M., Zimmer, C. \& Rivault, C. 2007.
+\newblock {Kin recognition and incest avoidance in a group-living insect}.
+\newblock \textit{Behav. Ecol.} \textbf{18}:880--887.
+
+\bibitem[{Liu \textit{et~al.}(2014)Liu, Tu, He, Chen \& Xue}]{Liu2014}
+Liu, X., Tu, X., He, H., Chen, C. \& Xue, F. 2014.
+\newblock {Evidence for inbreeding depression and pre-copulatory, but not post
+  copulatory inbreeding avoidance in the cabbage beetle \textit{Colaphellus bowringi}.}
+\newblock \textit{PloS one} \textbf{9}:e94389.
+
+\bibitem[{Lynch \& Walsh(1998)}]{Lynch1998}
+Lynch, M. \& Walsh, B. 1998.
+\newblock {\textit{Genetics and Analysis of Quantitative Traits}}.
+\newblock Sinauer, Sunderland.
+
+\bibitem[{Metzger \textit{et~al.}(2010{\natexlab{\emph{a}}})Metzger, Bernstein,
+  Hoffmeister \& Desouhant}]{Metzger2010}
+Metzger, M., Bernstein, C., Hoffmeister, T.~S. \& Desouhant, E.
+  2010{\natexlab{\emph{a}}}.
+\newblock {Does kin recognition and sib-mating avoidance limit the risk of
+  genetic incompatibility in a parasitic wasp?}
+\newblock \textit{PLoS One} \textbf{5}:1--6.
+
+\bibitem[{Metzger \textit{et~al.}(2010{\natexlab{\emph{b}}})Metzger, Fischbein, Auguste,
+  Fauvergue, Bernstein \& Desouhant}]{Metzger2010a}
+Metzger, M., Fischbein, D., Auguste, A., Fauvergue, X., Bernstein, C., \&
+  Desouhant, E. 2010{\natexlab{\emph{b}}}.
+\newblock {Synergy in information use for mate finding: Demonstration in a
+  parasitoid wasp}.
+\newblock \textit{Anim. Behav.} 79:1307--1315.
+
+\bibitem[{Mills \& Smouse(1994)}]{Mills1994}
+Mills, L.~S. \& Smouse, P.~E. 1994.
+\newblock {Demographic consequences of inbreeding in remnant populations}.
+\newblock \textit{Am. Nat.} \textbf{144}:412--431.
+
+\bibitem[{Morton et~al.(1956)Morton, Crow \& Muller}]{Morton1956}
+Morton, N.~E., Crow, J.~F., \& Muller, H.~J. 1956.
+\newblock {An estimate of the mutational damage in man from data on
+  consanguineous marriages}.
+\newblock \textit{Proc. Natl. Acad. Sci. USA} \textbf{42}:855--863.
+
+\bibitem[{Nowak \textit{et~al.}(1997)Nowak, Boerlijst, Cooke, \& {Maynard
+  Smith}}]{Nowak1997}
+Nowak, M.~A., Boerlijst, M.~C., Cooke, J. \& {Maynard Smith}, J. 1997.
+\newblock {Evolution of genetic redundancy}.
+\newblock \textit{Nature} \textbf{388}:167--171.
+
+\bibitem[{Park \& Friston(2013)}]{Park2013}
+Park, H.~J. \& Friston, K.~J. 2013.
+\newblock {Structural and functional brain networks: from connections to
+  cognition.}
+\newblock \textit{Science} \textbf{342}:1238411.
+
+\bibitem[{Parker(1979)}]{Parker1979}
+Parker, G.~A. 1979.
+\newblock {Sexual selection and sexual conflict}.
+\newblock Pages 123--166 \emph{in} M.~S. Blum \& N.~A. Blum, eds. \textit{Sexual
+  selection and reproductive competition in insects}. Academic Press, Inc, New
+  York.
+
+\bibitem[{Parker(2006)}]{Parker2006}
+Parker, G.~A. 2006.
+\newblock {Sexual conflict over mating and fertilization: an overview}.
+\newblock \textit{Phil. Trans. R. Soc. Lond. B Biol. Sci.} \textbf{361}:235--259.
+
+\bibitem[{Pizzari \textit{et~al.}(2004)Pizzari, L{\o}vlie, \& Cornwallis}]{Pizzari2004}
+Pizzari, T., L{\o}vlie, H. \& Cornwallis, C.~K. 2004.
+\newblock {Sex-specific, counteracting responses to inbreeding in a bird}.
+\newblock \textit{Proc. Biol. Sci.} \textbf{271}:2115--2121.
+
+\bibitem[{Pomiankowski(1987)}]{Pomiankowski1987}
+Pomiankowski, A. 1987.
+\newblock {The costs of choice in sexual selection}.
+\newblock \textit{J. Theor. Biol.} \textbf{128}:195--218.
+
+\bibitem[{Potts \textit{et~al.}(1991)Potts, Manning \& Wakeland}]{Potts1991}
+Potts, W.~K., Manning, C.~J. \& Wakeland, E.~K. 1991.
+\newblock {Mating patterns in seminatural populations of mice influenced by MHC
+  genotype}.
+\newblock \textit{Nature} \textbf{352}:619--621.
+
+\bibitem[{Price \& Friston(2002)}]{Price2002}
+Price, C.~J. \& Friston, K.~J. 2002.
+\newblock {Degeneracy and cognitive anatomy}.
+\newblock \textit{Trends Cogn. Sci.} \textbf{6}:416--421.
+
+\bibitem[{Pusey \& Wolf(1996)}]{Pusey1996}
+Pusey, A., \& Wolf, M. 1996.
+\newblock {Inbreeding avoidance in animals}.
+\newblock \textit{Trends Ecol. Evol.} \textbf{5347}:298--301.
+
+\bibitem[{Reeve(2000)}]{Reeve2000}
+Reeve, J.~P. 2000.
+\newblock {Predicting long-term response to selection}.
+\newblock \textit{Genet. Res.} \textbf{75}:83--94.
+
+\bibitem[{Reid(2015)}]{Reid2015a}
+Reid, J.~M. 2015.
+\newblock {What can we really say about relatedness and extrapair paternity: a
+  comment on Arct \textit{et al}}.
+\newblock \textit{Behav. Ecol.} \textbf{26}:969--970.
+
+\bibitem[{Reid \textit{et~al.}(2015{\natexlab{\emph{a}}})Reid, Arcese, Keller, Germain,
+  Duthie, Losdat, Wolak \& Nietlisbach}]{Reid2014}
+Reid, J.~M., Arcese, P., Keller, L.~F., Germain, R.~R., Duthie, A.~B., Losdat, S.,
+  Wolak, M.~E. \& Nietlisbach, P. 2015{\natexlab{\emph{a}}}.
+\newblock {Quantifying inbreeding avoidance through extra-pair reproduction}.
+\newblock \textit{Evolution} \textbf{69}:59--74.
+
+\bibitem[{Reid \textit{et~al.}(2015{\natexlab{\emph{b}}})Reid, Duthie, Wolak \&
+  Arcese}]{Reid2015}
+Reid, J.~M., Duthie, A.~B., Wolak, M.~E. \& Arcese, P.
+  2015{\natexlab{\emph{b}}}.
+\newblock {Demographic mechanisms of inbreeding adjustment through extra-pair
+  reproduction}.
+\newblock \textit{J. Anim. Ecol.} \textbf{84}:1029--1040.
+
+\bibitem[{Roberts \textit{et~al.}(2015)Roberts, Evison, Baer \& Hughes}]{Roberts2015a}
+Roberts, K.~E., Evison, S.~E.~F., Baer, B. \& Hughes, W.~O.~H. 2015.
+\newblock {The cost of promiscuity: sexual transmission of \textit{Nosema
+  microsporidian} parasites in polyandrous honey bees}.
+\newblock \textit{Sci. Rep.} \textbf{5}:10982.
+
+\bibitem[{Roff(1996)}]{Roff1996}
+Roff, D.~A. 1996.
+\newblock {The evolution of threshold traits in animals}.
+\newblock \textit{Q. Rev. Biol.} \textbf{71}:3--35.
+
+\bibitem[{Roff(1998)}]{Roff1998}
+Roff, D.~A. 1998.
+\newblock {Evolution of threshold traits: the balance between directional
+  selection, drift and mutation}.
+\newblock \textit{Heredity} \textbf{80}:25--32.
+
+\bibitem[{Ronkainen \& Ylonen(1994)}]{Ronkainen1994}
+Ronkainen, H. \& Ylonen, H. 1994.
+\newblock {Behaviour of cyclic bank voles under risk of mustelid predation: Do
+  females avoid copulations?}
+\newblock \textit{Oecologia} \textbf{97}:377--381.
+
+\bibitem[{Rowe(1988)}]{Rowe1988}
+Rowe, L. 1988.
+\newblock {Cost of mating for female insects: risk of predation in \textit{Photinus
+  collustrans} (Coleoptera: Lampyridae)}.
+\newblock \textit{Am. Nat.} \textbf{121}:139--142.
+
+\bibitem[{Rowe \textit{et~al.}(1994)Rowe, Arnqvist, Sih \& Krupa}]{Rowe1994}
+Rowe, L., Arnqvist, G., Sih, A. \& Krupa, J.~J. 1994.
+\newblock {Sexual conflict and the evolutionary ecology of mating patterns:
+  water striders as a model system}.
+\newblock \textit{Trends Ecol. Evol.} \textbf{9}:289--293.
+
+\bibitem[{Simmons \textit{et~al.}(2006)Simmons, Beveridge, Wedell \&
+  Tregenza}]{Simmons2006}
+Simmons, L.~W., Beveridge, M., Wedell, N. \& Tregenza, T. 2006.
+\newblock {Postcopulatory inbreeding avoidance by female crickets only revealed
+  by molecular markers}.
+\newblock \textit{Mol. Ecol.} \textbf{15}:3817--3824.
+
+\bibitem[{Suraci \textit{et~al.}(2017)Suraci, Clinchy \& Zanette}]{Suraci2017}
+Suraci, J.~P., Clinchy, M. \& Zanette, L.~Y. 2017.
+\newblock {Do large carnivores and mesocarnivores have redundant impacts on
+  intertidal prey?}
+\newblock \textit{PLoS One} \textbf{12}:e0170255.
+
+\bibitem[{Szulkin \textit{et~al.}(2013)Szulkin, Stopher, Pemberton \&
+  Reid}]{Szulkin2012}
+Szulkin, M., Stopher, K.~V., Pemberton, J.~M. \& Reid, J.~M. 2013.
+\newblock {Inbreeding avoidance, tolerance, or preference in animals?}
+\newblock \textit{Trends Ecol. Evol.} \textbf{28}:205--211.
+
+\bibitem[{Tan \textit{et~al.}(2012)Tan, L{\o}vlie, Pizzari \& Wigby}]{Tan2012}
+Tan, C. K.~W., L{\o}vlie, H., Pizzari, T. \& Wigby, S. 2012.
+\newblock {No evidence for precopulatory inbreeding avoidance in \textit{Drosophila
+  melanogaster}}.
+\newblock \textit{Anim. Behav.} \textbf{83}:1433--1441.
+
+\bibitem[{Tregenza \& Wedell(2002)}]{Tregenza2002}
+Tregenza, T. \& Wedell, N. 2002.
+\newblock {Polyandrous females avoid costs of inbreeding}.
+\newblock \textit{Nature} \textbf{415}:71--73.
+
+\bibitem[{Tuni \textit{et~al.}(2013)Tuni, Beveridge \& Simmons}]{Tuni2013}
+Tuni, C., Beveridge, M. \& Simmons, L.~W. 2013.
+\newblock {Female crickets assess relatedness during mate guarding and bias
+  storage of sperm towards unrelated males}.
+\newblock \textit{J. Evol. Biol.} \textbf{26}:1261--1268.
+
+\bibitem[{Varian-Ramos \& Webster(2012)}]{Varian-Ramos2012}
+Varian-Ramos, C.~W. \& Webster, M.~S. 2012.
+\newblock {Extrapair copulations reduce inbreeding for female red-backed
+  fairy-wrens, \textit{Malurus melanocephalus}}.
+\newblock \textit{Anim. Behav.} \textbf{83}:857--864.
+
+\bibitem[{Whitacre \& Bender(2010)}]{Whitacre2010}
+Whitacre, J. \& Bender, A. 2010.
+\newblock {Degeneracy: A design principle for achieving robustness and
+  evolvability}.
+\newblock \textit{J. Theor Biol.} \textbf{263}:143--153.
+
+\bibitem[{Whitacre(2010)}]{Whitacre2010a}
+Whitacre, J.~M. 2010.
+\newblock {Degeneracy: a link between evolvability, robustness and complexity
+  in biological systems}.
+\newblock \textit{Theor. Biol. Med. Model.} \textbf{7}:6.
+
+\bibitem[{Zeh \& Zeh(1997)}]{Zeh1997}
+Zeh, J.~A. \& Zeh, D.~W. 1997.
+\newblock {The evolution of polyandry II: post-copulatory defenses against
+  genetic incompatibility}.
+\newblock \textit{Proc. Biol. Sci.} \textbf{264}:69--75.
+
+\end{thebibliography}
+
+%\end{small}
 

### 2017-04-28 ms_pre_post.Rmd
Clean some things off before starting on new version

@@
 author: ''
-date: "5 April 2017"
+date: "28 April 2017"
 output:
@@
 ******************************
-
-<!--- 
-General notes about this version:
-
-If we're interested in evolution and not selection (hence the phrasing), and not wanting to assume that the latter strictly implies the former (as of course is sometimes the case in nature), then we really need to put more energy into looking at the assumptions underlying genetic variance, and other things having to do with quantitative genetics.
-At the moment, we're just assuming that there is pretty much always enough genetic variance on which selection to act.
-I've assumed we'd be most interested in selection given three reproductive strategy traits, but if we're interested in evolvability of traits, then I think we're ignoring some key things.
-Hence my previous concerns about the theoretical question really not being entirely clear here.
-
-I think people will have a problem with our approach if it is not clear why our approach is the best one for addressing our key questions.
-I sometimes see researchers using a population, adaptive dynamic, individual-based, etc., not because it is the appropriate model for addressing their question, but because it's the one with which they are most familiar.
-As a result, models can become mathematically intractable (should have used an IBM) or conceptually incoherent (should have simplified in some way).
-We need to be able to make it clear why we are using such a complex individual-based model instead of something else.
-
-My concern with some unusual highlighting of assumptions isn't (of course) that we're going to make some readers less confused.
-My concern is that we're going to make some readers *more* confused.
-Theoretically literate readers might be confused by some of the assumptions we keep coming back to, thinking that we're making a biological point about their relative importance that I don't think we are.
-I don't want to write a paper just that gets through review by playing to people's misconceptions (even if those who hold such misconceptions are the majority) because it rienforces the idea that those misconceptions are justified.
-If we continue to do this, then writing and publishing good theory will get even more difficult in the future.
-Increasingly I fear that I am doing my colleagues who work on theory a disservice by writing papers that placating people's concerns rather than articulating why (some, but of course not all) these concerns are misplaced, and hence setting a bad precedent.
-
-Hence, when we explain why a cost of 0.02 is appropriate, we are giving readers the impression that its value really needed to be justified.
-I would much prefer to explain why this isn't necessarily the case, and what a cost means in the context of exploring theory, so as to avoid reviewers of other papers point to Duthie et al.
-(XXXX) and say, ''they justified their cost, so you should have to as well!''.
-I tend to see the same thing for mutation rates -- the whole point of setting a mutation rate (usually to 0.001, for purely arbitrary reasons) is to introduce a bit of variation and see what happens.
-The exact rate is inconsequential with respect to most theoretical questions that models address (i.e., changing it might changes outcomes a bit, perhaps even qualitatively, but it would not change how peoples *thinking* and *conceptualisation* of biology would be affected by the model).
-If a reader is worried about the exact rate of mutation then they probably aren't actually understanding the point of the model.
-
-Honestly, I also think that some of our wording here is a bit insulting to empirical biologists, many of whom are quite capable of reading, understanding, and applying theory.
-
-The empirical examples almost make this worse.
-It seems like part of our point in the discussion is that indirection selection on polyandry via post-copulatory inbreeding avoidance is possible, but then we already knew that as a result of the empirical examples.
-Why did we need this model?
-We need to explain what it is that the model adds in terms of interpretation and theoretical understanding.
-Just recreating something already observed in empirical studies isn't particularly helpful.
-
---->
 

### 2017-04-28 ms_pre_post.Rmd
Make edits from Greta's comments

@@
 Further, fixed pre-copulatory inbreeding avoidance generally precluded evolution of polyandry and therefore post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance.
-We thereby provide a general framework for understanding joint evolution of pre-copulatory and/or post-copulatory inbreeding avoidance, and conclude that evolution of inbreeding avoidance phenotypes and associated polyandry are predicted to be strongly affected by evolutionary feedbacks and degeneracy, and by direct costs on phenotypes affecting reproductive strategy.
+Evolution of inbreeding avoidance phenotypes and associated polyandry are likely to be affected by evolutionary feedbacks and degeneracy.
+All else being equal, while evolution of pre-copulatory inbreeding avoidance and associated low polyandry is more likely when pre-copulatory inbreeding avoidance is precluded or costly, evolution of post-copulatory inbreeding avoidance greatly facilitates evolution of costly polyandry.
 
@@
 
-From the perspective of a focal breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
-Evolution of post-copulatory inbreeding avoidance requires that females express some non-trivial degree of polyandry, defined as mating with multiple males during a single reproductive bout.
+From the perspective of a breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
+Evolution of post-copulatory inbreeding avoidance requires that females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout.
 Further, given inbreeding depression, such polyandry might itself be under selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative.
@@
 Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002].
-Resulting indirect selection on polyandry could explain its evolution in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct fitness costs on polyandrous females.
+Resulting indirect selection on polyandry to increase offspring fitness could explain its evolution in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct fitness costs on polyandrous females.
 However, despite such widely-invoked hypotheses, there is surprising little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
 
-Despite the paucity of theory and resulting predictions, numerous empirical studies on diverse species have tested for, and in some cases found evidence of, female inbreeding avoidance in systems where polyandry also occurs [@Tregenza2002; @Varian-Ramos2012; @Kingma2013; @Arct2015; but see @Reid2015a].
+Despite the paucity of theory, numerous empirical studies on diverse species have tested for, and in some cases found evidence of, female inbreeding avoidance in systems where polyandry also occurs [@Tregenza2002; @Varian-Ramos2012; @Kingma2013; @Arct2015; but see @Reid2015a].
 However, relatively few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
@@
 However, there is as yet no theory that predicts what combinations of pre-copulatory and post-copulatory inbreeding avoidance and polyandry should be favoured by selection when all combinations of phenotypes can evolve.
-Consequently, there is no theory that allows the diversity of existing empirical results regarding pre-copulatory and post-copulatory inbreeding avoidance to be interpreted, and no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
+Consequently, there is no theory that allows the diversity of observed pre-copulatory and post-copulatory inbreeding avoidance to be interpreted, and no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
 
-To develop theory on evolution of polyandry given inbreeding depression, @Duthie used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance.
+@Duthie used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance.
 Net selection for polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., 'costs') on polyandry was weak, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
-Without these conditions, increasing polyandry tended to increase rather than decrease the overall degree of inbreeding that females experienced, and hence reduce offspring fitness.
+Without these conditions, and without the possibility for post-copulatory female choice, increasing polyandry tended to increase rather than decrease the overall degree of inbreeding that females experienced, and hence reduce offspring fitness.
 This occurred because, once pre-copulatory inbreeding avoidance evolved, polyandrous females had already chosen available unrelated males as their initial mates.
@@
 Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance, and hence the resulting degree of inbreeding avoidance, was consequently restricted [@Duthie].
+If post-copulatory inbreeding avoidance could also evolve, polyandrous females would have the opportunity to bias paternity towards unrelated males within their set of chosen mates.
+Evolution of post-copulatory inbreeding avoidance might consequently reduce the cost of polyandry stemming from the accumulation of related mates across multiple matings, potentially facilitating evolution of polyandry to avoid inbreeding under broader conditions, and driving further evolution of pre-copulatory or post-copulatory mate choice strategies.
 
-However, if post-copulatory inbreeding avoidance could also evolve, polyandrous females would also have an opportunity to bias paternity towards unrelated males within their set of chosen mates.
-Evolution of post-copulatory inbreeding avoidance might consequently reduce the cost of polyandry stemming from the accumulation of related mates across multiple matings, potentially facilitating evolution of polyandry to avoid inbreeding under broader conditions, and driving further evolution of pre-copulatory or post-copulatory mate choice strategies.
 However, if polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, the long-term dynamics of these three reproductive strategies become difficult to predict.
@@
 By addressing these questions, we illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
-We thereby provide a framework for deriving hypotheses amenable to empirical tests within and across taxa.
 

### 2017-04-28 ms_pre_post.Rmd
Add Greta's comments up to Results

@@
 
-We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply 'inbreeding strategies' because the model did not preclude evolution of inbreeding preference), by tracking the dynamics of alleles underlying reproductive strategies enacted by interacting females and males within a small focal population.
+We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply 'inbreeding strategies' because the model did not preclude evolution of inbreeding preference), in a small focal population of females and males by tracking the dynamics of alleles underlying reproductive strategies expressed by females.
 We thereby track evolutionary dynamics given internally consistent patterns of relatedness caused by non-random mating and allowing for effects of mutation, gene flow, drift, and selection.
-Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$, i.e., 'polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., 'fertilisation' alleles).
-All alleles can take the value of any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014] and combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively, whereby an individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
-In overview, each generation proceeds with females paying costs and expressing polyandry, mating, and fertilisation.
-Offspring inherit a randomly sampled allele from each parent at each locus with no physical linkage.
+All individuals have 10 physically unlinked diploid loci, and therefore 20 alleles, underlying each of three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$, i.e., 'polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., 'fertilisation' alleles).
+All alleles can take the value of any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014] and combine additively to determine genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively, whereby an individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
+Phenotype values $M_{p} = M_{g}$ and $F_{p} = F_{g}$, where negative and positive values cause inbreeding avoidance and preference, respectively (see details of mating and fertilisation strategies below).
+In contrast, $P_{p} = P_{g}$ only if $P_{g} \geq 0$ to cause increasingly greater tendency for polyandry, while $P_{p} = 0$ if $P_{g} < 0$ because females cannot choose a negative number of mates (see details of polyandry below).
+Polyandry is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998; @Duthie] that is influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
+Any negative $P_{g}$ value therefore generates phenotypic monandry, while positive $P_{g}$ values can lead to different degrees of realised polyandry (i.e., different numbers of mates, $N_{males}$).
+
+In overview, each generation proceeds with females paying costs related to their reproductive strategy.
+Offspring inherit a randomly sampled allele from each parent at each locus.
 Alleles can then mutate and offspring express inbreeding depression in viability.
@@
 
-Phenotypic values of $P_{p}$, $M_{p}$, and $F_{p}$ each have costs that are assumed to independently increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
+Phenotypic values have costs that are assumed to combine independently to increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
 The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
 Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
-Absolute values are used for applying costs to inbreeding avoidance strategies because both negative and positive $M_{p}$ and $F_{p}$ values could potentially arise and affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively (see details of mating and fertilisation strategies below).
-In contrast, only positive values of $P_{p}$ cause females to be polyandrous (see details of polyandry below).
+Absolute values are used for applying costs to inbreeding avoidance strategies because both negative and positive $M_{p}$ and $F_{p}$ values could potentially arise and affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively.
 Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
 
-Polyandry
+Mating and pre-copulatory inbreeding avoidance
 ----------------------------------------------
@@
 This ensures that all surviving females choose at least one mate, and causes some stochastic variation around the expected mean $N_{males}$ of $P_{p}+1$.
-A female's value of $P_{p}$ depends on the sum of her 20 $P_{a}$ allele values (i.e., $P_{g}$), which might be negative or positive.
-However, because females cannot mate with a negative number of males, $P_{p}$ is constrained to be zero or positive such that $P_{p} = 0$ when $P_{g} < 0$, but $P_{p} = P_{g}$ when $P_{g} \geq 0$.
-Polyandry is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998; @Duthie] that is influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
-Any negative $P_{g}$ value therefore generates phenotypic monandry, while positive $P_{g}$ values can lead to different degrees of realised polyandry (i.e., different numbers of mates, $N_{males}$).
-
-Mating and pre-copulatory inbreeding avoidance
-----------------------------------------------
 
@@
 We therefore assume that there is no opportunity cost of male mating, so mating with one female does not reduce a male's availability to mate with any other female.
-Individual females mate with their total allotment of $N_{males}$ without replacement, meaning that $N_{males}$ models a female's total number of different mates rather than solely her total number of matings.
+Females mate with $N_{males}$ without replacement, meaning that $N_{males}$ models a female's total number of different mates rather than solely her total number of matings.
 
@@
 
-To calculate the probability that a focal female $i$ mates with a male $j$ to whom she is related by some kinship $k_{ij}$, each male is first assigned a perceived mate quality $Q^{m}_{ij}$.
+To calculate the probability that a female $i$ mates with a male $j$ to whom she is related by some kinship $k_{ij}$, each male is first assigned a perceived mate quality $Q^{m}_{ij}$.
 If the female has a strategy of pre-copulatory inbreeding avoidance ($M_{p}<0$), then $Q^{m}_{ij} = (-M_{p} \times k_{ij} + 1)^{-1}$, meaning that $Q^{m}_{ij}$ decreases linearly with increasingly positive values of $k_{ij}$ and increasingly negative values of $M_{p}$.
@@
 
-Each male's value with respect to a focal female is then divided by the sum of all $Q^{m}_{ij}$ values across all males with respect to that female, thereby assigning each male a relative perceived quality $q^{m}_{ij}$, which is constrained to values between zero and one.
-The value of $q^{m}_{ij}$ then defines the probability that a focal female mates with the male.
+Each male's value with respect to a female $i$ is then divided by the sum of all $Q^{m}_{ij}$ values across all males with respect to that female, thereby assigning each male a relative perceived quality $q^{m}_{ij}$, which is constrained to values between zero and one.
+The value of $q^{m}_{ij}$ then defines the probability that female $i$ mates with male $j$.
 Mating is therefore stochastic, and females do not always mate with the male of the highest $q^{m}_{ij}$.
@@
 Following mating, fertilisation occurs such that each of a female's $n$ offspring is independently assigned a sire (with replacement) from the $N_{males}$ with which the female mated.
-Sire identity depends on female's kinship with each mate ($k_{ij}$) and her post-copulatory inbreeding strategy phenotype ($F_{p}$), which equals her genotype ($F_{g}$).
+Sire identity depends on female's kinship with each mate ($k_{ij}$) and her post-copulatory inbreeding strategy phenotype ($F_{p}$).
 Negative and positive values of $F_{p}$ correspond to post-copulatory inbreeding avoidance or preference, respectively, whereas $F_{p}=0$ causes random fertilisation with respect to kinship.
 
-The probability that an offspring of a focal female $i$ is sired by any one of $i$'s mates $j$ is calculated by assigning a perceived fertilisation quality to each $j$ with respect to $i$, $Q^{f}_{ij}$.
-Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if a focal female has a strategy of post-copulatory inbreeding avoidance ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$.
-If the focal female has strategy of post-copulatory inbreeding preference ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$.
+The probability that an offspring of female $i$ is sired by any one of $i$'s mates $j$ is calculated by assigning a perceived fertilisation quality to each $j$ with respect to $i$, $Q^{f}_{ij}$.
+Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if female $i$ has a strategy of post-copulatory inbreeding avoidance ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$.
+If the female has strategy of post-copulatory inbreeding preference ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$.
 A relative quality ($q^{f}_{ij}$) is then calculated for each male by dividing his $Q^{f}_{ij}$ by the sum of the $Q^{f}_{ij}$ values across all of a female's mates.
 These $q^{f}_{ij}$ values, which lie between zero and one, define the probability of paternity.
-Females produce $n$ offspring, so $q^{f}_{ij}$ values are sampled $n$ times independently and with replacement for each female to determine the realised distribution of sires.
+Females produce $n$ offspring, so a female $i$ samples from her mates $n$ times independently and with replacement with a probability of $q^{f}_{ij}$ for each male $j$ to determine the realised distribution of sires.
+Offspring produced have equal probability of being female or male.
 
@@
 
-The viability of a focal female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a log-linear function of her kinship with the sire $j$ of the offspring ($k_{ij}$) and inbreeding depression slope $\beta$,
+The viability of a female $i$'s offspring ($\Psi_{\textrm{off}}$) decreases as a log-linear function of her kinship with the sire $j$ of the offspring ($k_{ij}$) and inbreeding depression slope $\beta$,
 \begin{equation}
@@
 Further, immigrants' $P_{a}$, $M_{a}$, and $F_{a}$ allele values are randomly sampled from normal distributions with means and standard deviations equal to those in the focal population at the time of immigration, meaning that they do not directly cause any change in the distribution of allele values.
-We thereby effectively assume that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$.
+We thereby effectively assume that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$ [@Duthie; @Duthie2016a].
 
@@
 To address how selection on an initially rare strategy of pre-copulatory or post-copulatory inbreeding avoidance, and resulting evolution, is affected by the other strategy of inbreeding avoidance already being fixed in the population, we first used exploratory simulations to quantify evolution of pre-copulatory inbreeding strategy, and of post-copulatory inbreeding strategy and associated polyandry, in isolation.
-Then, to test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance were fixed, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., meaning that $F_{p}$ and $P_{p}$ were expressed did not evolve further).
+Then, to test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance were fixed, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., $F_{p}$ and $P_{p}$ were expressed did not evolve further).
 Similarly, to test whether post-copulatory inbreeding avoidance would evolve when pre-copulatory inbreeding avoidance was already fixed, we initiated $F_{a}$ and $P_{a}$ allele values at zero but fixed $M_{a}$ allele values at $-10$.
@@
 ******************************
+
+<!--- --------------------------------------------------------------------- --->
+<!--- ========== LEFT OFF HERE ============================================ --->
+<!--- --------------------------------------------------------------------- --->
 

### 2017-04-28 ms_pre_post.Rmd
Add Greta's comments up to Discussion

@@
 
-<!--- --------------------------------------------------------------------- --->
-<!--- ========== LEFT OFF HERE ============================================ --->
-<!--- --------------------------------------------------------------------- --->
-
 Results
@@
 Trajectories of allele values in individual simulations were typically highly stochastic, but were consistent in their long-term direction (Supporting Information Figures S1-S8).
-Overall, this implies that, even given strong inbreeding depression in offspring viability and simultaneous evolution of pre-copulatory and post-copulatory strategies, inbreeding avoidance might generally be a weak force driving polyandry evolution.
+Overall, post-copulatory inbreeding avoidance can drive evolution of polyandry as long as direct costs are sufficiently low, but high costs might cause such evolution of polyandry to be weak even given strong inbreeding depression in offspring viability.
 
 Strong post-copulatory inbreeding avoidance, manifested as very negative $F_{a}$ values, consistently evolved in all simulations where such evolution was allowed (black lines, Figure 1B,D,F,H).
-Evolution of post-copulatory inbreeding avoidance occurred even when $P_{a}$ values were expected to be slightly negative, and hence when there was selection against polyandry (Figure 1F,H).
+Evolution of post-copulatory inbreeding avoidance occurred even when $P_{a}$ values were expected to be slightly negative, and hence when there was selection against alleles underlying polyandry (Figure 1F,H).
 This reflects the threshold nature of phenotypic expression of polygenic polyandry, wherein random sampling of alleles means that polyandry is expressed by some females (i.e., $P_{g}>0$) even when mean $P_{a}$ values are negative (Figure 2).
@@
 However, when both pre-copulatory and post-copulatory inbreeding avoidance could evolve, their relative evolutionary dynamics depended on their relative costs.
-When pre-copulatory but not post-copulatory inbreeding avoidance was costly ($c_{M}=0.02$ and $c_{F}=0$), pre-copulatory inbreeding avoidance initially evolved (i.e., negative $M_{a}$) but then evolved back towards random mating (i.e., $M_{a}=0$) following increasing evolution of post-copulatory inbreeding avoidance (Figure 3B).
+When pre-copulatory but not post-copulatory inbreeding avoidance was costly ($c_{M}=0.02$ and $c_{F}=0$), pre-copulatory inbreeding avoidance initially evolved (i.e., negative $M_{a}$) but then evolved back towards random mating (i.e., $M_{a}=0$) following increasing evolution of post-copulatory inbreeding avoidance and polyandry (Figure 3B).
 Similarly, when post-copulatory but not pre-copulatory inbreeding avoidance was costly ($c_{F}=0.02$ and $c_{M}=0$), post-copulatory inbreeding avoidance initially evolved ($F_{a}=0$) before evolving back to random fertilisation after ca $20000$ generations (Figure 3D).
@@
 Fixation of pre-copulatory inbreeding avoidance therefore prevented evolution of post-copulatory inbreeding avoidance.
-However, in this case, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
+In this case, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
 Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values among replicates (illustrated by wide standard errors, Figure 4C).
@@
 ===================================================
+
+<!--- --------------------------------------------------------------------- --->
+<!--- ========== LEFT OFF HERE ============================================ --->
+<!--- --------------------------------------------------------------------- --->
 

### 2017-04-28 ms_pre_post.Rmd
Add all of Greta's comments

@@
 
-<!--- --------------------------------------------------------------------- --->
-<!--- ========== LEFT OFF HERE ============================================ --->
-<!--- --------------------------------------------------------------------- --->
-
 Evolution of different reproductive strategies cannot be presumed to occur in isolation from each other in real-world populations.
@@
 For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently drive selection for polyandry [e.g., @Zeh1997; @Jennions2000; @Tregenza2002].
-Evolution of inbreeding avoidance can be driven by selection on both pre-copulatory and post-copulatory mechanisms, so simultaneous evolution of each phenotype is likely to be defined by degeneracy, in addition to any direct costs on phenotypes.
+Evolution of inbreeding avoidance can be driven by selection on both pre-copulatory and post-copulatory mechanisms, so simultaneous evolution of each phenotype might be defined by degeneracy, in addition to any direct costs on phenotypes.
 We used individual-based modelling to explore evolution of pre-copulatory and post-copulatory inbreeding strategy and polyandry given (1) hard constraints on evolution of post-copulatory inbreeding strategy, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding strategy, and (3) evolution of one inbreeding strategy phenotype given the pre-existence of the other.
@@
 
+<!--- --------------------------------------------------------------------- --->
+<!--- ========== LEFT OFF HERE ============================================ --->
+<!--- --------------------------------------------------------------------- --->
+
 Evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but was affected by the joint evolution of polyandry and the existence of asymmetric costs.
@@
 We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should benefit from a higher tolerance of inbreeding than females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
-Here we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of pre-copulatory inbreeding strategy as a lost of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy.
+Here we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of pre-copulatory inbreeding strategy as a loss of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy.
 While these costs reflect empirical observations in some populations and are therefore biologically realistic, other types of costs have also been observed and could be considered in future models tailored to specific systems.
@@
 Different types of costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
-Evolution of individual phenotypes therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.
+Evolution of reproductive strategies therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.
+
+<!--- Greta brings up a relevant point here, which is kind of in line with why I have pushed back a bit on the modelling details of the implementation over costs.
+I know reviewers have expressed concerns about the implementation of costs in the past, but is there any real reason to expect that our results would be much different if the cost implementation were different (assuming the *net* cost modelled were the same -- which is a fair hypothetical assumption to make because the actual values of the costs don't really mean anything except within the context of the model; i.e., you can't apply the values to empirical populations and expect to get the quantitative predictions in the model)?
+--->
 
@@
 Additionally, the opportunity for post-copulatory inbreeding avoidance will also depend on the degree to which females are polyandrous.
-For species in which pre-copulatory inbreeding avoidance occurs and polyandry is uncommon [@Lihoreau2007; @Metzger2010; @Metzger2010a], evolution of post-copulatory inbreeding avoidance is highly unlikely even if such a strategy incurs little direct cost.
+For species in which pre-copulatory inbreeding avoidance occurs and polyandry is uncommon [@Lihoreau2007; @Metzger2010; @Metzger2010a], evolution of post-copulatory inbreeding avoidance is unlikely even if such a strategy incurs little direct cost.
 
@@
 
-![Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs.
+![Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with identical initial conditions, default parameter values, and zero costs.
 Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations.

### 2017-05-01 ms_pre_post.Rmd
Add Matthew's comments

@@
 author: ''
-date: "28 April 2017"
+date: "1 May 2017"
 output:
@@
 We use individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression and different evolutionary constraints and direct costs.
-We find that evolution of post-copulatory inbreeding avoidance causes selection for increased polyandry, and that selection for a costly inbreeding avoidance strategy was weak or negligible given a cost free alternative strategy.
-Further, fixed pre-copulatory inbreeding avoidance generally precluded evolution of polyandry and therefore post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance.
-Evolution of inbreeding avoidance phenotypes and associated polyandry are likely to be affected by evolutionary feedbacks and degeneracy.
+We find that evolution of post-copulatory inbreeding avoidance increases selection for initially rare polyandry, and that selection for a costly inbreeding avoidance strategy was weak or negligible given a cost free alternative strategy.
+Further, fixed pre-copulatory inbreeding avoidance often completely precluded evolution of polyandry and therefore post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance.
+Evolution of inbreeding avoidance phenotypes and associated polyandry are likely affected by evolutionary feedbacks and degeneracy.
 All else being equal, while evolution of pre-copulatory inbreeding avoidance and associated low polyandry is more likely when pre-copulatory inbreeding avoidance is precluded or costly, evolution of post-copulatory inbreeding avoidance greatly facilitates evolution of costly polyandry.
@@
 
+<!---
+
+I'm confused by Ryan's point:
+
+''It is 'required' in this sense but could a reviewer flag up that other forms of post-cop inbreeding avoidance could evolve without the need of polyandry?
+
+I'm thinking in terms of sperm rejection/embryo inviability or something along those lines (such like you mention in the discussion), since females could then mate with a different male for subsequent events.
+Very pedantic I know, but maybe a word or two of clarity re: polyandry is required for this specific type of post-cop inbreeding avoidance could cut this potential criticism off right away.''
+
+If females mate with a different male, then it must be during a different bout of reproduction (else it's not polyandry as we define it).
+Perhaps what is meant is that inviability in one event effectively kills any parental investment that could affect future reproductive bouts?
+To me, it isn't really a different 'bout' if there is lingering parental investment that could affect current reproduction, but I guess I can see how a very pedantic reviewer could get confused.
+To make it completely air-tight (though a bit dense), I've added ''through fertilisation biased toward non-relatives''.
+
+--->
+
 From the perspective of a breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
-Evolution of post-copulatory inbreeding avoidance requires that females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout.
-Further, given inbreeding depression, such polyandry might itself be under selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative.
-Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm provided by females' mates (i.e., 'fair raffle').
+Evolution of post-copulatory inbreeding avoidance through fertilisation biased toward non-relatives requires that females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout.
+Such polyandry might initially be under selection and evolve if it allows for pre-copulatory inbreeding avoidance when females have the opportunity to mate with additional unrelated males following initial mating with a relative, assuming sufficiently strong inbreeding depression [@Duthie].
+Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm provided by females' mates (i.e., under conditions of a 'fair raffle').
 Overall, polyandry can therefore simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
 Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002].
-Resulting indirect selection on polyandry to increase offspring fitness could explain its evolution in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct fitness costs on polyandrous females.
-However, despite such widely-invoked hypotheses, there is surprising little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
+Selection on polyandry to increase offspring fitness could explain its evolution in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct costs on polyandrous females.
+However, despite such widely-invoked hypotheses regarding the role of inbreeding depression on evolving strategies for pre-copulatory and post-copulatory inbreeding avoidance and hence polyandry, there is surprisingly little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
 
@@
 However, relatively few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
-Pre-copulatory inbreeding avoidance has been reported in diverse species, spanning sweet potato weevils [*Cylas formicarius*, @Kuriwada2011], purple-crowned fairy-wrens [*Malurus coronatus*, @Kuriwada2011], and a tropical butterfly [*Bicyclus anynana*, @Fischer2015], while post-copulatory inbreeding avoidance has been reported in red junglefowl [*Gallus gallus*, @Pizzari2004] and crickets [*Teleogryllus oceanicus*, @Simmons2006; *Gryllus bimaculatus*, @Bretman2009].
+Pre-copulatory inbreeding avoidance has been reported in diverse species, spanning sweet potato weevils [*Cylas formicarius*, @Kuriwada2011], purple-crowned fairy-wrens [*Malurus coronatus*, @Kuriwada2011], and squinting bush brown butterflies [*Bicyclus anynana*, @Fischer2015], while post-copulatory inbreeding avoidance has been reported in red junglefowl [*Gallus gallus*, @Pizzari2004] and crickets [*Teleogryllus oceanicus*, @Simmons2006; *Gryllus bimaculatus*, @Bretman2009].
 Evidence for both pre-copulatory and post-copulatory inbreeding avoidance is available across different studies of Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015].
@@
 However, @Ala-Honkola2011 and @Tan2012 found no evidence for pre-copulatory or post-copulatory inbreeding avoidance in fruit flies (*Drosophila melanogaster*), respectively, and Reid et al.
-[-@Reid2014; -@Reid2015] found no net inbreeding avoidance in song sparrows (*Melospiza melodia*) despite strong inbreeding depression.
-Taken together, these studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature alongside polyandry.
-However, there is as yet no theory that predicts what combinations of pre-copulatory and post-copulatory inbreeding avoidance and polyandry should be favoured by selection when all combinations of phenotypes can evolve.
+[-@Reid2014; -@Reid2015] found no net inbreeding avoidance in song sparrows (*Melospiza melodia*) despite strong inbreeding depression, suggesting neither pre-copulatory or post-copulatory inbreeding avoidance.
+Taken together, these studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature.
+However, there is as yet no theory that predicts what combinations of pre-copulatory and post-copulatory inbreeding avoidance and and associated polyandry should be favoured by selection when all combinations of phenotypes can evolve.
 Consequently, there is no theory that allows the diversity of observed pre-copulatory and post-copulatory inbreeding avoidance to be interpreted, and no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
@@
 Evolution of different reproductive strategies cannot be presumed to occur in isolation from each other in real-world populations.
-Rather, such evolution is likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundance) among phenotypes under selection.
+Rather, such evolution is likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundancy) among phenotypes under selection.
 For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently drive selection for polyandry [e.g., @Zeh1997; @Jennions2000; @Tregenza2002].

### 2017-05-02 ms_pre_post.Rmd
Abstract edits from Jane

@@
 We find that evolution of post-copulatory inbreeding avoidance increases selection for initially rare polyandry, and that selection for a costly inbreeding avoidance strategy was weak or negligible given a cost free alternative strategy.
-Further, fixed pre-copulatory inbreeding avoidance often completely precluded evolution of polyandry and therefore post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance.
-Evolution of inbreeding avoidance phenotypes and associated polyandry are likely affected by evolutionary feedbacks and degeneracy.
-All else being equal, while evolution of pre-copulatory inbreeding avoidance and associated low polyandry is more likely when pre-copulatory inbreeding avoidance is precluded or costly, evolution of post-copulatory inbreeding avoidance greatly facilitates evolution of costly polyandry.
+Further, fixed pre-copulatory inbreeding avoidance often completely precluded evolution of polyandry and hence post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance.
+Evolution of inbreeding avoidance phenotypes and associated polyandry are therefore affected by evolutionary feedbacks and degeneracy.
+All else being equal, evolution of pre-copulatory inbreeding avoidance and resulting low polyandry is more likely when post-copulatory inbreeding avoidance is precluded or costly, and evolution of post-copulatory inbreeding avoidance greatly facilitates evolution of costly polyandry.
 

### 2017-05-02 ms_pre_post.Rmd
Edit through Introduction

@@
 
-<!---
-
-I'm confused by Ryan's point:
-
-''It is 'required' in this sense but could a reviewer flag up that other forms of post-cop inbreeding avoidance could evolve without the need of polyandry?
-
-I'm thinking in terms of sperm rejection/embryo inviability or something along those lines (such like you mention in the discussion), since females could then mate with a different male for subsequent events.
-Very pedantic I know, but maybe a word or two of clarity re: polyandry is required for this specific type of post-cop inbreeding avoidance could cut this potential criticism off right away.''
-
-If females mate with a different male, then it must be during a different bout of reproduction (else it's not polyandry as we define it).
-Perhaps what is meant is that inviability in one event effectively kills any parental investment that could affect future reproductive bouts?
-To me, it isn't really a different 'bout' if there is lingering parental investment that could affect current reproduction, but I guess I can see how a very pedantic reviewer could get confused.
-To make it completely air-tight (though a bit dense), I've added ''through fertilisation biased toward non-relatives''.
-
---->
-
 From the perspective of a breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
-Evolution of post-copulatory inbreeding avoidance through fertilisation biased toward non-relatives requires that females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout.
-Such polyandry might initially be under selection and evolve if it allows for pre-copulatory inbreeding avoidance when females have the opportunity to mate with additional unrelated males following initial mating with a relative, assuming sufficiently strong inbreeding depression [@Duthie].
+Evolution of such post-copulatory inbreeding avoidance is likely to be facilitated females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout [but see @Dougherty2016].
+Such polyandry might itself be under selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative.
 Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm provided by females' mates (i.e., under conditions of a 'fair raffle').
@@
 Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002].
-Selection on polyandry to increase offspring fitness could explain its evolution in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct costs on polyandrous females.
-However, despite such widely-invoked hypotheses regarding the role of inbreeding depression on evolving strategies for pre-copulatory and post-copulatory inbreeding avoidance and hence polyandry, there is surprisingly little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
+Resulting indirect selection on polyandry to increase offspring fitness could explain evolution of polyandry in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct costs on polyandrous females.
+However, despite such widely-invoked hypotheses regarding the role of inbreeding depression in driving pre-copulatory and post-copulatory strategies and polyandry, there is surprisingly little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
+
+<!--- I really don't think the connection between 'resulting indirect selection' and *offspring* rather than *parent* fitness is going to be made easily by a lot of readers.
+You've thought a lot about this, so I think we need to be careful for readers who are still not up to date on the selection-on-inbreeding versus selection-on-being-inbred distinction.
+--->
 
@@
 However, @Ala-Honkola2011 and @Tan2012 found no evidence for pre-copulatory or post-copulatory inbreeding avoidance in fruit flies (*Drosophila melanogaster*), respectively, and Reid et al.
-[-@Reid2014; -@Reid2015] found no net inbreeding avoidance in song sparrows (*Melospiza melodia*) despite strong inbreeding depression, suggesting neither pre-copulatory or post-copulatory inbreeding avoidance.
-Taken together, these studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature.
-However, there is as yet no theory that predicts what combinations of pre-copulatory and post-copulatory inbreeding avoidance and and associated polyandry should be favoured by selection when all combinations of phenotypes can evolve.
-Consequently, there is no theory that allows the diversity of observed pre-copulatory and post-copulatory inbreeding avoidance to be interpreted, and no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
+[-@Reid2014; -@Reid2015] found no net inbreeding avoidance in song sparrows (*Melospiza melodia*) despite strong inbreeding depression and opportunities for both pre-copulatory and post-copulatory inbreeding avoidance.
+Taken together, these studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance, or lack thereof, occur in nature.
+However, there is as yet no theory that predicts what combinations of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry should be favoured by selection when all can evolve.
+Consequently, there is no theory that allows the diversity of observed pre-copulatory and post-copulatory inbreeding avoidance strategies to be interpreted, and no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
 
-@Duthie used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance.
+@Duthie used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve due to selection stemming from pre-copulatory inbreeding avoidance in the absence of any post-copulatory inbreeding strategy.
 Net selection for polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., 'costs') on polyandry was weak, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
-Without these conditions, and without the possibility for post-copulatory female choice, increasing polyandry tended to increase rather than decrease the overall degree of inbreeding that females experienced, and hence reduce offspring fitness.
+Without these conditions, increasing polyandry tended to increase rather than decrease the overall degree of inbreeding that females experienced, and hence reduce offspring fitness.
 This occurred because, once pre-copulatory inbreeding avoidance evolved, polyandrous females had already chosen available unrelated males as their initial mates.
@@
 Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance, and hence the resulting degree of inbreeding avoidance, was consequently restricted [@Duthie].
-If post-copulatory inbreeding avoidance could also evolve, polyandrous females would have the opportunity to bias paternity towards unrelated males within their set of chosen mates.
+
+However, if post-copulatory inbreeding avoidance could also evolve, polyandrous females would have the opportunity to bias paternity towards unrelated males within their set of chosen mates.
 Evolution of post-copulatory inbreeding avoidance might consequently reduce the cost of polyandry stemming from the accumulation of related mates across multiple matings, potentially facilitating evolution of polyandry to avoid inbreeding under broader conditions, and driving further evolution of pre-copulatory or post-copulatory mate choice strategies.
-
-However, if polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, the long-term dynamics of these three reproductive strategies become difficult to predict.
+Subsequently, if polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, the long-term dynamics of these three reproductive strategies become difficult to predict.
 Strong inbreeding depression might drive initial evolution of both pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
-However, the co-occurence of pre-copulatory and post-copulatory inbreeding avoidance might engender some degree of 'degeneracy', defined as a phenomenon by which different elements of a system result in identical outputs [i.e., @Edelman2001].
+However, the co-occurrence of pre-copulatory and post-copulatory inbreeding avoidance might engender some degree of 'degeneracy', defined as a phenomenon by which different elements of a system result in identical outputs [i.e., @Edelman2001].
 Consequently, if evolution of polyandry and post-copulatory inbreeding avoidance renders pre-copulatory inbreeding avoidance functionally redundant, or vice versa, then only one inbreeding avoidance strategy might be maintained in the long-term.
@@
 Females that express post-copulatory choice might pay initial energetic costs associated with developing the physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
-If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly inbreeding avoidance strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
-However, such trajectories will also depend on the indirect benefits of each strategy, which might also differ and vary in relation to the evolution of the other strategy.
+If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly strategy might become extinct, especially if their effects are made redundant by evolution of the less costly strategy.
+Evolutionary dynamics will therefore depend on the benefits of each strategy, which might also differ and vary in relation to the evolution of the other strategy.
 Dynamic models that track the frequencies of alleles underlying multiple reproductive strategies that might influence each others evolution across generations, and that are enacted among relatives that themselves result from reproductive strategies and inbreeding depression expressed in previous generations, are consequently useful to understand and predict evolutionary outcomes.

### 2017-05-02 ms_pre_post.Rmd
Edit through Methods

@@
 We thereby track evolutionary dynamics given internally consistent patterns of relatedness caused by non-random mating and allowing for effects of mutation, gene flow, drift, and selection.
+
 All individuals have 10 physically unlinked diploid loci, and therefore 20 alleles, underlying each of three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$, i.e., 'polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., 'fertilisation' alleles).
-All alleles can take the value of any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014] and combine additively to determine genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively, whereby an individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
-Phenotype values $M_{p} = M_{g}$ and $F_{p} = F_{g}$, where negative and positive values cause inbreeding avoidance and preference, respectively (see details of mating and fertilisation strategies below).
-In contrast, $P_{p} = P_{g}$ only if $P_{g} \geq 0$ to cause increasingly greater tendency for polyandry, while $P_{p} = 0$ if $P_{g} < 0$ because females cannot choose a negative number of mates (see details of polyandry below).
+All alleles can take the value of any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014] and combine additively to determine genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and resulting phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively.
+Each individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
+Each individual's phenotypic values for pre-copulatory and post-copulatory inbreeding strategy equal their respective genotypic values ($M_{p} = M_{g}$ and $F_{p} = F_{g}$), where negative and positive values cause inbreeding avoidance and preference, respectively (see details of mating and fertilisation strategies below).
+In contrast, phenotypic values for tendency for polyandry equal genotypic values ($P_{p} = P_{g}$) only if $P_{g} \geq 0$, while $P_{p} = 0$ if $P_{g} < 0$ because females cannot choose a negative number of mates.
 Polyandry is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998; @Duthie] that is influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
-Any negative $P_{g}$ value therefore generates phenotypic monandry, while positive $P_{g}$ values can lead to different degrees of realised polyandry (i.e., different numbers of mates, $N_{males}$).
+A negative $P_{g}$ value therefore generates a female that is phenotypically monandrous, while a positive $P_{g}$ value generates a female that can express some degree of polyandry (see details below).
 
-In overview, each generation proceeds with females paying costs related to their reproductive strategy.
+In overview, each generation proceeds with females paying costs associated with their reproductive strategy traits, and expressing polyandry, mating, and fertilisation.
 Offspring inherit a randomly sampled allele from each parent at each locus.
@@
 
-Phenotypic values have costs that are assumed to combine independently to increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
+Phenotypic values of the three reproductive strategy traits each have costs that are assumed to combine independently to increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
 The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
@@
 Absolute values are used for applying costs to inbreeding avoidance strategies because both negative and positive $M_{p}$ and $F_{p}$ values could potentially arise and affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively.
+In contrast, $P_{p}$ cannot be negative.
 Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
@@
 After costs are realised, each remaining female chooses $N_{males}$ males to mate with, where $N_{males}$ is calculated by sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
-This ensures that all surviving females choose at least one mate, and causes some stochastic variation around the expected mean $N_{males}$ of $P_{p}+1$.
+This ensures that all surviving females choose at least one mate and generates each female's realised degree of polyandry with some stochastic variation around the expected mean $N_{males}$ of $P_{p}+1$.
 
@@
 Most often, $N_{males}$ will be smaller than the total number of available males [@Duthie].
-Each female then chooses her $N_{males}$ mates based on her pre-copulatory inbreeding avoidance phenotype ($M_{p}$), which equals her genotype ($M_{g}$).
+Each female then chooses her $N_{males}$ mates based on her pre-copulatory inbreeding avoidance phenotype ($M_{p}$).
 Negative or positive $M_{p}$ values cause a female to avoid or prefer mating with kin, respectively, whereas $M_{p}=0$ cause females to mate randomly with respect to kinship.
@@
 Females produce $n$ offspring, so a female $i$ samples from her mates $n$ times independently and with replacement with a probability of $q^{f}_{ij}$ for each male $j$ to determine the realised distribution of sires.
-Offspring produced have equal probability of being female or male.
+Offspring have equal probability of being female or male.
 
@@
 When a mutation occurs, a mutation effect is sampled from a normal distribution with a mean of zero and a standard deviation of $\mu_{SD}$ and added to the original allele value [@Kimura1965; @Lande1976; @Bocedi2014; @Duthie].
-The value of $\mu_{SD}$ is set to $\sqrt{1/20}$.
+The value of $\mu_{SD}$ is set to $\sqrt{1/20}$ because 20 independent alleles underlie each trait's genotypic value.
 
@@
 Given our current objectives, we simulate evolution under conditions where inbreeding avoidance is adaptive due to strong inbreeding depression, and not evolution where inbreeding preference is adaptive due to weak or zero inbreeding depression [@Parker1979; @Kokko2006; @Duthie2016a], or given outbreeding depression [@Bateson1983; @Greeff2009].
-However, as described above, positive $M_{p}$ and $F_{p}$ values resulting in inbreeding preference are permitted to evolve, and could potentially arise due to mutation or drift.
+However, as described above, positive $M_{p}$ and $F_{p}$ values resulting in inbreeding preference are not precluded from evolving, and could potentially arise due to mutation or drift.
 
@@
 
-To address whether or not evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance can facilitate evolution of polyandry, we compare simulations in which polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, with otherwise identical simulations in which post-copulatory inbreeding avoidance cannot evolve given four different costs of polyandry ($c_{P} = \{0, 0.0025, 0.005,  0.01\}$).
-To prevent post-copulatory inbreeding avoidance from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes cause random fertilisation with respect to kinship, so $F_{a}$ alleles have no phenotypic effect.
+To address whether or not evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance can facilitate evolution of polyandry, we compare simulations in which polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve with otherwise identical simulations in which post-copulatory inbreeding avoidance cannot evolve.
+To achieve this, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes cause random fertilisation with respect to kinship, so $F_{a}$ alleles have no phenotypic effect.
+Simulations were repeated across four different costs of polyandry ($c_{P} = \{0, 0.0025, 0.005,  0.01\}$).
 

### 2017-05-02 ms_pre_post.Rmd
Edit through Results

@@
 Trajectories of allele values in individual simulations were typically highly stochastic, but were consistent in their long-term direction (Supporting Information Figures S1-S8).
-Overall, post-copulatory inbreeding avoidance can drive evolution of polyandry as long as direct costs are sufficiently low, but high costs might cause such evolution of polyandry to be weak even given strong inbreeding depression in offspring viability.
+Overall, these results illustrate that post-copulatory inbreeding avoidance can facilitate evolution of polyandry as long as direct costs are sufficiently low (Figure 1B,D).
+However, given higher costs, evolution of polyandry is constrained even given strong inbreeding depression in offspring viability, and given resulting evolution of both pre-copulatory and post-copulatory inbreeding avoidance (Figure 1F,H).
 
@@
 Likewise, when pre-copulatory inbreeding avoidance allele values ($M_{a}$) were fixed to zero, costly post-copulatory inbreeding avoidance evolved (Figure 3C).
-Females therefore evolved to avoid inbreeding, and thereby avoid the cost of producing inbred offspring, through whichever route was available.
+Females therefore evolved to avoid inbreeding, and thereby avoid the indirect cost of producing inbred offspring, through whichever route was available.
 
 However, when both pre-copulatory and post-copulatory inbreeding avoidance could evolve, their relative evolutionary dynamics depended on their relative costs.
-When pre-copulatory but not post-copulatory inbreeding avoidance was costly ($c_{M}=0.02$ and $c_{F}=0$), pre-copulatory inbreeding avoidance initially evolved (i.e., negative $M_{a}$) but then evolved back towards random mating (i.e., $M_{a}=0$) following increasing evolution of post-copulatory inbreeding avoidance and polyandry (Figure 3B).
-Similarly, when post-copulatory but not pre-copulatory inbreeding avoidance was costly ($c_{F}=0.02$ and $c_{M}=0$), post-copulatory inbreeding avoidance initially evolved ($F_{a}=0$) before evolving back to random fertilisation after ca $20000$ generations (Figure 3D).
+When pre-copulatory but not post-copulatory inbreeding avoidance was costly ($c_{M}=0.02$ and $c_{F}=0$), pre-copulatory inbreeding avoidance initially evolved (i.e., $M_{a} < 0$) but then evolved back towards random mating (i.e., $M_{a} \approx 0$) following increasing evolution of post-copulatory inbreeding avoidance and polyandry (Figure 3B).
+Similarly, when post-copulatory but not pre-copulatory inbreeding avoidance was costly ($c_{F}=0.02$ and $c_{M}=0$), post-copulatory inbreeding avoidance initially evolved (i.e., $F_{a} < 0$) before evolving back to random fertilisation (i.e., $F_{a} \approx 0$) after ca $20000$ generations (Figure 3D).
 
@@
 
-How do evolution of pre-copulatory and post-copulatory inbreeding avoidance affect one another?
+How does fixation of pre-copulatory or post-copulatory inbreeding avoidance affect evolution?
 ----------------------------------------------
@@
 Fixation of pre-copulatory inbreeding avoidance therefore prevented evolution of post-copulatory inbreeding avoidance.
-In this case, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
-Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values among replicates (illustrated by wide standard errors, Figure 4C).
+In this case, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless of whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
+Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values (resulting in variation among replicates illustrated by the wide standard errors in Figure 4C).
 However, when $c_{F}=0.02$, $F_{a}$ values remained near zero to minimise direct costs.
@@
 ******************************
+
+<!--- --------------------------------------------------------------------- --->
+<!--- LEFT OFF HERE  ------------------------------------------------------ --->
+<!--- --------------------------------------------------------------------- --->
 

### 2017-05-03 ms_pre_post.Rmd
Revised manuscript with all coauthor comments

@@
 output:
+  html_document: default
+  pdf_document:
+    fig_caption: yes
   word_document:
@@
 For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently drive selection for polyandry [e.g., @Zeh1997; @Jennions2000; @Tregenza2002].
-Evolution of inbreeding avoidance can be driven by selection on both pre-copulatory and post-copulatory mechanisms, so simultaneous evolution of each phenotype might be defined by degeneracy, in addition to any direct costs on phenotypes.
-We used individual-based modelling to explore evolution of pre-copulatory and post-copulatory inbreeding strategy and polyandry given (1) hard constraints on evolution of post-copulatory inbreeding strategy, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding strategy, and (3) evolution of one inbreeding strategy phenotype given the pre-existence of the other.
-We thereby highlight fundamental but theoretically under-developed relationships between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding strategy.
+Inbreeding avoidance could be manifested through both pre-copulatory and post-copulatory mechanisms, meaning that simultaneous evolution of each phenotype might be defined by degeneracy in addition to trait-specific costs.
+We used individual-based modelling to highlight fundamental but theoretically under-developed relationships between evolution of polyandry and pre-copulatory versus post-copulatory inbreeding strategy given (1) hard constraints on evolution of post-copulatory inbreeding strategy, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding strategy, and (3) evolution of one inbreeding strategy phenotype given the pre-existence of the other.
 We present our model and simulation results as a tool for thinking more clearly about the dynamics of simultaneously evolving reproductive strategies, not for making accurate quantitative predictions for any specific system.
@@
 
-<!--- --------------------------------------------------------------------- --->
-<!--- ========== LEFT OFF HERE ============================================ --->
-<!--- --------------------------------------------------------------------- --->
-
-Evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but was affected by the joint evolution of polyandry and the existence of asymmetric costs.
-One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population by modifying its effect on inbreeding avoidance (Figure 3).
+Evolution of both pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but were affected by the evolution of polyandry and the existence of asymmetric costs.
+One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population (Figure 3).
 Consequently, long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given sufficient cost asymmetry.
 Since direct costs strongly affected the evolution of the focal phenotype(s), quantifying costs is necessary for predicting evolution of inbreeding strategies.
+
 Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging [@Pomiankowski1987; @Kokko2003].
 @Pomiankowski1987 categorised four types of costs that are relevant to mate choice, which are also relevant for polyandry, and include costs of elevated risks of predation or disease transmission, and costs incurred through time or energy expenditure.
-Another relevant cost is risk of male harm caused by sexual conflict [e.g., @Arnqvist2005a; @Parker2006].
-We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should benefit from a higher tolerance of inbreeding than females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
-Here we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of pre-copulatory inbreeding strategy as a loss of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy.
+Consequently, we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of pre-copulatory inbreeding strategy as a loss of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy, all manifested as an increased probability of total reproductive failure.
 While these costs reflect empirical observations in some populations and are therefore biologically realistic, other types of costs have also been observed and could be considered in future models tailored to specific systems.
-For example, increased risk of disease transmission has been observed for highly polyandrous females [@Roberts2015a], and such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry.
-Different types of costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
+For example, highly polyandrous females might experience increased risk of disease transmission [@Roberts2015a].
+Such a cost would more realistically apply to a female's realised number of mates rather than her tendency for polyandry.
+Polyandrous females might also risk harm caused by sexual conflict over multiple mating [e.g., @Arnqvist2005a; @Parker2006].
+We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should be more tolerant of inbreeding than females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
+Future models could formally consider sexual conflict over both polyandry and inbreeding.
+Overall, such different types of costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
 Evolution of reproductive strategies therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.
 
-<!--- Greta brings up a relevant point here, which is kind of in line with why I have pushed back a bit on the modelling details of the implementation over costs.
-I know reviewers have expressed concerns about the implementation of costs in the past, but is there any real reason to expect that our results would be much different if the cost implementation were different (assuming the *net* cost modelled were the same -- which is a fair hypothetical assumption to make because the actual values of the costs don't really mean anything except within the context of the model; i.e., you can't apply the values to empirical populations and expect to get the quantitative predictions in the model)?
---->
-
-In our model, existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
-However, existence of adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Figure 3A,B).
+In our model, existence of fixed adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, precluded evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
+However, existence of fixed adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Figure 3A,B).
 In wild populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
@@
 
-Post-copulatory inbreeding avoidance cannot be realised if females are not polyandrous, and is most effective for highly polyandrous females that can choose amongst multiple mates and therefore bias fertilisation accordingly.
+Post-copulatory inbreeding avoidance cannot be effectively realised if females are not polyandrous in any form, and is likely to be most effective for highly polyandrous females that can choose amongst sperm contributed by multiple mates and therefore bias fertilisation accordingly.
 In contrast, pre-copulatory inbreeding avoidance mechanisms are most critical for females that mate only once and therefore have no post-copulatory opportunity to avoiding inbreeding.
@@
 Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information Figure S9).
-In addition to polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).
-It would therefore be interesting to test the hypothesis that, across taxa, occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with the degree of polyandry.
+In addition to initial polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back effect that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).
+It would therefore be interesting to test the hypothesis that, across taxa, the occurrence of post-copulatory inbreeding avoidance covaries positively, and the occurrence of pre-copulatory inbreeding avoidance covaries negatively, with the degree of polyandry.
 To test this hypothesis, more work is needed to quantify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.

### 2017-05-03 ms_pre_post.Rmd
Add reference and start to revise for biorXiv version

@@
 Strong inbreeding depression might drive initial evolution of both pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
-However, the co-occurrence of pre-copulatory and post-copulatory inbreeding avoidance might engender some degree of 'degeneracy', defined as a phenomenon by which different elements of a system result in identical outputs [i.e., @Edelman2001].
+However, the co-occurrence of pre-copulatory and post-copulatory inbreeding avoidance might engender some degree of 'degeneracy', defined as a phenomenon by which different elements of a system result in identical outputs [@Edelman2001].
 Consequently, if evolution of polyandry and post-copulatory inbreeding avoidance renders pre-copulatory inbreeding avoidance functionally redundant, or vice versa, then only one inbreeding avoidance strategy might be maintained in the long-term.

### 2017-05-03 pre_post_biorxiv.tex
Add reference and start to revise for biorXiv version

@@
 \\
-A. Bradley Duthie\textsuperscript{1,*}, [...],
-%Greta Bocedi\textsuperscript{1},
-%Ryan R. Germain\textsuperscript{1},
+A. Bradley Duthie\textsuperscript{1,*},
+Greta Bocedi\textsuperscript{2},
+Ryan R. Germain\textsuperscript{2},
 %Matthew E. Wolak\textsuperscript{1},
@@
 However, surprisingly little theory or modelling critically examines selection for pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, given evolutionary constraints and direct costs, or examines how evolution of inbreeding avoidance strategies might feed back to affect evolution of polyandry.
-Selection for post-copulatory inbreeding avoidance, but not for pre-copulatory inbreeding avoidance, requires polyandry, while interactions between pre-copulatory and post-copulatory inbreeding avoidance might cause functional redundancy (i.e., 'degeneracy') potentially generating complex evolutionary dynamics among inbreeding strategies and polyandry.
+Selection for post-copulatory inbreeding avoidance, but not for pre-copulatory inbreeding avoidance, requires polyandry, while interactions between pre-copulatory and post-copulatory inbreeding avoidance might cause functional redundancy (i.e., `degeneracy') potentially generating complex evolutionary dynamics among inbreeding strategies and polyandry.
 We use individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression and different evolutionary constraints and direct costs.
-We find that evolution of post-copulatory inbreeding avoidance causes selection for increased polyandry, and that selection for a costly inbreeding avoidance strategy was weak or negligible given a cost free alternative strategy.
-Further, fixed pre-copulatory inbreeding avoidance generally precluded evolution of polyandry and therefore post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance.
-We thereby provide a general framework for understanding joint evolution of pre-copulatory and/or post-copulatory inbreeding avoidance, and conclude that evolution of inbreeding avoidance phenotypes and associated polyandry are predicted to be strongly affected by evolutionary feedbacks and degeneracy, and by direct costs on phenotypes affecting reproductive strategy.
+We find that evolution of post-copulatory inbreeding avoidance increases selection for initially rare polyandry, and that selection for a costly inbreeding avoidance strategy was weak or negligible given a cost free alternative strategy.
+Further, fixed pre-copulatory inbreeding avoidance often completely precluded evolution of polyandry and hence post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance.
+Evolution of inbreeding avoidance phenotypes and associated polyandry are therefore affected by evolutionary feedbacks and degeneracy.
+All else being equal, evolution of pre-copulatory inbreeding avoidance and resulting low polyandry is more likely when post-copulatory inbreeding avoidance is precluded or costly, and evolution of post-copulatory inbreeding avoidance greatly facilitates evolution of costly polyandry.
 
@@
 
-From the perspective of a focal breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
-Evolution of post-copulatory inbreeding avoidance requires that females express some non-trivial degree of polyandry, defined as mating with multiple males during a single reproductive bout.
-Further, given inbreeding depression, such polyandry might itself be under selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative.
-Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm provided by females' mates (i.e., `fair raffle').
+From the perspective of a breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
+Evolution of such post-copulatory inbreeding avoidance is likely to be facilitated females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout \cite[but see][]{Dougherty2016}.
+Such polyandry might itself be under selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative.
+Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm provided by females' mates (i.e., under conditions of a `fair raffle').
 Overall, polyandry can therefore simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
 Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness \cite[][]{Zeh1997, Jennions2000, Tregenza2002}.
-Resulting indirect selection on polyandry could explain its evolution in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct fitness costs on polyandrous females.
-However, despite such widely-invoked hypotheses, there is surprising little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
-
-Despite the paucity of theory and resulting predictions, numerous empirical studies on diverse species have tested for, and in some cases found evidence of, female inbreeding avoidance in systems where polyandry also occurs \cite[][but see \citealt{Reid2015a}]{Tregenza2002, Varian-Ramos2012, Kingma2013, Arct2015}.
+Resulting indirect selection on polyandry to increase offspring fitness could explain evolution of polyandry in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct costs on polyandrous females.
+However, despite such widely-invoked hypotheses regarding the role of inbreeding depression in driving pre-copulatory and post-copulatory strategies and polyandry, there is surprisingly little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
+
+Despite the paucity of theory, numerous empirical studies on diverse species have tested for, and in some cases found evidence of, female inbreeding avoidance in systems where polyandry also occurs \cite[][but see \citealt{Reid2015a}]{Tregenza2002, Varian-Ramos2012, Kingma2013, Arct2015}.
 However, relatively few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
-Pre-copulatory inbreeding avoidance has been reported in diverse species, spanning sweet potato weevils \cite[\textit{Cylas formicarius};][]{Kuriwada2011}, purple-crowned fairy-wrens \cite[\textit{Malurus coronatus};][]{Kuriwada2011}, and a tropical butterfly \cite[\textit{Bicyclus anynana};][]{Fischer2015}, while post-copulatory inbreeding avoidance has been reported in red junglefowl \cite[\textit{Gallus gallus};][]{Pizzari2004} and crickets \cite[\textit{Teleogryllus oceanicus}, \textit{Gryllus bimaculatus};][]{Simmons2006, Bretman2009}.
+Pre-copulatory inbreeding avoidance has been reported in diverse species, spanning sweet potato weevils \cite[\textit{Cylas formicarius};][]{Kuriwada2011}, purple-crowned fairy-wrens \cite[\textit{Malurus coronatus};][]{Kuriwada2011}, and squinting bush brown butterflies \cite[\textit{Bicyclus anynana};][]{Fischer2015}, while post-copulatory inbreeding avoidance has been reported in red junglefowl \cite[\textit{Gallus gallus};][]{Pizzari2004} and crickets \cite[\textit{Teleogryllus oceanicus}, \textit{Gryllus bimaculatus};][]{Simmons2006, Bretman2009}.
 Evidence for both pre-copulatory and post-copulatory inbreeding avoidance is available across different studies of Trinidadian guppies \cite[\textit{Poecilia reticulata};][]{Gasparini2011, Daniel2015} and house mice \cite[\textit{Mus domesticus};][]{Potts1991, Firman2015}.
@@
 However, \cite{Ala-Honkola2011} and \cite{Tan2012} found no evidence for pre-copulatory or post-copulatory inbreeding avoidance in fruit flies (\textit{Drosophila melanogaster}), respectively, and Reid et al.
-\citeyearpar{Reid2014, Reid2015} found no net inbreeding avoidance in song sparrows (\textit{Melospiza melodia}) despite strong inbreeding depression.
-Taken together, these studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature alongside polyandry.
-However, there is as yet no theory that predicts what combinations of pre-copulatory and post-copulatory inbreeding avoidance and polyandry should be favoured by selection when all combinations of phenotypes can evolve.
-Consequently, there is no theory that allows the diversity of existing empirical results regarding pre-copulatory and post-copulatory inbreeding avoidance to be interpreted, and no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
-
-To develop theory on evolution of polyandry given inbreeding depression, \cite{Duthie} used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance.
+\citeyearpar{Reid2014, Reid2015} found no net inbreeding avoidance in song sparrows (\textit{Melospiza melodia}) despite strong inbreeding depression and opportunities for both pre-copulatory and post-copulatory inbreeding avoidance.
+Taken together, these studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance, or lack thereof, occur in nature.
+However, there is as yet no theory that predicts what combinations of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry should be favoured by selection when all can evolve.
+Consequently, there is no theory that allows the diversity of observed pre-copulatory and post-copulatory inbreeding avoidance strategies to be interpreted, and no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
+
+\cite{Duthie} used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve due to selection stemming from pre-copulatory inbreeding avoidance in the absence of any post-copulatory inbreeding strategy.
 Net selection for polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., `costs') on polyandry was weak, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate \cite[][]{Duthie}.
@@
 
-However, if post-copulatory inbreeding avoidance could also evolve, polyandrous females would also have an opportunity to bias paternity towards unrelated males within their set of chosen mates.
+However, if post-copulatory inbreeding avoidance could also evolve, polyandrous females would have the opportunity to bias paternity towards unrelated males within their set of chosen mates.
 Evolution of post-copulatory inbreeding avoidance might consequently reduce the cost of polyandry stemming from the accumulation of related mates across multiple matings, potentially facilitating evolution of polyandry to avoid inbreeding under broader conditions, and driving further evolution of pre-copulatory or post-copulatory mate choice strategies.
-However, if polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, the long-term dynamics of these three reproductive strategies become difficult to predict.
+Subsequently, if polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, the long-term dynamics of these three reproductive strategies become difficult to predict.
 Strong inbreeding depression might drive initial evolution of both pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
-However, the co-occurence of pre-copulatory and post-copulatory inbreeding avoidance might engender some degree of `degeneracy', defined as a phenomenon by which different elements of a system result in identical outputs \cite[i.e.,][]{Edelman2001}.
+However, the co-occurrence of pre-copulatory and post-copulatory inbreeding avoidance might engender some degree of `degeneracy', defined as a phenomenon by which different elements of a system result in identical outputs \cite[][]{Edelman2001}.
 Consequently, if evolution of polyandry and post-copulatory inbreeding avoidance renders pre-copulatory inbreeding avoidance functionally redundant, or vice versa, then only one inbreeding avoidance strategy might be maintained in the long-term.
@@
 Females that express post-copulatory choice might pay initial energetic costs associated with developing the physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation \cite[e.g.,][]{Gasparini2011, Tuni2013, Fitzpatrick2014b}.
-If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly inbreeding avoidance strategy might become extinct if their effects are both costly and made redundant by the less costly strategy.
-However, such trajectories will also depend on the indirect benefits of each strategy, which might also differ and vary in relation to the evolution of the other strategy.
+If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly strategy might become extinct, especially if their effects are made redundant by evolution of the less costly strategy.
+Evolutionary dynamics will therefore depend on the benefits of each strategy, which might also differ and vary in relation to the evolution of the other strategy.
 Dynamic models that track the frequencies of alleles underlying multiple reproductive strategies that might influence each others evolution across generations, and that are enacted among relatives that themselves result from reproductive strategies and inbreeding depression expressed in previous generations, are consequently useful to understand and predict evolutionary outcomes.
@@
 By addressing these questions, we illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
-We thereby provide a framework for deriving hypotheses amenable to empirical tests within and across taxa.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\bibitem[{Dougherty et~al.(2016)}]{Dougherty2016}
+Dougherty, L.~R., Simmons, L.~W. \& Shuker, D.~M. 2016. 
+\newblock {Postcopulatory sexual selection when a female mates once}.
+\newblock \textit{Anim. Behav.} \textbf{116}:13--16.
+
 \bibitem[{Duthie \textit{et~al.}(2016)Duthie, Bocedi, \& Reid}]{Duthie}
-Duthie, A.~B., Bocedi G. \& Reid, J.~M. 2016.
+Duthie, A.~B., Bocedi, G. \& Reid, J.~M. 2016.
 \newblock {When does female multiple mating evolve to adjust inbreeding?

### 2017-05-03 pre_post_biorxiv.tex
Final formatting of biorXiv TEX file

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section*{Model}
 
-We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply 'inbreeding strategies' because the model did not preclude evolution of inbreeding preference), by tracking the dynamics of alleles underlying reproductive strategies enacted by interacting females and males within a small focal population.
+We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply `inbreeding strategies' because the model did not preclude evolution of inbreeding preference), in a small focal population of females and males by tracking the dynamics of alleles underlying reproductive strategies expressed by females.
 We thereby track evolutionary dynamics given internally consistent patterns of relatedness caused by non-random mating and allowing for effects of mutation, gene flow, drift, and selection.
-Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$, i.e., `polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., `mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., `fertilisation' alleles).
-All alleles can take the value of any real number \cite[i.e., a continuum-of-alleles model;][]{Kimura1965, Lande1976, Reeve2000, Bocedi2014} and combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively, whereby an individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
-In overview, each generation proceeds with females paying costs and expressing polyandry, mating, and fertilisation.
-Offspring inherit a randomly sampled allele from each parent at each locus with no physical linkage.
+
+All individuals have 10 physically unlinked diploid loci, and therefore 20 alleles, underlying each of three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$, i.e., `polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., `mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., `fertilisation' alleles).
+All alleles can take the value of any real number \cite[i.e., a continuum-of-alleles model;][]{Kimura1965, Lande1976, Reeve2000, Bocedi2014} and combine additively to determine genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and resulting phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively.
+Each individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
+Each individual's phenotypic values for pre-copulatory and post-copulatory inbreeding strategy equal their respective genotypic values ($M_{p} = M_{g}$ and $F_{p} = F_{g}$), where negative and positive values cause inbreeding avoidance and preference, respectively (see details of mating and fertilisation strategies below).
+In contrast, phenotypic values for tendency for polyandry equal genotypic values ($P_{p} = P_{g}$) only if $P_{g} \geq 0$, while $P_{p} = 0$ if $P_{g} < 0$ because females cannot choose a negative number of mates.
+Polyandry is therefore modelled as a threshold trait \cite[][]{Lynch1998, Roff1996, Roff1998, Duthie} that is influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
+A negative $P_{g}$ value therefore generates a female that is phenotypically monandrous, while a positive $P_{g}$ value generates a female that can express some degree of polyandry (see details below).
+
+In overview, each generation proceeds with females paying costs associated with their reproductive strategy traits, and expressing polyandry, mating, and fertilisation.
+Offspring inherit a randomly sampled allele from each parent at each locus.
 Alleles can then mutate and offspring express inbreeding depression in viability.
@@
 
-Phenotypic values of $P_{p}$, $M_{p}$, and $F_{p}$ each have costs that are assumed to independently increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
+Phenotypic values of the three reproductive strategy traits each have costs that are assumed to combine independently to increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
 The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
 Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
-Absolute values are used for applying costs to inbreeding avoidance strategies because both negative and positive $M_{p}$ and $F_{p}$ values could potentially arise and affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively (see details of mating and fertilisation strategies below).
-In contrast, only positive values of $P_{p}$ cause females to be polyandrous (see details of polyandry below).
+Absolute values are used for applying costs to inbreeding avoidance strategies because both negative and positive $M_{p}$ and $F_{p}$ values could potentially arise and affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively.
+In contrast, $P_{p}$ cannot be negative.
 Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
@@
 
-\subsection*{Polyandry}
+\subsection*{Mating and pre-copulatory inbreeding avoidance}
 
 After costs are realised, each remaining female chooses $N_{males}$ males to mate with, where $N_{males}$ is calculated by sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
-This ensures that all surviving females choose at least one mate, and causes some stochastic variation around the expected mean $N_{males}$ of $P_{p}+1$.
-A female's value of $P_{p}$ depends on the sum of her 20 $P_{a}$ allele values (i.e., $P_{g}$), which might be negative or positive.
-However, because females cannot mate with a negative number of males, $P_{p}$ is constrained to be zero or positive such that $P_{p} = 0$ when $P_{g} < 0$, but $P_{p} = P_{g}$ when $P_{g} \geq 0$.
-Polyandry is therefore modelled as a threshold trait \cite[][]{Lynch1998, Roff1996, Roff1998, Duthie} that is influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
-Any negative $P_{g}$ value therefore generates phenotypic monandry, while positive $P_{g}$ values can lead to different degrees of realised polyandry (i.e., different numbers of mates, $N_{males}$).
-
-\subsection*{Mating}
+This ensures that all surviving females choose at least one mate and generates each female's realised degree of polyandry with some stochastic variation around the expected mean $N_{males}$ of $P_{p}+1$.
 
@@
 We therefore assume that there is no opportunity cost of male mating, so mating with one female does not reduce a male's availability to mate with any other female.
-Individual females mate with their total allotment of $N_{males}$ without replacement, meaning that $N_{males}$ models a female's total number of different mates rather than solely her total number of matings.
+Females mate with $N_{males}$ without replacement, meaning that $N_{males}$ models a female's total number of different mates rather than solely her total number of matings.
 
 Most often, $N_{males}$ will be smaller than the total number of available males \cite[][]{Duthie}.
-Each female then chooses her $N_{males}$ mates based on her pre-copulatory inbreeding avoidance phenotype ($M_{p}$), which equals her genotype ($M_{g}$).
+Each female then chooses her $N_{males}$ mates based on her pre-copulatory inbreeding avoidance phenotype ($M_{p}$).
 Negative or positive $M_{p}$ values cause a female to avoid or prefer mating with kin, respectively, whereas $M_{p}=0$ cause females to mate randomly with respect to kinship.
 
-To calculate the probability that a focal female $i$ mates with a male $j$ to whom she is related by some kinship $k_{ij}$, each male is first assigned a perceived mate quality $Q^{m}_{ij}$.
+To calculate the probability that a female $i$ mates with a male $j$ to whom she is related by some kinship $k_{ij}$, each male is first assigned a perceived mate quality $Q^{m}_{ij}$.
 If the female has a strategy of pre-copulatory inbreeding avoidance ($M_{p}<0$), then $Q^{m}_{ij} = (-M_{p} \times k_{ij} + 1)^{-1}$, meaning that $Q^{m}_{ij}$ decreases linearly with increasingly positive values of $k_{ij}$ and increasingly negative values of $M_{p}$.
@@
 
-\subsection*{Fertilisation}
+\subsection*{Fertilisation and post-copulatory inbreeding avoidance}
 
 Following mating, fertilisation occurs such that each of a female's $n$ offspring is independently assigned a sire (with replacement) from the $N_{males}$ with which the female mated.
-Sire identity depends on female's kinship with each mate ($k_{ij}$) and her post-copulatory inbreeding strategy phenotype ($F_{p}$), which equals her genotype ($F_{g}$).
+Sire identity depends on female's kinship with each mate ($k_{ij}$) and her post-copulatory inbreeding strategy phenotype ($F_{p}$).
 Negative and positive values of $F_{p}$ correspond to post-copulatory inbreeding avoidance or preference, respectively, whereas $F_{p}=0$ causes random fertilisation with respect to kinship.
 
-The probability that an offspring of a focal female $i$ is sired by any one of $i$'s mates $j$ is calculated by assigning a perceived fertilisation quality to each $j$ with respect to $i$, $Q^{f}_{ij}$.
-Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if a focal female has a strategy of post-copulatory inbreeding avoidance ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$.
-If the focal female has strategy of post-copulatory inbreeding preference ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$.
+The probability that an offspring of female $i$ is sired by any one of $i$'s mates $j$ is calculated by assigning a perceived fertilisation quality to each $j$ with respect to $i$, $Q^{f}_{ij}$.
+Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if female $i$ has a strategy of post-copulatory inbreeding avoidance ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$.
+If the female has strategy of post-copulatory inbreeding preference ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$.
 A relative quality ($q^{f}_{ij}$) is then calculated for each male by dividing his $Q^{f}_{ij}$ by the sum of the $Q^{f}_{ij}$ values across all of a female's mates.
 These $q^{f}_{ij}$ values, which lie between zero and one, define the probability of paternity.
-Females produce $n$ offspring, so $q^{f}_{ij}$ values are sampled $n$ times independently and with replacement for each female to determine the realised distribution of sires.
+Females produce $n$ offspring, so a female $i$ samples from her mates $n$ times independently and with replacement with a probability of $q^{f}_{ij}$ for each male $j$ to determine the realised distribution of sires.
+Offspring have equal probability of being female or male.
 
@@
 When a mutation occurs, a mutation effect is sampled from a normal distribution with a mean of zero and a standard deviation of $\mu_{SD}$ and added to the original allele value \cite[][]{Kimura1965, Lande1976, Bocedi2014, Duthie}.
-The value of $\mu_{SD}$ is set to $\sqrt{1/20}$.
+The value of $\mu_{SD}$ is set to $\sqrt{1/20}$ because 20 independent alleles underlie each trait's genotypic value.
 
@@
 Given our current objectives, we simulate evolution under conditions where inbreeding avoidance is adaptive due to strong inbreeding depression, and not evolution where inbreeding preference is adaptive due to weak or zero inbreeding depression \cite[][]{Parker1979, Kokko2006, Duthie2016a}, or given outbreeding depression \cite[][]{Bateson1983, Greeff2009}.
-However, as described above, positive $M_{p}$ and $F_{p}$ values resulting in inbreeding preference are permitted to evolve, and could potentially arise due to mutation or drift.
+However, as described above, positive $M_{p}$ and $F_{p}$ values resulting in inbreeding preference are not precluded from evolving, and could potentially arise due to mutation or drift.
 
@@
 Further, immigrants' $P_{a}$, $M_{a}$, and $F_{a}$ allele values are randomly sampled from normal distributions with means and standard deviations equal to those in the focal population at the time of immigration, meaning that they do not directly cause any change in the distribution of allele values.
-We thereby effectively assume that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$.
+We thereby effectively assume that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$ \cite[][]{@Duthie; @Duthie2016a}.
 
@@
 
-When post-copulatory inbreeding avoidance was allowed to evolve, mean $P_{a}$ values became substantially higher than in comparable simulations where $F_{a}$ values were fixed to zero and post-copulatory inbreeding avoidance could not evolve (Figure 1B,D,F,H).
-Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry to the degree that most females mated multiply given low costs of polyandry ($c_{P} < 0.005$; e.g., Figure 2A,B).
-Here, $P_{a}$ allele values increased from zero and persisted at low positive values (Figure 1B,D).
-Given higher costs of polyandry ($c_{P} \geq 0.005$), $P_{a}$ allele values still initially increased from zero, but then became slightly negative over generations (Figure 1F,H).
-Trajectories of allele values in individual simulations were typically highly stochastic, but were consistent in their long-term direction (Supporting Information Figures S1-S8).
-Overall, this implies that, even given strong inbreeding depression in offspring viability and simultaneous evolution of pre-copulatory and post-copulatory strategies, inbreeding avoidance might generally be a weak force driving polyandry evolution.
-
+\vspace{2 mm}
 {\color{Gray}
@@
 }
+\vspace{2 mm}
+
+When post-copulatory inbreeding avoidance was allowed to evolve, mean $P_{a}$ values became substantially higher than in comparable simulations where $F_{a}$ values were fixed to zero and post-copulatory inbreeding avoidance could not evolve (Figure 1B,D,F,H).
+Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry to the degree that most females mated multiply given low costs of polyandry ($c_{P} < 0.005$; e.g., Figure 2A,B).
+Here, $P_{a}$ allele values increased from zero and persisted at low positive values (Figure 1B,D).
+Given higher costs of polyandry ($c_{P} \geq 0.005$), $P_{a}$ allele values still initially increased from zero, but then became slightly negative over generations (Figure 1F,H).
+Trajectories of allele values in individual simulations were typically highly stochastic, but were consistent in their long-term direction (Supporting Information Figures S1-S8).
+Overall, these results illustrate that post-copulatory inbreeding avoidance can facilitate evolution of polyandry as long as direct costs are sufficiently low (Figure 1B,D).
+However, given higher costs, evolution of polyandry is constrained even given strong inbreeding depression in offspring viability, and given resulting evolution of both pre-copulatory and post-copulatory inbreeding avoidance (Figure 1F,H).
 
@@
 This means that, even in populations where female reproductive strategy evolves toward monandry, there is still commonly some opportunity for expression of post-copulatory inbreeding avoidance and associated selection that drives evolution of post-copulatory inbreeding avoidance.
-
-Strong pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}<0$) in all simulations, irrespective of $c_{P}$ and irrespective of whether post-copulatory inbreeding avoidance was allowed to evolve or hence whether polyandry evolved (Figure 1).
-This might be expected given strong inbreeding depression in offspring viability, which imposes selection against inbreeding.
 
@@
 
+Strong pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}<0$) in all simulations, irrespective of $c_{P}$ and irrespective of whether post-copulatory inbreeding avoidance was allowed to evolve or hence whether polyandry evolved (Figure 1).
+This might be expected given strong inbreeding depression in offspring viability, which imposes selection against inbreeding.
+
 \subsection*{How do cost asymmetries affect long-term persistence of reproductive strategies?}
@@
 Likewise, when pre-copulatory inbreeding avoidance allele values ($M_{a}$) were fixed to zero, costly post-copulatory inbreeding avoidance evolved (Figure 3C).
-Females therefore evolved to avoid inbreeding, and thereby avoid the cost of producing inbred offspring, through whichever route was available.
-
-However, when both pre-copulatory and post-copulatory inbreeding avoidance could evolve, their relative evolutionary dynamics depended on their relative costs.
-When pre-copulatory but not post-copulatory inbreeding avoidance was costly ($c_{M}=0.02$ and $c_{F}=0$), pre-copulatory inbreeding avoidance initially evolved (i.e., negative $M_{a}$) but then evolved back towards random mating (i.e., $M_{a}=0$) following increasing evolution of post-copulatory inbreeding avoidance (Figure 3B).
-Similarly, when post-copulatory but not pre-copulatory inbreeding avoidance was costly ($c_{F}=0.02$ and $c_{M}=0$), post-copulatory inbreeding avoidance initially evolved ($F_{a}=0$) before evolving back to random fertilisation after ca $20000$ generations (Figure 3D).
-
-When pre-copulatory inbreeding avoidance was costly, allowing evolution of cost free post-copulatory inbreeding avoidance greatly facilitated evolution of polyandry (Figure 3A versus 3B).
-However when post-copulatory inbreeding avoidance was costly, allowing evolution of cost free pre-copulatory inbreeding avoidance caused $P_{a}$ alleles to decrease to very negative values, reducing expression of polyandry (Figure 3C versus 3D; polyandry was cost free in all these simulations).
-Results for all possible cost combinations of $0$ and $0.02$ are provided in Supporting Information (Figure S9).
+Females therefore evolved to avoid inbreeding, and thereby avoid the indirect cost of producing inbred offspring, through whichever route was available.
 
@@
 
-\subsection*{How do evolution of pre-copulatory and post-copulatory inbreeding avoidance affect one another?}
+However, when both pre-copulatory and post-copulatory inbreeding avoidance could evolve, their relative evolutionary dynamics depended on their relative costs.
+When pre-copulatory but not post-copulatory inbreeding avoidance was costly ($c_{M}=0.02$ and $c_{F}=0$), pre-copulatory inbreeding avoidance initially evolved (i.e., $M_{a} < 0$) but then evolved back towards random mating (i.e., $M_{a} \approx 0$) following increasing evolution of post-copulatory inbreeding avoidance and polyandry (Figure 3B).
+Similarly, when post-copulatory but not pre-copulatory inbreeding avoidance was costly ($c_{F}=0.02$ and $c_{M}=0$), post-copulatory inbreeding avoidance initially evolved (i.e., $F_{a} < 0$) before evolving back to random fertilisation (i.e., $F_{a} \approx 0$) after ca $20000$ generations (Figure 3D).
+
+When pre-copulatory inbreeding avoidance was costly, allowing evolution of cost free post-copulatory inbreeding avoidance greatly facilitated evolution of polyandry (Figure 3A versus 3B).
+However when post-copulatory inbreeding avoidance was costly, allowing evolution of cost free pre-copulatory inbreeding avoidance caused $P_{a}$ alleles to decrease to very negative values, reducing expression of polyandry (Figure 3C versus 3D; polyandry was cost free in all these simulations).
+Results for all possible cost combinations of $0$ and $0.02$ are provided in Supporting Information (Figure S9).
+
+{\color{Gray}
+\begin{adjustwidth}{-2.2in}{0in}
+\mysidecaption{0.70}
+{%
+   \includegraphics[height=13.5cm]{figures/fixed_adapt.pdf}%
+}
+{%
+   \captionof{figures/fixed_adapt.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is cost-free (A, $c_{M} = 0$; C, $c_{F} = 0$) or costly (B, $c_{M}=0.02$; D, $c_{F}=0.02$).
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.
+\end{justify}{\t}%
+}
+\end{adjustwidth}
+}
+
+\subsection*{How does fixation of pre-copulatory or post-copulatory inbreeding avoidance affect evolution?}
 
@@
 
-{\color{Gray}
-\begin{adjustwidth}{-2.2in}{0in}
-\mysidecaption{0.70}
-{%
-   \includegraphics[height=13.5cm]{figures/fixed_adapt.pdf}%
-}
-{%
-   \captionof{figures/fixed_adapt.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is cost-free (A, $c_{M} = 0$; C, $c_{F} = 0$) or costly (B, $c_{M}=0.02$; D, $c_{F}=0.02$).
-Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
-Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.
-\end{justify}{\t}%
-}
-\end{adjustwidth}
-}
-
 Conversely, when pre-copulatory inbreeding allele ($M_{a}$) values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently become negative over generations (Figure 4C,D).
 Fixation of pre-copulatory inbreeding avoidance therefore prevented evolution of post-copulatory inbreeding avoidance.
-However, in this case, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
-Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values among replicates (illustrated by wide standard errors, Figure 4C).
+In this case, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless of whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
+Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values (resulting in variation among replicates illustrated by the wide standard errors in Figure 4C).
 However, when $c_{F}=0.02$, $F_{a}$ values remained near zero to minimise direct costs.
@@
 Evolution of different reproductive strategies cannot be presumed to occur in isolation from each other in real-world populations.
-Rather, such evolution is likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundance) among phenotypes under selection.
+Rather, such evolution is likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundancy) among phenotypes under selection.
 For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently drive selection for polyandry \cite[e.g., ][]{Zeh1997, Jennions2000, Tregenza2002}.
-Evolution of inbreeding avoidance can be driven by selection on both pre-copulatory and post-copulatory mechanisms, so simultaneous evolution of each phenotype is likely to be defined by degeneracy, in addition to any direct costs on phenotypes.
-We used individual-based modelling to explore evolution of pre-copulatory and post-copulatory inbreeding strategy and polyandry given (1) hard constraints on evolution of post-copulatory inbreeding strategy, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding strategy, and (3) evolution of one inbreeding strategy phenotype given the pre-existence of the other.
-We thereby highlight fundamental but theoretically under-developed relationships between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding strategy.
+Inbreeding avoidance could be manifested through both pre-copulatory and post-copulatory mechanisms, meaning that simultaneous evolution of each phenotype might be defined by degeneracy in addition to trait-specific costs.
+We used individual-based modelling to highlight fundamental but theoretically under-developed relationships between evolution of polyandry and pre-copulatory versus post-copulatory inbreeding strategy given (1) hard constraints on evolution of post-copulatory inbreeding strategy, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding strategy, and (3) evolution of one inbreeding strategy phenotype given the pre-existence of the other.
 We present our model and simulation results as a tool for thinking more clearly about the dynamics of simultaneously evolving reproductive strategies, not for making accurate quantitative predictions for any specific system.
@@
 
-Evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but was affected by the joint evolution of polyandry and the existence of asymmetric costs.
-One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population by modifying its effect on inbreeding avoidance (Figure 3).
+Evolution of both pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but were affected by the evolution of polyandry and the existence of asymmetric costs.
+One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population (Figure 3).
 Consequently, long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given sufficient cost asymmetry.
 Since direct costs strongly affected the evolution of the focal phenotype(s), quantifying costs is necessary for predicting evolution of inbreeding strategies.
+
 Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging \cite[][]{Pomiankowski1987, Kokko2003}.
 \cite{Pomiankowski1987} categorised four types of costs that are relevant to mate choice, which are also relevant for polyandry, and include costs of elevated risks of predation or disease transmission, and costs incurred through time or energy expenditure.
-Another relevant cost is risk of male harm caused by sexual conflict \cite[e.g.,][]{Arnqvist2005a, Parker2006}.
-We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should benefit from a higher tolerance of inbreeding than females, leading to sexual conflict over inbreeding \cite[][]{Parker1979, Parker2006, Kokko2006, Duthie2015a}.
-Here we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates \cite[e.g.,][]{Rowe1988, Rowe1994}, a cost of pre-copulatory inbreeding strategy as a lost of time \cite[i.e., risk of not finding a mate in time due to choosiness; e.g.,][]{Kokko2013}, and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy.
+Consequently, we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates \cite[e.g.,][]{Rowe1988, Rowe1994}, a cost of pre-copulatory inbreeding strategy as a loss of time \cite[i.e., risk of not finding a mate in time due to choosiness; e.g.,][]{Kokko2013}, and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy, all manifested as an increased probability of total reproductive failure.
 While these costs reflect empirical observations in some populations and are therefore biologically realistic, other types of costs have also been observed and could be considered in future models tailored to specific systems.
-For example, increased risk of disease transmission has been observed for highly polyandrous females \cite[][]{Roberts2015a}, and such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry.
-Different types of costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
-Evolution of individual phenotypes therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.
-
-In our model, existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
-However, existence of adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Figure 3A,B).
+For example, highly polyandrous females might experience increased risk of disease transmission \cite[][]{Roberts2015a}.
+Such a cost would more realistically apply to a female's realised number of mates rather than her tendency for polyandry.
+Polyandrous females might also risk harm caused by sexual conflict over multiple mating \cite[e.g.,][]{Arnqvist2005a, Parker2006}.
+We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should be more tolerant of inbreeding than females, leading to sexual conflict over inbreeding \cite[][]{Parker1979, Parker2006, Kokko2006, Duthie2015a}.
+Future models could formally consider sexual conflict over both polyandry and inbreeding.
+Overall, such different types of costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
+Evolution of reproductive strategies therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.
+
+In our model, existence of fixed adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, precluded evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
+However, existence of fixed adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Figure 3A,B).
 In wild populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
@@
 Additionally, the opportunity for post-copulatory inbreeding avoidance will also depend on the degree to which females are polyandrous.
-For species in which pre-copulatory inbreeding avoidance occurs and polyandry is uncommon \cite[][]{Lihoreau2007, Metzger2010, Metzger2010a}, evolution of post-copulatory inbreeding avoidance is highly unlikely even if such a strategy incurs little direct cost.
+For species in which pre-copulatory inbreeding avoidance occurs and polyandry is uncommon \cite[][]{Lihoreau2007, Metzger2010, Metzger2010a}, evolution of post-copulatory inbreeding avoidance is unlikely even if such a strategy incurs little direct cost.
 
@@
 
-This work was funded by a European Research Council Starting Grant to JMR. Computer simulations were performed using the Maxwell Computing Cluster at the University of Aberdeen.
-
-%\begin{small}
+This work was funded by a European Research Council Starting Grant to JMR.
+Computer simulations were performed using the Maxwell Computing Cluster at the University of Aberdeen.
+We thank Matthew E.
+Wolak for very helpful comments on this manuscript.
+
+\begin{small}
 
@@
 
-%\end{small}
+\end{small}
 

### 2017-05-09 pre_post_biorxiv.tex
Remove clause in methods sentence

@@
 From the perspective of a breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
-Evolution of such post-copulatory inbreeding avoidance is likely to be facilitated females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout \cite[but see][]{Dougherty2016}.
+Evolution of such post-copulatory inbreeding avoidance is likely to be facilitated when females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout \cite[but see][]{Dougherty2016}.
 Such polyandry might itself be under selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative.
@@
 Overall, polyandry can therefore simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
-Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness \cite[][]{Zeh1997, Jennions2000, Tregenza2002}.
-Resulting indirect selection on polyandry to increase offspring fitness could explain evolution of polyandry in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct costs on polyandrous females.
+Polyandry has consequently been widely hypothesised to allow females to avoid inbreeding and thereby increase offspring fitness \cite[][]{Zeh1997, Jennions2000, Tregenza2002}.
+Resulting indirect selection on polyandry that stems from the increase in offspring fitness could explain evolution of polyandry in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct costs on polyandrous females.
 However, despite such widely-invoked hypotheses regarding the role of inbreeding depression in driving pre-copulatory and post-copulatory strategies and polyandry, there is surprisingly little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
@@
 
-\cite{Duthie} used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve due to selection stemming from pre-copulatory inbreeding avoidance in the absence of any post-copulatory inbreeding strategy.
+\cite{Duthie} used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve due to selection stemming from pre-copulatory inbreeding avoidance in the absence of any post-copulatory inbreeding avoidance.
 Net selection for polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., `costs') on polyandry was weak, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate \cite[][]{Duthie}.
@@
 When a mutation occurs, a mutation effect is sampled from a normal distribution with a mean of zero and a standard deviation of $\mu_{SD}$ and added to the original allele value \cite[][]{Kimura1965, Lande1976, Bocedi2014, Duthie}.
-The value of $\mu_{SD}$ is set to $\sqrt{1/20}$ because 20 independent alleles underlie each trait's genotypic value.
+The value of $\mu_{SD}$ is set to $\sqrt{1/20}$.
 
@@
 {
-   \includegraphics[height=18cm]{figures/poly_costs.pdf}%
+   \includegraphics[height=18cm]{figures/poly_costs.png}%
 }
@@
 {
-   \includegraphics[height=10.25cm]{figures/Pp_vals.pdf}%
+   \includegraphics[height=10.25cm]{figures/Pp_vals.png}%
 }
@@
 {%
-   \includegraphics[height=13.5cm]{figures/rel_costs.pdf}%
+   \includegraphics[height=13.5cm]{figures/rel_costs.png}%
 }%
@@
 {%
-   \includegraphics[height=13.5cm]{figures/fixed_adapt.pdf}%
+   \includegraphics[height=13.5cm]{figures/fixed_adapt.png}%
 }

### 2017-05-09 pre_post_biorxiv.tex
Edit Acknowledgements

@@
 Further, immigrants' $P_{a}$, $M_{a}$, and $F_{a}$ allele values are randomly sampled from normal distributions with means and standard deviations equal to those in the focal population at the time of immigration, meaning that they do not directly cause any change in the distribution of allele values.
-We thereby effectively assume that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$ \cite[][]{@Duthie; @Duthie2016a}.
+We thereby effectively assume that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$ \cite[][]{Duthie, Duthie2016a}.
 
@@
 We thank Matthew E.
-Wolak for very helpful comments on this manuscript.
+Wolak for very helpful comments.
 

### 2017-05-11 pre_post.tex
Working PDF of submitting and biorXiv versions
Final tweaks for submission

@@
 
-\renewbibmacro*{name:andothers}{% Based on name:andothers from biblatex.def
-  \ifboolexpr{
-    test {\ifnumequal{\value{listcount}}{\value{liststop}}}
-    and
-    test \ifmorenames
-  }
-    {\ifnumgreater{\value{liststop}}{1}
-       {\finalandcomma}
-       {}%
-     \andothersdelim\bibstring[\emph]{andothers}}
-    {}}
-
-\title{Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry}
+\title{Evolution of pre-copulatory and post-copulatory strategies of inbreeding avoidance and associated polyandry}
 
 \date{}
+
+\pagestyle{fancy}
+\lhead{PRE- AND POST-COPULATORY INBREEDING AVOIDANCE}
+\renewcommand{\headrulewidth}{0pt}
 
@@
 
-%\noindent {\bf A. Bradley Duthie\textsuperscript{1,*}, Aline M. Lee\textsuperscript{1}, and Jane M. Reid\textsuperscript{1}}
+%\noindent {\bf A. Bradley Duthie\textsuperscript{1,*}, Greta Bocedi\textsuperscript{2}, Ryan R. Germain\textsuperscript{2}, and Jane M. Reid\textsuperscript{2}}
 
@@
 
-%\noindent{\footnotesize \textsuperscript{1} Institute of Biological and Environmental Sciences, School of Biological Sciences, Zoology Building, Tillydrone Avenue, University of Aberdeen, Aberdeen AB24 2TZ, United Kingdom \textsuperscript{*} E-mail: aduthie@abdn.ac.uk}
+%\noindent{\footnotesize \textsuperscript{1}  Biological and Environmental Sciences, University of Stirling, Stirling FK9 4LA, United Kingdom \textsuperscript{*} E-mail: aduthie@abdn.ac.uk, Telephone: +44 7561 408101} \\
+%\noindent{\footnotesize \textsuperscript{2} Institute of Biological and Environmental Sciences, School of Biological Sciences, Zoology Building, Tillydrone Avenue, University of Aberdeen, Aberdeen AB24 2TZ, United Kingdom}
 
@@
 \noindent Submitted to the \emph{Journal of Evolutionary Biology}
+
+\vspace{15 mm}
+
+\noindent 6609 words (excluding abstract, referenes, and legends)
 
@@
 \modulolinenumbers[2]
-\doublespacing
+\onehalfspacing
 
@@
 However, surprisingly little theory or modelling critically examines selection for pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, given evolutionary constraints and direct costs, or examines how evolution of inbreeding avoidance strategies might feed back to affect evolution of polyandry.
-Selection for post-copulatory inbreeding avoidance, but not for pre-copulatory inbreeding avoidance, requires polyandry, while interactions between pre-copulatory and post-copulatory inbreeding avoidance might cause functional redundancy (i.e., 'degeneracy') potentially generating complex evolutionary dynamics among inbreeding strategies and polyandry.
+Selection for post-copulatory inbreeding avoidance, but not for pre-copulatory inbreeding avoidance, requires polyandry, while interactions between pre-copulatory and post-copulatory inbreeding avoidance might cause functional redundancy (i.e., `degeneracy') potentially generating complex evolutionary dynamics among inbreeding strategies and polyandry.
 We use individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression and different evolutionary constraints and direct costs.
-We find that evolution of post-copulatory inbreeding avoidance causes selection for increased polyandry, and that selection for a costly inbreeding avoidance strategy was weak or negligible given a cost free alternative strategy.
-Further, fixed pre-copulatory inbreeding avoidance generally precluded evolution of polyandry and therefore post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance.
-We thereby provide a general framework for understanding joint evolution of pre-copulatory and/or post-copulatory inbreeding avoidance, and conclude that evolution of inbreeding avoidance phenotypes and associated polyandry are predicted to be strongly affected by evolutionary feedbacks and degeneracy, and by direct costs on phenotypes affecting reproductive strategy.
+We find that evolution of post-copulatory inbreeding avoidance increases selection for initially rare polyandry, and that selection for a costly inbreeding avoidance strategy was weak or negligible given a cost free alternative strategy.
+Further, fixed pre-copulatory inbreeding avoidance often completely precluded evolution of polyandry and hence post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance.
+Evolution of inbreeding avoidance phenotypes and associated polyandry are therefore affected by evolutionary feedbacks and degeneracy.
+All else being equal, evolution of pre-copulatory inbreeding avoidance and resulting low polyandry is more likely when post-copulatory inbreeding avoidance is precluded or costly, and evolution of post-copulatory inbreeding avoidance greatly facilitates evolution of costly polyandry.
+
+\clearpage
 
@@
 
-From the perspective of a focal breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
-Evolution of post-copulatory inbreeding avoidance requires that females express some non-trivial degree of polyandry, defined as mating with multiple males during a single reproductive bout.
-Further, given inbreeding depression, such polyandry might itself be under selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative.
-Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm provided by females' mates (i.e., `fair raffle').
+From the perspective of a breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
+Evolution of such post-copulatory inbreeding avoidance is likely to be facilitated when females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout \cite[but see][]{Dougherty2016}.
+Such polyandry might itself be under selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative.
+Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm provided by females' mates (i.e., under conditions of a `fair raffle').
 Overall, polyandry can therefore simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
-Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness \cite[][]{Zeh1997, Jennions2000, Tregenza2002}.
-Resulting indirect selection on polyandry could explain its evolution in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct fitness costs on polyandrous females.
-However, despite such widely-invoked hypotheses, there is surprising little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
+Polyandry has consequently been widely hypothesised to allow females to avoid inbreeding and thereby increase offspring fitness \cite[][]{Zeh1997, Jennions2000, Tregenza2002}.
+Resulting indirect selection on polyandry that stems from the increase in offspring fitness could explain evolution of polyandry in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct costs on polyandrous females.
+However, despite such widely-invoked hypotheses regarding the role of inbreeding depression in driving pre-copulatory and post-copulatory strategies and polyandry, there is surprisingly little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
 
-Despite the paucity of theory and resulting predictions, numerous empirical studies on diverse species have tested for, and in some cases found evidence of, female inbreeding avoidance in systems where polyandry also occurs \cite[][but see \citealt{Reid2015a}]{Tregenza2002, Varian-Ramos2012, Kingma2013, Arct2015}.
+Despite the paucity of theory, numerous empirical studies on diverse species have tested for, and in some cases found evidence of, female inbreeding avoidance in systems where polyandry also occurs \cite[][but see \citealt{Reid2015a}]{Tregenza2002, Varian-Ramos2012, Kingma2013, Arct2015}.
 However, relatively few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
-Pre-copulatory inbreeding avoidance has been reported in diverse species, spanning sweet potato weevils \cite[\textit{Cylas formicarius};][]{Kuriwada2011}, purple-crowned fairy-wrens \cite[\textit{Malurus coronatus};][]{Kuriwada2011}, and a tropical butterfly \cite[\textit{Bicyclus anynana};][]{Fischer2015}, while post-copulatory inbreeding avoidance has been reported in red junglefowl \cite[\textit{Gallus gallus};][]{Pizzari2004} and crickets \cite[\textit{Teleogryllus oceanicus}, \textit{Gryllus bimaculatus};][]{Simmons2006, Bretman2009}.
+Pre-copulatory inbreeding avoidance has been reported in diverse species, spanning sweet potato weevils \cite[\textit{Cylas formicarius};][]{Kuriwada2011}, purple-crowned fairy-wrens \cite[\textit{Malurus coronatus};][]{Kuriwada2011}, and squinting bush brown butterflies \cite[\textit{Bicyclus anynana};][]{Fischer2015}, while post-copulatory inbreeding avoidance has been reported in red junglefowl \cite[\textit{Gallus gallus};][]{Pizzari2004} and crickets \cite[\textit{Teleogryllus oceanicus}, \textit{Gryllus bimaculatus};][]{Simmons2006, Bretman2009}.
 Evidence for both pre-copulatory and post-copulatory inbreeding avoidance is available across different studies of Trinidadian guppies \cite[\textit{Poecilia reticulata};][]{Gasparini2011, Daniel2015} and house mice \cite[\textit{Mus domesticus};][]{Potts1991, Firman2015}.
 Meanwhile, \cite{Liu2014} found evidence of pre-copulatory but not post-copulatory inbreeding avoidance within a single study of cabbage beetles (\textit{Colaphellus bowringi}).
-However, \cite{Ala-Honkola2011} and \cite{Tan2012} found no evidence for pre-copulatory or post-copulatory inbreeding avoidance in fruit flies (\textit{Drosophila melanogaster}), respectively, and Reid \textit{et al.} \citeyearpar{Reid2014, Reid2015} found no net inbreeding avoidance in song sparrows (\textit{Melospiza melodia}) despite strong inbreeding depression.
-Taken together, these studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature alongside polyandry.
-However, there is as yet no theory that predicts what combinations of pre-copulatory and post-copulatory inbreeding avoidance and polyandry should be favoured by selection when all combinations of phenotypes can evolve.
-Consequently, there is no theory that allows the diversity of existing empirical results regarding pre-copulatory and post-copulatory inbreeding avoidance to be interpreted, and no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
+However, \cite{Ala-Honkola2011} and \cite{Tan2012} found no evidence for pre-copulatory or post-copulatory inbreeding avoidance in fruit flies (\textit{Drosophila melanogaster}), respectively, and Reid et al.
+\citeyearpar{Reid2014, Reid2015} found no net inbreeding avoidance in song sparrows (\textit{Melospiza melodia}) despite strong inbreeding depression and opportunities for both pre-copulatory and post-copulatory inbreeding avoidance.
+Taken together, these studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance, or lack thereof, occur in nature.
+However, there is as yet no theory that predicts what combinations of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry should be favoured by selection when all can evolve.
+Consequently, there is no theory that allows the diversity of observed pre-copulatory and post-copulatory inbreeding avoidance strategies to be interpreted, and no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
 
-To develop theory on evolution of polyandry given inbreeding depression, \cite{Duthie} used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance.
+\cite{Duthie} used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve due to selection stemming from pre-copulatory inbreeding avoidance in the absence of any post-copulatory inbreeding avoidance.
 Net selection for polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., `costs') on polyandry was weak, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate \cite[][]{Duthie}.
@@
 
-We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply 'inbreeding strategies' because the model did not preclude evolution of inbreeding preference), by tracking the dynamics of alleles underlying reproductive strategies enacted by interacting females and males within a small focal population.
+We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply `inbreeding strategies' because the model did not preclude evolution of inbreeding preference), in a small focal population of females and males by tracking the dynamics of alleles underlying reproductive strategies expressed by females.
 We thereby track evolutionary dynamics given internally consistent patterns of relatedness caused by non-random mating and allowing for effects of mutation, gene flow, drift, and selection.
-Each individual has 10 diploid loci, and therefore 20 alleles, underlying each of three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$, i.e., `polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., `mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., `fertilisation' alleles).
-All alleles can take the value of any real number \cite[i.e., a continuum-of-alleles model;][]{Kimura1965, Lande1976, Reeve2000, Bocedi2014} and combine additively to affect genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively, whereby an individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
-In overview, each generation proceeds with females paying costs and expressing polyandry, mating, and fertilisation.
-Offspring inherit a randomly sampled allele from each parent at each locus with no physical linkage.
+
+All individuals have 10 physically unlinked diploid loci, and therefore 20 alleles, underlying each of three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$, i.e., `polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., `mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., `fertilisation' alleles).
+All alleles can take the value of any real number \cite[i.e., a continuum-of-alleles model;][]{Kimura1965, Lande1976, Reeve2000, Bocedi2014} and combine additively to determine genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and resulting phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively.
+Each individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
+Each individual's phenotypic values for pre-copulatory and post-copulatory inbreeding strategy equal their respective genotypic values ($M_{p} = M_{g}$ and $F_{p} = F_{g}$), where negative and positive values cause inbreeding avoidance and preference, respectively (see details of mating and fertilisation strategies below).
+In contrast, phenotypic values for tendency for polyandry equal genotypic values ($P_{p} = P_{g}$) only if $P_{g} \geq 0$, while $P_{p} = 0$ if $P_{g} < 0$ because females cannot choose a negative number of mates.
+Polyandry is therefore modelled as a threshold trait \cite[][]{Lynch1998, Roff1996, Roff1998, Duthie} that is influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
+A negative $P_{g}$ value therefore generates a female that is phenotypically monandrous, while a positive $P_{g}$ value generates a female that can express some degree of polyandry (see details below).
+
+In overview, each generation proceeds with females paying costs associated with their reproductive strategy traits, and expressing polyandry, mating, and fertilisation.
+Offspring inherit a randomly sampled allele from each parent at each locus.
 Alleles can then mutate and offspring express inbreeding depression in viability.
@@
 
-Phenotypic values of $P_{p}$, $M_{p}$, and $F_{p}$ each have costs that are assumed to independently increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
+Phenotypic values of the three reproductive strategy traits each have costs that are assumed to combine independently to increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
 The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
 Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
-Absolute values are used for applying costs to inbreeding avoidance strategies because both negative and positive $M_{p}$ and $F_{p}$ values could potentially arise and affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively (see details of mating and fertilisation strategies below).
-In contrast, only positive values of $P_{p}$ cause females to be polyandrous (see details of polyandry below).
+Absolute values are used for applying costs to inbreeding avoidance strategies because both negative and positive $M_{p}$ and $F_{p}$ values could potentially arise and affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively.
+In contrast, $P_{p}$ cannot be negative.
 Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
 
-\subsection*{Polyandry}
+\subsection*{Mating and pre-copulatory inbreeding avoidance}
 
 After costs are realised, each remaining female chooses $N_{males}$ males to mate with, where $N_{males}$ is calculated by sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
-This ensures that all surviving females choose at least one mate, and causes some stochastic variation around the expected mean $N_{males}$ of $P_{p}+1$.
-A female's value of $P_{p}$ depends on the sum of her 20 $P_{a}$ allele values (i.e., $P_{g}$), which might be negative or positive.
-However, because females cannot mate with a negative number of males, $P_{p}$ is constrained to be zero or positive such that $P_{p} = 0$ when $P_{g} < 0$, but $P_{p} = P_{g}$ when $P_{g} \geq 0$.
-Polyandry is therefore modelled as a threshold trait \cite[][]{Lynch1998, Roff1996, Roff1998, Duthie} that is influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
-Any negative $P_{g}$ value therefore generates phenotypic monandry, while positive $P_{g}$ values can lead to different degrees of realised polyandry (i.e., different numbers of mates, $N_{males}$).
-
-\subsection*{Mating}
+This ensures that all surviving females choose at least one mate and generates each female's realised degree of polyandry with some stochastic variation around the expected mean $N_{males}$ of $P_{p}+1$.
 
@@
 Further, immigrants' $P_{a}$, $M_{a}$, and $F_{a}$ allele values are randomly sampled from normal distributions with means and standard deviations equal to those in the focal population at the time of immigration, meaning that they do not directly cause any change in the distribution of allele values.
-We thereby effectively assume that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$.
+We thereby effectively assume that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$ \cite[][]{Duthie, Duthie2016a}.
 
@@
 
-To address whether or not evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance can facilitate evolution of polyandry, we compare simulations in which polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, with otherwise identical simulations in which post-copulatory inbreeding avoidance cannot evolve given four different costs of polyandry ($c_{P}$ = $\{$0, 0.0025, 0.005,  0.01$\}$).
-To prevent post-copulatory inbreeding avoidance from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes cause random fertilisation with respect to kinship, so $F_{a}$ alleles have no phenotypic effect.
+To address whether or not evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance can facilitate evolution of polyandry, we compare simulations in which polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve with otherwise identical simulations in which post-copulatory inbreeding avoidance cannot evolve.
+To achieve this, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes cause random fertilisation with respect to kinship, so $F_{a}$ alleles have no phenotypic effect.
+Simulations were repeated across four different costs of polyandry ($c_{P} = \{0, 0.0025, 0.005,  0.01\}$).
 
@@
 
-When post-copulatory inbreeding avoidance alleles ($F_{a}$) had no effect (i.e., $F_{g}$ values were fixed to zero), meaning that $F_{p}$ could not evolve, $P_{a}$ alleles underlying polyandry always decreased to negative values over generations (red lines, Figure 1A,C,E,G).
-This shows that despite strong inbreeding depression in offspring viability, there is selection against unconditional polyandry even given zero direct cost ($c_{P}=0$; Figure 1A).
-This is because $M_{a}$ values became negative over generations, meaning that females typically avoided inbreeding through their initial mating (blue lines, Figure 1A,C,E,G).
+When post-copulatory inbreeding avoidance alleles ($F_{a}$) had no effect (i.e., $F_{g}$ values were fixed to zero), meaning that $F_{p}$ could not evolve, $P_{a}$ alleles underlying polyandry always decreased to negative values over generations (red lines, Fig.
+1A,C,E,G).
+This shows that despite strong inbreeding depression in offspring viability, there is selection against unconditional polyandry even given zero direct cost ($c_{P}=0$; Fig.
+1A).
+This is because $M_{a}$ values became negative over generations, meaning that females typically avoided inbreeding through their initial mating (blue lines, Fig.
+1A,C,E,G).
 Polyandrous females that subsequently sampled more males from the available population were consequently more likely to mate with some relatives and hence produce some inbred offspring with low viability \cite[][]{Duthie}.
 
-When post-copulatory inbreeding avoidance was allowed to evolve, mean $P_{a}$ values became substantially higher than in comparable simulations where $F_{a}$ values were fixed to zero and post-copulatory inbreeding avoidance could not evolve (Figure 1B,D,F,H).
-Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry to the degree that most females mated multiply given low costs of polyandry ($c_{P} < 0.005$; e.g., Figure 2A,B).
-Here, $P_{a}$ allele values increased from zero and persisted at low positive values (Figure 1B,D).
-Given higher costs of polyandry ($c_{P} \geq 0.005$), $P_{a}$ allele values still initially increased from zero, but then became slightly negative over generations (Figure 1F,H).
-Trajectories of allele values in individual simulations were typically highly stochastic, but were consistent in their long-term direction (Supporting Information Figures S1-S8).
-Overall, this implies that, even given strong inbreeding depression in offspring viability and simultaneous evolution of pre-copulatory and post-copulatory strategies, inbreeding avoidance might generally be a weak force driving polyandry evolution.
+When post-copulatory inbreeding avoidance was allowed to evolve, mean $P_{a}$ values became substantially higher than in comparable simulations where $F_{a}$ values were fixed to zero and post-copulatory inbreeding avoidance could not evolve (Fig.
+1B,D,F,H).
+Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry to the degree that most females mated multiply given low costs of polyandry ($c_{P} < 0.005$; e.g., Fig.
+2A,B).
+Here, $P_{a}$ allele values increased from zero and persisted at low positive values (Fig.
+1B,D).
+Given higher costs of polyandry ($c_{P} \geq 0.005$), $P_{a}$ allele values still initially increased from zero, but then became slightly negative over generations (Fig.
+1F,H).
+Trajectories of allele values in individual simulations were typically highly stochastic, but were consistent in their long-term direction (Supporting Information Fig.
+S1-S8).
+Overall, these results illustrate that post-copulatory inbreeding avoidance can facilitate evolution of polyandry as long as direct costs are sufficiently low (Fig.
+1B,D).
+However, given higher costs, evolution of polyandry is constrained even given strong inbreeding depression in offspring viability, and given resulting evolution of both pre-copulatory and post-copulatory inbreeding avoidance (Fig.
+1F,H).
 
-Strong post-copulatory inbreeding avoidance, manifested as very negative $F_{a}$ values, consistently evolved in all simulations where such evolution was allowed (black lines, Figure 1B,D,F,H).
-Evolution of post-copulatory inbreeding avoidance occurred even when $P_{a}$ values were expected to be slightly negative, and hence when there was selection against polyandry (Figure 1F,H).
-This reflects the threshold nature of phenotypic expression of polygenic polyandry, wherein random sampling of alleles means that polyandry is expressed by some females (i.e., $P_{g}>0$) even when mean $P_{a}$ values are negative (Figure 2).
+Strong post-copulatory inbreeding avoidance, manifested as very negative $F_{a}$ values, consistently evolved in all simulations where such evolution was allowed (black lines, Fig.
+1B,D,F,H).
+Evolution of post-copulatory inbreeding avoidance occurred even when $P_{a}$ values were expected to be slightly negative, and hence when there was selection against polyandry (Fig.
+1F,H).
+This reflects the threshold nature of phenotypic expression of polygenic polyandry, wherein random sampling of alleles means that polyandry is expressed by some females (i.e., $P_{g}>0$) even when mean $P_{a}$ values are negative (Fig.
+2).
 This means that, even in populations where female reproductive strategy evolves toward monandry, there is still commonly some opportunity for expression of post-copulatory inbreeding avoidance and associated selection that drives evolution of post-copulatory inbreeding avoidance.
 
-Strong pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}<0$) in all simulations, irrespective of $c_{P}$ and irrespective of whether post-copulatory inbreeding avoidance was allowed to evolve or hence whether polyandry evolved (Figure 1).
+Strong pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}<0$) in all simulations, irrespective of $c_{P}$ and irrespective of whether post-copulatory inbreeding avoidance was allowed to evolve or hence whether polyandry evolved (Fig.
+1).
 This might be expected given strong inbreeding depression in offspring viability, which imposes selection against inbreeding.
@@
 
-When post-copulatory inbreeding avoidance allele values ($F_{a}$) were fixed to zero, pre-copulatory inbreeding avoidance evolved even when costly (Figure 3A).
-Likewise, when pre-copulatory inbreeding avoidance allele values ($M_{a}$) were fixed to zero, costly post-copulatory inbreeding avoidance evolved (Figure 3C).
-Females therefore evolved to avoid inbreeding, and thereby avoid the cost of producing inbred offspring, through whichever route was available.
+When post-copulatory inbreeding avoidance allele values ($F_{a}$) were fixed to zero, pre-copulatory inbreeding avoidance evolved even when costly (Fig.
+3A).
+Likewise, when pre-copulatory inbreeding avoidance allele values ($M_{a}$) were fixed to zero, costly post-copulatory inbreeding avoidance evolved (Fig.
+3C).
+Females therefore evolved to avoid inbreeding, and thereby avoid the indirect cost of producing inbred offspring, through whichever route was available.
 
 However, when both pre-copulatory and post-copulatory inbreeding avoidance could evolve, their relative evolutionary dynamics depended on their relative costs.
-When pre-copulatory but not post-copulatory inbreeding avoidance was costly ($c_{M}=0.02$ and $c_{F}=0$), pre-copulatory inbreeding avoidance initially evolved (i.e., negative $M_{a}$) but then evolved back towards random mating (i.e., $M_{a}=0$) following increasing evolution of post-copulatory inbreeding avoidance (Figure 3B).
-Similarly, when post-copulatory but not pre-copulatory inbreeding avoidance was costly ($c_{F}=0.02$ and $c_{M}=0$), post-copulatory inbreeding avoidance initially evolved ($F_{a}=0$) before evolving back to random fertilisation after ca $20000$ generations (Figure 3D).
+When pre-copulatory but not post-copulatory inbreeding avoidance was costly ($c_{M}=0.02$ and $c_{F}=0$), pre-copulatory inbreeding avoidance initially evolved (i.e., $M_{a} < 0$) but then evolved back towards random mating (i.e., $M_{a} \approx 0$) following increasing evolution of post-copulatory inbreeding avoidance and polyandry (Fig.
+3B).
+Similarly, when post-copulatory but not pre-copulatory inbreeding avoidance was costly ($c_{F}=0.02$ and $c_{M}=0$), post-copulatory inbreeding avoidance initially evolved (i.e., $F_{a} < 0$) before evolving back to random fertilisation (i.e., $F_{a} \approx 0$) after ca $20000$ generations (Fig.
+3D).
 
-When pre-copulatory inbreeding avoidance was costly, allowing evolution of cost free post-copulatory inbreeding avoidance greatly facilitated evolution of polyandry (Figure 3A versus 3B).
-However when post-copulatory inbreeding avoidance was costly, allowing evolution of cost free pre-copulatory inbreeding avoidance caused $P_{a}$ alleles to decrease to very negative values, reducing expression of polyandry (Figure 3C versus 3D; polyandry was cost free in all these simulations).
-Results for all possible cost combinations of $0$ and $0.02$ are provided in Supporting Information (Figure S9).
+When pre-copulatory inbreeding avoidance was costly, allowing evolution of cost free post-copulatory inbreeding avoidance greatly facilitated evolution of polyandry (Fig.
+3A versus 3B).
+However when post-copulatory inbreeding avoidance was costly, allowing evolution of cost free pre-copulatory inbreeding avoidance caused $P_{a}$ alleles to decrease to very negative values, reducing expression of polyandry (Fig.
+3C versus 3D; polyandry was cost free in all these simulations).
+Results for all possible cost combinations of $0$ and $0.02$ are provided in Supporting Information (Fig.
+S9).
 
-\subsection*{How do evolution of pre-copulatory and post-copulatory inbreeding avoidance affect one another?}
+\subsection*{How does fixation of pre-copulatory or post-copulatory inbreeding avoidance affect evolution?}
 
-When polyandry alleles ($P_{a}$) were fixed to be positive so that all females were expected to mate multiply and post-copulatory inbreeding allele ($F_{a}$) values were fixed for adaptive inbreeding avoidance, pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}$ values became increasingly negative; Figure 4A).
-Such evolution still occurred, but to a much smaller degree, when pre-copulatory inbreeding avoidance was costly (Figure 4B).
+When polyandry alleles ($P_{a}$) were fixed to be positive so that all females were expected to mate multiply and post-copulatory inbreeding allele ($F_{a}$) values were fixed for adaptive inbreeding avoidance, pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}$ values became increasingly negative; Fig.
+4A).
+Such evolution still occurred, but to a much smaller degree, when pre-copulatory inbreeding avoidance was costly (Fig.
+4B).
 However, after $40000$ generations, $M_{a}$ values were less negative when post-copulatory inbreeding avoidance and polyandry were fixed at non-zero values than when they also evolved from initial values of zero ($-15.45$ vs.
-$-17.62$; compare the blue lines in Figures 4A versus Figure 1B).
+$-17.62$; compare the blue lines in Fig.
+4A versus Fig.
+1B).
 This shows that fixation of post-copulatory inbreeding avoidance weakens selection for pre-copulatory inbreeding avoidance.
 
-Conversely, when pre-copulatory inbreeding allele ($M_{a}$) values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently become negative over generations (Figure 4C,D).
+Conversely, when pre-copulatory inbreeding allele ($M_{a}$) values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently become negative over generations (Fig.
+4C,D).
 Fixation of pre-copulatory inbreeding avoidance therefore prevented evolution of post-copulatory inbreeding avoidance.
-However, in this case, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
-Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values among replicates (illustrated by wide standard errors, Figure 4C).
+In this case, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless of whether or not post-copulatory inbreeding avoidance was costly (Fig.
+4C,D).
+Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values (resulting in variation among replicates illustrated by the wide standard errors in Fig.
+4C).
 However, when $c_{F}=0.02$, $F_{a}$ values remained near zero to minimise direct costs.
 This lack of selection for post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
-When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information Figure S10).
+When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Fig.
+4A,B (see Supporting Information Fig.
+S10).
 
@@
 The opportunity to adjust inbreeding has been widely suggested to be a driver of adaptive evolution of polyandry \cite[][]{Tregenza2002, Foerster2003, Akcay2007, Varian-Ramos2012, Kingma2013, Lehtonen2015, Reid2014}.
-We found that when post-copulatory inbreeding avoidance could evolve, selection for and resulting evolution of polyandry was greatly strengthened (Figure 1).
+We found that when post-copulatory inbreeding avoidance could evolve, selection for and resulting evolution of polyandry was greatly strengthened (Fig.
+1).
 The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new \cite[e.g.,][]{Zeh1997}, but our model clarifies this verbal hypothesis and therefore has widespread implications for future studies of evolution of polyandry.
 
-We predict evolution of polyandry in populations where inbreeding depression is severe and inbreeding avoidance through post-copulatory mechanisms can also evolve, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
+We predict evolution of polyandry in populations where inbreeding depression is severe and inbreeding avoidance through post-copulatory mechanisms can also evolve, especially if pre-copulatory inbreeding avoidance is costly (Fig.
+1).
 Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa \cite[e.g.,][]{Pizzari2004, Firman2008, Bretman2009, Gasparini2011, Tuni2013, Firman2015}.
@@
 
-Evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but was affected by the joint evolution of polyandry and the existence of asymmetric costs.
-One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population by modifying its effect on inbreeding avoidance (Figure 3).
+Evolution of both pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but were affected by the evolution of polyandry and the existence of asymmetric costs.
+One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population (Fig.
+3).
 Consequently, long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given sufficient cost asymmetry.
 Since direct costs strongly affected the evolution of the focal phenotype(s), quantifying costs is necessary for predicting evolution of inbreeding strategies.
+
 Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging \cite[][]{Pomiankowski1987, Kokko2003}.
 \cite{Pomiankowski1987} categorised four types of costs that are relevant to mate choice, which are also relevant for polyandry, and include costs of elevated risks of predation or disease transmission, and costs incurred through time or energy expenditure.
-Another relevant cost is risk of male harm caused by sexual conflict \cite[e.g.,][]{Arnqvist2005a, Parker2006}.
-We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should benefit from a higher tolerance of inbreeding than females, leading to sexual conflict over inbreeding \cite[][]{Parker1979, Parker2006, Kokko2006, Duthie2015a}.
-Here we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates \cite[e.g.,][]{Rowe1988, Rowe1994}, a cost of pre-copulatory inbreeding strategy as a lost of time \cite[i.e., risk of not finding a mate in time due to choosiness; e.g.,][]{Kokko2013}, and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy.
+Consequently, we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates \cite[e.g.,][]{Rowe1988, Rowe1994}, a cost of pre-copulatory inbreeding strategy as a loss of time \cite[i.e., risk of not finding a mate in time due to choosiness; e.g.,][]{Kokko2013}, and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy, all manifested as an increased probability of total reproductive failure.
 While these costs reflect empirical observations in some populations and are therefore biologically realistic, other types of costs have also been observed and could be considered in future models tailored to specific systems.
-For example, increased risk of disease transmission has been observed for highly polyandrous females \cite[][]{Roberts2015a}, and such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry.
-Different types of costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
-Evolution of individual phenotypes therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.
+For example, highly polyandrous females might experience increased risk of disease transmission \cite[][]{Roberts2015a}.
+Such a cost would more realistically apply to a female's realised number of mates rather than her tendency for polyandry.
+Polyandrous females might also risk harm caused by sexual conflict over multiple mating \cite[e.g.,][]{Arnqvist2005a, Parker2006}.
+We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should be more tolerant of inbreeding than females, leading to sexual conflict over inbreeding \cite[][]{Parker1979, Parker2006, Kokko2006, Duthie2015a}.
+Future models could formally consider sexual conflict over both polyandry and inbreeding.
+Overall, such different types of costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
+Evolution of reproductive strategies therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.
 
-In our model, existence of adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
-However, existence of adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Figure 3A,B).
+In our model, existence of fixed adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, precluded evolution of post-copulatory inbreeding avoidance (Fig.
+3C,D).
+However, existence of fixed adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Fig.
+3A,B).
 In wild populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
@@
 
-Post-copulatory inbreeding avoidance cannot be realised if females are not polyandrous, and is most effective for highly polyandrous females that can choose amongst multiple mates and therefore bias fertilisation accordingly.
+Post-copulatory inbreeding avoidance cannot be effectively realised if females are not polyandrous in any form, and is likely to be most effective for highly polyandrous females that can choose amongst sperm contributed by multiple mates and therefore bias fertilisation accordingly.
 In contrast, pre-copulatory inbreeding avoidance mechanisms are most critical for females that mate only once and therefore have no post-copulatory opportunity to avoiding inbreeding.
-This theory is borne out in our simulation results, as selection for, and consequent evolution of, post-copulatory inbreeding avoidance was negligible in populations where polyandry did not evolve, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D).
-Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information Figure S9).
-In addition to polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).
-It would therefore be interesting to test the hypothesis that, across taxa, occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with the degree of polyandry.
+This theory is borne out in our simulation results, as selection for, and consequent evolution of, post-copulatory inbreeding avoidance was negligible in populations where polyandry did not evolve, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Fig.
+4C,D).
+Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Fig.
+3A vs 3B; see also Supporting Information Fig.
+S9).
+In addition to initial polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back effect that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Fig.
+1).
+It would therefore be interesting to test the hypothesis that, across taxa, the occurrence of post-copulatory inbreeding avoidance covaries positively, and the occurrence of pre-copulatory inbreeding avoidance covaries negatively, with the degree of polyandry.
 To test this hypothesis, more work is needed to quantify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
@@
 \newblock \textit{Evolution} \textbf{60}:467--475.
-% ==================================================================================================
+
 \bibitem[{Kuriwada \textit{et~al.}(2011)Kuriwada, Kumano, Shiromoto \&
@@
   copulatory inbreeding avoidance in the cabbage beetle \textit{Colaphellus bowringi}.}
-\newblock \textit{PloS one} \textbf{9}:e94389.
+\newblock \textit{PloS One} \textbf{9}:e94389.
 
@@
   Duthie, Losdat, Wolak \& Nietlisbach}]{Reid2014}
-Reid, J.~M., Arcese, P., Keller, L.~F., Germain, R.~R., Duthie, A.~B., Losdat, S.,
-  Wolak, M.~E. \& Nietlisbach, P. 2015{\natexlab{\emph{a}}}.
+Reid, J.~M., Arcese, P., Keller, L.~F., Germain, R.~R., Duthie, A.~B., Losdat, S. 
+\textit{et~al.} 2015{\natexlab{\emph{a}}}.
 \newblock {Quantifying inbreeding avoidance through extra-pair reproduction}.
@@
 \begin{center}				
-\includegraphics[scale=0.85]{figures/poly_costs.pdf}
+\includegraphics[scale=0.85]{poly_costs.eps}
 \end{center}
@@
 \begin{center}				
-\includegraphics[scale=0.60]{figures/Pp_vals.pdf}
+\includegraphics[scale=0.60]{Pp_vals.eps}
 \end{center}
@@
 \begin{center}				
-\includegraphics[scale=1.00]{figures/rel_costs.pdf}
+\includegraphics[scale=1.00]{rel_costs.eps}
 \end{center}
@@
 \begin{center}				
-\includegraphics[scale=1.00]{figures/fixed_adapt.pdf}
+\includegraphics[scale=1.00]{fixed_adapt.eps}
 \end{center}

### 2017-07-04 ms_pre_post.Rmd
Fix text for first two reviewer comments

@@
 author: ''
-date: "1 May 2017"
+date: "4 May 2017"
 output:
-  html_document: default
-  pdf_document:
-    fig_caption: yes
   word_document:
@@
 From the perspective of a breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
-Evolution of such post-copulatory inbreeding avoidance is likely to be facilitated females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout [but see @Dougherty2016].
+Evolution of such post-copulatory inbreeding avoidance is likely to be facilitated when females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout [but see @Dougherty2016].
 Such polyandry might itself be under selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative.
@@
 Overall, polyandry can therefore simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
-Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002].
-Resulting indirect selection on polyandry to increase offspring fitness could explain evolution of polyandry in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct costs on polyandrous females.
+Polyandry has consequently been widely hypothesised to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002].
+Resulting indirect selection on polyandry that stems from the increase in offspring fitness could explain evolution of polyandry in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct costs on polyandrous females.
 However, despite such widely-invoked hypotheses regarding the role of inbreeding depression in driving pre-copulatory and post-copulatory strategies and polyandry, there is surprisingly little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
-
-<!--- I really don't think the connection between 'resulting indirect selection' and *offspring* rather than *parent* fitness is going to be made easily by a lot of readers.
-You've thought a lot about this, so I think we need to be careful for readers who are still not up to date on the selection-on-inbreeding versus selection-on-being-inbred distinction.
---->
 
@@
 However, relatively few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
-Pre-copulatory inbreeding avoidance has been reported in diverse species, spanning sweet potato weevils [*Cylas formicarius*, @Kuriwada2011], purple-crowned fairy-wrens [*Malurus coronatus*, @Kuriwada2011], and squinting bush brown butterflies [*Bicyclus anynana*, @Fischer2015], while post-copulatory inbreeding avoidance has been reported in red junglefowl [*Gallus gallus*, @Pizzari2004] and crickets [*Teleogryllus oceanicus*, @Simmons2006; *Gryllus bimaculatus*, @Bretman2009].
+Pre-copulatory inbreeding avoidance has been reported in diverse species, spanning sweet potato weevils [*Cylas formicarius*, @Kuriwada2011], purple-crowned fairy-wrens [*Malurus coronatus*, @Kuriwada2011], and squinting bush brown butterflies [*Bicyclus anynana*, @Fischer2015], while post-copulatory inbreeding avoidance has been reported in, **e.g.,** red junglefowl [*Gallus gallus*, @Pizzari2004] and crickets [*Teleogryllus oceanicus*, @Simmons2006; *Gryllus bimaculatus*, @Bretman2009].
 Evidence for both pre-copulatory and post-copulatory inbreeding avoidance is available across different studies of Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015].
@@
 
-@Duthie used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve due to selection stemming from pre-copulatory inbreeding avoidance in the absence of any post-copulatory inbreeding strategy.
-Net selection for polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., 'costs') on polyandry was weak, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
-Without these conditions, increasing polyandry tended to increase rather than decrease the overall degree of inbreeding that females experienced, and hence reduce offspring fitness.
-This occurred because, once pre-copulatory inbreeding avoidance evolved, polyandrous females had already chosen available unrelated males as their initial mates.
+@Duthie used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve due to selection stemming from pre-copulatory inbreeding avoidance in the absence of any post-copulatory inbreeding avoidance.
+**Even when selection for pre-copulatory inbreeding avoidance was strong and females consequently preferred unrelated mates, selection for polyandry specifically as a mechanism to facilitate this inbreeding avoidance** occurred only under highly restricted conditions, requiring that direct negative selection (i.e., 'costs') on polyandry was weak, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
+Without these conditions, **females that engaged in** polyandry tended **to be constrained** to increase rather than decrease **their** overall degree of inbreeding, **ultimately** reduc**ing** offspring fitness.
+This **constraint** occurred because, once pre-copulatory inbreeding avoidance evolved, polyandrous females had already chosen available unrelated males as their initial mates.
 Their additional mates, chosen from the remaining male population, were therefore increasingly likely to include relatives.

### 2017-07-05 ms_pre_post.Rmd
Fix all concerns raised by Reviewer 1

@@
 
-Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will depend not only on the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also on the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
-Polyandrous females can pay costs of mate searching or mating, for example, because these activities increase predation risk [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
+Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will **be affected not only by** the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also **by** the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
+**There are multiple mechanisms by which direct costs might by incurred for polyandry, pre-copulatory choice, and post-copulatory choice; here we focus on three examples observed in empirical populations.** Polyandrous females **might** pay costs of mate searching or mating because these activities increase predation risk [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
 Females that express pre-copulatory choice and consequent reluctance to mate with relatives might pay costs of increased risk of complete mating failure or harm caused by sexual conflict [@Rowe1994; @Kokko2013].
-Females that express post-copulatory choice might pay initial energetic costs associated with developing the physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
+**Finally,** females that express post-copulatory choice might pay initial energetic costs associated with developing the physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
 If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly strategy might become extinct, especially if their effects are made redundant by evolution of the less costly strategy.
@@
 Third, how is selection for initially rare pre-copulatory or post-copulatory inbreeding avoidance affected if the other strategy of inbreeding avoidance is already fixed?
-By addressing these questions, we illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
+**For each question, we isolate the effect of the biological mechanism of interest (i.e., post-copulatory inbreeding avoidance, cost asymmetry, and another fixed strategy of inbreeding avoidance) by running simulations in which the mechanism is present and comparing the results to those of simulations in which the it is absent but all other parameter values are identical** By addressing these **three** questions, we illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
 
@@
 Alleles can then mutate and offspring express inbreeding depression in viability.
-Immigrants arrive in the population and density regulation limits population growth.
+Immigrants arrive in the population and density regulation limits population growth **(see below)**.
 We record the population pedigree and directly calculate the coefficient of kinship ($k$) between all potential mates in each generation (defined as the probability that two homologous alleles will be identical-by-descent), allowing individual pre-copulatory and post-copulatory inbreeding strategies to be enacted.
@@
 Offspring have equal probability of being female or male.
+**After offspring production, all female and male adults die so that generations are non-overlapping.**
 
@@
 We therefore define $\Psi_{\textrm{off}}$ as the probability that an offspring is viable, and sample its realised viability (versus mortality) using a Bernoulli trial.
-Given our current objectives, we simulate evolution under conditions where inbreeding avoidance is adaptive due to strong inbreeding depression, and not evolution where inbreeding preference is adaptive due to weak or zero inbreeding depression [@Parker1979; @Kokko2006; @Duthie2016a], or given outbreeding depression [@Bateson1983; @Greeff2009].
+**Offspring that are viable after the Bernoulli trial become adults.** Given our current objectives, we simulate evolution under conditions where inbreeding avoidance is adaptive due to strong inbreeding depression, and not evolution where inbreeding preference is adaptive due to weak or zero inbreeding depression [@Parker1979; @Kokko2006; @Duthie2016a], or given outbreeding depression [@Bateson1983; @Greeff2009].
 However, as described above, positive $M_{p}$ and $F_{p}$ values resulting in inbreeding preference are not precluded from evolving, and could potentially arise due to mutation or drift.
@@
 To avoid unrestricted population growth, we set separate carrying capacities for the total numbers of females ($K_{f}$) and males ($K_{m}$) in the focal population following immigration [@Guillaume2009; @Duthie].
-If at the end of a generation the number of females or males exceeds $K_{f}$ or $K_{m}$  respectively, then individuals are randomly removed until each sex is at its carrying capacity.
+Hence, if at the end of a generation the number of female or male **offspring** exceeds $K_{f}$ or $K_{m}$  respectively, then individuals are randomly removed until each sex is at its carrying capacity.
 Such removal can be interpreted as some combination of dispersal and mortality.
@@
 
-How does fixation of pre-copulatory or post-copulatory inbreeding avoidance affect evolution?
+How does fixation of pre-copulatory or post-copulatory inbreeding avoidance affect evolution **of an alternative strategy of inbreeding avoidance**?
 ----------------------------------------------
@@
 ******************************
-
-<!--- --------------------------------------------------------------------- --->
-<!--- LEFT OFF HERE  ------------------------------------------------------ --->
-<!--- --------------------------------------------------------------------- --->
 
@@
 Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging [@Pomiankowski1987; @Kokko2003].
-@Pomiankowski1987 categorised four types of costs that are relevant to mate choice, which are also relevant for polyandry, and include costs of elevated risks of predation or disease transmission, and costs incurred through time or energy expenditure.
+@Pomiankowski1987 categorised four types of costs that are relevant to **mating frequency and** mate choice, which are also relevant for polyandry, and include costs of elevated risks of predation or disease transmission, and costs incurred through time or energy expenditure.
 Consequently, we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of pre-copulatory inbreeding strategy as a loss of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy, all manifested as an increased probability of total reproductive failure.

### 2017-07-06 analysis.R
Add new figures to be made after cost asymmetry supplemental simulations are complete

@@ -1726,7 +1726,6 @@ dev.off();
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 
 
-
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 # XXX SUPPORTING INFORMATION FOR P00 M02 F02 SIMULATIONS  XXX XXX XXX XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
@@ -1905,3 +1904,164 @@ mtext(expression(paste("Mean allele value correlation\t\t\t\t\t\t")),
 dev.off();
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
 
+
+
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX SUPPORTING INFORMATION ADDRESSING REVIEWER COST COMMENT XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+
+setEPS(); # postscript below for final publication?
+cairo_ps("figures/rel_costs_01.eps",family="Arial",height=6,width=5.5);
+par(mfrow=c(2,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
+# ------------------------------------------------------------------------#
+evo_cc_02 <- read.table(file="results/fig2/evo_M02_P00_Ff0.txt", header=FALSE);
+evB <- evo_cc_02[evo_cc_02[,3]==0.02 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0,];
+evo <- evB[evB[,2]==beta_val,]; 
+mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
+mPO <- tapply(X=evo[,8],INDEX=evo[,6],FUN=mean);
+mEP <- tapply(X=evo[,9],INDEX=evo[,6],FUN=mean);
+sWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=sd);
[…]

### 2017-07-06 ms_pre_post.Rmd
Respond to two of Reviewer 2's major concerns

@@
 
-Phenotypic values of the three reproductive strategy traits each have costs that are assumed to combine independently to increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
+Phenotypic values of the three reproductive strategy traits each have costs that are assumed to combine independently to increase the probability that a focal female will die before mating.
+**The ability to set costs independently and a priori in this way is critical because it permits the direct comparison of evolution of pre-copulatory versus post-copulatory inbreeding avoidance** (see Discussion for consideration of other costs).
 The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
@@
 In contrast, $P_{p}$ cannot be negative.
-Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
+**Values of $c_{P}$, $c_{M}$, and $c_{F}$ can be interpreted mechanistically as the increased mortality risk caused by mate searching [e.g., @Koga1998], resisting male harrassment [i.e., sexual conflict; @Rowe1994], and energetic loss from development of post-copulatory inbreeding avoidance mechanisms [e.g., @Gasparini2011], respectively.** Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
 
@@
 Equation 1 assumes independent allelic effects, generating multiplicative effects on offspring viability [@Morton1956; @Mills1994].
-We model inbreeding depression as having an absolute rather than relative effect on offspring viability (i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
+**It also assumes that inbreeding does not covary with inbreeding load (i.e., no purging), allowing the effects of kinship on inbreeding depression to be consistent across replicate simulations.
+Additionally, previous modelling has found that inbreeding avoidance in biparental populations has a negligible effect on load [@Duthie2016a].** We model inbreeding depression as having an absolute rather than relative effect on offspring viability (i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
 We assume that inbreeding always decreases offspring viability (i.e., $\beta > 0$, giving inbreeding depression but no outbreeding depression).
@@
 Consequently, long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given sufficient cost asymmetry.
-Since direct costs strongly affected the evolution of the focal phenotype(s), quantifying costs is necessary for predicting evolution of inbreeding strategies.
+Since direct costs strongly affected evolution of the focal phenotype(s), quantifying costs is necessary for predicting evolution of inbreeding strategies.
 
-Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging [@Pomiankowski1987; @Kokko2003].
-@Pomiankowski1987 categorised four types of costs that are relevant to **mating frequency and** mate choice, which are also relevant for polyandry, and include costs of elevated risks of predation or disease transmission, and costs incurred through time or energy expenditure.
-Consequently, we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of pre-copulatory inbreeding strategy as a loss of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy, all manifested as an increased probability of total reproductive failure.
-While these costs reflect empirical observations in some populations and are therefore biologically realistic, other types of costs have also been observed and could be considered in future models tailored to specific systems.
+**To facilitate a general comparison of the effects of direct costs across phenotypes, all costs in our model were manifested as an increased probability of total reproductive failure.
+We thereby interpreted as a cost of polyandy as an elevated risk of predation as might be incurred while searching for mates [e.g., @Koga1998], a cost of pre-copulatory inbreeding strategy as a risk associated with male harrassment [e.g., @Rowe1994], and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy needed for post-copulatory kin discrimination [e.g., @Gasparini2011]**.
+While these costs reflect empirical observations in some populations and are therefore biologically realistic, **more mechanistic** costs could be **assumed or predicted from future models tailored to specific empirical systems.** In empirical systems, quantifying direct costs of phenotypes associated with polyandry and mate choice is challenging [@Pomiankowski1987; @Kokko2003].
+@Pomiankowski1987 categorised four types of costs that are relevant to **mating frequency and** mate choice, which include costs of elevated risks of predation or disease transmission, and costs incurred through time or energy expenditure.
 For example, highly polyandrous females might experience increased risk of disease transmission [@Roberts2015a].
@@
 Polyandrous females might also risk harm caused by sexual conflict over multiple mating [e.g., @Arnqvist2005a; @Parker2006].
-We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should be more tolerant of inbreeding than females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
-Future models could formally consider sexual conflict over both polyandry and inbreeding.
-Overall, such different types of costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
+Inbreeding theory predicts that males should be more tolerant of inbreeding than females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
+Future models could **therefore** formally consider sexual conflict over both polyandry and inbreeding.
+Overall, such different types of **potentially interacting** costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
 Evolution of reproductive strategies therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.

### 2017-07-07 ms_pre_post.Rmd
Address one of Reviewer 2's minor comments

@@
 Evolution of such post-copulatory inbreeding avoidance is likely to be facilitated when females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout [but see @Dougherty2016].
-Such polyandry might itself be under selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative.
+Such polyandry might itself be under **indirect** selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative**, or if it allows females to mate with additional unrelated males that would not be available during initial mate choice due to changes in mate availability or relatedness distribution in a population [e.g., @Reid2015; @Duthie]**.
 Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm provided by females' mates (i.e., under conditions of a 'fair raffle').
+<!--- FIXIT: Reid et al.
+2015 comes up as 'b', should be 'a' --->
+
 Overall, polyandry can therefore simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.

### 2017-07-19 ms_pre_post.Rmd
Change abstract

@@
 We use individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression and different evolutionary constraints and direct costs.
-We find that evolution of post-copulatory inbreeding avoidance increases selection for initially rare polyandry, and that selection for a costly inbreeding avoidance strategy was weak or negligible given a cost free alternative strategy.
+We find that evolution of post-copulatory inbreeding avoidance increases selection for initially rare polyandry, and that selection for a costly inbreeding avoidance strategy was weak or negligible given a lower cost alternative strategy.
 Further, fixed pre-copulatory inbreeding avoidance often completely precluded evolution of polyandry and hence post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance.

### 2017-07-19 ms_pre_post.Rmd
Address Reviewer 1 comments about model restrictions

@@
 We use individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression and different evolutionary constraints and direct costs.
-We find that evolution of post-copulatory inbreeding avoidance increases selection for initially rare polyandry, and that selection for a costly inbreeding avoidance strategy was weak or negligible given a lower cost alternative strategy.
+We find that evolution of post-copulatory inbreeding avoidance increases selection for initially rare polyandry, and that evolution of a costly inbreeding avoidance strategy became negligible over time given a lower cost alternative strategy.
 Further, fixed pre-copulatory inbreeding avoidance often completely precluded evolution of polyandry and hence post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance.
@@
 However, despite such widely-invoked hypotheses regarding the role of inbreeding depression in driving pre-copulatory and post-copulatory strategies and polyandry, there is surprisingly little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
+**To comprehensively understand evolution of mating strategies given inbreeding depression, it is necessary to consider the fundamental effects of selection on pre-copulatory and post-copulatory inbreeding avoidance and polyandry.**
 
 Despite the paucity of theory, numerous empirical studies on diverse species have tested for, and in some cases found evidence of, female inbreeding avoidance in systems where polyandry also occurs [@Tregenza2002; @Varian-Ramos2012; @Kingma2013; @Arct2015; but see @Reid2015a].
-However, relatively few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
-Pre-copulatory inbreeding avoidance has been reported in diverse species, spanning sweet potato weevils [*Cylas formicarius*, @Kuriwada2011], purple-crowned fairy-wrens [*Malurus coronatus*, @Kuriwada2011], and squinting bush brown butterflies [*Bicyclus anynana*, @Fischer2015], while post-copulatory inbreeding avoidance has been reported in, **e.g.,** red junglefowl [*Gallus gallus*, @Pizzari2004] and crickets [*Teleogryllus oceanicus*, @Simmons2006; *Gryllus bimaculatus*, @Bretman2009].
+However, few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
+Pre-copulatory inbreeding avoidance has been reported in sweet potato weevils [*Cylas formicarius*, @Kuriwada2011], purple-crowned fairy-wrens [*Malurus coronatus*, @Kuriwada2011], and squinting bush brown butterflies [*Bicyclus anynana*, @Fischer2015], while post-copulatory inbreeding avoidance has been reported in, **e.g.,** red junglefowl [*Gallus gallus*, @Pizzari2004] and crickets [*Teleogryllus oceanicus*, @Simmons2006; *Gryllus bimaculatus*, @Bretman2009].
 Evidence for both pre-copulatory and post-copulatory inbreeding avoidance is available across different studies of Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015].
@@
 
-The few previous models that considered the evolution of inbreeding avoidance through mate choice (as opposed to dispersal) have implicitly or explicitly considered the fate of a rare allele underlying pre-copulatory inbreeding avoidance in a population initially fixed for random mating [e.g., @Parker1979; @Parker2006; @Duthie; @Duthie2016a].
+The few previous models that considered evolution of inbreeding avoidance through mate choice (as opposed to dispersal) have implicitly or explicitly considered the fate of a rare allele underlying pre-copulatory inbreeding avoidance in a population initially fixed for random mating [e.g., @Parker1979; @Parker2006; @Duthie; @Duthie2016a].
 Such models are useful for isolating the invasion fitness of this single strategy.
@@
 Third, how is selection for initially rare pre-copulatory or post-copulatory inbreeding avoidance affected if the other strategy of inbreeding avoidance is already fixed?
-**For each question, we isolate the effect of the biological mechanism of interest (i.e., post-copulatory inbreeding avoidance, cost asymmetry, and another fixed strategy of inbreeding avoidance) by running simulations in which the mechanism is present and comparing the results to those of simulations in which the it is absent but all other parameter values are identical** By addressing these **three** questions, we illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
+**For each question, we isolate the effect of the biological mechanism of interest (i.e., post-copulatory inbreeding avoidance, cost asymmetry, and another fixed strategy of inbreeding avoidance) by running simulations in which the mechanism is present and comparing the results to those of simulations in which the it is absent but all other parameter values are identical.** **We restrict our model to simulate how evolution of traits are affected by their direct costs and indirect benefits due to inbreeding avoidance.
+Although empirical populations will include additional beneficial traits that might affect evolution of mating strategies, targeting our focus on traits affecting inbreeding and polyandry allows us to better isolate their effects and therefore better develop hypotheses for empirical systems.** By addressing **our three** questions, we illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
 
@@
 These analyses allowed us to infer how allele values changed over generations in response to costs, but also in response to the changing values of other alleles and therefore potential evolutionary feedbacks among reproductive strategies.
-For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling [@Duthie] showed to be sufficient for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
+**In our analyses, we do not use statistical tests to interpret simulation results; such tests are innappropriate because they violate the underlying assumptions of statistical hypothesis testing, and because statistical power (and therefore p-values) would be entirely determined by the number of simulation replicates performed [@White2014].** For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling [@Duthie] showed to be sufficient for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
 For all replicates, we set $\rho=5$ immigrants, which produced a range of kin and non-kin in each generation allowing females to express inbreeding strategies, and $n=8$ offspring, which was sufficient to keep populations consistently at carrying capacities and avoid population extinction.

### 2017-07-19 ms_pre_post.Rmd
Add threshold trait stuff

@@
 
-All individuals have 10 physically unlinked diploid loci, and therefore 20 alleles, underlying each of three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$, i.e., 'polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., 'fertilisation' alleles).
+**Complex traits such as reproductive behaviour are likely to be highly polygenic [@Evans2008].** **Hence, in our model,** all individuals have 10 physically unlinked diploid loci, and therefore 20 alleles, underlying each of three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$, i.e., 'polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., 'fertilisation' alleles).
 All alleles can take the value of any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014] and combine additively to determine genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and resulting phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively.
@@
 Each individual's phenotypic values for pre-copulatory and post-copulatory inbreeding strategy equal their respective genotypic values ($M_{p} = M_{g}$ and $F_{p} = F_{g}$), where negative and positive values cause inbreeding avoidance and preference, respectively (see details of mating and fertilisation strategies below).
-In contrast, phenotypic values for tendency for polyandry equal genotypic values ($P_{p} = P_{g}$) only if $P_{g} \geq 0$, while $P_{p} = 0$ if $P_{g} < 0$ because females cannot choose a negative number of mates.
+**In contrast to inbreeding strategy, the polygenic nature of polyandry does not translate to continuous phenotypes affecting mate choice [e.g., @Shuker2007; @Evans2013].** **Polyandry is more realistically defined as a ''threshold trait'', influenced by continuous genetic variation but expressed at some discrete phenotypic value(s) [@Lynch1998; @Roff1996; @Roff1998; @Duthie].
+One important consequence of this threshold genetic architecture is that threshold traits can often reappear despite sustained negative selection as a consequence of previously masked deleterious alleles being reapparing due to recombination [@Roff1996; @Roff1998].
+We incorporate this key feature into our model by allowing** phenotypic values for tendency for polyandry *to* equal genotypic values ($P_{p} = P_{g}$) only if $P_{g} \geq 0$, while $P_{p} = 0$ if $P_{g} < 0$ because females cannot choose a negative number of mates.
 Polyandry is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998; @Duthie] that is influenced by continuous genetic variation but only expressed when $P_{g} > 0$.

### 2017-07-19 ms_pre_post.Rmd
Initial attempt through methods

@@
 Each individual's phenotypic values for pre-copulatory and post-copulatory inbreeding strategy equal their respective genotypic values ($M_{p} = M_{g}$ and $F_{p} = F_{g}$), where negative and positive values cause inbreeding avoidance and preference, respectively (see details of mating and fertilisation strategies below).
-**In contrast to inbreeding strategy, the polygenic nature of polyandry does not translate to continuous phenotypes affecting mate choice [e.g., @Shuker2007; @Evans2013].** **Polyandry is more realistically defined as a ''threshold trait'', influenced by continuous genetic variation but expressed at some discrete phenotypic value(s) [@Lynch1998; @Roff1996; @Roff1998; @Duthie].
-One important consequence of this threshold genetic architecture is that threshold traits can often reappear despite sustained negative selection as a consequence of previously masked deleterious alleles being reapparing due to recombination [@Roff1996; @Roff1998].
-We incorporate this key feature into our model by allowing** phenotypic values for tendency for polyandry *to* equal genotypic values ($P_{p} = P_{g}$) only if $P_{g} \geq 0$, while $P_{p} = 0$ if $P_{g} < 0$ because females cannot choose a negative number of mates.
-Polyandry is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998; @Duthie] that is influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
+**In contrast to inbreeding strategies, the polygenic nature of polyandry cannot translate to continuous phenotypes affecting mate choice [e.g., @Shuker2007; @Evans2013].** **Polyandry is more realistically defined as a "threshold trait", influenced by continuous genetic variation but expressed at some discrete phenotypic value(s) [@Lynch1998; @Roff1996; @Roff1998; @Duthie].
+We incorporate this genetic architecture into our model by allowing** phenotypic values for tendency for polyandry **to** equal genotypic values ($P_{p} = P_{g}$) only if $P_{g} \geq 0$, while $P_{p} = 0$ if $P_{g} < 0$ because females cannot choose a negative number of mates.
+Polyandry is therefore influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
 A negative $P_{g}$ value therefore generates a female that is phenotypically monandrous, while a positive $P_{g}$ value generates a female that can express some degree of polyandry (see details below).
+**One important consequence of this genetic architecture is that threshold traits often reappear in a population despite sustained negative selection, as caused by recombination of previously masked deleterious alleles [@Roff1996; @Roff1998].**
 
@@
 
-Phenotypic values of the three reproductive strategy traits each have costs that are assumed to combine independently to increase the probability that a focal female will die before mating.
-**The ability to set costs independently and a priori in this way is critical because it permits the direct comparison of evolution of pre-copulatory versus post-copulatory inbreeding avoidance** (see Discussion for consideration of other costs).
+Phenotypic values of the three reproductive strategy traits each have **pre-determined** costs that are assumed to combine independently to increase the probability that a focal female will die before mating.
+**The ability to set costs independently and a priori in this way is critical because it permits the direct comparison of evolution of pre-copulatory versus post-copulatory inbreeding avoidance** (see Discussion for consideration **of more mechanistic costs**).
 The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
@@
 To avoid unrestricted population growth, we set separate carrying capacities for the total numbers of females ($K_{f}$) and males ($K_{m}$) in the focal population following immigration [@Guillaume2009; @Duthie].
-Hence, if at the end of a generation the number of female or male **offspring** exceeds $K_{f}$ or $K_{m}$  respectively, then individuals are randomly removed until each sex is at its carrying capacity.
+Hence, if at the end of a generation the number of females or males exceeds $K_{f}$ or $K_{m}$  respectively, then individuals are randomly removed until each sex is at its carrying capacity.
 Such removal can be interpreted as some combination of dispersal and mortality.
@@
 Previous modelling using similar genetic architecture suggests that a cost of $0.02$ imposes strong but not overwhelming direct negative selection on polyandry [@Duthie].
-This value is therefore appropriate to illustrate the different evolutionary consequences that could result from asymmetrical costs.
+This value is therefore appropriate to illustrate the different evolutionary consequences that could result from asymmetrical costs **(but see Supporting Information for other asymmetric cost combinations)**.
 

### 2017-07-20 ms_pre_post.Rmd
Some finishing initial edits

@@
 
-When post-copulatory inbreeding avoidance alleles ($F_{a}$) had no effect (i.e., $F_{g}$ values were fixed to zero), meaning that $F_{p}$ could not evolve, $P_{a}$ alleles underlying polyandry always decreased to negative values over generations (red lines, Figure 1A,C,E,G).
+When post-copulatory inbreeding avoidance alleles ($F_{a}$) had no effect (i.e., $F_{g}$ values were fixed to zero), meaning that $F_{p}$ could not evolve, $P_{a}$ alleles underlying polyandry decreased to negative values over generations (red lines, Figure 1A,C,E,G).
 This shows that despite strong inbreeding depression in offspring viability, there is selection against unconditional polyandry even given zero direct cost ($c_{P}=0$; Figure 1A).
@@
 Similarly, when post-copulatory but not pre-copulatory inbreeding avoidance was costly ($c_{F}=0.02$ and $c_{M}=0$), post-copulatory inbreeding avoidance initially evolved (i.e., $F_{a} < 0$) before evolving back to random fertilisation (i.e., $F_{a} \approx 0$) after ca $20000$ generations (Figure 3D).
+**This evolution of a high cost strategy back toward random mating or fertilisation in the presence of a relatively low cost alternative inbreeding strategy is a general consequence of differential selection on each strategy induced by cost asymmetry.
+Hence, this pattern can be observed for both non-zero low relative costs (e.g., values of 0.01 and 0.03; Figure S9) and smaller cost asymmetries (e.g., values of 0.01 and 0.02; Figure S10).**
 
@@
 However when post-copulatory inbreeding avoidance was costly, allowing evolution of cost free pre-copulatory inbreeding avoidance caused $P_{a}$ alleles to decrease to very negative values, reducing expression of polyandry (Figure 3C versus 3D; polyandry was cost free in all these simulations).
-Results for all possible cost combinations of $0$ and $0.02$ are provided in Supporting Information (Figure S9).
+Results for all possible cost combinations of $0$ and $0.02$ are provided in Supporting Information (Figure S**11**).
 
@@
 $-17.62$; compare the blue lines in Figures 4A versus Figure 1B).
-This shows that fixation of post-copulatory inbreeding avoidance weakens selection for pre-copulatory inbreeding avoidance.
+**Hence, we hypothesise that existence of fixed post-copulatory inbreeding avoidance can weaken selection and subsequent evolution of pre-copulatory inbreeding avoidance.**
 
 Conversely, when pre-copulatory inbreeding allele ($M_{a}$) values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently become negative over generations (Figure 4C,D).
-Fixation of pre-copulatory inbreeding avoidance therefore prevented evolution of post-copulatory inbreeding avoidance.
-In this case, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless of whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
+**Hence, we hypothesise that existence of fixed pre-copulatory inbreeding avoidance can prevent evolution of post-copulatory inbreeding avoidance.** **In our model**, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless of whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
 Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values (resulting in variation among replicates illustrated by the wide standard errors in Figure 4C).
@@
 This lack of selection for post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
-When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information Figure S10).
+When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information Figure S**12**).
 
@@
 One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population (Figure 3).
-Consequently, long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given sufficient cost asymmetry.
-Since direct costs strongly affected evolution of the focal phenotype(s), quantifying costs is necessary for predicting evolution of inbreeding strategies.
+**Hence, our model demonstrates a novel mechanism by which degenerate inbreeding avoidance strategies can interact with one another, and this mechanism might usefult to consider when developing hypotheses concerning reproductive strategy within and across systems.** **In particular**, **indefinite** persistence of both pre-copulatory and post-copulatory inbreeding avoidance **should not be** expected in populations given **a** sufficient**ly large and sustained cost asymmetry.** **However, the length of time required for the more costly inbreeding strategy to go extinct might be quite long (Figure 3), and spatial or temporal variation in costs might facilitate the coexistence of multiple inbreeding avoidance strategies.
+Nevertheless,** since direct costs strongly affected evolution of the focal phenotype(s), quantifying costs is necessary for predicting evolution of inbreeding strategies.
 
@@
 Inbreeding theory predicts that males should be more tolerant of inbreeding than females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
-Future models could **therefore** formally consider sexual conflict over both polyandry and inbreeding.
+Future models could **therefore more mechanistically** consider sexual conflict over both polyandry and inbreeding.
 Overall, such different types of **potentially interacting** costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
@@
 In contrast, pre-copulatory inbreeding avoidance mechanisms are most critical for females that mate only once and therefore have no post-copulatory opportunity to avoiding inbreeding.
-This theory is borne out in our simulation results, as selection for, and consequent evolution of, post-copulatory inbreeding avoidance was negligible in populations where polyandry did not evolve, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D).
-Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information Figure S9).
+This theory is borne out in our simulation results, as selection for, and consequent evolution of, post-copulatory inbreeding avoidance was negligible in populations where polyandry did not evolve, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C).
+Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information Figure S**11**).
 In addition to initial polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back effect that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).

### 2017-07-21 ms_pre_post.Rmd
Remove the bold for changed text

--- 2017-07-20 ms_pre_post.Rmd
@@
 Evolution of such post-copulatory inbreeding avoidance is likely to be facilitated when females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout [but see @Dougherty2016].
-Such polyandry might itself be under **indirect** selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative**, or if it allows females to mate with additional unrelated males that would not be available during initial mate choice due to changes in mate availability or relatedness distribution in a population [e.g., @Reid2015; @Duthie]**.
+Such polyandry might itself be under indirect selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative, or if it allows females to mate with additional unrelated males that would not be available during initial mate choice due to changes in mate availability or relatedness distribution in a population [e.g., @Reid2015; @Duthie].
 Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm provided by females' mates (i.e., under conditions of a 'fair raffle').
-<!--- FIXIT: Reid et al.
-2015 comes up as 'b', should be 'a' --->
 
@@
 However, despite such widely-invoked hypotheses regarding the role of inbreeding depression in driving pre-copulatory and post-copulatory strategies and polyandry, there is surprisingly little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
-**To comprehensively understand evolution of mating strategies given inbreeding depression, it is necessary to consider the fundamental effects of selection on pre-copulatory and post-copulatory inbreeding avoidance and polyandry.**
+To comprehensively understand evolution of mating strategies given inbreeding depression, it is necessary to consider the fundamental effects of selection on pre-copulatory and post-copulatory inbreeding avoidance and polyandry.
 
@@
 However, few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
-Pre-copulatory inbreeding avoidance has been reported in sweet potato weevils [*Cylas formicarius*, @Kuriwada2011], purple-crowned fairy-wrens [*Malurus coronatus*, @Kuriwada2011], and squinting bush brown butterflies [*Bicyclus anynana*, @Fischer2015], while post-copulatory inbreeding avoidance has been reported in, **e.g.,** red junglefowl [*Gallus gallus*, @Pizzari2004] and crickets [*Teleogryllus oceanicus*, @Simmons2006; *Gryllus bimaculatus*, @Bretman2009].
+Pre-copulatory inbreeding avoidance has been reported in sweet potato weevils [*Cylas formicarius*, @Kuriwada2011], purple-crowned fairy-wrens [*Malurus coronatus*, @Kuriwada2011], and squinting bush brown butterflies [*Bicyclus anynana*, @Fischer2015], while post-copulatory inbreeding avoidance has been reported in, e.g., red junglefowl [*Gallus gallus*, @Pizzari2004] and crickets [*Teleogryllus oceanicus*, @Simmons2006; *Gryllus bimaculatus*, @Bretman2009].
 Evidence for both pre-copulatory and post-copulatory inbreeding avoidance is available across different studies of Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015].
@@
 @Duthie used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve due to selection stemming from pre-copulatory inbreeding avoidance in the absence of any post-copulatory inbreeding avoidance.
-**Even when selection for pre-copulatory inbreeding avoidance was strong and females consequently preferred unrelated mates, selection for polyandry specifically as a mechanism to facilitate this inbreeding avoidance** occurred only under highly restricted conditions, requiring that direct negative selection (i.e., 'costs') on polyandry was weak, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
-Without these conditions, **females that engaged in** polyandry tended **to be constrained** to increase rather than decrease **their** overall degree of inbreeding, **ultimately** reduc**ing** offspring fitness.
-This **constraint** occurred because, once pre-copulatory inbreeding avoidance evolved, polyandrous females had already chosen available unrelated males as their initial mates.
+Even when selection for pre-copulatory inbreeding avoidance was strong and females consequently preferred unrelated mates, selection for polyandry specifically as a mechanism to facilitate this inbreeding avoidance occurred only under highly restricted conditions, requiring that direct negative selection (i.e., 'costs') on polyandry was weak, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
+Without these conditions, females that engaged in polyandry tended to be constrained to increase rather than decrease their overall degree of inbreeding, ultimately reducing offspring fitness.
+This constraint occurred because, once pre-copulatory inbreeding avoidance evolved, polyandrous females had already chosen available unrelated males as their initial mates.
 Their additional mates, chosen from the remaining male population, were therefore increasingly likely to include relatives.
@@
 
-Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will **be affected not only by** the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also **by** the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
-**There are multiple mechanisms by which direct costs might by incurred for polyandry, pre-copulatory choice, and post-copulatory choice; here we focus on three examples observed in empirical populations.** Polyandrous females **might** pay costs of mate searching or mating because these activities increase predation risk [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
+Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will be affected not only by the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also by the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
+There are multiple mechanisms by which direct costs might by incurred for polyandry, pre-copulatory choice, and post-copulatory choice; here we focus on three examples observed in empirical populations.
+Polyandrous females might pay costs of mate searching or mating because these activities increase predation risk [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
 Females that express pre-copulatory choice and consequent reluctance to mate with relatives might pay costs of increased risk of complete mating failure or harm caused by sexual conflict [@Rowe1994; @Kokko2013].
-**Finally,** females that express post-copulatory choice might pay initial energetic costs associated with developing the physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
+Finally, females that express post-copulatory choice might pay initial energetic costs associated with developing the physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
 If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly strategy might become extinct, especially if their effects are made redundant by evolution of the less costly strategy.
@@
 Third, how is selection for initially rare pre-copulatory or post-copulatory inbreeding avoidance affected if the other strategy of inbreeding avoidance is already fixed?
-**For each question, we isolate the effect of the biological mechanism of interest (i.e., post-copulatory inbreeding avoidance, cost asymmetry, and another fixed strategy of inbreeding avoidance) by running simulations in which the mechanism is present and comparing the results to those of simulations in which the it is absent but all other parameter values are identical.** **We restrict our model to simulate how evolution of traits are affected by their direct costs and indirect benefits due to inbreeding avoidance.
-Although empirical populations will include additional beneficial traits that might affect evolution of mating strategies, targeting our focus on traits affecting inbreeding and polyandry allows us to better isolate their effects and therefore better develop hypotheses for empirical systems.** By addressing **our three** questions, we illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
+For each question, we isolate the effect of the biological mechanism of interest (i.e., post-copulatory inbreeding avoidance, cost asymmetry, and another fixed strategy of inbreeding avoidance) by running simulations in which the mechanism is present and comparing the results to those of simulations in which the it is absent but all other parameter values are identical.
+We restrict our model to simulate how evolution of traits are affected by their direct costs and indirect benefits due to inbreeding avoidance.
+Although empirical populations will include additional beneficial traits that might affect evolution of mating strategies, targeting our focus on traits affecting inbreeding and polyandry allows us to better isolate their effects and therefore better develop hypotheses for empirical systems.
+By addressing our three questions, we illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
 
@@
 
-**Complex traits such as reproductive behaviour are likely to be highly polygenic [@Evans2008].** **Hence, in our model,** all individuals have 10 physically unlinked diploid loci, and therefore 20 alleles, underlying each of three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$, i.e., 'polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., 'fertilisation' alleles).
+Complex traits such as reproductive behaviour are likely to be highly polygenic [@Evans2008].
+Hence, in our model, all individuals have 10 physically unlinked diploid loci, and therefore 20 alleles, underlying each of three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$, i.e., 'polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., 'fertilisation' alleles).
 All alleles can take the value of any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014] and combine additively to determine genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and resulting phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively.
@@
 Each individual's phenotypic values for pre-copulatory and post-copulatory inbreeding strategy equal their respective genotypic values ($M_{p} = M_{g}$ and $F_{p} = F_{g}$), where negative and positive values cause inbreeding avoidance and preference, respectively (see details of mating and fertilisation strategies below).
-**In contrast to inbreeding strategies, the polygenic nature of polyandry cannot translate to continuous phenotypes affecting mate choice [e.g., @Shuker2007; @Evans2013].** **Polyandry is more realistically defined as a "threshold trait", influenced by continuous genetic variation but expressed at some discrete phenotypic value(s) [@Lynch1998; @Roff1996; @Roff1998; @Duthie].
-We incorporate this genetic architecture into our model by allowing** phenotypic values for tendency for polyandry **to** equal genotypic values ($P_{p} = P_{g}$) only if $P_{g} \geq 0$, while $P_{p} = 0$ if $P_{g} < 0$ because females cannot choose a negative number of mates.
+In contrast to inbreeding strategies, the polygenic nature of polyandry cannot translate to continuous phenotypes affecting mate choice [e.g., @Shuker2007; @Evans2013].
+Polyandry is more realistically defined as a "threshold trait", influenced by continuous genetic variation but expressed at some discrete phenotypic value(s) [@Lynch1998; @Roff1996; @Roff1998; @Duthie].
+We incorporate this genetic architecture into our model by allowing phenotypic values for tendency for polyandry to equal genotypic values ($P_{p} = P_{g}$) only if $P_{g} \geq 0$, while $P_{p} = 0$ if $P_{g} < 0$ because females cannot choose a negative number of mates.
 Polyandry is therefore influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
 A negative $P_{g}$ value therefore generates a female that is phenotypically monandrous, while a positive $P_{g}$ value generates a female that can express some degree of polyandry (see details below).
-**One important consequence of this genetic architecture is that threshold traits often reappear in a population despite sustained negative selection, as caused by recombination of previously masked deleterious alleles [@Roff1996; @Roff1998].**
+One important consequence of this genetic architecture is that threshold traits often reappear in a population despite sustained negative selection, as caused by recombination of previously masked deleterious alleles [@Roff1996; @Roff1998].
 
@@
 Alleles can then mutate and offspring express inbreeding depression in viability.
-Immigrants arrive in the population and density regulation limits population growth **(see below)**.
+Immigrants arrive in the population and density regulation limits population growth (see below).
 We record the population pedigree and directly calculate the coefficient of kinship ($k$) between all potential mates in each generation (defined as the probability that two homologous alleles will be identical-by-descent), allowing individual pre-copulatory and post-copulatory inbreeding strategies to be enacted.
@@
 
-Phenotypic values of the three reproductive strategy traits each have **pre-determined** costs that are assumed to combine independently to increase the probability that a focal female will die before mating.
-**The ability to set costs independently and a priori in this way is critical because it permits the direct comparison of evolution of pre-copulatory versus post-copulatory inbreeding avoidance** (see Discussion for consideration **of more mechanistic costs**).
+Phenotypic values of the three reproductive strategy traits each have pre-determined costs that are assumed to combine independently to increase the probability that a focal female will die before mating.
+The ability to set costs independently and a priori in this way is critical because it permits the direct comparison of evolution of pre-copulatory versus post-copulatory inbreeding avoidance (see Discussion for consideration of more mechanistic costs).
 The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
@@
 In contrast, $P_{p}$ cannot be negative.
-**Values of $c_{P}$, $c_{M}$, and $c_{F}$ can be interpreted mechanistically as the increased mortality risk caused by mate searching [e.g., @Koga1998], resisting male harrassment [i.e., sexual conflict; @Rowe1994], and energetic loss from development of post-copulatory inbreeding avoidance mechanisms [e.g., @Gasparini2011], respectively.** Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
+Values of $c_{P}$, $c_{M}$, and $c_{F}$ can be interpreted mechanistically as the increased mortality risk caused by mate searching [e.g., @Koga1998], resisting male harrassment [i.e., sexual conflict; @Rowe1994], and energetic loss from development of post-copulatory inbreeding avoidance mechanisms [e.g., @Gasparini2011], respectively.
+Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
 
@@
 Offspring have equal probability of being female or male.
-**After offspring production, all female and male adults die so that generations are non-overlapping.**
+After offspring production, all female and male adults die so that generations are non-overlapping.
 
@@
 Equation 1 assumes independent allelic effects, generating multiplicative effects on offspring viability [@Morton1956; @Mills1994].
-**It also assumes that inbreeding does not covary with inbreeding load (i.e., no purging), allowing the effects of kinship on inbreeding depression to be consistent across replicate simulations.
-Additionally, previous modelling has found that inbreeding avoidance in biparental populations has a negligible effect on load [@Duthie2016a].** We model inbreeding depression as having an absolute rather than relative effect on offspring viability (i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
+It also assumes that inbreeding does not covary with inbreeding load (i.e., no purging), allowing the effects of kinship on inbreeding depression to be consistent across replicate simulations.
+Additionally, previous modelling has found that inbreeding avoidance in biparental populations has a negligible effect on load [@Duthie2016a].
+We model inbreeding depression as having an absolute rather than relative effect on offspring viability (i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
 We assume that inbreeding always decreases offspring viability (i.e., $\beta > 0$, giving inbreeding depression but no outbreeding depression).
@@
 We therefore define $\Psi_{\textrm{off}}$ as the probability that an offspring is viable, and sample its realised viability (versus mortality) using a Bernoulli trial.
-**Offspring that are viable after the Bernoulli trial become adults.** Given our current objectives, we simulate evolution under conditions where inbreeding avoidance is adaptive due to strong inbreeding depression, and not evolution where inbreeding preference is adaptive due to weak or zero inbreeding depression [@Parker1979; @Kokko2006; @Duthie2016a], or given outbreeding depression [@Bateson1983; @Greeff2009].
+Offspring that are viable after the Bernoulli trial become adults.
+Given our current objectives, we simulate evolution under conditions where inbreeding avoidance is adaptive due to strong inbreeding depression, and not evolution where inbreeding preference is adaptive due to weak or zero inbreeding depression [@Parker1979; @Kokko2006; @Duthie2016a], or given outbreeding depression [@Bateson1983; @Greeff2009].
 However, as described above, positive $M_{p}$ and $F_{p}$ values resulting in inbreeding preference are not precluded from evolving, and could potentially arise due to mutation or drift.
@@
 Previous modelling using similar genetic architecture suggests that a cost of $0.02$ imposes strong but not overwhelming direct negative selection on polyandry [@Duthie].
-This value is therefore appropriate to illustrate the different evolutionary consequences that could result from asymmetrical costs **(but see Supporting Information for other asymmetric cost combinations)**.
+This value is therefore appropriate to illustrate the different evolutionary consequences that could result from asymmetrical costs (but see Supporting Information for other asymmetric cost combinations).
 
@@
 These analyses allowed us to infer how allele values changed over generations in response to costs, but also in response to the changing values of other alleles and therefore potential evolutionary feedbacks among reproductive strategies.
-**In our analyses, we do not use statistical tests to interpret simulation results; such tests are innappropriate because they violate the underlying assumptions of statistical hypothesis testing, and because statistical power (and therefore p-values) would be entirely determined by the number of simulation replicates performed [@White2014].** For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling [@Duthie] showed to be sufficient for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
+In our analyses, we do not use statistical tests to interpret simulation results; such tests are innappropriate because they violate the underlying assumptions of statistical hypothesis testing, and because statistical power (and therefore p-values) would be entirely determined by the number of simulation replicates performed [@White2014].
+For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling [@Duthie] showed to be sufficient for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
 For all replicates, we set $\rho=5$ immigrants, which produced a range of kin and non-kin in each generation allowing females to express inbreeding strategies, and $n=8$ offspring, which was sufficient to keep populations consistently at carrying capacities and avoid population extinction.
@@
 Similarly, when post-copulatory but not pre-copulatory inbreeding avoidance was costly ($c_{F}=0.02$ and $c_{M}=0$), post-copulatory inbreeding avoidance initially evolved (i.e., $F_{a} < 0$) before evolving back to random fertilisation (i.e., $F_{a} \approx 0$) after ca $20000$ generations (Figure 3D).
-**This evolution of a high cost strategy back toward random mating or fertilisation in the presence of a relatively low cost alternative inbreeding strategy is a general consequence of differential selection on each strategy induced by cost asymmetry.
-Hence, this pattern can be observed for both non-zero low relative costs (e.g., values of 0.01 and 0.03; Figure S9) and smaller cost asymmetries (e.g., values of 0.01 and 0.02; Figure S10).**
+This evolution of a high cost strategy back toward random mating or fertilisation in the presence of a relatively low cost alternative inbreeding strategy is a general consequence of differential selection on each strategy induced by cost asymmetry.
+Hence, this pattern can be observed for both non-zero low relative costs (e.g., values of 0.01 and 0.03; Figure S9) and smaller cost asymmetries (e.g., values of 0.01 and 0.02; Figure S10).
 
@@
 However when post-copulatory inbreeding avoidance was costly, allowing evolution of cost free pre-copulatory inbreeding avoidance caused $P_{a}$ alleles to decrease to very negative values, reducing expression of polyandry (Figure 3C versus 3D; polyandry was cost free in all these simulations).
-Results for all possible cost combinations of $0$ and $0.02$ are provided in Supporting Information (Figure S**11**).
+Results for all possible cost combinations of $0$ and $0.02$ are provided in Supporting Information (Figure S11).
 
-How does fixation of pre-copulatory or post-copulatory inbreeding avoidance affect evolution **of an alternative strategy of inbreeding avoidance**?
+How does fixation of pre-copulatory or post-copulatory inbreeding avoidance affect evolution of an alternative strategy of inbreeding avoidance?
 ----------------------------------------------
@@
 $-17.62$; compare the blue lines in Figures 4A versus Figure 1B).
-**Hence, we hypothesise that existence of fixed post-copulatory inbreeding avoidance can weaken selection and subsequent evolution of pre-copulatory inbreeding avoidance.**
+Hence, we hypothesise that existence of fixed post-copulatory inbreeding avoidance can weaken selection and subsequent evolution of pre-copulatory inbreeding avoidance.
 
 Conversely, when pre-copulatory inbreeding allele ($M_{a}$) values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently become negative over generations (Figure 4C,D).
-**Hence, we hypothesise that existence of fixed pre-copulatory inbreeding avoidance can prevent evolution of post-copulatory inbreeding avoidance.** **In our model**, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless of whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
+Hence, we hypothesise that existence of fixed pre-copulatory inbreeding avoidance can prevent evolution of post-copulatory inbreeding avoidance.
+In our model, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless of whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
 Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values (resulting in variation among replicates illustrated by the wide standard errors in Figure 4C).
@@
 This lack of selection for post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
-When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information Figure S**12**).
+When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information Figure S12).
 
@@
 One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population (Figure 3).
-**Hence, our model demonstrates a novel mechanism by which degenerate inbreeding avoidance strategies can interact with one another, and this mechanism might usefult to consider when developing hypotheses concerning reproductive strategy within and across systems.** **In particular**, **indefinite** persistence of both pre-copulatory and post-copulatory inbreeding avoidance **should not be** expected in populations given **a** sufficient**ly large and sustained cost asymmetry.** **However, the length of time required for the more costly inbreeding strategy to go extinct might be quite long (Figure 3), and spatial or temporal variation in costs might facilitate the coexistence of multiple inbreeding avoidance strategies.
-Nevertheless,** since direct costs strongly affected evolution of the focal phenotype(s), quantifying costs is necessary for predicting evolution of inbreeding strategies.
+Hence, our model demonstrates a novel mechanism by which degenerate inbreeding avoidance strategies can interact with one another, and this mechanism might usefult to consider when developing hypotheses concerning reproductive strategy within and across systems.
+In particular, indefinite persistence of both pre-copulatory and post-copulatory inbreeding avoidance should not be expected in populations given a sufficiently large and sustained cost asymmetry.
+However, the length of time required for the more costly inbreeding strategy to go extinct might be quite long (Figure 3), and spatial or temporal variation in costs might facilitate the coexistence of multiple inbreeding avoidance strategies.
+Nevertheless, since direct costs strongly affected evolution of the focal phenotype(s), quantifying costs is necessary for predicting evolution of inbreeding strategies.
 
-**To facilitate a general comparison of the effects of direct costs across phenotypes, all costs in our model were manifested as an increased probability of total reproductive failure.
-We thereby interpreted as a cost of polyandy as an elevated risk of predation as might be incurred while searching for mates [e.g., @Koga1998], a cost of pre-copulatory inbreeding strategy as a risk associated with male harrassment [e.g., @Rowe1994], and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy needed for post-copulatory kin discrimination [e.g., @Gasparini2011]**.
-While these costs reflect empirical observations in some populations and are therefore biologically realistic, **more mechanistic** costs could be **assumed or predicted from future models tailored to specific empirical systems.** In empirical systems, quantifying direct costs of phenotypes associated with polyandry and mate choice is challenging [@Pomiankowski1987; @Kokko2003].
-@Pomiankowski1987 categorised four types of costs that are relevant to **mating frequency and** mate choice, which include costs of elevated risks of predation or disease transmission, and costs incurred through time or energy expenditure.
+To facilitate a general comparison of the effects of direct costs across phenotypes, all costs in our model were manifested as an increased probability of total reproductive failure.
+We thereby interpreted as a cost of polyandy as an elevated risk of predation as might be incurred while searching for mates [e.g., @Koga1998], a cost of pre-copulatory inbreeding strategy as a risk associated with male harrassment [e.g., @Rowe1994], and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy needed for post-copulatory kin discrimination [e.g., @Gasparini2011].
+While these costs reflect empirical observations in some populations and are therefore biologically realistic, more mechanistic costs could be assumed or predicted from future models tailored to specific empirical systems.
+In empirical systems, quantifying direct costs of phenotypes associated with polyandry and mate choice is challenging [@Pomiankowski1987; @Kokko2003].
+@Pomiankowski1987 categorised four types of costs that are relevant to mating frequency and mate choice, which include costs of elevated risks of predation or disease transmission, and costs incurred through time or energy expenditure.
 For example, highly polyandrous females might experience increased risk of disease transmission [@Roberts2015a].
@@
 Inbreeding theory predicts that males should be more tolerant of inbreeding than females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
-Future models could **therefore more mechanistically** consider sexual conflict over both polyandry and inbreeding.
-Overall, such different types of **potentially interacting** costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
+Future models could therefore more mechanistically consider sexual conflict over both polyandry and inbreeding.
+Overall, such different types of potentially interacting costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
 Evolution of reproductive strategies therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.
@@
 This theory is borne out in our simulation results, as selection for, and consequent evolution of, post-copulatory inbreeding avoidance was negligible in populations where polyandry did not evolve, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C).
-Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information Figure S**11**).
+Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information Figure S11).
 In addition to initial polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back effect that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).

### 2017-07-21 ms_pre_post.Rmd
Fix typo

@@
 author: ''
-date: "4 May 2017"
+date: "21 July 2017"
 output:
@@
 When a mutation occurs, a mutation effect is sampled from a normal distribution with a mean of zero and a standard deviation of $\mu_{SD}$ and added to the original allele value [@Kimura1965; @Lande1976; @Bocedi2014; @Duthie].
-The value of $\mu_{SD}$ is set to $\sqrt{1/20}$ because 20 independent alleles underlie each trait's genotypic value.
+The value of $\mu_{SD}$ is set to $\sqrt{1/20}$.
 
@@
 One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population (Figure 3).
-Hence, our model demonstrates a novel mechanism by which degenerate inbreeding avoidance strategies can interact with one another, and this mechanism might usefult to consider when developing hypotheses concerning reproductive strategy within and across systems.
+Hence, our model demonstrates a novel mechanism by which degenerate inbreeding avoidance strategies can interact with one another, and this mechanism might useful to consider when developing hypotheses concerning reproductive strategy within and across systems.
 In particular, indefinite persistence of both pre-copulatory and post-copulatory inbreeding avoidance should not be expected in populations given a sufficiently large and sustained cost asymmetry.

### 2017-07-21 ms_pre_post.Rmd
Minor edits

@@
 One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population (Figure 3).
-Hence, our model demonstrates a novel mechanism by which degenerate inbreeding avoidance strategies can interact with one another, and this mechanism might useful to consider when developing hypotheses concerning reproductive strategy within and across systems.
+Hence, our model demonstrates a novel mechanism by which degenerate inbreeding avoidance strategies can interact with one another, and this mechanism might usefulg to consider when developing hypotheses concerning reproductive strategy within and across systems.
 In particular, indefinite persistence of both pre-copulatory and post-copulatory inbreeding avoidance should not be expected in populations given a sufficiently large and sustained cost asymmetry.

### 2017-07-26 ms_pre_post.Rmd
First few paragraphs of editing

@@
 
-From the perspective of a breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
-Evolution of such post-copulatory inbreeding avoidance is likely to be facilitated when females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout [but see @Dougherty2016].
-Such polyandry might itself be under indirect selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative, or if it allows females to mate with additional unrelated males that would not be available during initial mate choice due to changes in mate availability or relatedness distribution in a population [e.g., @Reid2015; @Duthie].
-Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm provided by females' mates (i.e., under conditions of a 'fair raffle').
+From a female's perspective, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males following mating (i.e., post-copulatory inbreeding avoidance).
+Evolution of post-copulatory inbreeding avoidance is likely to be facilitated when females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout [but see @Dougherty2016].
+Further, such polyandry might itself evolve because it allows females to mate with additional unrelated males following an initial mating with a relative, potentially including males that were unavailable for initial mate choice [e.g., @Reid2015; @Duthie].
+Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm (i.e., under conditions of a 'fair raffle').
 
-Overall, polyandry can therefore simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
-Polyandry has consequently been widely hypothesised to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002].
-Resulting indirect selection on polyandry that stems from the increase in offspring fitness could explain evolution of polyandry in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct costs on polyandrous females.
-However, despite such widely-invoked hypotheses regarding the role of inbreeding depression in driving pre-copulatory and post-copulatory strategies and polyandry, there is surprisingly little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
-To comprehensively understand evolution of mating strategies given inbreeding depression, it is necessary to consider the fundamental effects of selection on pre-copulatory and post-copulatory inbreeding avoidance and polyandry.
+Overall, polyandry can therefore simultaneously allow females to mate with less closely related males and create opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
+Indirect selection on polyandry resulting from reduced inbreeding depression in offspring fitness could help explain evolution of polyandry in cases where multiple mating decreases female reproductive success, imposing a direct cost on polyandrous females [@Zeh1997; @Jennions2000; @Tregenza2002].
+However, despite such widely-invoked hypotheses, there is surprisingly little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how evolution of such strategies might feed back to affect underlying evolution of polyandry.
+Comprehensive understanding of evolution of reproductive strategies given inbreeding depression requires consideration of the fundamental joint effects of selection on pre-copulatory and post-copulatory inbreeding avoidance and polyandry.
 

### 2017-07-26 ms_pre_post.Rmd
Introduction edits made

@@
 However, few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
-Pre-copulatory inbreeding avoidance has been reported in sweet potato weevils [*Cylas formicarius*, @Kuriwada2011], purple-crowned fairy-wrens [*Malurus coronatus*, @Kuriwada2011], and squinting bush brown butterflies [*Bicyclus anynana*, @Fischer2015], while post-copulatory inbreeding avoidance has been reported in, e.g., red junglefowl [*Gallus gallus*, @Pizzari2004] and crickets [*Teleogryllus oceanicus*, @Simmons2006; *Gryllus bimaculatus*, @Bretman2009].
+Among these studies, pre-copulatory inbreeding avoidance has been reported in sweet potato weevils [*Cylas formicarius*, @Kuriwada2011], purple-crowned fairy-wrens [*Malurus coronatus*, @Kuriwada2011], and squinting bush brown butterflies [*Bicyclus anynana*, @Fischer2015], while post-copulatory inbreeding avoidance has been reported in, for example, red junglefowl [*Gallus gallus*, @Pizzari2004] and crickets [*Teleogryllus oceanicus*, @Simmons2006; *Gryllus bimaculatus*, @Bretman2009].
 Evidence for both pre-copulatory and post-copulatory inbreeding avoidance is available across different studies of Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015].
@@
 
-@Duthie used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve due to selection stemming from pre-copulatory inbreeding avoidance in the absence of any post-copulatory inbreeding avoidance.
-Even when selection for pre-copulatory inbreeding avoidance was strong and females consequently preferred unrelated mates, selection for polyandry specifically as a mechanism to facilitate this inbreeding avoidance occurred only under highly restricted conditions, requiring that direct negative selection (i.e., 'costs') on polyandry was weak, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
-Without these conditions, females that engaged in polyandry tended to be constrained to increase rather than decrease their overall degree of inbreeding, ultimately reducing offspring fitness.
-This constraint occurred because, once pre-copulatory inbreeding avoidance evolved, polyandrous females had already chosen available unrelated males as their initial mates.
+In one first step, @Duthie used a genetically-explicit individual-based model to examine conditions under which polyandry is predicted to evolve due to selection stemming from pre-copulatory inbreeding avoidance in the absence of post-copulatory inbreeding avoidance.
+Simulations showed that even when selection for pre-copulatory inbreeding avoidance was strong and females consequently preferred unrelated mates, selection for polyandry specifically to facilitate this inbreeding avoidance occurred only under highly restricted conditions.
+Key requirements were that direct negative selection (i.e., 'costs') on polyandry was weak, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie].
+Without these conditions, polyandrous females tended to increase rather than decrease their overall degree of inbreeding, ultimately reducing offspring fitness.
+This increase occurred because, once pre-copulatory inbreeding avoidance evolved, polyandrous females had already chosen available unrelated males as their initial mates.
 Their additional mates, chosen from the remaining male population, were therefore increasingly likely to include relatives.
-Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance, and hence the resulting degree of inbreeding avoidance, was consequently restricted [@Duthie].
+Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance, and hence resulting inbreeding avoidance, was consequently restricted [@Duthie].
 
-However, if post-copulatory inbreeding avoidance could also evolve, polyandrous females would have the opportunity to bias paternity towards unrelated males within their set of chosen mates.
+However, if post-copulatory inbreeding avoidance could evolve alongside pre-copulatory inbreeding avoidance, then polyandrous females could bias fertilisation towards unrelated males within their set of mates.
 Evolution of post-copulatory inbreeding avoidance might consequently reduce the cost of polyandry stemming from the accumulation of related mates across multiple matings, potentially facilitating evolution of polyandry to avoid inbreeding under broader conditions, and driving further evolution of pre-copulatory or post-copulatory mate choice strategies.
-Subsequently, if polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, the long-term dynamics of these three reproductive strategies become difficult to predict.
+Yet, if polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, the long-term dynamics of these three reproductive strategies become difficult to predict.
 Strong inbreeding depression might drive initial evolution of both pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
@@
 
-The few previous models that considered evolution of inbreeding avoidance through mate choice (as opposed to dispersal) have implicitly or explicitly considered the fate of a rare allele underlying pre-copulatory inbreeding avoidance in a population initially fixed for random mating [e.g., @Parker1979; @Parker2006; @Duthie; @Duthie2016a].
+The few previous models that considered evolution of biparental inbreeding avoidance through mate choice (as opposed to dispersal) have implicitly or explicitly considered the fate of a rare allele underlying pre-copulatory inbreeding avoidance in a population initially fixed for random mating [e.g., @Parker1979; @Parker2006; @Duthie; @Duthie2016a].
 Such models are useful for isolating the invasion fitness of this single strategy.
@@
 
-Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will be affected not only by the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also by the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
-There are multiple mechanisms by which direct costs might by incurred for polyandry, pre-copulatory choice, and post-copulatory choice; here we focus on three examples observed in empirical populations.
-Polyandrous females might pay costs of mate searching or mating because these activities increase predation risk [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
-Females that express pre-copulatory choice and consequent reluctance to mate with relatives might pay costs of increased risk of complete mating failure or harm caused by sexual conflict [@Rowe1994; @Kokko2013].
-Finally, females that express post-copulatory choice might pay initial energetic costs associated with developing the physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b].
-If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly strategy might become extinct, especially if their effects are made redundant by evolution of the less costly strategy.
-Evolutionary dynamics will therefore depend on the benefits of each strategy, which might also differ and vary in relation to the evolution of the other strategy.
-Dynamic models that track the frequencies of alleles underlying multiple reproductive strategies that might influence each others evolution across generations, and that are enacted among relatives that themselves result from reproductive strategies and inbreeding depression expressed in previous generations, are consequently useful to understand and predict evolutionary outcomes.
+In the context of inbreeding as the postulated driver of reproductive strategy evolution, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will be affected not only by the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also by the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
+Empirical studies on diverse systems have demonstrated diverse costs of mating and mate choice, for example, including energetic costs of developing, maintaining, or enacting necessary physiologies [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b]; increased risks of predation or disease stemming from increased mate-searching or mating [e.g., @Rowe1988; @Ronkainen1994; @Koga1998]; increased risk of complete mating or fertilisation failure given extreme choosiness [@Kokko2013]; and risks of harm stemming from sexual conflict over fertilisation [e.g., @Rowe1994].
+If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly strategy might go extinct, especially if their effects become redundant following evolution of the less costly strategy.
+Evolutionary dynamics will therefore depend on the inbreeding avoidance benefit of each strategy, which might also differ and vary in relation to the evolution of the other strategy.
+Dynamic models that track the frequencies of alleles underlying multiple potentially costly inbreeding avoidance strategies that might influence each other's evolution across generations, and that are enacted among relatives that themselves result from reproductive strategies and inbreeding depression expressed in previous generations, are consequently useful to understand and predict evolutionary outcomes.
 
 We use individual-based modelling to address three key questions regarding evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given opportunity for inbreeding and strong inbreeding depression.
-First, does evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance facilitate evolution of polyandry that is otherwise severely constrained by increasing relatedness of polyandrous females' additional mates?
+First, does evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance facilitate evolution of polyandry that is otherwise severely constrained by increasing relatedness of polyandrous females to their additional mates?
 Second, how do costs associated with polyandry and pre-copulatory and post-copulatory inbreeding avoidance affect evolutionary outcomes and, in particular, the long-term persistence of these reproductive strategies given cost asymmetry?
 Third, how is selection for initially rare pre-copulatory or post-copulatory inbreeding avoidance affected if the other strategy of inbreeding avoidance is already fixed?
-For each question, we isolate the effect of the biological mechanism of interest (i.e., post-copulatory inbreeding avoidance, cost asymmetry, and another fixed strategy of inbreeding avoidance) by running simulations in which the mechanism is present and comparing the results to those of simulations in which the it is absent but all other parameter values are identical.
-We restrict our model to simulate how evolution of traits are affected by their direct costs and indirect benefits due to inbreeding avoidance.
-Although empirical populations will include additional beneficial traits that might affect evolution of mating strategies, targeting our focus on traits affecting inbreeding and polyandry allows us to better isolate their effects and therefore better develop hypotheses for empirical systems.
-By addressing our three questions, we illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
+To address each question, we isolate the effect of the biological mechanism of interest (i.e., post-copulatory inbreeding avoidance, cost asymmetry, and strategy pre-existence, respectively) by comparing simulations with the mechanism present versus absent with otherwise identical parameter values and conditions.
+We thereby illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
 

### 2017-07-26 ms_pre_post.Rmd
Edits through the costs

@@
 We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply 'inbreeding strategies' because the model did not preclude evolution of inbreeding preference), in a small focal population of females and males by tracking the dynamics of alleles underlying reproductive strategies expressed by females.
-We thereby track evolutionary dynamics given internally consistent patterns of relatedness caused by non-random mating and allowing for effects of mutation, gene flow, drift, and selection.
+We thereby track evolutionary dynamics given internally consistent patterns of relatedness caused by non-random mating and capture effects of mutation, gene flow, drift, and selection.
 
-Complex traits such as reproductive behaviour are likely to be highly polygenic [@Evans2008].
-Hence, in our model, all individuals have 10 physically unlinked diploid loci, and therefore 20 alleles, underlying each of three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$, i.e., 'polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., 'fertilisation' alleles).
-All alleles can take the value of any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014] and combine additively to determine genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and resulting phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively.
+Complex traits such as reproductive strategies are likely to be polygenic [@Evans2008].
+Hence, we model individuals with 10 physically unlinked diploid loci (and therefore 20 alleles), underlying each of three reproductive strategy traits: tendency for polyandry ($P_{a}$, i.e., 'polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., 'fertilisation' alleles).
+All individuals therefore have 30 diploid loci (and hence 60 alleles) in total, each of which can take the value of any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014].
+
+Alleles combine additively to determine genotypic values ($P_{g}$, $M_{g}$, and $F_{g}$) and resulting phenotypic values ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively.
 Each individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
 Each individual's phenotypic values for pre-copulatory and post-copulatory inbreeding strategy equal their respective genotypic values ($M_{p} = M_{g}$ and $F_{p} = F_{g}$), where negative and positive values cause inbreeding avoidance and preference, respectively (see details of mating and fertilisation strategies below).
-In contrast to inbreeding strategies, the polygenic nature of polyandry cannot translate to continuous phenotypes affecting mate choice [e.g., @Shuker2007; @Evans2013].
-Polyandry is more realistically defined as a "threshold trait", influenced by continuous genetic variation but expressed at some discrete phenotypic value(s) [@Lynch1998; @Roff1996; @Roff1998; @Duthie].
-We incorporate this genetic architecture into our model by allowing phenotypic values for tendency for polyandry to equal genotypic values ($P_{p} = P_{g}$) only if $P_{g} \geq 0$, while $P_{p} = 0$ if $P_{g} < 0$ because females cannot choose a negative number of mates.
+
+In contrast, individuals' phenotypic values for tendency for polyandry ($P_{p}$) cannot map directly onto their genotypic values ($P_{g}$) because $P_{g}$ can evolve to be negative, but females cannot mate with a negative number of additional males [e.g., @Shuker2007; @Evans2013].
+Rather, polyandry is more realistically considered as a "threshold trait", whereby continuous genotypic variation translates into expression of discrete phenotypic value(s) at some threshold [@Lynch1998; @Roff1996; @Roff1998; @Duthie].
+Accordingly, we allow individuals' phenotypic values for tendency for polyandry to equal genotypic values ($P_{p} = P_{g}$) if $P_{g} \geq 0$, but set $P_{p} = 0$ if $P_{g} < 0$.
+A negative $P_{g}$ value therefore generates a female that is phenotypically monandrous, while a positive $P_{g}$ value generates a female that can express some degree of polyandry (see details below).
 Polyandry is therefore influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
-A negative $P_{g}$ value therefore generates a female that is phenotypically monandrous, while a positive $P_{g}$ value generates a female that can express some degree of polyandry (see details below).
-One important consequence of this genetic architecture is that threshold traits often reappear in a population despite sustained negative selection, as caused by recombination of previously masked deleterious alleles [@Roff1996; @Roff1998].
+One important general property of such threshold traits is that deleterious traits are occasionally expressed despite sustained negative selection because recombination among deleterious alleles can cause the underlying genotypic value to exceed the threshold for expression [@Roff1996; @Roff1998].
 
-In overview, each generation proceeds with females paying costs associated with their reproductive strategy traits, and expressing polyandry, mating, and fertilisation.
+In overview, each model generation proceeds with females paying costs associated with their reproductive strategy traits, and expressing polyandry, mating, and fertilisation.
 Offspring inherit a randomly sampled allele from each parent at each locus.
@@
 
-Phenotypic values of the three reproductive strategy traits each have pre-determined costs that are assumed to combine independently to increase the probability that a focal female will die before mating.
-The ability to set costs independently and a priori in this way is critical because it permits the direct comparison of evolution of pre-copulatory versus post-copulatory inbreeding avoidance (see Discussion for consideration of more mechanistic costs).
-The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
+Phenotypic values of the three reproductive strategy traits each incur set costs that combine independently to increase the probability that a focal female will die before mating.
+Numerous forms and mechanisms of direct costs of reproductive strategies could potentially be hypothesised and modelled; the most appropriate formulation depends on the question posed (see Discussion).
+By allowing costs of the three strategies to be directly and independently controlled, our model facilitates direct comparison of evolution of pre-copulatory versus post-copulatory inbreeding avoidance given known cost asymmetries.
+Such costs on female survival probably are biologically reasonable.
+For example, polyandrous females that undertake increased mate searching or mating can experience increased predation risk [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
+Females that express pre-copulatory choice can increase the risk of mortality due to harm caused by sexual conflict over mating, and also risk complete mating failure [which equates to pre-reproductive mortality in semelparous organisms; @Rowe1994; @Kokko2013].
+Finally, females that express post-copulatory choice can pay up-front energetic costs, and associated trade-offs with survival, due to developing physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014].
+
+Accordingly, the probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
 Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
 Absolute values are used for applying costs to inbreeding avoidance strategies because both negative and positive $M_{p}$ and $F_{p}$ values could potentially arise and affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively.
-In contrast, $P_{p}$ cannot be negative.
-Values of $c_{P}$, $c_{M}$, and $c_{F}$ can be interpreted mechanistically as the increased mortality risk caused by mate searching [e.g., @Koga1998], resisting male harrassment [i.e., sexual conflict; @Rowe1994], and energetic loss from development of post-copulatory inbreeding avoidance mechanisms [e.g., @Gasparini2011], respectively.
+In contrast, $P_{p}$ is already defined to be non-negative.
 Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.

### 2017-07-27 ms_pre_post.Rmd
Edit through Results

@@
 
-After costs are realised, each remaining female chooses $N_{males}$ males to mate with, where $N_{males}$ is calculated by sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
+After costs are realised, each surviving female chooses $N_{males}$ males to mate with, where $N_{males}$ is calculated by sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$.
 This ensures that all surviving females choose at least one mate and generates each female's realised degree of polyandry with some stochastic variation around the expected mean $N_{males}$ of $P_{p}+1$.
@@
 Each female then chooses her $N_{males}$ mates based on her pre-copulatory inbreeding avoidance phenotype ($M_{p}$).
-Negative or positive $M_{p}$ values cause a female to avoid or prefer mating with kin, respectively, whereas $M_{p}=0$ cause females to mate randomly with respect to kinship.
+Negative or positive $M_{p}$ values cause a female to avoid or prefer mating with kin, respectively, whereas $M_{p}=0$ causes a female to mate randomly with respect to kinship.
 
@@
 
-The probability that an offspring of female $i$ is sired by any one of $i$'s mates $j$ is calculated by assigning a perceived fertilisation quality to each $j$ with respect to $i$, $Q^{f}_{ij}$.
+The probability that an offspring of female $i$ is sired by any one of her mates $j$ is calculated by assigning a perceived fertilisation quality to each $j$ with respect to $i$, $Q^{f}_{ij}$.
 Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if female $i$ has a strategy of post-copulatory inbreeding avoidance ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$.
@@
 Equation 1 assumes independent allelic effects, generating multiplicative effects on offspring viability [@Morton1956; @Mills1994].
-It also assumes that inbreeding does not covary with inbreeding load (i.e., no purging), allowing the effects of kinship on inbreeding depression to be consistent across replicate simulations.
-Additionally, previous modelling has found that inbreeding avoidance in biparental populations has a negligible effect on load [@Duthie2016a].
+It also assumes that inbreeding does not covary with inbreeding load (i.e., no purging).
+This formulation ensures that the relationship between $k_{ij}$ and the magnitude of inbreeding depression in offspring is consistent across replicate simulations and is justified because previous genetically-explicit modelling [@Duthie2016a] showed that inbreeding avoidance in biparental populations has a negligible effect on load given small-effect deleterious mutations [see also @Wang1999; @Guillaume2006].
 We model inbreeding depression as having an absolute rather than relative effect on offspring viability (i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
@@
 Offspring that are viable after the Bernoulli trial become adults.
-Given our current objectives, we simulate evolution under conditions where inbreeding avoidance is adaptive due to strong inbreeding depression, and not evolution where inbreeding preference is adaptive due to weak or zero inbreeding depression [@Parker1979; @Kokko2006; @Duthie2016a], or given outbreeding depression [@Bateson1983; @Greeff2009].
+Given our current objectives, we simulate evolution under conditions where inbreeding avoidance is adaptive due to strong inbreeding depression, not where inbreeding preference is adaptive due to weak or zero inbreeding depression [@Parker1979; @Kokko2006; @Duthie2016a] or outbreeding depression [@Bateson1983; @Greeff2009].
 However, as described above, positive $M_{p}$ and $F_{p}$ values resulting in inbreeding preference are not precluded from evolving, and could potentially arise due to mutation or drift.
@@
 
-Simulations and analysis
+Simulations and analyses
 ----------------------------------------------
@@
 Previous modelling using similar genetic architecture suggests that a cost of $0.02$ imposes strong but not overwhelming direct negative selection on polyandry [@Duthie].
-This value is therefore appropriate to illustrate the different evolutionary consequences that could result from asymmetrical costs (but see Supporting Information for other asymmetric cost combinations).
+This value is therefore appropriate to illustrate the different evolutionary consequences that could result from asymmetrical costs (see Supporting Information).
 
 To address how selection on an initially rare strategy of pre-copulatory or post-copulatory inbreeding avoidance, and resulting evolution, is affected by the other strategy of inbreeding avoidance already being fixed in the population, we first used exploratory simulations to quantify evolution of pre-copulatory inbreeding strategy, and of post-copulatory inbreeding strategy and associated polyandry, in isolation.
-Then, to test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance were fixed, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., $F_{p}$ and $P_{p}$ were expressed did not evolve further).
+Then, to test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance were fixed, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., $F_{p}$ and $P_{p}$ were expressed but did not evolve further).
 Similarly, to test whether post-copulatory inbreeding avoidance would evolve when pre-copulatory inbreeding avoidance was already fixed, we initiated $F_{a}$ and $P_{a}$ allele values at zero but fixed $M_{a}$ allele values at $-10$.
@@
 These analyses allowed us to infer how allele values changed over generations in response to costs, but also in response to the changing values of other alleles and therefore potential evolutionary feedbacks among reproductive strategies.
-In our analyses, we do not use statistical tests to interpret simulation results; such tests are innappropriate because they violate the underlying assumptions of statistical hypothesis testing, and because statistical power (and therefore p-values) would be entirely determined by the number of simulation replicates performed [@White2014].
+We do not use statistical tests to interpret simulation results; such tests are inappropriate because simulations violate key assumptions of statistical hypothesis testing, and statistical power (and therefore p-values) is determined entirely by the number of simulation replicates [@White2014].
+
 For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling [@Duthie] showed to be sufficient for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
@@
 Similarly, when post-copulatory but not pre-copulatory inbreeding avoidance was costly ($c_{F}=0.02$ and $c_{M}=0$), post-copulatory inbreeding avoidance initially evolved (i.e., $F_{a} < 0$) before evolving back to random fertilisation (i.e., $F_{a} \approx 0$) after ca $20000$ generations (Figure 3D).
-This evolution of a high cost strategy back toward random mating or fertilisation in the presence of a relatively low cost alternative inbreeding strategy is a general consequence of differential selection on each strategy induced by cost asymmetry.
-Hence, this pattern can be observed for both non-zero low relative costs (e.g., values of 0.01 and 0.03; Figure S9) and smaller cost asymmetries (e.g., values of 0.01 and 0.02; Figure S10).
+
+Further simulations illustrate that such evolution of a high cost inbreeding strategy back toward random mating or random fertilisation in the presence of a relatively low cost alternative strategy is a general consequence of differential selection on each strategy induced by cost asymmetry within a range of relatively small costs, not specific to values of $c_{F}$ and $c_{M}$ of 0 and 0.02.
+For example, cost-specific evolution of pre-copulatory or post-copulatory inbreeding avoidance also occurred given non-zero small costs (e.g., $c_{F}$ and $c_{M}$ values of 0.01 and 0.03 and vice versa; Figure S9) and smaller cost asymmetries (e.g., $c_{F}$ and $c_{M}$ values of 0.01 and 0.02 and vice versa; Figure S10).
 
@@
 However when post-copulatory inbreeding avoidance was costly, allowing evolution of cost free pre-copulatory inbreeding avoidance caused $P_{a}$ alleles to decrease to very negative values, reducing expression of polyandry (Figure 3C versus 3D; polyandry was cost free in all these simulations).
-Results for all possible cost combinations of $0$ and $0.02$ are provided in Supporting Information (Figure S11).
+Results for all possible cost combinations of $0$ and $0.02$, including costly polyandry, are provided in Supporting Information (Figure S11).
 
@@
 $-17.62$; compare the blue lines in Figures 4A versus Figure 1B).
-Hence, we hypothesise that existence of fixed post-copulatory inbreeding avoidance can weaken selection and subsequent evolution of pre-copulatory inbreeding avoidance.
+This implies that pre-existence of fixed post-copulatory inbreeding avoidance can weaken selection and subsequent evolution of pre-copulatory inbreeding avoidance, but does not necessarily preclude it.
 
-Conversely, when pre-copulatory inbreeding allele ($M_{a}$) values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently become negative over generations (Figure 4C,D).
-Hence, we hypothesise that existence of fixed pre-copulatory inbreeding avoidance can prevent evolution of post-copulatory inbreeding avoidance.
-In our model, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless of whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
+In contrast, when pre-copulatory inbreeding allele ($M_{a}$) values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently become negative over generations (Figure 4C,D).
+This implies that existence of fixed pre-copulatory inbreeding avoidance can prevent evolution of post-copulatory inbreeding avoidance.
+In these simulations, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless of whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
 Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values (resulting in variation among replicates illustrated by the wide standard errors in Figure 4C).
 However, when $c_{F}=0.02$, $F_{a}$ values remained near zero to minimise direct costs.
-This lack of selection for post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
+The lack of selection for post-copulatory inbreeding avoidance when pre-copulatory inbreeding avoidance was fixed was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
 When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information Figure S12).

### 2017-07-28 ms_pre_post.Rmd
First part of Discussion initial revision

@@
 Evolution of different reproductive strategies cannot be presumed to occur in isolation from each other in real-world populations.
-Rather, such evolution is likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundancy) among phenotypes under selection.
-For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently drive selection for polyandry [e.g., @Zeh1997; @Jennions2000; @Tregenza2002].
-Inbreeding avoidance could be manifested through both pre-copulatory and post-copulatory mechanisms, meaning that simultaneous evolution of each phenotype might be defined by degeneracy in addition to trait-specific costs.
-We used individual-based modelling to highlight fundamental but theoretically under-developed relationships between evolution of polyandry and pre-copulatory versus post-copulatory inbreeding strategy given (1) hard constraints on evolution of post-copulatory inbreeding strategy, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding strategy, and (3) evolution of one inbreeding strategy phenotype given the pre-existence of the other.
-We present our model and simulation results as a tool for thinking more clearly about the dynamics of simultaneously evolving reproductive strategies, not for making accurate quantitative predictions for any specific system.
-While the logic of our model can be usefully applied to constructing hypotheses within and across empirical systems, accurate quantitative prediction would require additional detail and the incorporation of empirical data for model parameterisation.
+Rather, there is likely to be considerable potential for feedbacks and degeneracy (i.e., functional redundancy) among multiple interacting phenotypes.
+For example, inbreeding avoidance could be manifested through both pre-copulatory and post-copulatory mechanisms and associated polyandry, meaning that simultaneous evolution of each phenotype might be defined by degeneracy in addition to trait-specific costs.
+
+We used individual-based modelling to highlight fundamental but theoretically under-developed relationships between evolution of polyandry and pre-copulatory versus post-copulatory inbreeding strategy given (1) hard constraints on evolution of post-copulatory inbreeding strategy, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding strategy, and (3) evolution of one inbreeding strategy phenotype given pre-existence of the other.
+We present our model and simulation results as tools for thinking more clearly about the dynamics of simultaneously evolving reproductive strategies, not for making accurate quantitative predictions for any specific system.
+While the logic of our model can be usefully applied to construct hypotheses within and across empirical systems, accurate quantitative prediction would require additional empirical detail and data for model parameterisation.
 

### 2017-07-28 ms_pre_post.Rmd
Second Discussion section -- comment out fertilisation bias

@@
 
-Evolution of polyandry
+Interacting evolution of polyandry and inbreeding avoidance strategies
 -------------------------------------------------------------------
 
-The opportunity to adjust inbreeding has been widely suggested to be a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
-We found that when post-copulatory inbreeding avoidance could evolve, selection for and resulting evolution of polyandry was greatly strengthened (Figure 1).
-The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but our model clarifies this verbal hypothesis and therefore has widespread implications for future studies of evolution of polyandry.
+The opportunity to adjust inbreeding is widely suggested to be a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
+Our model and simulations show that when post-copulatory inbreeding avoidance could evolve, selection for and resulting evolution of polyandry was greatly strengthened (Figure 1).
+The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but our model clarifies this verbal hypothesis and therefore has widespread implications for future studies of polyandry evolution.
 
 We predict evolution of polyandry in populations where inbreeding depression is severe and inbreeding avoidance through post-copulatory mechanisms can also evolve, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
-Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa [e.g., @Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015].
+Indeed, post-copulatory inbreeding avoidance has been observed under these conditions in experimental systems across diverse taxa [e.g., @Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015].
+
+<!---
 Recent studies have shown how females can successfully bias fertilisation after mating has occurred.
@@
 In black field crickets (*Teleogryllus commodus*), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs [@Bussiere2006; @Tuni2013].
+--->
 

### 2017-07-28 ms_pre_post.Rmd
Update Discussion up to before new addition of Model Assumptions and Extensions

@@
 
-Evolution of different reproductive strategies cannot be presumed to occur in isolation from each other in real-world populations.
+Evolution of different reproductive strategies cannot be presumed to occur in isolation from each other.
 Rather, there is likely to be considerable potential for feedbacks and degeneracy (i.e., functional redundancy) among multiple interacting phenotypes.
@@
 
-Interaction of polyandry and inbreeding avoidance strategies
--------------------------------------------------------------------
+Evolution of both pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but were affected by the evolution of polyandry and by cost asymmetries.
+One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population (Figure 3).
+Hence, our model demonstrates that degenerate inbreeding avoidance strategies can interact with one another, and implies that such interactions should be considered when developing hypotheses concerning reproductive strategy within and across systems.
+In particular, indefinite persistence of both pre-copulatory and post-copulatory inbreeding avoidance should not be expected in populations given a sufficiently large and sustained cost asymmetry.
+However, the time required for the more costly inbreeding strategy to go extinct might be on the order of tens of thousands of generations (Figure 3), and spatial or temporal variation in costs might facilitate coexistence of multiple inbreeding avoidance strategies.
 
-Evolution of both pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but were affected by the evolution of polyandry and the existence of asymmetric costs.
-One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population (Figure 3).
-Hence, our model demonstrates a novel mechanism by which degenerate inbreeding avoidance strategies can interact with one another, and this mechanism might usefulg to consider when developing hypotheses concerning reproductive strategy within and across systems.
-In particular, indefinite persistence of both pre-copulatory and post-copulatory inbreeding avoidance should not be expected in populations given a sufficiently large and sustained cost asymmetry.
-However, the length of time required for the more costly inbreeding strategy to go extinct might be quite long (Figure 3), and spatial or temporal variation in costs might facilitate the coexistence of multiple inbreeding avoidance strategies.
-Nevertheless, since direct costs strongly affected evolution of the focal phenotype(s), quantifying costs is necessary for predicting evolution of inbreeding strategies.
-
+<!---
 To facilitate a general comparison of the effects of direct costs across phenotypes, all costs in our model were manifested as an increased probability of total reproductive failure.
@@
 Evolution of reproductive strategies therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.
+--->
 
-In our model, existence of fixed adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, precluded evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
+Further, pre-existence of fixed adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, precluded evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
 However, existence of fixed adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Figure 3A,B).
-In wild populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
+In most populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
 Rather, the timing of the invasion of adaptive inbreeding avoidance phenotypes will differ, so the initial evolution of one inbreeding strategy will likely occur in the absence of the other, or where selection for and subsequent evolution of the other strategy has already occurred.

### 2017-07-28 ms_pre_post.Rmd
Final suggested Discussion writing, prep for another round

@@
 
-Interacting evolution of polyandry and inbreeding avoidance strategies
--------------------------------------------------------------------
-
-The opportunity to adjust inbreeding is widely suggested to be a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
-Our model and simulations show that when post-copulatory inbreeding avoidance could evolve, selection for and resulting evolution of polyandry was greatly strengthened (Figure 1).
-The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but our model clarifies this verbal hypothesis and therefore has widespread implications for future studies of polyandry evolution.
-
-We predict evolution of polyandry in populations where inbreeding depression is severe and inbreeding avoidance through post-copulatory mechanisms can also evolve, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
-Indeed, post-copulatory inbreeding avoidance has been observed under these conditions in experimental systems across diverse taxa [e.g., @Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015].
-
-<!---
-Recent studies have shown how females can successfully bias fertilisation after mating has occurred.
-For example, when female guppies (*Poecilia reticulata*) were artificially inseminated with equal quantities of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full siblings' sperm were reduced by females' ovarian fluids [@Gasparini2011].
-In black field crickets (*Teleogryllus commodus*), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs [@Bussiere2006; @Tuni2013].
---->
-
-Evolution of both pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but were affected by the evolution of polyandry and by cost asymmetries.
-One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population (Figure 3).
-Hence, our model demonstrates that degenerate inbreeding avoidance strategies can interact with one another, and implies that such interactions should be considered when developing hypotheses concerning reproductive strategy within and across systems.
-In particular, indefinite persistence of both pre-copulatory and post-copulatory inbreeding avoidance should not be expected in populations given a sufficiently large and sustained cost asymmetry.
-However, the time required for the more costly inbreeding strategy to go extinct might be on the order of tens of thousands of generations (Figure 3), and spatial or temporal variation in costs might facilitate coexistence of multiple inbreeding avoidance strategies.
-
-<!---
-To facilitate a general comparison of the effects of direct costs across phenotypes, all costs in our model were manifested as an increased probability of total reproductive failure.
-We thereby interpreted as a cost of polyandy as an elevated risk of predation as might be incurred while searching for mates [e.g., @Koga1998], a cost of pre-copulatory inbreeding strategy as a risk associated with male harrassment [e.g., @Rowe1994], and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy needed for post-copulatory kin discrimination [e.g., @Gasparini2011].
-While these costs reflect empirical observations in some populations and are therefore biologically realistic, more mechanistic costs could be assumed or predicted from future models tailored to specific empirical systems.
-In empirical systems, quantifying direct costs of phenotypes associated with polyandry and mate choice is challenging [@Pomiankowski1987; @Kokko2003].
-@Pomiankowski1987 categorised four types of costs that are relevant to mating frequency and mate choice, which include costs of elevated risks of predation or disease transmission, and costs incurred through time or energy expenditure.
-For example, highly polyandrous females might experience increased risk of disease transmission [@Roberts2015a].
-Such a cost would more realistically apply to a female's realised number of mates rather than her tendency for polyandry.
-Polyandrous females might also risk harm caused by sexual conflict over multiple mating [e.g., @Arnqvist2005a; @Parker2006].
-Inbreeding theory predicts that males should be more tolerant of inbreeding than females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
-Future models could therefore more mechanistically consider sexual conflict over both polyandry and inbreeding.
-Overall, such different types of potentially interacting costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
-Evolution of reproductive strategies therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.
---->
-
-Further, pre-existence of fixed adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, precluded evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
-However, existence of fixed adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Figure 3A,B).
-In most populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
-Rather, the timing of the invasion of adaptive inbreeding avoidance phenotypes will differ, so the initial evolution of one inbreeding strategy will likely occur in the absence of the other, or where selection for and subsequent evolution of the other strategy has already occurred.
-When framing hypotheses for existence of post-copulatory inbreeding avoidance and polyandry, it might therefore be necessary to consider whether or not inbreeding avoidance already occurs through pre-copulatory mate choice.
-Additionally, the opportunity for post-copulatory inbreeding avoidance will also depend on the degree to which females are polyandrous.
-For species in which pre-copulatory inbreeding avoidance occurs and polyandry is uncommon [@Lihoreau2007; @Metzger2010; @Metzger2010a], evolution of post-copulatory inbreeding avoidance is unlikely even if such a strategy incurs little direct cost.
-
 General predictions concerning inbreeding avoidance and polyandry
@@
 
-Post-copulatory inbreeding avoidance cannot be effectively realised if females are not polyandrous in any form, and is likely to be most effective for highly polyandrous females that can choose amongst sperm contributed by multiple mates and therefore bias fertilisation accordingly.
+Post-copulatory inbreeding avoidance cannot be effectively realised if females are not polyandrous in any form, and is likely to be most effective for highly polyandrous females that can bias fertilisation amongst sperm contributed by multiple mates.
 In contrast, pre-copulatory inbreeding avoidance mechanisms are most critical for females that mate only once and therefore have no post-copulatory opportunity to avoiding inbreeding.
@@
 The relevance of degeneracy with respect to such reproductive strategies therefore requires further theoretical development, which could result in new empirical predictions and conceptual synthesis across biological scales.
+
+Interacting evolution of polyandry and inbreeding avoidance strategies
+-------------------------------------------------------------------
+
+The opportunity to adjust inbreeding is widely suggested to be a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
+Our model and simulations show that when post-copulatory inbreeding avoidance could evolve, selection for and resulting evolution of polyandry was greatly strengthened (Figure 1).
+The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but our model clarifies this verbal hypothesis and therefore has widespread implications for future studies of polyandry evolution.
+
+We predict evolution of polyandry in populations where inbreeding depression is severe and inbreeding avoidance through post-copulatory mechanisms can also evolve, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
+Indeed, post-copulatory inbreeding avoidance has been observed under these conditions in experimental systems across diverse taxa [e.g., @Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015].
+
+Evolution of both pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but were affected by the evolution of polyandry and by cost asymmetries.
+One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population (Figure 3).
+Hence, our model demonstrates that degenerate inbreeding avoidance strategies can interact with one another, and implies that such interactions should be considered when developing hypotheses concerning reproductive strategy within and across systems.
+In particular, indefinite persistence of both pre-copulatory and post-copulatory inbreeding avoidance should not be expected in populations given a sufficiently large and sustained cost asymmetry.
+However, the time required for the more costly inbreeding strategy to go extinct might be on the order of tens of thousands of generations (Figure 3), and spatial or temporal variation in costs might facilitate coexistence of multiple inbreeding avoidance strategies.
+
+Further, pre-existence of fixed adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, precluded evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
+However, existence of fixed adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Figure 3A,B).
+In most populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
+Rather, the timing of the invasion of adaptive inbreeding avoidance phenotypes will differ, so the initial evolution of one inbreeding strategy will likely occur in the absence of the other, or where selection for and subsequent evolution of the other strategy has already occurred.
+When framing hypotheses for existence of post-copulatory inbreeding avoidance and polyandry, it might therefore be necessary to consider whether or not inbreeding avoidance already occurs through pre-copulatory mate choice.
+Additionally, the opportunity for post-copulatory inbreeding avoidance will also depend on the degree to which females are polyandrous.
+For species in which pre-copulatory inbreeding avoidance occurs and polyandry is uncommon [@Lihoreau2007; @Metzger2010; @Metzger2010a], evolution of post-copulatory inbreeding avoidance is unlikely even if such a strategy incurs little direct cost.
+
+Model assumptions and extensions
+-------------------------------------------------------------------
+
+To acheive our current objective of providing general conceptual comparison of the effects of direct costs across phenotypes, we modelled all costs as analogous increased probabilities of total reproductive failure, thereby facilitating direct comparison across traits.
+This cost formulation reflects empirical observations in some populations [see Model; e.g., @Rowe1994; @Koga1998; @Gasparini2011], and is therefore a biologically realistic means of standardising costs across traits.
+However, different forms of costs could be incorporated into future models designed to predict evolutionary dynamics that might occur in specific systems.
+@Pomiankowski1987 identified four costs categories relevant to mating frequency and mate choice, including elevated risks of predation or disease transmission, and time or energey expenditure.
+For example, polyandrous females might experience increased risk of disease transmission [@Roberts2015].
+This cost would more realistically apply to a female's realised number of mates rather than her tendency for polyandry.
+Polyandrous females might also risk harm caused by sexual conflict over multiple mating [e.g., @Arnqvist2005; @Parker2006].
+Inbreeding theory predicts that males should be more tolerant of inbreeding females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
+Future models could therefore explicitly consider sexual conflict over both polyandry and inbreeding, and hence capture internally-consistent mechanistic costs.
+
+<!--- TODO: Edit first sentence --->
+Models could then be further developed such that costs arise from explicit reproductive mechanisms, requiring further biological detail.
+Recent studies have elucidated key mechanisms of post-copulatory inbreeding avoidance.
+For example, when female guppies (*Poecilia reticulata*) were artificially inseminated with equal quantitites of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full sibling's sperm were reduced by females' ovarian fluids [@Gasparini2011].
+In black field crickets (*Teleogryllus commodus*), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs [@Bussiere2006; @Tuni2013].
+
+<!--- TODO: Edit first sentence ---> 
+We restricted our model to simulate how evolution of traits were affected by their direct costs and indirect benefits due to inbreeding avoidance.
+Although empirical populations will include additional beneficial traits that might affect evolution of mating strategies, targeting our focus on traits affecting inbreeding and polyandry allows us to better isolate their effects and therefore better develop hypotheses for natural systems.
 

### 2017-07-28 ms_pre_post.Rmd
Substantial changes to end of Discussion

@@
 Their additional mates, chosen from the remaining male population, were therefore increasingly likely to include relatives.
-Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance, and hence resulting inbreeding avoidance, was consequently restricted [@Duthie].
+Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance was consequently restricted [@Duthie].
 
@@
 Offsprings' alleles mutate with independent probabilities $\mu=0.001$.
-When a mutation occurs, a mutation effect is sampled from a normal distribution with a mean of zero and a standard deviation of $\mu_{SD}$ and added to the original allele value [@Kimura1965; @Lande1976; @Bocedi2014; @Duthie].
+When a mutation occurs, a mutation effect size is sampled from a normal distribution with a mean of zero and a standard deviation of $\mu_{SD}$ and added to the original allele value [@Kimura1965; @Lande1976; @Bocedi2014; @Duthie].
 The value of $\mu_{SD}$ is set to $\sqrt{1/20}$.
@@
 It also assumes that inbreeding does not covary with inbreeding load (i.e., no purging).
-This formulation ensures that the relationship between $k_{ij}$ and the magnitude of inbreeding depression in offspring is consistent across replicate simulations and is justified because previous genetically-explicit modelling [@Duthie2016a] showed that inbreeding avoidance in biparental populations has a negligible effect on load given small-effect deleterious mutations [see also @Wang1999; @Guillaume2006].
-We model inbreeding depression as having an absolute rather than relative effect on offspring viability (i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
+This formulation ensures that the relationship between $k_{ij}$ and the magnitude of inbreeding depression in offspring is consistent across replicate simulations and is further justified because previous genetically-explicit modelling [@Duthie2016a] showed that inbreeding avoidance in biparental populations has a negligible effect on load given small-effect deleterious mutations [see also @Wang1999; @Guillaume2006].
+We model inbreeding depression as having an absolute rather than relative effect on offspring viability (i.e., hard rather than soft selection) so that the effect of $\beta$ is consistent across generations and different parameter combinations.
 We assume that inbreeding always decreases offspring viability (i.e., $\beta > 0$, giving inbreeding depression but no outbreeding depression).
@@
 We present our model and simulation results as tools for thinking more clearly about the dynamics of simultaneously evolving reproductive strategies, not for making accurate quantitative predictions for any specific system.
-While the logic of our model can be usefully applied to construct hypotheses within and across empirical systems, accurate quantitative prediction would require additional empirical detail and data for model parameterisation.
+While the logic of our model can be usefully applied to construct general hypotheses within and across empirical systems, accurate quantitative prediction would require additional empirical detail and data for model parameterisation.
 
-General predictions concerning inbreeding avoidance and polyandry
+General hypotheses concerning inbreeding avoidance and polyandry
 -------------------------------------------------------------------
@@
 Post-copulatory inbreeding avoidance cannot be effectively realised if females are not polyandrous in any form, and is likely to be most effective for highly polyandrous females that can bias fertilisation amongst sperm contributed by multiple mates.
-In contrast, pre-copulatory inbreeding avoidance mechanisms are most critical for females that mate only once and therefore have no post-copulatory opportunity to avoiding inbreeding.
+In contrast, pre-copulatory inbreeding avoidance mechanisms are most critical for females that mate only once and therefore have no post-copulatory opportunity to avoid inbreeding.
 This theory is borne out in our simulation results, as selection for, and consequent evolution of, post-copulatory inbreeding avoidance was negligible in populations where polyandry did not evolve, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C).
@@
 Further, pre-existence of fixed adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, precluded evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
-However, existence of fixed adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Figure 3A,B).
-In most populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
+However, pre-existence of fixed adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Figure 3A,B).
+In natural populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
 Rather, the timing of the invasion of adaptive inbreeding avoidance phenotypes will differ, so the initial evolution of one inbreeding strategy will likely occur in the absence of the other, or where selection for and subsequent evolution of the other strategy has already occurred.
@@
 
-To acheive our current objective of providing general conceptual comparison of the effects of direct costs across phenotypes, we modelled all costs as analogous increased probabilities of total reproductive failure, thereby facilitating direct comparison across traits.
+To achieve our current objective of providing general conceptual comparison of the effects of direct costs across phenotypes, we modelled all costs as analogous increased probabilities of total reproductive failure.
 This cost formulation reflects empirical observations in some populations [see Model; e.g., @Rowe1994; @Koga1998; @Gasparini2011], and is therefore a biologically realistic means of standardising costs across traits.
 However, different forms of costs could be incorporated into future models designed to predict evolutionary dynamics that might occur in specific systems.
-@Pomiankowski1987 identified four costs categories relevant to mating frequency and mate choice, including elevated risks of predation or disease transmission, and time or energey expenditure.
+Models could then be further developed such that costs arise from explicit reproductive mechanisms, requiring further biological detail.
+
+For example, @Pomiankowski1987 identified four costs categories relevant to mating frequency and mate choice, including elevated risks of predation or disease transmission, and time or energey expenditure.
 For example, polyandrous females might experience increased risk of disease transmission [@Roberts2015].
@@
 Polyandrous females might also risk harm caused by sexual conflict over multiple mating [e.g., @Arnqvist2005; @Parker2006].
-Inbreeding theory predicts that males should be more tolerant of inbreeding females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
-Future models could therefore explicitly consider sexual conflict over both polyandry and inbreeding, and hence capture internally-consistent mechanistic costs.
-
-<!--- TODO: Edit first sentence --->
-Models could then be further developed such that costs arise from explicit reproductive mechanisms, requiring further biological detail.
-Recent studies have elucidated key mechanisms of post-copulatory inbreeding avoidance.
+Inbreeding theory predicts that males should be more tolerant of inbreeding than females, leading to sexual conflict over inbreeding in mating encounters [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a].
+Future models could therefore explicitly consider sexual conflict over both polyandry and pre-copulatory inbreeding, and hence capture internally-consistent mechanistic costs.
+Further, sexual conflict might also affect post-copulatory inbreeding.
 For example, when female guppies (*Poecilia reticulata*) were artificially inseminated with equal quantitites of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full sibling's sperm were reduced by females' ovarian fluids [@Gasparini2011].
@@
 
-<!--- TODO: Edit first sentence ---> 
-We restricted our model to simulate how evolution of traits were affected by their direct costs and indirect benefits due to inbreeding avoidance.
-Although empirical populations will include additional beneficial traits that might affect evolution of mating strategies, targeting our focus on traits affecting inbreeding and polyandry allows us to better isolate their effects and therefore better develop hypotheses for natural systems.
+We restricted our model to simulate how evolution of traits was affected by their direct costs and indirect benefits due to inbreeding avoidance.
+Although natural populations will include additional beneficial traits that might affect evolution of mating strategies, targeting our focus on traits affecting inbreeding and polyandry allows us to better isolate their effects and therefore better develop general hypotheses.
+Future models could be further developed to include additional benefits and costs of reproductive strategies, and benefit and cost values could be parameterised using data from empirical populations, hence facilitating more quantitative predictions for specific systems.
+The addition of such mechanistic detail, and the inclusion of data from populations of interest to parameterise model extensions, could ultimately improve understanding and prediction of reproductive strategy evolution and thereby link theory, modelling, and empirical hypothesis testing.
 

### 2017-07-28 ms_pre_post.Rmd
Minor edits

@@
 In black field crickets (*Teleogryllus commodus*), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs [@Bussiere2006; @Tuni2013].
+Model extensions might therefore incorporate such post-copulatory sexual conflict to better understand female and male reproductive strategy evolution.
 
@@
 Although natural populations will include additional beneficial traits that might affect evolution of mating strategies, targeting our focus on traits affecting inbreeding and polyandry allows us to better isolate their effects and therefore better develop general hypotheses.
-Future models could be further developed to include additional benefits and costs of reproductive strategies, and benefit and cost values could be parameterised using data from empirical populations, hence facilitating more quantitative predictions for specific systems.
+Future models could be further developed to include additional benefits and costs of reproductive strategies, and benefit and cost values could be parameterised using data from empirical populations, hence enabling more quantitative predictions for specific systems.
 The addition of such mechanistic detail, and the inclusion of data from populations of interest to parameterise model extensions, could ultimately improve understanding and prediction of reproductive strategy evolution and thereby link theory, modelling, and empirical hypothesis testing.

### 2017-08-01 ms_pre_post.Rmd
Minor edits to Discussion

@@
 
-Evolution of different reproductive strategies cannot be presumed to occur in isolation from each other.
-Rather, there is likely to be considerable potential for feedbacks and degeneracy (i.e., functional redundancy) among multiple interacting phenotypes.
-For example, inbreeding avoidance could be manifested through both pre-copulatory and post-copulatory mechanisms and associated polyandry, meaning that simultaneous evolution of each phenotype might be defined by degeneracy in addition to trait-specific costs.
+Evolution of different reproductive strategies cannot be presumed to occur in isolation from one another.
+Rather, there is likely to be considerable potential for feedbacks and degeneracy (i.e., functional redundancy) among interacting phenotypes.
+For example, inbreeding avoidance could be manifested through both pre-copulatory and post-copulatory mechanisms and associated polyandry, meaning that simultaneous evolution of each phenotype might be affected by degeneracy, in addition to trait-specific benefits and costs.
 
@@
 Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information Figure S11).
-In addition to initial polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back effect that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).
+In addition to initial polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feedback effect that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).
 It would therefore be interesting to test the hypothesis that, across taxa, the occurrence of post-copulatory inbreeding avoidance covaries positively, and the occurrence of pre-copulatory inbreeding avoidance covaries negatively, with the degree of polyandry.
@@
 The opportunity to adjust inbreeding is widely suggested to be a driver of adaptive evolution of polyandry [@Tregenza2002; @Foerster2003; @Akcay2007; @Varian-Ramos2012; @Kingma2013; @Lehtonen2015; @Reid2014].
-Our model and simulations show that when post-copulatory inbreeding avoidance could evolve, selection for and resulting evolution of polyandry was greatly strengthened (Figure 1).
+Our simulations show that when post-copulatory inbreeding avoidance could evolve, selection for and resulting evolution of polyandry was greatly strengthened (Figure 1).
 The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but our model clarifies this verbal hypothesis and therefore has widespread implications for future studies of polyandry evolution.
@@
 One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population (Figure 3).
-Hence, our model demonstrates that degenerate inbreeding avoidance strategies can interact with one another, and implies that such interactions should be considered when developing hypotheses concerning reproductive strategy within and across systems.
+Hence, our model demonstrates degeneracy between inbreeding avoidance strategies, and implies that such interactions should be considered when developing hypotheses concerning reproductive strategy within and across systems.
 In particular, indefinite persistence of both pre-copulatory and post-copulatory inbreeding avoidance should not be expected in populations given a sufficiently large and sustained cost asymmetry.
@@
 Rather, the timing of the invasion of adaptive inbreeding avoidance phenotypes will differ, so the initial evolution of one inbreeding strategy will likely occur in the absence of the other, or where selection for and subsequent evolution of the other strategy has already occurred.
-When framing hypotheses for existence of post-copulatory inbreeding avoidance and polyandry, it might therefore be necessary to consider whether or not inbreeding avoidance already occurs through pre-copulatory mate choice.
+When framing hypotheses for existence of post-copulatory inbreeding avoidance and polyandry, it might therefore be necessary to consider whether or not inbreeding avoidance is already known to occur through pre-copulatory mate choice.
 Additionally, the opportunity for post-copulatory inbreeding avoidance will also depend on the degree to which females are polyandrous.
@@
 
-To achieve our current objective of providing general conceptual comparison of the effects of direct costs across phenotypes, we modelled all costs as analogous increased probabilities of total reproductive failure.
+To provide a general conceptual comparison of the effects of direct costs across phenotypes, we modelled all costs as analogous increased probabilities of total reproductive failure.
 This cost formulation reflects empirical observations in some populations [see Model; e.g., @Rowe1994; @Koga1998; @Gasparini2011], and is therefore a biologically realistic means of standardising costs across traits.
@@
 
-For example, @Pomiankowski1987 identified four costs categories relevant to mating frequency and mate choice, including elevated risks of predation or disease transmission, and time or energey expenditure.
-For example, polyandrous females might experience increased risk of disease transmission [@Roberts2015].
-This cost would more realistically apply to a female's realised number of mates rather than her tendency for polyandry.
+For example, @Pomiankowski1987 identified four cost categories relevant to mating frequency and mate choice, including elevated risks of predation or disease transmission, and time or energy expenditure.
+Polyandrous females might experience increased risk of disease transmission [@Roberts2015], a cost that would more realistically apply to a female's realised number of mates rather than her tendency for polyandry.
 Polyandrous females might also risk harm caused by sexual conflict over multiple mating [e.g., @Arnqvist2005; @Parker2006].
@@
 
-We restricted our model to simulate how evolution of traits was affected by their direct costs and indirect benefits due to inbreeding avoidance.
+We restricted our model to simulate how evolution of traits was affected by direct costs and indirect benefits due to inbreeding avoidance.
 Although natural populations will include additional beneficial traits that might affect evolution of mating strategies, targeting our focus on traits affecting inbreeding and polyandry allows us to better isolate their effects and therefore better develop general hypotheses.

### 2017-08-02 analysis.R
Add new analysis for relative costs

@@ -1907,11 +1907,10 @@ dev.off();
 
 
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
-# XXX SUPPORTING INFORMATION ADDRESSING REVIEWER COST COMMENT XXX #
+# XXX SI ADDRESSING REVIEWER COST COMMENT (Costs 01 & 02)     XXX #
 # XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
-
 setEPS(); # postscript below for final publication?
-cairo_ps("figures/rel_costs_01.eps",family="Arial",height=6,width=5.5);
+cairo_ps("figures/rel_costs_01_02.eps",family="Arial",height=6,width=5.5);
 par(mfrow=c(2,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
 # ------------------------------------------------------------------------#
 evo_cc_02 <- read.table(file="results/fig2/evo_M02_P00_Ff0.txt", header=FALSE);
@@ -2166,3 +2165,162 @@ dev.off();
 
 
 
+
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+# XXX SI ADDRESSING REVIEWER COST COMMENT (Costs 01 & 03)     XXX #
+# XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX #
+setEPS(); # postscript below for final publication?
+cairo_ps("figures/rel_costs_01_03.eps",family="Arial",height=6,width=5.5);
+par(mfrow=c(2,2),oma=c(5,5,1,1), mar=c(0.5,0.5,0.5,0.5));
+# ------------------------------------------------------------------------#
+evo_cc_02 <- read.table(file="results/fig2/evo_M03_P00_Ff0.txt", header=FALSE);
+evB <- evo_cc_02[evo_cc_02[,3]==0.03 & evo_cc_02[,4]==0 & evo_cc_02[,5]==0.01,];
+evo <- evB[evB[,2]==beta_val,]; 
+mWP <- tapply(X=evo[,7],INDEX=evo[,6],FUN=mean);
[…]

### 2017-08-02 analysis.R
Minor edits fixing file links

@@ -2257,7 +2257,7 @@ xxx <- tapply(X=evo[,6],INDEX=evo[,6],FUN=mean);
 len <- dim(evo)[1];
 plot(x=xxx,y=mWP,type="n",lwd=2,ylim=c(-24,14),col="blue",xaxt="n",yaxt="n",
      xlab="",ylab="",cex.lab=2,cex.axis=1.5);
-points(x=xxx,y=mPO,type="l",lwd=2,col="red");
+points(x=xxx,y=mPO,type="l",lwd=2,col="red"g);
 points(x=xxx,y=mEP,type="l",lwd=2,col="black");
 uWP <- mWP + sWP / sqrt(sum(evo[,6]==gens));
 lWP <- mWP - sWP / sqrt(sum(evo[,6]==gens));

### 2017-08-02 Supplement.tex
Commit multiple files for revision
Add positions for key SI figures
Minor edits fixing file links
Add captions to new SI figures

@@
 %\lhead{DUTHIE ET AL}
-\rhead{PRE- \& POST-COPULATORY (SUPPLEMENT)}
+\lhead{PRE- AND POST-COPULATORY INBREEDING AVOIDANCE (SUPPLEMENT)}
 \renewcommand{\headrulewidth}{0pt}
@@
 \begin{center}				
+\includegraphics[scale=0.8]{figures/rel_costs_01_03.png}
+\end{center}
+\caption{Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.03$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve but is less costly ($c_{F} = 0.01$), and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.03$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve but is less costly ($c_{M} = 0.01$).
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.
+In all panels, polyandry is cost free.
+Overall, costly pre-copulatory and post-copulatory inbreeding strategy allele values become less negative (i.e., closer to zero, indicating reduced inbreeding avoidance) over generations given the co-occurence of a less costly inbreeding strategy.}
+\label{rel_costs_01_03}
+\end{figure}
+
+\clearpage
+\begin{figure}
+\begin{center}				
+\includegraphics[scale=0.8]{figures/rel_costs_01_02.png}
+\end{center}
+\caption{Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve but is less costly ($c_{F} = 0.01$), and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve but is less costly ($c_{M} = 0.01$).
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.
+In all panels, polyandry is cost free.
+Overall, costly pre-copulatory and post-copulatory inbreeding strategy allele values become less negative (i.e., closer to zero, indicating reduced inbreeding avoidance) over generations given the co-occurence of a less costly inbreeding strategy.}
+\label{rel_costs_01_02}
+\end{figure}
+
+\clearpage
+\begin{figure}
+\begin{center}				
 \includegraphics[scale=0.82]{figures/evo_combs.png}

### 2017-08-02 ms_pre_post.Rmd
Add Jennions reference

@@
 Selection for post-copulatory inbreeding avoidance, but not for pre-copulatory inbreeding avoidance, requires polyandry, while interactions between pre-copulatory and post-copulatory inbreeding avoidance might cause functional redundancy (i.e., 'degeneracy') potentially generating complex evolutionary dynamics among inbreeding strategies and polyandry.
-We use individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression and different evolutionary constraints and direct costs.
-We find that evolution of post-copulatory inbreeding avoidance increases selection for initially rare polyandry, and that evolution of a costly inbreeding avoidance strategy became negligible over time given a lower cost alternative strategy.
+We used individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression and different evolutionary constraints and direct costs.
+We found that evolution of post-copulatory inbreeding avoidance increased selection for initially rare polyandry, and that evolution of a costly inbreeding avoidance strategy became negligible over time given a lower cost alternative strategy.
 Further, fixed pre-copulatory inbreeding avoidance often completely precluded evolution of polyandry and hence post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance.
@@
 Our simulations show that when post-copulatory inbreeding avoidance could evolve, selection for and resulting evolution of polyandry was greatly strengthened (Figure 1).
-The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997], but our model clarifies this verbal hypothesis and therefore has widespread implications for future studies of polyandry evolution.
+The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new [e.g., @Zeh1997; @Jennions2000], but our model clarifies this verbal hypothesis and therefore has widespread implications for future studies of polyandry evolution.
 

### 2017-08-02 ms_pre_post.Rmd
Fix purple-crown fairy wren incorrect reference

@@
 Inbreeding, defined as reproduction between relatives, often greatly reduces the fitness of resulting inbred offspring [termed 'inbreeding depression'; @Charlesworth1999; @Keller2002; @Charlesworth2009].
-Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple interacting reproductive strategies [@Parker1979; @Parker2006; @Pusey1996; @Szulkin2012].
+Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple reproductive strategies [@Parker1979; @Parker2006; @Pusey1996; @Szulkin2012].
 
@@
 However, few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
-Among these studies, pre-copulatory inbreeding avoidance has been reported in sweet potato weevils [*Cylas formicarius*, @Kuriwada2011], purple-crowned fairy-wrens [*Malurus coronatus*, @Kuriwada2011], and squinting bush brown butterflies [*Bicyclus anynana*, @Fischer2015], while post-copulatory inbreeding avoidance has been reported in, for example, red junglefowl [*Gallus gallus*, @Pizzari2004] and crickets [*Teleogryllus oceanicus*, @Simmons2006; *Gryllus bimaculatus*, @Bretman2009].
+Among these studies, pre-copulatory inbreeding avoidance has been reported in sweet potato weevils [*Cylas formicarius*, @Kuriwada2011], purple-crowned fairy-wrens [*Malurus coronatus*, @Kingma2013], and squinting bush brown butterflies [*Bicyclus anynana*, @Fischer2015], while post-copulatory inbreeding avoidance has been reported in, for example, red junglefowl [*Gallus gallus*, @Pizzari2004] and crickets [*Teleogryllus oceanicus*, @Simmons2006; *Gryllus bimaculatus*, @Bretman2009].
 Evidence for both pre-copulatory and post-copulatory inbreeding avoidance is available across different studies of Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015].

### 2017-08-02 ms_pre_post.Rmd
Tweaks to methods to make clearer

@@
 In the context of inbreeding as the postulated driver of reproductive strategy evolution, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will be affected not only by the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also by the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
-Empirical studies on diverse systems have demonstrated diverse costs of mating and mate choice, for example, including energetic costs of developing, maintaining, or enacting necessary physiologies [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b]; increased risks of predation or disease stemming from increased mate-searching or mating [e.g., @Rowe1988; @Ronkainen1994; @Koga1998]; increased risk of complete mating or fertilisation failure given extreme choosiness [@Kokko2013]; and risks of harm stemming from sexual conflict over fertilisation [e.g., @Rowe1994].
+Empirical studies have demonstrated diverse costs of mating and mate choice, for example, including energetic costs of developing, maintaining, or enacting necessary physiologies [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b]; increased risks of predation or disease stemming from increased mate-searching or mating [e.g., @Rowe1988; @Ronkainen1994; @Koga1998]; increased risk of complete mating or fertilisation failure given extreme choosiness [@Kokko2013]; and risks of harm stemming from sexual conflict over fertilisation [e.g., @Rowe1994].
 If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly strategy might go extinct, especially if their effects become redundant following evolution of the less costly strategy.
@@
 By allowing costs of the three strategies to be directly and independently controlled, our model facilitates direct comparison of evolution of pre-copulatory versus post-copulatory inbreeding avoidance given known cost asymmetries.
-Such costs on female survival probably are biologically reasonable.
+Such costs on female survival probability are biologically reasonable.
 For example, polyandrous females that undertake increased mate searching or mating can experience increased predation risk [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
 Females that express pre-copulatory choice can increase the risk of mortality due to harm caused by sexual conflict over mating, and also risk complete mating failure [which equates to pre-reproductive mortality in semelparous organisms; @Rowe1994; @Kokko2013].
-Finally, females that express post-copulatory choice can pay up-front energetic costs, and associated trade-offs with survival, due to developing physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014].
+Finally, females that express post-copulatory choice can pay up-front energetic costs, which might result in trade-offs with survival due to developing physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014].
 
@@
 Previous modelling using similar genetic architecture suggests that a cost of $0.02$ imposes strong but not overwhelming direct negative selection on polyandry [@Duthie].
-This value is therefore appropriate to illustrate the different evolutionary consequences that could result from asymmetrical costs (see Supporting Information).
+This value is therefore appropriate to illustrate the different evolutionary consequences that could result from asymmetrical costs (see Supporting Information for additional cost value combinations).
 

### 2017-08-03 Supplement.tex
Rescale new figures
Add revised table of contents and SI abstract

@@
 Figures S\ref{SI_M00_P00_E00}-S\ref{SI_M02_P02_E02} show the dynamics of individual replicate simulations for all trait cost combinations of \bm{$0$} and \bm{$0.02$}; these figures also show correlations of mean allele values among replicates.
+Figures S\ref{rel_costs_01_03} and S\ref{rel_costs_01_02} show cost asymmetry simulations that do not appear in the main text.
 Figure S\ref{allcombs} summarises trajectories of allele values across replicate simulations for all cost combinations of \bm{$0$} and \bm{$0.02$} for polyandry (\bm{$c_{P}$}), pre-copulatory inbreeding strategy (\bm{$c_{M}$}), and post-copulatory inbreeding strategy (\bm{$c_{F}$}).
@@
 \contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P02_E02}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0.02$}}}{S10}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{allcombs}: All cost combinations}}{S11}
-\contentsline {section}{\tocsection {}{}{\small Figure S\ref{extra_MfPf}: Dynamic \bm{$F_{a}$}, fixed \bm{$P_{a}=1$} and \bm{$M_{a}=-10$}}}{S12}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{rel_costs_01_03}: Relative cost asymmetries \bm{$0.01$} \& \bm{$0.03$} }}{S11}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{rel_costs_01_02}: Relative cost asymmetries \bm{$0.01$} \& \bm{$0.02$}}}{S12}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{allcombs}: All cost combinations}}{S13}
+\contentsline {section}{\tocsection {}{}{\small Figure S\ref{extra_MfPf}: Dynamic \bm{$F_{a}$}, fixed \bm{$P_{a}=1$} and \bm{$M_{a}=-10$}}}{S14}
 
@@
 \begin{center}				
-\includegraphics[scale=0.8]{figures/rel_costs_01_03.png}
+\includegraphics[scale=1.0]{figures/rel_costs_01_03.png}
 \end{center}
@@
 \begin{center}				
-\includegraphics[scale=0.8]{figures/rel_costs_01_02.png}
+\includegraphics[scale=1.0]{figures/rel_costs_01_02.png}
 \end{center}

### 2017-08-03 ms_pre_post.Rmd
Fix date

@@
 author: ''
-date: "21 July 2017"
+date: "3 August 2017"
 output:

### 2017-08-08 ms_pre_post.Rmd
Minor changes

@@
 
-In the context of inbreeding as the postulated driver of reproductive strategy evolution, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will be affected not only by the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also by the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
+In the context of inbreeding avoidance as a key hypothesised driver of reproductive strategy evolution, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will be affected not only by the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also by the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
 Empirical studies have demonstrated diverse costs of mating and mate choice, for example, including energetic costs of developing, maintaining, or enacting necessary physiologies [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b]; increased risks of predation or disease stemming from increased mate-searching or mating [e.g., @Rowe1988; @Ronkainen1994; @Koga1998]; increased risk of complete mating or fertilisation failure given extreme choosiness [@Kokko2013]; and risks of harm stemming from sexual conflict over fertilisation [e.g., @Rowe1994].
@@
 Third, how is selection for initially rare pre-copulatory or post-copulatory inbreeding avoidance affected if the other strategy of inbreeding avoidance is already fixed?
-To address each question, we isolate the effect of the biological mechanism of interest (i.e., post-copulatory inbreeding avoidance, cost asymmetry, and strategy pre-existence, respectively) by comparing simulations with the mechanism present versus absent with otherwise identical parameter values and conditions.
+To address these questions, our model is designed to allow each biological mechanism of interest (i.e., post-copulatory inbreeding avoidance, cost asymmetry, and strategy pre-existence, respectively) to be isolated, thereby facilitating direct comparison of simulations with the mechanism present versus absent with otherwise identical parameter values and conditions.
 We thereby illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
@@
 
-Phenotypic values of the three reproductive strategy traits each incur set costs that combine independently to increase the probability that a focal female will die before mating.
+Phenotypic values of the three reproductive strategy traits each incur set costs that combine to independently increase the probability that a focal female will die before mating.
 Numerous forms and mechanisms of direct costs of reproductive strategies could potentially be hypothesised and modelled; the most appropriate formulation depends on the question posed (see Discussion).
@@
 Previous modelling using similar genetic architecture suggests that a cost of $0.02$ imposes strong but not overwhelming direct negative selection on polyandry [@Duthie].
-This value is therefore appropriate to illustrate the different evolutionary consequences that could result from asymmetrical costs (see Supporting Information for additional cost value combinations).
+This value is therefore appropriate to illustrate the different evolutionary consequences that could result from asymmetrical costs, but simulations with additional cost value combinations are provided in Supporting Information.
 
@@
 This is because $M_{a}$ values became negative over generations, meaning that females typically avoided inbreeding through their initial mating (blue lines, Figure 1A,C,E,G).
-Polyandrous females that subsequently sampled more males from the available population were consequently more likely to mate with some relatives and hence produce some inbred offspring with low viability [@Duthie].
+Polyandrous females that subsequently sampled more males from the available population were consequently more likely to mate with some relatives and hence produce some inbred offspring with low viability [see also @Duthie].
 
@@
 
-Evolution of different reproductive strategies cannot be presumed to occur in isolation from one another.
+Different reproductive strategies cannot be presumed to evolve in isolation from one another.
 Rather, there is likely to be considerable potential for feedbacks and degeneracy (i.e., functional redundancy) among interacting phenotypes.
@@
 We used individual-based modelling to highlight fundamental but theoretically under-developed relationships between evolution of polyandry and pre-copulatory versus post-copulatory inbreeding strategy given (1) hard constraints on evolution of post-copulatory inbreeding strategy, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding strategy, and (3) evolution of one inbreeding strategy phenotype given pre-existence of the other.
-We present our model and simulation results as tools for thinking more clearly about the dynamics of simultaneously evolving reproductive strategies, not for making accurate quantitative predictions for any specific system.
-While the logic of our model can be usefully applied to construct general hypotheses within and across empirical systems, accurate quantitative prediction would require additional empirical detail and data for model parameterisation.
-
-General hypotheses concerning inbreeding avoidance and polyandry
--------------------------------------------------------------------
-
-Post-copulatory inbreeding avoidance cannot be effectively realised if females are not polyandrous in any form, and is likely to be most effective for highly polyandrous females that can bias fertilisation amongst sperm contributed by multiple mates.
-In contrast, pre-copulatory inbreeding avoidance mechanisms are most critical for females that mate only once and therefore have no post-copulatory opportunity to avoid inbreeding.
-This theory is borne out in our simulation results, as selection for, and consequent evolution of, post-copulatory inbreeding avoidance was negligible in populations where polyandry did not evolve, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C).
-Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information Figure S11).
-In addition to initial polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feedback effect that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).
-It would therefore be interesting to test the hypothesis that, across taxa, the occurrence of post-copulatory inbreeding avoidance covaries positively, and the occurrence of pre-copulatory inbreeding avoidance covaries negatively, with the degree of polyandry.
-To test this hypothesis, more work is needed to quantify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
-
-Degeneracy occurs at nearly all biological scales [@Edelman2001], including complex systems affecting organismal development [e.g., @Nowak1997], adaptation [@Whitacre2010; @Whitacre2010a], and cognition [@Price2002; @Park2013], as well as population [@Atamas2009], community [@Suraci2017], and ecosystem [e.g., @Levin2008] dynamics.
-In our model, degeneracy occurred through overlaps in how different reproductive strategies caused adaptive inbreeding avoidance.
-In general, degeneracy might increase biological robustness by fine-tuning degenerate phenotypes to different local environments [@Gardner2006; @Whitacre2010a].
-For example, degeneracy might ensure successful inbreeding avoidance through either pre-copulatory or post-copulatory mechanisms when avoidance through the other mechanism is ineffective (e.g., due to sexual conflict affecting mate choice or injury affecting fertilisation).
-However, evolution of one inbreeding avoidance mechanism might also weaken selection on the other by modifying the latter's impact on total realised inbreeding avoidance [*sensu* evolution of genetic redundancy; see @Nowak1997].
-The relevance of degeneracy with respect to such reproductive strategies therefore requires further theoretical development, which could result in new empirical predictions and conceptual synthesis across biological scales.
+Our current model and simulation results thereby provide tools for thinking more clearly about the dynamics of simultaneously evolving reproductive strategies in the context of polyandry and inbreeding avoidance.
 
@@
 
-Model assumptions and extensions
+General hypotheses concerning inbreeding avoidance and polyandry
 -------------------------------------------------------------------
 
-To provide a general conceptual comparison of the effects of direct costs across phenotypes, we modelled all costs as analogous increased probabilities of total reproductive failure.
-This cost formulation reflects empirical observations in some populations [see Model; e.g., @Rowe1994; @Koga1998; @Gasparini2011], and is therefore a biologically realistic means of standardising costs across traits.
-However, different forms of costs could be incorporated into future models designed to predict evolutionary dynamics that might occur in specific systems.
+Post-copulatory inbreeding avoidance cannot be effectively realised if females are not polyandrous in any form, and is likely to be most effective for highly polyandrous females that can bias fertilisation amongst sperm contributed by multiple mates.
+In contrast, pre-copulatory inbreeding avoidance mechanisms are most critical for females that mate only once and therefore have no post-copulatory opportunity to avoid inbreeding.
+This theory is borne out in our simulation results, as selection for, and consequent evolution of, post-copulatory inbreeding avoidance was negligible in populations where polyandry did not evolve, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C).
+Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information Figure S11).
+In addition to initial polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feedback effect that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).
+It would therefore be interesting to test the hypothesis that, across taxa, the occurrence of post-copulatory inbreeding avoidance covaries positively, and the occurrence of pre-copulatory inbreeding avoidance covaries negatively, with the degree of polyandry.
+To test this hypothesis, more work is needed to quantify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
+
+Degeneracy occurs at nearly all biological scales [@Edelman2001], including complex systems affecting organismal development [e.g., @Nowak1997], adaptation [@Whitacre2010; @Whitacre2010a], and cognition [@Price2002; @Park2013], as well as population [@Atamas2009], community [@Suraci2017], and ecosystem [e.g., @Levin2008] dynamics.
+In our model, degeneracy occurred through overlaps in how different reproductive strategies caused adaptive inbreeding avoidance.
+In general, degeneracy might increase biological robustness by fine-tuning degenerate phenotypes to different local environments [@Gardner2006; @Whitacre2010a].
+For example, degeneracy might ensure successful inbreeding avoidance through either pre-copulatory or post-copulatory mechanisms when avoidance through the other mechanism is ineffective (e.g., due to sexual conflict affecting mate choice or injury affecting fertilisation).
+However, evolution of one inbreeding avoidance mechanism might also weaken selection on the other by modifying the latter's impact on total realised inbreeding avoidance [*sensu* evolution of genetic redundancy; see @Nowak1997].
+The relevance of degeneracy with respect to such reproductive strategies therefore requires further theoretical development, which could result in new empirical predictions and conceptual synthesis across biological scales.
+
+Model structure, assumptions, and extensions
+-------------------------------------------------------------------
+
+While the logic of our current model can be usefully applied to construct general hypotheses within and across empirical systems, accurate quantitative prediction for specific systems would require additional empirical detail and data for model parameterisation.
+To facilitate general conceptual comparison of the effects of direct costs across phenotypes, we modelled all costs as analogous increased probabilities of female mortality and hence total reproductive failure.
+This cost formulation reflects empirical observations in some populations [see Model; e.g., @Rowe1994; @Koga1998; @Gasparini2011], and is therefore a biologically realistic method of standardising costs across traits.
+However, different forms of costs could be incorporated into future models designed to predict specific evolutionary dynamics.
 Models could then be further developed such that costs arise from explicit reproductive mechanisms, requiring further biological detail.
@@
 In black field crickets (*Teleogryllus commodus*), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs [@Bussiere2006; @Tuni2013].
-Model extensions might therefore incorporate such post-copulatory sexual conflict to better understand female and male reproductive strategy evolution.
+Future models could therefore explicitly incorporate such mechanisms in order to better understand effects of post-copulatory sexual conflict on female and male reproductive strategy evolution.
 
-We restricted our model to simulate how evolution of traits was affected by direct costs and indirect benefits due to inbreeding avoidance.
-Although natural populations will include additional beneficial traits that might affect evolution of mating strategies, targeting our focus on traits affecting inbreeding and polyandry allows us to better isolate their effects and therefore better develop general hypotheses.
-Future models could be further developed to include additional benefits and costs of reproductive strategies, and benefit and cost values could be parameterised using data from empirical populations, hence enabling more quantitative predictions for specific systems.
+We restricted our current model to examine how reproductive strategy evolution was affected by direct costs and indirect benefits stemming from inbreeding avoidance, thereby isolating such effects and explicitly addressing key general hypotheses regarding the effects of inbreeding depression.
+In natural populations, reproductive strategy evolution will also be affected by other costs and benefits, for example stemming from additive genetic effects (i.e., pre-copulatory or post-copulatory mate choice for 'good genes').
+Future modelling could consequently include multiple benefits and costs of reproductive strategies, which could then be parameterised using empirical data.
 The addition of such mechanistic detail, and the inclusion of data from populations of interest to parameterise model extensions, could ultimately improve understanding and prediction of reproductive strategy evolution and thereby link theory, modelling, and empirical hypothesis testing.

### 2017-08-08 ms_pre_post.Rmd
Additional minor comments -- ready to go, potentially

@@
 Strong inbreeding depression might drive initial evolution of both pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
-However, the co-occurrence of pre-copulatory and post-copulatory inbreeding avoidance might engender some degree of 'degeneracy', defined as a phenomenon by which different elements of a system result in identical outputs [@Edelman2001].
+However, the co-occurrence of pre-copulatory and post-copulatory inbreeding avoidance might cause some degree of 'degeneracy', defined as a phenomenon by which different elements of a system result in identical outputs [@Edelman2001].
 Consequently, if evolution of polyandry and post-copulatory inbreeding avoidance renders pre-copulatory inbreeding avoidance functionally redundant, or vice versa, then only one inbreeding avoidance strategy might be maintained in the long-term.
@@
 In natural populations, reproductive strategy evolution will also be affected by other costs and benefits, for example stemming from additive genetic effects (i.e., pre-copulatory or post-copulatory mate choice for 'good genes').
-Future modelling could consequently include multiple benefits and costs of reproductive strategies, which could then be parameterised using empirical data.
+Future investigations could consequently model multiple benefits and costs of reproductive strategies, and be parameterised using empirical data.
 The addition of such mechanistic detail, and the inclusion of data from populations of interest to parameterise model extensions, could ultimately improve understanding and prediction of reproductive strategy evolution and thereby link theory, modelling, and empirical hypothesis testing.

### 2017-08-10 Supplement.tex
Add more explanation (and earlier explanation) to figure legends

--- 2017-04-05 Supplement.tex
@@
 \begin{center}				
+\includegraphics[scale=0.9]{figures/rel_costs_01_03.png}
+\end{center}
+\caption{Additional simulations with asymmetric direct costs, which are comparable to Figure 3 of the main text.
+These supplemental simulations support the general conclusion that costly pre-copulatory and post-copulatory inbreeding strategy allele values become less negative (i.e., closer to zero, indicating reduced inbreeding avoidance) over generations given the co-occurence of a less costly inbreeding strategy.
+Values in this figure reflect the same amount of cost asymmetry between traits, but with both traits having non-zero direct costs.
+Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.03$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve but is less costly ($c_{F} = 0.01$), and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.03$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve but is less costly ($c_{M} = 0.01$).
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.
+In all panels, polyandry is cost free.}
+\label{rel_costs_01_03}
+\end{figure}
+
+\clearpage
+\begin{figure}
+\begin{center}				
+\includegraphics[scale=0.9]{figures/rel_costs_01_02.png}
+\end{center}
+\caption{Additional simulations with asymmetric direct costs, which are comparable to Figure 3 of the main text.
+These supplemental simulations support the general conclusion that costly pre-copulatory and post-copulatory inbreeding strategy allele values become less negative (i.e., closer to zero, indicating reduced inbreeding avoidance) over generations given the co-occurence of a less costly inbreeding strategy.
+Values in this figure reflect a smaller cost asymmetry between traits than simulated in the main text, with both traits having non-zero direct costs.
+Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve but is less costly ($c_{F} = 0.01$), and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve but is less costly ($c_{M} = 0.01$).
+Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
+Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.
+In all panels, polyandry is cost free.}
+\label{rel_costs_01_02}
+\end{figure}
+
+\clearpage
+\begin{figure}
+\begin{center}				
 \includegraphics[scale=0.82]{figures/evo_combs.png}

### 2017-08-10 ms_pre_post.Rmd
Introduction edits

@@
 
-In the context of inbreeding avoidance as a key hypothesised driver of reproductive strategy evolution, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will be affected not only by the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also by the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
+In the context of inbreeding depression as a key hypothesised driver of reproductive strategy evolution, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will be affected not only by the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also by the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
 Empirical studies have demonstrated diverse costs of mating and mate choice, for example, including energetic costs of developing, maintaining, or enacting necessary physiologies [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b]; increased risks of predation or disease stemming from increased mate-searching or mating [e.g., @Rowe1988; @Ronkainen1994; @Koga1998]; increased risk of complete mating or fertilisation failure given extreme choosiness [@Kokko2013]; and risks of harm stemming from sexual conflict over fertilisation [e.g., @Rowe1994].
 If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly strategy might go extinct, especially if their effects become redundant following evolution of the less costly strategy.
-Evolutionary dynamics will therefore depend on the inbreeding avoidance benefit of each strategy, which might also differ and vary in relation to the evolution of the other strategy.
-Dynamic models that track the frequencies of alleles underlying multiple potentially costly inbreeding avoidance strategies that might influence each other's evolution across generations, and that are enacted among relatives that themselves result from reproductive strategies and inbreeding depression expressed in previous generations, are consequently useful to understand and predict evolutionary outcomes.
+Dynamic models that track the frequencies of alleles underlying multiple, potentially interacting, inbreeding avoidance strategies that are enacted among relatives resulting from reproductive strategies and inbreeding depression expressed in previous generations, are consequently useful to understand and predict evolutionary outcomes.
 
 We use individual-based modelling to address three key questions regarding evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given opportunity for inbreeding and strong inbreeding depression.
-First, does evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance facilitate evolution of polyandry that is otherwise severely constrained by increasing relatedness of polyandrous females to their additional mates?
+First, does evolution of post-copulatory inbreeding avoidance, alongside pre-copulatory inbreeding avoidance, facilitate evolution of polyandry?
 Second, how do costs associated with polyandry and pre-copulatory and post-copulatory inbreeding avoidance affect evolutionary outcomes and, in particular, the long-term persistence of these reproductive strategies given cost asymmetry?
 Third, how is selection for initially rare pre-copulatory or post-copulatory inbreeding avoidance affected if the other strategy of inbreeding avoidance is already fixed?
-To address these questions, our model is designed to allow each biological mechanism of interest (i.e., post-copulatory inbreeding avoidance, cost asymmetry, and strategy pre-existence, respectively) to be isolated, thereby facilitating direct comparison of simulations with the mechanism present versus absent with otherwise identical parameter values and conditions.
+To address these questions, we designed our model to isolate the effect of the biological mechanism of interest (i.e., post-copulatory inbreeding avoidance, cost asymmetry, and strategy pre-existence, respectively) and allow comparison of simulations with the mechanism present versus absent with otherwise identical parameter values and conditions.
 We thereby illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.

### 2017-08-10 ms_pre_post.Rmd
Model section edits

@@
 
-We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply 'inbreeding strategies' because the model did not preclude evolution of inbreeding preference), in a small focal population of females and males by tracking the dynamics of alleles underlying reproductive strategies expressed by females.
+We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply 'inbreeding strategies' because the model did not preclude evolution of inbreeding preference), in a small focal population by tracking the dynamics of alleles underlying reproductive strategies expressed by females.
 We thereby track evolutionary dynamics given internally consistent patterns of relatedness caused by non-random mating and capture effects of mutation, gene flow, drift, and selection.
@@
 Complex traits such as reproductive strategies are likely to be polygenic [@Evans2008].
-Hence, we model individuals with 10 physically unlinked diploid loci (and therefore 20 alleles), underlying each of three reproductive strategy traits: tendency for polyandry ($P_{a}$, i.e., 'polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., 'mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., 'fertilisation' alleles).
-All individuals therefore have 30 diploid loci (and hence 60 alleles) in total, each of which can take the value of any real number [i.e., a continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014].
+Hence, we model individuals with 10 physically unlinked diploid loci (i.e., 20 alleles), underlying each of three reproductive strategy traits: tendency for polyandry ($P_{a}$, 'polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, 'mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, 'fertilisation' alleles).
+All individuals therefore have 30 diploid loci (i.e., 60 alleles) in total, each of which can take the value of any real number [continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014].
 
@@
 In contrast, individuals' phenotypic values for tendency for polyandry ($P_{p}$) cannot map directly onto their genotypic values ($P_{g}$) because $P_{g}$ can evolve to be negative, but females cannot mate with a negative number of additional males [e.g., @Shuker2007; @Evans2013].
-Rather, polyandry is more realistically considered as a "threshold trait", whereby continuous genotypic variation translates into expression of discrete phenotypic value(s) at some threshold [@Lynch1998; @Roff1996; @Roff1998; @Duthie].
+Rather, we considered polyandry "threshold trait", whereby continuous genotypic variation translates into expression of discrete phenotypic value(s) at some threshold [@Lynch1998; @Roff1996; @Roff1998; @Duthie].
 Accordingly, we allow individuals' phenotypic values for tendency for polyandry to equal genotypic values ($P_{p} = P_{g}$) if $P_{g} \geq 0$, but set $P_{p} = 0$ if $P_{g} < 0$.
@@
 Phenotypic values of the three reproductive strategy traits each incur set costs that combine to independently increase the probability that a focal female will die before mating.
-Numerous forms and mechanisms of direct costs of reproductive strategies could potentially be hypothesised and modelled; the most appropriate formulation depends on the question posed (see Discussion).
+Numerous forms and mechanisms of direct costs of reproductive strategies could be hypothesised and modelled; the most appropriate formulation depends on the question (see Discussion).
 By allowing costs of the three strategies to be directly and independently controlled, our model facilitates direct comparison of evolution of pre-copulatory versus post-copulatory inbreeding avoidance given known cost asymmetries.
-Such costs on female survival probability are biologically reasonable.
+Qualitatively, such costs on female survival probability are biologically reasonable.
 For example, polyandrous females that undertake increased mate searching or mating can experience increased predation risk [e.g., @Rowe1988; @Ronkainen1994; @Koga1998].
@@
 It also assumes that inbreeding does not covary with inbreeding load (i.e., no purging).
-This formulation ensures that the relationship between $k_{ij}$ and the magnitude of inbreeding depression in offspring is consistent across replicate simulations and is further justified because previous genetically-explicit modelling [@Duthie2016a] showed that inbreeding avoidance in biparental populations has a negligible effect on load given small-effect deleterious mutations [see also @Wang1999; @Guillaume2006].
+This formulation ensures that the relationship between $k_{ij}$ and the magnitude of inbreeding depression in offspring is consistent across replicate simulations.
+This choice, as opposed to a more mechanistic model of inbreeding depression that allows purging, is further justified because previous genetically-explicit modelling [@Duthie2016a] showed that inbreeding avoidance in biparental populations has a negligible effect on load given small-effect deleterious mutations [see also @Wang1999; @Guillaume2006].
+
 We model inbreeding depression as having an absolute rather than relative effect on offspring viability (i.e., hard rather than soft selection) so that the effect of $\beta$ is consistent across generations and different parameter combinations.
@@
 Previous modelling using similar genetic architecture suggests that a cost of $0.02$ imposes strong but not overwhelming direct negative selection on polyandry [@Duthie].
-This value is therefore appropriate to illustrate the different evolutionary consequences that could result from asymmetrical costs, but simulations with additional cost value combinations are provided in Supporting Information.
+This value is therefore appropriate to illustrate the different evolutionary consequences that could result from asymmetrical costs.
+Results from simulations with additional cost value combinations are provided in Supporting Information.
 
-To address how selection on an initially rare strategy of pre-copulatory or post-copulatory inbreeding avoidance, and resulting evolution, is affected by the other strategy of inbreeding avoidance already being fixed in the population, we first used exploratory simulations to quantify evolution of pre-copulatory inbreeding strategy, and of post-copulatory inbreeding strategy and associated polyandry, in isolation.
+To address how selection on an initially rare inbreeding avoidance strategy, and resulting evolution, is affected by the other strategy of inbreeding avoidance already being fixed in the population, we first used exploratory simulations to quantify evolution of pre-copulatory inbreeding strategy, and of post-copulatory inbreeding strategy and associated polyandry, in isolation.
 Then, to test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance were fixed, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., $F_{p}$ and $P_{p}$ were expressed but did not evolve further).

### 2017-08-10 ms_pre_post.Rmd
Minor wording tweaks

@@
 author: ''
-date: "3 August 2017"
+date: "10 August 2017"
 output:
@@
 We restricted our current model to examine how reproductive strategy evolution was affected by direct costs and indirect benefits stemming from inbreeding avoidance, thereby isolating such effects and explicitly addressing key general hypotheses regarding the effects of inbreeding depression.
-In natural populations, reproductive strategy evolution will also be affected by other costs and benefits, for example stemming from additive genetic effects (i.e., pre-copulatory or post-copulatory mate choice for 'good genes').
-Future investigations could consequently model multiple benefits and costs of reproductive strategies, and be parameterised using empirical data.
-The addition of such mechanistic detail, and the inclusion of data from populations of interest to parameterise model extensions, could ultimately improve understanding and prediction of reproductive strategy evolution and thereby link theory, modelling, and empirical hypothesis testing.
+In natural populations, reproductive strategy evolution will also be affected by other costs and benefits, for example, stemming from additive genetic effects (i.e., pre-copulatory or post-copulatory mate choice for 'good genes').
+Future investigations could consequently be to develop theory and models that include multiple benefits and costs of reproductive strategies, which could then be parameterised using empirical data.
+While good theory should always strive for conceptual clarity and the avoidance of unnecessary nuance [@Healy2017], the prudent use of multi-faceted mechanistic models could usefully link theory, modelling, and empirical hypothesis testing and thereby improve both general and specific understanding and prediction of reproductive strategy evolution.
 

### 2017-08-11 ms_pre_post.Rmd
Tweak for compiling

@@
 However, there is as yet no theory that predicts what combinations of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry should be favoured by selection when all can evolve.
-Consequently, there is no theory that allows the diversity of observed pre-copulatory and post-copulatory inbreeding avoidance strategies to be interpreted, and no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
+Consequently, there is no theory that allows the diversity of observed pre-copulatory and post-copulatory inbreeding avoidance strategies to be interpreted, and there are no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
 
@@
 If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly strategy might go extinct, especially if their effects become redundant following evolution of the less costly strategy.
-Dynamic models that track the frequencies of alleles underlying multiple, potentially interacting, inbreeding avoidance strategies that are enacted among relatives resulting from reproductive strategies and inbreeding depression expressed in previous generations, are consequently useful to understand and predict evolutionary outcomes.
+Dynamic models that track the frequencies of alleles underlying multiple, potentially interacting, inbreeding avoidance strategies that are enacted among relatives resulting from reproductive strategies and inbreeding depression expressed in previous generations are consequently useful to understand and predict evolutionary outcomes.
 

### 2017-08-11 ms_pre_post.Rmd
Remove Healy reference

@@
 Future investigations could consequently be to develop theory and models that include multiple benefits and costs of reproductive strategies, which could then be parameterised using empirical data.
-While good theory should always strive for conceptual clarity and the avoidance of unnecessary nuance [@Healy2017], the prudent use of multi-faceted mechanistic models could usefully link theory, modelling, and empirical hypothesis testing and thereby improve both general and specific understanding and prediction of reproductive strategy evolution.
+While good theory should always strive for conceptual clarity and the avoidance of unnecessary nuance, the prudent use of multi-faceted mechanistic models could usefully link theory, modelling, and empirical hypothesis testing and thereby improve both general and specific understanding and prediction of reproductive strategy evolution.
 

### 2017-08-15 ms_pre_post.Rmd
Minor edits

@@
 Third, how is selection for initially rare pre-copulatory or post-copulatory inbreeding avoidance affected if the other strategy of inbreeding avoidance is already fixed?
-To address these questions, we designed our model to isolate the effect of the biological mechanism of interest (i.e., post-copulatory inbreeding avoidance, cost asymmetry, and strategy pre-existence, respectively) and allow comparison of simulations with the mechanism present versus absent with otherwise identical parameter values and conditions.
+To address these questions, we designed our model to isolate the effect of each biological mechanism of interest (i.e., post-copulatory inbreeding avoidance, cost asymmetry, and strategy pre-existence, respectively) and hence to allow comparison of simulations with the mechanism present versus absent with otherwise identical parameter values and conditions.
 We thereby illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
@@
 It would therefore be interesting to test the hypothesis that, across taxa, the occurrence of post-copulatory inbreeding avoidance covaries positively, and the occurrence of pre-copulatory inbreeding avoidance covaries negatively, with the degree of polyandry.
-To test this hypothesis, more work is needed to quantify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
+To test this hypothesis, further empirical work is needed to quantify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
 
@@
 Future models could therefore explicitly consider sexual conflict over both polyandry and pre-copulatory inbreeding, and hence capture internally-consistent mechanistic costs.
-Further, sexual conflict might also affect post-copulatory inbreeding.
+Further, sexual conflict might also affect post-copulatory inbreeding avoidance.
 For example, when female guppies (*Poecilia reticulata*) were artificially inseminated with equal quantitites of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full sibling's sperm were reduced by females' ovarian fluids [@Gasparini2011].
@@
 In natural populations, reproductive strategy evolution will also be affected by other costs and benefits, for example, stemming from additive genetic effects (i.e., pre-copulatory or post-copulatory mate choice for 'good genes').
-Future investigations could consequently be to develop theory and models that include multiple benefits and costs of reproductive strategies, which could then be parameterised using empirical data.
+Future objectives could consequently be to develop theory and models that include multiple benefits and costs of reproductive strategies, which could then be parameterised using empirical data.
 While good theory should always strive for conceptual clarity and the avoidance of unnecessary nuance, the prudent use of multi-faceted mechanistic models could usefully link theory, modelling, and empirical hypothesis testing and thereby improve both general and specific understanding and prediction of reproductive strategy evolution.

### 2017-08-15 pre_post_biorxiv.tex
Small changes to pre-print
Edits through Introduction

@@
 {\LARGE
-\textbf\newline{Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry}
+\textbf\newline{Evolution of pre-copulatory and post-copulatory strategies of inbreeding avoidance and associated polyandry}
 }
@@
 However, surprisingly little theory or modelling critically examines selection for pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, given evolutionary constraints and direct costs, or examines how evolution of inbreeding avoidance strategies might feed back to affect evolution of polyandry.
-Selection for post-copulatory inbreeding avoidance, but not for pre-copulatory inbreeding avoidance, requires polyandry, while interactions between pre-copulatory and post-copulatory inbreeding avoidance might cause functional redundancy (i.e., `degeneracy') potentially generating complex evolutionary dynamics among inbreeding strategies and polyandry.
-We use individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression and different evolutionary constraints and direct costs.
-We find that evolution of post-copulatory inbreeding avoidance increases selection for initially rare polyandry, and that selection for a costly inbreeding avoidance strategy was weak or negligible given a cost free alternative strategy.
+Selection for post-copulatory inbreeding avoidance, but not for pre-copulatory inbreeding avoidance, requires polyandry, while interactions between pre-copulatory and post-copulatory inbreeding avoidance might cause functional redundancy (i.e., 'degeneracy') potentially generating complex evolutionary dynamics among inbreeding strategies and polyandry.
+We used individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression and different evolutionary constraints and direct costs.
+We found that evolution of post-copulatory inbreeding avoidance increased selection for initially rare polyandry, and that evolution of a costly inbreeding avoidance strategy became negligible over time given a lower cost alternative strategy.
 Further, fixed pre-copulatory inbreeding avoidance often completely precluded evolution of polyandry and hence post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance.
@@
 Inbreeding, defined as reproduction between relatives, often greatly reduces the fitness of resulting inbred offspring \cite[termed `inbreeding depression';][]{Charlesworth1999, Keller2002, Charlesworth2009}.
-Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple interacting reproductive strategies \cite[][]{Parker1979, Parker2006, Pusey1996, Szulkin2012}.
-
-From the perspective of a breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance).
-Evolution of such post-copulatory inbreeding avoidance is likely to be facilitated when females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout \cite[but see][]{Dougherty2016}.
-Such polyandry might itself be under selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative.
-Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm provided by females' mates (i.e., under conditions of a `fair raffle').
-Overall, polyandry can therefore simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
-Polyandry has consequently been widely hypothesised to allow females to avoid inbreeding and thereby increase offspring fitness \cite[][]{Zeh1997, Jennions2000, Tregenza2002}.
-Resulting indirect selection on polyandry that stems from the increase in offspring fitness could explain evolution of polyandry in cases where multiple mating does not increase female reproductive success, or even reduces reproductive success and therefore imposes direct costs on polyandrous females.
-However, despite such widely-invoked hypotheses regarding the role of inbreeding depression in driving pre-copulatory and post-copulatory strategies and polyandry, there is surprisingly little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.
+Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple reproductive strategies \cite[][]{Parker1979, Parker2006, Pusey1996, Szulkin2012}.
+
+From a female's perspective, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males following mating (i.e., post-copulatory inbreeding avoidance).
+Evolution of post-copulatory inbreeding avoidance is likely to be facilitated when females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout \cite[but see][]{Dougherty2016}.
+Further, such polyandry might itself evolve because it allows females to mate with additional unrelated males following an initial mating with a relative, potentially including males that were unavailable for initial mate choice \cite[e.g.,][]{Reid2015, Duthie}.
+Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm (i.e., under conditions of a `fair raffle').
+
+Overall, polyandry can therefore simultaneously allow females to mate with less closely related males and create opportunity for further inbreeding avoidance enacted through active post-copulatory choice.
+Indirect selection on polyandry resulting from reduced inbreeding depression in offspring fitness could help explain evolution of polyandry in cases where multiple mating decreases female reproductive success, imposing a direct cost on polyandrous females \cite[][]{Zeh1997, Jennions2000, Tregenza2002}.
+However, despite such widely-invoked hypotheses, there is surprisingly little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how evolution of such strategies might feed back to affect underlying evolution of polyandry.
+Comprehensive understanding of evolution of reproductive strategies given inbreeding depression requires consideration of the fundamental joint effects of selection on pre-copulatory and post-copulatory inbreeding avoidance and polyandry.
 
 Despite the paucity of theory, numerous empirical studies on diverse species have tested for, and in some cases found evidence of, female inbreeding avoidance in systems where polyandry also occurs \cite[][but see \citealt{Reid2015a}]{Tregenza2002, Varian-Ramos2012, Kingma2013, Arct2015}.
-However, relatively few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
-Pre-copulatory inbreeding avoidance has been reported in diverse species, spanning sweet potato weevils \cite[\textit{Cylas formicarius};][]{Kuriwada2011}, purple-crowned fairy-wrens \cite[\textit{Malurus coronatus};][]{Kuriwada2011}, and squinting bush brown butterflies \cite[\textit{Bicyclus anynana};][]{Fischer2015}, while post-copulatory inbreeding avoidance has been reported in red junglefowl \cite[\textit{Gallus gallus};][]{Pizzari2004} and crickets \cite[\textit{Teleogryllus oceanicus}, \textit{Gryllus bimaculatus};][]{Simmons2006, Bretman2009}.
+However, few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms.
+Among these studies, pre-copulatory inbreeding avoidance has been reported in sweet potato weevils \cite[\textit{Cylas formicarius};][]{Kuriwada2011}, purple-crowned fairy-wrens \cite[\textit{Malurus coronatus};][]{Kuriwada2011}, and squinting bush brown butterflies \cite[\textit{Bicyclus anynana};][]{Fischer2015}, while post-copulatory inbreeding avoidance has been reported in, for example, red junglefowl \cite[\textit{Gallus gallus};][]{Pizzari2004} and crickets \cite[\textit{Teleogryllus oceanicus}, \textit{Gryllus bimaculatus};][]{Simmons2006, Bretman2009}.
 Evidence for both pre-copulatory and post-copulatory inbreeding avoidance is available across different studies of Trinidadian guppies \cite[\textit{Poecilia reticulata};][]{Gasparini2011, Daniel2015} and house mice \cite[\textit{Mus domesticus};][]{Potts1991, Firman2015}.
@@
 However, there is as yet no theory that predicts what combinations of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry should be favoured by selection when all can evolve.
-Consequently, there is no theory that allows the diversity of observed pre-copulatory and post-copulatory inbreeding avoidance strategies to be interpreted, and no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
-
-\cite{Duthie} used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve due to selection stemming from pre-copulatory inbreeding avoidance in the absence of any post-copulatory inbreeding avoidance.
-Net selection for polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., `costs') on polyandry was weak, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate \cite[][]{Duthie}.
-Without these conditions, increasing polyandry tended to increase rather than decrease the overall degree of inbreeding that females experienced, and hence reduce offspring fitness.
-This occurred because, once pre-copulatory inbreeding avoidance evolved, polyandrous females had already chosen available unrelated males as their initial mates.
+Consequently, there is no theory that allows the diversity of observed pre-copulatory and post-copulatory inbreeding avoidance strategies to be interpreted, and there are no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.
+
+In one first step, \cite{Duthie} used a genetically-explicit individual-based model to examine conditions under which polyandry is predicted to evolve due to selection stemming from pre-copulatory inbreeding avoidance in the absence of post-copulatory inbreeding avoidance.
+Simulations showed that even when selection for pre-copulatory inbreeding avoidance was strong and females consequently preferred unrelated mates, selection for polyandry specifically to facilitate this inbreeding avoidance occurred only under highly restricted conditions.
+Key requirements were that direct negative selection (i.e., `costs') on polyandry was weak, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate \cite[][]{Duthie}.
+Without these conditions, polyandrous females tended to increase rather than decrease their overall degree of inbreeding, ultimately reducing offspring fitness.
+This increase occurred because, once pre-copulatory inbreeding avoidance evolved, polyandrous females had already chosen available unrelated males as their initial mates.
 Their additional mates, chosen from the remaining male population, were therefore increasingly likely to include relatives.
-Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance, and hence the resulting degree of inbreeding avoidance, was consequently restricted \cite[][]{Duthie}.
-
-However, if post-copulatory inbreeding avoidance could also evolve, polyandrous females would have the opportunity to bias paternity towards unrelated males within their set of chosen mates.
+Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance was consequently restricted \cite[][]{Duthie}.
+
+However, if post-copulatory inbreeding avoidance could evolve alongside pre-copulatory inbreeding avoidance, then polyandrous females could bias fertilisation towards unrelated males within their set of mates.
 Evolution of post-copulatory inbreeding avoidance might consequently reduce the cost of polyandry stemming from the accumulation of related mates across multiple matings, potentially facilitating evolution of polyandry to avoid inbreeding under broader conditions, and driving further evolution of pre-copulatory or post-copulatory mate choice strategies.
-Subsequently, if polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, the long-term dynamics of these three reproductive strategies become difficult to predict.
+Yet, if polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all evolve, the long-term dynamics of these three reproductive strategies become difficult to predict.
 Strong inbreeding depression might drive initial evolution of both pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry.
-However, the co-occurrence of pre-copulatory and post-copulatory inbreeding avoidance might engender some degree of `degeneracy', defined as a phenomenon by which different elements of a system result in identical outputs \cite[][]{Edelman2001}.
+However, the co-occurrence of pre-copulatory and post-copulatory inbreeding avoidance might cause some degree of `degeneracy', defined as a phenomenon by which different elements of a system result in identical outputs \cite[][]{Edelman2001}.
 Consequently, if evolution of polyandry and post-copulatory inbreeding avoidance renders pre-copulatory inbreeding avoidance functionally redundant, or vice versa, then only one inbreeding avoidance strategy might be maintained in the long-term.
 
-The few previous models that considered the evolution of inbreeding avoidance through mate choice (as opposed to dispersal) have implicitly or explicitly considered the fate of a rare allele underlying pre-copulatory inbreeding avoidance in a population initially fixed for random mating \cite[e.g.,][]{Parker1979, Parker2006, Duthie, Duthie2016a}.
+The few previous models that considered evolution of biparental inbreeding avoidance through mate choice (as opposed to dispersal) have implicitly or explicitly considered the fate of a rare allele underlying pre-copulatory inbreeding avoidance in a population initially fixed for random mating \cite[e.g.,][]{Parker1979, Parker2006, Duthie, Duthie2016a}.
 Such models are useful for isolating the invasion fitness of this single strategy.
@@
 
-Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will depend not only on the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also on the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
-Polyandrous females can pay costs of mate searching or mating, for example, because these activities increase predation risk \cite[e.g.,][]{Rowe1988, Ronkainen1994, Koga1998}.
-Females that express pre-copulatory choice and consequent reluctance to mate with relatives might pay costs of increased risk of complete mating failure or harm caused by sexual conflict \cite[][]{Rowe1994, Kokko2013}.
-Females that express post-copulatory choice might pay initial energetic costs associated with developing the physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation \cite[e.g.,][]{Gasparini2011, Tuni2013, Fitzpatrick2014b}.
-If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly strategy might become extinct, especially if their effects are made redundant by evolution of the less costly strategy.
-Evolutionary dynamics will therefore depend on the benefits of each strategy, which might also differ and vary in relation to the evolution of the other strategy.
-Dynamic models that track the frequencies of alleles underlying multiple reproductive strategies that might influence each others evolution across generations, and that are enacted among relatives that themselves result from reproductive strategies and inbreeding depression expressed in previous generations, are consequently useful to understand and predict evolutionary outcomes.
+In the context of inbreeding depression as a key hypothesised driver of reproductive strategy evolution, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will be affected not only by the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also by the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
+Empirical studies have demonstrated diverse costs of mating and mate choice, for example, including energetic costs of developing, maintaining, or enacting necessary physiologies \cite[e.g.,][]{Gasparini2011, Tuni2013, Fitzpatrick2014b}; increased risks of predation or disease stemming from increased mate-searching or mating \cite[e.g.,][]{Rowe1988, Ronkainen1994, Koga1998}; increased risk of complete mating or fertilisation failure given extreme choosiness \cite[][]{Kokko2013}; and risks of harm stemming from sexual conflict over fertilisation \cite[e.g.,][]{Rowe1994}.
+If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly strategy might go extinct, especially if their effects become redundant following evolution of the less costly strategy.
+Dynamic models that track the frequencies of alleles underlying multiple, potentially interacting, inbreeding avoidance strategies that are enacted among relatives resulting from reproductive strategies and inbreeding depression expressed in previous generations are consequently useful to understand and predict evolutionary outcomes.
 
 We use individual-based modelling to address three key questions regarding evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given opportunity for inbreeding and strong inbreeding depression.
-First, does evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance facilitate evolution of polyandry that is otherwise severely constrained by increasing relatedness of polyandrous females' additional mates?
+First, does evolution of post-copulatory inbreeding avoidance, alongside pre-copulatory inbreeding avoidance, facilitate evolution of polyandry?
 Second, how do costs associated with polyandry and pre-copulatory and post-copulatory inbreeding avoidance affect evolutionary outcomes and, in particular, the long-term persistence of these reproductive strategies given cost asymmetry?
 Third, how is selection for initially rare pre-copulatory or post-copulatory inbreeding avoidance affected if the other strategy of inbreeding avoidance is already fixed?
-By addressing these questions, we illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
+To address these questions, we designed our model to isolate the effect of each biological mechanism of interest (i.e., post-copulatory inbreeding avoidance, cost asymmetry, and strategy pre-existence, respectively) and hence to allow comparison of simulations with the mechanism present versus absent with otherwise identical parameter values and conditions.
+We thereby illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
 
 \section*{Model}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2017-08-15 pre_post_biorxiv.tex
Edits up through Costs

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply `inbreeding strategies' because the model did not preclude evolution of inbreeding preference), in a small focal population of females and males by tracking the dynamics of alleles underlying reproductive strategies expressed by females.
-We thereby track evolutionary dynamics given internally consistent patterns of relatedness caused by non-random mating and allowing for effects of mutation, gene flow, drift, and selection.
-
-All individuals have 10 physically unlinked diploid loci, and therefore 20 alleles, underlying each of three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$, i.e., `polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., `mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., `fertilisation' alleles).
-All alleles can take the value of any real number \cite[i.e., a continuum-of-alleles model;][]{Kimura1965, Lande1976, Reeve2000, Bocedi2014} and combine additively to determine genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and resulting phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively.
+We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply `inbreeding strategies' because the model did not preclude evolution of inbreeding preference), in a small focal population by tracking the dynamics of alleles underlying reproductive strategies expressed by females.
+We thereby track evolutionary dynamics given internally consistent patterns of relatedness caused by non-random mating and capture effects of mutation, gene flow, drift, and selection.
+
+Complex traits such as reproductive strategies are likely to be polygenic \cite[][]{Evans2008}.
+Hence, we model individuals with 10 physically unlinked diploid loci (i.e., 20 alleles), underlying each of three reproductive strategy traits: tendency for polyandry ($P_{a}$, `polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, `mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, `fertilisation' alleles).
+All individuals therefore have 30 diploid loci (i.e., 60 alleles) in total, each of which can take the value of any real number \cite[continuum-of-alleles model;][]{Kimura1965, Lande1976, Reeve2000, Bocedi2014}.
+
+Alleles combine additively to determine genotypic values ($P_{g}$, $M_{g}$, and $F_{g}$) and resulting phenotypic values ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively.
 Each individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
 Each individual's phenotypic values for pre-copulatory and post-copulatory inbreeding strategy equal their respective genotypic values ($M_{p} = M_{g}$ and $F_{p} = F_{g}$), where negative and positive values cause inbreeding avoidance and preference, respectively (see details of mating and fertilisation strategies below).
-In contrast, phenotypic values for tendency for polyandry equal genotypic values ($P_{p} = P_{g}$) only if $P_{g} \geq 0$, while $P_{p} = 0$ if $P_{g} < 0$ because females cannot choose a negative number of mates.
-Polyandry is therefore modelled as a threshold trait \cite[][]{Lynch1998, Roff1996, Roff1998, Duthie} that is influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
+
+In contrast, individuals' phenotypic values for tendency for polyandry ($P_{p}$) cannot map directly onto their genotypic values ($P_{g}$) because $P_{g}$ can evolve to be negative, but females cannot mate with a negative number of additional males \cite[e.g.,][]{Shuker2007, Evans2013}.
+Rather, we considered polyandry ``threshold trait'', whereby continuous genotypic variation translates into expression of discrete phenotypic value(s) at some threshold \cite[][]{Lynch1998, Roff1996, Roff1998, Duthie}.
+Accordingly, we allow individuals' phenotypic values for tendency for polyandry to equal genotypic values ($P_{p} = P_{g}$) if $P_{g} \geq 0$, but set $P_{p} = 0$ if $P_{g} < 0$.
 A negative $P_{g}$ value therefore generates a female that is phenotypically monandrous, while a positive $P_{g}$ value generates a female that can express some degree of polyandry (see details below).
-
-In overview, each generation proceeds with females paying costs associated with their reproductive strategy traits, and expressing polyandry, mating, and fertilisation.
+Polyandry is therefore influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
+One important general property of such threshold traits is that deleterious traits are occasionally expressed despite sustained negative selection because recombination among deleterious alleles can cause the underlying genotypic value to exceed the threshold for expression \cite[][]{Roff1996, Roff1998}.
+
+In overview, each model generation proceeds with females paying costs associated with their reproductive strategy traits, and expressing polyandry, mating, and fertilisation.
 Offspring inherit a randomly sampled allele from each parent at each locus.
 Alleles can then mutate and offspring express inbreeding depression in viability.
-Immigrants arrive in the population and density regulation limits population growth.
+Immigrants arrive in the population and density regulation limits population growth (see below).
 We record the population pedigree and directly calculate the coefficient of kinship ($k$) between all potential mates in each generation (defined as the probability that two homologous alleles will be identical-by-descent), allowing individual pre-copulatory and post-copulatory inbreeding strategies to be enacted.
@@
 
-Phenotypic values of the three reproductive strategy traits each have costs that are assumed to combine independently to increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
-The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
-Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
-Absolute values are used for applying costs to inbreeding avoidance strategies because both negative and positive $M_{p}$ and $F_{p}$ values could potentially arise and affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively.
-In contrast, $P_{p}$ cannot be negative.
-Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
+Phenotypic values of the three reproductive strategy traits each incur set costs that combine to independently increase the probability that a focal female will die before mating.
+Numerous forms and mechanisms of direct costs of reproductive strategies could be hypothesised and modelled; the most appropriate formulation depends on the question (see Discussion).
+By allowing costs of the three strategies to be directly and independently controlled, our model facilitates direct comparison of evolution of pre-copulatory versus post-copulatory inbreeding avoidance given known cost asymmetries.
+Qualitatively, such costs on female survival probability are biologically reasonable.
+For example, polyandrous females that undertake increased mate searching or mating can experience increased predation risk \cite[e.g.,][]{Rowe1988, Ronkainen1994, Koga1998}.
+Females that express pre-copulatory choice can increase the risk of mortality due to harm caused by sexual conflict over mating, and also risk complete mating failure \cite[which equates to pre-reproductive mortality in semelparous organisms;][]{Rowe1994, Kokko2013}.
+Finally, females that express post-copulatory choice can pay up-front energetic costs, which might result in trade-offs with survival due to developing physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation \cite[e.g.,][]{Gasparini2011, Tuni2013, Fitzpatrick2014}.
 
@@
 
+Accordingly, the probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
+Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
+Absolute values are used for applying costs to inbreeding avoidance strategies because both negative and positive $M_{p}$ and $F_{p}$ values could potentially arise and affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively.
+In contrast, $P_{p}$ is already defined to be non-negative.
+Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection*{Mating and pre-copulatory inbreeding avoidance}

### 2017-08-16 pre_post_biorxiv.tex
Edits through Model

@@
 
+Accordingly, the probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
+Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
+Absolute values are used for applying costs to inbreeding avoidance strategies because both negative and positive $M_{p}$ and $F_{p}$ values could potentially arise and affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively.
+In contrast, $P_{p}$ is already defined to be non-negative.
+Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
+
 \vspace{5 mm}
@@
 
-Accordingly, the probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
-Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
-Absolute values are used for applying costs to inbreeding avoidance strategies because both negative and positive $M_{p}$ and $F_{p}$ values could potentially arise and affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively.
-In contrast, $P_{p}$ is already defined to be non-negative.
-Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Offspring have equal probability of being female or male.
+After offspring production, all female and male adults die so that generations are non-overlapping.
 
@@
 Offsprings' alleles mutate with independent probabilities $\mu=0.001$.
-When a mutation occurs, a mutation effect is sampled from a normal distribution with a mean of zero and a standard deviation of $\mu_{SD}$ and added to the original allele value \cite[][]{Kimura1965, Lande1976, Bocedi2014, Duthie}.
+When a mutation occurs, a mutation effect size is sampled from a normal distribution with a mean of zero and a standard deviation of $\mu_{SD}$ and added to the original allele value \cite[][]{Kimura1965, Lande1976, Bocedi2014, Duthie}.
 The value of $\mu_{SD}$ is set to $\sqrt{1/20}$.
@@
 Equation 1 assumes independent allelic effects, generating multiplicative effects on offspring viability \cite[][]{Morton1956, Mills1994}.
-We model inbreeding depression as having an absolute rather than relative effect on offspring viability (i.e., hard rather than soft selection), so that the effect of $\beta$ is consistent across generations and different parameter combinations.
+It also assumes that inbreeding does not covary with inbreeding load (i.e., no purging).
+This formulation ensures that the relationship between $k_{ij}$ and the magnitude of inbreeding depression in offspring is consistent across replicate simulations.
+This choice, as opposed to a more mechanistic model of inbreeding depression that allows purging, is further justified because previous genetically-explicit modelling \cite[][]{Duthie2016a} showed that inbreeding avoidance in biparental populations has a negligible effect on load given small-effect deleterious mutations \cite[see also][]{Wang1999, Guillaume2006}.
+
+We model inbreeding depression as having an absolute rather than relative effect on offspring viability (i.e., hard rather than soft selection) so that the effect of $\beta$ is consistent across generations and different parameter combinations.
 We assume that inbreeding always decreases offspring viability (i.e., $\beta > 0$, giving inbreeding depression but no outbreeding depression).
@@
 We therefore define $\Psi_{\textrm{off}}$ as the probability that an offspring is viable, and sample its realised viability (versus mortality) using a Bernoulli trial.
-Given our current objectives, we simulate evolution under conditions where inbreeding avoidance is adaptive due to strong inbreeding depression, and not evolution where inbreeding preference is adaptive due to weak or zero inbreeding depression \cite[][]{Parker1979, Kokko2006, Duthie2016a}, or given outbreeding depression \cite[][]{Bateson1983, Greeff2009}.
+Offspring that are viable after the Bernoulli trial become adults.
+Given our current objectives, we simulate evolution under conditions where inbreeding avoidance is adaptive due to strong inbreeding depression, not where inbreeding preference is adaptive due to weak or zero inbreeding depression \cite[][]{Parker1979, Kokko2006, Duthie2016a} or outbreeding depression \cite[][]{Bateson1983, Greeff2009}.
 However, as described above, positive $M_{p}$ and $F_{p}$ values resulting in inbreeding preference are not precluded from evolving, and could potentially arise due to mutation or drift.
@@
 To avoid unrestricted population growth, we set separate carrying capacities for the total numbers of females ($K_{f}$) and males ($K_{m}$) in the focal population following immigration \cite[][]{Guillaume2009, Duthie}.
-If at the end of a generation the number of females or males exceeds $K_{f}$ or $K_{m}$  respectively, then individuals are randomly removed until each sex is at its carrying capacity.
+Hence, if at the end of a generation the number of females or males exceeds $K_{f}$ or $K_{m}$  respectively, then individuals are randomly removed until each sex is at its carrying capacity.
 Such removal can be interpreted as some combination of dispersal and mortality.
@@
 This value is therefore appropriate to illustrate the different evolutionary consequences that could result from asymmetrical costs.
-
-To address how selection on an initially rare strategy of pre-copulatory or post-copulatory inbreeding avoidance, and resulting evolution, is affected by the other strategy of inbreeding avoidance already being fixed in the population, we first used exploratory simulations to quantify evolution of pre-copulatory inbreeding strategy, and of post-copulatory inbreeding strategy and associated polyandry, in isolation.
-Then, to test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance were fixed, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., $F_{p}$ and $P_{p}$ were expressed did not evolve further).
+Results from simulations with additional cost value combinations are provided in Supporting Information.
+
+To address how selection on an initially rare inbreeding avoidance strategy, and resulting evolution, is affected by the other strategy of inbreeding avoidance already being fixed in the population, we first used exploratory simulations to quantify evolution of pre-copulatory inbreeding strategy, and of post-copulatory inbreeding strategy and associated polyandry, in isolation.
+Then, to test whether pre-copulatory inbreeding avoidance would evolve when adaptive polyandry and post-copulatory inbreeding avoidance were fixed, we initiated $M_{a}$ allele values at zero, but fixed $F_{a}$ allele values at $-10$ and $P_{a}$ allele values at $1$ (i.e., $F_{p}$ and $P_{p}$ were expressed but did not evolve further).
 Similarly, to test whether post-copulatory inbreeding avoidance would evolve when pre-copulatory inbreeding avoidance was already fixed, we initiated $F_{a}$ and $P_{a}$ allele values at zero but fixed $M_{a}$ allele values at $-10$.
@@
 These analyses allowed us to infer how allele values changed over generations in response to costs, but also in response to the changing values of other alleles and therefore potential evolutionary feedbacks among reproductive strategies.
+We do not use statistical tests to interpret simulation results; such tests are inappropriate because simulations violate key assumptions of statistical hypothesis testing, and statistical power (and therefore p-values) is determined entirely by the number of simulation replicates \cite[][]{White2014}.
+
 For all replicates, we set the maximum number of generations to 40000, which exploratory simulations and previous modelling \cite[][]{Duthie} showed to be sufficient for inferring long-term dynamics of mean allele values and therefore selection on phenotypes.
@@
 Values of $K_{f}$ and $K_{m}$ were both set to 100 because previous modelling showed that populations of this size are small enough that mate encounters between kin occur with sufficient frequency for selection on inbreeding strategy, but not so small that selection is typically overwhelmed by drift \cite[][]{Duthie2016a}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2017-08-19 pre_post_biorxiv.tex
First section of results

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection*{Mating and pre-copulatory inbreeding avoidance}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section*{Results}
@@
 
-When post-copulatory inbreeding avoidance alleles ($F_{a}$) had no effect (i.e., $F_{g}$ values were fixed to zero), meaning that $F_{p}$ could not evolve, $P_{a}$ alleles underlying polyandry always decreased to negative values over generations (red lines, Figure 1A,C,E,G).
+When post-copulatory inbreeding avoidance alleles ($F_{a}$) had no effect (i.e., $F_{g}$ values were fixed to zero), meaning that $F_{p}$ could not evolve, $P_{a}$ alleles underlying polyandry decreased to negative values over generations (red lines, Figure 1A,C,E,G).
 This shows that despite strong inbreeding depression in offspring viability, there is selection against unconditional polyandry even given zero direct cost ($c_{P}=0$; Figure 1A).
 This is because $M_{a}$ values became negative over generations, meaning that females typically avoided inbreeding through their initial mating (blue lines, Figure 1A,C,E,G).
-Polyandrous females that subsequently sampled more males from the available population were consequently more likely to mate with some relatives and hence produce some inbred offspring with low viability \cite[][]{Duthie}.
+Polyandrous females that subsequently sampled more males from the available population were consequently more likely to mate with some relatives and hence produce some inbred offspring with low viability \cite[see also][]{Duthie}.
 
@@
 Strong post-copulatory inbreeding avoidance, manifested as very negative $F_{a}$ values, consistently evolved in all simulations where such evolution was allowed (black lines, Figure 1B,D,F,H).
-Evolution of post-copulatory inbreeding avoidance occurred even when $P_{a}$ values were expected to be slightly negative, and hence when there was selection against polyandry (Figure 1F,H).
+Evolution of post-copulatory inbreeding avoidance occurred even when $P_{a}$ values were expected to be slightly negative, and hence when there was selection against alleles underlying polyandry (Figure 1F,H).
 This reflects the threshold nature of phenotypic expression of polygenic polyandry, wherein random sampling of alleles means that polyandry is expressed by some females (i.e., $P_{g}>0$) even when mean $P_{a}$ values are negative (Figure 2).
@@
 This might be expected given strong inbreeding depression in offspring viability, which imposes selection against inbreeding.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2017-08-19 pre_post_biorxiv.tex
Second section of results

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection*{How do cost asymmetries affect long-term persistence of reproductive strategies?}
@@
 
+Further simulations illustrate that such evolution of a high cost inbreeding strategy back toward random mating or random fertilisation in the presence of a relatively low cost alternative strategy is a general consequence of differential selection on each strategy induced by cost asymmetry within a range of relatively small costs, not specific to values of $c_{F}$ and $c_{M}$ of 0 and 0.02.
+For example, cost-specific evolution of pre-copulatory or post-copulatory inbreeding avoidance also occurred given non-zero small costs (e.g., $c_{F}$ and $c_{M}$ values of 0.01 and 0.03 and vice versa; Figure S9) and smaller cost asymmetries (e.g., $c_{F}$ and $c_{M}$ values of 0.01 and 0.02 and vice versa; Figure S10).
+
 When pre-copulatory inbreeding avoidance was costly, allowing evolution of cost free post-copulatory inbreeding avoidance greatly facilitated evolution of polyandry (Figure 3A versus 3B).
 However when post-copulatory inbreeding avoidance was costly, allowing evolution of cost free pre-copulatory inbreeding avoidance caused $P_{a}$ alleles to decrease to very negative values, reducing expression of polyandry (Figure 3C versus 3D; polyandry was cost free in all these simulations).
-Results for all possible cost combinations of $0$ and $0.02$ are provided in Supporting Information (Figure S9).
+Results for all possible cost combinations of $0$ and $0.02$, including costly polyandry, are provided in Supporting Information (Figure S11).
 
@@
 
-\subsection*{How does fixation of pre-copulatory or post-copulatory inbreeding avoidance affect evolution?}
+\subsection*{How does fixation of pre-copulatory or post-copulatory inbreeding avoidance affect evolution of an alternative strategy of inbreeding avoidance?}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2017-08-19 pre_post_biorxiv.tex
Results finished through Results

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 When polyandry alleles ($P_{a}$) were fixed to be positive so that all females were expected to mate multiply and post-copulatory inbreeding allele ($F_{a}$) values were fixed for adaptive inbreeding avoidance, pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}$ values became increasingly negative; Figure 4A).
@@
 $-17.62$; compare the blue lines in Figures 4A versus Figure 1B).
-This shows that fixation of post-copulatory inbreeding avoidance weakens selection for pre-copulatory inbreeding avoidance.
-
-Conversely, when pre-copulatory inbreeding allele ($M_{a}$) values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently become negative over generations (Figure 4C,D).
-Fixation of pre-copulatory inbreeding avoidance therefore prevented evolution of post-copulatory inbreeding avoidance.
-In this case, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless of whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
+This implies that pre-existence of fixed post-copulatory inbreeding avoidance can weaken selection and subsequent evolution of pre-copulatory inbreeding avoidance, but does not necessarily preclude it.
+
+In contrast, when pre-copulatory inbreeding allele ($M_{a}$) values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently become negative over generations (Figure 4C,D).
+This implies that existence of fixed pre-copulatory inbreeding avoidance can prevent evolution of post-copulatory inbreeding avoidance.
+In these simulations, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless of whether or not post-copulatory inbreeding avoidance was costly (Figure 4C,D).
 Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values (resulting in variation among replicates illustrated by the wide standard errors in Figure 4C).
 However, when $c_{F}=0.02$, $F_{a}$ values remained near zero to minimise direct costs.
-This lack of selection for post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
-When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information Figure S10).
+The lack of selection for post-copulatory inbreeding avoidance when pre-copulatory inbreeding avoidance was fixed was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
+When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information Figure S12).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2017-08-19 pre_post_biorxiv.tex
Edits through Discussion

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section*{Discussion}
 
-Evolution of different reproductive strategies cannot be presumed to occur in isolation from each other in real-world populations.
-Rather, such evolution is likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundancy) among phenotypes under selection.
-For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently drive selection for polyandry \cite[e.g., ][]{Zeh1997, Jennions2000, Tregenza2002}.
-Inbreeding avoidance could be manifested through both pre-copulatory and post-copulatory mechanisms, meaning that simultaneous evolution of each phenotype might be defined by degeneracy in addition to trait-specific costs.
-We used individual-based modelling to highlight fundamental but theoretically under-developed relationships between evolution of polyandry and pre-copulatory versus post-copulatory inbreeding strategy given (1) hard constraints on evolution of post-copulatory inbreeding strategy, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding strategy, and (3) evolution of one inbreeding strategy phenotype given the pre-existence of the other.
-We present our model and simulation results as a tool for thinking more clearly about the dynamics of simultaneously evolving reproductive strategies, not for making accurate quantitative predictions for any specific system.
-While the logic of our model can be usefully applied to constructing hypotheses within and across empirical systems, accurate quantitative prediction would require additional detail and the incorporation of empirical data for model parameterisation.
-
-\subsection*{Evolution of polyandry}
-
-The opportunity to adjust inbreeding has been widely suggested to be a driver of adaptive evolution of polyandry \cite[][]{Tregenza2002, Foerster2003, Akcay2007, Varian-Ramos2012, Kingma2013, Lehtonen2015, Reid2014}.
-We found that when post-copulatory inbreeding avoidance could evolve, selection for and resulting evolution of polyandry was greatly strengthened (Figure 1).
-The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new \cite[e.g.,][]{Zeh1997}, but our model clarifies this verbal hypothesis and therefore has widespread implications for future studies of evolution of polyandry.
+Different reproductive strategies cannot be presumed to evolve in isolation from one another.
+Rather, there is likely to be considerable potential for feedbacks and degeneracy (i.e., functional redundancy) among interacting phenotypes.
+For example, inbreeding avoidance could be manifested through both pre-copulatory and post-copulatory mechanisms and associated polyandry, meaning that simultaneous evolution of each phenotype might be affected by degeneracy, in addition to trait-specific benefits and costs.
+
+We used individual-based modelling to highlight fundamental but theoretically under-developed relationships between evolution of polyandry and pre-copulatory versus post-copulatory inbreeding strategy given (1) hard constraints on evolution of post-copulatory inbreeding strategy, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding strategy, and (3) evolution of one inbreeding strategy phenotype given pre-existence of the other.
+Our current model and simulation results thereby provide tools for thinking more clearly about the dynamics of simultaneously evolving reproductive strategies in the context of polyandry and inbreeding avoidance.
+
+\subsection{Interacting evolution of polyandry and inbreeding avoidance strategies}
+
+The opportunity to adjust inbreeding is widely suggested to be a driver of adaptive evolution of polyandry \cite[][]{Tregenza2002, Foerster2003, Akcay2007, Varian-Ramos2012, Kingma2013, Lehtonen2015, Reid2014}.
+Our simulations show that when post-copulatory inbreeding avoidance could evolve, selection for and resulting evolution of polyandry was greatly strengthened (Figure 1).
+The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new \cite[e.g.,][]{Zeh1997, Jennions2000}, but our model clarifies this verbal hypothesis and therefore has widespread implications for future studies of polyandry evolution.
 
 We predict evolution of polyandry in populations where inbreeding depression is severe and inbreeding avoidance through post-copulatory mechanisms can also evolve, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
-Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa \cite[e.g.,][]{Pizzari2004, Firman2008, Bretman2009, Gasparini2011, Tuni2013, Firman2015}.
-Recent studies have shown how females can successfully bias fertilisation after mating has occurred.
-For example, when female guppies (\textit{Poecilia reticulata}) were artificially inseminated with equal quantities of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full siblings' sperm were reduced by females' ovarian fluids \cite[][]{Gasparini2011}.
-In black field crickets (\textit{Teleogryllus commodus}), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs \cite[][]{Bussiere2006, Tuni2013}.
-
-\subsection*{Interaction of polyandry and inbreeding avoidance strategies}
-
-Evolution of both pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but were affected by the evolution of polyandry and the existence of asymmetric costs.
+Indeed, post-copulatory inbreeding avoidance has been observed under these conditions in experimental systems across diverse taxa \cite[e.g.,][]{Pizzari2004, Firman2008, Bretman2009, Gasparini2011, Tuni2013, Firman2015}.
+
+Evolution of both pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but were affected by the evolution of polyandry and by cost asymmetries.
 One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population (Figure 3).
-Consequently, long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given sufficient cost asymmetry.
-Since direct costs strongly affected the evolution of the focal phenotype(s), quantifying costs is necessary for predicting evolution of inbreeding strategies.
-
-Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging \cite[][]{Pomiankowski1987, Kokko2003}.
-\cite{Pomiankowski1987} categorised four types of costs that are relevant to mate choice, which are also relevant for polyandry, and include costs of elevated risks of predation or disease transmission, and costs incurred through time or energy expenditure.
-Consequently, we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates \cite[e.g.,][]{Rowe1988, Rowe1994}, a cost of pre-copulatory inbreeding strategy as a loss of time \cite[i.e., risk of not finding a mate in time due to choosiness; e.g.,][]{Kokko2013}, and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy, all manifested as an increased probability of total reproductive failure.
-While these costs reflect empirical observations in some populations and are therefore biologically realistic, other types of costs have also been observed and could be considered in future models tailored to specific systems.
-For example, highly polyandrous females might experience increased risk of disease transmission \cite[][]{Roberts2015a}.
-Such a cost would more realistically apply to a female's realised number of mates rather than her tendency for polyandry.
-Polyandrous females might also risk harm caused by sexual conflict over multiple mating \cite[e.g.,][]{Arnqvist2005a, Parker2006}.
-We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should be more tolerant of inbreeding than females, leading to sexual conflict over inbreeding \cite[][]{Parker1979, Parker2006, Kokko2006, Duthie2015a}.
-Future models could formally consider sexual conflict over both polyandry and inbreeding.
-Overall, such different types of costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
-Evolution of reproductive strategies therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.
-
-In our model, existence of fixed adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, precluded evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
-However, existence of fixed adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Figure 3A,B).
-In wild populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
+Hence, our model demonstrates degeneracy between inbreeding avoidance strategies, and implies that such interactions should be considered when developing hypotheses concerning reproductive strategy within and across systems.
+In particular, indefinite persistence of both pre-copulatory and post-copulatory inbreeding avoidance should not be expected in populations given a sufficiently large and sustained cost asymmetry.
+However, the time required for the more costly inbreeding strategy to go extinct might be on the order of tens of thousands of generations (Figure 3), and spatial or temporal variation in costs might facilitate coexistence of multiple inbreeding avoidance strategies.
+
+Further, pre-existence of fixed adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, precluded evolution of post-copulatory inbreeding avoidance (Figure 3C,D).
+However, pre-existence of fixed adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Figure 3A,B).
+In natural populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
 Rather, the timing of the invasion of adaptive inbreeding avoidance phenotypes will differ, so the initial evolution of one inbreeding strategy will likely occur in the absence of the other, or where selection for and subsequent evolution of the other strategy has already occurred.
-When framing hypotheses for existence of post-copulatory inbreeding avoidance and polyandry, it might therefore be necessary to consider whether or not inbreeding avoidance already occurs through pre-copulatory mate choice.
+When framing hypotheses for existence of post-copulatory inbreeding avoidance and polyandry, it might therefore be necessary to consider whether or not inbreeding avoidance is already known to occur through pre-copulatory mate choice.
 Additionally, the opportunity for post-copulatory inbreeding avoidance will also depend on the degree to which females are polyandrous.
@@
 
-\subsection*{General predictions concerning inbreeding avoidance and polyandry}
-
-Post-copulatory inbreeding avoidance cannot be effectively realised if females are not polyandrous in any form, and is likely to be most effective for highly polyandrous females that can choose amongst sperm contributed by multiple mates and therefore bias fertilisation accordingly.
-In contrast, pre-copulatory inbreeding avoidance mechanisms are most critical for females that mate only once and therefore have no post-copulatory opportunity to avoiding inbreeding.
-This theory is borne out in our simulation results, as selection for, and consequent evolution of, post-copulatory inbreeding avoidance was negligible in populations where polyandry did not evolve, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D).
-Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information Figure S9).
-In addition to initial polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back effect that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).
+\subsection{General hypotheses concerning inbreeding avoidance and polyandry}
+
+Post-copulatory inbreeding avoidance cannot be effectively realised if females are not polyandrous in any form, and is likely to be most effective for highly polyandrous females that can bias fertilisation amongst sperm contributed by multiple mates.
+In contrast, pre-copulatory inbreeding avoidance mechanisms are most critical for females that mate only once and therefore have no post-copulatory opportunity to avoid inbreeding.
+This theory is borne out in our simulation results, as selection for, and consequent evolution of, post-copulatory inbreeding avoidance was negligible in populations where polyandry did not evolve, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C).
+Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Figure 3A vs 3B; see also Supporting Information Figure S11).
+In addition to initial polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feedback effect that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1).
 It would therefore be interesting to test the hypothesis that, across taxa, the occurrence of post-copulatory inbreeding avoidance covaries positively, and the occurrence of pre-copulatory inbreeding avoidance covaries negatively, with the degree of polyandry.
-To test this hypothesis, more work is needed to quantify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
+To test this hypothesis, further empirical work is needed to quantify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
 
@@
 The relevance of degeneracy with respect to such reproductive strategies therefore requires further theoretical development, which could result in new empirical predictions and conceptual synthesis across biological scales.
+
+\subsection{Model structure, assumptions, and extensions}
+
+While the logic of our current model can be usefully applied to construct general hypotheses within and across empirical systems, accurate quantitative prediction for specific systems would require additional empirical detail and data for model parameterisation.
+To facilitate general conceptual comparison of the effects of direct costs across phenotypes, we modelled all costs as analogous increased probabilities of female mortality and hence total reproductive failure.
+This cost formulation reflects empirical observations in some populations \cite[see Model; e.g.,][]{Rowe1994, Koga1998, Gasparini2011}, and is therefore a biologically realistic method of standardising costs across traits.
+However, different forms of costs could be incorporated into future models designed to predict specific evolutionary dynamics.
+Models could then be further developed such that costs arise from explicit reproductive mechanisms, requiring further biological detail.
+
+For example, \cite{Pomiankowski1987} identified four cost categories relevant to mating frequency and mate choice, including elevated risks of predation or disease transmission, and time or energy expenditure.
+Polyandrous females might experience increased risk of disease transmission \cite[][]{Roberts2015}, a cost that would more realistically apply to a female's realised number of mates rather than her tendency for polyandry.
+Polyandrous females might also risk harm caused by sexual conflict over multiple mating \cite[e.g.,][]{Arnqvist2005, Parker2006}.
+Inbreeding theory predicts that males should be more tolerant of inbreeding than females, leading to sexual conflict over inbreeding in mating encounters \cite[][]{Parker1979, Parker2006, Kokko2006, Duthie2015a}.
+Future models could therefore explicitly consider sexual conflict over both polyandry and pre-copulatory inbreeding, and hence capture internally-consistent mechanistic costs.
+Further, sexual conflict might also affect post-copulatory inbreeding avoidance.
+For example, when female guppies (\textit{Poecilia reticulata}) were artificially inseminated with equal quantitites of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full sibling's sperm were reduced by females' ovarian fluids \cite[][]{Gasparini2011}.
+In black field crickets (\textit{Teleogryllus commodus}), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs \cite[][]{Bussiere2006, Tuni2013}.
+Future models could therefore explicitly incorporate such mechanisms in order to better understand effects of post-copulatory sexual conflict on female and male reproductive strategy evolution.
+
+We restricted our current model to examine how reproductive strategy evolution was affected by direct costs and indirect benefits stemming from inbreeding avoidance, thereby isolating such effects and explicitly addressing key general hypotheses regarding the effects of inbreeding depression.
+In natural populations, reproductive strategy evolution will also be affected by other costs and benefits, for example, stemming from additive genetic effects (i.e., pre-copulatory or post-copulatory mate choice for `good genes').
+Future objectives could consequently be to develop theory and models that include multiple benefits and costs of reproductive strategies, which could then be parameterised using empirical data.
+While good theory should always strive for conceptual clarity and the avoidance of unnecessary nuance, the prudent use of multi-faceted mechanistic models could usefully link theory, modelling, and empirical hypothesis testing and thereby improve both general and specific understanding and prediction of reproductive strategy evolution.
 

### 2017-08-19 pre_post_biorxiv.tex
Figure legends

@@
         {\bf Figure 1:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fixed to zero (i.e., random fertilisation) or (B, D, F, and H) allowed to evolve freely.
-Costs of polyandry ($c_p$) increase across rows from zero (A and B) to 0.01 (G and H).
+Costs of polyandry (c_p) increase across rows from zero (A and B) to 0.01 (G and H).
 Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
@@
 {%
-   \captionof{figures/Pp_vals.png}\begin{justify}\vspace{0.75 mm} \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs.
+   \captionof{figures/Pp_vals.png}\begin{justify}\vspace{0.75 mm} \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with identical initial conditions, default parameter values, and zero costs.
 Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations.

### 2017-08-19 pre_post_biorxiv.tex
Minor typesetting edits

--- 2017-08-19 pre_post_biorxiv.tex
@@
 However, surprisingly little theory or modelling critically examines selection for pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, given evolutionary constraints and direct costs, or examines how evolution of inbreeding avoidance strategies might feed back to affect evolution of polyandry.
-Selection for post-copulatory inbreeding avoidance, but not for pre-copulatory inbreeding avoidance, requires polyandry, while interactions between pre-copulatory and post-copulatory inbreeding avoidance might cause functional redundancy (i.e., 'degeneracy') potentially generating complex evolutionary dynamics among inbreeding strategies and polyandry.
+Selection for post-copulatory inbreeding avoidance, but not for pre-copulatory inbreeding avoidance, requires polyandry, while interactions between pre-copulatory and post-copulatory inbreeding avoidance might cause functional redundancy (i.e., `degeneracy') potentially generating complex evolutionary dynamics among inbreeding strategies and polyandry.
 We used individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression and different evolutionary constraints and direct costs.
@@
 \begin{adjustwidth}{-2.2in}{0in}
-\mysidecaption{0.70}
+\mysidecaption{0.60}
 {
-   \includegraphics[height=10.25cm]{figures/Pp_vals.png}%
+   \includegraphics[height=9.25cm]{figures/Pp_vals.png}%
 }
 {%
-   \captionof{figures/Pp_vals.png}\begin{justify}\vspace{0.75 mm} \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs.
+   \captionof{figures/Pp_vals.png}\begin{justify}\vspace{2.75 mm} \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with identical initial conditions, default parameter values, and zero costs.
 Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations.
@@
 \end{adjustwidth}
+\vspace{4 mm}
 }
@@
 {%
-   \captionof{figures/fixed_adapt.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is cost-free (A, $c_{M} = 0$; C, $c_{F} = 0$) or costly (B, $c_{M}=0.02$; D, $c_{F}=0.02$).
+   \captionof{figures/fixed_adapt.png}\begin{justify}\vspace{-1.25 mm} \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is cost-free (A, $c_{M} = 0$; C, $c_{F} = 0$) or costly (B, $c_{M}=0.02$; D, $c_{F}=0.02$).
 Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations.
@@
 
-\subsection{Interacting evolution of polyandry and inbreeding avoidance strategies}
+\subsection*{Interacting evolution of polyandry and inbreeding avoidance strategies}
 
@@
 
-\subsection{General hypotheses concerning inbreeding avoidance and polyandry}
+\subsection*{General hypotheses concerning inbreeding avoidance and polyandry}
 
@@
 
-\subsection{Model structure, assumptions, and extensions}
+\subsection*{Model structure, assumptions, and extensions}
 

### 2017-08-19 Supplement.tex
Minor rewording of new figure legends
Minor tweaks

@@
 Figure S\ref{allcombs} summarises trajectories of allele values across replicate simulations for all cost combinations of \bm{$0$} and \bm{$0.02$} for polyandry (\bm{$c_{P}$}), pre-copulatory inbreeding strategy (\bm{$c_{M}$}), and post-copulatory inbreeding strategy (\bm{$c_{F}$}).
-Figure \ref{extra_MfPf} shows how \bm{$F_{a}$} alleles change over generations given that \bm{$M_{a}$} alleles are fixed for strong inbreeding avoidance and \bm{$P_{a}$} alleles are fixed for polyandry.}
+Figure S\ref{extra_MfPf} shows how \bm{$F_{a}$} alleles change over generations given that \bm{$M_{a}$} alleles are fixed for strong inbreeding avoidance and \bm{$P_{a}$} alleles are fixed for polyandry.}
 
@@
 \end{center}
-\caption{Additional simulations with asymmetric direct costs, which are comparable to Figure 3 of the main text.
+\caption{Simulations with asymmetric direct costs, which are different but comparable to Figure 3 of the main text.
 These supplemental simulations support the general conclusion that costly pre-copulatory and post-copulatory inbreeding strategy allele values become less negative (i.e., closer to zero, indicating reduced inbreeding avoidance) over generations given the co-occurence of a less costly inbreeding strategy.

### 2017-08-19 ms_pre_post.Rmd
Minor edit

@@
 
-In contrast, individuals' phenotypic values for tendency for polyandry ($P_{p}$) cannot map directly onto their genotypic values ($P_{g}$) because $P_{g}$ can evolve to be negative, but females cannot mate with a negative number of additional males [e.g., @Shuker2007; @Evans2013].
+In contrast, individuals' phenotypic values for tendency for polyandry ($P_{p}$) cannot map directly onto their genotypic values ($P_{g}$) because $P_{g}$ can evolve to be negative, but females cannot mate with a negative number of additional males [e.g., @Shuker2007; @Evans2013b].
 Rather, we considered polyandry "threshold trait", whereby continuous genotypic variation translates into expression of discrete phenotypic value(s) at some threshold [@Lynch1998; @Roff1996; @Roff1998; @Duthie].
@@
 Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if female $i$ has a strategy of post-copulatory inbreeding avoidance ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$.
-If the female has strategy of post-copulatory inbreeding preference ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$.
+If the female has a strategy of post-copulatory inbreeding preference ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$.
 A relative quality ($q^{f}_{ij}$) is then calculated for each male by dividing his $Q^{f}_{ij}$ by the sum of the $Q^{f}_{ij}$ values across all of a female's mates.
@@
 For example, @Pomiankowski1987 identified four cost categories relevant to mating frequency and mate choice, including elevated risks of predation or disease transmission, and time or energy expenditure.
-Polyandrous females might experience increased risk of disease transmission [@Roberts2015], a cost that would more realistically apply to a female's realised number of mates rather than her tendency for polyandry.
+Polyandrous females might experience increased risk of disease transmission [@Roberts2015a], a cost that would more realistically apply to a female's realised number of mates rather than her tendency for polyandry.
 Polyandrous females might also risk harm caused by sexual conflict over multiple mating [e.g., @Arnqvist2005; @Parker2006].

### 2017-08-19 pre_post_biorxiv.tex
Minor edit

@@
 
-In contrast, individuals' phenotypic values for tendency for polyandry ($P_{p}$) cannot map directly onto their genotypic values ($P_{g}$) because $P_{g}$ can evolve to be negative, but females cannot mate with a negative number of additional males \cite[e.g.,][]{Shuker2007, Evans2013}.
+In contrast, individuals' phenotypic values for tendency for polyandry ($P_{p}$) cannot map directly onto their genotypic values ($P_{g}$) because $P_{g}$ can evolve to be negative, but females cannot mate with a negative number of additional males \cite[e.g.,][]{Shuker2007, Evans2013b}.
 Rather, we considered polyandry ``threshold trait'', whereby continuous genotypic variation translates into expression of discrete phenotypic value(s) at some threshold \cite[][]{Lynch1998, Roff1996, Roff1998, Duthie}.
@@
 Females that express pre-copulatory choice can increase the risk of mortality due to harm caused by sexual conflict over mating, and also risk complete mating failure \cite[which equates to pre-reproductive mortality in semelparous organisms;][]{Rowe1994, Kokko2013}.
-Finally, females that express post-copulatory choice can pay up-front energetic costs, which might result in trade-offs with survival due to developing physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation \cite[e.g.,][]{Gasparini2011, Tuni2013, Fitzpatrick2014}.
+Finally, females that express post-copulatory choice can pay up-front energetic costs, which might result in trade-offs with survival due to developing physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation \cite[e.g.,][]{Gasparini2011, Tuni2013, Fitzpatrick2014a}.
 
@@
 We predict evolution of polyandry in populations where inbreeding depression is severe and inbreeding avoidance through post-copulatory mechanisms can also evolve, especially if pre-copulatory inbreeding avoidance is costly (Figure 1).
-Indeed, post-copulatory inbreeding avoidance has been observed under these conditions in experimental systems across diverse taxa \cite[e.g.,][]{Pizzari2004, Firman2008, Bretman2009, Gasparini2011, Tuni2013, Firman2015}.
+Indeed, post-copulatory inbreeding avoidance has been observed under these conditions in experimental systems across diverse taxa \cite[e.g.,][]{Pizzari2004, Firman2008, Firman2015, Bretman2009, Gasparini2011, Tuni2013}.
 
@@
 For example, \cite{Pomiankowski1987} identified four cost categories relevant to mating frequency and mate choice, including elevated risks of predation or disease transmission, and time or energy expenditure.
-Polyandrous females might experience increased risk of disease transmission \cite[][]{Roberts2015}, a cost that would more realistically apply to a female's realised number of mates rather than her tendency for polyandry.
-Polyandrous females might also risk harm caused by sexual conflict over multiple mating \cite[e.g.,][]{Arnqvist2005, Parker2006}.
+Polyandrous females might experience increased risk of disease transmission \cite[][]{Roberts2015a}, a cost that would more realistically apply to a female's realised number of mates rather than her tendency for polyandry.
+Polyandrous females might also risk harm caused by sexual conflict over multiple mating \cite[e.g.,][]{Arnqvist2005a, Parker2006}.
 Inbreeding theory predicts that males should be more tolerant of inbreeding than females, leading to sexual conflict over inbreeding in mating encounters \cite[][]{Parker1979, Parker2006, Kokko2006, Duthie2015a}.
@@
 
-\bibitem[{Dougherty et~al.(2016)}]{Dougherty2016}
+\bibitem[{Dougherty \textit{et~al.}(2016)}]{Dougherty2016}
 Dougherty, L.~R., Simmons, L.~W. \& Shuker, D.~M. 2016. 
@@
 
+\bibitem[{Evan \& Gasparini(2013)}]{Evans2013b}
+Evans, J.~P. \& Gasparini, C. 2013.
+\newblock {The genetic basis of female multiple mating in a polyandrous 
+  livebearing fish}.
+\newblock {\textit{Ecol. Evol.}} \textbf{3}:61--66.
+
+\bibitem[{Evans \& Simmons(2008)}]{Evans2008}
+Evans, J.~P. \& Simmons, L.~W. 2008.
+\newblock {The genetic basis of traits regulating sperm competition and 
+  polyandry: Can selection favour the evolution of good- and sexy-sperm?}
+\newblock \textit{Genetica} \textbf{134}:5--19.
+
 \bibitem[{Firman \& Simmons(2008)}]{Firman2008}
@@
 
+\bibitem[{Fitzpatrick \textit{et~al.}(2014)}]{Fitzpatrick2014a}
+Fitzpatrick, L.~J., Gasparini, C., Fitzpatrick, J.~L. \& Evans, J.~P. 2014.
+\newblock {Male-female relatedness and patterns of male reproductive investment 
+  in guppies}
+\newblock \textit{Biol. Lett.} \textbf{10}:20140166.
+
 \bibitem[{Foerster \textit{et~al.}(2003)Foerster, Delhey, Johnsen, Lifjeld, \&
   Kempenaers}]{Foerster2003}
-Foerster, K., Delhey K., Johnsen, A., Lifjeld, J.~T. \& Kempenaers B. 2003.
+Foerster, K., Delhey K., Johnsen, A., Lifjeld, J.~T. \& Kempenaers, B. 2003.
 \newblock {Females increase offspring heterozygosity and fitness through
@@
 \newblock \textit{Heredity} \textbf{102}:349--356.
+
+\bibitem[{Guillaume \& Perrin(2006)}]{Guillaume2006}
+Guillaume, F. \& Perrin, N. 2006.
+\newblock {Joint evolution of dispersal and inbreeding load.}
+\newblock \textit{Genetics} \textbf{173}:497--509.
 
@@
 
-\bibitem[{Morton et~al.(1956)Morton, Crow \& Muller}]{Morton1956}
+\bibitem[{Morton \textit{et~al.}(1956)Morton, Crow \& Muller}]{Morton1956}
 Morton, N.~E., Crow, J.~F., \& Muller, H.~J. 1956.
@@
 
+\bibitem[{Shuker \textit{et~al.}(2007)}]{Shuker2007}
+Shuker, D.~M., Phillimore, A.~J., Burton-Chellew, M.~N., Hodge, S.~E. \& West, S.~A. 2007.
+\newblock {The quantitative genetic basis of polyandry in the parasitoid wasp, 
+  \textit{Nasonia vitripennis}}.
+\newblock \textit{Heredity} \textbf{98}:69--73.
+
 \bibitem[{Simmons \textit{et~al.}(2006)Simmons, Beveridge, Wedell \&
@@
 
+\bibitem[{Wang \textit{et~al.}(1999)}]{Wang1999}
+Wang, J., Hill, W.~G., Charlesworth, D. \& Charlesworth, B. 1999.
+\newblock {Dynamics of inbreeding depression due to deleterious mutations in 
+  small populations: mutation parameters and inbreeding rate}.
+\newblock \textit{Genet. Res.} \textbf{74}:165--178.
+
 \bibitem[{Whitacre \& Bender(2010)}]{Whitacre2010}
@@
 
+\bibitem[{White \textit{et~al.}(2014)}]{White2014}
+White, J.~W., Rassweiler, A., Samhouri, J.~F., Stier, A.~C. \& White, C. 2014.
+\newblock {Ecologists should not use statistical significance tests to interpret
+  simulation model results}.
+\newblock \textit{Oikos} \textbf{123}:385--388.
+
 \bibitem[{Zeh \& Zeh(1997)}]{Zeh1997}

### 2017-08-20 pre_post.tex
Major changes copied from biorXiv version

@@
 \floatstyle{plain}
-\restylefloat{figure}
+\restylefloat{Fig.}
 
@@
 
-\noindent 6609 words (excluding abstract, referenes, and legends)
+\noindent 7226 words (excluding abstract, references, and legends)
 
@@
 Selection for post-copulatory inbreeding avoidance, but not for pre-copulatory inbreeding avoidance, requires polyandry, while interactions between pre-copulatory and post-copulatory inbreeding avoidance might cause functional redundancy (i.e., `degeneracy') potentially generating complex evolutionary dynamics among inbreeding strategies and polyandry.
-We use individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression and different evolutionary constraints and direct costs.
-We find that evolution of post-copulatory inbreeding avoidance increases selection for initially rare polyandry, and that selection for a costly inbreeding avoidance strategy was weak or negligible given a cost free alternative strategy.
+We used individual-based modelling to quantify evolution of interacting pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given strong inbreeding depression and different evolutionary constraints and direct costs.
+We found that evolution of post-copulatory inbreeding avoidance increased selection for initially rare polyandry, and that evolution of a costly inbreeding avoidance strategy became negligible over time given a lower cost alternative strategy.
 Further, fixed pre-copulatory inbreeding avoidance often completely precluded evolution of polyandry and hence post-copulatory inbreeding avoidance, but fixed post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance.
@@
 
-Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will depend not only on the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also on the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
-Polyandrous females can pay costs of mate searching or mating, for example, because these activities increase predation risk \cite[e.g.,][]{Rowe1988, Ronkainen1994, Koga1998}.
-Females that express pre-copulatory choice and consequent reluctance to mate with relatives might pay costs of increased risk of complete mating failure or harm caused by sexual conflict \cite[][]{Rowe1994, Kokko2013}.
-Females that express post-copulatory choice might pay initial energetic costs associated with developing the physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation \cite[e.g.,][]{Gasparini2011, Tuni2013, Fitzpatrick2014b}.
-If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly strategy might become extinct, especially if their effects are made redundant by evolution of the less costly strategy.
-Evolutionary dynamics will therefore depend on the benefits of each strategy, which might also differ and vary in relation to the evolution of the other strategy.
-Dynamic models that track the frequencies of alleles underlying multiple reproductive strategies that might influence each others evolution across generations, and that are enacted among relatives that themselves result from reproductive strategies and inbreeding depression expressed in previous generations, are consequently useful to understand and predict evolutionary outcomes.
+In the context of inbreeding depression as a key hypothesised driver of reproductive strategy evolution, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will be affected not only by the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also by the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy).
+Empirical studies have demonstrated diverse costs of mating and mate choice, for example, including energetic costs of developing, maintaining, or enacting necessary physiologies \cite[e.g.,][]{Gasparini2011, Tuni2013, Fitzpatrick2014b}; increased risks of predation or disease stemming from increased mate-searching or mating \cite[e.g.,][]{Rowe1988, Ronkainen1994, Koga1998}; increased risk of complete mating or fertilisation failure given extreme choosiness \cite[][]{Kokko2013}; and risks of harm stemming from sexual conflict over fertilisation \cite[e.g.,][]{Rowe1994}.
+If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly strategy might go extinct, especially if their effects become redundant following evolution of the less costly strategy.
+Dynamic models that track the frequencies of alleles underlying multiple, potentially interacting, inbreeding avoidance strategies that are enacted among relatives resulting from reproductive strategies and inbreeding depression expressed in previous generations are consequently useful to understand and predict evolutionary outcomes.
 
 We use individual-based modelling to address three key questions regarding evolution of pre-copulatory and post-copulatory inbreeding avoidance and associated polyandry given opportunity for inbreeding and strong inbreeding depression.
-First, does evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance facilitate evolution of polyandry that is otherwise severely constrained by increasing relatedness of polyandrous females' additional mates?
+First, does evolution of post-copulatory inbreeding avoidance, alongside pre-copulatory inbreeding avoidance, facilitate evolution of polyandry?
 Second, how do costs associated with polyandry and pre-copulatory and post-copulatory inbreeding avoidance affect evolutionary outcomes and, in particular, the long-term persistence of these reproductive strategies given cost asymmetry?
 Third, how is selection for initially rare pre-copulatory or post-copulatory inbreeding avoidance affected if the other strategy of inbreeding avoidance is already fixed?
-By addressing these questions, we illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
+To address these questions, we designed our model to isolate the effect of each biological mechanism of interest (i.e., post-copulatory inbreeding avoidance, cost asymmetry, and strategy pre-existence, respectively) and hence to allow comparison of simulations with the mechanism present versus absent with otherwise identical parameter values and conditions.
+We thereby illustrate how the simultaneous evolution of multiple interacting degenerate reproductive strategies can generate diverse evolutionary outcomes.
 
@@
 
-We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply `inbreeding strategies' because the model did not preclude evolution of inbreeding preference), in a small focal population of females and males by tracking the dynamics of alleles underlying reproductive strategies expressed by females.
-We thereby track evolutionary dynamics given internally consistent patterns of relatedness caused by non-random mating and allowing for effects of mutation, gene flow, drift, and selection.
-
-All individuals have 10 physically unlinked diploid loci, and therefore 20 alleles, underlying each of three reproductive strategy traits (i.e., 30 diploid loci in total): tendency for polyandry ($P_{a}$, i.e., `polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, i.e., `mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, i.e., `fertilisation' alleles).
-All alleles can take the value of any real number \cite[i.e., a continuum-of-alleles model;][]{Kimura1965, Lande1976, Reeve2000, Bocedi2014} and combine additively to determine genotypes ($P_{g}$, $M_{g}$, and $F_{g}$) and resulting phenotypes ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively.
+We model evolution of polyandry, and of pre-copulatory and post-copulatory inbreeding avoidance strategies (hereafter simply `inbreeding strategies' because the model did not preclude evolution of inbreeding preference), in a small focal population by tracking the dynamics of alleles underlying reproductive strategies expressed by females.
+We thereby track evolutionary dynamics given internally consistent patterns of relatedness caused by non-random mating and capture effects of mutation, gene flow, drift, and selection.
+
+Complex traits such as reproductive strategies are likely to be polygenic \cite[][]{Evans2008}.
+Hence, we model individuals with 10 physically unlinked diploid loci (i.e., 20 alleles), underlying each of three reproductive strategy traits: tendency for polyandry ($P_{a}$, `polyandry' alleles), pre-copulatory inbreeding strategy ($M_{a}$, `mating' alleles), and post-copulatory inbreeding strategy ($F_{a}$, `fertilisation' alleles).
+All individuals therefore have 30 diploid loci (i.e., 60 alleles) in total, each of which can take the value of any real number \cite[continuum-of-alleles model;][]{Kimura1965, Lande1976, Reeve2000, Bocedi2014}.
+
+Alleles combine additively to determine genotypic values ($P_{g}$, $M_{g}$, and $F_{g}$) and resulting phenotypic values ($P_{p}$, $M_{p}$, and $F_{p}$) for tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy, respectively.
 Each individual's genotypic values $P_{g}$, $M_{g}$, and $F_{g}$ equal the sum of its 20 alleles for each trait.
 Each individual's phenotypic values for pre-copulatory and post-copulatory inbreeding strategy equal their respective genotypic values ($M_{p} = M_{g}$ and $F_{p} = F_{g}$), where negative and positive values cause inbreeding avoidance and preference, respectively (see details of mating and fertilisation strategies below).
-In contrast, phenotypic values for tendency for polyandry equal genotypic values ($P_{p} = P_{g}$) only if $P_{g} \geq 0$, while $P_{p} = 0$ if $P_{g} < 0$ because females cannot choose a negative number of mates.
-Polyandry is therefore modelled as a threshold trait \cite[][]{Lynch1998, Roff1996, Roff1998, Duthie} that is influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
+
+In contrast, individuals' phenotypic values for tendency for polyandry ($P_{p}$) cannot map directly onto their genotypic values ($P_{g}$) because $P_{g}$ can evolve to be negative, but females cannot mate with a negative number of additional males \cite[e.g.,][]{Shuker2007, Evans2013b}.
+Rather, we considered polyandry ``threshold trait'', whereby continuous genotypic variation translates into expression of discrete phenotypic value(s) at some threshold \cite[][]{Lynch1998, Roff1996, Roff1998, Duthie}.
+Accordingly, we allow individuals' phenotypic values for tendency for polyandry to equal genotypic values ($P_{p} = P_{g}$) if $P_{g} \geq 0$, but set $P_{p} = 0$ if $P_{g} < 0$.
 A negative $P_{g}$ value therefore generates a female that is phenotypically monandrous, while a positive $P_{g}$ value generates a female that can express some degree of polyandry (see details below).
-
-In overview, each generation proceeds with females paying costs associated with their reproductive strategy traits, and expressing polyandry, mating, and fertilisation.
+Polyandry is therefore influenced by continuous genetic variation but only expressed when $P_{g} > 0$.
+One important general property of such threshold traits is that deleterious traits are occasionally expressed despite sustained negative selection because recombination among deleterious alleles can cause the underlying genotypic value to exceed the threshold for expression \cite[][]{Roff1996, Roff1998}.
+
+In overview, each model generation proceeds with females paying costs associated with their reproductive strategy traits, and expressing polyandry, mating, and fertilisation.
 Offspring inherit a randomly sampled allele from each parent at each locus.
 Alleles can then mutate and offspring express inbreeding depression in viability.
-Immigrants arrive in the population and density regulation limits population growth.
+Immigrants arrive in the population and density regulation limits population growth (see below).
 We record the population pedigree and directly calculate the coefficient of kinship ($k$) between all potential mates in each generation (defined as the probability that two homologous alleles will be identical-by-descent), allowing individual pre-copulatory and post-copulatory inbreeding strategies to be enacted.
@@
 
-Phenotypic values of the three reproductive strategy traits each have costs that are assumed to combine independently to increase the probability that a focal female will die before mating (see Discussion for consideration of other costs).
-The probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
+Phenotypic values of the three reproductive strategy traits each incur set costs that combine to independently increase the probability that a focal female will die before mating.
+Numerous forms and mechanisms of direct costs of reproductive strategies could be hypothesised and modelled; the most appropriate formulation depends on the question (see Discussion).
+By allowing costs of the three strategies to be directly and independently controlled, our model facilitates direct comparison of evolution of pre-copulatory versus post-copulatory inbreeding avoidance given known cost asymmetries.
+Qualitatively, such costs on female survival probability are biologically reasonable.
+For example, polyandrous females that undertake increased mate searching or mating can experience increased predation risk \cite[e.g.,][]{Rowe1988, Ronkainen1994, Koga1998}.
+Females that express pre-copulatory choice can increase the risk of mortality due to harm caused by sexual conflict over mating, and also risk complete mating failure \cite[which equates to pre-reproductive mortality in semelparous organisms;][]{Rowe1994, Kokko2013}.
+Finally, females that express post-copulatory choice can pay up-front energetic costs, which might result in trade-offs with survival due to developing physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation \cite[e.g.,][]{Gasparini2011, Tuni2013, Fitzpatrick2014a}.
+
+Accordingly, the probabilities of pre-mating mortality due to the costs of polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) are $P_{p} \times c_{P}$, $|M_{p}| \times c_{M}$, and $|F_{p}| \times c_{F}$, respectively.
 Here $|M_{p}|$ and $|F_{p}|$ are the absolute values of $M_{p}$ and $F_{p}$, respectively.
 Absolute values are used for applying costs to inbreeding avoidance strategies because both negative and positive $M_{p}$ and $F_{p}$ values could potentially arise and affect the degree of inbreeding, representing inbreeding avoidance and inbreeding preference, respectively.
-In contrast, $P_{p}$ cannot be negative.
+In contrast, $P_{p}$ is already defined to be non-negative.
 Overall, because generations are non-overlapping, a female's probability of total reproductive failure increases linearly with the phenotypic value of each trait.
@@
 
-The probability that an offspring of female $i$ is sired by any one of $i$'s mates $j$ is calculated by assigning a perceived fertilisation quality to each $j$ with respect to $i$, $Q^{f}_{ij}$.
+The probability that an offspring of female $i$ is sired by any one of her mates $j$ is calculated by assigning a perceived fertilisation quality to each $j$ with respect to $i$, $Q^{f}_{ij}$.
 Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if female $i$ has a strategy of post-copulatory inbreeding avoidance ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$.
-If the female has strategy of post-copulatory inbreeding preference ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$.
+If the female has a strategy of post-copulatory inbreeding preference ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$.
 A relative quality ($q^{f}_{ij}$) is then calculated for each male by dividing his $Q^{f}_{ij}$ by the sum of the $Q^{f}_{ij}$ values across all of a female's mates.
@@
 
-When post-copulatory inbreeding avoidance alleles ($F_{a}$) had no effect (i.e., $F_{g}$ values were fixed to zero), meaning that $F_{p}$ could not evolve, $P_{a}$ alleles underlying polyandry always decreased to negative values over generations (red lines, Fig.
+When post-copulatory inbreeding avoidance alleles ($F_{a}$) had no effect (i.e., $F_{g}$ values were fixed to zero), meaning that $F_{p}$ could not evolve, $P_{a}$ alleles underlying polyandry decreased to negative values over generations (red lines, Fig.
 1A,C,E,G).
@@
 1A,C,E,G).
-Polyandrous females that subsequently sampled more males from the available population were consequently more likely to mate with some relatives and hence produce some inbred offspring with low viability \cite[][]{Duthie}.
+Polyandrous females that subsequently sampled more males from the available population were consequently more likely to mate with some relatives and hence produce some inbred offspring with low viability \cite[see also][]{Duthie}.
 
@@
 1F,H).
-Trajectories of allele values in individual simulations were typically highly stochastic, but were consistent in their long-term direction (Supporting Information Fig.
-S1-S8).
+Trajectories of allele values in individual simulations were typically highly stochastic, but were consistent in their long-term direction (Supporting Information Fig.s S1-S8).
 Overall, these results illustrate that post-copulatory inbreeding avoidance can facilitate evolution of polyandry as long as direct costs are sufficiently low (Fig.
@@
 1B,D,F,H).
-Evolution of post-copulatory inbreeding avoidance occurred even when $P_{a}$ values were expected to be slightly negative, and hence when there was selection against polyandry (Fig.
+Evolution of post-copulatory inbreeding avoidance occurred even when $P_{a}$ values were expected to be slightly negative, and hence when there was selection against alleles underlying polyandry (Fig.
 1F,H).
@@
 
+Further simulations illustrate that such evolution of a high cost inbreeding strategy back toward random mating or random fertilisation in the presence of a relatively low cost alternative strategy is a general consequence of differential selection on each strategy induced by cost asymmetry within a range of relatively small costs, not specific to values of $c_{F}$ and $c_{M}$ of 0 and 0.02.
+For example, cost-specific evolution of pre-copulatory or post-copulatory inbreeding avoidance also occurred given non-zero small costs (e.g., $c_{F}$ and $c_{M}$ values of 0.01 and 0.03 and vice versa; Fig.
+S9) and smaller cost asymmetries (e.g., $c_{F}$ and $c_{M}$ values of 0.01 and 0.02 and vice versa; Fig.
+S10).
+
 When pre-copulatory inbreeding avoidance was costly, allowing evolution of cost free post-copulatory inbreeding avoidance greatly facilitated evolution of polyandry (Fig.
@@
 3C versus 3D; polyandry was cost free in all these simulations).
-Results for all possible cost combinations of $0$ and $0.02$ are provided in Supporting Information (Fig.
-S9).
-
-\subsection*{How does fixation of pre-copulatory or post-copulatory inbreeding avoidance affect evolution?}
+Results for all possible cost combinations of $0$ and $0.02$, including costly polyandry, are provided in Supporting Information (Fig.
+S11).
+
+\subsection*{How does fixation of pre-copulatory or post-copulatory inbreeding avoidance affect evolution of an alternative strategy of inbreeding avoidance?}
 
@@
 However, after $40000$ generations, $M_{a}$ values were less negative when post-copulatory inbreeding avoidance and polyandry were fixed at non-zero values than when they also evolved from initial values of zero ($-15.45$ vs.
-$-17.62$; compare the blue lines in Fig.
-4A versus Fig.
+$-17.62$; compare the blue lines in Fig.s 4A versus Fig.
 1B).
-This shows that fixation of post-copulatory inbreeding avoidance weakens selection for pre-copulatory inbreeding avoidance.
-
-Conversely, when pre-copulatory inbreeding allele ($M_{a}$) values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently become negative over generations (Fig.
+This implies that pre-existence of fixed post-copulatory inbreeding avoidance can weaken selection and subsequent evolution of pre-copulatory inbreeding avoidance, but does not necessarily preclude it.
+
+In contrast, when pre-copulatory inbreeding allele ($M_{a}$) values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently become negative over generations (Fig.
 4C,D).
-Fixation of pre-copulatory inbreeding avoidance therefore prevented evolution of post-copulatory inbreeding avoidance.
-In this case, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless of whether or not post-copulatory inbreeding avoidance was costly (Fig.
+This implies that existence of fixed pre-copulatory inbreeding avoidance can prevent evolution of post-copulatory inbreeding avoidance.
+In these simulations, mean $P_{a}$ allele values consistently decreased over generations, reflecting selection against polyandry regardless of whether or not post-copulatory inbreeding avoidance was costly (Fig.
 4C,D).
@@
 However, when $c_{F}=0.02$, $F_{a}$ values remained near zero to minimise direct costs.
-This lack of selection for post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
+The lack of selection for post-copulatory inbreeding avoidance when pre-copulatory inbreeding avoidance was fixed was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates.
 When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Fig.
 4A,B (see Supporting Information Fig.
-S10).
+S12).
 
@@
 
-Evolution of different reproductive strategies cannot be presumed to occur in isolation from each other in real-world populations.
-Rather, such evolution is likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundancy) among phenotypes under selection.
-For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently drive selection for polyandry \cite[e.g., ][]{Zeh1997, Jennions2000, Tregenza2002}.
-Inbreeding avoidance could be manifested through both pre-copulatory and post-copulatory mechanisms, meaning that simultaneous evolution of each phenotype might be defined by degeneracy in addition to trait-specific costs.
-We used individual-based modelling to highlight fundamental but theoretically under-developed relationships between evolution of polyandry and pre-copulatory versus post-copulatory inbreeding strategy given (1) hard constraints on evolution of post-copulatory inbreeding strategy, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding strategy, and (3) evolution of one inbreeding strategy phenotype given the pre-existence of the other.
-We present our model and simulation results as a tool for thinking more clearly about the dynamics of simultaneously evolving reproductive strategies, not for making accurate quantitative predictions for any specific system.
-While the logic of our model can be usefully applied to constructing hypotheses within and across empirical systems, accurate quantitative prediction would require additional detail and the incorporation of empirical data for model parameterisation.
-
-\subsection*{Evolution of polyandry}
-
-The opportunity to adjust inbreeding has been widely suggested to be a driver of adaptive evolution of polyandry \cite[][]{Tregenza2002, Foerster2003, Akcay2007, Varian-Ramos2012, Kingma2013, Lehtonen2015, Reid2014}.
-We found that when post-copulatory inbreeding avoidance could evolve, selection for and resulting evolution of polyandry was greatly strengthened (Fig.
+Different reproductive strategies cannot be presumed to evolve in isolation from one another.
+Rather, there is likely to be considerable potential for feedbacks and degeneracy (i.e., functional redundancy) among interacting phenotypes.
+For example, inbreeding avoidance could be manifested through both pre-copulatory and post-copulatory mechanisms and associated polyandry, meaning that simultaneous evolution of each phenotype might be affected by degeneracy, in addition to trait-specific benefits and costs.
+
+We used individual-based modelling to highlight fundamental but theoretically under-developed relationships between evolution of polyandry and pre-copulatory versus post-copulatory inbreeding strategy given (1) hard constraints on evolution of post-copulatory inbreeding strategy, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding strategy, and (3) evolution of one inbreeding strategy phenotype given pre-existence of the other.
+Our current model and simulation results thereby provide tools for thinking more clearly about the dynamics of simultaneously evolving reproductive strategies in the context of polyandry and inbreeding avoidance.
+
+\subsection*{Interacting evolution of polyandry and inbreeding avoidance strategies}
+
+The opportunity to adjust inbreeding is widely suggested to be a driver of adaptive evolution of polyandry \cite[][]{Tregenza2002, Foerster2003, Akcay2007, Varian-Ramos2012, Kingma2013, Lehtonen2015, Reid2014}.
+Our simulations show that when post-copulatory inbreeding avoidance could evolve, selection for and resulting evolution of polyandry was greatly strengthened (Fig.
 1).
-The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new \cite[e.g.,][]{Zeh1997}, but our model clarifies this verbal hypothesis and therefore has widespread implications for future studies of evolution of polyandry.
+The proposition that polyandry might facilitate cryptic female choice among males of varying compatibility is not new \cite[e.g.,][]{Zeh1997, Jennions2000}, but our model clarifies this verbal hypothesis and therefore has widespread implications for future studies of polyandry evolution.
 
@@
 1).
-Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa \cite[e.g.,][]{Pizzari2004, Firman2008, Bretman2009, Gasparini2011, Tuni2013, Firman2015}.
-Recent studies have shown how females can successfully bias fertilisation after mating has occurred.
-For example, when female guppies (\textit{Poecilia reticulata}) were artificially inseminated with equal quantities of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full siblings' sperm were reduced by females' ovarian fluids \cite[][]{Gasparini2011}.
-In black field crickets (\textit{Teleogryllus commodus}), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs \cite[][]{Bussiere2006, Tuni2013}.
-
-\subsection*{Interaction of polyandry and inbreeding avoidance strategies}
-
-Evolution of both pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but were affected by the evolution of polyandry and the existence of asymmetric costs.
+Indeed, post-copulatory inbreeding avoidance has been observed under these conditions in experimental systems across diverse taxa \cite[e.g.,][]{Pizzari2004, Firman2008, Firman2015, Bretman2009, Gasparini2011, Tuni2013}.
+
+Evolution of both pre-copulatory and post-copulatory inbreeding avoidance occurred in our model, but were affected by the evolution of polyandry and by cost asymmetries.
 One cost free strategy of inbreeding avoidance precluded another more costly strategy from persisting in a focal population (Fig.
 3).
-Consequently, long-term persistence of both pre-copulatory and post-copulatory inbreeding avoidance might not be expected in populations given sufficient cost asymmetry.
-Since direct costs strongly affected the evolution of the focal phenotype(s), quantifying costs is necessary for predicting evolution of inbreeding strategies.
-
-Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging \cite[][]{Pomiankowski1987, Kokko2003}.
-\cite{Pomiankowski1987} categorised four types of costs that are relevant to mate choice, which are also relevant for polyandry, and include costs of elevated risks of predation or disease transmission, and costs incurred through time or energy expenditure.
-Consequently, we interpreted a cost of polyandy as an elevated risk of predation as might be incurred while searching for or courting mates \cite[e.g.,][]{Rowe1988, Rowe1994}, a cost of pre-copulatory inbreeding strategy as a loss of time \cite[i.e., risk of not finding a mate in time due to choosiness; e.g.,][]{Kokko2013}, and a cost of post-copulatory inbreeding strategy as an up-front depletion of energy, all manifested as an increased probability of total reproductive failure.
-While these costs reflect empirical observations in some populations and are therefore biologically realistic, other types of costs have also been observed and could be considered in future models tailored to specific systems.
-For example, highly polyandrous females might experience increased risk of disease transmission \cite[][]{Roberts2015a}.
-Such a cost would more realistically apply to a female's realised number of mates rather than her tendency for polyandry.
-Polyandrous females might also risk harm caused by sexual conflict over multiple mating \cite[e.g.,][]{Arnqvist2005a, Parker2006}.
-We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should be more tolerant of inbreeding than females, leading to sexual conflict over inbreeding \cite[][]{Parker1979, Parker2006, Kokko2006, Duthie2015a}.
-Future models could formally consider sexual conflict over both polyandry and inbreeding.
-Overall, such different types of costs might affect selection both directly and indirectly through interactions between reproductive strategies, thereby affecting evolution of entire reproductive systems.
-Evolution of reproductive strategies therefore needs to be considered in the broader context of potentially interacting and phenotypes and their costs.
-
-In our model, existence of fixed adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, precluded evolution of post-copulatory inbreeding avoidance (Fig.
+Hence, our model demonstrates degeneracy between inbreeding avoidance strategies, and implies that such interactions should be considered when developing hypotheses concerning reproductive strategy within and across systems.
+In particular, indefinite persistence of both pre-copulatory and post-copulatory inbreeding avoidance should not be expected in populations given a sufficiently large and sustained cost asymmetry.
+However, the time required for the more costly inbreeding strategy to go extinct might be on the order of tens of thousands of generations (Fig.
+3), and spatial or temporal variation in costs might facilitate coexistence of multiple inbreeding avoidance strategies.
+
+Further, pre-existence of fixed adaptive pre-copulatory inbreeding avoidance precluded evolution of polyandry and, in turn, precluded evolution of post-copulatory inbreeding avoidance (Fig.
 3C,D).
-However, existence of fixed adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Fig.
+However, pre-existence of fixed adaptive post-copulatory inbreeding avoidance did not preclude evolution of pre-copulatory inbreeding avoidance (Fig.
 3A,B).
-In wild populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
+In natural populations, it is unlikely that pre-copulatory and post-copulatory inbreeding avoidance will evolve simultaneously from an ancestral population in which females mate and assign paternity randomly.
 Rather, the timing of the invasion of adaptive inbreeding avoidance phenotypes will differ, so the initial evolution of one inbreeding strategy will likely occur in the absence of the other, or where selection for and subsequent evolution of the other strategy has already occurred.
-When framing hypotheses for existence of post-copulatory inbreeding avoidance and polyandry, it might therefore be necessary to consider whether or not inbreeding avoidance already occurs through pre-copulatory mate choice.
+When framing hypotheses for existence of post-copulatory inbreeding avoidance and polyandry, it might therefore be necessary to consider whether or not inbreeding avoidance is already known to occur through pre-copulatory mate choice.
 Additionally, the opportunity for post-copulatory inbreeding avoidance will also depend on the degree to which females are polyandrous.
@@
 
-\subsection*{General predictions concerning inbreeding avoidance and polyandry}
-
-Post-copulatory inbreeding avoidance cannot be effectively realised if females are not polyandrous in any form, and is likely to be most effective for highly polyandrous females that can choose amongst sperm contributed by multiple mates and therefore bias fertilisation accordingly.
-In contrast, pre-copulatory inbreeding avoidance mechanisms are most critical for females that mate only once and therefore have no post-copulatory opportunity to avoiding inbreeding.
+\subsection*{General hypotheses concerning inbreeding avoidance and polyandry}
+
+Post-copulatory inbreeding avoidance cannot be effectively realised if females are not polyandrous in any form, and is likely to be most effective for highly polyandrous females that can bias fertilisation amongst sperm contributed by multiple mates.
+In contrast, pre-copulatory inbreeding avoidance mechanisms are most critical for females that mate only once and therefore have no post-copulatory opportunity to avoid inbreeding.
 This theory is borne out in our simulation results, as selection for, and consequent evolution of, post-copulatory inbreeding avoidance was negligible in populations where polyandry did not evolve, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Fig.
-4C,D).
+4C).
 Evolution of pre-copulatory inbreeding avoidance was also typically slightly stronger when polyandry did not evolve (e.g., Fig.
 3A vs 3B; see also Supporting Information Fig.
-S9).
-In addition to initial polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back effect that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Fig.
+S11).
+In addition to initial polyandry causing evolution of post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feedback effect that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Fig.
 1).
 It would therefore be interesting to test the hypothesis that, across taxa, the occurrence of post-copulatory inbreeding avoidance covaries positively, and the occurrence of pre-copulatory inbreeding avoidance covaries negatively, with the degree of polyandry.
-To test this hypothesis, more work is needed to quantify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
+To test this hypothesis, further empirical work is needed to quantify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.
 
@@
 
+\subsection*{Model structure, assumptions, and extensions}
+
+While the logic of our current model can be usefully applied to construct general hypotheses within and across empirical systems, accurate quantitative prediction for specific systems would require additional empirical detail and data for model parameterisation.
+To facilitate general conceptual comparison of the effects of direct costs across phenotypes, we modelled all costs as analogous increased probabilities of female mortality and hence total reproductive failure.
+This cost formulation reflects empirical observations in some populations \cite[see Model; e.g.,][]{Rowe1994, Koga1998, Gasparini2011}, and is therefore a biologically realistic method of standardising costs across traits.
+However, different forms of costs could be incorporated into future models designed to predict specific evolutionary dynamics.
+Models could then be further developed such that costs arise from explicit reproductive mechanisms, requiring further biological detail.
+
+For example, \cite{Pomiankowski1987} identified four cost categories relevant to mating frequency and mate choice, including elevated risks of predation or disease transmission, and time or energy expenditure.
+Polyandrous females might experience increased risk of disease transmission \cite[][]{Roberts2015a}, a cost that would more realistically apply to a female's realised number of mates rather than her tendency for polyandry.
+Polyandrous females might also risk harm caused by sexual conflict over multiple mating \cite[e.g.,][]{Arnqvist2005a, Parker2006}.
+Inbreeding theory predicts that males should be more tolerant of inbreeding than females, leading to sexual conflict over inbreeding in mating encounters \cite[][]{Parker1979, Parker2006, Kokko2006, Duthie2015a}.
+Future models could therefore explicitly consider sexual conflict over both polyandry and pre-copulatory inbreeding, and hence capture internally-consistent mechanistic costs.
+Further, sexual conflict might also affect post-copulatory inbreeding avoidance.
+For example, when female guppies (\textit{Poecilia reticulata}) were artificially inseminated with equal quantitites of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full sibling's sperm were reduced by females' ovarian fluids \cite[][]{Gasparini2011}.
+In black field crickets (\textit{Teleogryllus commodus}), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs \cite[][]{Bussiere2006, Tuni2013}.
+Future models could therefore explicitly incorporate such mechanisms in order to better understand effects of post-copulatory sexual conflict on female and male reproductive strategy evolution.
+
+We restricted our current model to examine how reproductive strategy evolution was affected by direct costs and indirect benefits stemming from inbreeding avoidance, thereby isolating such effects and explicitly addressing key general hypotheses regarding the effects of inbreeding depression.
+In natural populations, reproductive strategy evolution will also be affected by other costs and benefits, for example, stemming from additive genetic effects (i.e., pre-copulatory or post-copulatory mate choice for `good genes').
+Future objectives could consequently be to develop theory and models that include multiple benefits and costs of reproductive strategies, which could then be parameterised using empirical data.
+While good theory should always strive for conceptual clarity and the avoidance of unnecessary nuance, the prudent use of multi-faceted mechanistic models could usefully link theory, modelling, and empirical hypothesis testing and thereby improve both general and specific understanding and prediction of reproductive strategy evolution.
+
 %\subsection*{Competing interests}
@@
   copulatory inbreeding avoidance in the cabbage beetle \textit{Colaphellus bowringi}.}
-\newblock \textit{PloS One} \textbf{9}:e94389.
+\newblock \textit{PloS one} \textbf{9}:e94389.
 
@@
   Duthie, Losdat, Wolak \& Nietlisbach}]{Reid2014}
-Reid, J.~M., Arcese, P., Keller, L.~F., Germain, R.~R., Duthie, A.~B., Losdat, S. 
-\textit{et~al.} 2015{\natexlab{\emph{a}}}.
+Reid, J.~M., Arcese, P., Keller, L.~F., Germain, R.~R., Duthie, A.~B., Losdat, S.,
+  Wolak, M.~E. \& Nietlisbach, P. 2015{\natexlab{\emph{a}}}.
 \newblock {Quantifying inbreeding avoidance through extra-pair reproduction}.
@@
 \newblock \textit{Theor. Biol. Med. Model.} \textbf{7}:6.
+
+\bibitem[{White \textit{et~al.}(2014)}]{White2014}
+White, J.~W., Rassweiler, A., Samhouri, J.~F., Stier, A.~C. \& White, C. 2014.
+\newblock {Ecologists should not use statistical significance tests to interpret
+  simulation model results}.
+\newblock \textit{Oikos} \textbf{123}:385--388.
 
@@
 
-\noindent \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs.
+\noindent \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with identical initial conditions, default parameter values, and zero costs.
 Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations.
@@
 \begin{center}				
-\includegraphics[scale=0.85]{poly_costs.eps}
+\includegraphics[scale=0.85]{figures/poly_costs.png}
 \end{center}
@@
 \begin{center}				
-\includegraphics[scale=0.60]{Pp_vals.eps}
+\includegraphics[scale=0.60]{figures/Pp_vals.png}
 \end{center}
-\caption{Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs.
+\caption{Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with identical initial conditions, default parameter values, and zero costs.
 Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations.
@@
 \begin{center}				
-\includegraphics[scale=1.00]{rel_costs.eps}
+\includegraphics[scale=1.00]{figures/rel_costs.png}
 \end{center}
@@
 \begin{center}				
-\includegraphics[scale=1.00]{fixed_adapt.eps}
+\includegraphics[scale=1.00]{figures/fixed_adapt.png}
 \end{center}

### 2017-09-20 pre_post.tex
Final tweaks before sending to JEB
Initial commit and fix first comment

@@
 \usepackage{lipsum}
+\usepackage{soul}
 \floatstyle{plain}
@@
 From a female's perspective, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males following mating (i.e., post-copulatory inbreeding avoidance).
-Evolution of post-copulatory inbreeding avoidance is likely to be facilitated when females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout \cite[but see][]{Dougherty2016}.
+Evolution of post-copulatory inbreeding avoidance \textcolor{red}{\st{is likely to be facilitated when}} \textcolor{blue}{requires that} females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout \cite[but see][]{Dougherty2016}.
 Further, such polyandry might itself evolve because it allows females to mate with additional unrelated males following an initial mating with a relative, potentially including males that were unavailable for initial mate choice \cite[e.g.,][]{Reid2015, Duthie}.
@@
 \begin{center}				
-\includegraphics[scale=0.85]{figures/poly_costs.png}
+\includegraphics[scale=0.85]{poly_costs.eps}
 \end{center}
@@
 \begin{center}				
-\includegraphics[scale=0.60]{figures/Pp_vals.png}
+\includegraphics[scale=0.60]{Pp_vals.eps}
 \end{center}
@@
 \begin{center}				
-\includegraphics[scale=1.00]{figures/rel_costs.png}
+\includegraphics[scale=1.00]{rel_costs.eps}
 \end{center}
@@
 \begin{center}				
-\includegraphics[scale=1.00]{figures/fixed_adapt.png}
+\includegraphics[scale=1.00]{fixed_adapt.eps}
 \end{center}

### 2017-09-21 pre_post.tex
Fix kinship issue

@@
 Immigrants arrive in the population and density regulation limits population growth (see below).
-We record the population pedigree and directly calculate the coefficient of kinship ($k$) between all potential mates in each generation (defined as the probability that two homologous alleles will be identical-by-descent), allowing individual pre-copulatory and post-copulatory inbreeding strategies to be enacted.
+We record the population pedigree and directly calculate the coefficient of kinship ($k$) between all potential mates in each generation (defined as the probability that two homologous alleles will be identical-by-descent, \textcolor{blue}{therefore ranging from 0-1}), allowing individual pre-copulatory and post-copulatory inbreeding strategies to be enacted.
+\textcolor{blue}{Values of $k$ are calculated directly from the pedigree using a standard iterative algorithm \cite[e.g.,][]{Boyce1983, Duthie}}.
 Key individual traits, parameter values, and variables are described in Table 1.
@@
 \newblock \textit{Evolution} \textbf{69}:39--58.
+
+\bibitem[{Boyce(1983)}]{Boyce1983}
+Boyce, A. 1983.
+\newblock {Computation of inbreeding and kinship coefficients on extended pedigrees}
+\newblock \textit{J. Hered.} \textbf{74}:400--404.
 

### 2017-09-21 pre_post.tex
Address the statistical inference comment
Finished draft of all changes

@@
 
-\noindent 7226 words (excluding abstract, references, and legends)
+\noindent \textcolor{red}{\st{7226}} \textcolor{blue}{7267} words (excluding abstract, references, and legends)
 
@@
 
-Phenotypic values of the three reproductive strategy traits each incur set costs that combine to independently increase the probability that a focal female will die before mating.
-Numerous forms and mechanisms of direct costs of reproductive strategies could be hypothesised and modelled; the most appropriate formulation depends on the question (see Discussion).
+Phenotypic values of the three reproductive strategy traits each incur set costs that combine to independently increase the probability that a focal female will die before mating \textcolor{blue}{(realisation of costs precedes mating and fertilisation, so we present further details of mating and fertilisation below).} Numerous forms and mechanisms of direct costs of reproductive strategies could be hypothesised and modelled; the most appropriate formulation depends on the question (see Discussion).
 By allowing costs of the three strategies to be directly and independently controlled, our model facilitates direct comparison of evolution of pre-copulatory versus post-copulatory inbreeding avoidance given known cost asymmetries.
@@
 However, after $40000$ generations, $M_{a}$ values were less negative when post-copulatory inbreeding avoidance and polyandry were fixed at non-zero values than when they also evolved from initial values of zero ($-15.45$ vs.
-$-17.62$; compare the blue lines in Fig.s 4A versus Fig.
+$-17.62$\textcolor{blue}{, SEs $\approx$ $1.8$ \& $1.6$, respectively}; compare the blue lines in Fig.s 4A versus Fig.
 1B).

### 2017-09-23 pre_post.tex
Final edits approved by coauthors

--- 2017-09-20 pre_post.tex
@@
 
-\noindent 7226 words (excluding abstract, references, and legends)
+\noindent 7267 words (excluding abstract, references, and legends)
 
@@
 From a female's perspective, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males following mating (i.e., post-copulatory inbreeding avoidance).
-Evolution of post-copulatory inbreeding avoidance \textcolor{red}{\st{is likely to be facilitated when}} \textcolor{blue}{requires that} females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout \cite[but see][]{Dougherty2016}.
+Evolution of post-copulatory inbreeding avoidance requires that females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout \cite[but see][]{Dougherty2016}.
 Further, such polyandry might itself evolve because it allows females to mate with additional unrelated males following an initial mating with a relative, potentially including males that were unavailable for initial mate choice \cite[e.g.,][]{Reid2015, Duthie}.
@@
 Immigrants arrive in the population and density regulation limits population growth (see below).
-We record the population pedigree and directly calculate the coefficient of kinship ($k$) between all potential mates in each generation (defined as the probability that two homologous alleles will be identical-by-descent), allowing individual pre-copulatory and post-copulatory inbreeding strategies to be enacted.
+We record the population pedigree and directly calculate the coefficient of kinship ($k$) between all potential mates in each generation (defined as the probability that two homologous alleles will be identical-by-descent, therefore ranging from 0-1), allowing individual pre-copulatory and post-copulatory inbreeding strategies to be enacted.
+Values of $k$ are calculated directly from the pedigree using a standard iterative algorithm \cite[e.g.,][]{Boyce1983, Duthie}.
 Key individual traits, parameter values, and variables are described in Table 1.
@@
 
-Phenotypic values of the three reproductive strategy traits each incur set costs that combine to independently increase the probability that a focal female will die before mating.
+Phenotypic values of the three reproductive strategy traits each incur set costs that combine to independently increase the probability that a focal female will die before mating (realisation of costs precedes mating and fertilisation, so we present further details of mating and fertilisation below).
 Numerous forms and mechanisms of direct costs of reproductive strategies could be hypothesised and modelled; the most appropriate formulation depends on the question (see Discussion).
@@
 However, after $40000$ generations, $M_{a}$ values were less negative when post-copulatory inbreeding avoidance and polyandry were fixed at non-zero values than when they also evolved from initial values of zero ($-15.45$ vs.
-$-17.62$; compare the blue lines in Fig.s 4A versus Fig.
+$-17.62$, SEs $\approx$ $1.8$ \& $1.6$, respectively; compare the blue lines in Fig.s 4A versus Fig.
 1B).
@@
 
-%This work was funded by a European Research Council Starting Grant to JMR. Computer simulations were performed using the Maxwell Computing Cluster at the University of Aberdeen.
+%This work was funded by a European Research Council Starting Grant to JMR.
+Computer simulations were performed using the Maxwell Computing Cluster at the University of Aberdeen.
+We thank two anonymous reviewers for helpful comments.
 

### 2017-09-23 pre_post_biorxiv.tex
Final edits approved by coauthors

@@
 From a female's perspective, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males following mating (i.e., post-copulatory inbreeding avoidance).
-Evolution of post-copulatory inbreeding avoidance is likely to be facilitated when females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout \cite[but see][]{Dougherty2016}.
+Evolution of post-copulatory inbreeding avoidance requires that females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout \cite[but see][]{Dougherty2016}.
 Further, such polyandry might itself evolve because it allows females to mate with additional unrelated males following an initial mating with a relative, potentially including males that were unavailable for initial mate choice \cite[e.g.,][]{Reid2015, Duthie}.
@@
 However, after $40000$ generations, $M_{a}$ values were less negative when post-copulatory inbreeding avoidance and polyandry were fixed at non-zero values than when they also evolved from initial values of zero ($-15.45$ vs.
-$-17.62$; compare the blue lines in Figures 4A versus Figure 1B).
+$-17.62$, SEs $\approx$ $1.8$ \& $1.6$, respectively; compare the blue lines in Figures 4A versus Figure 1B).
 This implies that pre-existence of fixed post-copulatory inbreeding avoidance can weaken selection and subsequent evolution of pre-copulatory inbreeding avoidance, but does not necessarily preclude it.
@@
 
+\bibitem[{Boyce(1983)}]{Boyce1983}
+Boyce, A. 1983.
+\newblock {Computation of inbreeding and kinship coefficients on extended pedigrees}
+\newblock \textit{J. Hered.} \textbf{74}:400--404.
+
 \bibitem[{Bretman \textit{et~al.}(2009)Bretman, Newcombe, \& Tregenza}]{Bretman2009}

### 2018-02-21 presentation/inbreeding.Rmd
Initial inbreeding file initialised

---
title: "When, why, and how to avoid, prefer, or tolerate inbreeding"
subtitle: "https://bradduthie.shinyapps.io/inbreeding"
author: "Brad Duthie"
date: "6 March 2018"
output: 
  ioslides_presentation: 
    widescreen: yes
runtime: shiny
---

## Introduction

##

```{r, echo=FALSE}
OffATr <- function(r, m, mmin=1, Beta=1, c=1){
    return( (1/2)*(1+r) * (1 - exp(-c*(m - mmin - Beta*r)) ));
}
# Below is fmd for analysis and plotting
OffATrd <- function(r, m, mmin=1, Beta=1, c=1){
    return(  0.5 * (1 + r) * (exp(-c * (m - mmin - Beta * r)) * c)  );
    # Also can simplify: return(  (c/2)*(1+r)*exp(-c*(m-mmin-Beta*r))  );
} # We'll need the above to find m^{*} and \gamma^{*} 
# To find m^{*}, can use the function below
findm <- function(low.guess,high.guess,rval,mmin=1,Beta=1,c=1){
  fm  <- function(m,r=rval){ 
           OffATrd(r=rval, mmin=mmin, Beta=Beta, m=m, c=c)*(0-m) + 
             OffATr(r=rval, mmin=mmin, Beta=Beta, m=m, c=c);
         }
  lg  <- fm(m=low.guess, r=rval);
  hg  <- fm(m=high.guess,r=rval);
  if(lg > 0){
    u <- low.guess;
    l <- high.guess;
  }else{
    u <- high.guess;
    l <- low.guess;
  }
  if((fm(l) > 0 & fm(u) > 0) | (fm(l) < 0 & fm(u) < 0)){
    return("Value of m is outside the range");
  }else{
    check  <- 1;
    mguess <- 0.5 * (l+u);
    i      <- 0;
    while(abs(check) > 0.000001 & i < 1000000){
        check <- fm(r=rval, m=mguess);
        if(check > 0){
          u      <- mguess;
          mguess <- 0.5*(l+mguess); 
        }else{
          l      <- mguess;
          mguess <- 0.5*(u+mguess);
        }
        i <- i+1;
    }
    return(mguess);
  }
} # Running the below returns the estimate
fmpl  <- expression(zeta[off] == frac(1,2)*(1+r)*(1-e^{(-c*(m-m[min]-beta*r))}));
inputPanel(

  sliderInput("rval", label = "Relatedness", width="100%",
              min = 0.0, max = 1, value = 0, step = 0.05),

  sliderInput("cval", label = "PI curve", width="100%",
              min = 0.0, max = 3, value = 1, step=0.2),

  sliderInput("mmin", label = "Minimum m value", width="100%",
              min = 0.0, max = 2, value = 1, step = 0.1),

  sliderInput("Beta", label = "Inbreeding depression", 
              width="100%", min = 0.0, max = 5, value = 0, step = 0.2)
)

renderPlot({
  cc  <- as.numeric(input$cval);
  mm  <- as.numeric(input$mmin);
  bb  <- as.numeric(input$Beta);
  rr  <- as.numeric(input$rval);
  rmm <- findm(low.guess=0,high.guess=6,rval=rr,mmin=mm,Beta=bb,c=cc);
  mzt <- OffATr(r=rr, m=rmm, mmin=mm, Beta=bb, c=cc);
  rmg <- mzt / rmm;    
  PI  <- seq(from=0,to=4,by=0.01);
  All <- OffATr(r=rr, m=PI, mmin=mm, Beta=bb, c=cc);
  par(mar=c(5,5,2,2));
  plot(PI,All,type="l",lwd=4,ylim=c(0,1),
     xlab=expression(paste("Parental investment (",italic(m),")")),
     ylab=expression(paste("IBD alleles in offspring (",zeta[off],")")),
     cex.lab=1.5,cex.axis=1.5);
  abline(h=0,lty="dotted",lwd=0.8);
  abline(a=0,b=rmg,lty="solid", lwd=2,col="blue");
  arrows(x0=rmm,y0=mzt/2,x1=rmm,y1=0,length = 0.15,angle=30,code=2,lwd=3,col="blue");
  text(x=1,y=0.8,labels=fmpl,cex=2);
  text(x=rmm,y=0.5*mzt+0.07,labels=expression(paste(italic(m)^"*")),col="blue",cex=2);
  text(x=0.5,y=rmg*0.5+0.07,labels=expression(paste(italic(gamma^"*"))),
       srt=rmg,cex=2,col="blue");
})
```

### 2018-02-21 presentation/inbreeding.Rmd
Progress on the fancier bit

@@
 
-## Introduction
+## Inbreeding depression
+
+##
+
+```{r lmSim, fig.show='animate', echo = FALSE}
+inputPanel(
+  sliderInput("Imm", label = "Immigrants", width="100%",
+              min = 0.0, max = 1, value = 0, step = 0.05), 
+  sliderInput("ID", label = "Inbreeding Depression", width="100%",
+              min = 0.0, max = 1, value = 0, step = 0.05), 
+  sliderInput("cost", label = "Strategy Cost", width="100%",
+              min = 0.0, max = 1, value = 0, step = 0.05), 
+  sliderInput("mu", label = "Mutation Rate", width="100%",
+              min = 0.0, max = 1, value = 0, step = 0.05), 
+  actionButton("mate", "New Generation"),
+  actionButton("reset", "Reset")
+)
+
+ts    <- reactiveValues();
+ts$df <- data.frame(gen = numeric(0), val = numeric(0));
+
+Ds    <- observeEvent(input$mate, {
+        new   <- isolate(c(dim(ts$df)[1] + 1, runif(1, 0, 1)));
+        isolate(ts$df <- rbind(ts$df, new));
+})
+
+rs    <- observeEvent(input$reset, {
+       ts$df <- data.frame(gen = numeric(0), val = numeric(0)); 
+})
+
+renderPlot({
+  par(bg = 'transparent');
+  last <- dim(ts$df)[1];
+  if(last < 6){
+      plot(x = 0:10, y = 0:10, type = "n", ylim = c(0, 1), cex.axis = 1.5,
+           cex.lab = 1.5, xlab = "Generation", ylab = "k", bg = "transparent");
+      points(x = ts$df[,1], y = ts$df[,2], pch = 20, cex = 1.5, type = "b",
+             lwd = 2);
+  }else{
+      x0 <- last - 5;
+      x1 <- last + 5;
+      plot(x = x0:x1, y = x0:x1, type = "n", ylim = c(0, 1), cex.axis = 1.5,
+           cex.lab = 1.5, xlab = "Generation", ylab = "k");
+      points(x = ts$df[x0:x1,1], y = ts$df[x0:x1,2], pch = 20, cex = 1.5, type = "b",
+             lwd = 2);
+  }
+})
+```
+
+## Inbreeding tolerance
+
+## Inbreeding avoidance
+
+## Inbreeding preference
+
+## Parker's model
 

### 2018-02-21 presentation/toy_model.R
Recreate a toy version of the big IBM

@@ -1,0 +1,182 @@
+initialise_inds <- function(N = 200){
+    ID      <- matrix(data = 0, nrow = N, ncol = 30);
+    ID[,1]  <- 1:N;
+    ID[,2]  <- rbinom(n = N, size = 1, prob = 0.5);
+    ID[,3]  <- sample(x = 1:10, size = N, replace = TRUE);
+    ID[,4]  <- sample(x = 1:10, size = N, replace = TRUE);
+    ID[,5]  <- rep(x = 0, times = N);
+    ID[,6]  <- rep(x = -1, times = N);
+    ID[,7]  <- rep(x = -1, times = N);
+    ID[,8]  <- rep(x = 0, times = N);
+    ID[,9]  <- rep(x = -1, times = N);
+    ID[,10] <- rep(x = 0, times = N);
+    return(ID);
+}
+
+initialise_Rmat <- function(ID){
+    rows <- dim(ID)[1];
+    Rmat <- matrix(data = 0, nrow = rows, ncol = rows);
+    diag(Rmat) <- 1;
+    Rmat <- cbind(ID[,1], Rmat);
+    return(Rmat);
+}
+
+Rbuild <- function(Rmat, ID, Rmat_new){
+    inds <- dim(ID)[1];
+    for(i in 1:inds){
+        if(ID[i, 6] %in% Rmat[,1] == FALSE){
+            MomP <- -1;
+        }else{
+            MomP <- which(Rmat[,1] == ID[i, 6]);
+        }
+        if(ID[i, 7] %in% Rmat[,1] == FALSE){
+            DadP <- -1;
+        }else{
+            DadP <- which(Rmat[,1] == ID[i, 7]);
+        }
+        # Inbreeding coefficient
+        if(MomP < 0 | DadP < 0){
+            Rmat_new[i, i+1] <- 1; 
+        }else{
+            Rmat_new[i, i+1] <- 1 + Rmat[MomP, DadP+1]; 
+        }
+        # Kinship coefficient
+        j <- 1;
+        while(j < i){
+            if(ID[j, 6] %in% Rmat[,1] == FALSE){
+                Om <- -1;
+            }else{
+                Om <- which(Rmat[,1] == ID[j, 6]);
+            }
+            if(ID[j, 7] %in% Rmat[,1] == FALSE){
+                Od <- -1;
+            }else{
+                Od <- which(Rmat[,1] == ID[j, 7]);
+            }
+            
[…]

### 2018-02-22 presentation/toy_model.R
Full toy model needs a double-check

@@ -144,7 +144,127 @@ mateselect <- function(ID, Rmat_new){
     return(ID);
 }
 
-new_gen <- function(ID, Rmat, cost, imm, beta, mu, Kf = 100, Km = 100, nn = 6){
+make_offspring <- function(ID, Rmat_new, nn = 6){
+    start_ID <- max(ID[,1]) + 1;
+    for(i in 1:dim(ID)[1]){
+        if(ID[i, 2] == 0 & ID[i, 9] > 0 & ID[i, 5] == 0){
+            mum    <- ID[i,];
+            dadpos <- which(ID[,1] == ID[i, 9]);
+            dad    <- ID[dadpos,];
+            offs   <- matrix(data = 0, nrow = nn, ncol = dim(ID)[2]);
+            offs[,1] <- start_ID:(start_ID+nn-1);
+            start_ID <- start_ID + nn;
+            offs[,2] <- rbinom(n = nn, size = 1, prob = 0.5);
+            offs[,3] <- mum[3];
+            offs[,4] <- mum[4];
+            offs[,6] <- mum[1];
+            offs[,7] <- dad[1];
+            mrpos    <- which(Rmat_new[,1] == mum[1]);
+            drpos    <- which(Rmat_new[,1] == dad[1]);
+            offs[,8] <- Rmat_new[mrpos, drpos+1];
+            offs[,11:30] <- mum[11:30];
+            dum_vec  <- rbinom(n = length(offs[,11:30]), size = 1, prob = 0.5);
+            dummy    <- matrix(data = dum_vec, nrow = dim(offs)[1]);
+            dummy[dummy > 0] <- NA;
+            
+        }
+    }
+}
+
+produce_offs <- function(ID, Rmat_new, nn){
+    # NOTE: This toy model has unrealistic recombination between parents!
+    mums  <- sum(ID[,2] == 0 & ID[, 5] == 0 & ID[, 9] != 0);
+    offs  <- matrix(data = 0, nrow = mums * nn, ncol = dim(ID)[2]);
+    start <- 1;
+    for(i in 1:dim(ID)[1]){  # Unrealistic recombination saves some time.
+        if(ID[i,2] == 0 & ID[i, 5] == 0 & ID[i, 9] != 0){
+            her_off     <- matrix(data = ID[i,], nrow = nn, ncol = dim(ID)[2], 
[…]

### 2018-02-23 presentation/inbreeding.Rmd
Toy model working in shiny, needs refining

--- 2018-02-21 presentation/inbreeding.Rmd
@@
 
-## Introduction
+```{r, echo = FALSE}
+initialise_inds <- function(N = 200){
+    ID      <- matrix(data = 0, nrow = N, ncol = 30);
+    ID[,1]  <- 1:N;
+    ID[,2]  <- rbinom(n = N, size = 1, prob = 0.5);
+    ID[,3]  <- sample(x = 1:10, size = N, replace = TRUE);
+    ID[,4]  <- sample(x = 1:10, size = N, replace = TRUE);
+    ID[,5]  <- rep(x = 0, times = N);
+    ID[,6]  <- rep(x = -1, times = N);
+    ID[,7]  <- rep(x = -1, times = N);
+    ID[,8]  <- rep(x = 0, times = N);
+    ID[,9]  <- rep(x = -1, times = N);
+    ID[,10] <- rep(x = 0, times = N);
+    return(ID);
+}
+
+initialise_Rmat <- function(ID){
+    rows <- dim(ID)[1];
+    Rmat <- matrix(data = 0, nrow = rows, ncol = rows);
+    diag(Rmat) <- 1;
+    Rmat <- cbind(ID[,1], Rmat);
+    return(Rmat);
+}
+
+Rbuild <- function(Rmat, ID, Rmat_new){
+    inds <- dim(ID)[1];
+    for(i in 1:inds){
+        if(ID[i, 6] %in% Rmat[,1] == FALSE){
+            MomP <- -1;
+        }else{
+            MomP <- which(Rmat[,1] == ID[i, 6]);
+        }
+        if(ID[i, 7] %in% Rmat[,1] == FALSE){
+            DadP <- -1;
+        }else{
+            DadP <- which(Rmat[,1] == ID[i, 7]);
+        }
+        # Inbreeding coefficient
+        if(MomP < 0 | DadP < 0){
+            Rmat_new[i, i+1] <- 1; 
+        }else{
+            Rmat_new[i, i+1] <- 1 + Rmat[MomP, DadP+1]; 
+        }
+        # Kinship coefficient
+        j <- 1;
+        while(j < i){
+            if(ID[j, 6] %in% Rmat[,1] == FALSE){
+                Om <- -1;
+            }else{
+                Om <- which(Rmat[,1] == ID[j, 6]);
+            }
+            if(ID[j, 7] %in% Rmat[,1] == FALSE){
+                Od <- -1;
+            }else{
+                Od <- which(Rmat[,1] == ID[j, 7]);
+            }
+
+            if(ID[i,5] == 0 & ID[j,5] == 0){
+                if(Om < 0 | MomP < 0){
+                    w <- 0;
+                }else{
+                    if(MomP == Om){
+                        w <- 0.5 * Rmat[MomP, Om + 1];
+                    }else{
+                        w <- Rmat[MomP, Om + 1];
+                    }
+                }
+                if(Od < 0 | MomP < 0){
+                    y <- 0;
+                }else{
+                    y <- Rmat[MomP, Od + 1];
+                }
+                if(Om < 0 | DadP < 0){
+                    x <- 0;
+                }else{
+                    x <- Rmat[DadP, Om + 1];
+                }
+                if(Od < 0 | DadP < 0){
+                    z <- 0;
+                }else{
+                    if(DadP == Od){
+                        z <- 0.5 * Rmat[DadP, Od + 1];
+                    }else{
+                        z <- Rmat[DadP, Od + 1];
+                    }
+                }
+            }
+            rMmuP <- 0.5 * (w + y);
+            rDmuP <- 0.5 * (x + z);
+            rval  <- 0.5 * (rMmuP + rDmuP);
+
+            Rmat_new[i, j+1] <- rval;
+            Rmat_new[j, i+1] <- rval;
+            j <- j + 1;
+        }
+    }
+
+    for(i in 1:inds){
+        for(j in 1:inds){
+            if(ID[i, 6] == ID[j, 1]){
+                if(ID[j, 6] == -1){
+                    Rmat_new[i, j+1] = 0.25;
+                    Rmat_new[j, i+1] = 0.25;
+                }    
+            }
+            if(ID[i, 7] == ID[j, 1]){
+                if(ID[j, 7] == -1){
+                    Rmat_new[i, j+1] = 0.25;
+                    Rmat_new[j, i+1] = 0.25;
+                }    
+            }
+        }
+    }
+
+    return(Rmat_new);
+}
+
+mateselect <- function(ID, Rmat_new){
+    fem <- ID[ID[,2] == 0 & ID[,5] == 0,];
+    mal <- ID[ID[,2] == 1 & ID[,5] == 0,];
+    for(i in 1:dim(fem)[1]){
+        strat <- sum(fem[i,11:20]);
+        vals  <- rep(0, dim(mal)[1]);
+        fpos  <- which(Rmat_new[,1] == i); 
+        for(j in 1:length(vals)){
+            mpos    <- which(Rmat_new[,1] == j);
+            kval    <- Rmat_new[i, j+1];
+            vals[j] <- kval * strat;
+        }
+        if(strat < 0){
+            weight <- 1 / (1 + (-1 * vals));
+            probs  <- weight / sum(weight);
+        }else{
+            weight <- 1 + vals;
+            probs  <- weight / sum(weight);
+        }
+        mate    <- sample(x = 1:dim(mal)[1], size = 1, pr = probs);
+        mateID  <- mal[mate,1];
+        matepos <- which(ID[,1] == mateID);
+        ownID   <- fem[i, 1];
+        ownpos  <- which(ID[,1] == ownID);
+        ID[ownpos, 9]  <- mateID;
+        ID[matepos, 9] <- ownID;
+    }
+    return(ID);
+}
+
+make_offspring <- function(ID, Rmat_new, nn = 6){
+    start_ID <- max(ID[,1]) + 1;
+    for(i in 1:dim(ID)[1]){
+        if(ID[i, 2] == 0 & ID[i, 9] > 0 & ID[i, 5] == 0){
+            mum    <- ID[i,];
+            dadpos <- which(ID[,1] == ID[i, 9]);
+            dad    <- ID[dadpos,];
+            offs   <- matrix(data = 0, nrow = nn, ncol = dim(ID)[2]);
+            offs[,1] <- start_ID:(start_ID+nn-1);
+            start_ID <- start_ID + nn;
+            offs[,2] <- rbinom(n = nn, size = 1, prob = 0.5);
+            offs[,3] <- mum[3];
+            offs[,4] <- mum[4];
+            offs[,6] <- mum[1];
+            offs[,7] <- dad[1];
+            mrpos    <- which(Rmat_new[,1] == mum[1]);
+            drpos    <- which(Rmat_new[,1] == dad[1]);
+            offs[,8] <- Rmat_new[mrpos, drpos+1];
+            offs[,11:30] <- mum[11:30];
+            dum_vec  <- rbinom(n = length(offs[,11:30]), size = 1, prob = 0.5);
+            dummy    <- matrix(data = dum_vec, nrow = dim(offs)[1]);
+            dummy[dummy > 0] <- NA;
+
+        }
+    }
+}
+
+produce_offs <- function(ID, Rmat_new, nn){
+    # NOTE: This toy model has unrealistic recombination between parents!
+    mums  <- sum(ID[,2] == 0 & ID[, 5] == 0 & ID[, 9] != 0);
+    offs  <- matrix(data = 0, nrow = mums * nn, ncol = dim(ID)[2]);
+    start <- 1;
+    for(i in 1:dim(ID)[1]){  # Unrealistic recombination saves some time.
+        if(ID[i,2] == 0 & ID[i, 5] == 0 & ID[i, 9] != 0){
+            her_off     <- matrix(data = ID[i,], nrow = nn, ncol = dim(ID)[2], 
+                                  byrow = TRUE);
+            her_off[,2] <- rbinom(n = nn, size = 1, prob = 0.5);
+            her_off[,6] <- ID[i,1];
+            her_off[,7] <- ID[i,9];
+            mum_p       <- which(Rmat_new[,1] == ID[i,1]);
+            dad_p       <- which(Rmat_new[,1] == ID[i,9]);
+            her_off[,8] <- Rmat_new[mum_p, dad_p + 1];
+            dad_o       <- which(ID[,1] == ID[i,9]);
+            dad_overlay <- matrix(data = ID[dad_o,], nrow = nn, 
+                                  ncol = dim(ID)[2], byrow = TRUE);
+            to_vec      <- rbinom(n = nn*dim(ID)[2], size = 1, prob = 0.5);
+            to_overlay  <- matrix(data = to_vec, nrow = nn);
+            to_overlay[,1:10] <- 1;
+            her_off[to_overlay < 1] <- NA;
+            her_off[is.na(her_off)] <- dad_overlay[is.na(her_off)];
+            offs[start:(start+(nn-1)), 1:dim(ID)[2]] <- her_off;
+            start <- start + nn;
+        }
+    }
+    max_ID   <- max(ID[,1]);
+    offs[,1] <- (max_ID + 1):(max_ID + dim(offs)[1]); 
+    return(offs);
+}
+
+mortality <- function(offs, beta){
+    depression        <- exp(-1 * beta * offs[,8]);
+    alive             <- rbinom(n = dim(offs)[1], size = 1, prob = depression);
+    offs[alive < 1,5] <- -1;
+    offs              <- offs[offs[,5] > -1,];
+    return(offs);
+}
+
+mutation  <- function(offs, mu){
+    mutations <- rbinom(n = 20*dim(offs)[1], size = 1, prob = mu);
+    tot_mut   <- sum(mutations);
+    mut_mat   <- matrix(data = mutations, nrow = dim(offs)[1]);
+    mu_eff    <- rnorm(n = tot_mut, mean = 0, sd = 2);
+    mut_mat[mut_mat > 0] <- mu_eff;
+    offs[,11:30] <- offs[,11:30] + mut_mat;
+    return(offs);
+}
+
+retain <- function(ID, offs){
+    retainers <- rep(x = 0, times = dim(ID)[1]);
+    for(i in 1:dim(ID)[1]){
+        ID_num <- ID[i, 1];
+        ismum  <- sum(offs[,6] == ID_num);
+        isdad  <- sum(offs[,7] == ID_num);
+        ispar  <- ismum + isdad;
+        if(ispar < 1){
+            retainers[i] <- 1;
+        }
+    }
+    to_remove <- which(retainers == 1);
+    ID <- ID[-to_remove,];
+    return(ID);
+}
+
+get_stats <- function(ID){
+    mean_inbr <- mean(ID[,8]);
+    mean_aval <- mean(ID[,11:20]);
+    sd_aval   <- sd(ID[,11:20]);
+    mean_nval <- mean(ID[,21:30]);
+    sd_nval   <- sd(ID[,21:30]);
+    stat_vec  <- c(mean_inbr, mean_aval, sd_aval, mean_nval, sd_nval);
+    return(stat_vec);
+}
+
+immigration <- function(ID, imm, IDst){
+    max_ID     <- max(ID[,1]);
+    immigrants <- initialise_inds(N = imm);
+    avalues    <- rnorm(n = 10 * imm, mean = IDst[2], sd = IDst[3]);
+    nvalues    <- rnorm(n = 10 * imm, mean = IDst[4], sd = IDst[5]);
+    a_mat      <- matrix(data = avalues, nrow = imm);
+    n_mat      <- matrix(data = nvalues, nrow = imm);
+    immigrants[,2]     <- 1;
+    immigrants[,11:20] <- a_mat;
+    immigrants[,21:30] <- n_mat;
+    imm_IDs            <- (max_ID + 1):(max_ID + imm);
+    immigrants[,1]     <- imm_IDs;
+    ID <- rbind(ID, immigrants);
+    return(ID);
+}
+
+new_gen <- function(ID, Rmat, cost = 0, imm = 5, beta = 1, 
+                    mu = 0.01, Kf = 100, Km = 100, nn = 6){
+    N       <- dim(ID)[1];
+    death   <- rep(x = 0, times = N);
+    females <- sum(ID[,2] == 0 & ID[,5] <= 1);
+    males   <- sum(ID[,2] == 1 & ID[,5] <= 1);
+    strat   <- apply(X = ID[,11:20], MARGIN = 1, FUN = sum);
+    strat_c <- abs(strat) * cost;
+    strat_d <- rbinom(n = N, size = 1, prob = strat_c);
+    death   <- death + strat_d;
+    death   <- death + (ID[,5] > 1);
+    ID[,5]  <- -1 * death;
+    ID      <- ID[order(ID[,2], decreasing = FALSE),];
+    ID      <- ID[order(ID[,5], decreasing = FALSE),];
+    livef   <- sum(ID[,2] == 0 & ID[,5] < 2 & ID[,5] > -1);
+    livem   <- sum(ID[,2] == 1 & ID[,5] < 2 & ID[,5] > -1);
+    if(livef > Kf){
+        rm   <- livef - Kf;
+        rows <- which(ID[,2] == 0 & ID[,5] < 2 & ID[,5] > -1);
+        ID[rows[1:rm],5] <- -1;
+    }
+    if(livem > Km){
+        rm   <- livem - Km;
+        rows <- which(ID[,2] == 1 & ID[,5] < 2 & ID[,5] > -1);
+        ID[rows[1:rm],5] <- -1;
+    }
+    ID <- rbind(ID[ID[,5] >= 0,], ID[ID[,5] < 0,]);
+
+    Rmat_new <- initialise_Rmat(ID);
+    Rmat_new <- Rbuild(Rmat, ID, Rmat_new);
+
+    ID   <- mateselect(ID, Rmat_new);
+    offs <- produce_offs(ID, Rmat_new, nn);
+    offs <- mortality(offs, beta);
+    offs <- mutation(offs, mu);
+    IDst <- get_stats(ID);
+
+    ID[ID[,5] >= 0, 5] <- ID[ID[,5] >= 0,5] + 1;
+    ID[ID[,5] > 0, 5]  <- -1;
+
+    ID <- retain(ID, offs);
+    ID <- rbind(ID, offs);
+
+    ID <- immigration(ID, imm, IDst);
+
+    results <- list(ID = ID, Rmat = Rmat_new, stats = IDst);
+}
+```
+
+## Inbreeding depression
+
+##
+
+```{r lmSim, fig.show='animate', echo = FALSE}
+inputPanel(
+  sliderInput("Imm", label = "Immigrants", width="100%",
+              min = 0.0, max = 1, value = 0, step = 0.05), 
+  sliderInput("ID", label = "Inbreeding Depression", width="100%",
+              min = 0.0, max = 1, value = 0, step = 0.05), 
+  sliderInput("cost", label = "Strategy Cost", width="100%",
+              min = 0.0, max = 1, value = 0, step = 0.05), 
+  sliderInput("mu", label = "Mutation Rate", width="100%",
+              min = 0.0, max = 1, value = 0, step = 0.05), 
+  actionButton("mate", "New Generation"),
+  actionButton("reset", "Reset")
+)
+
+gen     <- reactiveValues();
+
+gen$dat <- list(ID = NULL, Rmat = NULL);
+
+Ds    <- observeEvent(input$mate, {
+
+        if( is.null(gen$dat$ID) == TRUE | is.null(gen$dat$ID) == TRUE){
+            gen$dat$ID   <- initialise_inds(N = 8);
+            gen$dat$Rmat <- initialise_Rmat(gen$dat$ID);
+        }else{
+            gen$dat <- new_gen(ID = gen$dat$ID, Rmat = gen$dat$Rmat, 
+                               Kf = 40, Km = 40, beta = 8, imm = 1);
+        }
+})
+
+rs    <- observeEvent(input$reset, {
+       gen$dat <- list(ID = NULL, Rmat = NULL);
+})
+
+renderPlot({
+  par(bg = 'transparent');
+  kval <- gen$dat$Rmat;
+  kval <- as.matrix(kval);
+  kval <- kval[,-1];
+  diag(kval) <- diag(kval)/2;
+  hist(kval);
+  #size <- hist(gen$dat$ID)[1];
+  #if(5 < 6){
+  #    plot(x = 0:10, y = 0:10, type = "n", ylim = c(0, 400), cex.axis = 1.5,
+  #         cex.lab = 1.5, xlab = "Generation", ylab = "k", bg = "transparent");
+  #    points(x = 2, y = size, pch = 20, cex = 1.5, type = "b",
+  #           lwd = 2);
+  #}#else{
+#      x0 <- last - 5;
+#      x1 <- last + 5;
+#      plot(x = x0:x1, y = x0:x1, type = "n", ylim = c(0, 1), cex.axis = 1.5,
+#           cex.lab = 1.5, xlab = "Generation", ylab = "k");
+#      points(x = ts$df[x0:x1,1], y = ts$df[x0:x1,2], pch = 20, cex = 1.5, type = "b",
+#             lwd = 2);
+#  }
+})
+```
+
+## Inbreeding tolerance
+
+## Inbreeding avoidance
+
+## Inbreeding preference
+
+## Parker's model
 

### 2018-02-23 presentation/toy_model.R
Minor edits

@@ -329,16 +329,25 @@ Rmat <- initialise_Rmat(ID);
 
 
 
-gen  <- new_gen(ID = ID, Rmat = Rmat, Kf = 40, Km = 40, beta = 8);
-
+gen  <- new_gen(ID = ID, Rmat = Rmat, Kf = 60, Km = 60, beta = 8, imm = 1);
 ID   <- gen$ID;
 Rmat <- gen$Rmat;
 
+tmat <- Rmat[,2:dim(Rmat)[1]]
+diag(tmat) <- NA;
+hist(tmat, xlim = c(0, 1), ylim = c(0, 40), freq = FALSE, col = "black");
 
 
 
 
 
+
+hist(ID[,11:20]);
+
+
+
+
+which(Rmat[,2:dim(Rmat)[1]] > 1)
 
 
 

### 2018-02-23 presentation/inbreeding.Rmd
Working nice figure of allele change

@@
   sliderInput("Imm", label = "Immigrants", width="100%",
-              min = 0.0, max = 1, value = 0, step = 0.05), 
+              min = 0.0, max = 10, value = 0, step = 1), 
   sliderInput("ID", label = "Inbreeding Depression", width="100%",
-              min = 0.0, max = 1, value = 0, step = 0.05), 
+              min = 0.0, max = 10, value = 0, step = 0.5), 
   sliderInput("cost", label = "Strategy Cost", width="100%",
-              min = 0.0, max = 1, value = 0, step = 0.05), 
+              min = 0.0, max = 0.1, value = 0, step = 0.01), 
   sliderInput("mu", label = "Mutation Rate", width="100%",
-              min = 0.0, max = 1, value = 0, step = 0.05), 
+              min = 0.0, max = 0.1, value = 0, step = 0.01), 
   actionButton("mate", "New Generation"),
@@
 gen     <- reactiveValues();
+iter    <- reactiveValues();
 
 gen$dat  <- list(ID = NULL, Rmat = NULL);
+iter$all <- 0;
+iter$nue <- 0;
 
 Ds    <- observeEvent(input$mate, {
-
         if( is.null(gen$dat$ID) == TRUE | is.null(gen$dat$ID) == TRUE){
@@
             gen$dat  <- new_gen(ID = gen$dat$ID, Rmat = gen$dat$Rmat, 
-                               Kf = 40, Km = 40, beta = 8, imm = 1);
+                                Kf = 40, Km = 40, beta = input$ID, 
+                                imm = input$Imm, cost = input$cost, 
+                                mu = input$mu);
+            iter$all <- c(iter$all, mean(gen$dat$ID[,11:20]));
+            iter$nue <- c(iter$nue, mean(gen$dat$ID[,21:30]));
         }
@@
        gen$dat <- list(ID = NULL, Rmat = NULL);
+       iter$all <- 0;
+       iter$nue <- 0;
 })
@@
   par(bg = 'transparent');
-  kval <- gen$dat$Rmat;
-  kval <- as.matrix(kval);
-  kval <- kval[,-1];
-  diag(kval) <- diag(kval)/2;
-  hist(kval);
-  #size <- hist(gen$dat$ID)[1];
-  #if(5 < 6){
-  #    plot(x = 0:10, y = 0:10, type = "n", ylim = c(0, 400), cex.axis = 1.5,
-  #         cex.lab = 1.5, xlab = "Generation", ylab = "k", bg = "transparent");
-  #    points(x = 2, y = size, pch = 20, cex = 1.5, type = "b",
-  #           lwd = 2);
-  #}#else{
-#      x0 <- last - 5;
-#      x1 <- last + 5;
-#      plot(x = x0:x1, y = x0:x1, type = "n", ylim = c(0, 1), cex.axis = 1.5,
-#           cex.lab = 1.5, xlab = "Generation", ylab = "k");
-#      points(x = ts$df[x0:x1,1], y = ts$df[x0:x1,2], pch = 20, cex = 1.5, type = "b",
-#             lwd = 2);
-#  }
+  malle <- iter$all;
+  mneut <- iter$nue
+  gens  <- 1:length(iter$all);
+  if(length(gens) < 6){
+      plot(x = 0:10, y = 0:10, type = "n", ylim = c(-1, 1), cex.axis = 1.5,
+           cex.lab = 1.5, xlab = "Generation", ylab = "Inbreeding strategy", 
+           bg = "transparent");
+      abline(h = 0, lty = "dotted", lwd = 0.8);
+      polygon(x=c(-0.125, 2.5, 2.5, -0.125), y=c(0.825, 0.825, 1.1, 1.1), 
+              border=NA, col="black");
+      polygon(x=c(-0.125, 2.5, 2.5, -0.125), y=c(-0.825, -0.825, -1.1, -1.1), 
+              border=NA, col="black");
+      abline(v = -0.125, lwd = 4);
+      text(x = 0, y = 0.95, labels = "Inbreeding Preference", cex = 1.5, 
+           col = "white", pos = 4);
+      text(x = 0, y = -0.95, labels = "Inbreeding Avoidance", cex = 1.5, 
+           col = "white", pos = 4);
+      if(length(gens) > 0){
+          points(x = gens, y = malle, pch = 20, cex = 1.5, type = "b",
+                 lwd = 2, col = "black");
+      }
+  }else{
+      x0 <- length(gens) - 5;
+      x1 <- length(gens) + 5;
+      plot(x = x0:x1, y = 0:10, type = "n", ylim = c(-1, 1), cex.axis = 1.5,
+           cex.lab = 1.5, xlab = "Generation", ylab = "Inbreeding strategy", 
+           bg = "transparent");
+      abline(h = 0, lty = "dotted", lwd = 0.8);
+      polygon(x=c(x0-0.125, x0+2.5, x0+2.5, x0-0.125), 
+              y=c(0.825, 0.825, 1.1, 1.1), border=NA, col="black");
+      polygon(x=c(x0-0.125, x0+2.5, x0+2.5, x0-0.125), 
+              y=c(-0.825, -0.825, -1.1, -1.1), border=NA, col="black");
+      abline(v = x0-0.125, lwd = 4);
+      text(x = x0, y = 0.95, labels = "Inbreeding Preference", cex = 1.5, 
+           col = "white", pos = 4);
+      text(x = x0, y = -0.95, labels = "Inbreeding Avoidance", cex = 1.5, 
+           col = "white", pos = 4);
+      points(x = gens, y = malle, pch = 20, cex = 1.5, type = "b",
+                 lwd = 2, col = "black");
+  }
 })

### 2018-02-23 presentation/inbreeding.Rmd
Figured out how to have multiple inputs while working with the same output

@@
 iter$nue <- 0;
+iter$kva <- 0;
 
@@
             iter$nue <- c(iter$nue, mean(gen$dat$ID[,21:30]));
+            kvalues  <- gen$dat$Rmat;
+            kvalues  <- kvalues[,-1];
+            if(dim(kvalues)[1] > 80){
+                kvalues <- kvalues[1:80, 1:80];
+            }
+            diag(kvalues) <- NA ;#diag(kvalues) * 0.5;
+            iter$kva <- kvalues;
         }
@@
        iter$nue <- 0;
+       iter$kva <- 0;
 })
@@
   if(length(gens) < 6){
-      plot(x = 0:10, y = 0:10, type = "n", ylim = c(-1, 1), cex.axis = 1.5,
+      par(mfrow = c(1, 2));
+      plot(x = 0:5, y = 0:5, type = "n", ylim = c(-1, 1), cex.axis = 1.5,
            cex.lab = 1.5, xlab = "Generation", ylab = "Inbreeding strategy", 
@@
       abline(h = 0, lty = "dotted", lwd = 0.8);
-      polygon(x=c(-0.125, 2.5, 2.5, -0.125), y=c(0.825, 0.825, 1.1, 1.1), 
+      polygon(x=c(-0.125, 2.65, 2.65, -0.125), y=c(0.825, 0.825, 1.1, 1.1), 
               border=NA, col="black");
-      polygon(x=c(-0.125, 2.5, 2.5, -0.125), y=c(-0.825, -0.825, -1.1, -1.1), 
+      polygon(x=c(-0.125, 2.65, 2.65, -0.125), y=c(-0.825, -0.825, -1.1, -1.1), 
               border=NA, col="black");
@@
                  lwd = 2, col = "black");
+          par(mar = c(7, 5, 5, 5));
+          hist(iter$kva, xlim = c(0, 1), ylim = c(0, 20), freq = FALSE, col = "black",
+               yaxt = "n", ylab = "", main = "", xlab = "", 
+               breaks = seq(from = 0, to = 1, by = 0.05), cex.axis = 1.5);
+          title(xlab = "Kinship (k)", line = 4, cex.axis = 1.5, cex.lab = 1.5);
+          box(lwd = 3);
       }
@@
       x0 <- length(gens) - 5;
-      x1 <- length(gens) + 5;
-      plot(x = x0:x1, y = 0:10, type = "n", ylim = c(-1, 1), cex.axis = 1.5,
+      x1 <- length(gens) + 0;
+      par(mfrow = c(1, 2));
+      plot(x = x0:x1, y = 0:5, type = "n", ylim = c(-1, 1), cex.axis = 1.5,
            cex.lab = 1.5, xlab = "Generation", ylab = "Inbreeding strategy", 
@@
       abline(h = 0, lty = "dotted", lwd = 0.8);
-      polygon(x=c(x0-0.125, x0+2.5, x0+2.5, x0-0.125), 
+      polygon(x=c(x0-0.125, x0+2.65, x0+2.65, x0-0.125), 
               y=c(0.825, 0.825, 1.1, 1.1), border=NA, col="black");
-      polygon(x=c(x0-0.125, x0+2.5, x0+2.5, x0-0.125), 
+      polygon(x=c(x0-0.125, x0+2.65, x0+2.65, x0-0.125), 
               y=c(-0.825, -0.825, -1.1, -1.1), border=NA, col="black");
@@
                  lwd = 2, col = "black");
+      par(mar = c(7, 5, 5, 5));
+      hist(iter$kva, xlim = c(0, 1), ylim = c(0, 20), freq = FALSE, col = "black",
+           yaxt = "n", ylab = "", main = "", xlab = "", 
+           breaks = seq(from = 0, to = 1, by = 0.05), cex.axis = 1.5);
+      title(xlab = "Kinship (k)", line = 4, cex.axis = 1.5, cex.lab = 1.5);
+      box(lwd = 3);
   }
@@
 ## Inbreeding tolerance
+
+##
+
+```{r lmSim2, fig.show='animate', echo = FALSE}
+inputPanel(
+  sliderInput("Imm2", label = "Immigrants", width="100%",
+              min = 0.0, max = 10, value = 0, step = 1), 
+  sliderInput("ID2", label = "Inbreeding Depression", width="100%",
+              min = 0.0, max = 10, value = 0, step = 0.5), 
+  sliderInput("cost2", label = "Strategy Cost", width="100%",
+              min = 0.0, max = 0.1, value = 0, step = 0.01), 
+  sliderInput("mu2", label = "Mutation Rate", width="100%",
+              min = 0.0, max = 0.1, value = 0, step = 0.01), 
+  actionButton("mate2", "New Generation"),
+  actionButton("reset2", "Reset")
+)
+
+Ds    <- observeEvent(input$mate2, {
+        if( is.null(gen$dat$ID) == TRUE | is.null(gen$dat$ID) == TRUE){
+            gen$dat$ID   <- initialise_inds(N = 8);
+            gen$dat$Rmat <- initialise_Rmat(gen$dat$ID);
+        }else{
+            gen$dat  <- new_gen(ID = gen$dat$ID, Rmat = gen$dat$Rmat, 
+                                Kf = 40, Km = 40, beta = input$ID2, 
+                                imm = input$Imm2, cost = input$cost2, 
+                                mu = input$mu2);
+            iter$all <- c(iter$all, mean(gen$dat$ID[,11:20]));
+            iter$nue <- c(iter$nue, mean(gen$dat$ID[,21:30]));
+            kvalues  <- gen$dat$Rmat;
+            kvalues  <- kvalues[,-1];
+            if(dim(kvalues)[1] > 80){
+                kvalues <- kvalues[1:80, 1:80];
+            }
+            diag(kvalues) <- NA ;#diag(kvalues) * 0.5;
+            iter$kva <- kvalues;
+        }
+})
+
+rs    <- observeEvent(input$reset2, {
+       gen$dat <- list(ID = NULL, Rmat = NULL);
+       iter$all <- 0;
+       iter$nue <- 0;
+       iter$kva <- 0;
+})
+
+renderPlot({
+  par(bg = 'transparent');
+  malle <- iter$all;
+  mneut <- iter$nue
+  gens  <- 1:length(iter$all);
+  if(length(gens) < 6){
+      par(mfrow = c(1, 2));
+      plot(x = 0:5, y = 0:5, type = "n", ylim = c(-1, 1), cex.axis = 1.5,
+           cex.lab = 1.5, xlab = "Generation", ylab = "Inbreeding strategy", 
+           bg = "transparent");
+      abline(h = 0, lty = "dotted", lwd = 0.8);
+      polygon(x=c(-0.125, 2.65, 2.65, -0.125), y=c(0.825, 0.825, 1.1, 1.1), 
+              border=NA, col="black");
+      polygon(x=c(-0.125, 2.65, 2.65, -0.125), y=c(-0.825, -0.825, -1.1, -1.1), 
+              border=NA, col="black");
+      abline(v = -0.125, lwd = 4);
+      text(x = 0, y = 0.95, labels = "Inbreeding Preference", cex = 1.5, 
+           col = "white", pos = 4);
+      text(x = 0, y = -0.95, labels = "Inbreeding Avoidance", cex = 1.5, 
+           col = "white", pos = 4);
+      if(length(gens) > 0){
+          points(x = gens, y = malle, pch = 20, cex = 1.5, type = "b",
+                 lwd = 2, col = "black");
+          par(mar = c(7, 5, 5, 5));
+          hist(iter$kva, xlim = c(0, 1), ylim = c(0, 20), freq = FALSE, col = "black",
+               yaxt = "n", ylab = "", main = "", xlab = "", 
+               breaks = seq(from = 0, to = 1, by = 0.05), cex.axis = 1.5);
+          title(xlab = "Kinship (k)", line = 4, cex.axis = 1.5, cex.lab = 1.5);
+          box(lwd = 3);
+      }
+  }else{
+      x0 <- length(gens) - 5;
+      x1 <- length(gens) + 0;
+      par(mfrow = c(1, 2));
+      plot(x = x0:x1, y = 0:5, type = "n", ylim = c(-1, 1), cex.axis = 1.5,
+           cex.lab = 1.5, xlab = "Generation", ylab = "Inbreeding strategy", 
+           bg = "transparent");
+      abline(h = 0, lty = "dotted", lwd = 0.8);
+      polygon(x=c(x0-0.125, x0+2.65, x0+2.65, x0-0.125), 
+              y=c(0.825, 0.825, 1.1, 1.1), border=NA, col="black");
+      polygon(x=c(x0-0.125, x0+2.65, x0+2.65, x0-0.125), 
+              y=c(-0.825, -0.825, -1.1, -1.1), border=NA, col="black");
+      abline(v = x0-0.125, lwd = 4);
+      text(x = x0, y = 0.95, labels = "Inbreeding Preference", cex = 1.5, 
+           col = "white", pos = 4);
+      text(x = x0, y = -0.95, labels = "Inbreeding Avoidance", cex = 1.5, 
+           col = "white", pos = 4);
+      points(x = gens, y = malle, pch = 20, cex = 1.5, type = "b",
+                 lwd = 2, col = "black");
+      par(mar = c(7, 5, 5, 5));
+      hist(iter$kva, xlim = c(0, 1), ylim = c(0, 20), freq = FALSE, col = "black",
+           yaxt = "n", ylab = "", main = "", xlab = "", 
+           breaks = seq(from = 0, to = 1, by = 0.05), cex.axis = 1.5);
+      title(xlab = "Kinship (k)", line = 4, cex.axis = 1.5, cex.lab = 1.5);
+      box(lwd = 3);
+  }
+})
+```
 

### 2018-02-23 presentation/toy_model.R
More playing around getting the interaction to work

@@ -319,23 +319,111 @@ new_gen <- function(ID, Rmat, cost = 0, imm = 5, beta = 1,
 
 
 
+females  <- sum(ID[,2] == 0 & ID[,5] == 0);
+males    <- sum(ID[,2] == 1 & ID[,5] == 0);
+distrb   <- seq(from = 0, to = 2*pi, length.out = females + males + 1);
+pchs     <- c(rep(15, females), rep(16, males));
+cols     <- c(rep("blue", females), rep("red", males));
+
+
+plot(x = 0, y = 0, xlim = c(-2, 2), ylim = c(-2, 2), xaxt = "n",
+     yaxt = "n", xlab = "", ylab = "", type = "n");
+
+points(x = 2 * cos(distrb), y = 2 * sin(distrb), pch = pchs, col = cols, 
+       cex = 3);
+
+
+
+mate_connect <- function(ID){
+    living     <- ID[ID[,5] == 0,];
+    fem_count  <- sum(living[,2] == 0);
+    livsor     <- living[order(living[,2]),];
+    livsor[,3] <- 1:dim(livsor)[1];
+    pointpairs <- matrix(data = 0, nrow = fem_count, ncol = 4);
+    for(i in 1:dim(livsor)[1]){
+        if(livsor[i, 2] == 0){
+            femID <- livsor[i, 1];
+            malID <- livsor[i, 9];
+            femps <- i;
+            malps <- which(livsor[,1] == malID);
+            pointpairs[i, 1] <- femID;
+            pointpairs[i, 2] <- malID;
+            pointpairs[i, 3] <- femps;
+        }
+    }
+    uniquem <- unique(pointpairs[,2]);
+    for(i in 1:dim(pointpairs)[1]){
+        pointpairs[i, 4] <- which(uniquem == pointpairs[i, 2]) + fem_count;
+    }
+    return(pointpairs);
+}
 
 
 
 
 
-ID   <- initialise_inds(N = 30);
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+iallofem <- c(rep(1, females), rep(2, males));
+lallofem <- 2 * pi * (1:length(iallofem)) / length(iallofem);
+xallofem <- cos(allofem);
+yallofem <- sin(allofem);
+
[…]

### 2018-02-23 presentation/toy_model.R
Finally got the interactions working

@@ -186,6 +186,7 @@ produce_offs <- function(ID, Rmat_new, nn){
             mum_p       <- which(Rmat_new[,1] == ID[i,1]);
             dad_p       <- which(Rmat_new[,1] == ID[i,9]);
             her_off[,8] <- Rmat_new[mum_p, dad_p + 1];
+            her_off[,9] <- -1;
             dad_o       <- which(ID[,1] == ID[i,9]);
             dad_overlay <- matrix(data = ID[dad_o,], nrow = nn, 
                                   ncol = dim(ID)[2], byrow = TRUE);
@@ -300,15 +301,17 @@ new_gen <- function(ID, Rmat, cost = 0, imm = 5, beta = 1,
     offs <- mutation(offs, mu);
     IDst <- get_stats(ID);
     
-    ID[ID[,5] >= 0, 5] <- ID[ID[,5] >= 0,5] + 1;
-    ID[ID[,5] > 0, 5]  <- -1;
+    lgn  <- ID[ID[,5] == 0,];
+    
+    ID[ID[,5] >= 0, 5] <- -1;
     
     ID <- retain(ID, offs);
     ID <- rbind(ID, offs);
     
     ID <- immigration(ID, imm, IDst);
     
-    results <- list(ID = ID, Rmat = Rmat_new, stats = IDst);
+    results <- list(ID = ID, Rmat = Rmat_new, stats = IDst, last_gen = lgn);
+    return(results);
 }
 
 
@@ -332,37 +335,75 @@ plot(x = 0, y = 0, xlim = c(-2, 2), ylim = c(-2, 2), xaxt = "n",
 points(x = 2 * cos(distrb), y = 2 * sin(distrb), pch = pchs, col = cols, 
        cex = 3);
 
-
-
 mate_connect <- function(ID){
     living     <- ID[ID[,5] == 0,];
     fem_count  <- sum(living[,2] == 0);
+    mal_count  <- sum(living[,2] == 1);
     livsor     <- living[order(living[,2]),];
     livsor[,3] <- 1:dim(livsor)[1];
-    pointpairs <- matrix(data = 0, nrow = fem_count, ncol = 4);
+    pointpairs <- matrix(data = 0, nrow = dim(livsor)[1], ncol = 8);
+    pointpairs[,1] <- livsor[,1];
     for(i in 1:dim(livsor)[1]){
         if(livsor[i, 2] == 0){
[…]

### 2018-02-23 presentation/inbreeding.Rmd
Presentation includes interaction mating map

@@
             her_off[,8] <- Rmat_new[mum_p, dad_p + 1];
+            her_off[,9] <- -1;
             dad_o       <- which(ID[,1] == ID[i,9]);
@@
 
-    ID[ID[,5] >= 0, 5] <- ID[ID[,5] >= 0,5] + 1;
-    ID[ID[,5] > 0, 5]  <- -1;
+    lgn  <- ID[ID[,5] == 0,];
+
+    ID[ID[,5] >= 0, 5] <- -1;
 
@@
 
-    results <- list(ID = ID, Rmat = Rmat_new, stats = IDst);
+    results <- list(ID = ID, Rmat = Rmat_new, stats = IDst, last_gen = lgn);
+    return(results);
+}
+
+mate_connect <- function(ID){
+    living     <- ID[ID[,5] == 0,];
+    fem_count  <- sum(living[,2] == 0);
+    mal_count  <- sum(living[,2] == 1);
+    livsor     <- living[order(living[,2]),];
+    livsor[,3] <- 1:dim(livsor)[1];
+    pointpairs <- matrix(data = 0, nrow = dim(livsor)[1], ncol = 8);
+    pointpairs[,1] <- livsor[,1];
+    for(i in 1:dim(livsor)[1]){
+        if(livsor[i, 2] == 0){
+            femID <- livsor[i, 1];
+            malID <- livsor[i, 9];
+            femps <- i;
+            malps <- which(livsor[,1] == malID);
+            pointpairs[i, 2] <- malID;
+        }
+    }
+    pointpairs[,3] <- 1:dim(pointpairs)[1];
+    distr <- seq(from = 0, to = 2*pi, length.out = dim(pointpairs)[1]);
+    for(i in 1:dim(pointpairs)[1]){
+        xplace            <- 2 * cos(distr[pointpairs[i, 3]]);
+        yplace            <- 2 * sin(distr[pointpairs[i, 3]]);
+        pointpairs[i, 5]  <- xplace;
+        pointpairs[i, 6]  <- yplace;
+    }
+    for(i in 1:dim(pointpairs)[1]){
+        if(i <= fem_count){
+            matepos           <- which(pointpairs[,1] == pointpairs[i, 2]);
+            pointpairs[i, 4]  <- matepos;
+            pointpairs[i, 7]  <- pointpairs[matepos, 5];
+            pointpairs[i, 8]  <- pointpairs[matepos, 6];
+        }
+    }
+    return(pointpairs);
 }
@@
 iter    <- reactiveValues();
+mtt     <- reactiveValues();
 
-gen$dat  <- list(ID = NULL, Rmat = NULL);
+gen$dat  <- list(ID = NULL, Rmat = NULL, lgn = NULL);
 iter$all <- 0;
@@
 iter$kva <- 0;
+iter$mkv <- 0;
+mtt$dat  <- NULL;
 
@@
             iter$kva <- kvalues;
+            iter$mkv <- c(iter$mkv, mean(kvalues, na.rm = TRUE));
+            mtID     <- gen$dat$last_gen;
+            mtt$dat  <- mate_connect(mtID);
         }
@@
        iter$kva <- 0;
+       iter$mkv <- 0;
 })
@@
   mneut <- iter$nue
+  mkval <- iter$mkv
   gens  <- 1:length(iter$all);
@@
       par(mfrow = c(1, 2));
-      plot(x = 0:5, y = 0:5, type = "n", ylim = c(-1, 1), cex.axis = 1.5,
-           cex.lab = 1.5, xlab = "Generation", ylab = "Inbreeding strategy", 
+      if(length(gens) > 1){
+          dat <- mtt$dat;
+          femrow <- 1:sum(dat[,2] > 0);
+          malrow <- (sum(dat[,2] > 0) + 1):dim(dat)[1];
+          plot(x = dat[, 5], y = dat[, 6], pch = 15, col = "blue", cex = 1.25,
+               xlim = c(-2, 2), ylim = c(-2, 2), xaxt = "n", yaxt = "n", xlab = "",
+               ylab = "", type = "n", bty = "n");
+          text(x = -2, y = -2, pos = 4, col = "red", labels = "Males", cex = 1.75);
+          text(x = -2, y =  2, pos = 4, col = "blue", labels = "Females", cex = 1.75);
+          arrows(x0 = dat[femrow,5], x1 = dat[femrow,7], y0 = dat[femrow,6], 
+              y1 = dat[femrow,8], length = 0, lwd = 2);
+          points(x = dat[femrow, 5], y = dat[femrow, 6], pch = 15, col = "blue", cex = 1.25);
+          points(x = dat[malrow, 5], y = dat[malrow, 6], pch = 16, col = "red", cex = 1.25);
+          plot(x = 0:5, y = 0:5, type = "n", ylim = c(0, 1), cex.axis = 1.5,
+               cex.lab = 1.5, xlab = "Generation", ylab = "Mean Kinship", 
                bg = "transparent");
-      abline(h = 0, lty = "dotted", lwd = 0.8);
-      polygon(x=c(-0.125, 2.65, 2.65, -0.125), y=c(0.825, 0.825, 1.1, 1.1), 
-              border=NA, col="black");
-      polygon(x=c(-0.125, 2.65, 2.65, -0.125), y=c(-0.825, -0.825, -1.1, -1.1), 
-              border=NA, col="black");
-      abline(v = -0.125, lwd = 4);
-      text(x = 0, y = 0.95, labels = "Inbreeding Preference", cex = 1.5, 
-           col = "white", pos = 4);
-      text(x = 0, y = -0.95, labels = "Inbreeding Avoidance", cex = 1.5, 
-           col = "white", pos = 4);
+          points(x = gens, y = mkval, pch = 20, cex = 1.5, type = "b",
+                 lwd = 2, col = "black");
+      }else{
+          plot.new();
+      }
+  }else{
+      par(mfrow = c(1, 2));
+      dat <- mtt$dat;
+      femrow <- 1:sum(dat[,2] > 0);
+      malrow <- (sum(dat[,2] > 0) + 1):dim(dat)[1];
+      plot(x = dat[, 5], y = dat[, 6], pch = 15, col = "blue", cex = 1.25,
+           xlim = c(-2, 2), ylim = c(-2, 2), xaxt = "n", yaxt = "n", xlab = "",
+           ylab = "", type = "n", bty = "n");
+           arrows(x0 = dat[femrow,5], x1 = dat[femrow,7], y0 = dat[femrow,6], 
+           y1 = dat[femrow,8], length = 0, lwd = 2);
+      text(x = -2, y = -2, pos = 4, col = "red", labels = "Males", cex = 1.75);
+      text(x = -2, y =  2, pos = 4, col = "blue", labels = "Females", cex = 1.75);
+      points(x = dat[femrow, 5], y = dat[femrow, 6], pch = 15, col = "blue", cex = 1.25);
+      points(x = dat[malrow, 5], y = dat[malrow, 6], pch = 15, col = "red", cex = 1.25);
+      x0 <- length(gens) - 5;
+      x1 <- length(gens) + 0;
+      plot(x = x0:x1, y = 0:5, type = "n", ylim = c(0, 1), cex.axis = 1.5,
+           cex.lab = 1.5, xlab = "Generation", ylab = "Mean Kinship", 
+           bg = "transparent");
+      points(x = gens, y = mkval, pch = 20, cex = 1.5, type = "b",
+                 lwd = 2, col = "black");
+  }
+})
+```
+
+## Inbreeding tolerance
+
+##
+
+```{r lmSim3, fig.show='animate', echo = FALSE}
+inputPanel(
+  sliderInput("Imm3", label = "Immigrants", width="100%",
+              min = 0.0, max = 10, value = 0, step = 1), 
+  sliderInput("ID3", label = "Inbreeding Depression", width="100%",
+              min = 0.0, max = 10, value = 0, step = 0.5), 
+  sliderInput("cost3", label = "Strategy Cost", width="100%",
+              min = 0.0, max = 0.1, value = 0, step = 0.01), 
+  sliderInput("mu3", label = "Mutation Rate", width="100%",
+              min = 0.0, max = 0.1, value = 0, step = 0.01), 
+  actionButton("mate3", "New Generation"),
+  actionButton("reset3", "Reset")
+)
+
+gen     <- reactiveValues();
+iter    <- reactiveValues();
+
+gen$dat  <- list(ID = NULL, Rmat = NULL);
+iter$all <- 0;
+iter$nue <- 0;
+iter$kva <- 0;
+iter$mkv <- 0;
+
+Ds    <- observeEvent(input$mate3, {
+        if( is.null(gen$dat$ID) == TRUE | is.null(gen$dat$ID) == TRUE){
+            gen$dat$ID   <- initialise_inds(N = 8);
+            gen$dat$Rmat <- initialise_Rmat(gen$dat$ID);
+        }else{
+            gen$dat  <- new_gen(ID = gen$dat$ID, Rmat = gen$dat$Rmat, 
+                                Kf = 40, Km = 40, beta = input$ID3, 
+                                imm = input$Imm3, cost = input$cost3, 
+                                mu = input$mu3);
+            iter$all <- c(iter$all, mean(gen$dat$ID[,11:20]));
+            iter$nue <- c(iter$nue, mean(gen$dat$ID[,21:30]));
+            kvalues  <- gen$dat$Rmat;
+            kvalues  <- kvalues[,-1];
+            if(dim(kvalues)[1] > 80){
+                kvalues <- kvalues[1:80, 1:80];
+            }
+            diag(kvalues) <- NA ;#diag(kvalues) * 0.5;
+            iter$kva <- kvalues;
+            iter$mkv <- c(iter$mkv, mean(kvalues, na.rm = TRUE));
+        }
+})
+
+rs    <- observeEvent(input$reset3, {
+       gen$dat <- list(ID = NULL, Rmat = NULL);
+       iter$all <- 0;
+       iter$nue <- 0;
+       iter$kva <- 0;
+       iter$mkv <- 0;
+})
+
+renderPlot({
+  par(bg = 'transparent');
+  malle <- iter$all;
+  mneut <- iter$nue
+  mkval <- iter$mkv
+  gens  <- 1:length(iter$all);
+  if(length(gens) < 6){
+      par(mfrow = c(1, 2));
       if(length(gens) > 0){
-          points(x = gens, y = malle, pch = 20, cex = 1.5, type = "b",
-                 lwd = 2, col = "black");
           par(mar = c(7, 5, 5, 5));
@@
           box(lwd = 3);
+          plot(x = 0:5, y = 0:5, type = "n", ylim = c(0, 1), cex.axis = 1.5,
+               cex.lab = 1.5, xlab = "Generation", ylab = "Mean Kinship", 
+               bg = "transparent");
+          points(x = gens, y = mkval, pch = 20, cex = 1.5, type = "b",
+                 lwd = 2, col = "black");
+      }else{
+          plot.new();
       }
@@
       x1 <- length(gens) + 0;
-      par(mfrow = c(1, 2));
-      plot(x = x0:x1, y = 0:5, type = "n", ylim = c(-1, 1), cex.axis = 1.5,
-           cex.lab = 1.5, xlab = "Generation", ylab = "Inbreeding strategy", 
-           bg = "transparent");
-      abline(h = 0, lty = "dotted", lwd = 0.8);
-      polygon(x=c(x0-0.125, x0+2.65, x0+2.65, x0-0.125), 
-              y=c(0.825, 0.825, 1.1, 1.1), border=NA, col="black");
-      polygon(x=c(x0-0.125, x0+2.65, x0+2.65, x0-0.125), 
-              y=c(-0.825, -0.825, -1.1, -1.1), border=NA, col="black");
-      abline(v = x0-0.125, lwd = 4);
-      text(x = x0, y = 0.95, labels = "Inbreeding Preference", cex = 1.5, 
-           col = "white", pos = 4);
-      text(x = x0, y = -0.95, labels = "Inbreeding Avoidance", cex = 1.5, 
-           col = "white", pos = 4);
-      points(x = gens, y = malle, pch = 20, cex = 1.5, type = "b",
-                 lwd = 2, col = "black");
-      par(mar = c(7, 5, 5, 5));
+      par(mfrow = c(1, 2), mar = c(7, 5, 5, 5));
       hist(iter$kva, xlim = c(0, 1), ylim = c(0, 20), freq = FALSE, col = "black",
@@
       box(lwd = 3);
+      plot(x = x0:x1, y = 0:5, type = "n", ylim = c(0, 1), cex.axis = 1.5,
+           cex.lab = 1.5, xlab = "Generation", ylab = "Mean Kinship", 
+           bg = "transparent");
+      points(x = gens, y = mkval, pch = 20, cex = 1.5, type = "b",
+                 lwd = 2, col = "black");
   }
@@
 
-## Inbreeding tolerance
+## More tolerance
 
@@
             iter$kva <- kvalues;
+            iter$mkv <- c(iter$mkv, mean(kvalues, na.rm = TRUE));
         }

### 2018-02-24 presentation/inbreeding.Rmd
Fix input so starts with useful parameters

@@
   sliderInput("Imm2", label = "Immigrants", width="100%",
-              min = 0.0, max = 10, value = 0, step = 1), 
+              min = 0.0, max = 10, value = 2, step = 1), 
   sliderInput("ID2", label = "Inbreeding Depression", width="100%",
-              min = 0.0, max = 10, value = 0, step = 0.5), 
+              min = 0.0, max = 10, value = 8, step = 0.5), 
   sliderInput("cost2", label = "Strategy Cost", width="100%",

### 2018-02-26 presentation/inbreeding.Rmd
Sketch out some introductory slides

@@
 ---
+
+<style>
+div.footnotes {
+  position: absolute;
+  bottom: 0;
+  margin-bottom: 10px;
+  width: 80%;
+  font-size: 0.6em;
+}
+</style>
+
+<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>
+
+<script>
+  $(document).ready(function() {
+    $('slide:not(.backdrop):not(.title-slide)').append('<div class=\"footnotes\">');
+
+    $('footnote').each(function(index) {
+      var text  = $(this).html();
+      var fnNum = (index+1).toString().sup();
+      $(this).html(text + fnNum);
+
+      var footnote   = fnNum + ': ' + $(this).attr('content') + '<br/>';
+      var oldContent = $(this).parents('slide').children('div.footnotes').html();
+      var newContent = oldContent + footnote;
+      $(this).parents('slide').children('div.footnotes').html(newContent);
+    });
+  });
+</script>
 
@@
 
+## Inbreeding
+
+- Define relatedness
+
 ## Inbreeding depression
+
+- What inbreeding depression is, exactly.
+
+## Inbreeding depression
+
+- What are the consequences of inbreeding depression.
+
+## Inbreeding behaviour
+
+- What do we exect to see given inbreeding depression?
+
+- inbreeding avoidance
+- inbreeding preference
+- inbreeding tolerance
+
+## Inbreeding theory
+
+Describe Parker's model
+
+- Resource and mate limited sexes
+- Mate encounter, opportunity to outbreed assumed
+
+## Inbreeding theory
+
+<div class = "columns-2">
+
+```{r echo = FALSE, fig.height = 4, fig.width = 5}
+inputPanel(
+  sliderInput("rr", label = "Relatedness", width="100%",
+              min = 0.0, max = 1, value = 0, step = 0.05), 
+  sliderInput("dd", label = "Inbreeding Depression", width="100%",
+              min = 0.0, max = 1, value = 0, step = 0.1)
+)
+par(bg = 'transparent', mar = c(0.5, 0.5, 0.5, 0.5));
+plot(x = 1:10, y = 1:10, xaxt = "n", yaxt = "n", xlab = "", ylab = "");
+# Add see-saw function here to animate the balance
+```
+
+<br><br>
+
+- Parker's model
+- Add a see-saw plot that weighs relatedness versus inbreeding depression
+
+$$\frac{n}{2} (1 + r)(1 - \delta) > \frac{n}{2}$$
+
+Is inclusive fitness from inbreeding (left) greater than inclusive fitness from outbreeding?
+
+$$\delta < \frac{r}{1+r}$$
+
+</div>
+
+## Interpreting Parker's model
+
+Some key takeaways:
+
+- Inbreeding avoidance is predicted given a sufficiently high threshold of inbreeding depression
+- Inbreeding depression thresholds differ between females and males causing sexual conflict
+- Females should prefer inbreeding below their inbreeding depression threshold (resource limited) <footnote content="The first awesoem footnote!">here</footnote>:
+- Males should *tolerate* inbreeding below their threshold, but *never prefer* (sis will be fine)
 
@@
         if( is.null(gen$dat$ID) == TRUE | is.null(gen$dat$ID) == TRUE){
-            gen$dat$ID   <- initialise_inds(N = 8);
+            gen$dat$ID   <- initialise_inds(N = 80);
             gen$dat$Rmat <- initialise_Rmat(gen$dat$ID);
@@
 
-## Inbreeding tolerance
-
 ##
@@
 
-## More tolerance
-
 ##
@@
 ```
-
-## Inbreeding avoidance
-
-## Inbreeding preference
-
-## Parker's model
 

### 2018-02-26 presentation/inbreeding.Rmd
Small changes

@@
 <script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>
-
 <script>
@@
     var text  = $(this).html();
-      var fnNum = (index+1).toString().sup();
-      $(this).html(text + fnNum);
+    var fnNum = (index+1).toString();
+    $(this).html(fnNum.sup());
 
-      var footnote   = fnNum + ': ' + $(this).attr('content') + '<br/>';
+    var footnote   = fnNum + '. ' + text + '<br/>';
     var oldContent = $(this).parents('slide').children('div.footnotes').html();
@@
 - Inbreeding depression thresholds differ between females and males causing sexual conflict
-- Females should prefer inbreeding below their inbreeding depression threshold (resource limited) <footnote content="The first awesoem footnote!">here</footnote>:
+- Females should prefer inbreeding below their inbreeding depression threshold (resource limited)<footnote content="The first awesoem footnote!">here</footnote>:
 - Males should *tolerate* inbreeding below their threshold, but *never prefer* (sis will be fine)
+
+## Extensions of Parker's model
+
+## Limitations of this modelling approach
+
+## Individual-based modelling
+
+- Much different assumptions
+- See if we can get a similar answer
 

### 2018-02-27 presentation/inbreeding.Rmd
Working balance

@@
 
-## Inbreeding theory
+## Inbeeding theory
 
@@
 
-```{r echo = FALSE, fig.height = 4, fig.width = 5}
+```{r echo = FALSE}
+mbox <- function(x0, x1, y0, y1){
+    xx <- seq(from=x0, to=x1, length.out = 100);
+    yy <- seq(from=y0, to=y1, length.out = 100);
+    xd <- c(rep(x0, 100), xx, rep(x1,100), rev(xx));
+    yd <- c(yy, rep(y1,100), rev(yy), rep(y0, 100));
+    return(list(x=xd, y=yd));
+}
 inputPanel(
@@
 )
+renderPlot({
     par(bg = 'transparent', mar = c(0.5, 0.5, 0.5, 0.5));
-plot(x = 1:10, y = 1:10, xaxt = "n", yaxt = "n", xlab = "", ylab = "");
-# Add see-saw function here to animate the balance
+    plot(x = -1:1, y = -1:1, xaxt = "n", yaxt = "n", xlab = "", ylab = "Fitness", 
+         type = "n", xlim = c(-1, 1), ylim = c(-1, 1), bty = "n");
+    points(x = 0, y = 0, cex = 5, pch = 20, col = "black");
+    val <- seq(from = (-1 * pi)/4, to = (1 * pi)/4, length = 1000);
+    hx  <- cos(val);
+    hy  <- sin(val);
+    fva <- seq(from = 0, to = 1, length = 1000);
+    fit <- 0.5*(1 + input$rr)*(1 - input$dd);
+    sqd <- (fva - fit)*(fva - fit);
+    clf <- which(sqd == min(sqd));
+    fx  <- cos(val[clf]);
+    fy  <- sin(val[clf]);
+    points(x = hx, y = hy, lwd = 2, type = "l");
+    points(x = seq(from = 0, to = 1, length = 100), y = rep(0, 100), 
+           type = "l", lty = "dotted", col = "red");
+    ia_box <- mbox(x0 = -1.1, x1 = -0.1, y0 = -0.9, y1 = -1.1);
+    polygon(x=ia_box$x, y=ia_box$y, lwd=3, border="black", col="black");
+    ip_box <- mbox(x0 = 0.1, x1 = 1.1, y0 = -0.9, y1 = -1.1);
+    polygon(x=ip_box$x, y=ip_box$y, lwd=3, border="black", col="black");
+    points(x = seq(from = -1, to = 1, length = 100), y = rep(-0.85, 100), 
+           lwd = 6, type = "l");
+    points(x = rep(0, 100), y = seq(from = -0.85, to = 0, length = 100), 
+           lwd = 6, type = "l");
+    text(x = -0.6, y = -1, labels = "Avoid inbreeding", cex = 1.75, col = "red");
+    text(x = 0.6, y = -1, labels = "Inbreeding", cex = 1.75, col = "white");
+    text(x = 0.8, y = 0.75, labels = "n", cex = 3);
+    text(x = 0.8, y = -0.75, labels = "0", cex = 3);
+    text(x = -1, y = 0, labels = expression(frac(n,2)), cex = 3);
+    points(x = 0, y = 0, cex = 3, pch = 20, col = "red");
+    arrows(x0 = 0, x1 = -0.9, y0 = 0, y1 = 0, lwd = 3, col = "red");
+    arrows(x0 = 0, x1 = fx, y0 = 0, y1 = fy, lwd = 3, col = "black");
+})
 ```
@@
 - Inbreeding depression thresholds differ between females and males causing sexual conflict
-- Females should prefer inbreeding below their inbreeding depression threshold (resource limited)<footnote content="The first awesoem footnote!">here</footnote>:
-- Males should *tolerate* inbreeding below their threshold, but *never prefer* (sis will be fine)
+- Females should prefer inbreeding below their inbreeding depression threshold (resource limited)<footnote content="foot1">[here](http://google.com)</footnote>:
+- Males should *tolerate* inbreeding below their threshold, but *never prefer*<footnote content="foot1">[Puurtinen](http://google.com)</footnote> (sis will be fine)
 

### 2018-02-27 presentation/inbreeding.Rmd
Annoying errors in compiling

--- 2018-02-26 presentation/inbreeding.Rmd
@@
 
-## Inbreeding theory
+<!---
+
+## Inbeeding theory
 
@@
 )
+renderPlot({
     par(bg = 'transparent', mar = c(0.5, 0.5, 0.5, 0.5));
-plot(x = 1:10, y = 1:10, xaxt = "n", yaxt = "n", xlab = "", ylab = "");
-# Add see-saw function here to animate the balance
+    plot(x = -1:1, y = -1:1, xaxt = "n", yaxt = "n", xlab = "", ylab = "Fitness", 
+         type = "n", xlim = c(-1, 1), ylim = c(-1, 1), bty = "n");
+    points(x = 0, y = 0, cex = 5, pch = 20, col = "black");
+    val <- seq(from = (-1 * pi)/4, to = (1 * pi)/4, length = 1000);
+    hx  <- cos(val);
+    hy  <- sin(val);
+    fva <- seq(from = 0, to = 1, length = 1000);
+    fit <- 0.5*(1 + input$rr)*(1 - input$dd);
+    sqd <- (fva - fit)*(fva - fit);
+    clf <- which(sqd == min(sqd));
+    fx  <- cos(val[clf]);
+    fy  <- sin(val[clf]);
+    points(x = hx, y = hy, lwd = 2, type = "l");
+    points(x = seq(from = 0, to = 1, length = 100), y = rep(0, 100), 
+           type = "l", lty = "dotted", col = "red");
+    ia_box <- mbox(x0 = -1.1, x1 = -0.1, y0 = -0.9, y1 = -1.1);
+    polygon(x=ia_box$x, y=ia_box$y, lwd=3, border="black", col="black");
+    ip_box <- mbox(x0 = 0.1, x1 = 1.1, y0 = -0.9, y1 = -1.1);
+    polygon(x=ip_box$x, y=ip_box$y, lwd=3, border="black", col="black");
+    points(x = seq(from = -1, to = 1, length = 100), y = rep(-0.85, 100), 
+           lwd = 6, type = "l");
+    points(x = rep(0, 100), y = seq(from = -0.85, to = 0, length = 100), 
+           lwd = 6, type = "l");
+    text(x = -0.6, y = -1, labels = "Avoid inbreeding", cex = 1.75, col = "red");
+    text(x = 0.6, y = -1, labels = "Inbreeding", cex = 1.75, col = "white");
+    text(x = 0.8, y = 0.75, labels = "n", cex = 3);
+    text(x = 0.8, y = -0.75, labels = "0", cex = 3);
+    text(x = -1, y = 0, labels = expression(frac(n,2)), cex = 3);
+    points(x = 0, y = 0, cex = 3, pch = 20, col = "red");
+    arrows(x0 = 0, x1 = fx, y0 = 0, y1 = fy, lwd = 3, col = "black");
+    arrows(x0 = 0, x1 = -0.9, y0 = 0, y1 = 0, lwd = 3, col = "red");
+})
 ```
@@
 
+--->
+
 ## Interpreting Parker's model
@@
 
-```{r lmSim, fig.show='animate', echo = FALSE}
+```{r IBM_1, fig.show='animate', echo = FALSE}
 inputPanel(
@@
 
+## Again
+
 ##
 
-```{r lmSim3, fig.show='animate', echo = FALSE}
+```{r IBM_3, fig.show = 'animate', echo = FALSE}
 inputPanel(
@@
 
+## Again
+
 ##
 
-```{r lmSim2, fig.show='animate', echo = FALSE}
+```{r IBM_2, fig.show = 'animate', echo = FALSE}
 inputPanel(
@@
 )
+
+gen     <- reactiveValues();
+iter    <- reactiveValues();
+
+gen$dat  <- list(ID = NULL, Rmat = NULL);
+iter$all <- 0;
+iter$nue <- 0;
+iter$kva <- 0;
+iter$mkv <- 0;
 

### 2018-02-28 presentation/inbreeding.Rmd
Working in R but not browser

@@
 
-<!---
-
 ## Inbeeding theory
@@
 })
+browser();
 ```
@@
 </div>
-
---->
 
@@
 
-```{r IBM_1, fig.show='animate', echo = FALSE}
+```{r IBM_1, fig.show='animate', echo = FALSE, fig.width = 4}
 inputPanel(
@@
 
-## Again
-
 ##

### 2018-02-28 presentation/inbreeding.Rmd
Add new picture slides

--- 2018-02-27 presentation/inbreeding.Rmd
@@
 
+<!---
 <style>
@@
 </script>
+--->
 
@@
 
+## Inbreeding theory
+
+<center>
+![](images/fem_choice_1.png)
+</center>
+
+## Inbreeding theory
+
+<center>
+![](images/fem_choice_2.png)
+</center>
+
+## Inbreeding theory
+
+<center>
+![](images/fem_choice_3.png)
+</center>
+
+## Inbreeding theory
+
+<center>
+![](images/fem_choice_4.png)
+</center>
+
 ## Inbeeding theory
@@
 
-```{r echo = FALSE}
+```{r, echo = FALSE, fig.width = 3}
 mbox <- function(x0, x1, y0, y1){
@@
          type = "n", xlim = c(-1, 1), ylim = c(-1, 1), bty = "n");
-    points(x = 0, y = 0, cex = 5, pch = 20, col = "black");
     val <- seq(from = (-1 * pi)/4, to = (1 * pi)/4, length = 1000);
@@
     text(x = -1, y = 0, labels = expression(frac(n,2)), cex = 3);
+    arrows(x0 = 0, x1 = fx, y0 = 0, y1 = fy, lwd = 3, col = "black");
+    arrows(x0 = 0, x1 = -0.9, y0 = 0, y1 = 0, lwd = 3, col = "red");
+    points(x = 0, y = 0, cex = 5, pch = 20, col = "black");
     points(x = 0, y = 0, cex = 3, pch = 20, col = "red");
-    arrows(x0 = 0, x1 = -0.9, y0 = 0, y1 = 0, lwd = 3, col = "red");
-    arrows(x0 = 0, x1 = fx, y0 = 0, y1 = fy, lwd = 3, col = "black");
 })
@@
 - Inbreeding depression thresholds differ between females and males causing sexual conflict
-- Females should prefer inbreeding below their inbreeding depression threshold (resource limited)<footnote content="foot1">[here](http://google.com)</footnote>:
-- Males should *tolerate* inbreeding below their threshold, but *never prefer*<footnote content="foot1">[Puurtinen](http://google.com)</footnote> (sis will be fine)
+- Females should prefer inbreeding below their inbreeding depression threshold (resource limited):
+- Males should *tolerate* inbreeding below their threshold, but *never prefer* [1] (sis will be fine)
+
+<hr>
+
+Puurtinen's paper
 
@@
 
-```{r lmSim, fig.show='animate', echo = FALSE}
+```{r, echo = FALSE, fig.width = 4}
 inputPanel(
@@
 
-```{r lmSim3, fig.show='animate', echo = FALSE}
+```{r, echo = FALSE, fig.width = 4}
 inputPanel(
@@
 
-```{r lmSim2, fig.show='animate', echo = FALSE}
+```{r, echo = FALSE, fig.width = 4}
 inputPanel(

### 2018-03-01 presentation/inbreeding.Rmd
Major updates with images

@@
 
-## Inbreeding
-
-- Define relatedness
-
-## Inbreeding depression
-
-- What inbreeding depression is, exactly.
-
-## Inbreeding depression
-
-- What are the consequences of inbreeding depression.
+## Biparental inbreeding theory
+
+<div class = "columns-2">
+
+![](images/female.png)
+
+![](images/male.png)
+
+</div>
+
+<br><br>
+
+<hr>
+
+Monster images: [http://cliparts.co](http://cliparts.co)
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_1.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_2.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_3.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_4.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_5.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_6.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_7.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_8.png)
+</center>
+
+## Inbreeding depression ($\delta$) slopes ($\beta$)
+
+<div class = "columns-2">
+
+```{r, echo = FALSE, fig.width = 4}
+fcoeff   <- seq(from = 0, to = 1, length = 1000);
+survB0   <- rep(1, 1000);
+survB0p2 <- exp(-1*0.2*fcoeff);
+survB1   <- exp(-1*1*fcoeff);
+survB2   <- exp(-1*2*fcoeff);
+survB5   <- exp(-1*5*fcoeff);
+par(mar = c(5, 5, 1, 0.5));
+plot(x = 0, y = 0, type = "n", xlab = "Inbreeding coefficient (f)",
+     ylab = expression(paste("Pr. offspring survival (1 - ",delta,")")),
+     xlim = c(0, 1), ylim = c(0, 1), cex.lab = 1.5, cex.axis = 1.5);
+points(x = fcoeff, y = survB0, type = "l", lwd = 3);
+points(x = fcoeff, y = survB0p2, type = "l", lwd = 3);
+points(x = fcoeff, y = survB1, type = "l", lwd = 3);
+points(x = fcoeff, y = survB2, type = "l", lwd = 3);
+points(x = fcoeff, y = survB5, type = "l", lwd = 3);
+text(x = 0.8, y = 0.94, labels = expression(beta == 0), cex = 1.5);
+text(x = 0.8, y = 0.79, labels = expression(beta == 0.2), cex = 1.5, srt = -8);
+text(x = 0.7, y = 0.43, labels = expression(beta == 1), cex = 1.5, srt = -24);
+text(x = 0.5, y = 0.30, labels = expression(beta == 2), cex = 1.5, srt = -32);
+text(x = 0.3, y = 0.14, labels = expression(beta == 5), cex = 1.5, srt = -40);
+```
+
+<br>
+
+- Inbreeding depression ($\delta$) generally increases with inbreeding coefficient ($f$)
+
+- Offspring fitness ($1 - \delta$) consequently decreases with $f$
+
+- Slope of decrease in offspring fitness defines $\beta$
+
+</div>
 
@@
 - Much different assumptions
+- Stochasticity
 - See if we can get a similar answer
+
+## Individuals
+
+<center>
+![](images/individuals.png)
+</center>
+
+## Individuals
+
+<center>
+![](images/individuals_1.png)
+</center>
+
+## Individuals
+
+<center>
+![](images/individuals_2.png)
+</center>
+
+## Individual interactions
+
+<center>
+![](images/ibm_general_1.png)
+</center>
+
+## Individual interactions
+
+<center>
+![](images/ibm_general_2.png)
+</center>
+
+## Individual interactions
+
+<center>
+![](images/ibm_general_3.png)
+</center>
+
+## Individual-based modelling questions
+
+- **When should we predict selection for a mutant allele causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**
+
+- **Why should we predict females will mate multiply to adjust the degree to which they inbreed? [2]**
+
+- **How should we predict females to avoid inbreeding (pre- versus post-copulatory avoidance)? [3]**
+
+<br><br><br><br>
+
+<hr>
+<span style="font-size: 18px;">
+1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf). <br>
+2. Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf). <br>
+3. Duthie, AB et al. (2018) *J. Evol. Biol.* [**31**:31-45](https://bradduthie.github.io/DuthieEtAl2017.pdf). <br>
+</span>
 
@@
 ```
+
+## Simulated kinships vs. Mandarte song sparrows
+
+<div class = "columns-2">
+
+<br>
+
+```{r, echo = FALSE, fig.width = 4}
+renderPlot({
+  par(bg = 'transparent');
+  malle <- iter$all;
+  mneut <- iter$nue
+  mkval <- iter$mkv
+  gens  <- 1:length(iter$all);
+  par(mar = c(7, 5, 5, 5));
+  hist(iter$kva, xlim = c(0, 1), ylim = c(0, 20), freq = FALSE, col = "black",
+        yaxt = "n", ylab = "", main = "", xlab = "", 
+        breaks = seq(from = 0, to = 1, by = 0.05), cex.axis = 1.5);
+  title(xlab = "Kinship (k)", line = 4, cex.axis = 1.5, cex.lab = 1.5);
+  box(lwd = 3);
+})
+```
+
+![](images/sparrow_pedigree.png)
+
+</div>
 

### 2018-03-01 presentation/inbreeding.Rmd
More progress

@@
 ---
+
+<style type="text/css">
+body p {
+  color: #000000;
+}
+</style>
 
@@
 
+## Inbreeding and its consequences for evolution {.smaller}
+
+![](images/opening.png)
+
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+1.
+[Wibowo Djatmiko](https://commons.wikimedia.org/wiki/User:Wie146).
+2.
+[George Shuklin](https://commons.wikimedia.org/wiki/User:George_Shuklin).
+3.
+[Natalie Pilakouta](https://www.nataliepilakouta.com/).
+4.
+[Neale Monks](https://en.wikipedia.org/wiki/User:Neale_Monks).
+5.
+[Jane Reid](https://www.abdn.ac.uk/ibes/profiles/jane.reid).
+6.
+[André Karwath](https://commons.wikimedia.org/wiki/User:Aka).
+7.
+[Benjamin Twist](https://commons.wikimedia.org/wiki/User:Benjamint444) 8.
+[Heinz Seehagel](https://de.wikipedia.org/wiki/Benutzer:HaSee).
+</span></div>
+
+<!---
+<hr>
+<span style="font-size: 14px;">
+1. *Poecilia reticula* image: [Wibowo_Djatmiko](https://commons.wikimedia.org/wiki/User:Wie146) <br>
+</span>
+--->
+
 ## Biparental inbreeding theory
@@
 
-- Inbreeding depression ($\delta$) generally increases with inbreeding coefficient ($f$)
+- Inbreeding depression ($\delta$) increases with inbreeding coefficient ($f$)
 
@@
 
+## General individual-based model assumptions
+
+- Non-overlapping generations
+
 ## Individual-based modelling questions

### 2018-03-02 presentation/inbreeding.Rmd
Update slides

@@
 [André Karwath](https://commons.wikimedia.org/wiki/User:Aka).
-7.
-[Benjamin Twist](https://commons.wikimedia.org/wiki/User:Benjamint444) 8.
+<br> 7.
+[Benjamin Twist](https://commons.wikimedia.org/wiki/User:Benjamint444) (benjamint444@gmail.com) 8.
 [Heinz Seehagel](https://de.wikipedia.org/wiki/Benutzer:HaSee).
+9.
+[Adam Hayward](https://adhayward.wordpress.com/)
 </span></div>
 
-<!---
+## **Avoidance** of breeding with relatives
+
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+Szulkin M, et al. (2013) *Trends Ecol. Evol.* [**28**:205–211](https://doi.org/10.1016/j.tree.2012.10.016).
+</span></div>
+
+## **Preference** for breeding with relatives
+
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+Szulkin M, et al. (2013) *Trends Ecol. Evol.* [**28**:205–211](https://doi.org/10.1016/j.tree.2012.10.016).
+</span></div>
+
+## No inbreeding avoidance/preference (**Tolerance**)
+
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+Szulkin M, et al. (2013) *Trends Ecol. Evol.* [**28**:205–211](https://doi.org/10.1016/j.tree.2012.10.016).
+</span></div>
+
+## Biparental inbreeding theory
+
+<div class = "columns-2">
+
+![](images/female.png)
+
+![](images/male.png)
+
+</div>
+
+<br><br>
+
 <hr>
+
+Monster images: [http://cliparts.co](http://cliparts.co)
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_1.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_2.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_3.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_4.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_5.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_6.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_7.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_8.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_9.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_10.png)
+</center>
+
+## Pedigrees and coefficients affecting inbreeding
+
+<center>
+![](images/pedigree_11.png)
+</center>
+
+## Encounter between relatives
+
+<center>
+![](images/fem_choice_1.png)
+</center>
+
+<div align="left" style="line-height: 0.6em;">
 <span style="font-size: 14px;">
-1. *Poecilia reticula* image: [Wibowo_Djatmiko](https://commons.wikimedia.org/wiki/User:Wie146) <br>
-</span>
---->
-
-## Biparental inbreeding theory
-
-<div class = "columns-2">
-
-![](images/female.png)
-
-![](images/male.png)
-
-</div>
-
-<br><br>
-
-<hr>
-
-Monster images: [http://cliparts.co](http://cliparts.co)
-
-## Pedigrees and coefficients affecting inbreeding
-
-<center>
-![](images/pedigree_1.png)
-</center>
-
-## Pedigrees and coefficients affecting inbreeding
-
-<center>
-![](images/pedigree_2.png)
-</center>
-
-## Pedigrees and coefficients affecting inbreeding
-
-<center>
-![](images/pedigree_3.png)
-</center>
-
-## Pedigrees and coefficients affecting inbreeding
-
-<center>
-![](images/pedigree_4.png)
-</center>
-
-## Pedigrees and coefficients affecting inbreeding
-
-<center>
-![](images/pedigree_5.png)
-</center>
-
-## Pedigrees and coefficients affecting inbreeding
-
-<center>
-![](images/pedigree_6.png)
-</center>
-
-## Pedigrees and coefficients affecting inbreeding
-
-<center>
-![](images/pedigree_7.png)
-</center>
-
-## Pedigrees and coefficients affecting inbreeding
-
-<center>
-![](images/pedigree_8.png)
-</center>
-
-## Inbreeding depression ($\delta$) slopes ($\beta$)
-
-<div class = "columns-2">
-
-```{r, echo = FALSE, fig.width = 4}
-fcoeff   <- seq(from = 0, to = 1, length = 1000);
-survB0   <- rep(1, 1000);
-survB0p2 <- exp(-1*0.2*fcoeff);
-survB1   <- exp(-1*1*fcoeff);
-survB2   <- exp(-1*2*fcoeff);
-survB5   <- exp(-1*5*fcoeff);
-par(mar = c(5, 5, 1, 0.5));
-plot(x = 0, y = 0, type = "n", xlab = "Inbreeding coefficient (f)",
-     ylab = expression(paste("Pr. offspring survival (1 - ",delta,")")),
-     xlim = c(0, 1), ylim = c(0, 1), cex.lab = 1.5, cex.axis = 1.5);
-points(x = fcoeff, y = survB0, type = "l", lwd = 3);
-points(x = fcoeff, y = survB0p2, type = "l", lwd = 3);
-points(x = fcoeff, y = survB1, type = "l", lwd = 3);
-points(x = fcoeff, y = survB2, type = "l", lwd = 3);
-points(x = fcoeff, y = survB5, type = "l", lwd = 3);
-text(x = 0.8, y = 0.94, labels = expression(beta == 0), cex = 1.5);
-text(x = 0.8, y = 0.79, labels = expression(beta == 0.2), cex = 1.5, srt = -8);
-text(x = 0.7, y = 0.43, labels = expression(beta == 1), cex = 1.5, srt = -24);
-text(x = 0.5, y = 0.30, labels = expression(beta == 2), cex = 1.5, srt = -32);
-text(x = 0.3, y = 0.14, labels = expression(beta == 5), cex = 1.5, srt = -40);
-```
-
-<br>
-
-- Inbreeding depression ($\delta$) increases with inbreeding coefficient ($f$)
-
-- Offspring fitness ($1 - \delta$) consequently decreases with $f$
-
-- Slope of decrease in offspring fitness defines $\beta$
-
-</div>
-
-## Inbreeding behaviour
-
-- What do we exect to see given inbreeding depression?
-
-- inbreeding avoidance
-- inbreeding preference
-- inbreeding tolerance
-
-## Inbreeding theory
-
-Describe Parker's model
-
-- Resource and mate limited sexes
-- Mate encounter, opportunity to outbreed assumed
-
-## Inbreeding theory
-
-<center>
-![](images/fem_choice_1.png)
-</center>
-
-## Inbreeding theory
+Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
+</span></div>
+
+## Encounter between relatives
 
@@
 
-## Inbreeding theory
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
+</span></div>
+
+## Encounter between relatives
 
@@
 
-## Inbeeding theory
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
+</span></div>
+
+## Encounter between relatives
+
+<center>
+![](images/fem_choice_5.png)
+
+</center>
+
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
+</span></div>
+
+## Encounter between relatives
+
+<center>
+![](images/fem_choice_6.png)
+
+</center>
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
+</span></div>
+
+## When to inbreed versus avoid inbreeding?
 
@@
 
-<br><br>
-
-- Parker's model
-- Add a see-saw plot that weighs relatedness versus inbreeding depression
-
-$$\frac{n}{2} (1 + r)(1 - \delta) > \frac{n}{2}$$
-
-Is inclusive fitness from inbreeding (left) greater than inclusive fitness from outbreeding?
+<br><br><br><br>
+
+Is inclusive fitness from avoiding inbreeding (left side) less than inbreeding (right side)?
+
+$$\frac{n}{2} < \frac{n}{2} (1 + r)(1 - \delta)$$
+
+More generally, is inclusive fitness from inbreeding (left) greater than inclusive fitness from outbreeding?
 
@@
 
-## Interpreting Parker's model
-
-Some key takeaways:
+## Key conceptual take-aways
+
+<div class = "columns-2">
+
+```{r, echo = FALSE, fig.width = 4.5}
+ri <- matrix(data=c(1,0.5,0,0.5,1,0,0,0,1),nrow=3,byrow=TRUE);
+Inbreed <- function(focal,mate,alt){
+  Inb <- ri[focal,focal] + ri[focal,mate];
+  Out <- ri[focal,mate]  + ri[focal,alt];
+  DEL <- 1 - (Out/Inb);
+  return(DEL);
+}
+rs <- seq(from=0,to=1,by=0.0001);
+dl <- rep(x=0,length=length(rs));
+for(i in 1:length(rs)){
+  ri <- matrix(data=c(1,rs[i],0,rs[i],1,0,0,0,1),nrow=3,byrow=TRUE);
+  dl[i] <- Inbreed(focal=1,mate=2,alt=3);
+}
+par(mar=c(5,5,1,1));
+plot(x=rs,y=dl,type="l",lwd=2,
+  xlab=expression(paste("Relatedness (",italic(r),")")),
+  ylab=expression(paste(italic(delta)," threshold")),
+  cex.lab=1.5,cex.axis=1.25,ylim=c(0,1));
+Inbreed <- function(focal,mate,alt){
+  Inb <- ri[focal,focal] + ri[focal,mate];
+  Out <- ri[focal,focal]  + ri[focal,alt];
+  DEL <- 1 - (Out/Inb);
+  return(DEL);
+}
+dk <- rep(x=0,length=length(rs));
+for(i in 1:length(rs)){
+  ri <- matrix(data=c(1,rs[i],0,rs[i],1,0,0,0,1),nrow=3,byrow=TRUE);
+  dk[i] <- Inbreed(focal=2,mate=1,alt=3);
+}
+points(x=rs,y=dk,type="l",lwd=2,
+  cex.lab=1.25,cex.axis=1.5,ylim=c(0,1));
+polygon(x=c(rs,rev(rs)),y=c(dk,rev(dl)),col="black");
+polygon(x=c(rs,rev(rs)),y=c(rep(0,length(dk)),rev(dk)),col="grey40");
+points(x=seq(from=0,to=1,by=0.1),y=rep(1,11),type="l");
+points(y=seq(from=0,to=1,by=0.1),x=rep(1,11),type="l");
+text(x=0.75,y=0.16,labels=expression(paste(italic(Female))),cex=1.75, col = "black");
+arrows(x0=0.75,y0=0.2,x1=0.6,y1=0.375, length = 0.15, angle = 30, code = 2, lwd=2);
+text(x=0.75,y=0.84,labels=expression(paste(italic(Male))),cex=1.75, col  = "black");
+arrows(x0=0.75,y0=0.8,x1=0.6,y1=0.625, length = 0.15, angle = 30, code = 2, lwd=2);
+```
 
 - Inbreeding avoidance is predicted given a sufficiently high threshold of inbreeding depression
+
 - Inbreeding depression thresholds differ between females and males causing sexual conflict
-- Females should prefer inbreeding below their inbreeding depression threshold (resource limited):
-- Males should *tolerate* inbreeding below their threshold, but *never prefer* [1] (sis will be fine)
+
+</div>
 
@@
 
-Puurtinen's paper
-
-## Extensions of Parker's model
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+Parker (1979) *Sexual selection and reproductive competition in insects* (pp.
+123–166).
+Parker (2006) *Philos.
+Trans.
+Royal Soc.
+B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
+<br> Duthie, AB & JM Reid (2015) *PLoS One* [**10**:e0125140](https://bradduthie.github.io/Duthie%26Reid2015.pdf).
+</span></div>
+
+## Key conceptual take-aways
+
+<div class = "columns-2">
+
+```{r, echo = FALSE, fig.width = 4.5}
+ri <- matrix(data=c(1,0.5,0,0.5,1,0,0,0,1),nrow=3,byrow=TRUE);
+Inbreed <- function(focal,mate,alt){
+  Inb <- ri[focal,focal] + ri[focal,mate];
+  Out <- ri[focal,mate]  + ri[focal,alt];
+  DEL <- 1 - (Out/Inb);
+  return(DEL);
+}
+rs <- seq(from=0,to=1,by=0.0001);
+dl <- rep(x=0,length=length(rs));
+for(i in 1:length(rs)){
+  ri <- matrix(data=c(1,rs[i],0,rs[i],1,0,0,0,1),nrow=3,byrow=TRUE);
+  dl[i] <- Inbreed(focal=1,mate=2,alt=3);
+}
+par(mar=c(5,5,1,1));
+plot(x=rs,y=dl,type="l",lwd=2,
+  xlab=expression(paste("Relatedness (",italic(r),")")),
+  ylab=expression(paste(italic(delta)," threshold")),
+  cex.lab=1.5,cex.axis=1.25,ylim=c(0,1));
+Inbreed <- function(focal,mate,alt){
+  Inb <- ri[focal,focal] + ri[focal,mate];
+  Out <- ri[focal,focal]  + ri[focal,alt];
+  DEL <- 1 - (Out/Inb);
+  return(DEL);
+}
+dk <- rep(x=0,length=length(rs));
+for(i in 1:length(rs)){
+  ri <- matrix(data=c(1,rs[i],0,rs[i],1,0,0,0,1),nrow=3,byrow=TRUE);
+  dk[i] <- Inbreed(focal=2,mate=1,alt=3);
+}
+points(x=rs,y=dk,type="l",lwd=2,
+  cex.lab=1.25,cex.axis=1.5,ylim=c(0,1));
+polygon(x=c(rs,rev(rs)),y=c(dk,rev(dl)),col="black");
+polygon(x=c(rs,rev(rs)),y=c(rep(0,length(dk)),rev(dk)),col="grey40");
+points(x=seq(from=0,to=1,by=0.1),y=rep(1,11),type="l");
+points(y=seq(from=0,to=1,by=0.1),x=rep(1,11),type="l");
+text(x=0.75,y=0.16,labels=expression(paste(italic(Female))),cex=1.75, col = "black");
+arrows(x0=0.75,y0=0.2,x1=0.6,y1=0.375, length = 0.15, angle = 30, code = 2, lwd=2);
+text(x=0.75,y=0.84,labels=expression(paste(italic(Male))),cex=1.75, col  = "black");
+arrows(x0=0.75,y0=0.8,x1=0.6,y1=0.625, length = 0.15, angle = 30, code = 2, lwd=2);
+```
+
+- Inbreeding tolerance increases with lower encounter rates (Kokko & Ots 2006)
+
+- Dispersal has effects (Lehmann & Perrin 2003)
+
+- Thresholds change given subsequent mating decisions of relatives (Duthie & Reid 2015)
+
+- Thresholds change given modulation of parental investment (Duthie et al. 2016)
+
+</div>
+
+<hr>
+
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+Parker (1979) *Sexual selection and reproductive competition in insects* (pp.
+123–166).
+Parker (2006) *Philos.
+Trans.
+Royal Soc.
+B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
+<br> Duthie, AB & JM Reid (2015) *PLoS One* [**10**:e0125140](https://bradduthie.github.io/Duthie%26Reid2015.pdf).
+</span></div>
 
 ## Limitations of this modelling approach
+
+## Inbreeding depression ($\delta$) slopes ($\beta$)
+
+<div class = "columns-2">
+
+```{r, echo = FALSE, fig.width = 4}
+fcoeff   <- seq(from = 0, to = 1, length = 1000);
+survB0   <- rep(1, 1000);
+survB0p2 <- exp(-1*0.2*fcoeff);
+survB1   <- exp(-1*1*fcoeff);
+survB2   <- exp(-1*2*fcoeff);
+survB5   <- exp(-1*5*fcoeff);
+par(mar = c(5, 5, 1, 0.5));
+plot(x = 0, y = 0, type = "n", xlab = "Inbreeding coefficient (f)",
+     ylab = expression(paste("Pr. offspring survival (1 - ",delta,")")),
+     xlim = c(0, 1), ylim = c(0, 1), cex.lab = 1.5, cex.axis = 1.5);
+points(x = fcoeff, y = survB0, type = "l", lwd = 3);
+points(x = fcoeff, y = survB0p2, type = "l", lwd = 3);
+points(x = fcoeff, y = survB1, type = "l", lwd = 3);
+points(x = fcoeff, y = survB2, type = "l", lwd = 3);
+points(x = fcoeff, y = survB5, type = "l", lwd = 3);
+text(x = 0.8, y = 0.94, labels = expression(beta == 0), cex = 1.5);
+text(x = 0.8, y = 0.79, labels = expression(beta == 0.2), cex = 1.5, srt = -8);
+text(x = 0.7, y = 0.43, labels = expression(beta == 1), cex = 1.5, srt = -24);
+text(x = 0.5, y = 0.30, labels = expression(beta == 2), cex = 1.5, srt = -32);
+text(x = 0.3, y = 0.14, labels = expression(beta == 5), cex = 1.5, srt = -40);
+```
+
+<br>
+
+- Inbreeding depression ($\delta$) increases with inbreeding coefficient ($f$)
+
+- Offspring fitness ($1 - \delta$) consequently decreases with $f$
+
+- Slope of decrease in offspring fitness defines $\beta$
+
+</div>
 

### 2018-03-02 presentation/inbreeding.Rmd
More progress

@@
 
-- Inbreeding avoidance is predicted given a sufficiently high threshold of inbreeding depression
-
-- Inbreeding depression thresholds differ between females and males causing sexual conflict
+- Inbreeding avoidance is predicted given a sufficiently high threshold of inbreeding depression [1,2]
+
+- Inbreeding depression thresholds differ between females and males causing sexual conflict [1,2]
 
@@
 <span style="font-size: 14px;">
-Parker (1979) *Sexual selection and reproductive competition in insects* (pp.
-123–166).
-Parker (2006) *Philos.
-Trans.
-Royal Soc.
-B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
-<br> Duthie, AB & JM Reid (2015) *PLoS One* [**10**:e0125140](https://bradduthie.github.io/Duthie%26Reid2015.pdf).
+[1] Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). <br>
+[2] Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785). 
 </span></div>
@@
 
-- Inbreeding tolerance increases with lower encounter rates (Kokko & Ots 2006)
-
-- Dispersal has effects (Lehmann & Perrin 2003)
-
-- Thresholds change given subsequent mating decisions of relatives (Duthie & Reid 2015)
-
-- Thresholds change given modulation of parental investment (Duthie et al. 2016)
+- Inbreeding tolerance increases with lower encounter rates [1].
 
@@
 <span style="font-size: 14px;">
-Parker (1979) *Sexual selection and reproductive competition in insects* (pp.
-123–166).
-Parker (2006) *Philos.
-Trans.
-Royal Soc.
-B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
-<br> Duthie, AB & JM Reid (2015) *PLoS One* [**10**:e0125140](https://bradduthie.github.io/Duthie%26Reid2015.pdf).
+[1] Kokko, H & I Ots (2006) *Evolution* [**60**:467-475](http://onlinelibrary.wiley.com/doi/10.1111/j.0014-3820.2006.tb01128.x/abstract).
+</span></div>
+
+## Key conceptual take-aways
+
+<div class = "columns-2">
+
+```{r, echo = FALSE, fig.width = 4.5}
+ri <- matrix(data=c(1,0.5,0,0.5,1,0,0,0,1),nrow=3,byrow=TRUE);
+Inbreed <- function(focal,mate,alt){
+  Inb <- ri[focal,focal] + ri[focal,mate];
+  Out <- ri[focal,mate]  + ri[focal,alt];
+  DEL <- 1 - (Out/Inb);
+  return(DEL);
+}
+rs <- seq(from=0,to=1,by=0.0001);
+dl <- rep(x=0,length=length(rs));
+for(i in 1:length(rs)){
+  ri <- matrix(data=c(1,rs[i],0,rs[i],1,0,0,0,1),nrow=3,byrow=TRUE);
+  dl[i] <- Inbreed(focal=1,mate=2,alt=3);
+}
+par(mar=c(5,5,1,1));
+plot(x=rs,y=dl,type="l",lwd=2,
+  xlab=expression(paste("Relatedness (",italic(r),")")),
+  ylab=expression(paste(italic(delta)," threshold")),
+  cex.lab=1.5,cex.axis=1.25,ylim=c(0,1));
+Inbreed <- function(focal,mate,alt){
+  Inb <- ri[focal,focal] + ri[focal,mate];
+  Out <- ri[focal,focal]  + ri[focal,alt];
+  DEL <- 1 - (Out/Inb);
+  return(DEL);
+}
+dk <- rep(x=0,length=length(rs));
+for(i in 1:length(rs)){
+  ri <- matrix(data=c(1,rs[i],0,rs[i],1,0,0,0,1),nrow=3,byrow=TRUE);
+  dk[i] <- Inbreed(focal=2,mate=1,alt=3);
+}
+points(x=rs,y=dk,type="l",lwd=2,
+  cex.lab=1.25,cex.axis=1.5,ylim=c(0,1));
+polygon(x=c(rs,rev(rs)),y=c(dk,rev(dl)),col="black");
+polygon(x=c(rs,rev(rs)),y=c(rep(0,length(dk)),rev(dk)),col="grey40");
+points(x=seq(from=0,to=1,by=0.1),y=rep(1,11),type="l");
+points(y=seq(from=0,to=1,by=0.1),x=rep(1,11),type="l");
+text(x=0.75,y=0.16,labels=expression(paste(italic(Female))),cex=1.75, col = "black");
+arrows(x0=0.75,y0=0.2,x1=0.6,y1=0.375, length = 0.15, angle = 30, code = 2, lwd=2);
+text(x=0.75,y=0.84,labels=expression(paste(italic(Male))),cex=1.75, col  = "black");
+arrows(x0=0.75,y0=0.8,x1=0.6,y1=0.625, length = 0.15, angle = 30, code = 2, lwd=2);
+```
+
+- Inbreeding tolerance increases with lower encounter rates [1].
+
+- Inbreeding avoidance or preference can affect dispersal [2].
+
+</div>
+
+<hr>
+
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+[1] Kokko, H & I Ots (2006) *Evolution* [**60**:467-475](http://onlinelibrary.wiley.com/doi/10.1111/j.0014-3820.2006.tb01128.x/abstract).
+[2] Lehmann, L & N Perrin (2003) *Am. Nat.* [**162**:638-652](https://www.journals.uchicago.edu/doi/10.1086/378823). <br>
+</span></div>
+
+## Key conceptual take-aways
+
+<div class = "columns-2">
+
+```{r, echo = FALSE, fig.width = 4.5}
+ri <- matrix(data=c(1,0.5,0,0.5,1,0,0,0,1),nrow=3,byrow=TRUE);
+Inbreed <- function(focal,mate,alt){
+  Inb <- ri[focal,focal] + ri[focal,mate];
+  Out <- ri[focal,mate]  + ri[focal,alt];
+  DEL <- 1 - (Out/Inb);
+  return(DEL);
+}
+rs <- seq(from=0,to=1,by=0.0001);
+dl <- rep(x=0,length=length(rs));
+for(i in 1:length(rs)){
+  ri <- matrix(data=c(1,rs[i],0,rs[i],1,0,0,0,1),nrow=3,byrow=TRUE);
+  dl[i] <- Inbreed(focal=1,mate=2,alt=3);
+}
+par(mar=c(5,5,1,1));
+plot(x=rs,y=dl,type="l",lwd=2,
+  xlab=expression(paste("Relatedness (",italic(r),")")),
+  ylab=expression(paste(italic(delta)," threshold")),
+  cex.lab=1.5,cex.axis=1.25,ylim=c(0,1));
+Inbreed <- function(focal,mate,alt){
+  Inb <- ri[focal,focal] + ri[focal,mate];
+  Out <- ri[focal,focal]  + ri[focal,alt];
+  DEL <- 1 - (Out/Inb);
+  return(DEL);
+}
+dk <- rep(x=0,length=length(rs));
+for(i in 1:length(rs)){
+  ri <- matrix(data=c(1,rs[i],0,rs[i],1,0,0,0,1),nrow=3,byrow=TRUE);
+  dk[i] <- Inbreed(focal=2,mate=1,alt=3);
+}
+points(x=rs,y=dk,type="l",lwd=2,
+  cex.lab=1.25,cex.axis=1.5,ylim=c(0,1));
+polygon(x=c(rs,rev(rs)),y=c(dk,rev(dl)),col="black");
+polygon(x=c(rs,rev(rs)),y=c(rep(0,length(dk)),rev(dk)),col="grey40");
+points(x=seq(from=0,to=1,by=0.1),y=rep(1,11),type="l");
+points(y=seq(from=0,to=1,by=0.1),x=rep(1,11),type="l");
+text(x=0.75,y=0.16,labels=expression(paste(italic(Female))),cex=1.75, col = "black");
+arrows(x0=0.75,y0=0.2,x1=0.6,y1=0.375, length = 0.15, angle = 30, code = 2, lwd=2);
+text(x=0.75,y=0.84,labels=expression(paste(italic(Male))),cex=1.75, col  = "black");
+arrows(x0=0.75,y0=0.8,x1=0.6,y1=0.625, length = 0.15, angle = 30, code = 2, lwd=2);
+```
+
+- Inbreeding tolerance increases with lower encounter rates [1].
+
+- Inbreeding avoidance or preference can affect dispersal [2].
+
+- Thresholds change given mating decisions of avoided relatives [3].
+
+</div>
+
+<hr>
+
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+[1] Kokko, H & I Ots (2006) *Evolution* [**60**:467-475](http://onlinelibrary.wiley.com/doi/10.1111/j.0014-3820.2006.tb01128.x/abstract).
+[2] Lehmann, L & N Perrin (2003) *Am. Nat.* [**162**:638-652](https://www.journals.uchicago.edu/doi/10.1086/378823). <br>
+[3] Duthie, AB & JM Reid (2015) *PLoS One* [**10**:e0125140](https://bradduthie.github.io/Duthie%26Reid2015.pdf). 
+</span></div>
+
+## Key conceptual take-aways
+
+<div class = "columns-2">
+
+```{r, echo = FALSE, fig.width = 4.5}
+ri <- matrix(data=c(1,0.5,0,0.5,1,0,0,0,1),nrow=3,byrow=TRUE);
+Inbreed <- function(focal,mate,alt){
+  Inb <- ri[focal,focal] + ri[focal,mate];
+  Out <- ri[focal,mate]  + ri[focal,alt];
+  DEL <- 1 - (Out/Inb);
+  return(DEL);
+}
+rs <- seq(from=0,to=1,by=0.0001);
+dl <- rep(x=0,length=length(rs));
+for(i in 1:length(rs)){
+  ri <- matrix(data=c(1,rs[i],0,rs[i],1,0,0,0,1),nrow=3,byrow=TRUE);
+  dl[i] <- Inbreed(focal=1,mate=2,alt=3);
+}
+par(mar=c(5,5,1,1));
+plot(x=rs,y=dl,type="l",lwd=2,
+  xlab=expression(paste("Relatedness (",italic(r),")")),
+  ylab=expression(paste(italic(delta)," threshold")),
+  cex.lab=1.5,cex.axis=1.25,ylim=c(0,1));
+Inbreed <- function(focal,mate,alt){
+  Inb <- ri[focal,focal] + ri[focal,mate];
+  Out <- ri[focal,focal]  + ri[focal,alt];
+  DEL <- 1 - (Out/Inb);
+  return(DEL);
+}
+dk <- rep(x=0,length=length(rs));
+for(i in 1:length(rs)){
+  ri <- matrix(data=c(1,rs[i],0,rs[i],1,0,0,0,1),nrow=3,byrow=TRUE);
+  dk[i] <- Inbreed(focal=2,mate=1,alt=3);
+}
+points(x=rs,y=dk,type="l",lwd=2,
+  cex.lab=1.25,cex.axis=1.5,ylim=c(0,1));
+polygon(x=c(rs,rev(rs)),y=c(dk,rev(dl)),col="black");
+polygon(x=c(rs,rev(rs)),y=c(rep(0,length(dk)),rev(dk)),col="grey40");
+points(x=seq(from=0,to=1,by=0.1),y=rep(1,11),type="l");
+points(y=seq(from=0,to=1,by=0.1),x=rep(1,11),type="l");
+text(x=0.75,y=0.16,labels=expression(paste(italic(Female))),cex=1.75, col = "black");
+arrows(x0=0.75,y0=0.2,x1=0.6,y1=0.375, length = 0.15, angle = 30, code = 2, lwd=2);
+text(x=0.75,y=0.84,labels=expression(paste(italic(Male))),cex=1.75, col  = "black");
+arrows(x0=0.75,y0=0.8,x1=0.6,y1=0.625, length = 0.15, angle = 30, code = 2, lwd=2);
+```
+
+- Inbreeding tolerance increases with lower encounter rates [1].
+
+- Inbreeding avoidance or preference can affect dispersal [2].
+
+- Thresholds change given mating decisions of avoided relatives [3].
+
+- Thresholds change if parental investment can be modulated [4].
+
+</div>
+
+<hr>
+
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+[1] Kokko, H & I Ots (2006) *Evolution* [**60**:467-475](http://onlinelibrary.wiley.com/doi/10.1111/j.0014-3820.2006.tb01128.x/abstract).
+[2] Lehmann, L & N Perrin (2003) *Am. Nat.* [**162**:638-652](https://www.journals.uchicago.edu/doi/10.1086/378823). <br>
+[3] Duthie, AB & JM Reid (2015) *PLoS One* [**10**:e0125140](https://bradduthie.github.io/Duthie%26Reid2015.pdf). 
+[4] Duthie, AB et. al (2016) *Proc. R. Soc. B.* [**282**:20161845](https://bradduthie.github.io/Duthie%26Reid2015.pdf).
+</span></div>
+
+## Key conceptual take-aways
+
+<div class = "columns-2">
+
+```{r, echo = FALSE, fig.width = 4.5}
+ri <- matrix(data=c(1,0.5,0,0.5,1,0,0,0,1),nrow=3,byrow=TRUE);
+Inbreed <- function(focal,mate,alt){
+  Inb <- ri[focal,focal] + ri[focal,mate];
+  Out <- ri[focal,mate]  + ri[focal,alt];
+  DEL <- 1 - (Out/Inb);
+  return(DEL);
+}
+rs <- seq(from=0,to=1,by=0.0001);
+dl <- rep(x=0,length=length(rs));
+for(i in 1:length(rs)){
+  ri <- matrix(data=c(1,rs[i],0,rs[i],1,0,0,0,1),nrow=3,byrow=TRUE);
+  dl[i] <- Inbreed(focal=1,mate=2,alt=3);
+}
+par(mar=c(5,5,1,1));
+plot(x=rs,y=dl,type="l",lwd=2,
+  xlab=expression(paste("Relatedness (",italic(r),")")),
+  ylab=expression(paste(italic(delta)," threshold")),
+  cex.lab=1.5,cex.axis=1.25,ylim=c(0,1));
+Inbreed <- function(focal,mate,alt){
+  Inb <- ri[focal,focal] + ri[focal,mate];
+  Out <- ri[focal,focal]  + ri[focal,alt];
+  DEL <- 1 - (Out/Inb);
+  return(DEL);
+}
+dk <- rep(x=0,length=length(rs));
+for(i in 1:length(rs)){
+  ri <- matrix(data=c(1,rs[i],0,rs[i],1,0,0,0,1),nrow=3,byrow=TRUE);
+  dk[i] <- Inbreed(focal=2,mate=1,alt=3);
+}
+points(x=rs,y=dk,type="l",lwd=2,
+  cex.lab=1.25,cex.axis=1.5,ylim=c(0,1));
+polygon(x=c(rs,rev(rs)),y=c(dk,rev(dl)),col="black");
+polygon(x=c(rs,rev(rs)),y=c(rep(0,length(dk)),rev(dk)),col="grey40");
+points(x=seq(from=0,to=1,by=0.1),y=rep(1,11),type="l");
+points(y=seq(from=0,to=1,by=0.1),x=rep(1,11),type="l");
+text(x=0.75,y=0.16,labels=expression(paste(italic(Female))),cex=1.75, col = "black");
+arrows(x0=0.75,y0=0.2,x1=0.6,y1=0.375, length = 0.15, angle = 30, code = 2, lwd=2);
+text(x=0.75,y=0.84,labels=expression(paste(italic(Male))),cex=1.75, col  = "black");
+arrows(x0=0.75,y0=0.8,x1=0.6,y1=0.625, length = 0.15, angle = 30, code = 2, lwd=2);
+```
+
+- Inbreeding tolerance increases with lower encounter rates [1].
+
+- Inbreeding avoidance or preference can affect dispersal [2].
+
+- Thresholds change given mating decisions of avoided relatives [3].
+
+- Thresholds change if parental investment can be modulated [4].
+
+- Thresholds change if there are male opportunity costs [5]
+
+</div>
+
+<hr>
+
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+[1] Kokko, H & I Ots (2006) *Evolution* [**60**:467-475](http://onlinelibrary.wiley.com/doi/10.1111/j.0014-3820.2006.tb01128.x/abstract).
+[2] Lehmann, L & N Perrin (2003) *Am. Nat.* [**162**:638-652](https://www.journals.uchicago.edu/doi/10.1086/378823). <br>
+[3] Duthie, AB & JM Reid (2015) *PLoS One* [**10**:e0125140](https://bradduthie.github.io/Duthie%26Reid2015.pdf). 
+[4] Duthie, AB et. al (2016) *Proc. R. Soc. B.* [**282**:20161845](https://bradduthie.github.io/Duthie%26Reid2015.pdf). <br>
+[5] Waser PM, et. al. (1986) *Am. Nat.* [**128**:529-537](https://www.journals.uchicago.edu/doi/abs/10.1086/284585).
 </span></div>
@@
 
+<div class = "columns-2">
+
+```{r, echo = FALSE, fig.width = 4.5}
+ri <- matrix(data=c(1,0.5,0,0.5,1,0,0,0,1),nrow=3,byrow=TRUE);
+Inbreed <- function(focal,mate,alt){
+  Inb <- ri[focal,focal] + ri[focal,mate];
+  Out <- ri[focal,mate]  + ri[focal,alt];
+  DEL <- 1 - (Out/Inb);
+  return(DEL);
+}
+rs <- seq(from=0,to=1,by=0.0001);
+dl <- rep(x=0,length=length(rs));
+for(i in 1:length(rs)){
+  ri <- matrix(data=c(1,rs[i],0,rs[i],1,0,0,0,1),nrow=3,byrow=TRUE);
+  dl[i] <- Inbreed(focal=1,mate=2,alt=3);
+}
+par(mar=c(5,5,1,1));
+plot(x=rs,y=dl,type="l",lwd=2,
+  xlab=expression(paste("Relatedness (",italic(r),")")),
+  ylab=expression(paste(italic(delta)," threshold")),
+  cex.lab=1.5,cex.axis=1.25,ylim=c(0,1));
+Inbreed <- function(focal,mate,alt){
+  Inb <- ri[focal,focal] + ri[focal,mate];
+  Out <- ri[focal,focal]  + ri[focal,alt];
+  DEL <- 1 - (Out/Inb);
+  return(DEL);
+}
+dk <- rep(x=0,length=length(rs));
+for(i in 1:length(rs)){
+  ri <- matrix(data=c(1,rs[i],0,rs[i],1,0,0,0,1),nrow=3,byrow=TRUE);
+  dk[i] <- Inbreed(focal=2,mate=1,alt=3);
+}
+points(x=rs,y=dk,type="l",lwd=2,
+  cex.lab=1.25,cex.axis=1.5,ylim=c(0,1));
+polygon(x=c(rs,rev(rs)),y=c(dk,rev(dl)),col="black");
+polygon(x=c(rs,rev(rs)),y=c(rep(0,length(dk)),rev(dk)),col="grey40");
+points(x=seq(from=0,to=1,by=0.1),y=rep(1,11),type="l");
+points(y=seq(from=0,to=1,by=0.1),x=rep(1,11),type="l");
+text(x=0.75,y=0.16,labels=expression(paste(italic(Female))),cex=1.75, col = "black");
+arrows(x0=0.75,y0=0.2,x1=0.6,y1=0.375, length = 0.15, angle = 30, code = 2, lwd=2);
+text(x=0.75,y=0.84,labels=expression(paste(italic(Male))),cex=1.75, col  = "black");
+arrows(x0=0.75,y0=0.8,x1=0.6,y1=0.625, length = 0.15, angle = 30, code = 2, lwd=2);
+```
+
+- Focuses on selection to the exclusion of drift, mutation, immigration
+
+</div>
+
+## Limitations of this modelling approach
+
+<div class = "columns-2">
+
+![](images/real_pedigree.png)
+
+- Focuses on selection to the exclusion of drift, mutation, immigration
+
+- Does not consider realistic distributions of kinship
+
+</div>
+
+## Limitations of this modelling approach
+
+<div class = "columns-2">
+
+![](images/polyandry_eg.png)
+
+- Focuses on selection to the exclusion of drift, mutation, immigration
+
+- Does not consider realistic distributions of kinship
+
+- Does not consider complex strategies such as female multiple mating (polyandry) [but see 1]
+
+</div>
+
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+[1] Lehtonen, J & H Kokko (2015) *Proc. R. Soc. B* [**282**:20142716](http://rspb.royalsocietypublishing.org/content/282/1801/20142716).
+</span></div>
+
+## Limitations of this modelling approach
+
+<div class = "columns-2">
+
+![](images/polyandry_eg.png)
+
+- Focuses on selection to the exclusion of drift, mutation, immigration
+
+- Does not consider realistic distributions of kinship
+
+- Does not consider complex strategies such as female multiple mating (polyandry) [but see 1]
+
+- Does not account for post-copulatory inbreeding avoidance or preference
+
+</div>
+
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+[1] Lehtonen, J & H Kokko (2015) *Proc. R. Soc. B* [**282**:20142716](http://rspb.royalsocietypublishing.org/content/282/1801/20142716).
+</span></div>
+
+## Individual-based modelling approach
+
+<div class = "columns-2">
+
+![](images/ibm_approach.png)
+
+- Models discrete individual females and males in a finite population
+
+- Explicitly tracks pedigree to calculate kinship between individuals
+
+- Allows for simultaneous evolution of inbreeding behaviour and polyandry
+
+- Allows for the evolution of pre- and post-copulatory inbreeding behaviour
+
+</div>
+
+<!--- 
 ## Inbreeding depression ($\delta$) slopes ($\beta$)
@@
 
-## Individual-based modelling
-
-- Much different assumptions
-- Stochasticity
-- See if we can get a similar answer
-
-## Individuals
+--->
+
+## The polyinbreeding team
+
+![](images/polyinbreeders.png)
+
+## Individual traits and genomes
 
@@
 
-## Individuals
+## Individual traits and genomes
 
@@
 </center>
-
-## General individual-based model assumptions
-
-- Non-overlapping generations
 
@@
 </span>
+
+## General modelling steps
 

### 2018-03-02 presentation/inbreeding.Rmd
More slides

@@
 
-## Individual interactions
-
-<center>
-![](images/ibm_general_1.png)
-</center>
-
-## Individual interactions
-
-<center>
-![](images/ibm_general_2.png)
-</center>
-
-## Individual interactions
-
-<center>
-![](images/ibm_general_3.png)
-</center>
-
 ## Individual-based modelling questions
@@
 
-## General modelling steps
+## General individual-based model overview
+
+<center>
+![](images/ibm_steps_1.png)
+</center>
+
+<span style="font-size: 18px;">
+Code [available on GitHub](https://github.com/bradduthie/PolyInbreed)
+</span>
+
+## General individual-based model overview
+
+<center>
+![](images/ibm_steps_2.png)
+</center>
+
+<span style="font-size: 18px;">
+Code [available on GitHub](https://github.com/bradduthie/PolyInbreed)
+</span>
+
+## General individual-based model overview
+
+<center>
+![](images/ibm_steps_3.png)
+</center>
+
+<span style="font-size: 18px;">
+Code [available on GitHub](https://github.com/bradduthie/PolyInbreed)
+</span>
+
+## General individual-based model overview
+
+<center>
+![](images/ibm_steps_4a.png)
+</center>
+
+<span style="font-size: 18px;">
+Code [available on GitHub](https://github.com/bradduthie/PolyInbreed)
+</span>
+
+## General individual-based model overview
+
+<center>
+![](images/ibm_steps_4b.png)
+</center>
+
+<span style="font-size: 18px;">
+Code [available on GitHub](https://github.com/bradduthie/PolyInbreed)
+</span>
+
+## General individual-based model overview
+
+<center>
+![](images/ibm_steps_5a.png)
+</center>
+
+<span style="font-size: 18px;">
+Code [available on GitHub](https://github.com/bradduthie/PolyInbreed)
+</span>
+
+## General individual-based model overview
+
+<center>
+![](images/ibm_steps_5b.png)
+</center>
+
+<span style="font-size: 18px;">
+Code [available on GitHub](https://github.com/bradduthie/PolyInbreed)
+</span>
+
+## General individual-based model overview
+
+<center>
+![](images/ibm_steps_6.png)
+</center>
+
+<span style="font-size: 18px;">
+Code [available on GitHub](https://github.com/bradduthie/PolyInbreed)
+</span>
 

### 2018-03-02 presentation/inbreeding.Rmd
Slide adjustments

@@
 
-![](images/male.png)
+**Predict when inbreeding avoidance, preference, and tolerance will occur in obligately biparental diploid populations**
 
@@
 
-More generally, is inclusive fitness from inbreeding (left) greater than inclusive fitness from outbreeding?
+More generally, is inclusive fitness from inbreeding (right) greater than inclusive fitness from outbreeding (left)?
 
@@
 <span style="font-size: 14px;">
-[1] Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). <br>
+[1] Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166).
 [2] Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785). 
@@
 
-- Inbreeding tolerance increases with lower encounter rates [1].
+- Inbreeding avoidance is predicted given a sufficiently high threshold of inbreeding depression [1,2]
+
+- Inbreeding depression thresholds differ between females and males causing sexual conflict [1,2]
+
+- **Above** thresholds we predict inbreeding avoidance
+
+- **Below** thresholds we predict inbreeding preference (females) or tolerance (males) [3,4]
 
@@
 <span style="font-size: 14px;">
-[1] Kokko, H & I Ots (2006) *Evolution* [**60**:467-475](http://onlinelibrary.wiley.com/doi/10.1111/j.0014-3820.2006.tb01128.x/abstract).
+[1] Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). 
+[2] Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785). <br>
+[3] Puurtinen (2011) *Evolution* [**65**:1501-1505](https://doi.org/10.1111/j.1558-5646.2010.01217.x).
+[4] Duthie, AB & JM Reid (2016) *Am. Nat.* [188:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf).
+
 </span></div>
@@
 
-- Inbreeding avoidance or preference can affect dispersal [2].
-
 </div>
@@
 [1] Kokko, H & I Ots (2006) *Evolution* [**60**:467-475](http://onlinelibrary.wiley.com/doi/10.1111/j.0014-3820.2006.tb01128.x/abstract).
-[2] Lehmann, L & N Perrin (2003) *Am. Nat.* [**162**:638-652](https://www.journals.uchicago.edu/doi/10.1086/378823). <br>
 </span></div>
@@
 
-- Thresholds change given mating decisions of avoided relatives [3].
-
 </div>
@@
 [2] Lehmann, L & N Perrin (2003) *Am. Nat.* [**162**:638-652](https://www.journals.uchicago.edu/doi/10.1086/378823). <br>
-[3] Duthie, AB & JM Reid (2015) *PLoS One* [**10**:e0125140](https://bradduthie.github.io/Duthie%26Reid2015.pdf). 
 </span></div>
@@
 
-- Thresholds change if parental investment can be modulated [4].
-
 </div>
@@
 [3] Duthie, AB & JM Reid (2015) *PLoS One* [**10**:e0125140](https://bradduthie.github.io/Duthie%26Reid2015.pdf). 
-[4] Duthie, AB et. al (2016) *Proc. R. Soc. B.* [**282**:20161845](https://bradduthie.github.io/Duthie%26Reid2015.pdf).
 </span></div>
@@
 
-- Thresholds change if there are male opportunity costs [5]
-
 </div>
@@
 [3] Duthie, AB & JM Reid (2015) *PLoS One* [**10**:e0125140](https://bradduthie.github.io/Duthie%26Reid2015.pdf). 
-[4] Duthie, AB et. al (2016) *Proc. R. Soc. B.* [**282**:20161845](https://bradduthie.github.io/Duthie%26Reid2015.pdf). <br>
-[5] Waser PM, et. al. (1986) *Am. Nat.* [**128**:529-537](https://www.journals.uchicago.edu/doi/abs/10.1086/284585).
+[4] Duthie, AB et. al (2016) *Proc. R. Soc. B.* [**282**:20161845](https://bradduthie.github.io/Duthie%26Reid2015.pdf).
 </span></div>
 
-## Limitations of this modelling approach
+## Key conceptual take-aways
 
@@
 
-- Focuses on selection to the exclusion of drift, mutation, immigration
+- Inbreeding tolerance increases with lower encounter rates [1].
+
+- Inbreeding avoidance or preference can affect dispersal [2].
+
+- Thresholds change given mating decisions of avoided relatives [3].
+
+- Thresholds change if parental investment can be modulated [4].
+
+- Thresholds change if there are male opportunity costs [5]
 
@@
 
-## Limitations of this modelling approach
-
-<div class = "columns-2">
-
-![](images/real_pedigree.png)
-
-- Focuses on selection to the exclusion of drift, mutation, immigration
-
-- Does not consider realistic distributions of kinship
-
-</div>
-
-## Limitations of this modelling approach
-
-<div class = "columns-2">
-
-![](images/polyandry_eg.png)
-
-- Focuses on selection to the exclusion of drift, mutation, immigration
-
-- Does not consider realistic distributions of kinship
-
-- Does not consider complex strategies such as female multiple mating (polyandry) [but see 1]
-
-</div>
+<hr>
 
@@
 <span style="font-size: 14px;">
-[1] Lehtonen, J & H Kokko (2015) *Proc. R. Soc. B* [**282**:20142716](http://rspb.royalsocietypublishing.org/content/282/1801/20142716).
+[1] Kokko, H & I Ots (2006) *Evolution* [**60**:467-475](http://onlinelibrary.wiley.com/doi/10.1111/j.0014-3820.2006.tb01128.x/abstract).
+[2] Lehmann, L & N Perrin (2003) *Am. Nat.* [**162**:638-652](https://www.journals.uchicago.edu/doi/10.1086/378823). <br>
+[3] Duthie, AB & JM Reid (2015) *PLoS One* [**10**:e0125140](https://bradduthie.github.io/Duthie%26Reid2015.pdf). 
+[4] Duthie, AB et. al (2016) *Proc. R. Soc. B.* [**282**:20161845](https://bradduthie.github.io/Duthie%26Reid2015.pdf). <br>
+[5] Waser PM, et. al. (1986) *Am. Nat.* [**128**:529-537](https://www.journals.uchicago.edu/doi/abs/10.1086/284585).
 </span></div>
@@
 
+```{r, echo = FALSE, fig.width = 4.5}
+ri <- matrix(data=c(1,0.5,0,0.5,1,0,0,0,1),nrow=3,byrow=TRUE);
+Inbreed <- function(focal,mate,alt){
+  Inb <- ri[focal,focal] + ri[focal,mate];
+  Out <- ri[focal,mate]  + ri[focal,alt];
+  DEL <- 1 - (Out/Inb);
+  return(DEL);
+}
+rs <- seq(from=0,to=1,by=0.0001);
+dl <- rep(x=0,length=length(rs));
+for(i in 1:length(rs)){
+  ri <- matrix(data=c(1,rs[i],0,rs[i],1,0,0,0,1),nrow=3,byrow=TRUE);
+  dl[i] <- Inbreed(focal=1,mate=2,alt=3);
+}
+par(mar=c(5,5,1,1));
+plot(x=rs,y=dl,type="l",lwd=2,
+  xlab=expression(paste("Relatedness (",italic(r),")")),
+  ylab=expression(paste(italic(delta)," threshold")),
+  cex.lab=1.5,cex.axis=1.25,ylim=c(0,1));
+Inbreed <- function(focal,mate,alt){
+  Inb <- ri[focal,focal] + ri[focal,mate];
+  Out <- ri[focal,focal]  + ri[focal,alt];
+  DEL <- 1 - (Out/Inb);
+  return(DEL);
+}
+dk <- rep(x=0,length=length(rs));
+for(i in 1:length(rs)){
+  ri <- matrix(data=c(1,rs[i],0,rs[i],1,0,0,0,1),nrow=3,byrow=TRUE);
+  dk[i] <- Inbreed(focal=2,mate=1,alt=3);
+}
+points(x=rs,y=dk,type="l",lwd=2,
+  cex.lab=1.25,cex.axis=1.5,ylim=c(0,1));
+polygon(x=c(rs,rev(rs)),y=c(dk,rev(dl)),col="black");
+polygon(x=c(rs,rev(rs)),y=c(rep(0,length(dk)),rev(dk)),col="grey40");
+points(x=seq(from=0,to=1,by=0.1),y=rep(1,11),type="l");
+points(y=seq(from=0,to=1,by=0.1),x=rep(1,11),type="l");
+text(x=0.75,y=0.16,labels=expression(paste(italic(Female))),cex=1.75, col = "black");
+arrows(x0=0.75,y0=0.2,x1=0.6,y1=0.375, length = 0.15, angle = 30, code = 2, lwd=2);
+text(x=0.75,y=0.84,labels=expression(paste(italic(Male))),cex=1.75, col  = "black");
+arrows(x0=0.75,y0=0.8,x1=0.6,y1=0.625, length = 0.15, angle = 30, code = 2, lwd=2);
+```
+
+- Focuses on selection to the exclusion of drift, mutation, immigration
+
+</div>
+
+## Limitations of this modelling approach
+
+<div class = "columns-2">
+
+![](images/real_pedigree.png)
+
+- Focuses on selection to the exclusion of drift, mutation, immigration
+
+- Does not consider realistic distributions of kinship
+
+</div>
+
+## Limitations of this modelling approach
+
+<div class = "columns-2">
+
 ![](images/polyandry_eg.png)
@@
 
-- Does not consider complex strategies such as female multiple mating (polyandry) [but see 1]
+- Does not consider complex genetic architecture
+
+</div>
+
+## Limitations of this modelling approach
+
+<div class = "columns-2">
+
+![](images/polyandry_eg.png)
+
+- Focuses on selection to the exclusion of drift, mutation, immigration
+
+- Does not consider realistic distributions of kinship
+
+- Does not consider complex genetic architecture
 
@@
 
-<div align="left" style="line-height: 0.6em;">
-<span style="font-size: 14px;">
-[1] Lehtonen, J & H Kokko (2015) *Proc. R. Soc. B* [**282**:20142716](http://rspb.royalsocietypublishing.org/content/282/1801/20142716).
-</span></div>
-
 ## Individual-based modelling approach
@@
 
-- Allows for simultaneous evolution of inbreeding behaviour and polyandry
-
-- Allows for the evolution of pre- and post-copulatory inbreeding behaviour
+- Account for complex genetic architecture undelrying phenotypes
+
+- Allows for the evolution of pre- and post-copulatory inbreeding, and polyandry
 
@@
 </center>
-
-## Individual-based modelling questions
-
-- **When should we predict selection for a mutant allele causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**
-
-- **Why should we predict females will mate multiply to adjust the degree to which they inbreed? [2]**
-
-- **How should we predict females to avoid inbreeding (pre- versus post-copulatory avoidance)? [3]**
-
-<br><br><br><br>
-
-<hr>
-<span style="font-size: 18px;">
-1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf). <br>
-2. Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf). <br>
-3. Duthie, AB et al. (2018) *J. Evol. Biol.* [**31**:31-45](https://bradduthie.github.io/DuthieEtAl2017.pdf). <br>
-</span>
 
@@
 
+## Individual-based modelling questions
+
+- **When should we predict selection for a mutant allele causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**
+
+- **Why should we predict females will mate multiply to adjust the degree to which they inbreed? [2]**
+
+- **How should we predict females to avoid inbreeding (pre- versus post-copulatory avoidance)? [3]**
+
+<br><br><br><br>
+
+<hr>
+<span style="font-size: 18px;">
+1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf). <br>
+2. Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf). <br>
+3. Duthie, AB et al. (2018) *J. Evol. Biol.* [**31**:31-45](https://bradduthie.github.io/DuthieEtAl2017.pdf). <br>
+</span>
+
 ##

### 2018-03-03 presentation/inbreeding.Rmd
More slides, start on results

@@
 
+![](images/terms_ia.png)
+
 <div align="left" style="line-height: 0.6em;">
-<span style="font-size: 14px;">
+<span style="font-size: 14px;"><br>
 Szulkin M, et al. (2013) *Trends Ecol. Evol.* [**28**:205–211](https://doi.org/10.1016/j.tree.2012.10.016). 
+Images: [A. C. Duthie](catherineduthiearts@gmail.com)
 </span></div>
@@
 
+![](images/terms_ip.png)
+
 <div align="left" style="line-height: 0.6em;">
-<span style="font-size: 14px;">
+<span style="font-size: 14px;"><br>
 Szulkin M, et al. (2013) *Trends Ecol. Evol.* [**28**:205–211](https://doi.org/10.1016/j.tree.2012.10.016).
+Images: [A. C. Duthie](catherineduthiearts@gmail.com)
 </span></div>
@@
 
+![](images/terms_it.png)
+
 <div align="left" style="line-height: 0.6em;">
-<span style="font-size: 14px;">
+<span style="font-size: 14px;"><br>
 Szulkin M, et al. (2013) *Trends Ecol. Evol.* [**28**:205–211](https://doi.org/10.1016/j.tree.2012.10.016).
+Images: [A. C. Duthie](catherineduthiearts@gmail.com)
 </span></div>
@@
 <div align="left" style="line-height: 0.6em;">
-<span style="font-size: 14px;">
+<span style="font-size: 14px;"><br>
 Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
@@
 ![](images/fem_choice_3.png)
-</center>
-
+
+</center>
 <div align="left" style="line-height: 0.6em;">
-<span style="font-size: 14px;">
+<span style="font-size: 14px;"><br>
 Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
@@
 <center>
-![](images/fem_choice_4.png)
-</center>
-
+![](images/fem_choice_6.png)
+
+</center>
 <div align="left" style="line-height: 0.6em;">
-<span style="font-size: 14px;">
-Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
-</span></div>
-
-## Encounter between relatives
-
-<center>
-![](images/fem_choice_5.png)
-
-</center>
-
-<div align="left" style="line-height: 0.6em;">
-<span style="font-size: 14px;">
-Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
-</span></div>
-
-## Encounter between relatives
-
-<center>
-![](images/fem_choice_6.png)
-
-</center>
-<div align="left" style="line-height: 0.6em;">
-<span style="font-size: 14px;">
+<span style="font-size: 14px;"><br>
 Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
@@
 
-- Account for complex genetic architecture undelrying phenotypes
+- Account for complex genetic architecture underlying phenotypes
 
@@
 
-- **When should we predict selection for a mutant allele causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**
+- **When should we predict selection for a alleles causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**
 
@@
 </span>
+
+## Mutant allele underlying inbreeding avoidance
+
+<div class = "columns-2">
+
+![](images/avoid_over_time.png)
+
+- Fact one of simulation
+- Fact two
+
+</div>
+<span style="font-size: 18px;">
+1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf). From [Appendix B](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf)
+</span>
+
+## What to do
+
+Histograms -- females and males, versus neutral, add costs.
+
+Emphasis on stochasticity
+
+Population size important
+
+Selection coefficients, inbreeding coefficients, and delta on a half-sib or cousin
+
+Agreement with an infinite alleles model with 10 loci.
+
+##
 

### 2018-03-03 presentation/inbreeding.Rmd
Add more images

@@
 
-- Inbreeding avoidance is predicted given a sufficiently high threshold of inbreeding depression [1,2]
-
-- Inbreeding depression thresholds differ between females and males causing sexual conflict [1,2]
+Inbreeding avoidance is predicted given a sufficiently high threshold of inbreeding depression [1,2]
+
+Inbreeding depression thresholds differ between females and males causing sexual conflict [1,2]
 
@@
 
-- Inbreeding avoidance is predicted given a sufficiently high threshold of inbreeding depression [1,2]
-
-- Inbreeding depression thresholds differ between females and males causing sexual conflict [1,2]
-
-- **Above** thresholds we predict inbreeding avoidance
-
-- **Below** thresholds we predict inbreeding preference (females) or tolerance (males) [3,4]
+Inbreeding avoidance is predicted given a sufficiently high threshold of inbreeding depression [1,2]
+
+Inbreeding depression thresholds differ between females and males causing sexual conflict [1,2]
+
+**Above** thresholds we predict inbreeding avoidance
+
+**Below** thresholds we predict inbreeding preference (females) or tolerance (males) [3,4]
 
@@
 
-- Inbreeding tolerance increases with lower encounter rates [1].
+Inbreeding tolerance increases with lower encounter rates [1].
 
@@
 
-- Inbreeding tolerance increases with lower encounter rates [1].
-
-- Inbreeding avoidance or preference can affect dispersal [2].
+Inbreeding tolerance increases with lower encounter rates [1].
+
+Inbreeding avoidance or preference can affect dispersal [2].
 
@@
 
-- Inbreeding tolerance increases with lower encounter rates [1].
-
-- Inbreeding avoidance or preference can affect dispersal [2].
-
-- Thresholds change given mating decisions of avoided relatives [3].
+Inbreeding tolerance increases with lower encounter rates [1].
+
+Inbreeding avoidance or preference can affect dispersal [2].
+
+Thresholds change given mating decisions of avoided relatives [3].
 
@@
 
-- Inbreeding tolerance increases with lower encounter rates [1].
-
-- Inbreeding avoidance or preference can affect dispersal [2].
-
-- Thresholds change given mating decisions of avoided relatives [3].
-
-- Thresholds change if parental investment can be modulated [4].
+Inbreeding tolerance increases with lower encounter rates [1].
+
+Inbreeding avoidance or preference can affect dispersal [2].
+
+Thresholds change given mating decisions of avoided relatives [3].
+
+Thresholds change if parental investment can be modulated [4].
 
@@
 
-- Inbreeding tolerance increases with lower encounter rates [1].
-
-- Inbreeding avoidance or preference can affect dispersal [2].
-
-- Thresholds change given mating decisions of avoided relatives [3].
-
-- Thresholds change if parental investment can be modulated [4].
-
-- Thresholds change if there are male opportunity costs [5]
+Inbreeding tolerance increases with lower encounter rates [1].
+
+Inbreeding avoidance or preference can affect dispersal [2].
+
+Thresholds change given mating decisions of avoided relatives [3].
+
+Thresholds change if parental investment can be modulated [4].
+
+Thresholds change if there are male opportunity costs [5]
 
@@
 
-- Focuses on selection to the exclusion of drift, mutation, immigration
+Focuses on selection to the exclusion of drift, mutation, immigration
 
@@
 
-- Focuses on selection to the exclusion of drift, mutation, immigration
-
-- Does not consider realistic distributions of kinship
+Focuses on selection to the exclusion of drift, mutation, immigration
+
+Does not consider realistic distributions of kinship
 
@@
 
-- Focuses on selection to the exclusion of drift, mutation, immigration
-
-- Does not consider realistic distributions of kinship
-
-- Does not consider complex genetic architecture
+Focuses on selection to the exclusion of drift, mutation, immigration
+
+Does not consider realistic distributions of kinship
+
+Does not consider complex genetic architecture
 
@@
 
-- Focuses on selection to the exclusion of drift, mutation, immigration
-
-- Does not consider realistic distributions of kinship
-
-- Does not consider complex genetic architecture
-
-- Does not account for post-copulatory inbreeding avoidance or preference
+Focuses on selection to the exclusion of drift, mutation, immigration
+
+Does not consider realistic distributions of kinship
+
+Does not consider complex genetic architecture
+
+Does not account for post-copulatory inbreeding avoidance or preference
 
@@
 
-- Models discrete individual females and males in a finite population
-
-- Explicitly tracks pedigree to calculate kinship between individuals
-
-- Account for complex genetic architecture underlying phenotypes
-
-- Allows for the evolution of pre- and post-copulatory inbreeding, and polyandry
+Models discrete individual females and males in a finite population
+
+Explicitly tracks pedigree to calculate kinship between individuals
+
+Account for complex genetic architecture underlying phenotypes
+
+Allows for the evolution of pre- and post-copulatory inbreeding, and polyandry
 
@@
 
-- **When should we predict selection for a alleles causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**
-
-- **Why should we predict females will mate multiply to adjust the degree to which they inbreed? [2]**
-
-- **How should we predict females to avoid inbreeding (pre- versus post-copulatory avoidance)? [3]**
+**When should we predict selection for a alleles causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**
+
+**Why should we predict females will mate multiply to adjust the degree to which they inbreed? [2]**
+
+**How should we predict females to avoid inbreeding (pre- versus post-copulatory avoidance)? [3]**
 
@@
 
-## Mutant allele underlying inbreeding avoidance
+## Mutant allele underlying inbreeding avoidance {.smaller}
 
@@
 
-- Fact one of simulation
-- Fact two
+Compared frequency of a mutant allele underlying inbreeding avoidance to a mutant neutral allele after 3000 generations.
+
+**100 simulation replicates across multiple parameter values:**
+
+- Selection against deleterious recessives
+- Dominance coefficient of deleterious recessives
+- Direct selection against inbreeding avoidance
+- Offspring produced per female
+- Maximum mates per male
+- Immigrants per generation
+- Female and male carrying capacity
+- Allele mutation rate (forward & back)
+- Effect strength of inbreeding avoidance allele
 
@@
 
+## Mutant allele underlying inbreeding avoidance
+
+<div class = "columns-2">
+
+![](images/F_A.png)
+
+1000 loci with deleterious recessive alleles (homozygotes 2\% survival cost)
+
+Inbreeding depression slope $\beta \approx 1$
+
+$\delta \approx 0.22$ for full siblings
+
+$\delta \approx 0.12$ for half siblings
+
+$\delta \approx 0.06$ for first cousins
+
+</div>
+<span style="font-size: 18px;">
+1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf). From [Appendix B](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf)
+</span>
+
+## Mutant allele underlying inbreeding avoidance
+
+<div class = "columns-2">
+
+![](images/F_A_c0pt01.png)
+
+**Selection for inbreeding avoidance is no longer predicted given a direct fitness cost of 1% for carrying the allele.**
+
+</div>
+<span style="font-size: 18px;">
+1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf). From [Appendix B](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf)
+</span>
+
+## Mutant allele underlying inbreeding avoidance
+
+<div class = "columns-2">
+
+![](images/F_A_alpha20.png)
+
+Selection for inbreeding avoidance is no longer predicted given a direct fitness cost of 1% for carrying the allele.
+
+**Selection for inbreeding avoidance increases when the *effect* of the allele is strengthened (i.e., relatives are avoided at higher probability)**
+
+</div>
+<span style="font-size: 18px;">
+1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf). From [Appendix B](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf)
+</span>
+
+## Mutant allele underlying inbreeding avoidance
+
+<div class = "columns-2">
+
+![](images/M_A.png)
+
+Selection for inbreeding avoidance is no longer predicted given a direct fitness cost of 1% for carrying the allele.
+
+Selection for inbreeding avoidance increases when the *effect* of the allele is strengthened (i.e., relatives are avoided at higher probability)
+
+**Selection for inbreeding avoidance comparable when males rather than females chose mates** (*Note:* Males were mate-limited)
+
+</div>
+<span style="font-size: 18px;">
+1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf). From [Appendix B](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf)
+</span>
+
 ## What to do
 
-Histograms -- females and males, versus neutral, add costs.
-
-Emphasis on stochasticity
-
-Population size important
-
-Selection coefficients, inbreeding coefficients, and delta on a half-sib or cousin
-
-Agreement with an infinite alleles model with 10 loci.
+Add effective population size plot to females before showing males
+
+After briefly showing males, then move on to showing inbreeding preference
+
+Note that inbreeding preference is predicted for females, not males
+
+Move on to different genetic architecture where inbreeding avoidance/preference in same sim
 

### 2018-03-04 presentation/inbreeding.Rmd
More slides up to model 2

@@
   color: #000000;
+}
+ul {
+  color: black;
+}
+ol {
+  color: black;
+}
+a {
+    color: darkblue;
+    text-decoration: none
 }
@@
 
-**When should we predict selection for a alleles causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**
+**When should we predict selection for alleles causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**
 
@@
 
-- Selection against deleterious recessives
-- Dominance coefficient of deleterious recessives
-- Direct selection against inbreeding avoidance
-- Offspring produced per female
-- Maximum mates per male
-- Immigrants per generation
-- Female and male carrying capacity
-- Allele mutation rate (forward & back)
-- Effect strength of inbreeding avoidance allele
-
-</div>
-<span style="font-size: 18px;">
-1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf). From [Appendix B](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf)
+1. Selection against deleterious recessives
+2. Direct selection against inbreeding avoidance
+3. Kin discrimination ability (all vs. only sibs)
+4. Effect strength of inbreeding avoidance allele
+5. Female and male carrying capacity
+6. Dominance coefficient of deleterious recessives
+7. Offspring produced per female
+8. Maximum mates per male
+9. Immigrants per generation
+10. Allele mutation rate (forward & back)
+
+</div>
+<span style="font-size: 18px;">
+Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf). From [Appendix B](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf)
+</span>
+
+## Mutant allele underlying inbreeding avoidance {.smaller}
+
+<div class = "columns-2">
+
+![](images/avoid_over_time.png)
+
+Compared frequency of a mutant allele underlying inbreeding avoidance to a mutant neutral allele after 3000 generations.
+
+**100 simulation replicates across multiple parameter values:**
+
+1. [Selection against deleterious recessives](https://bradduthie.github.io/Duthie_Reid2016.pdf#page=7)
+2. [Direct selection against inbreeding avoidance](https://bradduthie.github.io/Duthie_Reid2016.pdf#page=7)
+3. [Kin discrimination ability (all vs. only sibs)](https://bradduthie.github.io/Duthie_Reid2016_SM.pdf#page=11)
+4. [Effect strength of inbreeding avoidance allele](https://bradduthie.github.io/Duthie_Reid2016_SM.pdf#page=19)
+5. [Female and male carrying capacity](https://bradduthie.github.io/Duthie_Reid2016_SM.pdf#page=17)
+6. Dominance coefficient of deleterious recessives
+7. Offspring produced per female
+8. Maximum mates per male
+9. Immigrants per generation
+10. Allele mutation rate (forward & back)
+
+</div>
+<span style="font-size: 18px;">
+Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf). From [Appendix B](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf)
+</span>
+
+## Mutant allele underlying inbreeding avoidance {.smaller}
+
+<div class = "columns-2">
+
+![](images/neutrals.png)
+
+Compared frequency of a mutant allele underlying inbreeding avoidance to a mutant neutral allele after 3000 generations.
+
+**100 simulation replicates across multiple parameter values:**
+
+1. [Selection against deleterious recessives](https://bradduthie.github.io/Duthie_Reid2016.pdf#page=7)
+2. [Direct selection against inbreeding avoidance](https://bradduthie.github.io/Duthie_Reid2016.pdf#page=7)
+3. [Kin discrimination ability (all vs. only sibs)](https://bradduthie.github.io/Duthie_Reid2016_SM.pdf#page=11)
+4. [Effect strength of inbreeding avoidance allele](https://bradduthie.github.io/Duthie_Reid2016_SM.pdf#page=19)
+5. [Female and male carrying capacity](https://bradduthie.github.io/Duthie_Reid2016_SM.pdf#page=17)
+6. Dominance coefficient of deleterious recessives
+7. Offspring produced per female
+8. Maximum mates per male
+9. Immigrants per generation
+10. Allele mutation rate (forward & back)
+
+</div>
+<span style="font-size: 18px;">
+Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016_AppendixA.pdf). From [Appendix A](https://bradduthie.github.io/Duthie_Reid2016_AppendixA.pdf)
 </span>
@@
 
-$\delta \approx 0.22$ for full siblings
-
-$\delta \approx 0.12$ for half siblings
-
-$\delta \approx 0.06$ for first cousins
-
-</div>
-<span style="font-size: 18px;">
-1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf). From [Appendix B](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf)
+$\delta \approx 0.22$ for offspring of full siblings
+
+$\delta \approx 0.12$ for offspring of half siblings
+
+$\delta \approx 0.06$ for offspring of first cousins
+
+</div>
+<span style="font-size: 18px;">
+Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016).
 </span>
@@
 <span style="font-size: 18px;">
-1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf). From [Appendix B](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf)
+Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf).
 </span>
@@
 
+![](images/F_A_sib.png)
+
+Selection for inbreeding avoidance is no longer predicted given a direct fitness cost of 1% for carrying the allele.
+
+**Selection for inbreeding avoidance was limited when females could only identify siblings as kin.**
+
+</div>
+<span style="font-size: 18px;">
+Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf). 
+</span>
+
+## Mutant allele underlying inbreeding avoidance
+
+<div class = "columns-2">
+
 ![](images/F_A_alpha20.png)
@@
 
-**Selection for inbreeding avoidance increases when the *effect* of the allele is strengthened (i.e., relatives are avoided at higher probability)**
-
-</div>
-<span style="font-size: 18px;">
-1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf). From [Appendix B](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf)
+Selection for inbreeding avoidance was limited when females could only identify siblings as kin.
+
+**Selection for inbreeding avoidance increases when the *effect* of the allele is strengthened (i.e., relatives are avoided at higher probability).**
+
+</div>
+<span style="font-size: 18px;">
+Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf). 
 </span>
@@
 
-![](images/M_A.png)
+![](images/F_A_Ne.png)
 
@@
 
-Selection for inbreeding avoidance increases when the *effect* of the allele is strengthened (i.e., relatives are avoided at higher probability)
-
-**Selection for inbreeding avoidance comparable when males rather than females chose mates** (*Note:* Males were mate-limited)
-
-</div>
-<span style="font-size: 18px;">
-1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf). From [Appendix B](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf)
-</span>
-
-## What to do
-
-Add effective population size plot to females before showing males
-
-After briefly showing males, then move on to showing inbreeding preference
-
-Note that inbreeding preference is predicted for females, not males
-
-Move on to different genetic architecture where inbreeding avoidance/preference in same sim
-
-##
+Selection for inbreeding avoidance was limited when females could only identify siblings as kin.
+
+Selection for inbreeding avoidance increases when the *effect* of the allele is strengthened (i.e., relatives are avoided at higher probability).
+
+**Selection was stronger at *lower* N<sub>e</sub> due to *increased* inbreeding risk.**
+
+</div>
+<span style="font-size: 18px;">
+Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf). 
+</span>
+
+## Mutant allele underlying inbreeding preference
+
+<div class = "columns-2">
+
+![](images/F_P.png)
+
+1000 loci with deleterious recessive alleles (homozygotes 0.4\% survival cost)
+
+Inbreeding depression slope $\beta \approx 0.5$
+
+$\delta \approx 0.12$ for offspring of full siblings
+
+$\delta \approx 0.06$ for offspring of half siblings
+
+$\delta \approx 0.03$ for offspring of first cousins
+
+</div>
+<span style="font-size: 18px;">
+Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016).
+</span>
+
+## Population genetic model conclusions
+
+**Overall, selection for a mutant allele underlying inbreeding avoidance:**
+
+1. **Increased** given [stronger selection against deleterious recessives](https://bradduthie.github.io/Duthie_Reid2016.pdf#page=7)
+2. **Decreased** given [direct selection against inbreeding avoidance](https://bradduthie.github.io/Duthie_Reid2016.pdf#page=7)
+3. **Decreased** given restricted [kin discrimination ability (all vs. only sibs)](https://bradduthie.github.io/Duthie_Reid2016_SM.pdf#page=11)
+4. **Increased** given an increasing [effect strength of inbreeding avoidance allele](https://bradduthie.github.io/Duthie_Reid2016_SM.pdf#page=19)
+5. **Decreased** given increased [female and male carrying capacity](https://bradduthie.github.io/Duthie_Reid2016_SM.pdf#page=17) (and consequent increase in effective population size)
+
+<br><br><br><br>
+
+</div>
+<span style="font-size: 18px;">
+Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016).
+</span>
+
+## Population genetic model conclusions
+
+**Additional conclusions:**
+
+- [Comparable selection](https://bradduthie.github.io/Duthie_Reid2016_SM.pdf\page=11) for inbreeding avoidance alleles was observed when males chose (*note*, males were mate limited when choosing).
+- Weak inbreeding depression caused selection for inbreeding preference when *females* chose, but not when *males* chose mates.
+- [No evidence of purging](https://bradduthie.github.io/Duthie_Reid2016_SM.pdf#page=5) in simulations with mutant alleles underlying inbreeding avoidance or preference.
+
+<br><br><br><br><br><br>
+
+</div>
+<span style="font-size: 18px;">
+Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016).
+</span>
+
+## Multi-locus model with infinite alleles
+
+<div class = "columns-2">
+
+![](images/beta_slopes.png)
+
+Multi-locus genetic architecture:
+
+- Fixed inbreeding depression for individual *f*
+- Allele values at 10 loci increase (positive) or decrease (negative) inbreeding
+- Allele values sum additively to determine overall inbreeding behaviour phenotype
+
+</div>
+
+<span style="font-size: 18px;">
+Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf).
+</span>
+
+## Multi-locus model with infinite alleles
+
+<div class = "columns-2">
+
+![](images/IA_quant.png)
+
+Multi-locus genetic architecture:
+
+- Fixed inbreeding depression for individual *f*
+- Allele values at 10 loci increase (positive) or decrease (negative) inbreeding
+- Allele values sum additively to determine overall inbreeding behaviour phenotype
+
+</div>
+
+<span style="font-size: 18px;">
+Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf).
+</span>
+
+## Inbreeding adjustment through multiple mating {.smaller}
 

### 2018-03-04 presentation/inbreeding.Rmd
Small tweaks -- presentation moved to 4 APR

@@
 
+## Selection against inbreeding
+
+<div class = "columns-2">
+
+![](images/par_vs_off.png)
+
+**Selection against being inbred does not necessarily imply selection against inbreeding**
+
+</div>
+
+<span style="font-size: 18px;">
+Reid, JM et al. (2015). *Evolution* [69:2846-2861](https://doi.org/10.5061/dryad.0015b).
+</span>
+
 ## Inbreeding adjustment through multiple mating {.smaller}
+
+## Other stuff to do
+
+Make point about inbreeding adjustment given strong constraints
+
+Make point that it's hard to detect through a change in kinship (and subject to bias)
+
+Make point that pre, post and polyandry evolve given strong ID and no costs
+
+Make point that opportunity for post-cop greatly increases polyandry selection
+
+Make point that selection tends to go with the least costly IA route
 

### 2018-03-05 presentation/inbreeding.Rmd
Fix date

@@
 author: "Brad Duthie"
-date: "6 March 2018"
+date: "3 April 2018"
 output: 

### 2018-03-31 presentation/inbreeding.Rmd
Update slides
More slides

@@
 
+<center>
+![](images/pop_gen_inds.png)
+</center>
+
+## Mutant allele underlying inbreeding avoidance {.smaller}
+
 <div class = "columns-2">
@@
 
-<div class = "columns-2">
-
-![](images/beta_slopes.png)
-
-Multi-locus genetic architecture:
-
-- Fixed inbreeding depression for individual *f*
-- Allele values at 10 loci increase (positive) or decrease (negative) inbreeding
-- Allele values sum additively to determine overall inbreeding behaviour phenotype
+<center>
+![](images/quant_inds.png)
+</center>
+
+## Multi-locus model with infinite alleles
+
+<center>
+
+![](images/fixed_ID_inds.png)
+
+</center>
+
+## Multi-locus model with infinite alleles
+
+<center>
+![](images/neutral_exp_inds.png)
+</center>
+
+## Multi-locus model with infinite alleles
+
+<div class = "columns-2">
+
+![](images/IA_quant.png)
+
+<br><br><br><br>
+
+High variation of inbreeding behaviour across inbreeding depression slopes.
 
@@
 
-## Multi-locus model with infinite alleles
-
-<div class = "columns-2">
-
-![](images/IA_quant.png)
-
-Multi-locus genetic architecture:
-
-- Fixed inbreeding depression for individual *f*
-- Allele values at 10 loci increase (positive) or decrease (negative) inbreeding
-- Allele values sum additively to determine overall inbreeding behaviour phenotype
-
-</div>
-
-<span style="font-size: 18px;">
-Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf).
-</span>
-
 ## Selection against inbreeding
@@
 
-**Selection against being inbred does not necessarily imply selection against inbreeding**
+<br><br><br><br>
+
+Selection against being inbred does not necessarily imply selection against inbreeding
 
@@
 ## Inbreeding adjustment through multiple mating {.smaller}
+
+<center>
+![](images/poly_inds.png)
+
+</center>
+
+## Inbreeding adjustment through multiple mating {.smaller}
+
+<center>
+![](images/mate_select_1.png)
+
+</center>
+
+## Inbreeding adjustment through multiple mating {.smaller}
+
+<center>
+![](images/mate_select_2.png)
+
+</center>
+
+## Inbreeding adjustment through multiple mating {.smaller}
+
+<center>
+![](images/mate_select_3.png)
+
+</center>
+
+## Inbreeding adjustment through multiple mating {.smaller}
+
+<center>
+![](images/mate_select_4.png)
+
+</center>
+
+## Inbreeding adjustment through multiple mating {.smaller}
+
+<center>
+![](images/mate_select_5.png)
+
+</center>
+
+## Inbreeding adjustment through multiple mating {.smaller}
+
+<center>
+![](images/mate_select_6.png)
+
+</center>
+
+## Inbreeding adjustment through multiple mating {.smaller}
+
+<center>
+![](images/mate_select_7.png)
+
+</center>
+
+## Inbreeding adjustment through multiple mating {.smaller}
+
+<center>
+![](images/poly_allele_res.png)
+
+</center>
+
+## Inbreeding adjustment through multiple mating {.smaller}
+
+<center>
+![](images/poly_pheno_res.png)
+
+</center>
 

### 2018-03-31 presentation/inbreeding.Rmd
More slides

@@
 <center>
+![](images/poly_motivation.png)
+
+</center>
+
+## Inbreeding adjustment through multiple mating {.smaller}
+
+<center>
+![](images/fem_poly_1.png)
+
+</center>
+
+## Inbreeding adjustment through multiple mating {.smaller}
+
+<center>
+![](images/fem_poly_2.png)
+
+</center>
+
+## Inbreeding adjustment through multiple mating {.smaller}
+
+<center>
 ![](images/poly_inds.png)
@@
 
+<span style="font-size: 18px;">
+Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf).
+</span>
+
 ## Inbreeding adjustment through multiple mating {.smaller}
@@
 
+<span style="font-size: 18px;">
+Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf).
+</span>
+
+## Inbreeding adjustment through multiple mating {.smaller}
+
+<center>
+![](images/inbr_adjust_res0.png)
+
+</center>
+
+## Inbreeding adjustment through multiple mating {.smaller}
+
+<center>
+![](images/inbr_adjust_res.png)
+
+</center>
+
+<span style="font-size: 18px;">
+Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf).
+</span>
+
+## Inbreeding adjustment conclusions
+
+1.
+Selection for females to increase or decrease pre-copulatory inbreeding through multiple mating, [depending on inbreeding depression](https://bradduthie.github.io/DuthieEtAl2016b.pdf#page=11) ($\beta$).
+2. Realised inbreeding adjustment ($k_{adj}$) often [small and difficult to detect](https://bradduthie.github.io/DuthieEtAl2016b.pdf#page=11).
+
+<br><br><br><br>
+
+</div>
+<span style="font-size: 18px;">
+Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf).
+</span>
+
+## Post-copulatory inbreeding avoidance {.smaller}
+
+<center>
+![](images/pre_post_1.png)
+
+</center>
+
+<span style="font-size: 18px;">
+Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf).
+</span>
+
+## Post-copulatory inbreeding avoidance {.smaller}
+
+<center>
+![](images/pre_post_2.png)
+
+</center>
+
+<span style="font-size: 18px;">
+Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf).
+</span>
+
+## Post-copulatory inbreeding avoidance {.smaller}
+
+<center>
+![](images/pre_post_3.png)
+
+</center>
+
+<span style="font-size: 18px;">
+Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf).
+</span>
+
 ## Other stuff to do
-
-Make point about inbreeding adjustment given strong constraints
 

### 2018-04-01 presentation/inbreeding.Rmd
More slides

@@
 
-## When to inbreed versus avoid inbreeding?
-
-<div class = "columns-2">
-
-```{r, echo = FALSE, fig.width = 3}
-mbox <- function(x0, x1, y0, y1){
-    xx <- seq(from=x0, to=x1, length.out = 100);
-    yy <- seq(from=y0, to=y1, length.out = 100);
-    xd <- c(rep(x0, 100), xx, rep(x1,100), rev(xx));
-    yd <- c(yy, rep(y1,100), rev(yy), rep(y0, 100));
-    return(list(x=xd, y=yd));
-}
-inputPanel(
-  sliderInput("rr", label = "Relatedness", width="100%",
-              min = 0.0, max = 1, value = 0, step = 0.05), 
-  sliderInput("dd", label = "Inbreeding Depression", width="100%",
-              min = 0.0, max = 1, value = 0, step = 0.1)
-)
-renderPlot({
-    par(bg = 'transparent', mar = c(0.5, 0.5, 0.5, 0.5));
-    plot(x = -1:1, y = -1:1, xaxt = "n", yaxt = "n", xlab = "", ylab = "Fitness", 
-         type = "n", xlim = c(-1, 1), ylim = c(-1, 1), bty = "n");
-    val <- seq(from = (-1 * pi)/4, to = (1 * pi)/4, length = 1000);
-    hx  <- cos(val);
-    hy  <- sin(val);
-    fva <- seq(from = 0, to = 1, length = 1000);
-    fit <- 0.5*(1 + input$rr)*(1 - input$dd);
-    sqd <- (fva - fit)*(fva - fit);
-    clf <- which(sqd == min(sqd));
-    fx  <- cos(val[clf]);
-    fy  <- sin(val[clf]);
-    points(x = hx, y = hy, lwd = 2, type = "l");
-    points(x = seq(from = 0, to = 1, length = 100), y = rep(0, 100), 
-           type = "l", lty = "dotted", col = "red");
-    ia_box <- mbox(x0 = -1.1, x1 = -0.1, y0 = -0.9, y1 = -1.1);
-    polygon(x=ia_box$x, y=ia_box$y, lwd=3, border="black", col="black");
-    ip_box <- mbox(x0 = 0.1, x1 = 1.1, y0 = -0.9, y1 = -1.1);
-    polygon(x=ip_box$x, y=ip_box$y, lwd=3, border="black", col="black");
-    points(x = seq(from = -1, to = 1, length = 100), y = rep(-0.85, 100), 
-           lwd = 6, type = "l");
-    points(x = rep(0, 100), y = seq(from = -0.85, to = 0, length = 100), 
-           lwd = 6, type = "l");
-    text(x = -0.6, y = -1, labels = "Avoid inbreeding", cex = 1.75, col = "red");
-    text(x = 0.6, y = -1, labels = "Inbreeding", cex = 1.75, col = "white");
-    text(x = 0.8, y = 0.75, labels = "n", cex = 3);
-    text(x = 0.8, y = -0.75, labels = "0", cex = 3);
-    text(x = -1, y = 0, labels = expression(frac(n,2)), cex = 3);
-    arrows(x0 = 0, x1 = fx, y0 = 0, y1 = fy, lwd = 3, col = "black");
-    arrows(x0 = 0, x1 = -0.9, y0 = 0, y1 = 0, lwd = 3, col = "red");
-    points(x = 0, y = 0, cex = 5, pch = 20, col = "black");
-    points(x = 0, y = 0, cex = 3, pch = 20, col = "red");
-})
-```
-
-<br><br><br><br>
-
-Is inclusive fitness from avoiding inbreeding (left side) less than inbreeding (right side)?
-
-$$\frac{n}{2} < \frac{n}{2} (1 + r)(1 - \delta)$$
-
-More generally, is inclusive fitness from inbreeding (right) greater than inclusive fitness from outbreeding (left)?
-
-$$\delta < \frac{r}{1+r}$$
-
-</div>
+## Encounter between relatives
+
+<center>
+![](images/fem_choice_7.png)
+
+</center>
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;"><br>
+Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785).
+</span></div>
 
@@
 Inbreeding depression thresholds differ between females and males causing sexual conflict [1,2]
+
+**Female threshold:**
+
+$$1 > (1+r)(1-\delta)$$
+
+**Male threshold:**
+
+$$r > (1+r)(1-\delta)$$
 
@@
 
+![](images/hist_blank.png)
+<br><br><br><br><br><br><br><br>
+
+</div>
+
+## Mutant allele underlying inbreeding avoidance
+
+<div class = "columns-2">
+
 ![](images/F_A.png)
@@
 
-<br><br><br><br><br><br>
+<br><br><br><br><br>
 
@@
 
+<br><br><br><br><br><br><br><br><br><br><br>
+
+</div>
+<span style="font-size: 18px;">
+Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf).
+</span>
+
+## Post-copulatory inbreeding avoidance {.smaller}
+
+<center>
+![](images/pre_post_inds.png)
+
+</center>
+
+## Effect of post-copulatory selection on polyandry {.smaller}
+
+<center>
+![](images/pre_post_1.png)
+
+</center>
+
+<br>
+
+<span style="font-size: 18px;">
+Duthie, AB et al. (2018) *J. Evol. Biol.* [**31**:31-45](https://bradduthie.github.io/DuthieEtAl2017.pdf).
+</span>
+
+## Effect of post-copulatory selection on polyandry {.smaller}
+
+<center>
+![](images/pre_post_2.png)
+
+</center>
+
+<br>
+
+<span style="font-size: 18px;">
+Duthie, AB et al. (2018) *J. Evol. Biol.* [**31**:31-45](https://bradduthie.github.io/DuthieEtAl2017.pdf).
+</span>
+
+## Effect of post-copulatory selection on polyandry {.smaller}
+
+<center>
+![](images/pre_post_3.png)
+
+</center>
+
+<br>
+
+<span style="font-size: 18px;">
+Duthie, AB et al. (2018) *J. Evol. Biol.* [**31**:31-45](https://bradduthie.github.io/DuthieEtAl2017.pdf).
+</span>
+
+## Effect of post-copulatory selection on polyandry {.smaller}
+
+<center>
+![](images/pre_post_cost_comp.png)
+</center>
+
+<br>
+
+<span style="font-size: 18px;">
+Duthie, AB et al. (2018) *J. Evol. Biol.* [**31**:31-45](https://bradduthie.github.io/DuthieEtAl2017.pdf).
+</span>
+
+## Post-copulatory inbreeding avoidance conclusions
+
+1. Post-copulatory inbreeding avoidance can [greatly strengthen for polyandry](https://bradduthie.github.io/DuthieEtAl2017.pdf#page=8)
+2. How inbreeding is avoided is affected by the [relative cost of pre-copulatory versus post-copulatory choice](https://bradduthie.github.io/DuthieEtAl2017.pdf#page=10)
+
+<br><br><br><br><br><br><br><br><br>
+
+<span style="font-size: 18px;">
+Duthie, AB et al. (2018) *J. Evol. Biol.* [**31**:31-45](https://bradduthie.github.io/DuthieEtAl2017.pdf).
+</span>
+
+## Individual-based models: general conclusions
+
+**When should we predict selection for alleles causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**
+
+**Why should we predict females will mate multiply to adjust the degree to which they inbreed? [2]**
+
+**How should we predict females to avoid inbreeding (pre- versus post-copulatory avoidance)? [3]**
+
 <br><br><br><br>
 
-</div>
-<span style="font-size: 18px;">
-Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf).
-</span>
-
-## Post-copulatory inbreeding avoidance {.smaller}
-
-<center>
-![](images/pre_post_1.png)
-
-</center>
-
-<span style="font-size: 18px;">
-Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf).
-</span>
-
-## Post-copulatory inbreeding avoidance {.smaller}
-
-<center>
-![](images/pre_post_2.png)
-
-</center>
-
-<span style="font-size: 18px;">
-Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf).
-</span>
-
-## Post-copulatory inbreeding avoidance {.smaller}
-
-<center>
-![](images/pre_post_3.png)
-
-</center>
-
-<span style="font-size: 18px;">
-Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf).
-</span>
-
-## Other stuff to do
-
-Make point that it's hard to detect through a change in kinship (and subject to bias)
-
-Make point that pre, post and polyandry evolve given strong ID and no costs
-
-Make point that opportunity for post-cop greatly increases polyandry selection
-
-Make point that selection tends to go with the least costly IA route
+<hr>
+<span style="font-size: 18px;">
+1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf). <br>
+2. Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf). <br>
+3. Duthie, AB et al. (2018) *J. Evol. Biol.* [**31**:31-45](https://bradduthie.github.io/DuthieEtAl2017.pdf). <br>
+</span>
+
+## Individual-based models: general conclusions
+
+**When should we predict selection for alleles causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**
+
+<hr>
+<span style="font-size: 18px;">
+1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf). <br>
+
+</span>
+
+## Individual-based models: general conclusions
+
+**Why should we predict females will mate multiply to adjust the degree to which they inbreed? [2]**
+
+<br><br><br><br>
+
+<hr>
+<span style="font-size: 18px;">
+2. Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf). <br>
+</span>
+
+## Individual-based models: general conclusions
+
+**How should we predict females to avoid inbreeding (pre- versus post-copulatory avoidance)? [3]**
+
+<br><br><br><br>
+
+<hr>
+<span style="font-size: 18px;">
+3. Duthie, AB et al. (2018) *J. Evol. Biol.* [**31**:31-45](https://bradduthie.github.io/DuthieEtAl2017.pdf). <br>
+</span>
+
+## Modulating parental investment and inbreeding
 

### 2018-04-02 presentation/inbreeding.Rmd
New slides

@@
 
-## Individual-based models: general conclusions
+## Individual-based models: general conclusions {.smaller}
 
@@
 
+- Inbreeding depression strong (avoidance) or very weak (preference)
+- Low direct costs of non-random mating
+- Small population size where risk of inbreeding is high
+
+<br><br><br><br>
+
+<br><br><br><br>
+
+<hr>
+<span style="font-size: 18px;">
+1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf). <br>
+</span>
+
+## Individual-based models: general conclusions {.smaller}
+
+**When should we predict selection for alleles causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**
+
+- Inbreeding depression strong (avoidance) or very weak (preference)
+- Low direct costs of non-random mating
+- Small population size where risk of inbreeding is high
+
 **Why should we predict females will mate multiply to adjust the degree to which they inbreed? [2]**
 
+- Strong constraints on initial mate choice
+- Opportunity for post-copulatory inbreeding adjustment
+
+<br><br><br><br>
+
+<hr>
+<span style="font-size: 18px;">
+1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf). <br>
+2. Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf). <br>
+</span>
+
+## Individual-based models: general conclusions {.smaller}
+
+**When should we predict selection for alleles causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**
+
+- Inbreeding depression strong (avoidance) or very weak (preference)
+- Low direct costs of non-random mating
+- Small population size where risk of inbreeding is high
+
+**Why should we predict females will mate multiply to adjust the degree to which they inbreed? [2]**
+
+- Strong constraints on initial mate choice
+- Opportunity for post-copulatory inbreeding adjustment
+
 **How should we predict females to avoid inbreeding (pre- versus post-copulatory avoidance)? [3]**
 
-<br><br><br><br>
+- Selection for less costly way to avoid inbreeding
+- Polyandry modulates importance of pre-copulatory versus post-copulatory inbreeding avoidance
 
@@
 
-## Individual-based models: general conclusions
-
-**When should we predict selection for alleles causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**
+## Modulating parental investment and inbreeding
+
+![](images/opening.png)
+
+<div align="left" style="line-height: 0.6em;">
+<span style="font-size: 14px;">
+1.
+[Wibowo Djatmiko](https://commons.wikimedia.org/wiki/User:Wie146).
+2.
+[George Shuklin](https://commons.wikimedia.org/wiki/User:George_Shuklin).
+3.
+[Natalie Pilakouta](https://www.nataliepilakouta.com/).
+4.
+[Neale Monks](https://en.wikipedia.org/wiki/User:Neale_Monks).
+5.
+[Jane Reid](https://www.abdn.ac.uk/ibes/profiles/jane.reid).
+6.
+[André Karwath](https://commons.wikimedia.org/wiki/User:Aka).
+<br> 7.
+[Benjamin Twist](https://commons.wikimedia.org/wiki/User:Benjamint444) (benjamint444@gmail.com) 8.
+[Heinz Seehagel](https://de.wikipedia.org/wiki/Benutzer:HaSee).
+9.
+[Adam Hayward](https://adhayward.wordpress.com/)
+</span></div>
+
+## What parental investment is, specifically
+
+**Anything that a parent does to increase its offspring's viability *at the expense of its other actual or potential offspring*** [1]
+
+<br><br><br>
+
+(Includes, but is not limited to, behaviour)
+
+<br><br><br><br><br><br>
 
@@
 <span style="font-size: 18px;">
-1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf). <br>
-
-</span>
-
-## Individual-based models: general conclusions
-
-**Why should we predict females will mate multiply to adjust the degree to which they inbreed? [2]**
-
-<br><br><br><br>
-
+1. Trivers R. (1974) *Am. Zool.* [**14**:249–264](https://doi.org/10.1093/icb/14.1.249) <br>
+</span>
+
+## Why parental investment is important
+
+<div class = "columns-2">
+
+- Models of inbreeding assume no concurrent modulation of parental investment or offspring production
+
+- Parents might be able to increase the viability of their inbred offspring through parental investment [1]
+
+- Parents are more closely related to inbred offspring than outbred offspring
+
+![](images/N_vespilloides_1.jpg)
+
+</div>
+<br>
 <hr>
 <span style="font-size: 18px;">
-2. Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf). <br>
-</span>
-
-## Individual-based models: general conclusions
-
-**How should we predict females to avoid inbreeding (pre- versus post-copulatory avoidance)? [3]**
-
-<br><br><br><br>
-
-<hr>
-<span style="font-size: 18px;">
-3. Duthie, AB et al. (2018) *J. Evol. Biol.* [**31**:31-45](https://bradduthie.github.io/DuthieEtAl2017.pdf). <br>
-</span>
-
-## Modulating parental investment and inbreeding
+1. Pilakouta, N et al. (2015) *PNAS* [**112**:201500658](http://www.pnas.org/content/112/26/8031). <br>
+</span>
+
+## Parental investment and offspring number
+
+<div class = "columns-2">
+```{r, echo = FALSE, fig.width = 5}
+M <- 10;
+m <- seq(from = 0, to = 4, by = 0.1);
+n <- M/m;
+par(mar = c(5, 5, 1, 1));
+plot(x = m, y = n, type = "l", lwd = 3, cex.lab = 1.5, cex.axis = 1.5,
+     xlab = "Parental investment (m)", ylab = "Offspring produced (n)",
+     ylim = c(0, 20));
+text(x = 3.25, y = 16, labels = expression(paste(n == frac(M,m))), cex = 2.5);
+```
+
+- Offspring produced (n) decreases with investment per offspring (m)
+
+## Parental investment and offspring number
+
+<div class = "columns-2">
+```{r, echo = FALSE, fig.width = 5}
+V <- 1 * (1 - exp(-1 * (m - 1)));
+V[V<0] <- NA;
+par(mar = c(5, 5, 1, 1));
+plot(x = m, y = V, type = "l", lwd = 3, cex.lab = 1.5, cex.axis = 1.5,
+     xlab = "Parental investment (m)", 
+     ylab = expression(paste("Offspring viability (",upsilon,")")),
+     ylim = c(0, 1));
+text(x = 1.2, y = 0.9, labels = expression(upsilon == 1 - e^{-c(m - m[min])}), 
+     cex = 1.75);
+```
+
+- Offspring produced ($n$) decreases with investment per offspring ($m$)
+- Offspring viability ($\upsilon$) increases with investment per offspring
+
+## Parental investment and offspring number
+
+<div class = "columns-2">
+```{r, echo = FALSE, fig.width = 5}
+V <- 1 * (1 - exp(-1 * (m - 1)));
+V[V<0] <- NA;
+par(mar = c(5, 5, 1, 1));
+plot(x = m, y = V, type = "l", lwd = 3, cex.lab = 1.5, cex.axis = 1.5,
+     xlab = "Parental investment (m)", 
+     ylab = expression(paste("Offspring viability (",upsilon,")")),
+     ylim = c(0, 1));
+text(x = 1.2, y = 0.9, labels = expression(upsilon == 1 - e^{-c(m - m[min])}), 
+     cex = 1.75);
+abline(a = 0, b = 2*0.3410784 / 2.146197, lty = "dashed");
+arrows(x0=2.146197,y0=0.3,x1=2.146197,y1=0,
+       length = 0.15,angle=30,code=2,lwd=3);
+text(x=2.146197,y=0.4,labels=expression(paste(italic(m)^"*")),cex=2);
+```
+
+- Offspring produced ($n$) decreases with investment per offspring ($m$)
+- Offspring viability ($\upsilon$) increases with investment per offspring
+- Highest rate of viable offspring production defines optimal parental investment ($m^{*}$)
 

### 2018-04-02 presentation/inbreeding.Rmd
New slides, almost done

@@
 
+</div>
+
 ## Parental investment and offspring number
@@
 - Offspring viability ($\upsilon$) increases with investment per offspring
+
+</div>
 
@@
 - Highest rate of viable offspring production defines optimal parental investment ($m^{*}$)
+
+## Parental investment and offspring number
+
+<div class = "columns-2">
+```{r, echo = FALSE, fig.width = 5}
+V <- 1 * (1 - exp(-1 * (m - 1)));
+V[V<0] <- NA;
+par(mar = c(5, 5, 1, 1));
+plot(x = m, y = V, type = "l", lwd = 3, cex.lab = 1.5, cex.axis = 1.5,
+     xlab = "Parental investment (m)", 
+     ylab = expression(paste("Offspring viability (",upsilon,")")),
+     ylim = c(0, 1));
+text(x = 1.2, y = 0.9, labels = expression(upsilon == 1 - e^{-c(m - m[min])}), 
+     cex = 1.75);
+abline(a = 0, b = 2*0.3410784 / 2.146197, lty = "dashed");
+arrows(x0=2.146197,y0=0.3,x1=2.146197,y1=0,
+       length = 0.15,angle=30,code=2,lwd=3);
+text(x=2.146197,y=0.4,labels=expression(paste(italic(m)^"*")),cex=2);
+```
+
+- Offspring produced ($n$) decreases with investment per offspring ($m$)
+- Offspring viability ($\upsilon$) increases with investment per offspring
+- Highest rate of viable offspring production defines optimal parental investment ($m^{*}$)
+- Optimally investing parents produce $W = n \times \upsilon^{*}$ offspring
+
+</div>
+
+## Synthesis of inbreeding and parental investment
+
+<center>
+![](images/In_PI_1.png)
+</center>
+
+<span style="font-size: 18px;">
+1. Duthie, AB et al. (2016) *Proc. R. Soc. B* [**282**:20161845](https://bradduthie.github.io/DuthieEtAl2016c.pdf). <br>
+</span>
+
+## Synthesis of inbreeding and parental investment
+
+<center>
+![](images/In_PI_2.png)
+</center>
+
+<span style="font-size: 18px;">
+1. Duthie, AB et al. (2016) *Proc. R. Soc. B* [**282**:20161845](https://bradduthie.github.io/DuthieEtAl2016c.pdf). <br>
+</span>
+
+## Synthesis of inbreeding and parental investment
+
+<center>
+![](images/In_PI_3.png)
+</center>
+
+<span style="font-size: 18px;">
+1. Duthie, AB et al. (2016) *Proc. R. Soc. B* [**282**:20161845](https://bradduthie.github.io/DuthieEtAl2016c.pdf). <br>
+</span>
+
+## Synthesis of inbreeding and parental investment
+
+<center>
+![](images/In_PI_4.png)
+</center>
+
+<span style="font-size: 18px;">
+1. Duthie, AB et al. (2016) *Proc. R. Soc. B* [**282**:20161845](https://bradduthie.github.io/DuthieEtAl2016c.pdf). [SI-1](https://bradduthie.github.io/DuthieEtAl2016c_SI.pdf) <br>
+</span>
+
+## Synthesis of inbreeding and parental investment
+
+<center>
+![](images/In_PI_5.png)
+</center>
+
+<span style="font-size: 18px;">
+1. Duthie, AB et al. (2016) *Proc. R. Soc. B* [**282**:20161845](https://bradduthie.github.io/DuthieEtAl2016c.pdf). [SI-1](https://bradduthie.github.io/DuthieEtAl2016c_SI.pdf) <br>
+</span>
 
@@
 ```
+
+## Acknowledgements
+
+## General conclusions {.smaller}
+
+**Predict selection for an allele causing inbreeding avoidance or preference when:**
+
+- Inbreeding depression strong (avoidance) or very weak (preference)
+- Low direct costs of non-random mating
+- Small population size where risk of inbreeding is high
+
+**Females should mate multiply to adjust inbreeding given:**
+
+- Strong constraints on initial mate choice
+- Opportunity for post-copulatory inbreeding adjustment
+
+**Multiple factors affecting how to avoid inbreeding, including:**
+
+- Direct costs on pre- versus post-copulatory inbreeding avoidance
+- Polyandry modulates selection on pre- versus post-copulatory inbreeding avoidance
+
+**Increased mate relatedness and inbreeding depression will cause optimal parental investment to increase**

### 2018-04-02 presentation/inbreeding.Rmd
Nearly finished with all slides

@@
 
+<br><br><br>
+
 - Offspring produced (n) decreases with investment per offspring (m)
@@
 ```
+
+<br><br><br>
 
@@
 
+<br><br><br>
+
 - Offspring produced ($n$) decreases with investment per offspring ($m$)
@@
 - Highest rate of viable offspring production defines optimal parental investment ($m^{*}$)
+
+</div>
 
@@
 
-## Acknowledgements
+##
+
+<div class = "columns-2">
+
+**Coauthors**
+
+- [Greta Bocedi](https://www.abdn.ac.uk/sbs/people/profiles/greta.bocedi)
+- [Ryan Germain](http://ryanrgermain.wixsite.com/ecol-evol)
+- [Aline Lee](https://www.ntnu.edu/employees/aline.m.lee)
+- [Jane Reid](https://www.abdn.ac.uk/ibes/profiles/jane.reid)
+- [Matthew Wolak](https://matthewwolak.github.io/)
+
+**Maxwell computing cluster**
+
+- Naveed Khan
+
+![](images/leverhulme.png)
+
+![](images/LOGO-ERC.jpg)
+
+<br>
+![](images/aberdeen.png)
+
+<br>
+
+![](images/UoS_logo.png)
+
+</div>
 
@@
 **Increased mate relatedness and inbreeding depression will cause optimal parental investment to increase**
+
+<span style="font-size: 14px;">
+Duthie, AB & JM Reid (2015) *PLoS One* [10:e0125140](https://bradduthie.github.io/Duthie%26Reid2015.pdf) [SI](https://bradduthie.github.io/Duthie%26Reid2015SI.pdf); Duthie, AB & JM Reid (2016) *Am.
+Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf) [A1](https://bradduthie.github.io/Duthie_Reid2016_AppendixA.pdf) [A2](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf) [SI](https://bradduthie.github.io/Duthie_Reid2016_SM.pdf); Duthie, AB et al.
+(2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf) [SI-1](https://bradduthie.github.io/DuthieEtAl2016_SI1.pdf) [SI-2](https://bradduthie.github.io/DuthieEtAl2016_SI2.pdf); Duthie, AB et al.
+(2018) *J.
+Evol.
+Biol.* [**31**:31-45](https://bradduthie.github.io/DuthieEtAl2017.pdf) [SI](https://bradduthie.github.io/DuthieEtAl2017_SI.pdf);  Duthie, AB et al.
+(2016) *Proc.
+R.
+Soc.
+B* [**282**:20161845](https://bradduthie.github.io/DuthieEtAl2016c.pdf) [SI](https://bradduthie.github.io/DuthieEtAl2016c_SI.pdf)
+</span>

### 2018-04-03 presentation/inbreeding.Rmd
Final changes before talk

--- 2018-04-02 presentation/inbreeding.Rmd
@@
 
-**Increased mate relatedness and inbreeding depression will cause optimal parental investment to increase**
+**Higher mate relatedness & inbreeding depression causes optimal parental investment to increase**
+
+<span style="font-size: 14px;">
+Duthie, AB & JM Reid (2015) *PLoS One* [10:e0125140](https://bradduthie.github.io/Duthie%26Reid2015.pdf) [SI](https://bradduthie.github.io/Duthie%26Reid2015SI.pdf) [[code]](https://github.com/bradduthie/Duthie_and_Reid_2015_Figs); Duthie, AB & JM Reid (2016) *Am.
+Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf) [A1](https://bradduthie.github.io/Duthie_Reid2016_AppendixA.pdf) [A2](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf) [SI](https://bradduthie.github.io/Duthie_Reid2016_SM.pdf) [[code]](https://github.com/bradduthie/Inbreeding); Duthie, AB et al.
+(2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf) [SI-1](https://bradduthie.github.io/DuthieEtAl2016_SI1.pdf) [SI-2](https://bradduthie.github.io/DuthieEtAl2016_SI2.pdf) [[code]](https://github.com/bradduthie/PolyInbreed); Duthie, AB et al.
+(2018) *J.
+Evol.
+Biol.* [**31**:31-45](https://bradduthie.github.io/DuthieEtAl2017.pdf) [SI](https://bradduthie.github.io/DuthieEtAl2017_SI.pdf) [[code]](https://github.com/bradduthie/pre_post_cop);  Duthie, AB et al.
+(2016) *Proc.
+R.
+Soc.
+B* [**282**:20161845](https://bradduthie.github.io/DuthieEtAl2016c.pdf) [SI](https://bradduthie.github.io/DuthieEtAl2016c_SI.pdf) [[code]](https://github.com/bradduthie/Inbreeding_Care); Reid, JM et al.
+(2015) *Evolution* [**70**:1512-1529](https://bradduthie.github.io/ReidEtAl2015c.pdf); Reid, JM et al.
+(2016) *Evolution* [**69**:2846-2861](https://bradduthie.github.io/ReidEtAl2015c.pdf); <br> Reid, JM et al.
+(2015) *J.
+Anim.
+Ecol.* [84:1029-1040](https://bradduthie.github.io/ReidEtAl2015b.pdf); Reid, JM et al.
+(2015) *Evolution* [69:59-74](https://bradduthie.github.io/ReidEtAl2015.pdf)
+</span>
